### 2021-02-09 evaluation/report-template.Rmd
add code for a new leaderboard

---
output:
  html_document
title: "EpiExpert Crowd-Forecasting Performance Board"
# toc: true
# toc_float: true
# toc_collapsed: true
# toc_depth: 3
---

```{r setup, include=FALSE}
library(scoringutils)
library(dplyr)
library(DT)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE)
```

<br>

This is our evaluation of forecasting models and individual forecasters who have contributed forecasts of Covid-19 case and death numbers in Germany and Poland. These forecasts were submitted to the 
[German and Polish Forecast Hub](https://github.com/KITmetricslab/covid19-forecast-hub-de)
each week.

The evaluations are our own and not authorised by the German Forecast Hub team. We cannot rule out mistakes 
and the analyses are subject to change.

If you have questions or want to give feedback, please create an issue on our 
[github repository](https://github.com/epiforecasts/covid.german.forecasts)

```{r load-data}
# load all data ----------------------------------------------------------------
root_dir <- here::here("crowd-forecast", "processed-forecast-data")
file_paths_forecast <- here::here(root_dir, list.files(root_dir))

prediction_data <- purrr::map_dfr(file_paths_forecast, 
                                  .f = function(x) {
                                    data <- data.table::fread(x) %>%
                                      dplyr::mutate(target_end_date = as.Date(target_end_date), 
                                                    submission_date = as.Date(submission_date), 
                                                    forecast_date = as.Date(forecast_date))
                                  }) %>%
  dplyr::mutate(target_type = ifelse(grepl("death", target), "death", "case")) %>%
  dplyr::rename(prediction = value) %>%
  dplyr::mutate(forecast_date = as.Date(submission_date)) %>%
  dplyr::rename(model = board_name) %>%
  dplyr::filter(type == "quantile", 
                location_name %in% c("Germany", "Poland")) %>%
  dplyr::select(location, location_name, forecast_date, quantile, prediction, model, target_end_date, horizon, target, target_type)

# filter forecasters such that only those are kept that have submitted forecasts
# in the last four weeks
keep_fc <- prediction_data %>%
  dplyr::filter(forecast_date > (Sys.Date() - 4 * 7)) %>%
  dplyr::pull(model) %>%
  unique()

prediction_data <- dplyr::filter(prediction_data, 
                                 model %in% keep_fc)

files <- list.files(here::here("data-raw"))
file_paths <- here::here("data-raw", files[grepl("weekly-incident", files)])
names(file_paths) <- c("case", "death")

truth_data <- purrr::map_dfr(file_paths, readr::read_csv, .id = "target_type") %>%
  dplyr::rename(true_value = value) %>%
  dplyr::mutate(target_end_date = as.Date(target_end_date)) %>%
  dplyr::arrange(location, target_type, target_end_date) %>%
  dplyr::filter(location_name %in% c("Germany", "Poland"))

data <- scoringutils::merge_pred_and_obs(prediction_data, truth_data, 
                                         join = "full")

```

<br>
<br>

# Forecaster ranking {.tabset}

Here is an overall ranking of all forecasters. The ranking is made according to relative skill. Relative skill is calculated by looking at all pairwise comparisons between forecasters in terms of the weighted interval score (WIS). See below for a more detailed explanation of the scoring metrics used.

```{r ranking, include = FALSE}
out <- NULL

tabtitle = "overall"
summarise_by = c("model")
filter_list = list()
out = c(out, knit_child(here::here("evaluation", "template-ranking-table.Rmd")))

tabtitle = "Cases"
summarise_by = c("model", "target_type")
filter_list = list('target_type == "case"')
out = c(out, knit_child(here::here("evaluation", "template-ranking-table.Rmd")),
        quiet = TRUE)

tabtitle = "Deaths"
summarise_by = c("model", "target_type")
filter_list = list('target_type == "death"')
out = c(out, knit_child(here::here("evaluation", "template-ranking-table.Rmd")),
        quiet = TRUE)

tabtitle = "Germany"
summarise_by = c("model", "location_name")
filter_list = list('location_name == "Germany"')
out = c(out, knit_child(here::here("evaluation", "template-ranking-table.Rmd")),
        quiet = TRUE)

tabtitle = "Poland"
summarise_by = c("model", "location_name")
filter_list = list('location_name == "Poland"')
out = c(out, knit_child(here::here("evaluation", "template-ranking-table.Rmd")),
        quiet = TRUE)

tabtitle = "overall by horizon"
summarise_by = c("model", "horizon")
filter_list = NULL
out = c(out, knit_child(here::here("evaluation", "template-ranking-table.Rmd")),
        quiet = TRUE)

tabtitle = "Detailed"
summarise_by = NULL
filter_list = NULL
out = c(out, knit_child(here::here("evaluation", "template-ranking-table.Rmd")),
        quiet = TRUE)

```

`r paste(knit(text = out), collapse = '\n\n')`

# {.unlisted .unnumbered}

**The following metrics are used:**

 - Relative skill is a metric based on the weighted interval score (WIS) that is using a 'pairwise comparison tournament'. All pairs of forecasters are compared against each other in terms of the weighted interval score. The mean score of both models based on the set of common targets for which both models have made a prediction are calculated to obtain mean score ratios. The relative skill is the geometric mean of these mean score ratios. Smaller values are better and a value smaller than one means that the model beats the average forecasting model. 
 - The weighted interval score is a proper scoring rule (meaning you can't cheat it) suited to scoring forecasts in an interval format. It has three components: sharpness, underprediction and overprediction. Sharpness is the width of your prediction interval. Over- and underprediction only come into play if the prediction interval does not cover the true value. They are the absolute value of the difference between the upper or lower bound of your prediction interval (depending on whether your forecast is too high or too low). 
 - coverage deviation is the average difference between nominal and empirical interval coverage. Say your 50 percent prediction interval covers only 20 percent of all true values, then your coverage deviation is 0.5 - 0.2 = -0.3. The coverage deviation value in the table is calculated by averaging over the coverage deviation calculated for all possible prediction intervals. If the value is negative you have covered less then you should. If it is positve, then your forecasts could be a little more confident. 
 - bias is a measure between -1 and 1 that expresses your tendency to underpredict (-1) or overpredict (1). In contrast to the over- and underprediction components of the WIS it is bound between -1 and 1 and cannot go to infinity. It is therefore less susceptible to outliers. 
 - aem is the absolute error of your median forecasts. A high aem means your median forecasts tend to be far away from the true values.

<br>

# Forecast visualisation {.tabset}

This is a visualisation of all forecasts made so far.

```{r forecast-vis, include = FALSE}

locations <- c("Germany", "Poland")
forecast_dates <- as.character(unique(data$forecast_date[!is.na(data$forecast_date)]))
target_types <- c("case", "death")

out <- NULL
out = c(out, knit_child(here::here("evaluation", "template-plot-forecasts.Rmd")))
```

`r paste(knit(text = out), collapse = '\n\n')`

<br>

# Performance over time

This table gives the rank of every forecaster among all forecasters for a given target and forecast date (1 is the best). Ranks are determined based on the weighted interval scores.

```{r ranking-over-time, include = FALSE}
out <- NULL
out = c(out, knit_child(here::here("evaluation", "template-ranking-over-time.Rmd")))
```

`r paste(knit(text = out), collapse = '\n\n')`

<br>

# Weighted Interval Score Decomposition

The weighted interval score can be decomposed into three parts: sharpness (the amount of uncertainty around the forecast), overprediction and underprediction. This visualisation gives an impression of the distribution between these three forms of penalties for the different forecasters.

```{r wis-components, include = FALSE}
out <- NULL
out = c(out, knit_child(here::here("evaluation", "template-wis-components.Rmd")))
```

`r paste(knit(text = out), collapse = '\n\n')`

<br>

# Models and available forecasts

The following graphic gives an overview of the forecasters and models analysed and the number of forecasts they contributed.

```{r show-avail-forecasts, results = 'asis'}
plot <- scoringutils::show_avail_forecasts(prediction_data,
                                           show_numbers = FALSE,
                                           summarise_by = c("forecast_date", "model", "horizon"),
                                           legend_position = "bottom")
print(plot)
```

Most of the 'models' are human forecasters, but some are not:

 - EpiExpert-ensemble is the ensemble that is formed as the mean of all human forecasts submitted
 - [EpiNow2](https://epiforecasts.io/EpiNow2/) is an exponential growth model that uses a time-varying Rt trajectory to predict latent infections, and then convolves these infections with estimated delays to observations, via a negative binomial model coupled with a day of the week effect. It makes limited assumptions and is not tuned to the specifities of Covid in Germany and Poland beyond epidemioligical details such as literature estimates of the generation time, incubation period and the population of each area. The method and underlying theory are under active development with more details available [here](https://epiforecasts.io/covid/methods.
 - EpiNow2-secondary is an EpiNow2 model that infers deaths from cases by convoluting case numbers with a delay distribution
 - Crowd-Rt-Forecast is an ensemble that is constructed by taking human crowd forecasts of Rt and calculating implied case numbers from that using EpiNow2

### 2021-02-09 evaluation/template-plot-forecasts.Rmd
add code for a new leaderboard

```{r prediction-plots, echo = FALSE, results='asis', fig.width = 10, fig.height=20}

for (forecast_date in forecast_dates) {
  cat(paste0("\n\n## ", forecast_date), "{.tabset}\n\n")
  for (target_type in target_types) {
    cat("\n\n###", target_type, "\n\n")

    filter_both <- list(paste0("target_type %in% '", target_type, "'"))
    filter_truth <- list(paste0("target_end_date > '", as.Date(forecast_date) - 7 * 10, "'"), 
                         paste0("target_end_date <= '", as.Date(forecast_date) + 7 * 4, "'"))
    filter_forecasts <- list(paste0("forecast_date == '", as.Date(forecast_date), "'"))

    plot <- scoringutils::plot_predictions(data,
                                           x = "target_end_date",
                                           filter_both = filter_both,
                                           filter_truth = filter_truth,
                                           filter_forecasts = filter_forecasts,
                                           facet_wrap_or_grid = "grid",
                                           facet_formula = model ~ location_name,
                                           allow_truth_without_pred = FALSE,
                                           scales = "free") +
      ggplot2::ggtitle(paste0("Predictions for incident ", target_type,  "s")) + 
      ggplot2::theme(legend.position = "bottom")

    print(plot)
  }
}

```

### 2021-02-09 evaluation/template-ranking-over-time.Rmd
add code for a new leaderboard

```{r ranking-time, results = 'asis', fig.width=10, fig.height=9}
scores <- scoringutils::eval_forecasts(data,
                                         summarise_by = c("model", 
                                                          "location_name", 
                                                          "target_type",
                                                          "forecast_date"), 
                                       compute_relative_skill = FALSE)

ranked_scores <- scores %>%
    dplyr::mutate(forecast_date = as.Date(forecast_date)) %>%
    dplyr::group_by(forecast_date, location_name, target_type) %>%
    dplyr::mutate(rank = rank(interval_score, ties.method = "average",
                              na.last = NA)) %>%
    dplyr::ungroup()

plot <- score_heatmap(ranked_scores, metric = "rank", 
                      x = "forecast_date",
                      facet_wrap_or_grid = "grid",
                      facet_formula = location_name ~ target_type) + 
  ggplot2::theme(legend.position = "bottom")

print(plot)

```

### 2021-02-09 evaluation/template-wis-components.Rmd
add code for a new leaderboard

```{r wis-component-plot, results = 'asis', fig.width=10}
scores <- scoringutils::eval_forecasts(data,
                                       summarise_by = c("model", "location_name", "target_type"), 
                                       compute_relative_skill = FALSE)
plot <- scoringutils::wis_components(scores, 
                                     facet_wrap_or_grid = "grid",
                                     relative_contributions = TRUE,
                                     facet_formula = . ~ target_type + location_name) + 
  ggplot2::coord_flip() + 
  ggplot2::theme(legend.position = "bottom")

print(plot)
```

### 2021-02-09 evaluation/update-new-report.R

@@ -1,0 +1,69 @@
+# packages ---------------------------------------------------------------------
+library(purrr)
+library(dplyr)
+library(here)
+library(readr)
+library(scoringutils)
+library(rmarkdown)
+library(data.table)
+
+# helper function to read in all past submissions from a model, bind them together
+# to one file and copy them into the crowd forecast app folder 
+# having them in one place allows to easily include other models in the 
+# crowd forecast report. Could in principle also do without copying
+load_and_copy_forecasts <- function(root_dir,
+                                    out_file_path,
+                                    new_board_name) {
+  folders <- list.files(root_dir)
+  files <- map(folders,
+               .f = function(folder_name) {
+                 files <- list.files(here(root_dir, folder_name))
+                 paste(here(root_dir, folder_name, files))
+               }) %>%
+    unlist()
+  
+  forecasts <- suppressMessages(map_dfr(files, read_csv) %>%
+                                  mutate(board_name = new_board_name,
+                                         submission_date = forecast_date,
+                                         horizon = as.numeric(gsub("([0-9]+).*$", "\\1", target))) %>%
+                                  filter(grepl("inc", target),
+                                         type == "quantile"))
+  fwrite(forecasts, out_file_path)
+}
+
+# read in the EpiExpert ensemble forecast and EpiNow2 models
+load_and_copy_forecasts(
+  root_dir = here("submissions", "crowd-forecasts"), 
+  out_file_path = here("crowd-forecast", "processed-forecast-data",
+                       "all-epiexpert-forecasts.csv"), 
+  new_board_name = "EpiExpert-ensemble"
+)
+
+# also read all EpiNow2 forecasts, give them a board_name 
+load_and_copy_forecasts(
+  root_dir = here("submissions", "rt-forecasts"), 
+  out_file_path = here("crowd-forecast", "processed-forecast-data", 
+                       "all-epinow2-forecasts.csv"), 
+  new_board_name = "EpiNow2"
+)
+
+# also read all EpiNow2 secondary forecasts, give them a board_name 
+load_and_copy_forecasts(
+  root_dir = here("submissions", "deaths-from-cases"), 
+  out_file_path = here("crowd-forecast", "processed-forecast-data", 
+                       "all-epinow2_secondary-forecasts.csv"), 
+  new_board_name = "EpiNow2_secondary"
+)
+
+# also read all EpiNow2 Rt crowd forecasts, give them a board_name 
[…]

### 2021-02-11 evaluation/report-template.Rmd
switch to new leaderboard

@@
 locations <- c("Germany", "Poland")
-forecast_dates <- as.character(unique(data$forecast_date[!is.na(data$forecast_date)]))
+forecast_dates <- rev(as.character(unique(data$forecast_date[!is.na(data$forecast_date)])))
 target_types <- c("case", "death")
@@
 
-This table gives the rank of every forecaster among all forecasters for a given target and forecast date (1 is the best). Ranks are determined based on the weighted interval scores.
+This table shows (100 - the forecaster percentile rank) among all forecasters for a given target and forecast date.
+What happens is basically this: Every forecaster gets assigned a rank (1 is the best and the worst equals the number of available forecasts for that date).
+This rank is then transformed to a scale from 1 to 100 such that 100 is best and 0 is worst.
+Ranks are determined based on the weighted interval scores.
 

### 2021-02-11 evaluation/template-plot-forecasts.Rmd
switch to new leaderboard

@@
-```{r prediction-plots, echo = FALSE, results='asis', fig.width = 10, fig.height=20}
+```{r prediction-plots, echo = FALSE, results='asis', fig.width = 10, fig.height=10}
 
 for (forecast_date in forecast_dates) {
-  cat(paste0("\n\n## ", forecast_date), "{.tabset}\n\n")
+  cat(paste0("\n\n## ", forecast_date, "{.tabset} \n\n"))
+  #, "{.tabset}\n\n")
+  # plot_df <- dplyr::left_join(tidyr::expand(data = data, target_type, true_value, location_name, model), 
+  #                             data)
+
+  for (location in locations) {
+    cat("\n\n###", location, "{.tabset} \n\n")
+
     for (target_type in target_types) {
-    cat("\n\n###", target_type, "\n\n")
+      cat("\n\n####", target_type, "\n\n")
 
-    filter_both <- list(paste0("target_type %in% '", target_type, "'"))
+      filter_both <- list(paste0("target_type %in% '", target_type, "'"), 
+                          paste0("location_name %in% '", location, "'"))
       filter_truth <- list(paste0("target_end_date > '", as.Date(forecast_date) - 7 * 10, "'"), 
@@
                                              filter_forecasts = filter_forecasts,
-                                           facet_wrap_or_grid = "grid",
-                                           facet_formula = model ~ location_name,
+                                             facet_formula = ~ model,
+                                             # facet_formula = model ~ target_type + location_name,
+                                             # facet_wrap_or_grid = "facet",
                                              allow_truth_without_pred = FALSE,
                                              scales = "free") + 
-      ggplot2::ggtitle(paste0("Predictions for incident ", target_type,  "s")) + 
-      ggplot2::theme(legend.position = "bottom")
+        # ggplot2::ggtitle(paste0("Predictions for incident ", target_type,  "s")) + 
+        ggplot2::theme(legend.position = "bottom", 
+                       strip.placement = "outside")
 
@@
   }
+}
 

### 2021-02-11 evaluation/template-ranking-over-time.Rmd
switch to new leaderboard

@@
-```{r ranking-time, results = 'asis', fig.width=10, fig.height=9}
+```{r ranking-time, results = 'asis', fig.width=12, fig.height=10}
 scores <- scoringutils::eval_forecasts(data,
@@
   dplyr::group_by(forecast_date, location_name, target_type) %>%
-    dplyr::mutate(rank = rank(interval_score, ties.method = "average",
-                              na.last = NA)) %>%
+  dplyr::mutate(num_forecasts = dplyr::n(), 
+                unstandardised_rank = rank(interval_score, ties.method = "average",
+                                           na.last = NA), 
+                rank = round((1 - (unstandardised_rank - 1) / (num_forecasts - 1)) * 100)) %>%
   dplyr::ungroup()
@@
                       facet_formula = location_name ~ target_type) + 
-  ggplot2::theme(legend.position = "bottom")
+  ggplot2::theme(legend.position = "bottom") +
+    ggplot2::scale_fill_gradient(high = "white", low = "coral")
 

### 2021-02-11 evaluation/report.R

@@ -4,7 +4,9 @@ library(dplyr)
 library(here)
 library(readr)
 library(scoringutils)
+library(rmarkdown)
 library(data.table)
+
 
 # helper function to read in all past submissions from a model, bind them together
 # to one file and copy them into the crowd forecast app folder 
@@ -15,18 +17,18 @@ load_and_copy_forecasts <- function(root_dir,
                                     new_board_name) {
   folders <- list.files(root_dir)
   files <- map(folders,
-  .f = function(folder_name) {
-    files <- list.files(here(root_dir, folder_name))
-    paste(here(root_dir, folder_name, files))
-    }) %>%
+               .f = function(folder_name) {
+                 files <- list.files(here(root_dir, folder_name))
+                 paste(here(root_dir, folder_name, files))
+               }) %>%
     unlist()
-
+  
   forecasts <- suppressMessages(map_dfr(files, read_csv) %>%
-    mutate(board_name = new_board_name,
-           submission_date = forecast_date,
-           horizon = as.numeric(gsub("([0-9]+).*$", "\\1", target))) %>%
-    filter(grepl("inc", target),
-                  type == "quantile"))
+                                  mutate(board_name = new_board_name,
+                                         submission_date = forecast_date,
+                                         horizon = as.numeric(gsub("([0-9]+).*$", "\\1", target))) %>%
+                                  filter(grepl("inc", target),
+                                         type == "quantile"))
   fwrite(forecasts, out_file_path)
 }
 
@@ -36,7 +38,7 @@ load_and_copy_forecasts(
   out_file_path = here("crowd-forecast", "processed-forecast-data",
                        "all-epiexpert-forecasts.csv"), 
   new_board_name = "EpiExpert-ensemble"
-  )
+)
 
 # also read all EpiNow2 forecasts, give them a board_name 
 load_and_copy_forecasts(
@@ -44,7 +46,7 @@ load_and_copy_forecasts(
   out_file_path = here("crowd-forecast", "processed-forecast-data", 
                        "all-epinow2-forecasts.csv"), 
   new_board_name = "EpiNow2"
-  )
+)
 
 # also read all EpiNow2 secondary forecasts, give them a board_name 
 load_and_copy_forecasts(
@@ -52,7 +54,7 @@ load_and_copy_forecasts(
   out_file_path = here("crowd-forecast", "processed-forecast-data", 
                        "all-epinow2_secondary-forecasts.csv"), 
[…]

### 2021-02-11 evaluation/update-new-report.R

@@ -1,69 +1,0 @@
-# packages ---------------------------------------------------------------------
-library(purrr)
-library(dplyr)
-library(here)
-library(readr)
-library(scoringutils)
-library(rmarkdown)
-library(data.table)
-
-# helper function to read in all past submissions from a model, bind them together
-# to one file and copy them into the crowd forecast app folder 
-# having them in one place allows to easily include other models in the 
-# crowd forecast report. Could in principle also do without copying
-load_and_copy_forecasts <- function(root_dir,
-                                    out_file_path,
-                                    new_board_name) {
-  folders <- list.files(root_dir)
-  files <- map(folders,
-               .f = function(folder_name) {
-                 files <- list.files(here(root_dir, folder_name))
-                 paste(here(root_dir, folder_name, files))
-               }) %>%
-    unlist()
-  
-  forecasts <- suppressMessages(map_dfr(files, read_csv) %>%
-                                  mutate(board_name = new_board_name,
-                                         submission_date = forecast_date,
-                                         horizon = as.numeric(gsub("([0-9]+).*$", "\\1", target))) %>%
-                                  filter(grepl("inc", target),
-                                         type == "quantile"))
-  fwrite(forecasts, out_file_path)
-}
-
-# read in the EpiExpert ensemble forecast and EpiNow2 models
-load_and_copy_forecasts(
-  root_dir = here("submissions", "crowd-forecasts"), 
-  out_file_path = here("crowd-forecast", "processed-forecast-data",
-                       "all-epiexpert-forecasts.csv"), 
-  new_board_name = "EpiExpert-ensemble"
-)
-
-# also read all EpiNow2 forecasts, give them a board_name 
-load_and_copy_forecasts(
-  root_dir = here("submissions", "rt-forecasts"), 
-  out_file_path = here("crowd-forecast", "processed-forecast-data", 
-                       "all-epinow2-forecasts.csv"), 
-  new_board_name = "EpiNow2"
-)
-
-# also read all EpiNow2 secondary forecasts, give them a board_name 
-load_and_copy_forecasts(
-  root_dir = here("submissions", "deaths-from-cases"), 
-  out_file_path = here("crowd-forecast", "processed-forecast-data", 
-                       "all-epinow2_secondary-forecasts.csv"), 
-  new_board_name = "EpiNow2_secondary"
-)
-
-# also read all EpiNow2 Rt crowd forecasts, give them a board_name 
[…]

### 2021-02-13 crowd-forecast/email-templates/email-template.Rmd
update performance board and add code to send emails

---
  output: 
    blastula::blastula_email
  title: "Crowd Forecast Updates"
  fig_caption: false
---

```{r echo=FALSE}

knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE)

library(here)
library(scoringutils)
library(dplyr)
library(data.table)
library(covid.german.forecasts)
library(kableExtra)
```

```{r load-data, echo=FALSE, message = FALSE, warning = FALSE}
# load all data ----------------------------------------------------------------
root_dir <- here::here("crowd-forecast", "processed-forecast-data")
file_paths_forecast <- here::here(root_dir, list.files(root_dir))

prediction_data <- purrr::map_dfr(file_paths_forecast, 
                                  .f = function(x) {
                                    data <- data.table::fread(x) %>%
                                      dplyr::mutate(target_end_date = as.Date(target_end_date), 
                                                    submission_date = as.Date(submission_date), 
                                                    forecast_date = as.Date(forecast_date))
                                  }) %>%
  dplyr::mutate(target_type = ifelse(grepl("death", target), "death", "case")) %>%
  dplyr::rename(prediction = value) %>%
  dplyr::mutate(forecast_date = as.Date(submission_date)) %>%
  dplyr::rename(model = board_name) %>%
  dplyr::filter(type == "quantile", 
                location_name %in% c("Germany", "Poland")) %>%
  dplyr::select(location, location_name, forecast_date, quantile, prediction, model, target_end_date, horizon, target, target_type)

# filter forecasters such that only those are kept that have submitted forecasts
# in the last four weeks
keep_fc <- prediction_data %>%
  dplyr::filter(forecast_date > (Sys.Date() - 4 * 7)) %>%
  dplyr::pull(model) %>%
  unique()

prediction_data <- dplyr::filter(prediction_data, 
                                 model %in% keep_fc)

files <- list.files(here::here("data-raw"))
file_paths <- here::here("data-raw", files[grepl("weekly-incident", files)])
names(file_paths) <- c("case", "death")

truth_data <- purrr::map_dfr(file_paths, readr::read_csv, .id = "target_type") %>%
  dplyr::rename(true_value = value) %>%
  dplyr::mutate(target_end_date = as.Date(target_end_date)) %>%
  dplyr::arrange(location, target_type, target_end_date) %>%
  dplyr::filter(location_name %in% c("Germany", "Poland"))

data <- scoringutils::merge_pred_and_obs(prediction_data, truth_data, 
                                         join = "full")

```

### Dear `r name`,

Good to have you as a forecaster! You're receiving this message because you gave us your email address when you registered for the [Epiforecasts Crowd Forecast App](https://cmmid-lshtm.shinyapps.io/crowd-forecast/).

It has been a long time, but finally we managed to get this email newsletter running! From now on you will receive a weekly email with

- announcements and other information
- a reminder to submit a forecast
- some information about last weeks forecast and your performance

If you don't want to receive future emails simply write me a quick message. We're working on a way that allows you to unsubscribe from within the app, but that is work in progress. Baby steps, but we're getting there.

If you want to lean more about this project, have a look at our [github repo](https://github.com/epiforecasts/covid.german.forecasts). If you want to learn more about the German and Polish Forecast Hub, where we submit the forecasts to, have a look [here](https://kitmetricslab.github.io/forecasthub/forecast).

<br>

### Reminder for the weekly forecasts

We **update our data every Saturday at 6.30pm CET**. You can then make a forecast until **2pm CET (1pm UK time) on Tuesday** using our [forecast app](https://cmmid-lshtm.shinyapps.io/crowd-forecast/). We would be very happy to have a forecast from you this week!

<br>

### Forecast and Performance overview

But now, let's have a look at last weeks forecasts and performance!

In the following we put together a short overview for you. You can find more detailed information on our performance board [here](https://epiforecasts.io/covid.german.forecasts).

*Here are the latest EpiExpert ensemble forecasts and next to them your own forecasts
if you have submitted any.*

```{r plot-forecasts, echo=FALSE, out.width="49%", fig.show="hold", fig.cap = "Plot of the forecasts"}

forecast_date <- covid.german.forecasts::latest_weekday(Sys.Date())

filter_truth <- list('target_end_date >= Sys.Date() - 14 * 7')
models <- c("anonymous_Human", "EpiExpert-ensemble")
filter_forecasts <- list("model %in% 'EpiExpert-ensemble'", 
                         paste0("forecast_date == '", forecast_date, "'"))

plot_predictions(data = data, 
                 x = "target_end_date",
                 filter_truth = filter_truth, 
                 filter_forecasts = filter_forecasts,
                 facet_formula = target_type ~ location_name, 
                 facet_wrap_or_grid = "grid") + 
  ggplot2::labs(x = "Date", title = "Ensemble Forecasts") + 
  ggplot2::theme(legend.position = "bottom")

forecast_date <- covid.german.forecasts::latest_weekday(Sys.Date())

filter_truth <- list('target_end_date >= Sys.Date() - 14 * 7')
filter_forecasts <- list(paste0("model %in% '", board_name, "'"), 
                         paste0("forecast_date == '", forecast_date, "'"))

p <- plot_predictions(data = data, 
                 x = "target_end_date",
                 filter_truth = filter_truth, 
                 filter_forecasts = filter_forecasts,
                 facet_formula = target_type ~ location_name, 
                 facet_wrap_or_grid = "grid") 
if (!is.null(p)) {
  p <- p + 
  ggplot2::labs(x = "Date", title = "Your Forecasts") + 
  ggplot2::theme(legend.position = "bottom")
  print(p)
}

```

<br>

*Here is the list with the current top 5 forecasters (based on the last 5 weeks): *

```{r rank-table, echo=FALSE, fig.align="center"}
cut_off <- covid.german.forecasts::latest_weekday(Sys.Date()) - 5 * 7
df <- data %>%
  filter(forecast_date >= cut_off)

table <- eval_forecasts(data, summarise_by = c("model"), 
                        compute_relative_skill = TRUE)

table %>%
    arrange(relative_skill) %>%
    dplyr::select(-scaled_rel_skill) %>%
    mutate_if(is.numeric, round, 2) %>%
    dplyr::rename(wis = interval_score,
                  underpred = underprediction,
                  overpred = overprediction,
                  cvrage_dev = coverage_deviation,
                  rel_skill = relative_skill) %>%
  select(model, rel_skill) %>%
  head(5) %>%
  knitr::kable(format = "html") %>% 
  kable_styling(bootstrap_options = "striped", full_width = F)

```

<br>

*And here is a plot with the rank by date and target of all active forecasters over time:*

```{r rank-over-time, echo=FALSE, fig.align = "center", fig.width=10, fig.height=8, out.width="80%", fig.cap = "Ranking over time"}
scores <- scoringutils::eval_forecasts(data,
                                         summarise_by = c("model", 
                                                          "location_name", 
                                                          "target_type",
                                                          "forecast_date"), 
                                       compute_relative_skill = FALSE)

ranked_scores <- scores %>%
  dplyr::mutate(forecast_date = as.Date(forecast_date)) %>%
  dplyr::group_by(forecast_date, location_name, target_type) %>%
  dplyr::mutate(num_forecasts = dplyr::n(), 
                rank = rank(interval_score, ties.method = "average",
                                           na.last = NA), 
                standard_rank = round((1 - (rank - 1) / (num_forecasts - 1)) * 100)) %>%
  dplyr::ungroup()

plot <- score_heatmap(ranked_scores, metric = "rank", 
                      x = "forecast_date",
                      facet_wrap_or_grid = "grid",
                      facet_formula = location_name ~ target_type) + 
  ggplot2::theme(legend.position = "bottom") +
    ggplot2::scale_fill_gradient(low = "white", high = "coral")

print(plot)
```

<br>

If you have any questions or feedback, please don't hesitate to reach out. You can drop us an email or submit an issue to our [github repo](https://github.com/epiforecasts/covid.german.forecasts)

Thank you very much for your support and participation. We very much appreciate it!

Best wishes,

Nikos for the Epiforecasts team

### 2021-02-13 evaluation/report-template.Rmd
update performance board and add code to send emails

@@
 ```{r setup, include=FALSE}
+library(covid.german.forecasts)
 library(scoringutils)
@@
 See below for a more detailed explanation of the scoring metrics used.
+'Overall' shows the complete ranking, 'latest' only spans the last 5-6 weeks of data.
+'Detailed' represents the full data set that you can download for your own analysis.
 
@@
 filter_list = list()
+out = c(out, knit_child(here::here("evaluation", "template-ranking-table.Rmd")))
+
+tabtitle = "latest"
+summarise_by = c("model")
+cut_off <- covid.german.forecasts::latest_weekday(Sys.Date()) - 5 * 7
+filter_list = list(paste0("forecast_date >= '", cut_off, "'"))
 out = c(out, knit_child(here::here("evaluation", "template-ranking-table.Rmd")))
@@
 
-# Performance over time
+# Performance over time {.tabset}
 
-This table shows (100 - the forecaster percentile rank) among all forecasters for a given target and forecast date.
+This table shows you either your rank among all forecasters or the standardised rank.
+The standardised rank is computed as (100 - the forecaster percentile rank) among all forecasters for a given target and forecast date.
 What happens is basically this: Every forecaster gets assigned a rank (1 is the best and the worst equals the number of available forecasts for that date).

### 2021-02-13 evaluation/template-ranking-over-time.Rmd
update performance board and add code to send emails

@@
   dplyr::mutate(num_forecasts = dplyr::n(), 
-                unstandardised_rank = rank(interval_score, ties.method = "average",
+                rank = rank(interval_score, ties.method = "average",
                                            na.last = NA), 
-                rank = round((1 - (unstandardised_rank - 1) / (num_forecasts - 1)) * 100)) %>%
+                standard_rank = round((1 - (rank - 1) / (num_forecasts - 1)) * 100)) %>%
   dplyr::ungroup()
 
+cat("\n\n ## model rank")
 plot <- score_heatmap(ranked_scores, metric = "rank", 
+                      x = "forecast_date",
+                      facet_wrap_or_grid = "grid",
+                      facet_formula = location_name ~ target_type) + 
+  ggplot2::theme(legend.position = "bottom") +
+    ggplot2::scale_fill_gradient(low = "white", high = "coral")
+
+print(plot)
+
+cat("\n\n ## standardised model rank")
+plot <- score_heatmap(ranked_scores, metric = "standard_rank", 
                       x = "forecast_date",

### 2021-02-13 crowd-forecast/send-emails.R

@@ -1,0 +1,58 @@
+library(here)
+library(blastula)
+library(googledrive)
+library(googlesheets4)
+library(covid.german.forecasts)
+library(data.table)
+
+# Google sheets authentification -----------------------------------------------
+options(gargle_oauth_cache = ".secrets")
+drive_auth(cache = ".secrets", email = "epiforecasts@gmail.com")
+gs4_auth(token = drive_token())
+
+spread_sheet <- "1nOy3BfHoIKCHD4dfOtJaz4QMxbuhmEvsWzsrSMx_grI"
+identification_sheet <- "1GJ5BNcN1UfAlZSkYwgr1-AxgsVA2wtwQ9bRwZ64ZXRQ"
+
+ids <- try_and_wait(read_sheet(ss = identification_sheet, sheet = "ids"))
+
+
+participant_data <- ids %>%
+  dplyr::filter(!is.na(email)) %>%
+  dplyr::select(name, username, email, forecaster_id, board_name) %>%
+  dplyr::mutate(name = ifelse(is.na(name), username, name))
+
+participant_data <- participant_data %>% 
+  dplyr::filter(name %in% c("Habakuk"))
+
+for (i in 1:nrow(participant_data)) {
+  
+  temp_data <- as.data.table(participant_data)[i]
+
+  name <- temp_data[["name"]]
+  board_name <- temp_data[["board_name"]]
+  mail_address <- temp_data[["email"]]
+  
+  # render email
+  email <- render_email(here("crowd-forecast", "email-templates", "email-template.Rmd"))
+  
+  # send email
+  smtp_send(email, to = mail_address, from = "epiforecasts@gmail.com", 
+            credentials = creds_key(id = "epiforecasts@gmail.com"), 
+            subject = paste("EpiForecasts Crowd Forecast Update -", Sys.Date()))
+}
+
+
+
+
+
+create_smtp_creds_key(
+  id = "epiforecasts@gmail.com",
+  user = "epiforecasts@gmail.com",
+  provider = "gmail",
+  overwrite = FALSE, 
+  use_ssl = TRUE
+)
+
+
+
+

### 2021-02-15 R/utils.R
fix calculation of weekly cases

@@ -18,25 +18,29 @@ check_dir <- function(dir) {
 #' @importFrom dplyr filter group_by count left_join mutate
 #' @importFrom tibble tibble
 #' @importFrom lubridate epiweek
+#' @importFrom tidyr unnest
 dates_to_epiweek <- function(df){
 
   seq <- tibble(date = unique(df$date),
                 epiweek = epiweek(date),
+                year = epiyear(date),
                  day = weekdays(date))
 
   epiweek_end_date <- seq %>%
     filter(day == "Saturday")
 
   epiweek_complete <- seq %>%
-    group_by(epiweek) %>%
+    group_by(epiweek, year) %>%
     count() %>%
     filter(n == 7) %>%
-    left_join(epiweek_end_date, by = "epiweek")
+    left_join(epiweek_end_date, by = c("epiweek", "year")) %>%
+    mutate(date = list(date - 0:6)) %>%
+    unnest(cols = c(date))
  
   df_dated <- df %>%
     mutate(epiweek = epiweek(date),
            epiweek_end = date %in% epiweek_end_date$date,
-           epiweek_full = epiweek %in% epiweek_complete$epiweek)
+           epiweek_full = date %in% epiweek_complete$date)
 
   return(df_dated)
 }

### 2021-02-15 evaluation/report-template.Rmd
update evaluation and app

@@
 library(scoringutils)
+library(ggplot2)
 library(dplyr)
@@
 
-# Performance over time {.tabset}
+# Performance and observations over time
+
+Here you can see a visualisation of forecaster scores together next to the true observed values:
+
+```{r forecast-and-scores, include = FALSE}
+out <- NULL
+out = c(out, knit_child(here::here("evaluation", "template-scores-and-truth-time.Rmd")))
+```
+
+`r paste(knit(text = out), collapse = '\n\n')`
+
+<br>
+
+# Ranks over time {.tabset}
 

### 2021-02-15 evaluation/template-ranking-over-time.Rmd
update evaluation and app

@@
 
-cat("\n\n ## model rank")
+cat("\n\n## model rank\n\n")
 plot <- score_heatmap(ranked_scores, metric = "rank", 
@@
 
-cat("\n\n ## standardised model rank")
+cat("\n\n## standardised model rank\n\n")
 plot <- score_heatmap(ranked_scores, metric = "standard_rank", 

### 2021-02-15 evaluation/template-scores-and-truth-time.Rmd
update evaluation and app

```{r scores-and-truth1, results = 'asis', fig.width=10, fig.height = 5}

library(ggplot2)
library(dplyr)
library(scoringutils)

scores <- eval_forecasts(data, 
                         summarise_by = c("model", "target_type", 
                                          "location_name", "forecast_date"), 
                         compute_relative_skill = FALSE)

p1 <- data %>%
  select(target_end_date, true_value, location_name, target_type) %>%
  filter(target_end_date > "2020-10-12", 
         !is.na(true_value)) %>%
  unique() %>%
  ggplot(aes(x = target_end_date, y = true_value)) + 
  geom_line() + 
  geom_point() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  theme(legend.position = "bottom") + 
  labs(y = "true observed values", x = "date", title = "Observed data")

cat("\n\n")
print(p1)
cat("\n\n")
```

```{r scores-and-truth2, results = 'asis', fig.width=10, fig.height = 7}

p2 <- scores %>%
  ggplot(aes(x = forecast_date, y = interval_score, colour = model)) + 
  geom_line() + 
  geom_point() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  theme(legend.position = "bottom") +
  labs(y = "weighted interval score", x = "date", title = "Forecaster Scores")

cat("\n\n")
print(p2)
cat("\n\n")
```

### 2021-02-15 crowd-forecast/email-templates/email-template.Rmd

@@
 
-```{r echo=FALSE}
+```{r echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-```{r plot-forecasts, echo=FALSE, out.width="49%", fig.show="hold", fig.cap = "Plot of the forecasts"}
+```{r plot-forecasts, echo=FALSE, out.width="49%", fig.show="hold"}
 
+if (weekdays(Sys.Date()) == "Monday") {
+  forecast_date <- covid.german.forecasts::latest_weekday(Sys.Date() - 7)
+} else {
   forecast_date <- covid.german.forecasts::latest_weekday(Sys.Date())
+}
 
 filter_truth <- list('target_end_date >= Sys.Date() - 14 * 7')
-models <- c("anonymous_Human", "EpiExpert-ensemble")
 filter_forecasts <- list("model %in% 'EpiExpert-ensemble'", 
@@
   ggplot2::theme(legend.position = "bottom")
-
-forecast_date <- covid.german.forecasts::latest_weekday(Sys.Date())
 
@@
 
-```{r rank-over-time, echo=FALSE, fig.align = "center", fig.width=10, fig.height=8, out.width="80%", fig.cap = "Ranking over time"}
+```{r rank-over-time, echo=FALSE, fig.align = "center", fig.width=10, fig.height=8, out.width="80%"}
 scores <- scoringutils::eval_forecasts(data,

### 2021-02-15 crowd-forecast/send-emails.R
server check

@@ -30,19 +30,24 @@ participant_data <- ids %>%
   dplyr::mutate(name = ifelse(is.na(name), username, name))
 
 # iterate over rows and send an email
-for (i in 1:nrow(participant_data)) {
-  
+for (i in seq_len(nrow(participant_data))) {
+
   temp_data <- as.data.table(participant_data)[i]
 
   name <- temp_data[["name"]]
   board_name <- temp_data[["board_name"]]
   mail_address <- temp_data[["email"]]
-  
+
   # render email
-  email <- render_email(here("crowd-forecast", "email-templates", "email-template.Rmd"))
-  
+  email <- render_email(
+    here("crowd-forecast", "email-templates", "email-template.Rmd")
+    )
+
   # send email
-  smtp_send(email, to = mail_address, from = "epiforecasts@gmail.com", 
-            credentials = creds_file(here(".secrets", "epiforecasts-email-creds")), 
-            subject = paste("EpiForecasts Crowd Forecast Update -", Sys.Date()))
+  smtp_send(
+    email,
+    to = mail_address, from = "epiforecasts@gmail.com",
+    credentials = creds_file(here(".secrets", "epiforecasts-email-creds")),
+    subject = paste("EpiForecasts Crowd Forecast Update -", Sys.Date())
+    )
 }

### 2021-02-15 crowd-forecast/send-emails.R
reformat

@@ -8,7 +8,7 @@ library(data.table)
 # set up email credential if not present
 if (!file.exists(here::here(".secrets", "epiforecasts-email-creds"))) {
   create_smtp_creds_file(
-    file = here(".secrets", "epiforecasts-email-creds"), 
+    file = here(".secrets", "epiforecasts-email-creds"),
     user = "epiforecasts@gmail.com",
     provider = "gmail"
   )

### 2021-02-15 crowd-forecast/update-submissions.R
allow server to clean up google forecast sheet

@@ -17,7 +17,6 @@ spread_sheet <- "1nOy3BfHoIKCHD4dfOtJaz4QMxbuhmEvsWzsrSMx_grI"
 identification_sheet <- "1GJ5BNcN1UfAlZSkYwgr1-AxgsVA2wtwQ9bRwZ64ZXRQ"
 
 # setup ------------------------------------------------------------------------
-# - 1 as this is usually updated on a Tuesday
 submission_date <- latest_weekday()
 median_ensemble <- FALSE
 # grid of quantiles to obtain / submit from forecasts
@@ -29,7 +28,7 @@ ids <- try_and_wait(read_sheet(ss = identification_sheet, sheet = "ids"))
 # load forecasts
 forecasts <- try_and_wait(read_sheet(ss = spread_sheet))
 
-delete_data <- FALSE
+delete_data <- TRUE
 if (delete_data) {
   # add forecasts to backup sheet
   try_and_wait(

### 2021-02-15 rt-crowd-forecast/extract-samples.R

@@ -28,7 +28,7 @@ median_ensemble <- FALSE
 ids <- try_and_wait(read_sheet(ss = identification_sheet, sheet = "ids"))
 forecasts <- try_and_wait(read_sheet(ss = spread_sheet))
 
-delete_data <- FALSE
+delete_data <- TRUE
 if (delete_data) {
   # add forecasts to backup sheet
   try_and_wait(sheet_append(ss = spread_sheet, sheet = "oldforecasts",

### 2021-02-16 crowd-forecast/send-emails.R
merge conflict / automated update

@@ -8,7 +8,7 @@ library(data.table)
 # set up email credential if not present
 if (!file.exists(here::here(".secrets", "epiforecasts-email-creds"))) {
   create_smtp_creds_file(
-    file = here(".secrets", "epiforecasts-email-creds"), 
+    file = here(".secrets", "epiforecasts-email-creds"),
     user = "epiforecasts@gmail.com",
     provider = "gmail"
   )
@@ -30,19 +30,24 @@ participant_data <- ids %>%
   dplyr::mutate(name = ifelse(is.na(name), username, name))
 
 # iterate over rows and send an email
-for (i in 1:nrow(participant_data)) {
-  
+for (i in seq_len(nrow(participant_data))) {
+
   temp_data <- as.data.table(participant_data)[i]
 
   name <- temp_data[["name"]]
   board_name <- temp_data[["board_name"]]
   mail_address <- temp_data[["email"]]
-  
+
   # render email
-  email <- render_email(here("crowd-forecast", "email-templates", "email-template.Rmd"))
-  
+  email <- render_email(
+    here("crowd-forecast", "email-templates", "email-template.Rmd")
+    )
+
   # send email
-  smtp_send(email, to = mail_address, from = "epiforecasts@gmail.com", 
-            credentials = creds_file(here(".secrets", "epiforecasts-email-creds")), 
-            subject = paste("EpiForecasts Crowd Forecast Update -", Sys.Date()))
+  smtp_send(
+    email,
+    to = mail_address, from = "epiforecasts@gmail.com",
+    credentials = creds_file(here(".secrets", "epiforecasts-email-creds")),
+    subject = paste("EpiForecasts Crowd Forecast Update -", Sys.Date())
+    )
 }

### 2021-02-16 crowd-forecast/update-submissions.R
update submission script and correct submission

@@ -216,7 +216,8 @@ forecast_cum <- forecast_inc %>%
   select(-last_value, -case, -target_type)
 
 forecast_submission <- bind_rows(forecast_inc, forecast_cum) %>%
-  mutate(forecast_date = submission_date)
+  mutate(forecast_date = submission_date) %>%
+  select(-target_type)
 
 # write submission files -------------------------------------------------------
 check_dir(here("submissions", "crowd-forecasts", submission_date))

### 2021-02-17 submissions/submit.sh
add automated submission script

@@ -1,0 +1,46 @@
+#!bin/bash
+
+#define date
+ForecastDate=$(date +'%Y-%m-%d')
+
+# Clone the hub repository if not already present
+#git clone --depth 1 https://github.com/KITmetricslab/covid19-forecast-hub-de
+
+# install GitHub CLI
+# https://cli.github.com/
+
+# Authenticate with GitHub
+# gh auth login
+
+# Update the hub repository
+cd ../covid19-forecast-hub-de
+git checkout master 
+git pull 
+# Switch to submission branch
+git checkout -b submission
+git merge -Xtheirs master
+
+# Move back into forecast repository
+cd ../covid.german.forecasts
+
+# Copy your forecast from local folder to submission folder
+cp -R -f "./submissions/rt-forecasts/$ForecastDate/." \
+      "../covid19-forecast-hub-de/data-processed/epiforecasts-EpiNow2/"
+cp -R -f "./submissions/deaths-from-cases/$ForecastDate/." \
+      "../covid19-forecast-hub-de/data-processed/epiforecasts-EpiNow2_secondary/"
+cp -R -f "./submissions/crowd-rt-forecasts/$ForecastDate/." \
+      "../covid19-forecast-hub-de/data-processed/epiforecasts-EpiExpert_Rt/"
+cp -R -f "./submissions/crowd-forecasts/$ForecastDate/." \
+      "../covid19-forecast-hub-de/data-processed/epiforecasts-EpiExpert/"
+
+# Commit submission to branch
+cd ../covid19-forecast-hub-de
+git add --all
+git commit -m "submission"
+
+# Create PR
+gh pr create --title "$ForecastDate - EpiForecast submission" --body "This is an automated submission."
+
+# Remove local submission branch 
+git checkout master
+git branch -d submission

### 2021-02-22 R/utils.R
update utils

@@ -34,7 +34,7 @@ dates_to_epiweek <- function(df){
     count() %>%
     filter(n == 7) %>%
     left_join(epiweek_end_date, by = c("epiweek", "year")) %>%
-    mutate(date = list(date - 0:6)) %>%
+    mutate(date = list(as.Date(date) - 0:6)) %>%
     unnest(cols = c(date))
  
   df_dated <- df %>%

### 2021-02-22 rt-crowd-forecast/extract-samples.R

@@ -177,7 +177,9 @@ forecast_samples_daily <- forecast_samples %>%
   mutate(value = na.approx(value))
 
 # save forecasts in quantile-format
-fwrite(forecast_samples_daily %>% mutate(submission_date = submission_date),
+fwrite(forecast_samples_daily %>% 
+         mutate(submission_date = submission_date, 
+                target_type = "case"),
        here("rt-crowd-forecast", "processed-forecast-data",
             paste0(submission_date, "-processed-forecasts.csv")))
 

### 2021-02-22 crowd-forecast/email-templates/email-template.Rmd
update email template

@@
 Good to have you as a forecaster!
+Here is this weeks reminder and an update about what has happened lately.
 You're receiving this message because you gave us your email address when you registered for the [Epiforecasts Crowd Forecast App](https://cmmid-lshtm.shinyapps.io/crowd-forecast/).
-
-It has been a long time, but finally we managed to get this email newsletter running! From now on you will receive a weekly email with
-
-- announcements and other information
-- a reminder to submit a forecast
-- some information about last weeks forecast and your performance
-
-If you don't want to receive future emails simply write me a quick message.
-We're working on a way that allows you to unsubscribe from within the app, but that is work in progress.
-Baby steps, but we're getting there.
 
@@
 
-If you have any questions or feedback, please don't hesitate to reach out. You can drop us an email or submit an issue to our [github repo](https://github.com/epiforecasts/covid.german.forecasts)
+### Quota issues
+
+One last thing.
+As you may have experienced, we sometimes experience issues when too many people try to log in at the same time.
+We are using Google drive to store and load the forecasts and are getting an error that says "Quoata exceeded".
+Usually, this shouldn't happen at our usage level.
+We made a Stackoverflow question about it [here](https://stackoverflow.com/questions/66186332/googlesheets-quota-limit-issues-possible-failure-to-use-api-key).
+In case you have thoughts on that or know people who might, please reach out!
+
+<br>
+
+If you have any further questions or feedback, please don't hesitate to reach out.
+You can drop us an email or submit an issue to our [github repo](https://github.com/epiforecasts/covid.german.forecasts)
 
@@
 Nikos for the Epiforecasts team
+
+<br>
+
+PS: If you don't want to receive future emails simply write me a quick message.
+We're working on a way that allows you to unsubscribe from within the app, but that is work in progress.
+Baby steps, but we're getting there.

### 2021-02-22 crowd-forecast/send-emails.R
create script to copy latest rt data into the app (#47)
* create script to copy latest rt data into the app

* update utils

* update email template

@@ -29,6 +29,9 @@ participant_data <- ids %>%
   dplyr::select(name, username, email, forecaster_id, board_name) %>%
   dplyr::mutate(name = ifelse(is.na(name), username, name))
 
+# update data (probably needs to happen only on local machine)
+source(here("data-raw", "update.R"))
+
 # iterate over rows and send an email
 for (i in seq_len(nrow(participant_data))) {
 

### 2021-02-22 rt-crowd-forecast/update-epinow-data.R

@@ -1,0 +1,20 @@
+# update-rt-data by copying it from the Rt folder
+library(here)
+library(covid.german.forecasts)
+locations <- c("Germany", "Poland")
+
+date <- latest_weekday(Sys.Date())
+
+for (location in locations) {
+
+  file_names <- c("summarised_estimates.rds", "estimate_samples.rds", 
+                  "model_fit.rds", "model_args.rds", "reported_cases.rds")
+  target_dir <- here("rt-crowd-forecast", "data-raw", "rt-epinow-data", 
+                     location)
+  check_dir(target_dir)
+  for (file_name in file_names) {
+    file.copy(from = here::here("rt-forecast", "data", "samples", "cases", 
+                                location, date, file_name), 
+              to = here(target_dir, file_name))
+  }
+}

### 2021-02-23 submissions/submit.sh
make submission be for tomorrow

@@ -1,7 +1,7 @@
 #!bin/bash
 
 #define date
-ForecastDate=$(date +'%Y-%m-%d')
+ForecastDate=$(date +'%Y-%m-%d' -d "yesterday")
 
 # Clone the hub repository if not already present
 #git clone --depth 1 https://github.com/KITmetricslab/covid19-forecast-hub-de

### 2021-02-23 submissions/submit.sh
end up back in folder

@@ -44,3 +44,4 @@ gh pr create --title "$ForecastDate - EpiForecast submission" --body "This is an
 # Remove local submission branch 
 git checkout master
 git branch -d submission
+cd ../covid.german.forecasts

### 2021-03-01 crowd-forecast/email-templates/email-template.Rmd
update email template

@@
 If you want to learn more about the German and Polish Forecast Hub, where we submit the forecasts to, have a look [here](https://kitmetricslab.github.io/forecasthub/forecast).
+
+<br>
+
+### The European Forecast Hub
+
+On March 8th, the [European Forecast Hub](https://covid19forecasthub.eu/) will launch.
+Our crowd forecast app will therefore be expanded to include a set of 32 countries.
+If you like you can stick to forecasting Germany and Poland, but more observations will be available.
+We'll send more detailed information around next week.
+
+<br>
+
+### Introduction video
+
+To help new forecasters get used to the user interface, we created a [short video](https://www.youtube.com/watch?v=NzZkNxXFgm8) that explains how to make a forecast. If you like, check it out.
 
@@
 
-### Quota issues
-
-One last thing.
-As you may have experienced, we sometimes experience issues when too many people try to log in at the same time.
-We are using Google drive to store and load the forecasts and are getting an error that says "Quoata exceeded".
-Usually, this shouldn't happen at our usage level.
-We made a Stackoverflow question about it [here](https://stackoverflow.com/questions/66186332/googlesheets-quota-limit-issues-possible-failure-to-use-api-key).
-In case you have thoughts on that or know people who might, please reach out!
-
-<br>
-
 If you have any further questions or feedback, please don't hesitate to reach out.
@@
 Baby steps, but we're getting there.
+
+PPS: We solved our quota issues. Thank you very much for your helpful comments last week!

### 2021-03-09 crowd-forecast/update-submissions.R
change script to work with new forecast app

@@ -44,6 +44,7 @@ if (delete_data) {
 
 # obtain raw and filtered forecasts, save raw forecasts-------------------------
 raw_forecasts <- forecasts %>%
+  dplyr::filter(location_name %in% c("Germany", "Poland")) %>%
   mutate(location = ifelse(location_name == "Germany", "GM", "PL"))
 
 # use only the latest forecast from a given forecaster

### 2021-03-09 crowd-forecast/update.sh
don't redeploy as this is handled by the ECDC repo

@@ -2,6 +2,3 @@
 
 # create crowd forecast app submission data
 Rscript crowd-forecast/update-submissions.R
-
-# Redeploy forecast app (to update submission date to next week)
-Rscript crowd-forecast/redeploy.R

### 2021-03-11 evaluation/report-template.Rmd
update report template

@@
 each week.
-
+Currently, we submit an unweighted mean ensemble to the Forecast Hub, but this will likely be changed in the future.
+We will transition to submitting forecasts to the [European Forecast Hub](https://github.com/epiforecasts/covid19-forecast-hub-europe) in the future.
 The evaluations are our own and not authorised by the German Forecast Hub team. We cannot rule out mistakes 
@@
 [github repository](https://github.com/epiforecasts/covid.german.forecasts)
+
+You can register to become a forecaster [here](https://cmmid-lshtm.shinyapps.io/crowd-forecast/).
 

### 2021-03-19 analysis/analysis.R
start set up for analysis for paper

@@ -1,0 +1,31 @@
+library(here)
+library(magrittr)
+library(stringr)
+library(data.table)
+
+# update data ------------------------------------------------------------------
+## update forecasts
+# trying to use 'here', but the problem is that there is a white space in my 
+# folder path and that therefore fails
+system(
+  paste(". analysis/update-forecasts.sh")
+)
+
+## update truth data 
+# not sure how we want to handle this - ideally we want to avoid dependencies 
+# on this repo / package for later reproducibiity?
+# for now I'm just loading it from file
+
+source(here("data-raw", "update.R"))
+
+
+# load forecasts ---------------------------------------------------------------
+file_paths <- get_file_paths()
+forecasts <- load_all_forecasts(file_paths)
+
+# load truth data --------------------------------------------------------------
+# problem here is that the truth data source changed in the middle. 
+# need to talk to Johannes about that
+truth <- load_all_truth()
+
+# score forecasts --------------------------------------------------------------

### 2021-03-19 analysis/analysis_utils.R

@@ -1,0 +1,56 @@
+# helper function to get the file paths to all forecasts made
+get_file_paths <- function(root_dir = here::here("analysis")) {
+  folders <- here::here(root_dir, list.files(root_dir))
+  folders <- folders[grepl("epiforecasts", folders)]
+  
+  file_paths <- purrr::map(folders, 
+                           .f = function(folder) {
+                             files <- list.files(folder)
+                             out <- here::here(folder, files)
+                             return(out)}) %>%
+    unlist()
+  file_paths <- file_paths[grepl(".csv", file_paths)]
+  return(file_paths)
+}
+
+
+# helper function to get model name from a file path
+get_model_name <- function(file_path) {
+  split <- str_split(a, pattern = "/")[[1]]
+  model <- split[length(split) - 1]
+  return(model)
+}
+
+# helper function to load forecasts
+# sorry for the mix of data.table and dplyr, will correct in the future
+load_all_forecasts <- function(file_paths) {
+  prediction_data <- purrr::map_dfr(file_paths, 
+                                    .f = function(file_path) {
+                                      data <- data.table::fread(file_path)
+                                      data[, `:=`(
+                                        target_end_date = as.Date(target_end_date), 
+                                        submission_date = as.Date(submission_date), 
+                                        forecast_date = as.Date(forecast_date), 
+                                        model = get_model_name(file_path)
+                                      )]
+                                      return(data)
+                                    }) %>%
+    dplyr::mutate(target_type = ifelse(grepl("death", target), "death", "case")) %>%
+    dplyr::rename(prediction = value) %>%
+    dplyr::mutate(forecast_date = as.Date(submission_date)) %>%
+    dplyr::filter(type == "quantile", 
+                  location_name %in% c("Germany", "Poland")) %>%
+    dplyr::select(location, location_name, forecast_date, quantile, prediction, model, target_end_date, target, target_type)
+  return(prediction_data)
+}
+
+
+# helper function to load all truth
+load_all_truth <- function() {
+  weekly_cases <- fread(here("data-raw", "weekly-incident-cases.csv"))
+  weekly_deaths <- fread(here("data-raw", "weekly-incident-deaths.csv"))
+  truth <- rbindlist(list(weekly_cases, weekly_deaths)) 
+  truth <- truth[location_name %in% c("Germany", "Poland")]
+  return(truth)
+}
+

### 2021-03-19 analysis/update-forecasts.sh

@@ -1,0 +1,14 @@
+#!bin/bash
+
+# this requires subversion to be installed
+
+## Move out one directory and clone (or pull) data repo
+cd analysis
+printf "Cloning forecasts folder\n"
+svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data-processed/epiforecasts-EpiExpert
+svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data-processed/epiforecasts-EpiExpert_Rt
+svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data-processed/epiforecasts-EpiNow2
+svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data-processed/epiforecasts-EpiNow2_secondary
+
+cd ..
+

### 2021-03-25 R/utils.R
correct calculation of weekly data

@@ -55,11 +55,15 @@ make_weekly <- function(inc) {
   inc_weekly <- inc %>%
     dates_to_epiweek() %>% 
     filter(epiweek_full == TRUE) %>% 
-    group_by(location, location_name, epiweek) %>%
+    mutate(year = year(date)) %>%
+    group_by(location, location_name, epiweek, year) %>%
     summarise(value = sum(value), 
               target_end_date = max(date),
               .groups = "drop_last") %>% 
-    ungroup()
+    ungroup() %>%
+    select(-year)
+  
+  return(inc_weekly)
 } 
 #' Make Data Cumulative
 #'

### 2021-03-25 analysis/analysis.Rmd
create analysis script and add data to package

---
title: "Analysis paper"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(covid.german.forecasts)
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)

# load and set up data
cases <- combined_data[target_type == "case" & 
                         as.Date(forecast_date) %in% forecast_dates$cases]
deaths <- combined_data[target_type == "death" & 
                         as.Date(forecast_date) %in% forecast_dates$deaths]
data <- rbindlist(list(cases, deaths))
```

## Figure with 2 week ahead forecasts and scores

-[x] create plots
-[x] combine plots into one
-[ ] shade dates that are excluded in scores
-[ ] maybe add density plot on the y axis
-[ ] maybe use mean scores ratio instead of WIS for plot with score over time

### Forecasts vs. truth data
```{r}
df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
                      grepl("2", target) & 
                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]

df <- dcast(df, ... ~ quantile, value.var = "prediction")

df %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
                 size = 1.5,
                 alpha = 0.4,
                 position = position_dodge(width = 3)) + 
  geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                 size = 1.5,
                 alpha = 0.8,
                 position = position_dodge(width = 3)) + 
  labs(y = "value", x = "date") + 
  geom_point() + 
  geom_line() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  theme(legend.position = "bottom")

ggsave(here("analysis", "plots", "truth-and-2-wk-ahead.png"))

```

### plot with interval score

```{r}
# plot with scores over time ---------------------------------------------------
scores_target_forecastdate <- eval_forecasts(
  data = data[grepl("2", target)],
  summarise_by = c("model", "location_name", "target_type", "forecast_date"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

scores_target_forecastdate  %>%
  ggplot(aes(x = as.Date(forecast_date), y = interval_score, colour = model)) + 
  geom_line() + 
  geom_point() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") +
  theme(legend.position = "bottom") +
  labs(y = "weighted interval score", x = "date")

ggsave(here("analysis", "plots", "wis-over-time.png"))
```

### same plot with mean score ratio
not sure why there is a whole in the plot...
```{r}
scores_target_forecastdate  %>%
  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, colour = model)) + 
  geom_line() + 
  geom_point() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") +
  theme(legend.position = "bottom") +
  labs(y = "mean score ratio", x = "date") 
```

---

## Summary table with scores
-[] create summary table for scores visualised before
-[] exclude Christmas period
-[] use whole period for cases
-[] use only period for which we have all models for deaths
-[] also add 50% and 90% coverage in table

```{r}
# create helper function to make table
make_score_table <- function(scores) {
  scores <- as.data.table(scores)
  setnames(scores, 
           old = c("target_type", "interval_score", "aem", "relative_skill", "scaled_rel_skill"), 
           new = c("target", "WIS", "absolute error", "rel. skill", "scaled rel. skill"))

  table <- scores[, .SD,  .SDcols = !c("coverage_deviation", "rel. skill")][
    order(target, `scaled rel. skill`)
  ] %>%
    kable(format = "markdown")
  return(table)
}
```

### 2 weeks ahead
```{r }
# scores by target type for 2 week ahead forecasts
eval_forecasts(
  data[grepl("2", target)], 
  summarise_by = c("model", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
) %>%
  make_score_table()
```

### 4 weeks ahead
```{r }
# scores by target type for 4 week ahead forecasts
eval_forecasts(
  data[grepl("4", target)], 
  summarise_by = c("model", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
) %>%
  make_score_table()

```

---

## Look more closely at relative skill

---

## Analyse distribution of model rankings
- one possibility would be to take the ridge plot from Cramer et al from the Hub

---

## Look at WIS contributions
```{r}
scores_target <- eval_forecasts(
  data[grepl("2", target)], 
  summarise_by = c("model", "target_type"), 
  compute_relative_skill = TRUE
)

wis_components(scores_target, 
               facet_formula = ~ target_type, 
               scales = "free_x", 
               x_text_angle = 0) + 
  theme(legend.position = "bottom") + 
  coord_flip() + 
  labs(title = "Components of the weighted interval score for 2-week ahead forecasts", 
       x = NULL)

ggsave(here("analysis", "plots", "wis-components.png"))
```

---

## Look more closely at interventions and change points

---

## Look at the effect of data exclusions
- look at first period, second period etc
```{r, eval = FALSE}
scores <- list()
# scores for restricted data set
scores_full <- eval_forecasts(data, 
                              summarise_by = c("model", "target_type", "target"), 
                              compute_relative_skill = TRUE, 
                              baseline = "Baseline")

scores[["full"]] <- 
  scores_full[, .(model, target_type, scaled_rel_skill, interval_score, target,
                  scenario = "full")]

res <- rbindlist(scores)
res %>%
  ggplot(aes(x = scenario, y = scaled_rel_skill, color = model, group = model)) + 
  geom_point() + 
  facet_wrap( ~ target, scales = "free", ncol = 2) + 
  theme(legend.position = "bottom")
```

---

## Look more closely at calibration and sharpness

### 2021-03-25 R/datasets.R

@@ -5,3 +5,27 @@
 ##' @name locations
 ##' @docType data
 "locations"
+
+##' Truth data used for the paper 
+##'
+##' @name locations
+##' @docType data
+"truth_data"
+
+##' Forecast data used for the paper 
+##'
+##' @name locations
+##' @docType data
+"prediction_data"
+
+##' Combined forecast and truth data used for the paper 
+##'
+##' @name locations
+##' @docType data
+"combined_data"
+
+##' Forecast dates used for the paper 
+##'
+##' @name locations
+##' @docType data
+"forecast_dates"

### 2021-03-25 R/utils.R

@@ -50,7 +50,7 @@ dates_to_epiweek <- function(df){
 #' `epiweek`.
 #' @return A data frame grouped by week.
 #' @export
-#' @importFrom dplyr filter group_by summarise ungroup
+#' @importFrom dplyr filter group_by summarise ungroup select
 make_weekly <- function(inc) {
   inc_weekly <- inc %>%
     dates_to_epiweek() %>% 

### 2021-03-25 analysis/analysis.R

@@ -1,31 +1,0 @@
-library(here)
-library(magrittr)
-library(stringr)
-library(data.table)
-
-# update data ------------------------------------------------------------------
-## update forecasts
-# trying to use 'here', but the problem is that there is a white space in my 
-# folder path and that therefore fails
-system(
-  paste(". analysis/update-forecasts.sh")
-)
-
-## update truth data 
-# not sure how we want to handle this - ideally we want to avoid dependencies 
-# on this repo / package for later reproducibiity?
-# for now I'm just loading it from file
-
-source(here("data-raw", "update.R"))
-
-
-# load forecasts ---------------------------------------------------------------
-file_paths <- get_file_paths()
-forecasts <- load_all_forecasts(file_paths)
-
-# load truth data --------------------------------------------------------------
-# problem here is that the truth data source changed in the middle. 
-# need to talk to Johannes about that
-truth <- load_all_truth()
-
-# score forecasts --------------------------------------------------------------

### 2021-03-25 analysis/analysis_utils.R

@@ -1,56 +1,0 @@
-# helper function to get the file paths to all forecasts made
-get_file_paths <- function(root_dir = here::here("analysis")) {
-  folders <- here::here(root_dir, list.files(root_dir))
-  folders <- folders[grepl("epiforecasts", folders)]
-  
-  file_paths <- purrr::map(folders, 
-                           .f = function(folder) {
-                             files <- list.files(folder)
-                             out <- here::here(folder, files)
-                             return(out)}) %>%
-    unlist()
-  file_paths <- file_paths[grepl(".csv", file_paths)]
-  return(file_paths)
-}
-
-
-# helper function to get model name from a file path
-get_model_name <- function(file_path) {
-  split <- str_split(a, pattern = "/")[[1]]
-  model <- split[length(split) - 1]
-  return(model)
-}
-
-# helper function to load forecasts
-# sorry for the mix of data.table and dplyr, will correct in the future
-load_all_forecasts <- function(file_paths) {
-  prediction_data <- purrr::map_dfr(file_paths, 
-                                    .f = function(file_path) {
-                                      data <- data.table::fread(file_path)
-                                      data[, `:=`(
-                                        target_end_date = as.Date(target_end_date), 
-                                        submission_date = as.Date(submission_date), 
-                                        forecast_date = as.Date(forecast_date), 
-                                        model = get_model_name(file_path)
-                                      )]
-                                      return(data)
-                                    }) %>%
-    dplyr::mutate(target_type = ifelse(grepl("death", target), "death", "case")) %>%
-    dplyr::rename(prediction = value) %>%
-    dplyr::mutate(forecast_date = as.Date(submission_date)) %>%
-    dplyr::filter(type == "quantile", 
-                  location_name %in% c("Germany", "Poland")) %>%
-    dplyr::select(location, location_name, forecast_date, quantile, prediction, model, target_end_date, target, target_type)
-  return(prediction_data)
-}
-
-
-# helper function to load all truth
-load_all_truth <- function() {
-  weekly_cases <- fread(here("data-raw", "weekly-incident-cases.csv"))
-  weekly_deaths <- fread(here("data-raw", "weekly-incident-deaths.csv"))
-  truth <- rbindlist(list(weekly_cases, weekly_deaths)) 
-  truth <- truth[location_name %in% c("Germany", "Poland")]
-  return(truth)
-}
-

### 2021-03-25 data-raw/paper.R

@@ -1,0 +1,140 @@
+library(here)
+library(magrittr)
+library(stringr)
+library(data.table)
+
+# ==============================================================================
+# ------------------------------ update data -----------------------------------
+# ==============================================================================
+
+# update forecast data from server ---------------------------------------------
+system(
+  paste(". data-raw/paper.sh")
+)
+
+# get the correct file paths to all forecasts ----------------------------------
+folders <- here::here("data-raw", list.files("data-raw"))
+folders <- folders[
+  !(grepl("\\.R", folders) | grepl(".sh", folders) | grepl(".csv", folders))
+]
+
+file_paths <- purrr::map(folders, 
+                         .f = function(folder) {
+                           files <- list.files(folder)
+                           out <- here::here(folder, files)
+                           return(out)}) %>%
+  unlist()
+file_paths <- file_paths[grepl(".csv", file_paths)]
+file_paths <- file_paths[!(
+  grepl("EpiExpert_Rt", file_paths) |
+    grepl("mean_ensemble", file_paths)
+)]
+  
+# load all past forecasts ------------------------------------------------------
+# ceate a helper function to get model name from a file path
+get_model_name <- function(file_path) {
+  split <- str_split(file_path, pattern = "/")[[1]]
+  model <- split[length(split) - 1]
+  return(model)
+}
+
+prediction_data <- purrr::map_dfr(file_paths, 
+                                  .f = function(file_path) {
+                                    data <- data.table::fread(file_path)
+                                    data[, `:=`(
+                                      target_end_date = as.Date(target_end_date), 
+                                      forecast_date = as.Date(forecast_date), 
+                                      model = get_model_name(file_path)
+                                    )]
+                                    return(data)
+                                  }) %>%
+  dplyr::mutate(target_type = ifelse(grepl("death", target), "death", "case")) %>%
+  dplyr::rename(prediction = value) %>%
+  dplyr::mutate(location_name = ifelse(location == "GM", "Germany", "Poland")) %>%
+  dplyr::filter(type == "quantile", 
+                grepl("inc", target),
+                location %in% c("GM", "PL")) %>%
[…]

### 2021-03-25 data-raw/paper.sh

@@ -3,12 +3,13 @@
 # this requires subversion to be installed
 
 ## Move out one directory and clone (or pull) data repo
-cd analysis
+cd data-raw
 printf "Cloning forecasts folder\n"
 svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data-processed/epiforecasts-EpiExpert
 svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data-processed/epiforecasts-EpiExpert_Rt
 svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data-processed/epiforecasts-EpiNow2
 svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data-processed/epiforecasts-EpiNow2_secondary
-
+svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data-processed/KITCOVIDhub-median_ensemble
+svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data-processed/KIT-baseline
 cd ..
 

### 2021-03-26 analysis/analysis.Rmd
add some interpretation

@@
 
--[x] create plots
--[x] combine plots into one
--[ ] shade dates that are excluded in scores
--[ ] maybe add density plot on the y axis
--[ ] maybe use mean scores ratio instead of WIS for plot with score over time
+- [x] create plots
+- [x] combine plots into one
+- [ ] shade dates that are excluded in scores
+- [ ] maybe add density plot on the y axis
+- [ ] maybe use mean scores ratio instead of WIS for plot with score over time
 
@@
 ```
+**What we learn from this plot**
+- severe overshooting for Renewal model
+- need to increase value for position dodge
+- reporting artifacts around christmas
 
@@
 
+**What we learn from this plot**
+- all models perform terribly around Christmas
+- the effect is much stronger in Germany than in Poland
+- these artifacts around Christmas hit Renewal hardest
+- in Germany scores are high in the beginning and the end, but it doesn't seem to correlate perfectly with the absolute value of the number of weekly cases
+
+**Further things we could look at**
+- maybe look at correlation between the number of weekly cases and the score?
+- look at scores for rising and falling parts of the epidemic separately
+
 ### same plot with mean score ratio
-not sure why there is a whole in the plot...
 ```{r}
@@
 ```
+
+**What we learn from this plot**
+- There is a gap in the plot where there shouldn't be a gap.
+Nikos is a bad Padawan and needs to look at this again.
+Need to think a minute about what we actually see here.
+It is not exactly the WIS of one model over the WIS of the baseline, but something slightly different
+- In German cases there are two spikes that I think would be interesting to look at
+- death forecasts look quite a lot messier than case forecasts
 

### 2021-03-27 analysis/analysis.Rmd
add analysis

@@
 ```
+
 **What we learn from this plot**
+
 - severe overshooting for Renewal model
@@
 **What we learn from this plot**
+
 - all models perform terribly around Christmas
@@
 **Further things we could look at**
+
 - maybe look at correlation between the number of weekly cases and the score?
@@
 **What we learn from this plot**
+
 - There is a gap in the plot where there shouldn't be a gap.
@@
 ## Summary table with scores
--[] create summary table for scores visualised before
--[] exclude Christmas period
--[] use whole period for cases
--[] use only period for which we have all models for deaths
--[] also add 50% and 90% coverage in table
+
+- [x] create summary table for scores visualised before
+- [x] exclude Christmas period
+- [x] use whole period for cases
+- [x] use only period for which we have all models for deaths
+- [] also add 50% and 90% coverage in table
 
@@
 ## Analyse distribution of model rankings
+
 - one possibility would be to take the ridge plot from Cramer et al from the Hub
+- decide on whether to use rank or standardised rank
+
+```{r }
+# scores by target type for 4 week ahead forecasts
+scores <- eval_forecasts(
+  data[grepl("2", target)], 
+  summarise_by = c("model", "target_type", "location_name", "forecast_date")
+)
+
+ranked_scores <- scores %>%
+  dplyr::mutate(forecast_date = as.Date(forecast_date)) %>%
+  dplyr::group_by(forecast_date, location_name, target_type) %>%
+  dplyr::mutate(num_forecasts = dplyr::n(), 
+                rank = rank(interval_score, ties.method = "average",
+                                           na.last = NA), 
+                standard_rank = round((1 - (rank - 1) / (num_forecasts - 1)) * 100)) %>%
+  dplyr::ungroup()
+
+library(ggridges)
+ggplot(ranked_scores, aes(y = model, x = standard_rank, 
+                          group = model, fill = model)) + 
+  ggridges::geom_density_ridges()
+
+ggplot(ranked_scores, aes(y = model, x = standard_rank, 
+                          group = model, fill = model)) + 
+  ggridges::geom_density_ridges() + 
+  facet_wrap(~ target_type)
+
+ggplot(ranked_scores, aes(y = model, x = standard_rank, 
+                          group = model, fill = model)) + 
+  ggridges::geom_density_ridges() + 
+  facet_wrap(location_name ~ target_type)
+
+```
+
+**what we learn from this plot**
+
+- bimodal distribution is interesting
+- maybe a ridge plot is not a good way of analysing this as values go from -50 to 150 on the plot? In reality, they should be between 0 and 100. Is there an option to adapt this?
 
@@
 ggsave(here("analysis", "plots", "wis-components.png"))
+
+scores_target <- eval_forecasts(
+  data[grepl("2", target)], 
+  summarise_by = c("model", "location_name", "target_type"), 
+  compute_relative_skill = TRUE
+)
+
+wis_components(scores_target, 
+               facet_formula = location_name ~ target_type, 
+               facet_wrap_or_grid = "grid",
+               scales = "free_x", 
+               x_text_angle = 0) + 
+  theme(legend.position = "bottom") + 
+  coord_flip() + 
+  labs(title = "Components of the weighted interval score for 2-week ahead forecasts", 
+       x = NULL)
+
 ```
@@
 
+- one interesting point Johannes brought up is that scoring predictions aroud change points may not even be such a good idea.
+The reason is that if you have a modle that always predicts a change point, theat model will do very well according to this metric even if it doesn't add much value.
+For example, we would expect the baseline model to do very well according to this change point metric
+
 ---
@@
 ## Look at the effect of data exclusions
+
 - look at first period, second period etc
@@
 ## Look more closely at calibration and sharpness
+
+```{r, eval = FALSE}
+scores_target <- eval_forecasts(
+  data[grepl("2", target)], 
+  summarise_by = c("model", "target_type", "range", "quantile"), 
+  compute_relative_skill = TRUE
+)
+
+interval_coverage(scores_target, 
+                  facet_formula = ~ target_type)
+
+scores_target <- eval_forecasts(
+  data[grepl("2", target)], 
+  summarise_by = c("model", "location_name", "target_type", "range", "quantile"), 
+  compute_relative_skill = TRUE
+)
+
+interval_coverage(scores_target, 
+                  facet_formula = location_name ~ target_type, 
+                  facet_wrap_or_grid = "grid")
+
+```
+
+**What we learn from this plot**
+
+- models are widely overconfident in their predictive ability
+- more overconfidence with cases than deaths

### 2021-03-30 R/utils.R
switch to grates package for calculating epiweeks

@@ -50,19 +50,19 @@ dates_to_epiweek <- function(df){
 #' `epiweek`.
 #' @return A data frame grouped by week.
 #' @export
+#' @importFrom grates as_yrwk
 #' @importFrom dplyr filter group_by summarise ungroup select
 make_weekly <- function(inc) {
   inc_weekly <- inc %>%
     dates_to_epiweek() %>% 
     filter(epiweek_full == TRUE) %>% 
-    mutate(year = year(date)) %>%
-    group_by(location, location_name, epiweek, year) %>%
+    mutate(year_week = as_yrwk(date, firstday = 7L)) %>%
+    group_by(location, location_name, year_week) %>%
     summarise(value = sum(value), 
               target_end_date = max(date),
               .groups = "drop_last") %>% 
     ungroup() %>%
-    select(-year)
-  
+    select(-year_week)
   return(inc_weekly)
 } 
 #' Make Data Cumulative

### 2021-03-31 analysis/analysis.Rmd
update analysis

@@
 library(ggplot2)
+library(ggridges)
+library(patchwork)
 
@@
 
-## Figure with 2 week ahead forecasts and scores
+## Visualisation of forecasts and scores
 
-- [x] create plots
-- [x] combine plots into one
-- [ ] shade dates that are excluded in scores
-- [ ] maybe add density plot on the y axis
-- [ ] maybe use mean scores ratio instead of WIS for plot with score over time
+This includes all available dates for the forecast plot.
+For the score plot it includes the full set for cases, and a restricted set for deaths.
+The restricted set is all forecasts from "2020-12-07" on to make sure that we have a full set of forecasts for deaths.
+The plot also includes the Christmas period - it probably makes sense to gray that out.
 
-### Forecasts vs. truth data
-```{r}
+```{r fig.height=10, fig.width=15}
 df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
@@
 
-df %>%
+truth_vs_forecast_2 <- df %>%
   ggplot(aes(y = true_value, x = target_end_date)) + 
@@
 
-ggsave(here("analysis", "plots", "truth-and-2-wk-ahead.png"))
+ggsave(here("analysis", "plots", "truth-and-2-wk-ahead.png"), 
+       plot = truth_vs_forecast_2)
 
@@
 
-**What we learn from this plot**
-
-- severe overshooting for Renewal model
-- need to increase value for position dodge
-- reporting artifacts around christmas
-
-### plot with interval score
-
-```{r}
+```{r fig.height=10, fig.width=15}
 # plot with scores over time ---------------------------------------------------
@@
 
-scores_target_forecastdate  %>%
+wis_scores_time_2 <- scores_target_forecastdate  %>%
   ggplot(aes(x = as.Date(forecast_date), y = interval_score, colour = model)) + 
@@
 
-ggsave(here("analysis", "plots", "wis-over-time.png"))
+ggsave(here("analysis", "plots", "wis-over-time.png"), 
+       plot = wis_scores_time_2)
 ```
 
-**What we learn from this plot**
-
-- all models perform terribly around Christmas
-- the effect is much stronger in Germany than in Poland
-- these artifacts around Christmas hit Renewal hardest
-- in Germany scores are high in the beginning and the end, but it doesn't seem to correlate perfectly with the absolute value of the number of weekly cases
-
-**Further things we could look at**
-
-- maybe look at correlation between the number of weekly cases and the score?
-- look at scores for rising and falling parts of the epidemic separately
-
+```{r}
 ### same plot with mean score ratio
-```{r}
-scores_target_forecastdate  %>%
+rel_skill_time_2 <- scores_target_forecastdate  %>%
   ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, colour = model)) + 
@@
   theme(legend.position = "bottom") +
-  labs(y = "mean score ratio", x = "date") 
+  labs(y = "relative skill", x = "date")
+
+ggsave(here("analysis", "plots", "wis-over-time.png"), 
+       plot = rel_skill_time_2)
+```
+
+```{r fig.height=10, fig.width=20}
+# glue two plots together
+truth_vs_forecast_2 + rel_skill_time_2
+ggsave(here("analysis", "plots", "figure-forecasts-2.png"))
 ```
@@
 
-- There is a gap in the plot where there shouldn't be a gap.
-Nikos is a bad Padawan and needs to look at this again.
-Need to think a minute about what we actually see here.
-It is not exactly the WIS of one model over the WIS of the baseline, but something slightly different
-- In German cases there are two spikes that I think would be interesting to look at
-- death forecasts look quite a lot messier than case forecasts
+- severe overshooting for Renewal model
+- all models are terrible around Christmas
+- the artifacts around Christmas hit Renewal hardest
+- the Christmas effect is much stronger in Germany than in Poland
+- need to increase value for position dodge
+- reporting artifacts around christmas
+
+**Todo**
+
+- [ ] shade dates that are excluded in "official scoring"
+- [ ] maybe add density plot with scores on the y axis
+- [ ] remove baseline from relative skill plot
+- [ ] make both plots nicer
+    - [ ] increase dodge
+    - [ ] change colour scheme
+    - [ ] adjust size of points
+- [ ] presumably change how plots are arranged
+- [ ] make final decision whether we want to have relative skill or just WIS on the other plot
+    - WIS would show the overall level (which scales with the number of cases)
+    - relative skill corrects for that in some sene, but also introduces other biases
+
+**Further things we could look at**
+
+- maybe look at correlation between the number of weekly cases and the score?
+- look at scores for rising and falling parts of the epidemic separately
+- maybe it would be interesting to look at other baseline models, e.g. "how hard is it to beat a model that just always continues the trend?"
 
@@
 
-- [x] create summary table for scores visualised before
-- [x] exclude Christmas period
-- [x] use whole period for cases
-- [x] use only period for which we have all models for deaths
-- [] also add 50% and 90% coverage in table
+This excludes all forecasts made on c("2020-12-21", "2020-12-28").
 
@@
 
+**To do**
+- [] also add 50% and 90% coverage in table
+- [] make a final decision (and document it somewhere) about how we want to exclude the Christmas period. Right now we are excluding forecast dates, but do not restrict target end dates in any way.
+
+**Further things to look at**
+- maybe think about some kind of stratification by time?
+
 ---
@@
 
+--> not sure what we wanted to do here.
+
 ---
@@
 ## Analyse distribution of model rankings
-
-- one possibility would be to take the ridge plot from Cramer et al from the Hub
-- decide on whether to use rank or standardised rank
 
@@
 
-library(ggridges)
-ggplot(ranked_scores, aes(y = model, x = standard_rank, 
+setDT(ranked_scores)
+df <- ranked_scores[, .(rank_count = .N), 
+                    by = c("target_type", "location_name", "model", "rank")][, 
+                      sum := .N, by = c("target_type", "location_name")
+                    ][, rank_count := rank_count / sum]
+
+ggplot(df, aes(y = model, x = rank, 
                           group = model, fill = model)) + 
-  ggridges::geom_density_ridges()
+  ggridges::geom_ridgeline(aes(height = rank_count)) + 
+  facet_wrap(location_name ~ target_type, scales = "free_x")
 
-ggplot(ranked_scores, aes(y = model, x = standard_rank, 
+ggplot(ranked_scores, aes(y = model, x = rank, 
                           group = model, fill = model)) + 
-  ggridges::geom_density_ridges() + 
-  facet_wrap(~ target_type)
-
-ggplot(ranked_scores, aes(y = model, x = standard_rank, 
-                          group = model, fill = model)) + 
-  ggridges::geom_density_ridges() + 
-  facet_wrap(location_name ~ target_type)
+  ggridges::geom_density_ridges(stat = "binline") + 
+  facet_wrap(location_name ~ target_type, scales = "free_x")
 
@@
 - bimodal distribution is interesting
-- maybe a ridge plot is not a good way of analysing this as values go from -50 to 150 on the plot? In reality, they should be between 0 and 100. Is there an option to adapt this?
+
+**To do**
+
+- [ ] make plot nicer
 
@@
                scales = "free_x", 
+               relative_contributions = TRUE,
                x_text_angle = 0) + 
@@
 scores_target <- eval_forecasts(
-  data[grepl("2", target)], 
+  data[grepl("4", target)], 
   summarise_by = c("model", "location_name", "target_type"), 
@@
 
-```{r, eval = FALSE}
+```{r, eval = TRUE}
 scores_target <- eval_forecasts(
@@
 - more overconfidence with cases than deaths
+
+## Further interesting things
+
+- look at crowd performance as a function of the number of forecasts --> maybe leave that to a second paper

### 2021-04-07 analysis/analysis.Rmd
expand analysis

@@
 # scores by target type for 2 week ahead forecasts
+
+coverage <- eval_forecasts(
+  data[grepl("2", target)], 
+  summarise_by = c("model", "target_type", "range"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)[range %in% c(50, 90), 
+                   .(model, target_type, coverage, range)] %>%
+  dcast(formula = ... ~ range, value.var = "coverage")
+setnames(coverage, old = c("50", "90"), new = c("coverage 50%", "coverage 90%"))
+
 eval_forecasts(
@@
 ) %>%
+  merge(coverage, all.x = TRUE, by = c("model", "target_type")) %>%
   make_score_table()
@@
 # scores by target type for 4 week ahead forecasts
+coverage <- eval_forecasts(
+  data[grepl("4", target)], 
+  summarise_by = c("model", "target_type", "range"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)[range %in% c(50, 90), 
+                   .(model, target_type, coverage, range)] %>%
+  dcast(formula = ... ~ range, value.var = "coverage")
+setnames(coverage, old = c("50", "90"), new = c("coverage 50%", "coverage 90%"))
+
 eval_forecasts(
@@
 **To do**
-- [] also add 50% and 90% coverage in table
 - [] make a final decision (and document it somewhere) about how we want to exclude the Christmas period. Right now we are excluding forecast dates, but do not restrict target end dates in any way.
@@
   summarise_by = c("model", "target_type", "range", "quantile"), 
-  compute_relative_skill = TRUE
+  compute_relative_skill = FALSE
 )
@@
   summarise_by = c("model", "location_name", "target_type", "range", "quantile"), 
-  compute_relative_skill = TRUE
+  compute_relative_skill = FALSE
 )
@@
 
+---
+
+## Look at scores based on log predictions and log truth values
+```{r, eval = TRUE}
+
+log_data <- copy(data)[, `:=`(true_value = log(true_value), 
+                              prediction = log(prediction))]
+
+```
+
+### Table 2 weeks ahead
+```{r, eval = TRUE}
+log_scores_target_2 <- eval_forecasts(
+  log_data[grepl("2", target)], 
+  summarise_by = c("model", "target_type"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)
+
+log_scores_target_2 %>%
+  make_score_table()
+```
+
+### Table 2 weeks ahead
+```{r, eval = TRUE}
+log_scores_target_4 <- eval_forecasts(
+  log_data[grepl("4", target)], 
+  summarise_by = c("model", "target_type"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)
+
+log_scores_target_4 %>%
+  make_score_table()
+```
+
+**What we learn**
+- results and rankings change if we look at scores of log values
+- this makes sense as presumably outliers aren't punished so harshly (inconsistent? models with large outliers are treated more leniently)
+
+### scores for logged values over time
+```{r, eval = TRUE}
+log_scores_target_forecast_date_2 <- eval_forecasts(
+  log_data[grepl("2", target)], 
+  summarise_by = c("model", "target_type", "forecast_date", "location_name"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)
+
+rel_skill_time_2 <- log_scores_target_forecast_date_2  %>%
+  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, colour = model)) + 
+  geom_line() + 
+  geom_point() + 
+  theme_light() + 
+  facet_grid(target_type ~ location_name, scales = "free") +
+  theme(legend.position = "bottom") +
+  labs(y = "relative skill", x = "date")
+
+rel_skill_time_2
+```
+
+**what we learn**
+- nothing? 
+- it looks slightly different, but similar and also similarly confusing
+
+### WIS components for scores of logged values
+```{r, eval = TRUE}
+log_scores_target_location_2 <- eval_forecasts(
+  log_data[grepl("2", target)], 
+  summarise_by = c("model", "target_type", "location_name"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)
+
+wis_components(log_scores_target_location_2, 
+               facet_formula = location_name ~ target_type, 
+               facet_wrap_or_grid = "grid",
+               scales = "free_x", 
+               x_text_angle = 0) + 
+  theme(legend.position = "bottom") + 
+  coord_flip() + 
+  labs(title = "Components of the weighted interval score for 2-week ahead forecasts", 
+       x = NULL) 
+```
+**what we learn**
+
+- the Renewal model benefits from this scoring scheme (except for Polish deaths)
+- interesting (confusing?) that the Baseline model is now the worst model for Polish cases. What's the mechanism behind that? is it just bad on average, but has no outliers?
+
+**To do**
+
+- at least for me (Nikos): get an intuition for what actually changes when you look at scores of logged predictions and what does it imply.
+What kind of model benefits from one or the other evaluation scheme?
+
+Thoughts about what changes when you look at logged predictions
+
+- models with outliers benefit
+- do models lose out that aren't great, but have no outliers?
+
 ## Further interesting things

### 2021-04-08 analysis/analysis.Rmd
update analysis with some todos

@@
 truth_vs_forecast_2 <- df %>%
-  ggplot(aes(y = true_value, x = target_end_date)) + 
+  ggplot(aes(y = true_value, x = target_end_date, colour = model, fill = model)) + 
   geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
@@
 rel_skill_time_2 <- scores_target_forecastdate  %>%
-  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, colour = model)) + 
+  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, fill = model, colour = model)) + 
   geom_line() + 
@@
 
-```{r fig.height=10, fig.width=20}
+```{r fig.height=16, fig.width=8}
 # glue two plots together
-truth_vs_forecast_2 + rel_skill_time_2
+truth_vs_forecast_2 / rel_skill_time_2 + 
+  plot_layout(guides = "collect") & theme(legend.position = 'bottom') 
 ggsave(here("analysis", "plots", "figure-forecasts-2.png"))
@@
 - [ ] make plot nicer
+- [ ] maybe make this with relative skill instead
+- [ ] finish this todo list
+- [ ] maybe a density plot instead of a ridge plot?
 
@@
 ```
+
+**Todo**
+
+- [ ] have the second plot stratified by epidemic period
 
@@
 - more overconfidence with cases than deaths
+
+**Todo**
+
+- maybe make tihs a PIT plot
+- stratify by period
 

### 2021-04-08 analysis/analysis.Rmd
first proposal to divide epidemic

@@
 data <- rbindlist(list(cases, deaths))
+```
+
+## Visualisation of data
+
+```{r fig.height=10, fig.width=15}
+df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
+                      grepl("2", target) & 
+                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]
+
+truth <- dcast(df, ... ~ quantile, value.var = "prediction")[
+  , .(location_name, target_end_date, target_type, true_value)] %>%
+  unique()
+
+truth <- truth[order(location_name, target_type, target_end_date)]
+
+epi_classification <- function(actual_value, first_diff, threshold = 0.05) {
+  out <- ifelse(first_diff > 0, "rising", "falling")
+  out[abs(first_diff) < 0.05 * actual_value] <- "stable"
+  return(out)
+}
+
+truth[, first_diff := c(NA, diff(true_value)), 
+      by = c("location_name", "target_type")]
+truth[, epi_class := epi_classification(true_value, first_diff), 
+      by = c("location_name", "target_type")]
+truth[, shift_date := shift(target_end_date, -1), 
+      by = c("location_name", "target_type")]
+# truth[, second_diff := c(NA, diff(first_diff)), 
+#       by = c("location_name", "target_type")]
+
+ggplot(truth, aes(x = target_end_date)) + 
+  geom_rect(aes(xmin = target_end_date, xmax = shift_date, ymin = -Inf, ymax = Inf, fill = factor(epi_class)), alpha = 0.2) +
+  geom_line(aes(y = true_value, color = "truth")) + 
+  geom_line(aes(y = first_diff, color = "first diff")) +
+  labs(y = "value", x = "date") + 
+  theme_light() + 
+  facet_grid(target_type ~ location_name, scales = "free") + 
+  theme(legend.position = "bottom")
+
 ```

### 2021-04-08 analysis/analysis.Rmd
add ridge plot for relative skill

--- 2021-04-08 analysis/analysis.Rmd
@@
 data <- rbindlist(list(cases, deaths))
+```
+
+## Visualisation of data
+
+```{r fig.height=10, fig.width=15}
+df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
+                      grepl("2", target) & 
+                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]
+
+truth <- dcast(df, ... ~ quantile, value.var = "prediction")[
+  , .(location_name, target_end_date, target_type, true_value)] %>%
+  unique()
+
+truth <- truth[order(location_name, target_type, target_end_date)]
+
+epi_classification <- function(actual_value, first_diff, threshold = 0.05) {
+  out <- ifelse(first_diff > 0, "rising", "falling")
+  out[abs(first_diff) < 0.05 * actual_value] <- "stable"
+  return(out)
+}
+
+truth[, first_diff := c(NA, diff(true_value)), 
+      by = c("location_name", "target_type")]
+truth[, epi_class := epi_classification(true_value, shift(first_diff, -1)), 
+      by = c("location_name", "target_type")]
+truth[, shift_date := shift(target_end_date, -1), 
+      by = c("location_name", "target_type")]
+# truth[, second_diff := c(NA, diff(first_diff)), 
+#       by = c("location_name", "target_type")]
+
+ggplot(truth, aes(x = target_end_date)) + 
+  geom_rect(aes(xmin = target_end_date, xmax = shift_date, ymin = -Inf, ymax = Inf, fill = epi_class), alpha = 0.2) +
+  geom_line(aes(y = true_value, color = "truth")) + 
+  geom_line(aes(y = first_diff, color = "first diff")) +
+  labs(y = "value", x = "date") + 
+  theme_light() + 
+  facet_grid(target_type ~ location_name, scales = "free") + 
+  theme(legend.position = "bottom")
+
 ```
@@
 **To do**
+
 - [] make a final decision (and document it somewhere) about how we want to exclude the Christmas period. Right now we are excluding forecast dates, but do not restrict target end dates in any way.
@@
   ggridges::geom_density_ridges(stat = "binline") + 
+  facet_wrap(location_name ~ target_type, scales = "free_x")
+
+```
+
+### Model rankings in terms of scaled relative skill
+
+```{r }
+# scores by target type for 4 week ahead forecasts
+scores <- eval_forecasts(
+  data[grepl("2", target)], 
+  summarise_by = c("model", "target_type", "location_name", "forecast_date"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)[model != "Baseline"]
+
+ggplot(scores, aes(y = model, x = (scaled_rel_skill), 
+                          group = model, fill = model)) + 
+  ggridges::geom_density_ridges() + 
+  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
   facet_wrap(location_name ~ target_type, scales = "free_x")

### 2021-04-19 submissions/submit.sh
change submission script so it can be run on a Monday

@@ -1,7 +1,7 @@
-#!bin/bash
+#!/bin/bash
 
 #define date
-ForecastDate=$(date +'%Y-%m-%d' -d "yesterday")
+ForecastDate=$(date +'%Y-%m-%d')
 
 # Clone the hub repository if not already present
 #git clone --depth 1 https://github.com/KITmetricslab/covid19-forecast-hub-de

### 2021-04-20 analysis/analysis.Rmd
update plots in report

--- 2021-04-08 analysis/analysis.Rmd
@@
 library(ggridges)
+library(RColorBrewer)
 library(patchwork)
@@
 data <- rbindlist(list(cases, deaths))
+data[, location_target := paste0(target_type, "s", " in ", location_name)]
+```
+
+## Visualisation of data
+
+```{r fig.height=10, fig.width=15}
+df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
+                      grepl("2", target) & 
+                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]
+
+truth <- dcast(df, ... ~ quantile, value.var = "prediction")[
+  , .(location_name, target_end_date, target_type, true_value)] %>%
+  unique()
+
+truth <- truth[order(target_type, location_name, target_end_date)]
+
+# classify epidemic according to whether, on a given forecast date, the two
+# weeks before that have seen monotonic rise, decline, or an unclear trend
+classify_epidemic <- function(data, cutoff = 0.05, growth_cutoff = 2) {
+  dt <- as.data.table(data)
+
+  # calculate differences and set differences smaller than 
+  # a certain cutoff to zero
+  dt[, diff_1 := c(NA, diff(true_value, 1)), 
+     by = c("location_name", "target_type")]
+  dt[abs(diff_1) < (cutoff * true_value), diff_1 := 0]
+  dt[, diff_prev := c(shift(diff_1, 1)), 
+     by = c("location_name", "target_type")]
+
+  # assign a label depending on observed differences
+  dt[, c("classification", "speed") := "unclear"]
+  dt[(diff_1 >= 0 & diff_prev >= 0), 
+     classification := "increasing"]
+  dt[(diff_1 <= 0 & diff_prev <= 0 ), 
+     classification := "decreasing"]
+  dt[(diff_1 == 0 & diff_prev == 0), 
+     classification := "unclear"]
+  dt[(classification == "increasing") & 
+       diff_1 > growth_cutoff * diff_prev, 
+     speed := "accelerating"]
+    dt[(classification == "increasing") & 
+         diff_1 < 1/growth_cutoff * diff_prev, 
+     speed := "decelerating"]
+  dt[(classification == "decreasing") & 
+       abs(diff_1) > growth_cutoff * abs(diff_prev), 
+     speed := "accelerating"]
+  dt[(classification == "decreasing") & 
+       abs(diff_1) < 1/growth_cutoff * abs(diff_prev), 
+     speed := "decelerating"]
+
+  dt[, c("diff_1", "diff_prev") := NULL]
+  return(dt)
+}
+
+dt <- classify_epidemic(truth)
+
+p <- ggplot(dt, aes(x = target_end_date)) +
+
+  geom_line(aes(y = true_value)) + 
+  geom_point(aes(y = true_value, color = classification)) + 
+  labs(y = "value", x = "date") + 
+  theme_light() + 
+  facet_grid(target_type ~ location_name, scales = "free") + 
+  theme(legend.position = "bottom")
+
+show_acceleration <- FALSE
+if (show_acceleration) {
+  p <- p + 
+    geom_rect(aes(xmin = target_end_date - 7,
+                  xmax = target_end_date,
+                  ymin = -Inf,
+                  ymax = Inf,
+                  fill = speed), alpha = 0.2) +
+    scale_fill_manual(values = c(
+      "accelerating" = "darkgrey",
+      "decelerating" = "lightgrey",
+      "unclear" = "white"
+    ))
+}
+
+print(p)
+
 ```
@@
                       quantile %in% c(0.025, 0.25, 0.75, 0.975)]
+df[, location_target := paste0(target_type, "s", " in ", location_name)]
 
@@
 
+df <- classify_epidemic(df)
+
 truth_vs_forecast_2 <- df %>%
-  ggplot(aes(y = true_value, x = target_end_date, colour = model, fill = model)) + 
-  geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
-                 size = 1.5,
-                 alpha = 0.4,
-                 position = position_dodge(width = 3)) + 
+  ggplot(aes(y = true_value, x = target_end_date)) + 
+  # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
+  #                size = 1.5,
+  #                alpha = 0.4,
+  #                position = position_dodge(width = 3)) + 
   geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                  size = 1.5,
-                 alpha = 0.8,
-                 position = position_dodge(width = 3)) + 
+                 alpha = 1,
+                 position = position_dodge(width = 6)) + 
   labs(y = "value", x = "date") + 
-  geom_point() + 
+  geom_point(aes(shape = classification)) + 
   geom_line() + 
   theme_light() + 
-  facet_grid(target_type ~ location_name, scales = "free") + 
-  theme(legend.position = "bottom")
+  facet_wrap(~ location_target, scales = "free", ncol = 1) + 
+  theme(legend.position = "bottom") + 
+  scale_color_brewer(palette = "Accent") + 
+  theme(panel.background = element_rect(fill = "#e1f0fe"))
 
@@
   data = data[grepl("2", target)],
-  summarise_by = c("model", "location_name", "target_type", "forecast_date"), 
+  summarise_by = c("model", "location_name", "target_type", "forecast_date", "location_target"), 
   compute_relative_skill = TRUE, 
@@
 )
+truth <- classify_epidemic(truth)
+tmp <- copy(truth)
+tmp[, target_end_date := as.Date(target_end_date) + 2]
+scores_target_forecastdate[, forecast_date := as.Date(forecast_date)]
+setnames(tmp, old = "target_end_date", new = "forecast_date")
+scores_target_forecastdate <- merge(
+  scores_target_forecastdate, tmp, 
+  by = c("location_name", "forecast_date", "target_type"), 
+  all.x = TRUE)
 
@@
   theme_light() + 
-  facet_grid(target_type ~ location_name, scales = "free") +
+  facet_wrap(~ location_target, scales = "free", ncol = 1) +
   theme(legend.position = "bottom") +
-  labs(y = "weighted interval score", x = "date")
+  labs(y = "weighted interval score", x = "date") +
+  scale_color_brewer(palette = "Accent") + 
+  theme(panel.background = element_rect(fill = "#e1f0fe"))
 
@@
   geom_line() + 
-  geom_point() + 
+  geom_point(aes(shape = classification)) + 
   theme_light() + 
-  facet_grid(target_type ~ location_name, scales = "free") +
+  facet_wrap( ~ location_target, ncol = 1, scales = "free") +
   theme(legend.position = "bottom") +
-  labs(y = "relative skill", x = "date")
+  labs(y = "relative skill", x = "date") +
+  scale_color_brewer(palette = "Accent") + 
+  theme(panel.background = element_rect(fill = "#e1f0fe"))
 
-ggsave(here("analysis", "plots", "wis-over-time.png"), 
+ggsave(here("analysis", "plots", "rel-skill-over-time.png"), 
        plot = rel_skill_time_2)
@@
 
-```{r fig.height=16, fig.width=8}
+```{r fig.height=10, fig.width=15}
 # glue two plots together
-truth_vs_forecast_2 / rel_skill_time_2 + 
-  plot_layout(guides = "collect") & theme(legend.position = 'bottom') 
+truth_vs_forecast_2 | rel_skill_time_2 + 
+  plot_layout(guides = "collect") & 
+  theme(legend.position = 'bottom') 
 ggsave(here("analysis", "plots", "figure-forecasts-2.png"))
@@
 
+### Model rankings in terms of scaled relative skill
+
+```{r }
+# scores by target type for 4 week ahead forecasts
+scores <- eval_forecasts(
+  data[grepl("2", target)], 
+  summarise_by = c("model", "target_type", "location_name", "forecast_date"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)[model != "Baseline"]
+
+ggplot(scores, aes(y = model, x = (scaled_rel_skill), 
+                          group = model, fill = model)) + 
+  ggridges::geom_density_ridges() + 
+  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
+  facet_wrap(location_name ~ target_type, scales = "free_x")
+
+```
+
 **what we learn from this plot**
@@
 
+palette = 
 **To do**

### 2021-04-22 analysis/analysis-graveyard.Rmd
update analysis

--- 2021-04-20 analysis/analysis.Rmd
@@
 ---
-title: "Analysis paper"
+title: "analysis-graveyard"
 output: html_document
@@
 library(patchwork)
-
-# load and set up data
-cases <- combined_data[target_type == "case" & 
-                         as.Date(forecast_date) %in% forecast_dates$cases]
-deaths <- combined_data[target_type == "death" & 
-                         as.Date(forecast_date) %in% forecast_dates$deaths]
-data <- rbindlist(list(cases, deaths))
-data[, location_target := paste0(target_type, "s", " in ", location_name)]
 ```
 
-## Visualisation of data
-
-```{r fig.height=10, fig.width=15}
-df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
-                      grepl("2", target) & 
-                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]
-
-truth <- dcast(df, ... ~ quantile, value.var = "prediction")[
-  , .(location_name, target_end_date, target_type, true_value)] %>%
-  unique()
-
-truth <- truth[order(target_type, location_name, target_end_date)]
-
+```{r helper-functions}
 # classify epidemic according to whether, on a given forecast date, the two
@@
 
+```
+
+**Further things we could look at**
+
+- maybe look at correlation between the number of weekly cases and the score?
+- maybe it would be interesting to look at other baseline models, e.g. "how hard is it to beat a model that just always continues the trend?"
+
+```{r fig.height=10, fig.width=15}
+df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
+                      grepl("2", target) & 
+                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]
+
+truth <- dcast(df, ... ~ quantile, value.var = "prediction")[
+  , .(location_name, target_end_date, target_type, true_value)] %>%
+  unique()
+
+truth <- truth[order(target_type, location_name, target_end_date)]
+
 dt <- classify_epidemic(truth)
@@
 
-## Visualisation of forecasts and scores
-
-This includes all available dates for the forecast plot.
-For the score plot it includes the full set for cases, and a restricted set for deaths.
-The restricted set is all forecasts from "2020-12-07" on to make sure that we have a full set of forecasts for deaths.
-The plot also includes the Christmas period - it probably makes sense to gray that out.
-
-```{r fig.height=10, fig.width=15}
-df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
-                      grepl("2", target) & 
-                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]
-df[, location_target := paste0(target_type, "s", " in ", location_name)]
-
-df <- dcast(df, ... ~ quantile, value.var = "prediction")
-
-df <- classify_epidemic(df)
-
-truth_vs_forecast_2 <- df %>%
-  ggplot(aes(y = true_value, x = target_end_date)) + 
-  # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
-  #                size = 1.5,
-  #                alpha = 0.4,
-  #                position = position_dodge(width = 3)) + 
-  geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
-                 size = 1.5,
-                 alpha = 1,
-                 position = position_dodge(width = 6)) + 
-  labs(y = "value", x = "date") + 
-  geom_point(aes(shape = classification)) + 
-  geom_line() + 
-  theme_light() + 
-  facet_wrap(~ location_target, scales = "free", ncol = 1) + 
-  theme(legend.position = "bottom") + 
-  scale_color_brewer(palette = "Accent") + 
-  theme(panel.background = element_rect(fill = "#e1f0fe"))
-
-ggsave(here("analysis", "plots", "truth-and-2-wk-ahead.png"), 
-       plot = truth_vs_forecast_2)
-
-```
-
-```{r fig.height=10, fig.width=15}
-# plot with scores over time ---------------------------------------------------
-scores_target_forecastdate <- eval_forecasts(
-  data = data[grepl("2", target)],
-  summarise_by = c("model", "location_name", "target_type", "forecast_date", "location_target"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-)
-truth <- classify_epidemic(truth)
-tmp <- copy(truth)
-tmp[, target_end_date := as.Date(target_end_date) + 2]
-scores_target_forecastdate[, forecast_date := as.Date(forecast_date)]
-setnames(tmp, old = "target_end_date", new = "forecast_date")
-scores_target_forecastdate <- merge(
-  scores_target_forecastdate, tmp, 
-  by = c("location_name", "forecast_date", "target_type"), 
-  all.x = TRUE)
+``` {r}
 
@@
        plot = wis_scores_time_2)
-```
-
-```{r}
-### same plot with mean score ratio
-rel_skill_time_2 <- scores_target_forecastdate  %>%
-  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, fill = model, colour = model)) + 
-  geom_line() + 
-  geom_point(aes(shape = classification)) + 
-  theme_light() + 
-  facet_wrap( ~ location_target, ncol = 1, scales = "free") +
-  theme(legend.position = "bottom") +
-  labs(y = "relative skill", x = "date") +
-  scale_color_brewer(palette = "Accent") + 
-  theme(panel.background = element_rect(fill = "#e1f0fe"))
-
-ggsave(here("analysis", "plots", "rel-skill-over-time.png"), 
-       plot = rel_skill_time_2)
-```
-
-```{r fig.height=10, fig.width=15}
-# glue two plots together
-truth_vs_forecast_2 | rel_skill_time_2 + 
-  plot_layout(guides = "collect") & 
-  theme(legend.position = 'bottom') 
-ggsave(here("analysis", "plots", "figure-forecasts-2.png"))
-```
-
-**What we learn from this plot**
-
-- severe overshooting for Renewal model
-- all models are terrible around Christmas
-- the artifacts around Christmas hit Renewal hardest
-- the Christmas effect is much stronger in Germany than in Poland
-- need to increase value for position dodge
-- reporting artifacts around christmas
-
-**Todo**
-
-- [ ] shade dates that are excluded in "official scoring"
-- [ ] maybe add density plot with scores on the y axis
-- [ ] remove baseline from relative skill plot
-- [ ] make both plots nicer
-    - [ ] increase dodge
-    - [ ] change colour scheme
-    - [ ] adjust size of points
-- [ ] presumably change how plots are arranged
-- [ ] make final decision whether we want to have relative skill or just WIS on the other plot
-    - WIS would show the overall level (which scales with the number of cases)
-    - relative skill corrects for that in some sene, but also introduces other biases
-
-**Further things we could look at**
-
-- maybe look at correlation between the number of weekly cases and the score?
-- look at scores for rising and falling parts of the epidemic separately
-- maybe it would be interesting to look at other baseline models, e.g. "how hard is it to beat a model that just always continues the trend?"
-
----
-
-## Summary table with scores
-
-This excludes all forecasts made on c("2020-12-21", "2020-12-28").
-
-```{r}
-# create helper function to make table
-make_score_table <- function(scores) {
-  scores <- as.data.table(scores)
-  setnames(scores, 
-           old = c("target_type", "interval_score", "aem", "relative_skill", "scaled_rel_skill"), 
-           new = c("target", "WIS", "absolute error", "rel. skill", "scaled rel. skill"))
-
-  table <- scores[, .SD,  .SDcols = !c("coverage_deviation", "rel. skill")][
-    order(target, `scaled rel. skill`)
-  ] %>%
-    kable(format = "markdown")
-  return(table)
-}
-```
-
-### 2 weeks ahead
-```{r }
-# scores by target type for 2 week ahead forecasts
-
-coverage <- eval_forecasts(
-  data[grepl("2", target)], 
-  summarise_by = c("model", "target_type", "range"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-)[range %in% c(50, 90), 
-                   .(model, target_type, coverage, range)] %>%
-  dcast(formula = ... ~ range, value.var = "coverage")
-setnames(coverage, old = c("50", "90"), new = c("coverage 50%", "coverage 90%"))
-
-eval_forecasts(
-  data[grepl("2", target)], 
-  summarise_by = c("model", "target_type"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-) %>%
-  merge(coverage, all.x = TRUE, by = c("model", "target_type")) %>%
-  make_score_table()
-```
-
-### 4 weeks ahead
-```{r }
-# scores by target type for 4 week ahead forecasts
-coverage <- eval_forecasts(
-  data[grepl("4", target)], 
-  summarise_by = c("model", "target_type", "range"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-)[range %in% c(50, 90), 
-                   .(model, target_type, coverage, range)] %>%
-  dcast(formula = ... ~ range, value.var = "coverage")
-setnames(coverage, old = c("50", "90"), new = c("coverage 50%", "coverage 90%"))
-
-eval_forecasts(
-  data[grepl("4", target)], 
-  summarise_by = c("model", "target_type"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-) %>%
-  merge(coverage, all.x = TRUE, by = c("model", "target_type")) %>%
-  make_score_table()
 
@@
 
-**To do**
-
-- [] make a final decision (and document it somewhere) about how we want to exclude the Christmas period. Right now we are excluding forecast dates, but do not restrict target end dates in any way.
-
-**Further things to look at**
-- maybe think about some kind of stratification by time?
-
----
-
-## Look more closely at relative skill
-
---> not sure what we wanted to do here.
-
----
-
-## Analyse distribution of model rankings
-
-```{r }
-# scores by target type for 4 week ahead forecasts
+``` {r}
 scores <- eval_forecasts(
@@
 
-### Model rankings in terms of scaled relative skill
-
-```{r }
-# scores by target type for 4 week ahead forecasts
-scores <- eval_forecasts(
-  data[grepl("2", target)], 
-  summarise_by = c("model", "target_type", "location_name", "forecast_date"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-)[model != "Baseline"]
-
-ggplot(scores, aes(y = model, x = (scaled_rel_skill), 
-                          group = model, fill = model)) + 
-  ggridges::geom_density_ridges() + 
-  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
-  facet_wrap(location_name ~ target_type, scales = "free_x")
-
-```
-
-**what we learn from this plot**
-
-- bimodal distribution is interesting
-
-palette = 
-**To do**
-
-- [ ] make plot nicer
-- [ ] maybe make this with relative skill instead
-- [ ] finish this todo list
-- [ ] maybe a density plot instead of a ridge plot?
-
----
-
-## Look at WIS contributions
 ```{r}
-scores_target <- eval_forecasts(
-  data[grepl("2", target)], 
-  summarise_by = c("model", "target_type"), 
-  compute_relative_skill = TRUE
-)
-
-wis_components(scores_target, 
-               facet_formula = ~ target_type, 
-               scales = "free_x", 
-               relative_contributions = TRUE,
-               x_text_angle = 0) + 
-  theme(legend.position = "bottom") + 
-  coord_flip() + 
-  labs(title = "Components of the weighted interval score for 2-week ahead forecasts", 
-       x = NULL)
-
-ggsave(here("analysis", "plots", "wis-components.png"))
-
 scores_target <- eval_forecasts(
@@
        x = NULL) 
-
 ```
 
-**Todo**
-
-- [ ] have the second plot stratified by epidemic period
-
----
-
-## Look more closely at interventions and change points
-
-- one interesting point Johannes brought up is that scoring predictions aroud change points may not even be such a good idea.
-The reason is that if you have a modle that always predicts a change point, theat model will do very well according to this metric even if it doesn't add much value.
-For example, we would expect the baseline model to do very well according to this change point metric
-
----
-
-## Look at the effect of data exclusions
-
-- look at first period, second period etc
-```{r, eval = FALSE}
-scores <- list()
-# scores for restricted data set
-scores_full <- eval_forecasts(data, 
-                              summarise_by = c("model", "target_type", "target"), 
-                              compute_relative_skill = TRUE, 
-                              baseline = "Baseline")
-
-scores[["full"]] <- 
-  scores_full[, .(model, target_type, scaled_rel_skill, interval_score, target,
-                  scenario = "full")]
-
-res <- rbindlist(scores)
-res %>%
-  ggplot(aes(x = scenario, y = scaled_rel_skill, color = model, group = model)) + 
-  geom_point() + 
-  facet_wrap( ~ target, scales = "free", ncol = 2) + 
-  theme(legend.position = "bottom")
-```
-
----
-
-## Look more closely at calibration and sharpness
-
-```{r, eval = TRUE}
-scores_target <- eval_forecasts(
-  data[grepl("2", target)], 
-  summarise_by = c("model", "target_type", "range", "quantile"), 
-  compute_relative_skill = FALSE
-)
-
-interval_coverage(scores_target, 
-                  facet_formula = ~ target_type)
-
+```{r}
 scores_target <- eval_forecasts(
@@
                   facet_wrap_or_grid = "grid")
-
 ```
 
-**What we learn from this plot**
-
-- models are widely overconfident in their predictive ability
-- more overconfidence with cases than deaths
-
-**Todo**
-
-- maybe make tihs a PIT plot
-- stratify by period
-
----
+## Part about scoring log predictions and log truth
 
@@
 - do models lose out that aren't great, but have no outliers?
-
-## Further interesting things
-
-- look at crowd performance as a function of the number of forecasts --> maybe leave that to a second paper

### 2021-04-22 analysis/analysis.Rmd
update analysis

--- 2021-04-08 analysis/analysis.Rmd
@@
 knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+options(knitr.kable.NA = '')
 library(covid.german.forecasts)
@@
 library(ggridges)
+library(RColorBrewer)
 library(patchwork)
+```
 
+```{r helper-functions}
+# classify epidemic according to whether, on a given forecast date, the two
+# weeks before that have seen monotonic rise, decline, or an unclear trend
+classify_epidemic <- function(data, cutoff = 0.05, growth_cutoff = 2) {
+  dt <- as.data.table(data)
+
+  # calculate differences and set differences smaller than 
+  # a certain cutoff to zero
+  dt[, diff_1 := c(NA, diff(true_value, 1)), 
+     by = c("location_name", "target_type")]
+  dt[abs(diff_1) < (cutoff * true_value), diff_1 := 0]
+  dt[, diff_prev := c(shift(diff_1, 1)), 
+     by = c("location_name", "target_type")]
+
+  # assign a label depending on observed differences
+  dt[, c("classification", "speed") := "unclear"]
+  dt[(diff_1 >= 0 & diff_prev >= 0), 
+     classification := "increasing"]
+  dt[(diff_1 <= 0 & diff_prev <= 0 ), 
+     classification := "decreasing"]
+  dt[(diff_1 == 0 & diff_prev == 0), 
+     classification := "unclear"]
+  dt[(classification == "increasing") & 
+       diff_1 > growth_cutoff * diff_prev, 
+     speed := "accelerating"]
+    dt[(classification == "increasing") & 
+         diff_1 < 1/growth_cutoff * diff_prev, 
+     speed := "decelerating"]
+  dt[(classification == "decreasing") & 
+       abs(diff_1) > growth_cutoff * abs(diff_prev), 
+     speed := "accelerating"]
+  dt[(classification == "decreasing") & 
+       abs(diff_1) < 1/growth_cutoff * abs(diff_prev), 
+     speed := "decelerating"]
+
+  dt[, c("diff_1", "diff_prev") := NULL]
+  return(dt)
+}
+
+```
+
+```{r}
 # load and set up data
@@
 data <- rbindlist(list(cases, deaths))
+data[, location_target := paste0(target_type, "s", " in ", location_name)]
+
+# obtain classification
+epitrend <- classify_epidemic(truth_data)
+epitrend[, forecast_date := target_end_date + 2]
+epitrend[, true_value := NULL]
+
 ```
 
-## Visualisation of data
+## Todo
 
-```{r fig.height=10, fig.width=15}
+- [ ] final decision on the Christmas period. Do we want to also exclude target end dates, or just forceast dates? Do we want to exclude the 2nd of January?
+- [ ] look more closely into the stratification: do we want the current thing or do we want something else that has the outcome in it as well?
+One thing I thought was have another category: inflection or no inflection and also score that?
+- [ ] Talk to Johannes about whether we want to score log forecasts and log truth values instead.
+I for now removed that part for the following reasons: I currently don't have a good feeling for what it does.
+I'm somewhat hesitant that establishing a completely new way of scoring forecasts could be beyond the scope of this paper.
+Very happy to switch to it entirely if we agree it is the better metric, but not sure we are at that point yet.
+
+## Visualisation of 2 week ahead forecasts and scores
+
+```{r truth-vs-forecasts, fig.height=10, fig.width=15}
+# load unfiltered combined data 
 df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
@@
                       quantile %in% c(0.025, 0.25, 0.75, 0.975)]
-
-truth <- dcast(df, ... ~ quantile, value.var = "prediction")[
-  , .(location_name, target_end_date, target_type, true_value)] %>%
-  unique()
-
-truth <- truth[order(location_name, target_type, target_end_date)]
-
-epi_classification <- function(actual_value, first_diff, threshold = 0.05) {
-  out <- ifelse(first_diff > 0, "rising", "falling")
-  out[abs(first_diff) < 0.05 * actual_value] <- "stable"
-  return(out)
-}
-
-truth[, first_diff := c(NA, diff(true_value)), 
-      by = c("location_name", "target_type")]
-truth[, epi_class := epi_classification(true_value, first_diff), 
-      by = c("location_name", "target_type")]
-truth[, shift_date := shift(target_end_date, -1), 
-      by = c("location_name", "target_type")]
-# truth[, second_diff := c(NA, diff(first_diff)), 
-#       by = c("location_name", "target_type")]
-
-ggplot(truth, aes(x = target_end_date)) + 
-  geom_rect(aes(xmin = target_end_date, xmax = shift_date, ymin = -Inf, ymax = Inf, fill = factor(epi_class)), alpha = 0.2) +
-  geom_line(aes(y = true_value, color = "truth")) + 
-  geom_line(aes(y = first_diff, color = "first diff")) +
-  labs(y = "value", x = "date") + 
-  theme_light() + 
-  facet_grid(target_type ~ location_name, scales = "free") + 
-  theme(legend.position = "bottom")
-
-```
-
-## Visualisation of forecasts and scores
-
-This includes all available dates for the forecast plot.
-For the score plot it includes the full set for cases, and a restricted set for deaths.
-The restricted set is all forecasts from "2020-12-07" on to make sure that we have a full set of forecasts for deaths.
-The plot also includes the Christmas period - it probably makes sense to gray that out.
-
-```{r fig.height=10, fig.width=15}
-df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
-                      grepl("2", target) & 
-                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]
+df[, location_target := paste0(target_type, "s", " in ", location_name)]
 
@@
 
+# add trend classification
+df <- merge(df, epitrend, 
+            by = c("target_end_date", "location_name", "target_type"))
+
 truth_vs_forecast_2 <- df %>%
-  ggplot(aes(y = true_value, x = target_end_date, colour = model, fill = model)) + 
-  geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
-                 size = 1.5,
-                 alpha = 0.4,
-                 position = position_dodge(width = 3)) + 
+  ggplot(aes(y = true_value, x = target_end_date)) + 
+  # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
+  #                size = 1.5,
+  #                alpha = 0.4,
+  #                position = position_dodge(width = 3)) + 
   geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                  size = 1.5,
-                 alpha = 0.8,
-                 position = position_dodge(width = 3)) + 
+                 alpha = 1,
+                 position = position_dodge(width = 6)) + 
   labs(y = "value", x = "date") + 
-  geom_point() + 
+  geom_point(aes(shape = classification)) + 
   geom_line() + 
+  geom_rect(aes(xmin = min(forecast_dates$christmas) + 14, # 2wk ahead forecast
+                xmax = max(forecast_dates$christmas) + 14,
+                ymin = -Inf,
+                ymax = Inf), fill = "lightgrey", alpha = 0.002) +
   theme_light() + 
-  facet_grid(target_type ~ location_name, scales = "free") + 
-  theme(legend.position = "bottom")
+  facet_wrap(~ location_target, scales = "free", ncol = 1) + 
+  theme(legend.position = "bottom") + 
+  scale_color_brewer(palette = "Accent") + 
+  theme(panel.background = element_rect(fill = "#e1f0fe"))
 
@@
 
-```{r fig.height=10, fig.width=15}
+```{r scores-over-time, fig.height=10, fig.width=15}
 # plot with scores over time ---------------------------------------------------
@@
 
-wis_scores_time_2 <- scores_target_forecastdate  %>%
-  ggplot(aes(x = as.Date(forecast_date), y = interval_score, colour = model)) + 
-  geom_line() + 
-  geom_point() + 
+# add epi trend classification
+scores_target_forecastdate[, forecast_date := as.Date(forecast_date)]
+scores_target_forecastdate <-  merge(scores_target_forecastdate, epitrend, 
+            by = c("forecast_date", "location_name", "target_type"))
+
+rel_skill_time_2 <- scores_target_forecastdate  %>%
+  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill)) + 
+  geom_line(aes(colour = model)) + 
+  geom_point(aes(shape = classification, colour = model)) + 
   theme_light() + 
-  facet_grid(target_type ~ location_name, scales = "free") +
+  facet_wrap( ~ location_target, ncol = 1, scales = "free_y") +
   theme(legend.position = "bottom") +
-  labs(y = "weighted interval score", x = "date")
+  labs(y = "relative skill", x = "date") + 
+  geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
+                xmax = max(forecast_dates$christmas) + 14,
+                ymin = 0,
+                ymax = Inf), fill = "lightgrey", alpha = 0.002) +
+  scale_color_brewer(palette = "Accent") + 
+  theme(panel.background = element_rect(fill = "#e1f0fe")) +
+  scale_y_log10()
 
-ggsave(here("analysis", "plots", "wis-over-time.png"), 
-       plot = wis_scores_time_2)
-```
-
-```{r}
-### same plot with mean score ratio
-rel_skill_time_2 <- scores_target_forecastdate  %>%
-  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, fill = model, colour = model)) + 
-  geom_line() + 
-  geom_point() + 
-  theme_light() + 
-  facet_grid(target_type ~ location_name, scales = "free") +
-  theme(legend.position = "bottom") +
-  labs(y = "relative skill", x = "date")
-
-ggsave(here("analysis", "plots", "wis-over-time.png"), 
+ggsave(here("analysis", "plots", "rel-skill-over-time.png"), 
        plot = rel_skill_time_2)
@@
 
-```{r fig.height=16, fig.width=8}
+```{r fig.height=10, fig.width=15}
 # glue two plots together
-truth_vs_forecast_2 / rel_skill_time_2 + 
-  plot_layout(guides = "collect") & theme(legend.position = 'bottom') 
+truth_vs_forecast_2 | rel_skill_time_2 + 
+  plot_layout(guides = "collect") & 
+  theme(legend.position = 'bottom') 
 ggsave(here("analysis", "plots", "figure-forecasts-2.png"))
 ```
+*Figure 1.
+Left: Visualisation of 2 week ahead forecasts against the true observed values.
+The shape indicates whether there has been a monotonic increase or decrease over the last two weeks, or an unclear trend.
+Forecasts made during the Christmas period (from 2020-12-19 until 2021-01-02) are grayed out.
+Right: Corresponding scaled relative skill scores for the forecasts shown on the left.
+Scaled relative skill scores can be thought of as 'improvement over the baseline model' (see Methods for details).*
 
@@
 - the Christmas effect is much stronger in Germany than in Poland
-- need to increase value for position dodge
-- reporting artifacts around christmas
 
 **Todo**
-
-- [ ] shade dates that are excluded in "official scoring"
-- [ ] maybe add density plot with scores on the y axis
-- [ ] remove baseline from relative skill plot
-- [ ] make both plots nicer
-    - [ ] increase dodge
-    - [ ] change colour scheme
-    - [ ] adjust size of points
-- [ ] presumably change how plots are arranged
-- [ ] make final decision whether we want to have relative skill or just WIS on the other plot
-    - WIS would show the overall level (which scales with the number of cases)
-    - relative skill corrects for that in some sene, but also introduces other biases
-
-**Further things we could look at**
-
-- maybe look at correlation between the number of weekly cases and the score?
-- look at scores for rising and falling parts of the epidemic separately
-- maybe it would be interesting to look at other baseline models, e.g. "how hard is it to beat a model that just always continues the trend?"
+- [ ] maybe remove baseline from relative skill plot
+- [ ] maybe rearrange plots
+- [ ] make plots nicer (legend, maybe point size on the left / remove either points or lines)
 
@@
 ## Summary table with scores
-
-This excludes all forecasts made on c("2020-12-21", "2020-12-28").
 
@@
   setnames(scores, 
-           old = c("target_type", "interval_score", "aem", "relative_skill", "scaled_rel_skill"), 
-           new = c("target", "WIS", "absolute error", "rel. skill", "scaled rel. skill"))
+           old = c("model", "target_type", "interval_score", "aem", 
+                   "relative_skill", "scaled_rel_skill", "sharpness", 
+                   "underprediction", "overprediction", "bias", 
+                   "50", "90"), 
+           new = c("Model", "Target", "WIS", "Abs. error", 
+                   "rel. skill", "Skill", "Sharpness", 
+                   "Underpred.", "Overpred.", "Bias", 
+                   "50%-Cov.", "90%-Cov."))
 
-  table <- scores[, .SD,  .SDcols = !c("coverage_deviation", "rel. skill")][
-    order(target, `scaled rel. skill`)
-  ] %>%
-    kable(format = "markdown")
+  scores <- scores[, lapply(.SD, FUN = function(x) {
+    if (is.numeric(x)) {
+      return(round(signif(x, 3), 2))
+    } else {
+      return(x)
+    }
+  })]
+
+  scores <- scores[, .SD,  .SDcols = !c("coverage_deviation", "rel. skill")][
+    order(Target, `Skill`)
+  ]
+
+  setcolorder(scores, 
+              neworder = c("Model", "Target", "Skill"))
+
+  # add an empty line to data.frame to separate deaths and cases
+  table <- 
+    rbindlist(list(
+    scores[1:4], 
+    as.list(rep(NA, ncol(scores))), 
+    scores[5:9]
+  )) %>%
+    kable(format = "markdown") %>%
+    kable_styling(bootstrap_options = "striped")
   return(table)
@@
   dcast(formula = ... ~ range, value.var = "coverage")
-setnames(coverage, old = c("50", "90"), new = c("coverage 50%", "coverage 90%"))
 
@@
 
-### 4 weeks ahead
-```{r }
+*Table 1: Scores for 2 week ahead forecasts (excluding the 21st and 28th of December 2020, cut to three significant digits and rounded).
+Skill is the scaled relative skill, a measure of relative performance with respect to the baseline model.
+Sharpness, overprediction and underprediction together some up to the weighted interval score (WIS).
+Bias (between -1 and 1) represents the general average tendency of a model to over- or underpredict.
+50% and 90%-coverage are the percentage of observed values that fell within the 50% and 90% prediction intervals of a model.*
+
+---
+
+## Analyse distribution of scores
+
+```{r}
 # scores by target type for 4 week ahead forecasts
-coverage <- eval_forecasts(
-  data[grepl("4", target)], 
-  summarise_by = c("model", "target_type", "range"), 
+scores <- eval_forecasts(
+  data[grepl("2", target)], 
+  summarise_by = c("model", "target_type", "location_name", "forecast_date", 
+                   "location_target"), 
   compute_relative_skill = TRUE, 
   baseline = "Baseline"
-)[range %in% c(50, 90), 
-                   .(model, target_type, coverage, range)] %>%
-  dcast(formula = ... ~ range, value.var = "coverage")
-setnames(coverage, old = c("50", "90"), new = c("coverage 50%", "coverage 90%"))
+)[model != "Baseline"]
 
-eval_forecasts(
-  data[grepl("4", target)], 
-  summarise_by = c("model", "target_type"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-) %>%
-  merge(coverage, all.x = TRUE, by = c("model", "target_type")) %>%
-  make_score_table()
+scores[, forecast_date := as.Date(forecast_date)]
+scores <-  merge(scores, epitrend, 
+            by = c("forecast_date", "location_name", "target_type"))
 
@@
 
-**To do**
-- [] make a final decision (and document it somewhere) about how we want to exclude the Christmas period. Right now we are excluding forecast dates, but do not restrict target end dates in any way.
+```{r}
+p <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
+                          group = model, fill = model)) + 
+  ggridges::geom_density_ridges() + 
+  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
+  scale_fill_brewer(palette = "Accent") + 
+  theme(panel.background = element_rect(fill = "#e1f0fe")) +
+  facet_wrap( ~ location_target) + 
+  theme(legend.position = "bottom") + 
+  labs(y = "Scaled relative skill") + 
+  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
+                limits = c(0.015, 50))
+```
 
-**Further things to look at**
-- maybe think about some kind of stratification by time?
+```{r}
+# scores for different phases of the epidemic
+scores[, target_phase := paste0(target_type, "s - ", classification, " phase")]
+p_phases <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
+                          group = model, fill = model)) + 
+  ggridges::geom_density_ridges() + 
+  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
+  scale_fill_brewer(palette = "Accent") + 
+  theme(panel.background = element_rect(fill = "#e1f0fe")) +
+  facet_wrap( ~ target_phase) + 
+  theme(legend.position = "bottom") + 
+  labs(y = "Scaled relative skill") + 
+  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
+                limits = c(0.015, 50))
+```
+
+```{r fig.height=10, fig.width=15}
+
+p / p_phases + 
+  plot_layout(guides = "collect") & 
+  theme(legend.position = 'bottom')
+
+```
+
+*Figure 2.
+Top: Distribution of the scaled relative skill scores for the different model and forecast targets.
+The vertical black line represents the baseline model.
+Models beat the baseline more easily for death forecasts.
+The renewal model had by far the most variance in terms of its performance, while the crowd forecasting model seems most consistent.
+Bottom: Distribution of scaled relative skill in different phases of the epidemic.
+The epidemic was classified as 'increasing', if the forecast point and the two data points before form a monotonically rising line, 'decreasing' if numbers were falling and 'unclear' otherwise.
+This plot seems like a lot of noise to me, but unsure.*
 
@@
 
-## Look more closely at relative skill
+## WIS contributions
+```{r}
+df <- data[grepl("2", target)] %>%
+  merge(epitrend, 
+        by = c("target_end_date", "location_name", "target_type"))
 
---> not sure what we wanted to do here.
-
----
-
-## Analyse distribution of model rankings
-
-```{r }
-# scores by target type for 4 week ahead forecasts
-scores <- eval_forecasts(
-  data[grepl("2", target)], 
-  summarise_by = c("model", "target_type", "location_name", "forecast_date")
-)
-
-ranked_scores <- scores %>%
-  dplyr::mutate(forecast_date = as.Date(forecast_date)) %>%
-  dplyr::group_by(forecast_date, location_name, target_type) %>%
-  dplyr::mutate(num_forecasts = dplyr::n(), 
-                rank = rank(interval_score, ties.method = "average",
-                                           na.last = NA), 
-                standard_rank = round((1 - (rank - 1) / (num_forecasts - 1)) * 100)) %>%
-  dplyr::ungroup()
-
-setDT(ranked_scores)
-df <- ranked_scores[, .(rank_count = .N), 
-                    by = c("target_type", "location_name", "model", "rank")][, 
-                      sum := .N, by = c("target_type", "location_name")
-                    ][, rank_count := rank_count / sum]
-
-ggplot(df, aes(y = model, x = rank, 
-                          group = model, fill = model)) + 
-  ggridges::geom_ridgeline(aes(height = rank_count)) + 
-  facet_wrap(location_name ~ target_type, scales = "free_x")
-
-ggplot(ranked_scores, aes(y = model, x = rank, 
-                          group = model, fill = model)) + 
-  ggridges::geom_density_ridges(stat = "binline") + 
-  facet_wrap(location_name ~ target_type, scales = "free_x")
-
-```
-
-**what we learn from this plot**
-
-- bimodal distribution is interesting
-
-**To do**
-
-- [ ] make plot nicer
-- [ ] maybe make this with relative skill instead
-- [ ] finish this todo list
-- [ ] maybe a density plot instead of a ridge plot?
-
----
-
-## Look at WIS contributions
-```{r}
 scores_target <- eval_forecasts(
-  data[grepl("2", target)], 
-  summarise_by = c("model", "target_type"), 
+  df, 
+  summarise_by = c("model", "target_type", "classification"), 
   compute_relative_skill = TRUE
@@
 
+scores_target[, target_phase := paste0(target_type, "s - ", 
+                                       classification, " phase")]
+
 wis_components(scores_target, 
-               facet_formula = ~ target_type, 
+               facet_formula = ~ target_phase, 
                scales = "free_x", 
@@
   coord_flip() + 
-  labs(title = "Components of the weighted interval score for 2-week ahead forecasts", 
-       x = NULL)
+  labs(x = NULL)
 
@@
 
+```
+
+*Figure 3.
+Relative contributions of sharpness, overprediction and underprediction to the weighted interval scores.
+Models overpredict in a decreasing phase and underpredict in a decreasing phase.
+So far so obvious.
+Somehow adding inflection points would be really cool - maybe stratify according to "decreasing, but inflection afterwards etc.?".
+Apparently the baseline model is really good in an unclear phase, just much too uncertain?.*
+
+---
+
+## Calibration
+
+```{r, eval = TRUE}
+df <- data[grepl("2", target)] %>%
+  merge(epitrend, 
+        by = c("target_end_date", "location_name", "target_type"))
+
 scores_target <- eval_forecasts(
-  data[grepl("4", target)], 
-  summarise_by = c("model", "location_name", "target_type"), 
-  compute_relative_skill = TRUE
+  df, 
+  summarise_by = c("model", "target_type", "classification", "range", "quantile"), 
+  compute_relative_skill = FALSE, 
+  pit_plots = TRUE
 )
 
-wis_components(scores_target, 
-               facet_formula = location_name ~ target_type, 
-               facet_wrap_or_grid = "grid",
-               scales = "free_x", 
-               x_text_angle = 0) + 
-  theme(legend.position = "bottom") + 
-  coord_flip() + 
-  labs(title = "Components of the weighted interval score for 2-week ahead forecasts", 
-       x = NULL)
+interval_coverage(scores_target, 
+                  facet_formula = ~ target_type + classification)
 
@@
 
+  *Figure 4: Comparison of nominal and empirical coverage (percentage of true observed values covered by a given prediction interval).
+The one thing I find interesting about this plot is that models are apparently much too confident when there is an increasing trend.
+I feel this is probably actionable advice (even though it could probably be made better using a separate analysis about optimal uncertainty that is beyond the scope of this paper).
+*
+
 **Todo**
 
-- [ ] have the second plot stratified by epidemic period
+- maybe make this a PIT plot
 
@@
 
-## Look more closely at interventions and change points
+## Supplementary Material
 
-- one interesting point Johannes brought up is that scoring predictions aroud change points may not even be such a good idea.
-The reason is that if you have a modle that always predicts a change point, theat model will do very well according to this metric even if it doesn't add much value.
-For example, we would expect the baseline model to do very well according to this change point metric
-
----
-
-## Look at the effect of data exclusions
+### Look at the effect of data exclusions
 
@@
 
----
+<!-- **Further things we could look at** -->
 
-## Look more closely at calibration and sharpness
-
-```{r, eval = TRUE}
-scores_target <- eval_forecasts(
-  data[grepl("2", target)], 
-  summarise_by = c("model", "target_type", "range", "quantile"), 
-  compute_relative_skill = FALSE
-)
-
-interval_coverage(scores_target, 
-                  facet_formula = ~ target_type)
-
-scores_target <- eval_forecasts(
-  data[grepl("2", target)], 
-  summarise_by = c("model", "location_name", "target_type", "range", "quantile"), 
-  compute_relative_skill = FALSE
-)
-
-interval_coverage(scores_target, 
-                  facet_formula = location_name ~ target_type, 
-                  facet_wrap_or_grid = "grid")
-
-```
-
-**What we learn from this plot**
-
-- models are widely overconfident in their predictive ability
-- more overconfidence with cases than deaths
-
-**Todo**
-
-- maybe make tihs a PIT plot
-- stratify by period
-
----
-
-## Look at scores based on log predictions and log truth values
-```{r, eval = TRUE}
-
-log_data <- copy(data)[, `:=`(true_value = log(true_value), 
-                              prediction = log(prediction))]
-
-```
-
-### Table 2 weeks ahead
-```{r, eval = TRUE}
-log_scores_target_2 <- eval_forecasts(
-  log_data[grepl("2", target)], 
-  summarise_by = c("model", "target_type"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-)
-
-log_scores_target_2 %>%
-  make_score_table()
-```
-
-### Table 2 weeks ahead
-```{r, eval = TRUE}
-log_scores_target_4 <- eval_forecasts(
-  log_data[grepl("4", target)], 
-  summarise_by = c("model", "target_type"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-)
-
-log_scores_target_4 %>%
-  make_score_table()
-```
-
-**What we learn**
-- results and rankings change if we look at scores of log values
-- this makes sense as presumably outliers aren't punished so harshly (inconsistent? models with large outliers are treated more leniently)
-
-### scores for logged values over time
-```{r, eval = TRUE}
-log_scores_target_forecast_date_2 <- eval_forecasts(
-  log_data[grepl("2", target)], 
-  summarise_by = c("model", "target_type", "forecast_date", "location_name"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-)
-
-rel_skill_time_2 <- log_scores_target_forecast_date_2  %>%
-  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, colour = model)) + 
-  geom_line() + 
-  geom_point() + 
-  theme_light() + 
-  facet_grid(target_type ~ location_name, scales = "free") +
-  theme(legend.position = "bottom") +
-  labs(y = "relative skill", x = "date")
-
-rel_skill_time_2
-```
-
-**what we learn**
-- nothing? 
-- it looks slightly different, but similar and also similarly confusing
-
-### WIS components for scores of logged values
-```{r, eval = TRUE}
-log_scores_target_location_2 <- eval_forecasts(
-  log_data[grepl("2", target)], 
-  summarise_by = c("model", "target_type", "location_name"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-)
-
-wis_components(log_scores_target_location_2, 
-               facet_formula = location_name ~ target_type, 
-               facet_wrap_or_grid = "grid",
-               scales = "free_x", 
-               x_text_angle = 0) + 
-  theme(legend.position = "bottom") + 
-  coord_flip() + 
-  labs(title = "Components of the weighted interval score for 2-week ahead forecasts", 
-       x = NULL) 
-```
-**what we learn**
-
-- the Renewal model benefits from this scoring scheme (except for Polish deaths)
-- interesting (confusing?) that the Baseline model is now the worst model for Polish cases. What's the mechanism behind that? is it just bad on average, but has no outliers?
-
-**To do**
-
-- at least for me (Nikos): get an intuition for what actually changes when you look at scores of logged predictions and what does it imply.
-What kind of model benefits from one or the other evaluation scheme?
-
-Thoughts about what changes when you look at logged predictions
-
-- models with outliers benefit
-- do models lose out that aren't great, but have no outliers?
-
-## Further interesting things
-
-- look at crowd performance as a function of the number of forecasts --> maybe leave that to a second paper
+<!-- - maybe look at correlation between the number of weekly cases and the score? -->
+<!-- - maybe it would be interesting to look at other baseline models, e.g. "how hard is it to beat a model that just always continues the trend?" -->
+<!-- - look at crowd performance as a function of the number of forecasts --> maybe leave that to a second paper -->

### 2021-04-22 data-raw/paper.R

@@ -137,4 +137,7 @@ forecast_dates[["second_period"]] <-
 forecast_dates[["deaths"]] <- 
   forecast_dates$cases[as.Date(forecast_dates$cases) >= "2020-12-07"]
 
+forecast_dates[["christmas"]] <- 
+  seq.Date(as.Date("2020-12-19"), as.Date("2021-01-07"), "week")
+
 usethis::use_data(forecast_dates, overwrite = TRUE)

### 2021-05-02 analysis/analysis.Rmd
add daily truth data and save table as png

@@
 Very happy to switch to it entirely if we agree it is the better metric, but not sure we are at that point yet.
+
+## Visualsiation of daily data
+
+```{r}
+dailytruth_data %>%
+  dplyr::filter(target_end_date >= min(forecast_dates$full_hub_period), 
+                target_end_date <= max(forecast_dates$full_hub_period)) %>%
+  ggplot(aes(y = true_value, x = target_end_date)) + 
+  geom_point() + 
+  geom_line() + 
+  facet_grid(target_type ~ location_name, scales = "free")
+
+ggsave(here("analysis", "plots", "daily_truth.png"))
+```
 
@@
   )) %>%
-    kable(format = "markdown") %>%
+    kable() %>% #format = "markdown"
     kable_styling(bootstrap_options = "striped")
@@
 
-eval_forecasts(
+table <- eval_forecasts(
   data[grepl("2", target)], 
@@
   make_score_table()
+
+save_kable(table, file = here("analysis", "plots", "table_scores_2_ahead.png"))
+
 ```

### 2021-05-02 R/datasets.R

@@ -12,6 +12,12 @@
 ##' @docType data
 "truth_data"
 
+##' Daily truth data used for the paper 
+##'
+##' @name locations
+##' @docType data
+"dailytruth_data"
+
 ##' Forecast data used for the paper 
 ##'
 ##' @name locations

### 2021-05-02 R/utils.R

@@ -170,7 +170,7 @@ globalVariables(
   c("cum_value", "day", "epiweek_full", "horizon", "location", "location_name",
     "locations", "n", "quantile", "region", "target", "target_end_date",
     "type", "value", ".", "primary", "secondary", "target_date", "variable", 
-    "epiyear", "year"
+    "epiyear", "year", "year_week"
   )
 )
 

### 2021-05-02 data-raw/paper.R

@@ -88,6 +88,7 @@ usethis::use_data(prediction_data, overwrite = TRUE)
 # update truth data ------------------------------------------------------------
 source(here("data-raw", "update.R"))
 
+# weekly truth data
 weekly_cases <- fread(here("data-raw", "weekly-incident-cases.csv"))
 weekly_cases[, target_type := "case"]
 weekly_deaths <- fread(here("data-raw", "weekly-incident-deaths.csv"))
@@ -99,6 +100,20 @@ truth_data <- truth[, `:=` (location = NULL, epiweek = NULL,
 setnames(truth_data, old = "value", new = "true_value")
 
 usethis::use_data(truth_data, overwrite = TRUE)
+
+# daily truth data
+daily_cases <- fread(here("data-raw", "daily-incidence-cases.csv"))
+daily_cases[, target_type := "case"]
+daily_deaths <- fread(here("data-raw", "daily-incidence-deaths.csv"))
+daily_deaths[, target_type := "death"]
+dailytruth <- rbindlist(list(daily_cases, daily_deaths)) 
+dailytruth <- dailytruth[location_name %in% c("Germany", "Poland")]
+dailytruth_data <- dailytruth[, `:=` (location = NULL,
+                                      target_end_date = as.Date(date))]
+setnames(dailytruth_data, old = "value", new = "true_value")
+
+usethis::use_data(dailytruth_data, overwrite = TRUE)
+
 
 # combine data -----------------------------------------------------------------
 combined_data <- merge_pred_and_obs(

### 2021-05-03 analysis/analysis.Rmd
update plots

@@
 library(patchwork)
+library(stringr)
 ```
@@
                       quantile %in% c(0.025, 0.25, 0.75, 0.975)]
-df[, location_target := paste0(target_type, "s", " in ", location_name)]
+df[, location_target := str_to_title(paste0(target_type, "s", " in ", location_name))]
 
@@
   plot_layout(guides = "collect") & 
+  plot_annotation(tag_levels = 'A') &
   theme(legend.position = 'bottom')
+
+# for some reason the A / B annotation doesn't work here
+
 ggsave(here("analysis", "plots", "figure-forecasts-2.png"))
@@
   geom_vline(aes(xintercept = 1), alpha = 0.4) + 
-  scale_fill_brewer(palette = "Accent") + 
+  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
   theme(panel.background = element_rect(fill = "#e1f0fe")) +
@@
 # scores for different phases of the epidemic
-scores[, target_phase := paste0(target_type, "s - ", classification, " phase")]
+scores[, target_phase := str_to_title(paste0(target_type, "s - ", 
+                                             classification, " phase"))]
+scores[, target_phase := factor(target_phase, 
+                                levels = str_to_title(c("Cases - decreasing phase", 
+                                                        "Cases - unclear phase", 
+                                                        "Cases - increasing phase", 
+                                                        "Deaths - decreasing phase", 
+                                                        "Deaths - unclear phase", 
+                                                        "Deaths - increasing phase")))]
+
+scores[, .(target_count = .N), by = c("target_phase")]
+
 p_phases <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                           group = model, fill = model)) + 
-  ggridges::geom_density_ridges() + 
+  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
   geom_vline(aes(xintercept = 1), alpha = 0.4) + 
-  scale_fill_brewer(palette = "Accent") + 
+  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
   theme(panel.background = element_rect(fill = "#e1f0fe")) +
@@
   plot_layout(guides = "collect") & 
+  plot_annotation(tag_levels = 'A') &
   theme(legend.position = 'bottom')
@@
 Apparently the baseline model is really good in an unclear phase, just much too uncertain?.*
+
+---
+
+```{r, eval = TRUE}
+scores <- eval_forecasts(
+  data[, horizon := substring(target, 1, 1)], 
+  summarise_by = c("model", "target_type", "location_name", "horizon"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)
+
+scores %>%
+  ggplot(aes(y = interval_score, x = horizon, color = model, 
+             group = model)) + 
+  geom_point() + 
+  geom_line() + 
+  theme(panel.background = element_rect(fill = "#e1f0fe")) +
+  scale_color_brewer(palette = "Accent") + 
+  scale_y_log10() + 
+  facet_grid(target_type ~ location_name, scales = "free") + 
+  theme(legend.position = "bottom")
+
+```
 

### 2021-05-04 analysis/analysis.Rmd
add plot with performance by horizon

@@
 
+```{r, eval = TRUE}
+scores_full <- eval_forecasts(
+  data[, horizon := substring(target, 1, 1)], 
+  summarise_by = c("model", "location_target", "horizon", "forecast_date"), 
+  compute_relative_skill = FALSE, 
+  baseline = "Baseline"
+)
+
+means <- scores_full[, .(meanval = mean(interval_score), 
+                         medianval = median(interval_score)), 
+                     by =c("model", "location_target", "horizon")]
+
+scores_full %>%
+  ggplot(aes(y = interval_score, x = horizon, 
+             fill = model, color = model)) +
+  geom_boxplot(outlier.shape = 21, coef = 1.5, 
+               width=0.5, alpha = 0.1, 
+               position = position_dodge2(width = 0.5)) + 
+  geom_line(data = means, 
+            aes(group = model, y = meanval, color = model), 
+            position = position_dodge2(width = 0.5), 
+            size = 2) +
+  theme(panel.background = element_rect(fill = "#e1f0fe")) +
+  scale_color_brewer(palette = "Accent") + 
+  geom_point(data = means, 
+             mapping = aes(y = meanval, fill = model),
+             color = "black",
+             # fill = "red",
+             shape = 21,
+             size = 2,
+             position = position_dodge2(width = 0.5)) + 
+    geom_point(data = means, 
+             mapping = aes(y = medianval, fill = model),
+             color = "black",
+             # fill = "red",
+             shape = 22,
+             size = 2,
+             position = position_dodge2(width = 0.5)) + 
+  scale_fill_brewer(palette = "Accent") + 
+  scale_y_log10() + 
+  facet_wrap( ~ location_target, scales = "free") + 
+  theme(legend.position = "bottom")
+
+ggsave("plots/scores_horizons.png")
+
+```
+
 ---

### 2021-05-04 analysis/analysis.Rmd
update plots

--- 2021-05-03 analysis/analysis.Rmd
@@
 
+```{r, eval = TRUE}
+scores_full <- eval_forecasts(
+  data[, horizon := substring(target, 1, 1)], 
+  summarise_by = c("model", "location_target", "horizon", "forecast_date"), 
+  compute_relative_skill = FALSE, 
+  baseline = "Baseline"
+)
+
+means <- scores_full[, .(meanval = mean(interval_score), 
+                         medianval = median(interval_score)), 
+                     by =c("model", "location_target", "horizon")]
+
+scores_full %>%
+  ggplot(aes(y = interval_score, x = horizon, 
+             fill = model, color = model)) +
+  geom_boxplot(outlier.shape = 21, coef = 1.5, 
+               width=0.5, alpha = 1, 
+               position = position_dodge2(width = 0.5)) + 
+  # geom_line(data = means, 
+  #           aes(group = model, y = meanval, color = model), 
+  #           position = position_dodge2(width = 0.5), 
+  #           size = 2) +
+  theme(panel.background = element_rect(fill = "#e1f0fe")) +
+  scale_color_brewer(palette = "Accent") + 
+  geom_point(data = means, 
+             mapping = aes(y = meanval, fill = model),
+             color = "black",
+             # fill = "red",
+             shape = 21,
+             size = 2,
+             position = position_dodge2(width = 0.5)) + 
+    geom_point(data = means, 
+             mapping = aes(y = medianval, fill = model),
+             color = "black",
+             # fill = "red",
+             shape = 22,
+             size = 2,
+             position = position_dodge2(width = 0.5)) + 
+  scale_fill_brewer(palette = "Accent") + 
+  scale_y_log10() + 
+  facet_wrap( ~ location_target, scales = "free") + 
+  theme(legend.position = "bottom")
+
+ggsave("plots/scores_horizons.png")
+
+```
+
 ---

### 2021-05-04 analysis/analysis.Rmd
save distrbution plot
add some plots for individual forecasters

@@
 ggsave(here("analysis", "plots", "daily_truth.png"))
+```
+## Number of expert forecasters
+
+```{r num-forecasters, results = 'asis'}
+dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
+                                        "EpiNow2_secondary", 
+                                        "EpiExpert-ensemble", 
+                                        "EpiNow2")), 
+                         .(`number of forecasters` = length(unique(model))), , 
+                         by = c("forecast_date", "location_name", "target_type")
+][order(forecast_date)][
+  !is.na(forecast_date)]
+
+dt[, .(sd = sd(`number of forecasters`), 
+                             mean = mean(`number of forecasters`), 
+                             min  = min(`number of forecasters`), 
+                             max = max(`number of forecasters`), 
+                             median = median(`number of forecasters`)), 
+   by = c("location_name", "target_type")]
+
+```
+```{r, results = 'asis'}
+dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
+                                        "EpiNow2_secondary", 
+                                        "EpiExpert-ensemble", 
+                                        "EpiNow2")) & forecast_date %in% forecast_dates$unfiltered]
+
+num_fc <- dt[, .(n_forecasts = length(unique(forecast_date))),
+             by = c("model")][order(n_forecasts)]
+
+num_fc %>%
+  ggplot(aes(x = n_forecasts)) + 
+  geom_bar() + 
+  theme_light() + 
+  labs(x = "Number of available submissions", 
+       y = "Number of forecasters")
+
+ggsave("plots/crowdforecast_regularity.png")
+
+```
+
+## Number of expert forecasters
+
+```{r, results = 'asis'}
+
+dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
+                                        "EpiNow2_secondary", 
+                                        "EpiNow2")) & forecast_date %in% forecast_dates$unfiltered]
+
+crowddata <- merge_pred_and_obs(dt, truth_data)
+
+scores <- eval_forecasts(
+  data = crowddata[grepl("2", target)],
+  summarise_by = c("model", "target_type"), 
+  compute_relative_skill = TRUE, 
+  baseline = "EpiExpert-ensemble"
+)
+
+plot_df <- merge(num_fc, scores, by = "model")
+
+plot_df %>%
+  ggplot(aes(y = scaled_rel_skill, x = n_forecasts)) + 
+  geom_point() + 
+  theme_light() + 
+  facet_wrap(~ target_type) + 
+  labs(y = "Scaled relative skill", x = "Number of available submissions") + 
+  geom_smooth(method='lm', formula= y~x)
+
+ggsave("plots/skill-vs-forecast-freq.png")
+
 ```
@@
 
+ggsave("plots/distribution_scores.png")
+
 ```

### 2021-05-04 R/datasets.R

@@ -24,6 +24,12 @@
 ##' @docType data
 "prediction_data"
 
+##' Crowd forecast data used for the paper 
+##'
+##' @name locations
+##' @docType data
+"crowdforecast_data"
+
 ##' Combined forecast and truth data used for the paper 
 ##'
 ##' @name locations

### 2021-05-04 data-raw/paper.R

@@ -156,3 +156,47 @@ forecast_dates[["christmas"]] <-
   seq.Date(as.Date("2020-12-19"), as.Date("2021-01-07"), "week")
 
 usethis::use_data(forecast_dates, overwrite = TRUE)
+
+
+
+
+
+
+# check number of available forecasters
+root_dir <- here::here("crowd-forecast", "processed-forecast-data")
+file_paths_forecast <- here::here(root_dir, list.files(root_dir))
+
+crowdforecast_data <- purrr::map_dfr(file_paths_forecast, 
+                                  .f = function(x) {
+                                    data <- data.table::fread(x) %>%
+                                      dplyr::mutate(target_end_date = as.Date(target_end_date), 
+                                                    submission_date = as.Date(submission_date), 
+                                                    forecast_date = as.Date(forecast_date))
+                                  }) %>%
+  dplyr::mutate(target_type = ifelse(grepl("death", target), "death", "case")) %>%
+  dplyr::rename(prediction = value) %>%
+  dplyr::mutate(forecast_date = as.Date(submission_date)) %>%
+  dplyr::rename(model = board_name) %>%
+  dplyr::filter(type == "quantile", 
+                location_name %in% c("Germany", "Poland")) %>%
+  dplyr::select(location, location_name, forecast_date, quantile, prediction, model, target_end_date, horizon, target, target_type)
+
+usethis::use_data(crowdforecast_data, overwrite = TRUE)
+
+dt <- prediction_data[!(model %in% c("Crowd-Rt-Forecast",
+                               "EpiNow2_secondary", 
+                               "EpiExpert-ensemble", 
+                               "EpiNow2")), 
+                .(`number of forecasters` = length(unique(model))), , 
+                by = c("forecast_date", "location_name", "target_type")
+][order(forecast_date)][
+  !is.na(forecast_date)]
+
+
+dt[, .(sd = sd(`number of forecasters`), 
+                             mean = mean(`number of forecasters`), 
+                             min  = min(`number of forecasters`), 
+                             max = max(`number of forecasters`), 
+                             median = median(`number of forecasters`)), 
+   by = c("location_name", "target_type")] 
+

### 2021-05-17 analysis/analysis.Rmd
update report and move data wrangling into package

@@
 library(stringr)
-```
-
-```{r helper-functions}
-# classify epidemic according to whether, on a given forecast date, the two
-# weeks before that have seen monotonic rise, decline, or an unclear trend
-classify_epidemic <- function(data, cutoff = 0.05, growth_cutoff = 2) {
-  dt <- as.data.table(data)
-
-  # calculate differences and set differences smaller than 
-  # a certain cutoff to zero
-  dt[, diff_1 := c(NA, diff(true_value, 1)), 
-     by = c("location_name", "target_type")]
-  dt[abs(diff_1) < (cutoff * true_value), diff_1 := 0]
-  dt[, diff_prev := c(shift(diff_1, 1)), 
-     by = c("location_name", "target_type")]
-
-  # assign a label depending on observed differences
-  dt[, c("classification", "speed") := "unclear"]
-  dt[(diff_1 >= 0 & diff_prev >= 0), 
-     classification := "increasing"]
-  dt[(diff_1 <= 0 & diff_prev <= 0 ), 
-     classification := "decreasing"]
-  dt[(diff_1 == 0 & diff_prev == 0), 
-     classification := "unclear"]
-  dt[(classification == "increasing") & 
-       diff_1 > growth_cutoff * diff_prev, 
-     speed := "accelerating"]
-    dt[(classification == "increasing") & 
-         diff_1 < 1/growth_cutoff * diff_prev, 
-     speed := "decelerating"]
-  dt[(classification == "decreasing") & 
-       abs(diff_1) > growth_cutoff * abs(diff_prev), 
-     speed := "accelerating"]
-  dt[(classification == "decreasing") & 
-       abs(diff_1) < 1/growth_cutoff * abs(diff_prev), 
-     speed := "decelerating"]
-
-  dt[, c("diff_1", "diff_prev") := NULL]
-  return(dt)
-}
-
-```
-
-```{r}
-# load and set up data
-cases <- combined_data[target_type == "case" & 
-                         as.Date(forecast_date) %in% forecast_dates$cases]
-deaths <- combined_data[target_type == "death" & 
-                         as.Date(forecast_date) %in% forecast_dates$deaths]
-data <- rbindlist(list(cases, deaths))
-data[, location_target := paste0(target_type, "s", " in ", location_name)]
-
-# obtain classification
-epitrend <- classify_epidemic(truth_data)
-epitrend[, forecast_date := target_end_date + 2]
-epitrend[, true_value := NULL]
-
 ```
@@
 ```
-## Number of expert forecasters
-
-```{r num-forecasters, results = 'asis'}
-dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
-                                        "EpiNow2_secondary", 
-                                        "EpiExpert-ensemble", 
-                                        "EpiNow2")), 
-                         .(`number of forecasters` = length(unique(model))), , 
-                         by = c("forecast_date", "location_name", "target_type")
-][order(forecast_date)][
-  !is.na(forecast_date)]
-
-dt[, .(sd = sd(`number of forecasters`), 
-                             mean = mean(`number of forecasters`), 
-                             min  = min(`number of forecasters`), 
-                             max = max(`number of forecasters`), 
-                             median = median(`number of forecasters`)), 
-   by = c("location_name", "target_type")]
-
-```
-```{r, results = 'asis'}
-dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
-                                        "EpiNow2_secondary", 
-                                        "EpiExpert-ensemble", 
-                                        "EpiNow2")) & forecast_date %in% forecast_dates$unfiltered]
-
-num_fc <- dt[, .(n_forecasts = length(unique(forecast_date))),
-             by = c("model")][order(n_forecasts)]
-
-num_fc %>%
-  ggplot(aes(x = n_forecasts)) + 
-  geom_bar() + 
-  theme_light() + 
-  labs(x = "Number of available submissions", 
-       y = "Number of forecasters")
-
-ggsave("plots/crowdforecast_regularity.png")
-
-```
-
-## Number of expert forecasters
-
-```{r, results = 'asis'}
-
-dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
-                                        "EpiNow2_secondary", 
-                                        "EpiNow2")) & forecast_date %in% forecast_dates$unfiltered]
-
-crowddata <- merge_pred_and_obs(dt, truth_data)
-
-scores <- eval_forecasts(
-  data = crowddata[grepl("2", target)],
-  summarise_by = c("model", "target_type"), 
-  compute_relative_skill = TRUE, 
-  baseline = "EpiExpert-ensemble"
-)
-
-plot_df <- merge(num_fc, scores, by = "model")
-
-plot_df %>%
-  ggplot(aes(y = scaled_rel_skill, x = n_forecasts)) + 
-  geom_point() + 
-  theme_light() + 
-  facet_wrap(~ target_type) + 
-  labs(y = "Scaled relative skill", x = "Number of available submissions") + 
-  geom_smooth(method='lm', formula= y~x)
-
-ggsave("plots/skill-vs-forecast-freq.png")
-
-```
 
@@
 
+Todo:
+
+-   do we want to keep the decreasing / increasing points at all on the plot?
+-   it is a bit odd that here we look at the classification at the target end date, while below we look at it in terms of the forecast_date
+
 ```{r truth-vs-forecasts, fig.height=10, fig.width=15}
 # load unfiltered combined data 
-df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
-                      grepl("2", target) & 
+df <- unfiltered_data[grepl("2", target) & 
                       quantile %in% c(0.025, 0.25, 0.75, 0.975)]
-df[, location_target := str_to_title(paste0(target_type, "s", " in ", location_name))]
-
 df <- dcast(df, ... ~ quantile, value.var = "prediction")
 
-# add trend classification
-df <- merge(df, epitrend, 
-            by = c("target_end_date", "location_name", "target_type"))
+# add trend classification by target_end_date (and remove classification by forecast_date)
+df <- merge(
+  df[, c("classification", "speed") := NULL], 
+  copy(epitrend)[, forecast_date := NULL], 
+  by = c("target_end_date", "location_name", "target_type")
+)
 
-truth_vs_forecast_2 <- df %>%
+truth_and_obs_plot <- function(df) {
+  p <- df %>%
   ggplot(aes(y = true_value, x = target_end_date)) + 
-  # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
-  #                size = 1.5,
-  #                alpha = 0.4,
-  #                position = position_dodge(width = 3)) + 
   geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
@@
   theme_light() + 
-  facet_wrap(~ location_target, scales = "free", ncol = 1) + 
+  facet_wrap(~ location_target, scales = "free", ncol = 2) + 
   theme(legend.position = "bottom") + 
-  scale_color_brewer(palette = "Accent") + 
-  theme(panel.background = element_rect(fill = "#e1f0fe"))
+  theme(panel.background = element_rect(fill = "#e1f0fe")) + 
+  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
+                          max(forecast_dates$full_hub_period)))
+  return(p)
+}
 
-ggsave(here("analysis", "plots", "truth-and-2-wk-ahead.png"), 
-       plot = truth_vs_forecast_2)
+truth_vs_forecast_2_cases <- df %>%
+  dplyr::filter(target_type == "case") %>%
+  truth_and_obs_plot() + 
+  scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[2:5])
+
+ggsave(here("analysis", "plots", "truth-and-2-wk-ahead_cases.png"), 
+       plot = truth_vs_forecast_2_cases)
+
+truth_vs_forecast_2_deaths <- df %>%
+  dplyr::filter(target_type == "death") %>%
+  truth_and_obs_plot()  + 
+  scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[1:5])
+
+ggsave(here("analysis", "plots", "truth-and-2-wk-ahead_deaths.png"), 
+       plot = truth_vs_forecast_2_deaths)
 
@@
 ```{r scores-over-time, fig.height=10, fig.width=15}
+# load unfiltered combined data 
+df <- unfiltered_data[grepl("2", target)]
+
 # plot with scores over time ---------------------------------------------------
 scores_target_forecastdate <- eval_forecasts(
-  data = data[grepl("2", target)],
-  summarise_by = c("model", "location_name", "target_type", "forecast_date", "location_target"), 
+  data = df,
+  summarise_by = c("model", "location_name", "target_type", 
+                   "forecast_date", "target_end_date", "location_target", 
+                   "classification"), 
   compute_relative_skill = TRUE, 
@@
 
-# add epi trend classification
-scores_target_forecastdate[, forecast_date := as.Date(forecast_date)]
-scores_target_forecastdate <-  merge(scores_target_forecastdate, epitrend, 
-            by = c("forecast_date", "location_name", "target_type"))
-
-rel_skill_time_2 <- scores_target_forecastdate  %>%
-  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill)) + 
+scores_over_time_plot <- function(scores) {
+  p <- scores %>%
+  ggplot(aes(x = as.Date(target_end_date), y = scaled_rel_skill)) + 
   geom_line(aes(colour = model)) + 
@@
   theme_light() + 
-  facet_wrap( ~ location_target, ncol = 1, scales = "free_y") +
+  facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
   theme(legend.position = "bottom") +
@@
                 ymax = Inf), fill = "lightgrey", alpha = 0.002) +
-  scale_color_brewer(palette = "Accent") + 
   theme(panel.background = element_rect(fill = "#e1f0fe")) +
-  scale_y_log10()
+  scale_y_log10() + 
+  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
+                          max(forecast_dates$full_hub_period)))
+  return(p)
+}
 
-ggsave(here("analysis", "plots", "rel-skill-over-time.png"), 
-       plot = rel_skill_time_2)
+rel_skill_time_2_case <- scores_target_forecastdate %>%
+  dplyr::filter(target_type == "case") %>%
+  scores_over_time_plot() + 
+  scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[2:5])
+
+ggsave(here("analysis", "plots", "rel-skill-over-time-cases.png"), 
+       plot = rel_skill_time_2_case)
+
+rel_skill_time_2_deaths <- scores_target_forecastdate %>%
+  dplyr::filter(target_type == "death") %>%
+  scores_over_time_plot() + 
+  scale_color_brewer(palette = "Accent")
+
+ggsave(here("analysis", "plots", "rel-skill-over-time-deaths.png"), 
+       plot = rel_skill_time_2_deaths)
 ```
@@
 # glue two plots together
-truth_vs_forecast_2 | rel_skill_time_2 +
+
+# cases_plot <- truth_vs_forecast_2_cases / rel_skill_time_2_case + 
+#   plot_layout(guides = "collect") & 
+#   theme(legend.position = 'bottom') 
+# 
+# deaths_plot <- truth_vs_forecast_2_deaths / rel_skill_time_2_deaths + 
+#   plot_layout(guides = "collect") & 
+#   theme(legend.position = 'bottom')
+
+truth_vs_forecast_2_cases / rel_skill_time_2_case / truth_vs_forecast_2_deaths / rel_skill_time_2_deaths + 
   plot_layout(guides = "collect") & 
@@
 ```
+
 *Figure 1.
-Left: Visualisation of 2 week ahead forecasts against the true observed values.
+A and C: Visualisation of 2 week ahead forecasts against the true observed values.
 The shape indicates whether there has been a monotonic increase or decrease over the last two weeks, or an unclear trend.
 Forecasts made during the Christmas period (from 2020-12-19 until 2021-01-02) are grayed out.
-Right: Corresponding scaled relative skill scores for the forecasts shown on the left.
+B and D: Corresponding scaled relative skill scores for the forecasts shown on the left.
 Scaled relative skill scores can be thought of as 'improvement over the baseline model' (see Methods for details).*
@@
 
-**Todo**
-- [ ] maybe remove baseline from relative skill plot
-- [ ] maybe rearrange plots
-- [ ] make plots nicer (legend, maybe point size on the left / remove either points or lines)
+**Todo** - [ ] maybe remove baseline from relative skill plot - [ ] maybe rearrange plots - [ ] make plots nicer (legend, maybe point size on the left / remove either points or lines)
 
----
+------------------------------------------------------------------------
 
@@
 ### 2 weeks ahead
+
 ```{r }
@@
 coverage <- eval_forecasts(
-  data[grepl("2", target)], 
+  filtered_data[grepl("2", target)], 
   summarise_by = c("model", "target_type", "range"), 
@@
 table <- eval_forecasts(
-  data[grepl("2", target)], 
+  filtered_data[grepl("2", target)], 
   summarise_by = c("model", "target_type"), 
@@
 
----
+------------------------------------------------------------------------
 
@@
 ```{r}
-# scores by target type for 4 week ahead forecasts
+# scores by target type for 2 week ahead forecasts
 scores <- eval_forecasts(
-  data[grepl("2", target)], 
+  filtered_data[grepl("2", target)], 
   summarise_by = c("model", "target_type", "location_name", "forecast_date", 
-                   "location_target"), 
+                   "location_target", "classification"), 
   compute_relative_skill = TRUE, 
@@
 
-scores[, forecast_date := as.Date(forecast_date)]
-scores <-  merge(scores, epitrend, 
-            by = c("forecast_date", "location_name", "target_type"))
+# scores[, forecast_date := as.character(forecast_date)]
+# scores <-  merge(scores, epitrend, 
+#             by = c("forecast_date", "location_name", "target_type"))
 
@@
 
----
+------------------------------------------------------------------------
 
 ## WIS contributions
+
 ```{r}
-df <- data[grepl("2", target)] %>%
-  merge(epitrend, 
-        by = c("target_end_date", "location_name", "target_type"))
+# df <- data[grepl("2", target)] %>%
+#   merge(epitrend, 
+#         by = c("target_end_date", "location_name", "target_type"))
 
 scores_target <- eval_forecasts(
-  df, 
+  filtered_data, 
   summarise_by = c("model", "target_type", "classification"), 
@@
 scores <- eval_forecasts(
-  data[, horizon := substring(target, 1, 1)], 
+  filtered_data, 
   summarise_by = c("model", "target_type", "location_name", "horizon"), 
@@
 scores_full <- eval_forecasts(
-  data[, horizon := substring(target, 1, 1)], 
+  filtered_data, 
   summarise_by = c("model", "location_target", "horizon", "forecast_date"), 
@@
 ```{r, eval = TRUE}
-df <- data[grepl("2", target)] %>%
-  merge(epitrend, 
-        by = c("target_end_date", "location_name", "target_type"))
+# df <- data[grepl("2", target)] %>%
+#   merge(epitrend, 
+#         by = c("target_end_date", "location_name", "target_type"))
 
 scores_target <- eval_forecasts(
-  df, 
+  filtered_data, 
   summarise_by = c("model", "target_type", "classification", "range", "quantile"), 
@@
 The one thing I find interesting about this plot is that models are apparently much too confident when there is an increasing trend.
-I feel this is probably actionable advice (even though it could probably be made better using a separate analysis about optimal uncertainty that is beyond the scope of this paper).
-*
+I feel this is probably actionable advice (even though it could probably be made better using a separate analysis about optimal uncertainty that is beyond the scope of this paper).*
 
@@
 -   look at first period, second period etc
+
 ```{r, eval = FALSE}
@@
 # scores for restricted data set
-scores_full <- eval_forecasts(data, 
+scores_full <- eval_forecasts(filtered_data, 
                               summarise_by = c("model", "target_type", "target"), 
@@
 <!-- - maybe look at correlation between the number of weekly cases and the score? -->
+
 <!-- - maybe it would be interesting to look at other baseline models, e.g. "how hard is it to beat a model that just always continues the trend?" -->
-<!-- - look at crowd performance as a function of the number of forecasts --> maybe leave that to a second paper -->
+
+<!-- - look at crowd performance as a function of the number of forecasts -->
+
+maybe leave that to a second paper --\>
+
+## Number of expert forecasters
+
+```{r num-forecasters, results = 'asis'}
+dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
+                                        "EpiNow2_secondary", 
+                                        "EpiExpert-ensemble", 
+                                        "EpiNow2")), 
+                         .(`number of forecasters` = length(unique(model))), , 
+                         by = c("forecast_date", "location_name", "target_type")
+][order(forecast_date)][
+  !is.na(forecast_date)]
+
+dt[, .(sd = sd(`number of forecasters`), 
+                             mean = mean(`number of forecasters`), 
+                             min  = min(`number of forecasters`), 
+                             max = max(`number of forecasters`), 
+                             median = median(`number of forecasters`)), 
+   by = c("location_name", "target_type")]
+
+```
+
+```{r num-forecasters2, results = 'asis'}
+dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
+                                        "EpiNow2_secondary", 
+                                        "EpiExpert-ensemble", 
+                                        "EpiNow2")), 
+                         .(`number of forecasters` = length(unique(model))), , 
+                         by = c("forecast_date", "location_name", "target_type")
+][order(forecast_date)][
+  !is.na(forecast_date)]
+
+dt %>%
+  ggplot(aes(y = `number of forecasters`, x = forecast_date)) + 
+  geom_line() + 
+  facet_wrap(location_name ~ target_type)
+
+```
+
+```{r, results = 'asis'}
+dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
+                                        "EpiNow2_secondary", 
+                                        "EpiExpert-ensemble", 
+                                        "EpiNow2")) & forecast_date %in% forecast_dates$unfiltered]
+
+num_fc <- dt[, .(n_forecasts = length(unique(forecast_date))),
+             by = c("model")][order(n_forecasts)]
+
+median(num_fc$n_forecasts)
+mean(num_fc$n_forecasts)
+
+num_fc %>%
+  ggplot(aes(x = n_forecasts)) + 
+  geom_bar() + 
+  theme_light() + 
+  labs(x = "Number of available submissions", 
+       y = "Number of forecasters")
+
+ggsave("plots/crowdforecast_regularity.png")
+
+```
+
+## Number of expert forecasters
+
+```{r, results = 'asis'}
+
+dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
+                                        "EpiNow2_secondary", 
+                                        "EpiNow2")) & forecast_date %in% forecast_dates$unfiltered]
+
+crowddata <- merge_pred_and_obs(dt, truth_data)
+
+scores <- eval_forecasts(
+  data = crowddata[grepl("2", target)],
+  summarise_by = c("model", "target_type"), 
+  compute_relative_skill = TRUE, 
+  baseline = "EpiExpert-ensemble"
+)
+
+plot_df <- merge(num_fc, scores, by = "model")
+
+plot_df %>%
+  ggplot(aes(y = scaled_rel_skill, x = n_forecasts)) + 
+  geom_point() + 
+  theme_light() + 
+  facet_wrap(~ target_type) + 
+  labs(y = "Scaled relative skill", x = "Number of available submissions") + 
+  geom_smooth(method='lm', formula= y~x)
+
+ggsave("plots/skill-vs-forecast-freq.png")
+
+```

### 2021-05-17 R/datasets.R

@@ -41,3 +41,21 @@
 ##' @name locations
 ##' @docType data
 "forecast_dates"
+
+##' Pre-filtered data used for the paper
+##'
+##' @name locations
+##' @docType data
+"filtered_data"
+
+##' Unfiltered version of the data used for the paper
+##'
+##' @name locations
+##' @docType data
+"unfiltered_data"
+
+##' Classification of the epidemic into falling, rising etc
+##'
+##' @name locations
+##' @docType data
+"epitrend"

### 2021-05-17 data-raw/paper.R

@@ -115,7 +115,7 @@ setnames(dailytruth_data, old = "value", new = "true_value")
 usethis::use_data(dailytruth_data, overwrite = TRUE)
 
 
-# combine data -----------------------------------------------------------------
+# combine raw data and store ---------------------------------------------------
 combined_data <- merge_pred_and_obs(
   prediction_data, 
   truth_data, 
@@ -126,43 +126,150 @@ combined_data <- merge_pred_and_obs(
 
 usethis::use_data(combined_data, overwrite = TRUE)
 
-# define different date periods ------------------------------------------------
+
+
+# ==============================================================================
+# -------------------- filter data and perform stratification ------------------
+# ==============================================================================
+
+# define different date periods relevant for the paper--------------------------
 forecast_dates <- list()
 
+# all unfiltered dates
 forecast_dates[["unfiltered"]] <- c(
   seq.Date(from = as.Date("2020-10-12"), to = as.Date("2021-03-01"), "week") 
 )
 
+# all dates relevant to the hubs
 forecast_dates[["full_hub_period"]] <- c(
   seq.Date(from = as.Date("2020-10-12"), to = as.Date("2020-12-14"), "week"), 
   seq.Date(from = as.Date("2021-01-11"), to = as.Date("2021-03-01"), "week") 
 )
   
-forecast_dates[["cases"]] <- 
-  forecast_dates$unfiltered[
-    !(forecast_dates$unfiltered %in% c("2020-12-21", "2020-12-28"))
-  ]
-
+# first period in the Hub paper
 forecast_dates[["first_period"]] <- 
   forecast_dates$cases[as.Date(forecast_dates$cases) <= "2020-12-19"]
 
+# second period in the hub paper
 forecast_dates[["second_period"]] <- 
   forecast_dates$cases[as.Date(forecast_dates$cases) >= "2021-01-04"]
 
-forecast_dates[["deaths"]] <- 
-  forecast_dates$cases[as.Date(forecast_dates$cases) >= "2020-12-07"]
-
+# christmas period
 forecast_dates[["christmas"]] <- 
   seq.Date(as.Date("2020-12-19"), as.Date("2021-01-07"), "week")
 
+# dates not scored for death forecasts
+forecast_dates[["death_not_scored"]] <- 
+  forecast_dates$unfiltered[as.Date(forecast_dates$unfiltered) < "2020-12-14"]
+
[…]

### 2021-05-17 analysis/analysis.Rmd
update analysis

@@
   truth_and_obs_plot()  + 
-  scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[1:5])
+  scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
+  geom_rect(aes(xmin = min(forecast_dates$full_hub_period) + 14,
+                xmax = max(forecast_dates$death_not_scored) + 14,
+                ymin = 0,
+                ymax = Inf), fill = "lightgrey", alpha = 0.002)
 
@@
   scores_over_time_plot() + 
-  scale_color_brewer(palette = "Accent")
+  scale_color_brewer(palette = "Accent") + 
+  geom_rect(aes(xmin = min(forecast_dates$full_hub_period) + 14,
+                xmax = max(forecast_dates$death_not_scored) + 14,
+                ymin = 0,
+                ymax = Inf), fill = "lightgrey", alpha = 0.002)
 
@@
 #   theme(legend.position = 'bottom') 
-
 truth_vs_forecast_2_cases / rel_skill_time_2_case / truth_vs_forecast_2_deaths / rel_skill_time_2_deaths + 
@@
 ```{r}
-# scores by target type for 2 week ahead forecasts
 scores <- eval_forecasts(
@@
 ```{r}
+
+p_combined <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
+                          group = model, fill = model)) + 
+  ggridges::geom_density_ridges() + 
+  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
+  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
+  theme(panel.background = element_rect(fill = "#e1f0fe")) +
+  facet_wrap( ~ target_type, ncol = 1) + 
+  theme(legend.position = "bottom") + 
+  labs(y = "Scaled relative skill") + 
+  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
+                limits = c(0.015, 50))
+
 p <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
@@
 ```{r fig.height=10, fig.width=15}
+scores %>%
+  gridExtra::tableGrob(theme = theme_minimal(), rows = NULL)
+```
 
-p / p_phases + 
+```{r fig.height=10, fig.width=15}
+
+(p_combined + p) / p_phases + 
   plot_layout(guides = "collect") & 

### 2021-05-22 analysis/analysis.Rmd
add tables for different phases

@@
                    "underprediction", "overprediction", "bias", 
-                   "50", "90"), 
+                   "50", "90", "location_target", "target_phase"), 
            new = c("Model", "Target", "WIS", "Abs. error", 
@@
                    "Underpred.", "Overpred.", "Bias", 
-                   "50%-Cov.", "90%-Cov."))
+                   "50%-Cov.", "90%-Cov.", "Target", "Target"), 
+           skip_absent = TRUE)
 
@@
 ```{r fig.height=10, fig.width=15}
-scores %>%
-  gridExtra::tableGrob(theme = theme_minimal(), rows = NULL)
+
+coverage_tables <- eval_forecasts(
+  filtered_data[grepl("2", target)], 
+  summarise_by = c("model", "target_phase", "classification", "range"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)[range %in% c(50, 90), 
+                   .(model, target_phase, coverage, classification, range)] %>%
+  dcast(formula = ... ~ range, value.var = "coverage")
+
+scores_tables <- eval_forecasts(
+  filtered_data[grepl("2", target)], 
+  summarise_by = c("model", "target_phase", "classification"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)
+
+tbl <- scores_tables %>%
+  merge(coverage_tables, all.x = TRUE, by = c("modellocation_target", "target_phase", "classification"))
+
+tables <- list()
+table_dfs <- list()
+targets <- unique(tbl$target_phase)
+
+for (tar in targets) {
+  tables[[tar]] <- make_score_table(tbl[target_phase == tar])
+}
+
+for (tar in targets) {
+  table_dfs[[tar]] <- tbl[target_phase == tar, 
+                          .("Model" = model, 
+                            # "Target" = target_phase,
+                            "WIS" = interval_score,
+                            # "Rel. skill" = scaled_rel_skill, 
+                            "Sharpn." = sharpness, 
+                            "Underp.." = underprediction, 
+                            "Overp." = overprediction)#, 
+                            # "Bias" = bias,
+                            # "50%-Cov." = `50`, 
+                            # "90%-Cov." = `90`)
+                          ]
+  table_dfs[[tar]] <- table_dfs[[tar]][, lapply(.SD, FUN = function(x) {
+    if (is.numeric(x)) {
+      return(round(signif(x, 3), 2))
+    } else {
+      return(x)
+    }
+  })]
+}
+
 ```
@@
 
-(p_combined + p) / p_phases + 
+pl <- (p_combined + p) / p_phases + 
   plot_layout(guides = "collect") & 
@@
 
+print(pl)
 ggsave("plots/distribution_scores.png")
+
+# make plots with tables
+library(gridExtra)
+
+tbl_plt <- grid.arrange(tableGrob(table_dfs[[1]]), 
+             tableGrob(table_dfs[[2]]), 
+             tableGrob(table_dfs[[3]]), 
+             tableGrob(table_dfs[[4]]), 
+             tableGrob(table_dfs[[5]]), 
+             tableGrob(table_dfs[[6]]), 
+             nrow = 2)
+
+print(tbl_plt)
+ggsave("plots/distribution_scores_table.png")
 

### 2021-05-22 data-raw/paper.R

@@ -239,6 +239,17 @@ unfiltered_data <- merge(
   by = c("location_name", "target_type", "forecast_date")
 )
 
+
+unfiltered_data[, target_phase := str_to_title(paste0(target_type, "s - ", 
+                                                      classification, " phase"))]
+unfiltered_data[, target_phase := factor(target_phase, 
+                                         levels = str_to_title(c("Cases - decreasing phase", 
+                                                                 "Cases - unclear phase", 
+                                                                 "Cases - increasing phase", 
+                                                                 "Deaths - decreasing phase", 
+                                                                 "Deaths - unclear phase", 
+                                                                 "Deaths - increasing phase")))]
+
 usethis::use_data(unfiltered_data, overwrite = TRUE)
 
 

### 2021-05-24 analysis/analysis.Rmd
save plot
update plot
fix transparency in plot

@@
   geom_line() + 
-  geom_rect(aes(xmin = min(forecast_dates$christmas) + 14, # 2wk ahead forecast
-                xmax = max(forecast_dates$christmas) + 14,
-                ymin = -Inf,
-                ymax = Inf), fill = "lightgrey", alpha = 0.002) +
+  # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14, # 2wk ahead forecast
+  #               xmax = max(forecast_dates$christmas) + 14,
+  #               ymin = -Inf,
+  #               ymax = Inf), fill = "lightgrey", alpha = 0.002) +
   theme_light() + 
@@
   scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
-  geom_rect(aes(xmin = min(forecast_dates$full_hub_period) + 14,
+  annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
                 xmax = max(forecast_dates$death_not_scored) + 14,
                 ymin = 0,
-                ymax = Inf), fill = "lightgrey", alpha = 0.002)
+                ymax = Inf, fill = "grey10", alpha = 0.1)
 
@@
   labs(y = "relative skill", x = "date") + 
-  geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
-                xmax = max(forecast_dates$christmas) + 14,
-                ymin = 0,
-                ymax = Inf), fill = "lightgrey", alpha = 0.002) +
+  # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
+  #               xmax = max(forecast_dates$christmas) + 14,
+  #               ymin = 0,
+  #               ymax = Inf), fill = "lightgrey", alpha = 0.002) +
   theme(panel.background = element_rect(fill = "#e1f0fe")) +
@@
   scale_color_brewer(palette = "Accent") + 
-  geom_rect(aes(xmin = min(forecast_dates$full_hub_period) + 14,
+  annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
                 xmax = max(forecast_dates$death_not_scored) + 14,
                 ymin = 0,
-                ymax = Inf), fill = "lightgrey", alpha = 0.002)
+                ymax = Inf, fill = "grey10", alpha = 0.1)
 
@@
 
+ tbl <- tbl[, lapply(.SD, FUN = function(x) {
+    if (is.numeric(x)) {
+      return(round(signif(x, 3), 2))
+    } else {
+      return(x)
+    }
+  })]
+
 tables <- list()
@@
                           ]
-  table_dfs[[tar]] <- table_dfs[[tar]][, lapply(.SD, FUN = function(x) {
-    if (is.numeric(x)) {
-      return(round(signif(x, 3), 2))
-    } else {
-      return(x)
-    }
-  })]
 }
@@
 
-print(pl)
+pl
 ggsave("plots/distribution_scores.png")
@@
 
-print(tbl_plt)
+tbl_plt <- ggplotify::as.ggplot(tbl_plt)
+
+tbl_plt
+
 ggsave("plots/distribution_scores_table.png")
+
+tbl[, 
+    .("Model" = model, 
+      "Target" = target_phase,
+      "WIS" = interval_score,
+      # "Rel. skill" = scaled_rel_skill, 
+      "Sharpn." = sharpness, 
+      "Underp.." = underprediction, 
+      "Overp." = overprediction)#, 
+    # "Bias" = bias,
+    # "50%-Cov." = `50`, 
+    # "90%-Cov." = `90`)
+] %>%
+  gt(rowname_col = "Model", 
+     groupname_col = "Target")
 

### 2021-05-24 analysis/analysis.Rmd
add median lines to score distribution plot and rescale

@@
 ```{r}
-
+scores[, target_type := paste0(str_to_title(target_type), "s overall")]
 p_combined <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                           group = model, fill = model)) + 
-  ggridges::geom_density_ridges() + 
+  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
   geom_vline(aes(xintercept = 1), alpha = 0.4) + 
@@
                           group = model, fill = model)) + 
-  ggridges::geom_density_ridges() + 
+  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
   geom_vline(aes(xintercept = 1), alpha = 0.4) + 
@@
   scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
-                limits = c(0.015, 50))
+                limits = c(0.015, 50)) + 
+  theme(axis.title.y=element_blank(),
+        axis.text.y=element_blank(), 
+        axis.ticks.y = element_blank())
 ```
@@
 
-coverage_tables <- eval_forecasts(
-  filtered_data[grepl("2", target)], 
-  summarise_by = c("model", "target_phase", "classification", "range"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-)[range %in% c(50, 90), 
-                   .(model, target_phase, coverage, classification, range)] %>%
-  dcast(formula = ... ~ range, value.var = "coverage")
-
-scores_tables <- eval_forecasts(
-  filtered_data[grepl("2", target)], 
-  summarise_by = c("model", "target_phase", "classification"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-)
-
-tbl <- scores_tables %>%
-  merge(coverage_tables, all.x = TRUE, by = c("modellocation_target", "target_phase", "classification"))
-
- tbl <- tbl[, lapply(.SD, FUN = function(x) {
-    if (is.numeric(x)) {
-      return(round(signif(x, 3), 2))
-    } else {
-      return(x)
-    }
-  })]
-
-tables <- list()
-table_dfs <- list()
-targets <- unique(tbl$target_phase)
-
-for (tar in targets) {
-  tables[[tar]] <- make_score_table(tbl[target_phase == tar])
-}
-
-for (tar in targets) {
-  table_dfs[[tar]] <- tbl[target_phase == tar, 
-                          .("Model" = model, 
-                            # "Target" = target_phase,
-                            "WIS" = interval_score,
-                            # "Rel. skill" = scaled_rel_skill, 
-                            "Sharpn." = sharpness, 
-                            "Underp.." = underprediction, 
-                            "Overp." = overprediction)#, 
-                            # "Bias" = bias,
-                            # "50%-Cov." = `50`, 
-                            # "90%-Cov." = `90`)
-                          ]
-}
-
-```
-
-```{r fig.height=10, fig.width=15}
-
-pl <- (p_combined + p) / p_phases + 
+pl <- wrap_plots(p_combined, p, widths = c(1, 2)) / p_phases + 
   plot_layout(guides = "collect") & 
@@
 This plot seems like a lot of noise to me, but unsure.*
+
+```{r fig.height=10, fig.width=15}
+
+coverage_tables <- eval_forecasts(
+  filtered_data[grepl("2", target)], 
+  summarise_by = c("model", "target_phase", "classification", "range"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)[range %in% c(50, 90), 
+                   .(model, target_phase, coverage, classification, range)] %>%
+  dcast(formula = ... ~ range, value.var = "coverage")
+
+scores_tables <- eval_forecasts(
+  filtered_data[grepl("2", target)], 
+  summarise_by = c("model", "target_phase", "classification"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)
+
+tbl <- scores_tables %>%
+  merge(coverage_tables, all.x = TRUE, by = c("model", "target_phase", "classification"))
+
+ tbl <- tbl[, lapply(.SD, FUN = function(x) {
+    if (is.numeric(x)) {
+      return(round(signif(x, 3), 2))
+    } else {
+      return(x)
+    }
+  })]
+
+tables <- list()
+table_dfs <- list()
+targets <- unique(tbl$target_phase)
+
+for (tar in targets) {
+  tables[[tar]] <- make_score_table(tbl[target_phase == tar])
+}
+
+for (tar in targets) {
+  table_dfs[[tar]] <- tbl[target_phase == tar, 
+                          .("Model" = model, 
+                            # "Target" = target_phase,
+                            "WIS" = interval_score,
+                            # "Rel. skill" = scaled_rel_skill, 
+                            "Sharpn." = sharpness, 
+                            "Underp.." = underprediction, 
+                            "Overp." = overprediction)#, 
+                            # "Bias" = bias,
+                            # "50%-Cov." = `50`, 
+                            # "90%-Cov." = `90`)
+                          ]
+}
+
+```
 

### 2021-05-24 analysis/analysis.Rmd
add distribution plot for wis

@@
   summarise_by = c("model", "target_type", "location_name", "forecast_date", 
+                   "target_phase",
                    "location_target", "classification"), 
@@
   baseline = "Baseline"
-)[model != "Baseline"]
+)
 
@@
 scores[, target_type := paste0(str_to_title(target_type), "s overall")]
-p_combined <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
-                          group = model, fill = model)) + 
+
+# look at variance to check
+scores[, .(sd = sd(scaled_rel_skill)), by = c("model")]
+
+distribution_plot <- function(df, x = "scaled_rel_skill") {
+  df %>%
+  ggplot(aes_string(y = "model", x = x, 
+                          group = "model", fill = "model")) + 
   ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
@@
   theme(panel.background = element_rect(fill = "#e1f0fe")) +
-  facet_wrap( ~ target_type, ncol = 1) + 
   theme(legend.position = "bottom") + 
@@
                 limits = c(0.015, 50))
+}
 
-p <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
-                          group = model, fill = model)) + 
+distribution_plot_wis <- function(df, x = "interval_score") {
+  df %>%
+  ggplot(aes_string(y = "model", x = x, 
+                          group = "model", fill = "model")) + 
   ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
-  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
-  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
+  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
   theme(panel.background = element_rect(fill = "#e1f0fe")) +
-  facet_wrap( ~ location_target) + 
   theme(legend.position = "bottom") + 
   labs(y = "Scaled relative skill") + 
-  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
-                limits = c(0.015, 50)) + 
+  scale_x_log10(labels = scales::number_format(accuracy = 1))
+}
+
+p_combined <- distribution_plot(df = scores[model != "Baseline"]) + 
+  facet_wrap(~ target_type, ncol = 1)
+
+p_combined_wis <- distribution_plot_wis(df = scores, 
+                                        x = "interval_score") +
+  facet_wrap(~ target_type, ncol = 1, scales = "free_x")
+
+p <- distribution_plot(df = scores[model != "Baseline"]) + 
   theme(axis.title.y=element_blank(),
         axis.text.y=element_blank(), 
-        axis.ticks.y = element_blank())
+        axis.ticks.y = element_blank()) + 
+  facet_wrap(~ location_target, ncol = 2)
+
+p_wis <- distribution_plot_wis(df = scores) + 
+  theme(axis.title.y=element_blank(),
+        axis.text.y=element_blank(), 
+        axis.ticks.y = element_blank()) + 
+  facet_wrap(~ location_target, ncol = 2, scale = "free_x")
+
 ```
@@
 # scores for different phases of the epidemic
-scores[, target_phase := str_to_title(paste0(target_type, "s - ", 
-                                             classification, " phase"))]
 scores[, target_phase := factor(target_phase, 
@@
 
-p_phases <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
-                          group = model, fill = model)) + 
-  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
-  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
-  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
-  theme(panel.background = element_rect(fill = "#e1f0fe")) +
-  facet_wrap( ~ target_phase) + 
-  theme(legend.position = "bottom") + 
-  labs(y = "Scaled relative skill") + 
-  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
-                limits = c(0.015, 50))
+p_phases <- distribution_plot(df = scores[model != "Baseline"]) + 
+  facet_wrap( ~ target_phase)
+
+p_phases_wis <- distribution_plot_wis(df = scores) + 
+  facet_wrap( ~ target_phase, scales = "free_x")
+
 ```
@@
 
-# make plots with tables
-library(gridExtra)
+pl_wis <- wrap_plots(p_combined_wis, p_wis, widths = c(1, 2)) / p_phases_wis + 
+  plot_layout(guides = "collect") & 
+  plot_annotation(tag_levels = 'A') &
+  theme(legend.position = 'bottom')
 
-tbl_plt <- grid.arrange(tableGrob(table_dfs[[1]]), 
-             tableGrob(table_dfs[[2]]), 
-             tableGrob(table_dfs[[3]]), 
-             tableGrob(table_dfs[[4]]), 
-             tableGrob(table_dfs[[5]]), 
-             tableGrob(table_dfs[[6]]), 
-             nrow = 2)
-
-tbl_plt <- ggplotify::as.ggplot(tbl_plt)
-
-tbl_plt
-
-ggsave("plots/distribution_scores_table.png")
-
-tbl[, 
-    .("Model" = model, 
-      "Target" = target_phase,
-      "WIS" = interval_score,
-      # "Rel. skill" = scaled_rel_skill, 
-      "Sharpn." = sharpness, 
-      "Underp.." = underprediction, 
-      "Overp." = overprediction)#, 
-    # "Bias" = bias,
-    # "50%-Cov." = `50`, 
-    # "90%-Cov." = `90`)
-] %>%
-  gt(rowname_col = "Model", 
-     groupname_col = "Target")
+pl_wis
+ggsave("plots/distribution_scores_wis.png")
 
@@
 }
+
+# make plots with tables
+library(gridExtra)
+
+tbl_plt <- grid.arrange(tableGrob(table_dfs[[1]]), 
+             tableGrob(table_dfs[[2]]), 
+             tableGrob(table_dfs[[3]]), 
+             tableGrob(table_dfs[[4]]), 
+             tableGrob(table_dfs[[5]]), 
+             tableGrob(table_dfs[[6]]), 
+             nrow = 2)
+
+tbl_plt <- ggplotify::as.ggplot(tbl_plt)
+
+tbl_plt
+
+ggsave("plots/distribution_scores_table.png")
+
+tbl[, 
+    .("Model" = model, 
+      "Target" = target_phase,
+      "WIS" = interval_score,
+      # "Rel. skill" = scaled_rel_skill, 
+      "Sharpn." = sharpness, 
+      "Underp.." = underprediction, 
+      "Overp." = overprediction)#, 
+    # "Bias" = bias,
+    # "50%-Cov." = `50`, 
+    # "90%-Cov." = `90`)
+] %>%
+  gt(rowname_col = "Model", 
+     groupname_col = "Target")
 

### 2021-05-24 analysis/analysis.Rmd
add absolute error distribution plot

@@
 
+p_combined_ae <- distribution_plot_wis(df = scores, 
+                                        x = "aem") +
+  facet_wrap(~ target_type, ncol = 1, scales = "free_x")
+
 p <- distribution_plot(df = scores[model != "Baseline"]) + 
@@
 p_wis <- distribution_plot_wis(df = scores) + 
+  theme(axis.title.y=element_blank(),
+        axis.text.y=element_blank(), 
+        axis.ticks.y = element_blank()) + 
+  facet_wrap(~ location_target, ncol = 2, scale = "free_x")
+
+p_ae <- distribution_plot_wis(df = scores, x = "aem") + 
   theme(axis.title.y=element_blank(),
@@
 
+p_phases_ae <- distribution_plot_wis(df = scores, x = "aem") + 
+  facet_wrap( ~ target_phase, scales = "free_x")
+
 ```
@@
 ggsave("plots/distribution_scores_wis.png")
+
+pl_ae <- wrap_plots(p_combined_ae, p_ae, widths = c(1, 2)) / p_phases_wis + 
+  plot_layout(guides = "collect") & 
+  plot_annotation(tag_levels = 'A') &
+  theme(legend.position = 'bottom')
+
+pl_ae
+ggsave("plots/distribution_scores_ae.png")
 

### 2021-05-30 paper/make_paper.sh
update citations and correct some spelling errors

@@ -1,0 +1,3 @@
+pandoc paper.md --standalone \
+	--citeproc \
+	-o paper.pdf

### 2021-06-01 analysis/analysis.Rmd
create and streamline plots and tables

@@
   ggplot(aes(y = true_value, x = target_end_date)) + 
-  geom_point() + 
-  geom_line() + 
-  facet_grid(target_type ~ location_name, scales = "free")
+  geom_point(size = 0.3) + 
+  geom_line(size = 0.5) + 
+  facet_grid(target_type ~ location_name, scales = "free") + 
+  labs(y = "Observed values", x = "Date") + 
+  theme_light()
 
@@
 
-## Visualisation of 2 week ahead forecasts and scores
+## Visualisation for 1, 2, 3, 4 week ahead forecasts and scores
 
-Todo:
-
--   do we want to keep the decreasing / increasing points at all on the plot?
--   it is a bit odd that here we look at the classification at the target end date, while below we look at it in terms of the forecast_date
+### Plots that visualise truth vs. predictions
 
 ```{r truth-vs-forecasts, fig.height=10, fig.width=15}
-# load unfiltered combined data 
-df <- unfiltered_data[grepl("2", target) & 
-                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]
-df <- dcast(df, ... ~ quantile, value.var = "prediction")
-
-# add trend classification by target_end_date (and remove classification by forecast_date)
-df <- merge(
-  df[, c("classification", "speed") := NULL], 
-  copy(epitrend)[, forecast_date := NULL], 
-  by = c("target_end_date", "location_name", "target_type")
-)
-
-truth_and_obs_plot <- function(df) {
+# create helper function for the plot ------------------------------------------
+truth_and_pred_plot <- function(df) {
   p <- df %>%
@@
   geom_line() + 
-  # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14, # 2wk ahead forecast
-  #               xmax = max(forecast_dates$christmas) + 14,
-  #               ymin = -Inf,
-  #               ymax = Inf), fill = "lightgrey", alpha = 0.002) +
   theme_light() + 
@@
 
-truth_vs_forecast_2_cases <- df %>%
+# prepare data for plotting ----------------------------------------------------
+# - load ufiltered data and pivot wider
+# - add trend classification by target_end_date 
+#   (and remove classification by forecast_date that is already present)
+
+df <- unfiltered_data[quantile %in% c(0.025, 0.25, 0.75, 0.975)] %>%
+  dcast(... ~ quantile, value.var = "prediction")
+df <- merge(
+  df[, c("classification", "speed") := NULL], 
+  copy(epitrend)[, forecast_date := NULL], 
+  by = c("target_end_date", "location_name", "target_type")
+)
+
+# create plots for deaths and cases --------------------------------------------
+
+for (horizon in 1:4) {
+  # plot for cases
+  truth_vs_forecast_cases <- df[grepl(horizon, target)] %>%
   dplyr::filter(target_type == "case") %>%
-  truth_and_obs_plot() + 
+  truth_and_pred_plot() + 
   scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[2:5])
 
-ggsave(here("analysis", "plots", "truth-and-2-wk-ahead_cases.png"), 
-       plot = truth_vs_forecast_2_cases)
+  filename <- here("analysis", "plots", 
+                   paste0("truth-and-", horizon, "-wk-ahead_cases"))
+  ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_cases)
 
-truth_vs_forecast_2_deaths <- df %>%
+  saveRDS(truth_vs_forecast_cases, 
+          paste0(filename, ".RDS"))
+
+  # plot for deaths
+  truth_vs_forecast_deaths <- df[grepl(horizon, target)] %>%
   dplyr::filter(target_type == "death") %>%
-  truth_and_obs_plot()  + 
+  truth_and_pred_plot()  + 
   scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
@@
 
-ggsave(here("analysis", "plots", "truth-and-2-wk-ahead_deaths.png"), 
-       plot = truth_vs_forecast_2_deaths)
+  filename <- here("analysis", "plots", 
+                   paste0("truth-and-", horizon, "-wk-ahead_deaths"))
+  ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_deaths)
 
+  saveRDS(truth_vs_forecast_deaths, 
+          paste0(filename, ".RDS"))
+}
 ```
 
+### Plots that visualise the achieved scores over time
+
 ```{r scores-over-time, fig.height=10, fig.width=15}
-# load unfiltered combined data 
-df <- unfiltered_data[grepl("2", target)]
-
-# plot with scores over time ---------------------------------------------------
+# score forecasts --------------------------------------------------------------
+# obtain scores and then do pairwise comparisons between models
+summarise_by <- c("model", "horizon", "location_name", "target_type", 
+                   "forecast_date", "target_end_date", "location_target", 
+                   "classification")
 scores_target_forecastdate <- eval_forecasts(
-  data = df,
-  summarise_by = c("model", "location_name", "target_type", 
-                   "forecast_date", "target_end_date", "location_target", 
-                   "classification"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
+  data = unfiltered_data,
+  summarise_by = summarise_by
 )
 
-scores_over_time_plot <- function(scores) {
+pairwise <- pairwise_comparison(scores_target_forecastdate, 
+                                summarise_by = summarise_by, 
+                                baseline = "Baseline")
+pairwise <- pairwise[compare_against == "Baseline"]
+
+# create helper function to plot forecasts -------------------------------------
+scores_over_time_plot <- function(scores, y = "mean_scores_ratio") {
   p <- scores %>%
-  ggplot(aes(x = as.Date(target_end_date), y = scaled_rel_skill)) + 
+  ggplot(aes(x = as.Date(target_end_date), y = get(y))) + 
   geom_line(aes(colour = model)) + 
@@
   theme(legend.position = "bottom") +
-  labs(y = "relative skill", x = "date") + 
+  labs(y = "WIS relative to baseline", x = "Date") + 
   # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
@@
 
-rel_skill_time_2_case <- scores_target_forecastdate %>%
-  dplyr::filter(target_type == "case") %>%
+# create plots for all horizons ------------------------------------------------
+for (i in 1:4) {
+  scores_over_time_case <- pairwise[horizon == i & target_type == "case"] %>%
     scores_over_time_plot() + 
@@
 
-ggsave(here("analysis", "plots", "rel-skill-over-time-cases.png"), 
-       plot = rel_skill_time_2_case)
+  ggsave(here("analysis", "plots", paste0("score-over-time-cases-", i, ".png")), 
+         plot = scores_over_time_case)
 
-rel_skill_time_2_deaths <- scores_target_forecastdate %>%
-  dplyr::filter(target_type == "death") %>%
+  saveRDS(scores_over_time_case, 
+          here("analysis", "plots", paste0("score-over-time-cases-", i, ".RDS")))
+
+  scores_over_time_deaths <- pairwise[horizon == i & target_type == "death"] %>%
     scores_over_time_plot() + 
@@
 
-ggsave(here("analysis", "plots", "rel-skill-over-time-deaths.png"), 
-       plot = rel_skill_time_2_deaths)
+  ggsave(here("analysis", "plots", paste0("score-over-time-deaths-", i, ".png")), 
+         plot = scores_over_time_deaths)
+
+  saveRDS(scores_over_time_deaths, 
+          here("analysis", "plots", paste0("score-over-time-deaths-", i, ".RDS")))
+
+}
 ```
 
+### Combine the two plots
+
 ```{r fig.height=10, fig.width=15}
-# glue two plots together
 
-# cases_plot <- truth_vs_forecast_2_cases / rel_skill_time_2_case + 
-#   plot_layout(guides = "collect") & 
-#   theme(legend.position = 'bottom') 
-# 
-# deaths_plot <- truth_vs_forecast_2_deaths / rel_skill_time_2_deaths + 
-#   plot_layout(guides = "collect") & 
-#   theme(legend.position = 'bottom') 
-truth_vs_forecast_2_cases / rel_skill_time_2_case / truth_vs_forecast_2_deaths / rel_skill_time_2_deaths + 
+horizons <- 1:4
+
+for (horizon in horizons) {
+  truth_vs_pred_cases <- readRDS(file = here("analysis", "plots", 
+                                             paste0("truth-and-", horizon, 
+                                                    "-wk-ahead_cases.RDS")))
+
+  truth_vs_pred_deaths <- readRDS(file = here("analysis", "plots", 
+                                              paste0("truth-and-", horizon, 
+                                                     "-wk-ahead_deaths.RDS")))
+
+  scores_over_time_cases <- readRDS(file = here("analysis", "plots", 
+                                                paste0("score-over-time-cases-", 
+                                                       horizon,".RDS")))
+
+  scores_over_time_deaths <- readRDS(file = here("analysis", "plots", 
+                                                 paste0("score-over-time-deaths-", 
+                                                        horizon,".RDS")))
+
+  truth_vs_pred_cases / scores_over_time_cases / truth_vs_pred_deaths / scores_over_time_deaths + 
     plot_layout(guides = "collect") & 
@@
 
-# for some reason the A / B annotation doesn't work here
+  ggsave(here("analysis", "plots", paste0("figure-forecasts-", horizon, ".png")))
+}
 
-ggsave(here("analysis", "plots", "figure-forecasts-2.png"))
 ```
@@
 # create helper function to make table
-make_score_table <- function(scores) {
+make_score_table <- function(scores, 
+                             group = TRUE) {
+  # copy data, change names, round column values and reduce to sign. digits
   scores <- as.data.table(scores)
   setnames(scores, 
-           old = c("model", "target_type", "interval_score", "aem", 
+           old = c("horizon", "model", "target_type", "interval_score", "aem", 
                    "relative_skill", "scaled_rel_skill", "sharpness", 
@@
                    "50", "90", "location_target", "target_phase"), 
-           new = c("Model", "Target", "WIS", "Abs. error", 
+           new = c("Horizon", "Model", "Target", "WIS", "Abs. error", 
                    "rel. skill", "Skill", "Sharpness", 
@@
 
-  scores <- scores[, .SD,  .SDcols = !c("coverage_deviation", "rel. skill")][
-    order(Target, `Skill`)
-  ]
+  # remove some cols, change column order, sort table and rename horizon
+  scores <- scores[, .SD,  .SDcols = !c("coverage_deviation", "rel. skill")]
 
   setcolorder(scores, 
-              neworder = c("Model", "Target", "Skill"))
+              neworder = c("Target", "Horizon", "Model", "WIS"))
 
-  # add an empty line to data.frame to separate deaths and cases
-  table <- 
-    rbindlist(list(
-    scores[1:4], 
-    as.list(rep(NA, ncol(scores))), 
-    scores[5:9]
-  )) %>%
-    kable() %>% #format = "markdown"
-    kable_styling(bootstrap_options = "striped")
+  scores <- scores[order(Target, Horizon)]
+  scores[, Horizon := paste(Horizon, "wk ahead")]
+
+  # calculate where to group rows
+  case_rows <- nrow(scores[Target == "case"])
+
+  table <- scores[,!c("Target")] %>%
+    kable(format = "html", col.names = c(" ", names(scores)[-(1:2)])) %>% #format = "markdown"
+    collapse_rows(columns = 1) %>%
+    kable_styling(bootstrap_options = "striped") %>%
+    column_spec(1, background = "white")
+
+  if (group) {
+    table <- table %>%
+      pack_rows("Cases", 1, case_rows, indent = FALSE) %>% 
+      pack_rows("Deaths", case_rows + 1, nrow(scores), indent = FALSE)
+  }
+
   return(table)
 }
+
 ```
 
-### 2 weeks ahead
+### Create tables
 
 ```{r }
-# scores by target type for 2 week ahead forecasts
-
+# create scores ----------------------------------------------------------------
+# calculate coverage independently and merge with other scores
 coverage <- eval_forecasts(
-  filtered_data[grepl("2", target)], 
-  summarise_by = c("model", "target_type", "range"), 
+  filtered_data, 
+  summarise_by = c("horizon", "model", "target_type", "range"), 
   compute_relative_skill = TRUE, 
@@
 )[range %in% c(50, 90), 
-                   .(model, target_type, coverage, range)] %>%
+                   .(model, target_type, coverage, range, horizon)] %>%
   dcast(formula = ... ~ range, value.var = "coverage")
 
-table <- eval_forecasts(
-  filtered_data[grepl("2", target)], 
-  summarise_by = c("model", "target_type"), 
+df <- eval_forecasts(
+  filtered_data, 
+  summarise_by = c("model", "horizon", "target_type"), 
   compute_relative_skill = TRUE, 
@@
 ) %>%
-  merge(coverage, all.x = TRUE, by = c("model", "target_type")) %>%
-  make_score_table()
+  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))
 
+# tables for 1-2 weeks ahead and 3-4 weeks ahdead
+table <- make_score_table(df[horizon <= 2]) 
 save_kable(table, file = here("analysis", "plots", "table_scores_2_ahead.png"))
+
+table <- make_score_table(df[horizon > 2]) 
+save_kable(table, file = here("analysis", "plots", "table_scores_4_ahead.png"))
 
@@
 50% and 90%-coverage are the percentage of observed values that fell within the 50% and 90% prediction intervals of a model.*
+
+### Tables for different phases of the epidemic
+
+```{r fig.height=10, fig.width=15}
+
+coverage <- eval_forecasts(
+  filtered_data, 
+  summarise_by = c("horizon", "model", "target_type", "target_phase", "range"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+)[range %in% c(50, 90), 
+                   .(model, target_type, coverage, range, target_phase, horizon)] %>%
+  dcast(formula = ... ~ range, value.var = "coverage")
+
+df <- eval_forecasts(
+  filtered_data, 
+  summarise_by = c("model", "horizon", "target_type", "target_phase"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+) %>%
+  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_phase", "target_type"))
+
+tables <- list()
+table_dfs <- list()
+targets <- unique(df$target_phase)
+
+horizons = 2
+for (tar in targets) {
+  for (i in horizons) {
+    name <- paste0(tar, "-", i)
+
+    tmp_df <- df[target_phase == tar & horizon == i, 
+                 .(model, interval_score, sharpness,
+                   target_phase, horizon,
+                   coverage_deviation, relative_skill,  
+                   underprediction, overprediction)]
+
+    tables[[name]] <- make_score_table(tmp_df, 
+                                       group = FALSE) %>%
+      pack_rows(tar, 1, nrow(tmp_df), indent = FALSE)
+
+    save_kable(tables[[name]],
+               file = here("analysis", "plots",
+                           paste0("table-", gsub(" ", "", name), ".png")))
+  }
+}
+
+```
 
@@
 ggsave("plots/distribution_scores_table.png")
+
+library(gt)
 

### 2021-06-01 analysis/analysis.Rmd
update plot label

@@
 
-```{r truth-vs-forecasts, fig.height=10, fig.width=15}
+```{r truth-vs-forecasts, fig.height=12, fig.width=15}
 # create helper function for the plot ------------------------------------------
@@
                  position = position_dodge(width = 6)) + 
-  labs(y = "value", x = "date") + 
+  labs(y = "value", x = "Date") + 
   geom_point(aes(shape = classification)) + 

### 2021-06-01 analysis/analysis.Rmd
update table width

@@
 make_score_table <- function(scores, 
-                             group = TRUE) {
+                             group = TRUE, 
+                             full_width = TRUE) {
   # copy data, change names, round column values and reduce to sign. digits
@@
     collapse_rows(columns = 1) %>%
-    kable_styling(bootstrap_options = "striped") %>%
+    kable_styling(bootstrap_options = "striped", 
+                  full_width = full_width) %>%
     column_spec(1, background = "white")
@@
 
-```{r fig.height=10, fig.width=15}
+```{r fig.height=10, fig.width=5}
 
@@
     tables[[name]] <- make_score_table(tmp_df, 
-                                       group = FALSE) %>%
+                                       group = FALSE, 
+                                       full_width = FALSE) %>%
       pack_rows(tar, 1, nrow(tmp_df), indent = FALSE)

### 2021-06-02 analysis/analysis.Rmd
add median and sd to tables

@@
   # remove some cols, change column order, sort table and rename horizon
+  if (all(c("coverage_deviation", "rel. skill") %in% names(scores))) {
     scores <- scores[, .SD,  .SDcols = !c("coverage_deviation", "rel. skill")]
+  }
 
@@
   compute_relative_skill = TRUE, 
-  baseline = "Baseline"
+  baseline = "Baseline",
 )[range %in% c(50, 90), 
@@
 
+```{r}
+# calculate percentage differences in performance ------------------------------
+
+df <- eval_forecasts(
+  filtered_data, 
+  summarise_by = c("model", "horizon", "target_type")
+)
+
+df <- df %>%
+  merge(df[model == "Hub-ensemble", 
+           .(horizon, target_type, base_score = interval_score)])
+df[, rel_score := (interval_score / base_score) * 100 - 100]
+df[, diff_score := interval_score - base_score]
+df[, .(horizon, target_type, model, rel_score, diff_score)][order(target_type, horizon)]
+
+```
+
 ### Tables for different phases of the epidemic
@@
   summarise_by = c("horizon", "model", "target_type", "target_phase", "range"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
 )[range %in% c(50, 90), 
@@
   summarise_by = c("model", "horizon", "target_type", "target_phase"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
+  metrics = c("interval_score", "coverage_deviation"),
+  sd = TRUE, 
+  quantiles = 0.5
 ) %>%
@@
                    target_phase, horizon, 
-                   coverage_deviation, relative_skill,  
-                   underprediction, overprediction)]
+                   underprediction, overprediction, 
+                   `WIS - median` = interval_score_0.5, 
+                   `WIS - sd` = interval_score_sd)]
 
@@
 )
+
+scores[, .(sd = sd(interval_score)), by = c("model", "target_type")]
 

### 2021-06-02 analysis/analysis.Rmd
add table with sd and median of wis

@@
 
+  if ("WIS" %in% names(scores)) {
     setcolorder(scores, 
                 neworder = c("Target", "Horizon", "Model", "WIS"))  
+  }
 
@@
 50% and 90%-coverage are the percentage of observed values that fell within the 50% and 90% prediction intervals of a model.*
+
+```{r}
+# calculate median and sd of the WIS -------------------------------------------
+
+df <- eval_forecasts(
+  filtered_data, 
+  metric = "interval_score",
+  summarise_by = c("model", "horizon", "target_type"), 
+  sd = TRUE, 
+  quantile = 0.5
+)
+
+df <- df[, .(model, horizon, target_type, 
+             `WIS - mean` = interval_score, 
+             `WIS - median` = interval_score_0.5, 
+             `WIS - sd` = interval_score_sd)] %>%
+    dcast(... ~ ., value.var = c("WIS - mean", "WIS - median", "WIS - sd"))
+
+setcolorder(df, c("target_type", "horizon", "model"))
+
+table <- df[order(target_type, horizon, model)] %>%
+  make_score_table()
+
+save_kable(table, 
+           file = here("analysis", "plots", "table-wis-sd-median.png"))
+
+```
 

### 2021-06-02 analysis/analysis.Rmd
update plots with th new ensemble

@@
 library(stringr)
+
 ```
@@
                  position = position_dodge(width = 6)) + 
-  labs(y = "value", x = "Date") + 
   geom_point(aes(shape = classification)) + 
@@
 
-df <- unfiltered_data[quantile %in% c(0.025, 0.25, 0.75, 0.975)] %>%
+df <- unfiltered_data[model %in% regular_models &
+                        quantile %in% c(0.025, 0.25, 0.75, 0.975)] %>%
   dcast(... ~ quantile, value.var = "prediction")
@@
     truth_and_pred_plot() + 
-  scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[2:5])
+    scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[-2]) + 
+    labs(y = "Cases", x = "")
 
@@
                 ymin = 0,
-                ymax = Inf, fill = "grey10", alpha = 0.1)
+                ymax = Inf, fill = "grey10", alpha = 0.1) + 
+    labs(y = "Deaths", x = "")
 
@@
 scores_target_forecastdate <- eval_forecasts(
-  data = unfiltered_data,
+  data = unfiltered_data[model %in% regular_models],
   summarise_by = summarise_by
@@
   theme(legend.position = "bottom") +
-  labs(y = "WIS relative to baseline", x = "Date") + 
   # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
@@
     scores_over_time_plot() + 
-    scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[2:5])
+    scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[-2]) + 
+    labs(y = "WIS rel. to baseline", x = "")
 
@@
              ymin = 0,
-             ymax = Inf, fill = "grey10", alpha = 0.1)
+             ymax = Inf, fill = "grey10", alpha = 0.1) + 
+    labs(y = "WIS rel. to baseline", x = "Date")
 
@@
 
-```{r fig.height=10, fig.width=15}
-
+```{r fig.height=15, fig.width=10}
 horizons <- 1:4
@@
 
-  ggsave(here("analysis", "plots", paste0("figure-forecasts-", horizon, ".png")))
+  ggsave(here("analysis", "plots", paste0("figure-forecasts-", horizon, ".png")), width = 10, height = 12)
 }
@@
 ```
-
-*Figure 1.
-A and C: Visualisation of 2 week ahead forecasts against the true observed values.
-The shape indicates whether there has been a monotonic increase or decrease over the last two weeks, or an unclear trend.
-Forecasts made during the Christmas period (from 2020-12-19 until 2021-01-02) are grayed out.
-B and D: Corresponding scaled relative skill scores for the forecasts shown on the left.
-Scaled relative skill scores can be thought of as 'improvement over the baseline model' (see Methods for details).*
-
-**What we learn from this plot**
-
--   severe overshooting for Renewal model
--   all models are terrible around Christmas
--   the artifacts around Christmas hit Renewal hardest
--   the Christmas effect is much stronger in Germany than in Poland
 
@@
 coverage <- eval_forecasts(
-  filtered_data, 
+  filtered_data[model %in% regular_models], 
   summarise_by = c("horizon", "model", "target_type", "range"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline",
 )[range %in% c(50, 90), 
@@
 df <- eval_forecasts(
-  filtered_data, 
+  filtered_data[model %in% regular_models], 
   summarise_by = c("model", "horizon", "target_type"), 
@@
 
-*Table 1: Scores for 2 week ahead forecasts (excluding the 21st and 28th of December 2020, cut to three significant digits and rounded).
-Skill is the scaled relative skill, a measure of relative performance with respect to the baseline model.
-Sharpness, overprediction and underprediction together some up to the weighted interval score (WIS).
-Bias (between -1 and 1) represents the general average tendency of a model to over- or underpredict.
-50% and 90%-coverage are the percentage of observed values that fell within the 50% and 90% prediction intervals of a model.*
+### Create table for all median ensembles
+
+```{r }
+# create scores ----------------------------------------------------------------
+# calculate coverage independently and merge with other scores
+coverage <- eval_forecasts(
+  filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]], 
+  summarise_by = c("horizon", "model", "target_type", "range"), 
+)[range %in% c(50, 90), 
+                   .(model, target_type, coverage, range, horizon)] %>%
+  dcast(formula = ... ~ range, value.var = "coverage")
+
+df <- eval_forecasts(
+  filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]], 
+  summarise_by = c("model", "horizon", "target_type"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+) %>%
+  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))
+
+# tables for 1-2 weeks ahead and 3-4 weeks ahdead
+table <- make_score_table(df[horizon <= 2]) 
+save_kable(table, file = here("analysis", "plots", "table_median-ensemble_scores_2_ahead.png"))
+
+table <- make_score_table(df[horizon > 2]) 
+save_kable(table, file = here("analysis", "plots", "table_median-ensemble_scores_4_ahead.png"))
+
+```
+
+### Create table for all mean ensembles
+
+```{r }
+# create scores ----------------------------------------------------------------
+# calculate coverage independently and merge with other scores
+coverage <- eval_forecasts(
+  filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]], 
+  summarise_by = c("horizon", "model", "target_type", "range"), 
+)[range %in% c(50, 90), 
+                   .(model, target_type, coverage, range, horizon)] %>%
+  dcast(formula = ... ~ range, value.var = "coverage")
+
+df <- eval_forecasts(
+  filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]], 
+  summarise_by = c("model", "horizon", "target_type"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Baseline"
+) %>%
+  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))
+
+# tables for 1-2 weeks ahead and 3-4 weeks ahdead
+table <- make_score_table(df[horizon <= 2]) 
+save_kable(table, file = here("analysis", "plots", "table_mean-ensemble_scores_2_ahead.png"))
+
+table <- make_score_table(df[horizon > 2]) 
+save_kable(table, file = here("analysis", "plots", "table_mean-ensemble_scores_4_ahead.png"))
+
+```
 
@@
 df <- eval_forecasts(
-  filtered_data, 
+  filtered_data[model %in% regular_models], 
   metric = "interval_score",
@@
 df <- eval_forecasts(
-  filtered_data, 
+  filtered_data[model %in% regular_models], 
   summarise_by = c("model", "horizon", "target_type")
@@
 coverage <- eval_forecasts(
-  filtered_data, 
+  filtered_data[model %in% regular_models], 
   summarise_by = c("horizon", "model", "target_type", "target_phase", "range"), 
@@
 df <- eval_forecasts(
-  filtered_data, 
+  filtered_data[model %in% regular_models], 
   summarise_by = c("model", "horizon", "target_type", "target_phase"), 
@@
 scores <- eval_forecasts(
-  filtered_data[grepl("2", target)], 
+  filtered_data[(model %in% regular_models) & grepl("2", target)], 
   summarise_by = c("model", "target_type", "location_name", "forecast_date", 
@@
 
-# scores[, forecast_date := as.character(forecast_date)]
-# scores <-  merge(scores, epitrend, 
-#             by = c("forecast_date", "location_name", "target_type"))
-
-```
-
-```{r}
 scores[, target_type := paste0(str_to_title(target_type), "s overall")]

### 2021-06-02 data-raw/paper.R

@@ -2,6 +2,7 @@ library(here)
 library(magrittr)
 library(stringr)
 library(data.table)
+library(scoringutils)
 
 # ==============================================================================
 # ------------------------------ update data -----------------------------------
@@ -25,10 +26,7 @@ file_paths <- purrr::map(folders,
                            return(out)}) %>%
   unlist()
 file_paths <- file_paths[grepl(".csv", file_paths)]
-file_paths <- file_paths[!(
-  grepl("EpiExpert_Rt", file_paths) |
-    grepl("mean_ensemble", file_paths)
-)]
+file_paths <- file_paths[!(grepl("EpiExpert_Rt", file_paths))]
   
 # load all past forecasts ------------------------------------------------------
 # ceate a helper function to get model name from a file path
@@ -65,7 +63,9 @@ change_model_name <- function(names, old_name, new_name) {
 
 change_names <- list(
   c("KITCOVIDhub-median_ensemble", 
-    "Hub-ensemble"), 
+    "Hub-ensemble-all"), 
+  c("KITCOVIDhub-mean_ensemble", 
+    "Hub-ensemble-mean-all"), 
   c("KIT-baseline", 
     "Baseline"),
   c("epiforecasts-EpiExpert", 
@@ -73,7 +73,19 @@ change_names <- list(
   c("epiforecasts-EpiNow2", 
     "Renewal"), 
   c("epiforecasts-EpiNow2_secondary", 
-    "Convolution")
+    "Convolution"), 
+  c("KITCOVIDhub-median_ensemble_exclude_both", 
+    "Hub-ensemble"), 
+  c("KITCOVIDhub-median_ensemble_exclude_EpiExpert", 
+    "Hub-ensemble-without-crowd"), 
+  c("KITCOVIDhub-median_ensemble_exclude_EpiNow2", 
+    "Hub-ensemble-without-renewal"), 
+  c("KITCOVIDhub-mean_ensemble_exclude_both", 
+    "Hub-ensemble-mean"), 
+  c("KITCOVIDhub-mean_ensemble_exclude_EpiExpert", 
+    "Hub-ensemble-mean-without-crowd"), 
+  c("KITCOVIDhub-mean_ensemble_exclude_EpiNow2", 
+    "Hub-ensemble-mean-without-renewal")
 )
 
 purrr::walk(change_names, 
@@ -84,6 +96,15 @@ purrr::walk(change_names,
             })
 
 usethis::use_data(prediction_data, overwrite = TRUE)
+
+
[…]

### 2021-06-02 R/datasets.R
update plots

@@ -59,3 +59,15 @@
 ##' @name locations
 ##' @docType data
 "epitrend"
+
+##' Names of all ensemble models
+##'
+##' @name locations
+##' @docType data
+"ensemble_models"
+
+##' Names of all regular models
+##'
+##' @name locations
+##' @docType data
+"regular_models"

### 2021-06-03 analysis/analysis.Rmd
update plots

@@
   filtered_data[model %in% regular_models], 
-  summarise_by = c("model", "horizon", "target_type")
+  summarise_by = c("model", "horizon", "target_type"), 
+  compute_relative_skill = TRUE, 
+  baseline = "Hub-ensemble"
 )
@@
 df[, diff_score := interval_score - base_score]
-df[, .(horizon, target_type, model, rel_score, diff_score)][order(target_type, horizon)]
+df[, .(horizon, target_type, model, rel_score, scaled_rel_skill, diff_score)][order(target_type, horizon)]
 
@@
 
+### Look at ensemble forecasts
+
+```{r}
+
+models_plot <- c("Crowd forecast", "Hub-ensemble-with-crowd", "Hub-ensemble")
+
+comparison_ensembles <- function(models_to_plot) {
+  df <- unfiltered_data[model %in% models_to_plot &
+                          quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
+    dcast(... ~ quantile, value.var = "prediction")
+  df <- merge(
+    df[, c("classification", "speed") := NULL], 
+    copy(epitrend)[, forecast_date := NULL], 
+    by = c("target_end_date", "location_name", "target_type")
+  )
+
+  p <- df[grepl(2, target)] %>%
+    ggplot(aes(y = `0.5`, x = target_end_date, color = model)) +
+    geom_line() + 
+    theme_light() + 
+    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
+    theme(legend.position = "bottom") + 
+    theme(panel.background = element_rect(fill = "#e1f0fe")) + 
+    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
+                            max(forecast_dates$full_hub_period)))
+
+  return(p)
+}
+
+comparison_ensembles(models_plot)
+
+```
+
 ------------------------------------------------------------------------
@@
     ggplot(aes_string(y = "model", x = x, 
-                          group = "model", fill = "model")) + 
-  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
+                      group = "model")) + 
+    geom_density_ridges(aes(fill = model), 
+                                  quantile_lines = TRUE, quantiles = 0.5, 
+                                  rel_min_height = 0.01) + 
     geom_vline(aes(xintercept = 1), alpha = 0.4) + 
@@
     labs(y = "Scaled relative skill") + 
-  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
-                limits = c(0.015, 50))
+    scale_x_log10(labels = scales::number_format(accuracy = 0.1))
 }
@@
                       group = "model", fill = "model")) + 
-  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
+    geom_density_ridges(aes(fill = model), 
+                        quantile_lines = TRUE, quantiles = 0.5, 
+                        rel_min_height = 0.005, 
+                        scale = 0.95, 
+                        jittered_points = TRUE, 
+                        position = position_points_jitter(width = 0.05, height = 0),
+                        point_size = 1.5, 
+                        point_shape = 21,
+                        #point_shape = '|',
+                        point_alpha = 1, 
+                        alpha = 0.7) + 
+    geom_density_ridges(quantile_lines=TRUE,
+                        quantile_fun=function(x,...) mean(x), 
+                        linetype = "dotted", 
+                        alpha = 0, 
+                        scale = 0.95, 
+                        rel_min_height = 0.01) +
     scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
+    # scale_color_manual(aesthetics = "point_color", 
+    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
     theme(panel.background = element_rect(fill = "#e1f0fe")) +
     theme(legend.position = "bottom") + 
-  labs(y = "Scaled relative skill") + 
-  scale_x_log10(labels = scales::number_format(accuracy = 1))
+    labs(y = "Model", x = "Weighted interval score") + 
+  scale_x_continuous(labels = scales::label_number(suffix = "k", 
+                                                   scale = 1e-3, 
+                                                   accuracy = NULL))
 }
@@
                                         x = "interval_score") +
-  facet_wrap(~ target_type, ncol = 1, scales = "free_x")
+  facet_wrap(~ target_type, ncol = 1, scales = "free") + 
+  theme(plot.margin=unit(c(0,0.4,0,0),"cm"))
 
@@
         axis.ticks.y = element_blank()) + 
-  facet_wrap(~ location_target, ncol = 2, scale = "free_x")
+  facet_wrap(~ location_target, ncol = 2, scale = "free")
 
@@
 
-pl
-ggsave("plots/distribution_scores.png")
+ggsave("plots/distribution_scores.png", plot = pl, height = 9)
 
@@
 
-pl_wis
-ggsave("plots/distribution_scores_wis.png")
+ggsave("plots/distribution_scores_wis.png", pl_wis, height = 9)
 
@@
 
-pl_ae
-ggsave("plots/distribution_scores_ae.png")
+ggsave("plots/distribution_scores_ae.png", pl_ae, height = 9)
 

### 2021-06-03 data-raw/paper.R

@@ -77,15 +77,15 @@ change_names <- list(
   c("KITCOVIDhub-median_ensemble_exclude_both", 
     "Hub-ensemble"), 
   c("KITCOVIDhub-median_ensemble_exclude_EpiExpert", 
-    "Hub-ensemble-without-crowd"), 
+    "Hub-ensemble-with-renewal"), 
   c("KITCOVIDhub-median_ensemble_exclude_EpiNow2", 
-    "Hub-ensemble-without-renewal"), 
+    "Hub-ensemble-with-crowd"), 
   c("KITCOVIDhub-mean_ensemble_exclude_both", 
     "Hub-ensemble-mean"), 
   c("KITCOVIDhub-mean_ensemble_exclude_EpiExpert", 
-    "Hub-ensemble-mean-without-crowd"), 
+    "Hub-ensemble-mean-with-renewal"), 
   c("KITCOVIDhub-mean_ensemble_exclude_EpiNow2", 
-    "Hub-ensemble-mean-without-renewal")
+    "Hub-ensemble-mean-with-crowd")
 )
 
 purrr::walk(change_names, 

### 2021-06-03 analysis/analysis.Rmd
update tables

@@
   if ("WIS" %in% names(scores)) {
+    wis <- names(scores)[grepl("WIS", names(scores))]
     setcolorder(scores, 
-                neworder = c("Target", "Horizon", "Model", "WIS"))  
+                neworder = c("Target", "Horizon", "Model", wis))  
   }
@@
   compute_relative_skill = TRUE, 
-  baseline = "Baseline"
+  baseline = "Baseline", 
+  sd = TRUE, 
+  quantiles = 0.5
 ) %>%
   merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))
+
+del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
+                        !(grepl("interval", names(df)))]
+df[, (del_cols) := NULL]
+
+setnames(df, old = c("interval_score_0.5", "interval_score_sd"), 
+         new = c("WIS - median", 
+                 "WIS - sd"))
 
@@
   compute_relative_skill = TRUE, 
-  baseline = "Baseline"
+  baseline = "Baseline", 
+  sd = TRUE, 
+  quantiles = 0.5,
 ) %>%
   merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type")) 
+del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
+                        !(grepl("interval", names(df)))]
+df[, (del_cols) := NULL]
+
+setnames(df, old = c("interval_score_0.5", "interval_score_sd"), 
+         new = c("WIS - median", 
+                 "WIS - sd"))
 
@@
 
-ggsave("plots/distribution_scores_wis.png", pl_wis, height = 9)
+ggsave("plots/distribution_scores_wis.png", pl_wis, height = 10, width = 9)
 

### 2021-06-03 analysis/analysis.Rmd
update tables
update plots and tables

@@
            new = c("Horizon", "Model", "Target", "WIS", "Abs. error", 
-                   "rel. skill", "Skill", "Sharpness", 
+                   "rel. skill", "WIS - rel.", "Sharpness", 
                    "Underpred.", "Overpred.", "Bias", 
@@
 
-  if ("WIS" %in% names(scores)) {
+  if (all(c("WIS", "Horizon") %in% names(scores))) {
     wis <- names(scores)[grepl("WIS", names(scores))]
@@
 
+  if ("Horizon" %in% names(scores)) {
     scores <- scores[order(Target, Horizon)]
     scores[, Horizon := paste(Horizon, "wk ahead")]
+  }
 
@@
 
+del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
+                        !(grepl("interval", names(df)))]
+df[, (del_cols) := NULL]
+
+setnames(df, old = c("interval_score_0.5", "interval_score_sd"), 
+         new = c("WIS - median", 
+                 "WIS - sd"))
+
 tables <- list()
@@
 targets <- unique(df$target_phase)
+
+# for horizon <= 2
+labels <- df[horizon <= 2][order(target_phase, horizon)]$target_phase
+table <- make_score_table(df[horizon <= 2, !"target_type"], group = FALSE) %>%
+  pack_rows(index = table(labels), indent = FALSE)
+save_kable(table, 
+           file = here("analysis", "plots", "table-phases-2.png"))
+
+# for horizon > 2
+labels <- df[horizon > 2][order(target_phase, horizon)]$target_phase
+table <- make_score_table(df[horizon > 2, !"target_type"], group = FALSE) %>%
+  pack_rows(index = table(labels), indent = FALSE)
+save_kable(table, 
+           file = here("analysis", "plots", "table-phases-4.png"))
 
@@
                         rel_min_height = 0.005, 
-                        scale = 0.95, 
+                        scale = 0.9, 
                         jittered_points = TRUE, 
@@
                         alpha = 0, 
-                        scale = 0.95, 
+                        scale = 0.9, 
                         rel_min_height = 0.01) +
@@
 
-scores[, .(target_count = .N), by = c("target_phase")]
+scores[, .(target_count = .N), by = c("target_phase", "model")]
 
@@
   facet_wrap( ~ target_phase, scales = "free_x")
+
+scores[, .(n = .N), by = "target_phase"]
 
@@
 
-ggsave("plots/distribution_scores_wis.png", pl_wis, height = 10, width = 9)
+ggsave("plots/distribution_scores_wis.png", pl_wis, height = 11, width = 9)
 
@@
   filtered_data[grepl("2", target)], 
-  summarise_by = c("model", "target_phase", "classification", "range"), 
+  summarise_by = c("model", "target_phase", "classification", "range", "horizon"), 
   compute_relative_skill = TRUE, 
@@
   filtered_data[grepl("2", target)], 
-  summarise_by = c("model", "target_phase", "classification"), 
+  summarise_by = c("model", "target_phase", "classification", "horizon"), 
   compute_relative_skill = TRUE, 

### 2021-06-03 analysis/analysis.Rmd
add ensemble member plot

@@
 ### Look at ensemble forecasts
+
+#### Number of members in the ensemble
+```{r}
+ens <- ensemble_members[, .("GM_inc_case" = sum(GM_inc_case), 
+                     "PL_inc_case" = sum(PL_inc_case), 
+                     "GM_inc_death" = sum(GM_inc_death), 
+                     "PL_inc_death" = sum(PL_inc_death)), 
+                 by = "Date"] %>%
+  melt(id.vars = "Date")
+
+ens[, .(mean = mean(value), 
+       median = median(value)), by = "variable"]
+
+p <- ens %>%
+  ggplot(aes(y = value, x = Date, color = variable)) + 
+  geom_line()
+
+ggsave(here("analysis", "plots", "ensemble-members.png"), 
+       plot = p)
+
+```
 

### 2021-06-03 R/datasets.R

@@ -71,3 +71,9 @@
 ##' @name locations
 ##' @docType data
 "regular_models"
+
+##' Models included in the official hub ensemble
+##'
+##' @name locations
+##' @docType data
+"ensemble_members"

### 2021-06-03 data-raw/paper.R

@@ -148,6 +148,29 @@ combined_data <- merge_pred_and_obs(
 usethis::use_data(combined_data, overwrite = TRUE)
 
 
+# update data about the number of ensembles included in the Hub ----------------
+root_dir <- here("data-raw", "included_models")
+filenames <- list.files(root_dir)
+get_date <- function(filename) {
+  date <- substr(filename, 17, 26)
+  return(as.Date(date))
+}
+dates <- get_date(filenames)
+filenames <- filenames[dates >= "2020-10-12" & dates <= "2021-03-01"]
+
+ensemble_members <- purrr::map_dfr(filenames, 
+                                   .f = function(x) {
+                                     dt <- fread(here(root_dir, x))
+                                     dt[, Date := get_date(x)]
+                                     return(dt)
+                                   })
+
+del_cols <- names(ensemble_members)[grepl("XX", names(ensemble_members)) | 
+                                      grepl("cum", names(ensemble_members))]
+ensemble_members[, (del_cols) := NULL]
+
+usethis::use_data(ensemble_members, overwrite = TRUE)
+
 
 # ==============================================================================
 # -------------------- filter data and perform stratification ------------------

### 2021-06-03 data-raw/paper.sh

@@ -11,5 +11,6 @@ svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data
 svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data-processed/epiforecasts-EpiNow2_secondary
 svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data-processed/KITCOVIDhub-median_ensemble
 svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/data-processed/KIT-baseline
+svn checkout https://github.com/KITmetricslab/covid19-forecast-hub-de/trunk/code/ensemble/included_models
 cd ..
 

### 2021-06-03 analysis/analysis.Rmd
add ensemble plots

--- 2021-06-03 analysis/analysis.Rmd
@@
 
+#### Number of members in the ensemble
 ```{r}
-
-models_plot <- c("Crowd forecast", "Hub-ensemble-with-crowd", "Hub-ensemble")
+ens <- ensemble_members %>%
+  melt(id.vars = c("Date", "model"))
+
+epinow2_included <- ens[model == "epiforecasts-EpiNow2", "epinow" := value]
+crowd_included <- ens[model == "epiforecasts-EpiExpert", "crowd" := value]
+
+p <- ens[, .(value = sum(value), 
+             epinow = sum(epinow, na.rm = TRUE), 
+             crowd = sum(crowd, na.rm = TRUE)), by = c("variable", "Date")] %>%
+  ggplot(aes(y = value, x = Date, color = variable)) + 
+  geom_point()
+
+ggsave(here("analysis", "plots", "ensemble-members.png"), 
+       plot = p)
+
+```
+
+### Comparing ensembles with and without a model
+
+```{r}
 
@@
 
-comparison_ensembles(models_plot)
+models_plot <- c("Crowd forecast", "Hub-ensemble-with-crowd", "Hub-ensemble")
+p <- comparison_ensembles(models_plot)
+ggsave(here("analysis", "plots", "ensemble-with-and-without-crowd.png"), 
+       plot = p)
+
+models_plot <- c("Renewal", "Hub-ensemble-with-renewal", "Hub-ensemble")
+p <- comparison_ensembles(models_plot)
+ggsave(here("analysis", "plots", "ensemble-with-and-without-renewal.png"), 
+       plot = p)
+
+models_plot <- c("Renewal", "Crowd forecast", "Hub-ensemble-all", "Hub-ensemble")
+p <- comparison_ensembles(models_plot)
+ggsave(here("analysis", "plots", "ensemble-with-and-without-both.png"), 
+       plot = p)
 

### 2021-06-03 analysis/analysis.Rmd
update plots

@@
 del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
-                        !(grepl("interval", names(df)))]
+                        !(grepl("interval", names(df)))] %>%
+  c("coverage_deviation")
 df[, (del_cols) := NULL]
@@
     scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
-                            max(forecast_dates$full_hub_period)))
-
+                            max(forecast_dates$full_hub_period))) + 
+    labs(y = "Median forecast", x = "Date")
   return(p)
@@
 
-------------------------------------------------------------------------
-
-```{r, eval = TRUE}
-scores <- eval_forecasts(
+### Distribution of Bias over time
+
+```{r}
+# df <- data[grepl("2", target)] %>%
+#   merge(epitrend, 
+#         by = c("target_end_date", "location_name", "target_type"))
+
+scores_target <- eval_forecasts(
   filtered_data, 
-  summarise_by = c("model", "target_type", "location_name", "horizon"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
+  summarise_by = c("model", "target_type", "classification", "forecast_date")
 )
 
-scores %>%
-  ggplot(aes(y = interval_score, x = horizon, color = model, 
-             group = model)) + 
-  geom_point() + 
-  geom_line() + 
-  theme(panel.background = element_rect(fill = "#e1f0fe")) +
-  scale_color_brewer(palette = "Accent") + 
-  scale_y_log10() + 
-  facet_grid(target_type ~ location_name, scales = "free") + 
-  theme(legend.position = "bottom")
-
+scores_target[, target_phase := paste0(target_type, "s - ", 
+                                       classification, " phase")]
+
+p <- scores_target[model %in% regular_models] %>%
+  distribution_plot_wis(x = "bias") + 
+  scale_x_continuous() + 
+  facet_wrap(~ target_phase, ncol = 3) + 
+  geom_vline(xintercept = 0, color = "white", size = 1) + 
+  labs(y = "Bias")
+
+ggsave(here("analysis", "plots", "distribution_bias_phases.png"), plot = p)
 ```

### 2021-06-04 analysis/analysis.Rmd
update te code and figures

@@
 
-**Todo** - [ ] maybe remove baseline from relative skill plot - [ ] maybe rearrange plots - [ ] make plots nicer (legend, maybe point size on the left / remove either points or lines)
-
 ------------------------------------------------------------------------
@@
 df <- eval_forecasts(
-  filtered_data[model %in% regular_models], 
-  summarise_by = c("model", "horizon", "target_type"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Hub-ensemble"
+  filtered_data, 
+  summarise_by = c("model", "horizon", "target_type")
 )
@@
 df[, diff_score := interval_score - base_score]
-df[, .(horizon, target_type, model, rel_score, scaled_rel_skill, diff_score)][order(target_type, horizon)]
+df[, .(horizon, target_type, model, rel_score, diff_score)][order(target_type, horizon)]
 
@@
 
-horizons = 2
-for (tar in targets) {
-  for (i in horizons) {
-    name <- paste0(tar, "-", i)
-
-    tmp_df <- df[target_phase == tar & horizon == i, 
-                 .(model, interval_score, sharpness,
-                   target_phase, horizon, 
-                   underprediction, overprediction, 
-                   `WIS - median` = interval_score_0.5, 
-                   `WIS - sd` = interval_score_sd)]
-
-    tables[[name]] <- make_score_table(tmp_df, 
-                                       group = FALSE, 
-                                       full_width = FALSE) %>%
-      pack_rows(tar, 1, nrow(tmp_df), indent = FALSE)
-
-    save_kable(tables[[name]],
-               file = here("analysis", "plots",
-                           paste0("table-", gsub(" ", "", name), ".png")))
-  }
-}
+# 
+# horizons = 2
+# for (tar in targets) {
+#   for (i in horizons) {
+#     name <- paste0(tar, "-", i)
+#     
+#     tmp_df <- df[target_phase == tar & horizon == i, 
+#                  .(model, interval_score, sharpness,
+#                    target_phase, horizon, 
+#                    underprediction, overprediction, 
+#                    `WIS - median` = interval_score_0.5, 
+#                    `WIS - sd` = interval_score_sd)]
+#     
+#     tables[[name]] <- make_score_table(tmp_df, 
+#                                        group = FALSE, 
+#                                        full_width = FALSE) %>%
+#       pack_rows(tar, 1, nrow(tmp_df), indent = FALSE)
+#     
+#     save_kable(tables[[name]],
+#                file = here("analysis", "plots",
+#                            paste0("table-", gsub(" ", "", name), ".png")))
+#   }
+# }
 
@@
   facet_wrap(~ target_phase, ncol = 3) + 
-  geom_vline(xintercept = 0, color = "white", size = 1) + 
+  geom_vline(xintercept = 0, color = "black", size = 1.4) + 
   labs(y = "Bias")

### 2021-06-04 analysis/analysis.Rmd
update figures

@@
 scores_target <- eval_forecasts(
-  filtered_data, 
+  filtered_data[model %in% regular_models], 
   summarise_by = c("model", "target_type", "classification"), 

### 2021-06-08 analysis/analysis.Rmd
update plots

@@
 ```{r fig.height=10, fig.width=15}
-
-coverage_tables <- eval_forecasts(
-  filtered_data[grepl("2", target)], 
-  summarise_by = c("model", "target_phase", "classification", "range", "horizon"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-)[range %in% c(50, 90), 
-                   .(model, target_phase, coverage, classification, range)] %>%
-  dcast(formula = ... ~ range, value.var = "coverage")
-
-scores_tables <- eval_forecasts(
-  filtered_data[grepl("2", target)], 
-  summarise_by = c("model", "target_phase", "classification", "horizon"), 
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
-)
-
-tbl <- scores_tables %>%
-  merge(coverage_tables, all.x = TRUE, by = c("model", "target_phase", "classification"))
-
- tbl <- tbl[, lapply(.SD, FUN = function(x) {
-    if (is.numeric(x)) {
-      return(round(signif(x, 3), 2))
-    } else {
-      return(x)
-    }
-  })]
-
-tables <- list()
-table_dfs <- list()
-targets <- unique(tbl$target_phase)
-
-for (tar in targets) {
-  tables[[tar]] <- make_score_table(tbl[target_phase == tar])
-}
-
-for (tar in targets) {
-  table_dfs[[tar]] <- tbl[target_phase == tar, 
-                          .("Model" = model, 
+# 
+# coverage_tables <- eval_forecasts(
+#   filtered_data[grepl("2", target)], 
+#   summarise_by = c("model", "target_phase", "classification", "range", "horizon"), 
+#   compute_relative_skill = TRUE, 
+#   baseline = "Baseline"
+# )[range %in% c(50, 90), 
+#                    .(model, target_phase, coverage, classification, range)] %>%
+#   dcast(formula = ... ~ range, value.var = "coverage")
+# 
+# scores_tables <- eval_forecasts(
+#   filtered_data[grepl("2", target)], 
+#   summarise_by = c("model", "target_phase", "classification", "horizon"), 
+#   compute_relative_skill = TRUE, 
+#   baseline = "Baseline"
+# )
+# 
+# tbl <- scores_tables %>%
+#   merge(coverage_tables, all.x = TRUE, by = c("model", "target_phase", "classification")) 
+# 
+#  tbl <- tbl[, lapply(.SD, FUN = function(x) {
+#     if (is.numeric(x)) {
+#       return(round(signif(x, 3), 2))
+#     } else {
+#       return(x)
+#     }
+#   })]
+# 
+# tables <- list()
+# table_dfs <- list()
+# targets <- unique(tbl$target_phase)
+# 
+# for (tar in targets) {
+#   tables[[tar]] <- make_score_table(tbl[target_phase == tar])
+# }
+# 
+# for (tar in targets) {
+#   table_dfs[[tar]] <- tbl[target_phase == tar, 
+#                           .("Model" = model, 
+#                             # "Target" = target_phase,
+#                             "WIS" = interval_score,
+#                             # "Rel. skill" = scaled_rel_skill, 
+#                             "Sharpn." = sharpness, 
+#                             "Underp.." = underprediction, 
+#                             "Overp." = overprediction)#, 
+#                             # "Bias" = bias,
+#                             # "50%-Cov." = `50`, 
+#                             # "90%-Cov." = `90`)
+#                           ]
+# }
+# 
+# 
+# # make plots with tables
+# library(gridExtra)
+# 
+# tbl_plt <- grid.arrange(tableGrob(table_dfs[[1]]), 
+#              tableGrob(table_dfs[[2]]), 
+#              tableGrob(table_dfs[[3]]), 
+#              tableGrob(table_dfs[[4]]), 
+#              tableGrob(table_dfs[[5]]), 
+#              tableGrob(table_dfs[[6]]), 
+#              nrow = 2) 
+# 
+# tbl_plt <- ggplotify::as.ggplot(tbl_plt)
+# 
+# tbl_plt
+# 
+# ggsave("plots/distribution_scores_table.png")
+# 
+# library(gt)
+# 
+# tbl[, 
+#     .("Model" = model, 
 #       "Target" = target_phase,
-                            "WIS" = interval_score,
-                            # "Rel. skill" = scaled_rel_skill, 
-                            "Sharpn." = sharpness, 
-                            "Underp.." = underprediction, 
-                            "Overp." = overprediction)#, 
-                            # "Bias" = bias,
-                            # "50%-Cov." = `50`, 
-                            # "90%-Cov." = `90`)
-                          ]
-}
-
-# make plots with tables
-library(gridExtra)
-
-tbl_plt <- grid.arrange(tableGrob(table_dfs[[1]]), 
-             tableGrob(table_dfs[[2]]), 
-             tableGrob(table_dfs[[3]]), 
-             tableGrob(table_dfs[[4]]), 
-             tableGrob(table_dfs[[5]]), 
-             tableGrob(table_dfs[[6]]), 
-             nrow = 2)
-
-tbl_plt <- ggplotify::as.ggplot(tbl_plt)
-
-tbl_plt
-
-ggsave("plots/distribution_scores_table.png")
-
-library(gt)
-
-tbl[, 
-    .("Model" = model, 
-      "Target" = target_phase,
-      "WIS" = interval_score,
-      # "Rel. skill" = scaled_rel_skill, 
-      "Sharpn." = sharpness, 
-      "Underp.." = underprediction, 
-      "Overp." = overprediction)#, 
-    # "Bias" = bias,
-    # "50%-Cov." = `50`, 
-    # "90%-Cov." = `90`)
-] %>%
-  gt(rowname_col = "Model", 
-     groupname_col = "Target")
+#       "WIS" = interval_score,
+#       # "Rel. skill" = scaled_rel_skill, 
+#       "Sharpn." = sharpness, 
+#       "Underp.." = underprediction, 
+#       "Overp." = overprediction)#, 
+#     # "Bias" = bias,
+#     # "50%-Cov." = `50`, 
+#     # "90%-Cov." = `90`)
+# ] %>%
+#   gt(rowname_col = "Model", 
+#      groupname_col = "Target") 
+#
 
@@
 scores_target <- eval_forecasts(
-  filtered_data, 
+  filtered_data[model %in% regular_models], 
   summarise_by = c("model", "target_type", "classification", "forecast_date")
@@
 scores_full <- eval_forecasts(
-  filtered_data, 
+  filtered_data[model %in% regular_models], 
   summarise_by = c("model", "location_target", "horizon", "forecast_date"), 
@@
 scores_target <- eval_forecasts(
-  filtered_data, 
+  filtered_data[model %in% regular_models], 
   summarise_by = c("model", "target_type", "classification", "range", "quantile"), 

### 2021-06-08 R/utils.R

@@ -50,13 +50,13 @@ dates_to_epiweek <- function(df){
 #' `epiweek`.
 #' @return A data frame grouped by week.
 #' @export
-#' @importFrom grates as_yrwk
+#' @importFrom grates as_yearweek
 #' @importFrom dplyr filter group_by summarise ungroup select
 make_weekly <- function(inc) {
   inc_weekly <- inc %>%
     dates_to_epiweek() %>% 
     filter(epiweek_full == TRUE) %>% 
-    mutate(year_week = as_yrwk(date, firstday = 7L)) %>%
+    mutate(year_week = as_yearweek(date, firstday = 7L)) %>%
     group_by(location, location_name, year_week) %>%
     summarise(value = sum(value), 
               target_end_date = max(date),

### 2021-06-11 analysis/analysis.Rmd
update plots

@@
 options(knitr.kable.NA = '')
-library(covid.german.forecasts)
 library(here)
@@
 library(stringr)
+library(covid.german.forecasts)
 
@@
     geom_line() +
+    geom_line(aes(y = true_value), color = "black") + 
     theme_light() + 
@@
   geom_point() + 
+  geom_line() + 
   theme_light() + 

### 2021-06-11 data-raw/paper.R

@@ -26,7 +26,8 @@ file_paths <- purrr::map(folders,
                            return(out)}) %>%
   unlist()
 file_paths <- file_paths[grepl(".csv", file_paths)]
-file_paths <- file_paths[!(grepl("EpiExpert_Rt", file_paths))]
+file_paths <- file_paths[!(grepl("EpiExpert_Rt", file_paths)) & 
+                           !(grepl("included_models", file_paths))]
   
 # load all past forecasts ------------------------------------------------------
 # ceate a helper function to get model name from a file path

### 2021-06-15 analysis/analysis.Rmd
update plots

@@
 library(covid.german.forecasts)
-
-```
-
-## Todo
-
--   [ ] final decision on the Christmas period. Do we want to also exclude target end dates, or just forceast dates? Do we want to exclude the 2nd of January?
--   [ ] look more closely into the stratification: do we want the current thing or do we want something else that has the outcome in it as well?
-One thing I thought was have another category: inflection or no inflection and also score that?
--   [ ] Talk to Johannes about whether we want to score log forecasts and log truth values instead.
-I for now removed that part for the following reasons: I currently don't have a good feeling for what it does.
-I'm somewhat hesitant that establishing a completely new way of scoring forecasts could be beyond the scope of this paper.
-Very happy to switch to it entirely if we agree it is the better metric, but not sure we are at that point yet.
+library(grates)
+library(ggdist)
+
+# define colors for deaths and cases
+colcases <- brewer.pal(name = "Accent", n = 5)[-c(1, 4)]
+coldeaths <- brewer.pal(name = "Accent", n = 5)[-4]
+
+```
 
@@
   ggplot(aes(y = true_value, x = target_end_date)) + 
-  geom_point(size = 0.3) + 
-  geom_line(size = 0.5) + 
+  geom_point(size = 0.3, alpha = 0.4) + 
+  geom_line(size = 0.5, alpha = 0.4) + 
+  geom_line(data = truth_data, aes(y = true_value / 7)) + 
   facet_grid(target_type ~ location_name, scales = "free") + 
   labs(y = "Observed values", x = "Date") + 
+  scale_x_date(limits = c(min(forecast_dates$full_hub_period) - 28, 
+                            max(forecast_dates$full_hub_period)))
   theme_light()
@@
   geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
-                 size = 1.5,
+                 size = 1.7,
                  alpha = 1,
-                 position = position_dodge(width = 6)) + 
+                 position = position_dodge(width = 4)) + 
+    geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
+                   size = 1.7,
+                   alpha = 0.1,
+                   position = position_dodge(width = 4)) +   
     geom_point(aes(shape = classification)) + 
@@
   theme(legend.position = "bottom") + 
-  theme(panel.background = element_rect(fill = "#e1f0fe")) + 
+  # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
   scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
@@
 df <- unfiltered_data[model %in% regular_models &
-                        quantile %in% c(0.025, 0.25, 0.75, 0.975)] %>%
+                        quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
   dcast(... ~ quantile, value.var = "prediction")
@@
     truth_and_pred_plot() + 
-    scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[-2]) + 
+    scale_color_manual(values = colcases) + 
     labs(y = "Cases", x = "")
@@
   truth_and_pred_plot()  + 
-  scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
+  scale_color_manual(values = coldeaths) + 
   annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
@@
 
-pairwise <- pairwise_comparison(scores_target_forecastdate, 
-                                summarise_by = summarise_by, 
-                                baseline = "Baseline")
-pairwise <- pairwise[compare_against == "Baseline"]
+# pairwise <- pairwise_comparison(scores_target_forecastdate, 
+#                                 summarise_by = summarise_by, 
+#                                 baseline = "Baseline")
+# pairwise <- pairwise[compare_against == "Baseline"]
 
@@
   #               ymax = Inf), fill = "lightgrey", alpha = 0.002) +
-  theme(panel.background = element_rect(fill = "#e1f0fe")) +
-  scale_y_log10() + 
+  # theme(panel.background = element_rect(fill = "#e1f0fe")) +
+  # scale_y_log10() + 
   scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
@@
 for (i in 1:4) {
-  scores_over_time_case <- pairwise[horizon == i & target_type == "case"] %>%
-    scores_over_time_plot() + 
-    scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[-2]) + 
+  scores_over_time_case <- scores_target_forecastdate[horizon == i & target_type == "case"] %>%
+    scores_over_time_plot(y = "interval_score") + 
+    scale_color_manual(values = colcases) + 
     labs(y = "WIS rel. to baseline", x = "")
@@
 
-  scores_over_time_deaths <- pairwise[horizon == i & target_type == "death"] %>%
-    scores_over_time_plot() + 
+  scores_over_time_deaths <- scores_target_forecastdate[horizon == i & target_type == "death"] %>%
+    scores_over_time_plot(y = "interval_score") + 
     scale_color_brewer(palette = "Accent") + 
@@
   compute_relative_skill = TRUE,
-  baseline = "Baseline", 
   sd = TRUE, 
@@
   compute_relative_skill = TRUE, 
-  baseline = "Baseline", 
   sd = TRUE, 
@@
     theme(legend.position = "bottom") + 
-    theme(panel.background = element_rect(fill = "#e1f0fe")) + 
+    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
     scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
@@
 scores <- eval_forecasts(
-  filtered_data[(model %in% regular_models) & grepl("2", target)], 
-  summarise_by = c("model", "target_type", "location_name", "forecast_date", 
-                   "target_phase",
+  filtered_data[(model %in% regular_models)], 
+  summarise_by = c("model", "target_type", "location_name", "horizon", 
+                   "forecast_date", "target_phase",
                    "location_target", "classification"),
-  compute_relative_skill = TRUE, 
-  baseline = "Baseline"
+  compute_relative_skill = FALSE
 )
@@
 
-# look at variance to check
-scores[, .(sd = sd(scaled_rel_skill)), by = c("model")]
-
-distribution_plot <- function(df, x = "scaled_rel_skill") {
-  df %>%
-    ggplot(aes_string(y = "model", x = x, 
-                      group = "model")) + 
-    geom_density_ridges(aes(fill = model), 
-                                  quantile_lines = TRUE, quantiles = 0.5, 
-                                  rel_min_height = 0.01) + 
-    geom_vline(aes(xintercept = 1), alpha = 0.4) + 
-    scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
-    theme(panel.background = element_rect(fill = "#e1f0fe")) +
-    theme(legend.position = "bottom") + 
-    labs(y = "Scaled relative skill") + 
-    scale_x_log10(labels = scales::number_format(accuracy = 0.1))
-}
-
-distribution_plot_wis <- function(df, x = "interval_score") {
-  df %>%
-    ggplot(aes_string(y = "model", x = x, 
-                      group = "model", fill = "model")) + 
-    geom_density_ridges(aes(fill = model), 
-                        quantile_lines = TRUE, quantiles = 0.5, 
-                        rel_min_height = 0.005, 
-                        scale = 0.9, 
-                        jittered_points = TRUE, 
-                        position = position_points_jitter(width = 0.05, height = 0),
-                        point_size = 1.5, 
-                        point_shape = 21,
-                        #point_shape = '|',
-                        point_alpha = 1, 
-                        alpha = 0.7) + 
-    geom_density_ridges(quantile_lines=TRUE,
-                        quantile_fun=function(x,...) mean(x), 
-                        linetype = "dotted", 
-                        alpha = 0, 
-                        scale = 0.9, 
-                        rel_min_height = 0.01) +
-    scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
-    # scale_color_manual(aesthetics = "point_color", 
-    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
-    theme(panel.background = element_rect(fill = "#e1f0fe")) +
-    theme(legend.position = "bottom") + 
-    labs(y = "Model", x = "Weighted interval score") + 
-  scale_x_continuous(labels = scales::label_number(suffix = "k", 
-                                                   scale = 1e-3, 
-                                                   accuracy = NULL))
-}
-
-p_combined <- distribution_plot(df = scores[model != "Baseline"]) + 
-  facet_wrap(~ target_type, ncol = 1)
-
-p_combined_wis <- distribution_plot_wis(df = scores, 
-                                        x = "interval_score") +
-  facet_wrap(~ target_type, ncol = 1, scales = "free") + 
-  theme(plot.margin=unit(c(0,0.4,0,0),"cm"))
-
-p_combined_ae <- distribution_plot_wis(df = scores, 
-                                        x = "aem") +
-  facet_wrap(~ target_type, ncol = 1, scales = "free_x")
-
-p <- distribution_plot(df = scores[model != "Baseline"]) + 
-  theme(axis.title.y=element_blank(),
-        axis.text.y=element_blank(), 
-        axis.ticks.y = element_blank()) + 
-  facet_wrap(~ location_target, ncol = 2)
-
-p_wis <- distribution_plot_wis(df = scores) + 
-  theme(axis.title.y=element_blank(),
-        axis.text.y=element_blank(), 
-        axis.ticks.y = element_blank()) + 
-  facet_wrap(~ location_target, ncol = 2, scale = "free")
-
-p_ae <- distribution_plot_wis(df = scores, x = "aem") + 
-  theme(axis.title.y=element_blank(),
-        axis.text.y=element_blank(), 
-        axis.ticks.y = element_blank()) + 
-  facet_wrap(~ location_target, ncol = 2, scale = "free")
-
-```
-
-```{r}
 # scores for different phases of the epidemic
@@
 
-scores[, .(target_count = .N), by = c("target_phase", "model")]
-
-p_phases <- distribution_plot(df = scores[model != "Baseline"]) + 
-  facet_wrap( ~ target_phase)
-
-p_phases_wis <- distribution_plot_wis(df = scores) + 
+distribution_plot_wis <- function(df, x = "interval_score") {
+  df %>%
+    ggplot(aes_string(y = "model", x = x, 
+                      group = "model", fill = "model")) + 
+    # geom_density_ridges(aes(fill = model, color = NA),
+    #                     rel_min_height = 0.005,
+    #                     scale = 0.9,
+    #                     # jittered_points = TRUE,
+    #                     # position = position_points_jitter(width = 0.05, height = 0),
+    #                     point_size = 1.5,
+    #                     point_shape = 21,
+    #                     #point_shape = '|',
+    #                     point_alpha = 1,
+    #                     alpha = 0.3) +
+    ggdist::stat_dots(aes(color = model)) + 
+    ggdist::stat_pointinterval(point_interval = mean_qi, size = 3, shape = 16, fill = "black", .width = NA) + 
+    ggdist::stat_pointinterval(point_interval = median_qi, size = 3, shape = 15, fill = "black", .width = NA) + 
+        facet_wrap(~ target_type, ncol = 1, scales = "free") + 
+    theme(plot.margin=unit(c(0,0.4,0,0),"cm")) +
+    # geom_density_ridges(quantile_lines=TRUE,
+    #                     quantile_fun=function(x,...) mean(x), 
+    #                     linetype = "dotted", 
+    #                     alpha = 0, 
+    #                     scale = 0.9, 
+    #                     rel_min_height = 0.01) +
+    scale_fill_manual(values = coldeaths) + 
+    scale_color_manual(values = coldeaths) + 
+    # scale_color_manual(aesthetics = "point_color", 
+    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
+    # theme(panel.background = element_rect(fill = "#e1f0fe")) +
+    theme(legend.position = "bottom") + 
+    labs(y = "Model", x = "Weighted interval score") + 
+  scale_x_continuous(labels = scales::label_number(suffix = "k", 
+                                                   scale = 1e-3, 
+                                                   accuracy = NULL))
+}
+
+for (i in 1:4) {
+  p_combined_wis <- distribution_plot_wis(df = scores[horizon == i], 
+                                          x = "interval_score") +
+    facet_wrap(~ target_type, ncol = 1, scales = "free") + 
+    theme(plot.margin=unit(c(0,0.4,0,0),"cm"))
+
+  p_wis <- distribution_plot_wis(df = scores[horizon == i]) + 
+  theme(axis.title.y=element_blank(),
+        axis.text.y=element_blank(), 
+        axis.ticks.y = element_blank()) + 
+  facet_wrap(~ location_target, ncol = 2, scale = "free")
+
+  p_phases_wis <- distribution_plot_wis(df = scores[horizon == i]) + 
     facet_wrap( ~ target_phase, scales = "free_x")
-
-p_phases_ae <- distribution_plot_wis(df = scores, x = "aem") + 
-  facet_wrap( ~ target_phase, scales = "free_x")
-
-scores[, .(n = .N), by = "target_phase"]
-
-```
-
-```{r fig.height=10, fig.width=15}
-
-pl <- wrap_plots(p_combined, p, widths = c(1, 2)) / p_phases + 
-  plot_layout(guides = "collect") & 
-  plot_annotation(tag_levels = 'A') &
-  theme(legend.position = 'bottom')
-
-ggsave("plots/distribution_scores.png", plot = pl, height = 9)
 
@@
 
-ggsave("plots/distribution_scores_wis.png", pl_wis, height = 11, width = 9)
+  ggsave(here("analysis", "plots", 
+              paste0("distribution_scores_wis-", i, ".png")), 
+         pl_wis, height = 11, width = 9)
+
+}
+
+p_combined_ae <- distribution_plot_wis(df = scores, 
+                                        x = "aem") +
+  facet_wrap(~ target_type, ncol = 1, scales = "free_x")
+
+# p <- distribution_plot(df = scores[model != "Baseline"]) + 
+#   theme(axis.title.y=element_blank(),
+#         axis.text.y=element_blank(), 
+#         axis.ticks.y = element_blank()) + 
+#   facet_wrap(~ location_target, ncol = 2)
+
+p_ae <- distribution_plot_wis(df = scores, x = "aem") + 
+  theme(axis.title.y=element_blank(),
+        axis.text.y=element_blank(), 
+        axis.ticks.y = element_blank()) + 
+  facet_wrap(~ location_target, ncol = 2, scale = "free")
+
+```
+
+```{r}
+scores[, .(target_count = .N), by = c("target_phase", "model")]
+
+# p_phases <- distribution_plot(df = scores[model != "Baseline"]) + 
+#   facet_wrap( ~ target_phase)
+
+p_phases_ae <- distribution_plot_wis(df = scores, x = "aem") + 
+  facet_wrap( ~ target_phase, scales = "free_x")
+
+scores[, .(n = .N), by = "target_phase"]
+
+```
+
+```{r fig.height=10, fig.width=15}
+
+# pl <- wrap_plots(p_combined, p, widths = c(1, 2)) / p_phases + 
+#   plot_layout(guides = "collect") & 
+#   plot_annotation(tag_levels = 'A') &
+#   theme(legend.position = 'bottom') 
+# 
+# ggsave("plots/distribution_scores.png", plot = pl, height = 9)
 
@@
   summarise_by = c("model", "location_target", "horizon", "forecast_date"), 
-  compute_relative_skill = FALSE, 
-  baseline = "Baseline"
+  compute_relative_skill = FALSE
 )
@@
   #           size = 2) +
-  theme(panel.background = element_rect(fill = "#e1f0fe")) +
+  # theme(panel.background = element_rect(fill = "#e1f0fe")) +
   scale_color_brewer(palette = "Accent") + 
@@
                               summarise_by = c("model", "target_type", "target"), 
-                              compute_relative_skill = TRUE, 
-                              baseline = "Baseline")
+                              compute_relative_skill = TRUE)
 
@@
 ```
+
+``` {r}
+
+scores <- eval_forecasts(filtered_data[model %in% regular_models], 
+                         summarise_by = c("model", "target_type", "horizon"), 
+                         quantiles = 0.5, 
+                         sd = TRUE)
+
+# mean performance
+p_mean <- scores %>%
+  ggplot(aes(x = horizon, y = interval_score, group = model, color = model)) + 
+  geom_point() + 
+  geom_line() + 
+  facet_wrap(~ target_type, scales = "free_y") + 
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths)
+
+ggsave(here("analysis", "plots", "aggregate-performance-mean.png"))
+
+# median performance
+p_median <- scores %>%
+  ggplot(aes(x = horizon, y = interval_score_0.5, group = model, color = model)) + 
+  geom_point() + 
+  geom_line() + 
+  facet_wrap(~ target_type, scales = "free_y") + 
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths)
+
+ggsave(here("analysis", "plots", "aggregate-performance-median.png"))
+
+# sd of performance
+p_wis_sd <- scores %>%
+  ggplot(aes(x = horizon, y = interval_score_sd, group = model, color = model)) + 
+  geom_point() + 
+  geom_line() + 
+  facet_wrap(~ target_type, scales = "free_y") + 
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths)
+
+ggsave(here("analysis", "plots", "aggregate-performance-wis-sd.png"))
+
+# sharpness of performance
+p_sharpness <- scores %>%
+  ggplot(aes(x = horizon, y = sharpness, group = model, color = model)) + 
+  geom_point() + 
+  geom_line() + 
+  facet_wrap(~ target_type, scales = "free_y") + 
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths)
+
+ggsave(here("analysis", "plots", "aggregate-performance-sharpness.png"))
+
+# absolute error of performance
+p_aem <- scores %>%
+  ggplot(aes(x = horizon, y = aem, group = model, color = model)) + 
+  geom_point() + 
+  geom_line() + 
+  facet_wrap(~ target_type, scales = "free_y") + 
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths)
+
+ggsave(here("analysis", "plots", "aggregate-performance-aem.png"))
+
+# bias
+p_bias <- scores %>%
+  ggplot(aes(x = horizon, y = bias, group = model, color = model)) + 
+  geom_point() + 
+  geom_line() + 
+  facet_wrap(~ target_type, scales = "free_y") + 
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths)
+
+ggsave(here("analysis", "plots", "aggregate-performance-bias.png"))
+
+# coverage
+scores <- eval_forecasts(filtered_data[model %in% regular_models], 
+                         summarise_by = c("model", "target_type", "horizon", "range"), 
+                         quantiles = 0.5, 
+                         sd = TRUE)
+
+scores[range %in% c(50, 90)] %>%
+  ggplot(aes(x = horizon, y = coverage, group = range, color = range)) + 
+  geom_point() + 
+  geom_line() + 
+  facet_wrap(model ~ target_type , scales = "free_y")
+
+p_cov50 <- scores[range %in% c(50)] %>%
+  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
+  geom_point() + 
+  geom_line() + 
+  facet_wrap(~ target_type) + 
+  geom_hline(yintercept = 0.5, linetype = "dashed") +
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths)
+
+ggsave(here("analysis", "plots", "aggregate-performance-coverage50.png"))
+
+p_cov90 <- scores[range %in% c(90)] %>%
+  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
+  geom_point() + 
+  geom_line() + 
+  facet_wrap(~ target_type) + 
+  geom_hline(yintercept = 0.9, linetype = "dashed") +
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths)
+
+ggsave(here("analysis", "plots", "aggregate-performance-coverage90.png"))
+
+p_combined <- (p_mean + p_median) / 
+  (p_aem + p_wis_sd) / 
+  (p_sharpness + p_bias) / 
+  (p_cov50 + p_cov90) +  
+    plot_layout(guides = "collect") & 
+    plot_annotation(tag_levels = 'A') &
+    theme(legend.position = 'bottom')
+
+ggsave(here("analysis", "plots", "aggregate-performance-all.png"), 
+       height = 12, width = 10)
+
+```
+
+## Plots with all forecasts
+
+```{r}
+# only select every second forecast date to stratify
+df <- unfiltered_data[model %in% regular_models &
+                        quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
+  dcast(... ~ quantile, value.var = "prediction")
+df <- merge(
+  df[, c("classification", "speed") := NULL], 
+  copy(epitrend)[, forecast_date := NULL], 
+  by = c("target_end_date", "location_name", "target_type")
+)
+
+df[, forecast_date := as.Date(forecast_date)]
+df[, i := as.numeric(forecast_date - as.Date(min(forecast_date))) %% 2 + 1]
+
+plot_forecast <- function(df, m = "Renewal") {
+  min_date <- min(forecast_dates$unfiltered)
+  plot_dates <- c((min_date - c(28, 21, 14, 7)), forecast_dates$unfiltered)
+  plot_dates <- plot_dates - 2
+  d <- copy(truth_data)[, location_target := paste0(str_to_sentence(target_type), 
+                                                    "s", " in ", location_name)]
+  daily <- copy(dailytruth_data)[, location_target := paste0(str_to_sentence(target_type), 
+                                                             "s", " in ", location_name)]
+  daily[, week := as_yearweek(target_end_date, firstday = 7L)]
+  daily[, sum_val := sum(true_value), by = c("week", "location_target")]
+  daily[, scaled_val := true_value - sum_val / 7]
+
+  df <- copy(df)[, forecast_date := as.factor(forecast_date)]
+
+  df[model == m] %>%
+    ggplot(aes(y = true_value, x = target_end_date)) + 
+    geom_line() + 
+    geom_line(data = d[target_end_date %in% plot_dates],
+              aes(y = true_value, x = target_end_date)) +
+    geom_line(data = daily[target_end_date >= min(plot_dates) & target_end_date <= max(plot_dates)],
+              aes(y = scaled_val, x = target_end_date), alpha = 0.4) +
+    geom_vline(aes(xintercept = as.Date(forecast_date), 
+                   color = forecast_date), alpha = 0.3, size = 0.4) + 
+    ggplot2::geom_ribbon(ggplot2::aes(ymin = `0.025`, ymax = `0.975`, 
+                                      group = forecast_date, 
+                                      fill = forecast_date), alpha = 0.3) +
+    ggplot2::geom_ribbon(ggplot2::aes(ymin = `0.25`, ymax = `0.75`, 
+                                      group = forecast_date, 
+                                      fill = forecast_date), alpha = 0.5) +
+    ggplot2::geom_line(aes(y = `0.5`,group = forecast_date, 
+                           colour = forecast_date), alpha = 1) +
+    geom_point() + 
+    theme_light() + 
+    facet_grid(location_target ~ i, scale = "free_y") + 
+    theme(legend.position = "bottom") 
+    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
+    # scale_y_log10() 
+}
+
+for (m in c("Renewal", "Convolution", "Crowd forecast")) {
+  p <- plot_forecast(df[horizon <= 2], m = m)
+
+  saveRDS(p, file = here("analysis", "plots", 
+                         paste0("all-forecasts-", m,".RDS")))
+
+  ggsave(here("analysis", "plots", 
+                         paste0("all-forecasts-", m,".png")), 
+         height = 15, width = 10)
+
+}
+
+```

### 2021-06-15 data-raw/paper.R

@@ -100,7 +100,7 @@ usethis::use_data(prediction_data, overwrite = TRUE)
 
 
 # store names of regular models and ensemble models ----------------------------
-regular_models <- c("Renewal", "Baseline", "Hub-ensemble", "Crowd forecast", "Convolution")
+regular_models <- c("Renewal", "Hub-ensemble", "Crowd forecast", "Convolution")
 usethis::use_data(regular_models, overwrite = TRUE)
 
 ensemble_models <- unique(prediction_data$model)

### 2021-06-15 analysis/analysis.Rmd
update plots

@@
 
-for (horizon in 1:4) {
+for (i in 1:4) {
   # plot for cases
-  truth_vs_forecast_cases <- df[grepl(horizon, target)] %>%
+  truth_vs_forecast_cases <- df[grepl(i, target)] %>%
     dplyr::filter(target_type == "case") %>%
@@
   # plot for deaths
-  truth_vs_forecast_deaths <- df[grepl(horizon, target)] %>%
+  truth_vs_forecast_deaths <- df[grepl(i, target)] %>%
   dplyr::filter(target_type == "death") %>%
@@
   filename <- here("analysis", "plots", 
-                   paste0("truth-and-", horizon, "-wk-ahead_deaths"))
+                   paste0("truth-and-", i, "-wk-ahead_deaths"))
   ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_deaths)
@@
     scores_over_time_plot(y = "interval_score") + 
-    scale_color_brewer(palette = "Accent") + 
+    scale_color_manual(values = colcases) + 
     annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,

### 2021-06-15 analysis/analysis.Rmd
update plot

@@
     scores_over_time_plot(y = "interval_score") + 
-    scale_color_manual(values = colcases) + 
+    scale_color_manual(values = coldeaths) + 
     annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
@@
                                                    scale = 1e-3, 
-                                                   accuracy = NULL))
+                                                   accuracy = NULL)) + 
+    theme_light()
 }
@@
   # theme(panel.background = element_rect(fill = "#e1f0fe")) +
-  scale_color_brewer(palette = "Accent") + 
+  scale_color_manual(values = coldeaths) + 
+  scale_fill_manual(values = coldeaths) + 
   geom_point(data = means, 
@@
              position = position_dodge2(width = 0.5)) + 
-  scale_fill_brewer(palette = "Accent") + 
   scale_y_log10() + 

### 2021-06-15 analysis/analysis.Rmd
update plots

@@
                  position = position_dodge(width = 4)) + 
-    geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
-                   size = 1.7,
-                   alpha = 0.1,
-                   position = position_dodge(width = 4)) +   
+    # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
+    #                size = 1.7,
+    #                alpha = 0.1,
+    #                position = position_dodge(width = 4)) +   
     geom_point(aes(shape = classification)) + 

### 2021-06-15 analysis/analysis.Rmd
update plots

--- 2021-06-15 analysis/analysis.Rmd
@@
 # create helper function for the plot ------------------------------------------
-truth_and_pred_plot <- function(df) {
+truth_and_pred_plot <- function(df, ttype = "case") {
   p <- df %>%
+    dplyr::filter(target_type == ttype) %>%
     ggplot(aes(y = true_value, x = target_end_date)) + 
@@
                    position = position_dodge(width = 4)) + 
-    geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
-                   size = 1.7,
-                   alpha = 0.1,
-                   position = position_dodge(width = 4)) +   
-    geom_point(aes(shape = classification)) + 
-  geom_line() + 
+    # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
+    #                size = 1.7,
+    #                alpha = 0.1,
+    #                position = position_dodge(width = 4)) +   
+    geom_point(data = unfiltered_data[target_type == ttype], 
+               aes(shape = classification)) + 
+    geom_line(data = unfiltered_data[target_type == ttype]) + 
     theme_light() + 
@@
     # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
-  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
+    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 7, 
                             max(forecast_dates$full_hub_period)))
@@
   truth_vs_forecast_cases <- df[grepl(i, target)] %>%
-    dplyr::filter(target_type == "case") %>%
-    truth_and_pred_plot() + 
+    truth_and_pred_plot(ttype = "case") + 
     scale_color_manual(values = colcases) + 
@@
   truth_vs_forecast_deaths <- df[grepl(i, target)] %>%
-  dplyr::filter(target_type == "death") %>%
-  truth_and_pred_plot()  + 
+  truth_and_pred_plot(ttype = "death")  + 
   scale_color_manual(values = coldeaths) + 

### 2021-06-15 analysis/analysis.Rmd
update plots

@@
     # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
-    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 7, 
+    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                             max(forecast_dates$full_hub_period)))

### 2021-06-15 analysis/analysis.Rmd
update plots

@@
   filename <- here("analysis", "plots", 
-                   paste0("truth-and-", horizon, "-wk-ahead_cases"))
+                   paste0("truth-and-", i, "-wk-ahead_cases"))
   ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_cases)
@@
   # scale_y_log10() + 
-  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
+  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                           max(forecast_dates$full_hub_period)))

### 2021-06-17 analysis/analysis.Rmd
update plots

@@
     #                     alpha = 0.3) +
+    ggdist::stat_slab(alpha = 0.3, scale = 0.8, normalize = "panels") +
+  # ggridges::geom_density_ridges(aes(color = NA), scale = 1.3) + 
     ggdist::stat_dots(aes(color = model)) + 

### 2021-06-17 analysis/analysis.Rmd
update tables

@@
   summarise_by = c("model", "horizon", "target_type"), 
-  compute_relative_skill = TRUE,
+  compute_relative_skill = FALSE,
   sd = TRUE, 
@@
   summarise_by = c("model", "horizon", "target_type"), 
-  compute_relative_skill = TRUE, 
+  compute_relative_skill = FALSE, 
   sd = TRUE, 

### 2021-06-17 analysis/analysis.Rmd
update plots

--- 2021-06-17 analysis/analysis.Rmd
@@
                         !(grepl("interval", names(df)))]
+del_cols <- c(del_cols, "coverage_deviation")
 df[, (del_cols) := NULL]
@@
   theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths)
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "mean WIS", x = "Forecast horizon") + 
+  theme_light()
 
@@
   theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths)
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "median WIS", x = "Forecast horizon") + 
+  theme_light()
 
@@
   theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths)
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "WIS - standard deviation", x = "Forecast horizon") + 
+  theme_light()
 
@@
   theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths)
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "sharpness", x = "Forecast horizon") + 
+  theme_light()
 
@@
   theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths)
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "Absolute error", x = "Forecast horizon") + 
+  theme_light()
 
@@
   theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths)
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "Bias", x = "Forecast horizon") + 
+  theme_light()
 
@@
   theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths)
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "Empirical coverage", x = "Forecast horizon") + 
+  theme_light()
 
@@
   theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths)
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "empirical coverage", x = "Forecast horizon") + 
+  theme_light()
 

### 2021-06-19 analysis/analysis.Rmd
change plot theme

@@
 library(ggdist)
+library(ggthemes)
 
@@
                             max(forecast_dates$full_hub_period)))
-  theme_light()
+  theme_minimal()
 
@@
     geom_line(data = unfiltered_data[target_type == ttype]) + 
-    theme_light() + 
+    theme_minimal() + 
     facet_wrap(~ location_target, scales = "free", ncol = 2) + 
@@
   geom_point(aes(shape = classification, colour = model)) + 
-  theme_light() + 
+  theme_minimal() + 
   facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
@@
   sd = TRUE, 
-  quantiles = 0.5
-) %>%
+  quantiles = 0.5) %>%
   merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))
@@
     geom_line(aes(y = true_value), color = "black") + 
-    theme_light() + 
+    theme_minimal() + 
     facet_wrap(~ location_target, scales = "free", ncol = 2) + 
@@
                                                    accuracy = NULL)) + 
-    theme_light()
+    theme_minimal()
 }
@@
   geom_bar() + 
-  theme_light() + 
+  theme_minimal() + 
   labs(x = "Number of available submissions", 
@@
   geom_line() + 
-  theme_light() + 
+  theme_minimal() + 
   facet_wrap(~ target_type) + 
@@
   facet_wrap(~ target_type, scales = "free_y") + 
+  theme_minimal() + 
   theme(legend.position = "bottom") + 
   scale_color_manual(values = coldeaths) + 
-  labs(y = "mean WIS", x = "Forecast horizon") + 
-  theme_light()
+  labs(y = "mean WIS", x = "Forecast horizon")
 
@@
   labs(y = "median WIS", x = "Forecast horizon") + 
-  theme_light()
+  theme_minimal()
 
@@
   labs(y = "WIS - standard deviation", x = "Forecast horizon") + 
-  theme_light()
+  theme_minimal()
 
@@
   labs(y = "sharpness", x = "Forecast horizon") + 
-  theme_light()
+  theme_minimal()
 
@@
   labs(y = "Absolute error", x = "Forecast horizon") + 
-  theme_light()
+  theme_minimal()
 
@@
   labs(y = "Bias", x = "Forecast horizon") + 
-  theme_light()
+  theme_minimal()
 
@@
   geom_hline(yintercept = 0.5, linetype = "dashed") +
-  theme(legend.position = "bottom") + 
   scale_color_manual(values = coldeaths) + 
   labs(y = "Empirical coverage", x = "Forecast horizon") + 
-  theme_light()
+  theme_minimal() + 
+  expand_limits(y=c(0, 1)) + 
+  theme(legend.position = "bottom") + 
+  scale_y_continuous(labels = scales::percent)
 
@@
   facet_wrap(~ target_type) + 
-  geom_hline(yintercept = 0.9, linetype = "dashed") +
+  theme_minimal() + 
+  theme(legend.position = "bottom") + 
+  geom_hline(yintercept = 0.90, linetype = "dashed") +
   theme(legend.position = "bottom") + 
@@
   labs(y = "empirical coverage", x = "Forecast horizon") + 
-  theme_light()
+  expand_limits(y=c(0, 1)) + 
+  scale_y_continuous(labels = scales::percent)
 
@@
        height = 12, width = 10)
+
+```
+
+```{r}
+scores <- eval_forecasts(filtered_data[model %in% 
+                                         ensemble_models[!grepl("mean", ensemble_models)]], 
+                         summarise_by = c("model", "target_type", "horizon"), 
+                         quantiles = 0.5, 
+                         sd = TRUE)
+
+# mean performance
+p_mean_ens <- scores %>%
+  ggplot(aes(x = horizon, y = interval_score, group = model, color = model)) + 
+  geom_point() + 
+  geom_line() + 
+  facet_wrap(~ target_type, scales = "free_y") + 
+  theme_minimal() + 
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "mean WIS", x = "Forecast horizon")
+
+ggsave(here("analysis", "plots", "aggregate-performance-mean.png"))
+
+```
+
+``` {r}
+scores <- eval_forecasts(filtered_data[model %in% regular_models], 
+                         summarise_by = c("model", "target_type", "location", 
+                                          "horizon", "forecast_date"))
+scores <- scores[order(interval_score), , by = c("target_type", "location", 
+                                               "horizon", "forecast_date")]
+scores <- scores[, ranking := 1:.N, by = c("target_type", "location", 
+                                           "horizon", "forecast_date")]
 
@@
     geom_point() + 
-    theme_light() + 
+    theme_minimal() + 
     facet_grid(location_target ~ i, scale = "free_y") + 

### 2021-06-19 analysis/analysis.Rmd
update plots

@@
 coldeaths <- brewer.pal(name = "Accent", n = 5)[-4]
+
+# colcases <- few_pal()(4)[-1]
+# coldeaths <- few_pal()(4)
 
@@
   scale_color_manual(values = coldeaths) + 
-  labs(y = "mean WIS", x = "Forecast horizon")
-
-ggsave(here("analysis", "plots", "aggregate-performance-mean.png"))
+  labs(y = "mean WIS", x = NULL)
+
+# ggsave(here("analysis", "plots", "aggregate-performance-mean.png"))
 
@@
   scale_color_manual(values = coldeaths) + 
-  labs(y = "median WIS", x = "Forecast horizon") + 
+  labs(y = "median WIS", x = NULL) + 
   theme_minimal()
 
-ggsave(here("analysis", "plots", "aggregate-performance-median.png"))
+# ggsave(here("analysis", "plots", "aggregate-performance-median.png"))
 
@@
   scale_color_manual(values = coldeaths) + 
-  labs(y = "WIS - standard deviation", x = "Forecast horizon") + 
+  labs(y = "WIS - sd", x = NULL) + 
   theme_minimal()
 
-ggsave(here("analysis", "plots", "aggregate-performance-wis-sd.png"))
+# ggsave(here("analysis", "plots", "aggregate-performance-wis-sd.png"))
 
@@
   scale_color_manual(values = coldeaths) + 
-  labs(y = "sharpness", x = "Forecast horizon") + 
+  labs(y = "sharpness", x = NULL) + 
   theme_minimal()
 
-ggsave(here("analysis", "plots", "aggregate-performance-sharpness.png"))
+# ggsave(here("analysis", "plots", "aggregate-performance-sharpness.png"))
 
@@
   scale_color_manual(values = coldeaths) + 
-  labs(y = "Absolute error", x = "Forecast horizon") + 
+  labs(y = "Absolute error", x = NULL) + 
   theme_minimal()
 
-ggsave(here("analysis", "plots", "aggregate-performance-aem.png"))
+# ggsave(here("analysis", "plots", "aggregate-performance-aem.png"))
 
@@
   geom_line() + 
-  facet_wrap(~ target_type, scales = "free_y") + 
+  facet_wrap(~ target_type) + 
+  geom_hline(yintercept = 0, linetype = "dashed") +
   theme(legend.position = "bottom") + 
   scale_color_manual(values = coldeaths) + 
-  labs(y = "Bias", x = "Forecast horizon") + 
+  expand_limits(y=c(-0.2, 0.2)) + 
+  labs(y = "Bias", x = NULL) + 
   theme_minimal()
 
-ggsave(here("analysis", "plots", "aggregate-performance-bias.png"))
+# ggsave(here("analysis", "plots", "aggregate-performance-bias.png"))
 
@@
 
-ggsave(here("analysis", "plots", "aggregate-performance-coverage50.png"))
+# ggsave(here("analysis", "plots", "aggregate-performance-coverage50.png"))
 
@@
   scale_color_manual(values = coldeaths) + 
-  labs(y = "empirical coverage", x = "Forecast horizon") + 
+  labs(y = "Empirical coverage", x = "Forecast horizon") + 
   expand_limits(y=c(0, 1)) + 
@@
 
-ggsave(here("analysis", "plots", "aggregate-performance-coverage90.png"))
+# ggsave(here("analysis", "plots", "aggregate-performance-coverage90.png"))
 
@@
 ggsave(here("analysis", "plots", "aggregate-performance-all.png"), 
-       height = 12, width = 10)
+       height = 9.1, width = 10)
 

### 2021-06-19 analysis/analysis.Rmd
create new plots for comparing locations

@@
 
+### Aggregate performance across different horizons
+
 ``` {r}
@@
   scale_color_manual(values = coldeaths) + 
-  labs(y = "sharpness", x = NULL) + 
+  labs(y = "Sharpness", x = NULL) + 
   theme_minimal()
@@
   scale_color_manual(values = coldeaths) + 
-  labs(y = "Empirical coverage", x = "Forecast horizon") + 
+  labs(y = "Coverage - 50% PI", x = "Forecast horizon") + 
   theme_minimal() + 
@@
   scale_color_manual(values = coldeaths) + 
-  labs(y = "Empirical coverage", x = "Forecast horizon") + 
+  labs(y = "Coverage - 90% PI", x = "Forecast horizon") + 
   expand_limits(y=c(0, 1)) + 
@@
 
+### Aggregate performance across locations
+
+```{r}
+scores <- eval_forecasts(filtered_data[model %in% regular_models & horizon == 2], 
+                         summarise_by = c("model", "target_type", "location_name"), 
+                         quantiles = 0.5, 
+                         sd = TRUE)
+
+# mean performance
+p_mean <- scores %>%
+  ggplot(aes(x = location_name, y = interval_score, group = model, color = model)) + 
+  geom_point() + 
+  geom_line(linetype = "dashed", size = 0.3) + 
+  facet_wrap(~ target_type, scales = "free_y") + 
+  theme_minimal() + 
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "mean WIS", x = NULL)
+
+# mean performance
+p_mean <- scores %>%
+  ggplot(aes(x = location_name, y = interval_score, group = model, color = model)) + 
+  geom_point() + 
+  geom_line(linetype = "dashed", size = 0.3) + 
+  facet_wrap(~ target_type, scales = "free_y") + 
+  theme_minimal() + 
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "mean WIS", x = NULL)
+
+# ggsave(here("analysis", "plots", "aggregate-performance-mean.png"))
+
+# median performance
+p_median <- scores %>%
+  ggplot(aes(x = location_name, y = interval_score_0.5, group = model, color = model)) + 
+  geom_point() + 
+  geom_line(linetype = "dashed", size = 0.3) + 
+  facet_wrap(~ target_type, scales = "free_y") + 
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "median WIS", x = NULL) + 
+  theme_minimal()
+
+# ggsave(here("analysis", "plots", "aggregate-performance-median.png"))
+
+# sd of performance
+p_wis_sd <- scores %>%
+  ggplot(aes(x = location_name, y = interval_score_sd, group = model, color = model)) + 
+  geom_point() + 
+  geom_line(linetype = "dashed", size = 0.3) + 
+  facet_wrap(~ target_type, scales = "free_y") + 
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "WIS - sd", x = NULL) + 
+  theme_minimal()
+
+# ggsave(here("analysis", "plots", "aggregate-performance-wis-sd.png"))
+
+# sharpness of performance
+p_sharpness <- scores %>%
+  ggplot(aes(x = location_name, y = sharpness, group = model, color = model)) + 
+  geom_point() + 
+  geom_line(linetype = "dashed", size = 0.3) + 
+  facet_wrap(~ target_type, scales = "free_y") + 
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "Sharpness", x = NULL) + 
+  theme_minimal()
+
+# ggsave(here("analysis", "plots", "aggregate-performance-sharpness.png"))
+
+# absolute error of performance
+p_aem <- scores %>%
+  ggplot(aes(x = location_name, y = aem, group = model, color = model)) + 
+  geom_point() + 
+  geom_line(linetype = "dashed", size = 0.3) + 
+  facet_wrap(~ target_type, scales = "free_y") + 
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "Absolute error", x = NULL) + 
+  theme_minimal()
+
+# ggsave(here("analysis", "plots", "aggregate-performance-aem.png"))
+
+# bias
+p_bias <- scores %>%
+  ggplot(aes(x = location_name, y = bias, group = model, color = model)) + 
+  geom_point() + 
+  geom_line(linetype = "dashed", size = 0.3) + 
+  facet_wrap(~ target_type) + 
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths) + 
+  expand_limits(y=c(-0.2, 0.2)) + 
+  labs(y = "Bias", x = NULL) + 
+  theme_minimal()
+
+# ggsave(here("analysis", "plots", "aggregate-performance-bias.png"))
+
+# coverage
+scores <- eval_forecasts(filtered_data[model %in% regular_models], 
+                         summarise_by = c("model", "target_type", "location_name", "range"), 
+                         quantiles = 0.5, 
+                         sd = TRUE)
+
+p_cov50 <- scores[range %in% c(50)] %>%
+  ggplot(aes(x = location_name, y = coverage, group = model, color = model)) + 
+  geom_point() + 
+  geom_line(linetype = "dashed", size = 0.3) + 
+  facet_wrap(~ target_type) + 
+  geom_hline(yintercept = 0.5, linetype = "dashed") +
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "Coverage - 50% PI", x = "Location") + 
+  theme_minimal() + 
+  expand_limits(y=c(0, 1)) + 
+  theme(legend.position = "bottom") + 
+  scale_y_continuous(labels = scales::percent)
+
+# ggsave(here("analysis", "plots", "aggregate-performance-coverage50.png"))
+
+p_cov90 <- scores[range %in% c(90)] %>%
+  ggplot(aes(x = location_name, y = coverage, group = model, color = model)) + 
+  geom_point() + 
+  geom_line(linetype = "dashed", size = 0.3) + 
+  facet_wrap(~ target_type) + 
+  theme_minimal() + 
+  theme(legend.position = "bottom") + 
+  geom_hline(yintercept = 0.90, linetype = "dashed") +
+  theme(legend.position = "bottom") + 
+  scale_color_manual(values = coldeaths) + 
+  labs(y = "Coverage - 90% PI", x = "Location") + 
+  expand_limits(y=c(0, 1)) + 
+  scale_y_continuous(labels = scales::percent)
+
+# ggsave(here("analysis", "plots", "aggregate-performance-coverage90.png"))
+
+p_combined <- (p_mean + p_median) / 
+  (p_aem + p_wis_sd) / 
+  (p_sharpness + p_bias) / 
+  (p_cov50 + p_cov90) +  
+    plot_layout(guides = "collect") & 
+    plot_annotation(tag_levels = 'A') &
+    theme(legend.position = 'bottom')
+
+ggsave(here("analysis", "plots", "aggregate-performance-2-weeks-locations-all.png"), 
+       height = 9.1, width = 10)
+
+```
+
+}
 ```{r}

### 2021-06-21 analysis/analysis.Rmd
update plots

@@
   scale_x_date(limits = c(min(forecast_dates$full_hub_period) - 28, 
-                            max(forecast_dates$full_hub_period)))
+                            max(forecast_dates$full_hub_period))) + 
   theme_minimal()
@@
 truth_and_pred_plot <- function(df, ttype = "case") {
+
+  trend <- copy(epitrend)[, location_target := paste0(str_to_sentence(target_type), 
+                                                    "s", " in ", location_name)]
   p <- df %>%
@@
                    alpha = 1,
-                   position = position_dodge(width = 4)) + 
+                   position = position_dodge(width = 4.6)) + 
     # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
@@
     #                position = position_dodge(width = 4)) +   
-    geom_point(data = unfiltered_data[target_type == ttype], 
+    geom_point(data = trend[target_type == ttype],
                aes(shape = classification)) +
-    geom_line(data = unfiltered_data[target_type == ttype]) + 
+    # geom_point(data = unfiltered_data[target_type == ttype & horizon == 2]) + 
+    geom_line(data = unfiltered_data[target_type == ttype & horizon == 2]) + 
     theme_minimal() + 
@@
   df[, c("classification", "speed") := NULL], 
-  copy(epitrend)[, forecast_date := NULL], 
+  copy(epitrend)[, c("forecast_date", "true_value") := NULL], 
   by = c("target_end_date", "location_name", "target_type")
@@
                    paste0("truth-and-", i, "-wk-ahead_cases"))
-  ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_cases)
+  # ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_cases)
 
@@
                    paste0("truth-and-", i, "-wk-ahead_deaths"))
-  ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_deaths)
+  # ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_deaths)
 
@@
 summarise_by <- c("model", "horizon", "location_name", "target_type", 
-                   "forecast_date", "target_end_date", "location_target", 
-                   "classification")
+                   "forecast_date", "target_end_date", "location_target")
+
 scores_target_forecastdate <- eval_forecasts(
@@
   geom_line(aes(colour = model)) + 
-  geom_point(aes(shape = classification, colour = model)) + 
+  geom_point(aes(colour = model, shape = classification)) + 
   theme_minimal() + 
@@
 for (i in 1:4) {
+  epi_tmp <- copy(epitrend)
+  epi_tmp[, forecast_date := as.character(as.Date(forecast_date) + 7 * i)]
+  epi_tmp <- epi_tmp[, .(location_name, forecast_date, classification, target_type)] %>% 
+    unique()
+
   scores_over_time_case <- scores_target_forecastdate[horizon == i & target_type == "case"] %>%
+    merge(epi_tmp) %>%
     scores_over_time_plot(y = "interval_score") + 
@@
   scores_over_time_deaths <- scores_target_forecastdate[horizon == i & target_type == "death"] %>%
+    merge(epi_tmp) %>%
     scores_over_time_plot(y = "interval_score") + 
@@
     df[, c("classification", "speed") := NULL], 
-    copy(epitrend)[, forecast_date := NULL], 
+    copy(epitrend)[, c("forecast_date", "true_value") := NULL], 
     by = c("target_end_date", "location_name", "target_type")

### 2021-06-21 data-raw/paper.R

@@ -259,7 +259,6 @@ classify_epidemic <- function(data, cutoff = 0.05, growth_cutoff = 2) {
 # obtain classification
 epitrend <- classify_epidemic(truth_data)
 epitrend[, forecast_date := as.character(target_end_date + 2)]
-epitrend[, true_value := NULL]
 
 usethis::use_data(epitrend, overwrite = TRUE)
 
@@ -280,7 +279,7 @@ unfiltered_data[
 # and remove the forecast_date and merge by target_end_date instead
 unfiltered_data <- merge(
   unfiltered_data, 
-  copy(epitrend)[, target_end_date := NULL], 
+  copy(epitrend)[, c("target_end_date", "true_value") := NULL], 
   by = c("location_name", "target_type", "forecast_date")
 )
 

### 2021-06-24 analysis/analysis.Rmd
update plots, simplify code

--- 2021-06-19 analysis/analysis.Rmd
@@
 # define colors for deaths and cases
-colcases <- brewer.pal(name = "Accent", n = 5)[-c(1, 4)]
-coldeaths <- brewer.pal(name = "Accent", n = 5)[-4]
+colcases <- brewer.pal(name = "Accent", n = 8)[-c(1, 4)]
+coldeaths <- brewer.pal(name = "Accent", n = 8)[-4]
 
@@
 
-## Visualsiation of daily data
+--------------------------------------------------------------------------------
+## Plot with Visualsiation of daily data
 
@@
 
-## Visualisation for 1, 2, 3, 4 week ahead forecasts and scores
-
-### Plots that visualise truth vs. predictions
+--------------------------------------------------------------------------------
+## Plot with Visualsiation of x week ahead forecasts and scores
 
 ```{r truth-vs-forecasts, fig.height=12, fig.width=15}
-# create helper function for the plot ------------------------------------------
+
+# create helper functions for the plot 
+# ------------------------------------------------------------------------------
+# truth_and_pred_plot = helper function for the visualisation truth and forecast
+# scores_over_time_plot = helper function for plotting scores over time
+# forecasts_and_scores = function that organises creation of the plots
+
 truth_and_pred_plot <- function(df, ttype = "case") {
+
+  trend <- 
+    copy(epitrend)[, location_target := paste0(str_to_sentence(target_type), 
+                                               "s", " in ", location_name)]
   p <- df %>%
@@
                    alpha = 1,
-                   position = position_dodge(width = 4)) + 
-    # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
-    #                size = 1.7,
-    #                alpha = 0.1,
-    #                position = position_dodge(width = 4)) +   
-    geom_point(data = unfiltered_data[target_type == ttype], 
+                   position = position_dodge(width = 4.6)) + 
+    geom_point(data = trend[target_type == ttype],
                aes(shape = classification)) +
-    geom_line(data = unfiltered_data[target_type == ttype]) + 
+    geom_line(data = unfiltered_data[target_type == ttype & horizon == 2]) + 
     theme_minimal() + 
@@
     theme(legend.position = "bottom") + 
-    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
     scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
@@
 
-# prepare data for plotting ----------------------------------------------------
-# - load ufiltered data and pivot wider
-# - add trend classification by target_end_date 
-#   (and remove classification by forecast_date that is already present)
-
-df <- unfiltered_data[model %in% regular_models &
-                        quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
+scores_over_time_plot <- function(scores, y = "mean_scores_ratio") {
+  p <- scores %>%
+  ggplot(aes(x = as.Date(target_end_date), y = get(y))) + 
+  geom_line(aes(colour = model)) + 
+  geom_point(aes(colour = model, shape = classification)) + 
+  theme_minimal() + 
+  facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
+  theme(legend.position = "bottom") +
+  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
+                          max(forecast_dates$full_hub_period)))
+  return(p)
+}
+
+forecasts_and_scores <- function(data, 
+                                 output_dir = here("analysis", "plots"), 
+                                 plotname = "figure-forecasts", 
+                                 ensembles = FALSE) {
+
+  if (ensembles) {
+    colcases <- c(colcases[1:2], colcases[4], colcases[3])
+    coldeaths <- colcases
+  }
+
+  # create data.frame for plotting predictions ---------------------------------
+  df <- data[quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
     dcast(... ~ quantile, value.var = "prediction")
@@
     df[, c("classification", "speed") := NULL], 
-  copy(epitrend)[, forecast_date := NULL], 
+    copy(epitrend)[, c("forecast_date", "true_value") := NULL], 
     by = c("target_end_date", "location_name", "target_type")
@@
 
-# create plots for deaths and cases --------------------------------------------
-
+  # create data.frame for plotting scores --------------------------------------
+  summarise_by <- c("model", "horizon", "location_name", "target_type", 
+                    "forecast_date", "target_end_date", "location_target")
+
+  scores_target_forecastdate <- eval_forecasts(
+    data = data,
+    summarise_by = summarise_by
+  )[, forecast_date := as.Date(forecast_date)]
+
+  # copy epitrend data.frame and only keep necessary columns
+  epi_tmp <- copy(epitrend)
+  epi_tmp[, forecast_date := (as.Date(forecast_date))]
+  epi_tmp <- 
+    epi_tmp[, .(location_name, forecast_date, classification, target_type)] %>% 
+    unique()
+
+  # create plots for all horizons ----------------------------------------------
   for (i in 1:4) {
-  # plot for cases
+
+    # truth plot for cases 
     truth_vs_forecast_cases <- df[grepl(i, target)] %>%
@@
 
-  filename <- here("analysis", "plots", 
-                   paste0("truth-and-", i, "-wk-ahead_cases"))
-  ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_cases)
-
-  saveRDS(truth_vs_forecast_cases, 
-          paste0(filename, ".RDS"))
-
-  # plot for deaths
+    # truth plot for deaths
     truth_vs_forecast_deaths <- df[grepl(i, target)] %>%
@@
 
-  filename <- here("analysis", "plots", 
-                   paste0("truth-and-", i, "-wk-ahead_deaths"))
-  ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_deaths)
-
-  saveRDS(truth_vs_forecast_deaths, 
-          paste0(filename, ".RDS"))
-}
-```
-
-### Plots that visualise the achieved scores over time
-
-```{r scores-over-time, fig.height=10, fig.width=15}
-# score forecasts --------------------------------------------------------------
-# obtain scores and then do pairwise comparisons between models
-summarise_by <- c("model", "horizon", "location_name", "target_type", 
-                   "forecast_date", "target_end_date", "location_target", 
-                   "classification")
-scores_target_forecastdate <- eval_forecasts(
-  data = unfiltered_data[model %in% regular_models],
-  summarise_by = summarise_by
-)
-
-# pairwise <- pairwise_comparison(scores_target_forecastdate, 
-#                                 summarise_by = summarise_by, 
-#                                 baseline = "Baseline")
-# pairwise <- pairwise[compare_against == "Baseline"]
-
-# create helper function to plot forecasts -------------------------------------
-scores_over_time_plot <- function(scores, y = "mean_scores_ratio") {
-  p <- scores %>%
-  ggplot(aes(x = as.Date(target_end_date), y = get(y))) + 
-  geom_line(aes(colour = model)) + 
-  geom_point(aes(shape = classification, colour = model)) + 
-  theme_minimal() + 
-  facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
-  theme(legend.position = "bottom") +
-  # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
-  #               xmax = max(forecast_dates$christmas) + 14,
-  #               ymin = 0,
-  #               ymax = Inf), fill = "lightgrey", alpha = 0.002) +
-  # theme(panel.background = element_rect(fill = "#e1f0fe")) +
-  # scale_y_log10() + 
-  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
-                          max(forecast_dates$full_hub_period)))
-  return(p)
-}
-
-# create plots for all horizons ------------------------------------------------
-for (i in 1:4) {
-  scores_over_time_case <- scores_target_forecastdate[horizon == i & target_type == "case"] %>%
+    # scores plot for cases
+    scores_over_time_cases <- 
+      scores_target_forecastdate[horizon == i & target_type == "case"] %>%
+      merge(epi_tmp) %>%
       scores_over_time_plot(y = "interval_score") + 
       scale_color_manual(values = colcases) + 
-    labs(y = "WIS rel. to baseline", x = "")
-
-  ggsave(here("analysis", "plots", paste0("score-over-time-cases-", i, ".png")), 
-         plot = scores_over_time_case)
-
-  saveRDS(scores_over_time_case, 
-          here("analysis", "plots", paste0("score-over-time-cases-", i, ".RDS")))
-
-  scores_over_time_deaths <- scores_target_forecastdate[horizon == i & target_type == "death"] %>%
+      labs(y = "WIS", x = "")
+
+    # scores plot for deaths
+    scores_over_time_deaths <- 
+      scores_target_forecastdate[horizon == i & target_type == "death"] %>%
+      merge(epi_tmp) %>%
       scores_over_time_plot(y = "interval_score") + 
@@
                ymax = Inf, fill = "grey10", alpha = 0.1) + 
-    labs(y = "WIS rel. to baseline", x = "Date")
-
-  ggsave(here("analysis", "plots", paste0("score-over-time-deaths-", i, ".png")), 
-         plot = scores_over_time_deaths)
-
-  saveRDS(scores_over_time_deaths, 
-          here("analysis", "plots", paste0("score-over-time-deaths-", i, ".RDS")))
-
-}
-```
-
-### Combine the two plots
-
-```{r fig.height=15, fig.width=10}
-horizons <- 1:4
-
-for (horizon in horizons) {
-  truth_vs_pred_cases <- readRDS(file = here("analysis", "plots", 
-                                             paste0("truth-and-", horizon, 
-                                                    "-wk-ahead_cases.RDS")))
-
-  truth_vs_pred_deaths <- readRDS(file = here("analysis", "plots", 
-                                              paste0("truth-and-", horizon, 
-                                                     "-wk-ahead_deaths.RDS")))
-
-  scores_over_time_cases <- readRDS(file = here("analysis", "plots", 
-                                                paste0("score-over-time-cases-", 
-                                                       horizon,".RDS")))
-
-  scores_over_time_deaths <- readRDS(file = here("analysis", "plots", 
-                                                 paste0("score-over-time-deaths-", 
-                                                        horizon,".RDS")))
-
-  truth_vs_pred_cases / scores_over_time_cases / truth_vs_pred_deaths / scores_over_time_deaths + 
+      labs(y = "WIS", x = "Date")
+
+    # putting them all together
+    truth_vs_forecast_cases / scores_over_time_cases / 
+      truth_vs_forecast_deaths / scores_over_time_deaths + 
       plot_layout(guides = "collect") & 
@@
 
-  ggsave(here("analysis", "plots", paste0("figure-forecasts-", horizon, ".png")), width = 10, height = 12)
-}
-
-```
-
-------------------------------------------------------------------------
-
-## Summary table with scores
+    ggsave(here(output_dir, 
+                paste0(plotname, "-", i, ".png")), width = 10, height = 12)
+
+  }
+}
+
+# create plots -----------------------------------------------------------------
+# regular forecasts
+unfiltered_data[model %in% regular_models] %>%
+  forecasts_and_scores()
+
+# ensemble variants
+models <- c("Hub-ensemble-all", "Crowd forecast", "Hub-ensemble", "Renewal")
+unfiltered_data[model %in% models] %>%
+  forecasts_and_scores(plotname = "figure-forecasts-ensembles", 
+                       ensembles = TRUE)
+
+```
+
+--------------------------------------------------------------------------------
+### alternative visualisation of forecasts
+
+not yet done
 
 ```{r}
+scores_over_time_plot_components <- function(scores) {
+
+size = 1.8
+width = 4
+
+scores %>%
+  ggplot(aes(x = forecast_date, 
+             group = model, 
+             color = model)) +
+
+  geom_linerange(aes(ymin = -0.5*sharpness, ymax = 0.5 * sharpness, alpha = "Sharpness"), 
+                 size = size,
+                 alpha = 1,
+                 position = position_dodge(width = width)) +
+
+  geom_linerange(aes(ymax = -0.5 * sharpness, ymin = -0.5* sharpness - underprediction),
+                 size = size,
+                 position = position_dodge(width = width)) + 
+  geom_linerange(aes(ymax = -0.5 * sharpness, ymin = -0.5* sharpness - underprediction),
+                 size = size,
+                 colour = "white",
+                 size = size - 0.6,
+                 alpha = 0.6,
+                 position = position_dodge(width = width)) + 
+  geom_linerange(aes(ymin = 0.5 * sharpness, ymax = 0.5* sharpness + overprediction),
+                 size = size,
+                 position = position_dodge(width = width)) + 
+  geom_linerange(aes(ymin = 0.5 * sharpness, ymax = 0.5* sharpness + overprediction),
+                 size = size,
+                 colour = "white",
+                 size = size - 0.6,
+                 alpha = 0.6,
+                 position = position_dodge(width = width)) + 
+  theme_minimal() + 
+  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
+                          max(forecast_dates$full_hub_period)))
+
+}
+
+   scores_target_forecastdate[horizon == i & target_type == "case"] %>%
+    scores_over_time_plot_components() + 
+    scale_color_manual(values = colcases) + 
+    labs(y = "WIS rel. to baseline", x = "")
+
+```
+
+--------------------------------------------------------------------------------
+## Summary tables
+
+```{r}
+
 # create helper function to make table
-make_score_table <- function(scores, 
+# ------------------------------------------------------------------------------
+score_table <- function(scores, 
                              group = TRUE, 
@@
 
-```
-
-### Create tables
-
-```{r }
-# create scores ----------------------------------------------------------------
-# calculate coverage independently and merge with other scores
+make_table <- function(data, 
+                       plotname = "table_scores",
+                       output_dir = here("analysis", "plots")) {
+
   coverage <- eval_forecasts(
-  filtered_data[model %in% regular_models], 
+    data = data, 
     summarise_by = c("horizon", "model", "target_type", "range"), 
@@
   df <- eval_forecasts(
-  filtered_data[model %in% regular_models], 
+    data, 
     summarise_by = c("model", "horizon", "target_type"), 
@@
   # tables for 1-2 weeks ahead and 3-4 weeks ahdead
-table <- make_score_table(df[horizon <= 2]) 
-save_kable(table, file = here("analysis", "plots", "table_scores_2_ahead.png"))
-
-table <- make_score_table(df[horizon > 2]) 
-save_kable(table, file = here("analysis", "plots", "table_scores_4_ahead.png"))
-
-```
-
-### Create table for all median ensembles
-
-```{r }
-# create scores ----------------------------------------------------------------
-# calculate coverage independently and merge with other scores
-coverage <- eval_forecasts(
-  filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]], 
-  summarise_by = c("horizon", "model", "target_type", "range"), 
-)[range %in% c(50, 90), 
-                   .(model, target_type, coverage, range, horizon)] %>%
-  dcast(formula = ... ~ range, value.var = "coverage")
-
-df <- eval_forecasts(
-  filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]], 
-  summarise_by = c("model", "horizon", "target_type"), 
-  compute_relative_skill = FALSE, 
-  sd = TRUE, 
-  quantiles = 0.5,
-) %>%
-  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type")) 
-del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
-                        !(grepl("interval", names(df)))] %>%
-  c("coverage_deviation")
-df[, (del_cols) := NULL]
-
-setnames(df, old = c("interval_score_0.5", "interval_score_sd"), 
-         new = c("WIS - median", 
-                 "WIS - sd"))
-
-# tables for 1-2 weeks ahead and 3-4 weeks ahdead
-table <- make_score_table(df[horizon <= 2]) 
-save_kable(table, file = here("analysis", "plots", "table_median-ensemble_scores_2_ahead.png"))
-
-table <- make_score_table(df[horizon > 2]) 
-save_kable(table, file = here("analysis", "plots", "table_median-ensemble_scores_4_ahead.png"))
-
-```
-
-### Create table for all mean ensembles
-
-```{r }
-# create scores ----------------------------------------------------------------
-# calculate coverage independently and merge with other scores
-coverage <- eval_forecasts(
-  filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]], 
-  summarise_by = c("horizon", "model", "target_type", "range"), 
-)[range %in% c(50, 90), 
-                   .(model, target_type, coverage, range, horizon)] %>%
-  dcast(formula = ... ~ range, value.var = "coverage")
-
-df <- eval_forecasts(
-  filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]], 
-  summarise_by = c("model", "horizon", "target_type"), 
-  compute_relative_skill = FALSE, 
-  sd = TRUE, 
-  quantiles = 0.5,
-) %>%
-  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type")) 
-del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
-                        !(grepl("interval", names(df)))]
-del_cols <- c(del_cols, "coverage_deviation")
-df[, (del_cols) := NULL]
-
-setnames(df, old = c("interval_score_0.5", "interval_score_sd"), 
-         new = c("WIS - median", 
-                 "WIS - sd"))
-
-# tables for 1-2 weeks ahead and 3-4 weeks ahdead
-table <- make_score_table(df[horizon <= 2]) 
-save_kable(table, file = here("analysis", "plots", "table_mean-ensemble_scores_2_ahead.png"))
-
-table <- make_score_table(df[horizon > 2]) 
-save_kable(table, file = here("analysis", "plots", "table_mean-ensemble_scores_4_ahead.png"))
+  table <- score_table(df[horizon <= 2]) 
+  save_kable(table, file = here(output_dir, 
+                                paste0(plotname, "_", 2, "_ahead.png")))
+
+  table <- score_table(df[horizon > 2]) 
+  save_kable(table, file = here(output_dir, 
+                                paste0(plotname, "_", 4, "_ahead.png")))
+}
+
+# create tables
+# ------------------------------------------------------------------------------
+
+filtered_data[model %in% regular_models] %>%
+  make_table()
+
+filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]] %>%
+  make_table(plotname = "table_mean-ensemble_scores")
+
+filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]] %>%
+  make_table(plotname = "table_median-ensemble_scores")
 
@@
 ```{r}
-# calculate median and sd of the WIS -------------------------------------------
-
-df <- eval_forecasts(
-  filtered_data[model %in% regular_models], 
-  metric = "interval_score",
-  summarise_by = c("model", "horizon", "target_type"), 
-  sd = TRUE, 
-  quantile = 0.5
-)
-
-df <- df[, .(model, horizon, target_type, 
-             `WIS - mean` = interval_score, 
-             `WIS - median` = interval_score_0.5, 
-             `WIS - sd` = interval_score_sd)] %>%
-    dcast(... ~ ., value.var = c("WIS - mean", "WIS - median", "WIS - sd"))
-
-setcolorder(df, c("target_type", "horizon", "model"))
-
-table <- df[order(target_type, horizon, model)] %>%
-  make_score_table()
-
-save_kable(table, 
-           file = here("analysis", "plots", "table-wis-sd-median.png"))
+# # calculate median and sd of the WIS -------------------------------------------
+# 
+# df <- eval_forecasts(
+#   filtered_data[model %in% regular_models], 
+#   metric = "interval_score",
+#   summarise_by = c("model", "horizon", "target_type"), 
+#   sd = TRUE, 
+#   quantile = 0.5
+# ) 
+# 
+# 
+# df <- df[, .(model, horizon, target_type, 
+#              `WIS - mean` = interval_score, 
+#              `WIS - median` = interval_score_0.5, 
+#              `WIS - sd` = interval_score_sd)] %>%
+#     dcast(... ~ ., value.var = c("WIS - mean", "WIS - median", "WIS - sd"))
+# 
+# setcolorder(df, c("target_type", "horizon", "model"))
+# 
+# 
+# table <- df[order(target_type, horizon, model)] %>%
+#   score_table()
+# 
+# save_kable(table, 
+#            file = here("analysis", "plots", "table-wis-sd-median.png"))
 
@@
 labels <- df[horizon <= 2][order(target_phase, horizon)]$target_phase
-table <- make_score_table(df[horizon <= 2, !"target_type"], group = FALSE) %>%
+table <- score_table(df[horizon <= 2, !"target_type"], group = FALSE) %>%
   pack_rows(index = table(labels), indent = FALSE)
@@
 labels <- df[horizon > 2][order(target_phase, horizon)]$target_phase
-table <- make_score_table(df[horizon > 2, !"target_type"], group = FALSE) %>%
+table <- score_table(df[horizon > 2, !"target_type"], group = FALSE) %>%
   pack_rows(index = table(labels), indent = FALSE)
@@
 #     
-#     tables[[name]] <- make_score_table(tmp_df, 
+#     tables[[name]] <- score_table(tmp_df, 
 #                                        group = FALSE, 
@@
 # for (tar in targets) {
-#   tables[[tar]] <- make_score_table(tbl[target_phase == tar])
+#   tables[[tar]] <- score_table(tbl[target_phase == tar])
 # }
@@
 
+### Aggregate performance across different horizons
+
 ``` {r}
 
-scores <- eval_forecasts(filtered_data[model %in% regular_models], 
-                         summarise_by = c("model", "target_type", "horizon"), 
+aggregate_performance <- function(data, 
+                                  x = "horizon",
+                                  xlabel = "Forecast horizon",
+                                  output_dir = here("analysis", "plots"), 
+                                  plotname,
+                                  relative = FALSE,
+                                  facet_formula = ~ target_type) {
+
+  scores <- eval_forecasts(data, 
+                           summarise_by = c("model", "target_type", x), 
                            quantiles = 0.5, 
@@
 
-# mean performance
-p_mean <- scores %>%
-  ggplot(aes(x = horizon, y = interval_score, group = model, color = model)) + 
+  plot_helper <- function(tmp = scores, xvar = x, y, rel = relative) {
+    if (rel) {
+      tmp <- tmp %>%
+        arrange(target_type, get(x)) %>%
+        group_by(target_type, get(x)) %>%
+        mutate_at(y, ~ . - .[model == "Hub-ensemble"])
+    }
+
+    tmp %>%
+      ggplot(aes_string(x = xvar, y = y, group = "model", color = "model")) +
       geom_point() +
       geom_line() +
-  facet_wrap(~ target_type, scales = "free_y") + 
+      facet_wrap(facet_formula, scales = "free_y") +
       theme_minimal() +
       theme(legend.position = "bottom") +
-  scale_color_manual(values = coldeaths) + 
+      scale_color_manual(values = coldeaths)
+  }
+
+  # mean performance
+  p_mean <- 
+    plot_helper(scores, y = "interval_score") + 
     labs(y = "mean WIS", x = NULL)
 
-# ggsave(here("analysis", "plots", "aggregate-performance-mean.png"))
-
   # median performance
-p_median <- scores %>%
-  ggplot(aes(x = horizon, y = interval_score_0.5, group = model, color = model)) + 
-  geom_point() + 
-  geom_line() + 
-  facet_wrap(~ target_type, scales = "free_y") + 
-  theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths) + 
-  labs(y = "median WIS", x = NULL) + 
-  theme_minimal()
-
-# ggsave(here("analysis", "plots", "aggregate-performance-median.png"))
+  p_median <- 
+    plot_helper(scores, y = "interval_score_0.5") + 
+    labs(y = "median WIS", x = NULL)
 
   # sd of performance
-p_wis_sd <- scores %>%
-  ggplot(aes(x = horizon, y = interval_score_sd, group = model, color = model)) + 
-  geom_point() + 
-  geom_line() + 
-  facet_wrap(~ target_type, scales = "free_y") + 
-  theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths) + 
-  labs(y = "WIS - sd", x = NULL) + 
-  theme_minimal()
-
-# ggsave(here("analysis", "plots", "aggregate-performance-wis-sd.png"))
+  p_wis_sd <- 
+    plot_helper(scores, y = "interval_score_sd") + 
+    labs(y = "WIS - sd", x = NULL)
 
   # sharpness of performance
-p_sharpness <- scores %>%
-  ggplot(aes(x = horizon, y = sharpness, group = model, color = model)) + 
-  geom_point() + 
-  geom_line() + 
-  facet_wrap(~ target_type, scales = "free_y") + 
-  theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths) + 
-  labs(y = "sharpness", x = NULL) + 
-  theme_minimal()
-
-# ggsave(here("analysis", "plots", "aggregate-performance-sharpness.png"))
+  p_sharpness <- 
+    plot_helper(scores, y = "sharpness") + 
+    labs(y = "Sharpness", x = NULL)
 
   # absolute error of performance
-p_aem <- scores %>%
-  ggplot(aes(x = horizon, y = aem, group = model, color = model)) + 
-  geom_point() + 
-  geom_line() + 
-  facet_wrap(~ target_type, scales = "free_y") + 
-  theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths) + 
-  labs(y = "Absolute error", x = NULL) + 
-  theme_minimal()
-
-# ggsave(here("analysis", "plots", "aggregate-performance-aem.png"))
+  p_aem <-
+    plot_helper(scores, y = "aem") + 
+    labs(y = "Absolute error", x = NULL)
 
   # bias
-p_bias <- scores %>%
-  ggplot(aes(x = horizon, y = bias, group = model, color = model)) + 
-  geom_point() + 
-  geom_line() + 
-  facet_wrap(~ target_type) + 
+  p_bias <- 
+    plot_helper(scores, y = "bias") + 
+    labs(y = "Bias", x = NULL) +
     geom_hline(yintercept = 0, linetype = "dashed") +
-  theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths) + 
-  expand_limits(y=c(-0.2, 0.2)) + 
-  labs(y = "Bias", x = NULL) + 
-  theme_minimal()
-
-# ggsave(here("analysis", "plots", "aggregate-performance-bias.png"))
+    expand_limits(y=c(-0.2, 0.2))
 
   # coverage
-scores <- eval_forecasts(filtered_data[model %in% regular_models], 
-                         summarise_by = c("model", "target_type", "horizon", "range"), 
+  scores <- eval_forecasts(data, 
+                           summarise_by = c("model", "target_type", x, "range"), 
                            quantiles = 0.5, 
@@
 
-scores[range %in% c(50, 90)] %>%
-  ggplot(aes(x = horizon, y = coverage, group = range, color = range)) + 
-  geom_point() + 
-  geom_line() + 
-  facet_wrap(model ~ target_type , scales = "free_y")
-
   p_cov50 <- scores[range %in% c(50)] %>%
-  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
-  geom_point() + 
-  geom_line() + 
-  facet_wrap(~ target_type) + 
+    plot_helper(y = "coverage") + 
     geom_hline(yintercept = 0.5, linetype = "dashed") +
-  scale_color_manual(values = coldeaths) + 
-  labs(y = "Empirical coverage", x = "Forecast horizon") + 
-  theme_minimal() + 
-  expand_limits(y=c(0, 1)) + 
-  theme(legend.position = "bottom") + 
-  scale_y_continuous(labels = scales::percent)
-
-# ggsave(here("analysis", "plots", "aggregate-performance-coverage50.png"))
-
-p_cov90 <- scores[range %in% c(90)] %>%
-  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
-  geom_point() + 
-  geom_line() + 
-  facet_wrap(~ target_type) + 
-  theme_minimal() + 
-  theme(legend.position = "bottom") + 
-  geom_hline(yintercept = 0.90, linetype = "dashed") +
-  theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths) + 
-  labs(y = "Empirical coverage", x = "Forecast horizon") + 
+    labs(y = "Coverage - 50% PI", x = xlabel) + 
     expand_limits(y=c(0, 1)) + 
@@
 
-# ggsave(here("analysis", "plots", "aggregate-performance-coverage90.png"))
+  p_cov90 <- scores[range %in% c(90)] %>%
+    plot_helper(y = "coverage") + 
+    geom_hline(yintercept = 0.5, linetype = "dashed") +
+    labs(y = "Coverage - 50% PI", x = xlabel) + 
+    expand_limits(y=c(0, 1)) + 
+    scale_y_continuous(labels = scales::percent)
 
@@
 
-ggsave(here("analysis", "plots", "aggregate-performance-all.png"), 
+  ggsave(here(output_dir, paste0(plotname, ".png")), 
          height = 9.1, width = 10)
 
-```
-
-```{r}
-scores <- eval_forecasts(filtered_data[model %in% 
-                                         ensemble_models[!grepl("mean", ensemble_models)]], 
-                         summarise_by = c("model", "target_type", "horizon"), 
-                         quantiles = 0.5, 
-                         sd = TRUE)
-
-# mean performance
-p_mean_ens <- scores %>%
-  ggplot(aes(x = horizon, y = interval_score, group = model, color = model)) + 
-  geom_point() + 
-  geom_line() + 
-  facet_wrap(~ target_type, scales = "free_y") + 
-  theme_minimal() + 
-  theme(legend.position = "bottom") + 
-  scale_color_manual(values = coldeaths) + 
-  labs(y = "mean WIS", x = "Forecast horizon")
-
-ggsave(here("analysis", "plots", "aggregate-performance-mean.png"))
-
-```
-
-``` {r}
-scores <- eval_forecasts(filtered_data[model %in% regular_models], 
-                         summarise_by = c("model", "target_type", "location", 
-                                          "horizon", "forecast_date"))
-scores <- scores[order(interval_score), , by = c("target_type", "location", 
-                                               "horizon", "forecast_date")]
-scores <- scores[, ranking := 1:.N, by = c("target_type", "location", 
-                                           "horizon", "forecast_date")]
+}
+
+filtered_data[model %in% regular_models] %>%
+  aggregate_performance(plotname = "aggregate-performance-all")
+
+filtered_data[model %in% regular_models & horizon == 2] %>%
+  aggregate_performance(plotname = "aggregate-performance-2-weeks-locations-all", 
+                        x = "location_name", 
+                        xlabel = NULL)
+
+filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]] %>%
+  aggregate_performance(plotname = "aggregate-performance-rel-ensemble", 
+                        relative = TRUE)
 
@@
 ```
+
+### Plots with overprediction, sharpness etc over time
+
+``` {r}
+
+```

### 2021-06-24 analysis/analysis.Rmd
update plots and tables

@@
 
-  scores <- scores[, lapply(.SD, FUN = function(x) {
-    if (is.numeric(x)) {
-      return(round(signif(x, 3), 2))
-    } else {
-      return(x)
-    }
-  })]
-
   # remove some cols, change column order, sort table and rename horizon
@@
     merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))
+
+  # round digits
+  df <- df[, lapply(.SD, FUN = function(x) {
+    if (is.numeric(x)) {
+      return(round(signif(x, 3), 2))
+    } else {
+      return(x)
+    }
+  })]
+
+  percentage_cols <- c("interval_score", "interval_score_0.5", 
+                       "interval_score_sd", "sharpness", "underprediction", 
+                       "overprediction", "aem")
+
+  # no idea how to do that in data.table: 
+  df <- df %>%
+    dplyr::group_by(horizon, target_type) %>%
+    dplyr::mutate_at(percentage_cols, ~ paste0(., " (", 
+                                               round(100 * ./.[model == "Hub-ensemble"]), 
+                                               "%)"))
+
+  setDT(df)
 

### 2021-06-25 analysis/analysis.Rmd
update plots

@@
 library(ggthemes)
+library(scales)
 
@@
 
+  setnames(df, old = c("model"), new = c("Model"))
+
   trend <- 
@@
                                                "s", " in ", location_name)]
+  setnames(trend, old = c("classification"), new = c("Classification"))
   p <- df %>%
@@
     ggplot(aes(y = true_value, x = target_end_date)) + 
-    geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
-                   size = 1.7,
+    geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = Model), 
+                   size = 1.4,
                    alpha = 1,
@@
     geom_point(data = trend[target_type == ttype],
-               aes(shape = classification)) +
+               aes(shape = Classification)) +
     geom_line(data = unfiltered_data[target_type == ttype & horizon == 2]) + 
@@
     theme(legend.position = "bottom") +
+    scale_y_continuous(labels = comma) + # , 
+                       # trans = log_trans()) +
     scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
@@
                ymax = Inf, fill = "grey10", alpha = 0.1) + 
-      labs(y = "Deaths", x = "")
+      labs(y = "Deaths", x = "") +
+      theme(legend.position = "none") + 
+      guides(color = "none", shape = "none")
 
@@
       scale_color_manual(values = colcases) + 
-      labs(y = "WIS", x = "")
+      labs(y = "WIS", x = "") + 
+      theme(legend.position = "none") + 
+      guides(color = "none", shape = "none")
 
@@
                ymax = Inf, fill = "grey10", alpha = 0.1) + 
-      labs(y = "WIS", x = "Date")
+      labs(y = "WIS", x = "Date") + 
+      theme(legend.position = "none") + 
+      guides(color = "none", shape = "none")
 
@@
       plot_layout(guides = "collect") & 
+      # guides(fill = "guidetitle") &
       plot_annotation(tag_levels = 'A') &

### 2021-06-25 analysis/analysis.Rmd
update plots

@@
 library(scales)
+library(dplyr)
 
@@
 
-   scores_target_forecastdate[horizon == i & target_type == "case"] %>%
-    scores_over_time_plot_components() + 
-    scale_color_manual(values = colcases) + 
-    labs(y = "WIS rel. to baseline", x = "")
+# scores_target_forecastdate[horizon == i & target_type == "case"] %>%
+#   scores_over_time_plot_components() + 
+#   scale_color_manual(values = colcases) + 
+#   labs(y = "WIS rel. to baseline", x = "")
 

### 2021-06-25 analysis/analysis.Rmd
update plots

@@
 
+  setnames(scores, old = "model", new = "Model")
+
   plot_helper <- function(tmp = scores, xvar = x, y, rel = relative) {
@@
         group_by(target_type, get(x)) %>%
-        mutate_at(y, ~ . - .[model == "Hub-ensemble"])
+        mutate_at(y, ~ . - .[Model == "Hub-ensemble"])
     }
@@
     tmp %>%
-      ggplot(aes_string(x = xvar, y = y, group = "model", color = "model")) +
+      ggplot(aes_string(x = xvar, y = y, group = "Model", color = "Model")) +
       geom_point() +
@@
                            sd = TRUE)
+
+  setnames(scores, old = "model", new = "Model")
 

### 2021-06-25 analysis/analysis.Rmd
update plota

@@
 ```{r}
-dailytruth_data %>%
-  dplyr::filter(target_end_date >= min(forecast_dates$full_hub_period), 
-                target_end_date <= max(forecast_dates$full_hub_period)) %>%
+df <- copy(dailytruth_data)[
+  , target_location := paste0(str_to_title(target_type), "s in ", location_name)
+]
+
+weeklytruth <- copy(truth_data)[
+  , target_location := paste0(str_to_title(target_type), "s in ", location_name)
+]
+
+df %>%
   ggplot(aes(y = true_value, x = target_end_date)) + 
-  geom_point(size = 0.3, alpha = 0.4) + 
-  geom_line(size = 0.5, alpha = 0.4) + 
-  geom_line(data = truth_data, aes(y = true_value / 7)) + 
-  facet_grid(target_type ~ location_name, scales = "free") + 
+  # geom_point(size = 0.3, alpha = 0.4) + 
+  # geom_line(size = 0.5, alpha = 0.4) + 
+  geom_col(fill = "lightsteelblue", color = "white") + 
+  geom_line(data = weeklytruth, aes(y = true_value / 7)) + 
+  geom_point(data = weeklytruth, aes(y = true_value / 7), size = 0.3) +
+  facet_wrap( ~ target_location, scales = "free", ncol = 1) + 
   labs(y = "Observed values", x = "Date") + 
   scale_x_date(limits = c(min(forecast_dates$full_hub_period) - 28, 
-                            max(forecast_dates$full_hub_period))) + 
+                          max(forecast_dates$full_hub_period + 21))) + 
   theme_minimal()
 
-ggsave(here("analysis", "plots", "daily_truth.png"))
+ggsave(here("analysis", "plots", "daily_truth.png"), width = 10, height = 8)
 ```
@@
   p_cov50 <- scores[range %in% c(50)] %>%
-    plot_helper(y = "coverage") + 
+    plot_helper(y = "coverage", rel = FALSE) + 
     geom_hline(yintercept = 0.5, linetype = "dashed") +
@@
   p_cov90 <- scores[range %in% c(90)] %>%
-    plot_helper(y = "coverage") + 
+    plot_helper(y = "coverage", rel = FALSE) + 
     geom_hline(yintercept = 0.5, linetype = "dashed") +

### 2021-06-25 analysis/analysis.Rmd
update plots

@@
   , target_location := paste0(str_to_title(target_type), "s in ", location_name)
+][, target_end_date := as.Date(target_end_date)
 ]
+
+df[weekdays(target_end_date) == "Sunday", sundays := target_end_date]
 
@@
   geom_point(data = weeklytruth, aes(y = true_value / 7), size = 0.3) +
+  # geom_vline(aes(xintercept = sundays), linetype = "dashed", alpha = 0.2) + 
   facet_wrap( ~ target_location, scales = "free", ncol = 1) + 
@@
   ggplot(aes(y = value, x = Date, color = variable)) + 
-  geom_point()
+  # geom_col(aes(fill = variable), position = position_dodge()) + 
+  geom_point() + 
+  geom_line() + 
+  scale_color_manual(values = colcases) + 
+  theme_minimal()
 

### 2021-06-30 paper/make_paper.sh
update references, export to .odt format

@@ -1,3 +1,4 @@
 pandoc paper.md --standalone \
 	--citeproc \
-	-o paper.pdf
+	-o paper.odt
+

### 2021-08-10 R/get_observations.R
correct get_observations()
sometimes you find a bug, sometimes you introduce a bug... 
Should have tested that more carefully. Previous version relied on `target_date` as if it were a column of the data.table, which it isn't. Fixed now, sorry!

@@ -23,7 +23,7 @@ get_observations <- function(dir, target_date = Sys.Date(),
     .(region = as.character(location_name),
       date = as.Date(date), primary, secondary)
   ]
-  obs <- obs[date >= (max(target_date) - weeks * 7)]
+  obs <- obs[date >= (as.Date(target_date) - weeks * 7)]
   obs <- obs[date <= target_date]
   obs <- obs[primary < 0, primary := 0]
   obs <- obs[secondary < 0, secondary := 0]

### 2021-08-10 R/get_observations.R
create script to re-run past forecasts for the secondary model

@@ -22,7 +22,7 @@ get_observations <- function(dir, target_date = Sys.Date(),
     .(region = as.character(location_name),
       date = as.Date(date), primary, secondary)
   ]
-  obs <- obs[date >= (max(date) - weeks * 7)]
+  obs <- obs[date >= (as.Date(target_date) - weeks * 7)]
   obs <- obs[date <= target_date]
   obs <- obs[primary < 0, primary := 0]
   obs <- obs[secondary < 0, secondary := 0]

### 2021-08-10 analysis/past-convolution-forecasts.R

@@ -1,0 +1,81 @@
+# Packages -----------------------------------------------------------------
+library(covid.german.forecasts)
+library(EpiNow2, quietly = TRUE)
+library(data.table, quietly = TRUE)
+library(here, quietly = TRUE)
+library(future, quietly = TRUE)
+library(devtools, quietly = TRUE)
+library(lubridate, quietly = TRUE)
+library(ggplot2, quietly = TRUE)
+library(purrr, quietly = TRUE)
+
+dates <- as.character(as.Date("2020-10-12") + 7*(0:9))
+
+for (target_date in dates) {
+  # Get observations --------------------------------------------------------
+  observations <- get_observations(dir = here("data-raw"), target_date)
+  
+  # filter only Germany and Poland
+  observations <- observations[region %in% c("Germany", "Poland")]
+  
+  # Get case forecasts ------------------------------------------------------
+  case_forecast <- suppressWarnings(
+    get_regional_results(
+      results_dir = here("rt-forecast", "data", "samples", "cases"),
+      date = ymd(target_date), forecast = TRUE, samples = TRUE
+    )$estimated_reported_cases$samples
+  )
+  case_forecast <- case_forecast[sample <= 1000]
+  
+  # Forecast deaths from cases ----------------------------------------------
+  # set up parallel options
+  options(mc.cores = 4)
+  plan("sequential")
+  
+  # load the prototype regional_secondary function
+  source_gist("https://gist.github.com/seabbs/4dad3958ca8d83daca8f02b143d152e6")
+  # devtools::source_url("https://raw.githubusercontent.com/seabbs/regional-secondary/master/regional-secondary.R")
+  
+  # run across Poland and Germany specifying
+  # options for estimate_secondary (EpiNow2)
+  forecast <- regional_secondary(
+    observations, case_forecast,
+    delays = delay_opts(list(
+      mean = 2.5, mean_sd = 0.5,
+      sd = 0.47, sd_sd = 0.2, max = 30
+    )),
+    return_fit = FALSE,
+    secondary = secondary_opts(type = "incidence"),
+    obs = obs_opts(scale = list(mean = 0.01, sd = 0.05), week_effect = FALSE),
+    window = 3 * 7,
+    control = list(adapt_delta = 0.99, max_treedepth = 15),
+    verbose = TRUE
+  )
+  
+  # Save results to disk ----------------------------------------------------
+  samples_path <- here(
[…]

### 2021-08-10 analysis/past-convolution-forecasts.R
filter for Germany and Poland

@@ -26,6 +26,7 @@ for (target_date in dates) {
     )$estimated_reported_cases$samples
   )
   case_forecast <- case_forecast[sample <= 1000]
+  case_forecast <- case_forecast[region %in% c("Germany", "Poland")]
   
   # Forecast deaths from cases ----------------------------------------------
   # set up parallel options

### 2021-08-11 analysis/analysis.Rmd
update plots

@@
 
-  # median performance
-  p_median <- 
-    plot_helper(scores, y = "interval_score_0.5") + 
-    labs(y = "median WIS", x = NULL)
+    # absolute error of performance
+  p_aem <-
+    plot_helper(scores, y = "aem") + 
+    labs(y = "Absolute error", x = NULL)
 
@@
     labs(y = "Sharpness", x = NULL)
-
-  # absolute error of performance
-  p_aem <-
-    plot_helper(scores, y = "aem") + 
-    labs(y = "Absolute error", x = NULL)
 
@@
     plot_helper(y = "coverage", rel = FALSE) + 
-    geom_hline(yintercept = 0.5, linetype = "dashed") +
-    labs(y = "Coverage - 50% PI", x = xlabel) + 
+    geom_hline(yintercept = 0.9, linetype = "dashed") +
+    labs(y = "Coverage - 90% PI", x = xlabel) + 
     expand_limits(y=c(0, 1)) + 
@@
 
-  p_combined <- (p_mean + p_median) / 
-    (p_aem + p_wis_sd) / 
+  p_combined <- (p_mean + p_aem) / 
     (p_sharpness + p_bias) / 
-    (p_cov50 + p_cov90) +  
+    (p_cov50 + p_cov90) /
+    (p_wis_sd) +  
     plot_layout(guides = "collect") & 

### 2021-08-20 analysis/analysis.Rmd
update plots

@@
 library(dplyr)
+library(tidyr)
+library(forcats)
 
@@
 
+  # data = unfiltered_data[model %in% regular_models]
+  # df <- data[quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
+  #   dcast(... ~ quantile, value.var = "prediction")
+  # df <- merge(
+  #   df[, c("classification", "speed") := NULL], 
+  #   copy(epitrend)[, c("forecast_date", "true_value") := NULL], 
+  #   by = c("target_end_date", "location_name", "target_type")
+  # )
+  # df <- df[grepl(2, target)]
+
   setnames(df, old = c("model"), new = c("Model"))
@@
     geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = Model), 
-                   size = 1.4,
+                   size = 1.1,
                    alpha = 1,
-                   position = position_dodge(width = 4.6)) + 
+                   position = position_dodge(width = 3.6)) + 
     geom_point(data = trend[target_type == ttype],
@@
     theme_minimal() + 
+    theme(panel.grid.major.x = element_blank()) +
     facet_wrap(~ location_target, scales = "free", ncol = 2) + 
@@
     scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
-                            max(forecast_dates$full_hub_period)))
+                            max(forecast_dates$full_hub_period)), 
+                 minor_breaks = forecast_dates$unfiltered + 5)
   return(p)
@@
 
+  data <- filtered_data[model %in% regular_models]
+
+  scores <- eval_forecasts(data, 
+                           summarise_by = c("model", "target_type", "horizon"), 
+                           quantiles = 0.5, 
+                           sd = TRUE)
+
+  setnames(scores, old = "model", new = "Model")
+
+  component_plot <- function(scores, type) {
+
+    if (type == "case") {
+      vals <- colcases
+    } else {
+      vals <- coldeaths
+    }
+
+    scores %>%
+      select(Model, target_type, horizon, sharpness, interval_score,
+             underprediction, overprediction) %>%
+      filter(target_type == type) %>%
+      pivot_longer(names_to = "WIS components",
+                   cols = c(sharpness, overprediction, underprediction)) %>%
+      mutate(`WIS components` = fct_relevel(`WIS components`, 
+                                            c("sharpness", "underprediction", 
+                                              "overprediction"))) %>%
+      group_by(target_type, horizon) %>%
+      arrange(interval_score) %>%
+      ggplot(aes(x = reorder(Model, (interval_score)), y = value, fill = Model, 
+                 group = Model, alpha = `WIS components`)) + 
+      scale_alpha_manual(values = c(1, 0.1, 0.6)) +
+      scale_fill_manual(values = vals) + 
+      geom_bar(stat = "identity", position = "stack",
+               color = "black",
+               size = 0.1,
+               width = 0.8) +
+      facet_wrap(~ horizon, ncol = 4,
+                 strip.position="bottom") + 
+      theme_minimal() + 
+      theme(axis.text.x = element_blank(), 
+            plot.title = element_text(hjust = 0.5, 
+                                      size = 8), 
+            legend.position = c(0.12, 0.83)) + 
+      labs(x = NULL, title = type, y = "WIS") + 
+      guides(fill = "none")
+  }
+
+  component_case <- component_plot(scores, "case")
+  component_death <- component_plot(scores, "death")
+  components <- component_case + component_death
+
   # coverage
@@
     geom_hline(yintercept = 0.5, linetype = "dashed") +
-    labs(y = "Coverage - 50% PI", x = xlabel) + 
+    labs(y = "Coverage - 50% PI") + 
     expand_limits(y=c(0, 1)) + 
@@
     geom_hline(yintercept = 0.9, linetype = "dashed") +
-    labs(y = "Coverage - 90% PI", x = xlabel) + 
+    labs(y = "Coverage - 90% PI") + 
     expand_limits(y=c(0, 1)) + 
@@
 
-  p_combined <- (p_mean + p_aem) / 
-    (p_sharpness + p_bias) / 
-    (p_cov50 + p_cov90) /
-    (p_wis_sd) +  
+  p_combined <- (p_mean) / 
+    (p_cov50) /
+    (p_cov90) / 
+    (component_case + component_death) +  
     plot_layout(guides = "collect") & 
     plot_annotation(tag_levels = 'A') &
-    theme(legend.position = 'bottom')
+    theme(legend.position = 'bottom', 
+          legend.box="vertical", legend.margin=margin())
 
   ggsave(here(output_dir, paste0(plotname, ".png")), 
+         height = 9.1, width = 8)
+
+  p_combined2 <- (p_aem + p_wis_sd) /
+    (p_sharpness + p_bias) + 
+    plot_layout(guides = "collect") & 
+    plot_annotation(tag_levels = 'A') &
+    theme(legend.position = 'bottom', 
+          legend.box="vertical", legend.margin=margin())
+
+    ggsave(here(output_dir, paste0(plotname, "-2.png")), 
+         height = 5.1, width = 10)
+
+    p_combined3 <- (p_mean + p_aem) /
+        (p_cov50 + p_cov90) /
+        (p_sharpness + p_bias) /
+        (p_wis_sd + plot_spacer()) + 
+    plot_layout(guides = "collect") & 
+    plot_annotation(tag_levels = 'A')  &
+    theme(legend.position = 'bottom', 
+          legend.box="vertical", legend.margin=margin())
+
+    ggsave(here(output_dir, paste0(plotname, "-3.png")), 
          height = 9.1, width = 10)
 
+    p_combined4 <- 
+      components / 
+      (p_cov50 + p_cov90) /
+      (p_sharpness + p_bias) /
+      (p_aem + p_wis_sd) +
+    plot_layout(guides = "collect", 
+                heights = c(1.3, 1, 1, 1)) &
+    plot_annotation(tag_levels = 'A')  &
+    theme(legend.position = 'bottom', 
+          legend.box="vertical", legend.margin=margin())
+
+    ggsave(here(output_dir, paste0(plotname, "-4.png")), 
+           height = 9.1, width = 10)
 }

### 2021-08-21 analysis/analysis.Rmd
update plots

@@
 
+  if (ttype == "case") {
+    dodgewidth = 3.6
+  } else {
+    dodgewidth = 3.7
+  }
+
   setnames(df, old = c("model"), new = c("Model"))
@@
   setnames(trend, old = c("classification"), new = c("Classification"))
+
+  limits <- min(forecast_dates$full_hub_period) + 5 + 1:21 * 7
+
   p <- df %>%
@@
                    alpha = 1,
-                   position = position_dodge(width = 3.6)) + 
+                   position = position_dodge(width = dodgewidth)) + 
     geom_point(data = trend[target_type == ttype],
@@
     theme(panel.grid.major.x = element_blank()) +
-    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
+    facet_wrap(~ location_target, scales = "free", ncol = 1) + 
     theme(legend.position = "bottom") + 
-    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
-                            max(forecast_dates$full_hub_period)), 
-                 minor_breaks = forecast_dates$unfiltered + 5)
+    scale_x_date(limits = c(min(limits), max(limits)), 
+                 minor_breaks = limits)
   return(p)
@@
 scores_over_time_plot <- function(scores, y = "mean_scores_ratio") {
+  limits <- min(forecast_dates$full_hub_period) + 5 + 1:21 * 7
+
   p <- scores %>%
@@
     theme_minimal() + 
-    facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
+    facet_wrap( ~ location_target, ncol = 1, scales = "free") +
     theme(legend.position = "bottom") +
+    theme(panel.grid.major.x = element_blank()) +
     scale_y_continuous(labels = comma) + # , 
                        # trans = log_trans()) + 
-    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
-                            max(forecast_dates$full_hub_period)))
+    scale_x_date(limits = c(min(limits), max(limits)), 
+                 minor_breaks = limits)
   return(p)
@@
       scale_color_manual(values = colcases) + 
-      labs(y = "Cases", x = "")
+      labs(y = "Forecasts and observed values", x = "")  + 
+      theme(legend.position = "none") +
+      guides(color = "none", shape = "none") + 
+      theme(plot.margin = unit(c(0.5,1.3,0.5,0.5), "cm"))
 
@@
                ymax = Inf, fill = "grey10", alpha = 0.1) + 
-      labs(y = "Deaths", x = "") +
+      labs(y = "Forecasts and observed values", x = "") +
       theme(legend.position = "none") +
-      guides(color = "none", shape = "none")
+      guides(color = "none", shape = "none") + 
+      theme(plot.margin = unit(c(0.5,1.3,0.5,0.5), "cm"))
 
@@
       scale_color_manual(values = colcases) + 
-      labs(y = "WIS", x = "") + 
+      labs(y = "Weighted interval score", x = "") + 
       theme(legend.position = "none") +
@@
                ymax = Inf, fill = "grey10", alpha = 0.1) + 
-      labs(y = "WIS", x = "Date") + 
-      theme(legend.position = "none") + 
-      guides(color = "none", shape = "none")
+      labs(y = "Weighted interval score", x = "")
 
     # putting them all together
-    truth_vs_forecast_cases / scores_over_time_cases / 
-      truth_vs_forecast_deaths / scores_over_time_deaths + 
+    p <- (truth_vs_forecast_cases + scores_over_time_cases) / 
+      (truth_vs_forecast_deaths + scores_over_time_deaths) + 
       plot_layout(guides = "collect") &
-      # guides(fill = "guidetitle") &
+      plot_layout(widths = c(1.9, 1)) &
       plot_annotation(tag_levels = 'A') &
-      theme(legend.position = 'bottom')
+      theme(legend.position = 'bottom', 
+            legend.box="vertical", legend.margin = margin())
 
     ggsave(here(output_dir, 
-                paste0(plotname, "-", i, ".png")), width = 10, height = 12)
+                paste0(plotname, "-", i, ".png")), width = 10, height = 11)
 

### 2021-08-23 submissions/submit.sh
automated Rt update

@@ -17,7 +17,7 @@ cd ../covid19-forecast-hub-de
 git checkout master 
 git pull 
 # Switch to submission branch
-git checkout -b submission
+git checkout -b submission2
 git merge -Xtheirs master
 
 # Move back into forecast repository
@@ -43,5 +43,5 @@ gh pr create --title "$ForecastDate - EpiForecast submission" --body "This is an
 
 # Remove local submission branch 
 git checkout master
-git branch -d submission
+git branch -d submission2
 cd ../covid.german.forecasts

### 2021-08-27 analysis/analysis.Rmd
update ensemble plots

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)
 options(knitr.kable.NA = '')
@@
 coldeaths <- brewer.pal(name = "Accent", n = 8)[-4]
-
-# colcases <- few_pal()(4)[-1]
-# coldeaths <- few_pal()(4)
+colensemble <- c("#FDC086", brewer.pal(name = "Set2", n = 8))
 
@@
 
-distribution_plot_wis <- function(df, x = "interval_score") {
+distribution_plot_wis <- function(df, x = "interval_score", ranks = FALSE) {
+
+  scale_fn <- function(x) {
+    ifelse(x >= 5000,
+           paste0(x / 1000, "k"), x)
+  }
+
+  xlabel = "Weighted interval score"
+  dotsize = 1
+
+  if (ranks) {
+    df <- df %>%
+      group_by(location_name, target_type, horizon, forecast_date) %>%
+      arrange(location_name, target_type, horizon, forecast_date, interval_score) %>%
+      mutate(!!x := rank(get(x)))
+
+    xlabel <- "Rank in terms of WIS"
+    dotsize = 0.1
+
+  }
+  + runif(length(get(x)), min = -0.1, max = 0.1)
+
   df %>%
-    ggplot(aes_string(y = "model", x = x, 
-                      group = "model", fill = "model")) + 
-    # geom_density_ridges(aes(fill = model, color = NA),
-    #                     rel_min_height = 0.005,
-    #                     scale = 0.9,
-    #                     # jittered_points = TRUE,
-    #                     # position = position_points_jitter(width = 0.05, height = 0),
-    #                     point_size = 1.5,
-    #                     point_shape = 21,
-    #                     #point_shape = '|',
-    #                     point_alpha = 1,
-    #                     alpha = 0.3) +
+    rename(Model = model) %>%
+    ggplot(aes_string(y = "Model", x = x, 
+                      group = "Model", fill = "Model")) + 
     ggdist::stat_slab(alpha = 0.3, scale = 0.8, normalize = "panels") +
-  # ggridges::geom_density_ridges(aes(color = NA), scale = 1.3) + 
-    ggdist::stat_dots(aes(color = model)) + 
-    ggdist::stat_pointinterval(point_interval = mean_qi, size = 3, shape = 16, fill = "black", .width = NA) + 
-    ggdist::stat_pointinterval(point_interval = median_qi, size = 3, shape = 15, fill = "black", .width = NA) + 
+    ggdist::stat_dots(aes(color = Model),
+                      dotsize = dotsize) + 
+    ggdist::stat_pointinterval(point_interval = mean_qi, size = 3, 
+                               shape = 16, fill = "black", .width = NA) + 
+    ggdist::stat_pointinterval(point_interval = median_qi, size = 3, 
+                               shape = 15, fill = "black", .width = NA) + 
         facet_wrap(~ target_type, ncol = 1, scales = "free") + 
     theme(plot.margin=unit(c(0,0.4,0,0),"cm")) +
-    # geom_density_ridges(quantile_lines=TRUE,
-    #                     quantile_fun=function(x,...) mean(x), 
-    #                     linetype = "dotted", 
-    #                     alpha = 0, 
-    #                     scale = 0.9, 
-    #                     rel_min_height = 0.01) +
     scale_fill_manual(values = coldeaths) + 
     scale_color_manual(values = coldeaths) + 
-    # scale_color_manual(aesthetics = "point_color", 
-    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
-    # theme(panel.background = element_rect(fill = "#e1f0fe")) +
     theme(legend.position = "bottom") + 
-    labs(y = "Model", x = "Weighted interval score") + 
-  scale_x_continuous(labels = scales::label_number(suffix = "k", 
-                                                   scale = 1e-3, 
-                                                   accuracy = NULL)) + 
+    labs(y = "", x = xlabel) + 
+  scale_x_continuous(labels = scale_fn) + 
     theme_minimal()
@@
     facet_wrap(~ target_type, ncol = 1, scales = "free") + 
-    theme(plot.margin=unit(c(0,0.4,0,0),"cm"))
+    theme(plot.margin=unit(c(0,0.4,0,0),"cm")) + 
+    theme(legend.position = "none") + 
+    guides(shape = "none", colour = "none", fill = "none")
 
@@
 
-  pl_wis <- wrap_plots(p_combined_wis, p_wis, widths = c(1, 2)) / p_phases_wis + 
-    plot_layout(guides = "collect") & 
+  # pl_wis <- wrap_plots(p_combined_wis, p_wis, widths = c(1, 2)) / p_phases_wis + 
+  pl_wis <- p_combined_wis + p_wis +
+    plot_layout(guides = "collect", 
+                widths = c(1, 2)) &
     plot_annotation(tag_levels = 'A')  &
-    theme(legend.position = 'bottom')
+    theme(legend.position = 'bottom', 
+          legend.box="vertical", legend.margin=margin())
 
@@
               paste0("distribution_scores_wis-", i, ".png")), 
-         pl_wis, height = 11, width = 9)
-
-}
-
+         plot = pl_wis, height = 6, width = 9)
+
+}
+
+# plot with rank distributions
+for (i in 1:4) {
+  p_combined_wis <- distribution_plot_wis(df = scores[horizon == i], 
+                                          x = "interval_score", 
+                                          ranks = TRUE) +
+    facet_wrap(~ target_type, ncol = 1, scales = "free") + 
+    theme(plot.margin=unit(c(0,0.4,0,0),"cm")) + 
+    theme(legend.position = "none") + 
+    guides(shape = "none", colour = "none", fill = "none")
+
+  p_wis <- distribution_plot_wis(df = scores[horizon == i], 
+                                 ranks = TRUE) + 
+  theme(axis.title.y=element_blank(),
+        axis.text.y=element_blank(), 
+        axis.ticks.y = element_blank()) + 
+  facet_wrap(~ location_target, ncol = 2, scale = "free")
+
+  p_phases_wis <- distribution_plot_wis(df = scores[horizon == i]) + 
+    facet_wrap( ~ target_phase, scales = "free_x")
+
+  # pl_wis <- wrap_plots(p_combined_wis, p_wis, widths = c(1, 2)) / p_phases_wis + 
+  pl_wis <- p_combined_wis + p_wis +
+    plot_layout(guides = "collect", 
+                widths = c(1, 2)) &
+    plot_annotation(tag_levels = 'A')  &
+    theme(legend.position = 'bottom', 
+          legend.box="vertical", legend.margin=margin())
+
+  ggsave(here("analysis", "plots", 
+              paste0("distribution_scores_wis-", i, "-ranks.png")), 
+         plot = pl_wis, height = 6, width = 9)
+
+}
+
+# same plot for absolute error
 p_combined_ae <- distribution_plot_wis(df = scores, 
@@
   facet_wrap(~ target_type, ncol = 1, scales = "free_x")
-
-# p <- distribution_plot(df = scores[model != "Baseline"]) + 
-#   theme(axis.title.y=element_blank(),
-#         axis.text.y=element_blank(), 
-#         axis.ticks.y = element_blank()) + 
-#   facet_wrap(~ location_target, ncol = 2)
 
@@
 
-aggregate_performance <- function(data, 
-                                  x = "horizon",
-                                  xlabel = "Forecast horizon",
-                                  output_dir = here("analysis", "plots"), 
-                                  plotname,
-                                  relative = FALSE,
-                                  facet_formula = ~ target_type) {
-
-  scores <- eval_forecasts(data, 
-                           summarise_by = c("model", "target_type", x), 
-                           quantiles = 0.5, 
-                           sd = TRUE)
-
-  setnames(scores, old = "model", new = "Model")
-
-  plot_helper <- function(tmp = scores, xvar = x, y, rel = relative) {
+# function to make plot with mean of a given metric
+plot_helper <- function(tmp = scores, xvar = x, y, rel = relative, 
+                        facet_formula, colour) {
   if (rel) {
     tmp <- tmp %>%
-        arrange(target_type, get(x)) %>%
-        group_by(target_type, get(x)) %>%
-        mutate_at(y, ~ . - .[Model == "Hub-ensemble"])
+      arrange(target_type, !!sym(xvar)) %>%
+      group_by(target_type, !!sym(xvar)) %>%
+      mutate_at(y, ~ . / .[Model == "Hub-ensemble"])
   }
@@
     ggplot(aes_string(x = xvar, y = y, group = "Model", color = "Model")) +
-      geom_point() +
-      geom_line() +
+    geom_point(position = position_dodge(width = 0.1)) +
+    geom_line(position = position_dodge(width = 0.1)) +
     facet_wrap(facet_formula, scales = "free_y") +
@@
     theme(legend.position = "bottom") +
-      scale_color_manual(values = coldeaths)
-  }
-
-  # mean performance
-  p_mean <- 
-    plot_helper(scores, y = "interval_score") + 
-    labs(y = "mean WIS", x = NULL)
-
-    # absolute error of performance
-  p_aem <-
-    plot_helper(scores, y = "aem") + 
-    labs(y = "Absolute error", x = NULL)
-
-  # sd of performance
-  p_wis_sd <- 
-    plot_helper(scores, y = "interval_score_sd") + 
-    labs(y = "WIS - sd", x = NULL)
-
-  # sharpness of performance
-  p_sharpness <- 
-    plot_helper(scores, y = "sharpness") + 
-    labs(y = "Sharpness", x = NULL)
-
-  # bias
-  p_bias <- 
-    plot_helper(scores, y = "bias") + 
-    labs(y = "Bias", x = NULL) +
-    geom_hline(yintercept = 0, linetype = "dashed") +
-    expand_limits(y=c(-0.2, 0.2))
-
-  data <- filtered_data[model %in% regular_models]
-
-  scores <- eval_forecasts(data, 
-                           summarise_by = c("model", "target_type", "horizon"), 
-                           quantiles = 0.5, 
-                           sd = TRUE)
-
-  setnames(scores, old = "model", new = "Model")
-
-  component_plot <- function(scores, type) {
-
-    if (type == "case") {
+    scale_color_manual(values = colour)
+}
+
+# function for creating a component plot
+component_plot <- function(scores, type, x = x, rel = relative,
+                           facet_formula, vals = NULL) {
+
+  if (type == "case" & is.null(vals)) {
     vals <- colcases
-    } else {
+  } else if (type == "death" & is.null(vals)){
     vals <- coldeaths
-    }
-
-    scores %>%
-      select(Model, target_type, horizon, sharpness, interval_score,
-             underprediction, overprediction) %>%
+  } else if (type == "case") {
+    # filter out ensembles not needed
+    scores <- scores %>%
+      filter(!(Model %in% c("Hub-ensemble-with-all", "Hub-ensemble-with-convolution")))
+    vals <- vals[-c(3, 4)]
+  }
+
+  scores <- scores %>%
+    select(Model, target_type, sharpness, interval_score,
+           underprediction, overprediction, !!x) %>%
     filter(target_type == type) %>%
@@
                                           c("sharpness", "underprediction", 
-                                              "overprediction"))) %>%
-      group_by(target_type, horizon) %>%
-      arrange(interval_score) %>%
+                                            "overprediction")))
+
+  if (rel) {
+    scores <- scores %>%
+      arrange(!!sym(x), target_type, interval_score) %>%
+      group_by(!!sym(x), target_type) %>%
+      mutate_at("value", ~ . / interval_score[Model == "Hub-ensemble"])
+  }
+
+  p <- scores %>%
     ggplot(aes(x = reorder(Model, (interval_score)), y = value, fill = Model, 
-                 group = Model, alpha = `WIS components`)) + 
+               group = Model, alpha = `WIS components`))
+
+  if (rel) {
+    p <- p + 
+      geom_hline(yintercept = 1, linetype = "dashed")
+  }
+
+  p <- p + 
     scale_alpha_manual(values = c(1, 0.1, 0.6)) +
@@
              width = 0.8) +
-      facet_wrap(~ horizon, ncol = 4,
+    facet_wrap(as.formula(paste("~", x)), ncol = 4,
                strip.position="bottom") + 
@@
     guides(fill = "none")
-  }
-
-  component_case <- component_plot(scores, "case")
-  component_death <- component_plot(scores, "death")
+
+  return(p)
+}
+
+score_helper <- function(data, summarise_by) {
+  scores <- eval_forecasts(data, 
+                           summarise_by = summarise_by, 
+                           quantiles = 0.5, 
+                           sd = TRUE) %>%
+    filter(!(model %in% c("Hub-ensemble-with-all", 
+                          "Hub-ensemble-with-convolution") & 
+               target_type == "case"))
+
+  setnames(scores, old = "model", new = "Model")
+}
+
+aggregate_performance <- function(data, 
+                                  x = "horizon",
+                                  xlabel = "Forecast horizon",
+                                  output_dir = here("analysis", "plots"), 
+                                  plotname,
+                                  relative = FALSE,
+                                  facet_formula = ~ target_type, 
+                                  colour_scheme = c("normal", "ensemble"),
+                                  vals = NULL) {
+
+  # create scores
+  scores <- score_helper(data, c("model", "target_type", x))
+
+  if (colour_scheme[1] == "normal") {
+    vals <- coldeaths
+  } else {
+    vals <- colensemble
+  }
+
+  # mean performance
+  p_mean <- 
+    plot_helper(scores, y = "interval_score", rel = relative, 
+                facet_formula = facet_formula, colour = vals) + 
+    labs(y = "mean WIS", x = NULL)
+
+    # absolute error of performance
+  p_aem <-
+    plot_helper(scores, y = "aem", rel = relative, 
+                facet_formula = facet_formula, colour = vals) + 
+    labs(y = "Absolute error", x = NULL)
+
+  # sd of performance
+  p_wis_sd <- 
+    plot_helper(scores, y = "interval_score_sd", rel = relative, 
+                facet_formula = facet_formula, colour = vals) + 
+    labs(y = "WIS - sd", x = NULL)
+
+  # sharpness of performance
+  p_sharpness <- 
+    plot_helper(scores, y = "sharpness", rel = relative, 
+                facet_formula = facet_formula, colour = vals) + 
+    labs(y = "Sharpness", x = NULL)
+
+  # bias plot
+  bias_limits <- max(abs(scores$bias)) * c(-1.1, 1.1) %>% 
+    round(2)
+  p_bias <- 
+    plot_helper(scores, y = "bias", rel = FALSE, colour = vals, 
+                facet_formula = facet_formula) + 
+    labs(y = "Bias", x = NULL) +
+    geom_hline(yintercept = 0, linetype = "dashed") +
+    expand_limits(y=bias_limits)
+
+  # plot with wis components
+  component_case <- component_plot(scores, "case", x = x, vals = vals, 
+                                   facet_formula = facet_formula, rel = relative)
+  component_death <- component_plot(scores, "death", x = x, vals = vals, 
+                                    facet_formula = facet_formula, rel = relative)
   components <- component_case + component_death
 
-  # coverage
-  scores <- eval_forecasts(data, 
-                           summarise_by = c("model", "target_type", x, "range"), 
-                           quantiles = 0.5, 
-                           sd = TRUE)
-
-  setnames(scores, old = "model", new = "Model")
-
-  p_cov50 <- scores[range %in% c(50)] %>%
-    plot_helper(y = "coverage", rel = FALSE) + 
+  # coverage plots 
+  scores <- score_helper(data,  c("model", "target_type", x, "range"))
+
+  if (relative) {
+    scores <- scores %>%
+      arrange(target_type, range, !!sym(x)) %>%
+      group_by(target_type, range, !!sym(x)) %>%
+      mutate_at("coverage", ~ . - .[Model == "Hub-ensemble"])
+  }
+
+  p_cov50 <- scores %>%
+    filter(range == c(50)) %>%
+    plot_helper(y = "coverage", rel = FALSE, , facet_formula = facet_formula, 
+                colour = vals) +
+    labs(y = "Coverage - 50% PI") + 
+    scale_y_continuous(labels = scales::percent)
+
+  if (!relative) {
+    p_cov50 <- p_cov50 + 
+      expand_limits(y=c(0, 1)) + 
       geom_hline(yintercept = 0.5, linetype = "dashed") + 
-    labs(y = "Coverage - 50% PI") + 
+      labs(y = "Diff. cov. - 50% PI", x = "") + 
+      scale_y_continuous()
+    }
+
+  p_cov90 <-  scores %>%
+    filter(range == c(90)) %>%
+    plot_helper(y = "coverage", rel = FALSE, facet_formula = facet_formula, 
+                colour = vals) + 
+    labs(y = "Coverage - 90% PI", x = "") + 
+    scale_y_continuous(labels = scales::percent)
+
+    if (!relative) {
+      p_cov90 <- p_cov90 + 
         expand_limits(y=c(0, 1)) + 
-    scale_y_continuous(labels = scales::percent)
-
-  p_cov90 <- scores[range %in% c(90)] %>%
-    plot_helper(y = "coverage", rel = FALSE) + 
         geom_hline(yintercept = 0.9, linetype = "dashed") + 
-    labs(y = "Coverage - 90% PI") + 
-    expand_limits(y=c(0, 1)) + 
-    scale_y_continuous(labels = scales::percent)
+        labs(y = "Diff. cov. - 90% PI") + 
+        scale_y_continuous()
+    }
 
@@
 
+# plot for locations
 filtered_data[model %in% regular_models & horizon == 2] %>%
@@
 
+# relative plots for locations
+filtered_data[model %in% regular_models & horizon == 2] %>%
+  aggregate_performance(plotname = "aggregate-performance-2-weeks-locations-all-rel", 
+                        x = "location_name", 
+                        xlabel = NULL, relative = TRUE)
+
+# plot for ensemble
 filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]] %>%
+  # filter(!(model == "Hub-ensemble-with-all" & target_type == "case")) %>%
   aggregate_performance(plotname = "aggregate-performance-rel-ensemble", 
-                        relative = TRUE)
+                        relative = TRUE, colour_scheme = "ensemble")
 

### 2021-08-27 data-raw/paper.R

@@ -64,7 +64,7 @@ change_model_name <- function(names, old_name, new_name) {
 
 change_names <- list(
   c("KITCOVIDhub-median_ensemble", 
-    "Hub-ensemble-all"), 
+    "Hub-ensemble-realised"), 
   c("KITCOVIDhub-mean_ensemble", 
     "Hub-ensemble-mean-all"), 
   c("KIT-baseline", 
@@ -86,7 +86,11 @@ change_names <- list(
   c("KITCOVIDhub-mean_ensemble_exclude_EpiExpert", 
     "Hub-ensemble-mean-with-renewal"), 
   c("KITCOVIDhub-mean_ensemble_exclude_EpiNow2", 
-    "Hub-ensemble-mean-with-crowd")
+    "Hub-ensemble-mean-with-crowd"), 
+  c("KITCOVIDhub-median_ensemble_include_EpiNow2_secondary_additionally", 
+    "Hub-ensemble-with-all"), 
+  c("KITCOVIDhub-median_ensemble_include_only_EpiNow2_secondary", 
+    "Hub-ensemble-with-convolution")
 )
 
 purrr::walk(change_names, 
@@ -117,7 +121,7 @@ weekly_deaths <- fread(here("data-raw", "weekly-incident-deaths.csv"))
 weekly_deaths[, target_type := "death"]
 truth <- rbindlist(list(weekly_cases, weekly_deaths)) 
 truth <- truth[location_name %in% c("Germany", "Poland")]
-truth_data <- truth[, `:=` (location = NULL, epiweek = NULL, 
+truth_data <- truth[, `:=` (location = NULL, 
               target_end_date = as.Date(target_end_date))]
 setnames(truth_data, old = "value", new = "true_value")
 

### 2021-09-17 analysis/analysis-graveyard.Rmd
update code and plots

@@
 - do models lose out that aren't great, but have no outliers?
+
+--------------------------------------------------------------------------------
+### alternative visualisation of forecasts
+--> show underprediction, sharpness, overprediction in one plot
+
+not yet done
+
+```{r}
+scores_over_time_plot_components <- function(scores) {
+
+size = 1.8
+width = 4
+
+scores %>%
+  ggplot(aes(x = forecast_date, 
+             group = model, 
+             color = model)) +
+
+  geom_linerange(aes(ymin = -0.5*sharpness, ymax = 0.5 * sharpness, alpha = "Sharpness"), 
+                 size = size,
+                 alpha = 1,
+                 position = position_dodge(width = width)) +
+
+  geom_linerange(aes(ymax = -0.5 * sharpness, ymin = -0.5* sharpness - underprediction),
+                 size = size,
+                 position = position_dodge(width = width)) + 
+  geom_linerange(aes(ymax = -0.5 * sharpness, ymin = -0.5* sharpness - underprediction),
+                 size = size,
+                 colour = "white",
+                 size = size - 0.6,
+                 alpha = 0.6,
+                 position = position_dodge(width = width)) + 
+  geom_linerange(aes(ymin = 0.5 * sharpness, ymax = 0.5* sharpness + overprediction),
+                 size = size,
+                 position = position_dodge(width = width)) + 
+  geom_linerange(aes(ymin = 0.5 * sharpness, ymax = 0.5* sharpness + overprediction),
+                 size = size,
+                 colour = "white",
+                 size = size - 0.6,
+                 alpha = 0.6,
+                 position = position_dodge(width = width)) + 
+  theme_minimal() + 
+  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
+                          max(forecast_dates$full_hub_period)))
+
+}
+
+# scores_target_forecastdate[horizon == i & target_type == "case"] %>%
+#   scores_over_time_plot_components() + 
+#   scale_color_manual(values = colcases) + 
+#   labs(y = "WIS rel. to baseline", x = "")
+
+```
+
+```{r}
+# # calculate median and sd of the WIS -------------------------------------------
+# 
+# df <- eval_forecasts(
+#   filtered_data[model %in% regular_models], 
+#   metric = "interval_score",
+#   summarise_by = c("model", "horizon", "target_type"), 
+#   sd = TRUE, 
+#   quantile = 0.5
+# ) 
+# 
+# 
+# df <- df[, .(model, horizon, target_type, 
+#              `WIS - mean` = interval_score, 
+#              `WIS - median` = interval_score_0.5, 
+#              `WIS - sd` = interval_score_sd)] %>%
+#     dcast(... ~ ., value.var = c("WIS - mean", "WIS - median", "WIS - sd"))
+# 
+# setcolorder(df, c("target_type", "horizon", "model"))
+# 
+# 
+# table <- df[order(target_type, horizon, model)] %>%
+#   score_table()
+# 
+# save_kable(table, 
+#            file = here("analysis", "plots", "table-wis-sd-median.png"))
+
+```
+
+```{r}
+# calculate percentage differences in performance ------------------------------
+
+df <- eval_forecasts(
+  filtered_data, 
+  summarise_by = c("model", "horizon", "target_type")
+)
+
+df <- df %>%
+  merge(df[model == "Hub-ensemble", 
+           .(horizon, target_type, base_score = interval_score)])
+df[, rel_score := (interval_score / base_score) * 100 - 100]
+df[, diff_score := interval_score - base_score]
+df[, .(horizon, target_type, model, rel_score, diff_score)][order(target_type, horizon)]
+
+```

### 2021-09-17 analysis/analysis.Rmd
update code and plots

@@
 
+# helper function for labelling
+scale_fn <- function(x) {
+  ifelse(x >= 5000,
+         paste0(x / 1000, "k"), x)
+}
+
 ```
@@
     scale_x_date(limits = c(min(limits), max(limits)), 
-                 minor_breaks = limits)
+                 minor_breaks = limits) + 
+      scale_y_continuous(labels = scale_fn)
   return(p)
@@
     theme(panel.grid.major.x = element_blank()) +
-    scale_y_continuous(labels = comma) + # , 
+    scale_y_continuous(labels = scale_fn) + # , 
                        # trans = log_trans()) + 
@@
       guides(color = "none", shape = "none") + 
-      theme(plot.margin = unit(c(0.5,1.3,0.5,0.5), "cm"))
+      theme(plot.margin = unit(c(0.5,1.3,0.5,0.5), "cm")) + 
+      scale_y_continuous(labels = scale_fn)
 
@@
 # ensemble variants
-models <- c("Hub-ensemble-all", "Crowd forecast", "Hub-ensemble", "Renewal")
-unfiltered_data[model %in% models] %>%
-  forecasts_and_scores(plotname = "figure-forecasts-ensembles", 
-                       ensembles = TRUE)
-
-```
-
---------------------------------------------------------------------------------
-### alternative visualisation of forecasts
-
-not yet done
-
-```{r}
-scores_over_time_plot_components <- function(scores) {
-
-size = 1.8
-width = 4
-
-scores %>%
-  ggplot(aes(x = forecast_date, 
-             group = model, 
-             color = model)) +
-
-  geom_linerange(aes(ymin = -0.5*sharpness, ymax = 0.5 * sharpness, alpha = "Sharpness"), 
-                 size = size,
-                 alpha = 1,
-                 position = position_dodge(width = width)) +
-
-  geom_linerange(aes(ymax = -0.5 * sharpness, ymin = -0.5* sharpness - underprediction),
-                 size = size,
-                 position = position_dodge(width = width)) + 
-  geom_linerange(aes(ymax = -0.5 * sharpness, ymin = -0.5* sharpness - underprediction),
-                 size = size,
-                 colour = "white",
-                 size = size - 0.6,
-                 alpha = 0.6,
-                 position = position_dodge(width = width)) + 
-  geom_linerange(aes(ymin = 0.5 * sharpness, ymax = 0.5* sharpness + overprediction),
-                 size = size,
-                 position = position_dodge(width = width)) + 
-  geom_linerange(aes(ymin = 0.5 * sharpness, ymax = 0.5* sharpness + overprediction),
-                 size = size,
-                 colour = "white",
-                 size = size - 0.6,
-                 alpha = 0.6,
-                 position = position_dodge(width = width)) + 
-  theme_minimal() + 
-  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
-                          max(forecast_dates$full_hub_period)))
-
-}
-
-# scores_target_forecastdate[horizon == i & target_type == "case"] %>%
-#   scores_over_time_plot_components() + 
-#   scale_color_manual(values = colcases) + 
-#   labs(y = "WIS rel. to baseline", x = "")
+
+# models <- c("Hub-ensemble-all", "Crowd forecast", "Hub-ensemble", "Renewal")
+# unfiltered_data[model %in% models] %>%
+#   forecasts_and_scores(plotname = "figure-forecasts-ensembles", 
+#                        ensembles = TRUE)
 
@@
     .(model, target_type, coverage, range, horizon)] %>%
-    dcast(formula = ... ~ range, value.var = "coverage")
+    dcast(formula = ... ~ range, value.var = "coverage") %>%
+    filter(!(model %in% c("Hub-ensemble-with-all", 
+                          "Hub-ensemble-with-convolution", 
+                          "Hub-ensemble-with-all-mean", 
+                          "Hub-ensemble-with-convolution-mean") & 
+               target_type == "case"))
 
@@
     compute_relative_skill = FALSE,
-    sd = TRUE, 
-    quantiles = 0.5) %>%
+    sd = TRUE) %>%
+    filter(!(model %in% c("Hub-ensemble-with-all", 
+                          "Hub-ensemble-with-convolution", 
+                          "Hub-ensemble-with-all-mean", 
+                          "Hub-ensemble-with-convolution-mean") & 
+               target_type == "case")) %>%
     merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))
@@
 
-  percentage_cols <- c("interval_score", "interval_score_0.5", 
+  percentage_cols <- c("interval_score", 
                        "interval_score_sd", "sharpness", "underprediction", 
@@
     dplyr::group_by(horizon, target_type) %>%
-    dplyr::mutate_at(percentage_cols, ~ paste0(., " (", 
-                                               round(100 * ./.[model == "Hub-ensemble"]), 
+    dplyr::mutate_at(percentage_cols, 
+                     ~ paste0(., " (", 
+                              round(100 * ./.[model %in% c("Hub-ensemble", 
+                                                           "Hub-ensemble-mean")]), 
                               "%)"))
@@
 
-  setnames(df, old = c("interval_score_0.5", "interval_score_sd"), 
-           new = c("WIS - median", 
-                   "WIS - sd"))
+  setnames(df, old = c("interval_score_sd"), 
+           new = c("WIS - sd"))
 
@@
   make_table(plotname = "table_median-ensemble_scores")
-
-```
-
-```{r}
-# # calculate median and sd of the WIS -------------------------------------------
-# 
-# df <- eval_forecasts(
-#   filtered_data[model %in% regular_models], 
-#   metric = "interval_score",
-#   summarise_by = c("model", "horizon", "target_type"), 
-#   sd = TRUE, 
-#   quantile = 0.5
-# ) 
-# 
-# 
-# df <- df[, .(model, horizon, target_type, 
-#              `WIS - mean` = interval_score, 
-#              `WIS - median` = interval_score_0.5, 
-#              `WIS - sd` = interval_score_sd)] %>%
-#     dcast(... ~ ., value.var = c("WIS - mean", "WIS - median", "WIS - sd"))
-# 
-# setcolorder(df, c("target_type", "horizon", "model"))
-# 
-# 
-# table <- df[order(target_type, horizon, model)] %>%
-#   score_table()
-# 
-# save_kable(table, 
-#            file = here("analysis", "plots", "table-wis-sd-median.png"))
-
-```
-
-```{r}
-# calculate percentage differences in performance ------------------------------
-
-df <- eval_forecasts(
-  filtered_data, 
-  summarise_by = c("model", "horizon", "target_type")
-)
-
-df <- df %>%
-  merge(df[model == "Hub-ensemble", 
-           .(horizon, target_type, base_score = interval_score)])
-df[, rel_score := (interval_score / base_score) * 100 - 100]
-df[, diff_score := interval_score - base_score]
-df[, .(horizon, target_type, model, rel_score, diff_score)][order(target_type, horizon)]
 
@@
 
-  scale_fn <- function(x) {
-    ifelse(x >= 5000,
-           paste0(x / 1000, "k"), x)
-  }
-
   xlabel = "Weighted interval score"
@@
       arrange(location_name, target_type, horizon, forecast_date, interval_score) %>%
-      mutate(!!x := rank(get(x)))
-
+      mutate(!!x := rank(get(x))) %>%
+      ungroup() 
     xlabel <- "Rank in terms of WIS"
@@
   }
-  + runif(length(get(x)), min = -0.1, max = 0.1)
 
@@
       group_by(target_type, !!sym(xvar)) %>%
-      mutate_at(y, ~ . / .[Model == "Hub-ensemble"])
+      mutate_at(y, ~ . / .[Model %in% c("Hub-ensemble", 
+                                        "Hub-ensemble-mean")])
   }
@@
     theme(legend.position = "bottom") +
-    scale_color_manual(values = colour)
+    scale_color_manual(values = colour) + 
+    scale_y_continuous(labels = scale_fn)
 }
@@
 # function for creating a component plot
-component_plot <- function(scores, type, x = x, rel = relative,
+component_plot <- function(scores, type, colour_scheme, x = x, rel = relative,
                            facet_formula, vals = NULL) {
 
-  if (type == "case" & is.null(vals)) {
-    vals <- colcases
-  } else if (type == "death" & is.null(vals)){
-    vals <- coldeaths
-  } else if (type == "case") {
+ if (colour_scheme == "ensemble") {
     # filter out ensembles not needed
@@
     vals <- vals[-c(3, 4)]
+ } else if (type == "case") {
+    vals <- vals[-1]
   }
@@
       group_by(!!sym(x), target_type) %>%
-      mutate_at("value", ~ . / interval_score[Model == "Hub-ensemble"])
+      mutate_at("value", ~ . / interval_score[Model %in% c("Hub-ensemble", 
+                                                           "Hub-ensemble-mean")])
   }
@@
     filter(!(model %in% c("Hub-ensemble-with-all", 
-                          "Hub-ensemble-with-convolution") & 
+                          "Hub-ensemble-with-convolution", 
+                          "Hub-ensemble-with-all-mean", 
+                          "Hub-ensemble-with-convolution-mean") & 
                target_type == "case"))
@@
   p_mean <- 
-    plot_helper(scores, y = "interval_score", rel = relative, 
+    plot_helper(scores, y = "interval_score", rel = relative, xvar = x, 
                 facet_formula = facet_formula, colour = vals) + 
@@
   p_aem <-
-    plot_helper(scores, y = "aem", rel = relative, 
+    plot_helper(scores, y = "aem", rel = relative, xvar = x,
                 facet_formula = facet_formula, colour = vals) + 
@@
   p_wis_sd <- 
-    plot_helper(scores, y = "interval_score_sd", rel = relative, 
+    plot_helper(scores, y = "interval_score_sd", rel = relative, xvar = x,
                 facet_formula = facet_formula, colour = vals) + 
@@
   p_sharpness <- 
-    plot_helper(scores, y = "sharpness", rel = relative, 
+    plot_helper(scores, y = "sharpness", rel = relative, xvar = x,
                 facet_formula = facet_formula, colour = vals) + 
@@
   p_bias <- 
-    plot_helper(scores, y = "bias", rel = FALSE, colour = vals, 
+    plot_helper(scores, y = "bias", rel = FALSE, colour = vals, xvar = x,
                 facet_formula = facet_formula) + 
@@
   component_case <- component_plot(scores, "case", x = x, vals = vals, 
-                                   facet_formula = facet_formula, rel = relative)
+                                   facet_formula = facet_formula, rel = relative, 
+                                   colour_scheme = colour_scheme[1])
   component_death <- component_plot(scores, "death", x = x, vals = vals, 
-                                    facet_formula = facet_formula, rel = relative)
+                                    facet_formula = facet_formula, rel = relative, 
+                                    colour_scheme = colour_scheme[1])
   components <- component_case + component_death
@@
       group_by(target_type, range, !!sym(x)) %>%
-      mutate_at("coverage", ~ . - .[Model == "Hub-ensemble"])
+      mutate_at("coverage", ~ . - .[Model %in%  c("Hub-ensemble", 
+                                                  "Hub-ensemble-mean")])
   }
@@
     filter(range == c(50)) %>%
-    plot_helper(y = "coverage", rel = FALSE, , facet_formula = facet_formula, 
-                colour = vals) +
-    labs(y = "Coverage - 50% PI") + 
+    plot_helper(y = "coverage", rel = FALSE, facet_formula = facet_formula, 
+                colour = vals, xvar = x) +
+    labs(y = "Diff. cov. - 50% PI", x = "") + 
     scale_y_continuous(labels = scales::percent)
@@
       expand_limits(y=c(0, 1)) + 
+      labs(y = "Coverage - 50% PI", x = "") + 
       geom_hline(yintercept = 0.5, linetype = "dashed") + 
-      labs(y = "Diff. cov. - 50% PI", x = "") + 
-      scale_y_continuous()
+      scale_y_continuous(labels = scales::percent)
     }
@@
     plot_helper(y = "coverage", rel = FALSE, facet_formula = facet_formula, 
-                colour = vals) + 
-    labs(y = "Coverage - 90% PI", x = "") + 
+                xvar = x, colour = vals) + 
+    labs(y = "Diff. cov. - 90% PI") + 
     scale_y_continuous(labels = scales::percent)
@@
         expand_limits(y=c(0, 1)) + 
+        labs(y = "Coverage - 90% PI", x = "") + 
         geom_hline(yintercept = 0.9, linetype = "dashed") + 
-        labs(y = "Diff. cov. - 90% PI") + 
-        scale_y_continuous()
+        scale_y_continuous() + 
+        scale_y_continuous(labels = scales::percent)
     }
@@
   aggregate_performance(plotname = "aggregate-performance-rel-ensemble", 
+                        relative = TRUE, colour_scheme = "ensemble")
+
+filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]] %>%
+  # filter(!(model == "Hub-ensemble-with-all" & target_type == "case")) %>%
+  aggregate_performance(plotname = "aggregate-performance-rel-ensemble-mean", 
                         relative = TRUE, colour_scheme = "ensemble")

### 2021-09-17 data-raw/paper.R

@@ -9,9 +9,9 @@ library(scoringutils)
 # ==============================================================================
 
 # update forecast data from server ---------------------------------------------
-system(
-  paste(". data-raw/paper.sh")
-)
+# system(
+#   paste(". data-raw/paper.sh")
+# )
 
 # get the correct file paths to all forecasts ----------------------------------
 folders <- here::here("data-raw", list.files("data-raw"))
@@ -66,7 +66,8 @@ change_names <- list(
   c("KITCOVIDhub-median_ensemble", 
     "Hub-ensemble-realised"), 
   c("KITCOVIDhub-mean_ensemble", 
-    "Hub-ensemble-mean-all"), 
+    "Hub-ensemble-realised-mean"), 
+  
   c("KIT-baseline", 
     "Baseline"),
   c("epiforecasts-EpiExpert", 
@@ -75,23 +76,35 @@ change_names <- list(
     "Renewal"), 
   c("epiforecasts-EpiNow2_secondary", 
     "Convolution"), 
+  
   c("KITCOVIDhub-median_ensemble_exclude_both", 
     "Hub-ensemble"), 
-  c("KITCOVIDhub-median_ensemble_exclude_EpiExpert", 
-    "Hub-ensemble-with-renewal"), 
-  c("KITCOVIDhub-median_ensemble_exclude_EpiNow2", 
-    "Hub-ensemble-with-crowd"), 
   c("KITCOVIDhub-mean_ensemble_exclude_both", 
     "Hub-ensemble-mean"), 
+  
+  c("KITCOVIDhub-median_ensemble_exclude_EpiExpert", 
+    "Hub-ensemble-with-renewal"), 
   c("KITCOVIDhub-mean_ensemble_exclude_EpiExpert", 
-    "Hub-ensemble-mean-with-renewal"), 
+    "Hub-ensemble-with-renewal-mean"), 
+  
+  c("KITCOVIDhub-median_ensemble_exclude_EpiNow2", 
+    "Hub-ensemble-with-crowd"), 
   c("KITCOVIDhub-mean_ensemble_exclude_EpiNow2", 
-    "Hub-ensemble-mean-with-crowd"), 
+    "Hub-ensemble-with-crowd-mean"), 
+  
   c("KITCOVIDhub-median_ensemble_include_EpiNow2_secondary_additionally", 
     "Hub-ensemble-with-all"), 
[…]

### 2021-09-17 analysis/past-renewal-forecasts.R
add files to run past renewal and convolution forecasts

@@ -1,0 +1,60 @@
+# Packages -----------------------------------------------------------------
+library(covid.german.forecasts)
+library(EpiNow2, quietly = TRUE)
+library(data.table, quietly = TRUE)
+library(future, quietly = TRUE)
+library(here, quietly = TRUE)
+library(lubridate, quietly = TRUE)
+
+# Set target dates ---------------------------------------------------------
+dates <- as.character(as.Date("2020-10-12") + 7*(0:9))
+
+# Update delays -----------------------------------------------------------
+generation_time <- readRDS(here("rt-forecast", "data", "delays", "generation_time.rds"))
+incubation_period <- readRDS(here("rt-forecast", "data" ,"delays", "incubation_period.rds"))
+onset_to_report <- readRDS(here("rt-forecast", "data", "delays", "onset_to_report.rds"))
+
+
+for (target_date in dates) {
+  # Get cases  ---------------------------------------------------------------
+  cases <- fread(file.path("data-raw", "daily-incidence-cases.csv"))
+  cases <- cases[, .(region = as.character(location_name), date = as.Date(date), confirm = value)]
+  cases <- cases[confirm < 0, confirm := 0]
+  cases <- cases[date >= (max(date) - weeks(12))]
+  setorder(cases, region, date)
+  
+  # Set up parallel execution -----------------------------------------------
+  no_cores <- setup_future(cases)
+  
+  # Run Rt estimation -------------------------------------------------------
+  rt <- opts_list(rt_opts(prior = list(mean = 1.1, sd = 0.2), future = "latest"), cases)
+  # add population adjustment for each country
+  loc_names <- names(rt)
+  rt <- lapply(loc_names,  function(loc) {
+    rt_loc <- rt[[loc]]
+    rt_loc$pop <- locations[location_name %in% loc, ]$population
+    return(rt_loc)
+  })
+  names(rt) <- loc_names
+  
+  regional_epinow(reported_cases = cases,
+                  generation_time = generation_time, 
+                  delays = delay_opts(incubation_period, onset_to_report),
+                  rt = rt,
+                  stan = stan_opts(samples = 2000, warmup = 250, 
+                                   chains = 4, cores = no_cores),
+                  obs = obs_opts(scale = list(mean = 0.25, sd = 0.05)),
+                  horizon = 30,
+                  output = c("region", "summary", "timing", "samples", "fit"),
+                  target_date = target_date,
+                  target_folder = here("rt-forecast-retrospective", "data", "samples", "cases"), 
[…]

### 2021-09-17 rt-forecast-retrospective/past-convolution-forecasts.R
reorganise files

@@ -21,7 +21,7 @@ for (target_date in dates) {
   # Get case forecasts ------------------------------------------------------
   case_forecast <- suppressWarnings(
     get_regional_results(
-      results_dir = here("rt-forecast", "data", "samples", "cases"),
+      results_dir = here("rt-forecast-retrospective", "data", "samples", "cases"),
       date = ymd(target_date), forecast = TRUE, samples = TRUE
     )$estimated_reported_cases$samples
   )

### 2021-09-17 rt-forecast-retrospective/past-renewal-forecasts.R
update regions

@@ -21,6 +21,7 @@ for (target_date in dates) {
   cases <- cases[, .(region = as.character(location_name), date = as.Date(date), confirm = value)]
   cases <- cases[confirm < 0, confirm := 0]
   cases <- cases[date >= (max(date) - weeks(12))]
+  cases <- cases[region %in% c("GM", "PL")]
   setorder(cases, region, date)
   
   # Set up parallel execution -----------------------------------------------
@@ -30,6 +31,7 @@ for (target_date in dates) {
   rt <- opts_list(rt_opts(prior = list(mean = 1.1, sd = 0.2), future = "latest"), cases)
   # add population adjustment for each country
   loc_names <- names(rt)
+  loc_names <- c("GM", "PL")
   rt <- lapply(loc_names,  function(loc) {
     rt_loc <- rt[[loc]]
     rt_loc$pop <- locations[location_name %in% loc, ]$population

### 2021-09-17 rt-forecast-retrospective/past-renewal-forecasts.R
correct region names

@@ -21,7 +21,7 @@ for (target_date in dates) {
   cases <- cases[, .(region = as.character(location_name), date = as.Date(date), confirm = value)]
   cases <- cases[confirm < 0, confirm := 0]
   cases <- cases[date >= (max(date) - weeks(12))]
-  cases <- cases[region %in% c("GM", "PL")]
+  cases <- cases[region %in% c("Germany", "Poland")]
   setorder(cases, region, date)
   
   # Set up parallel execution -----------------------------------------------
@@ -31,7 +31,7 @@ for (target_date in dates) {
   rt <- opts_list(rt_opts(prior = list(mean = 1.1, sd = 0.2), future = "latest"), cases)
   # add population adjustment for each country
   loc_names <- names(rt)
-  loc_names <- c("GM", "PL")
+  loc_names <- c("Germany", "Poland")
   rt <- lapply(loc_names,  function(loc) {
     rt_loc <- rt[[loc]]
     rt_loc$pop <- locations[location_name %in% loc, ]$population

### 2021-09-17 rt-forecast-retrospective/past-renewal-forecasts.R
fix date issue

@@ -9,6 +9,8 @@ library(lubridate, quietly = TRUE)
 # Set target dates ---------------------------------------------------------
 dates <- as.character(as.Date("2020-10-12") + 7*(0:9))
 
+target_date <- covid.german.forecasts::latest_weekday()
+
 # Update delays -----------------------------------------------------------
 generation_time <- readRDS(here("rt-forecast", "data", "delays", "generation_time.rds"))
 incubation_period <- readRDS(here("rt-forecast", "data" ,"delays", "incubation_period.rds"))
@@ -20,7 +22,7 @@ for (target_date in dates) {
   cases <- fread(file.path("data-raw", "daily-incidence-cases.csv"))
   cases <- cases[, .(region = as.character(location_name), date = as.Date(date), confirm = value)]
   cases <- cases[confirm < 0, confirm := 0]
-  cases <- cases[date >= (max(date) - weeks(12))]
+  cases <- cases[date >= (max(target_date) - weeks(12))]
   cases <- cases[region %in% c("Germany", "Poland")]
   setorder(cases, region, date)
   

### 2021-09-17 rt-forecast-retrospective/past-renewal-forecasts.R
fix date issue again

@@ -22,7 +22,8 @@ for (target_date in dates) {
   cases <- fread(file.path("data-raw", "daily-incidence-cases.csv"))
   cases <- cases[, .(region = as.character(location_name), date = as.Date(date), confirm = value)]
   cases <- cases[confirm < 0, confirm := 0]
-  cases <- cases[date >= (max(target_date) - weeks(12))]
+  cases <- cases[date >= (max(as.Date(target_date)) - weeks(12))]
+  cases <- cases[date <= (as.Date(target_date))]
   cases <- cases[region %in% c("Germany", "Poland")]
   setorder(cases, region, date)
   

### 2021-09-17 rt-forecast-retrospective/past-renewal-forecasts.R
add script to create submissions for past forecasts

@@ -9,8 +9,6 @@ library(lubridate, quietly = TRUE)
 # Set target dates ---------------------------------------------------------
 dates <- as.character(as.Date("2020-10-12") + 7*(0:9))
 
-target_date <- covid.german.forecasts::latest_weekday()
-
 # Update delays -----------------------------------------------------------
 generation_time <- readRDS(here("rt-forecast", "data", "delays", "generation_time.rds"))
 incubation_period <- readRDS(here("rt-forecast", "data" ,"delays", "incubation_period.rds"))

### 2021-09-17 rt-forecast-retrospective/past-submissions.R

@@ -1,0 +1,69 @@
+# Package -----------------------------------------------------------------
+library(covid.german.forecasts)
+library(data.table)
+library(EpiNow2)
+library(lubridate)
+library(here)
+
+# Dates -------------------------------------------------------------------
+dates <- as.character(as.Date("2020-10-12") + 7*(0:9))
+
+for (target_date in dates) {
+  
+  
+}
+
+# Get forecasts -----------------------------------------------------------
+case_forecast <- suppressWarnings(
+  get_regional_results(results_dir = here("rt-forecast-retrospective", "data", "samples", "cases"),
+                       date = ymd(target_date), forecast = TRUE,
+                       samples = TRUE)$estimated_reported_cases$samples)
+
+death_from_cases_forecast <- fread(here("rt-forecast-retrospective", "data", "samples", "deaths-from-cases",
+                                        target_date, "samples.csv"))
+
+# Cumulative data ---------------------------------------------------------
+cum_cases <- fread(here("data-raw", "weekly-cumulative-cases.csv"))
+cum_deaths <- fread(here("data-raw", "weekly-cumulative-deaths.csv"))
+
+# Format forecasts --------------------------------------------------------
+case_forecast <- format_forecast(case_forecast[, value := cases],
+                                 locations = locations,
+                                 cumulative =  cum_cases,
+                                 forecast_date = target_date,
+                                 submission_date = target_date,
+                                 CrI_samples = 0.8,
+                                 target_value = "case")
+
+death_from_cases_forecast <- format_forecast(death_from_cases_forecast,
+                                             locations = locations,
+                                             cumulative = cum_deaths,
+                                             forecast_date = target_date,
+                                             submission_date = target_date,
+                                             target_value = "death")
+
+# Save forecasts ----------------------------------------------------------
+rt_folder <- here("submissions", "rt-forecasts-retrospective", target_date)
+deaths_folder <- here("submissions", "deaths-from-cases-retrospective", target_date)
+
+check_dir(rt_folder)
+check_dir(deaths_folder)
+
+save_rt <- function(...) {
+  save_forecast(model = "-epiforecasts-EpiNow2-retrospective", 
+                folder = rt_folder,
+                date = target_date,
+                ...)
+}
+
+save_rt(case_forecast, "Germany", "GM", "-case")
+save_rt(case_forecast, "Poland", "PL", "-case")
+
+save_conv <- function(...) {
[…]

### 2021-09-17 rt-forecast-retrospective/past-submissions.R
correct past submissions script

@@ -10,60 +10,58 @@ dates <- as.character(as.Date("2020-10-12") + 7*(0:9))
 
 for (target_date in dates) {
   
+  # Get forecasts -----------------------------------------------------------
+  case_forecast <- suppressWarnings(
+    get_regional_results(results_dir = here("rt-forecast-retrospective", "data", "samples", "cases"),
+                         date = ymd(target_date), forecast = TRUE,
+                         samples = TRUE)$estimated_reported_cases$samples)
   
+  death_from_cases_forecast <- fread(here("rt-forecast-retrospective", "data", "samples", "deaths-from-cases",
+                                          target_date, "samples.csv"))
+  
+  # Cumulative data ---------------------------------------------------------
+  cum_cases <- fread(here("data-raw", "weekly-cumulative-cases.csv"))
+  cum_deaths <- fread(here("data-raw", "weekly-cumulative-deaths.csv"))
+  
+  # Format forecasts --------------------------------------------------------
+  case_forecast <- format_forecast(case_forecast[, value := cases],
+                                   locations = locations,
+                                   cumulative =  cum_cases,
+                                   forecast_date = target_date,
+                                   submission_date = target_date,
+                                   CrI_samples = 0.8,
+                                   target_value = "case")
+  
+  death_from_cases_forecast <- format_forecast(death_from_cases_forecast,
+                                               locations = locations,
+                                               cumulative = cum_deaths,
+                                               forecast_date = target_date,
+                                               submission_date = target_date,
+                                               target_value = "death")
+  
+  # Save forecasts ----------------------------------------------------------
+  rt_folder <- here("submissions", "rt-forecasts-retrospective", target_date)
+  deaths_folder <- here("submissions", "deaths-from-cases-retrospective", target_date)
+  
+  check_dir(rt_folder)
+  check_dir(deaths_folder)
+  
+  save_rt <- function(...) {
+    save_forecast(model = "-epiforecasts-EpiNow2-retrospective", 
+                  folder = rt_folder,
+                  date = target_date,
+                  ...)
+  }
+  
+  save_rt(case_forecast, "Germany", "GM", "-case")
+  save_rt(case_forecast, "Poland", "PL", "-case")
+  
+  save_conv <- function(...) {
+    save_forecast(model = "-epiforecasts-EpiNow2_secondary-retrospective", 
+                  folder = deaths_folder,
+                  date = target_date,
+                  ...)
+  }
[…]

### 2021-09-18 analysis/analysis.Rmd
retrospective forecasts

@@
 # regular forecasts
-unfiltered_data[model %in% regular_models] %>%
+unfiltered_data[model %in% c(regular_models)] %>%
   forecasts_and_scores()
 
+df <- unfiltered_data[model %in% c(regular_models, "Renewal-retrospective", "Convolution-retrospective")]
+
+unfiltered_data$model %>% unique()
+
+df$model %>% unique()
 # ensemble variants

### 2021-09-18 data-raw/paper.R

@@ -74,8 +74,12 @@ change_names <- list(
     "Crowd forecast"), 
   c("epiforecasts-EpiNow2", 
     "Renewal"), 
+  c("epiforecasts-EpiNow2-retrospective", 
+    "Renewal-retrospective"), 
   c("epiforecasts-EpiNow2_secondary", 
     "Convolution"), 
+  c("epiforecasts-EpiNow2_secondary-retrospective", 
+    "Convolution-retrospective"),
   
   c("KITCOVIDhub-median_ensemble_exclude_both", 
     "Hub-ensemble"), 

### 2021-09-18 rt-forecast-retrospective/past-renewal-forecasts.R

@@ -14,7 +14,6 @@ generation_time <- readRDS(here("rt-forecast", "data", "delays", "generation_tim
 incubation_period <- readRDS(here("rt-forecast", "data" ,"delays", "incubation_period.rds"))
 onset_to_report <- readRDS(here("rt-forecast", "data", "delays", "onset_to_report.rds"))
 
-
 for (target_date in dates) {
   # Get cases  ---------------------------------------------------------------
   cases <- fread(file.path("data-raw", "daily-incidence-cases.csv"))

### 2021-09-24 rt-forecast-retrospective/past-renewal-forecasts.R
update script for old renewal forecasts to use stored data files

@@ -16,11 +16,8 @@ onset_to_report <- readRDS(here("rt-forecast", "data", "delays", "onset_to_repor
 
 for (target_date in dates) {
   # Get cases  ---------------------------------------------------------------
-  cases <- fread(file.path("data-raw", "daily-incidence-cases.csv"))
-  cases <- cases[, .(region = as.character(location_name), date = as.Date(date), confirm = value)]
-  cases <- cases[confirm < 0, confirm := 0]
-  cases <- cases[date >= (max(as.Date(target_date)) - weeks(12))]
-  cases <- cases[date <= (as.Date(target_date))]
+  cases <- fread(file.path("rt-forecast", "data", "summary", 
+                           "cases", target_date, "reported_cases.csv"))
   cases <- cases[region %in% c("Germany", "Poland")]
   setorder(cases, region, date)
   
@@ -45,7 +42,7 @@ for (target_date in dates) {
                   rt = rt,
                   stan = stan_opts(samples = 2000, warmup = 250, 
                                    chains = 4, cores = no_cores),
-                  obs = obs_opts(scale = list(mean = 0.25, sd = 0.05)),
+                  obs = obs_opts(scale = list(mean = 0.5, sd = 0.05)), #(mean = 0.25, sd = 0.05)),
                   horizon = 30,
                   output = c("region", "summary", "timing", "samples", "fit"),
                   target_date = target_date,

### 2021-09-24 rt-forecast-retrospective/past-convolution-forecasts.R
update script to rerun convolution model forecasts

@@ -47,11 +47,12 @@ for (target_date in dates) {
     )),
     return_fit = FALSE,
     secondary = secondary_opts(type = "incidence"),
-    obs = obs_opts(scale = list(mean = 0.01, sd = 0.05), week_effect = FALSE),
+    obs = obs_opts(scale = list(mean = 0.01, sd = 0.02)),
     window = 3 * 7,
-    control = list(adapt_delta = 0.99, max_treedepth = 15),
+    control = list(adapt_delta = 0.95, max_treedepth = 15),
     verbose = TRUE
   )
+  
   
   # Save results to disk ----------------------------------------------------
   samples_path <- here(

### 2021-09-24 rt-forecast-retrospective/past-convolution-forecasts.R
rerun past forecasts with correct data

@@ -27,7 +27,7 @@ for (target_date in dates) {
   )
   case_forecast <- case_forecast[sample <= 1000]
   case_forecast <- case_forecast[region %in% c("Germany", "Poland")]
-  
+  case_forecast[, date := as.Date(date)]
   # Forecast deaths from cases ----------------------------------------------
   # set up parallel options
   options(mc.cores = 4)

### 2021-09-25 rt-forecast-retrospective/copy-to-data-raw.sh
update script to run past forecasts

@@ -1,0 +1,12 @@
+#!bin/bash
+cd submissions
+cd rt-forecasts-retrospective
+find . -name '*.csv' -exec cp {} ../../data-raw/epiforecasts-EpiNow2-retrospective/ \;
+cd ..
+
+cd deaths-from-cases-retrospective
+find . -name '*.csv' -exec cp {} ../../data-raw/epiforecasts-EpiNow2_secondary-retrospective/ \;
+cd ../..
+
+  
+  

### 2021-09-25 rt-forecast-retrospective/past-renewal-forecasts.R

@@ -19,13 +19,21 @@ for (target_date in dates) {
   cases <- fread(file.path("rt-forecast", "data", "summary", 
                            "cases", target_date, "reported_cases.csv"))
   cases <- cases[region %in% c("Germany", "Poland")]
+  cases[, date := as.Date(date)]
   setorder(cases, region, date)
   
   # Set up parallel execution -----------------------------------------------
   no_cores <- setup_future(cases)
   
   # Run Rt estimation -------------------------------------------------------
-  rt <- opts_list(rt_opts(prior = list(mean = 1.1, sd = 0.2), future = "latest"), cases)
+  
+  if (target_date <= "2020-11-09") {
+    future <- "estimate"
+  } else {
+    future <- "latest"
+  }
+  
+  rt <- opts_list(rt_opts(prior = list(mean = 1.1, sd = 0.2), future = future), cases)
   # add population adjustment for each country
   loc_names <- names(rt)
   loc_names <- c("Germany", "Poland")
@@ -42,7 +50,7 @@ for (target_date in dates) {
                   rt = rt,
                   stan = stan_opts(samples = 2000, warmup = 250, 
                                    chains = 4, cores = no_cores),
-                  obs = obs_opts(scale = list(mean = 0.5, sd = 0.05)), #(mean = 0.25, sd = 0.05)),
+                  obs = obs_opts(scale = list(mean = 0.5, sd = 0.05)), #(mean = 0.25, sd = 0.05)), from 2020-12-07 on
                   horizon = 30,
                   output = c("region", "summary", "timing", "samples", "fit"),
                   target_date = target_date,

### 2021-09-25 rt-forecast-retrospective/update-past-forecasts.sh
update script to rerun past forecasts

@@ -1,4 +1,9 @@
 #!bin/bash
+
+Rscript rt-forecast-retrospective/past-renewal-forecasts.R
+Rscript rt-forecast-retrospective/past-convolution-forecasts.R
+Rscript rt-forecast-retrospective/past-submissions.R
+
 cd submissions
 cd rt-forecasts-retrospective
 find . -name '*.csv' -exec cp {} ../../data-raw/epiforecasts-EpiNow2-retrospective/ \;

### 2021-10-11 analysis/analysis.Rmd
update script to run past forecasts
set up trackdown manuscript

@@
 
-df <- unfiltered_data[model %in% c(regular_models, "Renewal-retrospective", "Convolution-retrospective")]
+data <- unfiltered_data[model %in% c(regular_models, "Renewal-retrospective", "Convolution-retrospective")]
 
@@
   make_table()
+
+filtered_data[model %in% regular_models] %>%
+  filter(!(forecast_date %in% as.character(forecast_dates$death_not_scored))) %>%
+  make_table(plotname = "table_mean-late-period")
 
@@
 ```{r fig.height=10, fig.width=15}
-
-# pl <- wrap_plots(p_combined, p, widths = c(1, 2)) / p_phases + 
-#   plot_layout(guides = "collect") & 
-#   plot_annotation(tag_levels = 'A') &
-#   theme(legend.position = 'bottom') 
-# 
-# ggsave("plots/distribution_scores.png", plot = pl, height = 9)
-
 pl_ae <- wrap_plots(p_combined_ae, p_ae, widths = c(1, 2)) / p_phases_wis + 
@@
 
+filtered_data[model %in% regular_models] %>%
+  filter(!(forecast_date %in% as.character(forecast_dates$death_not_scored))) %>%
+  aggregate_performance(plotname = "aggregate-performance-all-late-period")
+
 # plot for locations

### 2021-10-11 manuscript/manuscript.Rmd
set up trackdown manuscript

---
title: "Comparing human and model-based forecasts of COVID-19 in Germany and Poland"
output: 
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
# bibliography: 
#   - references.bib  
#   - GermanPolishpaper.bib
---

*Anonymous Alpaca and many friends*

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      out.width = "100%", 
                      fig.pos = "H", out.extra = "")
```

# Abstract (max 200 words, no subheadings)

Model-based forecasts, which have played an important role in shaping public policy throughout the Covid-19 pandemic, represent an implicit combination of model assumptions and the researcher’s subjective opinion. This work explicitly separates human opinion and model-derived insights to assess and compare the relative strengths and weaknesses of both approaches. We compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from researchers and volunteers (“crowd forecasts”), against predictions from two semi-mechanistic epidemiological models. In addition, we compared these forecasts against an ensemble of model-based, but expert-tuned, forecasts, submitted to the German and Polish Forecast Hub by other research institutions (“Hub ensemble”). We found an ensemble of crowd-sourced predictions to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble at a two-week horizon: 89%), but not when predicting deaths (rel. WIS 126%). Crowd forecasts were severely overconfident (55% and 75% coverage of the 95% prediction intervals for cases and deaths, respectively) when compared to model-based predictions. Performance of the untuned models deteriorated quickly with increasing forecast horizon when assumptions were no longer met (rel. WIS > 164% for all four week ahead predictions).

# Introduction

Infectious disease forecasting has a long tradition and has helped inform public health decisions about (among others) influenza [CITATION], dengue fever [Citation], ebola [Citation], chikungunya and now COVID-19 [Citation]. The aggregation of forecasts of COVID-19 cases, hospitalisations or deaths from multiple teams has created opportunities to compare the predictive performance of different models (CITE e.g UK, US and German/Polish papers). Yet it has been difficult to discern which factors lead to good COVID-19 forecasts. Answering this question is complicated by the varying and generally unobserved degree of manual expert intervention. Model-based forecasts usually represent an implicit combination of human judgement and model-derived insights, in the sense that forecasts have been generated with the help of epidemiological or statistical models, but throughout the process were manually changed and adjusted according to the researchers’ judgement.

Previous work has examined human predictions in various contexts, such as geopolitics (Tetlock et al. 2014; Atanasov et al. 2016), meta-science (Cite Replication Markets), and epidemiology (CITE FARROW ET AL, McAndrew et al. 2021, Cite that other paper). Several prediction platforms (Metaculus 2020, Hypermind, Foretell) and prediction markets (cite predictit) have been created to collate expert and non-expert predictions. However, with the notable exception of Farrow et al., these crowd forecasts  were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats. Farrow et al. found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available. They tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown there and then.

In this study, we attempt to further shed light on the role of human judgement and model-based insight and analyse respective strengths and weaknesses. To compare human judgement and model-derived insights we evaluate and compare forecasts of weekly reported cases and deaths from COVID-19 in Germany and Poland made in real time over 21 weeks from October 2020 until March 2021. Specifically, we created a crowd-sourced forecast (“crowd forecast”), elicited from participants through a web application [Citation], as well as two semi-mechanistic models informed by basic assumptions about COVID-19 epidemiology. In contrast to Farrow et al., we asked participants not only for point predictions, but also for their predictive uncertainty, to exploit the greater utility of probabilistic forecasts (CITE Held, Meyer, Bracher, 2017).

# Results

The crowd forecast was constructed as an unweighted average of submissions by individual participants. The first of the two epidemiological models, the “renewal model”, estimates the effective reproduction number Rt (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infections (i.e. active infections) times Rt (assuming Rt to stay constant in the future). Based on predicted infections, reported cases and deaths are obtained by using delay distributions to model the time between infection and report date or death. Cases and deaths were forecast completely separately, meaning that Rt was estimated once from reported cases and once from reported deaths independently, meaning that death forecasts from the renewal model were not informed by past cases. The second model (“convolution model”) was only used to forecast deaths and modeled these as a fraction of infected people who would die with some delay. Both models were left completely untuned and unchanged throughout the study period to create a baseline purely informed by epidemiological assumptions. Human forecasters, on the other hand, were able to adapt their forecasts to current or likely future interventions.

## Study period

Crowd forecasts and the renewal model were created over the whole period between October 12th 2020 until March 1st 2021. They were both submitted to the so-called German/Polish forecast hub (http ref) and thus time-stamped (with one belated submission for the renewal model on December 28). We only added the convolution model later and started submitting it on December 21st 2020. To ensure compatibility between models, all death forecasts were scored using only the period from December 14th on, whereas case forecasts were evaluated on the entire submission period. A total number of 31 participants submitted forecasts. The median number of forecasters was 6, the minimum 2 and the maximum 9 for a single forecast target. Participation rose steadily and peaked in February, before declining towards the end of the study period. The mean number of submissions from an individual forecaster was 4.7 but the median number was only one - most participants dropped out after their first submission. Only two participants submitted a forecast every single week, both of whom are authors on this study.

```{r}
caption <- "Visualisation of aggregate performance metrics across forecast horizons. A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components sharpness, over-prediction and under-prediction. C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect). D: Empirical coverage of the 90\\% prediction intervals. E: Sharpness (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of all WIS values for different horizons"
```

```{r agg-performance-all, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-all-4.png")
## change name to v4
```

```{r}
caption <- "A, C: Visualisation of two week ahead forecasts against the true observed values. The shape indicates whether there has been a monotonic increase or decrease over the last two weeks leading up to a given data point, or an unclear trend. Forecasts that aren’t scored (because there was no complete set of death forecasts available) are greyed out. B, D: Visualisation of corresponding WIS. The shape indicates whether the trend was rising, falling or unclear at the date when the corresponding forecast was made (i.e. two weeks earlier, which leads to a shift of two weeks when compared to panels A and C)"
```

```{r forecasts-and-truth, fig.cap=caption}
knitr::include_graphics("../analysis/plots/figure-forecasts-2.png")
```

## Case Forecasts

For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure S1A). For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 100%) was 89% for crowd forecasts and 140% for the renewal model (Table SX). Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was right-skewed, and average performance was heavily influenced by outliers (Figure 3). Overall, low variance in forecast performance was closely linked with good mean performance (Figures 1AX and 1DX), suggesting that the ability to avoid large errors was an important factor in determining overall performance. The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure XX), as well as the highest standard deviation of WIS values (relative WIS sd 154% a the two weeks ahead horizon), while the ensemble of crowd forecasts  (rel. WIS sd 76%) and the Hub ensemble (= 100%) showed more stable performance.

To varying degrees, all models exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened. For example, all models failed to predict the change in trend from increase to decrease that happened in early November... in Germany and severely overshot (Figure 2XX). This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past  of observations. The Hub ensemble and the crowd forecast, which had both been under-predicting throughout October, also failed to predict the change in trend after cases peaked, but less severely so. Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 (Deutsche Welle (www.dw.com) n.d.) and the change in the testing regime (with stricter test criteria) on November 11th 2020 (Ärzteblatt 2020), were fastest to adapt to the new trend, and the Hub ensemble slowest. In December, cases rose again in Germany, with all models under-predicting this growth to varying extents. As in October, the renewal model captured the phase of exponential growth in cases slightly better than other approaches, but again overshot when reported case numbers fell over Christmas. The large variance in predictions in January in Germany (severe under-prediction followed by severe over-prediction) may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting. Similar trends in performance were evident in Poland, with the crowd forecast quickest at adapting to the change in trend in November. In general, there were fewer large outlier forecasts in Poland and in particular the renewal model performed more in line with other forecasts there.

All forecasting approaches, including the Hub ensemble, were overconfident and showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure 1X and 1X). Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts. This was especially an issue for crowd forecasts, which were markedly sharper (i.e., narrower) than other approaches (Figure 1X) and only showed a small increase in uncertainty across forecast horizons. In spite of good performance in terms of the absolute error (Figure 1X), excessive sharpness led to forecasts which were severely overconfident (covering only 36% and 55% of observations with their 50% and 90% prediction intervals at a two week horizon, and only 5% and 38% four weeks ahead) (Figure 1X and Table SXX). Despite worse performance in terms of absolute error (Figure 1X), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly and non-linearly across forecast horizons.

The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons (as captured by our relative bias metric with values between -1 and 1 and 0 ideally). The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure 1X). Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figure X and Table X), implying that over-prediction (e.g. when missing a peak) tended to be more costly in terms of the WIS.

## Death Forecasts

For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure 1A, Figure S1A). Relative WIS values for the models two weeks ahead were 122% (convolution model), 126% (crowd forecast), 100% (Hub ensemble) and 179% (renewal model). The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure 1A, Figure S1A), and also better than the convolution model three and four weeks ahead. Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate Rt trace from deaths, is not well suited for the task. The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure 1A, Table SX).

Theoretical considerations suggest that predicting a change in trend may be easier for deaths than for cases (as past cases, hospitalisations and other data can be used as predictors). Even though all forecasts generally struggled with this, there were some instances where changing trends were well captured or even anticipated. In Poland, for example, the Hub ensemble was able to capture or even anticipate the peak in deaths in December quite well (whereas the renewal model and crowd forecast did not). The renewal model, which mostly exhibited trend-following behaviour, correctly predicted another increase in weekly deaths in mid-January (potentially based on changes in daily deaths, as the renewal model did not know about past cases). In Germany in early January, all models predicted a decrease in deaths two to three weeks before it actually happened. Predictions from the renewal model at that time were likely strongly influenced by an unexpected drop in reported deaths on December XXth. The other forecasting approaches and in particular, the convolution model may have been affected by potentially under-reported case numbers around Christmas. When the decrease that all models had predicted to happen in early January failed to materialise, the renewal model and the crowd forecast noticeably over-corrected and over-predicted deaths in the following weeks, while the Hub ensemble, and to a slightly lesser degree, the convolution model were able to capture the downturn well when it finally happened at the end of January.

Death forecasts, generally, showed greater coverage of the 50% and 90% prediction intervals than case forecasts and no decrease in coverage across forecast horizons, indicating that it might be easier to appropriately quantify uncertainty for death forecasts. The Hub ensemble had the greatest coverage, with empirical coverage of the 50% and 90% prediction intervals exceeding 50%, and 90%, respectively, across all forecast horizons. Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure 1X and XX). As for cases, the crowd forecast tended to be the sharpest and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest. The convolution model was relatively sharp for short forecast horizons, but had rapidly (and non-linearly) increasing uncertainty for longer forecast horizons, driven by increasing uncertainty in the underlying case forecasts.

For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict. The convolution model had a strong tendency to under-predict, which steadily decreased for longer forecast horizons. The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction. For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or underpredict than for cases (Figure XX).

```{r}
caption <- ""
```

```{r distribution-scores, fig.cap=caption}
knitr::include_graphics("../analysis/plots/distribution_scores_wis-2.png")
```

## Performance across locations (maybe not a separate section or more nuance)

Generally, trends in overall performance were similar across locations (Figure S1). Notably,the convolution model performed better, when assessed by both median and mean WIS, in Germany than Poland indicating a stronger connection between observed cases and deaths. Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly  (Figure S1).

All model-based predictions, but not the crowd forecasts, were noticeably sharper in Poland than in Germany (Figure S1), in line with their smaller overall WIS values. Crowd forecasts for cases (but not for deaths) were approximately equally sharp in Poland and in Germany. For both cases and deaths, forecasts tended to be lower relative to observed values in Poland than in Germany, with bias values lower for all forecasts in Poland than in Germany (except crowd forecasts of cases, Figure S1F).

```{r}
caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub ensemble. “Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included. Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions. For Coverage, this is an absolute difference, for other metrics this is a percentage difference. A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Sharpness (higher values mean greater dispersion of the forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\\% prediction intervals. F: Empirical coverage of the 90\\% prediction intervals"
```

```{r agg-performance-ensemble, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-4.png")
```

## Contribution to the Forecast Hub

Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (“hub-ensemble-realised”), while the convolution model was never included as it was deemed too similar to the existing renewal model, thus potentially introducing bias. Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.

For cases, our contributions (compared to the Hub ensemble without our contributions) consistently improved performance across all forecasting horizons (rel. WIS 90% two weeks ahead). Contributions from the crowd forecasts alone also were positive across all forecast horizons, while contributions from the renewal model became negative for longer horizons (rel. WIS 102% three weeks ahead, 106% four weeks ahead). The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects. Only for four week ahead predictions would removing the renewal model have improved performance (Table XX).

For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel. WIS of the hub-ensemble-realised 101% two weeks ahead, 105% four weeks ahead). Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons). This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Table XX) and especially worse for longer horizons.

We also considered the impact of our contributions on the mean, rather than the median ensemble. General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble. This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far. For both the mean and the median ensemble, changes in performance from adding or removing models were of a similar order of magnitude, suggesting that at least in this instance, with a relatively small ensemble size, the median ensemble was not necessarily more ‘robust’ to changes than the mean ensemble. However, the ensemble version with all our forecasts included (“hub-ensemble-with-all”) tended to perform relatively better for the median ensemble than the mean ensemble, suggesting that adding more models may be more beneficial or ‘safer’ for the median than for the mean ensemble as directional errors can more easily cancel out than errors in absolute terms.

# Discussion
Epidemiological forecasting usually represents a mix between human insight and model-based assumptions. In this study, we compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from a crowd of researchers and volunteers against predictions from two semi-mechanistic epidemiological models. In spite of the small number of participants and a general tendency to be overconfident, crowd forecasts consistently outperformed our epidemiological models as well as the Hub ensemble when forecasting cases but not when forecasting deaths. This suggests that humans are relatively good at foreseeing trends that are hard to model but may struggle to form an intuition for the exact relationship between cases and deaths. Our epidemiologicalUntuned models, on the other hand performed relatively well short-term, but not for longer horizons without any form of human intervention or assumption to guide behaviour when conditions evolve. Ensembles, in general, showed the greatest consistency in their performance (and best mean performance), but did often not provide the best forecasts for a given forecast date. Our contributions consistently improved the pre-existing Hub ensemble for cases, but not for deaths. We often found contributions to an ensemble to be beneficial even in instances where the forecasting approach entering the ensemble performed consistently worse than the pre-existing ensemble.

Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts. However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (Cite US Hub, cite Seb SPI-M), or exclusively on human forecasts (e.g. cite Tetlock, cite Grecchia, cite McAndrew). In contrast, we directly compare human and model-based forecasts. This is similar to the approach taken by Farrow et al., but extends it in several ways. While Farrow et al. only asked for point predictions and constructed a probabilistic forecast from these, we asked participants to quantify their uncertainty directly, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse aspects of the forecasts like overconfidence. In addition, we compared crowd forecasts to completely untuned models, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight. In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (J. Bracher et al. 2021; E. Y. Cramer et al. 2021; S. Funk et al. 2020).

The good performance of crowd forecasts we found is in line with results from Farrow et al. who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants. The advantage of crowd forecasts we observed over untuned models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models. However, this likely explains only part of the difference and performance relative to the Hub ensemble strongly suggests that human insight is valuable when predicting highly volatile and hard-to-predict quantities such as case numbers. Relatively good performance of our untuned models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time. This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data). While we were not able to observe how expert opinion informed other models submitted to the Forecast Hub, conversations with the Hub organisers suggest that forecasts tended to benefit from a large degree of human intervention. Unfortunately, we were not able to test a scenario in which users were asked to alter an existing model output, rather than create a new forecast from a naive baseline, and can therefore make no conclusive statements about the direct effects of researchers tuning their models.

Conversely, our results suggest that human intervention may be less beneficial when forecasting deaths (especially at shorter horizons, when deaths are largely dependent on already observed cases), which benefits from the ability to model the delays and exact epidemiological relationships between different leading and lagged indicators. Relatively good performance of the convolution model, especially compared to the poor performance of the renewal model on deaths (which used only deaths to estimate and predict the effective reproduction number) underlines the importance of including leading indicators such as cases as a predictor for deaths.

Given the low number of participants in our study, it is difficult to generalise conclusions about crowd predictions to other settings. In particular, our crowd forecasting application was not developed to a high standard of user friendliness. This may have precluded interested parties from submitting forecasts. It is both conceivable that a greater number of participants would have improved forecasts, but also that a larger audience may have decreased the mean quality of predictions. Motivating forecasters to contribute regularly proved challenging, especially given that the majority of our participants were from the UK and had little connection to either Germany or Poland. In addition, lack of effective outreach played an important role, as did a lack of time and resources to design the interface in a way that is appealing enough to attract large audiences outside of academia. Using an R shiny app as an interface arguably created some limits to user experience and performance, influencing the number of participants. On the other hand, it facilitated quick development and allows us to provide our crowd forecasting tooling as an open source R package, meaning that it is available for others to use, and to further develop, in their context.

In general, our results support the use of ensembles, rather than individual models to inform public health policies, as these provide consistently good forecasts and largely avoid particularly bad outlier forecasts. As an average, ensembles show the consensus opinion, which implies that in contrast to single models, they are not likely to reveal information, e.g. about future changes in trend, that is not in some way ‘obvious’ to the majority of forecasters. Indeed, as illustrated in Figure SXX, single models often outperform the ensemble (while also performing much worse at other times) and may therefore also play a role in informing public policy in specific circumstances alongside ensemble predictions.

In the context of evaluating different models and the merits of human intervention, what constitutes a ‘good’ forecast very much depends on the purpose of that forecast. Policymakers may care much more about certain types of errors, (e.g. under-prediction) than others in a way not captured by the weighted interval score. Also, it is helpful to distinguish between ‘forecasts’ and ‘projections’. For example, the outperformance of  the crowd forecasts on cases and in general on longer forecast horizons is perhaps not surprising, given that humans could factor in an expectation of future changes in conditions (e.g. future policy interventions, adherence to these interventions, testing policy, and the evolution of new disease variants) while our model-based forecasts could not. However, if the aim of a forecast is to inform policy and decision making, then attempting to factor in the interventions one is meant to inform may be problematic (and conversely, arguing for or against interventions based on predictions may be difficult depending on what the forecast assumes about future interventions). In that sense, crowd forecasts can be understood as forecasts, whereas our model predictions may be better understood as projections that show what would happen in the absence of any events that could change the trend. This may pose a problem in the context of a forecast hub if teams have a different understanding about the purpose of a forecast. Projections that are meant to inform policy makers about possible scenarios may be different from forecasts meant to inform the general public, and yet again different from forecasts submitted with the goal of advancing open research and in order to allow public scrutiny and discussion about the merits of different approaches.

Further work should explore the effects of human intervention on model-based forecasts in more detail. Model-based forecasts could be used as an input to human judgement, with researchers adjusting predictions generated by models. Tools need to be developed to facilitate this process at a larger scale. Human insight could also be used as an input to models. Such a ‘hybrid’ forecasting approach could for example ask humans to predict the trend of the effective reproduction number Rt or the doubling rate (i.e. how the epidemic evolves) into the future and use this to estimate the exact number of cases, hospitalisations or deaths this would imply. This approach seems especially promising for forecasting deaths if a model can accurately describe delay distributions and epidemiological relationships between different parameters. In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust confidence intervals may be another promising approach. Crowd forecasting in general could benefit a lot from the availability of tools suitable to appeal to a greater audience. Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile for researchers and policymakers to further develop and explore.

## Methods - missing

# Supplementary information

## Further details on the semi-mechanistic forecasting models

### Renewal equation model

The model was initialised prior to the first observed data point by assuming constant exponential growth for the mean of assumed delays from infection to case report.

\begin{align}
  I_{t} &= I_0 \exp  \left(r t \right)  \\
  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
  r &\sim \mathcal{LN}(r_{obs}, 0.2) \\
\end{align}

Where $I_{obs}$ and $r_{obs}$ are estimated form the first week of observed data. For the time window of the observed data infections were then modelled by weighting previous infections by the generation time and scaling by the instantaneous reproduction number. These infections were then convolved to cases by date ($O_t$) and cases by date of report ($D_t$) using log-normal delay distributions. This model can be defined mathematically as follows,

\begin{align}
  \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
  I_t &= R_t \sum_{\tau = 1}^{15} w(\tau | \mu_{w}, \sigma_{w}) I_{t - \tau} \\
  O_t &= \sum_{\tau = 0}^{15} \xi_{O}(\tau | \mu_{\xi_{O}}, \sigma_{\xi_{O}}) I_{t-\tau} \\
  D_t &= \alpha \sum_{\tau = 0}^{15} \xi_{D}(\tau | \mu_{\xi_{D}}, \sigma_{\xi_{D}}) O_{t-\tau} \\ 
  C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
\end{align}

Where,
\begin{align}
     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) \\
\end{align}

This model used the following priors for cases,

\begin{align}
     R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
    \mu_w &\sim \mathcal{N}(3.6, 0.7) \\
    \sigma_w &\sim \mathcal{N}(3.1, 0.8) \\
    \mu_{\xi_{O}} &\sim \mathcal{N}(1.62, 0.064) \\
    \sigma_{\xi_{O}} &\sim \mathcal{N}(0.418, 0.069) \\
    \mu_{\xi_{D}} &\sim \mathcal{N}(0.614, 0.066) \\
    \sigma_{\xi_{D}} &\sim \mathcal{N}(1.51, 0.048) \\
    \alpha &\sim \mathcal{N}(0.25, 0.05) \\
    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
    \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
\end{align}

and updated the reporting process as follows when forecasting deaths,

\begin{align}
    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
    \alpha &\sim \mathcal{N}(0.005, 0.0025) \\
\end{align}

$\alpha$, $\mu$, $\sigma$, and $\phi$ were truncated to be greater than 0 and with $\xi$, and $w$ normalised to sum to 1.

The prior for the generation time was sourced from [@generationinterval] but refit using a log-normal incubation period with a mean of 5.2 days (SD 1.1) and SD of 1.52 days (SD 1.1) with this incubation period also being used as a prior [@incubationperiod] for $\xi_{O}$. This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates. We estimated the delay between symyptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1% or 1769 samples of the available data  [@kraemer2020epidemiological; @covidregionaldata] and combining the posteriors for the mean and standard deviation of the log-normal distribution [@epinow2; @doiCovid19TemporalVariation; @EvaluatingUseReproduction; @rstan].

$GP_t$ is an approximate Hilbert space Gaussian process as defined in [@approxGP] using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20% of the number of days used in fitting). The lengthscale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days. The magnitude of the Gaussian process was assumed be normally distributed centred at 0 with a standard deviation of 0.1.

From the forecast time horizon ($T$) and onwards the last value of the Gaussian process was used (hence $R_t$ was assumed to be fixed) and latent infections were adjusted to account for the proportion of the population that was susceptible to infection as follows,

\begin{equation}
    I_t = (N - I^c_{t-1}) \left(1 - \exp \left(\frac{-I'_t}{N - I^c_{T}}\right)\right),
\end{equation}

where $I^c_t = \sum_{s< t} I_s$ are cumulative infections by $t-1$ and $I'_t$ are the unadjusted infections defined above. This adjustment is based on that implemented in the `epidemia` R package (@epidemia, cite @bhatt202).

#### Convolution model

The convolution model shares the same observation model as the renewal model but rather than assuming that an observation is predicted by itself instead assumes that it is predicted entirely by another observation after some parametric delay. It can be defined mathematically as follow,

\begin{equation} 
    D_{t} \sim \mathrm{NB}\left(\omega_{(t \mod 7)} \alpha \sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) C_{t-\tau},  \phi \right)
\end{equation}

with the following priors,

\begin{align}
    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
    \alpha &\sim \mathcal{N}(0.01, 0.02) \\
    \xi &\sim \mathcal{LN}(\mu, \sigma) \\
    \mu &\sim \mathcal{N}(2.5, 0.5) \\
\sigma &\sim \mathcal{N}(0.47, 0.2) \\
\phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
\end{align}

with $\alpha$, $\mu$, $\sigma$, and $\phi$ truncated to be greater than 0 and with $\xi$ normalised such that $\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1$.

### Model fitting

Both models were implemented using the `EpiNow2` R package (version 1.3.3) [@epinow2]. Each forecast target was fit independently for each model using Markov-chain Monte Carlo (MCMC) in stan [@rstan]. A minimum of 4 chains were used with a warmup of 250 samples for the renewal equation-based model and 1000 samples for the convolution model. 2000 samples total post warmup were used for the renewal equation model and 4000 samples for the convolution model. Different settings were chosen for each model to optimise compute time contigent on convergence. Convergence was assessed using the R hat diagnostic [@rstan]. For the convolution model forecast the case forecast from the renewal equation model was used in place of observed cases beyond the forecast horizon using 1000 posterior samples. 12 weeks of data was used for both models though only 3 weeks of data were included in the likelihood for the convolution model.

## Tables with results of the forecast evaluation

```{r}
caption <- ""
```

```{r score-table-2}
```

```{r}
caption <- ""
```

```{r score-table-4}
```

## Aggregate performance by location

### Performance across locations in absolute terms
```{r}
caption <- ""
```

```{r performance-locations, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-4.png")
```

## Performance across locations in relative terms

```{r}
caption <- ""
```

```{r performance-locations-rel, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-4.png")
```

## Visualisation of daily reported cases and deaths

```{r}
caption <- ""
```

```{r daily-truth, fig.cap=caption}
knitr::include_graphics("../analysis/plots/daily_truth.png")
```

### Visualisation of scores and forecasts 1, 3, 4 weeks ahead

```{r}
caption <- ""
```

```{r forecasts-and-truth-1, fig.cap=caption}
knitr::include_graphics("../analysis/plots/figure-forecasts-1.png")
```

```{r}
caption <- ""
```

```{r forecasts-and-truth-3, fig.cap=caption}
knitr::include_graphics("../analysis/plots/figure-forecasts-3.png")
```

```{r}
caption <- ""
```

```{r forecasts-and-truth-4, fig.cap=caption}
knitr::include_graphics("../analysis/plots/figure-forecasts-4.png")
```

### Distribution of scores for 1, 3, 4 week-ahead forecasts

```{r}
caption <- ""
```

```{r distribution-scores-1, fig.cap=caption}
knitr::include_graphics("../analysis/plots/distribution_scores_wis-1.png")
```

```{r}
caption <- ""
```

```{r distribution-scores-3, fig.cap=caption}
knitr::include_graphics("../analysis/plots/distribution_scores_wis-3.png")
```

```{r}
caption <- ""
```

```{r distribution-scores-4, fig.cap=caption}
knitr::include_graphics("../analysis/plots/distribution_scores_wis-4.png")
```

### Ranks achieved by forecasts

```{r}
caption <- ""
```

```{r distribution-scores-ranks-1, fig.cap=caption}
knitr::include_graphics("../analysis/plots/distribution_scores_wis-1-ranks.png")
```

```{r}
caption <- ""
```

```{r distribution-scores-ranks-2, fig.cap=caption}
knitr::include_graphics("../analysis/plots/distribution_scores_wis-2-ranks.png")
```

```{r}
caption <- ""
```

```{r distribution-scores-ranks-3, fig.cap=caption}
knitr::include_graphics("../analysis/plots/distribution_scores_wis-3-ranks.png")
```

```{r}
caption <- ""
```

```{r distribution-scores-ranks-4, fig.cap=caption}
knitr::include_graphics("../analysis/plots/distribution_scores_wis-4-ranks.png")
```

## Sensitivity analysis

- tables for limited period
- plot for limited period

### 2021-10-11 manuscript/manuscript.sh

@@ -1,0 +1,4 @@
+!#/bin/bash
+
+Rscript -e 'trackdown::update_file(file = "manuscript/manuscript.Rmd", gfile = "Comparing human and model-based forecasts of COVID-19 in Germany and Poland", hide_code = TRUE)'
+

### 2021-10-11 rt-forecast-retrospective/update-past-forecasts.sh

@@ -4,14 +4,5 @@ Rscript rt-forecast-retrospective/past-renewal-forecasts.R
 Rscript rt-forecast-retrospective/past-convolution-forecasts.R
 Rscript rt-forecast-retrospective/past-submissions.R
 
-cd submissions
-cd rt-forecasts-retrospective
-find . -name '*.csv' -exec cp {} ../../data-raw/epiforecasts-EpiNow2-retrospective/ \;
-cd ..
-
-cd deaths-from-cases-retrospective
-find . -name '*.csv' -exec cp {} ../../data-raw/epiforecasts-EpiNow2_secondary-retrospective/ \;
-cd ../..
-
   
   

### 2021-10-12 analysis/analysis.Rmd
rewrite of methods section

@@
 
+```{r num-forecasters0, results = 'asis'}
+# number of experts and non-experts --------------------------------------------
+crowdforecast_data %>%
+  select(model, expert) %>%
+  unique() %>%
+  summarise(experts = sum(expert), 
+            nonexpert = sum(!expert))
+```
+
 ```{r num-forecasters, results = 'asis'}
+# check number of available forecasters
 dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
@@
    by = c("location_name", "target_type")]
+
+dt[, .(sd = sd(`number of forecasters`), 
+       mean = mean(`number of forecasters`), 
+       min  = min(`number of forecasters`), 
+       max = max(`number of forecasters`), 
+       median = median(`number of forecasters`))]
 

### 2021-10-12 manuscript/manuscript.Rmd
rewrite of methods section

@@
     extra_dependencies: ["float"]
-# bibliography: 
-#   - references.bib  
-#   - GermanPolishpaper.bib
+bibliography:
+  - references.bib
+  - GermanPolishpaper.bib
 ---
@@
 
-In this study, we attempt to further shed light on the role of human judgement and model-based insight and analyse respective strengths and weaknesses.
-To compare human judgement and model-derived insights we evaluate and compare forecasts of weekly reported cases and deaths from COVID-19 in Germany and Poland made in real time over 21 weeks from October 2020 until March 2021.
-Specifically, we created a crowd-sourced forecast (“crowd forecast”), elicited from participants through a web application [Citation], as well as two semi-mechanistic models informed by basic assumptions about COVID-19 epidemiology.
-In contrast to Farrow et al., we asked participants not only for point predictions, but also for their predictive uncertainty, to exploit the greater utility of probabilistic forecasts (CITE Held, Meyer, Bracher, 2017).
+In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses by comparing human forecasts and model-based predictions.
+
+<!-- In contrast to Farrow et al., we analyse not only point predictions, but also for their predictive uncertainty, to exploit the greater utility of probabilistic forecasts (CITE Held, Meyer, Bracher, 2017).
+-->
+
+## Methods
+
+We created a crowd-sourced forecast (“crowd forecast”), elicited from participants through a web application [Citation], as well as two semi-mechanistic models ("renewal model" and "convolution model") informed by basic assumptions about COVID-19 epidemiology.
+Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (CITATION).
+All code and tools necessary to generate the forecasts and make a forecast submission are available in the `covid.german.forecasts` R package (N.
+Bosse et al.
+2020).
+This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub.
+Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the Forecast Hub.
+
+### Forecast targets and interaction with the German and Polish Forecast Hub
+
+The German and Polish Forecast Hub elicits predictions for various COVID-19 related forecast targets from different research institutions every week.
+Forecasts had to be made every Monday (with submissions allowed until Tuesday 3pm) using data available until Monday 11.59pm.
+We submitted forecasts for incident and cumulative weekly reported numbers of cases and deaths from COVID-19 on a national level in Germany and Poland over a one to four week forecast horizon.
+Weeks were defined as epiweeks starting on Sunday and ending on Saturday, meaning that forecast horizons were in fact 5, 12, 19 and 26 days.
+Submissions were required in a quantile-based format with 23 quantiles at levels 0.01, 0.025, 0.05, 0.10, 0.15, ..., 0.95, 0.975, 0.99.
+Forecasts submitted to the Forecast Hub were combined to different ensembles every week, with the median ensemble being the default ensemble shown on all official Forecast hub visualisations.
+
+<!-- In addition to the official Hub ensembles, we computed versions of the  -->
+
+Data on daily reported test positive cases and deaths linked to Covid-19 were provided by the organisers of the German and Polish forecast hub (J.
+Bracher et al.
+2021).
+Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) (“Download Historical Data (to 14 December 2020) on the Daily Number of New Reported COVID-19 Cases and Deaths Worldwide” 2020).
+After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (“RKI - Coronavirus SARS-CoV-2 - Aktueller Lage-/Situationsbericht Des RKI Zu COVID-19” n.d.).
+These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November (“Rozbieżności w statystykach koronawirusa.
+22 tys.
+przypadków będą doliczone do ogólnej liczby wyników” 16:07:56+0100)), changes in reporting over time and variation in testing regimes (e.g.
+in Germany from the 11th of November on (Ärzteblatt 2020)).
+
+### Crowd forecasts
+
+Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application  (https://cmmid-lshtm.shinyapps.io/crowd-forecast/).
+Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information avaialble until Monday.
+The application was built using the shiny and golem R packages (Chang et al.
+2021; Fay et al.
+2021) and is available in the crowdforecastr R package (N.
+I.
+Bosse et al.
+2020).
+To make a forecast in the application participants could select a predictive distribution, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values.
+The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e.
+as `sd(c(log(value4) - log(value3), log(value3) - log(value2), ...))`).
+Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from (“COVID-19 Data Explorer” n.d.).
+These data included e.g.
+notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
+
+Forecasts were stored in a Google Sheet and downloaded, cleaned and processed every week for submission.
+If a forecaster had submitted multiple predictions for a single target, only the latest submission was kept.
+Information on the chosen distribution as well as the parameters for median and width were used to obtain the required set of 23 quantiles from that distribution.
+Forecasts from all forecasters were then aggregated using an unweighted quantile-wise mean.
+On a few occasions, individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation.
+
+Participants were recruited mostly within the Centre of Mathematical Modeling of Infectious Diseases at the London School of Hygiene & Tropical Medicine, but participants were also invited personally or via social media to submit predictions.
+Depending on whether they had a background in either statistics, forecasting or epidemiology, participants were asked to self-identify as 'experts' or 'non-experts'.
+
+### Model-based forecasts
+
+We used two models from the EpiNow2 R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, et al.
+2020).
+The first of these models, here called “renewal model”, uses the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths.
+It estimates the effective reproduction number $R_t$ (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infections times $R_t$.
+$R_t$ was assumed to stay constant in the future, roughly corresponding to continuing the latest trend in cases.
+The $R_t$ value which was carried forward was slightly changed on November 9th 2020, where before that date the last 'reliable' $R_t$ estimate from X days before the forecast was used and after that the latest and most up-to-date (but possibly less stable) $R_t$ estimate made on the actual forecast date was used.
+Reported cases and deaths were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, et al.
+2020; DOI n.d.; “Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the Covid-19 Outbreak in England | medRxiv” n.d.) to model the time between infection and report date or death.
+The renewal model was used to predict cases as well as deaths, but the two were forecast completely indepdently, meaning that $R_t$ was forecast once from reported cases and once from reported deaths.
+Death forecasts from the renewal model were therefore not informed by past cases.
+
+The second model (“convolution model”) was only used to forecast deaths and modeled these as a fraction of infected people who would die with some delay.
+
+Both models were left completely untuned and unchanged throughout the study period to create a baseline purely informed by epidemiological assumptions.
+Human forecasters, on the other hand, were able to adapt their forecasts to current or likely future interventions.
+
+The second model, here called “convolution model”, which was only used to forecast deaths, assumed that deaths could be modelled using a scaling parameter, as a  convolution of test positive cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
+Both models assumed a negative binomial observation model and a multiplicative day-of-the-week effect (Abbott, Hellewell, et al.
+2020).
+
+All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fit separately.
+More details are available in the supplementary information.
+
+Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August.
+Population data at the national and state level in Germany and Poland used in the model-based forecasts was sourced from (Statistisches Bundesamt 2020) and (Statystyczny 2020).
+
+### Statistical analysis
+
+Crowd forecasts and the renewal model were created over the whole period between October 12th 2020 until March 1st 2021.
+We added the convolution model later and started creating and submitting it on December 7th 2020.
+As the first submission suffered from a software bug, we disregard it here.
+Crowd forecasts and renewal model forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021.
+We added the convolution model later and started creating it on December 7th 2020.
+As the first forecast suffered from a software bug, we disregard it here.
+All our forecasts were time-stamped and submitted to the German and Polish Forecast Hub (CITATION).
+All forecasts were processed in a Docker (Merkel 2014) container to ensure a reproducible environment.
+
+To ensure compatibility between models, all death forecasts were scored using only the period from December 14th on, whereas case forecasts were evaluated on the entire submission period.
+They were both submitted to the so-called German/Polish forecast hub (http ref) and thus time-stamped (with one belated submission for the renewal model on December 28).
+
+### Forecasts
+
+#### Model-based forecasts
+
+We used two models from the EpiNow2 R package (version 1.3.3) as our model forecasts (Abbott, Hellewell, et al.
+2020).
+The first of these models, here called “renewal model”, which was used to forecast both test positive cases and deaths, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to estimate the effective reproduction number over time for latent infections and then convolved these infections to the target observation using data based delay distributions (Abbott, Hellewell, et al.
+2020; DOI n.d.; “Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the Covid-19 Outbreak in England | medRxiv” n.d.).
+Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August.
+For the forecasts, the reproduction number was assumed to remain constant from X days before the last data for which case data was available, roughly corresponding to continuing the latest trend in cases.
+
+The second model, here called “convolution model”, which was only used to forecast deaths, assumed that deaths could be modelled using a scaling parameter, as a  convolution of test positive cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
+Both models assumed a negative binomial observation model and a multiplicative day-of-the-week effect (Abbott, Hellewell, et al.
+2020).
+All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fit separately.
+More details are available in the supplementary information.
 
@@
 To ensure compatibility between models, all death forecasts were scored using only the period from December 14th on, whereas case forecasts were evaluated on the entire submission period.
-A total number of 31 participants submitted forecasts.
-The median number of forecasters was 6, the minimum 2 and the maximum 9 for a single forecast target.
-Participation rose steadily and peaked in February, before declining towards the end of the study period.
+A total number of 32 participants submitted forecasts, 17 of those self-identified as 'expert'.
+The median number of forecasters for any given forecast target was 6, the minimum 2 and the maximum 10.
 The mean number of submissions from an individual forecaster was 4.7 but the median number was only one - most participants dropped out after their first submission.
@@
 Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile for researchers and policymakers to further develop and explore.
-
-## Methods - missing
 

### 2021-10-12 data-raw/paper.R

@@ -344,11 +344,39 @@ usethis::use_data(filtered_data, overwrite = TRUE)
 
 # additional analysis for individual forecasters -------------------------------
 
-# store prediction data for individual forecasters
-root_dir <- here::here("crowd-forecast", "processed-forecast-data")
-file_paths_forecast <- here::here(root_dir, list.files(root_dir))
+# check number of experts ------------------------------------------------------
 
-crowdforecast_data <- purrr::map_dfr(file_paths_forecast, 
+
+purrr::map_dfr(file_paths, 
+               .f = function(file_path) {
+                 data <- data.table::fread(file_path)
+                 data[, `:=`(
+                   target_end_date = as.Date(target_end_date), 
+                   submission_date = as.Date(submission_date),
+                   forecast_date = as.Date(forecast_date), 
+                   model = get_model_name(file_path)
+                 )]
+                 return(data)
+               }) %>%
+  select(board_name, expert) %>%
+  unique() %>%
+  summarise(experts = sum(expert), 
+            nonexpert = sum(!expert))
+
+
+
+
+
+
+# store prediction data for individual forecasters
+file_paths <- list.files(here::here("crowd-forecast", "processed-forecast-data"))
+file_dates <- substr(file_paths, 1, 10)
+indices <- (1:length(file_dates))[as.Date(file_dates) <= "2021-03-15" &
+                                    !is.na(as.Date(file_dates))]
+file_paths <- here::here("crowd-forecast", "processed-forecast-data", file_paths)
+file_paths <- file_paths[indices]
+
+crowdforecast_data <- purrr::map_dfr(file_paths, 
                                   .f = function(x) {
                                     data <- data.table::fread(x) %>%
                                       dplyr::mutate(target_end_date = as.Date(target_end_date), 
@@ -361,26 +389,6 @@ crowdforecast_data <- purrr::map_dfr(file_paths_forecast,
   dplyr::rename(model = board_name) %>%
   dplyr::filter(type == "quantile", 
                 location_name %in% c("Germany", "Poland")) %>%
-  dplyr::select(location, location_name, forecast_date, quantile, prediction, model, target_end_date, horizon, target, target_type)
+  dplyr::select(location, location_name, forecast_date, quantile, prediction, model, target_end_date, horizon, target, target_type, expert)
 
 usethis::use_data(crowdforecast_data, overwrite = TRUE)
-
-
-# check number of available forecasters
-dt <- prediction_data[!(model %in% c("Crowd-Rt-Forecast",
[…]

### 2021-10-12 manuscript/manuscript.Rmd
rewriting method section of the manuscript

@@
 
-<!-- In addition to the official Hub ensembles, we computed versions of the  -->
-
 Data on daily reported test positive cases and deaths linked to Covid-19 were provided by the organisers of the German and Polish forecast hub (J.
@@
 Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application  (https://cmmid-lshtm.shinyapps.io/crowd-forecast/).
-Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information avaialble until Monday.
+Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information available until Monday.
 The application was built using the shiny and golem R packages (Chang et al.
@@
 
-We used two models from the EpiNow2 R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, et al.
+We used two models from the `EpiNow2` R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, et al.
 2020).
-The first of these models, here called “renewal model”, uses the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths.
-It estimates the effective reproduction number $R_t$ (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infections times $R_t$.
-$R_t$ was assumed to stay constant in the future, roughly corresponding to continuing the latest trend in cases.
+The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths.
+It estimated the effective reproduction number $R_t$ (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infections times $R_t$.
+$R_t$ was assumed to stay constant in the future, roughly corresponding to continuing the latest trend in infections.
 The $R_t$ value which was carried forward was slightly changed on November 9th 2020, where before that date the last 'reliable' $R_t$ estimate from X days before the forecast was used and after that the latest and most up-to-date (but possibly less stable) $R_t$ estimate made on the actual forecast date was used.
@@
 2020; DOI n.d.; “Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the Covid-19 Outbreak in England | medRxiv” n.d.) to model the time between infection and report date or death.
-The renewal model was used to predict cases as well as deaths, but the two were forecast completely indepdently, meaning that $R_t$ was forecast once from reported cases and once from reported deaths.
+The renewal model was used to predict cases as well as deaths, but the two were forecast completely independently, meaning that $R_t$ was forecast once from reported cases and once from reported deaths.
 Death forecasts from the renewal model were therefore not informed by past cases.
+One submission of the renewal model on December 28th 2020 was belated and therefore not included in the official Forecast hub ensemble.
 
-The second model (“convolution model”) was only used to forecast deaths and modeled these as a fraction of infected people who would die with some delay.
-
-Both models were left completely untuned and unchanged throughout the study period to create a baseline purely informed by epidemiological assumptions.
-Human forecasters, on the other hand, were able to adapt their forecasts to current or likely future interventions.
-
-The second model, here called “convolution model”, which was only used to forecast deaths, assumed that deaths could be modelled using a scaling parameter, as a  convolution of test positive cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
-Both models assumed a negative binomial observation model and a multiplicative day-of-the-week effect (Abbott, Hellewell, et al.
+The second model (“convolution model”) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses).
+The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model.
+The convolution model predicted deaths these as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
+Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model and a multiplicative day-of-the-week effect (Abbott, Hellewell, et al.
 2020).
-
+Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August.
 All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fit separately.
@@
 
-Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August.
-Population data at the national and state level in Germany and Poland used in the model-based forecasts was sourced from (Statistisches Bundesamt 2020) and (Statystyczny 2020).
-
 ### Statistical analysis
 
-Crowd forecasts and the renewal model were created over the whole period between October 12th 2020 until March 1st 2021.
-We added the convolution model later and started creating and submitting it on December 7th 2020.
-As the first submission suffered from a software bug, we disregard it here.
-Crowd forecasts and renewal model forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021.
-We added the convolution model later and started creating it on December 7th 2020.
-As the first forecast suffered from a software bug, we disregard it here.
-All our forecasts were time-stamped and submitted to the German and Polish Forecast Hub (CITATION).
-All forecasts were processed in a Docker (Merkel 2014) container to ensure a reproducible environment.
+For the main analysis we focused on two week ahead predictions, as predictions beyond this horizon are often unreliable due to rapidly changing conditions (J.
+Bracher et al.
+2021).
+Forecasts for cases were scored using the full period from October 2020 until March 2021.
+To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available.
+To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) where scored only over the later period where are forecasts were available (see Section \@ref(sensitivity-analysis) in the SI).
+Results remained broadly unchanged.
 
-To ensure compatibility between models, all death forecasts were scored using only the period from December 14th on, whereas case forecasts were evaluated on the entire submission period.
-They were both submitted to the so-called German/Polish forecast hub (http ref) and thus time-stamped (with one belated submission for the renewal model on December 28).
+Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Johannes Bracher et al.
+2021), the absolute error, relative bias, and empirical coverage of the 50% and 90% prediction intervals.
+The WIS is a proper scoring rule (CITE GNEITING) and can be understood as a generalisation of the absolute error to quantile-based forecasts.
+It can be decomposed into three separate penalties: forecast spread (i.e.
+uncertainty of forecasts), over-prediction and under-prediction - lower values are always better.
+While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts.
+The bias metric we use captures how much probability mass of the forecast was above or below the true value and therefore represents a general tendency to over- or under-predict in relative terms.
+It is bound between -1 (all quantiles of the predictive distribution are below the observed value) and 1 (all quantiles are above the observed value).
+Empirical coverage is the percentage of observed values that fall inside a given prediction interval (e.g.
+how many observed values fall inside all 50% prediction intervals).
+Scoring metrics are explained in more detail in Table \@ref(tab:scoring-metrics) in the SI.
+All scores were calculated using the scoringutils R package (N.
+Bosse 2020).
 
-### Forecasts
-
-#### Model-based forecasts
-
-We used two models from the EpiNow2 R package (version 1.3.3) as our model forecasts (Abbott, Hellewell, et al.
-2020).
-The first of these models, here called “renewal model”, which was used to forecast both test positive cases and deaths, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to estimate the effective reproduction number over time for latent infections and then convolved these infections to the target observation using data based delay distributions (Abbott, Hellewell, et al.
-2020; DOI n.d.; “Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the Covid-19 Outbreak in England | medRxiv” n.d.).
-Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August.
-For the forecasts, the reproduction number was assumed to remain constant from X days before the last data for which case data was available, roughly corresponding to continuing the latest trend in cases.
-
-The second model, here called “convolution model”, which was only used to forecast deaths, assumed that deaths could be modelled using a scaling parameter, as a  convolution of test positive cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
-Both models assumed a negative binomial observation model and a multiplicative day-of-the-week effect (Abbott, Hellewell, et al.
-2020).
-All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fit separately.
-More details are available in the supplementary information.
+At all stages of the evaluation our forecasts were compared to the median ensemble of all other models submitted to the German and Polish Forecast Hub (Hub ensemble).
+The ensemble that we call "Hub ensemble" in this paper differs from the official Hub ensemble (here called "XXX") as our forecasts were excluded from it to allow for a more straightforward comparison.
+To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e.
+we divided all scores by those achieved by the Hub ensemble on the same set of forecasts.
+In addition to comparing our forecasts against the hub ensemble excluding our models, we also assessed the impact of our forecasts on the performance of the forecasting hub by recalculating separate versions of the Hub ensemble with only some (or all) of our forecasts included.
 
@@
 
-The crowd forecast was constructed as an unweighted average of submissions by individual participants.
-The first of the two epidemiological models, the “renewal model”, estimates the effective reproduction number Rt (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infections (i.e.
-active infections) times Rt (assuming Rt to stay constant in the future).
-Based on predicted infections, reported cases and deaths are obtained by using delay distributions to model the time between infection and report date or death.
-Cases and deaths were forecast completely separately, meaning that Rt was estimated once from reported cases and once from reported deaths independently, meaning that death forecasts from the renewal model were not informed by past cases.
-The second model (“convolution model”) was only used to forecast deaths and modeled these as a fraction of infected people who would die with some delay.
-Both models were left completely untuned and unchanged throughout the study period to create a baseline purely informed by epidemiological assumptions.
-Human forecasters, on the other hand, were able to adapt their forecasts to current or likely future interventions.
+## Crowd forecast participation
 
-## Study period
-
-Crowd forecasts and the renewal model were created over the whole period between October 12th 2020 until March 1st 2021.
-They were both submitted to the so-called German/Polish forecast hub (http ref) and thus time-stamped (with one belated submission for the renewal model on December 28).
-We only added the convolution model later and started submitting it on December 21st 2020.
-To ensure compatibility between models, all death forecasts were scored using only the period from December 14th on, whereas case forecasts were evaluated on the entire submission period.
 A total number of 32 participants submitted forecasts, 17 of those self-identified as 'expert'.
@@
 
+## Scoring metrics used
+
+```{r scoring-metrics}
+wis <- list(
+  Metric = "WIS (Weighted) interval score", 
+  `Explanation` = r"(The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
+It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
+The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction.
+For a single interval, the score is computed as
+  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
+  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e.
+the lower and upper bound of a single prediction interval.
+For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
+  $$WIS = \frac{1}{K + 0.5} \cdot (w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y)),$$ 
+  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
+
+Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.)", 
+  `Caveats` = "The wis is based on measures of absolute error. When averaging across multiple targets, it will therefore be dominated by targets with higher absolute values.",
+  `References` = ""
+)
+
+interval_coverage <- list(
+  `Metric` = "Interval coverage", 
+  `Explanation` = r"(Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
+Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
+we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.)",
+  `Caveats` = "",
+  `References` = ""
+)
+
+bias <- list(
+  `Metric` = "Bias", 
+  `Explanation` = r"((Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict.
+Values are between -1 and 1 and 0 ideally.
+For continuous forecasts, bias is given as
+$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
+where $F$ is the CDF of the predictive distribution and $y$ is the observed value.
+
+For quantile forecasts, $F(y)$ is replaced by a quantile rank.
+The appropriate quantile rank is determined by whether the median forecast is below  or above the true value.
+We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.
+
+In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
+It is therefore a more robust measurement.)",
+  `Caveats` = "",
+  `References` = ""
+)
+
+data <- rbind(as.data.frame(wis), 
+              as.data.frame(interval_coverage),
+              as.data.frame(bias))
+
+# saveRDS(data, file = "tables/scores-table.rds")
+
+library(kableExtra)
+library(magrittr)
+library(knitr)
+data[, 1:2] %>%
+  kableExtra::kbl(format = "latex", booktabs = TRUE, 
+                  escape = FALSE,
+                  caption = "Overview of the scoring metrics used.",
+                  longtable = TRUE,
+                  linesep = c('\\addlinespace \\addlinespace')) %>%
+  kableExtra::column_spec(1, width = "2.5cm") %>%
+  kableExtra::column_spec(2, width = "13.0cm") %>%
+  # kableExtra::column_spec(3, width = "4.5cm") %>%
+  kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))
+
+```
+
 ## Further details on the semi-mechanistic forecasting models
@@
 The convolution model shares the same observation model as the renewal model but rather than assuming that an observation is predicted by itself instead assumes that it is predicted entirely by another observation after some parametric delay.
-It can be defined mathematically as follow,
+It can be defined mathematically as follows,
 

### 2021-10-13 analysis/analysis.Rmd
update figures and manuscript

@@
                    position = position_dodge(width = dodgewidth)) + 
-    geom_point(data = trend[target_type == ttype],
-               aes(shape = Classification)) +
+    geom_point(data = trend[target_type == ttype], size = 0.7) +
     geom_line(data = unfiltered_data[target_type == ttype & horizon == 2]) + 
@@
 
-p <- ens[, .(value = sum(value), 
+targetvars <- data.frame(
+  variable = c("GM_inc_case", "GM_inc_death", "PL_inc_case", "PL_inc_death"), 
+  target = c("Cases - Germany", "Deaths - Germany", "Cases - Poland", "Deaths - Poland")
+)
+
+ens <- ens[, .(value = sum(value), 
              epinow = sum(epinow, na.rm = TRUE), 
              crowd = sum(crowd, na.rm = TRUE)), by = c("variable", "Date")] %>%
-  ggplot(aes(y = value, x = Date, color = variable)) + 
+  merge(targetvars)
+
+# number of submissions from crowd and epinow2
+ens[, .(crowd = sum(crowd) / 4, 
+        epinow = sum(epinow) / 4)]
+
+# how many models included in the ensemble? 
+ens %>%
+  summary()
+
+p <- ens %>%
+  ggplot(aes(y = value, x = Date)) + 
+  facet_wrap(~ target) + 
   # geom_col(aes(fill = variable), position = position_dodge()) + 
-  geom_point() + 
+  geom_point(size = 0.7) + 
   geom_line() + 
   scale_color_manual(values = colcases) + 
-  theme_minimal()
+  theme_minimal() + 
+  labs(y = "Number of ensemble members", x = "Date")
 

### 2021-10-13 manuscript/manuscript.Rmd
update figures and manuscript

@@
 
-## Methods
+# Methods
 
@@
 
-### Forecast targets and interaction with the German and Polish Forecast Hub
+## Forecast targets and interaction with the German and Polish Forecast Hub
 
@@
 
-### Crowd forecasts
+## Crowd forecasts
 
@@
 
-### Model-based forecasts
+## Model-based forecasts
 
@@
 
-### Statistical analysis
+## Analysis
 
@@
 Scoring metrics are explained in more detail in Table \@ref(tab:scoring-metrics) in the SI.
-All scores were calculated using the scoringutils R package (N.
+All scores were calculated using the `scoringutils` R package (N.
 Bosse 2020).
 
-At all stages of the evaluation our forecasts were compared to the median ensemble of all other models submitted to the German and Polish Forecast Hub (Hub ensemble).
-The ensemble that we call "Hub ensemble" in this paper differs from the official Hub ensemble (here called "XXX") as our forecasts were excluded from it to allow for a more straightforward comparison.
+At all stages of the evaluation our forecasts were compared to the median ensemble of all other models submitted to the German and Polish Forecast Hub ("Hub ensemble").
+This "Hub ensemble" was retrospectively computed and excludes all our models.
+It therefore differs from the official Hub ensemble (here called "hub-ensemble-realised") which included crowd forecasts as well as renewal model forecasts.
+
+The ensemble that we call "Hub ensemble" in this paper differs from the
+
+in that we removed our forecasts to allow for a more straightforward comparison.
 To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e.
@@
 In addition to comparing our forecasts against the hub ensemble excluding our models, we also assessed the impact of our forecasts on the performance of the forecasting hub by recalculating separate versions of the Hub ensemble with only some (or all) of our forecasts included.
+
+Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
 
@@
 
-The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons (as captured by our relative bias metric with values between -1 and 1 and 0 ideally).
+The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons.
 The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure 1X).
@@
 Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (“hub-ensemble-realised”), while the convolution model was never included as it was deemed too similar to the existing renewal model, thus potentially introducing bias.
+In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on December 28 2020 over the Christmas period) and a maximum of 10.
 Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
+An overview of all models and ensemble verisons is shown in Table \@ref(tab:table-ensemble-versions) in the SI.
 
@@
 We also considered the impact of our contributions on the mean, rather than the median ensemble. 
-General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble.
+<!-- In general, the median ensemble tended to perform slightly better than the mean ensemble - needs more analysis -->
+General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (REFERENCE FIGURE).
 This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far.
@@
 - plot for limited period
+
+```{r table-ensemble-versions}
+
+rbind(
+  list(
+    Name = "Hub-ensemble-realised", 
+    `Explanation` = "Official Forecast Hub median ensemble.
+Created by the Forecast Hub officially under the name 'KITCOVIDhub-median\\_ensemble' and used as the default ensemble.
+Included are our crowd forecasts as well as the renewal model (with one missed submission on December 28 2020, but not the convolution model which was deemed to similar to the renewal model."
+  ),
+  list(
+    Name = "Hub-ensemble-realised-mean", 
+    `Explanation` = "Official Forecast Hub mean ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-mean\\_ensemble'."
+  ),
+  list(Name = "", Explanation = ""),
+
+  list(
+    Name = "Hub-ensemble", 
+    `Explanation` = "Version of the official Hub median ensemble which excludes all our contributions."
+  ),
+  list(
+    Name = "Hub-ensemble-mean", 
+    `Explanation` = "Version of the official Hub mean ensemble which excludes all our contributions."
+  ),
+  list(
+    Name = "Hub-ensemble-with-renewal, 
+    Hub-ensemble-with-renewal-mean", 
+    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Renewal model."
+  ),
+  list(
+    Name = "Hub-ensemble-with-crowd, 
+    Hub-ensemble-with-crowd-mean", 
+    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Crowd forecast."
+  ),
+  list(
+    Name = "Hub-ensemble-with-convolution, 
+    Hub-ensemble-with-convolution-mean", 
+    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Convolution model (which originally was never included in any official Hub ensemble)."
+  ),
+    list(
+    Name = "Hub-ensemble-with-all, 
+    Hub-ensemble-with-all-mean", 
+    `Explanation` = "Versions of the official Hub ensembles which includes all our contributions.
+For cases, this is identical to the official Hub ensembles, but for deaths the convolution model was added."
+  ),
+
+  list(Name = "", Explanation = ""),
+  list(
+    Name = "Crowd forecast", 
+    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'"
+  ),  
+  list(
+    Name = "Renewal model", 
+    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'"
+  ),  
+  list(
+    Name = "Convolution model", 
+    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\\_secondary'"
+  )
+) %>%
+  kableExtra::kbl(format = "latex", booktabs = TRUE, 
+                  escape = FALSE,
+                  caption = "Overview of the models and ensembles used.",
+                  longtable = TRUE,
+                  linesep = c('\\addlinespace \\addlinespace')) %>%
+  kableExtra::column_spec(1, width = "4.5cm") %>%
+  kableExtra::column_spec(2, width = "11.0cm") %>%
+  # kableExtra::column_spec(3, width = "4.5cm") %>%
+  kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))
+
+```

### 2021-10-13 manuscript/manuscript.Rmd
update manuscript

@@
 
+Generally, trends in overall performance were broadly similar across locations (Figure XX).
+However, relative to the Hub ensemble, the crowd forecasts performed better in Germany than in Poland and the renewal model better in Poland than in Germany (Figure XXA, XXG).
+
 ## Death Forecasts
@@
 ```
-
-## Performance across locations (maybe not a separate section or more nuance)
-
-Generally, trends in overall performance were similar across locations (Figure S1).
-Notably,the convolution model performed better, when assessed by both median and mean WIS, in Germany than Poland indicating a stronger connection between observed cases and deaths.
-Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly  (Figure S1).
-
-All model-based predictions, but not the crowd forecasts, were noticeably sharper in Poland than in Germany (Figure S1), in line with their smaller overall WIS values.
-Crowd forecasts for cases (but not for deaths) were approximately equally sharp in Poland and in Germany.
-For both cases and deaths, forecasts tended to be lower relative to observed values in Poland than in Germany, with bias values lower for all forecasts in Poland than in Germany (except crowd forecasts of cases, Figure S1F).
 

### 2021-10-13 analysis/analysis.Rmd
update plots and manuscript

@@
 
- if (colour_scheme == "ensemble") {
+ if (colour_scheme == "ensemble" & type == "case") {
     # filter out ensembles not needed
@@
 
-  ggsave(here(output_dir, paste0(plotname, ".png")), 
+  ggsave(here(output_dir, paste0(plotname, "-v1.png")), 
          height = 9.1, width = 8)
@@
 
-    ggsave(here(output_dir, paste0(plotname, "-2.png")), 
+    ggsave(here(output_dir, paste0(plotname, "-v2.png")), 
          height = 5.1, width = 10)
@@
 
-    ggsave(here(output_dir, paste0(plotname, "-3.png")), 
+    ggsave(here(output_dir, paste0(plotname, "-v3.png")), 
          height = 9.1, width = 10)
@@
 
-    ggsave(here(output_dir, paste0(plotname, "-4.png")), 
+    ggsave(here(output_dir, paste0(plotname, "-v4.png")), 
            height = 9.1, width = 10)

### 2021-10-13 manuscript/manuscript.Rmd
update plots and manuscript

@@
 ```{r agg-performance-all, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-4.png")
+knitr::include_graphics("../analysis/plots/aggregate-performance-all-v4.png")
 ## change name to v4
@@
 Generally, trends in overall performance were broadly similar across locations (Figure XX).
-However, relative to the Hub ensemble, the crowd forecasts performed better in Germany than in Poland and the renewal model better in Poland than in Germany (Figure XXA, XXG).
+Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
+However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figure XXA, XXG).
 
@@
 The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction.
-For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or underpredict than for cases (Figure XX).
+For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure XX).
 
@@
 ```{r agg-performance-ensemble, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-4.png")
+knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-v4.png")
 ```
@@
 This suggests that humans are relatively good at foreseeing trends that are hard to model but may struggle to form an intuition for the exact relationship between cases and deaths.
-Our epidemiologicalUntuned models, on the other hand performed relatively well short-term, but not for longer horizons without any form of human intervention or assumption to guide behaviour when conditions evolve.
-Ensembles, in general, showed the greatest consistency in their performance (and best mean performance), but did often not provide the best forecasts for a given forecast date.
-Our contributions consistently improved the pre-existing Hub ensemble for cases, but not for deaths.
+
+<!-- Our contributions consistently improved the pre-existing Hub ensemble for cases, but not for deaths.
 We often found contributions to an ensemble to be beneficial even in instances where the forecasting approach entering the ensemble performed consistently worse than the pre-existing ensemble.
+-->
 
@@
 cite Tetlock, cite Grecchia, cite McAndrew).
-In contrast, we directly compare human and model-based forecasts.
+In contrast, we directly compared human and model-based forecasts.
 This is similar to the approach taken by Farrow et al., but extends it in several ways.
@@
 only asked for point predictions and constructed a probabilistic forecast from these, we asked participants to quantify their uncertainty directly, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse aspects of the forecasts like overconfidence.
-In addition, we compared crowd forecasts to completely untuned models, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight.
+In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight.
 In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (J.
@@
 who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants.
-The advantage of crowd forecasts we observed over untuned models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models.
-However, this likely explains only part of the difference and performance relative to the Hub ensemble strongly suggests that human insight is valuable when predicting highly volatile and hard-to-predict quantities such as case numbers.
-Relatively good performance of our untuned models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time.
+The advantage of crowd forecasts we observed over our semi-mechanistic models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models.
+However, this probably explains only part of the difference and performance relative to the Hub ensemble strongly suggests that human insight is valuable when predicting highly volatile and hard-to-predict quantities such as case numbers.
+Relatively good performance of our semi-mechanistic models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time.
 This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data).
+The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure XX), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.
 While we were not able to observe how expert opinion informed other models submitted to the Forecast Hub, conversations with the Hub organisers suggest that forecasts tended to benefit from a large degree of human intervention.
-Unfortunately, we were not able to test a scenario in which users were asked to alter an existing model output, rather than create a new forecast from a naive baseline, and can therefore make no conclusive statements about the direct effects of researchers tuning their models.
+Unfortunately, we were not able to test a scenario in which users were asked to alter an existing model output.
+We can therefore make no conclusive statements about the direct effects of researchers tuning their models, rather than create a new forecast from a naive baseline.
 
@@
 This may have precluded interested parties from submitting forecasts.
-It is both conceivable that a greater number of participants would have improved forecasts, but also that a larger audience may have decreased the mean quality of predictions.
-Motivating forecasters to contribute regularly proved challenging, especially given that the majority of our participants were from the UK and had little connection to either Germany or Poland.
+The low number of participants presumably resulted in higher variance of forecasts, but also potentially in better average forecast performance.
+Motivating forecasters to contribute regularly proved challenging, especially given that the majority of our participants were from the UK and had little connection to Germany and even less to Poland.
 In addition, lack of effective outreach played an important role, as did a lack of time and resources to design the interface in a way that is appealing enough to attract large audiences outside of academia.
@@
 
-In general, our results support the use of ensembles, rather than individual models to inform public health policies, as these provide consistently good forecasts and largely avoid particularly bad outlier forecasts.
+In general, our results support the use of ensembles, rather than individual models to inform public health policies, as these provide consistently good performance and largely avoid particularly bad outlier forecasts.
+Our results also suggest that at least for a small ensemble like the German and Polish Forecast Hub ensemble tends to be beneficial in most instances (with the version of the hub ensemble that includes all our contributions ("hub-ensemble-with-all") outperforming the realised official hub ensemble in almost all instances).
+We often found contributions to an ensemble to be beneficial even in instances where the forecasting approach entering the ensemble performed consistently worse than the pre-existing ensemble.
+Including more models may be easier when using a median ensemble, as extreme forecasts tend to have less of an influence there.
+Individual models, however, can still have a place in informing public policy.
 As an average, ensembles show the consensus opinion, which implies that in contrast to single models, they are not likely to reveal information, e.g.
 about future changes in trend, that is not in some way ‘obvious’ to the majority of forecasters.
-Indeed, as illustrated in Figure SXX, single models often outperform the ensemble (while also performing much worse at other times) and may therefore also play a role in informing public policy in specific circumstances alongside ensemble predictions.
 
@@
 Model-based forecasts could be used as an input to human judgement, with researchers adjusting predictions generated by models.
+Seeing a model-based forecasts could help humans calibrate uncertainty better, while allowing for manual intervention to adapt spurious trend predictions.
 Tools need to be developed to facilitate this process at a larger scale.
 Human insight could also be used as an input to models.
-Such a ‘hybrid’ forecasting approach could for example ask humans to predict the trend of the effective reproduction number Rt or the doubling rate (i.e.
+Such a ‘hybrid’ forecasting approach could for example ask humans to predict the trend of the effective reproduction number $R_t$ or the doubling rate (i.e.
 how the epidemic evolves) into the future and use this to estimate the exact number of cases, hospitalisations or deaths this would imply.
 This approach seems especially promising for forecasting deaths if a model can accurately describe delay distributions and epidemiological relationships between different parameters.
-In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust confidence intervals may be another promising approach.
-Crowd forecasting in general could benefit a lot from the availability of tools suitable to appeal to a greater audience.
+In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust and widen confidence intervals may be another promising approach.
+Crowd forecasting in general could benefit greatly from the availability of tools suitable to appeal to a greater audience.
 Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile for researchers and policymakers to further develop and explore.
@@
 ```{r performance-locations-rel, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-4.png")
+knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4.png")
 ```

### 2021-10-13 analysis/analysis.Rmd
update SI

@@
            new = c("Horizon", "Model", "Target", "WIS", "Abs. error", 
-                   "rel. skill", "WIS - rel.", "Sharpness", 
+                   "rel. skill", "WIS - rel.", "Dispersion", 
                    "Underpred.", "Overpred.", "Bias", 
@@
   table <- scores[,!c("Target")] %>%
-    kable(format = "html", col.names = c(" ", names(scores)[-(1:2)])) %>% #format = "markdown"
+    kable(format = "latex", booktabs = TRUE, 
+          align = c("l", "l", rep("c", 9)),
+          col.names = c(" ", names(scores)[-(1:2)])) %>%
     collapse_rows(columns = 1) %>%
-    kable_styling(bootstrap_options = "striped", 
-                  full_width = full_width) %>%
+    kable_styling(latex_options = c("scale_down", 
+                                    "hold_position")) %>%
     column_spec(1, background = "white")
@@
     table <- table %>%
-      pack_rows("Cases", 1, case_rows, indent = FALSE) %>% 
-      pack_rows("Deaths", case_rows + 1, nrow(scores), indent = FALSE)
+      pack_rows("Cases", 1, case_rows, indent = FALSE, 
+                hline_after = TRUE) %>% 
+      pack_rows("Deaths", case_rows + 1, nrow(scores), indent = FALSE, 
+                hline_after = TRUE)
   }
@@
                      ~ paste0(., " (", 
-                              round(100 * ./.[model %in% c("Hub-ensemble", 
-                                                           "Hub-ensemble-mean")]), 
-                              "%)"))
+                              round(./.[model %in% c("Hub-ensemble", 
+                                                     "Hub-ensemble-mean")], 2), 
+                              ")"))
 
@@
   table <- score_table(df[horizon <= 2])
-  save_kable(table, file = here(output_dir, 
-                                paste0(plotname, "_", 2, "_ahead.png")))
+
+  saveRDS(object = table, 
+          file = here("analysis", "plots", paste0(plotname, "_", 2, "_ahead.rds")))
 
   table <- score_table(df[horizon > 2]) 
-  save_kable(table, file = here(output_dir, 
-                                paste0(plotname, "_", 4, "_ahead.png")))
+  saveRDS(object = table, 
+          file = here("analysis", "plots", paste0(plotname, "_", 4, "_ahead.rds")))
 }
@@
   filter(!(forecast_date %in% as.character(forecast_dates$death_not_scored))) %>%
-  make_table(plotname = "table_mean-late-period")
+  make_table(plotname = "table-late-period")
 
@@
 ```
-
-*Figure 2.
-Top: Distribution of the scaled relative skill scores for the different model and forecast targets.
-The vertical black line represents the baseline model.
-Models beat the baseline more easily for death forecasts.
-The renewal model had by far the most variance in terms of its performance, while the crowd forecasting model seems most consistent.
-Bottom: Distribution of scaled relative skill in different phases of the epidemic.
-The epidemic was classified as 'increasing', if the forecast point and the two data points before form a monotonically rising line, 'decreasing' if numbers were falling and 'unclear' otherwise.
-This plot seems like a lot of noise to me, but unsure.*
 
@@
 
-<!-- **Further things we could look at** -->
-
-<!-- - maybe look at correlation between the number of weekly cases and the score? -->
-
-<!-- - maybe it would be interesting to look at other baseline models, e.g. "how hard is it to beat a model that just always continues the trend?" -->
-
-<!-- - look at crowd performance as a function of the number of forecasts -->
-
-maybe leave that to a second paper --\>
-
 ## Number of expert forecasters
@@
 
+dt[, location_target := paste0(str_to_title(target_type), 
+                               "s", " in ", location_name)]
+
 dt %>%
@@
   geom_line() + 
-  facet_wrap(location_name ~ target_type)
-
+  facet_wrap(~ location_target) + 
+  theme_minimal() + 
+  labs(y = "Number of forecasters", x = "Date")
+
+ggsave(filename = here("analysis", "plots", "number-forecasters.png"))
 ```

### 2021-10-13 manuscript/manuscript.Rmd
update SI

@@
                       fig.pos = "H", out.extra = "")
+library(kableExtra)
+library(magrittr)
+library(knitr)
 ```
@@
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components sharpness, over-prediction and under-prediction.
+WIS is decomposed into its components dispersion, over-prediction and under-prediction.
 C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
 D: Empirical coverage of the 90\\% prediction intervals.
-E: Sharpness (same as in panel A, B).
+E: Dispersion (same as in panel A, B).
 Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
@@
 knitr::include_graphics("../analysis/plots/aggregate-performance-all-v4.png")
-## change name to v4
 ```
@@
 ```{r}
-caption <- "A, C: Visualisation of two week ahead forecasts against the true observed values.
-The shape indicates whether there has been a monotonic increase or decrease over the last two weeks leading up to a given data point, or an unclear trend.
-Forecasts that aren’t scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.
-The shape indicates whether the trend was rising, falling or unclear at the date when the corresponding forecast was made (i.e.
-two weeks earlier, which leads to a shift of two weeks when compared to panels A and C)"
+caption <- "A, C: Visualisation of 50\\% prediction intervals of two week ahead forecasts against the true observed values.
+Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
+B, D: Visualisation of corresponding WIS."
 ```
@@
 ```{r}
-caption <- ""
+caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country."
 ```
@@
 ```{r}
-caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub ensemble.
+caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
 “Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included.
@@
 D: Standard deviation of the WIS.
-E: Sharpness (higher values mean greater dispersion of the forecast).
+E: Dispersion (higher values mean greater spread of the forecast).
 F: Bias, i.e.
@@
 
-<!-- Our contributions consistently improved the pre-existing Hub ensemble for cases, but not for deaths.
-We often found contributions to an ensemble to be beneficial even in instances where the forecasting approach entering the ensemble performed consistently worse than the pre-existing ensemble.
--->
-
 Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts.
@@
 In general, our results support the use of ensembles, rather than individual models to inform public health policies, as these provide consistently good performance and largely avoid particularly bad outlier forecasts.
-Our results also suggest that at least for a small ensemble like the German and Polish Forecast Hub ensemble tends to be beneficial in most instances (with the version of the hub ensemble that includes all our contributions ("hub-ensemble-with-all") outperforming the realised official hub ensemble in almost all instances).
+Our results also suggest that at least for a small median ensemble like the German and Polish Forecast Hub ensemble adding more models may increase performance in most instances (with the version of the hub ensemble that includes all our contributions ("hub-ensemble-with-all") outperforming the realised official hub ensemble in almost all instances).
 We often found contributions to an ensemble to be beneficial even in instances where the forecasting approach entering the ensemble performed consistently worse than the pre-existing ensemble.
@@
 Projections that are meant to inform policy makers about possible scenarios may be different from forecasts meant to inform the general public, and yet again different from forecasts submitted with the goal of advancing open research and in order to allow public scrutiny and discussion about the merits of different approaches.
-
 Further work should explore the effects of human intervention on model-based forecasts in more detail.
@@
 Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile for researchers and policymakers to further develop and explore.
+
+# (APPENDIX) Supplementary information {-}
 
@@
 
-# saveRDS(data, file = "tables/scores-table.rds")
-
-library(kableExtra)
-library(magrittr)
-library(knitr)
 data[, 1:2] %>%
@@
   kableExtra::column_spec(2, width = "13.0cm") %>%
-  # kableExtra::column_spec(3, width = "4.5cm") %>%
   kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))
@@
 ```
+
+\clearpage
 
@@
   I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
-  r &\sim \mathcal{LN}(r_{obs}, 0.2) \\
+  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
 \end{align}
@@
     \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
-    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) \\
+    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
 \end{align}
@@
     \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
-    \alpha &\sim \mathcal{N}(0.005, 0.0025) \\
+    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
 \end{align}
@@
 
+\clearpage
+
+```{r}
+add_caption <- function(table, caption) {
+  table <- gsub(pattern = "begin\\{table\\}\\[!h\\]",
+                replacement = paste0("begin\\{table\\}[!h]\n\\\\caption\\{",
+                                     caption,
+                                     "\\\\\\\\\\\\hspace{\\\\textwidth}\\}\n"),
+                x = table)
+  return(table)
+}
+```
+
 ## Tables with results of the forecast evaluation
@@
 ```{r}
-caption <- ""
+caption <- 
+  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
+Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
+Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
+the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
+WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
+Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
+Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
+50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
 ```
@@
 ```{r score-table-2}
+table <- readRDS("../analysis/plots/table_scores_2_ahead.rds")
+add_caption(table, caption)
 ```
@@
 ```{r}
-caption <- ""
+caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
 ```
@@
 ```{r score-table-4}
+table <- readRDS("../analysis/plots/table_scores_4_ahead.rds")
+add_caption(table, caption)
+
 ```
+
+\clearpage
 
@@
 ```{r}
-caption <- ""
+caption <- "Visualisation of aggregate performance metrics across locations.
+A: mean weighted interval score (WIS) across horizons.
+B: median WIS.
+C: Absolute error of the median forecast.
+D: Standard deviation of the WIS.
+E: Sharpness (higher values mean greater dispersion of the forecast).
+F: Bias, i.e.
+general tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Empirical coverage of the 50\\% prediction intervals.
+F: Empirical coverage of the 90\\% prediction intervals."
 ```
@@
 ```{r}
-caption <- ""
+caption <- " Visualisation of aggregate performance metrics across locations relative to the Hub ensemble (excluding our contributions).
+A: mean weighted interval score (WIS) across horizons.
+B: median WIS.
+C: Absolute error of the median forecast.
+D: Standard deviation of the WIS.
+E: Sharpness (higher values mean greater dispersion of the forecast).
+F: Bias, i.e.
+general tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Empirical coverage of the 50\\% prediction intervals.
+F: Empirical coverage of the 90\\% prediction intervals."
 ```
@@
 
+\clearpage
+
 ## Visualisation of daily reported cases and deaths
@@
 ```{r}
-caption <- ""
+caption <- "Visualisation of daily report data. The black line represents weekly data divided by seven. Data were last accessed through the German and Polish Forecast Hub on August 21 2021."
 ```
@@
 
-### Visualisation of scores and forecasts 1, 3, 4 weeks ahead
+\clearpage
+
+## Visualisation of scores and forecasts 1, 3, 4 weeks ahead
 
 ```{r}
-caption <- ""
+caption <- "A, C: Visualisation of 50\\% prediction intervals of one week ahead forecasts against the true observed values.
+Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
+B, D: Visualisation of corresponding WIS."
 ```
@@
 ```{r}
-caption <- ""
+caption <- gsub(x = caption, pattern = "one", replacement = "three")
 ```
@@
 ```{r}
-caption <- ""
+caption <- gsub(x = caption, pattern = "three", replacement = "four")
 ```
@@
 
-### Distribution of scores for 1, 3, 4 week-ahead forecasts
+\clearpage
+
+## Distribution of scores
+
+### Absolute scores
 
 ```{r}
-caption <- ""
+caption <- "A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country."
 ```
@@
 ```{r}
-caption <- ""
+caption <- "A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
+B: Distribution of ranks separate by country."
 ```
@@
 ```{r}
-caption <- ""
+caption <- gsub(x = caption, pattern = "one", replacement = "two")
 ```
@@
 ```{r}
-caption <- ""
+caption <- gsub(x = caption, pattern = "two", replacement = "three")
 ```
@@
 
+\clearpage
+
+## Comparison of ensembles
+
+### Performance visualisation mean ensemble
+
+```{r}
+caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
+“Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included.
+Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions.
+For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
+A: mean weighted interval score (WIS) across horizons.
+B: median WIS.
+C: Absolute error of the median forecast.
+D: Standard deviation of the WIS.
+E: Dispersion (higher values mean greater spread of the forecast).
+F: Bias, i.e.
+general tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Empirical coverage of the 50\\% prediction intervals.
+F: Empirical coverage of the 90\\% prediction intervals"
+```
+
+```{r agg-performance-ensemble-mean, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-mean-v4.png")
+```
+
+### Tables median ensemble
+
+```{r}
+caption <- 
+  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
+Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
+Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
+the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
+WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
+Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
+Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
+50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
+```
+
+```{r score-table-ensemble-2}
+table <- readRDS("../analysis/plots/table_median-ensemble_scores_2_ahead.rds")
+add_caption(table, caption)
+```
+
+```{r}
+caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
+```
+
+```{r score-table-ensemble-4}
+table <- readRDS("../analysis/plots/table_median-ensemble_scores_4_ahead.rds")
+add_caption(table, caption)
+```
+
+### Tables mean ensemble
+
+```{r}
+caption <- 
+  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
+Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
+Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
+the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
+WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
+Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
+Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
+50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
+```
+
+```{r score-table-ensemble-mean-2}
+table <- readRDS("../analysis/plots/table_mean-ensemble_scores_2_ahead.rds")
+add_caption(table, caption)
+```
+
+```{r}
+caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
+```
+
+```{r score-table-ensemble-mean-4}
+table <- readRDS("../analysis/plots/table_mean-ensemble_scores_4_ahead.rds")
+add_caption(table, caption)
+```
+
+\clearpage
+
 ## Sensitivity analysis
 
-- tables for limited period
-- plot for limited period
+In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later.
+This sensitivity shows performance of all models restricted to the period from October 14 2020 until March 1st 2021 where all models were available.
+
+```{r}
+caption <- "Visualisation of aggregate performance metrics across forecast horizons only for the period from October 14th 2020 on where all models were available.
+A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
+WIS is decomposed into its components dispersion, over-prediction and under-prediction.
+C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
+D: Empirical coverage of the 90\\% prediction intervals.
+E: Dispersion (same as in panel A, B).
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
+F: Bias, i.e.
+general (relative) tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Absolute error of the median forecast (lower is better).
+H.
+Standard deviation of all WIS values for different horizons"
+```
+
+```{r agg-performance-all-late, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/aggregate-performance-all-late-period-v4.png")
+```
+
+```{r}
+caption <- 
+  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
+Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
+the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
+WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
+Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
+Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
+50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
+```
+
+```{r score-table-late-2}
+table <- readRDS("../analysis/plots/table-late-period_2_ahead.rds")
+add_caption(table, caption)
+```
+
+```{r}
+caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
+```
+
+```{r score-table-late-4}
+table <- readRDS("../analysis/plots/table-late-period_4_ahead.rds")
+add_caption(table, caption)
+
+```
+
+\clearpage
+
+## Overview of models and forecasters
 
@@
   kableExtra::column_spec(2, width = "11.0cm") %>%
-  # kableExtra::column_spec(3, width = "4.5cm") %>%
   kableExtra::kable_styling(latex_options = c("striped", "repeat_header")) 
+```
 
+```{r num-forecasters, fig.cap="Number of participants who submitted a forecast over time."}
+knitr::include_graphics("../analysis/plots/number-forecasters.png")
 ```
+
+```{r num-ensemble-members, fig.cap="Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
+Note that the renewal model was not included in the ensemble on December 28th 2020."}
+knitr::include_graphics("../analysis/plots/ensemble-members.png")
+```
+
+\clearpage

### 2021-10-13 manuscript/manuscript.Rmd
fix table references

@@
     extra_dependencies: ["float"]
+    keep_tex:  true
 bibliography:
@@
 
-For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure S1A).
-For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 100%) was 89% for crowd forecasts and 140% for the renewal model (Table SX).
-Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was right-skewed, and average performance was heavily influenced by outliers (Figure 3).
-Overall, low variance in forecast performance was closely linked with good mean performance (Figures 1AX and 1DX), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure XX), as well as the highest standard deviation of WIS values (relative WIS sd 154% a the two weeks ahead horizon), while the ensemble of crowd forecasts  (rel.
-WIS sd 76%) and the Hub ensemble (= 100%) showed more stable performance.
+For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure \@ref(fig:performance-locations-rel)A).
+For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 100%) was 89% for crowd forecasts and 140% for the renewal model (Table \@ref(tab:score-table-2)).
+Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was right-skewed, and average performance was heavily influenced by outliers (Figure \@ref(fig:distribution-scores)).
+Overall, low variance in forecast performance was closely linked with good mean performance (Figures \@ref(fig:agg-performance-all)H and and \@ref(fig:agg-performance-all)A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
+The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores), as well as the highest standard deviation of WIS values (relative WIS sd 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts  (rel.
+WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
 
@@
 For example, all models failed to predict the change in trend from increase to decrease that happened in early November...
-in Germany and severely overshot (Figure 2XX).
+in Germany and severely overshot (Figure \@ref(fig:forecasts-and-truth)A).
 This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past  of observations.
@@
 
-All forecasting approaches, including the Hub ensemble, were overconfident and showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure 1X and 1X).
+All forecasting approaches, including the Hub ensemble, were overconfident and showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
 Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts.
-This was especially an issue for crowd forecasts, which were markedly sharper (i.e., narrower) than other approaches (Figure 1X) and only showed a small increase in uncertainty across forecast horizons.
-In spite of good performance in terms of the absolute error (Figure 1X), excessive sharpness led to forecasts which were severely overconfident (covering only 36% and 55% of observations with their 50% and 90% prediction intervals at a two week horizon, and only 5% and 38% four weeks ahead) (Figure 1X and Table SXX).
-Despite worse performance in terms of absolute error (Figure 1X), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly and non-linearly across forecast horizons.
+This was especially an issue for crowd forecasts, which were markedly sharper (i.e., narrower) than other approaches (Figure \@ref(fig:agg-performance-all)E) and only showed a small increase in uncertainty across forecast horizons.
+In spite of good performance in terms of the absolute error (Figure \@ref(fig:agg-performance-all)G), excessive sharpness led to forecasts which were severely overconfident (covering only 36% and 55% of observations with their 50% and 90% prediction intervals at a two week horizon, and only 5% and 38% four weeks ahead) (Figure \@ref(fig:agg-performance-all)C,D and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
+Despite worse performance in terms of absolute error (Figure \@ref(fig:agg-performance-all)G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly and non-linearly across forecast horizons.
 
 The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons.
-The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure 1X).
-Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figure X and Table X), implying that over-prediction (e.g.
+The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \@ref(fig:agg-performance-all)F).
+Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \@ref(fig:agg-performance-all)A and \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)), implying that over-prediction (e.g.
 when missing a peak) tended to be more costly in terms of the WIS.
 
-Generally, trends in overall performance were broadly similar across locations (Figure XX).
+Generally, trends in overall performance were broadly similar across locations (Figures \@ref(fig:performance-locations) and \@ref(fig:performance-locations-rel)).
 Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
-However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figure XXA, XXG).
+However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figure \@ref(fig:performance-locations-rel)A and \@ref(fig:performance-locations-rel)G).
 
@@
 
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure 1A, Figure S1A).
-Relative WIS values for the models two weeks ahead were 122% (convolution model), 126% (crowd forecast), 100% (Hub ensemble) and 179% (renewal model).
-The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure 1A, Figure S1A), and also better than the convolution model three and four weeks ahead.
-Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate Rt trace from deaths, is not well suited for the task.
-The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure 1A, Table SX).
+For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B).
+Relative WIS values for the models two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1 (Hub ensemble) and 1.79 (renewal model).
+The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B), and also better than the convolution model three and four weeks ahead.
+Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate $R_t$ trace from deaths, is not well suited for the task.
+The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \@ref(fig:agg-performance-all)B, Table \@ref(tab:score-table-4)).
 
@@
 The Hub ensemble had the greatest coverage, with empirical coverage of the 50% and 90% prediction intervals exceeding 50%, and 90%, respectively, across all forecast horizons.
-Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure 1X and XX).
+Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
 As for cases, the crowd forecast tended to be the sharpest and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
@@
 
-For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict.
+For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \@ref(fig:agg-performance-all)F.
 The convolution model had a strong tendency to under-predict, which steadily decreased for longer forecast horizons.
 The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction.
-For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure XX).
+For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \@ref(fig:agg-performance-all)A, \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2), \@ref(tab:score-table-4)).
 
@@
 Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
-An overview of all models and ensemble verisons is shown in Table \@ref(tab:table-ensemble-versions) in the SI.
+An overview of all models and ensemble versions is shown in Table \@ref(tab:table-ensemble-versions) in the SI.
 
 For cases, our contributions (compared to the Hub ensemble without our contributions) consistently improved performance across all forecasting horizons (rel.
-WIS 90% two weeks ahead).
+WIS 0.9 two weeks ahead, Table \@ref(tab:score-table-ensemble-2)).
 Contributions from the crowd forecasts alone also were positive across all forecast horizons, while contributions from the renewal model became negative for longer horizons (rel.
-WIS 102% three weeks ahead, 106% four weeks ahead).
+WIS 1.02 three weeks ahead, 1.06 four weeks ahead).
 The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects.
-Only for four week ahead predictions would removing the renewal model have improved performance (Table XX).
+Only for four week ahead predictions would removing the renewal model have improved performance (Table \@ref(tab:score-table-ensemble-4)).
 
 For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel.
-WIS of the hub-ensemble-realised 101% two weeks ahead, 105% four weeks ahead).
+WIS of the hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \@ref(tab:score-table-ensemble-2) and \@ref(tab:score-table-ensemble-4)).
 Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons).
-This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Table XX) and especially worse for longer horizons.
+This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \@ref(fig:agg-performance-all)) and especially worse for longer horizons.
 
@@
 <!-- In general, the median ensemble tended to perform slightly better than the mean ensemble - needs more analysis -->
-General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (REFERENCE FIGURE).
+General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \@ref(fig:agg-performance-ensemble)B and \@ref(fig:agg-performance-ensemble-mean)B).
 This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far.
@@
 This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data).
-The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure XX), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.
+The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \@ref(fig:forecasts-and-truth)A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.
 While we were not able to observe how expert opinion informed other models submitted to the Forecast Hub, conversations with the Hub organisers suggest that forecasts tended to benefit from a large degree of human intervention.
@@
 ```{r}
-add_caption <- function(table, caption) {
+add_caption <- function(table, caption, label = NULL) {
+  if (is.null(label)) {
+    label <- paste0("tab:", opts_current$get("label"))
+  }
   table <- gsub(pattern = "begin\\{table\\}\\[!h\\]",
-                replacement = paste0("begin\\{table\\}[!h]\n\\\\caption\\{",
+                replacement = paste0("begin\\{table\\}[!h]\n", 
+                                     "\\\\caption\\{",
+                                     "\\\\\\label\\{", label, "\\}",
                                      caption,
@@
 }
+
 ```
@@
 table <- readRDS("../analysis/plots/table_scores_2_ahead.rds")
-add_caption(table, caption)
+add_caption(table, caption, label = "tab:score-table-2")
 ```
@@
 table <- readRDS("../analysis/plots/table_scores_4_ahead.rds")
-add_caption(table, caption)
+add_caption(table, caption, label = "tab:score-table-4")
 
@@
 add_caption(table, caption)
+
 ```

### 2021-10-13 manuscript/manuscript.tex
fix table references

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{Comparing human and model-based forecasts of COVID-19 in Germany and Poland}
\author{}
\date{\vspace{-2.5em}}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Comparing human and model-based forecasts of COVID-19 in Germany and Poland},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{float}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\emph{Anonymous Alpaca and many friends}

\hypertarget{abstract-max-200-words-no-subheadings}{%
\section{Abstract (max 200 words, no subheadings)}\label{abstract-max-200-words-no-subheadings}}

Model-based forecasts, which have played an important role in shaping public policy throughout the Covid-19 pandemic, represent an implicit combination of model assumptions and the researcher's subjective opinion. This work explicitly separates human opinion and model-derived insights to assess and compare the relative strengths and weaknesses of both approaches. We compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from researchers and volunteers (``crowd forecasts''), against predictions from two semi-mechanistic epidemiological models. In addition, we compared these forecasts against an ensemble of model-based, but expert-tuned, forecasts, submitted to the German and Polish Forecast Hub by other research institutions (``Hub ensemble''). We found an ensemble of crowd-sourced predictions to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble at a two-week horizon: 89\%), but not when predicting deaths (rel. WIS 126\%). Crowd forecasts were severely overconfident (55\% and 75\% coverage of the 95\% prediction intervals for cases and deaths, respectively) when compared to model-based predictions. Performance of the untuned models deteriorated quickly with increasing forecast horizon when assumptions were no longer met (rel. WIS \textgreater{} 164\% for all four week ahead predictions).

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Infectious disease forecasting has a long tradition and has helped inform public health decisions about (among others) influenza {[}CITATION{]}, dengue fever {[}Citation{]}, ebola {[}Citation{]}, chikungunya and now COVID-19 {[}Citation{]}. The aggregation of forecasts of COVID-19 cases, hospitalisations or deaths from multiple teams has created opportunities to compare the predictive performance of different models (CITE e.g UK, US and German/Polish papers). Yet it has been difficult to discern which factors lead to good COVID-19 forecasts. Answering this question is complicated by the varying and generally unobserved degree of manual expert intervention. Model-based forecasts usually represent an implicit combination of human judgement and model-derived insights, in the sense that forecasts have been generated with the help of epidemiological or statistical models, but throughout the process were manually changed and adjusted according to the researchers' judgement.

Previous work has examined human predictions in various contexts, such as geopolitics (Tetlock et al.~2014; Atanasov et al.~2016), meta-science (Cite Replication Markets), and epidemiology (CITE FARROW ET AL, McAndrew et al.~2021, Cite that other paper). Several prediction platforms (Metaculus 2020, Hypermind, Foretell) and prediction markets (cite predictit) have been created to collate expert and non-expert predictions. However, with the notable exception of Farrow et al., these crowd forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats. Farrow et al.~found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available. They tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown there and then.

In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses by comparing human forecasts and model-based predictions.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We created a crowd-sourced forecast (``crowd forecast''), elicited from participants through a web application {[}Citation{]}, as well as two semi-mechanistic models (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology. Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (CITATION). All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (N. Bosse et al.~2020). This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub. Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the Forecast Hub.

\hypertarget{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}{%
\subsection{Forecast targets and interaction with the German and Polish Forecast Hub}\label{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}}

The German and Polish Forecast Hub elicits predictions for various COVID-19 related forecast targets from different research institutions every week. Forecasts had to be made every Monday (with submissions allowed until Tuesday 3pm) using data available until Monday 11.59pm. We submitted forecasts for incident and cumulative weekly reported numbers of cases and deaths from COVID-19 on a national level in Germany and Poland over a one to four week forecast horizon. Weeks were defined as epiweeks starting on Sunday and ending on Saturday, meaning that forecast horizons were in fact 5, 12, 19 and 26 days. Submissions were required in a quantile-based format with 23 quantiles at levels 0.01, 0.025, 0.05, 0.10, 0.15, \ldots, 0.95, 0.975, 0.99. Forecasts submitted to the Forecast Hub were combined to different ensembles every week, with the median ensemble being the default ensemble shown on all official Forecast hub visualisations.

Data on daily reported test positive cases and deaths linked to Covid-19 were provided by the organisers of the German and Polish forecast hub (J. Bracher et al.~2021). Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) (``Download Historical Data (to 14 December 2020) on the Daily Number of New Reported COVID-19 Cases and Deaths Worldwide'' 2020). After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (``RKI - Coronavirus SARS-CoV-2 - Aktueller Lage-/Situationsbericht Des RKI Zu COVID-19'' n.d.). These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November (``Rozbieżności w statystykach koronawirusa. 22 tys. przypadków będą doliczone do ogólnej liczby wyników'' 16:07:56+0100)), changes in reporting over time and variation in testing regimes (e.g.~in Germany from the 11th of November on (Ärzteblatt 2020)).

\hypertarget{crowd-forecasts}{%
\subsection{Crowd forecasts}\label{crowd-forecasts}}

Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application (\url{https://cmmid-lshtm.shinyapps.io/crowd-forecast/}). Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information available until Monday. The application was built using the shiny and golem R packages (Chang et al.~2021; Fay et al.~2021) and is available in the crowdforecastr R package (N. I. Bosse et al.~2020). To make a forecast in the application participants could select a predictive distribution, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values. The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e.~as \texttt{sd(c(log(value4)\ -\ log(value3),\ log(value3)\ -\ log(value2),\ ...))}).
Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from (``COVID-19 Data Explorer'' n.d.). These data included e.g.~notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.

Forecasts were stored in a Google Sheet and downloaded, cleaned and processed every week for submission. If a forecaster had submitted multiple predictions for a single target, only the latest submission was kept. Information on the chosen distribution as well as the parameters for median and width were used to obtain the required set of 23 quantiles from that distribution. Forecasts from all forecasters were then aggregated using an unweighted quantile-wise mean. On a few occasions, individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation.

Participants were recruited mostly within the Centre of Mathematical Modeling of Infectious Diseases at the London School of Hygiene \& Tropical Medicine, but participants were also invited personally or via social media to submit predictions. Depending on whether they had a background in either statistics, forecasting or epidemiology, participants were asked to self-identify as `experts' or `non-experts.'

\hypertarget{model-based-forecasts}{%
\subsection{Model-based forecasts}\label{model-based-forecasts}}

We used two models from the \texttt{EpiNow2} R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, et al.~2020). The first of these models, here called ``renewal model,'' used the renewal equation (Fraser 2007) to predict reported cases and deaths. It estimated the effective reproduction number \(R_t\) (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infections times \(R_t\). \(R_t\) was assumed to stay constant in the future, roughly corresponding to continuing the latest trend in infections. The \(R_t\) value which was carried forward was slightly changed on November 9th 2020, where before that date the last `reliable' \(R_t\) estimate from X days before the forecast was used and after that the latest and most up-to-date (but possibly less stable) \(R_t\) estimate made on the actual forecast date was used. Reported cases and deaths were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, et al.~2020; DOI n.d.; ``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the Covid-19 Outbreak in England \textbar{} medRxiv'' n.d.) to model the time between infection and report date or death. The renewal model was used to predict cases as well as deaths, but the two were forecast completely independently, meaning that \(R_t\) was forecast once from reported cases and once from reported deaths. Death forecasts from the renewal model were therefore not informed by past cases. One submission of the renewal model on December 28th 2020 was belated and therefore not included in the official Forecast hub ensemble.

The second model (``convolution model'') was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses). The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model. The convolution model predicted deaths these as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio). Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model and a multiplicative day-of-the-week effect (Abbott, Hellewell, et al.~2020). Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August. All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fit separately. More details are available in the supplementary information.

\hypertarget{analysis}{%
\subsection{Analysis}\label{analysis}}

For the main analysis we focused on two week ahead predictions, as predictions beyond this horizon are often unreliable due to rapidly changing conditions (J. Bracher et al.~2021). Forecasts for cases were scored using the full period from October 2020 until March 2021. To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available. To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) where scored only over the later period where are forecasts were available (see Section \ref{sensitivity-analysis} in the SI). Results remained broadly unchanged.

Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Johannes Bracher et al.~2021), the absolute error, relative bias, and empirical coverage of the 50\% and 90\% prediction intervals. The WIS is a proper scoring rule (CITE GNEITING) and can be understood as a generalisation of the absolute error to quantile-based forecasts. It can be decomposed into three separate penalties: forecast spread (i.e.~uncertainty of forecasts), over-prediction and under-prediction - lower values are always better. While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts. The bias metric we use captures how much probability mass of the forecast was above or below the true value and therefore represents a general tendency to over- or under-predict in relative terms. It is bound between -1 (all quantiles of the predictive distribution are below the observed value) and 1 (all quantiles are above the observed value). Empirical coverage is the percentage of observed values that fall inside a given prediction interval (e.g.~how many observed values fall inside all 50\% prediction intervals). Scoring metrics are explained in more detail in Table \ref{tab:scoring-metrics} in the SI. All scores were calculated using the \texttt{scoringutils} R package (N. Bosse 2020).

At all stages of the evaluation our forecasts were compared to the median ensemble of all other models submitted to the German and Polish Forecast Hub (``Hub ensemble''). This ``Hub ensemble'' was retrospectively computed and excludes all our models. It therefore differs from the official Hub ensemble (here called ``hub-ensemble-realised'') which included crowd forecasts as well as renewal model forecasts.

The ensemble that we call ``Hub ensemble'' in this paper differs from the

in that we removed our forecasts to allow for a more straightforward comparison. To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e.~we divided all scores by those achieved by the Hub ensemble on the same set of forecasts. In addition to comparing our forecasts against the hub ensemble excluding our models, we also assessed the impact of our forecasts on the performance of the forecasting hub by recalculating separate versions of the Hub ensemble with only some (or all) of our forecasts included.

Versions that included either all of our models (``hub-ensemble-with-all'') or only one of them (``hub-ensemble-with-X'') were computed retrospectively.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{crowd-forecast-participation}{%
\subsection{Crowd forecast participation}\label{crowd-forecast-participation}}

A total number of 32 participants submitted forecasts, 17 of those self-identified as `expert.' The median number of forecasters for any given forecast target was 6, the minimum 2 and the maximum 10. The mean number of submissions from an individual forecaster was 4.7 but the median number was only one - most participants dropped out after their first submission. Only two participants submitted a forecast every single week, both of whom are authors on this study.

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons. A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components dispersion, over-prediction and under-prediction. C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect). D: Empirical coverage of the 90\% prediction intervals. E: Dispersion (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all}
\end{figure}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} \caption{A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the true observed values. Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out. B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth}
\end{figure}

\hypertarget{case-forecasts}{%
\subsection{Case Forecasts}\label{case-forecasts}}

For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \ref{fig:agg-performance-all}A) and locations (Figure \ref{fig:performance-locations-rel}A). For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 100\%) was 89\% for crowd forecasts and 140\% for the renewal model (Table \ref{tab:score-table-2}). Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was right-skewed, and average performance was heavily influenced by outliers (Figure \ref{fig:distribution-scores}). Overall, low variance in forecast performance was closely linked with good mean performance (Figures \ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance. The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \ref{fig:distribution-scores}, as well as the highest standard deviation of WIS values (relative WIS sd 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.

To varying degrees, all models exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened. For example, all models failed to predict the change in trend from increase to decrease that happened in early November\ldots{} in Germany and severely overshot (Figure \ref{fig:forecasts-and-truth}A). This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past of observations. The Hub ensemble and the crowd forecast, which had both been under-predicting throughout October, also failed to predict the change in trend after cases peaked, but less severely so. Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 (Deutsche Welle (www.dw.com) n.d.) and the change in the testing regime (with stricter test criteria) on November 11th 2020 (Ärzteblatt 2020), were fastest to adapt to the new trend, and the Hub ensemble slowest. In December, cases rose again in Germany, with all models under-predicting this growth to varying extents. As in October, the renewal model captured the phase of exponential growth in cases slightly better than other approaches, but again overshot when reported case numbers fell over Christmas. The large variance in predictions in January in Germany (severe under-prediction followed by severe over-prediction) may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting. Similar trends in performance were evident in Poland, with the crowd forecast quickest at adapting to the change in trend in November. In general, there were fewer large outlier forecasts in Poland and in particular the renewal model performed more in line with other forecasts there.

All forecasting approaches, including the Hub ensemble, were overconfident and showed lower than nominal coverage (meaning that 50\% (90\%) prediction intervals generally covered less than 50\% (90\%) of the actually observed values) (Figure \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D). Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts. This was especially an issue for crowd forecasts, which were markedly sharper (i.e., narrower) than other approaches (Figure \ref{fig:agg-performance-all}E) and only showed a small increase in uncertainty across forecast horizons. In spite of good performance in terms of the absolute error (Figure \ref{fig:agg-performance-all}G), excessive sharpness led to forecasts which were severely overconfident (covering only 36\% and 55\% of observations with their 50\% and 90\% prediction intervals at a two week horizon, and only 5\% and 38\% four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}). Despite worse performance in terms of absolute error (Figure \ref{fig:agg-performance-all}G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly and non-linearly across forecast horizons.

The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons. The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \ref{fig:agg-performance-all}F). Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}), implying that over-prediction (e.g.~when missing a peak) tended to be more costly in terms of the WIS.

Generally, trends in overall performance were broadly similar across locations (Figures \ref{fig:performance-locations} and \ref{fig:performance-locations-rel}).
Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly. However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figure \ref{fig:performance-locations-rel}A and \ref{fig:performance-locations-rel}G).

\hypertarget{death-forecasts}{%
\subsection{Death Forecasts}\label{death-forecasts}}

For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure \ref{fig:agg-performance-all}B, Figure \ref{fig:performance-locations}B). Relative WIS values for the models two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1 (Hub ensemble) and 1.79 (renewal model). The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \ref{fig:agg-performance-all}B, Figure \ref{fig:performance-locations}B), and also better than the convolution model three and four weeks ahead. Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate \(R_t\) trace from deaths, is not well suited for the task. The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \ref{fig:agg-performance-all}B, Table \ref{tab:score-table-4}).

Theoretical considerations suggest that predicting a change in trend may be easier for deaths than for cases (as past cases, hospitalisations and other data can be used as predictors). Even though all forecasts generally struggled with this, there were some instances where changing trends were well captured or even anticipated. In Poland, for example, the Hub ensemble was able to capture or even anticipate the peak in deaths in December quite well (whereas the renewal model and crowd forecast did not). The renewal model, which mostly exhibited trend-following behaviour, correctly predicted another increase in weekly deaths in mid-January (potentially based on changes in daily deaths, as the renewal model did not know about past cases). In Germany in early January, all models predicted a decrease in deaths two to three weeks before it actually happened. Predictions from the renewal model at that time were likely strongly influenced by an unexpected drop in reported deaths on December XXth. The other forecasting approaches and in particular, the convolution model may have been affected by potentially under-reported case numbers around Christmas. When the decrease that all models had predicted to happen in early January failed to materialise, the renewal model and the crowd forecast noticeably over-corrected and over-predicted deaths in the following weeks, while the Hub ensemble, and to a slightly lesser degree, the convolution model were able to capture the downturn well when it finally happened at the end of January.

Death forecasts, generally, showed greater coverage of the 50\% and 90\% prediction intervals than case forecasts and no decrease in coverage across forecast horizons, indicating that it might be easier to appropriately quantify uncertainty for death forecasts. The Hub ensemble had the greatest coverage, with empirical coverage of the 50\% and 90\% prediction intervals exceeding 50\%, and 90\%, respectively, across all forecast horizons. Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D). As for cases, the crowd forecast tended to be the sharpest and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest. The convolution model was relatively sharp for short forecast horizons, but had rapidly (and non-linearly) increasing uncertainty for longer forecast horizons, driven by increasing uncertainty in the underlying case forecasts.

For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \ref{fig:agg-performance-all}F. The convolution model had a strong tendency to under-predict, which steadily decreased for longer forecast horizons. The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction. For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \ref{fig:agg-performance-all}A, \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2}, \ref{tab:score-table-4}).

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} \caption{A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country.}\label{fig:distribution-scores}
\end{figure}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble. “Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included. Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions. For Coverage, this is an absolute difference, for other metrics this is a percentage difference. A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Dispersion (higher values mean greater spread of the forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\% prediction intervals. F: Empirical coverage of the 90\% prediction intervals}\label{fig:agg-performance-ensemble}
\end{figure}

\hypertarget{contribution-to-the-forecast-hub}{%
\subsection{Contribution to the Forecast Hub}\label{contribution-to-the-forecast-hub}}

Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (``hub-ensemble-realised''), while the convolution model was never included as it was deemed too similar to the existing renewal model, thus potentially introducing bias. In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on December 28 2020 over the Christmas period) and a maximum of 10. Versions that included either all of our models (``hub-ensemble-with-all'') or only one of them (``hub-ensemble-with-X'') were computed retrospectively. An overview of all models and ensemble versions is shown in Table \ref{tab:table-ensemble-versions} in the SI.

For cases, our contributions (compared to the Hub ensemble without our contributions) consistently improved performance across all forecasting horizons (rel. WIS 0.9 two weeks ahead, Table \ref{tab:score-table-ensemble-2}). Contributions from the crowd forecasts alone also were positive across all forecast horizons, while contributions from the renewal model became negative for longer horizons (rel. WIS 1.02 three weeks ahead, 1.06 four weeks ahead). The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects. Only for four week ahead predictions would removing the renewal model have improved performance (Table \ref{tab:score-table-ensemble-4}).

For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel. WIS of the hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and \ref{tab:score-table-ensemble-4}). Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons). This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \ref{fig:agg-performance-all}) and especially worse for longer horizons.

We also considered the impact of our contributions on the mean, rather than the median ensemble.
General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \ref{fig:agg-performance-ensemble}B and \ref{fig:agg-performance-ensemble-mean}B). This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far. For both the mean and the median ensemble, changes in performance from adding or removing models were of a similar order of magnitude, suggesting that at least in this instance, with a relatively small ensemble size, the median ensemble was not necessarily more `robust' to changes than the mean ensemble. However, the ensemble version with all our forecasts included (``hub-ensemble-with-all'') tended to perform relatively better for the median ensemble than the mean ensemble, suggesting that adding more models may be more beneficial or `safer' for the median than for the mean ensemble as directional errors can more easily cancel out than errors in absolute terms.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Epidemiological forecasting usually represents a mix between human insight and model-based assumptions. In this study, we compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from a crowd of researchers and volunteers against predictions from two semi-mechanistic epidemiological models. In spite of the small number of participants and a general tendency to be overconfident, crowd forecasts consistently outperformed our epidemiological models as well as the Hub ensemble when forecasting cases but not when forecasting deaths. This suggests that humans are relatively good at foreseeing trends that are hard to model but may struggle to form an intuition for the exact relationship between cases and deaths.

Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts. However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (Cite US Hub, cite Seb SPI-M), or exclusively on human forecasts (e.g.~cite Tetlock, cite Grecchia, cite McAndrew). In contrast, we directly compared human and model-based forecasts. This is similar to the approach taken by Farrow et al., but extends it in several ways. While Farrow et al.~only asked for point predictions and constructed a probabilistic forecast from these, we asked participants to quantify their uncertainty directly, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse aspects of the forecasts like overconfidence. In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight. In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (J. Bracher et al.~2021; E. Y. Cramer et al.~2021; S. Funk et al.~2020).

The good performance of crowd forecasts we found is in line with results from Farrow et al.~who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants. The advantage of crowd forecasts we observed over our semi-mechanistic models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models. However, this probably explains only part of the difference and performance relative to the Hub ensemble strongly suggests that human insight is valuable when predicting highly volatile and hard-to-predict quantities such as case numbers. Relatively good performance of our semi-mechanistic models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time. This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data). The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \ref{fig:forecasts-and-truth}A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting. While we were not able to observe how expert opinion informed other models submitted to the Forecast Hub, conversations with the Hub organisers suggest that forecasts tended to benefit from a large degree of human intervention. Unfortunately, we were not able to test a scenario in which users were asked to alter an existing model output. We can therefore make no conclusive statements about the direct effects of researchers tuning their models, rather than create a new forecast from a naive baseline.

Conversely, our results suggest that human intervention may be less beneficial when forecasting deaths (especially at shorter horizons, when deaths are largely dependent on already observed cases), which benefits from the ability to model the delays and exact epidemiological relationships between different leading and lagged indicators. Relatively good performance of the convolution model, especially compared to the poor performance of the renewal model on deaths (which used only deaths to estimate and predict the effective reproduction number) underlines the importance of including leading indicators such as cases as a predictor for deaths.

Given the low number of participants in our study, it is difficult to generalise conclusions about crowd predictions to other settings. In particular, our crowd forecasting application was not developed to a high standard of user friendliness. This may have precluded interested parties from submitting forecasts. The low number of participants presumably resulted in higher variance of forecasts, but also potentially in better average forecast performance. Motivating forecasters to contribute regularly proved challenging, especially given that the majority of our participants were from the UK and had little connection to Germany and even less to Poland. In addition, lack of effective outreach played an important role, as did a lack of time and resources to design the interface in a way that is appealing enough to attract large audiences outside of academia. Using an R shiny app as an interface arguably created some limits to user experience and performance, influencing the number of participants. On the other hand, it facilitated quick development and allows us to provide our crowd forecasting tooling as an open source R package, meaning that it is available for others to use, and to further develop, in their context.

In general, our results support the use of ensembles, rather than individual models to inform public health policies, as these provide consistently good performance and largely avoid particularly bad outlier forecasts. Our results also suggest that at least for a small median ensemble like the German and Polish Forecast Hub ensemble adding more models may increase performance in most instances (with the version of the hub ensemble that includes all our contributions (``hub-ensemble-with-all'') outperforming the realised official hub ensemble in almost all instances). We often found contributions to an ensemble to be beneficial even in instances where the forecasting approach entering the ensemble performed consistently worse than the pre-existing ensemble. Including more models may be easier when using a median ensemble, as extreme forecasts tend to have less of an influence there. Individual models, however, can still have a place in informing public policy. As an average, ensembles show the consensus opinion, which implies that in contrast to single models, they are not likely to reveal information, e.g.~about future changes in trend, that is not in some way `obvious' to the majority of forecasters.

In the context of evaluating different models and the merits of human intervention, what constitutes a `good' forecast very much depends on the purpose of that forecast. Policymakers may care much more about certain types of errors, (e.g.~under-prediction) than others in a way not captured by the weighted interval score. Also, it is helpful to distinguish between `forecasts' and `projections.' For example, the outperformance of the crowd forecasts on cases and in general on longer forecast horizons is perhaps not surprising, given that humans could factor in an expectation of future changes in conditions (e.g.~future policy interventions, adherence to these interventions, testing policy, and the evolution of new disease variants) while our model-based forecasts could not. However, if the aim of a forecast is to inform policy and decision making, then attempting to factor in the interventions one is meant to inform may be problematic (and conversely, arguing for or against interventions based on predictions may be difficult depending on what the forecast assumes about future interventions). In that sense, crowd forecasts can be understood as forecasts, whereas our model predictions may be better understood as projections that show what would happen in the absence of any events that could change the trend. This may pose a problem in the context of a forecast hub if teams have a different understanding about the purpose of a forecast. Projections that are meant to inform policy makers about possible scenarios may be different from forecasts meant to inform the general public, and yet again different from forecasts submitted with the goal of advancing open research and in order to allow public scrutiny and discussion about the merits of different approaches.\\
Further work should explore the effects of human intervention on model-based forecasts in more detail. Model-based forecasts could be used as an input to human judgement, with researchers adjusting predictions generated by models. Seeing a model-based forecasts could help humans calibrate uncertainty better, while allowing for manual intervention to adapt spurious trend predictions. Tools need to be developed to facilitate this process at a larger scale. Human insight could also be used as an input to models. Such a `hybrid' forecasting approach could for example ask humans to predict the trend of the effective reproduction number \(R_t\) or the doubling rate (i.e.~how the epidemic evolves) into the future and use this to estimate the exact number of cases, hospitalisations or deaths this would imply. This approach seems especially promising for forecasting deaths if a model can accurately describe delay distributions and epidemiological relationships between different parameters. In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust and widen confidence intervals may be another promising approach. Crowd forecasting in general could benefit greatly from the availability of tools suitable to appeal to a greater audience. Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile for researchers and policymakers to further develop and explore.

\hypertarget{appendix-supplementary-information}{%
\appendix}

\hypertarget{supplementary-information}{%
\section{Supplementary information}\label{supplementary-information}}

\hypertarget{scoring-metrics-used}{%
\subsection{Scoring metrics used}\label{scoring-metrics-used}}

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{13.0cm}}
\caption{\label{tab:scoring-metrics}Overview of the scoring metrics used.}\\
\toprule
Metric & Explanation\\
\midrule
\endfirsthead
\caption[]{\label{tab:scoring-metrics}Overview of the scoring metrics used. \textit{(continued)}}\\
\toprule
Metric & Explanation\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
WIS (Weighted) interval score & The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts. It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals. The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction. For a single interval, the score is computed as 
  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e. the lower and upper bound of a single prediction interval. For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum, 
  $$WIS = \frac{1}{K + 0.5} \cdot (w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y)),$$ 
  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.

\cellcolor{gray!6}{Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.}\\
\addlinespace \addlinespace
Interval coverage & Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range. Nominal coverage represents the percentage of observed values that should ideally be covered (e.g. we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.\\
\addlinespace \addlinespace
Bias & (Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict. Values are between -1 and 1 and 0 ideally. For continuous forecasts, bias is given as 
$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
where $F$ is the CDF of the predictive distribution and $y$ is the observed value.

For quantile forecasts, $F(y)$ is replaced by a quantile rank. The appropriate quantile rank is determined by whether the median forecast is below  or above the true value. We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.

\cellcolor{gray!6}{In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction. It is therefore a more robust measurement.}\\*
\end{longtable}

\clearpage

\hypertarget{further-details-on-the-semi-mechanistic-forecasting-models}{%
\subsection{Further details on the semi-mechanistic forecasting models}\label{further-details-on-the-semi-mechanistic-forecasting-models}}

\hypertarget{renewal-equation-model}{%
\subsubsection{Renewal equation model}\label{renewal-equation-model}}

The model was initialised prior to the first observed data point by assuming constant exponential growth for the mean of assumed delays from infection to case report.

\begin{align}
  I_{t} &= I_0 \exp  \left(r t \right)  \\
  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
\end{align}

Where \(I_{obs}\) and \(r_{obs}\) are estimated form the first week of observed data. For the time window of the observed data infections were then modelled by weighting previous infections by the generation time and scaling by the instantaneous reproduction number. These infections were then convolved to cases by date (\(O_t\)) and cases by date of report (\(D_t\)) using log-normal delay distributions. This model can be defined mathematically as follows,

\begin{align}
  \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
  I_t &= R_t \sum_{\tau = 1}^{15} w(\tau | \mu_{w}, \sigma_{w}) I_{t - \tau} \\
  O_t &= \sum_{\tau = 0}^{15} \xi_{O}(\tau | \mu_{\xi_{O}}, \sigma_{\xi_{O}}) I_{t-\tau} \\
  D_t &= \alpha \sum_{\tau = 0}^{15} \xi_{D}(\tau | \mu_{\xi_{D}}, \sigma_{\xi_{D}}) O_{t-\tau} \\ 
  C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
\end{align}

Where,
\begin{align}
     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
\end{align}

This model used the following priors for cases,

\begin{align}
     R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
    \mu_w &\sim \mathcal{N}(3.6, 0.7) \\
    \sigma_w &\sim \mathcal{N}(3.1, 0.8) \\
    \mu_{\xi_{O}} &\sim \mathcal{N}(1.62, 0.064) \\
    \sigma_{\xi_{O}} &\sim \mathcal{N}(0.418, 0.069) \\
    \mu_{\xi_{D}} &\sim \mathcal{N}(0.614, 0.066) \\
    \sigma_{\xi_{D}} &\sim \mathcal{N}(1.51, 0.048) \\
    \alpha &\sim \mathcal{N}(0.25, 0.05) \\
    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
    \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
\end{align}

and updated the reporting process as follows when forecasting deaths,

\begin{align}
    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
\end{align}

\(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) were truncated to be greater than 0 and with \(\xi\), and \(w\) normalised to sum to 1.

The prior for the generation time was sourced from (Ganyani et al. 2020) but refit using a log-normal incubation period with a mean of 5.2 days (SD 1.1) and SD of 1.52 days (SD 1.1) with this incubation period also being used as a prior (Lauer et al. 2020) for \(\xi_{O}\). This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates. We estimated the delay between symyptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1\% or 1769 samples of the available data (Xu et al., n.d.; Abbott, Sherratt, et al. 2020) and combining the posteriors for the mean and standard deviation of the log-normal distribution (Abbott, Hellewell, et al. 2020; DOI n.d.; {``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid}-19 Outbreak in {England} \textbar{} {medRxiv}''} n.d.; Stan Development Team 2020).

\(GP_t\) is an approximate Hilbert space Gaussian process as defined in (Riutort-Mayol et al. 2020) using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20\% of the number of days used in fitting). The lengthscale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days. The magnitude of the Gaussian process was assumed be normally distributed centred at 0 with a standard deviation of 0.1.

From the forecast time horizon (\(T\)) and onwards the last value of the Gaussian process was used (hence \(R_t\) was assumed to be fixed) and latent infections were adjusted to account for the proportion of the population that was susceptible to infection as follows,

\begin{equation}
    I_t = (N - I^c_{t-1}) \left(1 - \exp \left(\frac{-I'_t}{N - I^c_{T}}\right)\right),
\end{equation}

where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\) and \(I'_t\) are the unadjusted infections defined above. This adjustment is based on that implemented in the \texttt{epidemia} R package (Scott et al. (2020), cite (\textbf{bhatt202?})).

\hypertarget{convolution-model}{%
\paragraph{Convolution model}\label{convolution-model}}

The convolution model shares the same observation model as the renewal model but rather than assuming that an observation is predicted by itself instead assumes that it is predicted entirely by another observation after some parametric delay. It can be defined mathematically as follows,

\begin{equation} 
    D_{t} \sim \mathrm{NB}\left(\omega_{(t \mod 7)} \alpha \sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) C_{t-\tau},  \phi \right)
\end{equation}

with the following priors,

\begin{align}
    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
    \alpha &\sim \mathcal{N}(0.01, 0.02) \\
    \xi &\sim \mathcal{LN}(\mu, \sigma) \\
    \mu &\sim \mathcal{N}(2.5, 0.5) \\
\sigma &\sim \mathcal{N}(0.47, 0.2) \\
\phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
\end{align}

with \(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) truncated to be greater than 0 and with \(\xi\) normalised such that \(\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1\).

\hypertarget{model-fitting}{%
\subsubsection{Model fitting}\label{model-fitting}}

Both models were implemented using the \texttt{EpiNow2} R package (version 1.3.3) (Abbott, Hellewell, et al. 2020). Each forecast target was fit independently for each model using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020). A minimum of 4 chains were used with a warmup of 250 samples for the renewal equation-based model and 1000 samples for the convolution model. 2000 samples total post warmup were used for the renewal equation model and 4000 samples for the convolution model. Different settings were chosen for each model to optimise compute time contigent on convergence. Convergence was assessed using the R hat diagnostic (Stan Development Team 2020). For the convolution model forecast the case forecast from the renewal equation model was used in place of observed cases beyond the forecast horizon using 1000 posterior samples. 12 weeks of data was used for both models though only 3 weeks of data were included in the likelihood for the convolution model.

\clearpage

\hypertarget{tables-with-results-of-the-forecast-evaluation}{%
\subsection{Tables with results of the forecast evaluation}\label{tables-with-results-of-the-forecast-evaluation}}

\begin{table}[!h]
\caption{\label{tab:score-table-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded). Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets. Numbers in brackets show the metrics relative to the Hub ensemble (i.e. the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions). WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model. Dispersion, over-prediction and under-prediction together sum up to the weighted interval score. Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict. 50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}

\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{>{}llccccccccc}
\toprule
  & Model & WIS & WIS - sd & Dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
\midrule
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Cases}}\\
\hline
\cellcolor{white}{} & Crowd forecast & 7010 (0.8) & 7480 (0.64) & 2680 (0.73) & 1700 (1.38) & 2630 (0.68) & -0.01 & 10400 (0.82) & 0.55 & 0.79\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 8740 (1) & 11800 (1.01) & 2190 (0.6) & 2720 (2.21) & 3830 (0.99) & 0.18 & 12000 (0.94) & 0.48 & 0.71\\
\cmidrule{1-11}
\cellcolor{white}{} & Crowd forecast & 16200 (0.89) & 16600 (0.76) & 3660 (0.6) & 5930 (1.56) & 6600 (0.78) & -0.01 & 23300 (0.87) & 0.36 & 0.55\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25600 (1.4) & 33800 (1.54) & 5420 (0.88) & 5920 (1.56) & 14200 (1.69) & 0.17 & 34600 (1.29) & 0.43 & 0.67\\
\cmidrule{1-11}
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Deaths}}\\
\hline
\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
\cmidrule{2-11}
\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
\cmidrule{1-11}
\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
\cmidrule{2-11}
\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}[!h]
\caption{\label{tab:score-table-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded). Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets. Numbers in brackets show the metrics relative to the Hub ensemble (i.e. the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions). WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model. Dispersion, over-prediction and under-prediction together sum up to the weighted interval score. Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict. 50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}

\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{>{}llccccccccc}
\toprule
  & Model & WIS & WIS - sd & Dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
\midrule
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Cases}}\\
\hline
\cellcolor{white}{} & Crowd forecast & 27000 (0.81) & 26200 (0.64) & 4750 (0.52) & 11000 (1.43) & 11200 (0.67) & 0.02 & 39000 (0.83) & 0.14 & 0.48\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 50600 (1.51) & 70000 (1.72) & 10800 (1.18) & 7710 (1) & 32100 (1.93) & 0.13 & 68700 (1.46) & 0.29 & 0.55\\
\cmidrule{1-11}
\cellcolor{white}{} & Crowd forecast & 39200 (0.7) & 38600 (0.52) & 5970 (0.49) & 15600 (1.26) & 17600 (0.56) & 0.07 & 54800 (0.74) & 0.05 & 0.38\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 91700 (1.64) & 135000 (1.83) & 19500 (1.6) & 8990 (0.72) & 63200 (2.02) & 0.09 & 125000 (1.68) & 0.31 & 0.48\\
\cmidrule{1-11}
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Deaths}}\\
\hline
\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
\cmidrule{2-11}
\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
\cmidrule{1-11}
\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
\cmidrule{2-11}
\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
\bottomrule
\end{tabular}}
\end{table}

\clearpage

\hypertarget{aggregate-performance-by-location}{%
\subsection{Aggregate performance by location}\label{aggregate-performance-by-location}}

\hypertarget{performance-across-locations-in-absolute-terms}{%
\subsubsection{Performance across locations in absolute terms}\label{performance-across-locations-in-absolute-terms}}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-4} \caption{Visualisation of aggregate performance metrics across locations. A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Sharpness (higher values mean greater dispersion of the forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\% prediction intervals. F: Empirical coverage of the 90\% prediction intervals.}\label{fig:performance-locations}
\end{figure}

\hypertarget{performance-across-locations-in-relative-terms}{%
\subsection{Performance across locations in relative terms}\label{performance-across-locations-in-relative-terms}}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4} \caption{ Visualisation of aggregate performance metrics across locations relative to the Hub ensemble (excluding our contributions). A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Sharpness (higher values mean greater dispersion of the forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\% prediction intervals. F: Empirical coverage of the 90\% prediction intervals.}\label{fig:performance-locations-rel}
\end{figure}

\clearpage

\hypertarget{visualisation-of-daily-reported-cases-and-deaths}{%
\subsection{Visualisation of daily reported cases and deaths}\label{visualisation-of-daily-reported-cases-and-deaths}}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/daily_truth} \caption{Visualisation of daily report data. The black line represents weekly data divided by seven. Data were last accessed through the German and Polish Forecast Hub on August 21 2021.}\label{fig:daily-truth}
\end{figure}

\clearpage

\hypertarget{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}{%
\subsection{Visualisation of scores and forecasts 1, 3, 4 weeks ahead}\label{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} \caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the true observed values. Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out. B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-1}
\end{figure}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} \caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the true observed values. Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out. B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-3}
\end{figure}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} \caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the true observed values. Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out. B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-4}
\end{figure}

\clearpage

\hypertarget{distribution-of-scores}{%
\subsection{Distribution of scores}\label{distribution-of-scores}}

\hypertarget{absolute-scores}{%
\subsubsection{Absolute scores}\label{absolute-scores}}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1} \caption{A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country.}\label{fig:distribution-scores-1}
\end{figure}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3} \caption{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country.}\label{fig:distribution-scores-3}
\end{figure}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4} \caption{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country.}\label{fig:distribution-scores-4}
\end{figure}

\hypertarget{ranks-achieved-by-forecasts}{%
\subsubsection{Ranks achieved by forecasts}\label{ranks-achieved-by-forecasts}}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets. B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-1}
\end{figure}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets. B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-2}
\end{figure}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets. B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-3}
\end{figure}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets. B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-4}
\end{figure}

\clearpage

\hypertarget{comparison-of-ensembles}{%
\subsection{Comparison of ensembles}\label{comparison-of-ensembles}}

\hypertarget{performance-visualisation-mean-ensemble}{%
\subsubsection{Performance visualisation mean ensemble}\label{performance-visualisation-mean-ensemble}}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble. “Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included. Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions. For Coverage, this is an absolute difference, for other metrics this is a percentage difference. A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Dispersion (higher values mean greater spread of the forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\% prediction intervals. F: Empirical coverage of the 90\% prediction intervals}\label{fig:agg-performance-ensemble-mean}
\end{figure}

\hypertarget{tables-median-ensemble}{%
\subsubsection{Tables median ensemble}\label{tables-median-ensemble}}

\begin{table}[!h]
\caption{\label{tab:score-table-ensemble-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble. Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets. Numbers in brackets show the metrics relative to the Hub ensemble (i.e. the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions). WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model. Dispersion, over-prediction and under-prediction together sum up to the weighted interval score. Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict. 50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}

\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{>{}llccccccccc}
\toprule
  & Model & WIS & WIS - sd & Dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
\midrule
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Cases}}\\
\hline
\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised & 6970 (0.79) & 8260 (0.71) & 3060 (0.83) & 943 (0.77) & 2970 (0.77) & 0.04 & 10800 (0.85) & 0.55 & 0.83\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd & 7820 (0.89) & 9630 (0.82) & 3270 (0.89) & 1210 (0.98) & 3330 (0.86) & -0.02 & 12000 (0.94) & 0.48 & 0.81\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 7960 (0.91) & 10300 (0.88) & 3190 (0.87) & 1020 (0.83) & 3760 (0.97) & 0.04 & 12100 (0.95) & 0.57 & 0.83\\
\cmidrule{1-11}
\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised & 16400 (0.9) & 19600 (0.89) & 5350 (0.87) & 3290 (0.87) & 7730 (0.92) & 0.02 & 24200 (0.9) & 0.43 & 0.69\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd & 16900 (0.92) & 19600 (0.89) & 5230 (0.85) & 4310 (1.13) & 7370 (0.88) & 0.00 & 24600 (0.92) & 0.38 & 0.64\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 17500 (0.96) & 21400 (0.98) & 5830 (0.95) & 2880 (0.76) & 8770 (1.04) & 0.00 & 25500 (0.95) & 0.45 & 0.71\\
\cmidrule{1-11}
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Deaths}}\\
\hline
\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised & 235 (0.95) & 332 (0.98) & 88.6 (0.96) & 90.4 (0.79) & 55.5 (1.33) & -0.01 & 323 (0.97) & 0.62 & 0.88\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-all & 234 (0.94) & 331 (0.98) & 85.2 (0.92) & 98.1 (0.85) & 50.2 (1.21) & -0.05 & 329 (0.99) & 0.62 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-convolution & 234 (0.94) & 329 (0.97) & 90.7 (0.98) & 118 (1.03) & 25.3 (0.61) & -0.08 & 333 (1) & 0.62 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd & 239 (0.96) & 337 (1) & 85.2 (0.92) & 99.6 (0.87) & 54.2 (1.3) & -0.03 & 322 (0.96) & 0.62 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 246 (0.99) & 342 (1.01) & 91.5 (0.99) & 106 (0.92) & 48.6 (1.17) & -0.06 & 342 (1.02) & 0.67 & 0.92\\
\cmidrule{1-11}
\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised & 296 (1.01) & 398 (1.03) & 125 (0.95) & 91 (0.84) & 80.2 (1.55) & 0.05 & 486 (1.13) & 0.58 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-all & 303 (1.04) & 423 (1.1) & 115 (0.87) & 122 (1.13) & 66.1 (1.27) & 0.00 & 483 (1.13) & 0.62 & 0.88\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-convolution & 270 (0.92) & 385 (1) & 121 (0.92) & 119 (1.1) & 29.9 (0.58) & -0.04 & 403 (0.94) & 0.58 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd & 303 (1.04) & 392 (1.02) & 122 (0.92) & 106 (0.98) & 74.6 (1.44) & 0.03 & 499 (1.16) & 0.58 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 296 (1.01) & 397 (1.03) & 128 (0.97) & 97.1 (0.9) & 71.2 (1.37) & -0.01 & 462 (1.08) & 0.67 & 0.92\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}[!h]
\caption{\label{tab:score-table-ensemble-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble. Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets. Numbers in brackets show the metrics relative to the Hub ensemble (i.e. the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions). WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model. Dispersion, over-prediction and under-prediction together sum up to the weighted interval score. Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict. 50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}

\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{>{}llccccccccc}
\toprule
  & Model & WIS & WIS - sd & Dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
\midrule
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Cases}}\\
\hline
\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised & 30800 (0.92) & 38600 (0.95) & 7910 (0.87) & 6890 (0.9) & 16000 (0.96) & 0.03 & 44200 (0.94) & 0.29 & 0.62\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd & 30800 (0.92) & 34100 (0.84) & 7500 (0.82) & 8960 (1.17) & 14300 (0.86) & 0.02 & 44100 (0.94) & 0.24 & 0.55\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 34000 (1.02) & 43100 (1.06) & 8860 (0.97) & 6300 (0.82) & 18900 (1.14) & 0.02 & 48100 (1.03) & 0.29 & 0.60\\
\cmidrule{1-11}
\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised & 51200 (0.92) & 69900 (0.95) & 10900 (0.89) & 11100 (0.9) & 29300 (0.94) & 0.04 & 69600 (0.94) & 0.19 & 0.57\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd & 48800 (0.87) & 58600 (0.8) & 9700 (0.8) & 13700 (1.1) & 25400 (0.81) & 0.00 & 65800 (0.88) & 0.19 & 0.48\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 59100 (1.06) & 84100 (1.14) & 12600 (1.03) & 10100 (0.81) & 36400 (1.16) & 0.01 & 78900 (1.06) & 0.29 & 0.55\\
\cmidrule{1-11}
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Deaths}}\\
\hline
\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised & 332 (1.04) & 388 (1.18) & 158 (0.92) & 78.7 (0.85) & 95 (1.72) & -0.02 & 547 (1.12) & 0.46 & 1.00\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-all & 321 (1.01) & 385 (1.17) & 153 (0.89) & 100 (1.08) & 68.1 (1.24) & -0.01 & 535 (1.1) & 0.54 & 1.00\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-convolution & 298 (0.93) & 337 (1.03) & 155 (0.9) & 106 (1.14) & 37.5 (0.68) & -0.04 & 441 (0.9) & 0.67 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd & 319 (1) & 342 (1.04) & 160 (0.93) & 85.1 (0.92) & 73.6 (1.34) & -0.02 & 547 (1.12) & 0.54 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 332 (1.04) & 363 (1.11) & 168 (0.98) & 86.1 (0.93) & 78.2 (1.42) & -0.02 & 528 (1.08) & 0.58 & 0.96\\
\cmidrule{1-11}
\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised & 445 (1.05) & 532 (1.2) & 193 (0.91) & 107 (0.85) & 144 (1.68) & -0.03 & 700 (1.04) & 0.54 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-all & 399 (0.94) & 438 (0.99) & 195 (0.92) & 105 (0.83) & 97.9 (1.14) & -0.05 & 692 (1.03) & 0.46 & 1.00\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-convolution & 384 (0.91) & 387 (0.87) & 196 (0.92) & 122 (0.97) & 65.9 (0.77) & -0.06 & 602 (0.89) & 0.54 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd & 407 (0.96) & 456 (1.03) & 202 (0.95) & 105 (0.83) & 101 (1.18) & -0.03 & 669 (0.99) & 0.67 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 457 (1.08) & 527 (1.19) & 208 (0.98) & 129 (1.02) & 121 (1.41) & -0.06 & 744 (1.1) & 0.50 & 0.96\\
\bottomrule
\end{tabular}}
\end{table}

\hypertarget{tables-mean-ensemble}{%
\subsubsection{Tables mean ensemble}\label{tables-mean-ensemble}}

\begin{table}[!h]
\caption{\label{tab:score-table-ensemble-mean-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble. Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets. Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e. the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions). WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model. Dispersion, over-prediction and under-prediction together sum up to the weighted interval score. Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict. 50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}

\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{>{}llccccccccc}
\toprule
  & Model & WIS & WIS - sd & Dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
\midrule
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Cases}}\\
\hline
\cellcolor{white}{} & Hub-ensemble-mean & 8680 (1) & 10300 (1) & 3700 (1) & 1460 (1) & 3520 (1) & -0.02 & 13400 (1) & 0.50 & 0.86\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised-mean & 7600 (0.88) & 8770 (0.85) & 3360 (0.91) & 1090 (0.75) & 3140 (0.89) & 0.01 & 11900 (0.89) & 0.52 & 0.90\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 8050 (0.93) & 9070 (0.88) & 3520 (0.95) & 1410 (0.97) & 3120 (0.89) & -0.02 & 12600 (0.94) & 0.48 & 0.88\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 8090 (0.93) & 9780 (0.95) & 3490 (0.94) & 1110 (0.76) & 3490 (0.99) & 0.02 & 12700 (0.95) & 0.57 & 0.88\\
\cmidrule{1-11}
\cellcolor{white}{} & Hub-ensemble-mean & 19000 (1) & 22100 (1) & 5960 (1) & 3690 (1) & 9340 (1) & 0.02 & 28800 (1) & 0.33 & 0.79\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised-mean & 17100 (0.9) & 20600 (0.93) & 5550 (0.93) & 2850 (0.77) & 8660 (0.93) & 0.05 & 26000 (0.9) & 0.38 & 0.76\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 17600 (0.93) & 20000 (0.9) & 5540 (0.93) & 3790 (1.03) & 8230 (0.88) & 0.01 & 26800 (0.93) & 0.36 & 0.76\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 18300 (0.96) & 22600 (1.02) & 5910 (0.99) & 2640 (0.72) & 9720 (1.04) & 0.06 & 27700 (0.96) & 0.38 & 0.76\\
\cmidrule{1-11}
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Deaths}}\\
\hline
\cellcolor{white}{} & Hub-ensemble-mean & 229 (1) & 292 (1) & 101 (1) & 90.4 (1) & 36.7 (1) & -0.07 & 315 (1) & 0.71 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised-mean & 219 (0.96) & 289 (0.99) & 96.8 (0.96) & 79.8 (0.88) & 42.6 (1.16) & -0.04 & 297 (0.94) & 0.71 & 0.88\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-all-mean & 217 (0.95) & 287 (0.98) & 95.3 (0.94) & 83.1 (0.92) & 38.7 (1.05) & -0.07 & 300 (0.95) & 0.67 & 0.88\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 225 (0.98) & 292 (1) & 98.7 (0.98) & 94.2 (1.04) & 32 (0.87) & -0.09 & 314 (1) & 0.71 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 222 (0.97) & 289 (0.99) & 98 (0.97) & 84.1 (0.93) & 39.6 (1.08) & -0.04 & 295 (0.94) & 0.71 & 0.88\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 225 (0.98) & 290 (0.99) & 99.7 (0.99) & 84.7 (0.94) & 40.5 (1.1) & -0.05 & 314 (1) & 0.71 & 0.88\\
\cmidrule{1-11}
\cellcolor{white}{} & Hub-ensemble-mean & 256 (1) & 306 (1) & 138 (1) & 64.5 (1) & 53.2 (1) & 0.04 & 374 (1) & 0.67 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised-mean & 270 (1.05) & 338 (1.1) & 136 (0.99) & 65.2 (1.01) & 68.1 (1.28) & 0.06 & 413 (1.1) & 0.75 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-all-mean & 268 (1.05) & 346 (1.13) & 133 (0.96) & 78.7 (1.22) & 57.1 (1.07) & 0.05 & 408 (1.09) & 0.75 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 259 (1.01) & 322 (1.05) & 133 (0.96) & 81.7 (1.27) & 44.4 (0.83) & 0.03 & 380 (1.02) & 0.67 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 264 (1.03) & 315 (1.03) & 133 (0.96) & 70.1 (1.09) & 60 (1.13) & 0.06 & 404 (1.08) & 0.71 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 264 (1.03) & 332 (1.08) & 141 (1.02) & 60.1 (0.93) & 63.1 (1.19) & 0.06 & 390 (1.04) & 0.79 & 0.92\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}[!h]
\caption{\label{tab:score-table-ensemble-mean-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble. Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets. Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e. the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions). WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model. Dispersion, over-prediction and under-prediction together sum up to the weighted interval score. Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict. 50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}

\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{>{}llccccccccc}
\toprule
  & Model & WIS & WIS - sd & Dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
\midrule
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Cases}}\\
\hline
\cellcolor{white}{} & Hub-ensemble-mean & 35600 (1) & 42100 (1) & 9340 (1) & 7050 (1) & 19200 (1) & 0.03 & 51200 (1) & 0.26 & 0.62\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised-mean & 32100 (0.9) & 40500 (0.96) & 8830 (0.95) & 4920 (0.7) & 18300 (0.95) & 0.07 & 47200 (0.92) & 0.29 & 0.64\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 32200 (0.9) & 36700 (0.87) & 8430 (0.9) & 7190 (1.02) & 16500 (0.86) & 0.04 & 46900 (0.92) & 0.24 & 0.64\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 35200 (0.99) & 46000 (1.09) & 9630 (1.03) & 4600 (0.65) & 20900 (1.09) & 0.08 & 51000 (1) & 0.38 & 0.67\\
\cmidrule{1-11}
\cellcolor{white}{} & Hub-ensemble-mean & 60300 (1) & 79300 (1) & 15700 (1) & 10400 (1) & 34100 (1) & 0.04 & 78600 (1) & 0.29 & 0.57\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised-mean & 55000 (0.91) & 77100 (0.97) & 14600 (0.93) & 6620 (0.64) & 33800 (0.99) & 0.11 & 75200 (0.96) & 0.33 & 0.64\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 53400 (0.89) & 66600 (0.84) & 13700 (0.87) & 10600 (1.02) & 29200 (0.86) & 0.06 & 70400 (0.9) & 0.26 & 0.60\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 61700 (1.02) & 89800 (1.13) & 16400 (1.04) & 6400 (0.62) & 38900 (1.14) & 0.12 & 82900 (1.05) & 0.31 & 0.64\\
\cmidrule{1-11}
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Deaths}}\\
\hline
\cellcolor{white}{} & Hub-ensemble-mean & 289 (1) & 293 (1) & 178 (1) & 45.9 (1) & 65.7 (1) & 0.01 & 443 (1) & 0.58 & 1.00\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised-mean & 310 (1.07) & 348 (1.19) & 182 (1.02) & 42 (0.92) & 86.5 (1.32) & 0.08 & 502 (1.13) & 0.58 & 1.00\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-all-mean & 315 (1.09) & 339 (1.16) & 178 (1) & 62.2 (1.36) & 74 (1.13) & 0.07 & 507 (1.14) & 0.62 & 1.00\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 297 (1.03) & 292 (1) & 174 (0.98) & 67.7 (1.47) & 55 (0.84) & 0.01 & 452 (1.02) & 0.67 & 1.00\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 294 (1.02) & 299 (1.02) & 172 (0.97) & 48 (1.05) & 74.2 (1.13) & 0.03 & 476 (1.07) & 0.58 & 1.00\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 310 (1.07) & 349 (1.19) & 189 (1.06) & 39.4 (0.86) & 81.9 (1.25) & 0.05 & 482 (1.09) & 0.62 & 1.00\\
\cmidrule{1-11}
\cellcolor{white}{} & Hub-ensemble-mean & 437 (1) & 568 (1) & 232 (1) & 72 (1) & 134 (1) & 0.00 & 702 (1) & 0.62 & 1.00\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-realised-mean & 445 (1.02) & 598 (1.05) & 237 (1.02) & 56.4 (0.78) & 152 (1.13) & 0.06 & 707 (1.01) & 0.58 & 1.00\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-all-mean & 421 (0.96) & 520 (0.92) & 239 (1.03) & 49.9 (0.69) & 132 (0.99) & 0.05 & 678 (0.97) & 0.58 & 1.00\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 398 (0.91) & 465 (0.82) & 235 (1.01) & 55.6 (0.77) & 107 (0.8) & 0.00 & 628 (0.89) & 0.67 & 1.00\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 418 (0.96) & 533 (0.94) & 222 (0.96) & 66.8 (0.93) & 129 (0.96) & 0.03 & 662 (0.94) & 0.58 & 1.00\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 467 (1.07) & 636 (1.12) & 248 (1.07) & 61 (0.85) & 158 (1.18) & 0.05 & 755 (1.08) & 0.67 & 1.00\\
\bottomrule
\end{tabular}}
\end{table}

\clearpage

\hypertarget{sensitivity-analysis}{%
\subsection{Sensitivity analysis}\label{sensitivity-analysis}}

In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later. This sensitivity shows performance of all models restricted to the period from October 14 2020 until March 1st 2021 where all models were available.

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from October 14th 2020 on where all models were available. A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components dispersion, over-prediction and under-prediction. C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect). D: Empirical coverage of the 90\% prediction intervals. E: Dispersion (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-late}
\end{figure}

\begin{table}[!h]
\caption{\label{tab:score-table-late-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021. Numbers in brackets show the metrics relative to the Hub ensemble (i.e. the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions). WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model. Dispersion, over-prediction and under-prediction together sum up to the weighted interval score. Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict. 50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}

\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{>{}llccccccccc}
\toprule
  & Model & WIS & WIS - sd & Dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
\midrule
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Cases}}\\
\hline
\cellcolor{white}{} & Crowd forecast & 4980 (0.74) & 5730 (0.64) & 2070 (0.6) & 728 (0.74) & 2190 (0.94) & 0.09 & 7810 (0.82) & 0.54 & 0.88\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 6730 (1) & 8960 (1) & 3430 (1) & 978 (1) & 2330 (1) & -0.09 & 9550 (1) & 0.62 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 9640 (1.43) & 13300 (1.48) & 1970 (0.57) & 4170 (4.26) & 3500 (1.5) & 0.09 & 12700 (1.33) & 0.46 & 0.71\\
\cmidrule{1-11}
\cellcolor{white}{} & Crowd forecast & 10700 (0.99) & 13800 (1.1) & 2880 (0.58) & 2350 (0.85) & 5430 (1.79) & 0.08 & 15400 (1.07) & 0.46 & 0.62\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 10800 (1) & 12500 (1) & 4940 (1) & 2780 (1) & 3030 (1) & -0.13 & 14400 (1) & 0.54 & 0.75\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25000 (2.31) & 34000 (2.72) & 4780 (0.97) & 8710 (3.13) & 11500 (3.8) & 0.05 & 32000 (2.22) & 0.50 & 0.67\\
\cmidrule{1-11}
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Deaths}}\\
\hline
\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
\cmidrule{2-11}
\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
\cmidrule{1-11}
\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
\cmidrule{2-11}
\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}[!h]
\caption{\label{tab:score-table-late-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021. Numbers in brackets show the metrics relative to the Hub ensemble (i.e. the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions). WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model. Dispersion, over-prediction and under-prediction together sum up to the weighted interval score. Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict. 50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}

\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{>{}llccccccccc}
\toprule
  & Model & WIS & WIS - sd & Dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
\midrule
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Cases}}\\
\hline
\cellcolor{white}{} & Crowd forecast & 17200 (1) & 16000 (0.98) & 3800 (0.63) & 5660 (0.85) & 7770 (1.74) & 0.07 & 26800 (1.1) & 0.08 & 0.58\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 17200 (1) & 16300 (1) & 6030 (1) & 6670 (1) & 4470 (1) & -0.16 & 24400 (1) & 0.33 & 0.67\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 37700 (2.19) & 55900 (3.43) & 8840 (1.47) & 10700 (1.6) & 18100 (4.05) & -0.03 & 49800 (2.04) & 0.33 & 0.58\\
\cmidrule{1-11}
\cellcolor{white}{} & Crowd forecast & 26100 (0.95) & 21000 (0.84) & 4810 (0.7) & 11300 (0.83) & 10100 (1.43) & 0.04 & 39400 (1.05) & 0.00 & 0.46\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 27600 (1) & 25000 (1) & 6900 (1) & 13600 (1) & 7060 (1) & -0.19 & 37400 (1) & 0.29 & 0.54\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 48900 (1.77) & 77800 (3.11) & 13800 (2) & 11900 (0.88) & 23200 (3.29) & -0.10 & 65500 (1.75) & 0.38 & 0.58\\
\cmidrule{1-11}
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Deaths}}\\
\hline
\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
\cmidrule{2-11}
\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
\cmidrule{1-11}
\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
\cmidrule{2-11}
\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
\cmidrule{2-11}
\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
\cmidrule{2-11}
\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
\bottomrule
\end{tabular}}
\end{table}

\clearpage

\hypertarget{overview-of-models-and-forecasters}{%
\subsection{Overview of models and forecasters}\label{overview-of-models-and-forecasters}}

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{11.0cm}}
\caption{\label{tab:table-ensemble-versions}Overview of the models and ensembles used.}\\
\toprule
Name & Explanation\\
\midrule
\endfirsthead
\caption[]{\label{tab:table-ensemble-versions}Overview of the models and ensembles used. \textit{(continued)}}\\
\toprule
Name & Explanation\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{Hub-ensemble-realised} & \cellcolor{gray!6}{Official Forecast Hub median ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-median\_ensemble' and used as the default ensemble. Included are our crowd forecasts as well as the renewal model (with one missed submission on December 28 2020, but not the convolution model which was deemed to similar to the renewal model.}\\
\addlinespace \addlinespace
Hub-ensemble-realised-mean & Official Forecast Hub mean ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-mean\_ensemble'.\\
\addlinespace \addlinespace
\cellcolor{gray!6}{ \vphantom{1}} & \cellcolor{gray!6}{}\\
\addlinespace \addlinespace
Hub-ensemble & Version of the official Hub median ensemble which excludes all our contributions.\\
\addlinespace \addlinespace
\cellcolor{gray!6}{Hub-ensemble-mean} & \cellcolor{gray!6}{Version of the official Hub mean ensemble which excludes all our contributions.}\\
\addlinespace \addlinespace
Hub-ensemble-with-renewal, 
    Hub-ensemble-with-renewal-mean & Versions of the official Hub ensembles which of our contributions includes only the Renewal model.\\
\addlinespace \addlinespace
Hub-ensemble-with-crowd, 
\cellcolor{gray!6}{    Hub-ensemble-with-crowd-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which of our contributions includes only the Crowd forecast.}\\
\addlinespace \addlinespace
Hub-ensemble-with-convolution, 
    Hub-ensemble-with-convolution-mean & Versions of the official Hub ensembles which of our contributions includes only the Convolution model (which originally was never included in any official Hub ensemble).\\
\addlinespace \addlinespace
Hub-ensemble-with-all, 
\cellcolor{gray!6}{    Hub-ensemble-with-all-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which includes all our contributions. For cases, this is identical to the official Hub ensembles, but for deaths the convolution model was added.}\\
\addlinespace \addlinespace
 & \\
\addlinespace \addlinespace
\cellcolor{gray!6}{Crowd forecast} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'}\\
\addlinespace \addlinespace
Renewal model & Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'\\
\addlinespace \addlinespace
\cellcolor{gray!6}{Convolution model} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\_secondary'}\\*
\end{longtable}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/number-forecasters} \caption{Number of participants who submitted a forecast over time.}\label{fig:num-forecasters}
\end{figure}

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/ensemble-members} \caption{Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble. Note that the renewal model was not included in the ensemble on December 28th 2020.}\label{fig:num-ensemble-members}
\end{figure}

\clearpage

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
Abbott, Sam, Joel Hellewell, Joe Hickson, James Munday, Katelyn Gostic, Peter Ellis, Katharine Sherratt, et al. 2020. {``EpiNow2: Estimate Real-Time Case Counts and Time-Varying Epidemiological Parameters.''} \emph{-} - (-): --. \url{https://doi.org/10.5281/zenodo.3957489}.

\leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
Abbott, Sam, Katharine Sherratt, Jonnie Bevan, Hamish Gibbs, Joel Hellewell, James Munday, Patrick Barks, Paul Campbell, Flavio Finger, and Sebastian Funk. 2020. {``Covidregionaldata: Subnational Data for the Covid-19 Outbreak.''} \emph{-} - (-): --. \url{https://doi.org/10.5281/zenodo.3957539}.

\leavevmode\vadjust pre{\hypertarget{ref-doiCovid19TemporalVariation}{}}%
DOI, Authors Affiliations Published Not published yet. n.d. {``Covid-19: Temporal Variation in Transmission During the {COVID}-19 Outbreak.''} {Covid-19}. Accessed May 30, 2021. \url{https://epiforecasts.io/covid/}.

\leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
{``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid}-19 Outbreak in {England} \textbar{} {medRxiv}.''} n.d. Accessed May 30, 2021. \url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}.

\leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
Fraser, Christophe. 2007. {``Estimating {Individual} and {Household Reproduction Numbers} in an {Emerging Epidemic}.''} \emph{PLOS ONE} 2 (8): e758. \url{https://doi.org/10.1371/journal.pone.0000758}.

\leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
Ganyani, Tapiwa, Cecile Kremer, Dongxuan Chen, Andrea Torneri, Christel Faes, Jacco Wallinga, and Niel Hens. 2020. {``Estimating the Generation Interval for Coronavirus Disease (COVID-19) Based on Symptom Onset Data, March 2020.''} \emph{Eurosurveillance} 25 (17).

\leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
Lauer, Stephen A, Kyra H Grantz, Qifang Bi, Forrest K Jones, Qulu Zheng, Hannah R Meredith, Andrew S Azman, Nicholas G Reich, and Justin Lessler. 2020. {``The Incubation Period of Coronavirus Disease 2019 (COVID-19) from Publicly Reported Confirmed Cases: Estimation and Application.''} \emph{Annals of Internal Medicine} 172 (9): 577--82.

\leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
Riutort-Mayol, Gabriel, Paul-Christian Bürkner, Michael R. Andersen, Arno Solin, and Aki Vehtari. 2020. {``Practical Hilbert Space Approximate Bayesian Gaussian Processes for Probabilistic Programming.''} \url{https://arxiv.org/abs/2004.11408}.

\leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
Scott, James A., Axel Gandy, Swapnil Mishra, Juliette Unwin, Seth Flaxman, and Samir Bhatt. 2020. {``Epidemia: Modeling of Epidemics Using Hierarchical Bayesian Models.''} \url{https://imperialcollegelondon.github.io/epidemia/}.

\leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
Stan Development Team. 2020. {``RStan: The r Interface to Stan.''} \url{http://mc-stan.org/}.

\leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
Xu, Bo, Bernardo Gutierrez, Sarah Hill, Samuel Scarpino, Alyssa Loskill, Jessie Wu, Kara Sewalk, et al. n.d. {``Epidemiological Data from the nCoV-2019 Outbreak: Early Descriptions from Publicly Available Data.''} \url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}.

\end{CSLReferences}

\end{document}

### 2021-10-13 manuscript/manuscript.Rmd
update a few citations

@@
 
-Previous work has examined human predictions in various contexts, such as geopolitics (Tetlock et al.
-2014; Atanasov et al.
-2016), meta-science (Cite Replication Markets), and epidemiology (CITE FARROW ET AL, McAndrew et al.
-2021, Cite that other paper).
-Several prediction platforms (Metaculus 2020, Hypermind, Foretell) and prediction markets (cite predictit) have been created to collate expert and non-expert predictions.
+Previous work has examined human predictions in various contexts, such as geopolitics [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016], meta-science [@hoogeveenLaypeopleCanPredict2020; ](Cite Replication Markets), and epidemiology [@farrowHumanJudgmentApproach2017; , @mcandrewExpertJudgmentModel2020, @recchiaHowWellDid2021] (Also Cite that other paper).
+Several prediction platforms (Metaculus 2020, Hypermind, Foretell) and prediction markets [@Predictit] have been created to collate expert and non-expert predictions.
 However, with the notable exception of Farrow et al., these crowd forecasts  were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats.

### 2021-10-13 manuscript/manuscript.Rmd
add citations

--- 2021-10-13 manuscript/manuscript.Rmd
@@
 
-Infectious disease forecasting has a long tradition and has helped inform public health decisions about (among others) influenza [CITATION], dengue fever [Citation], ebola [Citation], chikungunya and now COVID-19 [Citation].
-The aggregation of forecasts of COVID-19 cases, hospitalisations or deaths from multiple teams has created opportunities to compare the predictive performance of different models (CITE e.g UK, US and German/Polish papers).
+Infectious disease forecasting has a long tradition and has helped inform public health decisions about (among others) influenza [e.g.
+@mcgowanCollaborativeEffortsForecast2019; @reichCollaborativeMultiyearMultimodel2019; @shamanForecastingSeasonalOutbreaks2012; @biggerstaffResultsCentersDisease2016], dengue fever [e.g.
+@johanssonOpenChallengeAdvance2019; @yamanaSuperensembleForecastsDengue2016; @colon-gonzalezProbabilisticSeasonalDengue2021], ebola [e.g.
+@viboudRAPIDDEbolaForecasting2018; @funkAssessingPerformanceRealtime2019], chikungunya [e.g.
+@delvalleSummaryResults201420152018; @farrowHumanJudgmentApproach2017] and now COVID-19 [e.g.
+@funkShorttermForecastsInform2020; @esteecramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @EuroHub].
+The aggregation of forecasts of COVID-19 cases, hospitalisations or deaths from multiple teams has created opportunities to compare the predictive performance of different models.
 Yet it has been difficult to discern which factors lead to good COVID-19 forecasts.
@@
 
-Previous work has examined human predictions in various contexts, such as geopolitics (Tetlock et al.
-2014; Atanasov et al.
-2016), meta-science (Cite Replication Markets), and epidemiology (CITE FARROW ET AL, McAndrew et al.
-2021, Cite that other paper).
-Several prediction platforms (Metaculus 2020, Hypermind, Foretell) and prediction markets (cite predictit) have been created to collate expert and non-expert predictions.
+Previous work has examined human predictions in various contexts, such as geopolitics [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016], meta-science [@hoogeveenLaypeopleCanPredict2020; @ReplicationMarketsReliable], sports [@servan-schreiberPredictionMarketsDoes2004] and epidemiology [@farrowHumanJudgmentApproach2017; @mcandrewExpertJudgmentModel2020, @recchiaHowWellDid2021].
+Several prediction platforms [@metaculusPreliminaryLookMetaculus2020; @HypermindSupercollectiveIntelligence; @CSETForetell] and prediction markets [@Predictit] have been created to collate expert and non-expert predictions.
 However, with the notable exception of Farrow et al., these crowd forecasts  were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats.
@@
 
-In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses by comparing human forecasts and model-based predictions.
+In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses by comparing human forecasts with a full predictive distribution and model-based predictions.
 
@@
 
-We created a crowd-sourced forecast (“crowd forecast”), elicited from participants through a web application [Citation], as well as two semi-mechanistic models ("renewal model" and "convolution model") informed by basic assumptions about COVID-19 epidemiology.
-Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (CITATION).
-All code and tools necessary to generate the forecasts and make a forecast submission are available in the `covid.german.forecasts` R package (N.
-Bosse et al.
-2020).
+We created a crowd-sourced forecast (“crowd forecast”), elicited from participants through a web application [@crowdforecastr], as well as two semi-mechanistic models ("renewal model" and "convolution model") informed by basic assumptions about COVID-19 epidemiology.
+Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub [@bracherShorttermForecastingCOVID192021].
+All code and tools necessary to generate the forecasts and make a forecast submission are available in the `covid.german.forecasts` R package [@covidgermanforecasts].
 This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub.
@@
 2021).
-Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) (“Download Historical Data (to 14 December 2020) on the Daily Number of New Reported COVID-19 Cases and Deaths Worldwide” 2020).
-After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (“RKI - Coronavirus SARS-CoV-2 - Aktueller Lage-/Situationsbericht Des RKI Zu COVID-19” n.d.).
-These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November (“Rozbieżności w statystykach koronawirusa.
-22 tys.
-przypadków będą doliczone do ogólnej liczby wyników” 16:07:56+0100)), changes in reporting over time and variation in testing regimes (e.g.
-in Germany from the 11th of November on (Ärzteblatt 2020)).
+Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) [@DownloadHistoricalData2020a].
+After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period  [@RKICoronavirusSARSCoV2a].
+These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November [@RozbieznosciStatystykachKoronawirusa0100]), changes in reporting over time and variation in testing regimes (e.g.
+in Germany from the 11th of November on [@aerzteblattSARSCoV2DiagnostikRKIPasst2020]).
 
@@
 Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information available until Monday.
-The application was built using the shiny and golem R packages (Chang et al.
-2021; Fay et al.
-2021) and is available in the crowdforecastr R package (N.
-I.
-Bosse et al.
-2020).
+The application was built using the shiny and golem R packages [@golem; @shiny] and is available in the `crowdforecastr` R package [@crowdforecastr].
 To make a forecast in the application participants could select a predictive distribution, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values.
@@
 as `sd(c(log(value4) - log(value3), log(value3) - log(value2), ...))`).
-Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from (“COVID-19 Data Explorer” n.d.).
+Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  [@COVID19DataExplorer].
 These data included e.g.
@@
 
-We used two models from the `EpiNow2` R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, et al.
-2020).
+We used two models from the `EpiNow2` R package (version 1.3.3) as our model-based forecasts [@epinow2].
 The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths.
@@
 The $R_t$ value which was carried forward was slightly changed on November 9th 2020, where before that date the last 'reliable' $R_t$ estimate from X days before the forecast was used and after that the latest and most up-to-date (but possibly less stable) $R_t$ estimate made on the actual forecast date was used.
-Reported cases and deaths were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, et al.
-2020; DOI n.d.; “Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the Covid-19 Outbreak in England | medRxiv” n.d.) to model the time between infection and report date or death.
+Reported cases and deaths were obtained by convolving predicted infections over data-based delay distributions [@epinow2; @doiCovid19TemporalVariation; @EvaluatingUseReproduction] to model the time between infection and report date or death.
 The renewal model was used to predict cases as well as deaths, but the two were forecast completely independently, meaning that $R_t$ was forecast once from reported cases and once from reported deaths.
@@
 The convolution model predicted deaths these as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
-Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model and a multiplicative day-of-the-week effect (Abbott, Hellewell, et al.
-2020).
-Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August.
-All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fit separately.
+Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model and a multiplicative day-of-the-week effect [@epinow2].
+Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from [@kraemer2020epidemiological] with data available up to the 1st of August.
+All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan  [@rstan]  with each location and forecast target being fit separately.
 More details are available in the supplementary information.
@@
 2021), the absolute error, relative bias, and empirical coverage of the 50% and 90% prediction intervals.
-The WIS is a proper scoring rule (CITE GNEITING) and can be understood as a generalisation of the absolute error to quantile-based forecasts.
+The WIS is a proper scoring rule [@gneiting_strictly_2007] and can be understood as a generalisation of the absolute error to quantile-based forecasts.
 It can be decomposed into three separate penalties: forecast spread (i.e.
@@
 Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (Cite US Hub, cite Seb SPI-M), or exclusively on human forecasts (e.g.
-cite Tetlock, cite Grecchia, cite McAndrew).
+However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches [e.g.
+@funkShorttermForecastsInform2020; @esteecramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], or exclusively on human forecasts [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016; @mcandrewExpertJudgmentModel2020, @recchiaHowWellDid2021].
 In contrast, we directly compared human and model-based forecasts.
-This is similar to the approach taken by Farrow et al., but extends it in several ways.
+This is similar to the approach taken by @farrowHumanJudgmentApproach2017, but extends it in several ways.
 While Farrow et al.
@@
 where $I^c_t = \sum_{s< t} I_s$ are cumulative infections by $t-1$ and $I'_t$ are the unadjusted infections defined above.
-This adjustment is based on that implemented in the `epidemia` R package (@epidemia, cite @bhatt202).
+This adjustment is based on that implemented in the `epidemia` R package [@epidemia; @bhatt202].
 

### 2021-10-13 manuscript/manuscript.tex
add citations

@@
 
-Previous work has examined human predictions in various contexts, such as geopolitics (Tetlock et al.~2014; Atanasov et al.~2016), meta-science (Cite Replication Markets), and epidemiology (CITE FARROW ET AL, McAndrew et al.~2021, Cite that other paper).
-Several prediction platforms (Metaculus 2020, Hypermind, Foretell) and prediction markets (cite predictit) have been created to collate expert and non-expert predictions.
+Previous work has examined human predictions in various contexts, such as geopolitics (Tetlock et al.
+2014; Atanasov et al.
+2016), meta-science (Hoogeveen, Sarafoglou, and Wagenmakers 2020; {``Replication {Markets} -- {Reliable} Research Replicates\ldots you Can Bet on It.''} n.d.), sports (Servan-Schreiber et al.
+2004) and epidemiology Recchia, Freeman, and Spiegelhalter (2021).
+Several prediction platforms (Metaculus 2020; {``Hypermind \textbar{} {Supercollective} Intelligence for Decision Makers''} n.d.; {``{CSET Foretell}''} n.d.) and prediction markets (\textbf{Predictit?}) have been created to collate expert and non-expert predictions.
 However, with the notable exception of Farrow et al., these crowd forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
+Atanasov, Pavel, Phillip Rescober, Eric Stone, Samuel A.
+Swift, Emile Servan-Schreiber, Philip Tetlock, Lyle Ungar, and Barbara Mellers.
+2016.
+{``Distilling the {Wisdom} of {Crowds}: Prediction {Markets} Vs.
+{Prediction Polls}.''} \emph{Management Science} 63 (3): 691--706.
+\url{https://doi.org/10.1287/mnsc.2015.2374}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-CSETForetell}{}}%
+{``{CSET Foretell}.''} n.d. Accessed October 13, 2021. \url{https://www.cset-foretell.com/}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-doiCovid19TemporalVariation}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
+Farrow, David C., Logan C.
+Brooks, Sangwon Hyun, Ryan J.
+Tibshirani, Donald S.
+Burke, and Roni Rosenfeld.
+2017.
+{``A Human Judgment Approach to Epidemiological Forecasting.''} \emph{PLOS Computational Biology} 13 (3): e1005248.
+\url{https://doi.org/10.1371/journal.pcbi.1005248}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
+Hoogeveen, Suzanne, Alexandra Sarafoglou, and Eric-Jan Wagenmakers.
+2020.
+{``Laypeople {Can Predict Which Social}-{Science Studies Will Be Replicated Successfully}.''} \emph{Advances in Methods and Practices in Psychological Science} 3 (3): 267--85.
+\url{https://doi.org/10.1177/2515245920919667}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-HypermindSupercollectiveIntelligence}{}}%
+{``Hypermind \textbar{} {Supercollective} Intelligence for Decision Makers.''} n.d. {Hypermind}. Accessed October 13, 2021. \url{https://www.hypermind.com/en/}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
@@
 {``The Incubation Period of Coronavirus Disease 2019 (COVID-19) from Publicly Reported Confirmed Cases: Estimation and Application.''} \emph{Annals of Internal Medicine} 172 (9): 577--82.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
+McAndrew, Thomas Charles, and Nicholas G.
+Reich.
+2020.
+{``An Expert Judgment Model to Predict Early Stages of the {COVID}-19 Outbreak in the {United States}.''} \emph{medRxiv}, September, 2020.09.21.20196725.
+\url{https://doi.org/10.1101/2020.09.21.20196725}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
+Metaculus. 2020. {``A {Preliminary Look} at {Metaculus} and {Expert Forecasts}.''} June 22, 2020. \url{https://www.metaculus.com/news/2020/06/02/LRT/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
+Recchia, Gabriel, Alexandra L.
+J.
+Freeman, and David Spiegelhalter.
+2021.
+{``How Well Did Experts and Laypeople Forecast the Size of the {COVID}-19 Pandemic?''} \emph{PLOS ONE} 16 (5): e0250935.
+\url{https://doi.org/10.1371/journal.pone.0250935}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ReplicationMarketsReliable}{}}%
+{``Replication {Markets} -- {Reliable} Research Replicates\ldots you Can Bet on It.''} n.d. Accessed October 13, 2021. \url{https://www.replicationmarkets.com/}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
+Servan-Schreiber, Emile, Justin Wolfers, David M.
+Pennock, and Brian Galebach.
+2004.
+{``Prediction {Markets}: Does {Money Matter}?''} \emph{Electronic Markets} 14 (3): 243--51.
+\url{https://doi.org/10.1080/1019678042000245254}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
 Stan Development Team. 2020. {``RStan: The r Interface to Stan.''} \url{http://mc-stan.org/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
+Tetlock, Philip E., Barbara A.
+Mellers, Nick Rohrbaugh, and Eva Chen.
+2014.
+{``Forecasting {Tournaments}: Tools for {Increasing Transparency} and {Improving} the {Quality} of {Debate}.''} \emph{Current Directions in Psychological Science} 23 (4): 290--95.
+\url{https://doi.org/10.1177/0963721414534257}.
 

### 2021-10-14 manuscript/manuscript.Rmd
convert percentage numbers to decimals

@@
 In addition, we compared these forecasts against an ensemble of model-based, but expert-tuned, forecasts, submitted to the German and Polish Forecast Hub by other research institutions (“Hub ensemble”).
-We found an ensemble of crowd-sourced predictions to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble at a two-week horizon: 89%), but not when predicting deaths (rel.
-WIS 126%).
-Crowd forecasts were severely overconfident (55% and 75% coverage of the 95% prediction intervals for cases and deaths, respectively) when compared to model-based predictions.
+We found an ensemble of crowd-sourced predictions to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble at a two-week horizon: 0.89), but not when predicting deaths (rel.
+WIS 1.26).
+Crowd forecasts were severely overconfident (55% and 75% coverage of the 90% prediction intervals for cases and deaths, respectively) when compared to model-based predictions.
 Performance of the untuned models deteriorated quickly with increasing forecast horizon when assumptions were no longer met (rel.
-WIS > 164% for all four week ahead predictions).
+WIS > 1.64 for all four week ahead predictions).
 
@@
 For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure \@ref(fig:performance-locations-rel)A).
-For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 100%) was 89% for crowd forecasts and 140% for the renewal model (Table \@ref(tab:score-table-2)).
+For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \@ref(tab:score-table-2)).
 Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was right-skewed, and average performance was heavily influenced by outliers (Figure \@ref(fig:distribution-scores)).

### 2021-10-14 analysis/analysis.Rmd
code cleaning

@@
 
-# helper function for labelling
+# helper function for labeling plots
 scale_fn <- function(x) {
@@
 }
-
 ```
@@
 truth_and_pred_plot <- function(df, ttype = "case") {
-
-  # data = unfiltered_data[model %in% regular_models]
-  # df <- data[quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
-  #   dcast(... ~ quantile, value.var = "prediction")
-  # df <- merge(
-  #   df[, c("classification", "speed") := NULL], 
-  #   copy(epitrend)[, c("forecast_date", "true_value") := NULL], 
-  #   by = c("target_end_date", "location_name", "target_type")
-  # )
-  # df <- df[grepl(2, target)]
 
@@
 
-  setnames(df, old = c("interval_score_sd"), 
-           new = c("WIS - sd"))
-
-  # tables for 1-2 weeks ahead and 3-4 weeks ahdead
+  setnames(df, old = c("interval_score_sd, sharpness"), 
+           new = c("WIS - sd", "dispersion"))
+
+  # tables for 1-2 weeks ahead and 3-4 weeks ahead
   table <- score_table(df[horizon <= 2])
@@
            file = here("analysis", "plots", "table-phases-4.png"))
-
-# 
-# horizons = 2
-# for (tar in targets) {
-#   for (i in horizons) {
-#     name <- paste0(tar, "-", i)
-#     
-#     tmp_df <- df[target_phase == tar & horizon == i, 
-#                  .(model, interval_score, sharpness,
-#                    target_phase, horizon, 
-#                    underprediction, overprediction, 
-#                    `WIS - median` = interval_score_0.5, 
-#                    `WIS - sd` = interval_score_sd)]
-#     
-#     tables[[name]] <- score_table(tmp_df, 
-#                                        group = FALSE, 
-#                                        full_width = FALSE) %>%
-#       pack_rows(tar, 1, nrow(tmp_df), indent = FALSE)
-#     
-#     save_kable(tables[[name]],
-#                file = here("analysis", "plots",
-#                            paste0("table-", gsub(" ", "", name), ".png")))
-#   }
-# }
 
@@
 
-```{r fig.height=10, fig.width=15}
-# 
-# coverage_tables <- eval_forecasts(
-#   filtered_data[grepl("2", target)], 
-#   summarise_by = c("model", "target_phase", "classification", "range", "horizon"), 
-#   compute_relative_skill = TRUE, 
-#   baseline = "Baseline"
-# )[range %in% c(50, 90), 
-#                    .(model, target_phase, coverage, classification, range)] %>%
-#   dcast(formula = ... ~ range, value.var = "coverage")
-# 
-# scores_tables <- eval_forecasts(
-#   filtered_data[grepl("2", target)], 
-#   summarise_by = c("model", "target_phase", "classification", "horizon"), 
-#   compute_relative_skill = TRUE, 
-#   baseline = "Baseline"
-# )
-# 
-# tbl <- scores_tables %>%
-#   merge(coverage_tables, all.x = TRUE, by = c("model", "target_phase", "classification")) 
-# 
-#  tbl <- tbl[, lapply(.SD, FUN = function(x) {
-#     if (is.numeric(x)) {
-#       return(round(signif(x, 3), 2))
-#     } else {
-#       return(x)
-#     }
-#   })]
-# 
-# tables <- list()
-# table_dfs <- list()
-# targets <- unique(tbl$target_phase)
-# 
-# for (tar in targets) {
-#   tables[[tar]] <- score_table(tbl[target_phase == tar])
-# }
-# 
-# for (tar in targets) {
-#   table_dfs[[tar]] <- tbl[target_phase == tar, 
-#                           .("Model" = model, 
-#                             # "Target" = target_phase,
-#                             "WIS" = interval_score,
-#                             # "Rel. skill" = scaled_rel_skill, 
-#                             "Sharpn." = sharpness, 
-#                             "Underp.." = underprediction, 
-#                             "Overp." = overprediction)#, 
-#                             # "Bias" = bias,
-#                             # "50%-Cov." = `50`, 
-#                             # "90%-Cov." = `90`)
-#                           ]
-# }
-# 
-# 
-# # make plots with tables
-# library(gridExtra)
-# 
-# tbl_plt <- grid.arrange(tableGrob(table_dfs[[1]]), 
-#              tableGrob(table_dfs[[2]]), 
-#              tableGrob(table_dfs[[3]]), 
-#              tableGrob(table_dfs[[4]]), 
-#              tableGrob(table_dfs[[5]]), 
-#              tableGrob(table_dfs[[6]]), 
-#              nrow = 2) 
-# 
-# tbl_plt <- ggplotify::as.ggplot(tbl_plt)
-# 
-# tbl_plt
-# 
-# ggsave("plots/distribution_scores_table.png")
-# 
-# library(gt)
-# 
-# tbl[, 
-#     .("Model" = model, 
-#       "Target" = target_phase,
-#       "WIS" = interval_score,
-#       # "Rel. skill" = scaled_rel_skill, 
-#       "Sharpn." = sharpness, 
-#       "Underp.." = underprediction, 
-#       "Overp." = overprediction)#, 
-#     # "Bias" = bias,
-#     # "50%-Cov." = `50`, 
-#     # "90%-Cov." = `90`)
-# ] %>%
-#   gt(rowname_col = "Model", 
-#      groupname_col = "Target") 
-#
-
-```
-
 ------------------------------------------------------------------------
@@
 ```
-
-*Figure 3.
-Relative contributions of sharpness, overprediction and underprediction to the weighted interval scores.
-Models overpredict in a decreasing phase and underpredict in a decreasing phase.
-So far so obvious.
-Somehow adding inflection points would be really cool - maybe stratify according to "decreasing, but inflection afterwards etc.?".
-Apparently the baseline model is really good in an unclear phase, just much too uncertain?.*
 
@@
 ```{r, eval = TRUE}
-# df <- data[grepl("2", target)] %>%
-#   merge(epitrend, 
-#         by = c("target_end_date", "location_name", "target_type"))
-
 scores_target <- eval_forecasts(
@@
 ```
-
-*Figure 4: Comparison of nominal and empirical coverage (percentage of true observed values covered by a given prediction interval).
-The one thing I find interesting about this plot is that models are apparently much too confident when there is an increasing trend.
-I feel this is probably actionable advice (even though it could probably be made better using a separate analysis about optimal uncertainty that is beyond the scope of this paper).*
-
-**Todo**
-
--   maybe make this a PIT plot
-
-------------------------------------------------------------------------
-
-## Supplementary Material
-
-### Look at the effect of data exclusions
-
--   look at first period, second period etc
 
@@
   scores <- scores %>%
-    select(Model, target_type, sharpness, interval_score,
+    select(Model, target_type, dispersion, interval_score,
            underprediction, overprediction, !!x) %>%
+    rename("Dispersion" = dispersion, 
+           "Over-prediction" = overprediction, 
+           "Under-prediction" = underprediction) %>%
     filter(target_type == type) %>%
     pivot_longer(names_to = "WIS components",
-                 cols = c(sharpness, overprediction, underprediction)) %>%
+                 cols = c(`Dispersion`, `Over-prediction`, `Under-prediction`)) %>%
     mutate(`WIS components` = fct_relevel(`WIS components`, 
-                                          c("sharpness", "underprediction", 
-                                            "overprediction")))
+                                          c("Dispersion", "Under-prediction", 
+                                            "Over-prediction")))
 
@@
 
-  setnames(scores, old = "model", new = "Model")
+  setnames(scores, old = c("model", "sharpness"), 
+           new = c("Model", "dispersion"))
 }
@@
   p_sharpness <- 
-    plot_helper(scores, y = "sharpness", rel = relative, xvar = x,
+    plot_helper(scores, y = "dispersion", rel = relative, xvar = x,
                 facet_formula = facet_formula, colour = vals) + 
-    labs(y = "Sharpness", x = NULL)
+    labs(y = "Dispersion", x = NULL)
 
@@
     }
-
-  p_combined <- (p_mean) / 
-    (p_cov50) /
-    (p_cov90) / 
-    (component_case + component_death) +  
-    plot_layout(guides = "collect") & 
-    plot_annotation(tag_levels = 'A') &
-    theme(legend.position = 'bottom', 
-          legend.box="vertical", legend.margin=margin())
-
-  ggsave(here(output_dir, paste0(plotname, "-v1.png")), 
-         height = 9.1, width = 8)
-
-  p_combined2 <- (p_aem + p_wis_sd) /
-    (p_sharpness + p_bias) + 
-    plot_layout(guides = "collect") & 
-    plot_annotation(tag_levels = 'A') &
-    theme(legend.position = 'bottom', 
-          legend.box="vertical", legend.margin=margin())
-
-    ggsave(here(output_dir, paste0(plotname, "-v2.png")), 
-         height = 5.1, width = 10)
-
-    p_combined3 <- (p_mean + p_aem) /
-        (p_cov50 + p_cov90) /
-        (p_sharpness + p_bias) /
-        (p_wis_sd + plot_spacer()) + 
-    plot_layout(guides = "collect") & 
-    plot_annotation(tag_levels = 'A')  &
-    theme(legend.position = 'bottom', 
-          legend.box="vertical", legend.margin=margin())
-
-    ggsave(here(output_dir, paste0(plotname, "-v3.png")), 
-         height = 9.1, width = 10)
 
@@
 ```
-
-### Plots with overprediction, sharpness etc over time
-
-``` {r}
-
-```

### 2021-10-14 manuscript/manuscript.Rmd
code cleaning

@@
 
-In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses by comparing human forecasts with a full predictive distribution and model-based predictions.
-
-<!-- In contrast to Farrow et al., we analyse not only point predictions, but also for their predictive uncertainty, to exploit the greater utility of probabilistic forecasts (CITE Held, Meyer, Bracher, 2017).
--->
+In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses.
+To allow for a direct comparison on an equal footing we employ a novel approach that elicits full probabilistic forecasts [@heldProbabilisticForecastingInfectious2017] from participants, rather than constructing a predictive distribution from individual point predictions.
 
@@
 
-Data on daily reported test positive cases and deaths linked to Covid-19 were provided by the organisers of the German and Polish forecast hub (J.
-Bracher et al.
-2021).
+Data on daily reported test positive cases and deaths linked to Covid-19 were provided by the organisers of the German and Polish forecast hub.
 Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) [@DownloadHistoricalData2020a].
@@
 
-For the main analysis we focused on two week ahead predictions, as predictions beyond this horizon are often unreliable due to rapidly changing conditions (J.
-Bracher et al.
-2021).
+For the main analysis we focused on two week ahead predictions, as predictions beyond this horizon are often unreliable due to rapidly changing conditions [@bracherShorttermForecastingCOVID192021].
 Forecasts for cases were scored using the full period from October 2020 until March 2021.
@@
 
-Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Johannes Bracher et al.
-2021), the absolute error, relative bias, and empirical coverage of the 50% and 90% prediction intervals.
+Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) [@bracherEvaluatingEpidemicForecasts2021], the absolute error, relative bias, and empirical coverage of the 50% and 90% prediction intervals.
 The WIS is a proper scoring rule [@gneiting_strictly_2007] and can be understood as a generalisation of the absolute error to quantile-based forecasts.
@@
 In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight.
-In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (J.
-Bracher et al.
-2021; E.
-Y.
-Cramer et al.
-2021; S.
-Funk et al.
-2020).
+In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs [@esteecramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @EuroHub; @funkShorttermForecastsInform2020].
 
@@
 D: Standard deviation of the WIS.
-E: Sharpness (higher values mean greater dispersion of the forecast).
+E: Dispersion (higher values mean further spread out forecast).
 F: Bias, i.e.

### 2021-10-14 manuscript/manuscript.tex
code cleaning

@@
 In addition, we compared these forecasts against an ensemble of model-based, but expert-tuned, forecasts, submitted to the German and Polish Forecast Hub by other research institutions (``Hub ensemble'').
-We found an ensemble of crowd-sourced predictions to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble at a two-week horizon: 89\%), but not when predicting deaths (rel.
-WIS 126\%).
-Crowd forecasts were severely overconfident (55\% and 75\% coverage of the 95\% prediction intervals for cases and deaths, respectively) when compared to model-based predictions.
+We found an ensemble of crowd-sourced predictions to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble at a two-week horizon: 0.89), but not when predicting deaths (rel.
+WIS 1.26).
+Crowd forecasts were severely overconfident (55\% and 75\% coverage of the 90\% prediction intervals for cases and deaths, respectively) when compared to model-based predictions.
 Performance of the untuned models deteriorated quickly with increasing forecast horizon when assumptions were no longer met (rel.
-WIS \textgreater{} 164\% for all four week ahead predictions).
+WIS \textgreater{} 1.64 for all four week ahead predictions).
 
@@
 
-Infectious disease forecasting has a long tradition and has helped inform public health decisions about (among others) influenza {[}CITATION{]}, dengue fever {[}Citation{]}, ebola {[}Citation{]}, chikungunya and now COVID-19 {[}Citation{]}.
-The aggregation of forecasts of COVID-19 cases, hospitalisations or deaths from multiple teams has created opportunities to compare the predictive performance of different models (CITE e.g UK, US and German/Polish papers).
+Infectious disease forecasting has a long tradition and has helped inform public health decisions about (among others) influenza (e.g.
+McGowan et al.
+2019; \textbf{reichCollaborativeMultiyearMultimodel2019?}; Shaman and Karspeck 2012; \textbf{biggerstaffResultsCentersDisease2016?}), dengue fever (e.g.
+Johansson et al.
+2019; Yamana, Kandula, and Shaman 2016; Colón-González et al.
+2021), ebola (e.g.
+Viboud et al.
+2018; Funk et al.
+2019), chikungunya (e.g.
+Del Valle et al.
+2018; Farrow et al.
+2017) and now COVID-19 (e.g.
+Funk et al.
+2020; \textbf{esteecramerCOVID19ForecastHub2020?}; Cramer et al.
+2021; Bracher, Wolffram, et al.
+2021; Hub 2021).
+The aggregation of forecasts of COVID-19 cases, hospitalisations or deaths from multiple teams has created opportunities to compare the predictive performance of different models.
 Yet it has been difficult to discern which factors lead to good COVID-19 forecasts.
@@
 
-In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses by comparing human forecasts and model-based predictions.
+In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses.
+To allow for a direct comparison on an equal footing we employ a novel approach that elicits full probabilistic forecasts (Held, Meyer, and Bracher 2017) from participants, rather than constructing a predictive distribution from individual point predictions.
 
@@
 
-We created a crowd-sourced forecast (``crowd forecast''), elicited from participants through a web application {[}Citation{]}, as well as two semi-mechanistic models (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology.
-Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (CITATION).
+We created a crowd-sourced forecast (``crowd forecast''), elicited from participants through a web application (N.
+I.
+Bosse et al.
+2020), as well as two semi-mechanistic models (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology.
+Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (Bracher, Wolffram, et al.
+2021).
 All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (N.
-Bosse et al.~2020).
+Bosse et al.
+2020).
 This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub.
@@
 
-Data on daily reported test positive cases and deaths linked to Covid-19 were provided by the organisers of the German and Polish forecast hub (J.
-Bracher et al.~2021).
-Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) (``Download Historical Data (to 14 December 2020) on the Daily Number of New Reported COVID-19 Cases and Deaths Worldwide'' 2020).
-After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (``RKI - Coronavirus SARS-CoV-2 - Aktueller Lage-/Situationsbericht Des RKI Zu COVID-19'' n.d.).
-These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November (``Rozbieżności w statystykach koronawirusa.
+Data on daily reported test positive cases and deaths linked to Covid-19 were provided by the organisers of the German and Polish forecast hub.
+Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) ({``Download Historical Data (to 14 {December} 2020) on the Daily Number of New Reported {COVID}-19 Cases and Deaths Worldwide''} 2020).
+After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period ({``{RKI} - {Coronavirus SARS}-{CoV}-2 - {Aktueller Lage}-/{Situationsbericht} Des {RKI} Zu {COVID}-19''} n.d.).
+These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November ({``Rozbieżności w statystykach koronawirusa.
 22 tys.
-przypadków będą doliczone do ogólnej liczby wyników'' 16:07:56+0100)), changes in reporting over time and variation in testing regimes (e.g.~in Germany from the 11th of November on (Ärzteblatt 2020)).
+przypadków będą doliczone do ogólnej liczby wyników''} 16:07:56+0100)), changes in reporting over time and variation in testing regimes (e.g.~in Germany from the 11th of November on (Ärzteblatt 2020)).
 
@@
 Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information available until Monday.
-The application was built using the shiny and golem R packages (Chang et al.~2021; Fay et al.~2021) and is available in the crowdforecastr R package (N.
+The application was built using the shiny and golem R packages (Fay et al.
+2021; Chang et al.
+2021) and is available in the \texttt{crowdforecastr} R package (N.
 I.
-Bosse et al.~2020).
+Bosse et al.
+2020).
 To make a forecast in the application participants could select a predictive distribution, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values.
 The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e.~as \texttt{sd(c(log(value4)\ -\ log(value3),\ log(value3)\ -\ log(value2),\ ...))}).
-Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from (``COVID-19 Data Explorer'' n.d.).
+Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from ({``{COVID}-19 {Data Explorer}''} n.d.).
 These data included e.g.~notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
@@
 
-We used two models from the \texttt{EpiNow2} R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, et al.~2020).
+We used two models from the \texttt{EpiNow2} R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, et al.
+2020).
 The first of these models, here called ``renewal model,'' used the renewal equation (Fraser 2007) to predict reported cases and deaths.
@@
 The \(R_t\) value which was carried forward was slightly changed on November 9th 2020, where before that date the last `reliable' \(R_t\) estimate from X days before the forecast was used and after that the latest and most up-to-date (but possibly less stable) \(R_t\) estimate made on the actual forecast date was used.
-Reported cases and deaths were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, et al.~2020; DOI n.d.; ``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the Covid-19 Outbreak in England \textbar{} medRxiv'' n.d.) to model the time between infection and report date or death.
+Reported cases and deaths were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, et al.
+2020; DOI n.d.; {``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid}-19 Outbreak in {England} \textbar{} {medRxiv}''} n.d.) to model the time between infection and report date or death.
 The renewal model was used to predict cases as well as deaths, but the two were forecast completely independently, meaning that \(R_t\) was forecast once from reported cases and once from reported deaths.
@@
 The convolution model predicted deaths these as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
-Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model and a multiplicative day-of-the-week effect (Abbott, Hellewell, et al.~2020).
+Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model and a multiplicative day-of-the-week effect (Abbott, Hellewell, et al.
+2020).
 Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August.
@@
 
-For the main analysis we focused on two week ahead predictions, as predictions beyond this horizon are often unreliable due to rapidly changing conditions (J.
-Bracher et al.~2021).
+For the main analysis we focused on two week ahead predictions, as predictions beyond this horizon are often unreliable due to rapidly changing conditions (Bracher, Wolffram, et al.
+2021).
 Forecasts for cases were scored using the full period from October 2020 until March 2021.
@@
 
-Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Johannes Bracher et al.~2021), the absolute error, relative bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule (CITE GNEITING) and can be understood as a generalisation of the absolute error to quantile-based forecasts.
+Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Bracher, Ray, et al.
+2021), the absolute error, relative bias, and empirical coverage of the 50\% and 90\% prediction intervals.
+The WIS is a proper scoring rule (Gneiting and Raftery 2007) and can be understood as a generalisation of the absolute error to quantile-based forecasts.
 It can be decomposed into three separate penalties: forecast spread (i.e.~uncertainty of forecasts), over-prediction and under-prediction - lower values are always better.
@@
 For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \ref{fig:agg-performance-all}A) and locations (Figure \ref{fig:performance-locations-rel}A).
-For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 100\%) was 89\% for crowd forecasts and 140\% for the renewal model (Table \ref{tab:score-table-2}).
+For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \ref{tab:score-table-2}).
 Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was right-skewed, and average performance was heavily influenced by outliers (Figure \ref{fig:distribution-scores}).
@@
 Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (Cite US Hub, cite Seb SPI-M), or exclusively on human forecasts (e.g.~cite Tetlock, cite Grecchia, cite McAndrew).
+However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (e.g.
+Funk et al.
+2020; \textbf{esteecramerCOVID19ForecastHub2020?}; Cramer et al.
+2021), or exclusively on human forecasts Recchia, Freeman, and Spiegelhalter (2021).
 In contrast, we directly compared human and model-based forecasts.
-This is similar to the approach taken by Farrow et al., but extends it in several ways.
+This is similar to the approach taken by Farrow et al.
+(2017), but extends it in several ways.
 While Farrow et al.~only asked for point predictions and constructed a probabilistic forecast from these, we asked participants to quantify their uncertainty directly, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse aspects of the forecasts like overconfidence.
 In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight.
-In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (J.
-Bracher et al.~2021; E.
-Y.
-Cramer et al.~2021; S.
-Funk et al.~2020).
+In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (\textbf{esteecramerCOVID19ForecastHub2020?}; Cramer et al.
+2021; Bracher, Wolffram, et al.
+2021; Hub 2021; Funk et al.
+2020).
 
@@
 This adjustment is based on that implemented in the \texttt{epidemia} R package (Scott et al.
-(2020), cite (\textbf{bhatt202?})).
+2020; \textbf{bhatt202?}).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
+Ärzteblatt, Deutscher Ärzteverlag GmbH, Redaktion Deutsches.
+2020.
+{``SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an.''} {Deutsches Ärzteblatt}.
+November 3, 2020.
+\url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
+Bosse, Nikos I., Sam Abbott, EpiForecasts, and Sebastian Funk. 2020. \emph{Crowdforecastr: Eliciting Crowd Forecasts in r Shiny}. \url{https://doi.org/10.5281/zenodo.4618519}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
+Bosse, Nikos, Sam Abbott, EpiForecasts, and Sebastian Funk. 2020. \emph{Covid.german.forecasts: Forecasting Covid-19 Related Metrics for the German/Poland Forecast Hub}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
+Bracher, Johannes, Evan L.
+Ray, Tilmann Gneiting, and Nicholas G.
+Reich.
+2021.
+{``Evaluating Epidemic Forecasts in an Interval Format.''} \emph{PLoS Computational Biology} 17 (2): e1008618.
+\url{https://doi.org/10.1371/journal.pcbi.1008618}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
+Bracher, Johannes, Daniel Wolffram, J.
+Deuschel, K.
+Görgen, J.
+L.
+Ketterer, A.
+Ullrich, S.
+Abbott, et al.
+2021.
+{``Short-Term Forecasting of {COVID}-19 in {Germany} and {Poland} During the Second Wave -- a Preregistered Study.''} \emph{medRxiv}, January, 2020.12.24.20248826.
+\url{https://doi.org/10.1101/2020.12.24.20248826}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
+Chang, Winston, Joe Cheng, JJ Allaire, Carson Sievert, Barret Schloerke, Yihui Xie, Jeff Allen, Jonathan McPherson, Alan Dipert, and Barbara Borges.
+2021.
+\emph{Shiny: Web Application Framework for r}.
+\url{https://CRAN.R-project.org/package=shiny}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
+Colón-González, Felipe J., Leonardo Soares Bastos, Barbara Hofmann, Alison Hopkin, Quillon Harpham, Tom Crocker, Rosanna Amato, et al.
+2021.
+{``Probabilistic Seasonal Dengue Forecasting in {Vietnam}: A Modelling Study Using Superensembles.''} \emph{PLOS Medicine} 18 (3): e1003542.
+\url{https://doi.org/10.1371/journal.pmed.1003542}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-COVID19DataExplorer}{}}%
+{``{COVID}-19 {Data Explorer}.''} n.d. {Our World in Data}. Accessed May 30, 2021. \url{https://ourworldindata.org/coronavirus-data-explorer}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
+Cramer, Estee, Evan L.
+Ray, Velma K.
+Lopez, Johannes Bracher, Andrea Brennen, Alvaro J.
+Castro Rivadeneira, Aaron Gerding, et al.
+2021.
+{``Evaluation of Individual and Ensemble Probabilistic Forecasts of {COVID}-19 Mortality in the {US}.''} \emph{medRxiv}, February, 2021.02.03.21250974.
+\url{https://doi.org/10.1101/2021.02.03.21250974}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-CSETForetell}{}}%
 {``{CSET Foretell}.''} n.d. Accessed October 13, 2021. \url{https://www.cset-foretell.com/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
+Del Valle, Sara Y., Benjamin H.
+McMahon, Jason Asher, Richard Hatchett, Joceline C.
+Lega, Heidi E.
+Brown, Mark E.
+Leany, et al.
+2018.
+{``Summary Results of the 2014-2015 {DARPA Chikungunya} Challenge.''} \emph{BMC Infectious Diseases} 18 (1): 245.
+\url{https://doi.org/10.1186/s12879-018-3124-7}.
 
@@
 \url{https://epiforecasts.io/covid/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-DownloadHistoricalData2020a}{}}%
+{``Download Historical Data (to 14 {December} 2020) on the Daily Number of New Reported {COVID}-19 Cases and Deaths Worldwide.''} 2020.
+{European Centre for Disease Prevention and Control}.
+December 14, 2020.
+\url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
+Fay, Colin, Vincent Guyader, Sébastien Rochette, and Cervan Girard. 2021. \emph{Golem: A Framework for Robust Shiny Applications}. \url{https://github.com/ThinkR-open/golem}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
 Fraser, Christophe. 2007. {``Estimating {Individual} and {Household Reproduction Numbers} in an {Emerging Epidemic}.''} \emph{PLOS ONE} 2 (8): e758. \url{https://doi.org/10.1371/journal.pone.0000758}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
+Funk, Sebastian, Sam Abbott, B.
+D.
+Atkins, M.
+Baguelin, J.
+K.
+Baillie, P.
+Birrell, J.
+Blake, et al.
+2020.
+{``Short-Term Forecasts to Inform the Response to the {Covid}-19 Epidemic in the {UK}.''} \emph{medRxiv}, November, 2020.11.11.20220962.
+\url{https://doi.org/10.1101/2020.11.11.20220962}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
+Funk, Sebastian, Anton Camacho, Adam J.
+Kucharski, Rachel Lowe, Rosalind M.
+Eggo, and W.
+John Edmunds.
+2019.
+{``Assessing the Performance of Real-Time Epidemic Forecasts: A Case Study of {Ebola} in the {Western Area} Region of {Sierra Leone}, 2014-15.''} \emph{PLOS Computational Biology} 15 (2): e1006785.
+\url{https://doi.org/10.1371/journal.pcbi.1006785}.
 
@@
 {``Estimating the Generation Interval for Coronavirus Disease (COVID-19) Based on Symptom Onset Data, March 2020.''} \emph{Eurosurveillance} 25 (17).
+
+\leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
+Gneiting, Tilmann, and Adrian E Raftery.
+2007.
+{``Strictly Proper Scoring Rules, Prediction, and Estimation.''} \emph{Journal of the American Statistical Association} 102 (477): 359--78.
+\url{https://doi.org/10.1198/016214506000001437}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
+Held, Leonhard, Sebastian Meyer, and Johannes Bracher.
+2017.
+{``Probabilistic Forecasting in Infectious Disease Epidemiology: The 13th {Armitage} Lecture.''} \emph{Statistics in Medicine} 36 (22): 3443--60.
+\url{https://doi.org/10.1002/sim.7363}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-EuroHub}{}}%
+Hub, European COVID-19 Forecast. 2021. {``Forecasts of New Cases and Deaths Due to Covid-19 over the Next Four Weeks in Countries Across Europe and the UK.''} \url{https://covid19forecasthub.eu/}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-HypermindSupercollectiveIntelligence}{}}%
 {``Hypermind \textbar{} {Supercollective} Intelligence for Decision Makers.''} n.d. {Hypermind}. Accessed October 13, 2021. \url{https://www.hypermind.com/en/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
+Johansson, Michael A., Karyn M.
+Apfeldorf, Scott Dobson, Jason Devita, Anna L.
+Buczak, Benjamin Baugher, Linda J.
+Moniz, et al.
+2019.
+{``An Open Challenge to Advance Probabilistic Forecasting for Dengue Epidemics.''} \emph{Proceedings of the National Academy of Sciences} 116 (48): 24268--74.
+\url{https://doi.org/10.1073/pnas.1909865116}.
 
@@
 \url{https://doi.org/10.1101/2020.09.21.20196725}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
+McGowan, Craig J., Matthew Biggerstaff, Michael Johansson, Karyn M.
+Apfeldorf, Michal Ben-Nun, Logan Brooks, Matteo Convertino, et al.
+2019.
+{``Collaborative Efforts to Forecast Seasonal Influenza in the {United States}, 2015--2016.''} \emph{Scientific Reports} 9 (1, 1): 683.
+\url{https://doi.org/10.1038/s41598-018-36361-9}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-RKICoronavirusSARSCoV2a}{}}%
+{``{RKI} - {Coronavirus SARS}-{CoV}-2 - {Aktueller Lage}-/{Situationsbericht} Des {RKI} Zu {COVID}-19.''} n.d.
+Accessed May 30, 2021.
+\url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-RozbieznosciStatystykachKoronawirusa0100}{}}%
+{``Rozbieżności w statystykach koronawirusa.
+22 tys.
+przypadków będą doliczone do ogólnej liczby wyników.''} 16:07:56+0100.
+16:07:56+0100.
+\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
+Shaman, Jeffrey, and Alicia Karspeck.
+2012.
+{``Forecasting Seasonal Outbreaks of Influenza.''} \emph{Proceedings of the National Academy of Sciences} 109 (50): 20425--30.
+\url{https://doi.org/10.1073/pnas.1208772109}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
+Viboud, Cécile, Kaiyuan Sun, Robert Gaffey, Marco Ajelli, Laura Fumanelli, Stefano Merler, Qian Zhang, Gerardo Chowell, Lone Simonsen, and Alessandro Vespignani.
+2018.
+{``The {RAPIDD} Ebola Forecasting Challenge: Synthesis and Lessons Learnt.''} \emph{Epidemics}, The {RAPIDD Ebola Forecasting Challenge}, 22 (March): 13--21.
+\url{https://doi.org/10.1016/j.epidem.2017.08.002}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
+Yamana, Teresa K., Sasikiran Kandula, and Jeffrey Shaman.
+2016.
+{``Superensemble Forecasts of Dengue Outbreaks.''} \emph{Journal of The Royal Society Interface} 13 (123): 20160410.
+\url{https://doi.org/10.1098/rsif.2016.0410}.
+
 \end{CSLReferences}

### 2021-10-14 manuscript/manuscript.Rmd
update abstract

@@
 
-Model-based forecasts, which have played an important role in shaping public policy throughout the Covid-19 pandemic, represent an implicit combination of model assumptions and the researcher’s subjective opinion.
-This work explicitly separates human opinion and model-derived insights to assess and compare the relative strengths and weaknesses of both approaches.
-We compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from researchers and volunteers (“crowd forecasts”), against predictions from two semi-mechanistic epidemiological models.
-In addition, we compared these forecasts against an ensemble of model-based, but expert-tuned, forecasts, submitted to the German and Polish Forecast Hub by other research institutions (“Hub ensemble”).
-We found an ensemble of crowd-sourced predictions to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble at a two-week horizon: 0.89), but not when predicting deaths (rel.
+Model-based forecasts, which have played an important role in shaping public policy throughout the COVID-19 pandemic, represent an implicit combination of model assumptions and the researcher’s subjective opinion.
+This work analyses and compares human opinion against model-derived insights to discern relative strengths and weaknesses of both approaches.
+We compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from researchers and volunteers, against predictions from two semi-mechanistic epidemiological models.
+We also compared these forecasts against an ensemble of model-based, but expert-tuned, forecasts, submitted to the German and Polish Forecast Hub by other research institutions.
+In addition, we examined the effects of our contributions to the performance of the Hub ensemble.
+We found aggregated crowd forecasts to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble: 0.89), but not when predicting deaths (rel.
 WIS 1.26).
-Crowd forecasts were severely overconfident (55% and 75% coverage of the 90% prediction intervals for cases and deaths, respectively) when compared to model-based predictions.
-Performance of the untuned models deteriorated quickly with increasing forecast horizon when assumptions were no longer met (rel.
-WIS > 1.64 for all four week ahead predictions).
+Crowd forecasts were noticeably more overconfident (55% and 75% coverage of the 90% prediction intervals for cases and deaths, respectively) than model-based predictions.
+Performance of the semi-mechanistic models was good short-term, but deteriorated quickly over time when assumptions were no longer met.
 
@@
 
-Data on daily reported test positive cases and deaths linked to Covid-19 were provided by the organisers of the German and Polish forecast hub.
+Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish forecast hub.
 Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) [@DownloadHistoricalData2020a].

### 2021-10-14 manuscript/manuscript.Rmd
update manuscript

@@
 @delvalleSummaryResults201420152018; @farrowHumanJudgmentApproach2017] and now COVID-19 [e.g.
-@funkShorttermForecastsInform2020; @esteecramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @EuroHub].
+@funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @EuroHub].
 The aggregation of forecasts of COVID-19 cases, hospitalisations or deaths from multiple teams has created opportunities to compare the predictive performance of different models.
@@
 Previous work has examined human predictions in various contexts, such as geopolitics [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016], meta-science [@hoogeveenLaypeopleCanPredict2020; @ReplicationMarketsReliable], sports [@servan-schreiberPredictionMarketsDoes2004] and epidemiology [@farrowHumanJudgmentApproach2017; @mcandrewExpertJudgmentModel2020, @recchiaHowWellDid2021].
-Several prediction platforms [@metaculusPreliminaryLookMetaculus2020; @HypermindSupercollectiveIntelligence; @CSETForetell] and prediction markets [@Predictit] have been created to collate expert and non-expert predictions.
+Several prediction platforms [@metaculusPreliminaryLookMetaculus2020; @HypermindSupercollectiveIntelligence; @CSETForetell] and prediction markets [@PredictIt] have been created to collate expert and non-expert predictions.
 However, with the notable exception of Farrow et al., these crowd forecasts  were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats.
@@
 However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches [e.g.
-@funkShorttermForecastsInform2020; @esteecramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], or exclusively on human forecasts [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016; @mcandrewExpertJudgmentModel2020, @recchiaHowWellDid2021].
+@funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], or exclusively on human forecasts [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016; @mcandrewExpertJudgmentModel2020, @recchiaHowWellDid2021].
 In contrast, we directly compared human and model-based forecasts.
@@
 In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight.
-In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs [@esteecramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @EuroHub; @funkShorttermForecastsInform2020].
+In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs [@cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @EuroHub; @funkShorttermForecastsInform2020].
 
@@
 Projections that are meant to inform policy makers about possible scenarios may be different from forecasts meant to inform the general public, and yet again different from forecasts submitted with the goal of advancing open research and in order to allow public scrutiny and discussion about the merits of different approaches.
+
 Further work should explore the effects of human intervention on model-based forecasts in more detail.

### 2021-10-14 manuscript/manuscript.tex
update manuscript

@@
 
-Model-based forecasts, which have played an important role in shaping public policy throughout the Covid-19 pandemic, represent an implicit combination of model assumptions and the researcher's subjective opinion.
-This work explicitly separates human opinion and model-derived insights to assess and compare the relative strengths and weaknesses of both approaches.
-We compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from researchers and volunteers (``crowd forecasts''), against predictions from two semi-mechanistic epidemiological models.
-In addition, we compared these forecasts against an ensemble of model-based, but expert-tuned, forecasts, submitted to the German and Polish Forecast Hub by other research institutions (``Hub ensemble'').
-We found an ensemble of crowd-sourced predictions to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble at a two-week horizon: 0.89), but not when predicting deaths (rel.
+Model-based forecasts, which have played an important role in shaping public policy throughout the COVID-19 pandemic, represent an implicit combination of model assumptions and the researcher's subjective opinion.
+This work analyses and compares human opinion against model-derived insights to discern relative strengths and weaknesses of both approaches.
+We compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from researchers and volunteers, against predictions from two semi-mechanistic epidemiological models.
+We also compared these forecasts against an ensemble of model-based, but expert-tuned, forecasts, submitted to the German and Polish Forecast Hub by other research institutions.
+In addition, we examined the effects of our contributions to the performance of the Hub ensemble.
+We found aggregated crowd forecasts to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble: 0.89), but not when predicting deaths (rel.
 WIS 1.26).
-Crowd forecasts were severely overconfident (55\% and 75\% coverage of the 90\% prediction intervals for cases and deaths, respectively) when compared to model-based predictions.
-Performance of the untuned models deteriorated quickly with increasing forecast horizon when assumptions were no longer met (rel.
-WIS \textgreater{} 1.64 for all four week ahead predictions).
+Crowd forecasts were noticeably more overconfident (55\% and 75\% coverage of the 90\% prediction intervals for cases and deaths, respectively) than model-based predictions.
+Performance of the semi-mechanistic models was good short-term, but deteriorated quickly over time when assumptions were no longer met.
 
@@
 McGowan et al.
-2019; \textbf{reichCollaborativeMultiyearMultimodel2019?}; Shaman and Karspeck 2012; \textbf{biggerstaffResultsCentersDisease2016?}), dengue fever (e.g.
+2019; Reich et al.
+2019; Shaman and Karspeck 2012; Biggerstaff et al.
+2016), dengue fever (e.g.
 Johansson et al.
@@
 Funk et al.
-2020; \textbf{esteecramerCOVID19ForecastHub2020?}; Cramer et al.
+2020; Cramer et al.
+2020; Cramer et al.
 2021; Bracher, Wolffram, et al.
@@
 2004) and epidemiology Recchia, Freeman, and Spiegelhalter (2021).
-Several prediction platforms (Metaculus 2020; {``Hypermind \textbar{} {Supercollective} Intelligence for Decision Makers''} n.d.; {``{CSET Foretell}''} n.d.) and prediction markets (\textbf{Predictit?}) have been created to collate expert and non-expert predictions.
+Several prediction platforms (Metaculus 2020; {``Hypermind \textbar{} {Supercollective} Intelligence for Decision Makers''} n.d.; {``{CSET Foretell}''} n.d.) and prediction markets ({``{PredictIt}''} n.d.) have been created to collate expert and non-expert predictions.
 However, with the notable exception of Farrow et al., these crowd forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats.
@@
 
-Data on daily reported test positive cases and deaths linked to Covid-19 were provided by the organisers of the German and Polish forecast hub.
+Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish forecast hub.
 Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) ({``Download Historical Data (to 14 {December} 2020) on the Daily Number of New Reported {COVID}-19 Cases and Deaths Worldwide''} 2020).
@@
 Funk et al.
-2020; \textbf{esteecramerCOVID19ForecastHub2020?}; Cramer et al.
+2020; Cramer et al.
+2020; Cramer et al.
 2021), or exclusively on human forecasts Recchia, Freeman, and Spiegelhalter (2021).
@@
 In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight.
-In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (\textbf{esteecramerCOVID19ForecastHub2020?}; Cramer et al.
+In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (Cramer et al.
+2020; Cramer et al.
 2021; Bracher, Wolffram, et al.
@@
 This may pose a problem in the context of a forecast hub if teams have a different understanding about the purpose of a forecast.
-Projections that are meant to inform policy makers about possible scenarios may be different from forecasts meant to inform the general public, and yet again different from forecasts submitted with the goal of advancing open research and in order to allow public scrutiny and discussion about the merits of different approaches.\\
+Projections that are meant to inform policy makers about possible scenarios may be different from forecasts meant to inform the general public, and yet again different from forecasts submitted with the goal of advancing open research and in order to allow public scrutiny and discussion about the merits of different approaches.
+
 Further work should explore the effects of human intervention on model-based forecasts in more detail.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
+Biggerstaff, Matthew, David Alper, Mark Dredze, Spencer Fox, Isaac Chun-Hai Fung, Kyle S.
+Hickmann, Bryan Lewis, et al.
+2016.
+{``Results from the Centers for Disease Control and Prevention's Predict the 2013--2014 {Influenza Season Challenge}.''} \emph{BMC Infectious Diseases} 16 (1): 357.
+\url{https://doi.org/10.1186/s12879-016-1669-x}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
@@
 \url{https://doi.org/10.1101/2021.02.03.21250974}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
+Cramer, Estee, Nicholas G Reich, Serena Yijin Wang, Jarad Niemi, Abdul Hannan, Katie House, Youyang Gu, et al.
+2020.
+{``{COVID}-19 {Forecast Hub}: 4 {December} 2020 Snapshot.''} {Zenodo}.
+\url{https://doi.org/10.5281/zenodo.3963371}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-PredictIt}{}}%
+{``{PredictIt}.''} n.d. Accessed October 13, 2021. \url{https://www.predictit.org/}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
+Reich, Nicholas G., Logan C.
+Brooks, Spencer J.
+Fox, Sasikiran Kandula, Craig J.
+McGowan, Evan Moore, Dave Osthus, et al.
+2019.
+{``A Collaborative Multiyear, Multimodel Assessment of Seasonal Influenza Forecasting in the {United States}.''} \emph{Proceedings of the National Academy of Sciences} 116 (8): 3146--54.
+\url{https://doi.org/10.1073/pnas.1812594116}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-ReplicationMarketsReliable}{}}%

### 2021-10-14 analysis/analysis.Rmd
clean code for first Figure

@@
 }
+```
+
+# Visualisation of aggregate performance across horizons
+
+``` {r}
+# helper function to score forecasts
+score_helper <- function(data, summarise_by) {
+  scores <- eval_forecasts(data, 
+                           summarise_by = summarise_by, 
+                           quantiles = 0.5, 
+                           sd = TRUE)
+
+  # for cases, filter out redundant ensembles as convolution model only does 
+  # deaths (e.g. ensemble with all is identical to realised ensemble for cases)
+  scores <- scores %>%
+    filter(!(model %in% c("Hub-ensemble-with-all", 
+                          "Hub-ensemble-with-convolution", 
+                          "Hub-ensemble-with-all-mean", 
+                          "Hub-ensemble-with-convolution-mean") & 
+               target_type == "case")
+    )
+
+  setnames(scores, old = c("model", "sharpness"), 
+           new = c("Model", "dispersion"))
+}
+
+# helper function to create the WIS plot with its sub-components in panels A and B
+component_plot <- function(scores, type, colour_scheme, x = x, rel = relative,
+                           facet_formula, vals = NULL) {
+
+  # define colour values for plot
+  # for cases and ensembles, filter out identical ensembles
+  if (colour_scheme == "ensemble" & type == "case") {
+    scores <- scores %>%
+      filter(!(Model %in% c("Hub-ensemble-with-all", 
+                            "Hub-ensemble-with-convolution")))
+    vals <- vals[-c(3, 4)]
+  } else if (type == "case") {
+    vals <- vals[-1]
+  }
+
+  # pivot scores and rename WIS components
+  scores <- scores %>%
+    select(Model, target_type, dispersion, interval_score,
+           underprediction, overprediction, !!x) %>%
+    rename("Dispersion" = dispersion, 
+           "Over-prediction" = overprediction, 
+           "Under-prediction" = underprediction) %>%
+    filter(target_type == type) %>%
+    pivot_longer(names_to = "WIS components",
+                 cols = c(`Dispersion`, `Over-prediction`, `Under-prediction`)) %>%
+    mutate(`WIS components` = fct_relevel(`WIS components`, 
+                                          c("Dispersion", "Under-prediction", 
+                                            "Over-prediction")))
+
+  # compute relative version of the scores
+  if (rel) {
+    scores <- scores %>%
+      arrange(!!sym(x), target_type, interval_score) %>%
+      group_by(!!sym(x), target_type) %>%
+      mutate_at("value", ~ . / interval_score[Model %in% c("Hub-ensemble", 
+                                                           "Hub-ensemble-mean")])
+  }
+
+  # create plot
+  p <- scores %>%
+    ggplot(aes(x = reorder(Model, (interval_score)), y = value, fill = Model, 
+               group = Model, alpha = `WIS components`))
+
+  if (rel) {
+    p <- p + 
+      geom_hline(yintercept = 1, linetype = "dashed")
+  }
+
+  p <- p + 
+    scale_alpha_manual(values = c(1, 0.1, 0.6)) +
+    scale_fill_manual(values = vals) + 
+    geom_bar(stat = "identity", position = "stack",
+             color = "black",
+             size = 0.1,
+             width = 0.8) +
+    facet_wrap(as.formula(paste("~", x)), ncol = 4,
+               strip.position="bottom") + 
+    theme_minimal() + 
+    theme(axis.text.x = element_blank(), 
+          plot.title = element_text(hjust = 0.5, 
+                                    size = 8), 
+          legend.position = c(0.12, 0.83)) + 
+    labs(x = NULL, title = type, y = "WIS") + 
+    guides(fill = "none")
+
+  return(p)
+}
+
+# helper function to make subplots E - H
+plot_helper <- function(tmp = scores, xvar = x, y, rel = relative, 
+                        facet_formula, colour) {
+  if (rel) {
+    tmp <- tmp %>%
+      arrange(target_type, !!sym(xvar)) %>%
+      group_by(target_type, !!sym(xvar)) %>%
+      mutate_at(y, ~ . / .[Model %in% c("Hub-ensemble", 
+                                        "Hub-ensemble-mean")])
+  }
+
+  tmp %>%
+    ggplot(aes_string(x = xvar, y = y, group = "Model", color = "Model")) +
+    geom_point(position = position_dodge(width = 0.1)) +
+    geom_line(position = position_dodge(width = 0.1)) +
+    facet_wrap(facet_formula, scales = "free_y") +
+    theme_minimal() +
+    theme(legend.position = "bottom") +
+    scale_color_manual(values = colour) + 
+    scale_y_continuous(labels = scale_fn)
+}
+
+# function to create Figure 1
+aggregate_performance <- function(data, 
+                                  x = "horizon",
+                                  xlabel = "Forecast horizon",
+                                  output_dir = here("analysis", "plots"), 
+                                  plotname,
+                                  relative = FALSE,
+                                  facet_formula = ~ target_type, 
+                                  colour_scheme = c("normal", "ensemble"),
+                                  vals = NULL) {
+
+  # calculate scores
+  scores <- score_helper(data, c("model", "target_type", x))
+
+  # define colour values for the plot
+  if (colour_scheme[1] == "normal") {
+    vals <- coldeaths
+  } else {
+    vals <- colensemble
+  }
+
+  # plot with wis components (panels A and B) ----------------------------------
+  component_case <- component_plot(scores, "case", x = x, vals = vals, 
+                                   facet_formula = facet_formula, 
+                                   rel = relative, 
+                                   colour_scheme = colour_scheme[1])
+  component_death <- component_plot(scores, "death", x = x, vals = vals, 
+                                    facet_formula = facet_formula, 
+                                    rel = relative, 
+                                    colour_scheme = colour_scheme[1])
+
+  # plot with dispersion of forecasts in panel E -------------------------------
+  p_sharpness <- 
+    plot_helper(scores, y = "dispersion", rel = relative, xvar = x,
+                facet_formula = facet_formula, colour = vals) + 
+    labs(y = "Dispersion", x = NULL)
+
+  # bias plot in panel F -------------------------------------------------------
+  # define appropriate y limits
+  bias_limits <- max(abs(scores$bias)) * c(-1.1, 1.1) %>% 
+    round(2)
+  p_bias <- 
+    plot_helper(scores, y = "bias", rel = FALSE, colour = vals, xvar = x,
+                facet_formula = facet_formula) + 
+    labs(y = "Bias", x = NULL) +
+    geom_hline(yintercept = 0, linetype = "dashed") +
+    expand_limits(y=bias_limits)
+
+  # plot with absolute error of performance in panel G -------------------------
+  p_aem <-
+    plot_helper(scores, y = "aem", rel = relative, xvar = x,
+                facet_formula = facet_formula, colour = vals) + 
+    labs(y = "Absolute error", x = NULL)
+
+  # plot with sd of performance in panel H -------------------------------------
+  p_wis_sd <- 
+    plot_helper(scores, y = "interval_score_sd", rel = relative, xvar = x,
+                facet_formula = facet_formula, colour = vals) + 
+    labs(y = "WIS - sd", x = NULL)
+
+  # coverage plots (panel C and D) ---------------------------------------------
+  # calculate scores that also include the interval range
+  scores <- score_helper(data,  c("model", "target_type", x, "range"))
+
+  # take difference to Hub ensemble if relative
+  if (relative) {
+    scores <- scores %>%
+      arrange(target_type, range, !!sym(x)) %>%
+      group_by(target_type, range, !!sym(x)) %>%
+      mutate_at("coverage", ~ . - .[Model %in%  c("Hub-ensemble", 
+                                                  "Hub-ensemble-mean")])
+  }
+
+  p_cov50 <- scores %>%
+    filter(range == c(50)) %>%
+    plot_helper(y = "coverage", rel = FALSE, facet_formula = facet_formula, 
+                colour = vals, xvar = x) +
+    labs(y = "Diff. cov. - 50% PI", x = "") + 
+    scale_y_continuous(labels = scales::percent)
+
+  # if not relative, add a dashed line at 50%
+  if (!relative) {
+    p_cov50 <- p_cov50 + 
+      expand_limits(y=c(0, 1)) + 
+      labs(y = "Coverage - 50% PI", x = "") + 
+      geom_hline(yintercept = 0.5, linetype = "dashed") + 
+      scale_y_continuous(labels = scales::percent)
+    }
+
+  p_cov90 <-  scores %>%
+    filter(range == c(90)) %>%
+    plot_helper(y = "coverage", rel = FALSE, facet_formula = facet_formula, 
+                xvar = x, colour = vals) + 
+    labs(y = "Diff. cov. - 90% PI") + 
+    scale_y_continuous(labels = scales::percent)
+
+  # if not relative, add a dashed line at 90%
+  if (!relative) {
+    p_cov90 <- p_cov90 + 
+      expand_limits(y=c(0, 1)) + 
+      labs(y = "Coverage - 90% PI", x = "") + 
+      geom_hline(yintercept = 0.9, linetype = "dashed") + 
+      scale_y_continuous() + 
+      scale_y_continuous(labels = scales::percent)
+  }
+
+  # put all plots together -----------------------------------------------------
+  p_combined4 <- 
+    (component_case + component_death) / 
+    (p_cov50 + p_cov90) /
+    (p_sharpness + p_bias) /
+    (p_aem + p_wis_sd) +
+    plot_layout(guides = "collect", 
+                heights = c(1.3, 1, 1, 1)) &
+    plot_annotation(tag_levels = 'A')  &
+    theme(legend.position = 'bottom', 
+          legend.box="vertical", legend.margin=margin())
+
+    ggsave(here(output_dir, paste0(plotname, "-v4.png")), 
+           height = 9.1, width = 10)
+}
+
+# create plots with aggregate performance --------------------------------------
+# regular plot for Figure 1
+filtered_data[model %in% regular_models] %>%
+  aggregate_performance(plotname = "aggregate-performance-all")
+
+# plot with restricted time period for sensitivity analysis for SI
+filtered_data[model %in% regular_models] %>%
+  filter(!(forecast_date %in% as.character(forecast_dates$death_not_scored))) %>%
+  aggregate_performance(plotname = "aggregate-performance-all-late-period")
+
+# plot version that compares locations for SI
+filtered_data[model %in% regular_models & horizon == 2] %>%
+  aggregate_performance(plotname = "aggregate-performance-2-weeks-locations-all", 
+                        x = "location_name", 
+                        xlabel = NULL)
+
+# plot version that compares locations in relative terms for SI
+filtered_data[model %in% regular_models & horizon == 2] %>%
+  aggregate_performance(plotname = "aggregate-performance-2-weeks-locations-all-rel", 
+                        x = "location_name", 
+                        xlabel = NULL, relative = TRUE)
+
+# plot for different median ensembles (in relative terms) for SI
+filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]] %>%
+  # filter(!(model == "Hub-ensemble-with-all" & target_type == "case")) %>%
+  aggregate_performance(plotname = "aggregate-performance-rel-ensemble", 
+                        relative = TRUE, colour_scheme = "ensemble")
+
+# plot for different mean ensembles (in relative terms) for SI
+filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]] %>%
+  # filter(!(model == "Hub-ensemble-with-all" & target_type == "case")) %>%
+  aggregate_performance(plotname = "aggregate-performance-rel-ensemble-mean", 
+                        relative = TRUE, colour_scheme = "ensemble")
+
 ```
@@
 
-### Aggregate performance across different horizons
-
-``` {r}
-
-# function to make plot with mean of a given metric
-plot_helper <- function(tmp = scores, xvar = x, y, rel = relative, 
-                        facet_formula, colour) {
-  if (rel) {
-    tmp <- tmp %>%
-      arrange(target_type, !!sym(xvar)) %>%
-      group_by(target_type, !!sym(xvar)) %>%
-      mutate_at(y, ~ . / .[Model %in% c("Hub-ensemble", 
-                                        "Hub-ensemble-mean")])
-  }
-
-  tmp %>%
-    ggplot(aes_string(x = xvar, y = y, group = "Model", color = "Model")) +
-    geom_point(position = position_dodge(width = 0.1)) +
-    geom_line(position = position_dodge(width = 0.1)) +
-    facet_wrap(facet_formula, scales = "free_y") +
-    theme_minimal() +
-    theme(legend.position = "bottom") +
-    scale_color_manual(values = colour) + 
-    scale_y_continuous(labels = scale_fn)
-}
-
-# function for creating a component plot
-component_plot <- function(scores, type, colour_scheme, x = x, rel = relative,
-                           facet_formula, vals = NULL) {
-
- if (colour_scheme == "ensemble" & type == "case") {
-    # filter out ensembles not needed
-    scores <- scores %>%
-      filter(!(Model %in% c("Hub-ensemble-with-all", "Hub-ensemble-with-convolution")))
-    vals <- vals[-c(3, 4)]
- } else if (type == "case") {
-    vals <- vals[-1]
-  }
-
-  scores <- scores %>%
-    select(Model, target_type, dispersion, interval_score,
-           underprediction, overprediction, !!x) %>%
-    rename("Dispersion" = dispersion, 
-           "Over-prediction" = overprediction, 
-           "Under-prediction" = underprediction) %>%
-    filter(target_type == type) %>%
-    pivot_longer(names_to = "WIS components",
-                 cols = c(`Dispersion`, `Over-prediction`, `Under-prediction`)) %>%
-    mutate(`WIS components` = fct_relevel(`WIS components`, 
-                                          c("Dispersion", "Under-prediction", 
-                                            "Over-prediction")))
-
-  if (rel) {
-    scores <- scores %>%
-      arrange(!!sym(x), target_type, interval_score) %>%
-      group_by(!!sym(x), target_type) %>%
-      mutate_at("value", ~ . / interval_score[Model %in% c("Hub-ensemble", 
-                                                           "Hub-ensemble-mean")])
-  }
-
-  p <- scores %>%
-    ggplot(aes(x = reorder(Model, (interval_score)), y = value, fill = Model, 
-               group = Model, alpha = `WIS components`))
-
-  if (rel) {
-    p <- p + 
-      geom_hline(yintercept = 1, linetype = "dashed")
-  }
-
-  p <- p + 
-    scale_alpha_manual(values = c(1, 0.1, 0.6)) +
-    scale_fill_manual(values = vals) + 
-    geom_bar(stat = "identity", position = "stack",
-             color = "black",
-             size = 0.1,
-             width = 0.8) +
-    facet_wrap(as.formula(paste("~", x)), ncol = 4,
-               strip.position="bottom") + 
-    theme_minimal() + 
-    theme(axis.text.x = element_blank(), 
-          plot.title = element_text(hjust = 0.5, 
-                                    size = 8), 
-          legend.position = c(0.12, 0.83)) + 
-    labs(x = NULL, title = type, y = "WIS") + 
-    guides(fill = "none")
-
-  return(p)
-}
-
-score_helper <- function(data, summarise_by) {
-  scores <- eval_forecasts(data, 
-                           summarise_by = summarise_by, 
-                           quantiles = 0.5, 
-                           sd = TRUE) %>%
-    filter(!(model %in% c("Hub-ensemble-with-all", 
-                          "Hub-ensemble-with-convolution", 
-                          "Hub-ensemble-with-all-mean", 
-                          "Hub-ensemble-with-convolution-mean") & 
-               target_type == "case"))
-
-  setnames(scores, old = c("model", "sharpness"), 
-           new = c("Model", "dispersion"))
-}
-
-aggregate_performance <- function(data, 
-                                  x = "horizon",
-                                  xlabel = "Forecast horizon",
-                                  output_dir = here("analysis", "plots"), 
-                                  plotname,
-                                  relative = FALSE,
-                                  facet_formula = ~ target_type, 
-                                  colour_scheme = c("normal", "ensemble"),
-                                  vals = NULL) {
-
-  # create scores
-  scores <- score_helper(data, c("model", "target_type", x))
-
-  if (colour_scheme[1] == "normal") {
-    vals <- coldeaths
-  } else {
-    vals <- colensemble
-  }
-
-  # mean performance
-  p_mean <- 
-    plot_helper(scores, y = "interval_score", rel = relative, xvar = x, 
-                facet_formula = facet_formula, colour = vals) + 
-    labs(y = "mean WIS", x = NULL)
-
-    # absolute error of performance
-  p_aem <-
-    plot_helper(scores, y = "aem", rel = relative, xvar = x,
-                facet_formula = facet_formula, colour = vals) + 
-    labs(y = "Absolute error", x = NULL)
-
-  # sd of performance
-  p_wis_sd <- 
-    plot_helper(scores, y = "interval_score_sd", rel = relative, xvar = x,
-                facet_formula = facet_formula, colour = vals) + 
-    labs(y = "WIS - sd", x = NULL)
-
-  # sharpness of performance
-  p_sharpness <- 
-    plot_helper(scores, y = "dispersion", rel = relative, xvar = x,
-                facet_formula = facet_formula, colour = vals) + 
-    labs(y = "Dispersion", x = NULL)
-
-  # bias plot
-  bias_limits <- max(abs(scores$bias)) * c(-1.1, 1.1) %>% 
-    round(2)
-  p_bias <- 
-    plot_helper(scores, y = "bias", rel = FALSE, colour = vals, xvar = x,
-                facet_formula = facet_formula) + 
-    labs(y = "Bias", x = NULL) +
-    geom_hline(yintercept = 0, linetype = "dashed") +
-    expand_limits(y=bias_limits)
-
-  # plot with wis components
-  component_case <- component_plot(scores, "case", x = x, vals = vals, 
-                                   facet_formula = facet_formula, rel = relative, 
-                                   colour_scheme = colour_scheme[1])
-  component_death <- component_plot(scores, "death", x = x, vals = vals, 
-                                    facet_formula = facet_formula, rel = relative, 
-                                    colour_scheme = colour_scheme[1])
-  components <- component_case + component_death
-
-  # coverage plots 
-  scores <- score_helper(data,  c("model", "target_type", x, "range"))
-
-  if (relative) {
-    scores <- scores %>%
-      arrange(target_type, range, !!sym(x)) %>%
-      group_by(target_type, range, !!sym(x)) %>%
-      mutate_at("coverage", ~ . - .[Model %in%  c("Hub-ensemble", 
-                                                  "Hub-ensemble-mean")])
-  }
-
-  p_cov50 <- scores %>%
-    filter(range == c(50)) %>%
-    plot_helper(y = "coverage", rel = FALSE, facet_formula = facet_formula, 
-                colour = vals, xvar = x) +
-    labs(y = "Diff. cov. - 50% PI", x = "") + 
-    scale_y_continuous(labels = scales::percent)
-
-  if (!relative) {
-    p_cov50 <- p_cov50 + 
-      expand_limits(y=c(0, 1)) + 
-      labs(y = "Coverage - 50% PI", x = "") + 
-      geom_hline(yintercept = 0.5, linetype = "dashed") + 
-      scale_y_continuous(labels = scales::percent)
-    }
-
-  p_cov90 <-  scores %>%
-    filter(range == c(90)) %>%
-    plot_helper(y = "coverage", rel = FALSE, facet_formula = facet_formula, 
-                xvar = x, colour = vals) + 
-    labs(y = "Diff. cov. - 90% PI") + 
-    scale_y_continuous(labels = scales::percent)
-
-    if (!relative) {
-      p_cov90 <- p_cov90 + 
-        expand_limits(y=c(0, 1)) + 
-        labs(y = "Coverage - 90% PI", x = "") + 
-        geom_hline(yintercept = 0.9, linetype = "dashed") + 
-        scale_y_continuous() + 
-        scale_y_continuous(labels = scales::percent)
-    }
-
-    p_combined4 <- 
-      components / 
-      (p_cov50 + p_cov90) /
-      (p_sharpness + p_bias) /
-      (p_aem + p_wis_sd) +
-    plot_layout(guides = "collect", 
-                heights = c(1.3, 1, 1, 1)) &
-    plot_annotation(tag_levels = 'A')  &
-    theme(legend.position = 'bottom', 
-          legend.box="vertical", legend.margin=margin())
-
-    ggsave(here(output_dir, paste0(plotname, "-v4.png")), 
-           height = 9.1, width = 10)
-}
-
-filtered_data[model %in% regular_models] %>%
-  aggregate_performance(plotname = "aggregate-performance-all")
-
-filtered_data[model %in% regular_models] %>%
-  filter(!(forecast_date %in% as.character(forecast_dates$death_not_scored))) %>%
-  aggregate_performance(plotname = "aggregate-performance-all-late-period")
-
-# plot for locations
-filtered_data[model %in% regular_models & horizon == 2] %>%
-  aggregate_performance(plotname = "aggregate-performance-2-weeks-locations-all", 
-                        x = "location_name", 
-                        xlabel = NULL)
-
-# relative plots for locations
-filtered_data[model %in% regular_models & horizon == 2] %>%
-  aggregate_performance(plotname = "aggregate-performance-2-weeks-locations-all-rel", 
-                        x = "location_name", 
-                        xlabel = NULL, relative = TRUE)
-
-# plot for ensemble
-filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]] %>%
-  # filter(!(model == "Hub-ensemble-with-all" & target_type == "case")) %>%
-  aggregate_performance(plotname = "aggregate-performance-rel-ensemble", 
-                        relative = TRUE, colour_scheme = "ensemble")
-
-filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]] %>%
-  # filter(!(model == "Hub-ensemble-with-all" & target_type == "case")) %>%
-  aggregate_performance(plotname = "aggregate-performance-rel-ensemble-mean", 
-                        relative = TRUE, colour_scheme = "ensemble")
-
-```
-
 ## Plots with all forecasts

### 2021-10-14 manuscript/manuscript.Rmd
clean code for first Figure

@@
 The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e.
-as `sd(c(log(value4) - log(value3), log(value3) - log(value2), ...))`).
+as `sd(c(log(value4) - log(value3), log(value3) - log(value2), ...))`[a]).
 Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  [@COVID19DataExplorer].
@@
 The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths.
-It estimated the effective reproduction number $R_t$ (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infections times $R_t$.
-$R_t$ was assumed to stay constant in the future, roughly corresponding to continuing the latest trend in infections.
-The $R_t$ value which was carried forward was slightly changed on November 9th 2020, where before that date the last 'reliable' $R_t$ estimate from X days before the forecast was used and after that the latest and most up-to-date (but possibly less stable) $R_t$ estimate made on the actual forecast date was used.
-Reported cases and deaths were obtained by convolving predicted infections over data-based delay distributions [@epinow2; @doiCovid19TemporalVariation; @EvaluatingUseReproduction] to model the time between infection and report date or death.
-The renewal model was used to predict cases as well as deaths, but the two were forecast completely independently, meaning that $R_t$ was forecast once from reported cases and once from reported deaths.
+It estimated the effective reproduction number $R_t$ (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infection multiplied by $R_t$.
+$R_t$ was assumed to stay constant  beyond the forecast horizon, roughly corresponding to continuing the latest exponential trend in infections.
+On the 9th of November we altered the date when $R_t$ was assumed to be constant from two weeks prior to the date of the forecast to the forecast date.
+Reported notifications were obtained by convolving predicted infections over data-based delay distributions [@epinow2; @doiCovid19TemporalVariation; @EvaluatingUseReproduction] to model the time between infection and report date or death.
+The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately, meaning that $R_t$ was forecast once from reported cases and once from reported deaths.
 Death forecasts from the renewal model were therefore not informed by past cases.
-One submission of the renewal model on December 28th 2020 was belated and therefore not included in the official Forecast hub ensemble.
+One submission of the renewal model on December 28th 2020 was delayed and therefore not included in the official Forecast hub ensemble.
 
@@
 The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model.
-The convolution model predicted deaths these as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
-Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model and a multiplicative day-of-the-week effect [@epinow2].
-Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from [@kraemer2020epidemiological] with data available up to the 1st of August.
+The convolution model predicted deaths as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
+Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model with a multiplicative day-of-the-week effect [@epinow2].
+Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from [@kraemer2020epidemiological] with data available up to the 1st of August.
 All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan  [@rstan]  with each location and forecast target being fit separately.
@@
 To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available.
-To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) where scored only over the later period where are forecasts were available (see Section \@ref(sensitivity-analysis) in the SI).
+To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period where forecasts were available (see Section \@ref(sensitivity-analysis) in the SI).
 Results remained broadly unchanged.
@@
 
-\begin{align}
+\begin{align*}
   I_{t} &= I_0 \exp  \left(r t \right)  \\
@@
   r &\sim \mathcal{LN}(r_{obs}, 0.2) 
-\end{align}
+\end{align*}
 
-Where $I_{obs}$ and $r_{obs}$ are estimated form the first week of observed data.
+Where $I_{obs}$ and $r_{obs}$ are estimated from the first week of observed data.
 For the time window of the observed data infections were then modelled by weighting previous infections by the generation time and scaling by the instantaneous reproduction number.
@@
 
-\begin{align}
+\begin{align*}
   \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
@@
   C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
-\end{align}
+\end{align*}
 
 Where,
-\begin{align}
+\begin{align*}
      w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
@@
     \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
-\end{align}
+\end{align*}
 
@@
 
-\begin{align}
+\begin{align*}
      R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
@@
     \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
+\end{align*}
 
@@
 
-\begin{align}
+\begin{align*}
     \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
@@
     \alpha &\sim \mathcal{N}(0.005, 0.0025) 
-\end{align}
+\end{align*}
 
@@
 This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
-We estimated the delay between symyptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1% or 1769 samples of the available data  [@kraemer2020epidemiological; @covidregionaldata] and combining the posteriors for the mean and standard deviation of the log-normal distribution [@epinow2; @doiCovid19TemporalVariation; @EvaluatingUseReproduction; @rstan].
+We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1% or 1769 samples of the available data  [@kraemer2020epidemiological; @covidregionaldata] and combining the posteriors for the mean and standard deviation of the log-normal distribution [@epinow2; @doiCovid19TemporalVariation; @EvaluatingUseReproduction; @rstan].
 
 $GP_t$ is an approximate Hilbert space Gaussian process as defined in [@approxGP] using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20% of the number of days used in fitting).
-The lengthscale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
-The magnitude of the Gaussian process was assumed be normally distributed centred at 0 with a standard deviation of 0.1.
+The length scale of the Gaussian process[b] was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
+The magnitude of the Gaussian process was assumed to be normally distributed centred at 0 with a standard deviation of 0.1.
 
@@
 where $I^c_t = \sum_{s< t} I_s$ are cumulative infections by $t-1$ and $I'_t$ are the unadjusted infections defined above.
-This adjustment is based on that implemented in the `epidemia` R package [@epidemia; @bhatt202].
+This adjustment is based on that implemented in the `epidemia` R package [@epidemia; @bhattSemiMechanisticBayesianModeling].
 
@@
 
-The convolution model shares the same observation model as the renewal model but rather than assuming that an observation is predicted by itself instead assumes that it is predicted entirely by another observation after some parametric delay.
+The convolution model shares the same observation model as the renewal model but rather than assuming that an observation is predicted by itself using the renewal equation instead assumes that it is predicted entirely by another observation after some parametric delay.
 It can be defined mathematically as follows,
@@
 
-\begin{align}
+\begin{align*}
     \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
@@
 \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
+\end{align*}
 
@@
 Both models were implemented using the `EpiNow2` R package (version 1.3.3) [@epinow2].
-Each forecast target was fit independently for each model using Markov-chain Monte Carlo (MCMC) in stan [@rstan].
+Each forecast target was fitted independently for each model using Markov-chain Monte Carlo (MCMC) in stan [@rstan].
 A minimum of 4 chains were used with a warmup of 250 samples for the renewal equation-based model and 1000 samples for the convolution model.
 2000 samples total post warmup were used for the renewal equation model and 4000 samples for the convolution model.
-Different settings were chosen for each model to optimise compute time contigent on convergence.
+Different settings were chosen for each model to optimise compute time contingent on convergence.
 Convergence was assessed using the R hat diagnostic [@rstan].
@@
 \clearpage
+
+[a]-> maths?
+[b]that sentence seems odd. Is it supposed to be that way @Sam.Abbott@lshtm.ac.uk

### 2021-10-14 analysis/analysis.Rmd
clean code

@@
 
---------------------------------------------------------------------------------
-## Plot with Visualsiation of daily data
-
-```{r}
-df <- copy(dailytruth_data)[
-  , target_location := paste0(str_to_title(target_type), "s in ", location_name)
-][, target_end_date := as.Date(target_end_date)
-]
-
-df[weekdays(target_end_date) == "Sunday", sundays := target_end_date]
-
-weeklytruth <- copy(truth_data)[
-  , target_location := paste0(str_to_title(target_type), "s in ", location_name)
-]
-
-df %>%
-  ggplot(aes(y = true_value, x = target_end_date)) + 
-  # geom_point(size = 0.3, alpha = 0.4) + 
-  # geom_line(size = 0.5, alpha = 0.4) + 
-  geom_col(fill = "lightsteelblue", color = "white") + 
-  geom_line(data = weeklytruth, aes(y = true_value / 7)) + 
-  geom_point(data = weeklytruth, aes(y = true_value / 7), size = 0.3) +
-  # geom_vline(aes(xintercept = sundays), linetype = "dashed", alpha = 0.2) + 
-  facet_wrap( ~ target_location, scales = "free", ncol = 1) + 
-  labs(y = "Observed values", x = "Date") + 
-  scale_x_date(limits = c(min(forecast_dates$full_hub_period) - 28, 
-                          max(forecast_dates$full_hub_period + 21))) + 
-  theme_minimal()
-
-ggsave(here("analysis", "plots", "daily_truth.png"), width = 10, height = 8)
-```
-
---------------------------------------------------------------------------------
-## Plot with Visualsiation of x week ahead forecasts and scores
+# Plot with Visualsiation of x week ahead forecasts and scores
 
@@
 
-# create helper functions for the plot 
-# ------------------------------------------------------------------------------
-# truth_and_pred_plot = helper function for the visualisation truth and forecast
-# scores_over_time_plot = helper function for plotting scores over time
-# forecasts_and_scores = function that organises creation of the plots
-
+# helper function which creates panels A and C
 truth_and_pred_plot <- function(df, ttype = "case") {
 
+  # adjust distance between bars depending on case or death forecast
   if (ttype == "case") {
@@
 
+  # rename model column
   setnames(df, old = c("model"), new = c("Model"))
 
-  trend <- 
-    copy(epitrend)[, location_target := paste0(str_to_sentence(target_type), 
-                                               "s", " in ", location_name)]
-  setnames(trend, old = c("classification"), new = c("Classification"))
-
-  limits <- min(forecast_dates$full_hub_period) + 5 + 1:21 * 7
-
+  # define date limits for the plot
+  limits <- min(forecast_dates$full_hub_period) + 5 + 0:21 * 7
+
+  # create plot
   p <- df %>%
@@
                    position = position_dodge(width = dodgewidth)) + 
-    geom_point(data = trend[target_type == ttype], size = 0.7) +
-    geom_line(data = unfiltered_data[target_type == ttype & horizon == 2]) + 
+    geom_line(data = unfiltered_data[target_type == ttype & 
+                                       target_end_date %in% limits]) + 
     theme_minimal() + 
@@
     theme(legend.position = "bottom") + 
-    scale_x_date(limits = c(min(limits), max(limits)), 
+    scale_x_date(limits = c(min(limits) - 2, max(limits) + 2), 
                  minor_breaks = limits) + 
@@
 
+# helper function which creates panels B and D
 scores_over_time_plot <- function(scores, y = "mean_scores_ratio") {
-  limits <- min(forecast_dates$full_hub_period) + 5 + 1:21 * 7
+
+  # define plot limits on x axis
+  limits <- min(forecast_dates$full_hub_period) + 5 + 0:20 * 7
 
@@
     geom_line(aes(colour = model)) + 
-    geom_point(aes(colour = model, shape = classification)) + 
+    geom_point(aes(colour = model)) + 
     theme_minimal() + 
@@
 
+# helper function that creates the final plot
 forecasts_and_scores <- function(data, 
                                  output_dir = here("analysis", "plots"), 
-                                 plotname = "figure-forecasts", 
-                                 ensembles = FALSE) {
-
-  if (ensembles) {
-    colcases <- c(colcases[1:2], colcases[4], colcases[3])
-    coldeaths <- colcases
-  }
-
-  # create data.frame for plotting predictions ---------------------------------
-  df <- data[quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
-    dcast(... ~ quantile, value.var = "prediction")
-  df <- merge(
-    df[, c("classification", "speed") := NULL], 
-    copy(epitrend)[, c("forecast_date", "true_value") := NULL], 
-    by = c("target_end_date", "location_name", "target_type")
-  )
-
-  # create data.frame for plotting scores --------------------------------------
+                                 plotname = "figure-forecasts") {
+
+  # calculate scores
   summarise_by <- c("model", "horizon", "location_name", "target_type", 
@@
 
-  # copy epitrend data.frame and only keep necessary columns
-  epi_tmp <- copy(epitrend)
-  epi_tmp[, forecast_date := (as.Date(forecast_date))]
-  epi_tmp <- 
-    epi_tmp[, .(location_name, forecast_date, classification, target_type)] %>% 
-    unique()
-
-  # create plots for all horizons ----------------------------------------------
+  # create data.frame for plotting predictions 
+  df <- data[quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
+    dcast(... ~ quantile, value.var = "prediction")
+
+  # create plots for all horizons 
   for (i in 1:4) {
@@
       truth_and_pred_plot(ttype = "case") + 
-      scale_color_manual(values = colcases) + 
+      scale_color_manual(values = colcases, name = "Model") + 
       labs(y = "Forecasts and observed values", x = "")  + 
@@
       truth_and_pred_plot(ttype = "death")  + 
-      scale_color_manual(values = coldeaths) + 
-      annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
-               xmax = max(forecast_dates$death_not_scored) + 14,
+      scale_color_manual(values = coldeaths, name = "Model") + 
+      annotate('rect', xmin = min(forecast_dates$full_hub_period) + 5 + (i-1) * 7,
+               xmax = max(forecast_dates$death_not_scored) + 5 + (i-1) * 7,
                ymin = 0,
@@
       scores_target_forecastdate[horizon == i & target_type == "case"] %>%
-      merge(epi_tmp) %>%
       scores_over_time_plot(y = "interval_score") + 
-      scale_color_manual(values = colcases) + 
+      scale_color_manual(values = colcases, name = "Model") + 
       labs(y = "Weighted interval score", x = "") + 
@@
       scores_target_forecastdate[horizon == i & target_type == "death"] %>%
-      merge(epi_tmp) %>%
       scores_over_time_plot(y = "interval_score") + 
-      scale_color_manual(values = coldeaths) + 
+      scale_color_manual(values = coldeaths, name = "Model") + 
       annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
@@
   forecasts_and_scores()
-
-data <- unfiltered_data[model %in% c(regular_models, "Renewal-retrospective", "Convolution-retrospective")]
-
-unfiltered_data$model %>% unique()
-
-df$model %>% unique()
-# ensemble variants
-
-# models <- c("Hub-ensemble-all", "Crowd forecast", "Hub-ensemble", "Renewal")
-# unfiltered_data[model %in% models] %>%
-#   forecasts_and_scores(plotname = "figure-forecasts-ensembles", 
-#                        ensembles = TRUE)
-
-```
-
---------------------------------------------------------------------------------
-## Summary tables
+```
+
+# Create tables with scores
 
@@
 
-# create helper function to make table
-# ------------------------------------------------------------------------------
+# helper function to create the tables
 score_table <- function(scores, 
@@
                         full_width = TRUE) {
-  # copy data, change names, round column values and reduce to sign. digits
+
+  # change column names, round column values and reduce to sign. digits
   scores <- as.data.table(scores)
@@
 
-  # remove some cols, change column order, sort table and rename horizon
+  # remove some cols, change column order, sort table
   if (all(c("coverage_deviation", "rel. skill") %in% names(scores))) {
@@
 
+# function that actually makes the tables
 make_table <- function(data, 
@@
 
+  # get coverage values
   coverage <- eval_forecasts(
@@
 
+  # compute scores and merge with coverage values
   df <- eval_forecasts(
@@
 
-  # no idea how to do that in data.table: 
+  # add percentage values in brackets
   df <- df %>%
@@
 
+  # delete and rename a few columns
   del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
@@
   df[, (del_cols) := NULL] 
-
   setnames(df, old = c("interval_score_sd, sharpness"), 
@@
 
-  # tables for 1-2 weeks ahead and 3-4 weeks ahead
+  # create and save tables for 1-2 weeks ahead and 3-4 weeks ahead
   table <- score_table(df[horizon <= 2]) 
-
   saveRDS(object = table, 
@@
 # create tables
-# ------------------------------------------------------------------------------
-
+
+# regular models
 filtered_data[model %in% regular_models] %>%
@@
 
+# regular models with later period as sensitivity analysis in SI
 filtered_data[model %in% regular_models] %>%
@@
 
+# table for mean ensembles for SI
 filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]] %>%
@@
 
+# table for median ensembles for SI
 filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]] %>%
   make_table(plotname = "table_median-ensemble_scores")
-
-```
-
-### Tables for different phases of the epidemic
-
-```{r fig.height=10, fig.width=5}
-
-coverage <- eval_forecasts(
-  filtered_data[model %in% regular_models], 
-  summarise_by = c("horizon", "model", "target_type", "target_phase", "range"), 
-)[range %in% c(50, 90), 
-                   .(model, target_type, coverage, range, target_phase, horizon)] %>%
-  dcast(formula = ... ~ range, value.var = "coverage")
-
-df <- eval_forecasts(
-  filtered_data[model %in% regular_models], 
-  summarise_by = c("model", "horizon", "target_type", "target_phase"), 
-  metrics = c("interval_score", "coverage_deviation"),
-  sd = TRUE, 
-  quantiles = 0.5
-) %>%
-  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_phase", "target_type"))
-
-del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
-                        !(grepl("interval", names(df)))]
-del_cols <- c(del_cols, "coverage_deviation")
-df[, (del_cols) := NULL]
-
-setnames(df, old = c("interval_score_0.5", "interval_score_sd"), 
-         new = c("WIS - median", 
-                 "WIS - sd"))
-
-tables <- list()
-table_dfs <- list()
-targets <- unique(df$target_phase)
-
-# for horizon <= 2
-labels <- df[horizon <= 2][order(target_phase, horizon)]$target_phase
-table <- score_table(df[horizon <= 2, !"target_type"], group = FALSE) %>%
-  pack_rows(index = table(labels), indent = FALSE)
-save_kable(table, 
-           file = here("analysis", "plots", "table-phases-2.png"))
-
-# for horizon > 2
-labels <- df[horizon > 2][order(target_phase, horizon)]$target_phase
-table <- score_table(df[horizon > 2, !"target_type"], group = FALSE) %>%
-  pack_rows(index = table(labels), indent = FALSE)
-save_kable(table, 
-           file = here("analysis", "plots", "table-phases-4.png"))
-
-```
-
-### Look at ensemble forecasts
-
-#### Number of members in the ensemble
+```
+
+# Plot with Visualsiation of daily data
+
+```{r}
+
+# reformat daily truth data
+df <- copy(dailytruth_data)[
+  , target_location := paste0(str_to_title(target_type), "s in ", location_name)
+][, target_end_date := as.Date(target_end_date)
+]
+
+df[weekdays(target_end_date) == "Sunday", sundays := target_end_date]
+
+# reformat weekly truth data
+weeklytruth <- copy(truth_data)[
+  , target_location := paste0(str_to_title(target_type), "s in ", location_name)
+]
+
+# create plot
+df %>%
+  ggplot(aes(y = true_value, x = target_end_date)) + 
+  geom_col(fill = "lightsteelblue", color = "white") + 
+  geom_line(data = weeklytruth, aes(y = true_value / 7)) + 
+  geom_point(data = weeklytruth, aes(y = true_value / 7), size = 0.3) +
+  # geom_vline(aes(xintercept = sundays), linetype = "dashed", alpha = 0.2) + 
+  facet_wrap( ~ target_location, scales = "free", ncol = 1) + 
+  labs(y = "Observed values", x = "Date") + 
+  scale_x_date(limits = c(min(forecast_dates$full_hub_period) - 28, 
+                          max(forecast_dates$full_hub_period + 21))) + 
+  theme_minimal()
+
+ggsave(here("analysis", "plots", "daily_truth.png"), width = 10, height = 8)
+```
+
+# Number of member models in the Hub ensemble
+
 ```{r}
@@
        plot = p)
-
-```
-
-### Comparing ensembles with and without a model
+```
+
+# Plot with distribution of scores
 
 ```{r}
-
-comparison_ensembles <- function(models_to_plot) {
-  df <- unfiltered_data[model %in% models_to_plot &
-                          quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
-    dcast(... ~ quantile, value.var = "prediction")
-  df <- merge(
-    df[, c("classification", "speed") := NULL], 
-    copy(epitrend)[, c("forecast_date", "true_value") := NULL], 
-    by = c("target_end_date", "location_name", "target_type")
-  )
-
-  p <- df[grepl(2, target)] %>%
-    ggplot(aes(y = `0.5`, x = target_end_date, color = model)) +
-    geom_line() +
-    geom_line(aes(y = true_value), color = "black") + 
-    theme_minimal() + 
-    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
-    theme(legend.position = "bottom") + 
-    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
-    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
-                            max(forecast_dates$full_hub_period))) + 
-    labs(y = "Median forecast", x = "Date")
-  return(p)
-}
-
-models_plot <- c("Crowd forecast", "Hub-ensemble-with-crowd", "Hub-ensemble")
-p <- comparison_ensembles(models_plot)
-ggsave(here("analysis", "plots", "ensemble-with-and-without-crowd.png"), 
-       plot = p)
-
-models_plot <- c("Renewal", "Hub-ensemble-with-renewal", "Hub-ensemble")
-p <- comparison_ensembles(models_plot)
-ggsave(here("analysis", "plots", "ensemble-with-and-without-renewal.png"), 
-       plot = p)
-
-models_plot <- c("Renewal", "Crowd forecast", "Hub-ensemble-all", "Hub-ensemble")
-p <- comparison_ensembles(models_plot)
-ggsave(here("analysis", "plots", "ensemble-with-and-without-both.png"), 
-       plot = p)
-
-```
-
-------------------------------------------------------------------------
-
-## Analyse distribution of scores
-
-```{r}
+# score forecasts
 scores <- eval_forecasts(
@@
 
+# reformat column
+scores[, target_type := paste0(str_to_title(target_type), "s overall")]
+
+# display standard deviation for different models
 scores[, .(sd = sd(interval_score)), by = c("model", "target_type")]
 
-scores[, target_type := paste0(str_to_title(target_type), "s overall")]
-
-# scores for different phases of the epidemic
-scores[, target_phase := factor(target_phase, 
-                                levels = str_to_title(c("Cases - decreasing phase", 
-                                                        "Cases - unclear phase", 
-                                                        "Cases - increasing phase", 
-                                                        "Deaths - decreasing phase", 
-                                                        "Deaths - unclear phase", 
-                                                        "Deaths - increasing phase")))]
-
-distribution_plot_wis <- function(df, x = "interval_score", ranks = FALSE) {
+# helper function to create distribution plot
+distribution_plot_wis <- function(df, x = "interval_score", 
+                                  ranks = FALSE) {
 
@@
 
+# create plots for the distributions of WIS
 for (i in 1:4) {
+  # plot for locations combined
   p_combined_wis <- distribution_plot_wis(df = scores[horizon == i], 
@@
 
+  # plot for locations separate
   p_wis <- distribution_plot_wis(df = scores[horizon == i]) + 
@@
 
-  p_phases_wis <- distribution_plot_wis(df = scores[horizon == i]) + 
-    facet_wrap( ~ target_phase, scales = "free_x")
-
-  # pl_wis <- wrap_plots(p_combined_wis, p_wis, widths = c(1, 2)) / p_phases_wis + 
+  # combine plots and save
   pl_wis <- p_combined_wis + p_wis +
@@
          plot = pl_wis, height = 6, width = 9)
-
-}
-
-# plot with rank distributions
+}
+
+# create plots for the distributions of WIS rank
 for (i in 1:4) {
@@
 
-  p_phases_wis <- distribution_plot_wis(df = scores[horizon == i]) + 
-    facet_wrap( ~ target_phase, scales = "free_x")
-
-  # pl_wis <- wrap_plots(p_combined_wis, p_wis, widths = c(1, 2)) / p_phases_wis + 
   pl_wis <- p_combined_wis + p_wis +
@@
 }
-
-# same plot for absolute error
-p_combined_ae <- distribution_plot_wis(df = scores, 
-                                        x = "aem") +
-  facet_wrap(~ target_type, ncol = 1, scales = "free_x")
-
-p_ae <- distribution_plot_wis(df = scores, x = "aem") + 
-  theme(axis.title.y=element_blank(),
-        axis.text.y=element_blank(), 
-        axis.ticks.y = element_blank()) + 
-  facet_wrap(~ location_target, ncol = 2, scale = "free")
-
-```
-
-```{r}
-scores[, .(target_count = .N), by = c("target_phase", "model")]
-
-# p_phases <- distribution_plot(df = scores[model != "Baseline"]) + 
-#   facet_wrap( ~ target_phase)
-
-p_phases_ae <- distribution_plot_wis(df = scores, x = "aem") + 
-  facet_wrap( ~ target_phase, scales = "free_x")
-
-scores[, .(n = .N), by = "target_phase"]
-
-```
-
-```{r fig.height=10, fig.width=15}
-pl_ae <- wrap_plots(p_combined_ae, p_ae, widths = c(1, 2)) / p_phases_wis + 
-  plot_layout(guides = "collect") & 
-  plot_annotation(tag_levels = 'A') &
-  theme(legend.position = 'bottom')
-
-ggsave("plots/distribution_scores_ae.png", pl_ae, height = 9)
-
-```
-
-------------------------------------------------------------------------
-
-## WIS contributions
-
-```{r}
-# df <- data[grepl("2", target)] %>%
-#   merge(epitrend, 
-#         by = c("target_end_date", "location_name", "target_type"))
-
-scores_target <- eval_forecasts(
-  filtered_data[model %in% regular_models], 
-  summarise_by = c("model", "target_type", "classification"), 
-  compute_relative_skill = TRUE
-)
-
-scores_target[, target_phase := paste0(target_type, "s - ", 
-                                       classification, " phase")]
-
-wis_components(scores_target, 
-               facet_formula = ~ target_phase, 
-               scales = "free_x", 
-               relative_contributions = TRUE,
-               x_text_angle = 0) + 
-  theme(legend.position = "bottom") + 
-  coord_flip() + 
-  labs(x = NULL)
-
-ggsave(here("analysis", "plots", "wis-components.png"))
-
-```
-
-### Distribution of Bias over time
-
-```{r}
-# df <- data[grepl("2", target)] %>%
-#   merge(epitrend, 
-#         by = c("target_end_date", "location_name", "target_type"))
-
-scores_target <- eval_forecasts(
-  filtered_data[model %in% regular_models], 
-  summarise_by = c("model", "target_type", "classification", "forecast_date")
-)
-
-scores_target[, target_phase := paste0(target_type, "s - ", 
-                                       classification, " phase")]
-
-p <- scores_target[model %in% regular_models] %>%
-  distribution_plot_wis(x = "bias") + 
-  scale_x_continuous() + 
-  facet_wrap(~ target_phase, ncol = 3) + 
-  geom_vline(xintercept = 0, color = "black", size = 1.4) + 
-  labs(y = "Bias")
-
-ggsave(here("analysis", "plots", "distribution_bias_phases.png"), plot = p)
-```
-
-```{r, eval = TRUE}
-scores_full <- eval_forecasts(
-  filtered_data[model %in% regular_models], 
-  summarise_by = c("model", "location_target", "horizon", "forecast_date"), 
-  compute_relative_skill = FALSE
-)
-
-means <- scores_full[, .(meanval = mean(interval_score), 
-                         medianval = median(interval_score)), 
-                     by =c("model", "location_target", "horizon")]
-
-scores_full %>%
-  ggplot(aes(y = interval_score, x = horizon, 
-             fill = model, color = model)) +
-  geom_boxplot(outlier.shape = 21, coef = 1.5, 
-               width=0.5, alpha = 1, 
-               position = position_dodge2(width = 0.5)) + 
-  # geom_line(data = means, 
-  #           aes(group = model, y = meanval, color = model), 
-  #           position = position_dodge2(width = 0.5), 
-  #           size = 2) +
-  # theme(panel.background = element_rect(fill = "#e1f0fe")) +
-  scale_color_manual(values = coldeaths) + 
-  scale_fill_manual(values = coldeaths) + 
-  geom_point(data = means, 
-             mapping = aes(y = meanval, fill = model),
-             color = "black",
-             # fill = "red",
-             shape = 21,
-             size = 2,
-             position = position_dodge2(width = 0.5)) + 
-    geom_point(data = means, 
-             mapping = aes(y = medianval, fill = model),
-             color = "black",
-             # fill = "red",
-             shape = 22,
-             size = 2,
-             position = position_dodge2(width = 0.5)) + 
-  scale_y_log10() + 
-  facet_wrap( ~ location_target, scales = "free") + 
-  theme(legend.position = "bottom")
-
-ggsave("plots/scores_horizons.png")
-
-```
-
-------------------------------------------------------------------------
-
-## Calibration
-
-```{r, eval = TRUE}
-scores_target <- eval_forecasts(
-  filtered_data[model %in% regular_models], 
-  summarise_by = c("model", "target_type", "classification", "range", "quantile"), 
-  compute_relative_skill = FALSE, 
-  pit_plots = TRUE
-)
-
-interval_coverage(scores_target, 
-                  facet_formula = ~ target_type + classification)
-
-```
-
-```{r, eval = FALSE}
-scores <- list()
-# scores for restricted data set
-scores_full <- eval_forecasts(filtered_data, 
-                              summarise_by = c("model", "target_type", "target"), 
-                              compute_relative_skill = TRUE)
-
-scores[["full"]] <- 
-  scores_full[, .(model, target_type, scaled_rel_skill, interval_score, target,
-                  scenario = "full")]
-
-res <- rbindlist(scores)
-res %>%
-  ggplot(aes(x = scenario, y = scaled_rel_skill, color = model, group = model)) + 
-  geom_point() + 
-  facet_wrap( ~ target, scales = "free", ncol = 2) + 
-  theme(legend.position = "bottom")
-```
-
-## Number of expert forecasters
+```
+
+# Number of expert forecasters
 
@@
 
+# Number of forecasts over time
+
 ```{r num-forecasters, results = 'asis'}
-# check number of available forecasters
+# filter out ensembles and model-based forecasts
 dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
@@
 
+# display summary for the number of available forecasters
+dt[, .(sd = sd(`number of forecasters`), 
+       mean = mean(`number of forecasters`), 
+       min  = min(`number of forecasters`), 
+       max = max(`number of forecasters`), 
+       median = median(`number of forecasters`))]
+
+# display summary for the number of available forecasters by location and target
 dt[, .(sd = sd(`number of forecasters`), 
@@
    by = c("location_name", "target_type")] 
-
-dt[, .(sd = sd(`number of forecasters`), 
-       mean = mean(`number of forecasters`), 
-       min  = min(`number of forecasters`), 
-       max = max(`number of forecasters`), 
-       median = median(`number of forecasters`))]
-
 ```
@@
 ```{r num-forecasters2, results = 'asis'}
+# filter out ensembles and model-based forecasts
 dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
@@
 
+# plot number of forecasters over time
 dt %>%
@@
 
+# Number of submissions per forecaster
+
 ```{r, results = 'asis'}
@@
 ```
-
-## Number of expert forecasters
-
-```{r, results = 'asis'}
-
-dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
-                                        "EpiNow2_secondary", 
-                                        "EpiNow2")) & forecast_date %in% forecast_dates$unfiltered]
-
-crowddata <- merge_pred_and_obs(dt, truth_data)
-
-scores <- eval_forecasts(
-  data = crowddata[grepl("2", target)],
-  summarise_by = c("model", "target_type"), 
-  compute_relative_skill = TRUE, 
-  baseline = "EpiExpert-ensemble"
-)
-
-plot_df <- merge(num_fc, scores, by = "model")
-
-plot_df %>%
-  ggplot(aes(y = scaled_rel_skill, x = n_forecasts)) + 
-  geom_point() + 
-  geom_line() + 
-  theme_minimal() + 
-  facet_wrap(~ target_type) + 
-  labs(y = "Scaled relative skill", x = "Number of available submissions") + 
-  geom_smooth(method='lm', formula= y~x)
-
-ggsave("plots/skill-vs-forecast-freq.png")
-
-```
-
-## Plots with all forecasts
-
-```{r}
-# only select every second forecast date to stratify
-df <- unfiltered_data[model %in% regular_models &
-                        quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
-  dcast(... ~ quantile, value.var = "prediction")
-df <- merge(
-  df[, c("classification", "speed") := NULL], 
-  copy(epitrend)[, c("forecast_date", "true_value") := NULL], 
-  by = c("target_end_date", "location_name", "target_type")
-)
-
-df[, forecast_date := as.Date(forecast_date)]
-df[, i := as.numeric(forecast_date - as.Date(min(forecast_date))) %% 2 + 1]
-
-plot_forecast <- function(df, m = "Renewal") {
-  min_date <- min(forecast_dates$unfiltered)
-  plot_dates <- c((min_date - c(28, 21, 14, 7)), forecast_dates$unfiltered)
-  plot_dates <- plot_dates - 2
-  d <- copy(truth_data)[, location_target := paste0(str_to_sentence(target_type), 
-                                                    "s", " in ", location_name)]
-  daily <- copy(dailytruth_data)[, location_target := paste0(str_to_sentence(target_type), 
-                                                             "s", " in ", location_name)]
-  daily[, week := as_yearweek(target_end_date, firstday = 7L)]
-  daily[, sum_val := sum(true_value), by = c("week", "location_target")]
-  daily[, scaled_val := true_value - sum_val / 7]
-
-  df <- copy(df)[, forecast_date := as.factor(forecast_date)]
-
-  df[model == m] %>%
-    ggplot(aes(y = true_value, x = target_end_date)) + 
-    geom_line() + 
-    geom_line(data = d[target_end_date %in% plot_dates],
-              aes(y = true_value, x = target_end_date)) +
-    geom_line(data = daily[target_end_date >= min(plot_dates) & target_end_date <= max(plot_dates)],
-              aes(y = scaled_val, x = target_end_date), alpha = 0.4) +
-    geom_vline(aes(xintercept = as.Date(forecast_date), 
-                   color = forecast_date), alpha = 0.3, size = 0.4) + 
-    ggplot2::geom_ribbon(ggplot2::aes(ymin = `0.025`, ymax = `0.975`, 
-                                      group = forecast_date, 
-                                      fill = forecast_date), alpha = 0.3) +
-    ggplot2::geom_ribbon(ggplot2::aes(ymin = `0.25`, ymax = `0.75`, 
-                                      group = forecast_date, 
-                                      fill = forecast_date), alpha = 0.5) +
-    ggplot2::geom_line(aes(y = `0.5`,group = forecast_date, 
-                           colour = forecast_date), alpha = 1) +
-    geom_point() + 
-    theme_minimal() + 
-    facet_grid(location_target ~ i, scale = "free_y") + 
-    theme(legend.position = "bottom") 
-    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
-    # scale_y_log10() 
-}
-
-for (m in c("Renewal", "Convolution", "Crowd forecast")) {
-  p <- plot_forecast(df[horizon <= 2], m = m)
-
-  saveRDS(p, file = here("analysis", "plots", 
-                         paste0("all-forecasts-", m,".RDS")))
-
-  ggsave(here("analysis", "plots", 
-                         paste0("all-forecasts-", m,".png")), 
-         height = 15, width = 10)
-
-}
-
-```

### 2021-10-14 manuscript/manuscript.sh

@@ -2,3 +2,5 @@
 
 Rscript -e 'trackdown::update_file(file = "manuscript/manuscript.Rmd", gfile = "Comparing human and model-based forecasts of COVID-19 in Germany and Poland", hide_code = TRUE)'
 
+
+trackdown::download_file(file = "manuscript/manuscript.Rmd", gfile = "Comparing human and model-based forecasts of COVID-19 in Germany and Poland")

### 2021-10-14 analysis/analysis.Rmd
clean code and files

@@
   # delete and rename a few columns
+  setnames(df, 
+           old = c("interval_score_sd", "sharpness"), 
+           new = c("WIS - sd", "dispersion"))
   del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
@@
   df[, (del_cols) := NULL]
-  setnames(df, old = c("interval_score_sd, sharpness"), 
-           new = c("WIS - sd", "dispersion"))
 
@@
 # create tables
-
 # regular models

### 2021-10-14 manuscript/manuscript.Rmd
clean code and files

@@
 The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e.
-as `sd(c(log(value4) - log(value3), log(value3) - log(value2), ...))`[a]).
+as `sd(c(log(value4) - log(value3), log(value3) - log(value2), ...))`).
 Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  [@COVID19DataExplorer].
@@
 $GP_t$ is an approximate Hilbert space Gaussian process as defined in [@approxGP] using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20% of the number of days used in fitting).
-The length scale of the Gaussian process[b] was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
+The length scale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
 The magnitude of the Gaussian process was assumed to be normally distributed centred at 0 with a standard deviation of 0.1.
@@
 ```{r performance-locations, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-4.png")
+knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-v4.png")
 ```
@@
 \clearpage
-
-[a]-> maths?
-[b]that sentence seems odd. Is it supposed to be that way @Sam.Abbott@lshtm.ac.uk

### 2021-10-14 manuscript/manuscript.tex
clean code and files

@@
 The first of these models, here called ``renewal model,'' used the renewal equation (Fraser 2007) to predict reported cases and deaths.
-It estimated the effective reproduction number \(R_t\) (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infections times \(R_t\).
-\(R_t\) was assumed to stay constant in the future, roughly corresponding to continuing the latest trend in infections.
-The \(R_t\) value which was carried forward was slightly changed on November 9th 2020, where before that date the last `reliable' \(R_t\) estimate from X days before the forecast was used and after that the latest and most up-to-date (but possibly less stable) \(R_t\) estimate made on the actual forecast date was used.
-Reported cases and deaths were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, et al.
+It estimated the effective reproduction number \(R_t\) (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infection multiplied by \(R_t\).
+\(R_t\) was assumed to stay constant beyond the forecast horizon, roughly corresponding to continuing the latest exponential trend in infections.
+On the 9th of November we altered the date when \(R_t\) was assumed to be constant from two weeks prior to the date of the forecast to the forecast date.
+Reported notifications were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, et al.
 2020; DOI n.d.; {``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid}-19 Outbreak in {England} \textbar{} {medRxiv}''} n.d.) to model the time between infection and report date or death.
-The renewal model was used to predict cases as well as deaths, but the two were forecast completely independently, meaning that \(R_t\) was forecast once from reported cases and once from reported deaths.
+The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately, meaning that \(R_t\) was forecast once from reported cases and once from reported deaths.
 Death forecasts from the renewal model were therefore not informed by past cases.
-One submission of the renewal model on December 28th 2020 was belated and therefore not included in the official Forecast hub ensemble.
+One submission of the renewal model on December 28th 2020 was delayed and therefore not included in the official Forecast hub ensemble.
 
@@
 The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model.
-The convolution model predicted deaths these as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
-Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model and a multiplicative day-of-the-week effect (Abbott, Hellewell, et al.
+The convolution model predicted deaths as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
+Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model with a multiplicative day-of-the-week effect (Abbott, Hellewell, et al.
 2020).
-Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August.
+Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August.
 All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fit separately.
@@
 To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available.
-To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) where scored only over the later period where are forecasts were available (see Section \ref{sensitivity-analysis} in the SI).
+To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period where forecasts were available (see Section \ref{sensitivity-analysis} in the SI).
 Results remained broadly unchanged.
@@
   r &\sim \mathcal{LN}(r_{obs}, 0.2) 
-\end{align}
-
-Where \(I_{obs}\) and \(r_{obs}\) are estimated form the first week of observed data.
+\end{align*}
+
+Where \(I_{obs}\) and \(r_{obs}\) are estimated from the first week of observed data.
 For the time window of the observed data infections were then modelled by weighting previous infections by the generation time and scaling by the instantaneous reproduction number.
@@
 This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
-We estimated the delay between symyptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1\% or 1769 samples of the available data (Xu et al., n.d.; Abbott, Sherratt, et al.
+We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1\% or 1769 samples of the available data (Xu et al., n.d.; Abbott, Sherratt, et al.
 2020) and combining the posteriors for the mean and standard deviation of the log-normal distribution (Abbott, Hellewell, et al.
@@
 2020) using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20\% of the number of days used in fitting).
-The lengthscale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
-The magnitude of the Gaussian process was assumed be normally distributed centred at 0 with a standard deviation of 0.1.
+The length scale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
+The magnitude of the Gaussian process was assumed to be normally distributed centred at 0 with a standard deviation of 0.1.
 
@@
 This adjustment is based on that implemented in the \texttt{epidemia} R package (Scott et al.
-2020; \textbf{bhatt202?}).
+2020; Bhatt et al., n.d.).
 
@@
 2020).
-Each forecast target was fit independently for each model using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020).
+Each forecast target was fitted independently for each model using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020).
 A minimum of 4 chains were used with a warmup of 250 samples for the renewal equation-based model and 1000 samples for the convolution model.
 2000 samples total post warmup were used for the renewal equation model and 4000 samples for the convolution model.
-Different settings were chosen for each model to optimise compute time contigent on convergence.
+Different settings were chosen for each model to optimise compute time contingent on convergence.
 Convergence was assessed using the R hat diagnostic (Stan Development Team 2020).
@@
 \toprule
-  & Model & WIS & WIS - sd & Dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
+  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
 \midrule
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-4} \caption{Visualisation of aggregate performance metrics across locations.
+\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-v4} \caption{Visualisation of aggregate performance metrics across locations.
 A: mean weighted interval score (WIS) across horizons.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bhattSemiMechanisticBayesianModeling}{}}%
+Bhatt, Samir, Neil Ferguson, Seth Flaxman, Axel Gandy, Swapnil Mishra, and James A Scott. n.d. {``Semi-{Mechanistic Bayesian} Modeling of {COVID}-19 with {Renewal Processes},''} 14.
+
 \leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%

### 2021-10-14 manuscript/manuscript.tex
update citations

@@
 2014; Atanasov et al.
-2016), meta-science (Hoogeveen, Sarafoglou, and Wagenmakers 2020; {``Replication {Markets} -- {Reliable} Research Replicates\ldots you Can Bet on It.''} n.d.), sports (Servan-Schreiber et al.
-2004) and epidemiology Recchia, Freeman, and Spiegelhalter (2021).
-Several prediction platforms (Metaculus 2020; {``Hypermind \textbar{} {Supercollective} Intelligence for Decision Makers''} n.d.; {``{CSET Foretell}''} n.d.) and prediction markets ({``{PredictIt}''} n.d.) have been created to collate expert and non-expert predictions.
+2016), meta-science (Hoogeveen, Sarafoglou, and Wagenmakers 2020; ReplicationMarkets 2020), sports (Servan-Schreiber et al.
+2004) and epidemiology (Farrow et al.
+2017; McAndrew and Reich 2020; Recchia, Freeman, and Spiegelhalter 2021).
+Several prediction platforms (Metaculus 2020; Hypermind 2021; CSET Foretell 2021) and prediction markets (PredictIt 2021) have been created to collate expert and non-expert predictions.
 However, with the notable exception of Farrow et al., these crowd forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats.
@@
 
-We created a crowd-sourced forecast (``crowd forecast''), elicited from participants through a web application (N.
-I.
-Bosse et al.
-2020), as well as two semi-mechanistic models (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology.
+We created a crowd-sourced forecast (``crowd forecast''), elicited from participants through a web application (Bosse et al.
+2020b), as well as two semi-mechanistic models (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology.
 Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (Bracher, Wolffram, et al.
 2021).
-All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (N.
-Bosse et al.
-2020).
+All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (Bosse et al.
+2020a).
 This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub.
@@
 Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish forecast hub.
-Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) ({``Download Historical Data (to 14 {December} 2020) on the Daily Number of New Reported {COVID}-19 Cases and Deaths Worldwide''} 2020).
-After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period ({``{RKI} - {Coronavirus SARS}-{CoV}-2 - {Aktueller Lage}-/{Situationsbericht} Des {RKI} Zu {COVID}-19''} n.d.).
-These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November ({``Rozbieżności w statystykach koronawirusa.
-22 tys.
-przypadków będą doliczone do ogólnej liczby wyników''} 16:07:56+0100)), changes in reporting over time and variation in testing regimes (e.g.~in Germany from the 11th of November on (Ärzteblatt 2020)).
+Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) (ECDC 2020).
+After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (RKI 2021).
+These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November (Forsal.pl 2020)), changes in reporting over time and variation in testing regimes (e.g.~in Germany from the 11th of November on (Ärzteblatt 2020)).
 
@@
 2021; Chang et al.
-2021) and is available in the \texttt{crowdforecastr} R package (N.
-I.
-Bosse et al.
-2020).
+2021) and is available in the \texttt{crowdforecastr} R package (Bosse et al.
+2020b).
 To make a forecast in the application participants could select a predictive distribution, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values.
-The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e.~as \texttt{sd(c(log(value4)\ -\ log(value3),\ log(value3)\ -\ log(value2),\ ...))}).
+The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e.~as \(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
 Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from ({``{COVID}-19 {Data Explorer}''} n.d.).
@@
 Reported notifications were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, et al.
-2020; DOI n.d.; {``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid}-19 Outbreak in {England} \textbar{} {medRxiv}''} n.d.) to model the time between infection and report date or death.
+2020; epiforecasts.io/covid n.d.; Sherratt et al.
+2021) to model the time between infection and report date or death.
 The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately, meaning that \(R_t\) was forecast once from reported cases and once from reported deaths.
@@
 2020).
-Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August.
+Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al.
+2020) with data available up to the 1st of August.
 All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fit separately.
@@
 
+\hypertarget{the-crowdforecasting-app}{%
+\subsection{The crowdforecasting app}\label{the-crowdforecasting-app}}
+
+\begin{figure}[H]
+\includegraphics[width=1\linewidth,]{../crowd-forecast/Screenshot-forecasting-app} \caption{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).
+}\label{fig:screenshot}
+\end{figure}
+
 \hypertarget{further-details-on-the-semi-mechanistic-forecasting-models}{%
@@
 This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
-We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1\% or 1769 samples of the available data (Xu et al., n.d.; Abbott, Sherratt, et al.
+We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1\% or 1769 samples of the available data (Xu et al.
+2020; Abbott, Sherratt, et al.
 2020) and combining the posteriors for the mean and standard deviation of the log-normal distribution (Abbott, Hellewell, et al.
-2020; DOI n.d.; {``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid}-19 Outbreak in {England} \textbar{} {medRxiv}''} n.d.; Stan Development Team 2020).
+2020; epiforecasts.io/covid n.d.; {``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid}-19 Outbreak in {England} \textbar{} {medRxiv}''} n.d.; Stan Development Team 2020).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
+Bosse, Nikos I., Sam Abbott, EpiForecasts, and Sebastian Funk. 2020a. \emph{Covid.german.forecasts: Forecasting Covid-19 Related Metrics for the German/Poland Forecast Hub}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
-Bosse, Nikos I., Sam Abbott, EpiForecasts, and Sebastian Funk. 2020. \emph{Crowdforecastr: Eliciting Crowd Forecasts in r Shiny}. \url{https://doi.org/10.5281/zenodo.4618519}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
-Bosse, Nikos, Sam Abbott, EpiForecasts, and Sebastian Funk. 2020. \emph{Covid.german.forecasts: Forecasting Covid-19 Related Metrics for the German/Poland Forecast Hub}.
+---------. 2020b. \emph{Crowdforecastr: Eliciting Crowd Forecasts in r Shiny}. \url{https://doi.org/10.5281/zenodo.4618519}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-CSETForetell}{}}%
-{``{CSET Foretell}.''} n.d. Accessed October 13, 2021. \url{https://www.cset-foretell.com/}.
+\leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
+CSET Foretell. 2021. {``{CSET Foretell}.''} 2021. \url{https://www.cset-foretell.com/}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-doiCovid19TemporalVariation}{}}%
-DOI, Authors Affiliations Published Not published yet.
-n.d.
-{``Covid-19: Temporal Variation in Transmission During the {COVID}-19 Outbreak.''} {Covid-19}.
-Accessed May 30, 2021.
-\url{https://epiforecasts.io/covid/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-DownloadHistoricalData2020a}{}}%
-{``Download Historical Data (to 14 {December} 2020) on the Daily Number of New Reported {COVID}-19 Cases and Deaths Worldwide.''} 2020.
-{European Centre for Disease Prevention and Control}.
+\leavevmode\vadjust pre{\hypertarget{ref-ecdcDownloadHistoricalData2020}{}}%
+ECDC.
+2020.
+{``Download Historical Data (to 14 {December} 2020) on the Daily Number of New Reported {COVID}-19 Cases and Deaths Worldwide.''} {European Centre for Disease Prevention and Control}.
 December 14, 2020.
 \url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation}{}}%
+epiforecasts.io/covid. n.d. {``Covid-19: Temporal Variation in Transmission During the {COVID}-19 Outbreak.''} {Covid-19}. Accessed May 30, 2021. \url{https://epiforecasts.io/covid/}.
 
@@
 Fay, Colin, Vincent Guyader, Sébastien Rochette, and Cervan Girard. 2021. \emph{Golem: A Framework for Robust Shiny Applications}. \url{https://github.com/ThinkR-open/golem}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-forsal.plRozbieznosciStatystykachKoronawirusa2020}{}}%
+Forsal.pl.
+2020.
+{``Rozbieżności w statystykach koronawirusa.
+22 tys.
+przypadków będą doliczone do ogólnej liczby wyników.''} 2020.
+\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-HypermindSupercollectiveIntelligence}{}}%
-{``Hypermind \textbar{} {Supercollective} Intelligence for Decision Makers.''} n.d. {Hypermind}. Accessed October 13, 2021. \url{https://www.hypermind.com/en/}.
+\leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
+Hypermind. 2021. {``Hypermind \textbar{} {Supercollective} Intelligence for Decision Makers.''} {Hypermind}. 2021. \url{https://www.hypermind.com/en/}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-PredictIt}{}}%
-{``{PredictIt}.''} n.d. Accessed October 13, 2021. \url{https://www.predictit.org/}.
+\leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
+PredictIt. 2021. {``{PredictIt}.''} 2021. \url{https://www.predictit.org/}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ReplicationMarketsReliable}{}}%
-{``Replication {Markets} -- {Reliable} Research Replicates\ldots you Can Bet on It.''} n.d. Accessed October 13, 2021. \url{https://www.replicationmarkets.com/}.
+\leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
+ReplicationMarkets. 2020. {``Replication {Markets} -- {Reliable} Research Replicates\ldots you Can Bet on It.''} 2020. \url{https://www.replicationmarkets.com/}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RKICoronavirusSARSCoV2a}{}}%
-{``{RKI} - {Coronavirus SARS}-{CoV}-2 - {Aktueller Lage}-/{Situationsbericht} Des {RKI} Zu {COVID}-19.''} n.d.
-Accessed May 30, 2021.
+\leavevmode\vadjust pre{\hypertarget{ref-rkiRKICoronavirusSARSCoV22021}{}}%
+RKI.
+2021.
+{``{RKI} - {Coronavirus SARS}-{CoV}-2 - {Aktueller Lage}-/{Situationsbericht} Des {RKI} Zu {COVID}-19.''} 2021.
 \url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-RozbieznosciStatystykachKoronawirusa0100}{}}%
-{``Rozbieżności w statystykach koronawirusa.
-22 tys.
-przypadków będą doliczone do ogólnej liczby wyników.''} 16:07:56+0100.
-16:07:56+0100.
-\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
+Sherratt, Katharine, Sam Abbott, Sophie R.
+Meakin, Joel Hellewell, James D.
+Munday, Nikos Bosse, CMMID Covid-19 working Group, Mark Jit, and Sebastian Funk.
+2021.
+{``Exploring Surveillance Data Biases When Estimating the Reproduction Number: With Insights into Subpopulation Transmission of {Covid}-19 in {England},''} March, 2020.10.18.20214585.
+\url{https://doi.org/10.1101/2020.10.18.20214585}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
@@
 Xu, Bo, Bernardo Gutierrez, Sarah Hill, Samuel Scarpino, Alyssa Loskill, Jessie Wu, Kara Sewalk, et al.
-n.d.
+2020.
 {``Epidemiological Data from the nCoV-2019 Outbreak: Early Descriptions from Publicly Available Data.''} \url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}.

### 2021-10-15 R/datasets.R
update readme and data descriptions

@@ -8,72 +8,66 @@
 
 ##' Truth data used for the paper 
 ##'
-##' @name locations
+##' @name truth_data
 ##' @docType data
 "truth_data"
 
 ##' Daily truth data used for the paper 
 ##'
-##' @name locations
+##' @name dailytruth_data
 ##' @docType data
 "dailytruth_data"
 
 ##' Forecast data used for the paper 
 ##'
-##' @name locations
+##' @name prediction_data
 ##' @docType data
 "prediction_data"
 
 ##' Crowd forecast data used for the paper 
 ##'
-##' @name locations
+##' @name crowdforecast_data
 ##' @docType data
 "crowdforecast_data"
 
-##' Combined forecast and truth data used for the paper 
-##'
-##' @name locations
-##' @docType data
-"combined_data"
-
 ##' Forecast dates used for the paper 
 ##'
-##' @name locations
+##' @name forecast_dates
 ##' @docType data
 "forecast_dates"
 
-##' Pre-filtered data used for the paper
+##' Pre-filtered data used for the paper (with death forecasts restricted to the period after December 14th 2020)
 ##'
-##' @name locations
+##' @name filtered_data
 ##' @docType data
 "filtered_data"
 
-##' Unfiltered version of the data used for the paper
+##' Unfiltered version of the combined prediction and truth data used for the paper
 ##'
-##' @name locations
+##' @name unfiltered_data
 ##' @docType data
 "unfiltered_data"
 
-##' Classification of the epidemic into falling, rising etc
+##' Classification of the epidemic into falling, rising etc (not used)
 ##'
-##' @name locations
+##' @name epitrend
 ##' @docType data
 "epitrend"
 
 ##' Names of all ensemble models
 ##'
-##' @name locations
+##' @name ensemble_models
 ##' @docType data
 "ensemble_models"
 
 ##' Names of all regular models
 ##'
-##' @name locations
+##' @name regular_models
 ##' @docType data
 "regular_models"
 
 ##' Models included in the official hub ensemble
 ##'
-##' @name locations
+##' @name ensemble_members
 ##' @docType data
 "ensemble_members"

### 2021-10-15 data-raw/paper.R

@@ -167,9 +167,6 @@ combined_data <- merge_pred_and_obs(
   forecast_date := as.character(forecast_date)
 ]
 
-usethis::use_data(combined_data, overwrite = TRUE)
-
-
 # update data about the number of ensembles included in the Hub ----------------
 root_dir <- here("data-raw", "included_models")
 filenames <- list.files(root_dir)

### 2021-10-15 manuscript/manuscript.Rmd

@@
 
-Previous work has examined human predictions in various contexts, such as geopolitics [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016], meta-science [@hoogeveenLaypeopleCanPredict2020; @ReplicationMarketsReliable], sports [@servan-schreiberPredictionMarketsDoes2004] and epidemiology [@farrowHumanJudgmentApproach2017; @mcandrewExpertJudgmentModel2020, @recchiaHowWellDid2021].
-Several prediction platforms [@metaculusPreliminaryLookMetaculus2020; @HypermindSupercollectiveIntelligence; @CSETForetell] and prediction markets [@PredictIt] have been created to collate expert and non-expert predictions.
+Previous work has examined human predictions in various contexts, such as geopolitics [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016], meta-science [@hoogeveenLaypeopleCanPredict2020; @replicationmarketsReplicationMarketsReliable2020], sports [@servan-schreiberPredictionMarketsDoes2004] and epidemiology [@farrowHumanJudgmentApproach2017; @mcandrewExpertJudgmentModel2020; @recchiaHowWellDid2021].
+Several prediction platforms [@metaculusPreliminaryLookMetaculus2020; @hypermindHypermindSupercollectiveIntelligence2021; @csetforetellCSETForetell2021] and prediction markets [@predictitPredictIt2021] have been created to collate expert and non-expert predictions.
 However, with the notable exception of Farrow et al., these crowd forecasts  were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats.
@@
 Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish forecast hub.
-Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) [@DownloadHistoricalData2020a].
-After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period  [@RKICoronavirusSARSCoV2a].
-These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November [@RozbieznosciStatystykachKoronawirusa0100]), changes in reporting over time and variation in testing regimes (e.g.
+Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) [@ecdcDownloadHistoricalData2020].
+After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period  [@rkiRKICoronavirusSARSCoV22021].
+These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November [@forsal.plRozbieznosciStatystykachKoronawirusa2020]), changes in reporting over time and variation in testing regimes (e.g.
 in Germany from the 11th of November on [@aerzteblattSARSCoV2DiagnostikRKIPasst2020]).
@@
 The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e.
-as `sd(c(log(value4) - log(value3), log(value3) - log(value2), ...))`).
+as $\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )$).
 Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  [@COVID19DataExplorer].
@@
 On the 9th of November we altered the date when $R_t$ was assumed to be constant from two weeks prior to the date of the forecast to the forecast date.
-Reported notifications were obtained by convolving predicted infections over data-based delay distributions [@epinow2; @doiCovid19TemporalVariation; @EvaluatingUseReproduction] to model the time between infection and report date or death.
+Reported notifications were obtained by convolving predicted infections over data-based delay distributions [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation; @sherrattExploringSurveillanceData2021] to model the time between infection and report date or death.
 The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately, meaning that $R_t$ was forecast once from reported cases and once from reported deaths.
@@
 
+## The crowdforecasting app
+
+```{r}
+caption <- "Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021). "
+```
+
+```{r screenshot, fig.cap=caption}
+knitr::include_graphics("../crowd-forecast/Screenshot-forecasting-app.png")
+```
+
 ## Further details on the semi-mechanistic forecasting models
@@
 This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
-We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1% or 1769 samples of the available data  [@kraemer2020epidemiological; @covidregionaldata] and combining the posteriors for the mean and standard deviation of the log-normal distribution [@epinow2; @doiCovid19TemporalVariation; @EvaluatingUseReproduction; @rstan].
+We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1% or 1769 samples of the available data  [@kraemer2020epidemiological; @covidregionaldata] and combining the posteriors for the mean and standard deviation of the log-normal distribution [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation; @EvaluatingUseReproduction; @rstan].
 

### 2021-10-15 manuscript/manuscript.Rmd
update author list
remove old author statement

@@
     keep_tex:  true
+    toc: false
 bibliography:
@@
 
-*Anonymous Alpaca and many friends*
+Target journal: eLife
+
+*Nikos I. Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy Quilty, CMMID Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk*
 

### 2021-11-18 manuscript/manuscript.Rmd
incorporate google docs feedback

@@
 
-*Nikos I. Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy Quilty, CMMID Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk*
+*Nikos I. Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy J. Quilty, Mark Jit, CMMID Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk*
 
@@
 
-Model-based forecasts, which have played an important role in shaping public policy throughout the COVID-19 pandemic, represent an implicit combination of model assumptions and the researcher’s subjective opinion.
-This work analyses and compares human opinion against model-derived insights to discern relative strengths and weaknesses of both approaches.
-We compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from researchers and volunteers, against predictions from two semi-mechanistic epidemiological models.
-We also compared these forecasts against an ensemble of model-based, but expert-tuned, forecasts, submitted to the German and Polish Forecast Hub by other research institutions.
-In addition, we examined the effects of our contributions to the performance of the Hub ensemble.
-We found aggregated crowd forecasts to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble: 0.89), but not when predicting deaths (rel.
-WIS 1.26).
-Crowd forecasts were noticeably more overconfident (55% and 75% coverage of the 90% prediction intervals for cases and deaths, respectively) than model-based predictions.
-Performance of the semi-mechanistic models was good short-term, but deteriorated quickly over time when assumptions were no longer met.
+Forecasts based on epidemiological modelling have played an important role in shaping public policy throughout the COVID-19 pandemic.
+This modelling combines knowledge about infectious disease dynamics with the subjective opinion of the researcher who develops and refines the model and often also adjusts model outputs.
+Developing a forecast model is difficult, resource- and time-consuming.
+It is therefore worth asking what modelling is able to add beyond the subjective opinion of the researcher alone.
+To investigate this, we analysed different real-time forecasts of cases of and deaths from COVID-19 in Germany and Poland over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
+We compared crowd forecasts elicited from researchers and volunteers, against a) forecasts from two semi-mechanistic models based on common epidemiological assumptions and b) the ensemble of all other models submitted to the Forecast Hub.
+We found crowd forecasts, despite being overconfident, to outperform all other methods across all forecast horizons when forecasting cases (weighted interval score relative to the Hub ensemble 2 weeks ahead: 0.89).
+Forecasts based on computational models performed comparably better when predicting deaths (rel.
+WIS 1.26), suggesting that epidemiological modelling and human judgement can complement each other in important ways.
 
@@
 
-Infectious disease forecasting has a long tradition and has helped inform public health decisions about (among others) influenza [e.g.
+Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza [e.g.
 @mcgowanCollaborativeEffortsForecast2019; @reichCollaborativeMultiyearMultimodel2019; @shamanForecastingSeasonalOutbreaks2012; @biggerstaffResultsCentersDisease2016], dengue fever [e.g.
@@
 @delvalleSummaryResults201420152018; @farrowHumanJudgmentApproach2017] and now COVID-19 [e.g.
-@funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @EuroHub].
-The aggregation of forecasts of COVID-19 cases, hospitalisations or deaths from multiple teams has created opportunities to compare the predictive performance of different models.
-Yet it has been difficult to discern which factors lead to good COVID-19 forecasts.
-Answering this question is complicated by the varying and generally unobserved degree of manual expert intervention.
-Model-based forecasts usually represent an implicit combination of human judgement and model-derived insights, in the sense that forecasts have been generated with the help of epidemiological or statistical models, but throughout the process were manually changed and adjusted according to the researchers’ judgement.
+@funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021; @EuroHub].
+Applications of epidemiological models differ in the way they make statements about the future.
+Forecasts aim to predict the future as it will occur, while scenario modelling and projections aim to represent what the future could look like under certain scenario assumptions or if conditions stayed the same as they were in the past.
+Forecasts can be judged by comparing them against observed data.
+Since it is much harder to fairly assess the accuracy and usefulness of projections and scenario modelling in the same way, this work focuses on forecasts, which represent only a subset of all epidemiological modelling.
 
-Previous work has examined human predictions in various contexts, such as geopolitics [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016], meta-science [@hoogeveenLaypeopleCanPredict2020; @replicationmarketsReplicationMarketsReliable2020], sports [@servan-schreiberPredictionMarketsDoes2004] and epidemiology [@farrowHumanJudgmentApproach2017; @mcandrewExpertJudgmentModel2020; @recchiaHowWellDid2021].
+Since March 2020, forecasts of COVID-19 from multiple teams have been collected, aggregated and compared by Forecast Hubs such as the US Forecast Hub [@cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], the German and Polish Forecast Hub [@bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021] and the European Forecast Hub [@EuroHub].
+Often, different individual forecasts are combined into a single forecast, e.g.
+by taking the mean or median of all forecasts.
+These ensemble forecasts usually tend to perform better and more consistently than individual forecasts [see e.g.
+@yamanaSuperensembleForecastsDengue2016; reichAccuracyRealtimeMultimodel2019].
+
+Individual computational models usually rely to varying degrees on mechanistic assumptions about infectious disease dynamics (such as SIR-type compartmental models that aim to represent how individuals move from being susceptible to infected and then recovered or dead) or are more statistical in nature (such as time series models that detect statistical patterns without explicitly modelling disease dynamics).
+How exactly such a mathematical or computational model is constructed and which assumptions are made depends on subjective opinion and judgement of the researcher who develops and refines the model.
+Models are commonly adjusted and improved based on whether the model output looks plausible to the researchers involved.
+
+The process of model construction and refinement is laborious and time-consuming, and it is therefore worth asking what modelling can add beyond the subjective judgment of the researcher alone.
+In this work, we ask this question specifically in the context of predictive performance, and set aside other advantages of epidemiological modelling (such as reproducibility or the ability to obtain a deeper fundamental understanding of how diseases spread).
+One natural way to do this is to compare the predictive performance of forecasts based on computational models (“model-based forecasts”) against forecasts made by individual humans without explicit use of a computer model (“direct human forecasts”) or a combination of multiple such forecasts (“crowd forecasts”).
+
+Previous work has examined such direct human forecasts in various contexts, such as geopolitics [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016], meta-science [@hoogeveenLaypeopleCanPredict2020; @replicationmarketsReplicationMarketsReliable2020], sports [@servan-schreiberPredictionMarketsDoes2004] and epidemiology [@farrowHumanJudgmentApproach2017; @mcandrewExpertJudgmentModel2020; @recchiaHowWellDid2021].
 Several prediction platforms [@metaculusPreliminaryLookMetaculus2020; @hypermindHypermindSupercollectiveIntelligence2021; @csetforetellCSETForetell2021] and prediction markets [@predictitPredictIt2021] have been created to collate expert and non-expert predictions.
-However, with the notable exception of Farrow et al., these crowd forecasts  were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats.
-Farrow et al.
-found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available.
-They tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown there and then.
+However, with the notable exception of @farrowHumanJudgmentApproach2017, these forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) prediction formats.
+Direct human forecasts may be able to take into account insights and relationships between variables which are hard to specify using epidemiological models.
+However, it is not entirely clear in which situations human forecasts perform well or badly.
+For example, @farrowHumanJudgmentApproach2017 found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available.
+However, humans tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown there and then.
 
-In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses.
-To allow for a direct comparison on an equal footing we employ a novel approach that elicits full probabilistic forecasts [@heldProbabilisticForecastingInfectious2017] from participants, rather than constructing a predictive distribution from individual point predictions.
+In this study, we analyse the performance of direct human forecasts relative to model-based forecasts and discuss the added benefit of epidemiological modelling over human judgement alone.
+As a case study, we use different forecasts, involving varying degrees of human intervention, which we submitted in real time to the German and Polish Forecast Hub.
+In contrast to @farrowHumanJudgmentApproach2017 we elicited not only point predictions, but full predictive distributions (“probabilistic forecasts”)  [@heldProbabilisticForecastingInfectious2017] from participants.
+This allows us to compare not only predictive accuracy, but also how well human forecasters and model-based forecasts were able to quantify the appropriate forecast uncertainty.
 
@@
 
-We created a crowd-sourced forecast (“crowd forecast”), elicited from participants through a web application [@crowdforecastr], as well as two semi-mechanistic models ("renewal model" and "convolution model") informed by basic assumptions about COVID-19 epidemiology.
-Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub [@bracherShorttermForecastingCOVID192021].
+We created and submitted the following forecasts to the German and Polish Forecast Hub: 1) a direct human forecast (henceforth called “crowd forecast”), elicited from participants through a web application [@crowdforecastr] and 2) two semi-mechanistic model-based forecasts ("renewal model" and "convolution model") informed by basic assumptions about COVID-19 epidemiology.
+While the two semi-mechanistic forecasts were necessarily shaped by our implicit assumptions and decisions, they were designed such as to minimise the amount of human intervention involved.
+For example, we refrained from adjusting model outputs or refining the models based on past performance.
+Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub [@bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021].
 All code and tools necessary to generate the forecasts and make a forecast submission are available in the `covid.german.forecasts` R package [@covidgermanforecasts].
 This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub.
-Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the Forecast Hub.
+Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the German and Polish Forecast Hub.
 
@@
 The German and Polish Forecast Hub elicits predictions for various COVID-19 related forecast targets from different research institutions every week.
-Forecasts had to be made every Monday (with submissions allowed until Tuesday 3pm) using data available until Monday 11.59pm.
-We submitted forecasts for incident and cumulative weekly reported numbers of cases and deaths from COVID-19 on a national level in Germany and Poland over a one to four week forecast horizon.
-Weeks were defined as epiweeks starting on Sunday and ending on Saturday, meaning that forecast horizons were in fact 5, 12, 19 and 26 days.
-Submissions were required in a quantile-based format with 23 quantiles at levels 0.01, 0.025, 0.05, 0.10, 0.15, ..., 0.95, 0.975, 0.99.
-Forecasts submitted to the Forecast Hub were combined to different ensembles every week, with the median ensemble being the default ensemble shown on all official Forecast hub visualisations.
+Forecasts had to be made every Monday (with submissions allowed until Tuesday 3pm) and were permitted to use any data that was available by Monday 11.59pm.
+We submitted forecasts for incident and cumulative weekly reported numbers of cases of and deaths from COVID-19 on a national level in Germany and Poland over a one to four week forecast horizon.
+Forecasts were submitted on Mondays, but weeks were defined as ending on a Saturday (and starting on Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26 days.
+Submissions were required in a quantile-based format with 23 quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10, 0.15, ..., 0.95, 0.975, 0.99.
+Forecasts submitted to the Forecast Hub were combined into different ensembles every week, with the median ensemble (i.e., the $\alpha$-quantile of the ensemble is given by the median of all submitted $\alpha$-quantiles) being the default ensemble shown on all official Forecast hub visualisations (https://kitmetricslab.github.io/forecasthub/forecast).
 
 Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish forecast hub.
-Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) [@ecdcDownloadHistoricalData2020].
+Until December 14th, 2020, these data were sourced from the European Centre for Disease Control (ECDC) [@ecdcDownloadHistoricalData2020].
 After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period  [@rkiRKICoronavirusSARSCoV22021].
@@
 Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application (https://cmmid-lshtm.shinyapps.io/crowd-forecast/).
-Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information available until Monday.
+Weekly forecasts had to be submitted before Tuesday 12pm every week, but participants were asked to only use any information or data that was already available by Monday night.
 The application was built using the shiny and golem R packages [@golem; @shiny] and is available in the `crowdforecastr` R package [@crowdforecastr].
-To make a forecast in the application participants could select a predictive distribution, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values.
-The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e.
+To make a forecast in the application participants could select a predictive distribution representing the probability that the forecasted quantity took certain values, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values.
+[SCREENSHOT OF APPLICATION IN SI] The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.
 as $\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )$).
-Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  [@COVID19DataExplorer].
-These data included e.g.
-notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
+Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  [@ourworldindataCOVID19DataExplorer2020].
+These data included, for example, notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
 
-Forecasts were stored in a Google Sheet and downloaded, cleaned and processed every week for submission.
+Forecasts were stored in a Google Sheet and downloaded, cleaned and processed every week for submission to the Forecast Hub.
 If a forecaster had submitted multiple predictions for a single target, only the latest submission was kept.
 Information on the chosen distribution as well as the parameters for median and width were used to obtain the required set of 23 quantiles from that distribution.
-Forecasts from all forecasters were then aggregated using an unweighted quantile-wise mean.
-On a few occasions, individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation.
+Forecasts from all forecasters were then aggregated using an unweighted quantile-wise mean (i.e., the $\alpha$-quantile of the ensemble is given by the mean of all submitted $\alpha$-quantiles).
+On a few occasions, individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation and were excluded from the submission as well as the analysis.
 
@@
 
-We used two models from the `EpiNow2` R package (version 1.3.3) as our model-based forecasts [@epinow2].
-The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths.
-It estimated the effective reproduction number $R_t$ (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infection multiplied by $R_t$.
-$R_t$ was assumed to stay constant  beyond the forecast horizon, roughly corresponding to continuing the latest exponential trend in infections.
-On the 9th of November we altered the date when $R_t$ was assumed to be constant from two weeks prior to the date of the forecast to the forecast date.
-Reported notifications were obtained by convolving predicted infections over data-based delay distributions [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation; @sherrattExploringSurveillanceData2021] to model the time between infection and report date or death.
-The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately, meaning that $R_t$ was forecast once from reported cases and once from reported deaths.
+We used two Bayesian semi-mechanistic models from the `EpiNow2` R package (version 1.3.3) as our model-based forecasts [@epinow2].
+The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths (see details in the SI).
+It estimated the effective reproduction number $R_t$ (the average number of people each person infected at time t is expected to infect in turn) and modelled future infections as a weighted sum of past infection multiplied by $R_t$.
+$R_t$ was assumed to stay constant beyond the forecast date, roughly corresponding to continuing the latest exponential trend in infections.
+On the 9th of November we altered the date when $R_t$ was assumed to be constant from two weeks prior to the date of the forecast to the forecast date, which we found to yield a more stable $R_t$ estimate.
+Reported case and death notifications were obtained by convolving predicted infections over data-based delay distributions [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation; @sherrattExploringSurveillanceData2021; @abbottEstimatingTimevaryingReproduction2020a] to model the time between infection and report date.
+The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately.
 Death forecasts from the renewal model were therefore not informed by past cases.
@@
 
-The second model (“convolution model”) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses).
+The second model (“convolution model”, see details in SI) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses).
 The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model.
@@
 Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model with a multiplicative day-of-the-week effect [@epinow2].
+
 Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from [@kraemer2020epidemiological] with data available up to the 1st of August.
-All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan  [@rstan]  with each location and forecast target being fit separately.
-More details are available in the supplementary information.
+All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan [@rstan] with each location and forecast target being fitted separately.
 
@@
 
-For the main analysis we focused on two week ahead predictions, as predictions beyond this horizon are often unreliable due to rapidly changing conditions [@bracherShorttermForecastingCOVID192021].
+For the main analysis we focused mostly on two week ahead forecasts, as COVID-19 forecasts, especially for cases, were in the past found to have poor predictive performance  beyond this horizon [@bracherShorttermForecastingCOVID192021].
 Forecasts for cases were scored using the full period from October 2020 until March 2021.
 To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available.
-To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period where forecasts were available (see Section \@ref(sensitivity-analysis) in the SI).
+To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see Section \@ref(sensitivity-analysis) in the SI).
 Results remained broadly unchanged.
@@
 Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) [@bracherEvaluatingEpidemicForecasts2021], the absolute error, relative bias, and empirical coverage of the 50% and 90% prediction intervals.
-The WIS is a proper scoring rule [@gneiting_strictly_2007] and can be understood as a generalisation of the absolute error to quantile-based forecasts.
-It can be decomposed into three separate penalties: forecast spread (i.e.
-uncertainty of forecasts), over-prediction and under-prediction - lower values are always better.
+The WIS is a proper scoring rule [@gneiting_strictly_2007], meaning that in expectation the score is optimised by reporting a predictive distribution that is identical to the true data-generating distribution.
+Forecasters are therefore incentivised to report their true belief about the future.
+The WIS can be understood as a generalisation of the absolute error to quantile-based forecasts (also meaning that smaller values are better) and can be decomposed into three separate penalties: forecast spread (i.e.
+uncertainty of forecasts), over-prediction and under-prediction.
 While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts.
-The bias metric we use captures how much probability mass of the forecast was above or below the true value and therefore represents a general tendency to over- or under-predict in relative terms.
-It is bound between -1 (all quantiles of the predictive distribution are below the observed value) and 1 (all quantiles are above the observed value).
+The bias metric [@funkAssessingPerformanceRealtime2019] we use captures how much probability mass of the forecast was above or below the true value (mapped to values between -1 and 1) and therefore represents a general tendency to over- or under-predict in relative terms.
+A value of -1 implies that all quantiles of the predictive distribution are below the observed value and a value of 1 that all quantiles are above the observed value.
 Empirical coverage is the percentage of observed values that fall inside a given prediction interval (e.g.
@@
 Scoring metrics are explained in more detail in Table \@ref(tab:scoring-metrics) in the SI.
-All scores were calculated using the `scoringutils` R package (N.
-Bosse 2020).
+All scores were calculated using the `scoringutils` R package [@scoringutils].
 
-At all stages of the evaluation our forecasts were compared to the median ensemble of all other models submitted to the German and Polish Forecast Hub ("Hub ensemble").
+At all stages of the evaluation our forecasts were compared to the median ensemble of all *other* models submitted to the German and Polish Forecast Hub ("Hub ensemble").
 This "Hub ensemble" was retrospectively computed and excludes all our models.
 It therefore differs from the official Hub ensemble (here called "hub-ensemble-realised") which included crowd forecasts as well as renewal model forecasts.
-
-The ensemble that we call "Hub ensemble" in this paper differs from the
-
-in that we removed our forecasts to allow for a more straightforward comparison.
 To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e.
-we divided all scores by those achieved by the Hub ensemble on the same set of forecasts.
+we divided the average scores for a given model by the average score achieved by the Hub ensemble on the same set of forecasts (with values >1 implying worse and values <1 implying better performance than the Hub ensemble).
 In addition to comparing our forecasts against the hub ensemble excluding our models, we also assessed the impact of our forecasts on the performance of the forecasting hub by recalculating separate versions of the Hub ensemble with only some (or all) of our forecasts included.
-
 Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
@@
 
-A total number of 32 participants submitted forecasts, 17 of those self-identified as 'expert'.
+A total number of 32 participants submitted forecasts, 17 of those self-identified as 'expert' in either forecasting or epidemiology.
 The median number of forecasters for any given forecast target was 6, the minimum 2 and the maximum 10.
@@
 ```{r}
-caption <- "Visualisation of aggregate performance metrics across forecast horizons.
+caption <- "Visualisation of aggregate performance metrics across for forecasts one to four weeks into the future (marked as 1 - 4 on the x axis).
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
@@
 ```{r}
-caption <- "A, C: Visualisation of 50\\% prediction intervals of two week ahead forecasts against the true observed values.
+caption <- "A, C: Visualisation of 50\\% prediction intervals of two week ahead forecasts against the reported values.
 Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
@@
 For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \@ref(tab:score-table-2)).
-Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was right-skewed, and average performance was heavily influenced by outliers (Figure \@ref(fig:distribution-scores)).
+Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Figure \@ref(fig:distribution-scores)).
 Overall, low variance in forecast performance was closely linked with good mean performance (Figures \@ref(fig:agg-performance-all)H and and \@ref(fig:agg-performance-all)A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
@@
 
-To varying degrees, all models exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened.
-For example, all models failed to predict the change in trend from increase to decrease that happened in early November...
-in Germany and severely overshot (Figure \@ref(fig:forecasts-and-truth)A).
+To varying degrees, all forecasts exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened.
+For example, all forecasts failed to predict the change in trend from increase to decrease that happened in November in Germany and severely overshot reported cases (Figure \@ref(fig:forecasts-and-truth)A).
 This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past of observations.
 The Hub ensemble and the crowd forecast, which had both been under-predicting throughout October, also failed to predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 (Deutsche Welle (www.dw.com) n.d.) and the change in the testing regime (with stricter test criteria) on November 11th 2020 (Ärzteblatt 2020), were fastest to adapt to the new trend, and the Hub ensemble slowest.
+Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 [@deutschewelleCoronavirusGermanyImpose2020] and the change in the testing regime (with stricter test criteria) on November 11th 2020 [@aerzteblattSARSCoV2DiagnostikRKIPasst2020], were fastest to adapt to the new trend, and the Hub ensemble slowest.
 In December, cases rose again in Germany, with all models under-predicting this growth to varying extents.
@@
 
-All forecasting approaches, including the Hub ensemble, were overconfident and showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
+All forecasting approaches, including the Hub ensemble, were overconfident, i.e.
+they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
 Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts.
-This was especially an issue for crowd forecasts, which were markedly sharper (i.e., narrower) than other approaches (Figure \@ref(fig:agg-performance-all)E) and only showed a small increase in uncertainty across forecast horizons.
-In spite of good performance in terms of the absolute error (Figure \@ref(fig:agg-performance-all)G), excessive sharpness led to forecasts which were severely overconfident (covering only 36% and 55% of observations with their 50% and 90% prediction intervals at a two week horizon, and only 5% and 38% four weeks ahead) (Figure \@ref(fig:agg-performance-all)C,D and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
-Despite worse performance in terms of absolute error (Figure \@ref(fig:agg-performance-all)G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly and non-linearly across forecast horizons.
+This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \@ref(fig:agg-performance-all)E) and only showed a small increase in uncertainty across forecast horizons.
+In spite of good performance in terms of the absolute error (Figure \@ref(fig:agg-performance-all)G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Figure \@ref(fig:agg-performance-all)C,D and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
+Despite worse performance in terms of absolute error (Figure \@ref(fig:agg-performance-all)G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
 
@@
 The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B), and also better than the convolution model three and four weeks ahead.
-Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate $R_t$ trace from deaths, is not well suited for the task.
+Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate $R_t$ trace from deaths, does not use the available information efficiently.
 The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \@ref(fig:agg-performance-all)B, Table \@ref(tab:score-table-4)).
 
-Theoretical considerations suggest that predicting a change in trend may be easier for deaths than for cases (as past cases, hospitalisations and other data can be used as predictors).
+Theoretical considerations suggest that predicting a change in trend may be easier for deaths than for cases (as past cases and hospitalisations can be used as predictors).
 Even though all forecasts generally struggled with this, there were some instances where changing trends were well captured or even anticipated.
@@
 In Germany in early January, all models predicted a decrease in deaths two to three weeks before it actually happened.
-Predictions from the renewal model at that time were likely strongly influenced by an unexpected drop in reported deaths on December XXth.
+Predictions from the renewal model at that time were likely strongly influenced by an unexpected drop in reported deaths in December.
 The other forecasting approaches and in particular, the convolution model may have been affected by potentially under-reported case numbers around Christmas.
@@
 Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
-As for cases, the crowd forecast tended to be the sharpest and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
-The convolution model was relatively sharp for short forecast horizons, but had rapidly (and non-linearly) increasing uncertainty for longer forecast horizons, driven by increasing uncertainty in the underlying case forecasts.
+As for cases, the crowd forecast tended to have the narrowest prediction intervals and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
+The convolution model had relatively narrow prediction intervals for short forecast horizons, but had rapidly (and non-linearly) increasing uncertainty for longer forecast horizons, driven by increasing uncertainty in the underlying case forecasts.
 
@@
 ```{r}
-caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country."
+caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
+Points denote single forecasts scores, while the shaded area shows an estimated probability density.
+B: Distribution of WIS separate by country."
 ```
@@
 
-Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (“hub-ensemble-realised”), while the convolution model was never included as it was deemed too similar to the existing renewal model, thus potentially introducing bias.
-In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on December 28 2020 over the Christmas period) and a maximum of 10.
+Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (“hub-ensemble-realised”), while the convolution model was never included as it was deemed too similar to the existing renewal model.
+In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on 28 December 2020 over the Christmas period) and a maximum of 10.
 Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
@@
 WIS 0.9 two weeks ahead, Table \@ref(tab:score-table-ensemble-2)).
-Contributions from the crowd forecasts alone also were positive across all forecast horizons, while contributions from the renewal model became negative for longer horizons (rel.
+Contributions from the crowd forecasts alone also improved performance of the Hub ensemble across all forecast horizons, while contributions from the renewal model had a negative effect for longer horizons (rel.
 WIS 1.02 three weeks ahead, 1.06 four weeks ahead).
 The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects.
-Only for four week ahead predictions would removing the renewal model have improved performance (Table \@ref(tab:score-table-ensemble-4)).
+Only for predictions four weeks ahead would removing the renewal model have improved performance (Table \@ref(tab:score-table-ensemble-4)).
 
@@
 
-We also considered the impact of our contributions on the mean, rather than the median ensemble. 
+We also considered the impact of our contributions on a version of the Hub ensemble constructed by taking the quantile-wise mean, rather than the median. 
 <!-- In general, the median ensemble tended to perform slightly better than the mean ensemble - needs more analysis -->
@@
 # Discussion
-Epidemiological forecasting usually represents a mix between human insight and model-based assumptions.
-In this study, we compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from a crowd of researchers and volunteers against predictions from two semi-mechanistic epidemiological models.
+
+Epidemiological forecasting modelling combines knowledge about infectious disease dynamics with the subjective opinion of the researcher who develops and refines the model.
+In this study, we compared forecasts of cases of and deaths from COVID-19 in Germany and Poland based purely on human judgement and elicited from a crowd of researchers and volunteers against forecasts from two semi-mechanistic epidemiological models.
 In spite of the small number of participants and a general tendency to be overconfident, crowd forecasts consistently outperformed our epidemiological models as well as the Hub ensemble when forecasting cases but not when forecasting deaths.
-This suggests that humans are relatively good at foreseeing trends that are hard to model but may struggle to form an intuition for the exact relationship between cases and deaths.
+This suggests that humans might be relatively good at foreseeing trends that are hard to model but may struggle to form an intuition for the exact relationship between cases and deaths.
 
@@
 While Farrow et al.
-only asked for point predictions and constructed a probabilistic forecast from these, we asked participants to quantify their uncertainty directly, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse aspects of the forecasts like overconfidence.
-In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight.
+only asked for point predictions and constructed a predictive distribution from these, we asked participants to provide a full predictive distribution, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse how humans quantified their uncertainty.
+In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-based insight.
 In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs [@cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @EuroHub; @funkShorttermForecastsInform2020].
 
-The good performance of crowd forecasts we found is in line with results from Farrow et al.
+The strong performance of crowd forecasts in our study is in line with results from Farrow et al.
 who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants.
 The advantage of crowd forecasts we observed over our semi-mechanistic models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models.
-However, this probably explains only part of the difference and performance relative to the Hub ensemble strongly suggests that human insight is valuable when predicting highly volatile and hard-to-predict quantities such as case numbers.
+However, this probably explains only part of the difference, and performance relative to the Hub ensemble strongly suggests that human insight is valuable when forecasting highly volatile and potentially hard-to-predict quantities such as case numbers.
+One potential explanation is that humans can have access to data that is not available to or hard to integrate into model-based forecasts.
 Relatively good performance of our semi-mechanistic models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time.
@@
 The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \@ref(fig:forecasts-and-truth)A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.
-While we were not able to observe how expert opinion informed other models submitted to the Forecast Hub, conversations with the Hub organisers suggest that forecasts tended to benefit from a large degree of human intervention.
-Unfortunately, we were not able to test a scenario in which users were asked to alter an existing model output.
-We can therefore make no conclusive statements about the direct effects of researchers tuning their models, rather than create a new forecast from a naive baseline.
 
-Conversely, our results suggest that human intervention may be less beneficial when forecasting deaths (especially at shorter horizons, when deaths are largely dependent on already observed cases), which benefits from the ability to model the delays and exact epidemiological relationships between different leading and lagged indicators.
+Our results suggest that human intervention may be less beneficial when forecasting deaths (especially at shorter horizons, when deaths are largely dependent on already observed cases), which benefits from the ability to model the delays and exact epidemiological relationships between different leading and lagged indicators.
 Relatively good performance of the convolution model, especially compared to the poor performance of the renewal model on deaths (which used only deaths to estimate and predict the effective reproduction number) underlines the importance of including leading indicators such as cases as a predictor for deaths.
@@
 Given the low number of participants in our study, it is difficult to generalise conclusions about crowd predictions to other settings.
-In particular, our crowd forecasting application was not developed to a high standard of user friendliness.
-This may have precluded interested parties from submitting forecasts.
-The low number of participants presumably resulted in higher variance of forecasts, but also potentially in better average forecast performance.
-Motivating forecasters to contribute regularly proved challenging, especially given that the majority of our participants were from the UK and had little connection to Germany and even less to Poland.
-In addition, lack of effective outreach played an important role, as did a lack of time and resources to design the interface in a way that is appealing enough to attract large audiences outside of academia.
-Using an R shiny app as an interface arguably created some limits to user experience and performance, influencing the number of participants.
-On the other hand, it facilitated quick development and allows us to provide our crowd forecasting tooling as an open source R package, meaning that it is available for others to use, and to further develop, in their context.
+Using R shiny as a platform for the web application arguably created some limits to user experience and performance, influencing the number of participants and potentially creating a self-selection effect.
+Motivating forecasters to contribute regularly proved challenging, especially given that the majority of our participants were from the UK and may not have been familiar with all relevant details of the situation in Germany and Poland.
+On the other hand, R shiny facilitated quick development and allowed us to provide our crowd forecasting tooling as an open source R package, meaning that it is available for others to use, for example in settings like early-stage outbreaks where model-based forecasts are not available.
 
-In general, our results support the use of ensembles, rather than individual models to inform public health policies, as these provide consistently good performance and largely avoid particularly bad outlier forecasts.
-Our results also suggest that at least for a small median ensemble like the German and Polish Forecast Hub ensemble adding more models may increase performance in most instances (with the version of the hub ensemble that includes all our contributions ("hub-ensemble-with-all") outperforming the realised official hub ensemble in almost all instances).
-We often found contributions to an ensemble to be beneficial even in instances where the forecasting approach entering the ensemble performed consistently worse than the pre-existing ensemble.
-Including more models may be easier when using a median ensemble, as extreme forecasts tend to have less of an influence there.
-Individual models, however, can still have a place in informing public policy.
-As an average, ensembles show the consensus opinion, which implies that in contrast to single models, they are not likely to reveal information, e.g.
-about future changes in trend, that is not in some way ‘obvious’ to the majority of forecasters.
+Our work suggests that crowd forecasts and model-based forecasts have slightly different advantages and may be able to complement each other well.
+Humans can use information that is hard to input into a model, while model-based approaches can perform more advanced calculations and are more easily scalable.
+When interpreting outputs it is important to distinguish between projections (which show what would happen in the absence of any events that could change the trend) and “genuine” forecasts (aiming to predict future data points whilst accounting for all factors that might influence them).
+Forecasts may not be a suitable basis for informing policy decisions, if forecasters already have factored in the expectation of a future intervention.
+Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting real projections from humans may be harder.
 
-In the context of evaluating different models and the merits of human intervention, what constitutes a ‘good’ forecast very much depends on the purpose of that forecast.
-Policymakers may care much more about certain types of errors, (e.g.
-under-prediction) than others in a way not captured by the weighted interval score.
-Also, it is helpful to distinguish between ‘forecasts’ and ‘projections’.
-For example, the outperformance of the crowd forecasts on cases and in general on longer forecast horizons is perhaps not surprising, given that humans could factor in an expectation of future changes in conditions (e.g.
-future policy interventions, adherence to these interventions, testing policy, and the evolution of new disease variants) while our model-based forecasts could not.
-However, if the aim of a forecast is to inform policy and decision making, then attempting to factor in the interventions one is meant to inform may be problematic (and conversely, arguing for or against interventions based on predictions may be difficult depending on what the forecast assumes about future interventions).
-In that sense, crowd forecasts can be understood as forecasts, whereas our model predictions may be better understood as projections that show what would happen in the absence of any events that could change the trend.
-This may pose a problem in the context of a forecast hub if teams have a different understanding about the purpose of a forecast.
-Projections that are meant to inform policy makers about possible scenarios may be different from forecasts meant to inform the general public, and yet again different from forecasts submitted with the goal of advancing open research and in order to allow public scrutiny and discussion about the merits of different approaches.
-
-Further work should explore the effects of human intervention on model-based forecasts in more detail.
+Further work should explore the effects of humans refining their mathematical models or changing model outputs in more detail.
 Model-based forecasts could be used as an input to human judgement, with researchers adjusting predictions generated by models.
-Seeing a model-based forecasts could help humans calibrate uncertainty better, while allowing for manual intervention to adapt spurious trend predictions.
+Seeing a model-based forecast could help humans calibrate uncertainty better, while allowing for manual intervention to adapt spurious trend predictions.
 Tools need to be developed to facilitate this process at a larger scale.
@@
 how the epidemic evolves) into the future and use this to estimate the exact number of cases, hospitalisations or deaths this would imply.
-This approach seems especially promising for forecasting deaths if a model can accurately describe delay distributions and epidemiological relationships between different parameters.
-In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust and widen confidence intervals may be another promising approach.
+In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust and widen prediction intervals may be another promising approach.
 Crowd forecasting in general could benefit greatly from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile for researchers and policymakers to further develop and explore.
+Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile to further develop and explore.
+
+________________
 
@@
 
+\clearpage
+
 ## Further details on the semi-mechanistic forecasting models
@@
 
-\begin{align*}
+\begin{align}
   I_{t} &= I_0 \exp  \left(r t \right)  \\
@@
   r &\sim \mathcal{LN}(r_{obs}, 0.2) 
-\end{align*}
+\end{align}
 
@@
 
-\begin{align*}
+\begin{align}
   \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
@@
   C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
-\end{align*}
+\end{align}
 
 Where,
-\begin{align*}
+\begin{align}
      w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
@@
     \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
-\end{align*}
+\end{align}
 
@@
 
-\begin{align*}
+\begin{align}
      R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
@@
     \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align*}
+\end{align}
 
@@
 
-\begin{align*}
+\begin{align}
     \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
@@
     \alpha &\sim \mathcal{N}(0.005, 0.0025) 
-\end{align*}
+\end{align}
 
@@
 
-\begin{align*}
+\begin{align}
     \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
@@
 \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align*}
+\end{align}
 
@@
 ```{r}
-caption <- "A, C: Visualisation of 50\\% prediction intervals of one week ahead forecasts against the true observed values.
+caption <- "A, C: Visualisation of 50\\% prediction intervals of one week ahead forecasts against the reported values.
 Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.

### 2021-11-18 manuscript/manuscript.tex
incorporate google docs feedback

@@
 ]{article}
-\title{Comparing human and model-based forecasts of COVID-19 in Germany and Poland}
-\author{}
-\date{\vspace{-2.5em}}
-
 \usepackage{amsmath,amssymb}
@@
 
+\title{Comparing human and model-based forecasts of COVID-19 in Germany and Poland}
+\author{}
+\date{\vspace{-2.5em}}
+
 \begin{document}
@@
 
-{
-\setcounter{tocdepth}{2}
-\tableofcontents
-}
-\emph{Anonymous Alpaca and many friends}
+Target journal: eLife
+
+\emph{Nikos I. Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy J. Quilty, Mark Jit, CMMID Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk}
 
@@
 
-Model-based forecasts, which have played an important role in shaping public policy throughout the COVID-19 pandemic, represent an implicit combination of model assumptions and the researcher's subjective opinion.
-This work analyses and compares human opinion against model-derived insights to discern relative strengths and weaknesses of both approaches.
-We compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from researchers and volunteers, against predictions from two semi-mechanistic epidemiological models.
-We also compared these forecasts against an ensemble of model-based, but expert-tuned, forecasts, submitted to the German and Polish Forecast Hub by other research institutions.
-In addition, we examined the effects of our contributions to the performance of the Hub ensemble.
-We found aggregated crowd forecasts to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble: 0.89), but not when predicting deaths (rel.
-WIS 1.26).
-Crowd forecasts were noticeably more overconfident (55\% and 75\% coverage of the 90\% prediction intervals for cases and deaths, respectively) than model-based predictions.
-Performance of the semi-mechanistic models was good short-term, but deteriorated quickly over time when assumptions were no longer met.
+Forecasts based on epidemiological modelling have played an important role in shaping public policy throughout the COVID-19 pandemic.
+This modelling combines knowledge about infectious disease dynamics with the subjective opinion of the researcher who develops and refines the model and often also adjusts model outputs.
+Developing a forecast model is difficult, resource- and time-consuming.
+It is therefore worth asking what modelling is able to add beyond the subjective opinion of the researcher alone.
+To investigate this, we analysed different real-time forecasts of cases of and deaths from COVID-19 in Germany and Poland over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
+We compared crowd forecasts elicited from researchers and volunteers, against a) forecasts from two semi-mechanistic models based on common epidemiological assumptions and b) the ensemble of all other models submitted to the Forecast Hub.
+We found crowd forecasts, despite being overconfident, to outperform all other methods across all forecast horizons when forecasting cases (weighted interval score relative to the Hub ensemble 2 weeks ahead: 0.89).
+Forecasts based on computational models performed comparably better when predicting deaths (rel.
+WIS 1.26), suggesting that epidemiological modelling and human judgement can complement each other in important ways.
 
@@
 
-Infectious disease forecasting has a long tradition and has helped inform public health decisions about (among others) influenza (e.g.
+Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza (e.g.
 McGowan et al.
@@
 2020; Cramer et al.
-2021; Bracher, Wolffram, et al.
+2021; Johannes Bracher, Wolffram, et al.
+2021; J.
+Bracher et al.
 2021; Hub 2021).
-The aggregation of forecasts of COVID-19 cases, hospitalisations or deaths from multiple teams has created opportunities to compare the predictive performance of different models.
-Yet it has been difficult to discern which factors lead to good COVID-19 forecasts.
-Answering this question is complicated by the varying and generally unobserved degree of manual expert intervention.
-Model-based forecasts usually represent an implicit combination of human judgement and model-derived insights, in the sense that forecasts have been generated with the help of epidemiological or statistical models, but throughout the process were manually changed and adjusted according to the researchers' judgement.
-
-Previous work has examined human predictions in various contexts, such as geopolitics (Tetlock et al.
+Applications of epidemiological models differ in the way they make statements about the future.
+Forecasts aim to predict the future as it will occur, while scenario modelling and projections aim to represent what the future could look like under certain scenario assumptions or if conditions stayed the same as they were in the past.
+Forecasts can be judged by comparing them against observed data.
+Since it is much harder to fairly assess the accuracy and usefulness of projections and scenario modelling in the same way, this work focuses on forecasts, which represent only a subset of all epidemiological modelling.
+
+Since March 2020, forecasts of COVID-19 from multiple teams have been collected, aggregated and compared by Forecast Hubs such as the US Forecast Hub (Cramer et al.
+2020; Cramer et al.
+2021), the German and Polish Forecast Hub (Johannes Bracher, Wolffram, et al.
+2021; J.
+Bracher et al.
+2021) and the European Forecast Hub (Hub 2021).
+Often, different individual forecasts are combined into a single forecast, e.g.~by taking the mean or median of all forecasts.
+These ensemble forecasts usually tend to perform better and more consistently than individual forecasts {[}see e.g.
+Yamana, Kandula, and Shaman (2016); reichAccuracyRealtimeMultimodel2019{]}.
+
+Individual computational models usually rely to varying degrees on mechanistic assumptions about infectious disease dynamics (such as SIR-type compartmental models that aim to represent how individuals move from being susceptible to infected and then recovered or dead) or are more statistical in nature (such as time series models that detect statistical patterns without explicitly modelling disease dynamics).
+How exactly such a mathematical or computational model is constructed and which assumptions are made depends on subjective opinion and judgement of the researcher who develops and refines the model.
+Models are commonly adjusted and improved based on whether the model output looks plausible to the researchers involved.
+
+The process of model construction and refinement is laborious and time-consuming, and it is therefore worth asking what modelling can add beyond the subjective judgment of the researcher alone.
+In this work, we ask this question specifically in the context of predictive performance, and set aside other advantages of epidemiological modelling (such as reproducibility or the ability to obtain a deeper fundamental understanding of how diseases spread).
+One natural way to do this is to compare the predictive performance of forecasts based on computational models (``model-based forecasts'') against forecasts made by individual humans without explicit use of a computer model (``direct human forecasts'') or a combination of multiple such forecasts (``crowd forecasts'').
+
+Previous work has examined such direct human forecasts in various contexts, such as geopolitics (Tetlock et al.
 2014; Atanasov et al.
@@
 Several prediction platforms (Metaculus 2020; Hypermind 2021; CSET Foretell 2021) and prediction markets (PredictIt 2021) have been created to collate expert and non-expert predictions.
-However, with the notable exception of Farrow et al., these crowd forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats.
-Farrow et al.~found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available.
-They tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown there and then.
-
-In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses.
-To allow for a direct comparison on an equal footing we employ a novel approach that elicits full probabilistic forecasts (Held, Meyer, and Bracher 2017) from participants, rather than constructing a predictive distribution from individual point predictions.
+However, with the notable exception of Farrow et al.
+(2017), these forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) prediction formats.
+Direct human forecasts may be able to take into account insights and relationships between variables which are hard to specify using epidemiological models.
+However, it is not entirely clear in which situations human forecasts perform well or badly.
+For example, Farrow et al.
+(2017) found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available.
+However, humans tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown there and then.
+
+In this study, we analyse the performance of direct human forecasts relative to model-based forecasts and discuss the added benefit of epidemiological modelling over human judgement alone.
+As a case study, we use different forecasts, involving varying degrees of human intervention, which we submitted in real time to the German and Polish Forecast Hub.
+In contrast to Farrow et al.
+(2017) we elicited not only point predictions, but full predictive distributions (``probabilistic forecasts'') (Held, Meyer, and Bracher 2017) from participants.
+This allows us to compare not only predictive accuracy, but also how well human forecasters and model-based forecasts were able to quantify the appropriate forecast uncertainty.
 
@@
 
-We created a crowd-sourced forecast (``crowd forecast''), elicited from participants through a web application (Bosse et al.
-2020b), as well as two semi-mechanistic models (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology.
-Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (Bracher, Wolffram, et al.
+We created and submitted the following forecasts to the German and Polish Forecast Hub: 1) a direct human forecast (henceforth called ``crowd forecast''), elicited from participants through a web application (N.
+I.
+Bosse et al.
+2020b) and 2) two semi-mechanistic model-based forecasts (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology.
+While the two semi-mechanistic forecasts were necessarily shaped by our implicit assumptions and decisions, they were designed such as to minimise the amount of human intervention involved.
+For example, we refrained from adjusting model outputs or refining the models based on past performance.
+Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (Johannes Bracher, Wolffram, et al.
+2021; J.
+Bracher et al.
 2021).
-All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (Bosse et al.
+All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (N.
+I.
+Bosse et al.
 2020a).
 This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub.
-Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the Forecast Hub.
+Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the German and Polish Forecast Hub.
 
@@
 The German and Polish Forecast Hub elicits predictions for various COVID-19 related forecast targets from different research institutions every week.
-Forecasts had to be made every Monday (with submissions allowed until Tuesday 3pm) using data available until Monday 11.59pm.
-We submitted forecasts for incident and cumulative weekly reported numbers of cases and deaths from COVID-19 on a national level in Germany and Poland over a one to four week forecast horizon.
-Weeks were defined as epiweeks starting on Sunday and ending on Saturday, meaning that forecast horizons were in fact 5, 12, 19 and 26 days.
-Submissions were required in a quantile-based format with 23 quantiles at levels 0.01, 0.025, 0.05, 0.10, 0.15, \ldots, 0.95, 0.975, 0.99.
-Forecasts submitted to the Forecast Hub were combined to different ensembles every week, with the median ensemble being the default ensemble shown on all official Forecast hub visualisations.
+Forecasts had to be made every Monday (with submissions allowed until Tuesday 3pm) and were permitted to use any data that was available by Monday 11.59pm.
+We submitted forecasts for incident and cumulative weekly reported numbers of cases of and deaths from COVID-19 on a national level in Germany and Poland over a one to four week forecast horizon.
+Forecasts were submitted on Mondays, but weeks were defined as ending on a Saturday (and starting on Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26 days.
+Submissions were required in a quantile-based format with 23 quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10, 0.15, \ldots, 0.95, 0.975, 0.99.
+Forecasts submitted to the Forecast Hub were combined into different ensembles every week, with the median ensemble (i.e., the \(\alpha\)-quantile of the ensemble is given by the median of all submitted \(\alpha\)-quantiles) being the default ensemble shown on all official Forecast hub visualisations (\url{https://kitmetricslab.github.io/forecasthub/forecast}).
 
 Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish forecast hub.
-Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) (ECDC 2020).
+Until December 14th, 2020, these data were sourced from the European Centre for Disease Control (ECDC) (ECDC 2020).
 After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (RKI 2021).
@@
 Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application (\url{https://cmmid-lshtm.shinyapps.io/crowd-forecast/}).
-Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information available until Monday.
+Weekly forecasts had to be submitted before Tuesday 12pm every week, but participants were asked to only use any information or data that was already available by Monday night.
 The application was built using the shiny and golem R packages (Fay et al.
 2021; Chang et al.
-2021) and is available in the \texttt{crowdforecastr} R package (Bosse et al.
+2021) and is available in the \texttt{crowdforecastr} R package (N.
+I.
+Bosse et al.
 2020b).
-To make a forecast in the application participants could select a predictive distribution, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values.
-The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e.~as \(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
-Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from ({``{COVID}-19 {Data Explorer}''} n.d.).
-These data included e.g.~notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
-
-Forecasts were stored in a Google Sheet and downloaded, cleaned and processed every week for submission.
+To make a forecast in the application participants could select a predictive distribution representing the probability that the forecasted quantity took certain values, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values.
+{[}SCREENSHOT OF APPLICATION IN SI{]} The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.~as \(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
+Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from (Data 2020).
+These data included, for example, notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
+
+Forecasts were stored in a Google Sheet and downloaded, cleaned and processed every week for submission to the Forecast Hub.
 If a forecaster had submitted multiple predictions for a single target, only the latest submission was kept.
 Information on the chosen distribution as well as the parameters for median and width were used to obtain the required set of 23 quantiles from that distribution.
-Forecasts from all forecasters were then aggregated using an unweighted quantile-wise mean.
-On a few occasions, individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation.
+Forecasts from all forecasters were then aggregated using an unweighted quantile-wise mean (i.e., the \(\alpha\)-quantile of the ensemble is given by the mean of all submitted \(\alpha\)-quantiles).
+On a few occasions, individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation and were excluded from the submission as well as the analysis.
 
 Participants were recruited mostly within the Centre of Mathematical Modeling of Infectious Diseases at the London School of Hygiene \& Tropical Medicine, but participants were also invited personally or via social media to submit predictions.
-Depending on whether they had a background in either statistics, forecasting or epidemiology, participants were asked to self-identify as `experts' or `non-experts.'
+Depending on whether they had a background in either statistics, forecasting or epidemiology, participants were asked to self-identify as `experts' or `non-experts'.
 
@@
 
-We used two models from the \texttt{EpiNow2} R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, et al.
+We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, Hickson, et al.
 2020).
-The first of these models, here called ``renewal model,'' used the renewal equation (Fraser 2007) to predict reported cases and deaths.
-It estimated the effective reproduction number \(R_t\) (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infection multiplied by \(R_t\).
-\(R_t\) was assumed to stay constant beyond the forecast horizon, roughly corresponding to continuing the latest exponential trend in infections.
-On the 9th of November we altered the date when \(R_t\) was assumed to be constant from two weeks prior to the date of the forecast to the forecast date.
-Reported notifications were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, et al.
+The first of these models, here called ``renewal model'', used the renewal equation (Fraser 2007) to predict reported cases and deaths (see details in the SI).
+It estimated the effective reproduction number \(R_t\) (the average number of people each person infected at time t is expected to infect in turn) and modelled future infections as a weighted sum of past infection multiplied by \(R_t\).
+\(R_t\) was assumed to stay constant beyond the forecast date, roughly corresponding to continuing the latest exponential trend in infections.
+On the 9th of November we altered the date when \(R_t\) was assumed to be constant from two weeks prior to the date of the forecast to the forecast date, which we found to yield a more stable \(R_t\) estimate.
+Reported case and death notifications were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, Hickson, et al.
 2020; epiforecasts.io/covid n.d.; Sherratt et al.
-2021) to model the time between infection and report date or death.
-The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately, meaning that \(R_t\) was forecast once from reported cases and once from reported deaths.
+2021; Abbott, Hellewell, Thompson, et al.
+2020) to model the time between infection and report date.
+The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately.
 Death forecasts from the renewal model were therefore not informed by past cases.
@@
 
-The second model (``convolution model'') was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses).
+The second model (``convolution model'', see details in SI) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses).
 The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model.
 The convolution model predicted deaths as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
-Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model with a multiplicative day-of-the-week effect (Abbott, Hellewell, et al.
+Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model with a multiplicative day-of-the-week effect (Abbott, Hellewell, Hickson, et al.
 2020).
+
 Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al.
 2020) with data available up to the 1st of August.
-All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fit separately.
-More details are available in the supplementary information.
+All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fitted separately.
 
@@
 
-For the main analysis we focused on two week ahead predictions, as predictions beyond this horizon are often unreliable due to rapidly changing conditions (Bracher, Wolffram, et al.
+For the main analysis we focused mostly on two week ahead forecasts, as COVID-19 forecasts, especially for cases, were in the past found to have poor predictive performance beyond this horizon (Johannes Bracher, Wolffram, et al.
 2021).
@@
 To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available.
-To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period where forecasts were available (see Section \ref{sensitivity-analysis} in the SI).
+To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see Section \ref{sensitivity-analysis} in the SI).
 Results remained broadly unchanged.
 
-Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Bracher, Ray, et al.
+Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Johannes Bracher, Ray, et al.
 2021), the absolute error, relative bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule (Gneiting and Raftery 2007) and can be understood as a generalisation of the absolute error to quantile-based forecasts.
-It can be decomposed into three separate penalties: forecast spread (i.e.~uncertainty of forecasts), over-prediction and under-prediction - lower values are always better.
+The WIS is a proper scoring rule (Gneiting and Raftery 2007), meaning that in expectation the score is optimised by reporting a predictive distribution that is identical to the true data-generating distribution.
+Forecasters are therefore incentivised to report their true belief about the future.
+The WIS can be understood as a generalisation of the absolute error to quantile-based forecasts (also meaning that smaller values are better) and can be decomposed into three separate penalties: forecast spread (i.e.~uncertainty of forecasts), over-prediction and under-prediction.
 While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts.
-The bias metric we use captures how much probability mass of the forecast was above or below the true value and therefore represents a general tendency to over- or under-predict in relative terms.
-It is bound between -1 (all quantiles of the predictive distribution are below the observed value) and 1 (all quantiles are above the observed value).
+The bias metric (Funk et al.
+2019) we use captures how much probability mass of the forecast was above or below the true value (mapped to values between -1 and 1) and therefore represents a general tendency to over- or under-predict in relative terms.
+A value of -1 implies that all quantiles of the predictive distribution are below the observed value and a value of 1 that all quantiles are above the observed value.
 Empirical coverage is the percentage of observed values that fall inside a given prediction interval (e.g.~how many observed values fall inside all 50\% prediction intervals).
@@
 
-At all stages of the evaluation our forecasts were compared to the median ensemble of all other models submitted to the German and Polish Forecast Hub (``Hub ensemble'').
+At all stages of the evaluation our forecasts were compared to the median ensemble of all \emph{other} models submitted to the German and Polish Forecast Hub (``Hub ensemble'').
 This ``Hub ensemble'' was retrospectively computed and excludes all our models.
 It therefore differs from the official Hub ensemble (here called ``hub-ensemble-realised'') which included crowd forecasts as well as renewal model forecasts.
-
-The ensemble that we call ``Hub ensemble'' in this paper differs from the
-
-in that we removed our forecasts to allow for a more straightforward comparison.
-To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e.~we divided all scores by those achieved by the Hub ensemble on the same set of forecasts.
+To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e.~we divided the average scores for a given model by the average score achieved by the Hub ensemble on the same set of forecasts (with values \textgreater1 implying worse and values \textless1 implying better performance than the Hub ensemble).
 In addition to comparing our forecasts against the hub ensemble excluding our models, we also assessed the impact of our forecasts on the performance of the forecasting hub by recalculating separate versions of the Hub ensemble with only some (or all) of our forecasts included.
-
 Versions that included either all of our models (``hub-ensemble-with-all'') or only one of them (``hub-ensemble-with-X'') were computed retrospectively.
@@
 
-A total number of 32 participants submitted forecasts, 17 of those self-identified as `expert.' The median number of forecasters for any given forecast target was 6, the minimum 2 and the maximum 10.
+A total number of 32 participants submitted forecasts, 17 of those self-identified as `expert' in either forecasting or epidemiology.
+The median number of forecasters for any given forecast target was 6, the minimum 2 and the maximum 10.
 The mean number of submissions from an individual forecaster was 4.7 but the median number was only one - most participants dropped out after their first submission.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons.
+\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} \caption{Visualisation of aggregate performance metrics across for forecasts one to four weeks into the future (marked as 1 - 4 on the x axis).
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} \caption{A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the true observed values.
+\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} \caption{A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values.
 Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
@@
 For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \ref{tab:score-table-2}).
-Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was right-skewed, and average performance was heavily influenced by outliers (Figure \ref{fig:distribution-scores}).
+Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Figure \ref{fig:distribution-scores}).
 Overall, low variance in forecast performance was closely linked with good mean performance (Figures \ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
@@
 
-To varying degrees, all models exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened.
-For example, all models failed to predict the change in trend from increase to decrease that happened in early November\ldots{} in Germany and severely overshot (Figure \ref{fig:forecasts-and-truth}A).
+To varying degrees, all forecasts exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened.
+For example, all forecasts failed to predict the change in trend from increase to decrease that happened in November in Germany and severely overshot reported cases (Figure \ref{fig:forecasts-and-truth}A).
 This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past of observations.
 The Hub ensemble and the crowd forecast, which had both been under-predicting throughout October, also failed to predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 (Deutsche Welle (www.dw.com) n.d.) and the change in the testing regime (with stricter test criteria) on November 11th 2020 (Ärzteblatt 2020), were fastest to adapt to the new trend, and the Hub ensemble slowest.
+Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 (Deutsche Welle 2020) and the change in the testing regime (with stricter test criteria) on November 11th 2020 (Ärzteblatt 2020), were fastest to adapt to the new trend, and the Hub ensemble slowest.
 In December, cases rose again in Germany, with all models under-predicting this growth to varying extents.
@@
 
-All forecasting approaches, including the Hub ensemble, were overconfident and showed lower than nominal coverage (meaning that 50\% (90\%) prediction intervals generally covered less than 50\% (90\%) of the actually observed values) (Figure \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
+All forecasting approaches, including the Hub ensemble, were overconfident, i.e.~they showed lower than nominal coverage (meaning that 50\% (90\%) prediction intervals generally covered less than 50\% (90\%) of the actually observed values) (Figure \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
 Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts.
-This was especially an issue for crowd forecasts, which were markedly sharper (i.e., narrower) than other approaches (Figure \ref{fig:agg-performance-all}E) and only showed a small increase in uncertainty across forecast horizons.
-In spite of good performance in terms of the absolute error (Figure \ref{fig:agg-performance-all}G), excessive sharpness led to forecasts which were severely overconfident (covering only 36\% and 55\% of observations with their 50\% and 90\% prediction intervals at a two week horizon, and only 5\% and 38\% four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
-Despite worse performance in terms of absolute error (Figure \ref{fig:agg-performance-all}G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly and non-linearly across forecast horizons.
+This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \ref{fig:agg-performance-all}E) and only showed a small increase in uncertainty across forecast horizons.
+In spite of good performance in terms of the absolute error (Figure \ref{fig:agg-performance-all}G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36\% and 55\% of all observations with the 50\% and 90\% prediction intervals of all forecasts made at a two week forecast horizon, and only 5\% and 38\% four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
+Despite worse performance in terms of absolute error (Figure \ref{fig:agg-performance-all}G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
 
@@
 The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \ref{fig:agg-performance-all}B, Figure \ref{fig:performance-locations}B), and also better than the convolution model three and four weeks ahead.
-Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate \(R_t\) trace from deaths, is not well suited for the task.
+Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate \(R_t\) trace from deaths, does not use the available information efficiently.
 The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \ref{fig:agg-performance-all}B, Table \ref{tab:score-table-4}).
 
-Theoretical considerations suggest that predicting a change in trend may be easier for deaths than for cases (as past cases, hospitalisations and other data can be used as predictors).
+Theoretical considerations suggest that predicting a change in trend may be easier for deaths than for cases (as past cases and hospitalisations can be used as predictors).
 Even though all forecasts generally struggled with this, there were some instances where changing trends were well captured or even anticipated.
@@
 Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
-As for cases, the crowd forecast tended to be the sharpest and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
-The convolution model was relatively sharp for short forecast horizons, but had rapidly (and non-linearly) increasing uncertainty for longer forecast horizons, driven by increasing uncertainty in the underlying case forecasts.
+As for cases, the crowd forecast tended to have the narrowest prediction intervals and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
+The convolution model had relatively narrow prediction intervals for short forecast horizons, but had rapidly (and non-linearly) increasing uncertainty for longer forecast horizons, driven by increasing uncertainty in the underlying case forecasts.
 
@@
 \includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} \caption{A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
+Points denote single forecasts scores, while the shaded area shows an estimated probability density.
 B: Distribution of WIS separate by country.}\label{fig:distribution-scores}
@@
 
-Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (``hub-ensemble-realised''), while the convolution model was never included as it was deemed too similar to the existing renewal model, thus potentially introducing bias.
-In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on December 28 2020 over the Christmas period) and a maximum of 10.
+Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (``hub-ensemble-realised''), while the convolution model was never included as it was deemed too similar to the existing renewal model.
+In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on 28 December 2020 over the Christmas period) and a maximum of 10.
 Versions that included either all of our models (``hub-ensemble-with-all'') or only one of them (``hub-ensemble-with-X'') were computed retrospectively.
@@
 WIS 0.9 two weeks ahead, Table \ref{tab:score-table-ensemble-2}).
-Contributions from the crowd forecasts alone also were positive across all forecast horizons, while contributions from the renewal model became negative for longer horizons (rel.
+Contributions from the crowd forecasts alone also improved performance of the Hub ensemble across all forecast horizons, while contributions from the renewal model had a negative effect for longer horizons (rel.
 WIS 1.02 three weeks ahead, 1.06 four weeks ahead).
 The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects.
-Only for four week ahead predictions would removing the renewal model have improved performance (Table \ref{tab:score-table-ensemble-4}).
+Only for predictions four weeks ahead would removing the renewal model have improved performance (Table \ref{tab:score-table-ensemble-4}).
 
@@
 
-We also considered the impact of our contributions on the mean, rather than the median ensemble.
+We also considered the impact of our contributions on a version of the Hub ensemble constructed by taking the quantile-wise mean, rather than the median.
 General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \ref{fig:agg-performance-ensemble}B and \ref{fig:agg-performance-ensemble-mean}B).
@@
 
-Epidemiological forecasting usually represents a mix between human insight and model-based assumptions.
-In this study, we compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from a crowd of researchers and volunteers against predictions from two semi-mechanistic epidemiological models.
+Epidemiological forecasting modelling combines knowledge about infectious disease dynamics with the subjective opinion of the researcher who develops and refines the model.
+In this study, we compared forecasts of cases of and deaths from COVID-19 in Germany and Poland based purely on human judgement and elicited from a crowd of researchers and volunteers against forecasts from two semi-mechanistic epidemiological models.
 In spite of the small number of participants and a general tendency to be overconfident, crowd forecasts consistently outperformed our epidemiological models as well as the Hub ensemble when forecasting cases but not when forecasting deaths.
-This suggests that humans are relatively good at foreseeing trends that are hard to model but may struggle to form an intuition for the exact relationship between cases and deaths.
+This suggests that humans might be relatively good at foreseeing trends that are hard to model but may struggle to form an intuition for the exact relationship between cases and deaths.
 
@@
 (2017), but extends it in several ways.
-While Farrow et al.~only asked for point predictions and constructed a probabilistic forecast from these, we asked participants to quantify their uncertainty directly, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse aspects of the forecasts like overconfidence.
-In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight.
+While Farrow et al.~only asked for point predictions and constructed a predictive distribution from these, we asked participants to provide a full predictive distribution, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse how humans quantified their uncertainty.
+In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-based insight.
 In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (Cramer et al.
 2020; Cramer et al.
-2021; Bracher, Wolffram, et al.
+2021; Johannes Bracher, Wolffram, et al.
 2021; Hub 2021; Funk et al.
@@
 
-The good performance of crowd forecasts we found is in line with results from Farrow et al.~who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants.
+The strong performance of crowd forecasts in our study is in line with results from Farrow et al.~who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants.
 The advantage of crowd forecasts we observed over our semi-mechanistic models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models.
-However, this probably explains only part of the difference and performance relative to the Hub ensemble strongly suggests that human insight is valuable when predicting highly volatile and hard-to-predict quantities such as case numbers.
+However, this probably explains only part of the difference, and performance relative to the Hub ensemble strongly suggests that human insight is valuable when forecasting highly volatile and potentially hard-to-predict quantities such as case numbers.
+One potential explanation is that humans can have access to data that is not available to or hard to integrate into model-based forecasts.
 Relatively good performance of our semi-mechanistic models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time.
@@
 The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \ref{fig:forecasts-and-truth}A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.
-While we were not able to observe how expert opinion informed other models submitted to the Forecast Hub, conversations with the Hub organisers suggest that forecasts tended to benefit from a large degree of human intervention.
-Unfortunately, we were not able to test a scenario in which users were asked to alter an existing model output.
-We can therefore make no conclusive statements about the direct effects of researchers tuning their models, rather than create a new forecast from a naive baseline.
-
-Conversely, our results suggest that human intervention may be less beneficial when forecasting deaths (especially at shorter horizons, when deaths are largely dependent on already observed cases), which benefits from the ability to model the delays and exact epidemiological relationships between different leading and lagged indicators.
+
+Our results suggest that human intervention may be less beneficial when forecasting deaths (especially at shorter horizons, when deaths are largely dependent on already observed cases), which benefits from the ability to model the delays and exact epidemiological relationships between different leading and lagged indicators.
 Relatively good performance of the convolution model, especially compared to the poor performance of the renewal model on deaths (which used only deaths to estimate and predict the effective reproduction number) underlines the importance of including leading indicators such as cases as a predictor for deaths.
@@
 Given the low number of participants in our study, it is difficult to generalise conclusions about crowd predictions to other settings.
-In particular, our crowd forecasting application was not developed to a high standard of user friendliness.
-This may have precluded interested parties from submitting forecasts.
-The low number of participants presumably resulted in higher variance of forecasts, but also potentially in better average forecast performance.
-Motivating forecasters to contribute regularly proved challenging, especially given that the majority of our participants were from the UK and had little connection to Germany and even less to Poland.
-In addition, lack of effective outreach played an important role, as did a lack of time and resources to design the interface in a way that is appealing enough to attract large audiences outside of academia.
-Using an R shiny app as an interface arguably created some limits to user experience and performance, influencing the number of participants.
-On the other hand, it facilitated quick development and allows us to provide our crowd forecasting tooling as an open source R package, meaning that it is available for others to use, and to further develop, in their context.
-
-In general, our results support the use of ensembles, rather than individual models to inform public health policies, as these provide consistently good performance and largely avoid particularly bad outlier forecasts.
-Our results also suggest that at least for a small median ensemble like the German and Polish Forecast Hub ensemble adding more models may increase performance in most instances (with the version of the hub ensemble that includes all our contributions (``hub-ensemble-with-all'') outperforming the realised official hub ensemble in almost all instances).
-We often found contributions to an ensemble to be beneficial even in instances where the forecasting approach entering the ensemble performed consistently worse than the pre-existing ensemble.
-Including more models may be easier when using a median ensemble, as extreme forecasts tend to have less of an influence there.
-Individual models, however, can still have a place in informing public policy.
-As an average, ensembles show the consensus opinion, which implies that in contrast to single models, they are not likely to reveal information, e.g.~about future changes in trend, that is not in some way `obvious' to the majority of forecasters.
-
-In the context of evaluating different models and the merits of human intervention, what constitutes a `good' forecast very much depends on the purpose of that forecast.
-Policymakers may care much more about certain types of errors, (e.g.~under-prediction) than others in a way not captured by the weighted interval score.
-Also, it is helpful to distinguish between `forecasts' and `projections.' For example, the outperformance of the crowd forecasts on cases and in general on longer forecast horizons is perhaps not surprising, given that humans could factor in an expectation of future changes in conditions (e.g.~future policy interventions, adherence to these interventions, testing policy, and the evolution of new disease variants) while our model-based forecasts could not.
-However, if the aim of a forecast is to inform policy and decision making, then attempting to factor in the interventions one is meant to inform may be problematic (and conversely, arguing for or against interventions based on predictions may be difficult depending on what the forecast assumes about future interventions).
-In that sense, crowd forecasts can be understood as forecasts, whereas our model predictions may be better understood as projections that show what would happen in the absence of any events that could change the trend.
-This may pose a problem in the context of a forecast hub if teams have a different understanding about the purpose of a forecast.
-Projections that are meant to inform policy makers about possible scenarios may be different from forecasts meant to inform the general public, and yet again different from forecasts submitted with the goal of advancing open research and in order to allow public scrutiny and discussion about the merits of different approaches.
-
-Further work should explore the effects of human intervention on model-based forecasts in more detail.
+Using R shiny as a platform for the web application arguably created some limits to user experience and performance, influencing the number of participants and potentially creating a self-selection effect.
+Motivating forecasters to contribute regularly proved challenging, especially given that the majority of our participants were from the UK and may not have been familiar with all relevant details of the situation in Germany and Poland.
+On the other hand, R shiny facilitated quick development and allowed us to provide our crowd forecasting tooling as an open source R package, meaning that it is available for others to use, for example in settings like early-stage outbreaks where model-based forecasts are not available.
+
+Our work suggests that crowd forecasts and model-based forecasts have slightly different advantages and may be able to complement each other well.
+Humans can use information that is hard to input into a model, while model-based approaches can perform more advanced calculations and are more easily scalable.
+When interpreting outputs it is important to distinguish between projections (which show what would happen in the absence of any events that could change the trend) and ``genuine'' forecasts (aiming to predict future data points whilst accounting for all factors that might influence them).
+Forecasts may not be a suitable basis for informing policy decisions, if forecasters already have factored in the expectation of a future intervention.
+Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting real projections from humans may be harder.
+
+Further work should explore the effects of humans refining their mathematical models or changing model outputs in more detail.
 Model-based forecasts could be used as an input to human judgement, with researchers adjusting predictions generated by models.
-Seeing a model-based forecasts could help humans calibrate uncertainty better, while allowing for manual intervention to adapt spurious trend predictions.
+Seeing a model-based forecast could help humans calibrate uncertainty better, while allowing for manual intervention to adapt spurious trend predictions.
 Tools need to be developed to facilitate this process at a larger scale.
@@
 Such a `hybrid' forecasting approach could for example ask humans to predict the trend of the effective reproduction number \(R_t\) or the doubling rate (i.e.~how the epidemic evolves) into the future and use this to estimate the exact number of cases, hospitalisations or deaths this would imply.
-This approach seems especially promising for forecasting deaths if a model can accurately describe delay distributions and epidemiological relationships between different parameters.
-In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust and widen confidence intervals may be another promising approach.
+In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust and widen prediction intervals may be another promising approach.
 Crowd forecasting in general could benefit greatly from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile for researchers and policymakers to further develop and explore.
+Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile to further develop and explore.
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
 
@@
 
+\clearpage
+
 \hypertarget{further-details-on-the-semi-mechanistic-forecasting-models}{%
@@
 2020; Abbott, Sherratt, et al.
-2020) and combining the posteriors for the mean and standard deviation of the log-normal distribution (Abbott, Hellewell, et al.
+2020) and combining the posteriors for the mean and standard deviation of the log-normal distribution (Abbott, Hellewell, Hickson, et al.
 2020; epiforecasts.io/covid n.d.; {``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid}-19 Outbreak in {England} \textbar{} {medRxiv}''} n.d.; Stan Development Team 2020).
@@
 
-Both models were implemented using the \texttt{EpiNow2} R package (version 1.3.3) (Abbott, Hellewell, et al.
+Both models were implemented using the \texttt{EpiNow2} R package (version 1.3.3) (Abbott, Hellewell, Hickson, et al.
 2020).
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} \caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the true observed values.
+\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} \caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the reported values.
 Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} \caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the true observed values.
+\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} \caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the reported values.
 Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} \caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the true observed values.
+\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} \caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the reported values.
 Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-abbottEstimatingTimevaryingReproduction2020a}{}}%
+Abbott, Sam, Joel Hellewell, Robin N.
+Thompson, Katharine Sherratt, Hamish P.
+Gibbs, Nikos I.
+Bosse, James D.
+Munday, et al.
+2020.
+{``Estimating the Time-Varying Reproduction Number of {SARS}-{CoV}-2 Using National and Subnational Case Counts,''} no.
+5:112 (June).
+\url{https://doi.org/10.12688/wellcomeopenres.16006.1}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
@@
 \url{https://doi.org/10.1186/s12879-016-1669-x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
+Bosse, Nikos. 2020. \emph{Scoringutils: A Collection of Proper Scoring Rules and Metrics to Assess Predictions}. \url{https://github.com/epiforecasts/scoringutils}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
+Bracher, J., D.
+Wolffram, J.
+Deuschel, K.
+Görgen, J.
+L.
+Ketterer, A.
+Ullrich, S.
+Abbott, et al.
+2021.
+{``National and Subnational Short-Term Forecasting of {COVID}-19 in {Germany} and {Poland}, Early 2021,''} November, 2021.11.05.21265810.
+\url{https://doi.org/10.1101/2021.11.05.21265810}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
@@
 \url{https://doi.org/10.1371/journal.pmed.1003542}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-COVID19DataExplorer}{}}%
-{``{COVID}-19 {Data Explorer}.''} n.d. {Our World in Data}. Accessed May 30, 2021. \url{https://ourworldindata.org/coronavirus-data-explorer}.
 
@@
 CSET Foretell. 2021. {``{CSET Foretell}.''} 2021. \url{https://www.cset-foretell.com/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
+Data, Our World in. 2020. {``{COVID}-19 {Data Explorer}.''} {Our World in Data}. 2020. \url{https://ourworldindata.org/coronavirus-data-explorer}.
 
@@
 \url{https://doi.org/10.1186/s12879-018-3124-7}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-deutschewelleCoronavirusGermanyImpose2020}{}}%
+Deutsche Welle.
+2020.
+{``Coronavirus: Germany to Impose One-Month Partial Lockdown \textbar{} {DW} \textbar{} 28.10.2020.''} 2020.
+\url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}.
 

### 2021-11-19 analysis/analysis.Rmd
latest updates to manuscript

@@
           legend.position = c(0.12, 0.83)) + 
-    labs(x = NULL, title = type, y = "WIS") + 
-    guides(fill = "none")
+    labs(x = NULL, title = type, y = "WIS")
 
@@
     scale_color_manual(values = colour) + 
-    scale_y_continuous(labels = scale_fn)
+    scale_y_continuous(labels = scale_fn) + 
+    guides(fill = "none", colour = "none")
 }
@@
                                    rel = relative, 
-                                   colour_scheme = colour_scheme[1])
+                                   colour_scheme = colour_scheme[1]) + 
+    guides(fill = "none")
   component_death <- component_plot(scores, "death", x = x, vals = vals, 
@@
 
-# Plot with Visualsiation of x week ahead forecasts and scores
+# Plot with Visualisation of x week ahead forecasts and scores
 

### 2021-11-19 manuscript/manuscript.Rmd

@@
 
-Our work suggests that crowd forecasts and model-based forecasts have slightly different advantages and may be able to complement each other well.
-Humans can use information that is hard to input into a model, while model-based approaches can perform more advanced calculations and are more easily scalable.
-When interpreting outputs it is important to distinguish between projections (which show what would happen in the absence of any events that could change the trend) and “genuine” forecasts (aiming to predict future data points whilst accounting for all factors that might influence them).
+Our work suggests that crowd forecasts and model-based forecasts have different strengths and may be able to complement each other.
+When choosing a suitable approach for a given task it is important to take into account how the output will be used.
+In this work we focused on forecasts (which aim to predict future data points whilst accounting for all factors that might influence them), whereas policy makers might be more interested in projections (which show what would happen in the absence of any events that could change the trend) or scenario modelling.
 Forecasts may not be a suitable basis for informing policy decisions, if forecasters already have factored in the expectation of a future intervention.
-Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting real projections from humans may be harder.
+Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting projections that are not influenced by implicit assumptions about the future from humans may be harder.
 

### 2021-11-19 manuscript/manuscript.tex

@@
 
-Our work suggests that crowd forecasts and model-based forecasts have slightly different advantages and may be able to complement each other well.
-Humans can use information that is hard to input into a model, while model-based approaches can perform more advanced calculations and are more easily scalable.
-When interpreting outputs it is important to distinguish between projections (which show what would happen in the absence of any events that could change the trend) and ``genuine'' forecasts (aiming to predict future data points whilst accounting for all factors that might influence them).
+Our work suggests that crowd forecasts and model-based forecasts have different strengths and may be able to complement each other.
+When choosing a suitable approach for a given task it is important to take into account how the output will be used.
+In this work we focused on forecasts (which aim to predict future data points whilst accounting for all factors that might influence them), whereas policy makers might be more interested in projections (which show what would happen in the absence of any events that could change the trend) or scenario modelling.
 Forecasts may not be a suitable basis for informing policy decisions, if forecasters already have factored in the expectation of a future intervention.
-Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting real projections from humans may be harder.
+Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting projections that are not influenced by implicit assumptions about the future from humans may be harder.
 

### 2021-11-23 manuscript/manuscript.Rmd
add reference to figure in SI

@@
 The application was built using the shiny and golem R packages [@golem; @shiny] and is available in the `crowdforecastr` R package [@crowdforecastr].
-To make a forecast in the application participants could select a predictive distribution representing the probability that the forecasted quantity took certain values, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values.
-[SCREENSHOT OF APPLICATION IN SI] The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.
+To make a forecast in the application participants could select a predictive distribution representing the probability that the forecasted quantity took certain values, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values (see screenshot in Figure \@ref(fig:screenshot) in the SI).
+The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.
 as $\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )$).

### 2021-11-23 manuscript/manuscript.tex
add reference to figure in SI

@@
 2020b).
-To make a forecast in the application participants could select a predictive distribution representing the probability that the forecasted quantity took certain values, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values.
-{[}SCREENSHOT OF APPLICATION IN SI{]} The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.~as \(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
+To make a forecast in the application participants could select a predictive distribution representing the probability that the forecasted quantity took certain values, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values (see screenshot in Figure \ref{fig:screenshot} in the SI).
+The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.~as \(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
 Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from (Data 2020).

### 2021-12-01 manuscript/manuscript.Rmd
correct citations, add acknowledgements, add ethics statement

--- 2021-11-19 manuscript/manuscript.Rmd
@@
   - GermanPolishpaper.bib
+csl: apa.csl
 ---
 
-Target journal: eLife
-
-*Nikos I. Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy J. Quilty, Mark Jit, CMMID Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk*
+*Nikos I.
+Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy J.
+Quilty, Mark Jit, Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk*
 
@@
 
-# Abstract (max 200 words, no subheadings)
+# Abstract
 
@@
 @delvalleSummaryResults201420152018; @farrowHumanJudgmentApproach2017] and now COVID-19 [e.g.
-@funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021; @EuroHub].
+@funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021; @europeancovid-19forecasthubEuropeanCovid19Forecast2021].
 Applications of epidemiological models differ in the way they make statements about the future.
@@
 
-Since March 2020, forecasts of COVID-19 from multiple teams have been collected, aggregated and compared by Forecast Hubs such as the US Forecast Hub [@cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], the German and Polish Forecast Hub [@bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021] and the European Forecast Hub [@EuroHub].
+Since March 2020, forecasts of COVID-19 from multiple teams have been collected, aggregated and compared by Forecast Hubs such as the US Forecast Hub [@cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], the German and Polish Forecast Hub [@bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021] and the European Forecast Hub [@europeancovid-19forecasthubEuropeanCovid19Forecast2021].
 Often, different individual forecasts are combined into a single forecast, e.g.
 by taking the mean or median of all forecasts.
-These ensemble forecasts usually tend to perform better and more consistently than individual forecasts [see e.g.
-@yamanaSuperensembleForecastsDengue2016; reichAccuracyRealtimeMultimodel2019].
-
-Individual computational models usually rely to varying degrees on mechanistic assumptions about infectious disease dynamics (such as SIR-type compartmental models that aim to represent how individuals move from being susceptible to infected and then recovered or dead) or are more statistical in nature (such as time series models that detect statistical patterns without explicitly modelling disease dynamics).
+These ensemble forecasts usually tend to perform better and more consistently than individual forecasts (see e.g.
+@yamanaSuperensembleForecastsDengue2016; @reichAccuracyRealtimeMultimodel2019).
+
+Individual computational models usually rely to varying degrees on mechanistic assumptions about infectious disease dynamics (such as SIR-type compartmental models that aim to represent how individuals move from being susceptible to infected and then recovered or dead).
+Some are more statistical in nature (such as time series models that detect statistical patterns without explicitly modelling disease dynamics).
 How exactly such a mathematical or computational model is constructed and which assumptions are made depends on subjective opinion and judgement of the researcher who develops and refines the model.
@@
 For example, @farrowHumanJudgmentApproach2017 found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available.
-However, humans tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown there and then.
+However, humans tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown in these regions at the time.
 
@@
 As a case study, we use different forecasts, involving varying degrees of human intervention, which we submitted in real time to the German and Polish Forecast Hub.
-In contrast to @farrowHumanJudgmentApproach2017 we elicited not only point predictions, but full predictive distributions (“probabilistic forecasts”)  [@heldProbabilisticForecastingInfectious2017] from participants.
-This allows us to compare not only predictive accuracy, but also how well human forecasters and model-based forecasts were able to quantify the appropriate forecast uncertainty.
+In contrast to @farrowHumanJudgmentApproach2017 we elicited not only point predictions, but full predictive distributions (“probabilistic forecasts”, see e.g.
+@heldProbabilisticForecastingInfectious2017) from participants.
+This allows us to compare not only predictive accuracy, but also how well human forecasters and model-based forecasts were able to quantify forecast uncertainty.
 
@@
 
-The German and Polish Forecast Hub elicits predictions for various COVID-19 related forecast targets from different research institutions every week.
+The German and Polish Forecast Hub (now mostly merged into the @europeancovid-19forecasthubEuropeanCovid19Forecast2021) elicits predictions for various COVID-19 related forecast targets from different research groups every week.
 Forecasts had to be made every Monday (with submissions allowed until Tuesday 3pm) and were permitted to use any data that was available by Monday 11.59pm.
@@
 
-Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish forecast hub.
-Until December 14th, 2020, these data were sourced from the European Centre for Disease Control (ECDC) [@ecdcDownloadHistoricalData2020].
+Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish Forecast hub.
+Until December 14th, 2020, these data were sourced from the European Centre for Disease Control [@ecdcDownloadHistoricalData2020].
 After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period  [@rkiRKICoronavirusSARSCoV22021].
-These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November [@forsal.plRozbieznosciStatystykachKoronawirusa2020]), changes in reporting over time and variation in testing regimes (e.g.
-in Germany from the 11th of November on [@aerzteblattSARSCoV2DiagnostikRKIPasst2020]).
+These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, @forsal.plRozbieznosciStatystykachKoronawirusa2020), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, @aerzteblattSARSCoV2DiagnostikRKIPasst2020).
 
@@
 Weekly forecasts had to be submitted before Tuesday 12pm every week, but participants were asked to only use any information or data that was already available by Monday night.
-The application was built using the shiny and golem R packages [@golem; @shiny] and is available in the `crowdforecastr` R package [@crowdforecastr].
-To make a forecast in the application participants could select a predictive distribution representing the probability that the forecasted quantity took certain values, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values.
-[SCREENSHOT OF APPLICATION IN SI] The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.
+The application was built using the `shiny` and `golem` R packages [@golem; @shiny] and is available in the `crowdforecastr` R package [@crowdforecastr].
+To make a forecast in the application participants could select a predictive distribution (with the default being log-normal) to represent the probability that the forecasted quantity took certain values.
+Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in Figure \@ref(fig:screenshot) in the SI).
+The default shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.
 as $\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )$).
-Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  [@ourworldindataCOVID19DataExplorer2020].
+Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  @ourworldindataCOVID19DataExplorer2020.
 These data included, for example, notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
@@
 On the 9th of November we altered the date when $R_t$ was assumed to be constant from two weeks prior to the date of the forecast to the forecast date, which we found to yield a more stable $R_t$ estimate.
-Reported case and death notifications were obtained by convolving predicted infections over data-based delay distributions [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation; @sherrattExploringSurveillanceData2021; @abbottEstimatingTimevaryingReproduction2020a] to model the time between infection and report date.
+Reported case and death notifications were obtained by convolving predicted infections over data-based delay distributions [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation2020; @sherrattExploringSurveillanceData2021; @abbottEstimatingTimevaryingReproduction2020a] to model the time between infection and report date.
 The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately.
@@
 Overall, low variance in forecast performance was closely linked with good mean performance (Figures \@ref(fig:agg-performance-all)H and and \@ref(fig:agg-performance-all)A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores), as well as the highest standard deviation of WIS values (relative WIS sd 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts  (rel.
+The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
 WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
@@
 The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \@ref(fig:agg-performance-all)F).
-Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \@ref(fig:agg-performance-all)A and \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)), implying that over-prediction (e.g.
-when missing a peak) tended to be more costly in terms of the WIS.
+Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \@ref(fig:agg-performance-all)A and \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
 
@@
 
-Theoretical considerations suggest that predicting a change in trend may be easier for deaths than for cases (as past cases and hospitalisations can be used as predictors).
+As past cases and hospitalisations can be used as predictors, predicting a change in trend may be easier for deaths than for cases.
 Even though all forecasts generally struggled with this, there were some instances where changing trends were well captured or even anticipated.
@@
 Only for predictions four weeks ahead would removing the renewal model have improved performance (Table \@ref(tab:score-table-ensemble-4)).
+The realised ensemble performed comparably to the crowd forecasts for predictions one to two weeks ahead, and worse for greater forecast horizons.
 
@@
 However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches [e.g.
-@funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], or exclusively on human forecasts [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016; @mcandrewExpertJudgmentModel2020, @recchiaHowWellDid2021].
+@funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], or exclusively on human forecasts [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016; @mcandrewExpertJudgmentModel2020; @recchiaHowWellDid2021].
 In contrast, we directly compared human and model-based forecasts.
@@
 In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-based insight.
-In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs [@cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @EuroHub; @funkShorttermForecastsInform2020].
+In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs [@cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @europeancovid-19forecasthubEuropeanCovid19Forecast2021; @funkShorttermForecastsInform2020].
 
@@
 
-________________
+\clearpage
+
+**Acknowledgements**
+
+NIB received funding from the Health Protection Research Unit (grant code NIHR200908).
+SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z).
+The work of JB was supported by the Helmholtz Foundation via the SIMCARD Information and Data Science Pilot Project.
+This research was partly funded by the National Institute for Health Research (NIHR) (16/137/109 & 16/136/46) using UK aid from the UK Government to support global health research.
+The views expressed in this publication are those of the author(s) and not necessarily those of the NIHR or the UK Department of Health and Social Care.
+BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859).
+EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688).
+AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID, and the Academy of Medical Sciences.
+SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z), and the NIHR (NIHR200908).
+
+We thank all forecasters who participated in this study for their contribution.
+
+We would also like to acknowledge (in a randomised order) the members of Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group at the the London School of Hygiene & Tropical Medicine: Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie Diamond, Katherine E.
+Atkins, Rein M G J Houben, Jiayao Lei, Rachel Lowe, David Simons, Sophie R Meakin, Nicholas G.
+Davies, Timothy W Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly, Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas, Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson, Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun, Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche, James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday, Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael Pung, Anna M Foss.
+
+\clearpage
 
@@
 For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
-  $$WIS = \frac{1}{K + 0.5} \cdot (w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y)),$$ 
+  $$WIS = \frac{1}{K + 0.5} \cdot \left( w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y) \right), $$
   where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
@@
 This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
-We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1% or 1769 samples of the available data  [@kraemer2020epidemiological; @covidregionaldata] and combining the posteriors for the mean and standard deviation of the log-normal distribution [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation; @EvaluatingUseReproduction; @rstan].
+We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1% or 1769 samples of the available data  [@kraemer2020epidemiological; @covidregionaldata] and combining the posteriors for the mean and standard deviation of the log-normal distribution [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation2020; @EvaluatingUseReproduction; @rstan].
 

### 2021-12-01 manuscript/manuscript.tex
correct citations, add acknowledgements, add ethics statement

--- 2021-11-19 manuscript/manuscript.tex
@@
 
-Target journal: eLife
-
-\emph{Nikos I. Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy J. Quilty, Mark Jit, CMMID Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk}
-
-\hypertarget{abstract-max-200-words-no-subheadings}{%
-\section{Abstract (max 200 words, no subheadings)}\label{abstract-max-200-words-no-subheadings}}
+\emph{Nikos I.
+Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy J.
+Quilty, Mark Jit, Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk}
+
+\hypertarget{abstract}{%
+\section{Abstract}\label{abstract}}
 
@@
 
-Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza (e.g.
-McGowan et al.
-2019; Reich et al.
-2019; Shaman and Karspeck 2012; Biggerstaff et al.
-2016), dengue fever (e.g.
-Johansson et al.
-2019; Yamana, Kandula, and Shaman 2016; Colón-González et al.
-2021), ebola (e.g.
-Viboud et al.
-2018; Funk et al.
-2019), chikungunya (e.g.
-Del Valle et al.
-2018; Farrow et al.
-2017) and now COVID-19 (e.g.
-Funk et al.
-2020; Cramer et al.
-2020; Cramer et al.
-2021; Johannes Bracher, Wolffram, et al.
-2021; J.
-Bracher et al.
-2021; Hub 2021).
+Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza (Biggerstaff et al., 2016; e.g.
+McGowan et al., 2019; Reich, Brooks, et al., 2019; Shaman \& Karspeck, 2012), dengue fever (Colón-González et al., 2021; e.g.
+Johansson et al., 2019; Yamana et al., 2016), ebola (Funk et al., 2019; e.g.
+Viboud et al., 2018), chikungunya (e.g.
+Del Valle et al., 2018; Farrow et al., 2017) and now COVID-19 (Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Castro, et al., 2021; Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Fiedler, et al., 2021; Cramer et al., 2021; Cramer et al., 2020; European Covid-19 Forecast Hub, 2021; e.g.
+Funk et al., 2020).
 Applications of epidemiological models differ in the way they make statements about the future.
@@
 
-Since March 2020, forecasts of COVID-19 from multiple teams have been collected, aggregated and compared by Forecast Hubs such as the US Forecast Hub (Cramer et al.
-2020; Cramer et al.
-2021), the German and Polish Forecast Hub (Johannes Bracher, Wolffram, et al.
-2021; J.
-Bracher et al.
-2021) and the European Forecast Hub (Hub 2021).
+Since March 2020, forecasts of COVID-19 from multiple teams have been collected, aggregated and compared by Forecast Hubs such as the US Forecast Hub (Cramer et al., 2021; Cramer et al., 2020), the German and Polish Forecast Hub (Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Castro, et al., 2021; Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Fiedler, et al., 2021) and the European Forecast Hub (European Covid-19 Forecast Hub, 2021).
 Often, different individual forecasts are combined into a single forecast, e.g.~by taking the mean or median of all forecasts.
-These ensemble forecasts usually tend to perform better and more consistently than individual forecasts {[}see e.g.
-Yamana, Kandula, and Shaman (2016); reichAccuracyRealtimeMultimodel2019{]}.
-
-Individual computational models usually rely to varying degrees on mechanistic assumptions about infectious disease dynamics (such as SIR-type compartmental models that aim to represent how individuals move from being susceptible to infected and then recovered or dead) or are more statistical in nature (such as time series models that detect statistical patterns without explicitly modelling disease dynamics).
+These ensemble forecasts usually tend to perform better and more consistently than individual forecasts (see e.g.
+Yamana et al.
+(2016); Reich, McGowan, et al.
+(2019)).
+
+Individual computational models usually rely to varying degrees on mechanistic assumptions about infectious disease dynamics (such as SIR-type compartmental models that aim to represent how individuals move from being susceptible to infected and then recovered or dead).
+Some are more statistical in nature (such as time series models that detect statistical patterns without explicitly modelling disease dynamics).
 How exactly such a mathematical or computational model is constructed and which assumptions are made depends on subjective opinion and judgement of the researcher who develops and refines the model.
@@
 
-Previous work has examined such direct human forecasts in various contexts, such as geopolitics (Tetlock et al.
-2014; Atanasov et al.
-2016), meta-science (Hoogeveen, Sarafoglou, and Wagenmakers 2020; ReplicationMarkets 2020), sports (Servan-Schreiber et al.
-2004) and epidemiology (Farrow et al.
-2017; McAndrew and Reich 2020; Recchia, Freeman, and Spiegelhalter 2021).
-Several prediction platforms (Metaculus 2020; Hypermind 2021; CSET Foretell 2021) and prediction markets (PredictIt 2021) have been created to collate expert and non-expert predictions.
+Previous work has examined such direct human forecasts in various contexts, such as geopolitics (Atanasov et al., 2016; Tetlock et al., 2014), meta-science (Hoogeveen et al., 2020; ReplicationMarkets, 2020), sports (Servan-Schreiber et al., 2004) and epidemiology (Farrow et al., 2017; McAndrew \& Reich, 2020; Recchia et al., 2021).
+Several prediction platforms (CSET Foretell, 2021; Hypermind, 2021; Metaculus, 2020) and prediction markets (PredictIt, 2021) have been created to collate expert and non-expert predictions.
 However, with the notable exception of Farrow et al.
@@
 (2017) found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available.
-However, humans tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown there and then.
+However, humans tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown in these regions at the time.
 
@@
 In contrast to Farrow et al.
-(2017) we elicited not only point predictions, but full predictive distributions (``probabilistic forecasts'') (Held, Meyer, and Bracher 2017) from participants.
-This allows us to compare not only predictive accuracy, but also how well human forecasters and model-based forecasts were able to quantify the appropriate forecast uncertainty.
+(2017) we elicited not only point predictions, but full predictive distributions (``probabilistic forecasts'', see e.g.
+Held et al.
+(2017)) from participants.
+This allows us to compare not only predictive accuracy, but also how well human forecasters and model-based forecasts were able to quantify forecast uncertainty.
 
@@
 
-We created and submitted the following forecasts to the German and Polish Forecast Hub: 1) a direct human forecast (henceforth called ``crowd forecast''), elicited from participants through a web application (N.
-I.
-Bosse et al.
-2020b) and 2) two semi-mechanistic model-based forecasts (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology.
+We created and submitted the following forecasts to the German and Polish Forecast Hub: 1) a direct human forecast (henceforth called ``crowd forecast''), elicited from participants through a web application (Bosse, Abbott, EpiForecasts, et al., 2020b) and 2) two semi-mechanistic model-based forecasts (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology.
 While the two semi-mechanistic forecasts were necessarily shaped by our implicit assumptions and decisions, they were designed such as to minimise the amount of human intervention involved.
 For example, we refrained from adjusting model outputs or refining the models based on past performance.
-Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (Johannes Bracher, Wolffram, et al.
-2021; J.
-Bracher et al.
-2021).
-All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (N.
-I.
-Bosse et al.
-2020a).
+Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Castro, et al., 2021; Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Fiedler, et al., 2021).
+All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (Bosse, Abbott, EpiForecasts, et al., 2020a).
 This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub.
@@
 
-The German and Polish Forecast Hub elicits predictions for various COVID-19 related forecast targets from different research institutions every week.
+The German and Polish Forecast Hub (now mostly merged into the European Covid-19 Forecast Hub (2021)) elicits predictions for various COVID-19 related forecast targets from different research groups every week.
 Forecasts had to be made every Monday (with submissions allowed until Tuesday 3pm) and were permitted to use any data that was available by Monday 11.59pm.
@@
 
-Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish forecast hub.
-Until December 14th, 2020, these data were sourced from the European Centre for Disease Control (ECDC) (ECDC 2020).
-After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (RKI 2021).
-These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November (Forsal.pl 2020)), changes in reporting over time and variation in testing regimes (e.g.~in Germany from the 11th of November on (Ärzteblatt 2020)).
+Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish Forecast hub.
+Until December 14th, 2020, these data were sourced from the European Centre for Disease Control (ECDC, 2020).
+After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (RKI, 2021).
+These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, Forsal.pl (2020)), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, Ärzteblatt (2020)).
 
@@
 Weekly forecasts had to be submitted before Tuesday 12pm every week, but participants were asked to only use any information or data that was already available by Monday night.
-The application was built using the shiny and golem R packages (Fay et al.
-2021; Chang et al.
-2021) and is available in the \texttt{crowdforecastr} R package (N.
-I.
-Bosse et al.
-2020b).
-To make a forecast in the application participants could select a predictive distribution representing the probability that the forecasted quantity took certain values, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values.
-{[}SCREENSHOT OF APPLICATION IN SI{]} The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.~as \(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
-Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from (Data 2020).
+The application was built using the \texttt{shiny} and \texttt{golem} R packages (Chang et al., 2021; Fay et al., 2021) and is available in the \texttt{crowdforecastr} R package (Bosse, Abbott, EpiForecasts, et al., 2020b).
+To make a forecast in the application participants could select a predictive distribution (with the default being log-normal) to represent the probability that the forecasted quantity took certain values.
+Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in Figure \ref{fig:screenshot} in the SI).
+The default shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.~as \(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
+Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from Our World in Data (2020).
 These data included, for example, notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
@@
 
-We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, Hickson, et al.
-2020).
-The first of these models, here called ``renewal model'', used the renewal equation (Fraser 2007) to predict reported cases and deaths (see details in the SI).
+We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, Hickson, et al., 2020).
+The first of these models, here called ``renewal model'', used the renewal equation (Fraser, 2007) to predict reported cases and deaths (see details in the SI).
 It estimated the effective reproduction number \(R_t\) (the average number of people each person infected at time t is expected to infect in turn) and modelled future infections as a weighted sum of past infection multiplied by \(R_t\).
@@
 On the 9th of November we altered the date when \(R_t\) was assumed to be constant from two weeks prior to the date of the forecast to the forecast date, which we found to yield a more stable \(R_t\) estimate.
-Reported case and death notifications were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, Hickson, et al.
-2020; epiforecasts.io/covid n.d.; Sherratt et al.
-2021; Abbott, Hellewell, Thompson, et al.
-2020) to model the time between infection and report date.
+Reported case and death notifications were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, Thompson, et al., 2020; Abbott, Hellewell, Hickson, et al., 2020; epiforecasts.io/covid, 2020; Sherratt et al., 2021) to model the time between infection and report date.
 The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately.
@@
 The convolution model predicted deaths as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
-Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model with a multiplicative day-of-the-week effect (Abbott, Hellewell, Hickson, et al.
-2020).
-
-Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al.
-2020) with data available up to the 1st of August.
-All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fitted separately.
+Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model with a multiplicative day-of-the-week effect (Abbott, Hellewell, Hickson, et al., 2020).
+
+Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., 2020) with data available up to the 1st of August.
+All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team, 2020) with each location and forecast target being fitted separately.
 
@@
 
-For the main analysis we focused mostly on two week ahead forecasts, as COVID-19 forecasts, especially for cases, were in the past found to have poor predictive performance beyond this horizon (Johannes Bracher, Wolffram, et al.
-2021).
+For the main analysis we focused mostly on two week ahead forecasts, as COVID-19 forecasts, especially for cases, were in the past found to have poor predictive performance beyond this horizon (Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Castro, et al., 2021).
 Forecasts for cases were scored using the full period from October 2020 until March 2021.
@@
 
-Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Johannes Bracher, Ray, et al.
-2021), the absolute error, relative bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule (Gneiting and Raftery 2007), meaning that in expectation the score is optimised by reporting a predictive distribution that is identical to the true data-generating distribution.
+Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Bracher, Ray, et al., 2021), the absolute error, relative bias, and empirical coverage of the 50\% and 90\% prediction intervals.
+The WIS is a proper scoring rule (Gneiting \& Raftery, 2007), meaning that in expectation the score is optimised by reporting a predictive distribution that is identical to the true data-generating distribution.
 Forecasters are therefore incentivised to report their true belief about the future.
@@
 While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts.
-The bias metric (Funk et al.
-2019) we use captures how much probability mass of the forecast was above or below the true value (mapped to values between -1 and 1) and therefore represents a general tendency to over- or under-predict in relative terms.
+The bias metric (Funk et al., 2019) we use captures how much probability mass of the forecast was above or below the true value (mapped to values between -1 and 1) and therefore represents a general tendency to over- or under-predict in relative terms.
 A value of -1 implies that all quantiles of the predictive distribution are below the observed value and a value of 1 that all quantiles are above the observed value.
@@
 Scoring metrics are explained in more detail in Table \ref{tab:scoring-metrics} in the SI.
-All scores were calculated using the \texttt{scoringutils} R package (N.
-Bosse 2020).
+All scores were calculated using the \texttt{scoringutils} R package (Bosse, Abbott, EpiForecasts, et al., 2020c).
 
@@
 Overall, low variance in forecast performance was closely linked with good mean performance (Figures \ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \ref{fig:distribution-scores}, as well as the highest standard deviation of WIS values (relative WIS sd 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
+The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \ref{fig:distribution-scores}, as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
 WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
@@
 The Hub ensemble and the crowd forecast, which had both been under-predicting throughout October, also failed to predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 (Deutsche Welle 2020) and the change in the testing regime (with stricter test criteria) on November 11th 2020 (Ärzteblatt 2020), were fastest to adapt to the new trend, and the Hub ensemble slowest.
+Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 (Deutsche Welle, 2020) and the change in the testing regime (with stricter test criteria) on November 11th 2020 (Ärzteblatt, 2020), were fastest to adapt to the new trend, and the Hub ensemble slowest.
 In December, cases rose again in Germany, with all models under-predicting this growth to varying extents.
@@
 The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \ref{fig:agg-performance-all}F).
-Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}), implying that over-prediction (e.g.~when missing a peak) tended to be more costly in terms of the WIS.
+Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
 
@@
 Only for predictions four weeks ahead would removing the renewal model have improved performance (Table \ref{tab:score-table-ensemble-4}).
+The realised ensemble performed comparably to the crowd forecasts for predictions one to two weeks ahead, and worse for greater forecast horizons.
 
@@
 Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (e.g.
-Funk et al.
-2020; Cramer et al.
-2020; Cramer et al.
-2021), or exclusively on human forecasts Recchia, Freeman, and Spiegelhalter (2021).
+However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (Cramer et al., 2021; Cramer et al., 2020; e.g.
+Funk et al., 2020), or exclusively on human forecasts (Atanasov et al., 2016; McAndrew \& Reich, 2020; Recchia et al., 2021; Tetlock et al., 2014).
 In contrast, we directly compared human and model-based forecasts.
@@
 In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-based insight.
-In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (Cramer et al.
-2020; Cramer et al.
-2021; Johannes Bracher, Wolffram, et al.
-2021; Hub 2021; Funk et al.
-2020).
+In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Castro, et al., 2021; Cramer et al., 2021; Cramer et al., 2020; European Covid-19 Forecast Hub, 2021; Funk et al., 2020).
 
@@
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+\clearpage
+
+\textbf{Acknowledgements}
+
+NIB received funding from the Health Protection Research Unit (grant code NIHR200908).
+SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z).
+The work of JB was supported by the Helmholtz Foundation via the SIMCARD Information and Data Science Pilot Project.
+This research was partly funded by the National Institute for Health Research (NIHR) (16/137/109 \& 16/136/46) using UK aid from the UK Government to support global health research.
+The views expressed in this publication are those of the author(s) and not necessarily those of the NIHR or the UK Department of Health and Social Care.
+BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859).
+EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688).
+AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID, and the Academy of Medical Sciences.
+SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z), and the NIHR (NIHR200908).
+
+We thank all forecasters who participated in this study for their contribution.
+
+We would also like to acknowledge (in a randomised order) the members of Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group at the the London School of Hygiene \& Tropical Medicine: Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie Diamond, Katherine E.
+Atkins, Rein M G J Houben, Jiayao Lei, Rachel Lowe, David Simons, Sophie R Meakin, Nicholas G.
+Davies, Timothy W Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly, Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas, Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson, Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun, Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche, James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday, Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael Pung, Anna M Foss.
+
+\clearpage
 
@@
 
-The prior for the generation time was sourced from (Ganyani et al.
-2020) but refit using a log-normal incubation period with a mean of 5.2 days (SD 1.1) and SD of 1.52 days (SD 1.1) with this incubation period also being used as a prior (Lauer et al.
-2020) for \(\xi_{O}\).
+The prior for the generation time was sourced from (Ganyani et al., 2020) but refit using a log-normal incubation period with a mean of 5.2 days (SD 1.1) and SD of 1.52 days (SD 1.1) with this incubation period also being used as a prior (Lauer et al., 2020) for \(\xi_{O}\).
 This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
-We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1\% or 1769 samples of the available data (Xu et al.
-2020; Abbott, Sherratt, et al.
-2020) and combining the posteriors for the mean and standard deviation of the log-normal distribution (Abbott, Hellewell, Hickson, et al.
-2020; epiforecasts.io/covid n.d.; {``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid}-19 Outbreak in {England} \textbar{} {medRxiv}''} n.d.; Stan Development Team 2020).
-
-\(GP_t\) is an approximate Hilbert space Gaussian process as defined in (Riutort-Mayol et al.
-2020) using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20\% of the number of days used in fitting).
+We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1\% or 1769 samples of the available data (Abbott, Sherratt, et al., 2020; Xu et al., 2020) and combining the posteriors for the mean and standard deviation of the log-normal distribution (Abbott, Hellewell, Hickson, et al., 2020; epiforecasts.io/covid, 2020; \emph{Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid}-19 Outbreak in {England} \textbar{} {medRxiv}}, n.d.; Stan Development Team, 2020).
+
+\(GP_t\) is an approximate Hilbert space Gaussian process as defined in (Riutort-Mayol et al., 2020) using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20\% of the number of days used in fitting).
 The length scale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
@@
 where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\) and \(I'_t\) are the unadjusted infections defined above.
-This adjustment is based on that implemented in the \texttt{epidemia} R package (Scott et al.
-2020; Bhatt et al., n.d.).
+This adjustment is based on that implemented in the \texttt{epidemia} R package (Bhatt et al., n.d.; Scott et al., 2020).
 
@@
 
-Both models were implemented using the \texttt{EpiNow2} R package (version 1.3.3) (Abbott, Hellewell, Hickson, et al.
-2020).
-Each forecast target was fitted independently for each model using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020).
+Both models were implemented using the \texttt{EpiNow2} R package (version 1.3.3) (Abbott, Hellewell, Hickson, et al., 2020).
+Each forecast target was fitted independently for each model using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team, 2020).
 A minimum of 4 chains were used with a warmup of 250 samples for the renewal equation-based model and 1000 samples for the convolution model.
@@
 Different settings were chosen for each model to optimise compute time contingent on convergence.
-Convergence was assessed using the R hat diagnostic (Stan Development Team 2020).
+Convergence was assessed using the R hat diagnostic (Stan Development Team, 2020).
 For the convolution model forecast the case forecast from the renewal equation model was used in place of observed cases beyond the forecast horizon using 1000 posterior samples.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
-Abbott, Sam, Joel Hellewell, Joe Hickson, James Munday, Katelyn Gostic, Peter Ellis, Katharine Sherratt, et al.
-2020.
-{``EpiNow2: Estimate Real-Time Case Counts and Time-Varying Epidemiological Parameters.''} \emph{-} - (-): --.
-\url{https://doi.org/10.5281/zenodo.3957489}.
+Abbott, S., Hellewell, J., Hickson, J., Munday, J., Gostic, K., Ellis, P., Sherratt, K., Gibbs, H., Thompson, R., Meakin, S., Bosse, N.
+I., Mee, P., \& Funk, S.
+(2020).
+EpiNow2: Estimate real-time case counts and time-varying epidemiological parameters.
+\emph{-}, \emph{-}(-), --.
+\url{https://doi.org/10.5281/zenodo.3957489}
 
 \leavevmode\vadjust pre{\hypertarget{ref-abbottEstimatingTimevaryingReproduction2020a}{}}%
-Abbott, Sam, Joel Hellewell, Robin N.
-Thompson, Katharine Sherratt, Hamish P.
-Gibbs, Nikos I.
-Bosse, James D.
-Munday, et al.
-2020.
-{``Estimating the Time-Varying Reproduction Number of {SARS}-{CoV}-2 Using National and Subnational Case Counts,''} no.
-5:112 (June).
-\url{https://doi.org/10.12688/wellcomeopenres.16006.1}.
+Abbott, S., Hellewell, J., Thompson, R.
+N., Sherratt, K., Gibbs, H.
+P., Bosse, N.
+I., Munday, J.
+D., Meakin, S., Doughty, E.
+L., Chun, J.
+Y., Chan, Y.-W.
+D., Finger, F., Campbell, P., Endo, A., Pearson, C.
+A.
+B., Gimma, A., Russell, T., Group, C.
+C.
+modelling, Flasche, S., \ldots{} Funk, S.
+(2020).
+\emph{Estimating the time-varying reproduction number of {SARS}-{CoV}-2 using national and subnational case counts}.
+\emph{5:112}.
+\url{https://doi.org/10.12688/wellcomeopenres.16006.1}
 
 \leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
-Abbott, Sam, Katharine Sherratt, Jonnie Bevan, Hamish Gibbs, Joel Hellewell, James Munday, Patrick Barks, Paul Campbell, Flavio Finger, and Sebastian Funk.
-2020.
-{``Covidregionaldata: Subnational Data for the Covid-19 Outbreak.''} \emph{-} - (-): --.
-\url{https://doi.org/10.5281/zenodo.3957539}.
+Abbott, S., Sherratt, K., Bevan, J., Gibbs, H., Hellewell, J., Munday, J., Barks, P., Campbell, P., Finger, F., \& Funk, S.
+(2020).
+Covidregionaldata: Subnational data for the covid-19 outbreak.
+\emph{-}, \emph{-}(-), --.
+\url{https://doi.org/10.5281/zenodo.3957539}
 
 \leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
-Ärzteblatt, Deutscher Ärzteverlag GmbH, Redaktion Deutsches.
-2020.
-{``SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an.''} {Deutsches Ärzteblatt}.
-November 3, 2020.
-\url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}.
+Ärzteblatt, D.
+Ä.
+G., Redaktion Deutsches.
+(2020, November 3).
+\emph{SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an}.
+{Deutsches Ärzteblatt}.
+\url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}
 
 \leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
-Atanasov, Pavel, Phillip Rescober, Eric Stone, Samuel A.
-Swift, Emile Servan-Schreiber, Philip Tetlock, Lyle Ungar, and Barbara Mellers.
-2016.
-{``Distilling the {Wisdom} of {Crowds}: Prediction {Markets} Vs.
-{Prediction Polls}.''} \emph{Management Science} 63 (3): 691--706.
-\url{https://doi.org/10.1287/mnsc.2015.2374}.
+Atanasov, P., Rescober, P., Stone, E., Swift, S.
+A., Servan-Schreiber, E., Tetlock, P., Ungar, L., \& Mellers, B.
+(2016).
+Distilling the {Wisdom} of {Crowds}: Prediction {Markets} vs.
+{Prediction Polls}.
+\emph{Management Science}, \emph{63}(3), 691--706.
+\url{https://doi.org/10.1287/mnsc.2015.2374}
 
 \leavevmode\vadjust pre{\hypertarget{ref-bhattSemiMechanisticBayesianModeling}{}}%
-Bhatt, Samir, Neil Ferguson, Seth Flaxman, Axel Gandy, Swapnil Mishra, and James A Scott. n.d. {``Semi-{Mechanistic Bayesian} Modeling of {COVID}-19 with {Renewal Processes},''} 14.
+Bhatt, S., Ferguson, N., Flaxman, S., Gandy, A., Mishra, S., \& Scott, J. A. (n.d.). \emph{Semi-{Mechanistic Bayesian} modeling of {COVID}-19 with {Renewal Processes}}. 14.
 
 \leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
-Biggerstaff, Matthew, David Alper, Mark Dredze, Spencer Fox, Isaac Chun-Hai Fung, Kyle S.
-Hickmann, Bryan Lewis, et al.
-2016.
-{``Results from the Centers for Disease Control and Prevention's Predict the 2013--2014 {Influenza Season Challenge}.''} \emph{BMC Infectious Diseases} 16 (1): 357.
-\url{https://doi.org/10.1186/s12879-016-1669-x}.
+Biggerstaff, M., Alper, D., Dredze, M., Fox, S., Fung, I.
+C.-H., Hickmann, K.
+S., Lewis, B., Rosenfeld, R., Shaman, J., Tsou, M.-H., Velardi, P., Vespignani, A., Finelli, L., \& for the Influenza Forecasting Contest Working Group.
+(2016).
+Results from the centers for disease control and prevention's predict the 2013--2014 {Influenza Season Challenge}.
+\emph{BMC Infectious Diseases}, \emph{16}(1), 357.
+\url{https://doi.org/10.1186/s12879-016-1669-x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
+Bosse, N. I., Abbott, S., EpiForecasts, \& Funk, S. (2020a). \emph{Covid.german.forecasts: Forecasting covid-19 related metrics for the german/poland forecast hub}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
+Bosse, N. I., Abbott, S., EpiForecasts, \& Funk, S. (2020b). \emph{Crowdforecastr: Eliciting crowd forecasts in r shiny}. \url{https://doi.org/10.5281/zenodo.4618519}
 
 \leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
-Bosse, Nikos. 2020. \emph{Scoringutils: A Collection of Proper Scoring Rules and Metrics to Assess Predictions}. \url{https://github.com/epiforecasts/scoringutils}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
-Bosse, Nikos I., Sam Abbott, EpiForecasts, and Sebastian Funk. 2020a. \emph{Covid.german.forecasts: Forecasting Covid-19 Related Metrics for the German/Poland Forecast Hub}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
----------. 2020b. \emph{Crowdforecastr: Eliciting Crowd Forecasts in r Shiny}. \url{https://doi.org/10.5281/zenodo.4618519}.
+Bosse, N. I., Abbott, S., EpiForecasts, \& Funk, S. (2020c). \emph{Scoringutils: Utilities for scoring and assessing predictions}. \url{https://doi.org/10.5281/zenodo.4618017}
 
 \leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
-Bracher, Johannes, Evan L.
-Ray, Tilmann Gneiting, and Nicholas G.
-Reich.
-2021.
-{``Evaluating Epidemic Forecasts in an Interval Format.''} \emph{PLoS Computational Biology} 17 (2): e1008618.
-\url{https://doi.org/10.1371/journal.pcbi.1008618}.
+Bracher, J., Ray, E.
+L., Gneiting, T., \& Reich, N.
+G.
+(2021).
+Evaluating epidemic forecasts in an interval format.
+\emph{PLoS Computational Biology}, \emph{17}(2), e1008618.
+\url{https://doi.org/10.1371/journal.pcbi.1008618}
 
 \leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
-Bracher, Johannes, Daniel Wolffram, J.
-Deuschel, K.
-Görgen, J.
-L.
-Ketterer, A.
-Ullrich, S.
-Abbott, et al.
-2021.
-{``Short-Term Forecasting of {COVID}-19 in {Germany} and {Poland} During the Second Wave -- a Preregistered Study.''} \emph{medRxiv}, January, 2020.12.24.20248826.
-\url{https://doi.org/10.1101/2020.12.24.20248826}.
+Bracher, J., Wolffram, D., Deuschel, J., Görgen, K., Ketterer, J.
+L., Ullrich, A., Abbott, S., Barbarossa, M.
+V., Bertsimas, D., Bhatia, S., Bodych, M., Bosse, N.
+I., Burgard, J.
+P., Castro, L., Fairchild, G., Fuhrmann, J., Funk, S., Gogolewski, K., Gu, Q., \ldots{} Schienle, M.
+(2021).
+Short-term forecasting of {COVID}-19 in {Germany} and {Poland} during the second wave -- a preregistered study.
+\emph{medRxiv}, 2020.12.24.20248826.
+\url{https://doi.org/10.1101/2020.12.24.20248826}
 
 \leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
-Bracher, J., D.
-Wolffram, J.
-Deuschel, K.
-Görgen, J.
-L.
-Ketterer, A.
-Ullrich, S.
-Abbott, et al.
-2021.
-{``National and Subnational Short-Term Forecasting of {COVID}-19 in {Germany} and {Poland}, Early 2021,''} November, 2021.11.05.21265810.
-\url{https://doi.org/10.1101/2021.11.05.21265810}.
+Bracher, J., Wolffram, D., Deuschel, J., Görgen, K., Ketterer, J.
+L., Ullrich, A., Abbott, S., Barbarossa, M.
+V., Bertsimas, D., Bhatia, S., Bodych, M., Bosse, N.
+I., Burgard, J.
+P., Fiedler, J., Fuhrmann, J., Funk, S., Gambin, A., Gogolewski, K., Heyder, S., \ldots{} Schienle, M.
+(2021).
+\emph{National and subnational short-term forecasting of {COVID}-19 in {Germany} and {Poland}, early 2021}.
+2021.11.05.21265810.
+\url{https://doi.org/10.1101/2021.11.05.21265810}
 
 \leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
-Chang, Winston, Joe Cheng, JJ Allaire, Carson Sievert, Barret Schloerke, Yihui Xie, Jeff Allen, Jonathan McPherson, Alan Dipert, and Barbara Borges.
-2021.
-\emph{Shiny: Web Application Framework for r}.
-\url{https://CRAN.R-project.org/package=shiny}.
+Chang, W., Cheng, J., Allaire, J., Sievert, C., Schloerke, B., Xie, Y., Allen, J., McPherson, J., Dipert, A., \& Borges, B.
+(2021).
+\emph{Shiny: Web application framework for r}.
+\url{https://CRAN.R-project.org/package=shiny}
 
 \leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
-Colón-González, Felipe J., Leonardo Soares Bastos, Barbara Hofmann, Alison Hopkin, Quillon Harpham, Tom Crocker, Rosanna Amato, et al.
-2021.
-{``Probabilistic Seasonal Dengue Forecasting in {Vietnam}: A Modelling Study Using Superensembles.''} \emph{PLOS Medicine} 18 (3): e1003542.
-\url{https://doi.org/10.1371/journal.pmed.1003542}.
+Colón-González, F.
+J., Bastos, L.
+S., Hofmann, B., Hopkin, A., Harpham, Q., Crocker, T., Amato, R., Ferrario, I., Moschini, F., James, S., Malde, S., Ainscoe, E., Nam, V.
+S., Tan, D.
+Q., Khoa, N.
+D., Harrison, M., Tsarouchi, G., Lumbroso, D., Brady, O.
+J., \& Lowe, R.
+(2021).
+Probabilistic seasonal dengue forecasting in {Vietnam}: A modelling study using superensembles.
+\emph{PLOS Medicine}, \emph{18}(3), e1003542.
+\url{https://doi.org/10.1371/journal.pmed.1003542}
 
 \leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
-Cramer, Estee, Evan L.
-Ray, Velma K.
-Lopez, Johannes Bracher, Andrea Brennen, Alvaro J.
-Castro Rivadeneira, Aaron Gerding, et al.
-2021.
-{``Evaluation of Individual and Ensemble Probabilistic Forecasts of {COVID}-19 Mortality in the {US}.''} \emph{medRxiv}, February, 2021.02.03.21250974.
-\url{https://doi.org/10.1101/2021.02.03.21250974}.
+Cramer, E., Ray, E.
+L., Lopez, V.
+K., Bracher, J., Brennen, A., Rivadeneira, A.
+J.
+C., Gerding, A., Gneiting, T., House, K.
+H., Huang, Y., Jayawardena, D., Kanji, A.
+H., Khandelwal, A., Le, K., Mühlemann, A., Niemi, J., Shah, A., Stark, A., Wang, Y., \ldots{} Reich, N.
+G.
+(2021).
+Evaluation of individual and ensemble probabilistic forecasts of {COVID}-19 mortality in the {US}.
+\emph{medRxiv}, 2021.02.03.21250974.
+\url{https://doi.org/10.1101/2021.02.03.21250974}
 
 \leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
-Cramer, Estee, Nicholas G Reich, Serena Yijin Wang, Jarad Niemi, Abdul Hannan, Katie House, Youyang Gu, et al.
-2020.
-{``{COVID}-19 {Forecast Hub}: 4 {December} 2020 Snapshot.''} {Zenodo}.
-\url{https://doi.org/10.5281/zenodo.3963371}.
+Cramer, E., Reich, N.
+G., Wang, S.
+Y., Niemi, J., Hannan, A., House, K., Gu, Y., Xie, S., Horstman, S., aniruddhadiga, Walraven, R., starkari, Li, M.
+L., Gibson, G., Castro, L., Karlen, D., Wattanachit, N., jinghuichen, zyt9lsb, \ldots{} leyouz.
+(2020).
+\emph{{COVID}-19 {Forecast Hub}: 4 {December} 2020 snapshot} {[}Data set{]}.
+{Zenodo}.
+\url{https://doi.org/10.5281/zenodo.3963371}
 
 \leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
-CSET Foretell. 2021. {``{CSET Foretell}.''} 2021. \url{https://www.cset-foretell.com/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
-Data, Our World in. 2020. {``{COVID}-19 {Data Explorer}.''} {Our World in Data}. 2020. \url{https://ourworldindata.org/coronavirus-data-explorer}.
+CSET Foretell. (2021). \emph{{CSET Foretell}}. \url{https://www.cset-foretell.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
-Del Valle, Sara Y., Benjamin H.
-McMahon, Jason Asher, Richard Hatchett, Joceline C.
-Lega, Heidi E.
-Brown, Mark E.
-Leany, et al.
-2018.
-{``Summary Results of the 2014-2015 {DARPA Chikungunya} Challenge.''} \emph{BMC Infectious Diseases} 18 (1): 245.
-\url{https://doi.org/10.1186/s12879-018-3124-7}.
+Del Valle, S.
+Y., McMahon, B.
+H., Asher, J., Hatchett, R., Lega, J.
+C., Brown, H.
+E., Leany, M.
+E., Pantazis, Y., Roberts, D.
+J., Moore, S., Peterson, A.
+T., Escobar, L.
+E., Qiao, H., Hengartner, N.
+W., \& Mukundan, H.
+(2018).
+Summary results of the 2014-2015 {DARPA Chikungunya} challenge.
+\emph{BMC Infectious Diseases}, \emph{18}(1), 245.
+\url{https://doi.org/10.1186/s12879-018-3124-7}
 
@@
 Deutsche Welle.
-2020.
-{``Coronavirus: Germany to Impose One-Month Partial Lockdown \textbar{} {DW} \textbar{} 28.10.2020.''} 2020.
-\url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}.
+(2020).
+\emph{Coronavirus: Germany to impose one-month partial lockdown \textbar{} {DW} \textbar{} 28.10.2020}.
+\url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}
 
@@
 ECDC.
-2020.
-{``Download Historical Data (to 14 {December} 2020) on the Daily Number of New Reported {COVID}-19 Cases and Deaths Worldwide.''} {European Centre for Disease Prevention and Control}.
-December 14, 2020.
-\url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation}{}}%
-epiforecasts.io/covid. n.d. {``Covid-19: Temporal Variation in Transmission During the {COVID}-19 Outbreak.''} {Covid-19}. Accessed May 30, 2021. \url{https://epiforecasts.io/covid/}.
+(2020, December 14).
+\emph{Download historical data (to 14 {December} 2020) on the daily number of new reported {COVID}-19 cases and deaths worldwide}.
+{European Centre for Disease Prevention and Control}.
+\url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}
+
+\leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation2020}{}}%
+epiforecasts.io/covid. (2020). \emph{Covid-19: Temporal variation in transmission during the {COVID}-19 outbreak}. {Covid-19}. \url{https://epiforecasts.io/covid/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-europeancovid-19forecasthubEuropeanCovid19Forecast2021}{}}%
+European Covid-19 Forecast Hub. (2021). \emph{European {Covid}-19 {Forecast Hub}}. \url{https://covid19forecasthub.eu/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
-{``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid}-19 Outbreak in {England} \textbar{} {medRxiv}.''} n.d.
-Accessed May 30, 2021.
-\url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}.
+\emph{Evaluating the use of the reproduction number as an epidemiological tool, using spatio-temporal trends of the {Covid}-19 outbreak in {England} \textbar{} {medRxiv}}.
+(n.d.).
+Retrieved May 30, 2021, from \url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}
 
 \leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
-Farrow, David C., Logan C.
-Brooks, Sangwon Hyun, Ryan J.
-Tibshirani, Donald S.
-Burke, and Roni Rosenfeld.
-2017.
-{``A Human Judgment Approach to Epidemiological Forecasting.''} \emph{PLOS Computational Biology} 13 (3): e1005248.
-\url{https://doi.org/10.1371/journal.pcbi.1005248}.
+Farrow, D.
+C., Brooks, L.
+C., Hyun, S., Tibshirani, R.
+J., Burke, D.
+S., \& Rosenfeld, R.
+(2017).
+A human judgment approach to epidemiological forecasting.
+\emph{PLOS Computational Biology}, \emph{13}(3), e1005248.
+\url{https://doi.org/10.1371/journal.pcbi.1005248}
 
 \leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
-Fay, Colin, Vincent Guyader, Sébastien Rochette, and Cervan Girard. 2021. \emph{Golem: A Framework for Robust Shiny Applications}. \url{https://github.com/ThinkR-open/golem}.
+Fay, C., Guyader, V., Rochette, S., \& Girard, C. (2021). \emph{Golem: A framework for robust shiny applications}. \url{https://github.com/ThinkR-open/golem}
 
@@
 Forsal.pl.
-2020.
-{``Rozbieżności w statystykach koronawirusa.
+(2020).
+\emph{Rozbieżności w statystykach koronawirusa.
 22 tys.
-przypadków będą doliczone do ogólnej liczby wyników.''} 2020.
-\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}.
+przypadków będą doliczone do ogólnej liczby wyników}.
+\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}
 
 \leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
-Fraser, Christophe. 2007. {``Estimating {Individual} and {Household Reproduction Numbers} in an {Emerging Epidemic}.''} \emph{PLOS ONE} 2 (8): e758. \url{https://doi.org/10.1371/journal.pone.0000758}.
+Fraser, C. (2007). Estimating {Individual} and {Household Reproduction Numbers} in an {Emerging Epidemic}. \emph{PLOS ONE}, \emph{2}(8), e758. \url{https://doi.org/10.1371/journal.pone.0000758}
 
 \leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
-Funk, Sebastian, Sam Abbott, B.
-D.
-Atkins, M.
-Baguelin, J.
-K.
-Baillie, P.
-Birrell, J.
-Blake, et al.
-2020.
-{``Short-Term Forecasts to Inform the Response to the {Covid}-19 Epidemic in the {UK}.''} \emph{medRxiv}, November, 2020.11.11.20220962.
-\url{https://doi.org/10.1101/2020.11.11.20220962}.
+Funk, S., Abbott, S., Atkins, B.
+D., Baguelin, M., Baillie, J.
+K., Birrell, P., Blake, J., Bosse, N.
+I., Burton, J., Carruthers, J., Davies, N.
+G., Angelis, D.
+D., Dyson, L., Edmunds, W.
+J., Eggo, R.
+M., Ferguson, N.
+M., Gaythorpe, K., Gorsich, E., Guyver-Fletcher, G., \ldots{} Investigators, I.
+(2020).
+Short-term forecasts to inform the response to the {Covid}-19 epidemic in the {UK}.
+\emph{medRxiv}, 2020.11.11.20220962.
+\url{https://doi.org/10.1101/2020.11.11.20220962}
 
 \leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
-Funk, Sebastian, Anton Camacho, Adam J.
-Kucharski, Rachel Lowe, Rosalind M.
-Eggo, and W.
-John Edmunds.
-2019.
-{``Assessing the Performance of Real-Time Epidemic Forecasts: A Case Study of {Ebola} in the {Western Area} Region of {Sierra Leone}, 2014-15.''} \emph{PLOS Computational Biology} 15 (2): e1006785.
-\url{https://doi.org/10.1371/journal.pcbi.1006785}.
+Funk, S., Camacho, A., Kucharski, A.
+J., Lowe, R., Eggo, R.
+M., \& Edmunds, W.
+J.
+(2019).
+Assessing the performance of real-time epidemic forecasts: A case study of {Ebola} in the {Western Area} region of {Sierra Leone}, 2014-15.
+\emph{PLOS Computational Biology}, \emph{15}(2), e1006785.
+\url{https://doi.org/10.1371/journal.pcbi.1006785}
 
 \leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
-Ganyani, Tapiwa, Cecile Kremer, Dongxuan Chen, Andrea Torneri, Christel Faes, Jacco Wallinga, and Niel Hens.
-2020.
-{``Estimating the Generation Interval for Coronavirus Disease (COVID-19) Based on Symptom Onset Data, March 2020.''} \emph{Eurosurveillance} 25 (17).
+Ganyani, T., Kremer, C., Chen, D., Torneri, A., Faes, C., Wallinga, J., \& Hens, N.
+(2020).
+Estimating the generation interval for coronavirus disease (COVID-19) based on symptom onset data, march 2020.
+\emph{Eurosurveillance}, \emph{25}(17).
 
 \leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
-Gneiting, Tilmann, and Adrian E Raftery.
-2007.
-{``Strictly Proper Scoring Rules, Prediction, and Estimation.''} \emph{Journal of the American Statistical Association} 102 (477): 359--78.
-\url{https://doi.org/10.1198/016214506000001437}.
+Gneiting, T., \& Raftery, A.
+E.
+(2007).
+Strictly proper scoring rules, prediction, and estimation.
+\emph{Journal of the American Statistical Association}, \emph{102}(477), 359--378.
+\url{https://doi.org/10.1198/016214506000001437}
 
 \leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
-Held, Leonhard, Sebastian Meyer, and Johannes Bracher.
-2017.
-{``Probabilistic Forecasting in Infectious Disease Epidemiology: The 13th {Armitage} Lecture.''} \emph{Statistics in Medicine} 36 (22): 3443--60.
-\url{https://doi.org/10.1002/sim.7363}.
+Held, L., Meyer, S., \& Bracher, J.
+(2017).
+Probabilistic forecasting in infectious disease epidemiology: The 13th {Armitage} lecture.
+\emph{Statistics in Medicine}, \emph{36}(22), 3443--3460.
+\url{https://doi.org/10.1002/sim.7363}
 
 \leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
-Hoogeveen, Suzanne, Alexandra Sarafoglou, and Eric-Jan Wagenmakers.
-2020.
-{``Laypeople {Can Predict Which Social}-{Science Studies Will Be Replicated Successfully}.''} \emph{Advances in Methods and Practices in Psychological Science} 3 (3): 267--85.
-\url{https://doi.org/10.1177/2515245920919667}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-EuroHub}{}}%
-Hub, European COVID-19 Forecast. 2021. {``Forecasts of New Cases and Deaths Due to Covid-19 over the Next Four Weeks in Countries Across Europe and the UK.''} \url{https://covid19forecasthub.eu/}.
+Hoogeveen, S., Sarafoglou, A., \& Wagenmakers, E.-J.
+(2020).
+Laypeople {Can Predict Which Social}-{Science Studies Will Be Replicated Successfully}.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 267--285.
+\url{https://doi.org/10.1177/2515245920919667}
 
 \leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
-Hypermind. 2021. {``Hypermind \textbar{} {Supercollective} Intelligence for Decision Makers.''} {Hypermind}. 2021. \url{https://www.hypermind.com/en/}.
+Hypermind. (2021). \emph{Hypermind \textbar{} {Supercollective} intelligence for decision makers}. {Hypermind}. \url{https://www.hypermind.com/en/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
-Johansson, Michael A., Karyn M.
-Apfeldorf, Scott Dobson, Jason Devita, Anna L.
-Buczak, Benjamin Baugher, Linda J.
-Moniz, et al.
-2019.
-{``An Open Challenge to Advance Probabilistic Forecasting for Dengue Epidemics.''} \emph{Proceedings of the National Academy of Sciences} 116 (48): 24268--74.
-\url{https://doi.org/10.1073/pnas.1909865116}.
+Johansson, M.
+A., Apfeldorf, K.
+M., Dobson, S., Devita, J., Buczak, A.
+L., Baugher, B., Moniz, L.
+J., Bagley, T., Babin, S.
+M., Guven, E., Yamana, T.
+K., Shaman, J., Moschou, T., Lothian, N., Lane, A., Osborne, G., Jiang, G., Brooks, L.
+C., Farrow, D.
+C., \ldots{} Chretien, J.-P.
+(2019).
+An open challenge to advance probabilistic forecasting for dengue epidemics.
+\emph{Proceedings of the National Academy of Sciences}, \emph{116}(48), 24268--24274.
+\url{https://doi.org/10.1073/pnas.1909865116}
 
 \leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
-Lauer, Stephen A, Kyra H Grantz, Qifang Bi, Forrest K Jones, Qulu Zheng, Hannah R Meredith, Andrew S Azman, Nicholas G Reich, and Justin Lessler.
-2020.
-{``The Incubation Period of Coronavirus Disease 2019 (COVID-19) from Publicly Reported Confirmed Cases: Estimation and Application.''} \emph{Annals of Internal Medicine} 172 (9): 577--82.
+Lauer, S.
+A., Grantz, K.
+H., Bi, Q., Jones, F.
+K., Zheng, Q., Meredith, H.
+R., Azman, A.
+S., Reich, N.
+G., \& Lessler, J.
+(2020).
+The incubation period of coronavirus disease 2019 (COVID-19) from publicly reported confirmed cases: Estimation and application.
+\emph{Annals of Internal Medicine}, \emph{172}(9), 577--582.
 
 \leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
-McAndrew, Thomas Charles, and Nicholas G.
-Reich.
-2020.
-{``An Expert Judgment Model to Predict Early Stages of the {COVID}-19 Outbreak in the {United States}.''} \emph{medRxiv}, September, 2020.09.21.20196725.
-\url{https://doi.org/10.1101/2020.09.21.20196725}.
+McAndrew, T.
+C., \& Reich, N.
+G.
+(2020).
+An expert judgment model to predict early stages of the {COVID}-19 outbreak in the {United States}.
+\emph{medRxiv}, 2020.09.21.20196725.
+\url{https://doi.org/10.1101/2020.09.21.20196725}
 
 \leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
-McGowan, Craig J., Matthew Biggerstaff, Michael Johansson, Karyn M.
-Apfeldorf, Michal Ben-Nun, Logan Brooks, Matteo Convertino, et al.
-2019.
-{``Collaborative Efforts to Forecast Seasonal Influenza in the {United States}, 2015--2016.''} \emph{Scientific Reports} 9 (1, 1): 683.
-\url{https://doi.org/10.1038/s41598-018-36361-9}.
+McGowan, C.
+J., Biggerstaff, M., Johansson, M., Apfeldorf, K.
+M., Ben-Nun, M., Brooks, L., Convertino, M., Erraguntla, M., Farrow, D.
+C., Freeze, J., Ghosh, S., Hyun, S., Kandula, S., Lega, J., Liu, Y., Michaud, N., Morita, H., Niemi, J., Ramakrishnan, N., \ldots{} Reed, C.
+(2019).
+Collaborative efforts to forecast seasonal influenza in the {United States}, 2015--2016.
+\emph{Scientific Reports}, \emph{9}(1, 1), 683.
+\url{https://doi.org/10.1038/s41598-018-36361-9}
 
 \leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
-Metaculus. 2020. {``A {Preliminary Look} at {Metaculus} and {Expert Forecasts}.''} June 22, 2020. \url{https://www.metaculus.com/news/2020/06/02/LRT/}.
+Metaculus. (2020, June 22). \emph{A {Preliminary Look} at {Metaculus} and {Expert Forecasts}}. \url{https://www.metaculus.com/news/2020/06/02/LRT/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
+Our World in Data. (2020). \emph{{COVID}-19 {Data Explorer}}. {Our World in Data}. \url{https://ourworldindata.org/coronavirus-data-explorer}
 
 \leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
-PredictIt. 2021. {``{PredictIt}.''} 2021. \url{https://www.predictit.org/}.
+PredictIt. (2021). \emph{{PredictIt}}. \url{https://www.predictit.org/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
-Recchia, Gabriel, Alexandra L.
-J.
-Freeman, and David Spiegelhalter.
-2021.
-{``How Well Did Experts and Laypeople Forecast the Size of the {COVID}-19 Pandemic?''} \emph{PLOS ONE} 16 (5): e0250935.
-\url{https://doi.org/10.1371/journal.pone.0250935}.
+Recchia, G., Freeman, A.
+L.
+J., \& Spiegelhalter, D.
+(2021).
+How well did experts and laypeople forecast the size of the {COVID}-19 pandemic?
+\emph{PLOS ONE}, \emph{16}(5), e0250935.
+\url{https://doi.org/10.1371/journal.pone.0250935}
 
 \leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
-Reich, Nicholas G., Logan C.
-Brooks, Spencer J.
-Fox, Sasikiran Kandula, Craig J.
-McGowan, Evan Moore, Dave Osthus, et al.
-2019.
-{``A Collaborative Multiyear, Multimodel Assessment of Seasonal Influenza Forecasting in the {United States}.''} \emph{Proceedings of the National Academy of Sciences} 116 (8): 3146--54.
-\url{https://doi.org/10.1073/pnas.1812594116}.
+Reich, N.
+G., Brooks, L.
+C., Fox, S.
+J., Kandula, S., McGowan, C.
+J., Moore, E., Osthus, D., Ray, E.
+L., Tushar, A., Yamana, T.
+K., Biggerstaff, M., Johansson, M.
+A., Rosenfeld, R., \& Shaman, J.
+(2019).
+A collaborative multiyear, multimodel assessment of seasonal influenza forecasting in the {United States}.
+\emph{Proceedings of the National Academy of Sciences}, \emph{116}(8), 3146--3154.
+\url{https://doi.org/10.1073/pnas.1812594116}
+
+\leavevmode\vadjust pre{\hypertarget{ref-reichAccuracyRealtimeMultimodel2019}{}}%
+Reich, N.
+G., McGowan, C.
+J., Yamana, T.
+K., Tushar, A., Ray, E.
+L., Osthus, D., Kandula, S., Brooks, L.
+C., Crawford-Crudell, W., Gibson, G.
+C., Moore, E., Silva, R., Biggerstaff, M., Johansson, M.
+A., Rosenfeld, R., \& Shaman, J.
+(2019).
+Accuracy of real-time multi-model ensemble forecasts for seasonal influenza in the {U}.{S}.
+\emph{PLOS Computational Biology}, \emph{15}(11), e1007486.
+\url{https://doi.org/10.1371/journal.pcbi.1007486}
 
 \leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
-ReplicationMarkets. 2020. {``Replication {Markets} -- {Reliable} Research Replicates\ldots you Can Bet on It.''} 2020. \url{https://www.replicationmarkets.com/}.
+ReplicationMarkets. (2020). \emph{Replication {Markets} -- {Reliable} research replicates\ldots you can bet on it.} \url{https://www.replicationmarkets.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
-Riutort-Mayol, Gabriel, Paul-Christian Bürkner, Michael R.
-Andersen, Arno Solin, and Aki Vehtari.
-2020.
-{``Practical Hilbert Space Approximate Bayesian Gaussian Processes for Probabilistic Programming.''} \url{https://arxiv.org/abs/2004.11408}.
+Riutort-Mayol, G., Bürkner, P.-C., Andersen, M.
+R., Solin, A., \& Vehtari, A.
+(2020).
+\emph{Practical hilbert space approximate bayesian gaussian processes for probabilistic programming}.
+\url{https://arxiv.org/abs/2004.11408}
 
@@
 RKI.
-2021.
-{``{RKI} - {Coronavirus SARS}-{CoV}-2 - {Aktueller Lage}-/{Situationsbericht} Des {RKI} Zu {COVID}-19.''} 2021.
-\url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}.
+(2021).
+\emph{{RKI} - {Coronavirus SARS}-{CoV}-2 - {Aktueller Lage}-/{Situationsbericht} des {RKI} zu {COVID}-19}.
+\url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}
 
 \leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
-Scott, James A., Axel Gandy, Swapnil Mishra, Juliette Unwin, Seth Flaxman, and Samir Bhatt.
-2020.
-{``Epidemia: Modeling of Epidemics Using Hierarchical Bayesian Models.''} \url{https://imperialcollegelondon.github.io/epidemia/}.
+Scott, J.
+A., Gandy, A., Mishra, S., Unwin, J., Flaxman, S., \& Bhatt, S.
+(2020).
+\emph{Epidemia: Modeling of epidemics using hierarchical bayesian models}.
+\url{https://imperialcollegelondon.github.io/epidemia/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
-Servan-Schreiber, Emile, Justin Wolfers, David M.
-Pennock, and Brian Galebach.
-2004.
-{``Prediction {Markets}: Does {Money Matter}?''} \emph{Electronic Markets} 14 (3): 243--51.
-\url{https://doi.org/10.1080/1019678042000245254}.
+Servan-Schreiber, E., Wolfers, J., Pennock, D.
+M., \& Galebach, B.
+(2004).
+Prediction {Markets}: Does {Money Matter}?
+\emph{Electronic Markets}, \emph{14}(3), 243--251.
+\url{https://doi.org/10.1080/1019678042000245254}
 
 \leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
-Shaman, Jeffrey, and Alicia Karspeck.
-2012.
-{``Forecasting Seasonal Outbreaks of Influenza.''} \emph{Proceedings of the National Academy of Sciences} 109 (50): 20425--30.
-\url{https://doi.org/10.1073/pnas.1208772109}.
+Shaman, J., \& Karspeck, A.
+(2012).
+Forecasting seasonal outbreaks of influenza.
+\emph{Proceedings of the National Academy of Sciences}, \emph{109}(50), 20425--20430.
+\url{https://doi.org/10.1073/pnas.1208772109}
 
 \leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
-Sherratt, Katharine, Sam Abbott, Sophie R.
-Meakin, Joel Hellewell, James D.
-Munday, Nikos Bosse, CMMID Covid-19 working Group, Mark Jit, and Sebastian Funk.
-2021.
-{``Exploring Surveillance Data Biases When Estimating the Reproduction Number: With Insights into Subpopulation Transmission of {Covid}-19 in {England},''} March, 2020.10.18.20214585.
-\url{https://doi.org/10.1101/2020.10.18.20214585}.
+Sherratt, K., Abbott, S., Meakin, S.
+R., Hellewell, J., Munday, J.
+D., Bosse, N., Group, C.
+C.
+working, Jit, M., \& Funk, S.
+(2021).
+\emph{Exploring surveillance data biases when estimating the reproduction number: With insights into subpopulation transmission of {Covid}-19 in {England}}.
+2020.10.18.20214585.
+\url{https://doi.org/10.1101/2020.10.18.20214585}
 
 \leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
-Stan Development Team. 2020. {``RStan: The r Interface to Stan.''} \url{http://mc-stan.org/}.
+Stan Development Team. (2020). \emph{RStan: The r interface to stan}. \url{http://mc-stan.org/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
-Tetlock, Philip E., Barbara A.
-Mellers, Nick Rohrbaugh, and Eva Chen.
-2014.
-{``Forecasting {Tournaments}: Tools for {Increasing Transparency} and {Improving} the {Quality} of {Debate}.''} \emph{Current Directions in Psychological Science} 23 (4): 290--95.
-\url{https://doi.org/10.1177/0963721414534257}.
+Tetlock, P.
+E., Mellers, B.
+A., Rohrbaugh, N., \& Chen, E.
+(2014).
+Forecasting {Tournaments}: Tools for {Increasing Transparency} and {Improving} the {Quality} of {Debate}.
+\emph{Current Directions in Psychological Science}, \emph{23}(4), 290--295.
+\url{https://doi.org/10.1177/0963721414534257}
 
 \leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
-Viboud, Cécile, Kaiyuan Sun, Robert Gaffey, Marco Ajelli, Laura Fumanelli, Stefano Merler, Qian Zhang, Gerardo Chowell, Lone Simonsen, and Alessandro Vespignani.
-2018.
-{``The {RAPIDD} Ebola Forecasting Challenge: Synthesis and Lessons Learnt.''} \emph{Epidemics}, The {RAPIDD Ebola Forecasting Challenge}, 22 (March): 13--21.
-\url{https://doi.org/10.1016/j.epidem.2017.08.002}.
+Viboud, C., Sun, K., Gaffey, R., Ajelli, M., Fumanelli, L., Merler, S., Zhang, Q., Chowell, G., Simonsen, L., \& Vespignani, A.
+(2018).
+The {RAPIDD} ebola forecasting challenge: Synthesis and lessons learnt.
+\emph{Epidemics}, \emph{22}, 13--21.
+\url{https://doi.org/10.1016/j.epidem.2017.08.002}
 
 \leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
-Xu, Bo, Bernardo Gutierrez, Sarah Hill, Samuel Scarpino, Alyssa Loskill, Jessie Wu, Kara Sewalk, et al.
-2020.
-{``Epidemiological Data from the nCoV-2019 Outbreak: Early Descriptions from Publicly Available Data.''} \url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}.
+Xu, B., Gutierrez, B., Hill, S., Scarpino, S., Loskill, A., Wu, J., Sewalk, K., Mekaru, S., Zarebski, A., Pybus, O., Pigott, D., \& Kraemer, M.
+(2020).
+\emph{Epidemiological data from the nCoV-2019 outbreak: Early descriptions from publicly available data}.
+\url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}
 
 \leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
-Yamana, Teresa K., Sasikiran Kandula, and Jeffrey Shaman.
-2016.
-{``Superensemble Forecasts of Dengue Outbreaks.''} \emph{Journal of The Royal Society Interface} 13 (123): 20160410.
-\url{https://doi.org/10.1098/rsif.2016.0410}.
+Yamana, T.
+K., Kandula, S., \& Shaman, J.
+(2016).
+Superensemble forecasts of dengue outbreaks.
+\emph{Journal of The Royal Society Interface}, \emph{13}(123), 20160410.
+\url{https://doi.org/10.1098/rsif.2016.0410}
 

### 2022-01-11 manuscript/manuscript.Rmd
update manuscript formatting, add author summary

@@
 title: "Comparing human and model-based forecasts of COVID-19 in Germany and Poland"
+header-includes:
+    - \usepackage{lineno}
+    - \linenumbers
 output: 
@@
     toc: false
+linestretch: 2
 bibliography:
@@
   - GermanPolishpaper.bib
-csl: apa.csl
+csl: vancouver.csl
 ---
@@
 WIS 1.26), suggesting that epidemiological modelling and human judgement can complement each other in important ways.
+
+# Author summary
+
+Mathematical models of COVID-19 have played a key role in informing governments across the world.
+While mathematical models are informed by our knowledge of infectious disease dynamics, they are ultimately developed and iteratively adjusted by the researchers and shaped by their subjective opinions.
+To investigate what modelling is able to add beyond the subjective opinion of the researcher alone, we compared human forecasts with model-based predictions of COVID-19 cases and deaths submitted to the so-called German/Polish Forecast Hub (which collates a variety of models from a range of teams).
+We found that our human forecasts consistently outperformed an aggregate of all available model-based forecasts when predicting cases, but not when predicting deaths.
+Our findings suggest that human insight may be most valuable when forecasting highly uncertain quantities, which depend on many factors that are hard to model using equations, while mathematical models may be most useful in settings like predicting deaths, where leading indicators with a clear connection to the target variable are available.
+This potentially has very relevant policy implications, as agencies informing policy-makers could benefit from routinely eliciting human forecasts in addition to model-based predictions to inform policies.
 

### 2022-01-11 manuscript/manuscript.tex
update manuscript formatting, add author summary

@@
 \usepackage{lmodern}
+\usepackage{setspace}
 \usepackage{iftex}
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\usepackage{lineno}
+\linenumbers
 \usepackage{float}
@@
 
+\setstretch{2}
 \emph{Nikos I.
@@
 
+\hypertarget{author-summary}{%
+\section{Author summary}\label{author-summary}}
+
+Mathematical models of COVID-19 have played a key role in informing governments across the world.
+While mathematical models are informed by our knowledge of infectious disease dynamics, they are ultimately developed and iteratively adjusted by the researchers and shaped by their subjective opinions.
+To investigate what modelling is able to add beyond the subjective opinion of the researcher alone, we compared human forecasts with model-based predictions of COVID-19 cases and deaths submitted to the so-called German/Polish Forecast Hub (which collates a variety of models from a range of teams).\\
+We found that our human forecasts consistently outperformed an aggregate of all available model-based forecasts when predicting cases, but not when predicting deaths.
+Our findings suggest that human insight may be most valuable when forecasting highly uncertain quantities, which depend on many factors that are hard to model using equations, while mathematical models may be most useful in settings like predicting deaths, where leading indicators with a clear connection to the target variable are available.
+This potentially has very relevant policy implications, as agencies informing policy-makers could benefit from routinely eliciting human forecasts in addition to model-based predictions to inform policies.
+
 \hypertarget{introduction}{%
@@
 
-Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza (Biggerstaff et al., 2016; e.g.
-McGowan et al., 2019; Reich, Brooks, et al., 2019; Shaman \& Karspeck, 2012), dengue fever (Colón-González et al., 2021; e.g.
-Johansson et al., 2019; Yamana et al., 2016), ebola (Funk et al., 2019; e.g.
-Viboud et al., 2018), chikungunya (e.g.
-Del Valle et al., 2018; Farrow et al., 2017) and now COVID-19 (Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Castro, et al., 2021; Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Fiedler, et al., 2021; Cramer et al., 2021; Cramer et al., 2020; European Covid-19 Forecast Hub, 2021; e.g.
-Funk et al., 2020).
+Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza (e.g.
+1,2--4), dengue fever (e.g.
+5,6,7), ebola (e.g.
+8,9), chikungunya (e.g.
+10,11) and now COVID-19 (e.g.
+12,13--17).
 Applications of epidemiological models differ in the way they make statements about the future.
@@
 
-Since March 2020, forecasts of COVID-19 from multiple teams have been collected, aggregated and compared by Forecast Hubs such as the US Forecast Hub (Cramer et al., 2021; Cramer et al., 2020), the German and Polish Forecast Hub (Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Castro, et al., 2021; Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Fiedler, et al., 2021) and the European Forecast Hub (European Covid-19 Forecast Hub, 2021).
+Since March 2020, forecasts of COVID-19 from multiple teams have been collected, aggregated and compared by Forecast Hubs such as the US Forecast Hub (13,14), the German and Polish Forecast Hub (15,16) and the European Forecast Hub (17).
 Often, different individual forecasts are combined into a single forecast, e.g.~by taking the mean or median of all forecasts.
 These ensemble forecasts usually tend to perform better and more consistently than individual forecasts (see e.g.
-Yamana et al.
-(2016); Reich, McGowan, et al.
-(2019)).
+(6); (18)).
 
@@
 
-Previous work has examined such direct human forecasts in various contexts, such as geopolitics (Atanasov et al., 2016; Tetlock et al., 2014), meta-science (Hoogeveen et al., 2020; ReplicationMarkets, 2020), sports (Servan-Schreiber et al., 2004) and epidemiology (Farrow et al., 2017; McAndrew \& Reich, 2020; Recchia et al., 2021).
-Several prediction platforms (CSET Foretell, 2021; Hypermind, 2021; Metaculus, 2020) and prediction markets (PredictIt, 2021) have been created to collate expert and non-expert predictions.
-However, with the notable exception of Farrow et al.
-(2017), these forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) prediction formats.
+Previous work has examined such direct human forecasts in various contexts, such as geopolitics (19,20), meta-science (21,22), sports (23) and epidemiology (11,24,25).
+Several prediction platforms (26--28) and prediction markets (29) have been created to collate expert and non-expert predictions.
+However, with the notable exception of (11), these forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) prediction formats.
 Direct human forecasts may be able to take into account insights and relationships between variables which are hard to specify using epidemiological models.
 However, it is not entirely clear in which situations human forecasts perform well or badly.
-For example, Farrow et al.
-(2017) found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available.
+For example, (11) found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available.
 However, humans tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown in these regions at the time.
@@
 As a case study, we use different forecasts, involving varying degrees of human intervention, which we submitted in real time to the German and Polish Forecast Hub.
-In contrast to Farrow et al.
-(2017) we elicited not only point predictions, but full predictive distributions (``probabilistic forecasts'', see e.g.
-Held et al.
-(2017)) from participants.
+In contrast to (11) we elicited not only point predictions, but full predictive distributions (``probabilistic forecasts'', see e.g.
+(30)) from participants.
 This allows us to compare not only predictive accuracy, but also how well human forecasters and model-based forecasts were able to quantify forecast uncertainty.
@@
 
-We created and submitted the following forecasts to the German and Polish Forecast Hub: 1) a direct human forecast (henceforth called ``crowd forecast''), elicited from participants through a web application (Bosse, Abbott, EpiForecasts, et al., 2020b) and 2) two semi-mechanistic model-based forecasts (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology.
+We created and submitted the following forecasts to the German and Polish Forecast Hub: 1) a direct human forecast (henceforth called ``crowd forecast''), elicited from participants through a web application (31) and 2) two semi-mechanistic model-based forecasts (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology.
 While the two semi-mechanistic forecasts were necessarily shaped by our implicit assumptions and decisions, they were designed such as to minimise the amount of human intervention involved.
 For example, we refrained from adjusting model outputs or refining the models based on past performance.
-Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Castro, et al., 2021; Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Fiedler, et al., 2021).
-All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (Bosse, Abbott, EpiForecasts, et al., 2020a).
+Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (15,16).
+All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (32).
 This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub.
@@
 
-The German and Polish Forecast Hub (now mostly merged into the European Covid-19 Forecast Hub (2021)) elicits predictions for various COVID-19 related forecast targets from different research groups every week.
+The German and Polish Forecast Hub (now mostly merged into the (17)) elicits predictions for various COVID-19 related forecast targets from different research groups every week.
 Forecasts had to be made every Monday (with submissions allowed until Tuesday 3pm) and were permitted to use any data that was available by Monday 11.59pm.
@@
 Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish Forecast hub.
-Until December 14th, 2020, these data were sourced from the European Centre for Disease Control (ECDC, 2020).
-After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (RKI, 2021).
-These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, Forsal.pl (2020)), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, Ärzteblatt (2020)).
+Until December 14th, 2020, these data were sourced from the European Centre for Disease Control (33).
+After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (34).
+These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, (35)), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, (36)).
 
@@
 Weekly forecasts had to be submitted before Tuesday 12pm every week, but participants were asked to only use any information or data that was already available by Monday night.
-The application was built using the \texttt{shiny} and \texttt{golem} R packages (Chang et al., 2021; Fay et al., 2021) and is available in the \texttt{crowdforecastr} R package (Bosse, Abbott, EpiForecasts, et al., 2020b).
+The application was built using the \texttt{shiny} and \texttt{golem} R packages (37,38) and is available in the \texttt{crowdforecastr} R package (31).
 To make a forecast in the application participants could select a predictive distribution (with the default being log-normal) to represent the probability that the forecasted quantity took certain values.
@@
 The default shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.~as \(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
-Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from Our World in Data (2020).
+Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from (39).
 These data included, for example, notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
@@
 
-We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, Hickson, et al., 2020).
-The first of these models, here called ``renewal model'', used the renewal equation (Fraser, 2007) to predict reported cases and deaths (see details in the SI).
+We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R package (version 1.3.3) as our model-based forecasts (40).
+The first of these models, here called ``renewal model'', used the renewal equation (41) to predict reported cases and deaths (see details in the SI).
 It estimated the effective reproduction number \(R_t\) (the average number of people each person infected at time t is expected to infect in turn) and modelled future infections as a weighted sum of past infection multiplied by \(R_t\).
@@
 On the 9th of November we altered the date when \(R_t\) was assumed to be constant from two weeks prior to the date of the forecast to the forecast date, which we found to yield a more stable \(R_t\) estimate.
-Reported case and death notifications were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, Thompson, et al., 2020; Abbott, Hellewell, Hickson, et al., 2020; epiforecasts.io/covid, 2020; Sherratt et al., 2021) to model the time between infection and report date.
+Reported case and death notifications were obtained by convolving predicted infections over data-based delay distributions (40,42--44) to model the time between infection and report date.
 The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately.
@@
 The convolution model predicted deaths as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
-Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model with a multiplicative day-of-the-week effect (Abbott, Hellewell, Hickson, et al., 2020).
-
-Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., 2020) with data available up to the 1st of August.
-All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team, 2020) with each location and forecast target being fitted separately.
+Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model with a multiplicative day-of-the-week effect (40).
+
+Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (45) with data available up to the 1st of August.
+All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (46) with each location and forecast target being fitted separately.
 
@@
 
-For the main analysis we focused mostly on two week ahead forecasts, as COVID-19 forecasts, especially for cases, were in the past found to have poor predictive performance beyond this horizon (Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Castro, et al., 2021).
+For the main analysis we focused mostly on two week ahead forecasts, as COVID-19 forecasts, especially for cases, were in the past found to have poor predictive performance beyond this horizon (15).
 Forecasts for cases were scored using the full period from October 2020 until March 2021.
@@
 
-Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Bracher, Ray, et al., 2021), the absolute error, relative bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule (Gneiting \& Raftery, 2007), meaning that in expectation the score is optimised by reporting a predictive distribution that is identical to the true data-generating distribution.
+Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (47), the absolute error, relative bias, and empirical coverage of the 50\% and 90\% prediction intervals.
+The WIS is a proper scoring rule (48), meaning that in expectation the score is optimised by reporting a predictive distribution that is identical to the true data-generating distribution.
 Forecasters are therefore incentivised to report their true belief about the future.
@@
 While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts.
-The bias metric (Funk et al., 2019) we use captures how much probability mass of the forecast was above or below the true value (mapped to values between -1 and 1) and therefore represents a general tendency to over- or under-predict in relative terms.
+The bias metric (9) we use captures how much probability mass of the forecast was above or below the true value (mapped to values between -1 and 1) and therefore represents a general tendency to over- or under-predict in relative terms.
 A value of -1 implies that all quantiles of the predictive distribution are below the observed value and a value of 1 that all quantiles are above the observed value.
@@
 Scoring metrics are explained in more detail in Table \ref{tab:scoring-metrics} in the SI.
-All scores were calculated using the \texttt{scoringutils} R package (Bosse, Abbott, EpiForecasts, et al., 2020c).
+All scores were calculated using the \texttt{scoringutils} R package (49).
 
@@
 The Hub ensemble and the crowd forecast, which had both been under-predicting throughout October, also failed to predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 (Deutsche Welle, 2020) and the change in the testing regime (with stricter test criteria) on November 11th 2020 (Ärzteblatt, 2020), were fastest to adapt to the new trend, and the Hub ensemble slowest.
+Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 (50) and the change in the testing regime (with stricter test criteria) on November 11th 2020 (36), were fastest to adapt to the new trend, and the Hub ensemble slowest.
 In December, cases rose again in Germany, with all models under-predicting this growth to varying extents.
@@
 Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (Cramer et al., 2021; Cramer et al., 2020; e.g.
-Funk et al., 2020), or exclusively on human forecasts (Atanasov et al., 2016; McAndrew \& Reich, 2020; Recchia et al., 2021; Tetlock et al., 2014).
+However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (e.g.
+12,13,14), or exclusively on human forecasts (19,20,24,25).
 In contrast, we directly compared human and model-based forecasts.
-This is similar to the approach taken by Farrow et al.
-(2017), but extends it in several ways.
+This is similar to the approach taken by (11), but extends it in several ways.
 While Farrow et al.~only asked for point predictions and constructed a predictive distribution from these, we asked participants to provide a full predictive distribution, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse how humans quantified their uncertainty.
 In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-based insight.
-In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (Bracher, Wolffram, Deuschel, Görgen, Ketterer, Ullrich, Abbott, Barbarossa, Bertsimas, Bhatia, Bodych, Bosse, Burgard, Castro, et al., 2021; Cramer et al., 2021; Cramer et al., 2020; European Covid-19 Forecast Hub, 2021; Funk et al., 2020).
+In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (12--15,17).
 
@@
 
-The prior for the generation time was sourced from (Ganyani et al., 2020) but refit using a log-normal incubation period with a mean of 5.2 days (SD 1.1) and SD of 1.52 days (SD 1.1) with this incubation period also being used as a prior (Lauer et al., 2020) for \(\xi_{O}\).
+The prior for the generation time was sourced from (51) but refit using a log-normal incubation period with a mean of 5.2 days (SD 1.1) and SD of 1.52 days (SD 1.1) with this incubation period also being used as a prior (52) for \(\xi_{O}\).
 This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
-We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1\% or 1769 samples of the available data (Abbott, Sherratt, et al., 2020; Xu et al., 2020) and combining the posteriors for the mean and standard deviation of the log-normal distribution (Abbott, Hellewell, Hickson, et al., 2020; epiforecasts.io/covid, 2020; \emph{Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid}-19 Outbreak in {England} \textbar{} {medRxiv}}, n.d.; Stan Development Team, 2020).
-
-\(GP_t\) is an approximate Hilbert space Gaussian process as defined in (Riutort-Mayol et al., 2020) using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20\% of the number of days used in fitting).
+We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1\% or 1769 samples of the available data (45,53) and combining the posteriors for the mean and standard deviation of the log-normal distribution (40,42,46,54).
+
+\(GP_t\) is an approximate Hilbert space Gaussian process as defined in (55) using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20\% of the number of days used in fitting).
 The length scale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
@@
 where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\) and \(I'_t\) are the unadjusted infections defined above.
-This adjustment is based on that implemented in the \texttt{epidemia} R package (Bhatt et al., n.d.; Scott et al., 2020).
+This adjustment is based on that implemented in the \texttt{epidemia} R package (56,57).
 
@@
 
-Both models were implemented using the \texttt{EpiNow2} R package (version 1.3.3) (Abbott, Hellewell, Hickson, et al., 2020).
-Each forecast target was fitted independently for each model using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team, 2020).
+Both models were implemented using the \texttt{EpiNow2} R package (version 1.3.3) (40).
+Each forecast target was fitted independently for each model using Markov-chain Monte Carlo (MCMC) in stan (46).
 A minimum of 4 chains were used with a warmup of 250 samples for the renewal equation-based model and 1000 samples for the convolution model.
@@
 Different settings were chosen for each model to optimise compute time contingent on convergence.
-Convergence was assessed using the R hat diagnostic (Stan Development Team, 2020).
+Convergence was assessed using the R hat diagnostic (46).
 For the convolution model forecast the case forecast from the renewal equation model was used in place of observed cases beyond the forecast horizon using 1000 posterior samples.
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
+\CSLLeftMargin{1. }
+\CSLRightInline{McGowan CJ, Biggerstaff M, Johansson M, Apfeldorf KM, Ben-Nun M, Brooks L, et al.
+Collaborative efforts to forecast seasonal influenza in the {United States}, 2015--2016.
+Scientific Reports {[}Internet{]}.
+2019 Jan 24 {[}cited 2021 May 30{]};9(1, 1):683.
+Available from: \url{https://www.nature.com/articles/s41598-018-36361-9}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
+\CSLLeftMargin{2. }
+\CSLRightInline{Reich NG, Brooks LC, Fox SJ, Kandula S, McGowan CJ, Moore E, et al.
+A collaborative multiyear, multimodel assessment of seasonal influenza forecasting in the {United States}.
+PNAS {[}Internet{]}.
+2019 Feb 19 {[}cited 2021 Oct 13{]};116(8):3146--54.
+Available from: \url{https://www.pnas.org/content/116/8/3146}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
+\CSLLeftMargin{3. }
+\CSLRightInline{Shaman J, Karspeck A.
+Forecasting seasonal outbreaks of influenza.
+PNAS {[}Internet{]}.
+2012 Dec 11 {[}cited 2021 Oct 13{]};109(50):20425--30.
+Available from: \url{https://www.pnas.org/content/109/50/20425}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
+\CSLLeftMargin{4. }
+\CSLRightInline{Biggerstaff M, Alper D, Dredze M, Fox S, Fung IC-H, Hickmann KS, et al.
+Results from the centers for disease control and prevention's predict the 2013--2014 {Influenza Season Challenge}.
+BMC Infectious Diseases {[}Internet{]}.
+2016 Jul 22 {[}cited 2021 Oct 13{]};16(1):357.
+Available from: \url{https://doi.org/10.1186/s12879-016-1669-x}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
+\CSLLeftMargin{5. }
+\CSLRightInline{Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak AL, Baugher B, et al.
+An open challenge to advance probabilistic forecasting for dengue epidemics.
+PNAS {[}Internet{]}.
+2019 Nov 26 {[}cited 2021 May 30{]};116(48):24268--74.
+Available from: \url{https://www.pnas.org/content/116/48/24268}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
+\CSLLeftMargin{6. }
+\CSLRightInline{Yamana TK, Kandula S, Shaman J.
+Superensemble forecasts of dengue outbreaks.
+Journal of The Royal Society Interface {[}Internet{]}.
+2016 Oct 31 {[}cited 2021 May 30{]};13(123):20160410.
+Available from: \url{https://royalsocietypublishing.org/doi/full/10.1098/rsif.2016.0410}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
+\CSLLeftMargin{7. }
+\CSLRightInline{Colón-González FJ, Bastos LS, Hofmann B, Hopkin A, Harpham Q, Crocker T, et al.
+Probabilistic seasonal dengue forecasting in {Vietnam}: {A} modelling study using superensembles.
+PLOS Medicine {[}Internet{]}.
+2021 Mar 4 {[}cited 2021 Mar 6{]};18(3):e1003542.
+Available from: \url{https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.1003542}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
+\CSLLeftMargin{8. }
+\CSLRightInline{Viboud C, Sun K, Gaffey R, Ajelli M, Fumanelli L, Merler S, et al.
+The {RAPIDD} ebola forecasting challenge: {Synthesis} and lessons learnt.
+Epidemics {[}Internet{]}.
+2018 Mar 1 {[}cited 2021 May 30{]};22:13--21.
+Available from: \url{https://www.sciencedirect.com/science/article/pii/S1755436517301275}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
+\CSLLeftMargin{9. }
+\CSLRightInline{Funk S, Camacho A, Kucharski AJ, Lowe R, Eggo RM, Edmunds WJ.
+Assessing the performance of real-time epidemic forecasts: {A} case study of {Ebola} in the {Western Area} region of {Sierra Leone}, 2014-15.
+PLOS Computational Biology {[}Internet{]}.
+2019 Feb 11 {[}cited 2019 Sep 16{]};15(2):e1006785.
+Available from: \url{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1006785}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
+\CSLLeftMargin{10. }
+\CSLRightInline{Del Valle SY, McMahon BH, Asher J, Hatchett R, Lega JC, Brown HE, et al.
+Summary results of the 2014-2015 {DARPA Chikungunya} challenge.
+BMC Infectious Diseases {[}Internet{]}.
+2018 May 30 {[}cited 2021 Oct 13{]};18(1):245.
+Available from: \url{https://doi.org/10.1186/s12879-018-3124-7}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
+\CSLLeftMargin{11. }
+\CSLRightInline{Farrow DC, Brooks LC, Hyun S, Tibshirani RJ, Burke DS, Rosenfeld R.
+A human judgment approach to epidemiological forecasting.
+PLOS Computational Biology {[}Internet{]}.
+2017 Mar 10 {[}cited 2021 Jul 29{]};13(3):e1005248.
+Available from: \url{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005248}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
+\CSLLeftMargin{12. }
+\CSLRightInline{Funk S, Abbott S, Atkins BD, Baguelin M, Baillie JK, Birrell P, et al.
+Short-term forecasts to inform the response to the {Covid-19} epidemic in the {UK}.
+medRxiv {[}Internet{]}.
+2020 Nov 13 {[}cited 2020 Nov 28{]};2020.11.11.20220962.
+Available from: \url{https://www.medrxiv.org/content/10.1101/2020.11.11.20220962v1}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
+\CSLLeftMargin{13. }
+\CSLRightInline{Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K, et al.
+{COVID-19 Forecast Hub}: 4 {December} 2020 snapshot {[}Internet{]}.
+{Zenodo}; 2020 {[}cited 2021 May 29{]}.
+Available from: \url{https://zenodo.org/record/3963371}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
+\CSLLeftMargin{14. }
+\CSLRightInline{Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A, Rivadeneira AJC, et al.
+Evaluation of individual and ensemble probabilistic forecasts of {COVID-19} mortality in the {US}.
+medRxiv {[}Internet{]}.
+2021 Feb 5 {[}cited 2021 Apr 6{]};2021.02.03.21250974.
+Available from: \url{https://www.medrxiv.org/content/10.1101/2021.02.03.21250974v1}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
+\CSLLeftMargin{15. }
+\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer JL, Ullrich A, et al.
+Short-term forecasting of {COVID-19} in {Germany} and {Poland} during the second wave -- a preregistered study.
+medRxiv {[}Internet{]}.
+2021 Jan 11 {[}cited 2021 Apr 1{]};2020.12.24.20248826.
+Available from: \url{https://www.medrxiv.org/content/10.1101/2020.12.24.20248826v2}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
+\CSLLeftMargin{16. }
+\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer JL, Ullrich A, et al.
+National and subnational short-term forecasting of {COVID-19} in {Germany} and {Poland}, early 2021.
+2021 Nov 8 {[}cited 2021 Nov 18{]};2021.11.05.21265810.
+Available from: \url{https://www.medrxiv.org/content/10.1101/2021.11.05.21265810v1}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-europeancovid-19forecasthubEuropeanCovid19Forecast2021}{}}%
+\CSLLeftMargin{17. }
+\CSLRightInline{European Covid-19 Forecast Hub. European {Covid-19 Forecast Hub} {[}Internet{]}. 2021 {[}cited 2021 May 30{]}. Available from: \url{https://covid19forecasthub.eu/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-reichAccuracyRealtimeMultimodel2019}{}}%
+\CSLLeftMargin{18. }
+\CSLRightInline{Reich NG, McGowan CJ, Yamana TK, Tushar A, Ray EL, Osthus D, et al.
+Accuracy of real-time multi-model ensemble forecasts for seasonal influenza in the {U}.{S}.
+PLOS Computational Biology {[}Internet{]}.
+2019 Nov 22 {[}cited 2020 Aug 7{]};15(11):e1007486.
+Available from: \url{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1007486}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
+\CSLLeftMargin{19. }
+\CSLRightInline{Tetlock PE, Mellers BA, Rohrbaugh N, Chen E.
+Forecasting {Tournaments}: {Tools} for {Increasing Transparency} and {Improving} the {Quality} of {Debate}.
+Curr Dir Psychol Sci {[}Internet{]}.
+2014 Aug 1 {[}cited 2021 May 30{]};23(4):290--5.
+Available from: \url{https://doi.org/10.1177/0963721414534257}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
+\CSLLeftMargin{20. }
+\CSLRightInline{Atanasov P, Rescober P, Stone E, Swift SA, Servan-Schreiber E, Tetlock P, et al.
+Distilling the {Wisdom} of {Crowds}: {Prediction Markets} vs.
+{Prediction Polls}.
+Management Science {[}Internet{]}.
+2016 Apr 22 {[}cited 2021 May 30{]};63(3):691--706.
+Available from: \url{https://pubsonline.informs.org/doi/abs/10.1287/mnsc.2015.2374}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
+\CSLLeftMargin{21. }
+\CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers E-J.
+Laypeople {Can Predict Which Social-Science Studies Will Be Replicated Successfully}.
+Advances in Methods and Practices in Psychological Science {[}Internet{]}.
+2020 Sep 1 {[}cited 2021 Oct 13{]};3(3):267--85.
+Available from: \url{https://doi.org/10.1177/2515245920919667}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
+\CSLLeftMargin{22. }
+\CSLRightInline{ReplicationMarkets.
+Replication {Markets} -- {Reliable} research replicates\ldots you can bet on it.
+{[}Internet{]}.
+2020 {[}cited 2021 Oct 13{]}.
+Available from: \url{https://www.replicationmarkets.com/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
+\CSLLeftMargin{23. }
+\CSLRightInline{Servan-Schreiber E, Wolfers J, Pennock DM, Galebach B.
+Prediction {Markets}: {Does Money Matter}?
+Electronic Markets {[}Internet{]}.
+2004 Sep 1 {[}cited 2021 Oct 13{]};14(3):243--51.
+Available from: \url{http://www.informaworld.com/openurl?genre=article\&doi=10.1080/1019678042000245254\&magic=crossref\%7C\%7CD404A21C5BB053405B1A640AFFD44AE3}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
+\CSLLeftMargin{24. }
+\CSLRightInline{McAndrew TC, Reich NG.
+An expert judgment model to predict early stages of the {COVID-19} outbreak in the {United States}.
+medRxiv {[}Internet{]}.
+2020 Sep 23 {[}cited 2020 Sep 23{]};2020.09.21.20196725.
+Available from: \url{https://www.medrxiv.org/content/10.1101/2020.09.21.20196725v1}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
+\CSLLeftMargin{25. }
+\CSLRightInline{Recchia G, Freeman ALJ, Spiegelhalter D.
+How well did experts and laypeople forecast the size of the {COVID-19} pandemic?
+PLOS ONE {[}Internet{]}.
+2021 May 5 {[}cited 2021 Jun 2{]};16(5):e0250935.
+Available from: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0250935}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
+\CSLLeftMargin{26. }
+\CSLRightInline{Metaculus.
+A {Preliminary Look} at {Metaculus} and {Expert Forecasts} {[}Internet{]}.
+2020 {[}cited 2021 May 30{]}.
+Available from: \url{https://www.metaculus.com/news/2020/06/02/LRT/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
+\CSLLeftMargin{27. }
+\CSLRightInline{Hypermind.
+Hypermind \textbar{} {Supercollective} intelligence for decision makers {[}Internet{]}.
+{Hypermind}; 2021 {[}cited 2021 Oct 13{]}.
+Available from: \url{https://www.hypermind.com/en/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
+\CSLLeftMargin{28. }
+\CSLRightInline{CSET Foretell. {CSET Foretell} {[}Internet{]}. 2021 {[}cited 2021 Oct 13{]}. Available from: \url{https://www.cset-foretell.com/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
+\CSLLeftMargin{29. }
+\CSLRightInline{PredictIt. {PredictIt} {[}Internet{]}. 2021 {[}cited 2021 Oct 13{]}. Available from: \url{https://www.predictit.org/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
+\CSLLeftMargin{30. }
+\CSLRightInline{Held L, Meyer S, Bracher J.
+Probabilistic forecasting in infectious disease epidemiology: The 13th {Armitage} lecture.
+Statistics in Medicine {[}Internet{]}.
+2017 {[}cited 2019 Sep 16{]};36(22):3443--60.
+Available from: \url{https://onlinelibrary.wiley.com/doi/abs/10.1002/sim.7363}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
+\CSLLeftMargin{31. }
+\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Crowdforecastr: Eliciting crowd forecasts in r shiny. 2020. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
+\CSLLeftMargin{32. }
+\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Covid.german.forecasts: Forecasting covid-19 related metrics for the german/poland forecast hub. 2020. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-ecdcDownloadHistoricalData2020}{}}%
+\CSLLeftMargin{33. }
+\CSLRightInline{ECDC.
+Download historical data (to 14 {December} 2020) on the daily number of new reported {COVID-19} cases and deaths worldwide {[}Internet{]}.
+{European Centre for Disease Prevention and Control}; 2020 {[}cited 2021 May 30{]}.
+Available from: \url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rkiRKICoronavirusSARSCoV22021}{}}%
+\CSLLeftMargin{34. }
+\CSLRightInline{RKI.
+{RKI} - {Coronavirus SARS-CoV-2} - {Aktueller Lage-}/{Situationsbericht} des {RKI} zu {COVID-19} {[}Internet{]}.
+2021 {[}cited 2021 May 30{]}.
+Available from: \url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-forsal.plRozbieznosciStatystykachKoronawirusa2020}{}}%
+\CSLLeftMargin{35. }
+\CSLRightInline{Forsal.pl.
+Rozbieżności w statystykach koronawirusa.
+22 tys.
+przypadków będą doliczone do ogólnej liczby wyników {[}Internet{]}.
+2020 {[}cited 2021 May 30{]}.
+Available from: \url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
+\CSLLeftMargin{36. }
+\CSLRightInline{Ärzteblatt DÄG Redaktion Deutsches.
+SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an {[}Internet{]}.
+{Deutsches Ärzteblatt}; 2020 {[}cited 2021 May 30{]}.
+Available from: \url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
+\CSLLeftMargin{37. }
+\CSLRightInline{Fay C, Guyader V, Rochette S, Girard C. Golem: A framework for robust shiny applications {[}Internet{]}. 2021. Available from: \url{https://github.com/ThinkR-open/golem}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
+\CSLLeftMargin{38. }
+\CSLRightInline{Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie Y, et al.
+Shiny: Web application framework for r {[}Internet{]}.
+2021.
+Available from: \url{https://CRAN.R-project.org/package=shiny}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
+\CSLLeftMargin{39. }
+\CSLRightInline{Our World in Data.
+{COVID-19 Data Explorer} {[}Internet{]}.
+{Our World in Data}; 2020 {[}cited 2021 May 30{]}.
+Available from: \url{https://ourworldindata.org/coronavirus-data-explorer}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
-Abbott, S., Hellewell, J., Hickson, J., Munday, J., Gostic, K., Ellis, P., Sherratt, K., Gibbs, H., Thompson, R., Meakin, S., Bosse, N.
-I., Mee, P., \& Funk, S.
-(2020).
-EpiNow2: Estimate real-time case counts and time-varying epidemiological parameters.
-\emph{-}, \emph{-}(-), --.
-\url{https://doi.org/10.5281/zenodo.3957489}
+\CSLLeftMargin{40. }
+\CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K, Ellis P, et al. EpiNow2: Estimate real-time case counts and time-varying epidemiological parameters. -. 2020;-(-):--. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
+\CSLLeftMargin{41. }
+\CSLRightInline{Fraser C.
+Estimating {Individual} and {Household Reproduction Numbers} in an {Emerging Epidemic}.
+PLOS ONE {[}Internet{]}.
+2007 Aug 22 {[}cited 2021 Sep 29{]};2(8):e758.
+Available from: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0000758}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation2020}{}}%
+\CSLLeftMargin{42. }
+\CSLRightInline{epiforecasts.io/covid.
+Covid-19: {Temporal} variation in transmission during the {COVID-19} outbreak {[}Internet{]}.
+{Covid-19}; 2020 {[}cited 2021 May 30{]}.
+Available from: \url{https://epiforecasts.io/covid/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
+\CSLLeftMargin{43. }
+\CSLRightInline{Sherratt K, Abbott S, Meakin SR, Hellewell J, Munday JD, Bosse N, et al.
+Exploring surveillance data biases when estimating the reproduction number: With insights into subpopulation transmission of {Covid-19} in {England}.
+2021 Mar 18 {[}cited 2021 Oct 14{]};2020.10.18.20214585.
+Available from: \url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v2}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-abbottEstimatingTimevaryingReproduction2020a}{}}%
-Abbott, S., Hellewell, J., Thompson, R.
-N., Sherratt, K., Gibbs, H.
-P., Bosse, N.
-I., Munday, J.
-D., Meakin, S., Doughty, E.
-L., Chun, J.
-Y., Chan, Y.-W.
-D., Finger, F., Campbell, P., Endo, A., Pearson, C.
-A.
-B., Gimma, A., Russell, T., Group, C.
-C.
-modelling, Flasche, S., \ldots{} Funk, S.
-(2020).
-\emph{Estimating the time-varying reproduction number of {SARS}-{CoV}-2 using national and subnational case counts}.
-\emph{5:112}.
-\url{https://doi.org/10.12688/wellcomeopenres.16006.1}
+\CSLLeftMargin{44. }
+\CSLRightInline{Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs HP, Bosse NI, et al.
+Estimating the time-varying reproduction number of {SARS-CoV-2} using national and subnational case counts.
+2020 Jun 1 {[}cited 2021 Oct 14{]};(5:112).
+Available from: \url{https://wellcomeopenresearch.org/articles/5-112}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
+\CSLLeftMargin{45. }
+\CSLRightInline{Xu B, Gutierrez B, Hill S, Scarpino S, Loskill A, Wu J, et al.
+Epidemiological data from the nCoV-2019 outbreak: Early descriptions from publicly available data {[}Internet{]}.
+2020.
+Available from: \url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
+\CSLLeftMargin{46. }
+\CSLRightInline{Stan Development Team. RStan: The r interface to stan {[}Internet{]}. 2020. Available from: \url{http://mc-stan.org/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
+\CSLLeftMargin{47. }
+\CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG. Evaluating epidemic forecasts in an interval format. PLoS Comput Biol. 2021 Feb;17(2):e1008618. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
+\CSLLeftMargin{48. }
+\CSLRightInline{Gneiting T, Raftery AE.
+Strictly proper scoring rules, prediction, and estimation.
+Journal of the American Statistical Association {[}Internet{]}.
+2007 Mar {[}cited 2020 Mar 22{]};102(477):359--78.
+Available from: \url{http://www.tandfonline.com/doi/abs/10.1198/016214506000001437}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
+\CSLLeftMargin{49. }
+\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Scoringutils: Utilities for scoring and assessing predictions. 2020. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-deutschewelleCoronavirusGermanyImpose2020}{}}%
+\CSLLeftMargin{50. }
+\CSLRightInline{Deutsche Welle.
+Coronavirus: {Germany} to impose one-month partial lockdown \textbar{} {DW} \textbar{} 28.10.2020 {[}Internet{]}.
+2020 {[}cited 2021 Jun 29{]}.
+Available from: \url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
+\CSLLeftMargin{51. }
+\CSLRightInline{Ganyani T, Kremer C, Chen D, Torneri A, Faes C, Wallinga J, et al.
+Estimating the generation interval for coronavirus disease (COVID-19) based on symptom onset data, march 2020.
+Eurosurveillance.
+2020;25(17).
+}
+
+\leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
+\CSLLeftMargin{52. }
+\CSLRightInline{Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith HR, et al.
+The incubation period of coronavirus disease 2019 (COVID-19) from publicly reported confirmed cases: Estimation and application.
+Annals of Internal Medicine.
+2020;172(9):577--82.
+}
 
 \leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
-Abbott, S., Sherratt, K., Bevan, J., Gibbs, H., Hellewell, J., Munday, J., Barks, P., Campbell, P., Finger, F., \& Funk, S.
-(2020).
-Covidregionaldata: Subnational data for the covid-19 outbreak.
-\emph{-}, \emph{-}(-), --.
-\url{https://doi.org/10.5281/zenodo.3957539}
-
-\leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
-Ärzteblatt, D.
-Ä.
-G., Redaktion Deutsches.
-(2020, November 3).
-\emph{SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an}.
-{Deutsches Ärzteblatt}.
-\url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}
-
-\leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
-Atanasov, P., Rescober, P., Stone, E., Swift, S.
-A., Servan-Schreiber, E., Tetlock, P., Ungar, L., \& Mellers, B.
-(2016).
-Distilling the {Wisdom} of {Crowds}: Prediction {Markets} vs.
-{Prediction Polls}.
-\emph{Management Science}, \emph{63}(3), 691--706.
-\url{https://doi.org/10.1287/mnsc.2015.2374}
+\CSLLeftMargin{53. }
+\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J, Munday J, et al. Covidregionaldata: Subnational data for the covid-19 outbreak. -. 2020;-(-):--. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
+\CSLLeftMargin{54. }
+\CSLRightInline{Evaluating the use of the reproduction number as an epidemiological tool, using spatio-temporal trends of the {Covid-19} outbreak in {England} \textbar{} {medRxiv} {[}Internet{]}.
+{[}cited 2021 May 30{]}.
+Available from: \url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
+\CSLLeftMargin{55. }
+\CSLRightInline{Riutort-Mayol G, Bürkner P-C, Andersen MR, Solin A, Vehtari A.
+Practical hilbert space approximate bayesian gaussian processes for probabilistic programming {[}Internet{]}.
+2020.
+Available from: \url{https://arxiv.org/abs/2004.11408}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
+\CSLLeftMargin{56. }
+\CSLRightInline{Scott JA, Gandy A, Mishra S, Unwin J, Flaxman S, Bhatt S.
+Epidemia: Modeling of epidemics using hierarchical bayesian models {[}Internet{]}.
+2020.
+Available from: \url{https://imperialcollegelondon.github.io/epidemia/}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-bhattSemiMechanisticBayesianModeling}{}}%
-Bhatt, S., Ferguson, N., Flaxman, S., Gandy, A., Mishra, S., \& Scott, J. A. (n.d.). \emph{Semi-{Mechanistic Bayesian} modeling of {COVID}-19 with {Renewal Processes}}. 14.
-
-\leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
-Biggerstaff, M., Alper, D., Dredze, M., Fox, S., Fung, I.
-C.-H., Hickmann, K.
-S., Lewis, B., Rosenfeld, R., Shaman, J., Tsou, M.-H., Velardi, P., Vespignani, A., Finelli, L., \& for the Influenza Forecasting Contest Working Group.
-(2016).
-Results from the centers for disease control and prevention's predict the 2013--2014 {Influenza Season Challenge}.
-\emph{BMC Infectious Diseases}, \emph{16}(1), 357.
-\url{https://doi.org/10.1186/s12879-016-1669-x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
-Bosse, N. I., Abbott, S., EpiForecasts, \& Funk, S. (2020a). \emph{Covid.german.forecasts: Forecasting covid-19 related metrics for the german/poland forecast hub}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
-Bosse, N. I., Abbott, S., EpiForecasts, \& Funk, S. (2020b). \emph{Crowdforecastr: Eliciting crowd forecasts in r shiny}. \url{https://doi.org/10.5281/zenodo.4618519}
-
-\leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
-Bosse, N. I., Abbott, S., EpiForecasts, \& Funk, S. (2020c). \emph{Scoringutils: Utilities for scoring and assessing predictions}. \url{https://doi.org/10.5281/zenodo.4618017}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
-Bracher, J., Ray, E.
-L., Gneiting, T., \& Reich, N.
-G.
-(2021).
-Evaluating epidemic forecasts in an interval format.
-\emph{PLoS Computational Biology}, \emph{17}(2), e1008618.
-\url{https://doi.org/10.1371/journal.pcbi.1008618}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
-Bracher, J., Wolffram, D., Deuschel, J., Görgen, K., Ketterer, J.
-L., Ullrich, A., Abbott, S., Barbarossa, M.
-V., Bertsimas, D., Bhatia, S., Bodych, M., Bosse, N.
-I., Burgard, J.
-P., Castro, L., Fairchild, G., Fuhrmann, J., Funk, S., Gogolewski, K., Gu, Q., \ldots{} Schienle, M.
-(2021).
-Short-term forecasting of {COVID}-19 in {Germany} and {Poland} during the second wave -- a preregistered study.
-\emph{medRxiv}, 2020.12.24.20248826.
-\url{https://doi.org/10.1101/2020.12.24.20248826}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
-Bracher, J., Wolffram, D., Deuschel, J., Görgen, K., Ketterer, J.
-L., Ullrich, A., Abbott, S., Barbarossa, M.
-V., Bertsimas, D., Bhatia, S., Bodych, M., Bosse, N.
-I., Burgard, J.
-P., Fiedler, J., Fuhrmann, J., Funk, S., Gambin, A., Gogolewski, K., Heyder, S., \ldots{} Schienle, M.
-(2021).
-\emph{National and subnational short-term forecasting of {COVID}-19 in {Germany} and {Poland}, early 2021}.
-2021.11.05.21265810.
-\url{https://doi.org/10.1101/2021.11.05.21265810}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
-Chang, W., Cheng, J., Allaire, J., Sievert, C., Schloerke, B., Xie, Y., Allen, J., McPherson, J., Dipert, A., \& Borges, B.
-(2021).
-\emph{Shiny: Web application framework for r}.
-\url{https://CRAN.R-project.org/package=shiny}
-
-\leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
-Colón-González, F.
-J., Bastos, L.
-S., Hofmann, B., Hopkin, A., Harpham, Q., Crocker, T., Amato, R., Ferrario, I., Moschini, F., James, S., Malde, S., Ainscoe, E., Nam, V.
-S., Tan, D.
-Q., Khoa, N.
-D., Harrison, M., Tsarouchi, G., Lumbroso, D., Brady, O.
-J., \& Lowe, R.
-(2021).
-Probabilistic seasonal dengue forecasting in {Vietnam}: A modelling study using superensembles.
-\emph{PLOS Medicine}, \emph{18}(3), e1003542.
-\url{https://doi.org/10.1371/journal.pmed.1003542}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
-Cramer, E., Ray, E.
-L., Lopez, V.
-K., Bracher, J., Brennen, A., Rivadeneira, A.
-J.
-C., Gerding, A., Gneiting, T., House, K.
-H., Huang, Y., Jayawardena, D., Kanji, A.
-H., Khandelwal, A., Le, K., Mühlemann, A., Niemi, J., Shah, A., Stark, A., Wang, Y., \ldots{} Reich, N.
-G.
-(2021).
-Evaluation of individual and ensemble probabilistic forecasts of {COVID}-19 mortality in the {US}.
-\emph{medRxiv}, 2021.02.03.21250974.
-\url{https://doi.org/10.1101/2021.02.03.21250974}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
-Cramer, E., Reich, N.
-G., Wang, S.
-Y., Niemi, J., Hannan, A., House, K., Gu, Y., Xie, S., Horstman, S., aniruddhadiga, Walraven, R., starkari, Li, M.
-L., Gibson, G., Castro, L., Karlen, D., Wattanachit, N., jinghuichen, zyt9lsb, \ldots{} leyouz.
-(2020).
-\emph{{COVID}-19 {Forecast Hub}: 4 {December} 2020 snapshot} {[}Data set{]}.
-{Zenodo}.
-\url{https://doi.org/10.5281/zenodo.3963371}
-
-\leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
-CSET Foretell. (2021). \emph{{CSET Foretell}}. \url{https://www.cset-foretell.com/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
-Del Valle, S.
-Y., McMahon, B.
-H., Asher, J., Hatchett, R., Lega, J.
-C., Brown, H.
-E., Leany, M.
-E., Pantazis, Y., Roberts, D.
-J., Moore, S., Peterson, A.
-T., Escobar, L.
-E., Qiao, H., Hengartner, N.
-W., \& Mukundan, H.
-(2018).
-Summary results of the 2014-2015 {DARPA Chikungunya} challenge.
-\emph{BMC Infectious Diseases}, \emph{18}(1), 245.
-\url{https://doi.org/10.1186/s12879-018-3124-7}
-
-\leavevmode\vadjust pre{\hypertarget{ref-deutschewelleCoronavirusGermanyImpose2020}{}}%
-Deutsche Welle.
-(2020).
-\emph{Coronavirus: Germany to impose one-month partial lockdown \textbar{} {DW} \textbar{} 28.10.2020}.
-\url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ecdcDownloadHistoricalData2020}{}}%
-ECDC.
-(2020, December 14).
-\emph{Download historical data (to 14 {December} 2020) on the daily number of new reported {COVID}-19 cases and deaths worldwide}.
-{European Centre for Disease Prevention and Control}.
-\url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation2020}{}}%
-epiforecasts.io/covid. (2020). \emph{Covid-19: Temporal variation in transmission during the {COVID}-19 outbreak}. {Covid-19}. \url{https://epiforecasts.io/covid/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-europeancovid-19forecasthubEuropeanCovid19Forecast2021}{}}%
-European Covid-19 Forecast Hub. (2021). \emph{European {Covid}-19 {Forecast Hub}}. \url{https://covid19forecasthub.eu/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
-\emph{Evaluating the use of the reproduction number as an epidemiological tool, using spatio-temporal trends of the {Covid}-19 outbreak in {England} \textbar{} {medRxiv}}.
-(n.d.).
-Retrieved May 30, 2021, from \url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
-Farrow, D.
-C., Brooks, L.
-C., Hyun, S., Tibshirani, R.
-J., Burke, D.
-S., \& Rosenfeld, R.
-(2017).
-A human judgment approach to epidemiological forecasting.
-\emph{PLOS Computational Biology}, \emph{13}(3), e1005248.
-\url{https://doi.org/10.1371/journal.pcbi.1005248}
-
-\leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
-Fay, C., Guyader, V., Rochette, S., \& Girard, C. (2021). \emph{Golem: A framework for robust shiny applications}. \url{https://github.com/ThinkR-open/golem}
-
-\leavevmode\vadjust pre{\hypertarget{ref-forsal.plRozbieznosciStatystykachKoronawirusa2020}{}}%
-Forsal.pl.
-(2020).
-\emph{Rozbieżności w statystykach koronawirusa.
-22 tys.
-przypadków będą doliczone do ogólnej liczby wyników}.
-\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
-Fraser, C. (2007). Estimating {Individual} and {Household Reproduction Numbers} in an {Emerging Epidemic}. \emph{PLOS ONE}, \emph{2}(8), e758. \url{https://doi.org/10.1371/journal.pone.0000758}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
-Funk, S., Abbott, S., Atkins, B.
-D., Baguelin, M., Baillie, J.
-K., Birrell, P., Blake, J., Bosse, N.
-I., Burton, J., Carruthers, J., Davies, N.
-G., Angelis, D.
-D., Dyson, L., Edmunds, W.
-J., Eggo, R.
-M., Ferguson, N.
-M., Gaythorpe, K., Gorsich, E., Guyver-Fletcher, G., \ldots{} Investigators, I.
-(2020).
-Short-term forecasts to inform the response to the {Covid}-19 epidemic in the {UK}.
-\emph{medRxiv}, 2020.11.11.20220962.
-\url{https://doi.org/10.1101/2020.11.11.20220962}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
-Funk, S., Camacho, A., Kucharski, A.
-J., Lowe, R., Eggo, R.
-M., \& Edmunds, W.
-J.
-(2019).
-Assessing the performance of real-time epidemic forecasts: A case study of {Ebola} in the {Western Area} region of {Sierra Leone}, 2014-15.
-\emph{PLOS Computational Biology}, \emph{15}(2), e1006785.
-\url{https://doi.org/10.1371/journal.pcbi.1006785}
-
-\leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
-Ganyani, T., Kremer, C., Chen, D., Torneri, A., Faes, C., Wallinga, J., \& Hens, N.
-(2020).
-Estimating the generation interval for coronavirus disease (COVID-19) based on symptom onset data, march 2020.
-\emph{Eurosurveillance}, \emph{25}(17).
-
-\leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
-Gneiting, T., \& Raftery, A.
-E.
-(2007).
-Strictly proper scoring rules, prediction, and estimation.
-\emph{Journal of the American Statistical Association}, \emph{102}(477), 359--378.
-\url{https://doi.org/10.1198/016214506000001437}
-
-\leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
-Held, L., Meyer, S., \& Bracher, J.
-(2017).
-Probabilistic forecasting in infectious disease epidemiology: The 13th {Armitage} lecture.
-\emph{Statistics in Medicine}, \emph{36}(22), 3443--3460.
-\url{https://doi.org/10.1002/sim.7363}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
-Hoogeveen, S., Sarafoglou, A., \& Wagenmakers, E.-J.
-(2020).
-Laypeople {Can Predict Which Social}-{Science Studies Will Be Replicated Successfully}.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 267--285.
-\url{https://doi.org/10.1177/2515245920919667}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
-Hypermind. (2021). \emph{Hypermind \textbar{} {Supercollective} intelligence for decision makers}. {Hypermind}. \url{https://www.hypermind.com/en/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
-Johansson, M.
-A., Apfeldorf, K.
-M., Dobson, S., Devita, J., Buczak, A.
-L., Baugher, B., Moniz, L.
-J., Bagley, T., Babin, S.
-M., Guven, E., Yamana, T.
-K., Shaman, J., Moschou, T., Lothian, N., Lane, A., Osborne, G., Jiang, G., Brooks, L.
-C., Farrow, D.
-C., \ldots{} Chretien, J.-P.
-(2019).
-An open challenge to advance probabilistic forecasting for dengue epidemics.
-\emph{Proceedings of the National Academy of Sciences}, \emph{116}(48), 24268--24274.
-\url{https://doi.org/10.1073/pnas.1909865116}
-
-\leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
-Lauer, S.
-A., Grantz, K.
-H., Bi, Q., Jones, F.
-K., Zheng, Q., Meredith, H.
-R., Azman, A.
-S., Reich, N.
-G., \& Lessler, J.
-(2020).
-The incubation period of coronavirus disease 2019 (COVID-19) from publicly reported confirmed cases: Estimation and application.
-\emph{Annals of Internal Medicine}, \emph{172}(9), 577--582.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
-McAndrew, T.
-C., \& Reich, N.
-G.
-(2020).
-An expert judgment model to predict early stages of the {COVID}-19 outbreak in the {United States}.
-\emph{medRxiv}, 2020.09.21.20196725.
-\url{https://doi.org/10.1101/2020.09.21.20196725}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
-McGowan, C.
-J., Biggerstaff, M., Johansson, M., Apfeldorf, K.
-M., Ben-Nun, M., Brooks, L., Convertino, M., Erraguntla, M., Farrow, D.
-C., Freeze, J., Ghosh, S., Hyun, S., Kandula, S., Lega, J., Liu, Y., Michaud, N., Morita, H., Niemi, J., Ramakrishnan, N., \ldots{} Reed, C.
-(2019).
-Collaborative efforts to forecast seasonal influenza in the {United States}, 2015--2016.
-\emph{Scientific Reports}, \emph{9}(1, 1), 683.
-\url{https://doi.org/10.1038/s41598-018-36361-9}
-
-\leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
-Metaculus. (2020, June 22). \emph{A {Preliminary Look} at {Metaculus} and {Expert Forecasts}}. \url{https://www.metaculus.com/news/2020/06/02/LRT/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
-Our World in Data. (2020). \emph{{COVID}-19 {Data Explorer}}. {Our World in Data}. \url{https://ourworldindata.org/coronavirus-data-explorer}
-
-\leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
-PredictIt. (2021). \emph{{PredictIt}}. \url{https://www.predictit.org/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
-Recchia, G., Freeman, A.
-L.
-J., \& Spiegelhalter, D.
-(2021).
-How well did experts and laypeople forecast the size of the {COVID}-19 pandemic?
-\emph{PLOS ONE}, \emph{16}(5), e0250935.
-\url{https://doi.org/10.1371/journal.pone.0250935}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
-Reich, N.
-G., Brooks, L.
-C., Fox, S.
-J., Kandula, S., McGowan, C.
-J., Moore, E., Osthus, D., Ray, E.
-L., Tushar, A., Yamana, T.
-K., Biggerstaff, M., Johansson, M.
-A., Rosenfeld, R., \& Shaman, J.
-(2019).
-A collaborative multiyear, multimodel assessment of seasonal influenza forecasting in the {United States}.
-\emph{Proceedings of the National Academy of Sciences}, \emph{116}(8), 3146--3154.
-\url{https://doi.org/10.1073/pnas.1812594116}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichAccuracyRealtimeMultimodel2019}{}}%
-Reich, N.
-G., McGowan, C.
-J., Yamana, T.
-K., Tushar, A., Ray, E.
-L., Osthus, D., Kandula, S., Brooks, L.
-C., Crawford-Crudell, W., Gibson, G.
-C., Moore, E., Silva, R., Biggerstaff, M., Johansson, M.
-A., Rosenfeld, R., \& Shaman, J.
-(2019).
-Accuracy of real-time multi-model ensemble forecasts for seasonal influenza in the {U}.{S}.
-\emph{PLOS Computational Biology}, \emph{15}(11), e1007486.
-\url{https://doi.org/10.1371/journal.pcbi.1007486}
-
-\leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
-ReplicationMarkets. (2020). \emph{Replication {Markets} -- {Reliable} research replicates\ldots you can bet on it.} \url{https://www.replicationmarkets.com/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
-Riutort-Mayol, G., Bürkner, P.-C., Andersen, M.
-R., Solin, A., \& Vehtari, A.
-(2020).
-\emph{Practical hilbert space approximate bayesian gaussian processes for probabilistic programming}.
-\url{https://arxiv.org/abs/2004.11408}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rkiRKICoronavirusSARSCoV22021}{}}%
-RKI.
-(2021).
-\emph{{RKI} - {Coronavirus SARS}-{CoV}-2 - {Aktueller Lage}-/{Situationsbericht} des {RKI} zu {COVID}-19}.
-\url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
-Scott, J.
-A., Gandy, A., Mishra, S., Unwin, J., Flaxman, S., \& Bhatt, S.
-(2020).
-\emph{Epidemia: Modeling of epidemics using hierarchical bayesian models}.
-\url{https://imperialcollegelondon.github.io/epidemia/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
-Servan-Schreiber, E., Wolfers, J., Pennock, D.
-M., \& Galebach, B.
-(2004).
-Prediction {Markets}: Does {Money Matter}?
-\emph{Electronic Markets}, \emph{14}(3), 243--251.
-\url{https://doi.org/10.1080/1019678042000245254}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
-Shaman, J., \& Karspeck, A.
-(2012).
-Forecasting seasonal outbreaks of influenza.
-\emph{Proceedings of the National Academy of Sciences}, \emph{109}(50), 20425--20430.
-\url{https://doi.org/10.1073/pnas.1208772109}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
-Sherratt, K., Abbott, S., Meakin, S.
-R., Hellewell, J., Munday, J.
-D., Bosse, N., Group, C.
-C.
-working, Jit, M., \& Funk, S.
-(2021).
-\emph{Exploring surveillance data biases when estimating the reproduction number: With insights into subpopulation transmission of {Covid}-19 in {England}}.
-2020.10.18.20214585.
-\url{https://doi.org/10.1101/2020.10.18.20214585}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
-Stan Development Team. (2020). \emph{RStan: The r interface to stan}. \url{http://mc-stan.org/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
-Tetlock, P.
-E., Mellers, B.
-A., Rohrbaugh, N., \& Chen, E.
-(2014).
-Forecasting {Tournaments}: Tools for {Increasing Transparency} and {Improving} the {Quality} of {Debate}.
-\emph{Current Directions in Psychological Science}, \emph{23}(4), 290--295.
-\url{https://doi.org/10.1177/0963721414534257}
-
-\leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
-Viboud, C., Sun, K., Gaffey, R., Ajelli, M., Fumanelli, L., Merler, S., Zhang, Q., Chowell, G., Simonsen, L., \& Vespignani, A.
-(2018).
-The {RAPIDD} ebola forecasting challenge: Synthesis and lessons learnt.
-\emph{Epidemics}, \emph{22}, 13--21.
-\url{https://doi.org/10.1016/j.epidem.2017.08.002}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
-Xu, B., Gutierrez, B., Hill, S., Scarpino, S., Loskill, A., Wu, J., Sewalk, K., Mekaru, S., Zarebski, A., Pybus, O., Pigott, D., \& Kraemer, M.
-(2020).
-\emph{Epidemiological data from the nCoV-2019 outbreak: Early descriptions from publicly available data}.
-\url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}
-
-\leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
-Yamana, T.
-K., Kandula, S., \& Shaman, J.
-(2016).
-Superensemble forecasts of dengue outbreaks.
-\emph{Journal of The Royal Society Interface}, \emph{13}(123), 20160410.
-\url{https://doi.org/10.1098/rsif.2016.0410}
+\CSLLeftMargin{57. }
+\CSLRightInline{Bhatt S, Ferguson N, Flaxman S, Gandy A, Mishra S, Scott JA. Semi-{Mechanistic Bayesian} modeling of {COVID-19} with {Renewal Processes}. :14. }
 

### 2022-01-14 manuscript/manuscript.tex
update manuscript formatting

@@
 \linenumbers
+\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 \usepackage{float}
@@
 
+The study was approved by the Observational / Interventions Research Ethics Committee at the London School of Hygiene \& Tropical Medicine, LSHTM Ethics Reference: 22290.
+
 \hypertarget{model-based-forecasts}{%
@@
 
-NIB received funding from the Health Protection Research Unit (grant code NIHR200908).
-SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z).
-The work of JB was supported by the Helmholtz Foundation via the SIMCARD Information and Data Science Pilot Project.
-This research was partly funded by the National Institute for Health Research (NIHR) (16/137/109 \& 16/136/46) using UK aid from the UK Government to support global health research.
+NIB received funding from the Health Protection Research Unit (grant code NIHR200908, \url{https://www.nihr.ac.uk/}).
+SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z, \url{https://wellcome.org/}).
+The work of JB was supported by the Helmholtz Foundation (\url{https://www.helmholtz.de/}) via the SIMCARD Information and Data Science Pilot Project.
+This research was partly funded by the National Institute for Health Research (NIHR, \url{https://www.nihr.ac.uk/}) (16/137/109 \& 16/136/46) using UK aid from the UK Government to support global health research.
 The views expressed in this publication are those of the author(s) and not necessarily those of the NIHR or the UK Department of Health and Social Care.
-BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859).
-EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688).
-AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID, and the Academy of Medical Sciences.
-SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z), and the NIHR (NIHR200908).
+BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859, \url{https://www.gatesfoundation.org/}).
+EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908, \url{https://www.nihr.ac.uk/}) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688, \url{https://ec.europa.eu/programmes/horizon2020/}).
+AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID (\url{https://www.usaid.gov/}), and the Academy of Medical Sciences (\url{https://acmedsci.ac.uk/}).
+SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z, \url{https://wellcome.org/}), and the NIHR (NIHR200908, \url{https://www.nihr.ac.uk/}).
 
@@
 \clearpage
+
+\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
 

### 2022-05-12 analysis/analysis.Rmd
update manuscript with review suggestions

@@
 library(magrittr)
-library(scoringutils)
+library(scoringutils) #needs v0.18
+# remotes::install_github("epiforecasts/scoringutils@v0.1.8")
 library(knitr)
@@
 scale_fn <- function(x) {
-  ifelse(x >= 5000,
+  ifelse(abs(x) >= 5000,
          paste0(x / 1000, "k"), x)
@@
     p <- p + 
-      geom_hline(yintercept = 1, linetype = "dashed")
+      geom_hline(yintercept = 1, linetype = "dashed") +
+      expand_limits(y = c(0, 1)) +
+      scale_y_continuous(breaks = seq(0, max(scores$value), 0.25))
   }
@@
 plot_helper <- function(tmp = scores, xvar = x, y, rel = relative, 
-                        facet_formula, colour) {
+                        facet_formula, colour, scalefree = NULL) {
+  if (is.null(scalefree)) {
+    scalefree <- "free_y"
+  }
   if (rel) {
+    scalefree <- "fixed"
     tmp <- tmp %>%
@@
 
-  tmp %>%
+  out <- tmp %>%
     ggplot(aes_string(x = xvar, y = y, group = "Model", color = "Model")) +
@@
     geom_line(position = position_dodge(width = 0.1)) +
-    facet_wrap(facet_formula, scales = "free_y") +
     theme_minimal() +
@@
     scale_y_continuous(labels = scale_fn) + 
+    expand_limits(y = 0) +
+    facet_wrap(facet_formula, scales = scalefree) +
     guides(fill = "none", colour = "none")
+
+  return(out)
 }
@@
                                   x = "horizon",
-                                  xlabel = "Forecast horizon",
+                                  xlabel = "Forecast horizon (weeks)",
                                   output_dir = here("analysis", "plots"), 
@@
     plot_helper(scores, y = "bias", rel = FALSE, colour = vals, xvar = x,
-                facet_formula = facet_formula) + 
+                facet_formula = facet_formula, scalefree = "fixed") + 
     labs(y = "Bias", x = NULL) +
@@
                 facet_formula = facet_formula, colour = vals) + 
-    labs(y = "Absolute error", x = NULL)
+    labs(y = "Absolute error", x = xlabel)
 
@@
                 facet_formula = facet_formula, colour = vals) + 
-    labs(y = "WIS - sd", x = NULL)
+    labs(y = "WIS - sd", x = xlabel)
 
@@
     plot_helper(y = "coverage", rel = FALSE, facet_formula = facet_formula, 
-                colour = vals, xvar = x) +
+                colour = vals, xvar = x, scalefree = "fixed") +
     labs(y = "Diff. cov. - 50% PI", x = "") + 
@@
     plot_helper(y = "coverage", rel = FALSE, facet_formula = facet_formula, 
-                xvar = x, colour = vals) + 
-    labs(y = "Diff. cov. - 90% PI") + 
+                xvar = x, colour = vals, scalefree = "fixed") + 
+    labs(y = "Diff. cov. - 90% PI", x = "") + 
     scale_y_continuous(labels = scales::percent)
@@
     theme(legend.position = 'bottom', 
-          legend.box="vertical", legend.margin=margin())
+          legend.box="vertical", legend.margin=margin()) &
+    labs(x = xlabel)
 
@@
                         x = "location_name", 
-                        xlabel = NULL)
+                        xlabel = "Location")
 
@@
                         x = "location_name", 
-                        xlabel = NULL, relative = TRUE)
-
-# plot for different median ensembles (in relative terms) for SI
+                        xlabel = "Location", relative = TRUE)
+
+# plot for different median ensembles (in relative terms) Figure 4
 filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]] %>%
@@
                         relative = TRUE, colour_scheme = "ensemble")
+
+# make SI version of Figure 1 for Germany and Poland separately
+filtered_data[(model %in% regular_models) & location == "GM" ] %>%
+  aggregate_performance(plotname = "aggregate-performance-all-Germany")
+
+filtered_data[(model %in% regular_models) & location == "PL" ] %>%
+  aggregate_performance(plotname = "aggregate-performance-all-Poland")
 
@@
 ```
+
+Create comparison of crowd forecasts and baseline model - 2 Week ahead forecasts
+
+```{r}
+
+dailytruth_data
+
+crowdforecasts <- covid.german.forecasts::prediction_data %>% 
+  filter(model == "Crowd forecast")
+
+qs <- c(0.05, 0.25, 0.5, 0.75, 0.95)
+
+basline_forecasts <- truth_data %>%
+  mutate(difference = c(NA, diff(log(pmax(true_value, 1)))), 
+         target_end_date = as.Date(target_end_date), 
+         id = 1:n()) %>%
+  rowwise() %>%
+  mutate(sd = sd(d$difference[pmax(0, id - (4:1))]), 
+         quantile = list(qs)) %>%
+  tidyr::unnest(cols = quantile) %>%
+  mutate(prediction = exp(qnorm(quantile, mean = log(true_value), sd = sd)), 
+         model = "Baseline", 
+         forecast_date = target_end_date + 2) %>%
+  unique()
+
+plot_df <- prediction_data %>%
+  filter(model == "Crowd forecast", 
+         quantile %in% qs, 
+         grepl("2", target)) %>%
+  unique() %>%
+  rbind(basline_forecasts, fill = TRUE) %>%
+  filter(forecast_date %in% forecast_dates$unfiltered) %>%
+  pivot_wider(names_from = quantile, values_from = prediction) %>%
+  rename(Model = model) %>%
+  mutate(target_type = ifelse(target_type == "case", "Case", "Death"))
+
+plot_df %>%
+  ggplot(aes(x = forecast_date, colour = NULL, fill = Model)) +
+  geom_line(aes(y = `0.5`)) +
+  facet_wrap(location_name ~ target_type, scales = "free_y") +
+  geom_ribbon(aes(ymin = `0.05`, ymax = `0.95`), alpha = 0.2) +
+  geom_ribbon(aes(ymin = `0.25`, ymax = `0.75`), alpha = 0.5) +
+  theme_minimal() +
+  scale_y_continuous(labels = scale_fn) +
+  labs(y = "Prediction intervals", x = "Forecast date") +
+  theme(legend.position = "bottom")
+
+ggsave(here("analysis", "plots", "comparison-forecast-interals.png"), 
+       height = 6, width = 9)
+
+```
+
+Analysis of how data changed over time
+
+```{r}
+current_data <- 
+  rbind(
+    fread(here("data-raw", "daily-incidence-cases.csv")) %>%
+      mutate(target_type = "Case"), 
+    fread(here("data-raw", "daily-incidence-deaths.csv")) %>%
+      mutate(target_type = "Death")
+  ) %>%
+  filter(location_name %in% c("Germany", "Poland")) %>%
+  select(region = location_name, date, value, target_type) %>%
+  unique()
+
+original_cases <- original_deaths <- list()
+for (target_date in as.character(forecast_dates$unfiltered)) {
+  # Get cases  ---------------------------------------------------------------
+  original_cases[[target_date]] <- 
+    fread(file.path("rt-forecast", "data", "summary", 
+                    "cases", target_date, "reported_cases.csv")) %>%
+    mutate(fit_date = target_date)
+
+  original_deaths[[target_date]] <- 
+    fread(file.path("rt-forecast", "data", "summary", 
+                    "deaths", target_date, "reported_cases.csv")) %>%
+    mutate(fit_date = target_date)
+}
+original_cases <- rbindlist(original_cases) %>%
+  mutate(target_type = "Case") 
+original_deaths <- rbindlist(original_deaths) %>%
+  mutate(target_type = "Death")
+
+original <- 
+  rbind(original_cases, original_deaths) %>%
+  filter(region %in% c("Germany", "Poland")) %>%
+  unique() %>%
+  rename(value_original = confirm)
+
+dailycomparison <- full_join(current_data, original) %>%
+  filter(!is.na(value_original)) %>%
+  mutate(difference = value - value_original, 
+         rel_difference = difference / value_original)
+
+dailycomparison%>%
+  filter(date >= min(forecast_dates$unfiltered -2), 
+         date <= max(forecast_dates$unfiltered)) %>%
+  ggplot(aes(x = date)) +
+  geom_line(aes(y = difference)) +
+  theme_minimal() +
+  facet_wrap(region ~ target_type, scales = "free_y") +
+  labs(y = "Absolute change in data", x = "Date")
+
+ggsave(here("analysis", "plots", "daily-data-updates.png"), 
+       height = 6, width = 9)
+
+# weekly data
+weeklycomparison <- dailycomparison %>%
+  group_by(date, region, target_type) %>%
+  # only take the oldest one for comparison if an update has taken place
+  slice_head(n = 1) %>%
+  ungroup() %>%
+  select(-fit_date) %>%
+  unique() %>%
+  mutate(week = grates::as_yearweek(as.character(date), firstday = 7)) %>%
+  group_by(week, target_type, region) %>%
+  summarise(value = sum(value), 
+            date = max(date),
+            value_original = sum(value_original)) %>%
+  mutate(difference = value - value_original, 
+         rel_difference = difference / value_original)
+
+weeklycomparison %>%
+  filter(date >= min(forecast_dates$unfiltered -2), 
+         date <= max(forecast_dates$unfiltered)) %>%
+  ggplot(aes(x = date, y = rel_difference)) +
+  geom_line() +
+  facet_wrap(region ~ target_type, scales = "fixed") +
+  scale_y_continuous(labels = scales::percent) +
+  theme_minimal() +
+  labs(y = "Relative change in weekly data", x = "Date")
+
+ggsave(here("analysis", "plots", "weekly-data-updates.png"), 
+       height = 6, width = 9)
+
+```
+
+Plot with differences hub ensemble vs. crowd forecasts
+
+```{r}
+scores <- eval_forecasts(
+  filtered_data[(model %in% regular_models)], 
+  summarise_by = c("model", "target_type", "location_name", "horizon", 
+                   "forecast_date", "target_phase",
+                   "location_target", "classification"),
+  compute_relative_skill = FALSE
+)
+
+# reformat column
+scores[, target_type := str_to_title(target_type)]
+
+p <- scores[model %in% c("Crowd forecast", "Hub-ensemble")] %>%
+  filter(horizon == 2) %>%
+  select(target_type, model, location_name, forecast_date, interval_score) %>%
+  rename(Model = model) %>%
+  pivot_wider(names_from = Model, values_from = interval_score) %>%
+  ggplot(aes(x = `Crowd forecast` - `Hub-ensemble`)) +
+  ggdist::stat_slab(alpha = 1, scale = 1, normalize = "panels") +
+  scale_x_continuous(labels = scale_fn) +
+  theme(axis.ticks.y = element_blank(), 
+        axis.text.y = element_blank(), 
+        axis.title.y = element_blank()) +
+  scale_y_continuous(labels = NULL) +
+  lemon::scale_x_symmetric(labels = scale_fn) +
+  theme_minimal() +
+  labs(y = "Density", x = "WIS difference Crowd forecast - Hub-ensemble")
+
+p1 <- p +
+  facet_wrap(~ target_type, nrow = 2, scales = "free")
+p2 <- p +
+  facet_wrap(location_name ~ target_type, scales = "free")
+
+p1 + p2
+
+ggsave(here("analysis", "plots", "difference-wis-crowd-ensemble.png"), 
+       height = 6, width = 9)
+
+```
+
+Looking at removed forecasts - yields nothing
+
+```{r}
+
+files <- list.files(here("crowd-forecast", "raw-forecast-data/"))
+
+raw_forecasts <- purrr::map_dfr(
+  files,
+  .f = function(x) {
+    out <- fread(
+      here("crowd-forecast", "raw-forecast-data/", x)
+    ) %>%
+      mutate(target_end_date = as.character(target_end_date))
+    } 
+) %>%
+  dplyr::filter(location_name %in% c("Germany", "Poland")) %>%
+  mutate(location = ifelse(location_name == "Germany", "GM", "PL"), 
+         distribution = ifelse(is.na(distribution), "log-normal", distribution), 
+         width = ifelse(is.na(width), shape_log_normal, width), 
+         target_type = ifelse(is.na(target_type), type, target_type))
+
+# use only the latest forecast from a given forecaster
+filtered_forecasts <- raw_forecasts %>%
+  group_by(forecaster_id, location, target_type) %>%
+  dplyr::filter(forecast_time == max(forecast_time)) %>%
+  ungroup()
+
+# replace forecast duration with exact data about forecast date and time
+# define function to do this for raw and filtered forecasts
+replace_date_and_time <- function(forecasts) {
+  forecast_times <- forecasts %>%
+    group_by(forecaster_id, location, target_type) %>%
+    summarise(forecast_time = unique(forecast_time)) %>%
+    ungroup() %>%
+    arrange(forecaster_id, forecast_time) %>%
+    group_by(forecaster_id) %>%
+    mutate(forecast_duration = c(NA, diff(forecast_time))) %>%
+    ungroup()
+
+  forecasts <- inner_join(
+    forecasts, forecast_times,
+    by = c("forecaster_id", "location", "target_type", "forecast_time")) %>%
+    mutate(forecast_week = epiweek(forecast_date),
+           target_end_date = as.Date(target_end_date)) %>%
+    select(-forecast_time)
+  return(forecasts)
+}
+
+# replace time with duration and date with epiweek
+raw_forecasts <- replace_date_and_time(raw_forecasts)
+filtered_forecasts <- replace_date_and_time(filtered_forecasts)
+
+# obtain quantiles from forecasts ----------------------------------------------
+# define function that returns quantiles depending on condition and distribution
+calculate_quantiles <- function(quantile_grid, median, width, forecast_type, 
+                                distribution, lower_90, upper_90) {
+  if (distribution == "log-normal") {
+    values <- list(exp(qnorm(
+      quantile_grid, mean = log(as.numeric(median)), sd = as.numeric(width)
+      )))
+  } else if (distribution == "normal") {
+    values <- list((qnorm(
+      quantile_grid, mean = (as.numeric(median)), sd = as.numeric(width)
+      )))
+  } else if (distribution == "cubic-normal") {
+    values <- list((qnorm(quantile_grid,
+     mean = (as.numeric(median) ^ (1 / 3)), sd = as.numeric(width))
+      ) ^ 3)
+  } else if (distribution == "fifth-power-normal") {
+    values <- list((qnorm(quantile_grid, 
+    mean = (as.numeric(median) ^ (1 / 5)), sd = as.numeric(width)
+      )) ^ 5)
+  } else if (distribution == "seventh-power-normal") {
+    values <- list((qnorm(quantile_grid,
+     mean = (as.numeric(median) ^ (1 / 7)), sd = as.numeric(width))
+     ) ^ 7)
+  }
+  return(values)
+}
+
+quantile_grid <- c(0.01, 0.025, seq(0.05, 0.95, 0.05), 0.975, 0.99)
+
+forecast_quantiles <- filtered_forecasts %>%
+  # disregard quantile forecasts this week
+  rowwise() %>%
+  mutate(quantile = list(quantile_grid),
+        value = calculate_quantiles(quantile_grid, median, width, 
+        forecast_type, distribution, lower_90, upper_90)) %>%
+  unnest(cols = c(quantile, value)) %>%
+  ungroup() %>%
+  mutate(type = ifelse(target_type == "cases", "case", "death"), 
+         target = paste0(horizon, " wk ahead inc ", type), 
+         type = "quantile")
+
+# omit forecasters who haven't forecasted at least two targets
+forecasters_to_omit <- forecast_quantiles %>%
+  select(forecaster_id, location, target_type, forecast_date) %>%
+  unique() %>%
+  group_by(forecaster_id) %>%
+  mutate(n = n(), flag = n >= 2) %>%
+  dplyr::filter(!flag) %>%
+  pull(forecaster_id) %>%
+  unique()
+
+```

### 2022-05-12 manuscript/manuscript.Rmd
update manuscript with review suggestions

@@
     - \linenumbers
+    -  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 output: 
@@
                       fig.pos = "H", out.extra = "")
+
 library(kableExtra)
@@
 These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, @forsal.plRozbieznosciStatystykachKoronawirusa2020), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, @aerzteblattSARSCoV2DiagnostikRKIPasst2020).
+The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \@ref(fig:daily-truth-update) and \@ref(fig:weekly-truth-update))
 
@@
 Depending on whether they had a background in either statistics, forecasting or epidemiology, participants were asked to self-identify as 'experts' or 'non-experts'.
+
+The study was approved by the Observational / Interventions Research Ethics Committee at the London School of Hygiene & Tropical Medicine, LSHTM Ethics Reference: 22290.
 
@@
 At all stages of the evaluation our forecasts were compared to the median ensemble of all *other* models submitted to the German and Polish Forecast Hub ("Hub ensemble").
-This "Hub ensemble" was retrospectively computed and excludes all our models.
-It therefore differs from the official Hub ensemble (here called "hub-ensemble-realised") which included crowd forecasts as well as renewal model forecasts.
+This "Hub ensemble" was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see details in Section \@ref(contributions-hub), as well as in Table \@ref(tab:table-ensemble-versions) and Figure \@ref(fig:num-ensemble-members) in the SI).
+What we call "Hub ensemble" in this article therefore differs from the "official Hub ensemble" (here called "hub-ensemble-realised") which included crowd forecasts as well as renewal model forecasts.
 To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e.
@@
 ```{r}
-caption <- "Visualisation of aggregate performance metrics across for forecasts one to four weeks into the future (marked as 1 - 4 on the x axis).
+caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
@@
 Overall, low variance in forecast performance was closely linked with good mean performance (Figures \@ref(fig:agg-performance-all)H and and \@ref(fig:agg-performance-all)A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
+The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores)), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
 WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
@@
 Despite worse performance in terms of absolute error (Figure \@ref(fig:agg-performance-all)G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
+The crowd forecasts, on the other hand, showed a smaller bias than the renewal model, but were overconfident.
 
@@
 Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
-However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figure \@ref(fig:performance-locations-rel)A and \@ref(fig:performance-locations-rel)G).
+However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \@ref(fig:performance-locations-rel)A, \@ref(fig:performance-locations-rel)G, \@ref(fig:performance-all-Germany), \@ref(fig:performance-all-Poland)).
 
@@
 For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \@ref(fig:agg-performance-all)F.
-The convolution model had a strong tendency to under-predict, which steadily decreased for longer forecast horizons.
+The convolution model had a strong tendency to under-predict, with the magnitude of under-prediction steadily decreasing for longer forecast horizons.
 The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction.
@@
 Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country."
+B: Distribution of WIS separate by country.
+Black squares indicate median and black circles mean scores."
 ```
@@
 ```{r}
-caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
-“Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included.
-Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A: mean weighted interval score (WIS) across horizons.
-B: median WIS.
-C: Absolute error of the median forecast.
-D: Standard deviation of the WIS.
-E: Dispersion (higher values mean greater spread of the forecast).
+caption <- "Visualisation of relative aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
+“Hub-ensemble” *excludes* all our models, Hub-ensemble-all *includes* all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
+A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
+C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble.
+E: Dispersion relative to the dispersion of the Hub ensemble.
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
 F: Bias, i.e.
-general tendency to over- or underpredict.
+general (relative) tendency to over- orunderpredict.
 Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Empirical coverage of the 50\\% prediction intervals.
-F: Empirical coverage of the 90\\% prediction intervals"
-```
-
-```{r agg-performance-ensemble, fig.cap=caption}
+G: Absolute error of the median forecast relative to the Hub ensemble.
+H.
+Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
+```
+
+```{r agg-performance-ensemble-rel, fig.cap=caption}
 knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-v4.png")
@@
 
-## Contribution to the Forecast Hub
+## Contribution to the Forecast Hub {#contributions-hub}
 
@@
 For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel.
-WIS of the hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \@ref(tab:score-table-ensemble-2) and \@ref(tab:score-table-ensemble-4)).
+WIS of the Hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \@ref(tab:score-table-ensemble-2) and \@ref(tab:score-table-ensemble-4)).
 Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons).
@@
 This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data).
-The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \@ref(fig:forecasts-and-truth)A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.
+The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \@ref(fig:forecasts-and-truth)A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting which have less of an influence on weekly reporting.
 
@@
 
-NIB received funding from the Health Protection Research Unit (grant code NIHR200908).
-SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z).
-The work of JB was supported by the Helmholtz Foundation via the SIMCARD Information and Data Science Pilot Project.
-This research was partly funded by the National Institute for Health Research (NIHR) (16/137/109 & 16/136/46) using UK aid from the UK Government to support global health research.
+NIB received funding from the Health Protection Research Unit (grant code NIHR200908, https://www.nihr.ac.uk/).
+SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/).
+The work of JB was supported by the Helmholtz Foundation (https://www.helmholtz.de/) via the SIMCARD Information and Data Science Pilot Project.
+This research was partly funded by the National Institute for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 & 16/136/46) using UK aid from the UK Government to support global health research.
 The views expressed in this publication are those of the author(s) and not necessarily those of the NIHR or the UK Department of Health and Social Care.
-BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859).
-EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688).
-AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID, and the Academy of Medical Sciences.
-SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z), and the NIHR (NIHR200908).
+BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859, https://www.gatesfoundation.org/).
+EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908, https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688, https://ec.europa.eu/programmes/horizon2020/).
+AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/), and the Academy of Medical Sciences (https://acmedsci.ac.uk/).
+SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/), and the NIHR (NIHR200908, https://www.nihr.ac.uk/).
 
@@
 \clearpage
+
+\beginsupplement
 
@@
 
+### Performance in Germany
+
+```{r}
+caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
+A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
+WIS is decomposed into its components dispersion, over-prediction and under-prediction.
+C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
+D: Empirical coverage of the 90\\% prediction intervals.
+E: Dispersion (same as in panel A, B).
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
+F: Bias, i.e.
+general (relative) tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Absolute error of the median forecast (lower is better).
+H.
+Standard deviation of all WIS values for different horizons"
+```
+
+```{r agg-performance-all-Germany, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/aggregate-performance-all-Germany-v4.png")
+```
+
+### Performance in Poland
+
+```{r}
+caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
+A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
+WIS is decomposed into its components dispersion, over-prediction and under-prediction.
+C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
+D: Empirical coverage of the 90\\% prediction intervals.
+E: Dispersion (same as in panel A, B).
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
+F: Bias, i.e.
+general (relative) tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Absolute error of the median forecast (lower is better).
+H.
+Standard deviation of all WIS values for different horizons"
+```
+
+```{r agg-performance-all-Poland, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/aggregate-performance-all-Poland-v4.png")
+```
+
 ### Performance across locations in absolute terms
@@
 caption <- "Visualisation of aggregate performance metrics across locations.
-A: mean weighted interval score (WIS) across horizons.
-B: median WIS.
-C: Absolute error of the median forecast.
-D: Standard deviation of the WIS.
-E: Dispersion (higher values mean further spread out forecast).
+A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
+WIS is decomposed into its components dispersion, over-prediction and under-prediction.
+C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
+D: Empirical coverage of the 90\\% prediction intervals.
+E: Dispersion (same as in panel A, B).
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
 F: Bias, i.e.
-general tendency to over- or underpredict.
+general (relative) tendency to over- or underpredict.
 Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Empirical coverage of the 50\\% prediction intervals.
-F: Empirical coverage of the 90\\% prediction intervals."
+G: Absolute error of the median forecast (lower is better).
+H.
+Standard deviation of WIS values."
 ```
@@
 ```{r}
-caption <- " Visualisation of aggregate performance metrics across locations relative to the Hub ensemble (excluding our contributions).
-A: mean weighted interval score (WIS) across horizons.
-B: median WIS.
-C: Absolute error of the median forecast.
-D: Standard deviation of the WIS.
-E: Dispersion (higher values mean further spread out forecast).
+caption <- "Visualisation of relative aggregate performance metrics across locations.
+A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
+C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals.
+E: Dispersion.
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
 F: Bias, i.e.
-general tendency to over- or underpredict.
+general (relative) tendency to over- orunderpredict.
 Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Empirical coverage of the 50\\% prediction intervals.
-F: Empirical coverage of the 90\\% prediction intervals."
+G: Absolute error of the median forecast.
+H.
+Standard deviation of WIS values."
 ```
@@
 knitr::include_graphics("../analysis/plots/daily_truth.png")
+```
+
+```{r}
+caption <- "Visualisation of the absolute difference between the daily report data at the time and the data now.
+In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
+Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
+```
+
+```{r daily-truth-update, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/daily-data-updates.png")
+```
+
+```{r}
+caption <- "Visualisation of the relative difference between the weekly report data at the time and the data now.
+Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
+Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
+```
+
+```{r weekly-truth-update, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/weekly-data-updates.png")
 ```
@@
 
+```{r distribution-scores-differences, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts)."}
+knitr::include_graphics("../analysis/plots/difference-wis-crowd-ensemble.png")
+```
+
 \clearpage
@@
 caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included.
-Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions.
+“Hub-ensemble” *excludes* all our models, Hub-ensemble-all *includes* all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
+Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
 For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A: mean weighted interval score (WIS) across horizons.
-B: median WIS.
-C: Absolute error of the median forecast.
-D: Standard deviation of the WIS.
-E: Dispersion (higher values mean greater spread of the forecast).
+A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
+C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble.
+E: Dispersion relative to the dispersion of the Hub ensemble.
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
 F: Bias, i.e.
-general tendency to over- or underpredict.
+general (relative) tendency to over- orunderpredict.
 Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Empirical coverage of the 50\\% prediction intervals.
-F: Empirical coverage of the 90\\% prediction intervals"
+G: Absolute error of the median forecast relative to the Hub ensemble.
+H.
+Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
 ```
@@
 In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later.
-This sensitivity shows performance of all models restricted to the period from October 14 2020 until March 1st 2021 where all models were available.
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics across forecast horizons only for the period from October 14th 2020 on where all models were available.
+This sensitivity shows performance of all models restricted to the period from December 14 2020 until March 1st 2021 where all models were available.
+
+```{r}
+caption <- "Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
@@
 \clearpage
+
+## Comparison of crowd forecasts and application baseline
+
+```{r compare-forecasters, fig.cap="Crowd forecasts and baseline shown in the application for a two week horizon.
+Shown are the 90\\% and 50\\% prediction intervals as well as the median (in order of increasing opacity).
+For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons)."}
+knitr::include_graphics("../analysis/plots/comparison-forecast-interals.png")
+```

### 2022-05-12 manuscript/manuscript.tex
update manuscript with review suggestions

@@
 These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, (35)), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, (36)).
+The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update})
 
@@
 At all stages of the evaluation our forecasts were compared to the median ensemble of all \emph{other} models submitted to the German and Polish Forecast Hub (``Hub ensemble'').
-This ``Hub ensemble'' was retrospectively computed and excludes all our models.
-It therefore differs from the official Hub ensemble (here called ``hub-ensemble-realised'') which included crowd forecasts as well as renewal model forecasts.
+This ``Hub ensemble'' was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see details in Section \ref{contributions-hub}, as well as in Table \ref{tab:table-ensemble-versions} and Figure \ref{fig:num-ensemble-members} in the SI).
+What we call ``Hub ensemble'' in this article therefore differs from the ``official Hub ensemble'' (here called ``hub-ensemble-realised'') which included crowd forecasts as well as renewal model forecasts.
 To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e.~we divided the average scores for a given model by the average score achieved by the Hub ensemble on the same set of forecasts (with values \textgreater1 implying worse and values \textless1 implying better performance than the Hub ensemble).
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} \caption{Visualisation of aggregate performance metrics across for forecasts one to four weeks into the future (marked as 1 - 4 on the x axis).
+\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
@@
 Overall, low variance in forecast performance was closely linked with good mean performance (Figures \ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \ref{fig:distribution-scores}, as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
+The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \ref{fig:distribution-scores}), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
 WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
@@
 For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \ref{fig:agg-performance-all}F.
-The convolution model had a strong tendency to under-predict, which steadily decreased for longer forecast horizons.
+The convolution model had a strong tendency to under-predict, with the magnitude of under-prediction steadily decreasing for longer forecast horizons.
 The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction.
@@
 Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
-“Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included.
-Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A: mean weighted interval score (WIS) across horizons.
-B: median WIS.
-C: Absolute error of the median forecast.
-D: Standard deviation of the WIS.
-E: Dispersion (higher values mean greater spread of the forecast).
+B: Distribution of WIS separate by country.
+Black squares indicate median and black circles mean scores.}\label{fig:distribution-scores}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Visualisation of relative aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
+“Hub-ensemble” *excludes* all our models, Hub-ensemble-all *includes* all of our models, “Hub-ensemble-real” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
+A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
+C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
+E: Dispersion relative to the dispersion of the Hub ensemble.
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
 F: Bias, i.e.
-general tendency to over- or underpredict.
+general (relative) tendency to over- orunderpredict.
 Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Empirical coverage of the 50\% prediction intervals.
-F: Empirical coverage of the 90\% prediction intervals}\label{fig:agg-performance-ensemble}
-\end{figure}
-
-\hypertarget{contribution-to-the-forecast-hub}{%
-\subsection{Contribution to the Forecast Hub}\label{contribution-to-the-forecast-hub}}
+G: Absolute error of the median forecast relative to the Hub ensemble.
+H.
+Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-rel}
+\end{figure}
+
+\hypertarget{contributions-hub}{%
+\subsection{Contribution to the Forecast Hub}\label{contributions-hub}}
 
@@
 This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data).
-The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \ref{fig:forecasts-and-truth}A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.
+The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \ref{fig:forecasts-and-truth}A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting which have less of an influence on weekly reporting.
 
@@
 
+\hypertarget{performance-in-germany}{%
+\subsubsection{Performance in Germany}\label{performance-in-germany}}
+
+\begin{figure}[H]
+\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Germany-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
+A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
+WIS is decomposed into its components dispersion, over-prediction and under-prediction.
+C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
+D: Empirical coverage of the 90\% prediction intervals.
+E: Dispersion (same as in panel A, B).
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
+F: Bias, i.e.
+general (relative) tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Absolute error of the median forecast (lower is better).
+H.
+Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Germany}
+\end{figure}
+
+\hypertarget{performance-in-poland}{%
+\subsubsection{Performance in Poland}\label{performance-in-poland}}
+
+\begin{figure}[H]
+\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Poland-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
+A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
+WIS is decomposed into its components dispersion, over-prediction and under-prediction.
+C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
+D: Empirical coverage of the 90\% prediction intervals.
+E: Dispersion (same as in panel A, B).
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
+F: Bias, i.e.
+general (relative) tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Absolute error of the median forecast (lower is better).
+H.
+Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Poland}
+\end{figure}
+
 \hypertarget{performance-across-locations-in-absolute-terms}{%
@@
 \includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-v4} \caption{Visualisation of aggregate performance metrics across locations.
-A: mean weighted interval score (WIS) across horizons.
-B: median WIS.
-C: Absolute error of the median forecast.
-D: Standard deviation of the WIS.
-E: Dispersion (higher values mean further spread out forecast).
+A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
+WIS is decomposed into its components dispersion, over-prediction and under-prediction.
+C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
+D: Empirical coverage of the 90\% prediction intervals.
+E: Dispersion (same as in panel A, B).
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
 F: Bias, i.e.
-general tendency to over- or underpredict.
+general (relative) tendency to over- or underpredict.
 Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Empirical coverage of the 50\% prediction intervals.
-F: Empirical coverage of the 90\% prediction intervals.}\label{fig:performance-locations}
+G: Absolute error of the median forecast (lower is better).
+H.
+Standard deviation of WIS values.}\label{fig:performance-locations}
 \end{figure}
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4} \caption{ Visualisation of aggregate performance metrics across locations relative to the Hub ensemble (excluding our contributions).
-A: mean weighted interval score (WIS) across horizons.
-B: median WIS.
-C: Absolute error of the median forecast.
-D: Standard deviation of the WIS.
-E: Dispersion (higher values mean further spread out forecast).
+\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4} \caption{Visualisation of relative aggregate performance metrics across locations.
+A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
+C, D: Empirical coverage of the 50\% and 90\% prediction intervals.
+E: Dispersion.
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
 F: Bias, i.e.
-general tendency to over- or underpredict.
+general (relative) tendency to over- orunderpredict.
 Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Empirical coverage of the 50\% prediction intervals.
-F: Empirical coverage of the 90\% prediction intervals.}\label{fig:performance-locations-rel}
+G: Absolute error of the median forecast.
+H.
+Standard deviation of WIS values.}\label{fig:performance-locations-rel}
 \end{figure}
@@
 
+\begin{figure}[H]
+\includegraphics[width=1\linewidth,]{../analysis/plots/daily-data-updates} \caption{Visualisation of the absolute difference between the daily report data at the time and the data now.
+In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
+Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:daily-truth-update}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=1\linewidth,]{../analysis/plots/weekly-data-updates} \caption{Visualisation of the relative difference between the weekly report data at the time and the data now.
+Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
+Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:weekly-truth-update}
+\end{figure}
+
 \clearpage
@@
 
+\begin{figure}[H]
+\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} \caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts).}\label{fig:distribution-scores-differences}
+\end{figure}
+
 \clearpage
@@
 \includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included.
-Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions.
+“Hub-ensemble” *excludes* all our models, Hub-ensemble-all *includes* all of our models, “Hub-ensemble-real” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
+Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
 For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A: mean weighted interval score (WIS) across horizons.
-B: median WIS.
-C: Absolute error of the median forecast.
-D: Standard deviation of the WIS.
-E: Dispersion (higher values mean greater spread of the forecast).
+A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
+C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
+E: Dispersion relative to the dispersion of the Hub ensemble.
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
 F: Bias, i.e.
-general tendency to over- or underpredict.
+general (relative) tendency to over- orunderpredict.
 Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Empirical coverage of the 50\% prediction intervals.
-F: Empirical coverage of the 90\% prediction intervals}\label{fig:agg-performance-ensemble-mean}
+G: Absolute error of the median forecast relative to the Hub ensemble.
+H.
+Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-mean}
 \end{figure}
@@
 
+\hypertarget{comparison-of-crowd-forecasts-and-application-baseline}{%
+\subsection{Comparison of crowd forecasts and application baseline}\label{comparison-of-crowd-forecasts-and-application-baseline}}
+
+\begin{figure}[H]
+\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} \caption{Crowd forecasts and baseline shown in the application for a two week horizon.
+Shown are the 90\% and 50\% prediction intervals as well as the median (in order of increasing opacity).
+For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons).}\label{fig:compare-forecasters}
+\end{figure}
+
 \hypertarget{refs}{}
@@
 \CSLLeftMargin{31. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Crowdforecastr: Eliciting crowd forecasts in r shiny. 2020. }
+\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. \href{https://doi.org/10.5281/zenodo.4618519}{Crowdforecastr: Eliciting crowd forecasts in r shiny}. 2020. }
 
@@
 \CSLLeftMargin{40. }
-\CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K, Ellis P, et al. EpiNow2: Estimate real-time case counts and time-varying epidemiological parameters. -. 2020;-(-):--. }
+\CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K, Ellis P, et al.
+\href{https://doi.org/10.5281/zenodo.3957489}{EpiNow2: Estimate real-time case counts and time-varying epidemiological parameters}.
+-.
+2020;-(-):--.
+}
 
@@
 \CSLLeftMargin{47. }
-\CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG. Evaluating epidemic forecasts in an interval format. PLoS Comput Biol. 2021 Feb;17(2):e1008618. }
+\CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG.
+\href{https://doi.org/10.1371/journal.pcbi.1008618}{Evaluating epidemic forecasts in an interval format}.
+PLoS Comput Biol.
+2021 Feb;17(2):e1008618.
+}
 
@@
 \CSLLeftMargin{49. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Scoringutils: Utilities for scoring and assessing predictions. 2020. }
+\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. \href{https://doi.org/10.5281/zenodo.4618017}{Scoringutils: Utilities for scoring and assessing predictions}. 2020. }
 
@@
 \CSLLeftMargin{53. }
-\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J, Munday J, et al. Covidregionaldata: Subnational data for the covid-19 outbreak. -. 2020;-(-):--. }
+\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J, Munday J, et al.
+\href{https://doi.org/10.5281/zenodo.3957539}{Covidregionaldata: Subnational data for the covid-19 outbreak}.
+-.
+2020;-(-):--.
+}
 

### 2022-05-12 manuscript/manuscript-diff.sh

@@ -1,0 +1,3 @@
+latexdiff manuscript/original\ submission/manuscript.tex manuscript/manuscript.tex > manuscript/changes.tex
+
+

### 2022-05-19 analysis/analysis.Rmd
changes for manuscript revision

@@
       geom_hline(yintercept = 1, linetype = "dashed") +
-      expand_limits(y = c(0, 1)) +
       scale_y_continuous(breaks = seq(0, max(scores$value), 0.25))
@@
     scale_y_continuous(labels = scale_fn) + 
-    expand_limits(y = 0) +
     facet_wrap(facet_formula, scales = scalefree) +
     guides(fill = "none", colour = "none")
+
+  if (!rel) {
+    out <- out + 
+      expand_limits(y = 0)
+  }
 
@@
 
-p <- scores[model %in% c("Crowd forecast", "Hub-ensemble")] %>%
-  filter(horizon == 2) %>%
-  select(target_type, model, location_name, forecast_date, interval_score) %>%
-  rename(Model = model) %>%
-  pivot_wider(names_from = Model, values_from = interval_score) %>%
-  ggplot(aes(x = `Crowd forecast` - `Hub-ensemble`)) +
+diff_plot <- function(scores) {
+  p <- scores %>%
+    select(target_type, difference, location_name, forecast_date) %>%
+    ggplot(aes(x = difference)) +
     ggdist::stat_slab(alpha = 1, scale = 1, normalize = "panels") +
+    ggdist::stat_dots(fill = "black", color = "black", dotsize = 0.5) + 
     scale_x_continuous(labels = scale_fn) +
@@
     lemon::scale_x_symmetric(labels = scale_fn) +
-  theme_minimal() +
-  labs(y = "Density", x = "WIS difference Crowd forecast - Hub-ensemble")
-
+    theme_minimal()
 p1 <- p +
@@
 
-p1 + p2
+return(p1 + p2)
+}
+
+p <- scores[model %in% c("Crowd forecast", "Hub-ensemble")] %>%
+  filter(horizon == 2) %>%
+  select(target_type, model, horizon, interval_score, location_name, forecast_date) %>%
+  pivot_wider(names_from = model, values_from = interval_score) %>%
+  mutate(difference = `Crowd forecast` - `Hub-ensemble`) %>%
+  diff_plot()
 
 ggsave(here("analysis", "plots", "difference-wis-crowd-ensemble.png"), 
-       height = 6, width = 9)
+        plot = p,
+       height = 3.5, width = 9) +
+  labs(y = "Density", x = "WIS difference Crowd forecast - Hub-ensemble")
+
+p <- scores[model %in% c("Crowd forecast", "Renewal")] %>%
+  filter(horizon == 2) %>%
+  select(target_type, model, interval_score, location_name, forecast_date) %>%
+  pivot_wider(names_from = model, values_from = interval_score) %>%
+  mutate(difference = `Crowd forecast` - `Renewal`) %>%
+  diff_plot() +
+  labs(y = "Density", x = "WIS difference Crowd forecast - renewal")
+
+ggsave(here("analysis", "plots", "difference-wis-crowd-renewal.png"), plot = p,
+       height = 3.5, width = 9)
+
+# significant results
+significance <- function(scores, 
+                         A = "Crowd forecast", B = "Hub-ensemble", 
+                         horizons = 1:4) {
+  scores[model %in% c(A, B)] %>%
+    select(target_type, horizon, model, interval_score, location_name, forecast_date) %>%
+    filter(horizon %in% horizons) %>%
+    pivot_wider(names_from = model, values_from = interval_score) %>%
+    mutate(difference = .data[[A]] - .data[[B]]) %>%
+    pull(difference) %>%
+    wilcox.test()
+}
+
+significance(scores, B = "Hub-ensemble")
+significance(scores, B = "Renewal",  horizon = 4)
+significance(scores, B = "Convolution")
 

### 2022-05-19 manuscript/manuscript.Rmd
changes for manuscript revision

@@
 These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, @forsal.plRozbieznosciStatystykachKoronawirusa2020), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, @aerzteblattSARSCoV2DiagnostikRKIPasst2020).
-The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \@ref(fig:daily-truth-update) and \@ref(fig:weekly-truth-update))
+The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \@ref(fig:daily-truth-update) and \@ref(fig:weekly-truth-update)).
 
@@
 as $\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )$).
+A comparison of the crowd forecasts against the default baseline shown in the application is displayed in Figure \@ref(fig:compare-forecasters) in the Appendix.
 Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  @ourworldindataCOVID19DataExplorer2020.
 These data included, for example, notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
+From November 26 2020 on we displayed weekly small reports with a visualisation of past forecasts and scores on our website, epiforecasts.io.
 
@@
 Forecasts from all forecasters were then aggregated using an unweighted quantile-wise mean (i.e., the $\alpha$-quantile of the ensemble is given by the mean of all submitted $\alpha$-quantiles).
-On a few occasions, individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation and were excluded from the submission as well as the analysis.
+To avoid issues with users trying out the app and submitting a random forecast, we required that a forecaster needed to make a forecast for at least two targets for a given forecast in order to be included in the crowd forecast ensemble.
+On a few occasions we deleted forecasts that were clearly the result of a user or software error (such as for example forecasts that were zero everywhere).
+
+individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation and were excluded from the submission as well as the analysis.
 
@@
 This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \@ref(fig:agg-performance-all)E) and only showed a small increase in uncertainty across forecast horizons.
+The crowd forecasts prediction intervals were also noticeably narrower than the default baseline shown to forecasters in the application (see Figure \@ref(fig:compare-forecasters)).
+
 In spite of good performance in terms of the absolute error (Figure \@ref(fig:agg-performance-all)G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Figure \@ref(fig:agg-performance-all)C,D and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
@@
 Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
-However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \@ref(fig:performance-locations-rel)A, \@ref(fig:performance-locations-rel)G, \@ref(fig:performance-all-Germany), \@ref(fig:performance-all-Poland)).
+However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \@ref(fig:performance-locations-rel)A, \@ref(fig:performance-locations-rel)G, \@ref(fig:agg-performance-all-Germany), \@ref(fig:agg-performance-all-Poland)).
 
@@
 caption <- "Visualisation of relative aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
-“Hub-ensemble” *excludes* all our models, Hub-ensemble-all *includes* all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
+“Hub-ensemble” \textit{excludes} all our models, Hub-ensemble-all \textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
 A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
@@
 <!-- In general, the median ensemble tended to perform slightly better than the mean ensemble - needs more analysis -->
-General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \@ref(fig:agg-performance-ensemble)B and \@ref(fig:agg-performance-ensemble-mean)B).
+General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \@ref(fig:agg-performance-ensemble-rel)B and \@ref(fig:agg-performance-ensemble-mean)B).
 This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far.
@@
 On the other hand, R shiny facilitated quick development and allowed us to provide our crowd forecasting tooling as an open source R package, meaning that it is available for others to use, for example in settings like early-stage outbreaks where model-based forecasts are not available.
-
-Our work suggests that crowd forecasts and model-based forecasts have different strengths and may be able to complement each other.
+In light of the relatively small number of Hub ensemble models, performance of the Hub ensemble is also difficult to generalise.
+More research is needed to replicate these findings and investigate how crowd forecasts compare against the types of models and model ensembles policy makers use to inform their decisions.
+
+Our work suggests that crowd forecasts and model-based forecasts could have different strengths and may be able to complement each other.
 When choosing a suitable approach for a given task it is important to take into account how the output will be used.
@@
 
-```{r distribution-scores-differences, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts)."}
+```{r distribution-scores-differences, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
 knitr::include_graphics("../analysis/plots/difference-wis-crowd-ensemble.png")
@@
 
-\clearpage
+```{r distribution-scores-differences-renewal, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
+knitr::include_graphics("../analysis/plots/difference-wis-crowd-renewal.png")
+```
+
+\newpage
 
@@
 caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble” *excludes* all our models, Hub-ensemble-all *includes* all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
+“Hub-ensemble” \textit{excludes} all our models, Hub-ensemble-all \textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
 Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.

### 2022-05-19 manuscript/manuscript.tex
changes for manuscript revision

@@
 These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, (35)), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, (36)).
-The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update})
+The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).
 
@@
 The default shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.~as \(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
+A comparison of the crowd forecasts against the default baseline shown in the application is displayed in Figure \ref{fig:compare-forecasters} in the Appendix.
 Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from (39).
 These data included, for example, notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
+From November 26 2020 on we displayed weekly small reports with a visualisation of past forecasts and scores on our website, epiforecasts.io.
 
@@
 Forecasts from all forecasters were then aggregated using an unweighted quantile-wise mean (i.e., the \(\alpha\)-quantile of the ensemble is given by the mean of all submitted \(\alpha\)-quantiles).
-On a few occasions, individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation and were excluded from the submission as well as the analysis.
+To avoid issues with users trying out the app and submitting a random forecast, we required that a forecaster needed to make a forecast for at least two targets for a given forecast in order to be included in the crowd forecast ensemble.
+On a few occasions we deleted forecasts that were clearly the result of a user or software error (such as for example forecasts that were zero everywhere).
+
+individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation and were excluded from the submission as well as the analysis.
 
@@
 This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \ref{fig:agg-performance-all}E) and only showed a small increase in uncertainty across forecast horizons.
+The crowd forecasts prediction intervals were also noticeably narrower than the default baseline shown to forecasters in the application (see Figure \ref{fig:compare-forecasters}).
+
 In spite of good performance in terms of the absolute error (Figure \ref{fig:agg-performance-all}G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36\% and 55\% of all observations with the 50\% and 90\% prediction intervals of all forecasts made at a two week forecast horizon, and only 5\% and 38\% four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
 Despite worse performance in terms of absolute error (Figure \ref{fig:agg-performance-all}G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
+The crowd forecasts, on the other hand, showed a smaller bias than the renewal model, but were overconfident.
 
@@
 Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
-However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figure \ref{fig:performance-locations-rel}A and \ref{fig:performance-locations-rel}G).
+However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \ref{fig:performance-locations-rel}A, \ref{fig:performance-locations-rel}G, \ref{fig:agg-performance-all-Germany}, \ref{fig:agg-performance-all-Poland}).
 
@@
 \includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Visualisation of relative aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
-“Hub-ensemble” *excludes* all our models, Hub-ensemble-all *includes* all of our models, “Hub-ensemble-real” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
+“Hub-ensemble”   extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
 A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
@@
 For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel.
-WIS of the hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and \ref{tab:score-table-ensemble-4}).
+WIS of the Hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and \ref{tab:score-table-ensemble-4}).
 Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons).
@@
 We also considered the impact of our contributions on a version of the Hub ensemble constructed by taking the quantile-wise mean, rather than the median.
-General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \ref{fig:agg-performance-ensemble}B and \ref{fig:agg-performance-ensemble-mean}B).
+General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \ref{fig:agg-performance-ensemble-rel}B and \ref{fig:agg-performance-ensemble-mean}B).
 This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} \caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts).}\label{fig:distribution-scores-differences}
-\end{figure}
-
-\clearpage
+\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} \caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-renewal} \caption{Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences-renewal}
+\end{figure}
+
+\newpage
 
@@
 \includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble” *excludes* all our models, Hub-ensemble-all *includes* all of our models, “Hub-ensemble-real” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
+“Hub-ensemble”     extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
 Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
@@
 In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later.
-This sensitivity shows performance of all models restricted to the period from October 14 2020 until March 1st 2021 where all models were available.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from October 14th 2020 on where all models were available.
+This sensitivity shows performance of all models restricted to the period from December 14 2020 until March 1st 2021 where all models were available.
+
+\begin{figure}[H]
+\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.

### 2022-05-30 analysis/analysis.Rmd
correct Figure

@@
 
-basline_forecasts <- truth_data %>%
-  mutate(difference = c(NA, diff(log(pmax(true_value, 1)))), 
-         target_end_date = as.Date(target_end_date), 
-         id = 1:n()) %>%
+baseline_forecasts <- truth_data %>%
+  mutate(log_true_value = log(pmax(true_value, 1)),
+         difference = c(NA, diff(log_true_value)), 
+         target_end_date = as.Date(target_end_date))
+
+calc_baseline <- function(baseline_forecasts) {
+  baseline_forecasts %>%
+    mutate(id = 1:n()) %>%
     rowwise() %>%
-  mutate(sd = sd(d$difference[pmax(0, id - (4:1))]), 
+    mutate(sd = sd(baseline_forecasts$difference[pmax(0, id - (4:1))]), 
            quantile = list(qs)) %>%
@@
     unique()
+}
+
+baseline_forecasts <- 
+  rbind(
+    calc_baseline(filter(baseline_forecasts, location_name == "Germany" & target_type == "case")), 
+    calc_baseline(filter(baseline_forecasts, location_name == "Germany" & target_type == "death")), 
+    calc_baseline(filter(baseline_forecasts, location_name == "Poland" & target_type == "case")), 
+    calc_baseline(filter(baseline_forecasts, location_name == "Poland" & target_type == "death"))
+  )
 
@@
   unique() %>%
-  rbind(basline_forecasts, fill = TRUE) %>%
+  rbind(baseline_forecasts, fill = TRUE) %>%
   filter(forecast_date %in% forecast_dates$unfiltered) %>%

### 2022-05-30 manuscript/manuscript.Rmd
use PLOS latex template

@@
     - \usepackage{lineno}
+    - \usepackage[T1]{fontenc}
     - \linenumbers
@@
 output: 
-  bookdown::pdf_document2:
-    extra_dependencies: ["float"]
+  rticles::plos_article:
+    extra_dependencies: 
+      caption: null
     keep_tex:  true
@@
 linestretch: 2 
-bibliography:
-  - references.bib
-  - GermanPolishpaper.bib
-csl: vancouver.csl
----
-
-*Nikos I.
-Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy J.
-Quilty, Mark Jit, Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk*
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
-                      out.width = "100%", 
-                      fig.pos = "H", out.extra = "")
-
-library(kableExtra)
-library(magrittr)
-library(knitr)
-```
-
-# Abstract
-
+include-header: 
+  \usepackage[T1]{fontenc}
+author:
+  - name: Nikos I. Bosse
+    email: nikos.bosse@lshtm.ac.uk
+    affiliation: London School of Hygiene & Tropical Medicine
+    corresponding: nikos.bosse@lshtm.ac.uk
+  - name: Sam Abbott
+    email: sam.abbott@lshtm.ac.uk
+    affiliation: 
+      - London School of Hygiene & Tropical Medicine
+  - name: Johannes Bracher
+    email: johannes.bracher@kit.edu
+    affiliation: Karlsruhe Institute of Technology Institute of Economic Theory and Statistics
+  - name: Habakuk Hain
+    email: habakuk.hain@mpinat.mpg.de
+    affiliation: Max Planck Institute for Multidisciplinary Sciences
+  - name: Billy J. Quilty
+    email: Billy.Quilty@lshtm.ac.uk
+    affiliation: London School of Hygiene & Tropical Medicine
+  - name: Mark Jit
+    email: Mark.Jit@lshtm.ac.uk
+    affiliation: London School of Hygiene & Tropical Medicine
+  - name: Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group
+    email: cmmid@lshtm.ac.uk
+    affiliation: London School of Hygiene & Tropical Medicine
+  - name: Edwin van Leeuwen
+    email: Edwin.VanLeeuwen@phe.gov.uk
+    affiliation:
+      - UK Health Security Agency
+      - London School of Hygiene & Tropical Medicine
+  - name: Anne Cori
+    email: a.cori@imperial.ac.uk
+    affiliation: 
+      - Imperial College London
+  - name: Sebastian Funk
+    email: sebastian.funk@lshtm.ac.uk
+    affiliation: London School of Hygiene & Tropical Medicine
+address:
+  - code: London School of Hygiene & Tropical Medicine
+    address: London School of Hygiene & Tropical Medicine, Keppel Street, London WC1E7HT, United Kingdom
+  - code: Karlsruhe Institute of Technology Institute of Economic Theory and Statistics
+    address: Karlsruhe Institute of Technology - Institute of Economic Theory and Statistics, Post Box 6980, 76049 Karlsruhe, Germany
+  - code: Max Planck Institute for Multidisciplinary Sciences
+    address: Max Planck Institute for Multidisciplinary Sciences, Am Faßberg 11, 37077 Göttingen, Germany
+  - code: UK Health Security Agency
+    address: UK Health Security Agency, London NW9 5EQ, United Kingdom
+  - code: Imperial College London
+    address: Imperial College London, Norfolk Place, London W2 1PG, United Kingdom
+
+abstract: |
   Forecasts based on epidemiological modelling have played an important role in shaping public policy throughout the COVID-19 pandemic.
@@
 
-# Author summary
-
+author_summary: |
   Mathematical models of COVID-19 have played a key role in informing governments across the world.
@@
 To investigate what modelling is able to add beyond the subjective opinion of the researcher alone, we compared human forecasts with model-based predictions of COVID-19 cases and deaths submitted to the so-called German/Polish Forecast Hub (which collates a variety of models from a range of teams).
+|
   We found that our human forecasts consistently outperformed an aggregate of all available model-based forecasts when predicting cases, but not when predicting deaths.
@@
 This potentially has very relevant policy implications, as agencies informing policy-makers could benefit from routinely eliciting human forecasts in addition to model-based predictions to inform policies.
+
+bibliography:
+  - references.bib
+  - GermanPolishpaper.bib
+csl: plos.csl
+---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
+                      out.width = "100%", 
+                      fig.pos = "H", out.extra = "")
+
+library(kableExtra)
+library(magrittr)
+library(knitr)
+```
 
@@
 These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, @forsal.plRozbieznosciStatystykachKoronawirusa2020), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, @aerzteblattSARSCoV2DiagnostikRKIPasst2020).
-The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \@ref(fig:daily-truth-update) and \@ref(fig:weekly-truth-update)).
+The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).
 
@@
 To make a forecast in the application participants could select a predictive distribution (with the default being log-normal) to represent the probability that the forecasted quantity took certain values.
-Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in Figure \@ref(fig:screenshot) in the SI).
+Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in Figure \ref{fig:screenshot} in the SI).
 The default shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.
 as $\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )$).
-A comparison of the crowd forecasts against the default baseline shown in the application is displayed in Figure \@ref(fig:compare-forecasters) in the Appendix.
+A comparison of the crowd forecasts against the default baseline shown in the application is displayed in Figure \ref{fig:compare-forecasters} in the Appendix.
 Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  @ourworldindataCOVID19DataExplorer2020.
@@
 The study was approved by the Observational / Interventions Research Ethics Committee at the London School of Hygiene & Tropical Medicine, LSHTM Ethics Reference: 22290.
+Formal consent from participants was taken in written form through the web application.
 
@@
 To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available.
-To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see Section \@ref(sensitivity-analysis) in the SI).
+To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see Section \ref{sensitivity-analysis} in the SI).
 Results remained broadly unchanged.
@@
 how many observed values fall inside all 50% prediction intervals).
-Scoring metrics are explained in more detail in Table \@ref(tab:scoring-metrics) in the SI.
+Scoring metrics are explained in more detail in Table \ref{tab:scoring-metrics} in the SI.
 All scores were calculated using the `scoringutils` R package [@scoringutils].
@@
 At all stages of the evaluation our forecasts were compared to the median ensemble of all *other* models submitted to the German and Polish Forecast Hub ("Hub ensemble").
-This "Hub ensemble" was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see details in Section \@ref(contributions-hub), as well as in Table \@ref(tab:table-ensemble-versions) and Figure \@ref(fig:num-ensemble-members) in the SI).
+This "Hub ensemble" was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see details in Section \ref{contributions-hub}, as well as in Table \ref{tab:table-ensemble-versions} and Figure \ref{fig:num-ensemble-members} in the SI).
 What we call "Hub ensemble" in this article therefore differs from the "official Hub ensemble" (here called "hub-ensemble-realised") which included crowd forecasts as well as renewal model forecasts.
@@
 ```{r}
-caption <- "A, C: Visualisation of 50\\% prediction intervals of two week ahead forecasts against the reported values.
+caption <- "Two week ahead forecasts and corresponding scores.
+A, C: Visualisation of 50\\% prediction intervals of two week ahead forecasts against the reported values.
 Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
@@
 
-For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure \@ref(fig:performance-locations-rel)A).
-For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \@ref(tab:score-table-2)).
-Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Figure \@ref(fig:distribution-scores)).
-Overall, low variance in forecast performance was closely linked with good mean performance (Figures \@ref(fig:agg-performance-all)H and and \@ref(fig:agg-performance-all)A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores)), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
+For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \ref{fig:agg-performance-all}A) and locations (Figure \ref{fig:performance-locations-rel}A).
+For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \ref{tab:score-table-2}).
+Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Figure \ref{fig:distribution-scores}).
+Overall, low variance in forecast performance was closely linked with good mean performance (Figures \ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
+The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \ref{fig:distribution-scores}), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
 WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
@@
 To varying degrees, all forecasts exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened.
-For example, all forecasts failed to predict the change in trend from increase to decrease that happened in November in Germany and severely overshot reported cases (Figure \@ref(fig:forecasts-and-truth)A).
+For example, all forecasts failed to predict the change in trend from increase to decrease that happened in November in Germany and severely overshot reported cases (Figure \ref{fig:forecasts-and-truth}A).
 This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past of observations.
@@
 All forecasting approaches, including the Hub ensemble, were overconfident, i.e.
-they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
+they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
 Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts.
-This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \@ref(fig:agg-performance-all)E) and only showed a small increase in uncertainty across forecast horizons.
-The crowd forecasts prediction intervals were also noticeably narrower than the default baseline shown to forecasters in the application (see Figure \@ref(fig:compare-forecasters)).
-
-In spite of good performance in terms of the absolute error (Figure \@ref(fig:agg-performance-all)G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Figure \@ref(fig:agg-performance-all)C,D and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
-Despite worse performance in terms of absolute error (Figure \@ref(fig:agg-performance-all)G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
+This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \ref{fig:agg-performance-all}E) and only showed a small increase in uncertainty across forecast horizons.
+The crowd forecasts prediction intervals were also noticeably narrower than the default baseline shown to forecasters in the application (see Figure \ref{fig:compare-forecasters}).
+
+In spite of good performance in terms of the absolute error (Figure \ref{fig:agg-performance-all}G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
+Despite worse performance in terms of absolute error (Figure \ref{fig:agg-performance-all}G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
 The crowd forecasts, on the other hand, showed a smaller bias than the renewal model, but were overconfident.
@@
 The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons.
-The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \@ref(fig:agg-performance-all)F).
-Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \@ref(fig:agg-performance-all)A and \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
-
-Generally, trends in overall performance were broadly similar across locations (Figures \@ref(fig:performance-locations) and \@ref(fig:performance-locations-rel)).
+The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \ref{fig:agg-performance-all}F).
+Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2) and \ref{tab:score-table-4}).
+
+Generally, trends in overall performance were broadly similar across locations (Figures \ref{fig:performance-locations) and \ref{fig:performance-locations-rel}).
 Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
-However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \@ref(fig:performance-locations-rel)A, \@ref(fig:performance-locations-rel)G, \@ref(fig:agg-performance-all-Germany), \@ref(fig:agg-performance-all-Poland)).
+However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \ref{fig:performance-locations-rel}A, \ref{fig:performance-locations-rel}G, \ref{fig:agg-performance-all-Germany}, \ref{fig:agg-performance-all-Poland}).
 
@@
 
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B).
+For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure \ref{fig:agg-performance-all}B, Figure \ref{fig:performance-locations}B).
 Relative WIS values for the models two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1 (Hub ensemble) and 1.79 (renewal model).
-The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B), and also better than the convolution model three and four weeks ahead.
+The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \ref{fig:agg-performance-all}B, Figure \ref{fig:performance-locations}B), and also better than the convolution model three and four weeks ahead.
 Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate $R_t$ trace from deaths, does not use the available information efficiently.
-The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \@ref(fig:agg-performance-all)B, Table \@ref(tab:score-table-4)).
+The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \ref{fig:agg-performance-all}B, Table \ref{tab:score-table-4}).
 
@@
 The Hub ensemble had the greatest coverage, with empirical coverage of the 50% and 90% prediction intervals exceeding 50%, and 90%, respectively, across all forecast horizons.
-Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
+Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
 As for cases, the crowd forecast tended to have the narrowest prediction intervals and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
@@
 
-For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \@ref(fig:agg-performance-all)F.
+For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \ref{fig:agg-performance-all}F.
 The convolution model had a strong tendency to under-predict, with the magnitude of under-prediction steadily decreasing for longer forecast horizons.
 The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction.
-For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \@ref(fig:agg-performance-all)A, \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2), \@ref(tab:score-table-4)).
-
-```{r}
-caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
+For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \ref{fig:agg-performance-all}A, \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2}, \ref{tab:score-table-4}).
+
+```{r}
+caption <- "Distribution of scores.
+A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
 Points denote single forecasts scores, while the shaded area shows an estimated probability density.
@@
 ```{r}
-caption <- "Visualisation of relative aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
+caption <- "Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.
 “Hub-ensemble” \textit{excludes} all our models, Hub-ensemble-all \textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
@@
 Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
-An overview of all models and ensemble versions is shown in Table \@ref(tab:table-ensemble-versions) in the SI.
+An overview of all models and ensemble versions is shown in Table \ref{tab:table-ensemble-versions) in the SI.
 
 For cases, our contributions (compared to the Hub ensemble without our contributions) consistently improved performance across all forecasting horizons (rel.
-WIS 0.9 two weeks ahead, Table \@ref(tab:score-table-ensemble-2)).
+WIS 0.9 two weeks ahead, Table \ref{tab:score-table-ensemble-2}).
 Contributions from the crowd forecasts alone also improved performance of the Hub ensemble across all forecast horizons, while contributions from the renewal model had a negative effect for longer horizons (rel.
@@
 The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model have improved performance (Table \@ref(tab:score-table-ensemble-4)).
+Only for predictions four weeks ahead would removing the renewal model have improved performance (Table \ref{tab:score-table-ensemble-4}).
 The realised ensemble performed comparably to the crowd forecasts for predictions one to two weeks ahead, and worse for greater forecast horizons.
@@
 For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel.
-WIS of the Hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \@ref(tab:score-table-ensemble-2) and \@ref(tab:score-table-ensemble-4)).
+WIS of the Hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and \ref{tab:score-table-ensemble-4}).
 Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons).
-This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \@ref(fig:agg-performance-all)) and especially worse for longer horizons.
+This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \ref{fig:agg-performance-all}) and especially worse for longer horizons.
 
@@
 <!-- In general, the median ensemble tended to perform slightly better than the mean ensemble - needs more analysis -->
-General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \@ref(fig:agg-performance-ensemble-rel)B and \@ref(fig:agg-performance-ensemble-mean)B).
+General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \ref{fig:agg-performance-ensemble-rel}B and \ref{fig:agg-performance-ensemble-mean}B).
 This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far.
@@
 This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data).
-The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \@ref(fig:forecasts-and-truth)A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting which have less of an influence on weekly reporting.
+The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \ref{fig:forecasts-and-truth}A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting which have less of an influence on weekly reporting.
 
@@
   kableExtra::column_spec(1, width = "2.5cm") %>%
-  kableExtra::column_spec(2, width = "13.0cm") %>%
+  kableExtra::column_spec(2, width = "9.3cm") %>%
   kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))
@@
 
-## Further details on the semi-mechanistic forecasting models
+## Text S1. Further details on the semi-mechanistic forecasting models
 
@@
   kableExtra::column_spec(1, width = "4.5cm") %>%
-  kableExtra::column_spec(2, width = "11.0cm") %>%
+  kableExtra::column_spec(2, width = "7.3cm") %>%
   kableExtra::kable_styling(latex_options = c("striped", "repeat_header")) 

### 2022-05-30 manuscript/manuscript.tex
use PLOS latex template

@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-]{article}
+% Template for PLoS
+% Version 3.5 March 2018
+%
+% % % % % % % % % % % % % % % % % % % % % %
+%
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended
+% to minimize problems and delays during our production
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% Once your paper is accepted for publication,
+% PLEASE REMOVE ALL TRACKED CHANGES in this file
+% and leave only the final text of your manuscript.
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file.
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+%
+% Do not include text that is not math in the math environment.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column.
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{setspace}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
+\usepackage[utf8x]{inputenc}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+% \usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace}
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+% \bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
 \makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
+\renewcommand{\@biblabel}[1]{\quad#1.}
 \makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Comparing human and model-based forecasts of COVID-19 in Germany and Poland},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+%\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+%\setlength{\headheight}{27.023pt}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\today}
+
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
+
+% tightlist command for lists without linebreak
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
+
+% Pandoc citation processing
 \newlength{\cslhangindent}
@@
 \setlength{\cslentryspacingunit}{\parskip}
+% for Pandoc 2.8 to 2.10.1
+\newenvironment{cslreferences}%
+  {}%
+  {\par}
+% For Pandoc 2.11+
 \newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
 \usepackage{lineno}
+\usepackage[T1]{fontenc}
 \linenumbers
 \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-\usepackage{float}
+\usepackage{caption}
 \usepackage{booktabs}
@@
 \usepackage{wrapfig}
+\usepackage{float}
 \usepackage{colortbl}
@@
 \usepackage{xcolor}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-
-\title{Comparing human and model-based forecasts of COVID-19 in Germany and Poland}
-\author{}
-\date{\vspace{-2.5em}}
+
+\usepackage{forarray}
+\usepackage{xstring}
+\newcommand{\getIndex}[2]{
+  \ForEach{,}{\IfEq{#1}{\thislevelitem}{\number\thislevelcount\ExitForEach}{}}{#2}
+}
+
+\setcounter{secnumdepth}{0}
+
+\newcommand{\getAff}[1]{
+  \getIndex{#1}{London School of Hygiene \& Tropical Medicine,Karlsruhe
+Institute of Technology Institute of Economic Theory and Statistics,Max
+Planck Institute for Multidisciplinary Sciences,UK Health Security
+Agency,Imperial College London}
+}
 
 \begin{document}
-\maketitle
-
-\setstretch{2}
-\emph{Nikos I.
-Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy J.
-Quilty, Mark Jit, Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk}
-
-\hypertarget{abstract}{%
-\section{Abstract}\label{abstract}}
-
-Forecasts based on epidemiological modelling have played an important role in shaping public policy throughout the COVID-19 pandemic.
-This modelling combines knowledge about infectious disease dynamics with the subjective opinion of the researcher who develops and refines the model and often also adjusts model outputs.
-Developing a forecast model is difficult, resource- and time-consuming.
-It is therefore worth asking what modelling is able to add beyond the subjective opinion of the researcher alone.
-To investigate this, we analysed different real-time forecasts of cases of and deaths from COVID-19 in Germany and Poland over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
-We compared crowd forecasts elicited from researchers and volunteers, against a) forecasts from two semi-mechanistic models based on common epidemiological assumptions and b) the ensemble of all other models submitted to the Forecast Hub.
-We found crowd forecasts, despite being overconfident, to outperform all other methods across all forecast horizons when forecasting cases (weighted interval score relative to the Hub ensemble 2 weeks ahead: 0.89).
-Forecasts based on computational models performed comparably better when predicting deaths (rel.
-WIS 1.26), suggesting that epidemiological modelling and human judgement can complement each other in important ways.
-
-\hypertarget{author-summary}{%
-\section{Author summary}\label{author-summary}}
-
-Mathematical models of COVID-19 have played a key role in informing governments across the world.
-While mathematical models are informed by our knowledge of infectious disease dynamics, they are ultimately developed and iteratively adjusted by the researchers and shaped by their subjective opinions.
-To investigate what modelling is able to add beyond the subjective opinion of the researcher alone, we compared human forecasts with model-based predictions of COVID-19 cases and deaths submitted to the so-called German/Polish Forecast Hub (which collates a variety of models from a range of teams).\\
-We found that our human forecasts consistently outperformed an aggregate of all available model-based forecasts when predicting cases, but not when predicting deaths.
-Our findings suggest that human insight may be most valuable when forecasting highly uncertain quantities, which depend on many factors that are hard to model using equations, while mathematical models may be most useful in settings like predicting deaths, where leading indicators with a clear connection to the target variable are available.
-This potentially has very relevant policy implications, as agencies informing policy-makers could benefit from routinely eliciting human forecasts in addition to model-based predictions to inform policies.
-
+\vspace*{0.2in}
+
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{Comparing human and model-based forecasts of COVID-19 in
+Germany and
+Poland} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Nikos I. Bosse\textsuperscript{\getAff{London School of Hygiene \&
+Tropical Medicine}}\textsuperscript{*},
+Sam Abbott\textsuperscript{\getAff{London School of Hygiene \& Tropical
+Medicine}},
+Johannes Bracher\textsuperscript{\getAff{Karlsruhe Institute of
+Technology Institute of Economic Theory and Statistics}},
+Habakuk Hain\textsuperscript{\getAff{Max Planck Institute for
+Multidisciplinary Sciences}},
+Billy J. Quilty\textsuperscript{\getAff{London School of Hygiene \&
+Tropical Medicine}},
+Mark Jit\textsuperscript{\getAff{London School of Hygiene \& Tropical
+Medicine}},
+Centre for the Mathematical Modelling of Infectious Diseases COVID-19
+Working Group\textsuperscript{\getAff{London School of Hygiene \&
+Tropical Medicine}},
+Edwin van Leeuwen\textsuperscript{\getAff{UK Health Security
+Agency}, \getAff{London School of Hygiene \& Tropical Medicine}},
+Anne Cori\textsuperscript{\getAff{Imperial College London}},
+Sebastian Funk\textsuperscript{\getAff{London School of Hygiene \&
+Tropical Medicine}}\\
+\bigskip
+\textbf{\getAff{London School of Hygiene \& Tropical Medicine}}London
+School of Hygiene \& Tropical Medicine, Keppel Street, London WC1E7HT,
+United Kingdom\\
+\textbf{\getAff{Karlsruhe Institute of Technology Institute of Economic
+Theory and Statistics}}Karlsruhe Institute of Technology - Institute of
+Economic Theory and Statistics, Post Box 6980, 76049 Karlsruhe,
+Germany\\
+\textbf{\getAff{Max Planck Institute for Multidisciplinary Sciences}}Max
+Planck Institute for Multidisciplinary Sciences, Am Faßberg 11, 37077
+Göttingen, Germany\\
+\textbf{\getAff{UK Health Security Agency}}UK Health Security Agency,
+London NW9 5EQ, United Kingdom\\
+\textbf{\getAff{Imperial College London}}Imperial College London,
+Norfolk Place, London W2 1PG, United Kingdom\\
+\bigskip
+* Corresponding author: nikos.bosse@lshtm.ac.uk\\
+\end{flushleft}
+% Please keep the abstract below 300 words
+\section*{Abstract}
+Forecasts based on epidemiological modelling have played an important
+role in shaping public policy throughout the COVID-19 pandemic. This
+modelling combines knowledge about infectious disease dynamics with the
+subjective opinion of the researcher who develops and refines the model
+and often also adjusts model outputs. Developing a forecast model is
+difficult, resource- and time-consuming. It is therefore worth asking
+what modelling is able to add beyond the subjective opinion of the
+researcher alone. To investigate this, we analysed different real-time
+forecasts of cases of and deaths from COVID-19 in Germany and Poland
+over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
+We compared crowd forecasts elicited from researchers and volunteers,
+against a) forecasts from two semi-mechanistic models based on common
+epidemiological assumptions and b) the ensemble of all other models
+submitted to the Forecast Hub. We found crowd forecasts, despite being
+overconfident, to outperform all other methods across all forecast
+horizons when forecasting cases (weighted interval score relative to the
+Hub ensemble 2 weeks ahead: 0.89). Forecasts based on computational
+models performed comparably better when predicting deaths (rel. WIS
+1.26), suggesting that epidemiological modelling and human judgement can
+complement each other in important ways.
+
+% Please keep the Author Summary between 150 and 200 words
+% Use first person. PLOS ONE authors please skip this step.
+% Author Summary not valid for PLOS ONE submissions.
+\section*{Author summary}
+Mathematical models of COVID-19 have played a key role in informing
+governments across the world. While mathematical models are informed by
+our knowledge of infectious disease dynamics, they are ultimately
+developed and iteratively adjusted by the researchers and shaped by
+their subjective opinions. To investigate what modelling is able to add
+beyond the subjective opinion of the researcher alone, we compared human
+forecasts with model-based predictions of COVID-19 cases and deaths
+submitted to the so-called German/Polish Forecast Hub (which collates a
+variety of models from a range of teams). \textbar{} We found that our
+human forecasts consistently outperformed an aggregate of all available
+model-based forecasts when predicting cases, but not when predicting
+deaths. Our findings suggest that human insight may be most valuable
+when forecasting highly uncertain quantities, which depend on many
+factors that are hard to model using equations, while mathematical
+models may be most useful in settings like predicting deaths, where
+leading indicators with a clear connection to the target variable are
+available. This potentially has very relevant policy implications, as
+agencies informing policy-makers could benefit from routinely eliciting
+human forecasts in addition to model-based predictions to inform
+policies.
+
+\linenumbers
+
+% Use "Eq" instead of "Equation" for equation citations.
 \hypertarget{introduction}{%
@@
 
-Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza (e.g.
-1,2--4), dengue fever (e.g.
-5,6,7), ebola (e.g.
-8,9), chikungunya (e.g.
-10,11) and now COVID-19 (e.g.
-12,13--17).
-Applications of epidemiological models differ in the way they make statements about the future.
-Forecasts aim to predict the future as it will occur, while scenario modelling and projections aim to represent what the future could look like under certain scenario assumptions or if conditions stayed the same as they were in the past.
-Forecasts can be judged by comparing them against observed data.
-Since it is much harder to fairly assess the accuracy and usefulness of projections and scenario modelling in the same way, this work focuses on forecasts, which represent only a subset of all epidemiological modelling.
-
-Since March 2020, forecasts of COVID-19 from multiple teams have been collected, aggregated and compared by Forecast Hubs such as the US Forecast Hub (13,14), the German and Polish Forecast Hub (15,16) and the European Forecast Hub (17).
-Often, different individual forecasts are combined into a single forecast, e.g.~by taking the mean or median of all forecasts.
-These ensemble forecasts usually tend to perform better and more consistently than individual forecasts (see e.g.
-(6); (18)).
-
-Individual computational models usually rely to varying degrees on mechanistic assumptions about infectious disease dynamics (such as SIR-type compartmental models that aim to represent how individuals move from being susceptible to infected and then recovered or dead).
-Some are more statistical in nature (such as time series models that detect statistical patterns without explicitly modelling disease dynamics).
-How exactly such a mathematical or computational model is constructed and which assumptions are made depends on subjective opinion and judgement of the researcher who develops and refines the model.
-Models are commonly adjusted and improved based on whether the model output looks plausible to the researchers involved.
-
-The process of model construction and refinement is laborious and time-consuming, and it is therefore worth asking what modelling can add beyond the subjective judgment of the researcher alone.
-In this work, we ask this question specifically in the context of predictive performance, and set aside other advantages of epidemiological modelling (such as reproducibility or the ability to obtain a deeper fundamental understanding of how diseases spread).
-One natural way to do this is to compare the predictive performance of forecasts based on computational models (``model-based forecasts'') against forecasts made by individual humans without explicit use of a computer model (``direct human forecasts'') or a combination of multiple such forecasts (``crowd forecasts'').
-
-Previous work has examined such direct human forecasts in various contexts, such as geopolitics (19,20), meta-science (21,22), sports (23) and epidemiology (11,24,25).
-Several prediction platforms (26--28) and prediction markets (29) have been created to collate expert and non-expert predictions.
-However, with the notable exception of (11), these forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) prediction formats.
-Direct human forecasts may be able to take into account insights and relationships between variables which are hard to specify using epidemiological models.
-However, it is not entirely clear in which situations human forecasts perform well or badly.
-For example, (11) found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available.
-However, humans tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown in these regions at the time.
-
-In this study, we analyse the performance of direct human forecasts relative to model-based forecasts and discuss the added benefit of epidemiological modelling over human judgement alone.
-As a case study, we use different forecasts, involving varying degrees of human intervention, which we submitted in real time to the German and Polish Forecast Hub.
-In contrast to (11) we elicited not only point predictions, but full predictive distributions (``probabilistic forecasts'', see e.g.
-(30)) from participants.
-This allows us to compare not only predictive accuracy, but also how well human forecasters and model-based forecasts were able to quantify forecast uncertainty.
+Infectious disease modelling has a long tradition and has helped inform
+public health decisions both through scenario modelling, as well as
+actual forecasts of (among others) influenza {[}e.g. 1,2--4{]}, dengue
+fever {[}e.g. 5,6,7{]}, ebola {[}e.g. 8,9{]}, chikungunya {[}e.g.
+10,11{]} and now COVID-19 {[}e.g. 12,13--17{]}. Applications of
+epidemiological models differ in the way they make statements about the
+future. Forecasts aim to predict the future as it will occur, while
+scenario modelling and projections aim to represent what the future
+could look like under certain scenario assumptions or if conditions
+stayed the same as they were in the past. Forecasts can be judged by
+comparing them against observed data. Since it is much harder to fairly
+assess the accuracy and usefulness of projections and scenario modelling
+in the same way, this work focuses on forecasts, which represent only a
+subset of all epidemiological modelling.
+
+Since March 2020, forecasts of COVID-19 from multiple teams have been
+collected, aggregated and compared by Forecast Hubs such as the US
+Forecast Hub {[}13,14{]}, the German and Polish Forecast Hub {[}15,16{]}
+and the European Forecast Hub {[}17{]}. Often, different individual
+forecasts are combined into a single forecast, e.g.~by taking the mean
+or median of all forecasts. These ensemble forecasts usually tend to
+perform better and more consistently than individual forecasts (see e.g.
+{[}6{]}; {[}18{]}).
+
+Individual computational models usually rely to varying degrees on
+mechanistic assumptions about infectious disease dynamics (such as
+SIR-type compartmental models that aim to represent how individuals move
+from being susceptible to infected and then recovered or dead). Some are
+more statistical in nature (such as time series models that detect
+statistical patterns without explicitly modelling disease dynamics). How
+exactly such a mathematical or computational model is constructed and
+which assumptions are made depends on subjective opinion and judgement
+of the researcher who develops and refines the model. Models are
+commonly adjusted and improved based on whether the model output looks
+plausible to the researchers involved.
+
+The process of model construction and refinement is laborious and
+time-consuming, and it is therefore worth asking what modelling can add
+beyond the subjective judgment of the researcher alone. In this work, we
+ask this question specifically in the context of predictive performance,
+and set aside other advantages of epidemiological modelling (such as
+reproducibility or the ability to obtain a deeper fundamental
+understanding of how diseases spread). One natural way to do this is to
+compare the predictive performance of forecasts based on computational
+models (``model-based forecasts'') against forecasts made by individual
+humans without explicit use of a computer model (``direct human
+forecasts'') or a combination of multiple such forecasts (``crowd
+forecasts'').
+
+Previous work has examined such direct human forecasts in various
+contexts, such as geopolitics {[}19,20{]}, meta-science {[}21,22{]},
+sports {[}23{]} and epidemiology {[}11,24,25{]}. Several prediction
+platforms {[}26--28{]} and prediction markets {[}29{]} have been created
+to collate expert and non-expert predictions. However, with the notable
+exception of {[}11{]}, these forecasts were not designed to be evaluated
+alongside model-based forecasts and usually follow their own (often
+binary) prediction formats. Direct human forecasts may be able to take
+into account insights and relationships between variables which are hard
+to specify using epidemiological models. However, it is not entirely
+clear in which situations human forecasts perform well or badly. For
+example, {[}11{]} found that humans could outperform computer models at
+predicting the 2014/15 and 2015/16 flu season in the US, a setting where
+the disease was well known and information about previous seasons was
+available. However, humans tended to do slightly worse at predicting the
+2014/15 outbreak of chikungunya in the Americas, a disease previously
+largely unobserved and unknown in these regions at the time.
+
+In this study, we analyse the performance of direct human forecasts
+relative to model-based forecasts and discuss the added benefit of
+epidemiological modelling over human judgement alone. As a case study,
+we use different forecasts, involving varying degrees of human
+intervention, which we submitted in real time to the German and Polish
+Forecast Hub. In contrast to {[}11{]} we elicited not only point
+predictions, but full predictive distributions (``probabilistic
+forecasts'', see e.g. {[}30{]}) from participants. This allows us to
+compare not only predictive accuracy, but also how well human
+forecasters and model-based forecasts were able to quantify forecast
+uncertainty.
 
@@
 
-We created and submitted the following forecasts to the German and Polish Forecast Hub: 1) a direct human forecast (henceforth called ``crowd forecast''), elicited from participants through a web application (31) and 2) two semi-mechanistic model-based forecasts (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology.
-While the two semi-mechanistic forecasts were necessarily shaped by our implicit assumptions and decisions, they were designed such as to minimise the amount of human intervention involved.
-For example, we refrained from adjusting model outputs or refining the models based on past performance.
-Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (15,16).
-All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (32).
-This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub.
-Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the German and Polish Forecast Hub.
+We created and submitted the following forecasts to the German and
+Polish Forecast Hub: 1) a direct human forecast (henceforth called
+``crowd forecast''), elicited from participants through a web
+application {[}31{]} and 2) two semi-mechanistic model-based forecasts
+(``renewal model'' and ``convolution model'') informed by basic
+assumptions about COVID-19 epidemiology. While the two semi-mechanistic
+forecasts were necessarily shaped by our implicit assumptions and
+decisions, they were designed such as to minimise the amount of human
+intervention involved. For example, we refrained from adjusting model
+outputs or refining the models based on past performance. Forecasts were
+created in real time over a period of 21 weeks from October 12th 2020
+until March 1st 2021 and submitted to the German and Polish Forecast hub
+{[}15,16{]}. All code and tools necessary to generate the forecasts and
+make a forecast submission are available in the
+\texttt{covid.german.forecasts} R package {[}32{]}. This repository also
+contains a record of all forecasts submitted to the German and Polish
+Forecast Hub. Forecasts were evaluated using a variety of scoring
+metrics and compared among each other and against an ensemble of all
+other models submitted to the German and Polish Forecast Hub.
 
 \hypertarget{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}{%
-\subsection{Forecast targets and interaction with the German and Polish Forecast Hub}\label{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}}
-
-The German and Polish Forecast Hub (now mostly merged into the (17)) elicits predictions for various COVID-19 related forecast targets from different research groups every week.
-Forecasts had to be made every Monday (with submissions allowed until Tuesday 3pm) and were permitted to use any data that was available by Monday 11.59pm.
-We submitted forecasts for incident and cumulative weekly reported numbers of cases of and deaths from COVID-19 on a national level in Germany and Poland over a one to four week forecast horizon.
-Forecasts were submitted on Mondays, but weeks were defined as ending on a Saturday (and starting on Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26 days.
-Submissions were required in a quantile-based format with 23 quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10, 0.15, \ldots, 0.95, 0.975, 0.99.
-Forecasts submitted to the Forecast Hub were combined into different ensembles every week, with the median ensemble (i.e., the \(\alpha\)-quantile of the ensemble is given by the median of all submitted \(\alpha\)-quantiles) being the default ensemble shown on all official Forecast hub visualisations (\url{https://kitmetricslab.github.io/forecasthub/forecast}).
-
-Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish Forecast hub.
-Until December 14th, 2020, these data were sourced from the European Centre for Disease Control (33).
-After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (34).
-These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, (35)), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, (36)).
-The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).
+\subsection{Forecast targets and interaction with the German and Polish
+Forecast
+Hub}\label{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}}
+
+The German and Polish Forecast Hub (now mostly merged into the {[}17{]})
+elicits predictions for various COVID-19 related forecast targets from
+different research groups every week. Forecasts had to be made every
+Monday (with submissions allowed until Tuesday 3pm) and were permitted
+to use any data that was available by Monday 11.59pm. We submitted
+forecasts for incident and cumulative weekly reported numbers of cases
+of and deaths from COVID-19 on a national level in Germany and Poland
+over a one to four week forecast horizon. Forecasts were submitted on
+Mondays, but weeks were defined as ending on a Saturday (and starting on
+Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26
+days. Submissions were required in a quantile-based format with 23
+quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10,
+0.15, \ldots, 0.95, 0.975, 0.99. Forecasts submitted to the Forecast Hub
+were combined into different ensembles every week, with the median
+ensemble (i.e., the \(\alpha\)-quantile of the ensemble is given by the
+median of all submitted \(\alpha\)-quantiles) being the default ensemble
+shown on all official Forecast hub visualisations
+(https://kitmetricslab.github.io/forecasthub/forecast).
+
+Data on daily reported test positive cases and deaths linked to COVID-19
+were provided by the organisers of the German and Polish Forecast hub.
+Until December 14th, 2020, these data were sourced from the European
+Centre for Disease Control {[}33{]}. After ECDC stopped publishing daily
+data, observations were sourced from the Robert Koch Institute (RKI) and
+the Polish Ministry of Health for the remainder of the submission period
+{[}34{]}. These data are subject to reporting artefacts, (such as for
+example delayed case reporting in Poland on the 24th November,
+{[}35{]}), changes in reporting over time, and variation in testing
+regimes (for example in Germany from the 11th of November on, {[}36{]}).
+The ECDC data as well as the data published by the Polish Ministry of
+Health were also subject to data revisions, although most of them (with
+a notable exception of a data update for October 12 2020 in Germany)
+only affected daily, not weekly data (see Figures
+\ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).
 
@@
 
-Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application (\url{https://cmmid-lshtm.shinyapps.io/crowd-forecast/}).
-Weekly forecasts had to be submitted before Tuesday 12pm every week, but participants were asked to only use any information or data that was already available by Monday night.
-The application was built using the \texttt{shiny} and \texttt{golem} R packages (37,38) and is available in the \texttt{crowdforecastr} R package (31).
-To make a forecast in the application participants could select a predictive distribution (with the default being log-normal) to represent the probability that the forecasted quantity took certain values.
-Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in Figure \ref{fig:screenshot} in the SI).
-The default shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.~as \(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
-A comparison of the crowd forecasts against the default baseline shown in the application is displayed in Figure \ref{fig:compare-forecasters} in the Appendix.
-Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from (39).
-These data included, for example, notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
-From November 26 2020 on we displayed weekly small reports with a visualisation of past forecasts and scores on our website, epiforecasts.io.
-
-Forecasts were stored in a Google Sheet and downloaded, cleaned and processed every week for submission to the Forecast Hub.
-If a forecaster had submitted multiple predictions for a single target, only the latest submission was kept.
-Information on the chosen distribution as well as the parameters for median and width were used to obtain the required set of 23 quantiles from that distribution.
-Forecasts from all forecasters were then aggregated using an unweighted quantile-wise mean (i.e., the \(\alpha\)-quantile of the ensemble is given by the mean of all submitted \(\alpha\)-quantiles).
-To avoid issues with users trying out the app and submitting a random forecast, we required that a forecaster needed to make a forecast for at least two targets for a given forecast in order to be included in the crowd forecast ensemble.
-On a few occasions we deleted forecasts that were clearly the result of a user or software error (such as for example forecasts that were zero everywhere).
-
-individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation and were excluded from the submission as well as the analysis.
-
-Participants were recruited mostly within the Centre of Mathematical Modeling of Infectious Diseases at the London School of Hygiene \& Tropical Medicine, but participants were also invited personally or via social media to submit predictions.
-Depending on whether they had a background in either statistics, forecasting or epidemiology, participants were asked to self-identify as `experts' or `non-experts'.
-
-The study was approved by the Observational / Interventions Research Ethics Committee at the London School of Hygiene \& Tropical Medicine, LSHTM Ethics Reference: 22290.
+Our crowd forecasts were created as an ensemble of forecasts made by
+individual participants every week through a web application
+(https://cmmid-lshtm.shinyapps.io/crowd-forecast/). Weekly forecasts had
+to be submitted before Tuesday 12pm every week, but participants were
+asked to only use any information or data that was already available by
+Monday night. The application was built using the \texttt{shiny} and
+\texttt{golem} R packages {[}37,38{]} and is available in the
+\texttt{crowdforecastr} R package {[}31{]}. To make a forecast in the
+application participants could select a predictive distribution (with
+the default being log-normal) to represent the probability that the
+forecasted quantity took certain values. Median and width of the
+uncertainty could be adjusted by either interacting with a figure
+showing their forecast or providing numerical values (see screenshot in
+Figure \ref{fig:screenshot} in the SI). The default shown was a
+repetition of the last known observation with constant uncertainty
+around it computed as the standard deviation of the last four changes in
+weekly log observed forecasts (i.e.~as
+\(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
+A comparison of the crowd forecasts against the default baseline shown
+in the application is displayed in Figure \ref{fig:compare-forecasters}
+in the Appendix. Our interface also allowed participants to view past
+observations based on the hub data, as well as their forecasts, on a
+logarithmic scale and presented additional contextual COVID-19 data
+sourced from {[}39{]}. These data included, for example, notifications
+of both test positive COVID-19 cases and COVID-19 linked deaths and the
+number of COVID-19 tests conducted over time. From November 26 2020 on
+we displayed weekly small reports with a visualisation of past forecasts
+and scores on our website, epiforecasts.io.
+
+Forecasts were stored in a Google Sheet and downloaded, cleaned and
+processed every week for submission to the Forecast Hub. If a forecaster
+had submitted multiple predictions for a single target, only the latest
+submission was kept. Information on the chosen distribution as well as
+the parameters for median and width were used to obtain the required set
+of 23 quantiles from that distribution. Forecasts from all forecasters
+were then aggregated using an unweighted quantile-wise mean (i.e., the
+\(\alpha\)-quantile of the ensemble is given by the mean of all
+submitted \(\alpha\)-quantiles). To avoid issues with users trying out
+the app and submitting a random forecast, we required that a forecaster
+needed to make a forecast for at least two targets for a given forecast
+in order to be included in the crowd forecast ensemble. On a few
+occasions we deleted forecasts that were clearly the result of a user or
+software error (such as for example forecasts that were zero
+everywhere).
+
+individual forecasts were assessed as clearly erroneous by visual
+inspection and subsequently removed before aggregation and were excluded
+from the submission as well as the analysis.
+
+Participants were recruited mostly within the Centre of Mathematical
+Modeling of Infectious Diseases at the London School of Hygiene \&
+Tropical Medicine, but participants were also invited personally or via
+social media to submit predictions. Depending on whether they had a
+background in either statistics, forecasting or epidemiology,
+participants were asked to self-identify as `experts' or `non-experts'.
+
+The study was approved by the Observational / Interventions Research
+Ethics Committee at the London School of Hygiene \& Tropical Medicine,
+LSHTM Ethics Reference: 22290. Formal consent from participants was
+taken in written form through the web application.
 
@@
 
-We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R package (version 1.3.3) as our model-based forecasts (40).
-The first of these models, here called ``renewal model'', used the renewal equation (41) to predict reported cases and deaths (see details in the SI).
-It estimated the effective reproduction number \(R_t\) (the average number of people each person infected at time t is expected to infect in turn) and modelled future infections as a weighted sum of past infection multiplied by \(R_t\).
-\(R_t\) was assumed to stay constant beyond the forecast date, roughly corresponding to continuing the latest exponential trend in infections.
-On the 9th of November we altered the date when \(R_t\) was assumed to be constant from two weeks prior to the date of the forecast to the forecast date, which we found to yield a more stable \(R_t\) estimate.
-Reported case and death notifications were obtained by convolving predicted infections over data-based delay distributions (40,42--44) to model the time between infection and report date.
-The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately.
-Death forecasts from the renewal model were therefore not informed by past cases.
-One submission of the renewal model on December 28th 2020 was delayed and therefore not included in the official Forecast hub ensemble.
-
-The second model (``convolution model'', see details in SI) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses).
-The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model.
-The convolution model predicted deaths as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
-Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model with a multiplicative day-of-the-week effect (40).
-
-Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (45) with data available up to the 1st of August.
-All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (46) with each location and forecast target being fitted separately.
+We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R
+package (version 1.3.3) as our model-based forecasts {[}40{]}. The first
+of these models, here called ``renewal model'', used the renewal
+equation {[}41{]} to predict reported cases and deaths (see details in
+the SI). It estimated the effective reproduction number \(R_t\) (the
+average number of people each person infected at time t is expected to
+infect in turn) and modelled future infections as a weighted sum of past
+infection multiplied by \(R_t\). \(R_t\) was assumed to stay constant
+beyond the forecast date, roughly corresponding to continuing the latest
+exponential trend in infections. On the 9th of November we altered the
+date when \(R_t\) was assumed to be constant from two weeks prior to the
+date of the forecast to the forecast date, which we found to yield a
+more stable \(R_t\) estimate. Reported case and death notifications were
+obtained by convolving predicted infections over data-based delay
+distributions {[}40,42--44{]} to model the time between infection and
+report date. The renewal model was used to predict cases as well as
+deaths with forecasts being generated for each target separately. Death
+forecasts from the renewal model were therefore not informed by past
+cases. One submission of the renewal model on December 28th 2020 was
+delayed and therefore not included in the official Forecast hub
+ensemble.
+
+The second model (``convolution model'', see details in SI) was only
+used to forecast deaths and was added later, starting December 7th 2020
+(with the first forecast from December 7th suffering from a software bug
+and therefore disregarded in all further analyses). The convolution
+model was submitted, but never included in the official Forecast hub
+ensemble due to concerns that it could be too similar to the renewal
+model. The convolution model predicted deaths as a fraction of infected
+people who would die with some delay, by using a convolution of reported
+cases with a distribution that described the delay from case report to
+death and a scaling factor (the case-fatality ratio). Both the renewal
+and the convolution model used daily observations and assumed a negative
+binomial observation model with a multiplicative day-of-the-week effect
+{[}40{]}.
+
+Line list data used to inform the prior for the delay from symptom onset
+to test positive case report or death in the model-based forecasts was
+sourced from {[}45{]} with data available up to the 1st of August. All
+model fitting was done using Markov-chain Monte Carlo (MCMC) in stan
+{[}46{]} with each location and forecast target being fitted separately.
 
@@
 
-For the main analysis we focused mostly on two week ahead forecasts, as COVID-19 forecasts, especially for cases, were in the past found to have poor predictive performance beyond this horizon (15).
-Forecasts for cases were scored using the full period from October 2020 until March 2021.
-To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available.
-To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see Section \ref{sensitivity-analysis} in the SI).
-Results remained broadly unchanged.
-
-Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (47), the absolute error, relative bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule (48), meaning that in expectation the score is optimised by reporting a predictive distribution that is identical to the true data-generating distribution.
-Forecasters are therefore incentivised to report their true belief about the future.
-The WIS can be understood as a generalisation of the absolute error to quantile-based forecasts (also meaning that smaller values are better) and can be decomposed into three separate penalties: forecast spread (i.e.~uncertainty of forecasts), over-prediction and under-prediction.
-While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts.
-The bias metric (9) we use captures how much probability mass of the forecast was above or below the true value (mapped to values between -1 and 1) and therefore represents a general tendency to over- or under-predict in relative terms.
-A value of -1 implies that all quantiles of the predictive distribution are below the observed value and a value of 1 that all quantiles are above the observed value.
-Empirical coverage is the percentage of observed values that fall inside a given prediction interval (e.g.~how many observed values fall inside all 50\% prediction intervals).
-Scoring metrics are explained in more detail in Table \ref{tab:scoring-metrics} in the SI.
-All scores were calculated using the \texttt{scoringutils} R package (49).
-
-At all stages of the evaluation our forecasts were compared to the median ensemble of all \emph{other} models submitted to the German and Polish Forecast Hub (``Hub ensemble'').
-This ``Hub ensemble'' was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see details in Section \ref{contributions-hub}, as well as in Table \ref{tab:table-ensemble-versions} and Figure \ref{fig:num-ensemble-members} in the SI).
-What we call ``Hub ensemble'' in this article therefore differs from the ``official Hub ensemble'' (here called ``hub-ensemble-realised'') which included crowd forecasts as well as renewal model forecasts.
-To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e.~we divided the average scores for a given model by the average score achieved by the Hub ensemble on the same set of forecasts (with values \textgreater1 implying worse and values \textless1 implying better performance than the Hub ensemble).
-In addition to comparing our forecasts against the hub ensemble excluding our models, we also assessed the impact of our forecasts on the performance of the forecasting hub by recalculating separate versions of the Hub ensemble with only some (or all) of our forecasts included.
-Versions that included either all of our models (``hub-ensemble-with-all'') or only one of them (``hub-ensemble-with-X'') were computed retrospectively.
+For the main analysis we focused mostly on two week ahead forecasts, as
+COVID-19 forecasts, especially for cases, were in the past found to have
+poor predictive performance beyond this horizon {[}15{]}. Forecasts for
+cases were scored using the full period from October 2020 until March
+2021. To ensure comparability between models, all death forecasts were
+scored using only the period from December 14th on, where all models
+including the convolution model were available. To ensure robustness of
+our results we conducted a sensitivity analysis where all forecasts
+(including cases) were scored only over the later period for which all
+forecasts were available (see Section \ref{sensitivity-analysis} in the
+SI). Results remained broadly unchanged.
+
+Forecasts were analysed using the following scoring metrics: The
+weighted interval score (WIS) {[}47{]}, the absolute error, relative
+bias, and empirical coverage of the 50\% and 90\% prediction intervals.
+The WIS is a proper scoring rule {[}48{]}, meaning that in expectation
+the score is optimised by reporting a predictive distribution that is
+identical to the true data-generating distribution. Forecasters are
+therefore incentivised to report their true belief about the future. The
+WIS can be understood as a generalisation of the absolute error to
+quantile-based forecasts (also meaning that smaller values are better)
+and can be decomposed into three separate penalties: forecast spread
+(i.e.~uncertainty of forecasts), over-prediction and under-prediction.
+While the over- and under-prediction components of the WIS capture the
+amount of over-prediction and under-prediction in absolute terms, we
+also look at a relative tendency to make biased forecasts. The bias
+metric {[}9{]} we use captures how much probability mass of the forecast
+was above or below the true value (mapped to values between -1 and 1)
+and therefore represents a general tendency to over- or under-predict in
+relative terms. A value of -1 implies that all quantiles of the
+predictive distribution are below the observed value and a value of 1
+that all quantiles are above the observed value. Empirical coverage is
+the percentage of observed values that fall inside a given prediction
+interval (e.g.~how many observed values fall inside all 50\% prediction
+intervals). Scoring metrics are explained in more detail in Table
+\ref{tab:scoring-metrics} in the SI. All scores were calculated using
+the \texttt{scoringutils} R package {[}49{]}.
+
+At all stages of the evaluation our forecasts were compared to the
+median ensemble of all \emph{other} models submitted to the German and
+Polish Forecast Hub (``Hub ensemble''). This ``Hub ensemble'' was
+retrospectively computed and excludes all our models, leaving on average
+five ensemble member models (see details in Section
+\ref{contributions-hub}, as well as in Table
+\ref{tab:table-ensemble-versions} and Figure
+\ref{fig:num-ensemble-members} in the SI). What we call ``Hub ensemble''
+in this article therefore differs from the ``official Hub ensemble''
+(here called ``hub-ensemble-realised'') which included crowd forecasts
+as well as renewal model forecasts. To enhance interpretability of
+scores we mainly report WIS relative to the Hub ensemble in the main
+text, i.e.~we divided the average scores for a given model by the
+average score achieved by the Hub ensemble on the same set of forecasts
+(with values \textgreater1 implying worse and values \textless1 implying
+better performance than the Hub ensemble). In addition to comparing our
+forecasts against the hub ensemble excluding our models, we also
+assessed the impact of our forecasts on the performance of the
+forecasting hub by recalculating separate versions of the Hub ensemble
+with only some (or all) of our forecasts included. Versions that
+included either all of our models (``hub-ensemble-with-all'') or only
+one of them (``hub-ensemble-with-X'') were computed retrospectively.
 
@@
 \hypertarget{crowd-forecast-participation}{%
-\subsection{Crowd forecast participation}\label{crowd-forecast-participation}}
-
-A total number of 32 participants submitted forecasts, 17 of those self-identified as `expert' in either forecasting or epidemiology.
-The median number of forecasters for any given forecast target was 6, the minimum 2 and the maximum 10.
-The mean number of submissions from an individual forecaster was 4.7 but the median number was only one - most participants dropped out after their first submission.
-Only two participants submitted a forecast every single week, both of whom are authors on this study.
+\subsection{Crowd forecast
+participation}\label{crowd-forecast-participation}}
+
+A total number of 32 participants submitted forecasts, 17 of those
+self-identified as `expert' in either forecasting or epidemiology. The
+median number of forecasters for any given forecast target was 6, the
+minimum 2 and the maximum 10. The mean number of submissions from an
+individual forecaster was 4.7 but the median number was only one - most
+participants dropped out after their first submission. Only two
+participants submitted a forecast every single week, both of whom are
+authors on this study.
 
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} \caption{A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values.
+\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} \caption{Two week ahead forecasts and corresponding scores.
+A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values.
 Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
@@
 
-For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \ref{fig:agg-performance-all}A) and locations (Figure \ref{fig:performance-locations-rel}A).
-For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \ref{tab:score-table-2}).
-Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Figure \ref{fig:distribution-scores}).
-Overall, low variance in forecast performance was closely linked with good mean performance (Figures \ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \ref{fig:distribution-scores}), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
-WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
-
-To varying degrees, all forecasts exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened.
-For example, all forecasts failed to predict the change in trend from increase to decrease that happened in November in Germany and severely overshot reported cases (Figure \ref{fig:forecasts-and-truth}A).
-This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past of observations.
-The Hub ensemble and the crowd forecast, which had both been under-predicting throughout October, also failed to predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 (50) and the change in the testing regime (with stricter test criteria) on November 11th 2020 (36), were fastest to adapt to the new trend, and the Hub ensemble slowest.
-In December, cases rose again in Germany, with all models under-predicting this growth to varying extents.
-As in October, the renewal model captured the phase of exponential growth in cases slightly better than other approaches, but again overshot when reported case numbers fell over Christmas.
-The large variance in predictions in January in Germany (severe under-prediction followed by severe over-prediction) may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.
-Similar trends in performance were evident in Poland, with the crowd forecast quickest at adapting to the change in trend in November.
-In general, there were fewer large outlier forecasts in Poland and in particular the renewal model performed more in line with other forecasts there.
-
-All forecasting approaches, including the Hub ensemble, were overconfident, i.e.~they showed lower than nominal coverage (meaning that 50\% (90\%) prediction intervals generally covered less than 50\% (90\%) of the actually observed values) (Figure \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
-Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts.
-This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \ref{fig:agg-performance-all}E) and only showed a small increase in uncertainty across forecast horizons.
-The crowd forecasts prediction intervals were also noticeably narrower than the default baseline shown to forecasters in the application (see Figure \ref{fig:compare-forecasters}).
-
-In spite of good performance in terms of the absolute error (Figure \ref{fig:agg-performance-all}G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36\% and 55\% of all observations with the 50\% and 90\% prediction intervals of all forecasts made at a two week forecast horizon, and only 5\% and 38\% four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
-Despite worse performance in terms of absolute error (Figure \ref{fig:agg-performance-all}G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
-The crowd forecasts, on the other hand, showed a smaller bias than the renewal model, but were overconfident.
-
-The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons.
-The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \ref{fig:agg-performance-all}F).
-Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
-
-Generally, trends in overall performance were broadly similar across locations (Figures \ref{fig:performance-locations} and \ref{fig:performance-locations-rel}).
-Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
-However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \ref{fig:performance-locations-rel}A, \ref{fig:performance-locations-rel}G, \ref{fig:agg-performance-all-Germany}, \ref{fig:agg-performance-all-Poland}).
+For cases, crowd forecasts had a lower mean weighted interval score
+(WIS, lower values indicate better performance) than both the renewal
+model and the Hub ensemble across all forecast horizons (Figure
+\ref{fig:agg-performance-all}A) and locations (Figure
+\ref{fig:performance-locations-rel}A). For two week ahead forecasts,
+mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts
+and 1.40 for the renewal model (Table \ref{tab:score-table-2}). Across
+all forecasting approaches, locations and forecast horizons, the
+distribution of WIS values was very right-skewed, and average
+performance was heavily influenced by outliers (Figure
+\ref{fig:distribution-scores}). Overall, low variance in forecast
+performance was closely linked with good mean performance (Figures
+\ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A),
+suggesting that the ability to avoid large errors was an important
+factor in determining overall performance. The impact of outlier values
+was especially pronounced for the renewal model, which had more outliers
+(Figure \ref{fig:distribution-scores}), as well as the highest standard
+deviation of WIS values (standard deviation of the WIS relative to the
+WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon),
+while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub
+ensemble (= 1) showed more stable performance.
+
+To varying degrees, all forecasts exhibited trend-following behaviour
+and were rarely able to predict a change in trend before it had
+happened. For example, all forecasts failed to predict the change in
+trend from increase to decrease that happened in November in Germany and
+severely overshot reported cases (Figure
+\ref{fig:forecasts-and-truth}A). This was most striking for the renewal
+model, which extrapolated unconstrained exponential growth based on the
+recent past of observations. The Hub ensemble and the crowd forecast,
+which had both been under-predicting throughout October, also failed to
+predict the change in trend after cases peaked, but less severely so.
+Human forecasters, possibly aware of the semi-lockdown announced on
+November 2nd 2020 {[}50{]} and the change in the testing regime (with
+stricter test criteria) on November 11th 2020 {[}36{]}, were fastest to
+adapt to the new trend, and the Hub ensemble slowest. In December, cases
+rose again in Germany, with all models under-predicting this growth to
+varying extents. As in October, the renewal model captured the phase of
+exponential growth in cases slightly better than other approaches, but
+again overshot when reported case numbers fell over Christmas. The large
+variance in predictions in January in Germany (severe under-prediction
+followed by severe over-prediction) may in part be caused by the fact
+that the renewal model operated on daily data and therefore was
+susceptible to fluctuations in daily reporting around Christmas that
+would not have influenced on weekly reporting. Similar trends in
+performance were evident in Poland, with the crowd forecast quickest at
+adapting to the change in trend in November. In general, there were
+fewer large outlier forecasts in Poland and in particular the renewal
+model performed more in line with other forecasts there.
+
+All forecasting approaches, including the Hub ensemble, were
+overconfident, i.e.~they showed lower than nominal coverage (meaning
+that 50\% (90\%) prediction intervals generally covered less than 50\%
+(90\%) of the actually observed values) (Figure
+\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
+Coverage for all forecasts deteriorated with increasing forecast
+horizon, indicating that all forecasting approaches struggled to
+quantify uncertainty appropriately for case forecasts. This was
+especially an issue for crowd forecasts, which had markedly shorter
+prediction intervals (i.e., narrower and more confident predictive
+distributions) than other approaches (Figure
+\ref{fig:agg-performance-all}E) and only showed a small increase in
+uncertainty across forecast horizons. The crowd forecasts prediction
+intervals were also noticeably narrower than the default baseline shown
+to forecasters in the application (see Figure
+\ref{fig:compare-forecasters}).
+
+In spite of good performance in terms of the absolute error (Figure
+\ref{fig:agg-performance-all}G), the narrow forecast intervals led to
+forecasts which were severely overconfident (covering only 36\% and 55\%
+of all observations with the 50\% and 90\% prediction intervals of all
+forecasts made at a two week forecast horizon, and only 5\% and 38\%
+four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables
+\ref{tab:score-table-2} and \ref{tab:score-table-4}). Despite worse
+performance in terms of absolute error (Figure
+\ref{fig:agg-performance-all}G), the renewal model achieved better
+calibration (comparable to the Hub ensemble), as uncertainty increased
+rapidly across forecast horizons. The crowd forecasts, on the other
+hand, showed a smaller bias than the renewal model, but were
+overconfident.
+
+The renewal model exhibited a noticeable tendency towards
+over-predicting reported cases across all horizons. The crowd forecast
+tended to over-predict at longer forecast horizons, whereas the Hub
+ensemble showed no systematic bias (Figure
+\ref{fig:agg-performance-all}F). Regardless of a general relative
+tendency to over-predict, all forecasting approaches incurred larger
+absolute penalties from over- than from under-prediction (see
+decomposition of the WIS into absolute penalties for over-prediction,
+under-prediction and dispersion in Figures
+\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and
+Tables \textbackslash ref\{tab:score-table-2) and
+\ref{tab:score-table-4}).
+
+Generally, trends in overall performance were broadly similar across
+locations (Figures \textbackslash ref\{fig:performance-locations) and
+\ref{fig:performance-locations-rel}). Due to the differing population
+sizes and numbers of notifications in Germany and Poland absolute scores
+were difficult to compare directly. However, relative to the Hub
+ensemble, the crowd forecasts performed noticeably better in Germany
+than in Poland and the renewal model better in Poland than in Germany
+(Figures \ref{fig:performance-locations-rel}A,
+\ref{fig:performance-locations-rel}G,
+\ref{fig:agg-performance-all-Germany},
+\ref{fig:agg-performance-all-Poland}).
 
@@
 
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure \ref{fig:agg-performance-all}B, Figure \ref{fig:performance-locations}B).
-Relative WIS values for the models two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1 (Hub ensemble) and 1.79 (renewal model).
-The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \ref{fig:agg-performance-all}B, Figure \ref{fig:performance-locations}B), and also better than the convolution model three and four weeks ahead.
-Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate \(R_t\) trace from deaths, does not use the available information efficiently.
-The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \ref{fig:agg-performance-all}B, Table \ref{tab:score-table-4}).
-
-As past cases and hospitalisations can be used as predictors, predicting a change in trend may be easier for deaths than for cases.
-Even though all forecasts generally struggled with this, there were some instances where changing trends were well captured or even anticipated.
-In Poland, for example, the Hub ensemble was able to capture or even anticipate the peak in deaths in December quite well (whereas the renewal model and crowd forecast did not).
-The renewal model, which mostly exhibited trend-following behaviour, correctly predicted another increase in weekly deaths in mid-January (potentially based on changes in daily deaths, as the renewal model did not know about past cases).
-In Germany in early January, all models predicted a decrease in deaths two to three weeks before it actually happened.
-Predictions from the renewal model at that time were likely strongly influenced by an unexpected drop in reported deaths in December.
-The other forecasting approaches and in particular, the convolution model may have been affected by potentially under-reported case numbers around Christmas.
-When the decrease that all models had predicted to happen in early January failed to materialise, the renewal model and the crowd forecast noticeably over-corrected and over-predicted deaths in the following weeks, while the Hub ensemble, and to a slightly lesser degree, the convolution model were able to capture the downturn well when it finally happened at the end of January.
-
-Death forecasts, generally, showed greater coverage of the 50\% and 90\% prediction intervals than case forecasts and no decrease in coverage across forecast horizons, indicating that it might be easier to appropriately quantify uncertainty for death forecasts.
-The Hub ensemble had the greatest coverage, with empirical coverage of the 50\% and 90\% prediction intervals exceeding 50\%, and 90\%, respectively, across all forecast horizons.
-Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
-As for cases, the crowd forecast tended to have the narrowest prediction intervals and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
-The convolution model had relatively narrow prediction intervals for short forecast horizons, but had rapidly (and non-linearly) increasing uncertainty for longer forecast horizons, driven by increasing uncertainty in the underlying case forecasts.
-
-For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \ref{fig:agg-performance-all}F.
-The convolution model had a strong tendency to under-predict, with the magnitude of under-prediction steadily decreasing for longer forecast horizons.
-The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction.
-For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \ref{fig:agg-performance-all}A, \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2}, \ref{tab:score-table-4}).
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} \caption{A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
+For deaths, the Hub ensemble outperformed the crowd forecasts as well as
+our model-based approaches across all forecast horizons and locations
+(Figure \ref{fig:agg-performance-all}B, Figure
+\ref{fig:performance-locations}B). Relative WIS values for the models
+two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1
+(Hub ensemble) and 1.79 (renewal model). The crowd forecasts performed
+better than the renewal model across all forecast horizons and locations
+(Figure \ref{fig:agg-performance-all}B, Figure
+\ref{fig:performance-locations}B), and also better than the convolution
+model three and four weeks ahead. Poor performance of the renewal model,
+especially at longer horizons, indicates that an approach that does not
+know about past cases, but instead estimates and projects a separate
+\(R_t\) trace from deaths, does not use the available information
+efficiently. The convolution model was able to outperform both the
+renewal model and the crowd forecasts at shorter forecast horizons
+(where the delay between cases and deaths means that future deaths are
+largely informed by present cases), but saw performance deteriorate at
+three and four weeks ahead (where case predictions from the renewal
+model were increasingly used to inform death predictions) (Figure
+\ref{fig:agg-performance-all}B, Table \ref{tab:score-table-4}).
+
+As past cases and hospitalisations can be used as predictors, predicting
+a change in trend may be easier for deaths than for cases. Even though
+all forecasts generally struggled with this, there were some instances
+where changing trends were well captured or even anticipated. In Poland,
+for example, the Hub ensemble was able to capture or even anticipate the
+peak in deaths in December quite well (whereas the renewal model and
+crowd forecast did not). The renewal model, which mostly exhibited
+trend-following behaviour, correctly predicted another increase in
+weekly deaths in mid-January (potentially based on changes in daily
+deaths, as the renewal model did not know about past cases). In Germany
+in early January, all models predicted a decrease in deaths two to three
+weeks before it actually happened. Predictions from the renewal model at
+that time were likely strongly influenced by an unexpected drop in
+reported deaths in December. The other forecasting approaches and in
+particular, the convolution model may have been affected by potentially
+under-reported case numbers around Christmas. When the decrease that all
+models had predicted to happen in early January failed to materialise,
+the renewal model and the crowd forecast noticeably over-corrected and
+over-predicted deaths in the following weeks, while the Hub ensemble,
+and to a slightly lesser degree, the convolution model were able to
+capture the downturn well when it finally happened at the end of
+January.
+
+Death forecasts, generally, showed greater coverage of the 50\% and 90\%
+prediction intervals than case forecasts and no decrease in coverage
+across forecast horizons, indicating that it might be easier to
+appropriately quantify uncertainty for death forecasts. The Hub ensemble
+had the greatest coverage, with empirical coverage of the 50\% and 90\%
+prediction intervals exceeding 50\%, and 90\%, respectively, across all
+forecast horizons. Coverage for the crowd forecasts and our model-based
+approaches was generally lower than that of the Hub ensemble and mostly
+slightly lower than nominal coverage (Figure
+\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D). As
+for cases, the crowd forecast tended to have the narrowest prediction
+intervals and uncertainty increased most slowly across forecast
+horizons, and the renewal model forecasts generally were widest. The
+convolution model had relatively narrow prediction intervals for short
+forecast horizons, but had rapidly (and non-linearly) increasing
+uncertainty for longer forecast horizons, driven by increasing
+uncertainty in the underlying case forecasts.
+
+For deaths, the ensemble of crowd forecasts had a consistent tendency to
+over-predict \ref{fig:agg-performance-all}F. The convolution model had a
+strong tendency to under-predict, with the magnitude of under-prediction
+steadily decreasing for longer forecast horizons. The renewal model
+(which over-predicted for cases) and the Hub ensemble slightly tended
+towards under-prediction. For deaths, absolute over- and
+under-prediction penalties were more in line with a general relative
+tendency to over- or under-predict than for cases (Figure
+\ref{fig:agg-performance-all}A, \ref{fig:agg-performance-all}B and
+Tables \ref{tab:score-table-2}, \ref{tab:score-table-4}).
+
+\begin{figure}[H]
+\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} \caption{Distribution of scores.
+A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
 Points denote single forecasts scores, while the shaded area shows an estimated probability density.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Visualisation of relative aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
+\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.
 “Hub-ensemble”    extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
@@
 
-Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (``hub-ensemble-realised''), while the convolution model was never included as it was deemed too similar to the existing renewal model.
-In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on 28 December 2020 over the Christmas period) and a maximum of 10.
-Versions that included either all of our models (``hub-ensemble-with-all'') or only one of them (``hub-ensemble-with-X'') were computed retrospectively.
-An overview of all models and ensemble versions is shown in Table \ref{tab:table-ensemble-versions} in the SI.
-
-For cases, our contributions (compared to the Hub ensemble without our contributions) consistently improved performance across all forecasting horizons (rel.
-WIS 0.9 two weeks ahead, Table \ref{tab:score-table-ensemble-2}).
-Contributions from the crowd forecasts alone also improved performance of the Hub ensemble across all forecast horizons, while contributions from the renewal model had a negative effect for longer horizons (rel.
-WIS 1.02 three weeks ahead, 1.06 four weeks ahead).
-The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model have improved performance (Table \ref{tab:score-table-ensemble-4}).
-The realised ensemble performed comparably to the crowd forecasts for predictions one to two weeks ahead, and worse for greater forecast horizons.
-
-For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel.
-WIS of the Hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and \ref{tab:score-table-ensemble-4}).
-Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons).
-This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \ref{fig:agg-performance-all}) and especially worse for longer horizons.
-
-We also considered the impact of our contributions on a version of the Hub ensemble constructed by taking the quantile-wise mean, rather than the median.
-General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \ref{fig:agg-performance-ensemble-rel}B and \ref{fig:agg-performance-ensemble-mean}B).
-This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far.
-For both the mean and the median ensemble, changes in performance from adding or removing models were of a similar order of magnitude, suggesting that at least in this instance, with a relatively small ensemble size, the median ensemble was not necessarily more `robust' to changes than the mean ensemble.
-However, the ensemble version with all our forecasts included (``hub-ensemble-with-all'') tended to perform relatively better for the median ensemble than the mean ensemble, suggesting that adding more models may be more beneficial or `safer' for the median than for the mean ensemble as directional errors can more easily cancel out than errors in absolute terms.
+Of our three models, only the renewal model and the crowd forecast were
+included in the official Forecast Hub median ensemble
+(``hub-ensemble-realised''), while the convolution model was never
+included as it was deemed too similar to the existing renewal model. In
+the official Hub ensemble, there were on average 7.1 models included
+(including our own), with a median of 7, a minimum of 4 (on 28 December
+2020 over the Christmas period) and a maximum of 10. Versions that
+included either all of our models (``hub-ensemble-with-all'') or only
+one of them (``hub-ensemble-with-X'') were computed retrospectively. An
+overview of all models and ensemble versions is shown in Table
+\textbackslash ref\{tab:table-ensemble-versions) in the SI.
+
+For cases, our contributions (compared to the Hub ensemble without our
+contributions) consistently improved performance across all forecasting
+horizons (rel. WIS 0.9 two weeks ahead, Table
+\ref{tab:score-table-ensemble-2}). Contributions from the crowd
+forecasts alone also improved performance of the Hub ensemble across all
+forecast horizons, while contributions from the renewal model had a
+negative effect for longer horizons (rel. WIS 1.02 three weeks ahead,
+1.06 four weeks ahead). The realised ensemble including both models
+performed better or equal compared to all versions with only one model
+included for up to three weeks ahead, suggesting synergistic effects.
+Only for predictions four weeks ahead would removing the renewal model
+have improved performance (Table \ref{tab:score-table-ensemble-4}). The
+realised ensemble performed comparably to the crowd forecasts for
+predictions one to two weeks ahead, and worse for greater forecast
+horizons.
+
+For deaths, contributions from the renewal model and crowd forecast
+together improved performance only for one week ahead predictions and
+showed an increasingly negative impact on performance for longer
+horizons (rel. WIS of the Hub-ensemble-realised 1.01 two weeks ahead,
+1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and
+\ref{tab:score-table-ensemble-4}). Individual contributions from both
+the renewal model and the crowd forecast were largely negative, while a
+version of the Hub ensemble with only the convolution model included
+would have performed consistently better across all forecast horizons
+(with the positive impact increasing for longer horizons). This is
+especially interesting as the convolution model performed consistently
+worse than the pre-existing Hub ensemble (Figure
+\ref{fig:agg-performance-all}) and especially worse for longer horizons.
+
+We also considered the impact of our contributions on a version of the
+Hub ensemble constructed by taking the quantile-wise mean, rather than
+the median. General trends were similar, with the notable exception of
+the convolution model, which had a consistently positive impact on the
+median ensemble, but a mixed and mostly slightly negative impact on the
+mean ensemble (Figures \ref{fig:agg-performance-ensemble-rel}B and
+\ref{fig:agg-performance-ensemble-mean}B). This may happen if a model is
+more correct directionally relative to the pre-existing ensemble, but
+overshoots in absolute terms, thereby moving the ensemble too far. For
+both the mean and the median ensemble, changes in performance from
+adding or removing models were of a similar order of magnitude,
+suggesting that at least in this instance, with a relatively small
+ensemble size, the median ensemble was not necessarily more `robust' to
+changes than the mean ensemble. However, the ensemble version with all
+our forecasts included (``hub-ensemble-with-all'') tended to perform
+relatively better for the median ensemble than the mean ensemble,
+suggesting that adding more models may be more beneficial or `safer' for
+the median than for the mean ensemble as directional errors can more
+easily cancel out than errors in absolute terms.
 
@@
 
-Epidemiological forecasting modelling combines knowledge about infectious disease dynamics with the subjective opinion of the researcher who develops and refines the model.
-In this study, we compared forecasts of cases of and deaths from COVID-19 in Germany and Poland based purely on human judgement and elicited from a crowd of researchers and volunteers against forecasts from two semi-mechanistic epidemiological models.
-In spite of the small number of participants and a general tendency to be overconfident, crowd forecasts consistently outperformed our epidemiological models as well as the Hub ensemble when forecasting cases but not when forecasting deaths.
-This suggests that humans might be relatively good at foreseeing trends that are hard to model but may struggle to form an intuition for the exact relationship between cases and deaths.
-
-Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (e.g.
-12,13,14), or exclusively on human forecasts (19,20,24,25).
-In contrast, we directly compared human and model-based forecasts.
-This is similar to the approach taken by (11), but extends it in several ways.
-While Farrow et al.~only asked for point predictions and constructed a predictive distribution from these, we asked participants to provide a full predictive distribution, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse how humans quantified their uncertainty.
-In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-based insight.
-In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (12--15,17).
-
-The strong performance of crowd forecasts in our study is in line with results from Farrow et al.~who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants.
-The advantage of crowd forecasts we observed over our semi-mechanistic models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models.
-However, this probably explains only part of the difference, and performance relative to the Hub ensemble strongly suggests that human insight is valuable when forecasting highly volatile and potentially hard-to-predict quantities such as case numbers.
-One potential explanation is that humans can have access to data that is not available to or hard to integrate into model-based forecasts.
-Relatively good performance of our semi-mechanistic models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time.
-This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data).
-The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \ref{fig:forecasts-and-truth}A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting which have less of an influence on weekly reporting.
-
-Our results suggest that human intervention may be less beneficial when forecasting deaths (especially at shorter horizons, when deaths are largely dependent on already observed cases), which benefits from the ability to model the delays and exact epidemiological relationships between different leading and lagged indicators.
-Relatively good performance of the convolution model, especially compared to the poor performance of the renewal model on deaths (which used only deaths to estimate and predict the effective reproduction number) underlines the importance of including leading indicators such as cases as a predictor for deaths.
-
-Given the low number of participants in our study, it is difficult to generalise conclusions about crowd predictions to other settings.
-Using R shiny as a platform for the web application arguably created some limits to user experience and performance, influencing the number of participants and potentially creating a self-selection effect.
-Motivating forecasters to contribute regularly proved challenging, especially given that the majority of our participants were from the UK and may not have been familiar with all relevant details of the situation in Germany and Poland.
-On the other hand, R shiny facilitated quick development and allowed us to provide our crowd forecasting tooling as an open source R package, meaning that it is available for others to use, for example in settings like early-stage outbreaks where model-based forecasts are not available.
-In light of the relatively small number of Hub ensemble models, performance of the Hub ensemble is also difficult to generalise.
-More research is needed to replicate these findings and investigate how crowd forecasts compare against the types of models and model ensembles policy makers use to inform their decisions.
-
-Our work suggests that crowd forecasts and model-based forecasts could have different strengths and may be able to complement each other.
-When choosing a suitable approach for a given task it is important to take into account how the output will be used.
-In this work we focused on forecasts (which aim to predict future data points whilst accounting for all factors that might influence them), whereas policy makers might be more interested in projections (which show what would happen in the absence of any events that could change the trend) or scenario modelling.
-Forecasts may not be a suitable basis for informing policy decisions, if forecasters already have factored in the expectation of a future intervention.
-Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting projections that are not influenced by implicit assumptions about the future from humans may be harder.
-
-Further work should explore the effects of humans refining their mathematical models or changing model outputs in more detail.
-Model-based forecasts could be used as an input to human judgement, with researchers adjusting predictions generated by models.
-Seeing a model-based forecast could help humans calibrate uncertainty better, while allowing for manual intervention to adapt spurious trend predictions.
-Tools need to be developed to facilitate this process at a larger scale.
-Human insight could also be used as an input to models.
-Such a `hybrid' forecasting approach could for example ask humans to predict the trend of the effective reproduction number \(R_t\) or the doubling rate (i.e.~how the epidemic evolves) into the future and use this to estimate the exact number of cases, hospitalisations or deaths this would imply.
-In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust and widen prediction intervals may be another promising approach.
-Crowd forecasting in general could benefit greatly from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile to further develop and explore.
+Epidemiological forecasting modelling combines knowledge about
+infectious disease dynamics with the subjective opinion of the
+researcher who develops and refines the model. In this study, we
+compared forecasts of cases of and deaths from COVID-19 in Germany and
+Poland based purely on human judgement and elicited from a crowd of
+researchers and volunteers against forecasts from two semi-mechanistic
+epidemiological models. In spite of the small number of participants and
+a general tendency to be overconfident, crowd forecasts consistently
+outperformed our epidemiological models as well as the Hub ensemble when
+forecasting cases but not when forecasting deaths. This suggests that
+humans might be relatively good at foreseeing trends that are hard to
+model but may struggle to form an intuition for the exact relationship
+between cases and deaths.
+
+Past studies have evaluated the performance of model-based forecasting
+approaches as well as human experts and non-experts in various contexts.
+However, most of these studies either focused only on the evaluation of
+(expert-tuned) model-based approaches {[}e.g. 12,13,14{]}, or
+exclusively on human forecasts {[}19,20,24,25{]}. In contrast, we
+directly compared human and model-based forecasts. This is similar to
+the approach taken by {[}11{]}, but extends it in several ways. While
+Farrow et al.~only asked for point predictions and constructed a
+predictive distribution from these, we asked participants to provide a
+full predictive distribution, allowing us to compare human forecasts and
+models without any further assumptions, as well as to analyse how humans
+quantified their uncertainty. In addition, we compared crowd forecasts
+to two semi-mechanistic models informed by basic epidemiological
+knowledge of COVID-19, allowing us to assess not only relative
+performance but also to analyse qualitative differences between human
+judgement and model-based insight. In terms of interpretability of the
+results, exact knowledge of our two models, as well as focus on a
+limited set of targets and locations was a major advantage of our study
+compared to larger studies conducted by the Forecast Hubs
+{[}12--15,17{]}.
+
+The strong performance of crowd forecasts in our study is in line with
+results from Farrow et al.~who also report strong performance of human
+predictions in past Flu challenges despite difficulties to recruit a
+large number of participants. The advantage of crowd forecasts we
+observed over our semi-mechanistic models is likely in part explained by
+the fact that we compared an ensemble of crowd forecasts with single
+models. However, this probably explains only part of the difference, and
+performance relative to the Hub ensemble strongly suggests that human
+insight is valuable when forecasting highly volatile and potentially
+hard-to-predict quantities such as case numbers. One potential
+explanation is that humans can have access to data that is not available
+to or hard to integrate into model-based forecasts. Relatively good
+performance of our semi-mechanistic models short-term, but not
+longer-term, suggests that model-based forecasts are helpful to
+extrapolate from current conditions, but require some form of human
+intervention or additional assumptions to inform forecasts when
+conditions change over time. This human intervention may be particularly
+important when dealing with artefacts in reporting and data anomalies
+(and especially when using daily, rather than weekly data). The large
+variance in predictions in January in Germany for example (severe
+under-prediction followed by severe over-prediction, see Figure
+\ref{fig:forecasts-and-truth}A), may in part be caused by the fact that
+the renewal model operated on daily data and therefore was susceptible
+to fluctuations in daily reporting which have less of an influence on
+weekly reporting.
+
+Our results suggest that human intervention may be less beneficial when
+forecasting deaths (especially at shorter horizons, when deaths are
+largely dependent on already observed cases), which benefits from the
+ability to model the delays and exact epidemiological relationships
+between different leading and lagged indicators. Relatively good
+performance of the convolution model, especially compared to the poor
+performance of the renewal model on deaths (which used only deaths to
+estimate and predict the effective reproduction number) underlines the
+importance of including leading indicators such as cases as a predictor
+for deaths.
+
+Given the low number of participants in our study, it is difficult to
+generalise conclusions about crowd predictions to other settings. Using
+R shiny as a platform for the web application arguably created some
+limits to user experience and performance, influencing the number of
+participants and potentially creating a self-selection effect.
+Motivating forecasters to contribute regularly proved challenging,
+especially given that the majority of our participants were from the UK
+and may not have been familiar with all relevant details of the
+situation in Germany and Poland. On the other hand, R shiny facilitated
+quick development and allowed us to provide our crowd forecasting
+tooling as an open source R package, meaning that it is available for
+others to use, for example in settings like early-stage outbreaks where
+model-based forecasts are not available. In light of the relatively
+small number of Hub ensemble models, performance of the Hub ensemble is
+also difficult to generalise. More research is needed to replicate these
+findings and investigate how crowd forecasts compare against the types
+of models and model ensembles policy makers use to inform their
+decisions.
+
+Our work suggests that crowd forecasts and model-based forecasts could
+have different strengths and may be able to complement each other. When
+choosing a suitable approach for a given task it is important to take
+into account how the output will be used. In this work we focused on
+forecasts (which aim to predict future data points whilst accounting for
+all factors that might influence them), whereas policy makers might be
+more interested in projections (which show what would happen in the
+absence of any events that could change the trend) or scenario
+modelling. Forecasts may not be a suitable basis for informing policy
+decisions, if forecasters already have factored in the expectation of a
+future intervention. Model-based approaches can be either forecasts or
+projections depending on the assumptions, whereas eliciting projections
+that are not influenced by implicit assumptions about the future from
+humans may be harder.
+
+Further work should explore the effects of humans refining their
+mathematical models or changing model outputs in more detail.
+Model-based forecasts could be used as an input to human judgement, with
+researchers adjusting predictions generated by models. Seeing a
+model-based forecast could help humans calibrate uncertainty better,
+while allowing for manual intervention to adapt spurious trend
+predictions. Tools need to be developed to facilitate this process at a
+larger scale. Human insight could also be used as an input to models.
+Such a `hybrid' forecasting approach could for example ask humans to
+predict the trend of the effective reproduction number \(R_t\) or the
+doubling rate (i.e.~how the epidemic evolves) into the future and use
+this to estimate the exact number of cases, hospitalisations or deaths
+this would imply. In light of severe overconfidence, yet good
+performance in terms of the absolute error, post-processing of human
+forecasts to adjust and widen prediction intervals may be another
+promising approach. Crowd forecasting in general could benefit greatly
+from the availability of tools suitable to appeal to a greater audience.
+Given the good performance we and previous authors observed in spite of
+the limited resources available and the small number of participants,
+this seems worthwhile to further develop and explore.
 
@@
 
-NIB received funding from the Health Protection Research Unit (grant code NIHR200908, \url{https://www.nihr.ac.uk/}).
-SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z, \url{https://wellcome.org/}).
-The work of JB was supported by the Helmholtz Foundation (\url{https://www.helmholtz.de/}) via the SIMCARD Information and Data Science Pilot Project.
-This research was partly funded by the National Institute for Health Research (NIHR, \url{https://www.nihr.ac.uk/}) (16/137/109 \& 16/136/46) using UK aid from the UK Government to support global health research.
-The views expressed in this publication are those of the author(s) and not necessarily those of the NIHR or the UK Department of Health and Social Care.
-BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859, \url{https://www.gatesfoundation.org/}).
-EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908, \url{https://www.nihr.ac.uk/}) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688, \url{https://ec.europa.eu/programmes/horizon2020/}).
-AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID (\url{https://www.usaid.gov/}), and the Academy of Medical Sciences (\url{https://acmedsci.ac.uk/}).
-SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z, \url{https://wellcome.org/}), and the NIHR (NIHR200908, \url{https://www.nihr.ac.uk/}).
-
-We thank all forecasters who participated in this study for their contribution.
-
-We would also like to acknowledge (in a randomised order) the members of Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group at the the London School of Hygiene \& Tropical Medicine: Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie Diamond, Katherine E.
-Atkins, Rein M G J Houben, Jiayao Lei, Rachel Lowe, David Simons, Sophie R Meakin, Nicholas G.
-Davies, Timothy W Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly, Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas, Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson, Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun, Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche, James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday, Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael Pung, Anna M Foss.
+NIB received funding from the Health Protection Research Unit (grant
+code NIHR200908, https://www.nihr.ac.uk/). SA's work was funded by the
+Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/). The work
+of JB was supported by the Helmholtz Foundation
+(https://www.helmholtz.de/) via the SIMCARD Information and Data Science
+Pilot Project. This research was partly funded by the National Institute
+for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 \&
+16/136/46) using UK aid from the UK Government to support global health
+research. The views expressed in this publication are those of the
+author(s) and not necessarily those of the NIHR or the UK Department of
+Health and Social Care. BJQ is supported in part by a grant from the
+Bill and Melinda Gates Foundation (OPP1139859,
+https://www.gatesfoundation.org/). EvL acknowledges funding by the
+National Institute for Health Research (NIHR) Health Protection Research
+Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908,
+https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research
+and innovation programme - project EpiPose (101003688,
+https://ec.europa.eu/programmes/horizon2020/). AC acknowledges funding
+by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/),
+and the Academy of Medical Sciences (https://acmedsci.ac.uk/). SF's work
+was supported by the Wellcome Trust (grant: 210758/Z/18/Z,
+https://wellcome.org/), and the NIHR (NIHR200908,
+https://www.nihr.ac.uk/).
+
+We thank all forecasters who participated in this study for their
+contribution.
+
+We would also like to acknowledge (in a randomised order) the members of
+Centre for the Mathematical Modelling of Infectious Diseases COVID-19
+Working Group at the the London School of Hygiene \& Tropical Medicine:
+Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie
+Diamond, Katherine E. Atkins, Rein M G J Houben, Jiayao Lei, Rachel
+Lowe, David Simons, Sophie R Meakin, Nicholas G. Davies, Timothy W
+Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly,
+Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas,
+Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia
+Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson,
+Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang
+Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C
+Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun,
+Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche,
+James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday,
+Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan
+Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R
+Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael
+Pung, Anna M Foss.
 
@@
 \hypertarget{appendix-supplementary-information}{%
-\appendix}
+\section*{(APPENDIX) Supplementary
+information}\label{appendix-supplementary-information}}
+\addcontentsline{toc}{section}{(APPENDIX) Supplementary information}
 
@@
 
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{13.0cm}}
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{9.3cm}}
 \caption{\label{tab:scoring-metrics}Overview of the scoring metrics used.}\\
@@
 \endfirsthead
-\caption[]{\label{tab:scoring-metrics}Overview of the scoring metrics used. \textit{(continued)}}\\
+\caption[]{Overview of the scoring metrics used. \textit{(continued)}}\\
 \toprule
@@
 
-\hypertarget{further-details-on-the-semi-mechanistic-forecasting-models}{%
-\subsection{Further details on the semi-mechanistic forecasting models}\label{further-details-on-the-semi-mechanistic-forecasting-models}}
+\hypertarget{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}{%
+\subsection{Text S1. Further details on the semi-mechanistic forecasting
+models}\label{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}}
 
@@
 
-The model was initialised prior to the first observed data point by assuming constant exponential growth for the mean of assumed delays from infection to case report.
+The model was initialised prior to the first observed data point by
+assuming constant exponential growth for the mean of assumed delays from
+infection to case report.
 
@@
 
-Where \(I_{obs}\) and \(r_{obs}\) are estimated from the first week of observed data.
-For the time window of the observed data infections were then modelled by weighting previous infections by the generation time and scaling by the instantaneous reproduction number.
-These infections were then convolved to cases by date (\(O_t\)) and cases by date of report (\(D_t\)) using log-normal delay distributions.
-This model can be defined mathematically as follows,
+Where \(I_{obs}\) and \(r_{obs}\) are estimated from the first week of
+observed data. For the time window of the observed data infections were
+then modelled by weighting previous infections by the generation time
+and scaling by the instantaneous reproduction number. These infections
+were then convolved to cases by date (\(O_t\)) and cases by date of
+report (\(D_t\)) using log-normal delay distributions. This model can be
+defined mathematically as follows,
 
@@
 
-Where,
-\begin{align}
+Where, \begin{align}
      w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
@@
 
-\(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) were truncated to be greater than 0 and with \(\xi\), and \(w\) normalised to sum to 1.
-
-The prior for the generation time was sourced from (51) but refit using a log-normal incubation period with a mean of 5.2 days (SD 1.1) and SD of 1.52 days (SD 1.1) with this incubation period also being used as a prior (52) for \(\xi_{O}\).
-This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
-We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1\% or 1769 samples of the available data (45,53) and combining the posteriors for the mean and standard deviation of the log-normal distribution (40,42,46,54).
-
-\(GP_t\) is an approximate Hilbert space Gaussian process as defined in (55) using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20\% of the number of days used in fitting).
-The length scale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
-The magnitude of the Gaussian process was assumed to be normally distributed centred at 0 with a standard deviation of 0.1.
-
-From the forecast time horizon (\(T\)) and onwards the last value of the Gaussian process was used (hence \(R_t\) was assumed to be fixed) and latent infections were adjusted to account for the proportion of the population that was susceptible to infection as follows,
+\(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) were truncated to be
+greater than 0 and with \(\xi\), and \(w\) normalised to sum to 1.
+
+The prior for the generation time was sourced from {[}51{]} but refit
+using a log-normal incubation period with a mean of 5.2 days (SD 1.1)
+and SD of 1.52 days (SD 1.1) with this incubation period also being used
+as a prior {[}52{]} for \(\xi_{O}\). This resulted in a
+gamma-distributed generation time with mean 3.6 days (standard deviation
+(SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates. We estimated
+the delay between symptom onset and case report or death required to
+convolve latent infections to observations by fitting an integer
+adjusted log-normal distribution to 10 subsampled bootstraps of a public
+linelist for cases in Germany from April 2020 to June 2020 with each
+bootstrap using 1\% or 1769 samples of the available data {[}45,53{]}
+and combining the posteriors for the mean and standard deviation of the
+log-normal distribution {[}40,42,46,54{]}.
+
+\(GP_t\) is an approximate Hilbert space Gaussian process as defined in
+{[}55{]} using a Matern 3/2 kernel using a boundary factor of 1.5 and 17
+basis functions (20\% of the number of days used in fitting). The length
+scale of the Gaussian process was given a log-normal prior with a mean
+of 21 days, and a standard deviation of 7 days truncated to be greater
+than 3 days and less than 60 days. The magnitude of the Gaussian process
+was assumed to be normally distributed centred at 0 with a standard
+deviation of 0.1.
+
+From the forecast time horizon (\(T\)) and onwards the last value of the
+Gaussian process was used (hence \(R_t\) was assumed to be fixed) and
+latent infections were adjusted to account for the proportion of the
+population that was susceptible to infection as follows,
 
@@
 
-where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\) and \(I'_t\) are the unadjusted infections defined above.
-This adjustment is based on that implemented in the \texttt{epidemia} R package (56,57).
+where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\)
+and \(I'_t\) are the unadjusted infections defined above. This
+adjustment is based on that implemented in the \texttt{epidemia} R
+package {[}56,57{]}.
 
@@
 
-The convolution model shares the same observation model as the renewal model but rather than assuming that an observation is predicted by itself using the renewal equation instead assumes that it is predicted entirely by another observation after some parametric delay.
-It can be defined mathematically as follows,
+The convolution model shares the same observation model as the renewal
+model but rather than assuming that an observation is predicted by
+itself using the renewal equation instead assumes that it is predicted
+entirely by another observation after some parametric delay. It can be
+defined mathematically as follows,
 
@@
 
-with \(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) truncated to be greater than 0 and with \(\xi\) normalised such that \(\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1\).
+with \(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) truncated to be
+greater than 0 and with \(\xi\) normalised such that
+\(\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1\).
 
@@
 
-Both models were implemented using the \texttt{EpiNow2} R package (version 1.3.3) (40).
-Each forecast target was fitted independently for each model using Markov-chain Monte Carlo (MCMC) in stan (46).
-A minimum of 4 chains were used with a warmup of 250 samples for the renewal equation-based model and 1000 samples for the convolution model.
-2000 samples total post warmup were used for the renewal equation model and 4000 samples for the convolution model.
-Different settings were chosen for each model to optimise compute time contingent on convergence.
-Convergence was assessed using the R hat diagnostic (46).
-For the convolution model forecast the case forecast from the renewal equation model was used in place of observed cases beyond the forecast horizon using 1000 posterior samples.
-12 weeks of data was used for both models though only 3 weeks of data were included in the likelihood for the convolution model.
+Both models were implemented using the \texttt{EpiNow2} R package
+(version 1.3.3) {[}40{]}. Each forecast target was fitted independently
+for each model using Markov-chain Monte Carlo (MCMC) in stan {[}46{]}. A
+minimum of 4 chains were used with a warmup of 250 samples for the
+renewal equation-based model and 1000 samples for the convolution model.
+2000 samples total post warmup were used for the renewal equation model
+and 4000 samples for the convolution model. Different settings were
+chosen for each model to optimise compute time contingent on
+convergence. Convergence was assessed using the R hat diagnostic
+{[}46{]}. For the convolution model forecast the case forecast from the
+renewal equation model was used in place of observed cases beyond the
+forecast horizon using 1000 posterior samples. 12 weeks of data was used
+for both models though only 3 weeks of data were included in the
+likelihood for the convolution model.
 
@@
 \hypertarget{tables-with-results-of-the-forecast-evaluation}{%
-\subsection{Tables with results of the forecast evaluation}\label{tables-with-results-of-the-forecast-evaluation}}
+\subsection{Tables with results of the forecast
+evaluation}\label{tables-with-results-of-the-forecast-evaluation}}
 
@@
 \hypertarget{aggregate-performance-by-location}{%
-\subsection{Aggregate performance by location}\label{aggregate-performance-by-location}}
+\subsection{Aggregate performance by
+location}\label{aggregate-performance-by-location}}
 
@@
 \hypertarget{performance-across-locations-in-absolute-terms}{%
-\subsubsection{Performance across locations in absolute terms}\label{performance-across-locations-in-absolute-terms}}
+\subsubsection{Performance across locations in absolute
+terms}\label{performance-across-locations-in-absolute-terms}}
 
@@
 \hypertarget{performance-across-locations-in-relative-terms}{%
-\subsection{Performance across locations in relative terms}\label{performance-across-locations-in-relative-terms}}
+\subsection{Performance across locations in relative
+terms}\label{performance-across-locations-in-relative-terms}}
 
@@
 \hypertarget{visualisation-of-daily-reported-cases-and-deaths}{%
-\subsection{Visualisation of daily reported cases and deaths}\label{visualisation-of-daily-reported-cases-and-deaths}}
+\subsection{Visualisation of daily reported cases and
+deaths}\label{visualisation-of-daily-reported-cases-and-deaths}}
 
@@
 \hypertarget{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}{%
-\subsection{Visualisation of scores and forecasts 1, 3, 4 weeks ahead}\label{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}}
+\subsection{Visualisation of scores and forecasts 1, 3, 4 weeks
+ahead}\label{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}}
 
@@
 \hypertarget{ranks-achieved-by-forecasts}{%
-\subsubsection{Ranks achieved by forecasts}\label{ranks-achieved-by-forecasts}}
+\subsubsection{Ranks achieved by
+forecasts}\label{ranks-achieved-by-forecasts}}
 
@@
 \hypertarget{performance-visualisation-mean-ensemble}{%
-\subsubsection{Performance visualisation mean ensemble}\label{performance-visualisation-mean-ensemble}}
+\subsubsection{Performance visualisation mean
+ensemble}\label{performance-visualisation-mean-ensemble}}
 
@@
 
-In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later.
-This sensitivity shows performance of all models restricted to the period from December 14 2020 until March 1st 2021 where all models were available.
+In the original analysis, cases and deaths were scored on different
+periods, as the convolution model was only added later. This sensitivity
+shows performance of all models restricted to the period from December
+14 2020 until March 1st 2021 where all models were available.
 
@@
 \hypertarget{overview-of-models-and-forecasters}{%
-\subsection{Overview of models and forecasters}\label{overview-of-models-and-forecasters}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{11.0cm}}
+\subsection{Overview of models and
+forecasters}\label{overview-of-models-and-forecasters}}
+
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{7.3cm}}
 \caption{\label{tab:table-ensemble-versions}Overview of the models and ensembles used.}\\
@@
 \endfirsthead
-\caption[]{\label{tab:table-ensemble-versions}Overview of the models and ensembles used. \textit{(continued)}}\\
+\caption[]{Overview of the models and ensembles used. \textit{(continued)}}\\
 \toprule
@@
 \hypertarget{comparison-of-crowd-forecasts-and-application-baseline}{%
-\subsection{Comparison of crowd forecasts and application baseline}\label{comparison-of-crowd-forecasts-and-application-baseline}}
+\subsection{Comparison of crowd forecasts and application
+baseline}\label{comparison-of-crowd-forecasts-and-application-baseline}}
 
@@
 \CSLLeftMargin{1. }
-\CSLRightInline{McGowan CJ, Biggerstaff M, Johansson M, Apfeldorf KM, Ben-Nun M, Brooks L, et al.
-Collaborative efforts to forecast seasonal influenza in the {United States}, 2015--2016.
-Scientific Reports {[}Internet{]}.
-2019 Jan 24 {[}cited 2021 May 30{]};9(1, 1):683.
-Available from: \url{https://www.nature.com/articles/s41598-018-36361-9}}
+\CSLRightInline{McGowan CJ, Biggerstaff M, Johansson M, Apfeldorf KM,
+Ben-Nun M, Brooks L, et al. Collaborative efforts to forecast seasonal
+influenza in the {United States}, 2015--2016. Scientific Reports.
+2019;9: 683.
+doi:\href{https://doi.org/10.1038/s41598-018-36361-9}{10.1038/s41598-018-36361-9}}
 
@@
 \CSLLeftMargin{2. }
-\CSLRightInline{Reich NG, Brooks LC, Fox SJ, Kandula S, McGowan CJ, Moore E, et al.
-A collaborative multiyear, multimodel assessment of seasonal influenza forecasting in the {United States}.
-PNAS {[}Internet{]}.
-2019 Feb 19 {[}cited 2021 Oct 13{]};116(8):3146--54.
-Available from: \url{https://www.pnas.org/content/116/8/3146}}
+\CSLRightInline{Reich NG, Brooks LC, Fox SJ, Kandula S, McGowan CJ,
+Moore E, et al. A collaborative multiyear, multimodel assessment of
+seasonal influenza forecasting in the {United States}. PNAS. 2019;116:
+3146--3154.
+doi:\href{https://doi.org/10.1073/pnas.1812594116}{10.1073/pnas.1812594116}}
 
@@
 \CSLLeftMargin{3. }
-\CSLRightInline{Shaman J, Karspeck A.
-Forecasting seasonal outbreaks of influenza.
-PNAS {[}Internet{]}.
-2012 Dec 11 {[}cited 2021 Oct 13{]};109(50):20425--30.
-Available from: \url{https://www.pnas.org/content/109/50/20425}}
+\CSLRightInline{Shaman J, Karspeck A. Forecasting seasonal outbreaks of
+influenza. PNAS. 2012;109: 20425--20430.
+doi:\href{https://doi.org/10.1073/pnas.1208772109}{10.1073/pnas.1208772109}}
 
@@
 \CSLLeftMargin{4. }
-\CSLRightInline{Biggerstaff M, Alper D, Dredze M, Fox S, Fung IC-H, Hickmann KS, et al.
-Results from the centers for disease control and prevention's predict the 2013--2014 {Influenza Season Challenge}.
-BMC Infectious Diseases {[}Internet{]}.
-2016 Jul 22 {[}cited 2021 Oct 13{]};16(1):357.
-Available from: \url{https://doi.org/10.1186/s12879-016-1669-x}}
+\CSLRightInline{Biggerstaff M, Alper D, Dredze M, Fox S, Fung IC-H,
+Hickmann KS, et al. Results from the centers for disease control and
+prevention's predict the 2013--2014 {Influenza Season Challenge}. BMC
+Infectious Diseases. 2016;16: 357.
+doi:\href{https://doi.org/10.1186/s12879-016-1669-x}{10.1186/s12879-016-1669-x}}
 
@@
 \CSLLeftMargin{5. }
-\CSLRightInline{Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak AL, Baugher B, et al.
-An open challenge to advance probabilistic forecasting for dengue epidemics.
-PNAS {[}Internet{]}.
-2019 Nov 26 {[}cited 2021 May 30{]};116(48):24268--74.
-Available from: \url{https://www.pnas.org/content/116/48/24268}}
+\CSLRightInline{Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak
+AL, Baugher B, et al. An open challenge to advance probabilistic
+forecasting for dengue epidemics. PNAS. 2019;116: 24268--24274.
+doi:\href{https://doi.org/10.1073/pnas.1909865116}{10.1073/pnas.1909865116}}
 
@@
 \CSLLeftMargin{6. }
-\CSLRightInline{Yamana TK, Kandula S, Shaman J.
-Superensemble forecasts of dengue outbreaks.
-Journal of The Royal Society Interface {[}Internet{]}.
-2016 Oct 31 {[}cited 2021 May 30{]};13(123):20160410.
-Available from: \url{https://royalsocietypublishing.org/doi/full/10.1098/rsif.2016.0410}}
+\CSLRightInline{Yamana TK, Kandula S, Shaman J. Superensemble forecasts
+of dengue outbreaks. Journal of The Royal Society Interface. 2016;13:
+20160410.
+doi:\href{https://doi.org/10.1098/rsif.2016.0410}{10.1098/rsif.2016.0410}}
 
@@
 \CSLLeftMargin{7. }
-\CSLRightInline{Colón-González FJ, Bastos LS, Hofmann B, Hopkin A, Harpham Q, Crocker T, et al.
-Probabilistic seasonal dengue forecasting in {Vietnam}: {A} modelling study using superensembles.
-PLOS Medicine {[}Internet{]}.
-2021 Mar 4 {[}cited 2021 Mar 6{]};18(3):e1003542.
-Available from: \url{https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.1003542}}
+\CSLRightInline{Colón-González FJ, Bastos LS, Hofmann B, Hopkin A,
+Harpham Q, Crocker T, et al. Probabilistic seasonal dengue forecasting
+in {Vietnam}: {A} modelling study using superensembles. PLOS Medicine.
+2021;18: e1003542.
+doi:\href{https://doi.org/10.1371/journal.pmed.1003542}{10.1371/journal.pmed.1003542}}
 
@@
 \CSLLeftMargin{8. }
-\CSLRightInline{Viboud C, Sun K, Gaffey R, Ajelli M, Fumanelli L, Merler S, et al.
-The {RAPIDD} ebola forecasting challenge: {Synthesis} and lessons learnt.
-Epidemics {[}Internet{]}.
-2018 Mar 1 {[}cited 2021 May 30{]};22:13--21.
-Available from: \url{https://www.sciencedirect.com/science/article/pii/S1755436517301275}}
+\CSLRightInline{Viboud C, Sun K, Gaffey R, Ajelli M, Fumanelli L, Merler
+S, et al. The {RAPIDD} ebola forecasting challenge: {Synthesis} and
+lessons learnt. Epidemics. 2018;22: 13--21.
+doi:\href{https://doi.org/10.1016/j.epidem.2017.08.002}{10.1016/j.epidem.2017.08.002}}
 
@@
 \CSLLeftMargin{9. }
-\CSLRightInline{Funk S, Camacho A, Kucharski AJ, Lowe R, Eggo RM, Edmunds WJ.
-Assessing the performance of real-time epidemic forecasts: {A} case study of {Ebola} in the {Western Area} region of {Sierra Leone}, 2014-15.
-PLOS Computational Biology {[}Internet{]}.
-2019 Feb 11 {[}cited 2019 Sep 16{]};15(2):e1006785.
-Available from: \url{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1006785}}
+\CSLRightInline{Funk S, Camacho A, Kucharski AJ, Lowe R, Eggo RM,
+Edmunds WJ. Assessing the performance of real-time epidemic forecasts:
+{A} case study of {Ebola} in the {Western Area} region of {Sierra
+Leone}, 2014-15. PLOS Computational Biology. 2019;15: e1006785.
+doi:\href{https://doi.org/10.1371/journal.pcbi.1006785}{10.1371/journal.pcbi.1006785}}
 
@@
 \CSLLeftMargin{10. }
-\CSLRightInline{Del Valle SY, McMahon BH, Asher J, Hatchett R, Lega JC, Brown HE, et al.
-Summary results of the 2014-2015 {DARPA Chikungunya} challenge.
-BMC Infectious Diseases {[}Internet{]}.
-2018 May 30 {[}cited 2021 Oct 13{]};18(1):245.
-Available from: \url{https://doi.org/10.1186/s12879-018-3124-7}}
+\CSLRightInline{Del Valle SY, McMahon BH, Asher J, Hatchett R, Lega JC,
+Brown HE, et al. Summary results of the 2014-2015 {DARPA Chikungunya}
+challenge. BMC Infectious Diseases. 2018;18: 245.
+doi:\href{https://doi.org/10.1186/s12879-018-3124-7}{10.1186/s12879-018-3124-7}}
 
@@
 \CSLLeftMargin{11. }
-\CSLRightInline{Farrow DC, Brooks LC, Hyun S, Tibshirani RJ, Burke DS, Rosenfeld R.
-A human judgment approach to epidemiological forecasting.
-PLOS Computational Biology {[}Internet{]}.
-2017 Mar 10 {[}cited 2021 Jul 29{]};13(3):e1005248.
-Available from: \url{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005248}}
+\CSLRightInline{Farrow DC, Brooks LC, Hyun S, Tibshirani RJ, Burke DS,
+Rosenfeld R. A human judgment approach to epidemiological forecasting.
+PLOS Computational Biology. 2017;13: e1005248.
+doi:\href{https://doi.org/10.1371/journal.pcbi.1005248}{10.1371/journal.pcbi.1005248}}
 
@@
 \CSLLeftMargin{12. }
-\CSLRightInline{Funk S, Abbott S, Atkins BD, Baguelin M, Baillie JK, Birrell P, et al.
-Short-term forecasts to inform the response to the {Covid-19} epidemic in the {UK}.
-medRxiv {[}Internet{]}.
-2020 Nov 13 {[}cited 2020 Nov 28{]};2020.11.11.20220962.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2020.11.11.20220962v1}}
+\CSLRightInline{Funk S, Abbott S, Atkins BD, Baguelin M, Baillie JK,
+Birrell P, et al. Short-term forecasts to inform the response to the
+{Covid-19} epidemic in the {UK}. medRxiv. 2020; 2020.11.11.20220962.
+doi:\href{https://doi.org/10.1101/2020.11.11.20220962}{10.1101/2020.11.11.20220962}}
 
@@
 \CSLLeftMargin{13. }
-\CSLRightInline{Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K, et al.
-{COVID-19 Forecast Hub}: 4 {December} 2020 snapshot {[}Internet{]}.
-{Zenodo}; 2020 {[}cited 2021 May 29{]}.
-Available from: \url{https://zenodo.org/record/3963371}}
+\CSLRightInline{Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K,
+et al. {COVID-19 Forecast Hub}: 4 {December} 2020 snapshot. {Zenodo};
+2020.
+doi:\href{https://doi.org/10.5281/zenodo.3963371}{10.5281/zenodo.3963371}}
 
@@
 \CSLLeftMargin{14. }
-\CSLRightInline{Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A, Rivadeneira AJC, et al.
-Evaluation of individual and ensemble probabilistic forecasts of {COVID-19} mortality in the {US}.
-medRxiv {[}Internet{]}.
-2021 Feb 5 {[}cited 2021 Apr 6{]};2021.02.03.21250974.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2021.02.03.21250974v1}}
+\CSLRightInline{Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A,
+Rivadeneira AJC, et al. Evaluation of individual and ensemble
+probabilistic forecasts of {COVID-19} mortality in the {US}. medRxiv.
+2021; 2021.02.03.21250974.
+doi:\href{https://doi.org/10.1101/2021.02.03.21250974}{10.1101/2021.02.03.21250974}}
 
@@
 \CSLLeftMargin{15. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer JL, Ullrich A, et al.
-Short-term forecasting of {COVID-19} in {Germany} and {Poland} during the second wave -- a preregistered study.
-medRxiv {[}Internet{]}.
-2021 Jan 11 {[}cited 2021 Apr 1{]};2020.12.24.20248826.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2020.12.24.20248826v2}}
+\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
+JL, Ullrich A, et al. Short-term forecasting of {COVID-19} in {Germany}
+and {Poland} during the second wave -- a preregistered study. medRxiv.
+2021; 2020.12.24.20248826.
+doi:\href{https://doi.org/10.1101/2020.12.24.20248826}{10.1101/2020.12.24.20248826}}
 
@@
 \CSLLeftMargin{16. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer JL, Ullrich A, et al.
-National and subnational short-term forecasting of {COVID-19} in {Germany} and {Poland}, early 2021.
-2021 Nov 8 {[}cited 2021 Nov 18{]};2021.11.05.21265810.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2021.11.05.21265810v1}}
+\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
+JL, Ullrich A, et al. National and subnational short-term forecasting of
+{COVID-19} in {Germany} and {Poland}, early 2021. 2021;
+2021.11.05.21265810.
+doi:\href{https://doi.org/10.1101/2021.11.05.21265810}{10.1101/2021.11.05.21265810}}
 
@@
 \CSLLeftMargin{17. }
-\CSLRightInline{European Covid-19 Forecast Hub. European {Covid-19 Forecast Hub} {[}Internet{]}. 2021 {[}cited 2021 May 30{]}. Available from: \url{https://covid19forecasthub.eu/}}
+\CSLRightInline{European Covid-19 Forecast Hub. European {Covid-19
+Forecast Hub}. 2021 {[}cited 30 May 2021{]}. Available:
+\url{https://covid19forecasthub.eu/}}
 
@@
 \CSLLeftMargin{18. }
-\CSLRightInline{Reich NG, McGowan CJ, Yamana TK, Tushar A, Ray EL, Osthus D, et al.
-Accuracy of real-time multi-model ensemble forecasts for seasonal influenza in the {U}.{S}.
-PLOS Computational Biology {[}Internet{]}.
-2019 Nov 22 {[}cited 2020 Aug 7{]};15(11):e1007486.
-Available from: \url{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1007486}}
+\CSLRightInline{Reich NG, McGowan CJ, Yamana TK, Tushar A, Ray EL,
+Osthus D, et al. Accuracy of real-time multi-model ensemble forecasts
+for seasonal influenza in the {U}.{S}. PLOS Computational Biology.
+2019;15: e1007486.
+doi:\href{https://doi.org/10.1371/journal.pcbi.1007486}{10.1371/journal.pcbi.1007486}}
 
@@
 \CSLLeftMargin{19. }
-\CSLRightInline{Tetlock PE, Mellers BA, Rohrbaugh N, Chen E.
-Forecasting {Tournaments}: {Tools} for {Increasing Transparency} and {Improving} the {Quality} of {Debate}.
-Curr Dir Psychol Sci {[}Internet{]}.
-2014 Aug 1 {[}cited 2021 May 30{]};23(4):290--5.
-Available from: \url{https://doi.org/10.1177/0963721414534257}}
+\CSLRightInline{Tetlock PE, Mellers BA, Rohrbaugh N, Chen E. Forecasting
+{Tournaments}: {Tools} for {Increasing Transparency} and {Improving} the
+{Quality} of {Debate}. Curr Dir Psychol Sci. 2014;23: 290--295.
+doi:\href{https://doi.org/10.1177/0963721414534257}{10.1177/0963721414534257}}
 
@@
 \CSLLeftMargin{20. }
-\CSLRightInline{Atanasov P, Rescober P, Stone E, Swift SA, Servan-Schreiber E, Tetlock P, et al.
-Distilling the {Wisdom} of {Crowds}: {Prediction Markets} vs.
-{Prediction Polls}.
-Management Science {[}Internet{]}.
-2016 Apr 22 {[}cited 2021 May 30{]};63(3):691--706.
-Available from: \url{https://pubsonline.informs.org/doi/abs/10.1287/mnsc.2015.2374}}
+\CSLRightInline{Atanasov P, Rescober P, Stone E, Swift SA,
+Servan-Schreiber E, Tetlock P, et al. Distilling the {Wisdom} of
+{Crowds}: {Prediction Markets} vs. {Prediction Polls}. Management
+Science. 2016;63: 691--706.
+doi:\href{https://doi.org/10.1287/mnsc.2015.2374}{10.1287/mnsc.2015.2374}}
 
@@
 \CSLLeftMargin{21. }
-\CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers E-J.
-Laypeople {Can Predict Which Social-Science Studies Will Be Replicated Successfully}.
-Advances in Methods and Practices in Psychological Science {[}Internet{]}.
-2020 Sep 1 {[}cited 2021 Oct 13{]};3(3):267--85.
-Available from: \url{https://doi.org/10.1177/2515245920919667}}
+\CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers E-J. Laypeople
+{Can Predict Which Social-Science Studies Will Be Replicated
+Successfully}. Advances in Methods and Practices in Psychological
+Science. 2020;3: 267--285.
+doi:\href{https://doi.org/10.1177/2515245920919667}{10.1177/2515245920919667}}
 
@@
 \CSLLeftMargin{22. }
-\CSLRightInline{ReplicationMarkets.
-Replication {Markets} -- {Reliable} research replicates\ldots you can bet on it.
-{[}Internet{]}.
-2020 {[}cited 2021 Oct 13{]}.
-Available from: \url{https://www.replicationmarkets.com/}}
+\CSLRightInline{ReplicationMarkets. Replication {Markets} -- {Reliable}
+research replicates\ldots you can bet on it. 2020 {[}cited 13 Oct
+2021{]}. Available: \url{https://www.replicationmarkets.com/}}
 
@@
 \CSLRightInline{Servan-Schreiber E, Wolfers J, Pennock DM, Galebach B.
-Prediction {Markets}: {Does Money Matter}?
-Electronic Markets {[}Internet{]}.
-2004 Sep 1 {[}cited 2021 Oct 13{]};14(3):243--51.
-Available from: \url{http://www.informaworld.com/openurl?genre=article\&doi=10.1080/1019678042000245254\&magic=crossref\%7C\%7CD404A21C5BB053405B1A640AFFD44AE3}}
+Prediction {Markets}: {Does Money Matter}? Electronic Markets. 2004;14:
+243--251.
+doi:\href{https://doi.org/10.1080/1019678042000245254}{10.1080/1019678042000245254}}
 
@@
 \CSLLeftMargin{24. }
-\CSLRightInline{McAndrew TC, Reich NG.
-An expert judgment model to predict early stages of the {COVID-19} outbreak in the {United States}.
-medRxiv {[}Internet{]}.
-2020 Sep 23 {[}cited 2020 Sep 23{]};2020.09.21.20196725.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2020.09.21.20196725v1}}
+\CSLRightInline{McAndrew TC, Reich NG. An expert judgment model to
+predict early stages of the {COVID-19} outbreak in the {United States}.
+medRxiv. 2020; 2020.09.21.20196725.
+doi:\href{https://doi.org/10.1101/2020.09.21.20196725}{10.1101/2020.09.21.20196725}}
 
@@
 \CSLLeftMargin{25. }
-\CSLRightInline{Recchia G, Freeman ALJ, Spiegelhalter D.
-How well did experts and laypeople forecast the size of the {COVID-19} pandemic?
-PLOS ONE {[}Internet{]}.
-2021 May 5 {[}cited 2021 Jun 2{]};16(5):e0250935.
-Available from: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0250935}}
+\CSLRightInline{Recchia G, Freeman ALJ, Spiegelhalter D. How well did
+experts and laypeople forecast the size of the {COVID-19} pandemic? PLOS
+ONE. 2021;16: e0250935.
+doi:\href{https://doi.org/10.1371/journal.pone.0250935}{10.1371/journal.pone.0250935}}
 
@@
 \CSLLeftMargin{26. }
-\CSLRightInline{Metaculus.
-A {Preliminary Look} at {Metaculus} and {Expert Forecasts} {[}Internet{]}.
-2020 {[}cited 2021 May 30{]}.
-Available from: \url{https://www.metaculus.com/news/2020/06/02/LRT/}}
+\CSLRightInline{Metaculus. A {Preliminary Look} at {Metaculus} and
+{Expert Forecasts}. 22 Jun 2020 {[}cited 30 May 2021{]}. Available:
+\url{https://www.metaculus.com/news/2020/06/02/LRT/}}
 
@@
 \CSLLeftMargin{27. }
-\CSLRightInline{Hypermind.
-Hypermind \textbar{} {Supercollective} intelligence for decision makers {[}Internet{]}.
-{Hypermind}; 2021 {[}cited 2021 Oct 13{]}.
-Available from: \url{https://www.hypermind.com/en/}}
+\CSLRightInline{Hypermind. Hypermind \textbar{} {Supercollective}
+intelligence for decision makers. {Hypermind}; 2021 {[}cited 13 Oct
+2021{]}. Available: \url{https://www.hypermind.com/en/}}
 
@@
 \CSLLeftMargin{28. }
-\CSLRightInline{CSET Foretell. {CSET Foretell} {[}Internet{]}. 2021 {[}cited 2021 Oct 13{]}. Available from: \url{https://www.cset-foretell.com/}}
+\CSLRightInline{CSET Foretell. {CSET Foretell}. 2021 {[}cited 13 Oct
+2021{]}. Available: \url{https://www.cset-foretell.com/}}
 
@@
 \CSLLeftMargin{29. }
-\CSLRightInline{PredictIt. {PredictIt} {[}Internet{]}. 2021 {[}cited 2021 Oct 13{]}. Available from: \url{https://www.predictit.org/}}
+\CSLRightInline{PredictIt. {PredictIt}. 2021 {[}cited 13 Oct 2021{]}.
+Available: \url{https://www.predictit.org/}}
 
@@
 \CSLLeftMargin{30. }
-\CSLRightInline{Held L, Meyer S, Bracher J.
-Probabilistic forecasting in infectious disease epidemiology: The 13th {Armitage} lecture.
-Statistics in Medicine {[}Internet{]}.
-2017 {[}cited 2019 Sep 16{]};36(22):3443--60.
-Available from: \url{https://onlinelibrary.wiley.com/doi/abs/10.1002/sim.7363}}
+\CSLRightInline{Held L, Meyer S, Bracher J. Probabilistic forecasting in
+infectious disease epidemiology: The 13th {Armitage} lecture. Statistics
+in Medicine. 2017;36: 3443--3460.
+doi:\href{https://doi.org/10.1002/sim.7363}{10.1002/sim.7363}}
 
@@
 \CSLLeftMargin{31. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. \href{https://doi.org/10.5281/zenodo.4618519}{Crowdforecastr: Eliciting crowd forecasts in r shiny}. 2020. }
+\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
+Crowdforecastr: Eliciting crowd forecasts in r shiny. 2020.
+doi:\href{https://doi.org/10.5281/zenodo.4618519}{10.5281/zenodo.4618519}}
 
@@
 \CSLLeftMargin{32. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Covid.german.forecasts: Forecasting covid-19 related metrics for the german/poland forecast hub. 2020. }
+\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
+Covid.german.forecasts: Forecasting covid-19 related metrics for the
+german/poland forecast hub. 2020. }
 
@@
 \CSLLeftMargin{33. }
-\CSLRightInline{ECDC.
-Download historical data (to 14 {December} 2020) on the daily number of new reported {COVID-19} cases and deaths worldwide {[}Internet{]}.
-{European Centre for Disease Prevention and Control}; 2020 {[}cited 2021 May 30{]}.
-Available from: \url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}}
+\CSLRightInline{ECDC. Download historical data (to 14 {December} 2020)
+on the daily number of new reported {COVID-19} cases and deaths
+worldwide. {European Centre for Disease Prevention and Control}; 14 Dec
+2020 {[}cited 30 May 2021{]}. Available:
+\url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}}
 
@@
 \CSLLeftMargin{34. }
-\CSLRightInline{RKI.
-{RKI} - {Coronavirus SARS-CoV-2} - {Aktueller Lage-}/{Situationsbericht} des {RKI} zu {COVID-19} {[}Internet{]}.
-2021 {[}cited 2021 May 30{]}.
-Available from: \url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}}
+\CSLRightInline{RKI. {RKI} - {Coronavirus SARS-CoV-2} - {Aktueller
+Lage-}/{Situationsbericht} des {RKI} zu {COVID-19}. 2021 {[}cited 30 May
+2021{]}. Available:
+\url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}}
 
@@
 \CSLLeftMargin{35. }
-\CSLRightInline{Forsal.pl.
-Rozbieżności w statystykach koronawirusa.
-22 tys.
-przypadków będą doliczone do ogólnej liczby wyników {[}Internet{]}.
-2020 {[}cited 2021 May 30{]}.
-Available from: \url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}}
+\CSLRightInline{Forsal.pl. Rozbieżności w statystykach koronawirusa. 22
+tys. przypadków będą doliczone do ogólnej liczby wyników. 2020 {[}cited
+30 May 2021{]}. Available:
+\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}}
 
@@
 \CSLRightInline{Ärzteblatt DÄG Redaktion Deutsches.
-SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an {[}Internet{]}.
-{Deutsches Ärzteblatt}; 2020 {[}cited 2021 May 30{]}.
-Available from: \url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}}
+SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an. {Deutsches
+Ärzteblatt}; 3 Nov 2020 {[}cited 30 May 2021{]}. Available:
+\url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}}
 
@@
 \CSLLeftMargin{37. }
-\CSLRightInline{Fay C, Guyader V, Rochette S, Girard C. Golem: A framework for robust shiny applications {[}Internet{]}. 2021. Available from: \url{https://github.com/ThinkR-open/golem}}
+\CSLRightInline{Fay C, Guyader V, Rochette S, Girard C. Golem: A
+framework for robust shiny applications. 2021. Available:
+\url{https://github.com/ThinkR-open/golem}}
 
@@
 \CSLLeftMargin{38. }
-\CSLRightInline{Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie Y, et al.
-Shiny: Web application framework for r {[}Internet{]}.
-2021.
-Available from: \url{https://CRAN.R-project.org/package=shiny}}
+\CSLRightInline{Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie
+Y, et al. Shiny: Web application framework for r. 2021. Available:
+\url{https://CRAN.R-project.org/package=shiny}}
 
@@
 \CSLLeftMargin{39. }
-\CSLRightInline{Our World in Data.
-{COVID-19 Data Explorer} {[}Internet{]}.
-{Our World in Data}; 2020 {[}cited 2021 May 30{]}.
-Available from: \url{https://ourworldindata.org/coronavirus-data-explorer}}
+\CSLRightInline{Our World in Data. {COVID-19 Data Explorer}. {Our World
+in Data}; 2020 {[}cited 30 May 2021{]}. Available:
+\url{https://ourworldindata.org/coronavirus-data-explorer}}
 
@@
 \CSLLeftMargin{40. }
-\CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K, Ellis P, et al.
-\href{https://doi.org/10.5281/zenodo.3957489}{EpiNow2: Estimate real-time case counts and time-varying epidemiological parameters}.
--.
-2020;-(-):--.
-}
+\CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K,
+Ellis P, et al. EpiNow2: Estimate real-time case counts and time-varying
+epidemiological parameters. -. 2020;-: --.
+doi:\href{https://doi.org/10.5281/zenodo.3957489}{10.5281/zenodo.3957489}}
 
@@
 \CSLLeftMargin{41. }
-\CSLRightInline{Fraser C.
-Estimating {Individual} and {Household Reproduction Numbers} in an {Emerging Epidemic}.
-PLOS ONE {[}Internet{]}.
-2007 Aug 22 {[}cited 2021 Sep 29{]};2(8):e758.
-Available from: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0000758}}
+\CSLRightInline{Fraser C. Estimating {Individual} and {Household
+Reproduction Numbers} in an {Emerging Epidemic}. PLOS ONE. 2007;2: e758.
+doi:\href{https://doi.org/10.1371/journal.pone.0000758}{10.1371/journal.pone.0000758}}
 
@@
 \CSLLeftMargin{42. }
-\CSLRightInline{epiforecasts.io/covid.
-Covid-19: {Temporal} variation in transmission during the {COVID-19} outbreak {[}Internet{]}.
-{Covid-19}; 2020 {[}cited 2021 May 30{]}.
-Available from: \url{https://epiforecasts.io/covid/}}
+\CSLRightInline{epiforecasts.io/covid. Covid-19: {Temporal} variation in
+transmission during the {COVID-19} outbreak. {Covid-19}; 2020 {[}cited
+30 May 2021{]}. Available: \url{https://epiforecasts.io/covid/}}
 
@@
 \CSLLeftMargin{43. }
-\CSLRightInline{Sherratt K, Abbott S, Meakin SR, Hellewell J, Munday JD, Bosse N, et al.
-Exploring surveillance data biases when estimating the reproduction number: With insights into subpopulation transmission of {Covid-19} in {England}.
-2021 Mar 18 {[}cited 2021 Oct 14{]};2020.10.18.20214585.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v2}}
+\CSLRightInline{Sherratt K, Abbott S, Meakin SR, Hellewell J, Munday JD,
+Bosse N, et al. Exploring surveillance data biases when estimating the
+reproduction number: With insights into subpopulation transmission of
+{Covid-19} in {England}. 2021; 2020.10.18.20214585.
+doi:\href{https://doi.org/10.1101/2020.10.18.20214585}{10.1101/2020.10.18.20214585}}
 
@@
 \CSLLeftMargin{44. }
-\CSLRightInline{Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs HP, Bosse NI, et al.
-Estimating the time-varying reproduction number of {SARS-CoV-2} using national and subnational case counts.
-2020 Jun 1 {[}cited 2021 Oct 14{]};(5:112).
-Available from: \url{https://wellcomeopenresearch.org/articles/5-112}}
+\CSLRightInline{Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs
+HP, Bosse NI, et al. Estimating the time-varying reproduction number of
+{SARS-CoV-2} using national and subnational case counts. 2020 {[}cited
+14 Oct 2021{]}.
+doi:\href{https://doi.org/10.12688/wellcomeopenres.16006.1}{10.12688/wellcomeopenres.16006.1}}
 
@@
 \CSLLeftMargin{45. }
-\CSLRightInline{Xu B, Gutierrez B, Hill S, Scarpino S, Loskill A, Wu J, et al.
-Epidemiological data from the nCoV-2019 outbreak: Early descriptions from publicly available data {[}Internet{]}.
-2020.
-Available from: \url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}}
+\CSLRightInline{Xu B, Gutierrez B, Hill S, Scarpino S, Loskill A, Wu J,
+et al. Epidemiological data from the nCoV-2019 outbreak: Early
+descriptions from publicly available data. 2020. Available:
+\url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}}
 
@@
 \CSLLeftMargin{46. }
-\CSLRightInline{Stan Development Team. RStan: The r interface to stan {[}Internet{]}. 2020. Available from: \url{http://mc-stan.org/}}
+\CSLRightInline{Stan Development Team. RStan: The r interface to stan.
+2020. Available: \url{http://mc-stan.org/}}
 
@@
 \CSLLeftMargin{47. }
-\CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG.
-\href{https://doi.org/10.1371/journal.pcbi.1008618}{Evaluating epidemic forecasts in an interval format}.
-PLoS Comput Biol.
-2021 Feb;17(2):e1008618.
-}
+\CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG. Evaluating
+epidemic forecasts in an interval format. PLoS Comput Biol. 2021;17:
+e1008618.
+doi:\href{https://doi.org/10.1371/journal.pcbi.1008618}{10.1371/journal.pcbi.1008618}}
 
@@
 \CSLLeftMargin{48. }
-\CSLRightInline{Gneiting T, Raftery AE.
-Strictly proper scoring rules, prediction, and estimation.
-Journal of the American Statistical Association {[}Internet{]}.
-2007 Mar {[}cited 2020 Mar 22{]};102(477):359--78.
-Available from: \url{http://www.tandfonline.com/doi/abs/10.1198/016214506000001437}}
+\CSLRightInline{Gneiting T, Raftery AE. Strictly proper scoring rules,
+prediction, and estimation. Journal of the American Statistical
+Association. 2007;102: 359--378.
+doi:\href{https://doi.org/10.1198/016214506000001437}{10.1198/016214506000001437}}
 
@@
 \CSLLeftMargin{49. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. \href{https://doi.org/10.5281/zenodo.4618017}{Scoringutils: Utilities for scoring and assessing predictions}. 2020. }
+\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Scoringutils:
+Utilities for scoring and assessing predictions. 2020.
+doi:\href{https://doi.org/10.5281/zenodo.4618017}{10.5281/zenodo.4618017}}
 
@@
 \CSLLeftMargin{50. }
-\CSLRightInline{Deutsche Welle.
-Coronavirus: {Germany} to impose one-month partial lockdown \textbar{} {DW} \textbar{} 28.10.2020 {[}Internet{]}.
-2020 {[}cited 2021 Jun 29{]}.
-Available from: \url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}}
+\CSLRightInline{Deutsche Welle. Coronavirus: {Germany} to impose
+one-month partial lockdown \textbar{} {DW} \textbar{} 28.10.2020. 2020
+{[}cited 29 Jun 2021{]}. Available:
+\url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}}
 
@@
 \CSLLeftMargin{51. }
-\CSLRightInline{Ganyani T, Kremer C, Chen D, Torneri A, Faes C, Wallinga J, et al.
-Estimating the generation interval for coronavirus disease (COVID-19) based on symptom onset data, march 2020.
-Eurosurveillance.
-2020;25(17).
-}
+\CSLRightInline{Ganyani T, Kremer C, Chen D, Torneri A, Faes C, Wallinga
+J, et al. Estimating the generation interval for coronavirus disease
+(COVID-19) based on symptom onset data, march 2020. Eurosurveillance.
+2020;25. }
 
@@
 \CSLLeftMargin{52. }
-\CSLRightInline{Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith HR, et al.
-The incubation period of coronavirus disease 2019 (COVID-19) from publicly reported confirmed cases: Estimation and application.
-Annals of Internal Medicine.
-2020;172(9):577--82.
-}
+\CSLRightInline{Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith
+HR, et al. The incubation period of coronavirus disease 2019 (COVID-19)
+from publicly reported confirmed cases: Estimation and application.
+Annals of Internal Medicine. 2020;172: 577--582. }
 
@@
 \CSLLeftMargin{53. }
-\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J, Munday J, et al.
-\href{https://doi.org/10.5281/zenodo.3957539}{Covidregionaldata: Subnational data for the covid-19 outbreak}.
--.
-2020;-(-):--.
-}
+\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J,
+Munday J, et al. Covidregionaldata: Subnational data for the covid-19
+outbreak. -. 2020;-: --.
+doi:\href{https://doi.org/10.5281/zenodo.3957539}{10.5281/zenodo.3957539}}
 
@@
 \CSLLeftMargin{54. }
-\CSLRightInline{Evaluating the use of the reproduction number as an epidemiological tool, using spatio-temporal trends of the {Covid-19} outbreak in {England} \textbar{} {medRxiv} {[}Internet{]}.
-{[}cited 2021 May 30{]}.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}}
+\CSLRightInline{Evaluating the use of the reproduction number as an
+epidemiological tool, using spatio-temporal trends of the {Covid-19}
+outbreak in {England} \textbar{} {medRxiv}. {[}cited 30 May 2021{]}.
+Available:
+\url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}}
 
@@
 \CSLLeftMargin{55. }
-\CSLRightInline{Riutort-Mayol G, Bürkner P-C, Andersen MR, Solin A, Vehtari A.
-Practical hilbert space approximate bayesian gaussian processes for probabilistic programming {[}Internet{]}.
-2020.
-Available from: \url{https://arxiv.org/abs/2004.11408}}
+\CSLRightInline{Riutort-Mayol G, Bürkner P-C, Andersen MR, Solin A,
+Vehtari A. Practical hilbert space approximate bayesian gaussian
+processes for probabilistic programming. 2020. Available:
+\url{https://arxiv.org/abs/2004.11408}}
 
@@
 \CSLLeftMargin{56. }
-\CSLRightInline{Scott JA, Gandy A, Mishra S, Unwin J, Flaxman S, Bhatt S.
-Epidemia: Modeling of epidemics using hierarchical bayesian models {[}Internet{]}.
-2020.
-Available from: \url{https://imperialcollegelondon.github.io/epidemia/}}
+\CSLRightInline{Scott JA, Gandy A, Mishra S, Unwin J, Flaxman S, Bhatt
+S. Epidemia: Modeling of epidemics using hierarchical bayesian models.
+2020. Available:
+\url{https://imperialcollegelondon.github.io/epidemia/}}
 
@@
 \CSLLeftMargin{57. }
-\CSLRightInline{Bhatt S, Ferguson N, Flaxman S, Gandy A, Mishra S, Scott JA. Semi-{Mechanistic Bayesian} modeling of {COVID-19} with {Renewal Processes}. :14. }
+\CSLRightInline{Bhatt S, Ferguson N, Flaxman S, Gandy A, Mishra S, Scott
+JA. Semi-{Mechanistic Bayesian} modeling of {COVID-19} with {Renewal
+Processes}. : 14. }
 
@@
 
+\nolinenumbers
+
 \end{document}

### 2022-06-02 analysis/analysis.Rmd
Formatting requirements for manuscript submission

@@
 
-dailytruth_data
-
 crowdforecasts <- covid.german.forecasts::prediction_data %>% 
@@
 ```
-
-Looking at removed forecasts - yields nothing
-
-```{r}
-
-files <- list.files(here("crowd-forecast", "raw-forecast-data/"))
-
-raw_forecasts <- purrr::map_dfr(
-  files,
-  .f = function(x) {
-    out <- fread(
-      here("crowd-forecast", "raw-forecast-data/", x)
-    ) %>%
-      mutate(target_end_date = as.character(target_end_date))
-    } 
-) %>%
-  dplyr::filter(location_name %in% c("Germany", "Poland")) %>%
-  mutate(location = ifelse(location_name == "Germany", "GM", "PL"), 
-         distribution = ifelse(is.na(distribution), "log-normal", distribution), 
-         width = ifelse(is.na(width), shape_log_normal, width), 
-         target_type = ifelse(is.na(target_type), type, target_type))
-
-# use only the latest forecast from a given forecaster
-filtered_forecasts <- raw_forecasts %>%
-  group_by(forecaster_id, location, target_type) %>%
-  dplyr::filter(forecast_time == max(forecast_time)) %>%
-  ungroup()
-
-# replace forecast duration with exact data about forecast date and time
-# define function to do this for raw and filtered forecasts
-replace_date_and_time <- function(forecasts) {
-  forecast_times <- forecasts %>%
-    group_by(forecaster_id, location, target_type) %>%
-    summarise(forecast_time = unique(forecast_time)) %>%
-    ungroup() %>%
-    arrange(forecaster_id, forecast_time) %>%
-    group_by(forecaster_id) %>%
-    mutate(forecast_duration = c(NA, diff(forecast_time))) %>%
-    ungroup()
-
-  forecasts <- inner_join(
-    forecasts, forecast_times,
-    by = c("forecaster_id", "location", "target_type", "forecast_time")) %>%
-    mutate(forecast_week = epiweek(forecast_date),
-           target_end_date = as.Date(target_end_date)) %>%
-    select(-forecast_time)
-  return(forecasts)
-}
-
-# replace time with duration and date with epiweek
-raw_forecasts <- replace_date_and_time(raw_forecasts)
-filtered_forecasts <- replace_date_and_time(filtered_forecasts)
-
-# obtain quantiles from forecasts ----------------------------------------------
-# define function that returns quantiles depending on condition and distribution
-calculate_quantiles <- function(quantile_grid, median, width, forecast_type, 
-                                distribution, lower_90, upper_90) {
-  if (distribution == "log-normal") {
-    values <- list(exp(qnorm(
-      quantile_grid, mean = log(as.numeric(median)), sd = as.numeric(width)
-      )))
-  } else if (distribution == "normal") {
-    values <- list((qnorm(
-      quantile_grid, mean = (as.numeric(median)), sd = as.numeric(width)
-      )))
-  } else if (distribution == "cubic-normal") {
-    values <- list((qnorm(quantile_grid,
-     mean = (as.numeric(median) ^ (1 / 3)), sd = as.numeric(width))
-      ) ^ 3)
-  } else if (distribution == "fifth-power-normal") {
-    values <- list((qnorm(quantile_grid, 
-    mean = (as.numeric(median) ^ (1 / 5)), sd = as.numeric(width)
-      )) ^ 5)
-  } else if (distribution == "seventh-power-normal") {
-    values <- list((qnorm(quantile_grid,
-     mean = (as.numeric(median) ^ (1 / 7)), sd = as.numeric(width))
-     ) ^ 7)
-  }
-  return(values)
-}
-
-quantile_grid <- c(0.01, 0.025, seq(0.05, 0.95, 0.05), 0.975, 0.99)
-
-forecast_quantiles <- filtered_forecasts %>%
-  # disregard quantile forecasts this week
-  rowwise() %>%
-  mutate(quantile = list(quantile_grid),
-        value = calculate_quantiles(quantile_grid, median, width, 
-        forecast_type, distribution, lower_90, upper_90)) %>%
-  unnest(cols = c(quantile, value)) %>%
-  ungroup() %>%
-  mutate(type = ifelse(target_type == "cases", "case", "death"), 
-         target = paste0(horizon, " wk ahead inc ", type), 
-         type = "quantile")
-
-# omit forecasters who haven't forecasted at least two targets
-forecasters_to_omit <- forecast_quantiles %>%
-  select(forecaster_id, location, target_type, forecast_date) %>%
-  unique() %>%
-  group_by(forecaster_id) %>%
-  mutate(n = n(), flag = n >= 2) %>%
-  dplyr::filter(!flag) %>%
-  pull(forecaster_id) %>%
-  unique()
-
-```

### 2022-06-02 manuscript/manuscript.Rmd
Formatting requirements for manuscript submission

@@
 The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \ref{fig:agg-performance-all}F).
-Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2) and \ref{tab:score-table-4}).
-
-Generally, trends in overall performance were broadly similar across locations (Figures \ref{fig:performance-locations) and \ref{fig:performance-locations-rel}).
+Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
+
+Generally, trends in overall performance were broadly similar across locations (Figures \ref{fig:performance-locations} and \ref{fig:performance-locations-rel}).
 Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
@@
 Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
-An overview of all models and ensemble versions is shown in Table \ref{tab:table-ensemble-versions) in the SI.
+An overview of all models and ensemble versions is shown in Table \ref{tab:table-ensemble-versions} in the SI.
 
@@
 ```{r compare-forecasters, fig.cap="Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the 90\\% and 50\\% prediction intervals as well as the median (in order of increasing opacity).
+Shown are the median, as well as the 50\\% and 90\\% prediction intervals (in order of decreasing opacity).
 For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons)."}

### 2022-06-02 manuscript/manuscript.tex
Formatting requirements for manuscript submission

@@
 \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and
-Tables \textbackslash ref\{tab:score-table-2) and
-\ref{tab:score-table-4}).
+Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
 
 Generally, trends in overall performance were broadly similar across
-locations (Figures \textbackslash ref\{fig:performance-locations) and
+locations (Figures \ref{fig:performance-locations} and
 \ref{fig:performance-locations-rel}). Due to the differing population
@@
 overview of all models and ensemble versions is shown in Table
-\textbackslash ref\{tab:table-ensemble-versions) in the SI.
+\ref{tab:table-ensemble-versions} in the SI.
 
@@
 \includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} \caption{Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the 90\% and 50\% prediction intervals as well as the median (in order of increasing opacity).
+Shown are the median, as well as the 50\% and 90\% prediction intervals (in order of decreasing opacity).
 For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons).}\label{fig:compare-forecasters}

### 2022-08-04 manuscript/S1 Text.Rmd
final revisions

--- 2022-05-19 manuscript/manuscript.Rmd
@@
 ---
-title: "Comparing human and model-based forecasts of COVID-19 in Germany and Poland"
-header-includes:
-    - \usepackage{lineno}
-    - \linenumbers
-    -  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+title: "Text S1. Further details on the semi-mechanistic forecasting models"
 output: 
   bookdown::pdf_document2:
-    extra_dependencies: ["float"]
     keep_tex: true
-    toc: false
-linestretch: 2 
 bibliography:
@@
   - GermanPolishpaper.bib
-csl: vancouver.csl
 ---
 
-*Nikos I.
-Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy J.
-Quilty, Mark Jit, Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk*
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
-                      out.width = "100%", 
-                      fig.pos = "H", out.extra = "")
-
-library(kableExtra)
-library(magrittr)
-library(knitr)
-```
-
-# Abstract
-
-Forecasts based on epidemiological modelling have played an important role in shaping public policy throughout the COVID-19 pandemic.
-This modelling combines knowledge about infectious disease dynamics with the subjective opinion of the researcher who develops and refines the model and often also adjusts model outputs.
-Developing a forecast model is difficult, resource- and time-consuming.
-It is therefore worth asking what modelling is able to add beyond the subjective opinion of the researcher alone.
-To investigate this, we analysed different real-time forecasts of cases of and deaths from COVID-19 in Germany and Poland over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
-We compared crowd forecasts elicited from researchers and volunteers, against a) forecasts from two semi-mechanistic models based on common epidemiological assumptions and b) the ensemble of all other models submitted to the Forecast Hub.
-We found crowd forecasts, despite being overconfident, to outperform all other methods across all forecast horizons when forecasting cases (weighted interval score relative to the Hub ensemble 2 weeks ahead: 0.89).
-Forecasts based on computational models performed comparably better when predicting deaths (rel.
-WIS 1.26), suggesting that epidemiological modelling and human judgement can complement each other in important ways.
-
-# Author summary
-
-Mathematical models of COVID-19 have played a key role in informing governments across the world.
-While mathematical models are informed by our knowledge of infectious disease dynamics, they are ultimately developed and iteratively adjusted by the researchers and shaped by their subjective opinions.
-To investigate what modelling is able to add beyond the subjective opinion of the researcher alone, we compared human forecasts with model-based predictions of COVID-19 cases and deaths submitted to the so-called German/Polish Forecast Hub (which collates a variety of models from a range of teams).
-We found that our human forecasts consistently outperformed an aggregate of all available model-based forecasts when predicting cases, but not when predicting deaths.
-Our findings suggest that human insight may be most valuable when forecasting highly uncertain quantities, which depend on many factors that are hard to model using equations, while mathematical models may be most useful in settings like predicting deaths, where leading indicators with a clear connection to the target variable are available.
-This potentially has very relevant policy implications, as agencies informing policy-makers could benefit from routinely eliciting human forecasts in addition to model-based predictions to inform policies.
-
-# Introduction
-
-Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza [e.g.
-@mcgowanCollaborativeEffortsForecast2019; @reichCollaborativeMultiyearMultimodel2019; @shamanForecastingSeasonalOutbreaks2012; @biggerstaffResultsCentersDisease2016], dengue fever [e.g.
-@johanssonOpenChallengeAdvance2019; @yamanaSuperensembleForecastsDengue2016; @colon-gonzalezProbabilisticSeasonalDengue2021], ebola [e.g.
-@viboudRAPIDDEbolaForecasting2018; @funkAssessingPerformanceRealtime2019], chikungunya [e.g.
-@delvalleSummaryResults201420152018; @farrowHumanJudgmentApproach2017] and now COVID-19 [e.g.
-@funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021; @europeancovid-19forecasthubEuropeanCovid19Forecast2021].
-Applications of epidemiological models differ in the way they make statements about the future.
-Forecasts aim to predict the future as it will occur, while scenario modelling and projections aim to represent what the future could look like under certain scenario assumptions or if conditions stayed the same as they were in the past.
-Forecasts can be judged by comparing them against observed data.
-Since it is much harder to fairly assess the accuracy and usefulness of projections and scenario modelling in the same way, this work focuses on forecasts, which represent only a subset of all epidemiological modelling.
-
-Since March 2020, forecasts of COVID-19 from multiple teams have been collected, aggregated and compared by Forecast Hubs such as the US Forecast Hub [@cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], the German and Polish Forecast Hub [@bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021] and the European Forecast Hub [@europeancovid-19forecasthubEuropeanCovid19Forecast2021].
-Often, different individual forecasts are combined into a single forecast, e.g.
-by taking the mean or median of all forecasts.
-These ensemble forecasts usually tend to perform better and more consistently than individual forecasts (see e.g.
-@yamanaSuperensembleForecastsDengue2016; @reichAccuracyRealtimeMultimodel2019).
-
-Individual computational models usually rely to varying degrees on mechanistic assumptions about infectious disease dynamics (such as SIR-type compartmental models that aim to represent how individuals move from being susceptible to infected and then recovered or dead).
-Some are more statistical in nature (such as time series models that detect statistical patterns without explicitly modelling disease dynamics).
-How exactly such a mathematical or computational model is constructed and which assumptions are made depends on subjective opinion and judgement of the researcher who develops and refines the model.
-Models are commonly adjusted and improved based on whether the model output looks plausible to the researchers involved.
-
-The process of model construction and refinement is laborious and time-consuming, and it is therefore worth asking what modelling can add beyond the subjective judgment of the researcher alone.
-In this work, we ask this question specifically in the context of predictive performance, and set aside other advantages of epidemiological modelling (such as reproducibility or the ability to obtain a deeper fundamental understanding of how diseases spread).
-One natural way to do this is to compare the predictive performance of forecasts based on computational models (“model-based forecasts”) against forecasts made by individual humans without explicit use of a computer model (“direct human forecasts”) or a combination of multiple such forecasts (“crowd forecasts”).
-
-Previous work has examined such direct human forecasts in various contexts, such as geopolitics [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016], meta-science [@hoogeveenLaypeopleCanPredict2020; @replicationmarketsReplicationMarketsReliable2020], sports [@servan-schreiberPredictionMarketsDoes2004] and epidemiology [@farrowHumanJudgmentApproach2017; @mcandrewExpertJudgmentModel2020; @recchiaHowWellDid2021].
-Several prediction platforms [@metaculusPreliminaryLookMetaculus2020; @hypermindHypermindSupercollectiveIntelligence2021; @csetforetellCSETForetell2021] and prediction markets [@predictitPredictIt2021] have been created to collate expert and non-expert predictions.
-However, with the notable exception of @farrowHumanJudgmentApproach2017, these forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) prediction formats.
-Direct human forecasts may be able to take into account insights and relationships between variables which are hard to specify using epidemiological models.
-However, it is not entirely clear in which situations human forecasts perform well or badly.
-For example, @farrowHumanJudgmentApproach2017 found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available.
-However, humans tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown in these regions at the time.
-
-In this study, we analyse the performance of direct human forecasts relative to model-based forecasts and discuss the added benefit of epidemiological modelling over human judgement alone.
-As a case study, we use different forecasts, involving varying degrees of human intervention, which we submitted in real time to the German and Polish Forecast Hub.
-In contrast to @farrowHumanJudgmentApproach2017 we elicited not only point predictions, but full predictive distributions (“probabilistic forecasts”, see e.g.
-@heldProbabilisticForecastingInfectious2017) from participants.
-This allows us to compare not only predictive accuracy, but also how well human forecasters and model-based forecasts were able to quantify forecast uncertainty.
-
-# Methods
-
-We created and submitted the following forecasts to the German and Polish Forecast Hub: 1) a direct human forecast (henceforth called “crowd forecast”), elicited from participants through a web application [@crowdforecastr] and 2) two semi-mechanistic model-based forecasts ("renewal model" and "convolution model") informed by basic assumptions about COVID-19 epidemiology.
-While the two semi-mechanistic forecasts were necessarily shaped by our implicit assumptions and decisions, they were designed such as to minimise the amount of human intervention involved.
-For example, we refrained from adjusting model outputs or refining the models based on past performance.
-Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub [@bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021].
-All code and tools necessary to generate the forecasts and make a forecast submission are available in the `covid.german.forecasts` R package [@covidgermanforecasts].
-This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub.
-Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the German and Polish Forecast Hub.
-
-## Forecast targets and interaction with the German and Polish Forecast Hub
-
-The German and Polish Forecast Hub (now mostly merged into the @europeancovid-19forecasthubEuropeanCovid19Forecast2021) elicits predictions for various COVID-19 related forecast targets from different research groups every week.
-Forecasts had to be made every Monday (with submissions allowed until Tuesday 3pm) and were permitted to use any data that was available by Monday 11.59pm.
-We submitted forecasts for incident and cumulative weekly reported numbers of cases of and deaths from COVID-19 on a national level in Germany and Poland over a one to four week forecast horizon.
-Forecasts were submitted on Mondays, but weeks were defined as ending on a Saturday (and starting on Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26 days.
-Submissions were required in a quantile-based format with 23 quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10, 0.15, ..., 0.95, 0.975, 0.99.
-Forecasts submitted to the Forecast Hub were combined into different ensembles every week, with the median ensemble (i.e., the $\alpha$-quantile of the ensemble is given by the median of all submitted $\alpha$-quantiles) being the default ensemble shown on all official Forecast hub visualisations (https://kitmetricslab.github.io/forecasthub/forecast).
-
-Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish Forecast hub.
-Until December 14th, 2020, these data were sourced from the European Centre for Disease Control [@ecdcDownloadHistoricalData2020].
-After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period  [@rkiRKICoronavirusSARSCoV22021].
-These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, @forsal.plRozbieznosciStatystykachKoronawirusa2020), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, @aerzteblattSARSCoV2DiagnostikRKIPasst2020).
-The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \@ref(fig:daily-truth-update) and \@ref(fig:weekly-truth-update)).
-
-## Crowd forecasts
-
-Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application (https://cmmid-lshtm.shinyapps.io/crowd-forecast/).
-Weekly forecasts had to be submitted before Tuesday 12pm every week, but participants were asked to only use any information or data that was already available by Monday night.
-The application was built using the `shiny` and `golem` R packages [@golem; @shiny] and is available in the `crowdforecastr` R package [@crowdforecastr].
-To make a forecast in the application participants could select a predictive distribution (with the default being log-normal) to represent the probability that the forecasted quantity took certain values.
-Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in Figure \@ref(fig:screenshot) in the SI).
-The default shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.
-as $\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )$).
-A comparison of the crowd forecasts against the default baseline shown in the application is displayed in Figure \@ref(fig:compare-forecasters) in the Appendix.
-Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  @ourworldindataCOVID19DataExplorer2020.
-These data included, for example, notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
-From November 26 2020 on we displayed weekly small reports with a visualisation of past forecasts and scores on our website, epiforecasts.io.
-
-Forecasts were stored in a Google Sheet and downloaded, cleaned and processed every week for submission to the Forecast Hub.
-If a forecaster had submitted multiple predictions for a single target, only the latest submission was kept.
-Information on the chosen distribution as well as the parameters for median and width were used to obtain the required set of 23 quantiles from that distribution.
-Forecasts from all forecasters were then aggregated using an unweighted quantile-wise mean (i.e., the $\alpha$-quantile of the ensemble is given by the mean of all submitted $\alpha$-quantiles).
-To avoid issues with users trying out the app and submitting a random forecast, we required that a forecaster needed to make a forecast for at least two targets for a given forecast in order to be included in the crowd forecast ensemble.
-On a few occasions we deleted forecasts that were clearly the result of a user or software error (such as for example forecasts that were zero everywhere).
-
-individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation and were excluded from the submission as well as the analysis.
-
-Participants were recruited mostly within the Centre of Mathematical Modeling of Infectious Diseases at the London School of Hygiene & Tropical Medicine, but participants were also invited personally or via social media to submit predictions.
-Depending on whether they had a background in either statistics, forecasting or epidemiology, participants were asked to self-identify as 'experts' or 'non-experts'.
-
-The study was approved by the Observational / Interventions Research Ethics Committee at the London School of Hygiene & Tropical Medicine, LSHTM Ethics Reference: 22290.
-
-## Model-based forecasts
-
-We used two Bayesian semi-mechanistic models from the `EpiNow2` R package (version 1.3.3) as our model-based forecasts [@epinow2].
-The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths (see details in the SI).
-It estimated the effective reproduction number $R_t$ (the average number of people each person infected at time t is expected to infect in turn) and modelled future infections as a weighted sum of past infection multiplied by $R_t$.
-$R_t$ was assumed to stay constant beyond the forecast date, roughly corresponding to continuing the latest exponential trend in infections.
-On the 9th of November we altered the date when $R_t$ was assumed to be constant from two weeks prior to the date of the forecast to the forecast date, which we found to yield a more stable $R_t$ estimate.
-Reported case and death notifications were obtained by convolving predicted infections over data-based delay distributions [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation2020; @sherrattExploringSurveillanceData2021; @abbottEstimatingTimevaryingReproduction2020a] to model the time between infection and report date.
-The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately.
-Death forecasts from the renewal model were therefore not informed by past cases.
-One submission of the renewal model on December 28th 2020 was delayed and therefore not included in the official Forecast hub ensemble.
-
-The second model (“convolution model”, see details in SI) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses).
-The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model.
-The convolution model predicted deaths as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
-Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model with a multiplicative day-of-the-week effect [@epinow2].
-
-Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from [@kraemer2020epidemiological] with data available up to the 1st of August.
-All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan [@rstan] with each location and forecast target being fitted separately.
-
-## Analysis
-
-For the main analysis we focused mostly on two week ahead forecasts, as COVID-19 forecasts, especially for cases, were in the past found to have poor predictive performance  beyond this horizon [@bracherShorttermForecastingCOVID192021].
-Forecasts for cases were scored using the full period from October 2020 until March 2021.
-To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available.
-To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see Section \@ref(sensitivity-analysis) in the SI).
-Results remained broadly unchanged.
-
-Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) [@bracherEvaluatingEpidemicForecasts2021], the absolute error, relative bias, and empirical coverage of the 50% and 90% prediction intervals.
-The WIS is a proper scoring rule [@gneiting_strictly_2007], meaning that in expectation the score is optimised by reporting a predictive distribution that is identical to the true data-generating distribution.
-Forecasters are therefore incentivised to report their true belief about the future.
-The WIS can be understood as a generalisation of the absolute error to quantile-based forecasts (also meaning that smaller values are better) and can be decomposed into three separate penalties: forecast spread (i.e.
-uncertainty of forecasts), over-prediction and under-prediction.
-While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts.
-The bias metric [@funkAssessingPerformanceRealtime2019] we use captures how much probability mass of the forecast was above or below the true value (mapped to values between -1 and 1) and therefore represents a general tendency to over- or under-predict in relative terms.
-A value of -1 implies that all quantiles of the predictive distribution are below the observed value and a value of 1 that all quantiles are above the observed value.
-Empirical coverage is the percentage of observed values that fall inside a given prediction interval (e.g.
-how many observed values fall inside all 50% prediction intervals).
-Scoring metrics are explained in more detail in Table \@ref(tab:scoring-metrics) in the SI.
-All scores were calculated using the `scoringutils` R package [@scoringutils].
-
-At all stages of the evaluation our forecasts were compared to the median ensemble of all *other* models submitted to the German and Polish Forecast Hub ("Hub ensemble").
-This "Hub ensemble" was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see details in Section \@ref(contributions-hub), as well as in Table \@ref(tab:table-ensemble-versions) and Figure \@ref(fig:num-ensemble-members) in the SI).
-What we call "Hub ensemble" in this article therefore differs from the "official Hub ensemble" (here called "hub-ensemble-realised") which included crowd forecasts as well as renewal model forecasts.
-To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e.
-we divided the average scores for a given model by the average score achieved by the Hub ensemble on the same set of forecasts (with values >1 implying worse and values <1 implying better performance than the Hub ensemble).
-In addition to comparing our forecasts against the hub ensemble excluding our models, we also assessed the impact of our forecasts on the performance of the forecasting hub by recalculating separate versions of the Hub ensemble with only some (or all) of our forecasts included.
-Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
-
-# Results
-
-## Crowd forecast participation
-
-A total number of 32 participants submitted forecasts, 17 of those self-identified as 'expert' in either forecasting or epidemiology.
-The median number of forecasters for any given forecast target was 6, the minimum 2 and the maximum 10.
-The mean number of submissions from an individual forecaster was 4.7 but the median number was only one - most participants dropped out after their first submission.
-Only two participants submitted a forecast every single week, both of whom are authors on this study.
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-v4.png")
-```
-
-```{r}
-caption <- "A, C: Visualisation of 50\\% prediction intervals of two week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS."
-```
-
-```{r forecasts-and-truth, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-2.png")
-```
-
-## Case Forecasts
-
-For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure \@ref(fig:performance-locations-rel)A).
-For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \@ref(tab:score-table-2)).
-Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Figure \@ref(fig:distribution-scores)).
-Overall, low variance in forecast performance was closely linked with good mean performance (Figures \@ref(fig:agg-performance-all)H and and \@ref(fig:agg-performance-all)A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores)), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
-WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
-
-To varying degrees, all forecasts exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened.
-For example, all forecasts failed to predict the change in trend from increase to decrease that happened in November in Germany and severely overshot reported cases (Figure \@ref(fig:forecasts-and-truth)A).
-This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past of observations.
-The Hub ensemble and the crowd forecast, which had both been under-predicting throughout October, also failed to predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 [@deutschewelleCoronavirusGermanyImpose2020] and the change in the testing regime (with stricter test criteria) on November 11th 2020 [@aerzteblattSARSCoV2DiagnostikRKIPasst2020], were fastest to adapt to the new trend, and the Hub ensemble slowest.
-In December, cases rose again in Germany, with all models under-predicting this growth to varying extents.
-As in October, the renewal model captured the phase of exponential growth in cases slightly better than other approaches, but again overshot when reported case numbers fell over Christmas.
-The large variance in predictions in January in Germany (severe under-prediction followed by severe over-prediction) may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.
-Similar trends in performance were evident in Poland, with the crowd forecast quickest at adapting to the change in trend in November.
-In general, there were fewer large outlier forecasts in Poland and in particular the renewal model performed more in line with other forecasts there.
-
-All forecasting approaches, including the Hub ensemble, were overconfident, i.e.
-they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
-Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts.
-This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \@ref(fig:agg-performance-all)E) and only showed a small increase in uncertainty across forecast horizons.
-The crowd forecasts prediction intervals were also noticeably narrower than the default baseline shown to forecasters in the application (see Figure \@ref(fig:compare-forecasters)).
-
-In spite of good performance in terms of the absolute error (Figure \@ref(fig:agg-performance-all)G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Figure \@ref(fig:agg-performance-all)C,D and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
-Despite worse performance in terms of absolute error (Figure \@ref(fig:agg-performance-all)G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
-The crowd forecasts, on the other hand, showed a smaller bias than the renewal model, but were overconfident.
-
-The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons.
-The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \@ref(fig:agg-performance-all)F).
-Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \@ref(fig:agg-performance-all)A and \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
-
-Generally, trends in overall performance were broadly similar across locations (Figures \@ref(fig:performance-locations) and \@ref(fig:performance-locations-rel)).
-Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
-However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \@ref(fig:performance-locations-rel)A, \@ref(fig:performance-locations-rel)G, \@ref(fig:agg-performance-all-Germany), \@ref(fig:agg-performance-all-Poland)).
-
-## Death Forecasts
-
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B).
-Relative WIS values for the models two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1 (Hub ensemble) and 1.79 (renewal model).
-The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B), and also better than the convolution model three and four weeks ahead.
-Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate $R_t$ trace from deaths, does not use the available information efficiently.
-The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \@ref(fig:agg-performance-all)B, Table \@ref(tab:score-table-4)).
-
-As past cases and hospitalisations can be used as predictors, predicting a change in trend may be easier for deaths than for cases.
-Even though all forecasts generally struggled with this, there were some instances where changing trends were well captured or even anticipated.
-In Poland, for example, the Hub ensemble was able to capture or even anticipate the peak in deaths in December quite well (whereas the renewal model and crowd forecast did not).
-The renewal model, which mostly exhibited trend-following behaviour, correctly predicted another increase in weekly deaths in mid-January (potentially based on changes in daily deaths, as the renewal model did not know about past cases).
-In Germany in early January, all models predicted a decrease in deaths two to three weeks before it actually happened.
-Predictions from the renewal model at that time were likely strongly influenced by an unexpected drop in reported deaths in December.
-The other forecasting approaches and in particular, the convolution model may have been affected by potentially under-reported case numbers around Christmas.
-When the decrease that all models had predicted to happen in early January failed to materialise, the renewal model and the crowd forecast noticeably over-corrected and over-predicted deaths in the following weeks, while the Hub ensemble, and to a slightly lesser degree, the convolution model were able to capture the downturn well when it finally happened at the end of January.
-
-Death forecasts, generally, showed greater coverage of the 50% and 90% prediction intervals than case forecasts and no decrease in coverage across forecast horizons, indicating that it might be easier to appropriately quantify uncertainty for death forecasts.
-The Hub ensemble had the greatest coverage, with empirical coverage of the 50% and 90% prediction intervals exceeding 50%, and 90%, respectively, across all forecast horizons.
-Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
-As for cases, the crowd forecast tended to have the narrowest prediction intervals and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
-The convolution model had relatively narrow prediction intervals for short forecast horizons, but had rapidly (and non-linearly) increasing uncertainty for longer forecast horizons, driven by increasing uncertainty in the underlying case forecasts.
-
-For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \@ref(fig:agg-performance-all)F.
-The convolution model had a strong tendency to under-predict, with the magnitude of under-prediction steadily decreasing for longer forecast horizons.
-The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction.
-For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \@ref(fig:agg-performance-all)A, \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2), \@ref(tab:score-table-4)).
-
-```{r}
-caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
-Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores."
-```
-
-```{r distribution-scores, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-2.png")
-```
-
-```{r}
-caption <- "Visualisation of relative aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
-“Hub-ensemble” \textit{excludes} all our models, Hub-ensemble-all \textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
-```
-
-```{r agg-performance-ensemble-rel, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-v4.png")
-```
-
-## Contribution to the Forecast Hub {#contributions-hub}
-
-Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (“hub-ensemble-realised”), while the convolution model was never included as it was deemed too similar to the existing renewal model.
-In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on 28 December 2020 over the Christmas period) and a maximum of 10.
-Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
-An overview of all models and ensemble versions is shown in Table \@ref(tab:table-ensemble-versions) in the SI.
-
-For cases, our contributions (compared to the Hub ensemble without our contributions) consistently improved performance across all forecasting horizons (rel.
-WIS 0.9 two weeks ahead, Table \@ref(tab:score-table-ensemble-2)).
-Contributions from the crowd forecasts alone also improved performance of the Hub ensemble across all forecast horizons, while contributions from the renewal model had a negative effect for longer horizons (rel.
-WIS 1.02 three weeks ahead, 1.06 four weeks ahead).
-The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model have improved performance (Table \@ref(tab:score-table-ensemble-4)).
-The realised ensemble performed comparably to the crowd forecasts for predictions one to two weeks ahead, and worse for greater forecast horizons.
-
-For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel.
-WIS of the Hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \@ref(tab:score-table-ensemble-2) and \@ref(tab:score-table-ensemble-4)).
-Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons).
-This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \@ref(fig:agg-performance-all)) and especially worse for longer horizons.
-
-We also considered the impact of our contributions on a version of the Hub ensemble constructed by taking the quantile-wise mean, rather than the median. 
-<!-- In general, the median ensemble tended to perform slightly better than the mean ensemble - needs more analysis -->
-General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \@ref(fig:agg-performance-ensemble-rel)B and \@ref(fig:agg-performance-ensemble-mean)B).
-This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far.
-For both the mean and the median ensemble, changes in performance from adding or removing models were of a similar order of magnitude, suggesting that at least in this instance, with a relatively small ensemble size, the median ensemble was not necessarily more ‘robust’ to changes than the mean ensemble.
-However, the ensemble version with all our forecasts included (“hub-ensemble-with-all”) tended to perform relatively better for the median ensemble than the mean ensemble, suggesting that adding more models may be more beneficial or ‘safer’ for the median than for the mean ensemble as directional errors can more easily cancel out than errors in absolute terms.
-
-# Discussion
-
-Epidemiological forecasting modelling combines knowledge about infectious disease dynamics with the subjective opinion of the researcher who develops and refines the model.
-In this study, we compared forecasts of cases of and deaths from COVID-19 in Germany and Poland based purely on human judgement and elicited from a crowd of researchers and volunteers against forecasts from two semi-mechanistic epidemiological models.
-In spite of the small number of participants and a general tendency to be overconfident, crowd forecasts consistently outperformed our epidemiological models as well as the Hub ensemble when forecasting cases but not when forecasting deaths.
-This suggests that humans might be relatively good at foreseeing trends that are hard to model but may struggle to form an intuition for the exact relationship between cases and deaths.
-
-Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches [e.g.
-@funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], or exclusively on human forecasts [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016; @mcandrewExpertJudgmentModel2020; @recchiaHowWellDid2021].
-In contrast, we directly compared human and model-based forecasts.
-This is similar to the approach taken by @farrowHumanJudgmentApproach2017, but extends it in several ways.
-While Farrow et al.
-only asked for point predictions and constructed a predictive distribution from these, we asked participants to provide a full predictive distribution, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse how humans quantified their uncertainty.
-In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-based insight.
-In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs [@cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @europeancovid-19forecasthubEuropeanCovid19Forecast2021; @funkShorttermForecastsInform2020].
-
-The strong performance of crowd forecasts in our study is in line with results from Farrow et al.
-who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants.
-The advantage of crowd forecasts we observed over our semi-mechanistic models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models.
-However, this probably explains only part of the difference, and performance relative to the Hub ensemble strongly suggests that human insight is valuable when forecasting highly volatile and potentially hard-to-predict quantities such as case numbers.
-One potential explanation is that humans can have access to data that is not available to or hard to integrate into model-based forecasts.
-Relatively good performance of our semi-mechanistic models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time.
-This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data).
-The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \@ref(fig:forecasts-and-truth)A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting which have less of an influence on weekly reporting.
-
-Our results suggest that human intervention may be less beneficial when forecasting deaths (especially at shorter horizons, when deaths are largely dependent on already observed cases), which benefits from the ability to model the delays and exact epidemiological relationships between different leading and lagged indicators.
-Relatively good performance of the convolution model, especially compared to the poor performance of the renewal model on deaths (which used only deaths to estimate and predict the effective reproduction number) underlines the importance of including leading indicators such as cases as a predictor for deaths.
-
-Given the low number of participants in our study, it is difficult to generalise conclusions about crowd predictions to other settings.
-Using R shiny as a platform for the web application arguably created some limits to user experience and performance, influencing the number of participants and potentially creating a self-selection effect.
-Motivating forecasters to contribute regularly proved challenging, especially given that the majority of our participants were from the UK and may not have been familiar with all relevant details of the situation in Germany and Poland.
-On the other hand, R shiny facilitated quick development and allowed us to provide our crowd forecasting tooling as an open source R package, meaning that it is available for others to use, for example in settings like early-stage outbreaks where model-based forecasts are not available.
-In light of the relatively small number of Hub ensemble models, performance of the Hub ensemble is also difficult to generalise.
-More research is needed to replicate these findings and investigate how crowd forecasts compare against the types of models and model ensembles policy makers use to inform their decisions.
-
-Our work suggests that crowd forecasts and model-based forecasts could have different strengths and may be able to complement each other.
-When choosing a suitable approach for a given task it is important to take into account how the output will be used.
-In this work we focused on forecasts (which aim to predict future data points whilst accounting for all factors that might influence them), whereas policy makers might be more interested in projections (which show what would happen in the absence of any events that could change the trend) or scenario modelling.
-Forecasts may not be a suitable basis for informing policy decisions, if forecasters already have factored in the expectation of a future intervention.
-Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting projections that are not influenced by implicit assumptions about the future from humans may be harder.
-
-Further work should explore the effects of humans refining their mathematical models or changing model outputs in more detail.
-Model-based forecasts could be used as an input to human judgement, with researchers adjusting predictions generated by models.
-Seeing a model-based forecast could help humans calibrate uncertainty better, while allowing for manual intervention to adapt spurious trend predictions.
-Tools need to be developed to facilitate this process at a larger scale.
-Human insight could also be used as an input to models.
-Such a ‘hybrid’ forecasting approach could for example ask humans to predict the trend of the effective reproduction number $R_t$ or the doubling rate (i.e.
-how the epidemic evolves) into the future and use this to estimate the exact number of cases, hospitalisations or deaths this would imply.
-In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust and widen prediction intervals may be another promising approach.
-Crowd forecasting in general could benefit greatly from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile to further develop and explore.
-
-\clearpage
-
-**Acknowledgements**
-
-NIB received funding from the Health Protection Research Unit (grant code NIHR200908, https://www.nihr.ac.uk/).
-SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/).
-The work of JB was supported by the Helmholtz Foundation (https://www.helmholtz.de/) via the SIMCARD Information and Data Science Pilot Project.
-This research was partly funded by the National Institute for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 & 16/136/46) using UK aid from the UK Government to support global health research.
-The views expressed in this publication are those of the author(s) and not necessarily those of the NIHR or the UK Department of Health and Social Care.
-BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859, https://www.gatesfoundation.org/).
-EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908, https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688, https://ec.europa.eu/programmes/horizon2020/).
-AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/), and the Academy of Medical Sciences (https://acmedsci.ac.uk/).
-SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/), and the NIHR (NIHR200908, https://www.nihr.ac.uk/).
-
-We thank all forecasters who participated in this study for their contribution.
-
-We would also like to acknowledge (in a randomised order) the members of Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group at the the London School of Hygiene & Tropical Medicine: Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie Diamond, Katherine E.
-Atkins, Rein M G J Houben, Jiayao Lei, Rachel Lowe, David Simons, Sophie R Meakin, Nicholas G.
-Davies, Timothy W Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly, Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas, Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson, Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun, Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche, James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday, Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael Pung, Anna M Foss.
-
-\clearpage
-
-\beginsupplement
-
-# (APPENDIX) Supplementary information {-}
-
-# Supplementary information
-
-## Scoring metrics used
-
-```{r scoring-metrics}
-wis <- list(
-  Metric = "WIS (Weighted) interval score", 
-  `Explanation` = r"(The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
-It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
-The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction.
-For a single interval, the score is computed as
-  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
-  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e.
-the lower and upper bound of a single prediction interval.
-For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
-  $$WIS = \frac{1}{K + 0.5} \cdot \left( w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y) \right), $$
-  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
-
-Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.)", 
-  `Caveats` = "The wis is based on measures of absolute error. When averaging across multiple targets, it will therefore be dominated by targets with higher absolute values.",
-  `References` = ""
-)
-
-interval_coverage <- list(
-  `Metric` = "Interval coverage", 
-  `Explanation` = r"(Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
-Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
-we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.)",
-  `Caveats` = "",
-  `References` = ""
-)
-
-bias <- list(
-  `Metric` = "Bias", 
-  `Explanation` = r"((Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict.
-Values are between -1 and 1 and 0 ideally.
-For continuous forecasts, bias is given as
-$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
-where $F$ is the CDF of the predictive distribution and $y$ is the observed value.
-
-For quantile forecasts, $F(y)$ is replaced by a quantile rank.
-The appropriate quantile rank is determined by whether the median forecast is below  or above the true value.
-We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.
-
-In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
-It is therefore a more robust measurement.)",
-  `Caveats` = "",
-  `References` = ""
-)
-
-data <- rbind(as.data.frame(wis), 
-              as.data.frame(interval_coverage),
-              as.data.frame(bias))
-
-data[, 1:2] %>%
-  kableExtra::kbl(format = "latex", booktabs = TRUE, 
-                  escape = FALSE,
-                  caption = "Overview of the scoring metrics used.",
-                  longtable = TRUE,
-                  linesep = c('\\addlinespace \\addlinespace')) %>%
-  kableExtra::column_spec(1, width = "2.5cm") %>%
-  kableExtra::column_spec(2, width = "13.0cm") %>%
-  kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))
-
-```
-
-\clearpage
-
-## The crowdforecasting app
-
-```{r}
-caption <- "Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021). "
-```
-
-```{r screenshot, fig.cap=caption}
-knitr::include_graphics("../crowd-forecast/Screenshot-forecasting-app.png")
-```
-
-\clearpage
-
-## Further details on the semi-mechanistic forecasting models
+## Text S1. Further details on the semi-mechanistic forecasting models
 
@@
 \clearpage
-
-```{r}
-add_caption <- function(table, caption, label = NULL) {
-  if (is.null(label)) {
-    label <- paste0("tab:", opts_current$get("label"))
-  }
-  table <- gsub(pattern = "begin\\{table\\}\\[!h\\]",
-                replacement = paste0("begin\\{table\\}[!h]\n", 
-                                     "\\\\caption\\{",
-                                     "\\\\\\label\\{", label, "\\}",
-                                     caption,
-                                     "\\\\\\\\\\\\hspace{\\\\textwidth}\\}\n"),
-                x = table)
-  return(table)
-}
-
-```
-
-## Tables with results of the forecast evaluation
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-2}
-table <- readRDS("../analysis/plots/table_scores_2_ahead.rds")
-add_caption(table, caption, label = "tab:score-table-2")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-4}
-table <- readRDS("../analysis/plots/table_scores_4_ahead.rds")
-add_caption(table, caption, label = "tab:score-table-4")
-
-```
-
-\clearpage
-
-## Aggregate performance by location
-
-### Performance in Germany
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all-Germany, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-Germany-v4.png")
-```
-
-### Performance in Poland
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all-Poland, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-Poland-v4.png")
-```
-
-### Performance across locations in absolute terms
-```{r}
-caption <- "Visualisation of aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of WIS values."
-```
-
-```{r performance-locations, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-v4.png")
-```
-
-## Performance across locations in relative terms
-
-```{r}
-caption <- "Visualisation of relative aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals.
-E: Dispersion.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast.
-H.
-Standard deviation of WIS values."
-```
-
-```{r performance-locations-rel, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4.png")
-```
-
-\clearpage
-
-## Visualisation of daily reported cases and deaths
-
-```{r}
-caption <- "Visualisation of daily report data. The black line represents weekly data divided by seven. Data were last accessed through the German and Polish Forecast Hub on August 21 2021."
-```
-
-```{r daily-truth, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/daily_truth.png")
-```
-
-```{r}
-caption <- "Visualisation of the absolute difference between the daily report data at the time and the data now.
-In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
-```
-
-```{r daily-truth-update, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/daily-data-updates.png")
-```
-
-```{r}
-caption <- "Visualisation of the relative difference between the weekly report data at the time and the data now.
-Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
-```
-
-```{r weekly-truth-update, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/weekly-data-updates.png")
-```
-
-\clearpage
-
-## Visualisation of scores and forecasts 1, 3, 4 weeks ahead
-
-```{r}
-caption <- "A, C: Visualisation of 50\\% prediction intervals of one week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS."
-```
-
-```{r forecasts-and-truth-1, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-1.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one", replacement = "three")
-```
-
-```{r forecasts-and-truth-3, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-3.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-```
-
-```{r forecasts-and-truth-4, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-4.png")
-```
-
-\clearpage
-
-## Distribution of scores
-
-### Absolute scores
-
-```{r}
-caption <- "A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country."
-```
-
-```{r distribution-scores-1, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-1.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one", replacement = "three")
-```
-
-```{r distribution-scores-3, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-3.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-```
-
-```{r distribution-scores-4, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-4.png")
-```
-
-### Ranks achieved by forecasts
-
-```{r}
-caption <- "A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country."
-```
-
-```{r distribution-scores-ranks-1, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-1-ranks.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one", replacement = "two")
-```
-
-```{r distribution-scores-ranks-2, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-2-ranks.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "two", replacement = "three")
-```
-
-```{r distribution-scores-ranks-3, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-3-ranks.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-```
-
-```{r distribution-scores-ranks-4, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-4-ranks.png")
-```
-
-```{r distribution-scores-differences, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
-knitr::include_graphics("../analysis/plots/difference-wis-crowd-ensemble.png")
-```
-
-```{r distribution-scores-differences-renewal, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
-knitr::include_graphics("../analysis/plots/difference-wis-crowd-renewal.png")
-```
-
-\newpage
-
-## Comparison of ensembles
-
-### Performance visualisation mean ensemble
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble” \textit{excludes} all our models, Hub-ensemble-all \textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
-Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
-```
-
-```{r agg-performance-ensemble-mean, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-mean-v4.png")
-```
-
-### Tables median ensemble
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-ensemble-2}
-table <- readRDS("../analysis/plots/table_median-ensemble_scores_2_ahead.rds")
-add_caption(table, caption)
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-ensemble-4}
-table <- readRDS("../analysis/plots/table_median-ensemble_scores_4_ahead.rds")
-add_caption(table, caption)
-
-```
-
-### Tables mean ensemble
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-ensemble-mean-2}
-table <- readRDS("../analysis/plots/table_mean-ensemble_scores_2_ahead.rds")
-add_caption(table, caption)
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-ensemble-mean-4}
-table <- readRDS("../analysis/plots/table_mean-ensemble_scores_4_ahead.rds")
-add_caption(table, caption)
-```
-
-\clearpage
-
-## Sensitivity analysis
-
-In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later.
-This sensitivity shows performance of all models restricted to the period from December 14 2020 until March 1st 2021 where all models were available.
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all-late, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-late-period-v4.png")
-```
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-late-2}
-table <- readRDS("../analysis/plots/table-late-period_2_ahead.rds")
-add_caption(table, caption)
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-late-4}
-table <- readRDS("../analysis/plots/table-late-period_4_ahead.rds")
-add_caption(table, caption)
-
-```
-
-\clearpage
-
-## Overview of models and forecasters
-
-```{r table-ensemble-versions}
-
-rbind(
-  list(
-    Name = "Hub-ensemble-realised", 
-    `Explanation` = "Official Forecast Hub median ensemble.
-Created by the Forecast Hub officially under the name 'KITCOVIDhub-median\\_ensemble' and used as the default ensemble.
-Included are our crowd forecasts as well as the renewal model (with one missed submission on December 28 2020, but not the convolution model which was deemed to similar to the renewal model."
-  ),
-  list(
-    Name = "Hub-ensemble-realised-mean", 
-    `Explanation` = "Official Forecast Hub mean ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-mean\\_ensemble'."
-  ),
-  list(Name = "", Explanation = ""),
-
-  list(
-    Name = "Hub-ensemble", 
-    `Explanation` = "Version of the official Hub median ensemble which excludes all our contributions."
-  ),
-  list(
-    Name = "Hub-ensemble-mean", 
-    `Explanation` = "Version of the official Hub mean ensemble which excludes all our contributions."
-  ),
-  list(
-    Name = "Hub-ensemble-with-renewal, 
-    Hub-ensemble-with-renewal-mean", 
-    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Renewal model."
-  ),
-  list(
-    Name = "Hub-ensemble-with-crowd, 
-    Hub-ensemble-with-crowd-mean", 
-    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Crowd forecast."
-  ),
-  list(
-    Name = "Hub-ensemble-with-convolution, 
-    Hub-ensemble-with-convolution-mean", 
-    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Convolution model (which originally was never included in any official Hub ensemble)."
-  ),
-    list(
-    Name = "Hub-ensemble-with-all, 
-    Hub-ensemble-with-all-mean", 
-    `Explanation` = "Versions of the official Hub ensembles which includes all our contributions.
-For cases, this is identical to the official Hub ensembles, but for deaths the convolution model was added."
-  ),
-
-  list(Name = "", Explanation = ""),
-  list(
-    Name = "Crowd forecast", 
-    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'"
-  ),  
-  list(
-    Name = "Renewal model", 
-    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'"
-  ),  
-  list(
-    Name = "Convolution model", 
-    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\\_secondary'"
-  )
-) %>%
-  kableExtra::kbl(format = "latex", booktabs = TRUE, 
-                  escape = FALSE,
-                  caption = "Overview of the models and ensembles used.",
-                  longtable = TRUE,
-                  linesep = c('\\addlinespace \\addlinespace')) %>%
-  kableExtra::column_spec(1, width = "4.5cm") %>%
-  kableExtra::column_spec(2, width = "11.0cm") %>%
-  kableExtra::kable_styling(latex_options = c("striped", "repeat_header")) 
-```
-
-```{r num-forecasters, fig.cap="Number of participants who submitted a forecast over time."}
-knitr::include_graphics("../analysis/plots/number-forecasters.png")
-```
-
-```{r num-ensemble-members, fig.cap="Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
-Note that the renewal model was not included in the ensemble on December 28th 2020."}
-knitr::include_graphics("../analysis/plots/ensemble-members.png")
-```
-
-\clearpage
-
-## Comparison of crowd forecasts and application baseline
-
-```{r compare-forecasters, fig.cap="Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the 90\\% and 50\\% prediction intervals as well as the median (in order of increasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons)."}
-knitr::include_graphics("../analysis/plots/comparison-forecast-interals.png")
-```

### 2022-08-04 manuscript/S10 Table.Rmd
final revisions

--- 2022-05-19 manuscript/manuscript.Rmd
@@
 ---
-title: "Comparing human and model-based forecasts of COVID-19 in Germany and Poland"
-header-includes:
-    - \usepackage{lineno}
-    - \linenumbers
-    -  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 output: 
-  bookdown::pdf_document2:
-    extra_dependencies: ["float"]
+  pdf_document:
     keep_tex: true
-    toc: false
-linestretch: 2 
-bibliography:
-  - references.bib
-  - GermanPolishpaper.bib
-csl: vancouver.csl
 ---
 
-*Nikos I.
-Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy J.
-Quilty, Mark Jit, Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk*
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
-                      out.width = "100%", 
-                      fig.pos = "H", out.extra = "")
-
-library(kableExtra)
-library(magrittr)
-library(knitr)
-```
-
-# Abstract
-
-Forecasts based on epidemiological modelling have played an important role in shaping public policy throughout the COVID-19 pandemic.
-This modelling combines knowledge about infectious disease dynamics with the subjective opinion of the researcher who develops and refines the model and often also adjusts model outputs.
-Developing a forecast model is difficult, resource- and time-consuming.
-It is therefore worth asking what modelling is able to add beyond the subjective opinion of the researcher alone.
-To investigate this, we analysed different real-time forecasts of cases of and deaths from COVID-19 in Germany and Poland over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
-We compared crowd forecasts elicited from researchers and volunteers, against a) forecasts from two semi-mechanistic models based on common epidemiological assumptions and b) the ensemble of all other models submitted to the Forecast Hub.
-We found crowd forecasts, despite being overconfident, to outperform all other methods across all forecast horizons when forecasting cases (weighted interval score relative to the Hub ensemble 2 weeks ahead: 0.89).
-Forecasts based on computational models performed comparably better when predicting deaths (rel.
-WIS 1.26), suggesting that epidemiological modelling and human judgement can complement each other in important ways.
-
-# Author summary
-
-Mathematical models of COVID-19 have played a key role in informing governments across the world.
-While mathematical models are informed by our knowledge of infectious disease dynamics, they are ultimately developed and iteratively adjusted by the researchers and shaped by their subjective opinions.
-To investigate what modelling is able to add beyond the subjective opinion of the researcher alone, we compared human forecasts with model-based predictions of COVID-19 cases and deaths submitted to the so-called German/Polish Forecast Hub (which collates a variety of models from a range of teams).
-We found that our human forecasts consistently outperformed an aggregate of all available model-based forecasts when predicting cases, but not when predicting deaths.
-Our findings suggest that human insight may be most valuable when forecasting highly uncertain quantities, which depend on many factors that are hard to model using equations, while mathematical models may be most useful in settings like predicting deaths, where leading indicators with a clear connection to the target variable are available.
-This potentially has very relevant policy implications, as agencies informing policy-makers could benefit from routinely eliciting human forecasts in addition to model-based predictions to inform policies.
-
-# Introduction
-
-Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza [e.g.
-@mcgowanCollaborativeEffortsForecast2019; @reichCollaborativeMultiyearMultimodel2019; @shamanForecastingSeasonalOutbreaks2012; @biggerstaffResultsCentersDisease2016], dengue fever [e.g.
-@johanssonOpenChallengeAdvance2019; @yamanaSuperensembleForecastsDengue2016; @colon-gonzalezProbabilisticSeasonalDengue2021], ebola [e.g.
-@viboudRAPIDDEbolaForecasting2018; @funkAssessingPerformanceRealtime2019], chikungunya [e.g.
-@delvalleSummaryResults201420152018; @farrowHumanJudgmentApproach2017] and now COVID-19 [e.g.
-@funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021; @europeancovid-19forecasthubEuropeanCovid19Forecast2021].
-Applications of epidemiological models differ in the way they make statements about the future.
-Forecasts aim to predict the future as it will occur, while scenario modelling and projections aim to represent what the future could look like under certain scenario assumptions or if conditions stayed the same as they were in the past.
-Forecasts can be judged by comparing them against observed data.
-Since it is much harder to fairly assess the accuracy and usefulness of projections and scenario modelling in the same way, this work focuses on forecasts, which represent only a subset of all epidemiological modelling.
-
-Since March 2020, forecasts of COVID-19 from multiple teams have been collected, aggregated and compared by Forecast Hubs such as the US Forecast Hub [@cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], the German and Polish Forecast Hub [@bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021] and the European Forecast Hub [@europeancovid-19forecasthubEuropeanCovid19Forecast2021].
-Often, different individual forecasts are combined into a single forecast, e.g.
-by taking the mean or median of all forecasts.
-These ensemble forecasts usually tend to perform better and more consistently than individual forecasts (see e.g.
-@yamanaSuperensembleForecastsDengue2016; @reichAccuracyRealtimeMultimodel2019).
-
-Individual computational models usually rely to varying degrees on mechanistic assumptions about infectious disease dynamics (such as SIR-type compartmental models that aim to represent how individuals move from being susceptible to infected and then recovered or dead).
-Some are more statistical in nature (such as time series models that detect statistical patterns without explicitly modelling disease dynamics).
-How exactly such a mathematical or computational model is constructed and which assumptions are made depends on subjective opinion and judgement of the researcher who develops and refines the model.
-Models are commonly adjusted and improved based on whether the model output looks plausible to the researchers involved.
-
-The process of model construction and refinement is laborious and time-consuming, and it is therefore worth asking what modelling can add beyond the subjective judgment of the researcher alone.
-In this work, we ask this question specifically in the context of predictive performance, and set aside other advantages of epidemiological modelling (such as reproducibility or the ability to obtain a deeper fundamental understanding of how diseases spread).
-One natural way to do this is to compare the predictive performance of forecasts based on computational models (“model-based forecasts”) against forecasts made by individual humans without explicit use of a computer model (“direct human forecasts”) or a combination of multiple such forecasts (“crowd forecasts”).
-
-Previous work has examined such direct human forecasts in various contexts, such as geopolitics [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016], meta-science [@hoogeveenLaypeopleCanPredict2020; @replicationmarketsReplicationMarketsReliable2020], sports [@servan-schreiberPredictionMarketsDoes2004] and epidemiology [@farrowHumanJudgmentApproach2017; @mcandrewExpertJudgmentModel2020; @recchiaHowWellDid2021].
-Several prediction platforms [@metaculusPreliminaryLookMetaculus2020; @hypermindHypermindSupercollectiveIntelligence2021; @csetforetellCSETForetell2021] and prediction markets [@predictitPredictIt2021] have been created to collate expert and non-expert predictions.
-However, with the notable exception of @farrowHumanJudgmentApproach2017, these forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) prediction formats.
-Direct human forecasts may be able to take into account insights and relationships between variables which are hard to specify using epidemiological models.
-However, it is not entirely clear in which situations human forecasts perform well or badly.
-For example, @farrowHumanJudgmentApproach2017 found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available.
-However, humans tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown in these regions at the time.
-
-In this study, we analyse the performance of direct human forecasts relative to model-based forecasts and discuss the added benefit of epidemiological modelling over human judgement alone.
-As a case study, we use different forecasts, involving varying degrees of human intervention, which we submitted in real time to the German and Polish Forecast Hub.
-In contrast to @farrowHumanJudgmentApproach2017 we elicited not only point predictions, but full predictive distributions (“probabilistic forecasts”, see e.g.
-@heldProbabilisticForecastingInfectious2017) from participants.
-This allows us to compare not only predictive accuracy, but also how well human forecasters and model-based forecasts were able to quantify forecast uncertainty.
-
-# Methods
-
-We created and submitted the following forecasts to the German and Polish Forecast Hub: 1) a direct human forecast (henceforth called “crowd forecast”), elicited from participants through a web application [@crowdforecastr] and 2) two semi-mechanistic model-based forecasts ("renewal model" and "convolution model") informed by basic assumptions about COVID-19 epidemiology.
-While the two semi-mechanistic forecasts were necessarily shaped by our implicit assumptions and decisions, they were designed such as to minimise the amount of human intervention involved.
-For example, we refrained from adjusting model outputs or refining the models based on past performance.
-Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub [@bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021].
-All code and tools necessary to generate the forecasts and make a forecast submission are available in the `covid.german.forecasts` R package [@covidgermanforecasts].
-This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub.
-Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the German and Polish Forecast Hub.
-
-## Forecast targets and interaction with the German and Polish Forecast Hub
-
-The German and Polish Forecast Hub (now mostly merged into the @europeancovid-19forecasthubEuropeanCovid19Forecast2021) elicits predictions for various COVID-19 related forecast targets from different research groups every week.
-Forecasts had to be made every Monday (with submissions allowed until Tuesday 3pm) and were permitted to use any data that was available by Monday 11.59pm.
-We submitted forecasts for incident and cumulative weekly reported numbers of cases of and deaths from COVID-19 on a national level in Germany and Poland over a one to four week forecast horizon.
-Forecasts were submitted on Mondays, but weeks were defined as ending on a Saturday (and starting on Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26 days.
-Submissions were required in a quantile-based format with 23 quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10, 0.15, ..., 0.95, 0.975, 0.99.
-Forecasts submitted to the Forecast Hub were combined into different ensembles every week, with the median ensemble (i.e., the $\alpha$-quantile of the ensemble is given by the median of all submitted $\alpha$-quantiles) being the default ensemble shown on all official Forecast hub visualisations (https://kitmetricslab.github.io/forecasthub/forecast).
-
-Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish Forecast hub.
-Until December 14th, 2020, these data were sourced from the European Centre for Disease Control [@ecdcDownloadHistoricalData2020].
-After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period  [@rkiRKICoronavirusSARSCoV22021].
-These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, @forsal.plRozbieznosciStatystykachKoronawirusa2020), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, @aerzteblattSARSCoV2DiagnostikRKIPasst2020).
-The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \@ref(fig:daily-truth-update) and \@ref(fig:weekly-truth-update)).
-
-## Crowd forecasts
-
-Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application (https://cmmid-lshtm.shinyapps.io/crowd-forecast/).
-Weekly forecasts had to be submitted before Tuesday 12pm every week, but participants were asked to only use any information or data that was already available by Monday night.
-The application was built using the `shiny` and `golem` R packages [@golem; @shiny] and is available in the `crowdforecastr` R package [@crowdforecastr].
-To make a forecast in the application participants could select a predictive distribution (with the default being log-normal) to represent the probability that the forecasted quantity took certain values.
-Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in Figure \@ref(fig:screenshot) in the SI).
-The default shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.
-as $\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )$).
-A comparison of the crowd forecasts against the default baseline shown in the application is displayed in Figure \@ref(fig:compare-forecasters) in the Appendix.
-Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  @ourworldindataCOVID19DataExplorer2020.
-These data included, for example, notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
-From November 26 2020 on we displayed weekly small reports with a visualisation of past forecasts and scores on our website, epiforecasts.io.
-
-Forecasts were stored in a Google Sheet and downloaded, cleaned and processed every week for submission to the Forecast Hub.
-If a forecaster had submitted multiple predictions for a single target, only the latest submission was kept.
-Information on the chosen distribution as well as the parameters for median and width were used to obtain the required set of 23 quantiles from that distribution.
-Forecasts from all forecasters were then aggregated using an unweighted quantile-wise mean (i.e., the $\alpha$-quantile of the ensemble is given by the mean of all submitted $\alpha$-quantiles).
-To avoid issues with users trying out the app and submitting a random forecast, we required that a forecaster needed to make a forecast for at least two targets for a given forecast in order to be included in the crowd forecast ensemble.
-On a few occasions we deleted forecasts that were clearly the result of a user or software error (such as for example forecasts that were zero everywhere).
-
-individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation and were excluded from the submission as well as the analysis.
-
-Participants were recruited mostly within the Centre of Mathematical Modeling of Infectious Diseases at the London School of Hygiene & Tropical Medicine, but participants were also invited personally or via social media to submit predictions.
-Depending on whether they had a background in either statistics, forecasting or epidemiology, participants were asked to self-identify as 'experts' or 'non-experts'.
-
-The study was approved by the Observational / Interventions Research Ethics Committee at the London School of Hygiene & Tropical Medicine, LSHTM Ethics Reference: 22290.
-
-## Model-based forecasts
-
-We used two Bayesian semi-mechanistic models from the `EpiNow2` R package (version 1.3.3) as our model-based forecasts [@epinow2].
-The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths (see details in the SI).
-It estimated the effective reproduction number $R_t$ (the average number of people each person infected at time t is expected to infect in turn) and modelled future infections as a weighted sum of past infection multiplied by $R_t$.
-$R_t$ was assumed to stay constant beyond the forecast date, roughly corresponding to continuing the latest exponential trend in infections.
-On the 9th of November we altered the date when $R_t$ was assumed to be constant from two weeks prior to the date of the forecast to the forecast date, which we found to yield a more stable $R_t$ estimate.
-Reported case and death notifications were obtained by convolving predicted infections over data-based delay distributions [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation2020; @sherrattExploringSurveillanceData2021; @abbottEstimatingTimevaryingReproduction2020a] to model the time between infection and report date.
-The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately.
-Death forecasts from the renewal model were therefore not informed by past cases.
-One submission of the renewal model on December 28th 2020 was delayed and therefore not included in the official Forecast hub ensemble.
-
-The second model (“convolution model”, see details in SI) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses).
-The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model.
-The convolution model predicted deaths as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
-Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model with a multiplicative day-of-the-week effect [@epinow2].
-
-Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from [@kraemer2020epidemiological] with data available up to the 1st of August.
-All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan [@rstan] with each location and forecast target being fitted separately.
-
-## Analysis
-
-For the main analysis we focused mostly on two week ahead forecasts, as COVID-19 forecasts, especially for cases, were in the past found to have poor predictive performance  beyond this horizon [@bracherShorttermForecastingCOVID192021].
-Forecasts for cases were scored using the full period from October 2020 until March 2021.
-To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available.
-To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see Section \@ref(sensitivity-analysis) in the SI).
-Results remained broadly unchanged.
-
-Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) [@bracherEvaluatingEpidemicForecasts2021], the absolute error, relative bias, and empirical coverage of the 50% and 90% prediction intervals.
-The WIS is a proper scoring rule [@gneiting_strictly_2007], meaning that in expectation the score is optimised by reporting a predictive distribution that is identical to the true data-generating distribution.
-Forecasters are therefore incentivised to report their true belief about the future.
-The WIS can be understood as a generalisation of the absolute error to quantile-based forecasts (also meaning that smaller values are better) and can be decomposed into three separate penalties: forecast spread (i.e.
-uncertainty of forecasts), over-prediction and under-prediction.
-While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts.
-The bias metric [@funkAssessingPerformanceRealtime2019] we use captures how much probability mass of the forecast was above or below the true value (mapped to values between -1 and 1) and therefore represents a general tendency to over- or under-predict in relative terms.
-A value of -1 implies that all quantiles of the predictive distribution are below the observed value and a value of 1 that all quantiles are above the observed value.
-Empirical coverage is the percentage of observed values that fall inside a given prediction interval (e.g.
-how many observed values fall inside all 50% prediction intervals).
-Scoring metrics are explained in more detail in Table \@ref(tab:scoring-metrics) in the SI.
-All scores were calculated using the `scoringutils` R package [@scoringutils].
-
-At all stages of the evaluation our forecasts were compared to the median ensemble of all *other* models submitted to the German and Polish Forecast Hub ("Hub ensemble").
-This "Hub ensemble" was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see details in Section \@ref(contributions-hub), as well as in Table \@ref(tab:table-ensemble-versions) and Figure \@ref(fig:num-ensemble-members) in the SI).
-What we call "Hub ensemble" in this article therefore differs from the "official Hub ensemble" (here called "hub-ensemble-realised") which included crowd forecasts as well as renewal model forecasts.
-To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e.
-we divided the average scores for a given model by the average score achieved by the Hub ensemble on the same set of forecasts (with values >1 implying worse and values <1 implying better performance than the Hub ensemble).
-In addition to comparing our forecasts against the hub ensemble excluding our models, we also assessed the impact of our forecasts on the performance of the forecasting hub by recalculating separate versions of the Hub ensemble with only some (or all) of our forecasts included.
-Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
-
-# Results
-
-## Crowd forecast participation
-
-A total number of 32 participants submitted forecasts, 17 of those self-identified as 'expert' in either forecasting or epidemiology.
-The median number of forecasters for any given forecast target was 6, the minimum 2 and the maximum 10.
-The mean number of submissions from an individual forecaster was 4.7 but the median number was only one - most participants dropped out after their first submission.
-Only two participants submitted a forecast every single week, both of whom are authors on this study.
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-v4.png")
+```{r setup, echo=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
 ```
@@
 ```{r}
-caption <- "A, C: Visualisation of 50\\% prediction intervals of two week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS."
-```
-
-```{r forecasts-and-truth, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-2.png")
-```
-
-## Case Forecasts
-
-For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure \@ref(fig:performance-locations-rel)A).
-For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \@ref(tab:score-table-2)).
-Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Figure \@ref(fig:distribution-scores)).
-Overall, low variance in forecast performance was closely linked with good mean performance (Figures \@ref(fig:agg-performance-all)H and and \@ref(fig:agg-performance-all)A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores)), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
-WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
-
-To varying degrees, all forecasts exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened.
-For example, all forecasts failed to predict the change in trend from increase to decrease that happened in November in Germany and severely overshot reported cases (Figure \@ref(fig:forecasts-and-truth)A).
-This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past of observations.
-The Hub ensemble and the crowd forecast, which had both been under-predicting throughout October, also failed to predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 [@deutschewelleCoronavirusGermanyImpose2020] and the change in the testing regime (with stricter test criteria) on November 11th 2020 [@aerzteblattSARSCoV2DiagnostikRKIPasst2020], were fastest to adapt to the new trend, and the Hub ensemble slowest.
-In December, cases rose again in Germany, with all models under-predicting this growth to varying extents.
-As in October, the renewal model captured the phase of exponential growth in cases slightly better than other approaches, but again overshot when reported case numbers fell over Christmas.
-The large variance in predictions in January in Germany (severe under-prediction followed by severe over-prediction) may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.
-Similar trends in performance were evident in Poland, with the crowd forecast quickest at adapting to the change in trend in November.
-In general, there were fewer large outlier forecasts in Poland and in particular the renewal model performed more in line with other forecasts there.
-
-All forecasting approaches, including the Hub ensemble, were overconfident, i.e.
-they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
-Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts.
-This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \@ref(fig:agg-performance-all)E) and only showed a small increase in uncertainty across forecast horizons.
-The crowd forecasts prediction intervals were also noticeably narrower than the default baseline shown to forecasters in the application (see Figure \@ref(fig:compare-forecasters)).
-
-In spite of good performance in terms of the absolute error (Figure \@ref(fig:agg-performance-all)G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Figure \@ref(fig:agg-performance-all)C,D and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
-Despite worse performance in terms of absolute error (Figure \@ref(fig:agg-performance-all)G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
-The crowd forecasts, on the other hand, showed a smaller bias than the renewal model, but were overconfident.
-
-The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons.
-The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \@ref(fig:agg-performance-all)F).
-Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \@ref(fig:agg-performance-all)A and \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
-
-Generally, trends in overall performance were broadly similar across locations (Figures \@ref(fig:performance-locations) and \@ref(fig:performance-locations-rel)).
-Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
-However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \@ref(fig:performance-locations-rel)A, \@ref(fig:performance-locations-rel)G, \@ref(fig:agg-performance-all-Germany), \@ref(fig:agg-performance-all-Poland)).
-
-## Death Forecasts
-
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B).
-Relative WIS values for the models two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1 (Hub ensemble) and 1.79 (renewal model).
-The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B), and also better than the convolution model three and four weeks ahead.
-Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate $R_t$ trace from deaths, does not use the available information efficiently.
-The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \@ref(fig:agg-performance-all)B, Table \@ref(tab:score-table-4)).
-
-As past cases and hospitalisations can be used as predictors, predicting a change in trend may be easier for deaths than for cases.
-Even though all forecasts generally struggled with this, there were some instances where changing trends were well captured or even anticipated.
-In Poland, for example, the Hub ensemble was able to capture or even anticipate the peak in deaths in December quite well (whereas the renewal model and crowd forecast did not).
-The renewal model, which mostly exhibited trend-following behaviour, correctly predicted another increase in weekly deaths in mid-January (potentially based on changes in daily deaths, as the renewal model did not know about past cases).
-In Germany in early January, all models predicted a decrease in deaths two to three weeks before it actually happened.
-Predictions from the renewal model at that time were likely strongly influenced by an unexpected drop in reported deaths in December.
-The other forecasting approaches and in particular, the convolution model may have been affected by potentially under-reported case numbers around Christmas.
-When the decrease that all models had predicted to happen in early January failed to materialise, the renewal model and the crowd forecast noticeably over-corrected and over-predicted deaths in the following weeks, while the Hub ensemble, and to a slightly lesser degree, the convolution model were able to capture the downturn well when it finally happened at the end of January.
-
-Death forecasts, generally, showed greater coverage of the 50% and 90% prediction intervals than case forecasts and no decrease in coverage across forecast horizons, indicating that it might be easier to appropriately quantify uncertainty for death forecasts.
-The Hub ensemble had the greatest coverage, with empirical coverage of the 50% and 90% prediction intervals exceeding 50%, and 90%, respectively, across all forecast horizons.
-Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
-As for cases, the crowd forecast tended to have the narrowest prediction intervals and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
-The convolution model had relatively narrow prediction intervals for short forecast horizons, but had rapidly (and non-linearly) increasing uncertainty for longer forecast horizons, driven by increasing uncertainty in the underlying case forecasts.
-
-For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \@ref(fig:agg-performance-all)F.
-The convolution model had a strong tendency to under-predict, with the magnitude of under-prediction steadily decreasing for longer forecast horizons.
-The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction.
-For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \@ref(fig:agg-performance-all)A, \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2), \@ref(tab:score-table-4)).
-
-```{r}
-caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
-Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores."
-```
-
-```{r distribution-scores, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-2.png")
-```
-
-```{r}
-caption <- "Visualisation of relative aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
-“Hub-ensemble” \textit{excludes} all our models, Hub-ensemble-all \textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
-```
-
-```{r agg-performance-ensemble-rel, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-v4.png")
-```
-
-## Contribution to the Forecast Hub {#contributions-hub}
-
-Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (“hub-ensemble-realised”), while the convolution model was never included as it was deemed too similar to the existing renewal model.
-In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on 28 December 2020 over the Christmas period) and a maximum of 10.
-Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
-An overview of all models and ensemble versions is shown in Table \@ref(tab:table-ensemble-versions) in the SI.
-
-For cases, our contributions (compared to the Hub ensemble without our contributions) consistently improved performance across all forecasting horizons (rel.
-WIS 0.9 two weeks ahead, Table \@ref(tab:score-table-ensemble-2)).
-Contributions from the crowd forecasts alone also improved performance of the Hub ensemble across all forecast horizons, while contributions from the renewal model had a negative effect for longer horizons (rel.
-WIS 1.02 three weeks ahead, 1.06 four weeks ahead).
-The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model have improved performance (Table \@ref(tab:score-table-ensemble-4)).
-The realised ensemble performed comparably to the crowd forecasts for predictions one to two weeks ahead, and worse for greater forecast horizons.
-
-For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel.
-WIS of the Hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \@ref(tab:score-table-ensemble-2) and \@ref(tab:score-table-ensemble-4)).
-Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons).
-This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \@ref(fig:agg-performance-all)) and especially worse for longer horizons.
-
-We also considered the impact of our contributions on a version of the Hub ensemble constructed by taking the quantile-wise mean, rather than the median. 
-<!-- In general, the median ensemble tended to perform slightly better than the mean ensemble - needs more analysis -->
-General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \@ref(fig:agg-performance-ensemble-rel)B and \@ref(fig:agg-performance-ensemble-mean)B).
-This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far.
-For both the mean and the median ensemble, changes in performance from adding or removing models were of a similar order of magnitude, suggesting that at least in this instance, with a relatively small ensemble size, the median ensemble was not necessarily more ‘robust’ to changes than the mean ensemble.
-However, the ensemble version with all our forecasts included (“hub-ensemble-with-all”) tended to perform relatively better for the median ensemble than the mean ensemble, suggesting that adding more models may be more beneficial or ‘safer’ for the median than for the mean ensemble as directional errors can more easily cancel out than errors in absolute terms.
-
-# Discussion
-
-Epidemiological forecasting modelling combines knowledge about infectious disease dynamics with the subjective opinion of the researcher who develops and refines the model.
-In this study, we compared forecasts of cases of and deaths from COVID-19 in Germany and Poland based purely on human judgement and elicited from a crowd of researchers and volunteers against forecasts from two semi-mechanistic epidemiological models.
-In spite of the small number of participants and a general tendency to be overconfident, crowd forecasts consistently outperformed our epidemiological models as well as the Hub ensemble when forecasting cases but not when forecasting deaths.
-This suggests that humans might be relatively good at foreseeing trends that are hard to model but may struggle to form an intuition for the exact relationship between cases and deaths.
-
-Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches [e.g.
-@funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], or exclusively on human forecasts [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016; @mcandrewExpertJudgmentModel2020; @recchiaHowWellDid2021].
-In contrast, we directly compared human and model-based forecasts.
-This is similar to the approach taken by @farrowHumanJudgmentApproach2017, but extends it in several ways.
-While Farrow et al.
-only asked for point predictions and constructed a predictive distribution from these, we asked participants to provide a full predictive distribution, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse how humans quantified their uncertainty.
-In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-based insight.
-In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs [@cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @europeancovid-19forecasthubEuropeanCovid19Forecast2021; @funkShorttermForecastsInform2020].
-
-The strong performance of crowd forecasts in our study is in line with results from Farrow et al.
-who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants.
-The advantage of crowd forecasts we observed over our semi-mechanistic models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models.
-However, this probably explains only part of the difference, and performance relative to the Hub ensemble strongly suggests that human insight is valuable when forecasting highly volatile and potentially hard-to-predict quantities such as case numbers.
-One potential explanation is that humans can have access to data that is not available to or hard to integrate into model-based forecasts.
-Relatively good performance of our semi-mechanistic models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time.
-This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data).
-The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \@ref(fig:forecasts-and-truth)A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting which have less of an influence on weekly reporting.
-
-Our results suggest that human intervention may be less beneficial when forecasting deaths (especially at shorter horizons, when deaths are largely dependent on already observed cases), which benefits from the ability to model the delays and exact epidemiological relationships between different leading and lagged indicators.
-Relatively good performance of the convolution model, especially compared to the poor performance of the renewal model on deaths (which used only deaths to estimate and predict the effective reproduction number) underlines the importance of including leading indicators such as cases as a predictor for deaths.
-
-Given the low number of participants in our study, it is difficult to generalise conclusions about crowd predictions to other settings.
-Using R shiny as a platform for the web application arguably created some limits to user experience and performance, influencing the number of participants and potentially creating a self-selection effect.
-Motivating forecasters to contribute regularly proved challenging, especially given that the majority of our participants were from the UK and may not have been familiar with all relevant details of the situation in Germany and Poland.
-On the other hand, R shiny facilitated quick development and allowed us to provide our crowd forecasting tooling as an open source R package, meaning that it is available for others to use, for example in settings like early-stage outbreaks where model-based forecasts are not available.
-In light of the relatively small number of Hub ensemble models, performance of the Hub ensemble is also difficult to generalise.
-More research is needed to replicate these findings and investigate how crowd forecasts compare against the types of models and model ensembles policy makers use to inform their decisions.
-
-Our work suggests that crowd forecasts and model-based forecasts could have different strengths and may be able to complement each other.
-When choosing a suitable approach for a given task it is important to take into account how the output will be used.
-In this work we focused on forecasts (which aim to predict future data points whilst accounting for all factors that might influence them), whereas policy makers might be more interested in projections (which show what would happen in the absence of any events that could change the trend) or scenario modelling.
-Forecasts may not be a suitable basis for informing policy decisions, if forecasters already have factored in the expectation of a future intervention.
-Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting projections that are not influenced by implicit assumptions about the future from humans may be harder.
-
-Further work should explore the effects of humans refining their mathematical models or changing model outputs in more detail.
-Model-based forecasts could be used as an input to human judgement, with researchers adjusting predictions generated by models.
-Seeing a model-based forecast could help humans calibrate uncertainty better, while allowing for manual intervention to adapt spurious trend predictions.
-Tools need to be developed to facilitate this process at a larger scale.
-Human insight could also be used as an input to models.
-Such a ‘hybrid’ forecasting approach could for example ask humans to predict the trend of the effective reproduction number $R_t$ or the doubling rate (i.e.
-how the epidemic evolves) into the future and use this to estimate the exact number of cases, hospitalisations or deaths this would imply.
-In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust and widen prediction intervals may be another promising approach.
-Crowd forecasting in general could benefit greatly from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile to further develop and explore.
-
-\clearpage
-
-**Acknowledgements**
-
-NIB received funding from the Health Protection Research Unit (grant code NIHR200908, https://www.nihr.ac.uk/).
-SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/).
-The work of JB was supported by the Helmholtz Foundation (https://www.helmholtz.de/) via the SIMCARD Information and Data Science Pilot Project.
-This research was partly funded by the National Institute for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 & 16/136/46) using UK aid from the UK Government to support global health research.
-The views expressed in this publication are those of the author(s) and not necessarily those of the NIHR or the UK Department of Health and Social Care.
-BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859, https://www.gatesfoundation.org/).
-EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908, https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688, https://ec.europa.eu/programmes/horizon2020/).
-AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/), and the Academy of Medical Sciences (https://acmedsci.ac.uk/).
-SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/), and the NIHR (NIHR200908, https://www.nihr.ac.uk/).
-
-We thank all forecasters who participated in this study for their contribution.
-
-We would also like to acknowledge (in a randomised order) the members of Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group at the the London School of Hygiene & Tropical Medicine: Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie Diamond, Katherine E.
-Atkins, Rein M G J Houben, Jiayao Lei, Rachel Lowe, David Simons, Sophie R Meakin, Nicholas G.
-Davies, Timothy W Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly, Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas, Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson, Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun, Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche, James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday, Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael Pung, Anna M Foss.
-
-\clearpage
-
-\beginsupplement
-
-# (APPENDIX) Supplementary information {-}
-
-# Supplementary information
-
-## Scoring metrics used
-
-```{r scoring-metrics}
-wis <- list(
-  Metric = "WIS (Weighted) interval score", 
-  `Explanation` = r"(The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
-It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
-The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction.
-For a single interval, the score is computed as
-  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
-  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e.
-the lower and upper bound of a single prediction interval.
-For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
-  $$WIS = \frac{1}{K + 0.5} \cdot \left( w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y) \right), $$
-  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
-
-Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.)", 
-  `Caveats` = "The wis is based on measures of absolute error. When averaging across multiple targets, it will therefore be dominated by targets with higher absolute values.",
-  `References` = ""
-)
-
-interval_coverage <- list(
-  `Metric` = "Interval coverage", 
-  `Explanation` = r"(Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
-Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
-we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.)",
-  `Caveats` = "",
-  `References` = ""
-)
-
-bias <- list(
-  `Metric` = "Bias", 
-  `Explanation` = r"((Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict.
-Values are between -1 and 1 and 0 ideally.
-For continuous forecasts, bias is given as
-$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
-where $F$ is the CDF of the predictive distribution and $y$ is the observed value.
-
-For quantile forecasts, $F(y)$ is replaced by a quantile rank.
-The appropriate quantile rank is determined by whether the median forecast is below  or above the true value.
-We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.
-
-In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
-It is therefore a more robust measurement.)",
-  `Caveats` = "",
-  `References` = ""
-)
-
-data <- rbind(as.data.frame(wis), 
-              as.data.frame(interval_coverage),
-              as.data.frame(bias))
-
-data[, 1:2] %>%
-  kableExtra::kbl(format = "latex", booktabs = TRUE, 
-                  escape = FALSE,
-                  caption = "Overview of the scoring metrics used.",
-                  longtable = TRUE,
-                  linesep = c('\\addlinespace \\addlinespace')) %>%
-  kableExtra::column_spec(1, width = "2.5cm") %>%
-  kableExtra::column_spec(2, width = "13.0cm") %>%
-  kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))
-
-```
-
-\clearpage
-
-## The crowdforecasting app
-
-```{r}
-caption <- "Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021). "
-```
-
-```{r screenshot, fig.cap=caption}
-knitr::include_graphics("../crowd-forecast/Screenshot-forecasting-app.png")
-```
-
-\clearpage
-
-## Further details on the semi-mechanistic forecasting models
-
-### Renewal equation model
-
-The model was initialised prior to the first observed data point by assuming constant exponential growth for the mean of assumed delays from infection to case report.
-
-\begin{align}
-  I_{t} &= I_0 \exp  \left(r t \right)  \\
-  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
-  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
-\end{align}
-
-Where $I_{obs}$ and $r_{obs}$ are estimated from the first week of observed data.
-For the time window of the observed data infections were then modelled by weighting previous infections by the generation time and scaling by the instantaneous reproduction number.
-These infections were then convolved to cases by date ($O_t$) and cases by date of report ($D_t$) using log-normal delay distributions.
-This model can be defined mathematically as follows,
-
-\begin{align}
-  \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
-  I_t &= R_t \sum_{\tau = 1}^{15} w(\tau | \mu_{w}, \sigma_{w}) I_{t - \tau} \\
-  O_t &= \sum_{\tau = 0}^{15} \xi_{O}(\tau | \mu_{\xi_{O}}, \sigma_{\xi_{O}}) I_{t-\tau} \\
-  D_t &= \alpha \sum_{\tau = 0}^{15} \xi_{D}(\tau | \mu_{\xi_{D}}, \sigma_{\xi_{D}}) O_{t-\tau} \\ 
-  C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
-\end{align}
-
-Where,
-\begin{align}
-     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
-    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
-    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
-\end{align}
-
-This model used the following priors for cases,
-
-\begin{align}
-     R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
-    \mu_w &\sim \mathcal{N}(3.6, 0.7) \\
-    \sigma_w &\sim \mathcal{N}(3.1, 0.8) \\
-    \mu_{\xi_{O}} &\sim \mathcal{N}(1.62, 0.064) \\
-    \sigma_{\xi_{O}} &\sim \mathcal{N}(0.418, 0.069) \\
-    \mu_{\xi_{D}} &\sim \mathcal{N}(0.614, 0.066) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(1.51, 0.048) \\
-    \alpha &\sim \mathcal{N}(0.25, 0.05) \\
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-and updated the reporting process as follows when forecasting deaths,
-
-\begin{align}
-    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
-    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
-\end{align}
-
-$\alpha$, $\mu$, $\sigma$, and $\phi$ were truncated to be greater than 0 and with $\xi$, and $w$ normalised to sum to 1.
-
-The prior for the generation time was sourced from [@generationinterval] but refit using a log-normal incubation period with a mean of 5.2 days (SD 1.1) and SD of 1.52 days (SD 1.1) with this incubation period also being used as a prior [@incubationperiod] for $\xi_{O}$.
-This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
-We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1% or 1769 samples of the available data  [@kraemer2020epidemiological; @covidregionaldata] and combining the posteriors for the mean and standard deviation of the log-normal distribution [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation2020; @EvaluatingUseReproduction; @rstan].
-
-$GP_t$ is an approximate Hilbert space Gaussian process as defined in [@approxGP] using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20% of the number of days used in fitting).
-The length scale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
-The magnitude of the Gaussian process was assumed to be normally distributed centred at 0 with a standard deviation of 0.1.
-
-From the forecast time horizon ($T$) and onwards the last value of the Gaussian process was used (hence $R_t$ was assumed to be fixed) and latent infections were adjusted to account for the proportion of the population that was susceptible to infection as follows,
-
-\begin{equation}
-    I_t = (N - I^c_{t-1}) \left(1 - \exp \left(\frac{-I'_t}{N - I^c_{T}}\right)\right),
-\end{equation}
-
-where $I^c_t = \sum_{s< t} I_s$ are cumulative infections by $t-1$ and $I'_t$ are the unadjusted infections defined above.
-This adjustment is based on that implemented in the `epidemia` R package [@epidemia; @bhattSemiMechanisticBayesianModeling].
-
-#### Convolution model
-
-The convolution model shares the same observation model as the renewal model but rather than assuming that an observation is predicted by itself using the renewal equation instead assumes that it is predicted entirely by another observation after some parametric delay.
-It can be defined mathematically as follows,
-
-\begin{equation} 
-    D_{t} \sim \mathrm{NB}\left(\omega_{(t \mod 7)} \alpha \sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) C_{t-\tau},  \phi \right)
-\end{equation}
-
-with the following priors,
-
-\begin{align}
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \alpha &\sim \mathcal{N}(0.01, 0.02) \\
-    \xi &\sim \mathcal{LN}(\mu, \sigma) \\
-    \mu &\sim \mathcal{N}(2.5, 0.5) \\
-\sigma &\sim \mathcal{N}(0.47, 0.2) \\
-\phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-with $\alpha$, $\mu$, $\sigma$, and $\phi$ truncated to be greater than 0 and with $\xi$ normalised such that $\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1$.
-
-### Model fitting
-
-Both models were implemented using the `EpiNow2` R package (version 1.3.3) [@epinow2].
-Each forecast target was fitted independently for each model using Markov-chain Monte Carlo (MCMC) in stan [@rstan].
-A minimum of 4 chains were used with a warmup of 250 samples for the renewal equation-based model and 1000 samples for the convolution model.
-2000 samples total post warmup were used for the renewal equation model and 4000 samples for the convolution model.
-Different settings were chosen for each model to optimise compute time contingent on convergence.
-Convergence was assessed using the R hat diagnostic [@rstan].
-For the convolution model forecast the case forecast from the renewal equation model was used in place of observed cases beyond the forecast horizon using 1000 posterior samples.
-12 weeks of data was used for both models though only 3 weeks of data were included in the likelihood for the convolution model.
-
-\clearpage
-
-```{r}
-add_caption <- function(table, caption, label = NULL) {
-  if (is.null(label)) {
-    label <- paste0("tab:", opts_current$get("label"))
-  }
-  table <- gsub(pattern = "begin\\{table\\}\\[!h\\]",
-                replacement = paste0("begin\\{table\\}[!h]\n", 
-                                     "\\\\caption\\{",
-                                     "\\\\\\label\\{", label, "\\}",
-                                     caption,
-                                     "\\\\\\\\\\\\hspace{\\\\textwidth}\\}\n"),
-                x = table)
-  return(table)
-}
-
-```
-
-## Tables with results of the forecast evaluation
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-2}
-table <- readRDS("../analysis/plots/table_scores_2_ahead.rds")
-add_caption(table, caption, label = "tab:score-table-2")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-4}
-table <- readRDS("../analysis/plots/table_scores_4_ahead.rds")
-add_caption(table, caption, label = "tab:score-table-4")
-
-```
-
-\clearpage
-
-## Aggregate performance by location
-
-### Performance in Germany
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all-Germany, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-Germany-v4.png")
-```
-
-### Performance in Poland
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all-Poland, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-Poland-v4.png")
-```
-
-### Performance across locations in absolute terms
-```{r}
-caption <- "Visualisation of aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of WIS values."
-```
-
-```{r performance-locations, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-v4.png")
-```
-
-## Performance across locations in relative terms
-
-```{r}
-caption <- "Visualisation of relative aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals.
-E: Dispersion.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast.
-H.
-Standard deviation of WIS values."
-```
-
-```{r performance-locations-rel, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4.png")
-```
-
-\clearpage
-
-## Visualisation of daily reported cases and deaths
-
-```{r}
-caption <- "Visualisation of daily report data. The black line represents weekly data divided by seven. Data were last accessed through the German and Polish Forecast Hub on August 21 2021."
-```
-
-```{r daily-truth, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/daily_truth.png")
-```
-
-```{r}
-caption <- "Visualisation of the absolute difference between the daily report data at the time and the data now.
-In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
-```
-
-```{r daily-truth-update, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/daily-data-updates.png")
-```
-
-```{r}
-caption <- "Visualisation of the relative difference between the weekly report data at the time and the data now.
-Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
-```
-
-```{r weekly-truth-update, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/weekly-data-updates.png")
-```
-
-\clearpage
-
-## Visualisation of scores and forecasts 1, 3, 4 weeks ahead
-
-```{r}
-caption <- "A, C: Visualisation of 50\\% prediction intervals of one week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS."
-```
-
-```{r forecasts-and-truth-1, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-1.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one", replacement = "three")
-```
-
-```{r forecasts-and-truth-3, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-3.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-```
-
-```{r forecasts-and-truth-4, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-4.png")
-```
-
-\clearpage
-
-## Distribution of scores
-
-### Absolute scores
-
-```{r}
-caption <- "A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country."
-```
-
-```{r distribution-scores-1, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-1.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one", replacement = "three")
-```
-
-```{r distribution-scores-3, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-3.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-```
-
-```{r distribution-scores-4, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-4.png")
-```
-
-### Ranks achieved by forecasts
-
-```{r}
-caption <- "A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country."
-```
-
-```{r distribution-scores-ranks-1, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-1-ranks.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one", replacement = "two")
-```
-
-```{r distribution-scores-ranks-2, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-2-ranks.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "two", replacement = "three")
-```
-
-```{r distribution-scores-ranks-3, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-3-ranks.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-```
-
-```{r distribution-scores-ranks-4, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-4-ranks.png")
-```
-
-```{r distribution-scores-differences, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
-knitr::include_graphics("../analysis/plots/difference-wis-crowd-ensemble.png")
-```
-
-```{r distribution-scores-differences-renewal, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
-knitr::include_graphics("../analysis/plots/difference-wis-crowd-renewal.png")
-```
-
-\newpage
-
-## Comparison of ensembles
-
-### Performance visualisation mean ensemble
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble” \textit{excludes} all our models, Hub-ensemble-all \textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
-Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
-```
-
-```{r agg-performance-ensemble-mean, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-mean-v4.png")
-```
-
-### Tables median ensemble
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
+library(kableExtra)
 ```
@@
 ```{r score-table-ensemble-2}
-table <- readRDS("../analysis/plots/table_median-ensemble_scores_2_ahead.rds")
-add_caption(table, caption)
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-ensemble-4}
-table <- readRDS("../analysis/plots/table_median-ensemble_scores_4_ahead.rds")
-add_caption(table, caption)
-
-```
-
-### Tables mean ensemble
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-ensemble-mean-2}
-table <- readRDS("../analysis/plots/table_mean-ensemble_scores_2_ahead.rds")
-add_caption(table, caption)
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-ensemble-mean-4}
-table <- readRDS("../analysis/plots/table_mean-ensemble_scores_4_ahead.rds")
-add_caption(table, caption)
-```
-
-\clearpage
-
-## Sensitivity analysis
-
-In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later.
-This sensitivity shows performance of all models restricted to the period from December 14 2020 until March 1st 2021 where all models were available.
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all-late, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-late-period-v4.png")
-```
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-late-2}
-table <- readRDS("../analysis/plots/table-late-period_2_ahead.rds")
-add_caption(table, caption)
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-late-4}
-table <- readRDS("../analysis/plots/table-late-period_4_ahead.rds")
-add_caption(table, caption)
-
-```
-
-\clearpage
-
-## Overview of models and forecasters
-
-```{r table-ensemble-versions}
-
 rbind(
@@
                   escape = FALSE,
-                  caption = "Overview of the models and ensembles used.",
                   longtable = TRUE,
@@
   kableExtra::column_spec(1, width = "4.5cm") %>%
-  kableExtra::column_spec(2, width = "11.0cm") %>%
+  kableExtra::column_spec(2, width = "7.3cm") %>%
   kableExtra::kable_styling(latex_options = c("striped", "repeat_header")) 
 ```
-
-```{r num-forecasters, fig.cap="Number of participants who submitted a forecast over time."}
-knitr::include_graphics("../analysis/plots/number-forecasters.png")
-```
-
-```{r num-ensemble-members, fig.cap="Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
-Note that the renewal model was not included in the ensemble on December 28th 2020."}
-knitr::include_graphics("../analysis/plots/ensemble-members.png")
-```
-
-\clearpage
-
-## Comparison of crowd forecasts and application baseline
-
-```{r compare-forecasters, fig.cap="Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the 90\\% and 50\\% prediction intervals as well as the median (in order of increasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons)."}
-knitr::include_graphics("../analysis/plots/comparison-forecast-interals.png")
-```

### 2022-08-04 manuscript/S3 Table.Rmd
final revisions

--- 2022-05-19 manuscript/manuscript.Rmd
@@
 ```{r}
-caption <- "A, C: Visualisation of 50\\% prediction intervals of two week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS."
-```
-
-```{r forecasts-and-truth, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-2.png")
-```
-
-## Case Forecasts
-
-For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure \@ref(fig:performance-locations-rel)A).
-For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \@ref(tab:score-table-2)).
-Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Figure \@ref(fig:distribution-scores)).
-Overall, low variance in forecast performance was closely linked with good mean performance (Figures \@ref(fig:agg-performance-all)H and and \@ref(fig:agg-performance-all)A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores)), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
-WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
-
-To varying degrees, all forecasts exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened.
-For example, all forecasts failed to predict the change in trend from increase to decrease that happened in November in Germany and severely overshot reported cases (Figure \@ref(fig:forecasts-and-truth)A).
-This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past of observations.
-The Hub ensemble and the crowd forecast, which had both been under-predicting throughout October, also failed to predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 [@deutschewelleCoronavirusGermanyImpose2020] and the change in the testing regime (with stricter test criteria) on November 11th 2020 [@aerzteblattSARSCoV2DiagnostikRKIPasst2020], were fastest to adapt to the new trend, and the Hub ensemble slowest.
-In December, cases rose again in Germany, with all models under-predicting this growth to varying extents.
-As in October, the renewal model captured the phase of exponential growth in cases slightly better than other approaches, but again overshot when reported case numbers fell over Christmas.
-The large variance in predictions in January in Germany (severe under-prediction followed by severe over-prediction) may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.
-Similar trends in performance were evident in Poland, with the crowd forecast quickest at adapting to the change in trend in November.
-In general, there were fewer large outlier forecasts in Poland and in particular the renewal model performed more in line with other forecasts there.
-
-All forecasting approaches, including the Hub ensemble, were overconfident, i.e.
-they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
-Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts.
-This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \@ref(fig:agg-performance-all)E) and only showed a small increase in uncertainty across forecast horizons.
-The crowd forecasts prediction intervals were also noticeably narrower than the default baseline shown to forecasters in the application (see Figure \@ref(fig:compare-forecasters)).
-
-In spite of good performance in terms of the absolute error (Figure \@ref(fig:agg-performance-all)G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Figure \@ref(fig:agg-performance-all)C,D and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
-Despite worse performance in terms of absolute error (Figure \@ref(fig:agg-performance-all)G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
-The crowd forecasts, on the other hand, showed a smaller bias than the renewal model, but were overconfident.
-
-The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons.
-The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \@ref(fig:agg-performance-all)F).
-Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \@ref(fig:agg-performance-all)A and \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
-
-Generally, trends in overall performance were broadly similar across locations (Figures \@ref(fig:performance-locations) and \@ref(fig:performance-locations-rel)).
-Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
-However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \@ref(fig:performance-locations-rel)A, \@ref(fig:performance-locations-rel)G, \@ref(fig:agg-performance-all-Germany), \@ref(fig:agg-performance-all-Poland)).
-
-## Death Forecasts
-
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B).
-Relative WIS values for the models two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1 (Hub ensemble) and 1.79 (renewal model).
-The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B), and also better than the convolution model three and four weeks ahead.
-Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate $R_t$ trace from deaths, does not use the available information efficiently.
-The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \@ref(fig:agg-performance-all)B, Table \@ref(tab:score-table-4)).
-
-As past cases and hospitalisations can be used as predictors, predicting a change in trend may be easier for deaths than for cases.
-Even though all forecasts generally struggled with this, there were some instances where changing trends were well captured or even anticipated.
-In Poland, for example, the Hub ensemble was able to capture or even anticipate the peak in deaths in December quite well (whereas the renewal model and crowd forecast did not).
-The renewal model, which mostly exhibited trend-following behaviour, correctly predicted another increase in weekly deaths in mid-January (potentially based on changes in daily deaths, as the renewal model did not know about past cases).
-In Germany in early January, all models predicted a decrease in deaths two to three weeks before it actually happened.
-Predictions from the renewal model at that time were likely strongly influenced by an unexpected drop in reported deaths in December.
-The other forecasting approaches and in particular, the convolution model may have been affected by potentially under-reported case numbers around Christmas.
-When the decrease that all models had predicted to happen in early January failed to materialise, the renewal model and the crowd forecast noticeably over-corrected and over-predicted deaths in the following weeks, while the Hub ensemble, and to a slightly lesser degree, the convolution model were able to capture the downturn well when it finally happened at the end of January.
-
-Death forecasts, generally, showed greater coverage of the 50% and 90% prediction intervals than case forecasts and no decrease in coverage across forecast horizons, indicating that it might be easier to appropriately quantify uncertainty for death forecasts.
-The Hub ensemble had the greatest coverage, with empirical coverage of the 50% and 90% prediction intervals exceeding 50%, and 90%, respectively, across all forecast horizons.
-Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
-As for cases, the crowd forecast tended to have the narrowest prediction intervals and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
-The convolution model had relatively narrow prediction intervals for short forecast horizons, but had rapidly (and non-linearly) increasing uncertainty for longer forecast horizons, driven by increasing uncertainty in the underlying case forecasts.
-
-For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \@ref(fig:agg-performance-all)F.
-The convolution model had a strong tendency to under-predict, with the magnitude of under-prediction steadily decreasing for longer forecast horizons.
-The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction.
-For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \@ref(fig:agg-performance-all)A, \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2), \@ref(tab:score-table-4)).
-
-```{r}
-caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
-Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores."
-```
-
-```{r distribution-scores, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-2.png")
-```
-
-```{r}
-caption <- "Visualisation of relative aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
-“Hub-ensemble” \textit{excludes} all our models, Hub-ensemble-all \textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
-```
-
-```{r agg-performance-ensemble-rel, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-v4.png")
-```
-
-## Contribution to the Forecast Hub {#contributions-hub}
-
-Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (“hub-ensemble-realised”), while the convolution model was never included as it was deemed too similar to the existing renewal model.
-In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on 28 December 2020 over the Christmas period) and a maximum of 10.
-Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
-An overview of all models and ensemble versions is shown in Table \@ref(tab:table-ensemble-versions) in the SI.
-
-For cases, our contributions (compared to the Hub ensemble without our contributions) consistently improved performance across all forecasting horizons (rel.
-WIS 0.9 two weeks ahead, Table \@ref(tab:score-table-ensemble-2)).
-Contributions from the crowd forecasts alone also improved performance of the Hub ensemble across all forecast horizons, while contributions from the renewal model had a negative effect for longer horizons (rel.
-WIS 1.02 three weeks ahead, 1.06 four weeks ahead).
-The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model have improved performance (Table \@ref(tab:score-table-ensemble-4)).
-The realised ensemble performed comparably to the crowd forecasts for predictions one to two weeks ahead, and worse for greater forecast horizons.
-
-For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel.
-WIS of the Hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \@ref(tab:score-table-ensemble-2) and \@ref(tab:score-table-ensemble-4)).
-Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons).
-This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \@ref(fig:agg-performance-all)) and especially worse for longer horizons.
-
-We also considered the impact of our contributions on a version of the Hub ensemble constructed by taking the quantile-wise mean, rather than the median. 
-<!-- In general, the median ensemble tended to perform slightly better than the mean ensemble - needs more analysis -->
-General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \@ref(fig:agg-performance-ensemble-rel)B and \@ref(fig:agg-performance-ensemble-mean)B).
-This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far.
-For both the mean and the median ensemble, changes in performance from adding or removing models were of a similar order of magnitude, suggesting that at least in this instance, with a relatively small ensemble size, the median ensemble was not necessarily more ‘robust’ to changes than the mean ensemble.
-However, the ensemble version with all our forecasts included (“hub-ensemble-with-all”) tended to perform relatively better for the median ensemble than the mean ensemble, suggesting that adding more models may be more beneficial or ‘safer’ for the median than for the mean ensemble as directional errors can more easily cancel out than errors in absolute terms.
-
-# Discussion
-
-Epidemiological forecasting modelling combines knowledge about infectious disease dynamics with the subjective opinion of the researcher who develops and refines the model.
-In this study, we compared forecasts of cases of and deaths from COVID-19 in Germany and Poland based purely on human judgement and elicited from a crowd of researchers and volunteers against forecasts from two semi-mechanistic epidemiological models.
-In spite of the small number of participants and a general tendency to be overconfident, crowd forecasts consistently outperformed our epidemiological models as well as the Hub ensemble when forecasting cases but not when forecasting deaths.
-This suggests that humans might be relatively good at foreseeing trends that are hard to model but may struggle to form an intuition for the exact relationship between cases and deaths.
-
-Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches [e.g.
-@funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], or exclusively on human forecasts [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016; @mcandrewExpertJudgmentModel2020; @recchiaHowWellDid2021].
-In contrast, we directly compared human and model-based forecasts.
-This is similar to the approach taken by @farrowHumanJudgmentApproach2017, but extends it in several ways.
-While Farrow et al.
-only asked for point predictions and constructed a predictive distribution from these, we asked participants to provide a full predictive distribution, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse how humans quantified their uncertainty.
-In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-based insight.
-In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs [@cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @europeancovid-19forecasthubEuropeanCovid19Forecast2021; @funkShorttermForecastsInform2020].
-
-The strong performance of crowd forecasts in our study is in line with results from Farrow et al.
-who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants.
-The advantage of crowd forecasts we observed over our semi-mechanistic models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models.
-However, this probably explains only part of the difference, and performance relative to the Hub ensemble strongly suggests that human insight is valuable when forecasting highly volatile and potentially hard-to-predict quantities such as case numbers.
-One potential explanation is that humans can have access to data that is not available to or hard to integrate into model-based forecasts.
-Relatively good performance of our semi-mechanistic models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time.
-This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data).
-The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \@ref(fig:forecasts-and-truth)A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting which have less of an influence on weekly reporting.
-
-Our results suggest that human intervention may be less beneficial when forecasting deaths (especially at shorter horizons, when deaths are largely dependent on already observed cases), which benefits from the ability to model the delays and exact epidemiological relationships between different leading and lagged indicators.
-Relatively good performance of the convolution model, especially compared to the poor performance of the renewal model on deaths (which used only deaths to estimate and predict the effective reproduction number) underlines the importance of including leading indicators such as cases as a predictor for deaths.
-
-Given the low number of participants in our study, it is difficult to generalise conclusions about crowd predictions to other settings.
-Using R shiny as a platform for the web application arguably created some limits to user experience and performance, influencing the number of participants and potentially creating a self-selection effect.
-Motivating forecasters to contribute regularly proved challenging, especially given that the majority of our participants were from the UK and may not have been familiar with all relevant details of the situation in Germany and Poland.
-On the other hand, R shiny facilitated quick development and allowed us to provide our crowd forecasting tooling as an open source R package, meaning that it is available for others to use, for example in settings like early-stage outbreaks where model-based forecasts are not available.
-In light of the relatively small number of Hub ensemble models, performance of the Hub ensemble is also difficult to generalise.
-More research is needed to replicate these findings and investigate how crowd forecasts compare against the types of models and model ensembles policy makers use to inform their decisions.
-
-Our work suggests that crowd forecasts and model-based forecasts could have different strengths and may be able to complement each other.
-When choosing a suitable approach for a given task it is important to take into account how the output will be used.
-In this work we focused on forecasts (which aim to predict future data points whilst accounting for all factors that might influence them), whereas policy makers might be more interested in projections (which show what would happen in the absence of any events that could change the trend) or scenario modelling.
-Forecasts may not be a suitable basis for informing policy decisions, if forecasters already have factored in the expectation of a future intervention.
-Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting projections that are not influenced by implicit assumptions about the future from humans may be harder.
-
-Further work should explore the effects of humans refining their mathematical models or changing model outputs in more detail.
-Model-based forecasts could be used as an input to human judgement, with researchers adjusting predictions generated by models.
-Seeing a model-based forecast could help humans calibrate uncertainty better, while allowing for manual intervention to adapt spurious trend predictions.
-Tools need to be developed to facilitate this process at a larger scale.
-Human insight could also be used as an input to models.
-Such a ‘hybrid’ forecasting approach could for example ask humans to predict the trend of the effective reproduction number $R_t$ or the doubling rate (i.e.
-how the epidemic evolves) into the future and use this to estimate the exact number of cases, hospitalisations or deaths this would imply.
-In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust and widen prediction intervals may be another promising approach.
-Crowd forecasting in general could benefit greatly from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile to further develop and explore.
-
-\clearpage
-
-**Acknowledgements**
-
-NIB received funding from the Health Protection Research Unit (grant code NIHR200908, https://www.nihr.ac.uk/).
-SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/).
-The work of JB was supported by the Helmholtz Foundation (https://www.helmholtz.de/) via the SIMCARD Information and Data Science Pilot Project.
-This research was partly funded by the National Institute for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 & 16/136/46) using UK aid from the UK Government to support global health research.
-The views expressed in this publication are those of the author(s) and not necessarily those of the NIHR or the UK Department of Health and Social Care.
-BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859, https://www.gatesfoundation.org/).
-EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908, https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688, https://ec.europa.eu/programmes/horizon2020/).
-AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/), and the Academy of Medical Sciences (https://acmedsci.ac.uk/).
-SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/), and the NIHR (NIHR200908, https://www.nihr.ac.uk/).
-
-We thank all forecasters who participated in this study for their contribution.
-
-We would also like to acknowledge (in a randomised order) the members of Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group at the the London School of Hygiene & Tropical Medicine: Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie Diamond, Katherine E.
-Atkins, Rein M G J Houben, Jiayao Lei, Rachel Lowe, David Simons, Sophie R Meakin, Nicholas G.
-Davies, Timothy W Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly, Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas, Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson, Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun, Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche, James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday, Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael Pung, Anna M Foss.
-
-\clearpage
-
-\beginsupplement
-
-# (APPENDIX) Supplementary information {-}
-
-# Supplementary information
-
-## Scoring metrics used
-
-```{r scoring-metrics}
-wis <- list(
-  Metric = "WIS (Weighted) interval score", 
-  `Explanation` = r"(The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
-It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
-The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction.
-For a single interval, the score is computed as
-  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
-  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e.
-the lower and upper bound of a single prediction interval.
-For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
-  $$WIS = \frac{1}{K + 0.5} \cdot \left( w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y) \right), $$
-  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
-
-Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.)", 
-  `Caveats` = "The wis is based on measures of absolute error. When averaging across multiple targets, it will therefore be dominated by targets with higher absolute values.",
-  `References` = ""
-)
-
-interval_coverage <- list(
-  `Metric` = "Interval coverage", 
-  `Explanation` = r"(Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
-Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
-we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.)",
-  `Caveats` = "",
-  `References` = ""
-)
-
-bias <- list(
-  `Metric` = "Bias", 
-  `Explanation` = r"((Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict.
-Values are between -1 and 1 and 0 ideally.
-For continuous forecasts, bias is given as
-$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
-where $F$ is the CDF of the predictive distribution and $y$ is the observed value.
-
-For quantile forecasts, $F(y)$ is replaced by a quantile rank.
-The appropriate quantile rank is determined by whether the median forecast is below  or above the true value.
-We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.
-
-In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
-It is therefore a more robust measurement.)",
-  `Caveats` = "",
-  `References` = ""
-)
-
-data <- rbind(as.data.frame(wis), 
-              as.data.frame(interval_coverage),
-              as.data.frame(bias))
-
-data[, 1:2] %>%
-  kableExtra::kbl(format = "latex", booktabs = TRUE, 
-                  escape = FALSE,
-                  caption = "Overview of the scoring metrics used.",
-                  longtable = TRUE,
-                  linesep = c('\\addlinespace \\addlinespace')) %>%
-  kableExtra::column_spec(1, width = "2.5cm") %>%
-  kableExtra::column_spec(2, width = "13.0cm") %>%
-  kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))
-
-```
-
-\clearpage
-
-## The crowdforecasting app
-
-```{r}
-caption <- "Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021). "
-```
-
-```{r screenshot, fig.cap=caption}
-knitr::include_graphics("../crowd-forecast/Screenshot-forecasting-app.png")
-```
-
-\clearpage
-
-## Further details on the semi-mechanistic forecasting models
-
-### Renewal equation model
-
-The model was initialised prior to the first observed data point by assuming constant exponential growth for the mean of assumed delays from infection to case report.
-
-\begin{align}
-  I_{t} &= I_0 \exp  \left(r t \right)  \\
-  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
-  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
-\end{align}
-
-Where $I_{obs}$ and $r_{obs}$ are estimated from the first week of observed data.
-For the time window of the observed data infections were then modelled by weighting previous infections by the generation time and scaling by the instantaneous reproduction number.
-These infections were then convolved to cases by date ($O_t$) and cases by date of report ($D_t$) using log-normal delay distributions.
-This model can be defined mathematically as follows,
-
-\begin{align}
-  \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
-  I_t &= R_t \sum_{\tau = 1}^{15} w(\tau | \mu_{w}, \sigma_{w}) I_{t - \tau} \\
-  O_t &= \sum_{\tau = 0}^{15} \xi_{O}(\tau | \mu_{\xi_{O}}, \sigma_{\xi_{O}}) I_{t-\tau} \\
-  D_t &= \alpha \sum_{\tau = 0}^{15} \xi_{D}(\tau | \mu_{\xi_{D}}, \sigma_{\xi_{D}}) O_{t-\tau} \\ 
-  C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
-\end{align}
-
-Where,
-\begin{align}
-     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
-    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
-    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
-\end{align}
-
-This model used the following priors for cases,
-
-\begin{align}
-     R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
-    \mu_w &\sim \mathcal{N}(3.6, 0.7) \\
-    \sigma_w &\sim \mathcal{N}(3.1, 0.8) \\
-    \mu_{\xi_{O}} &\sim \mathcal{N}(1.62, 0.064) \\
-    \sigma_{\xi_{O}} &\sim \mathcal{N}(0.418, 0.069) \\
-    \mu_{\xi_{D}} &\sim \mathcal{N}(0.614, 0.066) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(1.51, 0.048) \\
-    \alpha &\sim \mathcal{N}(0.25, 0.05) \\
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-and updated the reporting process as follows when forecasting deaths,
-
-\begin{align}
-    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
-    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
-\end{align}
-
-$\alpha$, $\mu$, $\sigma$, and $\phi$ were truncated to be greater than 0 and with $\xi$, and $w$ normalised to sum to 1.
-
-The prior for the generation time was sourced from [@generationinterval] but refit using a log-normal incubation period with a mean of 5.2 days (SD 1.1) and SD of 1.52 days (SD 1.1) with this incubation period also being used as a prior [@incubationperiod] for $\xi_{O}$.
-This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
-We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1% or 1769 samples of the available data  [@kraemer2020epidemiological; @covidregionaldata] and combining the posteriors for the mean and standard deviation of the log-normal distribution [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation2020; @EvaluatingUseReproduction; @rstan].
-
-$GP_t$ is an approximate Hilbert space Gaussian process as defined in [@approxGP] using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20% of the number of days used in fitting).
-The length scale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
-The magnitude of the Gaussian process was assumed to be normally distributed centred at 0 with a standard deviation of 0.1.
-
-From the forecast time horizon ($T$) and onwards the last value of the Gaussian process was used (hence $R_t$ was assumed to be fixed) and latent infections were adjusted to account for the proportion of the population that was susceptible to infection as follows,
-
-\begin{equation}
-    I_t = (N - I^c_{t-1}) \left(1 - \exp \left(\frac{-I'_t}{N - I^c_{T}}\right)\right),
-\end{equation}
-
-where $I^c_t = \sum_{s< t} I_s$ are cumulative infections by $t-1$ and $I'_t$ are the unadjusted infections defined above.
-This adjustment is based on that implemented in the `epidemia` R package [@epidemia; @bhattSemiMechanisticBayesianModeling].
-
-#### Convolution model
-
-The convolution model shares the same observation model as the renewal model but rather than assuming that an observation is predicted by itself using the renewal equation instead assumes that it is predicted entirely by another observation after some parametric delay.
-It can be defined mathematically as follows,
-
-\begin{equation} 
-    D_{t} \sim \mathrm{NB}\left(\omega_{(t \mod 7)} \alpha \sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) C_{t-\tau},  \phi \right)
-\end{equation}
-
-with the following priors,
-
-\begin{align}
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \alpha &\sim \mathcal{N}(0.01, 0.02) \\
-    \xi &\sim \mathcal{LN}(\mu, \sigma) \\
-    \mu &\sim \mathcal{N}(2.5, 0.5) \\
-\sigma &\sim \mathcal{N}(0.47, 0.2) \\
-\phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-with $\alpha$, $\mu$, $\sigma$, and $\phi$ truncated to be greater than 0 and with $\xi$ normalised such that $\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1$.
-
-### Model fitting
-
-Both models were implemented using the `EpiNow2` R package (version 1.3.3) [@epinow2].
-Each forecast target was fitted independently for each model using Markov-chain Monte Carlo (MCMC) in stan [@rstan].
-A minimum of 4 chains were used with a warmup of 250 samples for the renewal equation-based model and 1000 samples for the convolution model.
-2000 samples total post warmup were used for the renewal equation model and 4000 samples for the convolution model.
-Different settings were chosen for each model to optimise compute time contingent on convergence.
-Convergence was assessed using the R hat diagnostic [@rstan].
-For the convolution model forecast the case forecast from the renewal equation model was used in place of observed cases beyond the forecast horizon using 1000 posterior samples.
-12 weeks of data was used for both models though only 3 weeks of data were included in the likelihood for the convolution model.
-
-\clearpage
-
-```{r}
+library(kableExtra)
 add_caption <- function(table, caption, label = NULL) {
@@
 
-## Tables with results of the forecast evaluation
-
 ```{r}
 caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
+  "Scores for three and four week ahead forecasts (cut to three significant digits and rounded).
 Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
@@
 ```{r score-table-2}
-table <- readRDS("../analysis/plots/table_scores_2_ahead.rds")
-add_caption(table, caption, label = "tab:score-table-2")
+table <- readRDS("../analysis/plots/table_scores_4_ahead.rds")
+table
+# add_caption(table, caption, label = "tab:score-table-2")
 ```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-4}
-table <- readRDS("../analysis/plots/table_scores_4_ahead.rds")
-add_caption(table, caption, label = "tab:score-table-4")
-
-```
-
-\clearpage
-
-## Aggregate performance by location
-
-### Performance in Germany
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all-Germany, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-Germany-v4.png")
-```
-
-### Performance in Poland
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all-Poland, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-Poland-v4.png")
-```
-
-### Performance across locations in absolute terms
-```{r}
-caption <- "Visualisation of aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of WIS values."
-```
-
-```{r performance-locations, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-v4.png")
-```
-
-## Performance across locations in relative terms
-
-```{r}
-caption <- "Visualisation of relative aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals.
-E: Dispersion.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast.
-H.
-Standard deviation of WIS values."
-```
-
-```{r performance-locations-rel, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4.png")
-```
-
-\clearpage
-
-## Visualisation of daily reported cases and deaths
-
-```{r}
-caption <- "Visualisation of daily report data. The black line represents weekly data divided by seven. Data were last accessed through the German and Polish Forecast Hub on August 21 2021."
-```
-
-```{r daily-truth, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/daily_truth.png")
-```
-
-```{r}
-caption <- "Visualisation of the absolute difference between the daily report data at the time and the data now.
-In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
-```
-
-```{r daily-truth-update, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/daily-data-updates.png")
-```
-
-```{r}
-caption <- "Visualisation of the relative difference between the weekly report data at the time and the data now.
-Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
-```
-
-```{r weekly-truth-update, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/weekly-data-updates.png")
-```
-
-\clearpage
-
-## Visualisation of scores and forecasts 1, 3, 4 weeks ahead
-
-```{r}
-caption <- "A, C: Visualisation of 50\\% prediction intervals of one week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS."
-```
-
-```{r forecasts-and-truth-1, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-1.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one", replacement = "three")
-```
-
-```{r forecasts-and-truth-3, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-3.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-```
-
-```{r forecasts-and-truth-4, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-4.png")
-```
-
-\clearpage
-
-## Distribution of scores
-
-### Absolute scores
-
-```{r}
-caption <- "A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country."
-```
-
-```{r distribution-scores-1, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-1.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one", replacement = "three")
-```
-
-```{r distribution-scores-3, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-3.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-```
-
-```{r distribution-scores-4, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-4.png")
-```
-
-### Ranks achieved by forecasts
-
-```{r}
-caption <- "A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country."
-```
-
-```{r distribution-scores-ranks-1, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-1-ranks.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one", replacement = "two")
-```
-
-```{r distribution-scores-ranks-2, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-2-ranks.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "two", replacement = "three")
-```
-
-```{r distribution-scores-ranks-3, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-3-ranks.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-```
-
-```{r distribution-scores-ranks-4, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-4-ranks.png")
-```
-
-```{r distribution-scores-differences, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
-knitr::include_graphics("../analysis/plots/difference-wis-crowd-ensemble.png")
-```
-
-```{r distribution-scores-differences-renewal, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
-knitr::include_graphics("../analysis/plots/difference-wis-crowd-renewal.png")
-```
-
-\newpage
-
-## Comparison of ensembles
-
-### Performance visualisation mean ensemble
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble” \textit{excludes} all our models, Hub-ensemble-all \textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
-Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
-```
-
-```{r agg-performance-ensemble-mean, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-mean-v4.png")
-```
-
-### Tables median ensemble
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-ensemble-2}
-table <- readRDS("../analysis/plots/table_median-ensemble_scores_2_ahead.rds")
-add_caption(table, caption)
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-ensemble-4}
-table <- readRDS("../analysis/plots/table_median-ensemble_scores_4_ahead.rds")
-add_caption(table, caption)
-
-```
-
-### Tables mean ensemble
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-ensemble-mean-2}
-table <- readRDS("../analysis/plots/table_mean-ensemble_scores_2_ahead.rds")
-add_caption(table, caption)
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-ensemble-mean-4}
-table <- readRDS("../analysis/plots/table_mean-ensemble_scores_4_ahead.rds")
-add_caption(table, caption)
-```
-
-\clearpage
-
-## Sensitivity analysis
-
-In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later.
-This sensitivity shows performance of all models restricted to the period from December 14 2020 until March 1st 2021 where all models were available.
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all-late, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-late-period-v4.png")
-```
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-late-2}
-table <- readRDS("../analysis/plots/table-late-period_2_ahead.rds")
-add_caption(table, caption)
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-late-4}
-table <- readRDS("../analysis/plots/table-late-period_4_ahead.rds")
-add_caption(table, caption)
-
-```
-
-\clearpage
-
-## Overview of models and forecasters
-
-```{r table-ensemble-versions}
-
-rbind(
-  list(
-    Name = "Hub-ensemble-realised", 
-    `Explanation` = "Official Forecast Hub median ensemble.
-Created by the Forecast Hub officially under the name 'KITCOVIDhub-median\\_ensemble' and used as the default ensemble.
-Included are our crowd forecasts as well as the renewal model (with one missed submission on December 28 2020, but not the convolution model which was deemed to similar to the renewal model."
-  ),
-  list(
-    Name = "Hub-ensemble-realised-mean", 
-    `Explanation` = "Official Forecast Hub mean ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-mean\\_ensemble'."
-  ),
-  list(Name = "", Explanation = ""),
-
-  list(
-    Name = "Hub-ensemble", 
-    `Explanation` = "Version of the official Hub median ensemble which excludes all our contributions."
-  ),
-  list(
-    Name = "Hub-ensemble-mean", 
-    `Explanation` = "Version of the official Hub mean ensemble which excludes all our contributions."
-  ),
-  list(
-    Name = "Hub-ensemble-with-renewal, 
-    Hub-ensemble-with-renewal-mean", 
-    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Renewal model."
-  ),
-  list(
-    Name = "Hub-ensemble-with-crowd, 
-    Hub-ensemble-with-crowd-mean", 
-    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Crowd forecast."
-  ),
-  list(
-    Name = "Hub-ensemble-with-convolution, 
-    Hub-ensemble-with-convolution-mean", 
-    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Convolution model (which originally was never included in any official Hub ensemble)."
-  ),
-    list(
-    Name = "Hub-ensemble-with-all, 
-    Hub-ensemble-with-all-mean", 
-    `Explanation` = "Versions of the official Hub ensembles which includes all our contributions.
-For cases, this is identical to the official Hub ensembles, but for deaths the convolution model was added."
-  ),
-
-  list(Name = "", Explanation = ""),
-  list(
-    Name = "Crowd forecast", 
-    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'"
-  ),  
-  list(
-    Name = "Renewal model", 
-    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'"
-  ),  
-  list(
-    Name = "Convolution model", 
-    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\\_secondary'"
-  )
-) %>%
-  kableExtra::kbl(format = "latex", booktabs = TRUE, 
-                  escape = FALSE,
-                  caption = "Overview of the models and ensembles used.",
-                  longtable = TRUE,
-                  linesep = c('\\addlinespace \\addlinespace')) %>%
-  kableExtra::column_spec(1, width = "4.5cm") %>%
-  kableExtra::column_spec(2, width = "11.0cm") %>%
-  kableExtra::kable_styling(latex_options = c("striped", "repeat_header")) 
-```
-
-```{r num-forecasters, fig.cap="Number of participants who submitted a forecast over time."}
-knitr::include_graphics("../analysis/plots/number-forecasters.png")
-```
-
-```{r num-ensemble-members, fig.cap="Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
-Note that the renewal model was not included in the ensemble on December 28th 2020."}
-knitr::include_graphics("../analysis/plots/ensemble-members.png")
-```
-
-\clearpage
-
-## Comparison of crowd forecasts and application baseline
-
-```{r compare-forecasters, fig.cap="Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the 90\\% and 50\\% prediction intervals as well as the median (in order of increasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons)."}
-knitr::include_graphics("../analysis/plots/comparison-forecast-interals.png")
-```

### 2022-08-04 manuscript/S4 Table.Rmd
final revisions

--- 2022-08-04 manuscript/S3 Table.Rmd
@@
 caption <- 
-  "Scores for three and four week ahead forecasts (cut to three significant digits and rounded).
+  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
 Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
@@
 
-```{r score-table-2}
-table <- readRDS("../analysis/plots/table_scores_4_ahead.rds")
+```{r score-table-ensemble-2}
+table <- readRDS("../analysis/plots/table_median-ensemble_scores_2_ahead.rds")
+# add_caption(table, caption)
 table
-# add_caption(table, caption, label = "tab:score-table-2")
 ```

### 2022-08-04 manuscript/final submission/Supplementary/S1-Table.tex
final revisions

--- 2022-05-19 manuscript/manuscript.tex
@@
 \usepackage{lmodern}
-\usepackage{setspace}
 \usepackage{iftex}
@@
 \hypersetup{
-  pdftitle={Comparing human and model-based forecasts of COVID-19 in Germany and Poland},
   hidelinks,
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
+\usepackage[margin=2cm]{geometry}
 \usepackage{graphicx}
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\usepackage{lineno}
-\linenumbers
-\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-\usepackage{float}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 \usepackage{booktabs}
@@
 
-\title{Comparing human and model-based forecasts of COVID-19 in Germany and Poland}
 \author{}
@@
 \begin{document}
-\maketitle
 
-\setstretch{2}
-\emph{Nikos I.
-Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy J.
-Quilty, Mark Jit, Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk}
-
-\hypertarget{abstract}{%
-\section{Abstract}\label{abstract}}
-
-Forecasts based on epidemiological modelling have played an important role in shaping public policy throughout the COVID-19 pandemic.
-This modelling combines knowledge about infectious disease dynamics with the subjective opinion of the researcher who develops and refines the model and often also adjusts model outputs.
-Developing a forecast model is difficult, resource- and time-consuming.
-It is therefore worth asking what modelling is able to add beyond the subjective opinion of the researcher alone.
-To investigate this, we analysed different real-time forecasts of cases of and deaths from COVID-19 in Germany and Poland over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
-We compared crowd forecasts elicited from researchers and volunteers, against a) forecasts from two semi-mechanistic models based on common epidemiological assumptions and b) the ensemble of all other models submitted to the Forecast Hub.
-We found crowd forecasts, despite being overconfident, to outperform all other methods across all forecast horizons when forecasting cases (weighted interval score relative to the Hub ensemble 2 weeks ahead: 0.89).
-Forecasts based on computational models performed comparably better when predicting deaths (rel.
-WIS 1.26), suggesting that epidemiological modelling and human judgement can complement each other in important ways.
-
-\hypertarget{author-summary}{%
-\section{Author summary}\label{author-summary}}
-
-Mathematical models of COVID-19 have played a key role in informing governments across the world.
-While mathematical models are informed by our knowledge of infectious disease dynamics, they are ultimately developed and iteratively adjusted by the researchers and shaped by their subjective opinions.
-To investigate what modelling is able to add beyond the subjective opinion of the researcher alone, we compared human forecasts with model-based predictions of COVID-19 cases and deaths submitted to the so-called German/Polish Forecast Hub (which collates a variety of models from a range of teams).\\
-We found that our human forecasts consistently outperformed an aggregate of all available model-based forecasts when predicting cases, but not when predicting deaths.
-Our findings suggest that human insight may be most valuable when forecasting highly uncertain quantities, which depend on many factors that are hard to model using equations, while mathematical models may be most useful in settings like predicting deaths, where leading indicators with a clear connection to the target variable are available.
-This potentially has very relevant policy implications, as agencies informing policy-makers could benefit from routinely eliciting human forecasts in addition to model-based predictions to inform policies.
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza (e.g.
-1,2--4), dengue fever (e.g.
-5,6,7), ebola (e.g.
-8,9), chikungunya (e.g.
-10,11) and now COVID-19 (e.g.
-12,13--17).
-Applications of epidemiological models differ in the way they make statements about the future.
-Forecasts aim to predict the future as it will occur, while scenario modelling and projections aim to represent what the future could look like under certain scenario assumptions or if conditions stayed the same as they were in the past.
-Forecasts can be judged by comparing them against observed data.
-Since it is much harder to fairly assess the accuracy and usefulness of projections and scenario modelling in the same way, this work focuses on forecasts, which represent only a subset of all epidemiological modelling.
-
-Since March 2020, forecasts of COVID-19 from multiple teams have been collected, aggregated and compared by Forecast Hubs such as the US Forecast Hub (13,14), the German and Polish Forecast Hub (15,16) and the European Forecast Hub (17).
-Often, different individual forecasts are combined into a single forecast, e.g.~by taking the mean or median of all forecasts.
-These ensemble forecasts usually tend to perform better and more consistently than individual forecasts (see e.g.
-(6); (18)).
-
-Individual computational models usually rely to varying degrees on mechanistic assumptions about infectious disease dynamics (such as SIR-type compartmental models that aim to represent how individuals move from being susceptible to infected and then recovered or dead).
-Some are more statistical in nature (such as time series models that detect statistical patterns without explicitly modelling disease dynamics).
-How exactly such a mathematical or computational model is constructed and which assumptions are made depends on subjective opinion and judgement of the researcher who develops and refines the model.
-Models are commonly adjusted and improved based on whether the model output looks plausible to the researchers involved.
-
-The process of model construction and refinement is laborious and time-consuming, and it is therefore worth asking what modelling can add beyond the subjective judgment of the researcher alone.
-In this work, we ask this question specifically in the context of predictive performance, and set aside other advantages of epidemiological modelling (such as reproducibility or the ability to obtain a deeper fundamental understanding of how diseases spread).
-One natural way to do this is to compare the predictive performance of forecasts based on computational models (``model-based forecasts'') against forecasts made by individual humans without explicit use of a computer model (``direct human forecasts'') or a combination of multiple such forecasts (``crowd forecasts'').
-
-Previous work has examined such direct human forecasts in various contexts, such as geopolitics (19,20), meta-science (21,22), sports (23) and epidemiology (11,24,25).
-Several prediction platforms (26--28) and prediction markets (29) have been created to collate expert and non-expert predictions.
-However, with the notable exception of (11), these forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) prediction formats.
-Direct human forecasts may be able to take into account insights and relationships between variables which are hard to specify using epidemiological models.
-However, it is not entirely clear in which situations human forecasts perform well or badly.
-For example, (11) found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available.
-However, humans tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown in these regions at the time.
-
-In this study, we analyse the performance of direct human forecasts relative to model-based forecasts and discuss the added benefit of epidemiological modelling over human judgement alone.
-As a case study, we use different forecasts, involving varying degrees of human intervention, which we submitted in real time to the German and Polish Forecast Hub.
-In contrast to (11) we elicited not only point predictions, but full predictive distributions (``probabilistic forecasts'', see e.g.
-(30)) from participants.
-This allows us to compare not only predictive accuracy, but also how well human forecasters and model-based forecasts were able to quantify forecast uncertainty.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-We created and submitted the following forecasts to the German and Polish Forecast Hub: 1) a direct human forecast (henceforth called ``crowd forecast''), elicited from participants through a web application (31) and 2) two semi-mechanistic model-based forecasts (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology.
-While the two semi-mechanistic forecasts were necessarily shaped by our implicit assumptions and decisions, they were designed such as to minimise the amount of human intervention involved.
-For example, we refrained from adjusting model outputs or refining the models based on past performance.
-Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (15,16).
-All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (32).
-This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub.
-Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the German and Polish Forecast Hub.
-
-\hypertarget{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}{%
-\subsection{Forecast targets and interaction with the German and Polish Forecast Hub}\label{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}}
-
-The German and Polish Forecast Hub (now mostly merged into the (17)) elicits predictions for various COVID-19 related forecast targets from different research groups every week.
-Forecasts had to be made every Monday (with submissions allowed until Tuesday 3pm) and were permitted to use any data that was available by Monday 11.59pm.
-We submitted forecasts for incident and cumulative weekly reported numbers of cases of and deaths from COVID-19 on a national level in Germany and Poland over a one to four week forecast horizon.
-Forecasts were submitted on Mondays, but weeks were defined as ending on a Saturday (and starting on Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26 days.
-Submissions were required in a quantile-based format with 23 quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10, 0.15, \ldots, 0.95, 0.975, 0.99.
-Forecasts submitted to the Forecast Hub were combined into different ensembles every week, with the median ensemble (i.e., the \(\alpha\)-quantile of the ensemble is given by the median of all submitted \(\alpha\)-quantiles) being the default ensemble shown on all official Forecast hub visualisations (\url{https://kitmetricslab.github.io/forecasthub/forecast}).
-
-Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish Forecast hub.
-Until December 14th, 2020, these data were sourced from the European Centre for Disease Control (33).
-After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (34).
-These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, (35)), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, (36)).
-The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).
-
-\hypertarget{crowd-forecasts}{%
-\subsection{Crowd forecasts}\label{crowd-forecasts}}
-
-Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application (\url{https://cmmid-lshtm.shinyapps.io/crowd-forecast/}).
-Weekly forecasts had to be submitted before Tuesday 12pm every week, but participants were asked to only use any information or data that was already available by Monday night.
-The application was built using the \texttt{shiny} and \texttt{golem} R packages (37,38) and is available in the \texttt{crowdforecastr} R package (31).
-To make a forecast in the application participants could select a predictive distribution (with the default being log-normal) to represent the probability that the forecasted quantity took certain values.
-Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in Figure \ref{fig:screenshot} in the SI).
-The default shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.~as \(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
-A comparison of the crowd forecasts against the default baseline shown in the application is displayed in Figure \ref{fig:compare-forecasters} in the Appendix.
-Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from (39).
-These data included, for example, notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
-From November 26 2020 on we displayed weekly small reports with a visualisation of past forecasts and scores on our website, epiforecasts.io.
-
-Forecasts were stored in a Google Sheet and downloaded, cleaned and processed every week for submission to the Forecast Hub.
-If a forecaster had submitted multiple predictions for a single target, only the latest submission was kept.
-Information on the chosen distribution as well as the parameters for median and width were used to obtain the required set of 23 quantiles from that distribution.
-Forecasts from all forecasters were then aggregated using an unweighted quantile-wise mean (i.e., the \(\alpha\)-quantile of the ensemble is given by the mean of all submitted \(\alpha\)-quantiles).
-To avoid issues with users trying out the app and submitting a random forecast, we required that a forecaster needed to make a forecast for at least two targets for a given forecast in order to be included in the crowd forecast ensemble.
-On a few occasions we deleted forecasts that were clearly the result of a user or software error (such as for example forecasts that were zero everywhere).
-
-individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation and were excluded from the submission as well as the analysis.
-
-Participants were recruited mostly within the Centre of Mathematical Modeling of Infectious Diseases at the London School of Hygiene \& Tropical Medicine, but participants were also invited personally or via social media to submit predictions.
-Depending on whether they had a background in either statistics, forecasting or epidemiology, participants were asked to self-identify as `experts' or `non-experts'.
-
-The study was approved by the Observational / Interventions Research Ethics Committee at the London School of Hygiene \& Tropical Medicine, LSHTM Ethics Reference: 22290.
-
-\hypertarget{model-based-forecasts}{%
-\subsection{Model-based forecasts}\label{model-based-forecasts}}
-
-We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R package (version 1.3.3) as our model-based forecasts (40).
-The first of these models, here called ``renewal model'', used the renewal equation (41) to predict reported cases and deaths (see details in the SI).
-It estimated the effective reproduction number \(R_t\) (the average number of people each person infected at time t is expected to infect in turn) and modelled future infections as a weighted sum of past infection multiplied by \(R_t\).
-\(R_t\) was assumed to stay constant beyond the forecast date, roughly corresponding to continuing the latest exponential trend in infections.
-On the 9th of November we altered the date when \(R_t\) was assumed to be constant from two weeks prior to the date of the forecast to the forecast date, which we found to yield a more stable \(R_t\) estimate.
-Reported case and death notifications were obtained by convolving predicted infections over data-based delay distributions (40,42--44) to model the time between infection and report date.
-The renewal model was used to predict cases as well as deaths with forecasts being generated for each target separately.
-Death forecasts from the renewal model were therefore not informed by past cases.
-One submission of the renewal model on December 28th 2020 was delayed and therefore not included in the official Forecast hub ensemble.
-
-The second model (``convolution model'', see details in SI) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses).
-The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model.
-The convolution model predicted deaths as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio).
-Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model with a multiplicative day-of-the-week effect (40).
-
-Line list data used to inform the prior for the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (45) with data available up to the 1st of August.
-All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (46) with each location and forecast target being fitted separately.
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-For the main analysis we focused mostly on two week ahead forecasts, as COVID-19 forecasts, especially for cases, were in the past found to have poor predictive performance beyond this horizon (15).
-Forecasts for cases were scored using the full period from October 2020 until March 2021.
-To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available.
-To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see Section \ref{sensitivity-analysis} in the SI).
-Results remained broadly unchanged.
-
-Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (47), the absolute error, relative bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule (48), meaning that in expectation the score is optimised by reporting a predictive distribution that is identical to the true data-generating distribution.
-Forecasters are therefore incentivised to report their true belief about the future.
-The WIS can be understood as a generalisation of the absolute error to quantile-based forecasts (also meaning that smaller values are better) and can be decomposed into three separate penalties: forecast spread (i.e.~uncertainty of forecasts), over-prediction and under-prediction.
-While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts.
-The bias metric (9) we use captures how much probability mass of the forecast was above or below the true value (mapped to values between -1 and 1) and therefore represents a general tendency to over- or under-predict in relative terms.
-A value of -1 implies that all quantiles of the predictive distribution are below the observed value and a value of 1 that all quantiles are above the observed value.
-Empirical coverage is the percentage of observed values that fall inside a given prediction interval (e.g.~how many observed values fall inside all 50\% prediction intervals).
-Scoring metrics are explained in more detail in Table \ref{tab:scoring-metrics} in the SI.
-All scores were calculated using the \texttt{scoringutils} R package (49).
-
-At all stages of the evaluation our forecasts were compared to the median ensemble of all \emph{other} models submitted to the German and Polish Forecast Hub (``Hub ensemble'').
-This ``Hub ensemble'' was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see details in Section \ref{contributions-hub}, as well as in Table \ref{tab:table-ensemble-versions} and Figure \ref{fig:num-ensemble-members} in the SI).
-What we call ``Hub ensemble'' in this article therefore differs from the ``official Hub ensemble'' (here called ``hub-ensemble-realised'') which included crowd forecasts as well as renewal model forecasts.
-To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e.~we divided the average scores for a given model by the average score achieved by the Hub ensemble on the same set of forecasts (with values \textgreater1 implying worse and values \textless1 implying better performance than the Hub ensemble).
-In addition to comparing our forecasts against the hub ensemble excluding our models, we also assessed the impact of our forecasts on the performance of the forecasting hub by recalculating separate versions of the Hub ensemble with only some (or all) of our forecasts included.
-Versions that included either all of our models (``hub-ensemble-with-all'') or only one of them (``hub-ensemble-with-X'') were computed retrospectively.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{crowd-forecast-participation}{%
-\subsection{Crowd forecast participation}\label{crowd-forecast-participation}}
-
-A total number of 32 participants submitted forecasts, 17 of those self-identified as `expert' in either forecasting or epidemiology.
-The median number of forecasters for any given forecast target was 6, the minimum 2 and the maximum 10.
-The mean number of submissions from an individual forecaster was 4.7 but the median number was only one - most participants dropped out after their first submission.
-Only two participants submitted a forecast every single week, both of whom are authors on this study.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} \caption{A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth}
-\end{figure}
-
-\hypertarget{case-forecasts}{%
-\subsection{Case Forecasts}\label{case-forecasts}}
-
-For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \ref{fig:agg-performance-all}A) and locations (Figure \ref{fig:performance-locations-rel}A).
-For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \ref{tab:score-table-2}).
-Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Figure \ref{fig:distribution-scores}).
-Overall, low variance in forecast performance was closely linked with good mean performance (Figures \ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \ref{fig:distribution-scores}), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
-WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
-
-To varying degrees, all forecasts exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened.
-For example, all forecasts failed to predict the change in trend from increase to decrease that happened in November in Germany and severely overshot reported cases (Figure \ref{fig:forecasts-and-truth}A).
-This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past of observations.
-The Hub ensemble and the crowd forecast, which had both been under-predicting throughout October, also failed to predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 (50) and the change in the testing regime (with stricter test criteria) on November 11th 2020 (36), were fastest to adapt to the new trend, and the Hub ensemble slowest.
-In December, cases rose again in Germany, with all models under-predicting this growth to varying extents.
-As in October, the renewal model captured the phase of exponential growth in cases slightly better than other approaches, but again overshot when reported case numbers fell over Christmas.
-The large variance in predictions in January in Germany (severe under-prediction followed by severe over-prediction) may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.
-Similar trends in performance were evident in Poland, with the crowd forecast quickest at adapting to the change in trend in November.
-In general, there were fewer large outlier forecasts in Poland and in particular the renewal model performed more in line with other forecasts there.
-
-All forecasting approaches, including the Hub ensemble, were overconfident, i.e.~they showed lower than nominal coverage (meaning that 50\% (90\%) prediction intervals generally covered less than 50\% (90\%) of the actually observed values) (Figure \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
-Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts.
-This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \ref{fig:agg-performance-all}E) and only showed a small increase in uncertainty across forecast horizons.
-The crowd forecasts prediction intervals were also noticeably narrower than the default baseline shown to forecasters in the application (see Figure \ref{fig:compare-forecasters}).
-
-In spite of good performance in terms of the absolute error (Figure \ref{fig:agg-performance-all}G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36\% and 55\% of all observations with the 50\% and 90\% prediction intervals of all forecasts made at a two week forecast horizon, and only 5\% and 38\% four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
-Despite worse performance in terms of absolute error (Figure \ref{fig:agg-performance-all}G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
-The crowd forecasts, on the other hand, showed a smaller bias than the renewal model, but were overconfident.
-
-The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons.
-The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \ref{fig:agg-performance-all}F).
-Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
-
-Generally, trends in overall performance were broadly similar across locations (Figures \ref{fig:performance-locations} and \ref{fig:performance-locations-rel}).
-Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
-However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \ref{fig:performance-locations-rel}A, \ref{fig:performance-locations-rel}G, \ref{fig:agg-performance-all-Germany}, \ref{fig:agg-performance-all-Poland}).
-
-\hypertarget{death-forecasts}{%
-\subsection{Death Forecasts}\label{death-forecasts}}
-
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure \ref{fig:agg-performance-all}B, Figure \ref{fig:performance-locations}B).
-Relative WIS values for the models two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1 (Hub ensemble) and 1.79 (renewal model).
-The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \ref{fig:agg-performance-all}B, Figure \ref{fig:performance-locations}B), and also better than the convolution model three and four weeks ahead.
-Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate \(R_t\) trace from deaths, does not use the available information efficiently.
-The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \ref{fig:agg-performance-all}B, Table \ref{tab:score-table-4}).
-
-As past cases and hospitalisations can be used as predictors, predicting a change in trend may be easier for deaths than for cases.
-Even though all forecasts generally struggled with this, there were some instances where changing trends were well captured or even anticipated.
-In Poland, for example, the Hub ensemble was able to capture or even anticipate the peak in deaths in December quite well (whereas the renewal model and crowd forecast did not).
-The renewal model, which mostly exhibited trend-following behaviour, correctly predicted another increase in weekly deaths in mid-January (potentially based on changes in daily deaths, as the renewal model did not know about past cases).
-In Germany in early January, all models predicted a decrease in deaths two to three weeks before it actually happened.
-Predictions from the renewal model at that time were likely strongly influenced by an unexpected drop in reported deaths in December.
-The other forecasting approaches and in particular, the convolution model may have been affected by potentially under-reported case numbers around Christmas.
-When the decrease that all models had predicted to happen in early January failed to materialise, the renewal model and the crowd forecast noticeably over-corrected and over-predicted deaths in the following weeks, while the Hub ensemble, and to a slightly lesser degree, the convolution model were able to capture the downturn well when it finally happened at the end of January.
-
-Death forecasts, generally, showed greater coverage of the 50\% and 90\% prediction intervals than case forecasts and no decrease in coverage across forecast horizons, indicating that it might be easier to appropriately quantify uncertainty for death forecasts.
-The Hub ensemble had the greatest coverage, with empirical coverage of the 50\% and 90\% prediction intervals exceeding 50\%, and 90\%, respectively, across all forecast horizons.
-Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
-As for cases, the crowd forecast tended to have the narrowest prediction intervals and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
-The convolution model had relatively narrow prediction intervals for short forecast horizons, but had rapidly (and non-linearly) increasing uncertainty for longer forecast horizons, driven by increasing uncertainty in the underlying case forecasts.
-
-For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \ref{fig:agg-performance-all}F.
-The convolution model had a strong tendency to under-predict, with the magnitude of under-prediction steadily decreasing for longer forecast horizons.
-The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction.
-For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \ref{fig:agg-performance-all}A, \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2}, \ref{tab:score-table-4}).
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} \caption{A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
-Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores.}\label{fig:distribution-scores}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Visualisation of relative aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
-“Hub-ensemble”   extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-rel}
-\end{figure}
-
-\hypertarget{contributions-hub}{%
-\subsection{Contribution to the Forecast Hub}\label{contributions-hub}}
-
-Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (``hub-ensemble-realised''), while the convolution model was never included as it was deemed too similar to the existing renewal model.
-In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on 28 December 2020 over the Christmas period) and a maximum of 10.
-Versions that included either all of our models (``hub-ensemble-with-all'') or only one of them (``hub-ensemble-with-X'') were computed retrospectively.
-An overview of all models and ensemble versions is shown in Table \ref{tab:table-ensemble-versions} in the SI.
-
-For cases, our contributions (compared to the Hub ensemble without our contributions) consistently improved performance across all forecasting horizons (rel.
-WIS 0.9 two weeks ahead, Table \ref{tab:score-table-ensemble-2}).
-Contributions from the crowd forecasts alone also improved performance of the Hub ensemble across all forecast horizons, while contributions from the renewal model had a negative effect for longer horizons (rel.
-WIS 1.02 three weeks ahead, 1.06 four weeks ahead).
-The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model have improved performance (Table \ref{tab:score-table-ensemble-4}).
-The realised ensemble performed comparably to the crowd forecasts for predictions one to two weeks ahead, and worse for greater forecast horizons.
-
-For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel.
-WIS of the Hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and \ref{tab:score-table-ensemble-4}).
-Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons).
-This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \ref{fig:agg-performance-all}) and especially worse for longer horizons.
-
-We also considered the impact of our contributions on a version of the Hub ensemble constructed by taking the quantile-wise mean, rather than the median.
-General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \ref{fig:agg-performance-ensemble-rel}B and \ref{fig:agg-performance-ensemble-mean}B).
-This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far.
-For both the mean and the median ensemble, changes in performance from adding or removing models were of a similar order of magnitude, suggesting that at least in this instance, with a relatively small ensemble size, the median ensemble was not necessarily more `robust' to changes than the mean ensemble.
-However, the ensemble version with all our forecasts included (``hub-ensemble-with-all'') tended to perform relatively better for the median ensemble than the mean ensemble, suggesting that adding more models may be more beneficial or `safer' for the median than for the mean ensemble as directional errors can more easily cancel out than errors in absolute terms.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Epidemiological forecasting modelling combines knowledge about infectious disease dynamics with the subjective opinion of the researcher who develops and refines the model.
-In this study, we compared forecasts of cases of and deaths from COVID-19 in Germany and Poland based purely on human judgement and elicited from a crowd of researchers and volunteers against forecasts from two semi-mechanistic epidemiological models.
-In spite of the small number of participants and a general tendency to be overconfident, crowd forecasts consistently outperformed our epidemiological models as well as the Hub ensemble when forecasting cases but not when forecasting deaths.
-This suggests that humans might be relatively good at foreseeing trends that are hard to model but may struggle to form an intuition for the exact relationship between cases and deaths.
-
-Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (e.g.
-12,13,14), or exclusively on human forecasts (19,20,24,25).
-In contrast, we directly compared human and model-based forecasts.
-This is similar to the approach taken by (11), but extends it in several ways.
-While Farrow et al.~only asked for point predictions and constructed a predictive distribution from these, we asked participants to provide a full predictive distribution, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse how humans quantified their uncertainty.
-In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-based insight.
-In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (12--15,17).
-
-The strong performance of crowd forecasts in our study is in line with results from Farrow et al.~who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants.
-The advantage of crowd forecasts we observed over our semi-mechanistic models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models.
-However, this probably explains only part of the difference, and performance relative to the Hub ensemble strongly suggests that human insight is valuable when forecasting highly volatile and potentially hard-to-predict quantities such as case numbers.
-One potential explanation is that humans can have access to data that is not available to or hard to integrate into model-based forecasts.
-Relatively good performance of our semi-mechanistic models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time.
-This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data).
-The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \ref{fig:forecasts-and-truth}A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting which have less of an influence on weekly reporting.
-
-Our results suggest that human intervention may be less beneficial when forecasting deaths (especially at shorter horizons, when deaths are largely dependent on already observed cases), which benefits from the ability to model the delays and exact epidemiological relationships between different leading and lagged indicators.
-Relatively good performance of the convolution model, especially compared to the poor performance of the renewal model on deaths (which used only deaths to estimate and predict the effective reproduction number) underlines the importance of including leading indicators such as cases as a predictor for deaths.
-
-Given the low number of participants in our study, it is difficult to generalise conclusions about crowd predictions to other settings.
-Using R shiny as a platform for the web application arguably created some limits to user experience and performance, influencing the number of participants and potentially creating a self-selection effect.
-Motivating forecasters to contribute regularly proved challenging, especially given that the majority of our participants were from the UK and may not have been familiar with all relevant details of the situation in Germany and Poland.
-On the other hand, R shiny facilitated quick development and allowed us to provide our crowd forecasting tooling as an open source R package, meaning that it is available for others to use, for example in settings like early-stage outbreaks where model-based forecasts are not available.
-In light of the relatively small number of Hub ensemble models, performance of the Hub ensemble is also difficult to generalise.
-More research is needed to replicate these findings and investigate how crowd forecasts compare against the types of models and model ensembles policy makers use to inform their decisions.
-
-Our work suggests that crowd forecasts and model-based forecasts could have different strengths and may be able to complement each other.
-When choosing a suitable approach for a given task it is important to take into account how the output will be used.
-In this work we focused on forecasts (which aim to predict future data points whilst accounting for all factors that might influence them), whereas policy makers might be more interested in projections (which show what would happen in the absence of any events that could change the trend) or scenario modelling.
-Forecasts may not be a suitable basis for informing policy decisions, if forecasters already have factored in the expectation of a future intervention.
-Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting projections that are not influenced by implicit assumptions about the future from humans may be harder.
-
-Further work should explore the effects of humans refining their mathematical models or changing model outputs in more detail.
-Model-based forecasts could be used as an input to human judgement, with researchers adjusting predictions generated by models.
-Seeing a model-based forecast could help humans calibrate uncertainty better, while allowing for manual intervention to adapt spurious trend predictions.
-Tools need to be developed to facilitate this process at a larger scale.
-Human insight could also be used as an input to models.
-Such a `hybrid' forecasting approach could for example ask humans to predict the trend of the effective reproduction number \(R_t\) or the doubling rate (i.e.~how the epidemic evolves) into the future and use this to estimate the exact number of cases, hospitalisations or deaths this would imply.
-In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust and widen prediction intervals may be another promising approach.
-Crowd forecasting in general could benefit greatly from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile to further develop and explore.
-
-\clearpage
-
-\textbf{Acknowledgements}
-
-NIB received funding from the Health Protection Research Unit (grant code NIHR200908, \url{https://www.nihr.ac.uk/}).
-SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z, \url{https://wellcome.org/}).
-The work of JB was supported by the Helmholtz Foundation (\url{https://www.helmholtz.de/}) via the SIMCARD Information and Data Science Pilot Project.
-This research was partly funded by the National Institute for Health Research (NIHR, \url{https://www.nihr.ac.uk/}) (16/137/109 \& 16/136/46) using UK aid from the UK Government to support global health research.
-The views expressed in this publication are those of the author(s) and not necessarily those of the NIHR or the UK Department of Health and Social Care.
-BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859, \url{https://www.gatesfoundation.org/}).
-EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908, \url{https://www.nihr.ac.uk/}) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688, \url{https://ec.europa.eu/programmes/horizon2020/}).
-AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID (\url{https://www.usaid.gov/}), and the Academy of Medical Sciences (\url{https://acmedsci.ac.uk/}).
-SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z, \url{https://wellcome.org/}), and the NIHR (NIHR200908, \url{https://www.nihr.ac.uk/}).
-
-We thank all forecasters who participated in this study for their contribution.
-
-We would also like to acknowledge (in a randomised order) the members of Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group at the the London School of Hygiene \& Tropical Medicine: Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie Diamond, Katherine E.
-Atkins, Rein M G J Houben, Jiayao Lei, Rachel Lowe, David Simons, Sophie R Meakin, Nicholas G.
-Davies, Timothy W Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly, Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas, Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson, Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun, Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche, James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday, Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael Pung, Anna M Foss.
-
-\clearpage
-
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
-
-\hypertarget{appendix-supplementary-information}{%
-\appendix}
-
-\hypertarget{supplementary-information}{%
-\section{Supplementary information}\label{supplementary-information}}
-
-\hypertarget{scoring-metrics-used}{%
-\subsection{Scoring metrics used}\label{scoring-metrics-used}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{13.0cm}}
-\caption{\label{tab:scoring-metrics}Overview of the scoring metrics used.}\\
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{9.3cm}}
 \toprule
@@
 \endfirsthead
-\caption[]{\label{tab:scoring-metrics}Overview of the scoring metrics used. \textit{(continued)}}\\
+\multicolumn{2}{@{}l}{\textit{(continued)}}\\
 \toprule
@@
 
-\clearpage
-
-\hypertarget{the-crowdforecasting-app}{%
-\subsection{The crowdforecasting app}\label{the-crowdforecasting-app}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../crowd-forecast/Screenshot-forecasting-app} \caption{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).
-}\label{fig:screenshot}
-\end{figure}
-
-\clearpage
-
-\hypertarget{further-details-on-the-semi-mechanistic-forecasting-models}{%
-\subsection{Further details on the semi-mechanistic forecasting models}\label{further-details-on-the-semi-mechanistic-forecasting-models}}
-
-\hypertarget{renewal-equation-model}{%
-\subsubsection{Renewal equation model}\label{renewal-equation-model}}
-
-The model was initialised prior to the first observed data point by assuming constant exponential growth for the mean of assumed delays from infection to case report.
-
-\begin{align}
-  I_{t} &= I_0 \exp  \left(r t \right)  \\
-  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
-  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
-\end{align}
-
-Where \(I_{obs}\) and \(r_{obs}\) are estimated from the first week of observed data.
-For the time window of the observed data infections were then modelled by weighting previous infections by the generation time and scaling by the instantaneous reproduction number.
-These infections were then convolved to cases by date (\(O_t\)) and cases by date of report (\(D_t\)) using log-normal delay distributions.
-This model can be defined mathematically as follows,
-
-\begin{align}
-  \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
-  I_t &= R_t \sum_{\tau = 1}^{15} w(\tau | \mu_{w}, \sigma_{w}) I_{t - \tau} \\
-  O_t &= \sum_{\tau = 0}^{15} \xi_{O}(\tau | \mu_{\xi_{O}}, \sigma_{\xi_{O}}) I_{t-\tau} \\
-  D_t &= \alpha \sum_{\tau = 0}^{15} \xi_{D}(\tau | \mu_{\xi_{D}}, \sigma_{\xi_{D}}) O_{t-\tau} \\ 
-  C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
-\end{align}
-
-Where,
-\begin{align}
-     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
-    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
-    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
-\end{align}
-
-This model used the following priors for cases,
-
-\begin{align}
-     R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
-    \mu_w &\sim \mathcal{N}(3.6, 0.7) \\
-    \sigma_w &\sim \mathcal{N}(3.1, 0.8) \\
-    \mu_{\xi_{O}} &\sim \mathcal{N}(1.62, 0.064) \\
-    \sigma_{\xi_{O}} &\sim \mathcal{N}(0.418, 0.069) \\
-    \mu_{\xi_{D}} &\sim \mathcal{N}(0.614, 0.066) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(1.51, 0.048) \\
-    \alpha &\sim \mathcal{N}(0.25, 0.05) \\
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-and updated the reporting process as follows when forecasting deaths,
-
-\begin{align}
-    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
-    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
-\end{align}
-
-\(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) were truncated to be greater than 0 and with \(\xi\), and \(w\) normalised to sum to 1.
-
-The prior for the generation time was sourced from (51) but refit using a log-normal incubation period with a mean of 5.2 days (SD 1.1) and SD of 1.52 days (SD 1.1) with this incubation period also being used as a prior (52) for \(\xi_{O}\).
-This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
-We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1\% or 1769 samples of the available data (45,53) and combining the posteriors for the mean and standard deviation of the log-normal distribution (40,42,46,54).
-
-\(GP_t\) is an approximate Hilbert space Gaussian process as defined in (55) using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20\% of the number of days used in fitting).
-The length scale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
-The magnitude of the Gaussian process was assumed to be normally distributed centred at 0 with a standard deviation of 0.1.
-
-From the forecast time horizon (\(T\)) and onwards the last value of the Gaussian process was used (hence \(R_t\) was assumed to be fixed) and latent infections were adjusted to account for the proportion of the population that was susceptible to infection as follows,
-
-\begin{equation}
-    I_t = (N - I^c_{t-1}) \left(1 - \exp \left(\frac{-I'_t}{N - I^c_{T}}\right)\right),
-\end{equation}
-
-where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\) and \(I'_t\) are the unadjusted infections defined above.
-This adjustment is based on that implemented in the \texttt{epidemia} R package (56,57).
-
-\hypertarget{convolution-model}{%
-\paragraph{Convolution model}\label{convolution-model}}
-
-The convolution model shares the same observation model as the renewal model but rather than assuming that an observation is predicted by itself using the renewal equation instead assumes that it is predicted entirely by another observation after some parametric delay.
-It can be defined mathematically as follows,
-
-\begin{equation} 
-    D_{t} \sim \mathrm{NB}\left(\omega_{(t \mod 7)} \alpha \sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) C_{t-\tau},  \phi \right)
-\end{equation}
-
-with the following priors,
-
-\begin{align}
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \alpha &\sim \mathcal{N}(0.01, 0.02) \\
-    \xi &\sim \mathcal{LN}(\mu, \sigma) \\
-    \mu &\sim \mathcal{N}(2.5, 0.5) \\
-\sigma &\sim \mathcal{N}(0.47, 0.2) \\
-\phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-with \(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) truncated to be greater than 0 and with \(\xi\) normalised such that \(\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1\).
-
-\hypertarget{model-fitting}{%
-\subsubsection{Model fitting}\label{model-fitting}}
-
-Both models were implemented using the \texttt{EpiNow2} R package (version 1.3.3) (40).
-Each forecast target was fitted independently for each model using Markov-chain Monte Carlo (MCMC) in stan (46).
-A minimum of 4 chains were used with a warmup of 250 samples for the renewal equation-based model and 1000 samples for the convolution model.
-2000 samples total post warmup were used for the renewal equation model and 4000 samples for the convolution model.
-Different settings were chosen for each model to optimise compute time contingent on convergence.
-Convergence was assessed using the R hat diagnostic (46).
-For the convolution model forecast the case forecast from the renewal equation model was used in place of observed cases beyond the forecast horizon using 1000 posterior samples.
-12 weeks of data was used for both models though only 3 weeks of data were included in the likelihood for the convolution model.
-
-\clearpage
-
-\hypertarget{tables-with-results-of-the-forecast-evaluation}{%
-\subsection{Tables with results of the forecast evaluation}\label{tables-with-results-of-the-forecast-evaluation}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 7010 (0.8) & 7480 (0.64) & 2680 (0.73) & 1700 (1.38) & 2630 (0.68) & -0.01 & 10400 (0.82) & 0.55 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 8740 (1) & 11800 (1.01) & 2190 (0.6) & 2720 (2.21) & 3830 (0.99) & 0.18 & 12000 (0.94) & 0.48 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 16200 (0.89) & 16600 (0.76) & 3660 (0.6) & 5930 (1.56) & 6600 (0.78) & -0.01 & 23300 (0.87) & 0.36 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25600 (1.4) & 33800 (1.54) & 5420 (0.88) & 5920 (1.56) & 14200 (1.69) & 0.17 & 34600 (1.29) & 0.43 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 27000 (0.81) & 26200 (0.64) & 4750 (0.52) & 11000 (1.43) & 11200 (0.67) & 0.02 & 39000 (0.83) & 0.14 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 50600 (1.51) & 70000 (1.72) & 10800 (1.18) & 7710 (1) & 32100 (1.93) & 0.13 & 68700 (1.46) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 39200 (0.7) & 38600 (0.52) & 5970 (0.49) & 15600 (1.26) & 17600 (0.56) & 0.07 & 54800 (0.74) & 0.05 & 0.38\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 91700 (1.64) & 135000 (1.83) & 19500 (1.6) & 8990 (0.72) & 63200 (2.02) & 0.09 & 125000 (1.68) & 0.31 & 0.48\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{aggregate-performance-by-location}{%
-\subsection{Aggregate performance by location}\label{aggregate-performance-by-location}}
-
-\hypertarget{performance-in-germany}{%
-\subsubsection{Performance in Germany}\label{performance-in-germany}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Germany-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Germany}
-\end{figure}
-
-\hypertarget{performance-in-poland}{%
-\subsubsection{Performance in Poland}\label{performance-in-poland}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Poland-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Poland}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-absolute-terms}{%
-\subsubsection{Performance across locations in absolute terms}\label{performance-across-locations-in-absolute-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-v4} \caption{Visualisation of aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-relative-terms}{%
-\subsection{Performance across locations in relative terms}\label{performance-across-locations-in-relative-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4} \caption{Visualisation of relative aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals.
-E: Dispersion.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast.
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations-rel}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-daily-reported-cases-and-deaths}{%
-\subsection{Visualisation of daily reported cases and deaths}\label{visualisation-of-daily-reported-cases-and-deaths}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily_truth} \caption{Visualisation of daily report data.
-The black line represents weekly data divided by seven.
-Data were last accessed through the German and Polish Forecast Hub on August 21 2021.}\label{fig:daily-truth}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily-data-updates} \caption{Visualisation of the absolute difference between the daily report data at the time and the data now.
-In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:daily-truth-update}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/weekly-data-updates} \caption{Visualisation of the relative difference between the weekly report data at the time and the data now.
-Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:weekly-truth-update}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}{%
-\subsection{Visualisation of scores and forecasts 1, 3, 4 weeks ahead}\label{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} \caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} \caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} \caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-4}
-\end{figure}
-
-\clearpage
-
-\hypertarget{distribution-of-scores}{%
-\subsection{Distribution of scores}\label{distribution-of-scores}}
-
-\hypertarget{absolute-scores}{%
-\subsubsection{Absolute scores}\label{absolute-scores}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1} \caption{A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3} \caption{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4} \caption{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-4}
-\end{figure}
-
-\hypertarget{ranks-achieved-by-forecasts}{%
-\subsubsection{Ranks achieved by forecasts}\label{ranks-achieved-by-forecasts}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-2}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-4}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} \caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-renewal} \caption{Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences-renewal}
-\end{figure}
-
-\newpage
-
-\hypertarget{comparison-of-ensembles}{%
-\subsection{Comparison of ensembles}\label{comparison-of-ensembles}}
-
-\hypertarget{performance-visualisation-mean-ensemble}{%
-\subsubsection{Performance visualisation mean ensemble}\label{performance-visualisation-mean-ensemble}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble”     extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
-Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-mean}
-\end{figure}
-
-\hypertarget{tables-median-ensemble}{%
-\subsubsection{Tables median ensemble}\label{tables-median-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 6970 (0.79) & 8260 (0.71) & 3060 (0.83) & 943 (0.77) & 2970 (0.77) & 0.04 & 10800 (0.85) & 0.55 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 7820 (0.89) & 9630 (0.82) & 3270 (0.89) & 1210 (0.98) & 3330 (0.86) & -0.02 & 12000 (0.94) & 0.48 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 7960 (0.91) & 10300 (0.88) & 3190 (0.87) & 1020 (0.83) & 3760 (0.97) & 0.04 & 12100 (0.95) & 0.57 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 16400 (0.9) & 19600 (0.89) & 5350 (0.87) & 3290 (0.87) & 7730 (0.92) & 0.02 & 24200 (0.9) & 0.43 & 0.69\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 16900 (0.92) & 19600 (0.89) & 5230 (0.85) & 4310 (1.13) & 7370 (0.88) & 0.00 & 24600 (0.92) & 0.38 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 17500 (0.96) & 21400 (0.98) & 5830 (0.95) & 2880 (0.76) & 8770 (1.04) & 0.00 & 25500 (0.95) & 0.45 & 0.71\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 235 (0.95) & 332 (0.98) & 88.6 (0.96) & 90.4 (0.79) & 55.5 (1.33) & -0.01 & 323 (0.97) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 234 (0.94) & 331 (0.98) & 85.2 (0.92) & 98.1 (0.85) & 50.2 (1.21) & -0.05 & 329 (0.99) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 234 (0.94) & 329 (0.97) & 90.7 (0.98) & 118 (1.03) & 25.3 (0.61) & -0.08 & 333 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 239 (0.96) & 337 (1) & 85.2 (0.92) & 99.6 (0.87) & 54.2 (1.3) & -0.03 & 322 (0.96) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 246 (0.99) & 342 (1.01) & 91.5 (0.99) & 106 (0.92) & 48.6 (1.17) & -0.06 & 342 (1.02) & 0.67 & 0.92\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 296 (1.01) & 398 (1.03) & 125 (0.95) & 91 (0.84) & 80.2 (1.55) & 0.05 & 486 (1.13) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 303 (1.04) & 423 (1.1) & 115 (0.87) & 122 (1.13) & 66.1 (1.27) & 0.00 & 483 (1.13) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 270 (0.92) & 385 (1) & 121 (0.92) & 119 (1.1) & 29.9 (0.58) & -0.04 & 403 (0.94) & 0.58 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 303 (1.04) & 392 (1.02) & 122 (0.92) & 106 (0.98) & 74.6 (1.44) & 0.03 & 499 (1.16) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 296 (1.01) & 397 (1.03) & 128 (0.97) & 97.1 (0.9) & 71.2 (1.37) & -0.01 & 462 (1.08) & 0.67 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 30800 (0.92) & 38600 (0.95) & 7910 (0.87) & 6890 (0.9) & 16000 (0.96) & 0.03 & 44200 (0.94) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 30800 (0.92) & 34100 (0.84) & 7500 (0.82) & 8960 (1.17) & 14300 (0.86) & 0.02 & 44100 (0.94) & 0.24 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 34000 (1.02) & 43100 (1.06) & 8860 (0.97) & 6300 (0.82) & 18900 (1.14) & 0.02 & 48100 (1.03) & 0.29 & 0.60\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 51200 (0.92) & 69900 (0.95) & 10900 (0.89) & 11100 (0.9) & 29300 (0.94) & 0.04 & 69600 (0.94) & 0.19 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 48800 (0.87) & 58600 (0.8) & 9700 (0.8) & 13700 (1.1) & 25400 (0.81) & 0.00 & 65800 (0.88) & 0.19 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 59100 (1.06) & 84100 (1.14) & 12600 (1.03) & 10100 (0.81) & 36400 (1.16) & 0.01 & 78900 (1.06) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 332 (1.04) & 388 (1.18) & 158 (0.92) & 78.7 (0.85) & 95 (1.72) & -0.02 & 547 (1.12) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 321 (1.01) & 385 (1.17) & 153 (0.89) & 100 (1.08) & 68.1 (1.24) & -0.01 & 535 (1.1) & 0.54 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 298 (0.93) & 337 (1.03) & 155 (0.9) & 106 (1.14) & 37.5 (0.68) & -0.04 & 441 (0.9) & 0.67 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 319 (1) & 342 (1.04) & 160 (0.93) & 85.1 (0.92) & 73.6 (1.34) & -0.02 & 547 (1.12) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 332 (1.04) & 363 (1.11) & 168 (0.98) & 86.1 (0.93) & 78.2 (1.42) & -0.02 & 528 (1.08) & 0.58 & 0.96\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 445 (1.05) & 532 (1.2) & 193 (0.91) & 107 (0.85) & 144 (1.68) & -0.03 & 700 (1.04) & 0.54 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 399 (0.94) & 438 (0.99) & 195 (0.92) & 105 (0.83) & 97.9 (1.14) & -0.05 & 692 (1.03) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 384 (0.91) & 387 (0.87) & 196 (0.92) & 122 (0.97) & 65.9 (0.77) & -0.06 & 602 (0.89) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 407 (0.96) & 456 (1.03) & 202 (0.95) & 105 (0.83) & 101 (1.18) & -0.03 & 669 (0.99) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 457 (1.08) & 527 (1.19) & 208 (0.98) & 129 (1.02) & 121 (1.41) & -0.06 & 744 (1.1) & 0.50 & 0.96\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\hypertarget{tables-mean-ensemble}{%
-\subsubsection{Tables mean ensemble}\label{tables-mean-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 8680 (1) & 10300 (1) & 3700 (1) & 1460 (1) & 3520 (1) & -0.02 & 13400 (1) & 0.50 & 0.86\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 7600 (0.88) & 8770 (0.85) & 3360 (0.91) & 1090 (0.75) & 3140 (0.89) & 0.01 & 11900 (0.89) & 0.52 & 0.90\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 8050 (0.93) & 9070 (0.88) & 3520 (0.95) & 1410 (0.97) & 3120 (0.89) & -0.02 & 12600 (0.94) & 0.48 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 8090 (0.93) & 9780 (0.95) & 3490 (0.94) & 1110 (0.76) & 3490 (0.99) & 0.02 & 12700 (0.95) & 0.57 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 19000 (1) & 22100 (1) & 5960 (1) & 3690 (1) & 9340 (1) & 0.02 & 28800 (1) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 17100 (0.9) & 20600 (0.93) & 5550 (0.93) & 2850 (0.77) & 8660 (0.93) & 0.05 & 26000 (0.9) & 0.38 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 17600 (0.93) & 20000 (0.9) & 5540 (0.93) & 3790 (1.03) & 8230 (0.88) & 0.01 & 26800 (0.93) & 0.36 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 18300 (0.96) & 22600 (1.02) & 5910 (0.99) & 2640 (0.72) & 9720 (1.04) & 0.06 & 27700 (0.96) & 0.38 & 0.76\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 229 (1) & 292 (1) & 101 (1) & 90.4 (1) & 36.7 (1) & -0.07 & 315 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 219 (0.96) & 289 (0.99) & 96.8 (0.96) & 79.8 (0.88) & 42.6 (1.16) & -0.04 & 297 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 217 (0.95) & 287 (0.98) & 95.3 (0.94) & 83.1 (0.92) & 38.7 (1.05) & -0.07 & 300 (0.95) & 0.67 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 225 (0.98) & 292 (1) & 98.7 (0.98) & 94.2 (1.04) & 32 (0.87) & -0.09 & 314 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 222 (0.97) & 289 (0.99) & 98 (0.97) & 84.1 (0.93) & 39.6 (1.08) & -0.04 & 295 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 225 (0.98) & 290 (0.99) & 99.7 (0.99) & 84.7 (0.94) & 40.5 (1.1) & -0.05 & 314 (1) & 0.71 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 256 (1) & 306 (1) & 138 (1) & 64.5 (1) & 53.2 (1) & 0.04 & 374 (1) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 270 (1.05) & 338 (1.1) & 136 (0.99) & 65.2 (1.01) & 68.1 (1.28) & 0.06 & 413 (1.1) & 0.75 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 268 (1.05) & 346 (1.13) & 133 (0.96) & 78.7 (1.22) & 57.1 (1.07) & 0.05 & 408 (1.09) & 0.75 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 259 (1.01) & 322 (1.05) & 133 (0.96) & 81.7 (1.27) & 44.4 (0.83) & 0.03 & 380 (1.02) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 264 (1.03) & 315 (1.03) & 133 (0.96) & 70.1 (1.09) & 60 (1.13) & 0.06 & 404 (1.08) & 0.71 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 264 (1.03) & 332 (1.08) & 141 (1.02) & 60.1 (0.93) & 63.1 (1.19) & 0.06 & 390 (1.04) & 0.79 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 35600 (1) & 42100 (1) & 9340 (1) & 7050 (1) & 19200 (1) & 0.03 & 51200 (1) & 0.26 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 32100 (0.9) & 40500 (0.96) & 8830 (0.95) & 4920 (0.7) & 18300 (0.95) & 0.07 & 47200 (0.92) & 0.29 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 32200 (0.9) & 36700 (0.87) & 8430 (0.9) & 7190 (1.02) & 16500 (0.86) & 0.04 & 46900 (0.92) & 0.24 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 35200 (0.99) & 46000 (1.09) & 9630 (1.03) & 4600 (0.65) & 20900 (1.09) & 0.08 & 51000 (1) & 0.38 & 0.67\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 60300 (1) & 79300 (1) & 15700 (1) & 10400 (1) & 34100 (1) & 0.04 & 78600 (1) & 0.29 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 55000 (0.91) & 77100 (0.97) & 14600 (0.93) & 6620 (0.64) & 33800 (0.99) & 0.11 & 75200 (0.96) & 0.33 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 53400 (0.89) & 66600 (0.84) & 13700 (0.87) & 10600 (1.02) & 29200 (0.86) & 0.06 & 70400 (0.9) & 0.26 & 0.60\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 61700 (1.02) & 89800 (1.13) & 16400 (1.04) & 6400 (0.62) & 38900 (1.14) & 0.12 & 82900 (1.05) & 0.31 & 0.64\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 289 (1) & 293 (1) & 178 (1) & 45.9 (1) & 65.7 (1) & 0.01 & 443 (1) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 310 (1.07) & 348 (1.19) & 182 (1.02) & 42 (0.92) & 86.5 (1.32) & 0.08 & 502 (1.13) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 315 (1.09) & 339 (1.16) & 178 (1) & 62.2 (1.36) & 74 (1.13) & 0.07 & 507 (1.14) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 297 (1.03) & 292 (1) & 174 (0.98) & 67.7 (1.47) & 55 (0.84) & 0.01 & 452 (1.02) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 294 (1.02) & 299 (1.02) & 172 (0.97) & 48 (1.05) & 74.2 (1.13) & 0.03 & 476 (1.07) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 310 (1.07) & 349 (1.19) & 189 (1.06) & 39.4 (0.86) & 81.9 (1.25) & 0.05 & 482 (1.09) & 0.62 & 1.00\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 437 (1) & 568 (1) & 232 (1) & 72 (1) & 134 (1) & 0.00 & 702 (1) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 445 (1.02) & 598 (1.05) & 237 (1.02) & 56.4 (0.78) & 152 (1.13) & 0.06 & 707 (1.01) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 421 (0.96) & 520 (0.92) & 239 (1.03) & 49.9 (0.69) & 132 (0.99) & 0.05 & 678 (0.97) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 398 (0.91) & 465 (0.82) & 235 (1.01) & 55.6 (0.77) & 107 (0.8) & 0.00 & 628 (0.89) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 418 (0.96) & 533 (0.94) & 222 (0.96) & 66.8 (0.93) & 129 (0.96) & 0.03 & 662 (0.94) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 467 (1.07) & 636 (1.12) & 248 (1.07) & 61 (0.85) & 158 (1.18) & 0.05 & 755 (1.08) & 0.67 & 1.00\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{sensitivity-analysis}{%
-\subsection{Sensitivity analysis}\label{sensitivity-analysis}}
-
-In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later.
-This sensitivity shows performance of all models restricted to the period from December 14 2020 until March 1st 2021 where all models were available.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-late}
-\end{figure}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 4980 (0.74) & 5730 (0.64) & 2070 (0.6) & 728 (0.74) & 2190 (0.94) & 0.09 & 7810 (0.82) & 0.54 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 6730 (1) & 8960 (1) & 3430 (1) & 978 (1) & 2330 (1) & -0.09 & 9550 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 9640 (1.43) & 13300 (1.48) & 1970 (0.57) & 4170 (4.26) & 3500 (1.5) & 0.09 & 12700 (1.33) & 0.46 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 10700 (0.99) & 13800 (1.1) & 2880 (0.58) & 2350 (0.85) & 5430 (1.79) & 0.08 & 15400 (1.07) & 0.46 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 10800 (1) & 12500 (1) & 4940 (1) & 2780 (1) & 3030 (1) & -0.13 & 14400 (1) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25000 (2.31) & 34000 (2.72) & 4780 (0.97) & 8710 (3.13) & 11500 (3.8) & 0.05 & 32000 (2.22) & 0.50 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 17200 (1) & 16000 (0.98) & 3800 (0.63) & 5660 (0.85) & 7770 (1.74) & 0.07 & 26800 (1.1) & 0.08 & 0.58\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 17200 (1) & 16300 (1) & 6030 (1) & 6670 (1) & 4470 (1) & -0.16 & 24400 (1) & 0.33 & 0.67\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 37700 (2.19) & 55900 (3.43) & 8840 (1.47) & 10700 (1.6) & 18100 (4.05) & -0.03 & 49800 (2.04) & 0.33 & 0.58\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 26100 (0.95) & 21000 (0.84) & 4810 (0.7) & 11300 (0.83) & 10100 (1.43) & 0.04 & 39400 (1.05) & 0.00 & 0.46\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 27600 (1) & 25000 (1) & 6900 (1) & 13600 (1) & 7060 (1) & -0.19 & 37400 (1) & 0.29 & 0.54\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 48900 (1.77) & 77800 (3.11) & 13800 (2) & 11900 (0.88) & 23200 (3.29) & -0.10 & 65500 (1.75) & 0.38 & 0.58\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{overview-of-models-and-forecasters}{%
-\subsection{Overview of models and forecasters}\label{overview-of-models-and-forecasters}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{11.0cm}}
-\caption{\label{tab:table-ensemble-versions}Overview of the models and ensembles used.}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{\label{tab:table-ensemble-versions}Overview of the models and ensembles used. \textit{(continued)}}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-\cellcolor{gray!6}{Hub-ensemble-realised} & \cellcolor{gray!6}{Official Forecast Hub median ensemble.
-Created by the Forecast Hub officially under the name 'KITCOVIDhub-median\_ensemble' and used as the default ensemble.
-Included are our crowd forecasts as well as the renewal model (with one missed submission on December 28 2020, but not the convolution model which was deemed to similar to the renewal model.}\\
-\addlinespace \addlinespace
-Hub-ensemble-realised-mean & Official Forecast Hub mean ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-mean\_ensemble'.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{ \vphantom{1}} & \cellcolor{gray!6}{}\\
-\addlinespace \addlinespace
-Hub-ensemble & Version of the official Hub median ensemble which excludes all our contributions.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Hub-ensemble-mean} & \cellcolor{gray!6}{Version of the official Hub mean ensemble which excludes all our contributions.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-renewal, 
-    Hub-ensemble-with-renewal-mean & Versions of the official Hub ensembles which of our contributions includes only the Renewal model.\\
-\addlinespace \addlinespace
-Hub-ensemble-with-crowd, 
-\cellcolor{gray!6}{    Hub-ensemble-with-crowd-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which of our contributions includes only the Crowd forecast.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-convolution, 
-    Hub-ensemble-with-convolution-mean & Versions of the official Hub ensembles which of our contributions includes only the Convolution model (which originally was never included in any official Hub ensemble).\\
-\addlinespace \addlinespace
-Hub-ensemble-with-all, 
-\cellcolor{gray!6}{    Hub-ensemble-with-all-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which includes all our contributions.
-For cases, this is identical to the official Hub ensembles, but for deaths the convolution model was added.}\\
-\addlinespace \addlinespace
- & \\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Crowd forecast} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'}\\
-\addlinespace \addlinespace
-Renewal model & Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Convolution model} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\_secondary'}\\*
-\end{longtable}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/number-forecasters} \caption{Number of participants who submitted a forecast over time.}\label{fig:num-forecasters}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/ensemble-members} \caption{Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
-Note that the renewal model was not included in the ensemble on December 28th 2020.}\label{fig:num-ensemble-members}
-\end{figure}
-
-\clearpage
-
-\hypertarget{comparison-of-crowd-forecasts-and-application-baseline}{%
-\subsection{Comparison of crowd forecasts and application baseline}\label{comparison-of-crowd-forecasts-and-application-baseline}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} \caption{Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the 90\% and 50\% prediction intervals as well as the median (in order of increasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons).}\label{fig:compare-forecasters}
-\end{figure}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{McGowan CJ, Biggerstaff M, Johansson M, Apfeldorf KM, Ben-Nun M, Brooks L, et al.
-Collaborative efforts to forecast seasonal influenza in the {United States}, 2015--2016.
-Scientific Reports {[}Internet{]}.
-2019 Jan 24 {[}cited 2021 May 30{]};9(1, 1):683.
-Available from: \url{https://www.nature.com/articles/s41598-018-36361-9}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Reich NG, Brooks LC, Fox SJ, Kandula S, McGowan CJ, Moore E, et al.
-A collaborative multiyear, multimodel assessment of seasonal influenza forecasting in the {United States}.
-PNAS {[}Internet{]}.
-2019 Feb 19 {[}cited 2021 Oct 13{]};116(8):3146--54.
-Available from: \url{https://www.pnas.org/content/116/8/3146}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Shaman J, Karspeck A.
-Forecasting seasonal outbreaks of influenza.
-PNAS {[}Internet{]}.
-2012 Dec 11 {[}cited 2021 Oct 13{]};109(50):20425--30.
-Available from: \url{https://www.pnas.org/content/109/50/20425}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Biggerstaff M, Alper D, Dredze M, Fox S, Fung IC-H, Hickmann KS, et al.
-Results from the centers for disease control and prevention's predict the 2013--2014 {Influenza Season Challenge}.
-BMC Infectious Diseases {[}Internet{]}.
-2016 Jul 22 {[}cited 2021 Oct 13{]};16(1):357.
-Available from: \url{https://doi.org/10.1186/s12879-016-1669-x}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak AL, Baugher B, et al.
-An open challenge to advance probabilistic forecasting for dengue epidemics.
-PNAS {[}Internet{]}.
-2019 Nov 26 {[}cited 2021 May 30{]};116(48):24268--74.
-Available from: \url{https://www.pnas.org/content/116/48/24268}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Yamana TK, Kandula S, Shaman J.
-Superensemble forecasts of dengue outbreaks.
-Journal of The Royal Society Interface {[}Internet{]}.
-2016 Oct 31 {[}cited 2021 May 30{]};13(123):20160410.
-Available from: \url{https://royalsocietypublishing.org/doi/full/10.1098/rsif.2016.0410}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Colón-González FJ, Bastos LS, Hofmann B, Hopkin A, Harpham Q, Crocker T, et al.
-Probabilistic seasonal dengue forecasting in {Vietnam}: {A} modelling study using superensembles.
-PLOS Medicine {[}Internet{]}.
-2021 Mar 4 {[}cited 2021 Mar 6{]};18(3):e1003542.
-Available from: \url{https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.1003542}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Viboud C, Sun K, Gaffey R, Ajelli M, Fumanelli L, Merler S, et al.
-The {RAPIDD} ebola forecasting challenge: {Synthesis} and lessons learnt.
-Epidemics {[}Internet{]}.
-2018 Mar 1 {[}cited 2021 May 30{]};22:13--21.
-Available from: \url{https://www.sciencedirect.com/science/article/pii/S1755436517301275}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Funk S, Camacho A, Kucharski AJ, Lowe R, Eggo RM, Edmunds WJ.
-Assessing the performance of real-time epidemic forecasts: {A} case study of {Ebola} in the {Western Area} region of {Sierra Leone}, 2014-15.
-PLOS Computational Biology {[}Internet{]}.
-2019 Feb 11 {[}cited 2019 Sep 16{]};15(2):e1006785.
-Available from: \url{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1006785}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Del Valle SY, McMahon BH, Asher J, Hatchett R, Lega JC, Brown HE, et al.
-Summary results of the 2014-2015 {DARPA Chikungunya} challenge.
-BMC Infectious Diseases {[}Internet{]}.
-2018 May 30 {[}cited 2021 Oct 13{]};18(1):245.
-Available from: \url{https://doi.org/10.1186/s12879-018-3124-7}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Farrow DC, Brooks LC, Hyun S, Tibshirani RJ, Burke DS, Rosenfeld R.
-A human judgment approach to epidemiological forecasting.
-PLOS Computational Biology {[}Internet{]}.
-2017 Mar 10 {[}cited 2021 Jul 29{]};13(3):e1005248.
-Available from: \url{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005248}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Funk S, Abbott S, Atkins BD, Baguelin M, Baillie JK, Birrell P, et al.
-Short-term forecasts to inform the response to the {Covid-19} epidemic in the {UK}.
-medRxiv {[}Internet{]}.
-2020 Nov 13 {[}cited 2020 Nov 28{]};2020.11.11.20220962.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2020.11.11.20220962v1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K, et al.
-{COVID-19 Forecast Hub}: 4 {December} 2020 snapshot {[}Internet{]}.
-{Zenodo}; 2020 {[}cited 2021 May 29{]}.
-Available from: \url{https://zenodo.org/record/3963371}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A, Rivadeneira AJC, et al.
-Evaluation of individual and ensemble probabilistic forecasts of {COVID-19} mortality in the {US}.
-medRxiv {[}Internet{]}.
-2021 Feb 5 {[}cited 2021 Apr 6{]};2021.02.03.21250974.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2021.02.03.21250974v1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer JL, Ullrich A, et al.
-Short-term forecasting of {COVID-19} in {Germany} and {Poland} during the second wave -- a preregistered study.
-medRxiv {[}Internet{]}.
-2021 Jan 11 {[}cited 2021 Apr 1{]};2020.12.24.20248826.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2020.12.24.20248826v2}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer JL, Ullrich A, et al.
-National and subnational short-term forecasting of {COVID-19} in {Germany} and {Poland}, early 2021.
-2021 Nov 8 {[}cited 2021 Nov 18{]};2021.11.05.21265810.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2021.11.05.21265810v1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-europeancovid-19forecasthubEuropeanCovid19Forecast2021}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{European Covid-19 Forecast Hub. European {Covid-19 Forecast Hub} {[}Internet{]}. 2021 {[}cited 2021 May 30{]}. Available from: \url{https://covid19forecasthub.eu/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichAccuracyRealtimeMultimodel2019}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Reich NG, McGowan CJ, Yamana TK, Tushar A, Ray EL, Osthus D, et al.
-Accuracy of real-time multi-model ensemble forecasts for seasonal influenza in the {U}.{S}.
-PLOS Computational Biology {[}Internet{]}.
-2019 Nov 22 {[}cited 2020 Aug 7{]};15(11):e1007486.
-Available from: \url{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1007486}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Tetlock PE, Mellers BA, Rohrbaugh N, Chen E.
-Forecasting {Tournaments}: {Tools} for {Increasing Transparency} and {Improving} the {Quality} of {Debate}.
-Curr Dir Psychol Sci {[}Internet{]}.
-2014 Aug 1 {[}cited 2021 May 30{]};23(4):290--5.
-Available from: \url{https://doi.org/10.1177/0963721414534257}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Atanasov P, Rescober P, Stone E, Swift SA, Servan-Schreiber E, Tetlock P, et al.
-Distilling the {Wisdom} of {Crowds}: {Prediction Markets} vs.
-{Prediction Polls}.
-Management Science {[}Internet{]}.
-2016 Apr 22 {[}cited 2021 May 30{]};63(3):691--706.
-Available from: \url{https://pubsonline.informs.org/doi/abs/10.1287/mnsc.2015.2374}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers E-J.
-Laypeople {Can Predict Which Social-Science Studies Will Be Replicated Successfully}.
-Advances in Methods and Practices in Psychological Science {[}Internet{]}.
-2020 Sep 1 {[}cited 2021 Oct 13{]};3(3):267--85.
-Available from: \url{https://doi.org/10.1177/2515245920919667}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{ReplicationMarkets.
-Replication {Markets} -- {Reliable} research replicates\ldots you can bet on it.
-{[}Internet{]}.
-2020 {[}cited 2021 Oct 13{]}.
-Available from: \url{https://www.replicationmarkets.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Servan-Schreiber E, Wolfers J, Pennock DM, Galebach B.
-Prediction {Markets}: {Does Money Matter}?
-Electronic Markets {[}Internet{]}.
-2004 Sep 1 {[}cited 2021 Oct 13{]};14(3):243--51.
-Available from: \url{http://www.informaworld.com/openurl?genre=article\&doi=10.1080/1019678042000245254\&magic=crossref\%7C\%7CD404A21C5BB053405B1A640AFFD44AE3}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{McAndrew TC, Reich NG.
-An expert judgment model to predict early stages of the {COVID-19} outbreak in the {United States}.
-medRxiv {[}Internet{]}.
-2020 Sep 23 {[}cited 2020 Sep 23{]};2020.09.21.20196725.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2020.09.21.20196725v1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Recchia G, Freeman ALJ, Spiegelhalter D.
-How well did experts and laypeople forecast the size of the {COVID-19} pandemic?
-PLOS ONE {[}Internet{]}.
-2021 May 5 {[}cited 2021 Jun 2{]};16(5):e0250935.
-Available from: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0250935}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Metaculus.
-A {Preliminary Look} at {Metaculus} and {Expert Forecasts} {[}Internet{]}.
-2020 {[}cited 2021 May 30{]}.
-Available from: \url{https://www.metaculus.com/news/2020/06/02/LRT/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Hypermind.
-Hypermind \textbar{} {Supercollective} intelligence for decision makers {[}Internet{]}.
-{Hypermind}; 2021 {[}cited 2021 Oct 13{]}.
-Available from: \url{https://www.hypermind.com/en/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{CSET Foretell. {CSET Foretell} {[}Internet{]}. 2021 {[}cited 2021 Oct 13{]}. Available from: \url{https://www.cset-foretell.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{PredictIt. {PredictIt} {[}Internet{]}. 2021 {[}cited 2021 Oct 13{]}. Available from: \url{https://www.predictit.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Held L, Meyer S, Bracher J.
-Probabilistic forecasting in infectious disease epidemiology: The 13th {Armitage} lecture.
-Statistics in Medicine {[}Internet{]}.
-2017 {[}cited 2019 Sep 16{]};36(22):3443--60.
-Available from: \url{https://onlinelibrary.wiley.com/doi/abs/10.1002/sim.7363}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. \href{https://doi.org/10.5281/zenodo.4618519}{Crowdforecastr: Eliciting crowd forecasts in r shiny}. 2020. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Covid.german.forecasts: Forecasting covid-19 related metrics for the german/poland forecast hub. 2020. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-ecdcDownloadHistoricalData2020}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{ECDC.
-Download historical data (to 14 {December} 2020) on the daily number of new reported {COVID-19} cases and deaths worldwide {[}Internet{]}.
-{European Centre for Disease Prevention and Control}; 2020 {[}cited 2021 May 30{]}.
-Available from: \url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rkiRKICoronavirusSARSCoV22021}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{RKI.
-{RKI} - {Coronavirus SARS-CoV-2} - {Aktueller Lage-}/{Situationsbericht} des {RKI} zu {COVID-19} {[}Internet{]}.
-2021 {[}cited 2021 May 30{]}.
-Available from: \url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-forsal.plRozbieznosciStatystykachKoronawirusa2020}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Forsal.pl.
-Rozbieżności w statystykach koronawirusa.
-22 tys.
-przypadków będą doliczone do ogólnej liczby wyników {[}Internet{]}.
-2020 {[}cited 2021 May 30{]}.
-Available from: \url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Ärzteblatt DÄG Redaktion Deutsches.
-SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an {[}Internet{]}.
-{Deutsches Ärzteblatt}; 2020 {[}cited 2021 May 30{]}.
-Available from: \url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Fay C, Guyader V, Rochette S, Girard C. Golem: A framework for robust shiny applications {[}Internet{]}. 2021. Available from: \url{https://github.com/ThinkR-open/golem}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie Y, et al.
-Shiny: Web application framework for r {[}Internet{]}.
-2021.
-Available from: \url{https://CRAN.R-project.org/package=shiny}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Our World in Data.
-{COVID-19 Data Explorer} {[}Internet{]}.
-{Our World in Data}; 2020 {[}cited 2021 May 30{]}.
-Available from: \url{https://ourworldindata.org/coronavirus-data-explorer}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K, Ellis P, et al.
-\href{https://doi.org/10.5281/zenodo.3957489}{EpiNow2: Estimate real-time case counts and time-varying epidemiological parameters}.
--.
-2020;-(-):--.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Fraser C.
-Estimating {Individual} and {Household Reproduction Numbers} in an {Emerging Epidemic}.
-PLOS ONE {[}Internet{]}.
-2007 Aug 22 {[}cited 2021 Sep 29{]};2(8):e758.
-Available from: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0000758}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation2020}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{epiforecasts.io/covid.
-Covid-19: {Temporal} variation in transmission during the {COVID-19} outbreak {[}Internet{]}.
-{Covid-19}; 2020 {[}cited 2021 May 30{]}.
-Available from: \url{https://epiforecasts.io/covid/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Sherratt K, Abbott S, Meakin SR, Hellewell J, Munday JD, Bosse N, et al.
-Exploring surveillance data biases when estimating the reproduction number: With insights into subpopulation transmission of {Covid-19} in {England}.
-2021 Mar 18 {[}cited 2021 Oct 14{]};2020.10.18.20214585.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v2}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abbottEstimatingTimevaryingReproduction2020a}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs HP, Bosse NI, et al.
-Estimating the time-varying reproduction number of {SARS-CoV-2} using national and subnational case counts.
-2020 Jun 1 {[}cited 2021 Oct 14{]};(5:112).
-Available from: \url{https://wellcomeopenresearch.org/articles/5-112}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Xu B, Gutierrez B, Hill S, Scarpino S, Loskill A, Wu J, et al.
-Epidemiological data from the nCoV-2019 outbreak: Early descriptions from publicly available data {[}Internet{]}.
-2020.
-Available from: \url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Stan Development Team. RStan: The r interface to stan {[}Internet{]}. 2020. Available from: \url{http://mc-stan.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG.
-\href{https://doi.org/10.1371/journal.pcbi.1008618}{Evaluating epidemic forecasts in an interval format}.
-PLoS Comput Biol.
-2021 Feb;17(2):e1008618.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Gneiting T, Raftery AE.
-Strictly proper scoring rules, prediction, and estimation.
-Journal of the American Statistical Association {[}Internet{]}.
-2007 Mar {[}cited 2020 Mar 22{]};102(477):359--78.
-Available from: \url{http://www.tandfonline.com/doi/abs/10.1198/016214506000001437}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. \href{https://doi.org/10.5281/zenodo.4618017}{Scoringutils: Utilities for scoring and assessing predictions}. 2020. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-deutschewelleCoronavirusGermanyImpose2020}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Deutsche Welle.
-Coronavirus: {Germany} to impose one-month partial lockdown \textbar{} {DW} \textbar{} 28.10.2020 {[}Internet{]}.
-2020 {[}cited 2021 Jun 29{]}.
-Available from: \url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Ganyani T, Kremer C, Chen D, Torneri A, Faes C, Wallinga J, et al.
-Estimating the generation interval for coronavirus disease (COVID-19) based on symptom onset data, march 2020.
-Eurosurveillance.
-2020;25(17).
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith HR, et al.
-The incubation period of coronavirus disease 2019 (COVID-19) from publicly reported confirmed cases: Estimation and application.
-Annals of Internal Medicine.
-2020;172(9):577--82.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J, Munday J, et al.
-\href{https://doi.org/10.5281/zenodo.3957539}{Covidregionaldata: Subnational data for the covid-19 outbreak}.
--.
-2020;-(-):--.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Evaluating the use of the reproduction number as an epidemiological tool, using spatio-temporal trends of the {Covid-19} outbreak in {England} \textbar{} {medRxiv} {[}Internet{]}.
-{[}cited 2021 May 30{]}.
-Available from: \url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Riutort-Mayol G, Bürkner P-C, Andersen MR, Solin A, Vehtari A.
-Practical hilbert space approximate bayesian gaussian processes for probabilistic programming {[}Internet{]}.
-2020.
-Available from: \url{https://arxiv.org/abs/2004.11408}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Scott JA, Gandy A, Mishra S, Unwin J, Flaxman S, Bhatt S.
-Epidemia: Modeling of epidemics using hierarchical bayesian models {[}Internet{]}.
-2020.
-Available from: \url{https://imperialcollegelondon.github.io/epidemia/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bhattSemiMechanisticBayesianModeling}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Bhatt S, Ferguson N, Flaxman S, Gandy A, Mishra S, Scott JA. Semi-{Mechanistic Bayesian} modeling of {COVID-19} with {Renewal Processes}. :14. }
-
-\end{CSLReferences}
-
 \end{document}

### 2022-08-04 manuscript/final submission/manuscript-no-plots.tex
final revisions

--- 2022-06-02 manuscript/manuscript.tex
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} 
+\caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} \caption{Two week ahead forecasts and corresponding scores.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} 
+\caption{Two week ahead forecasts and corresponding scores.
 A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} \caption{Distribution of scores.
+% \includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} 
+\caption{Distribution of scores.
 A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.
+% \includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4}
+\caption{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.
 “Hub-ensemble”    extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../crowd-forecast/Screenshot-forecasting-app} \caption{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).
-}\label{fig:screenshot}
+%\includegraphics[width=1\linewidth,]{../crowd-forecast/Screenshot-forecasting-app} 
+\caption{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021). }\label{fig:screenshot}
 \end{figure}
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Germany-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Germany-v4}
+\caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Poland-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Poland-v4}
+\caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-v4} \caption{Visualisation of aggregate performance metrics across locations.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-v4}
+\caption{Visualisation of aggregate performance metrics across locations.
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4} \caption{Visualisation of relative aggregate performance metrics across locations.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4}
+\caption{Visualisation of relative aggregate performance metrics across locations.
 A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily_truth} \caption{Visualisation of daily report data.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/daily_truth} 
+\caption{Visualisation of daily report data.
 The black line represents weekly data divided by seven.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily-data-updates} \caption{Visualisation of the absolute difference between the daily report data at the time and the data now.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/daily-data-updates}
+\caption{Visualisation of the absolute difference between the daily report data at the time and the data now.
 In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/weekly-data-updates} \caption{Visualisation of the relative difference between the weekly report data at the time and the data now.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/weekly-data-updates}
+\caption{Visualisation of the relative difference between the weekly report data at the time and the data now.
 Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} \caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the reported values.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} 
+\caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the reported values.
 Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} \caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the reported values.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} 
+\caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the reported values.
 Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} \caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the reported values.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} 
+\caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the reported values.
 Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1} \caption{A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1} 
+\caption{A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets.
 B: Distribution of WIS separate by country.}\label{fig:distribution-scores-1}
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3} \caption{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3} 
+\caption{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets.
 B: Distribution of WIS separate by country.}\label{fig:distribution-scores-3}
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4} \caption{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4} 
+\caption{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets.
 B: Distribution of WIS separate by country.}\label{fig:distribution-scores-4}
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1-ranks} 
+\caption{A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
 B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-1}
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2-ranks} 
+\caption{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets.
 B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-2}
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3-ranks} 
+\caption{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets.
 B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-3}
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4-ranks} 
+\caption{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets.
 B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-4}
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} \caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-renewal} \caption{Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences-renewal}
+%\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} 
+\caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences}
+\end{figure}
+
+\begin{figure}[H]
+%\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-renewal} 
+\caption{Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences-renewal}
 \end{figure}
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4}
+\caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
 “Hub-ensemble”     extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4}
+\caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/number-forecasters} \caption{Number of participants who submitted a forecast over time.}\label{fig:num-forecasters}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/ensemble-members} \caption{Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/number-forecasters} 
+\caption{Number of participants who submitted a forecast over time.}\label{fig:num-forecasters}
+\end{figure}
+
+\begin{figure}[H]
+%\includegraphics[width=1\linewidth,]{../analysis/plots/ensemble-members} 
+\caption{Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
 Note that the renewal model was not included in the ensemble on December 28th 2020.}\label{fig:num-ensemble-members}
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} \caption{Crowd forecasts and baseline shown in the application for a two week horizon.
+%\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} 
+\caption{Crowd forecasts and baseline shown in the application for a two week horizon.
 Shown are the median, as well as the 50\% and 90\% prediction intervals (in order of decreasing opacity).

### 2022-08-04 manuscript/final submission/manuscript.tex
final revisions

--- 2022-06-02 manuscript/manuscript.tex
@@
 \linenumbers
-\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}}
+\newfloat{text}{thp}{}
+\floatname{text}{Text}
+\renewcommand{\figurename}{}
+\newcommand{\newfigurename}{Hello}
+\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+\usepackage{nameref,hyperref}
 \usepackage{caption}
@@
 \bigskip
-\textbf{\getAff{London School of Hygiene \& Tropical Medicine}}London
-School of Hygiene \& Tropical Medicine, Keppel Street, London WC1E7HT,
-United Kingdom\\
+\textbf{\getAff{London School of Hygiene \& Tropical Medicine}}Centre
+for the Mathematical Modelling of Infectious Diseases, Department of
+Infectious Disease Epidemiology, London School of Hygiene \& Tropical
+Medicine, London, United Kingdom\\
 \textbf{\getAff{Karlsruhe Institute of Technology Institute of Economic
-Theory and Statistics}}Karlsruhe Institute of Technology - Institute of
-Economic Theory and Statistics, Post Box 6980, 76049 Karlsruhe,
-Germany\\
+Theory and Statistics}}Institute of Economic Theory and Statistics,
+Karlsruhe Institute of Technology, Karlsruhe, Germany\\
 \textbf{\getAff{Max Planck Institute for Multidisciplinary Sciences}}Max
-Planck Institute for Multidisciplinary Sciences, Am Faßberg 11, 37077
-Göttingen, Germany\\
+Planck Institute for Multidisciplinary Sciences, Göttingen, Germany\\
 \textbf{\getAff{UK Health Security Agency}}UK Health Security Agency,
-London NW9 5EQ, United Kingdom\\
-\textbf{\getAff{Imperial College London}}Imperial College London,
-Norfolk Place, London W2 1PG, United Kingdom\\
+London United Kingdom\\
+\textbf{\getAff{Imperial College London}}MRC Centre for Outbreak
+Analysis and Modelling, Department of Infectious Disease Epidemiology,
+School of Public Health, Imperial College London, London, United
+Kingdom\\
 \bigskip
-* Corresponding author: nikos.bosse@lshtm.ac.uk\\
+* nikos.bosse@lshtm.ac.uk\\
 \end{flushleft}
@@
 % Use "Eq" instead of "Equation" for equation citations.
+\newcommand{\createmylabel}[2]{%
+  \phantomsection
+  #1\def\@currentlabel{\unexpanded{#1}}\label{#2}%
+}
+
 \hypertarget{introduction}{%
@@
 \section{Methods}\label{methods}}
+
+\hypertarget{ethics-statement}{%
+\subsection{Ethics statement}\label{ethics-statement}}
+
+This study has been approved by the London School of Hygiene \& Tropical
+Medicine Research Ethics Committee (reference number 22290). Consent
+from participants was obtained in written form.
+
+\hypertarget{overview}{%
+\subsection{Overview}\label{overview}}
 
@@
 a notable exception of a data update for October 12 2020 in Germany)
-only affected daily, not weekly data (see Figures
-\ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).
+only affected daily, not weekly data (see Figs
+\nameref{fig:daily-truth-update} and \nameref{fig:weekly-truth-update}).
 
@@
 showing their forecast or providing numerical values (see screenshot in
-Figure \ref{fig:screenshot} in the SI). The default shown was a
-repetition of the last known observation with constant uncertainty
-around it computed as the standard deviation of the last four changes in
-weekly log observed forecasts (i.e.~as
+\nameref{fig:screenshot} in the SI). The default shown was a repetition
+of the last known observation with constant uncertainty around it
+computed as the standard deviation of the last four changes in weekly
+log observed forecasts (i.e.~as
 \(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
 A comparison of the crowd forecasts against the default baseline shown
-in the application is displayed in Figure \ref{fig:compare-forecasters}
-in the Appendix. Our interface also allowed participants to view past
+in the application is displayed in \nameref{fig:compare-forecasters} in
+the Appendix. Our interface also allowed participants to view past
 observations based on the hub data, as well as their forecasts, on a
@@
 
-individual forecasts were assessed as clearly erroneous by visual
-inspection and subsequently removed before aggregation and were excluded
-from the submission as well as the analysis.
-
 Participants were recruited mostly within the Centre of Mathematical
@@
 
-The study was approved by the Observational / Interventions Research
-Ethics Committee at the London School of Hygiene \& Tropical Medicine,
-LSHTM Ethics Reference: 22290. Formal consent from participants was
-taken in written form through the web application.
-
 \hypertarget{model-based-forecasts}{%
@@
 equation {[}41{]} to predict reported cases and deaths (see details in
-the SI). It estimated the effective reproduction number \(R_t\) (the
-average number of people each person infected at time t is expected to
-infect in turn) and modelled future infections as a weighted sum of past
-infection multiplied by \(R_t\). \(R_t\) was assumed to stay constant
-beyond the forecast date, roughly corresponding to continuing the latest
-exponential trend in infections. On the 9th of November we altered the
-date when \(R_t\) was assumed to be constant from two weeks prior to the
-date of the forecast to the forecast date, which we found to yield a
-more stable \(R_t\) estimate. Reported case and death notifications were
-obtained by convolving predicted infections over data-based delay
-distributions {[}40,42--44{]} to model the time between infection and
-report date. The renewal model was used to predict cases as well as
-deaths with forecasts being generated for each target separately. Death
-forecasts from the renewal model were therefore not informed by past
-cases. One submission of the renewal model on December 28th 2020 was
-delayed and therefore not included in the official Forecast hub
-ensemble.
+S1 Text in the SI). It estimated the effective reproduction number
+\(R_t\) (the average number of people each person infected at time t is
+expected to infect in turn) and modelled future infections as a weighted
+sum of past infection multiplied by \(R_t\). \(R_t\) was assumed to stay
+constant beyond the forecast date, roughly corresponding to continuing
+the latest exponential trend in infections. On the 9th of November we
+altered the date when \(R_t\) was assumed to be constant from two weeks
+prior to the date of the forecast to the forecast date, which we found
+to yield a more stable \(R_t\) estimate. Reported case and death
+notifications were obtained by convolving predicted infections over
+data-based delay distributions {[}40,42--44{]} to model the time between
+infection and report date. The renewal model was used to predict cases
+as well as deaths with forecasts being generated for each target
+separately. Death forecasts from the renewal model were therefore not
+informed by past cases. One submission of the renewal model on December
+28th 2020 was delayed and therefore not included in the official
+Forecast hub ensemble.
 
@@
 (including cases) were scored only over the later period for which all
-forecasts were available (see Section \ref{sensitivity-analysis} in the
-SI). Results remained broadly unchanged.
+forecasts were available (see \nameref{fig:agg-performance-all-late} and
+\nameref{tab:score-table-late-2} and \nameref{tab:score-table-late-4}s
+in the SI). Results remained broadly unchanged.
 
@@
 interval (e.g.~how many observed values fall inside all 50\% prediction
-intervals). Scoring metrics are explained in more detail in Table
-\ref{tab:scoring-metrics} in the SI. All scores were calculated using
-the \texttt{scoringutils} R package {[}49{]}.
+intervals). Scoring metrics are explained in more detail in
+\nameref{tab:scoring-metrics} in the SI. All scores were calculated
+using the \texttt{scoringutils} R package {[}49{]}.
 
@@
 retrospectively computed and excludes all our models, leaving on average
-five ensemble member models (see details in Section
-\ref{contributions-hub}, as well as in Table
-\ref{tab:table-ensemble-versions} and Figure
-\ref{fig:num-ensemble-members} in the SI). What we call ``Hub ensemble''
-in this article therefore differs from the ``official Hub ensemble''
-(here called ``hub-ensemble-realised'') which included crowd forecasts
-as well as renewal model forecasts. To enhance interpretability of
-scores we mainly report WIS relative to the Hub ensemble in the main
-text, i.e.~we divided the average scores for a given model by the
-average score achieved by the Hub ensemble on the same set of forecasts
-(with values \textgreater1 implying worse and values \textless1 implying
-better performance than the Hub ensemble). In addition to comparing our
-forecasts against the hub ensemble excluding our models, we also
-assessed the impact of our forecasts on the performance of the
-forecasting hub by recalculating separate versions of the Hub ensemble
-with only some (or all) of our forecasts included. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively.
+five ensemble member models (see \nameref{tab:table-ensemble-versions}
+and \nameref{fig:num-ensemble-members} in the SI). What we call ``Hub
+ensemble'' in this article therefore differs from the ``official Hub
+ensemble'' (here called ``hub-ensemble-realised'') which included crowd
+forecasts as well as renewal model forecasts. To enhance
+interpretability of scores we mainly report WIS relative to the Hub
+ensemble in the main text, i.e.~we divided the average scores for a
+given model by the average score achieved by the Hub ensemble on the
+same set of forecasts (with values \textgreater1 implying worse and
+values \textless1 implying better performance than the Hub ensemble). In
+addition to comparing our forecasts against the hub ensemble excluding
+our models, we also assessed the impact of our forecasts on the
+performance of the forecasting hub by recalculating separate versions of
+the Hub ensemble with only some (or all) of our forecasts included.
+Versions that included either all of our models
+(``hub-ensemble-with-all'') or only one of them
+(``hub-ensemble-with-X'') were computed retrospectively.
 
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
+\caption{\bf{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.}}
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
@@
 H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all}
+Standard deviation of all WIS values for different horizons
+\label{fig:agg-performance-all}
 \end{figure}
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} \caption{Two week ahead forecasts and corresponding scores.
+\caption{\bf{Two week ahead forecasts and corresponding scores. }}
 A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values.
 Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth}
+B, D: Visualisation of corresponding WIS.
+\label{fig:forecasts-and-truth}
 \end{figure}
@@
 (WIS, lower values indicate better performance) than both the renewal
-model and the Hub ensemble across all forecast horizons (Figure
-\ref{fig:agg-performance-all}A) and locations (Figure
-\ref{fig:performance-locations-rel}A). For two week ahead forecasts,
+model and the Hub ensemble across all forecast horizons (Fig
+\ref{fig:agg-performance-all}A) and locations (Fig
+\nameref{fig:performance-locations-rel}A). For two week ahead forecasts,
 mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts
-and 1.40 for the renewal model (Table \ref{tab:score-table-2}). Across
-all forecasting approaches, locations and forecast horizons, the
+and 1.40 for the renewal model (\nameref{tab:score-table-2} Table).
+Across all forecasting approaches, locations and forecast horizons, the
 distribution of WIS values was very right-skewed, and average
-performance was heavily influenced by outliers (Figure
+performance was heavily influenced by outliers (Fig
 \ref{fig:distribution-scores}). Overall, low variance in forecast
-performance was closely linked with good mean performance (Figures
+performance was closely linked with good mean performance (Figs
 \ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A),
@@
 was especially pronounced for the renewal model, which had more outliers
-(Figure \ref{fig:distribution-scores}), as well as the highest standard
+(Fig \ref{fig:distribution-scores}), as well as the highest standard
 deviation of WIS values (standard deviation of the WIS relative to the
@@
 trend from increase to decrease that happened in November in Germany and
-severely overshot reported cases (Figure
-\ref{fig:forecasts-and-truth}A). This was most striking for the renewal
-model, which extrapolated unconstrained exponential growth based on the
-recent past of observations. The Hub ensemble and the crowd forecast,
-which had both been under-predicting throughout October, also failed to
-predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on
-November 2nd 2020 {[}50{]} and the change in the testing regime (with
-stricter test criteria) on November 11th 2020 {[}36{]}, were fastest to
-adapt to the new trend, and the Hub ensemble slowest. In December, cases
-rose again in Germany, with all models under-predicting this growth to
+severely overshot reported cases (Fig \ref{fig:forecasts-and-truth}A).
+This was most striking for the renewal model, which extrapolated
+unconstrained exponential growth based on the recent past of
+observations. The Hub ensemble and the crowd forecast, which had both
+been under-predicting throughout October, also failed to predict the
+change in trend after cases peaked, but less severely so. Human
+forecasters, possibly aware of the semi-lockdown announced on November
+2nd 2020 {[}50{]} and the change in the testing regime (with stricter
+test criteria) on November 11th 2020 {[}36{]}, were fastest to adapt to
+the new trend, and the Hub ensemble slowest. In December, cases rose
+again in Germany, with all models under-predicting this growth to
 varying extents. As in October, the renewal model captured the phase of
@@
 that 50\% (90\%) prediction intervals generally covered less than 50\%
-(90\%) of the actually observed values) (Figure
+(90\%) of the actually observed values) (Fig
 \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
@@
 prediction intervals (i.e., narrower and more confident predictive
-distributions) than other approaches (Figure
+distributions) than other approaches (Fig
 \ref{fig:agg-performance-all}E) and only showed a small increase in
@@
 intervals were also noticeably narrower than the default baseline shown
-to forecasters in the application (see Figure
-\ref{fig:compare-forecasters}).
-
-In spite of good performance in terms of the absolute error (Figure
+to forecasters in the application (see
+\nameref{fig:compare-forecasters}).
+
+In spite of good performance in terms of the absolute error (Fig
 \ref{fig:agg-performance-all}G), the narrow forecast intervals led to
@@
 forecasts made at a two week forecast horizon, and only 5\% and 38\%
-four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables
-\ref{tab:score-table-2} and \ref{tab:score-table-4}). Despite worse
-performance in terms of absolute error (Figure
+four weeks ahead) (Fig \ref{fig:agg-performance-all}C, D as well as
+\nameref{tab:score-table-2} and \nameref{tab:score-table-4}s). Despite
+worse performance in terms of absolute error (Fig
 \ref{fig:agg-performance-all}G), the renewal model achieved better
@@
 tended to over-predict at longer forecast horizons, whereas the Hub
-ensemble showed no systematic bias (Figure
-\ref{fig:agg-performance-all}F). Regardless of a general relative
-tendency to over-predict, all forecasting approaches incurred larger
-absolute penalties from over- than from under-prediction (see
-decomposition of the WIS into absolute penalties for over-prediction,
-under-prediction and dispersion in Figures
-\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
+ensemble showed no systematic bias (Fig \ref{fig:agg-performance-all}F).
+Regardless of a general relative tendency to over-predict, all
+forecasting approaches incurred larger absolute penalties from over-
+than from under-prediction (see decomposition of the WIS into absolute
+penalties for over-prediction, under-prediction and dispersion in Figs
+\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as
+well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
 
 Generally, trends in overall performance were broadly similar across
-locations (Figures \ref{fig:performance-locations} and
-\ref{fig:performance-locations-rel}). Due to the differing population
-sizes and numbers of notifications in Germany and Poland absolute scores
-were difficult to compare directly. However, relative to the Hub
-ensemble, the crowd forecasts performed noticeably better in Germany
-than in Poland and the renewal model better in Poland than in Germany
-(Figures \ref{fig:performance-locations-rel}A,
-\ref{fig:performance-locations-rel}G,
-\ref{fig:agg-performance-all-Germany},
-\ref{fig:agg-performance-all-Poland}).
+locations (Figs \nameref{fig:performance-locations} and
+\nameref{fig:performance-locations-rel}). Due to the differing
+population sizes and numbers of notifications in Germany and Poland
+absolute scores were difficult to compare directly. However, relative to
+the Hub ensemble, the crowd forecasts performed noticeably better in
+Germany than in Poland and the renewal model better in Poland than in
+Germany (Figs \nameref{fig:performance-locations-rel}A,
+\nameref{fig:performance-locations-rel}G,
+\nameref{fig:agg-performance-all-Germany},
+\nameref{fig:agg-performance-all-Poland}).
 
@@
 our model-based approaches across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B). Relative WIS values for the models
-two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1
-(Hub ensemble) and 1.79 (renewal model). The crowd forecasts performed
-better than the renewal model across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B), and also better than the convolution
-model three and four weeks ahead. Poor performance of the renewal model,
-especially at longer horizons, indicates that an approach that does not
-know about past cases, but instead estimates and projects a separate
-\(R_t\) trace from deaths, does not use the available information
-efficiently. The convolution model was able to outperform both the
-renewal model and the crowd forecasts at shorter forecast horizons
-(where the delay between cases and deaths means that future deaths are
-largely informed by present cases), but saw performance deteriorate at
-three and four weeks ahead (where case predictions from the renewal
-model were increasingly used to inform death predictions) (Figure
-\ref{fig:agg-performance-all}B, Table \ref{tab:score-table-4}).
+(Figs \ref{fig:agg-performance-all}B and
+\nameref{fig:performance-locations}B). Relative WIS values for the
+models two weeks ahead were 1.22 (convolution model), 1.26 (crowd
+forecast), 1 (Hub ensemble) and 1.79 (renewal model). The crowd
+forecasts performed better than the renewal model across all forecast
+horizons and locations (Figs \ref{fig:agg-performance-all}B and
+\nameref{fig:performance-locations}B), and also better than the
+convolution model three and four weeks ahead. Poor performance of the
+renewal model, especially at longer horizons, indicates that an approach
+that does not know about past cases, but instead estimates and projects
+a separate \(R_t\) trace from deaths, does not use the available
+information efficiently. The convolution model was able to outperform
+both the renewal model and the crowd forecasts at shorter forecast
+horizons (where the delay between cases and deaths means that future
+deaths are largely informed by present cases), but saw performance
+deteriorate at three and four weeks ahead (where case predictions from
+the renewal model were increasingly used to inform death predictions)
+(Fig \ref{fig:agg-performance-all}B, \nameref{tab:score-table-4}).
 
@@
 approaches was generally lower than that of the Hub ensemble and mostly
-slightly lower than nominal coverage (Figure
+slightly lower than nominal coverage (Figs
 \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D). As
@@
 For deaths, the ensemble of crowd forecasts had a consistent tendency to
-over-predict \ref{fig:agg-performance-all}F. The convolution model had a
-strong tendency to under-predict, with the magnitude of under-prediction
-steadily decreasing for longer forecast horizons. The renewal model
-(which over-predicted for cases) and the Hub ensemble slightly tended
-towards under-prediction. For deaths, absolute over- and
+over-predict (see Fig \ref{fig:agg-performance-all}F). The convolution
+model had a strong tendency to under-predict, with the magnitude of
+under-prediction steadily decreasing for longer forecast horizons. The
+renewal model (which over-predicted for cases) and the Hub ensemble
+slightly tended towards under-prediction. For deaths, absolute over- and
 under-prediction penalties were more in line with a general relative
-tendency to over- or under-predict than for cases (Figure
-\ref{fig:agg-performance-all}A, \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2}, \ref{tab:score-table-4}).
+tendency to over- or under-predict than for cases (Figs
+\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as
+well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
 
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} \caption{Distribution of scores.
+\caption{\bf{Distribution of scores. }}
 A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
@@
 B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores.}\label{fig:distribution-scores}
+Black squares indicate median and black circles mean scores.
+\label{fig:distribution-scores}
 \end{figure}
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.
+\caption{\bf{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.}}
 “Hub-ensemble”  extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
@@
 H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-rel}
+Standard deviation of all WIS values for different horizons relative to the Hub ensemble.
+\label{fig:agg-performance-ensemble-rel}
 \end{figure}
 
-\hypertarget{contributions-hub}{%
-\subsection{Contribution to the Forecast Hub}\label{contributions-hub}}
+\hypertarget{contribution-to-the-forecast-hub}{%
+\subsection{Contribution to the Forecast
+Hub}\label{contribution-to-the-forecast-hub}}
+
+\label{contributions-hub}
 
@@
 one of them (``hub-ensemble-with-X'') were computed retrospectively. An
-overview of all models and ensemble versions is shown in Table
-\ref{tab:table-ensemble-versions} in the SI.
+overview of all models and ensemble versions is shown in
+\nameref{tab:table-ensemble-versions} in the SI.
 
@@
 contributions) consistently improved performance across all forecasting
-horizons (rel. WIS 0.9 two weeks ahead, Table
-\ref{tab:score-table-ensemble-2}). Contributions from the crowd
-forecasts alone also improved performance of the Hub ensemble across all
-forecast horizons, while contributions from the renewal model had a
-negative effect for longer horizons (rel. WIS 1.02 three weeks ahead,
-1.06 four weeks ahead). The realised ensemble including both models
-performed better or equal compared to all versions with only one model
-included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model
-have improved performance (Table \ref{tab:score-table-ensemble-4}). The
-realised ensemble performed comparably to the crowd forecasts for
-predictions one to two weeks ahead, and worse for greater forecast
-horizons.
+horizons (rel. WIS 0.9 two weeks ahead, see
+\nameref{tab:score-table-ensemble-2} Table). Contributions from the
+crowd forecasts alone also improved performance of the Hub ensemble
+across all forecast horizons, while contributions from the renewal model
+had a negative effect for longer horizons (rel. WIS 1.02 three weeks
+ahead, 1.06 four weeks ahead). The realised ensemble including both
+models performed better or equal compared to all versions with only one
+model included for up to three weeks ahead, suggesting synergistic
+effects. Only for predictions four weeks ahead would removing the
+renewal model have improved performance
+(\nameref{tab:score-table-ensemble-4}). The realised ensemble performed
+comparably to the crowd forecasts for predictions one to two weeks
+ahead, and worse for greater forecast horizons.
 
@@
 horizons (rel. WIS of the Hub-ensemble-realised 1.01 two weeks ahead,
-1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and
-\ref{tab:score-table-ensemble-4}). Individual contributions from both
+1.05 four weeks ahead, \ref{tab:score-table-ensemble-2} and
+\ref{tab:score-table-ensemble-4}s). Individual contributions from both
 the renewal model and the crowd forecast were largely negative, while a
@@
 especially interesting as the convolution model performed consistently
-worse than the pre-existing Hub ensemble (Figure
+worse than the pre-existing Hub ensemble (Fig
 \ref{fig:agg-performance-all}) and especially worse for longer horizons.
@@
 median ensemble, but a mixed and mostly slightly negative impact on the
-mean ensemble (Figures \ref{fig:agg-performance-ensemble-rel}B and
-\ref{fig:agg-performance-ensemble-mean}B). This may happen if a model is
-more correct directionally relative to the pre-existing ensemble, but
-overshoots in absolute terms, thereby moving the ensemble too far. For
-both the mean and the median ensemble, changes in performance from
-adding or removing models were of a similar order of magnitude,
-suggesting that at least in this instance, with a relatively small
-ensemble size, the median ensemble was not necessarily more `robust' to
-changes than the mean ensemble. However, the ensemble version with all
-our forecasts included (``hub-ensemble-with-all'') tended to perform
-relatively better for the median ensemble than the mean ensemble,
-suggesting that adding more models may be more beneficial or `safer' for
-the median than for the mean ensemble as directional errors can more
-easily cancel out than errors in absolute terms.
+mean ensemble (Figs \ref{fig:agg-performance-ensemble-rel}B and
+\nameref{fig:agg-performance-ensemble-mean}B). This may happen if a
+model is more correct directionally relative to the pre-existing
+ensemble, but overshoots in absolute terms, thereby moving the ensemble
+too far. For both the mean and the median ensemble, changes in
+performance from adding or removing models were of a similar order of
+magnitude, suggesting that at least in this instance, with a relatively
+small ensemble size, the median ensemble was not necessarily more
+`robust' to changes than the mean ensemble. However, the ensemble
+version with all our forecasts included (``hub-ensemble-with-all'')
+tended to perform relatively better for the median ensemble than the
+mean ensemble, suggesting that adding more models may be more beneficial
+or `safer' for the median than for the mean ensemble as directional
+errors can more easily cancel out than errors in absolute terms.
 
@@
 variance in predictions in January in Germany for example (severe
-under-prediction followed by severe over-prediction, see Figure
+under-prediction followed by severe over-prediction, see Fig
 \ref{fig:forecasts-and-truth}A), may in part be caused by the fact that
@@
 
-\textbf{Acknowledgements}
-
-NIB received funding from the Health Protection Research Unit (grant
-code NIHR200908, https://www.nihr.ac.uk/). SA's work was funded by the
-Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/). The work
-of JB was supported by the Helmholtz Foundation
-(https://www.helmholtz.de/) via the SIMCARD Information and Data Science
-Pilot Project. This research was partly funded by the National Institute
-for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 \&
-16/136/46) using UK aid from the UK Government to support global health
-research. The views expressed in this publication are those of the
-author(s) and not necessarily those of the NIHR or the UK Department of
-Health and Social Care. BJQ is supported in part by a grant from the
-Bill and Melinda Gates Foundation (OPP1139859,
-https://www.gatesfoundation.org/). EvL acknowledges funding by the
-National Institute for Health Research (NIHR) Health Protection Research
-Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908,
-https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research
-and innovation programme - project EpiPose (101003688,
-https://ec.europa.eu/programmes/horizon2020/). AC acknowledges funding
-by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/),
-and the Academy of Medical Sciences (https://acmedsci.ac.uk/). SF's work
-was supported by the Wellcome Trust (grant: 210758/Z/18/Z,
-https://wellcome.org/), and the NIHR (NIHR200908,
-https://www.nihr.ac.uk/).
+\section*{Acknowledgments}
 
@@
 
-We would also like to acknowledge (in a randomised order) the members of
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group at the the London School of Hygiene \& Tropical Medicine:
-Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie
-Diamond, Katherine E. Atkins, Rein M G J Houben, Jiayao Lei, Rachel
-Lowe, David Simons, Sophie R Meakin, Nicholas G. Davies, Timothy W
-Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly,
-Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas,
-Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia
-Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson,
-Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang
-Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C
-Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun,
-Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche,
-James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday,
-Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan
-Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R
+We would also like to thank all members of the Centre for the
+Mathematical Modelling of Infectious Diseases COVID-19 Working Group at
+the London School of Hygiene \& Tropical Medicine: Oliver Brady,
+Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie Diamond,
+Katherine E. Atkins, Rein M G J Houben, Jiayao Lei, Rachel Lowe, David
+Simons, Sophie R Meakin, Nicholas G. Davies, Timothy W Russell, Kevin
+van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly, Stéphane Hué,
+Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas, Thibaut
+Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia Showering,
+Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson, Frank G
+Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang Liu, Simon
+R Procter, Emily S Nightingale, William Waites, Rosanna C Barnard, Joel
+Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun, Hamish P Gibbs,
+Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche, James W Rudge, Akira
+Endo, Naomi R Waterlow, Paul Mee, James D Munday, Ciara V McCarthy,
+Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan Auzenbergs,
+Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R
 Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael
@@
 
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
-
-\hypertarget{appendix-supplementary-information}{%
-\section*{(APPENDIX) Supplementary
-information}\label{appendix-supplementary-information}}
-\addcontentsline{toc}{section}{(APPENDIX) Supplementary information}
-
-\hypertarget{supplementary-information}{%
-\section{Supplementary information}\label{supplementary-information}}
-
-\hypertarget{scoring-metrics-used}{%
-\subsection{Scoring metrics used}\label{scoring-metrics-used}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{9.3cm}}
-\caption{\label{tab:scoring-metrics}Overview of the scoring metrics used.}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{Overview of the scoring metrics used. \textit{(continued)}}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-WIS (Weighted) interval score & The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
-It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
-The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction.
-For a single interval, the score is computed as
-  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
-  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e.
-the lower and upper bound of a single prediction interval.
-For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
-  $$WIS = \frac{1}{K + 0.5} \cdot \left( w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y) \right), $$
-  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
-
-\cellcolor{gray!6}{Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.}\\
-\addlinespace \addlinespace
-Interval coverage & Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
-Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
-we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.\\
-\addlinespace \addlinespace
-Bias & (Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict. Values are between -1 and 1 and 0 ideally. For continuous forecasts, bias is given as 
-$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
-where $F$ is the CDF of the predictive distribution and $y$ is the observed value.
-
-For quantile forecasts, $F(y)$ is replaced by a quantile rank.
-The appropriate quantile rank is determined by whether the median forecast is below  or above the true value.
-We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.
-
-\cellcolor{gray!6}{In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
-It is therefore a more robust measurement.}\\*
-\end{longtable}
+\beginsupplement
+
+\section*{Supporting information}
+
+\paragraph*{S1 Table.}
+\label{tab:scoring-metrics}
+
+\textbf{Overview of the scoring metrics used.}
+
+\paragraph*{S1 Fig.}
+\label{fig:screenshot}
+
+\textbf{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).}
+
+\paragraph*{S2}
+
+\textbf{Table.} \label{tab:score-table-2}
+\textbf{Scores for one and two week ahead forecasts.} Scores are cut to
+three significant digits and rounded). Note that scores for cases (which
+include the whole period from October 12th 2020 until March 1st 2021)
+and deaths (which include only forecasts from the 21st of December 2020
+on) are computed on different subsets. Numbers in brackets show the
+metrics relative to the Hub ensemble (i.e.~the median ensemble of all
+other models submitted to the German and Polish Forecast Hub, excluding
+our contributions). WIS is the mean weighted interval score (lower
+values are better), WIS - sd is the standard deviation of all scores
+achieved by a model. Dispersion, over-prediction and under-prediction
+together sum up to the weighted interval score. Bias (between -1 and 1,
+0 is ideal) represents the general average tendency of a model to over-
+or underpredict. 50\% and 90\%-coverage are the percentage of observed
+values that fell within the 50\% and 90\% prediction intervals of a
+model.
+
+\paragraph*{S3 Table.}
+\label{tab:score-table-4}
+
+\textbf{Scores for three and four weeks ahead forecasts.} Scores are cut
+to three significant digits and rounded). Note that scores for cases
+(which include the whole period from October 12th 2020 until March 1st
+2021) and deaths (which include only forecasts from the 21st of December
+2020 on) are computed on different subsets. Numbers in brackets show the
+metrics relative to the Hub ensemble (i.e.~the median ensemble of all
+other models submitted to the German and Polish Forecast Hub, excluding
+our contributions). WIS is the mean weighted interval score (lower
+values are better), WIS - sd is the standard deviation of all scores
+achieved by a model. Dispersion, over-prediction and under-prediction
+together sum up to the weighted interval score. Bias (between -1 and 1,
+0 is ideal) represents the general average tendency of a model to over-
+or underpredict. 50\% and 90\%-coverage are the percentage of observed
+values that fell within the 50\% and 90\% prediction intervals of a
+model.
+
+\paragraph{S2}
+
+\textbf{Fig.} \label{fig:agg-performance-all-Germany}
+\textbf{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.}
+A, B: mean weighted interval score (WIS, lower indicates better
+performance) across horizons. WIS is decomposed into its components
+dispersion, over-prediction and under-prediction. C: Empirical coverage
+of the 50\% prediction intervals (50\% coverage is perfect). D:
+Empirical coverage of the 90\% prediction intervals. E: Dispersion (same
+as in panel A, B). Higher values mean greater dispersion of the forecast
+and imply ceteris paribus a worse score. F: Bias, i.e.~general
+(relative) tendency to over- or underpredict. Values are between -1
+(complete under-prediction) and 1 (complete over-prediction) and 0
+ideally. G: Absolute error of the median forecast (lower is better). H.
+Standard deviation of all WIS values for different horizons
+
+\paragraph{S3}
+
+\textbf{Fig.} \label{fig:agg-performance-all-Poland}
+\textbf{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.}
+A, B: mean weighted interval score (WIS, lower indicates better
+performance) across horizons. WIS is decomposed into its components
+dispersion, over-prediction and under-prediction. C: Empirical coverage
+of the 50\% prediction intervals (50\% coverage is perfect). D:
+Empirical coverage of the 90\% prediction intervals. E: Dispersion (same
+as in panel A, B). Higher values mean greater dispersion of the forecast
+and imply ceteris paribus a worse score. F: Bias, i.e.~general
+(relative) tendency to over- or underpredict. Values are between -1
+(complete under-prediction) and 1 (complete over-prediction) and 0
+ideally. G: Absolute error of the median forecast (lower is better). H.
+Standard deviation of all WIS values for different horizons
+
+\paragraph{S4}
+
+\textbf{Fig.} \label{fig:performance-locations}
+\textbf{Visualisation of aggregate performance metrics across locations.}
+A, B: mean weighted interval score (WIS, lower indicates better
+performance) across horizons. WIS is decomposed into its components
+dispersion, over-prediction and under-prediction. C: Empirical coverage
+of the 50\% prediction intervals (50\% coverage is perfect). D:
+Empirical coverage of the 90\% prediction intervals. E: Dispersion (same
+as in panel A, B). Higher values mean greater dispersion of the forecast
+and imply ceteris paribus a worse score. F: Bias, i.e.~general
+(relative) tendency to over- or underpredict. Values are between -1
+(complete under-prediction) and 1 (complete over-prediction) and 0
+ideally. G: Absolute error of the median forecast (lower is better). H.
+Standard deviation of WIS values.
+
+\paragraph{S5}
+
+\textbf{Fig.} \label{fig:performance-locations-rel}
+\textbf{Visualisation of aggregate performance metrics across locations in relative terms.}
+A, B: mean weighted interval score (WIS) across locations (lower values
+indicate better performance). C, D: Empirical coverage of the 50\% and
+90\% prediction intervals. E: Dispersion. Higher values mean greater
+dispersion of the forecast and imply ceteris paribus a worse score. F:
+Bias, i.e.~general (relative) tendency to over- orunderpredict. Values
+are between -1 (complete under-prediction) and 1 (complete
+over-prediction) and 0 ideally. G: Absolute error of the median
+forecast. H. Standard deviation of WIS values.
+
+\paragraph{S6}
+
+\textbf{Fig.} \label{fig:daily-truth}
+\textbf{Visualisation of daily report data.} The black line represents
+weekly data divided by seven. Data were last accessed through the German
+and Polish Forecast Hub on August 21 2021.
+
+\paragraph{S7}
+
+\textbf{Fig.} \label{fig:daily-truth-update}
+\textbf{Visualisation of the absolute difference between the daily report data at the time and the data now.}
+In Germany, there were zero cases and deaths reported on 2020-10-12, and
+only later 2467 cases and 6 deaths were added. Data were last accessed
+through the German and Polish Forecast Hub on May 10 2022.
+
+\paragraph{S8}
+
+\textbf{Fig.} \label{fig:weekly-truth-update}
+\textbf{Visualisation of the relative difference between the weekly report data at the time and the data now.}
+Apart from the data that was retrospectively added on 2020-10-12, data
+updates did not have a noticeable effect on weekly data (as shown in the
+forecasting application). Data were last accessed through the German and
+Polish Forecast Hub on May 10 2022.
+
+\paragraph{S9 Fig.}
+\label{fig:forecasts-and-truth-1}
+
+\textbf{Visualisation of forecasts and scores for one week ahead forecasts.}
+A, C: Visualisation of 50\% prediction intervals of one week ahead
+forecasts against the reported values. Forecasts that were not scored
+(because there was no complete set of death forecasts available) are
+greyed out. B, D: Visualisation of corresponding WIS.
+
+\paragraph{S10 Fig.}
+\label{fig:forecasts-and-truth-3}
+
+\textbf{Visualisation of forecasts and scores for three week ahead forecasts.}
+A, C: Visualisation of 50\% prediction intervals of three week ahead
+forecasts against the reported values. Forecasts that were not scored
+(because there was no complete set of death forecasts available) are
+greyed out. B, D: Visualisation of corresponding WIS.
+
+\paragraph{S11 Fig.}
+\label{fig:forecasts-and-truth-4}
+
+\textbf{Visualisation of forecasts and scores for three week ahead forecasts.}
+A, C: Visualisation of 50\% prediction intervals of four week ahead
+forecasts against the reported values. Forecasts that were not scored
+(because there was no complete set of death forecasts available) are
+greyed out. B, D: Visualisation of corresponding WIS.
+
+\paragraph{S12 Fig.}
+\label{fig:distribution-scores-1}
+
+\textbf{Distribution of weighted interval scores for one week ahead forecasts}
+A: Distribution of weighted interval scores for one week ahead forecasts
+of the different models and forecast targets pooled across locations. B:
+Distribution of WIS separate by country.
+
+\paragraph{S13 Fig.}
+\label{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets pooled across locations. B: Distribution of WIS separate by country.}
+
+\textbf{Distribution of weighted interval scores for three week ahead forecasts}
+A: Distribution of weighted interval scores for three week ahead
+forecasts of the different models and forecast targets pooled across
+locations. B: Distribution of WIS separate by country.
+
+\paragraph{S14 Fig.}
+\label{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets pooled across locations. B: Distribution of WIS separate by country.}
+
+\textbf{Distribution of weighted interval scores for four week ahead forecasts}
+A: Distribution of weighted interval scores for four week ahead
+forecasts of the different models and forecast targets pooled across
+locations. B: Distribution of WIS separate by country.
+
+\paragraph{S15 Fig.}
+\label{fig:distribution-scores-ranks-1}
+
+\textbf{Distribution of model ranks (in terms of WIS) for one week ahead forecasts}
+A: Distribution of the ranks (determined by the weighted interval score)
+for one week ahead forecasts of the different models and forecast
+targets, pooled across locations. B: Distribution of ranks separate by
+country.
+
+\paragraph{S16 Fig.}
+\label{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets, pooled across locations.
+B: Distribution of ranks separate by country.}
+
+\textbf{Distribution of model ranks (in terms of WIS) for two week ahead forecasts}
+A: Distribution of the ranks (determined by the weighted interval score)
+for two week ahead forecasts of the different models and forecast
+targets, pooled across locations. B: Distribution of ranks separate by
+country.
+
+\paragraph{S17 Fig.}
+\label{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets, pooled across locations.
+B: Distribution of ranks separate by country.}
+
+\textbf{Distribution of model ranks (in terms of WIS) for three week ahead forecasts}
+A: Distribution of the ranks (determined by the weighted interval score)
+for three week ahead forecasts of the different models and forecast
+targets, pooled across locations. B: Distribution of ranks separate by
+country.
+
+\paragraph{S18 Fig.}
+\label{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets, pooled across locations.
+B: Distribution of ranks separate by country.}
+
+\textbf{Distribution of model ranks (in terms of WIS) for four week ahead forecasts}
+A: Distribution of the ranks (determined by the weighted interval score)
+for four week ahead forecasts of the different models and forecast
+targets, pooled across locations. B: Distribution of ranks separate by
+country.
+
+\paragraph{S19 Fig.}
+\label{fig:distribution-scores-differences}
+
+\textbf{Difference in WIS between the Crowd forecast and the Hub ensemble for two week ahead forecasts.}
+Values below zero mean better performance of the Crowd forecasts.
+
+\paragraph{S20 Fig.}
+\label{fig:distribution-scores-differences-renewal}
+
+\textbf{Difference in WIS between the Crowd forecast and the Renewal model for two week ahead forecasts.}
+Values below zero mean better performance of the Crowd forecasts.
+
+\paragraph{S21}
+
+\textbf{Fig.} \label{fig:agg-performance-ensemble-mean}
+\textbf{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.}
+``Hub-ensemble'' extit\{excludes\} all our models, Hub-ensemble-all
+extit\{includes\} all of our models, ``Hub-ensemble-realised'' is the
+actual hub-ensemble observed in reality, which includes the renewal
+model and the crowd forecasts, but ont the convolution model. Values
+(except for Bias) are computed as differences to the Hub ensemble which
+excludes our contributions. For Coverage, this is an absolute
+difference, for other metrics this is a percentage difference. A, B:
+mean weighted interval score (WIS) across horizons relative to the Hub
+ensemble (lower values indicate better performance). C, D: Empirical
+coverage of the 50\% and 90\% prediction intervals minus empirical
+coverage observed for the Hub ensemble. E: Dispersion relative to the
+dispersion of the Hub ensemble. Higher values mean greater dispersion of
+the forecast and imply ceteris paribus a worse score. F: Bias,
+i.e.~general (relative) tendency to over- orunderpredict. Values are
+between -1 (complete under-prediction) and 1 (complete over-prediction)
+and 0 ideally. G: Absolute error of the median forecast relative to the
+Hub ensemble. H. Standard deviation of all WIS values for different
+horizons relative to the Hub ensemble.
+
+\paragraph{S4}
+
+\textbf{Table.} \label{tab:score-table-ensemble-2}
+\textbf{Scores for one and two week ahead forecasts for the different versions of the median ensemble.}
+Scores are cut to three significant digits and rounded. Note that scores
+for cases (which include the whole period from October 12th 2020 until
+March 1st 2021) and deaths (which include only forecasts from the 21st
+of December 2020 on) are computed on different subsets. Numbers in
+brackets show the metrics relative to the Hub ensemble (i.e.~the median
+ensemble of all other models submitted to the German and Polish Forecast
+Hub, excluding our contributions). WIS is the mean weighted interval
+score (lower values are better), WIS - sd is the standard deviation of
+all scores achieved by a model. Dispersion, over-prediction and
+under-prediction together sum up to the weighted interval score. Bias
+(between -1 and 1, 0 is ideal) represents the general average tendency
+of a model to over- or underpredict. 50\% and 90\%-coverage are the
+percentage of observed values that fell within the 50\% and 90\%
+prediction intervals of a model.
+
+\paragraph{S5 Table.}
+\label{tab:score-table-ensemble-4}
+
+\textbf{Scores for three and four week ahead forecasts for the different versions of the median ensemble.}
+Scores are cut to three significant digits and rounded. Note that scores
+for cases (which include the whole period from October 12th 2020 until
+March 1st 2021) and deaths (which include only forecasts from the 21st
+of December 2020 on) are computed on different subsets. Numbers in
+brackets show the metrics relative to the Hub ensemble (i.e.~the median
+ensemble of all other models submitted to the German and Polish Forecast
+Hub, excluding our contributions). WIS is the mean weighted interval
+score (lower values are better), WIS - sd is the standard deviation of
+all scores achieved by a model. Dispersion, over-prediction and
+under-prediction together sum up to the weighted interval score. Bias
+(between -1 and 1, 0 is ideal) represents the general average tendency
+of a model to over- or underpredict. 50\% and 90\%-coverage are the
+percentage of observed values that fell within the 50\% and 90\%
+prediction intervals of a model.
+
+\paragraph{S6 Table.}
+\label{tab:score-table-ensemble-mean-2}
+
+\textbf{Scores for one and two week ahead forecasts for the different versions of the mean ensemble}
+Scores are cut to three significant digits and rounded. Note that scores
+for cases (which include the whole period from October 12th 2020 until
+March 1st 2021) and deaths (which include only forecasts from the 21st
+of December 2020 on) are computed on different subsets. Numbers in
+brackets show the metrics relative to the Hub mean ensemble (i.e.~the
+mean ensemble of all other models submitted to the German and Polish
+Forecast Hub, excluding our contributions). WIS is the mean weighted
+interval score (lower values are better), WIS - sd is the standard
+deviation of all scores achieved by a model. Dispersion, over-prediction
+and under-prediction together sum up to the weighted interval score.
+Bias (between -1 and 1, 0 is ideal) represents the general average
+tendency of a model to over- or underpredict. 50\% and 90\%-coverage are
+the percentage of observed values that fell within the 50\% and 90\%
+prediction intervals of a model.
+
+\paragraph{S7 Table.}
+\label{tab:score-table-ensemble-mean-4}
+
+\textbf{Scores for three and four week ahead forecasts for the different versions of the mean ensemble}
+Scores are cut to three significant digits and rounded. Note that scores
+for cases (which include the whole period from October 12th 2020 until
+March 1st 2021) and deaths (which include only forecasts from the 21st
+of December 2020 on) are computed on different subsets. Numbers in
+brackets show the metrics relative to the Hub mean ensemble (i.e.~the
+mean ensemble of all other models submitted to the German and Polish
+Forecast Hub, excluding our contributions). WIS is the mean weighted
+interval score (lower values are better), WIS - sd is the standard
+deviation of all scores achieved by a model. Dispersion, over-prediction
+and under-prediction together sum up to the weighted interval score.
+Bias (between -1 and 1, 0 is ideal) represents the general average
+tendency of a model to over- or underpredict. 50\% and 90\%-coverage are
+the percentage of observed values that fell within the 50\% and 90\%
+prediction intervals of a model.
+
+\paragraph{S22 Fig.}
+\label{fig:agg-performance-all-late}
+
+\textbf{Visualisation of aggregate performance metrics across forecast horizons (period from December 14th 2020 on)}
+From December 14th 2020 on, all models were available. In the original
+analysis, cases and deaths were scored on different periods, as the
+convolution model was only added later. This sensitivity analysis shows
+performance of all models restricted to the period from December 14 2020
+until March 1st 2021 where all models were available. A, B: mean
+weighted interval score (WIS, lower indicates better performance) across
+horizons. WIS is decomposed into its components dispersion,
+over-prediction and under-prediction. C: Empirical coverage of the 50\%
+prediction intervals (50\% coverage is perfect). D: Empirical coverage
+of the 90\% prediction intervals. E: Dispersion (same as in panel A, B).
+Higher values mean greater dispersion of the forecast and imply ceteris
+paribus a worse score. F: Bias, i.e.~general (relative) tendency to
+over- or underpredict. Values are between -1 (complete under-prediction)
+and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the
+median forecast (lower is better). H. Standard deviation of all WIS
+values for different horizons
+
+\paragraph{S8}
+
+\textbf{Table.} \label{tab:score-table-late-2}
+\textbf{Scores for one and two week ahead forecasts (sensitivity analysis)}
+Scores are cut to three significant digits and rounded. In the original
+analysis, cases and deaths were scored on different periods, as the
+convolution model was only added later. This table shows performance of
+all models restricted to the period from December 14 2020 until March
+1st 2021 where all models were available. Numbers in brackets show the
+metrics relative to the Hub ensemble (i.e.~the median ensemble of all
+other models submitted to the German and Polish Forecast Hub, excluding
+our contributions). WIS is the mean weighted interval score (lower
+values are better), WIS - sd is the standard deviation of all scores
+achieved by a model. Dispersion, over-prediction and under-prediction
+together sum up to the weighted interval score. Bias (between -1 and 1,
+0 is ideal) represents the general average tendency of a model to over-
+or underpredict. 50\% and 90\%-coverage are the percentage of observed
+values that fell within the 50\% and 90\% prediction intervals of a
+model.
+
+\paragraph{S9 Table.}
+\label{tab:score-table-late-4}
+
+\textbf{Scores for three and four week ahead forecasts (sensitivity analysis)}
+Scores are cut to three significant digits and rounded. In the original
+analysis, cases and deaths were scored on different periods, as the
+convolution model was only added later. This table shows performance of
+all models restricted to the period from December 14 2020 until March
+1st 2021 where all models were available. Numbers in brackets show the
+metrics relative to the Hub ensemble (i.e.~the median ensemble of all
+other models submitted to the German and Polish Forecast Hub, excluding
+our contributions). WIS is the mean weighted interval score (lower
+values are better), WIS - sd is the standard deviation of all scores
+achieved by a model. Dispersion, over-prediction and under-prediction
+together sum up to the weighted interval score. Bias (between -1 and 1,
+0 is ideal) represents the general average tendency of a model to over-
+or underpredict. 50\% and 90\%-coverage are the percentage of observed
+values that fell within the 50\% and 90\% prediction intervals of a
+model.
+
+\paragraph{S10 Table.}
+\label{tab:table-ensemble-versions}
+
+\textbf{Overview of the models and ensembles used.}
+
+\paragraph{S23 Fig.}
+\label{fig:num-forecasters}
+
+\textbf{Number of participants who submitted a forecast over time.}
+
+\paragraph{S24 Fig.}
+\label{fig:num-ensemble-members}
+
+\textbf{Number of member models in the official Hub ensemble} This
+includes our crowd forecasts and the renewal model. Note that the
+renewal model was not included in the ensemble on December 28th 2020.
+
+\paragraph{S25 Fig.}
+\label{fig:compare-forecasters}
+
+\textbf{Crowd forecasts and baseline shown in the application for a two week horizon.}
+Shown are the median, as well as the 50\% and 90\% prediction intervals
+(in order of decreasing opacity). For any given point in time, the
+baseline shown in red is what forecasters saw when they opened the app
+(the baseline shown was constant across all forecast horizons).
 
@@
 
-\hypertarget{the-crowdforecasting-app}{%
-\subsection{The crowdforecasting app}\label{the-crowdforecasting-app}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../crowd-forecast/Screenshot-forecasting-app} \caption{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).
-}\label{fig:screenshot}
-\end{figure}
-
-\clearpage
-
-\hypertarget{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}{%
-\subsection{Text S1. Further details on the semi-mechanistic forecasting
-models}\label{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}}
-
-\hypertarget{renewal-equation-model}{%
-\subsubsection{Renewal equation model}\label{renewal-equation-model}}
-
-The model was initialised prior to the first observed data point by
-assuming constant exponential growth for the mean of assumed delays from
-infection to case report.
-
-\begin{align}
-  I_{t} &= I_0 \exp  \left(r t \right)  \\
-  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
-  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
-\end{align}
-
-Where \(I_{obs}\) and \(r_{obs}\) are estimated from the first week of
-observed data. For the time window of the observed data infections were
-then modelled by weighting previous infections by the generation time
-and scaling by the instantaneous reproduction number. These infections
-were then convolved to cases by date (\(O_t\)) and cases by date of
-report (\(D_t\)) using log-normal delay distributions. This model can be
-defined mathematically as follows,
-
-\begin{align}
-  \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
-  I_t &= R_t \sum_{\tau = 1}^{15} w(\tau | \mu_{w}, \sigma_{w}) I_{t - \tau} \\
-  O_t &= \sum_{\tau = 0}^{15} \xi_{O}(\tau | \mu_{\xi_{O}}, \sigma_{\xi_{O}}) I_{t-\tau} \\
-  D_t &= \alpha \sum_{\tau = 0}^{15} \xi_{D}(\tau | \mu_{\xi_{D}}, \sigma_{\xi_{D}}) O_{t-\tau} \\ 
-  C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
-\end{align}
-
-Where, \begin{align}
-     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
-    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
-    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
-\end{align}
-
-This model used the following priors for cases,
-
-\begin{align}
-     R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
-    \mu_w &\sim \mathcal{N}(3.6, 0.7) \\
-    \sigma_w &\sim \mathcal{N}(3.1, 0.8) \\
-    \mu_{\xi_{O}} &\sim \mathcal{N}(1.62, 0.064) \\
-    \sigma_{\xi_{O}} &\sim \mathcal{N}(0.418, 0.069) \\
-    \mu_{\xi_{D}} &\sim \mathcal{N}(0.614, 0.066) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(1.51, 0.048) \\
-    \alpha &\sim \mathcal{N}(0.25, 0.05) \\
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-and updated the reporting process as follows when forecasting deaths,
-
-\begin{align}
-    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
-    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
-\end{align}
-
-\(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) were truncated to be
-greater than 0 and with \(\xi\), and \(w\) normalised to sum to 1.
-
-The prior for the generation time was sourced from {[}51{]} but refit
-using a log-normal incubation period with a mean of 5.2 days (SD 1.1)
-and SD of 1.52 days (SD 1.1) with this incubation period also being used
-as a prior {[}52{]} for \(\xi_{O}\). This resulted in a
-gamma-distributed generation time with mean 3.6 days (standard deviation
-(SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates. We estimated
-the delay between symptom onset and case report or death required to
-convolve latent infections to observations by fitting an integer
-adjusted log-normal distribution to 10 subsampled bootstraps of a public
-linelist for cases in Germany from April 2020 to June 2020 with each
-bootstrap using 1\% or 1769 samples of the available data {[}45,53{]}
-and combining the posteriors for the mean and standard deviation of the
-log-normal distribution {[}40,42,46,54{]}.
-
-\(GP_t\) is an approximate Hilbert space Gaussian process as defined in
-{[}55{]} using a Matern 3/2 kernel using a boundary factor of 1.5 and 17
-basis functions (20\% of the number of days used in fitting). The length
-scale of the Gaussian process was given a log-normal prior with a mean
-of 21 days, and a standard deviation of 7 days truncated to be greater
-than 3 days and less than 60 days. The magnitude of the Gaussian process
-was assumed to be normally distributed centred at 0 with a standard
-deviation of 0.1.
-
-From the forecast time horizon (\(T\)) and onwards the last value of the
-Gaussian process was used (hence \(R_t\) was assumed to be fixed) and
-latent infections were adjusted to account for the proportion of the
-population that was susceptible to infection as follows,
-
-\begin{equation}
-    I_t = (N - I^c_{t-1}) \left(1 - \exp \left(\frac{-I'_t}{N - I^c_{T}}\right)\right),
-\end{equation}
-
-where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\)
-and \(I'_t\) are the unadjusted infections defined above. This
-adjustment is based on that implemented in the \texttt{epidemia} R
-package {[}56,57{]}.
-
-\hypertarget{convolution-model}{%
-\paragraph{Convolution model}\label{convolution-model}}
-
-The convolution model shares the same observation model as the renewal
-model but rather than assuming that an observation is predicted by
-itself using the renewal equation instead assumes that it is predicted
-entirely by another observation after some parametric delay. It can be
-defined mathematically as follows,
-
-\begin{equation} 
-    D_{t} \sim \mathrm{NB}\left(\omega_{(t \mod 7)} \alpha \sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) C_{t-\tau},  \phi \right)
-\end{equation}
-
-with the following priors,
-
-\begin{align}
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \alpha &\sim \mathcal{N}(0.01, 0.02) \\
-    \xi &\sim \mathcal{LN}(\mu, \sigma) \\
-    \mu &\sim \mathcal{N}(2.5, 0.5) \\
-\sigma &\sim \mathcal{N}(0.47, 0.2) \\
-\phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-with \(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) truncated to be
-greater than 0 and with \(\xi\) normalised such that
-\(\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1\).
-
-\hypertarget{model-fitting}{%
-\subsubsection{Model fitting}\label{model-fitting}}
-
-Both models were implemented using the \texttt{EpiNow2} R package
-(version 1.3.3) {[}40{]}. Each forecast target was fitted independently
-for each model using Markov-chain Monte Carlo (MCMC) in stan {[}46{]}. A
-minimum of 4 chains were used with a warmup of 250 samples for the
-renewal equation-based model and 1000 samples for the convolution model.
-2000 samples total post warmup were used for the renewal equation model
-and 4000 samples for the convolution model. Different settings were
-chosen for each model to optimise compute time contingent on
-convergence. Convergence was assessed using the R hat diagnostic
-{[}46{]}. For the convolution model forecast the case forecast from the
-renewal equation model was used in place of observed cases beyond the
-forecast horizon using 1000 posterior samples. 12 weeks of data was used
-for both models though only 3 weeks of data were included in the
-likelihood for the convolution model.
-
-\clearpage
-
-\hypertarget{tables-with-results-of-the-forecast-evaluation}{%
-\subsection{Tables with results of the forecast
-evaluation}\label{tables-with-results-of-the-forecast-evaluation}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 7010 (0.8) & 7480 (0.64) & 2680 (0.73) & 1700 (1.38) & 2630 (0.68) & -0.01 & 10400 (0.82) & 0.55 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 8740 (1) & 11800 (1.01) & 2190 (0.6) & 2720 (2.21) & 3830 (0.99) & 0.18 & 12000 (0.94) & 0.48 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 16200 (0.89) & 16600 (0.76) & 3660 (0.6) & 5930 (1.56) & 6600 (0.78) & -0.01 & 23300 (0.87) & 0.36 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25600 (1.4) & 33800 (1.54) & 5420 (0.88) & 5920 (1.56) & 14200 (1.69) & 0.17 & 34600 (1.29) & 0.43 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 27000 (0.81) & 26200 (0.64) & 4750 (0.52) & 11000 (1.43) & 11200 (0.67) & 0.02 & 39000 (0.83) & 0.14 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 50600 (1.51) & 70000 (1.72) & 10800 (1.18) & 7710 (1) & 32100 (1.93) & 0.13 & 68700 (1.46) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 39200 (0.7) & 38600 (0.52) & 5970 (0.49) & 15600 (1.26) & 17600 (0.56) & 0.07 & 54800 (0.74) & 0.05 & 0.38\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 91700 (1.64) & 135000 (1.83) & 19500 (1.6) & 8990 (0.72) & 63200 (2.02) & 0.09 & 125000 (1.68) & 0.31 & 0.48\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{aggregate-performance-by-location}{%
-\subsection{Aggregate performance by
-location}\label{aggregate-performance-by-location}}
-
-\hypertarget{performance-in-germany}{%
-\subsubsection{Performance in Germany}\label{performance-in-germany}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Germany-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Germany}
-\end{figure}
-
-\hypertarget{performance-in-poland}{%
-\subsubsection{Performance in Poland}\label{performance-in-poland}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Poland-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Poland}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-absolute-terms}{%
-\subsubsection{Performance across locations in absolute
-terms}\label{performance-across-locations-in-absolute-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-v4} \caption{Visualisation of aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-relative-terms}{%
-\subsection{Performance across locations in relative
-terms}\label{performance-across-locations-in-relative-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4} \caption{Visualisation of relative aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals.
-E: Dispersion.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast.
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations-rel}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-daily-reported-cases-and-deaths}{%
-\subsection{Visualisation of daily reported cases and
-deaths}\label{visualisation-of-daily-reported-cases-and-deaths}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily_truth} \caption{Visualisation of daily report data.
-The black line represents weekly data divided by seven.
-Data were last accessed through the German and Polish Forecast Hub on August 21 2021.}\label{fig:daily-truth}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily-data-updates} \caption{Visualisation of the absolute difference between the daily report data at the time and the data now.
-In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:daily-truth-update}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/weekly-data-updates} \caption{Visualisation of the relative difference between the weekly report data at the time and the data now.
-Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:weekly-truth-update}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}{%
-\subsection{Visualisation of scores and forecasts 1, 3, 4 weeks
-ahead}\label{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} \caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} \caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} \caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-4}
-\end{figure}
-
-\clearpage
-
-\hypertarget{distribution-of-scores}{%
-\subsection{Distribution of scores}\label{distribution-of-scores}}
-
-\hypertarget{absolute-scores}{%
-\subsubsection{Absolute scores}\label{absolute-scores}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1} \caption{A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3} \caption{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4} \caption{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-4}
-\end{figure}
-
-\hypertarget{ranks-achieved-by-forecasts}{%
-\subsubsection{Ranks achieved by
-forecasts}\label{ranks-achieved-by-forecasts}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-2}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-4}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} \caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-renewal} \caption{Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences-renewal}
-\end{figure}
-
-\newpage
-
-\hypertarget{comparison-of-ensembles}{%
-\subsection{Comparison of ensembles}\label{comparison-of-ensembles}}
-
-\hypertarget{performance-visualisation-mean-ensemble}{%
-\subsubsection{Performance visualisation mean
-ensemble}\label{performance-visualisation-mean-ensemble}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble”     extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
-Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-mean}
-\end{figure}
-
-\hypertarget{tables-median-ensemble}{%
-\subsubsection{Tables median ensemble}\label{tables-median-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 6970 (0.79) & 8260 (0.71) & 3060 (0.83) & 943 (0.77) & 2970 (0.77) & 0.04 & 10800 (0.85) & 0.55 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 7820 (0.89) & 9630 (0.82) & 3270 (0.89) & 1210 (0.98) & 3330 (0.86) & -0.02 & 12000 (0.94) & 0.48 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 7960 (0.91) & 10300 (0.88) & 3190 (0.87) & 1020 (0.83) & 3760 (0.97) & 0.04 & 12100 (0.95) & 0.57 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 16400 (0.9) & 19600 (0.89) & 5350 (0.87) & 3290 (0.87) & 7730 (0.92) & 0.02 & 24200 (0.9) & 0.43 & 0.69\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 16900 (0.92) & 19600 (0.89) & 5230 (0.85) & 4310 (1.13) & 7370 (0.88) & 0.00 & 24600 (0.92) & 0.38 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 17500 (0.96) & 21400 (0.98) & 5830 (0.95) & 2880 (0.76) & 8770 (1.04) & 0.00 & 25500 (0.95) & 0.45 & 0.71\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 235 (0.95) & 332 (0.98) & 88.6 (0.96) & 90.4 (0.79) & 55.5 (1.33) & -0.01 & 323 (0.97) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 234 (0.94) & 331 (0.98) & 85.2 (0.92) & 98.1 (0.85) & 50.2 (1.21) & -0.05 & 329 (0.99) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 234 (0.94) & 329 (0.97) & 90.7 (0.98) & 118 (1.03) & 25.3 (0.61) & -0.08 & 333 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 239 (0.96) & 337 (1) & 85.2 (0.92) & 99.6 (0.87) & 54.2 (1.3) & -0.03 & 322 (0.96) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 246 (0.99) & 342 (1.01) & 91.5 (0.99) & 106 (0.92) & 48.6 (1.17) & -0.06 & 342 (1.02) & 0.67 & 0.92\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 296 (1.01) & 398 (1.03) & 125 (0.95) & 91 (0.84) & 80.2 (1.55) & 0.05 & 486 (1.13) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 303 (1.04) & 423 (1.1) & 115 (0.87) & 122 (1.13) & 66.1 (1.27) & 0.00 & 483 (1.13) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 270 (0.92) & 385 (1) & 121 (0.92) & 119 (1.1) & 29.9 (0.58) & -0.04 & 403 (0.94) & 0.58 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 303 (1.04) & 392 (1.02) & 122 (0.92) & 106 (0.98) & 74.6 (1.44) & 0.03 & 499 (1.16) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 296 (1.01) & 397 (1.03) & 128 (0.97) & 97.1 (0.9) & 71.2 (1.37) & -0.01 & 462 (1.08) & 0.67 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 30800 (0.92) & 38600 (0.95) & 7910 (0.87) & 6890 (0.9) & 16000 (0.96) & 0.03 & 44200 (0.94) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 30800 (0.92) & 34100 (0.84) & 7500 (0.82) & 8960 (1.17) & 14300 (0.86) & 0.02 & 44100 (0.94) & 0.24 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 34000 (1.02) & 43100 (1.06) & 8860 (0.97) & 6300 (0.82) & 18900 (1.14) & 0.02 & 48100 (1.03) & 0.29 & 0.60\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 51200 (0.92) & 69900 (0.95) & 10900 (0.89) & 11100 (0.9) & 29300 (0.94) & 0.04 & 69600 (0.94) & 0.19 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 48800 (0.87) & 58600 (0.8) & 9700 (0.8) & 13700 (1.1) & 25400 (0.81) & 0.00 & 65800 (0.88) & 0.19 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 59100 (1.06) & 84100 (1.14) & 12600 (1.03) & 10100 (0.81) & 36400 (1.16) & 0.01 & 78900 (1.06) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 332 (1.04) & 388 (1.18) & 158 (0.92) & 78.7 (0.85) & 95 (1.72) & -0.02 & 547 (1.12) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 321 (1.01) & 385 (1.17) & 153 (0.89) & 100 (1.08) & 68.1 (1.24) & -0.01 & 535 (1.1) & 0.54 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 298 (0.93) & 337 (1.03) & 155 (0.9) & 106 (1.14) & 37.5 (0.68) & -0.04 & 441 (0.9) & 0.67 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 319 (1) & 342 (1.04) & 160 (0.93) & 85.1 (0.92) & 73.6 (1.34) & -0.02 & 547 (1.12) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 332 (1.04) & 363 (1.11) & 168 (0.98) & 86.1 (0.93) & 78.2 (1.42) & -0.02 & 528 (1.08) & 0.58 & 0.96\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 445 (1.05) & 532 (1.2) & 193 (0.91) & 107 (0.85) & 144 (1.68) & -0.03 & 700 (1.04) & 0.54 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 399 (0.94) & 438 (0.99) & 195 (0.92) & 105 (0.83) & 97.9 (1.14) & -0.05 & 692 (1.03) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 384 (0.91) & 387 (0.87) & 196 (0.92) & 122 (0.97) & 65.9 (0.77) & -0.06 & 602 (0.89) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 407 (0.96) & 456 (1.03) & 202 (0.95) & 105 (0.83) & 101 (1.18) & -0.03 & 669 (0.99) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 457 (1.08) & 527 (1.19) & 208 (0.98) & 129 (1.02) & 121 (1.41) & -0.06 & 744 (1.1) & 0.50 & 0.96\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\hypertarget{tables-mean-ensemble}{%
-\subsubsection{Tables mean ensemble}\label{tables-mean-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 8680 (1) & 10300 (1) & 3700 (1) & 1460 (1) & 3520 (1) & -0.02 & 13400 (1) & 0.50 & 0.86\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 7600 (0.88) & 8770 (0.85) & 3360 (0.91) & 1090 (0.75) & 3140 (0.89) & 0.01 & 11900 (0.89) & 0.52 & 0.90\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 8050 (0.93) & 9070 (0.88) & 3520 (0.95) & 1410 (0.97) & 3120 (0.89) & -0.02 & 12600 (0.94) & 0.48 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 8090 (0.93) & 9780 (0.95) & 3490 (0.94) & 1110 (0.76) & 3490 (0.99) & 0.02 & 12700 (0.95) & 0.57 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 19000 (1) & 22100 (1) & 5960 (1) & 3690 (1) & 9340 (1) & 0.02 & 28800 (1) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 17100 (0.9) & 20600 (0.93) & 5550 (0.93) & 2850 (0.77) & 8660 (0.93) & 0.05 & 26000 (0.9) & 0.38 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 17600 (0.93) & 20000 (0.9) & 5540 (0.93) & 3790 (1.03) & 8230 (0.88) & 0.01 & 26800 (0.93) & 0.36 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 18300 (0.96) & 22600 (1.02) & 5910 (0.99) & 2640 (0.72) & 9720 (1.04) & 0.06 & 27700 (0.96) & 0.38 & 0.76\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 229 (1) & 292 (1) & 101 (1) & 90.4 (1) & 36.7 (1) & -0.07 & 315 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 219 (0.96) & 289 (0.99) & 96.8 (0.96) & 79.8 (0.88) & 42.6 (1.16) & -0.04 & 297 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 217 (0.95) & 287 (0.98) & 95.3 (0.94) & 83.1 (0.92) & 38.7 (1.05) & -0.07 & 300 (0.95) & 0.67 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 225 (0.98) & 292 (1) & 98.7 (0.98) & 94.2 (1.04) & 32 (0.87) & -0.09 & 314 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 222 (0.97) & 289 (0.99) & 98 (0.97) & 84.1 (0.93) & 39.6 (1.08) & -0.04 & 295 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 225 (0.98) & 290 (0.99) & 99.7 (0.99) & 84.7 (0.94) & 40.5 (1.1) & -0.05 & 314 (1) & 0.71 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 256 (1) & 306 (1) & 138 (1) & 64.5 (1) & 53.2 (1) & 0.04 & 374 (1) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 270 (1.05) & 338 (1.1) & 136 (0.99) & 65.2 (1.01) & 68.1 (1.28) & 0.06 & 413 (1.1) & 0.75 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 268 (1.05) & 346 (1.13) & 133 (0.96) & 78.7 (1.22) & 57.1 (1.07) & 0.05 & 408 (1.09) & 0.75 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 259 (1.01) & 322 (1.05) & 133 (0.96) & 81.7 (1.27) & 44.4 (0.83) & 0.03 & 380 (1.02) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 264 (1.03) & 315 (1.03) & 133 (0.96) & 70.1 (1.09) & 60 (1.13) & 0.06 & 404 (1.08) & 0.71 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 264 (1.03) & 332 (1.08) & 141 (1.02) & 60.1 (0.93) & 63.1 (1.19) & 0.06 & 390 (1.04) & 0.79 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 35600 (1) & 42100 (1) & 9340 (1) & 7050 (1) & 19200 (1) & 0.03 & 51200 (1) & 0.26 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 32100 (0.9) & 40500 (0.96) & 8830 (0.95) & 4920 (0.7) & 18300 (0.95) & 0.07 & 47200 (0.92) & 0.29 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 32200 (0.9) & 36700 (0.87) & 8430 (0.9) & 7190 (1.02) & 16500 (0.86) & 0.04 & 46900 (0.92) & 0.24 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 35200 (0.99) & 46000 (1.09) & 9630 (1.03) & 4600 (0.65) & 20900 (1.09) & 0.08 & 51000 (1) & 0.38 & 0.67\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 60300 (1) & 79300 (1) & 15700 (1) & 10400 (1) & 34100 (1) & 0.04 & 78600 (1) & 0.29 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 55000 (0.91) & 77100 (0.97) & 14600 (0.93) & 6620 (0.64) & 33800 (0.99) & 0.11 & 75200 (0.96) & 0.33 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 53400 (0.89) & 66600 (0.84) & 13700 (0.87) & 10600 (1.02) & 29200 (0.86) & 0.06 & 70400 (0.9) & 0.26 & 0.60\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 61700 (1.02) & 89800 (1.13) & 16400 (1.04) & 6400 (0.62) & 38900 (1.14) & 0.12 & 82900 (1.05) & 0.31 & 0.64\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 289 (1) & 293 (1) & 178 (1) & 45.9 (1) & 65.7 (1) & 0.01 & 443 (1) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 310 (1.07) & 348 (1.19) & 182 (1.02) & 42 (0.92) & 86.5 (1.32) & 0.08 & 502 (1.13) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 315 (1.09) & 339 (1.16) & 178 (1) & 62.2 (1.36) & 74 (1.13) & 0.07 & 507 (1.14) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 297 (1.03) & 292 (1) & 174 (0.98) & 67.7 (1.47) & 55 (0.84) & 0.01 & 452 (1.02) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 294 (1.02) & 299 (1.02) & 172 (0.97) & 48 (1.05) & 74.2 (1.13) & 0.03 & 476 (1.07) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 310 (1.07) & 349 (1.19) & 189 (1.06) & 39.4 (0.86) & 81.9 (1.25) & 0.05 & 482 (1.09) & 0.62 & 1.00\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 437 (1) & 568 (1) & 232 (1) & 72 (1) & 134 (1) & 0.00 & 702 (1) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 445 (1.02) & 598 (1.05) & 237 (1.02) & 56.4 (0.78) & 152 (1.13) & 0.06 & 707 (1.01) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 421 (0.96) & 520 (0.92) & 239 (1.03) & 49.9 (0.69) & 132 (0.99) & 0.05 & 678 (0.97) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 398 (0.91) & 465 (0.82) & 235 (1.01) & 55.6 (0.77) & 107 (0.8) & 0.00 & 628 (0.89) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 418 (0.96) & 533 (0.94) & 222 (0.96) & 66.8 (0.93) & 129 (0.96) & 0.03 & 662 (0.94) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 467 (1.07) & 636 (1.12) & 248 (1.07) & 61 (0.85) & 158 (1.18) & 0.05 & 755 (1.08) & 0.67 & 1.00\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{sensitivity-analysis}{%
-\subsection{Sensitivity analysis}\label{sensitivity-analysis}}
-
-In the original analysis, cases and deaths were scored on different
-periods, as the convolution model was only added later. This sensitivity
-shows performance of all models restricted to the period from December
-14 2020 until March 1st 2021 where all models were available.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-late}
-\end{figure}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 4980 (0.74) & 5730 (0.64) & 2070 (0.6) & 728 (0.74) & 2190 (0.94) & 0.09 & 7810 (0.82) & 0.54 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 6730 (1) & 8960 (1) & 3430 (1) & 978 (1) & 2330 (1) & -0.09 & 9550 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 9640 (1.43) & 13300 (1.48) & 1970 (0.57) & 4170 (4.26) & 3500 (1.5) & 0.09 & 12700 (1.33) & 0.46 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 10700 (0.99) & 13800 (1.1) & 2880 (0.58) & 2350 (0.85) & 5430 (1.79) & 0.08 & 15400 (1.07) & 0.46 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 10800 (1) & 12500 (1) & 4940 (1) & 2780 (1) & 3030 (1) & -0.13 & 14400 (1) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25000 (2.31) & 34000 (2.72) & 4780 (0.97) & 8710 (3.13) & 11500 (3.8) & 0.05 & 32000 (2.22) & 0.50 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 17200 (1) & 16000 (0.98) & 3800 (0.63) & 5660 (0.85) & 7770 (1.74) & 0.07 & 26800 (1.1) & 0.08 & 0.58\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 17200 (1) & 16300 (1) & 6030 (1) & 6670 (1) & 4470 (1) & -0.16 & 24400 (1) & 0.33 & 0.67\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 37700 (2.19) & 55900 (3.43) & 8840 (1.47) & 10700 (1.6) & 18100 (4.05) & -0.03 & 49800 (2.04) & 0.33 & 0.58\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 26100 (0.95) & 21000 (0.84) & 4810 (0.7) & 11300 (0.83) & 10100 (1.43) & 0.04 & 39400 (1.05) & 0.00 & 0.46\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 27600 (1) & 25000 (1) & 6900 (1) & 13600 (1) & 7060 (1) & -0.19 & 37400 (1) & 0.29 & 0.54\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 48900 (1.77) & 77800 (3.11) & 13800 (2) & 11900 (0.88) & 23200 (3.29) & -0.10 & 65500 (1.75) & 0.38 & 0.58\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{overview-of-models-and-forecasters}{%
-\subsection{Overview of models and
-forecasters}\label{overview-of-models-and-forecasters}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{7.3cm}}
-\caption{\label{tab:table-ensemble-versions}Overview of the models and ensembles used.}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{Overview of the models and ensembles used. \textit{(continued)}}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-\cellcolor{gray!6}{Hub-ensemble-realised} & \cellcolor{gray!6}{Official Forecast Hub median ensemble.
-Created by the Forecast Hub officially under the name 'KITCOVIDhub-median\_ensemble' and used as the default ensemble.
-Included are our crowd forecasts as well as the renewal model (with one missed submission on December 28 2020, but not the convolution model which was deemed to similar to the renewal model.}\\
-\addlinespace \addlinespace
-Hub-ensemble-realised-mean & Official Forecast Hub mean ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-mean\_ensemble'.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{ \vphantom{1}} & \cellcolor{gray!6}{}\\
-\addlinespace \addlinespace
-Hub-ensemble & Version of the official Hub median ensemble which excludes all our contributions.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Hub-ensemble-mean} & \cellcolor{gray!6}{Version of the official Hub mean ensemble which excludes all our contributions.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-renewal, 
-    Hub-ensemble-with-renewal-mean & Versions of the official Hub ensembles which of our contributions includes only the Renewal model.\\
-\addlinespace \addlinespace
-Hub-ensemble-with-crowd, 
-\cellcolor{gray!6}{    Hub-ensemble-with-crowd-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which of our contributions includes only the Crowd forecast.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-convolution, 
-    Hub-ensemble-with-convolution-mean & Versions of the official Hub ensembles which of our contributions includes only the Convolution model (which originally was never included in any official Hub ensemble).\\
-\addlinespace \addlinespace
-Hub-ensemble-with-all, 
-\cellcolor{gray!6}{    Hub-ensemble-with-all-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which includes all our contributions.
-For cases, this is identical to the official Hub ensembles, but for deaths the convolution model was added.}\\
-\addlinespace \addlinespace
- & \\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Crowd forecast} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'}\\
-\addlinespace \addlinespace
-Renewal model & Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Convolution model} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\_secondary'}\\*
-\end{longtable}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/number-forecasters} \caption{Number of participants who submitted a forecast over time.}\label{fig:num-forecasters}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/ensemble-members} \caption{Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
-Note that the renewal model was not included in the ensemble on December 28th 2020.}\label{fig:num-ensemble-members}
-\end{figure}
-
-\clearpage
-
-\hypertarget{comparison-of-crowd-forecasts-and-application-baseline}{%
-\subsection{Comparison of crowd forecasts and application
-baseline}\label{comparison-of-crowd-forecasts-and-application-baseline}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} \caption{Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the median, as well as the 50\% and 90\% prediction intervals (in order of decreasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons).}\label{fig:compare-forecasters}
-\end{figure}
+\section*{References}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
-\CSLLeftMargin{1. }
+\CSLLeftMargin{1. }%
 \CSLRightInline{McGowan CJ, Biggerstaff M, Johansson M, Apfeldorf KM,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
-\CSLLeftMargin{2. }
+\CSLLeftMargin{2. }%
 \CSLRightInline{Reich NG, Brooks LC, Fox SJ, Kandula S, McGowan CJ,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
-\CSLLeftMargin{3. }
+\CSLLeftMargin{3. }%
 \CSLRightInline{Shaman J, Karspeck A. Forecasting seasonal outbreaks of
@@
 \leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
-\CSLLeftMargin{4. }
+\CSLLeftMargin{4. }%
 \CSLRightInline{Biggerstaff M, Alper D, Dredze M, Fox S, Fung IC-H,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
-\CSLLeftMargin{5. }
+\CSLLeftMargin{5. }%
 \CSLRightInline{Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak
@@
 \leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
-\CSLLeftMargin{6. }
+\CSLLeftMargin{6. }%
 \CSLRightInline{Yamana TK, Kandula S, Shaman J. Superensemble forecasts
@@
 \leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
-\CSLLeftMargin{7. }
+\CSLLeftMargin{7. }%
 \CSLRightInline{Colón-González FJ, Bastos LS, Hofmann B, Hopkin A,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
-\CSLLeftMargin{8. }
+\CSLLeftMargin{8. }%
 \CSLRightInline{Viboud C, Sun K, Gaffey R, Ajelli M, Fumanelli L, Merler
@@
 \leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
-\CSLLeftMargin{9. }
+\CSLLeftMargin{9. }%
 \CSLRightInline{Funk S, Camacho A, Kucharski AJ, Lowe R, Eggo RM,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
-\CSLLeftMargin{10. }
+\CSLLeftMargin{10. }%
 \CSLRightInline{Del Valle SY, McMahon BH, Asher J, Hatchett R, Lega JC,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
-\CSLLeftMargin{11. }
+\CSLLeftMargin{11. }%
 \CSLRightInline{Farrow DC, Brooks LC, Hyun S, Tibshirani RJ, Burke DS,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
-\CSLLeftMargin{12. }
+\CSLLeftMargin{12. }%
 \CSLRightInline{Funk S, Abbott S, Atkins BD, Baguelin M, Baillie JK,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
-\CSLLeftMargin{13. }
+\CSLLeftMargin{13. }%
 \CSLRightInline{Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
-\CSLLeftMargin{14. }
+\CSLLeftMargin{14. }%
 \CSLRightInline{Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
-\CSLLeftMargin{15. }
+\CSLLeftMargin{15. }%
 \CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
-\CSLLeftMargin{16. }
+\CSLLeftMargin{16. }%
 \CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
@@
 \leavevmode\vadjust pre{\hypertarget{ref-europeancovid-19forecasthubEuropeanCovid19Forecast2021}{}}%
-\CSLLeftMargin{17. }
+\CSLLeftMargin{17. }%
 \CSLRightInline{European Covid-19 Forecast Hub. European {Covid-19
@@
 \leavevmode\vadjust pre{\hypertarget{ref-reichAccuracyRealtimeMultimodel2019}{}}%
-\CSLLeftMargin{18. }
+\CSLLeftMargin{18. }%
 \CSLRightInline{Reich NG, McGowan CJ, Yamana TK, Tushar A, Ray EL,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
-\CSLLeftMargin{19. }
+\CSLLeftMargin{19. }%
 \CSLRightInline{Tetlock PE, Mellers BA, Rohrbaugh N, Chen E. Forecasting
@@
 \leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
-\CSLLeftMargin{20. }
+\CSLLeftMargin{20. }%
 \CSLRightInline{Atanasov P, Rescober P, Stone E, Swift SA,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
-\CSLLeftMargin{21. }
+\CSLLeftMargin{21. }%
 \CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers E-J. Laypeople
@@
 \leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{22. }%
 \CSLRightInline{ReplicationMarkets. Replication {Markets} -- {Reliable}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{23. }%
 \CSLRightInline{Servan-Schreiber E, Wolfers J, Pennock DM, Galebach B.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{24. }%
 \CSLRightInline{McAndrew TC, Reich NG. An expert judgment model to
@@
 \leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{25. }%
 \CSLRightInline{Recchia G, Freeman ALJ, Spiegelhalter D. How well did
@@
 \leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{26. }%
 \CSLRightInline{Metaculus. A {Preliminary Look} at {Metaculus} and
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{27. }%
 \CSLRightInline{Hypermind. Hypermind \textbar{} {Supercollective}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{28. }%
 \CSLRightInline{CSET Foretell. {CSET Foretell}. 2021 {[}cited 13 Oct
@@
 \leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{29. }%
 \CSLRightInline{PredictIt. {PredictIt}. 2021 {[}cited 13 Oct 2021{]}.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{30. }%
 \CSLRightInline{Held L, Meyer S, Bracher J. Probabilistic forecasting in
@@
 \leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{31. }%
 \CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{32. }%
 \CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ecdcDownloadHistoricalData2020}{}}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{33. }%
 \CSLRightInline{ECDC. Download historical data (to 14 {December} 2020)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rkiRKICoronavirusSARSCoV22021}{}}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{34. }%
 \CSLRightInline{RKI. {RKI} - {Coronavirus SARS-CoV-2} - {Aktueller
@@
 \leavevmode\vadjust pre{\hypertarget{ref-forsal.plRozbieznosciStatystykachKoronawirusa2020}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{35. }%
 \CSLRightInline{Forsal.pl. Rozbieżności w statystykach koronawirusa. 22
@@
 \leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{36. }%
 \CSLRightInline{Ärzteblatt DÄG Redaktion Deutsches.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{37. }%
 \CSLRightInline{Fay C, Guyader V, Rochette S, Girard C. Golem: A
@@
 \leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{38. }%
 \CSLRightInline{Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{39. }%
 \CSLRightInline{Our World in Data. {COVID-19 Data Explorer}. {Our World
@@
 \leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{40. }%
 \CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{41. }%
 \CSLRightInline{Fraser C. Estimating {Individual} and {Household
@@
 \leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation2020}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{42. }%
 \CSLRightInline{epiforecasts.io/covid. Covid-19: {Temporal} variation in
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{43. }%
 \CSLRightInline{Sherratt K, Abbott S, Meakin SR, Hellewell J, Munday JD,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-abbottEstimatingTimevaryingReproduction2020a}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{44. }%
 \CSLRightInline{Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{45. }%
 \CSLRightInline{Xu B, Gutierrez B, Hill S, Scarpino S, Loskill A, Wu J,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{46. }%
 \CSLRightInline{Stan Development Team. RStan: The r interface to stan.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{47. }%
 \CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG. Evaluating
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{48. }%
 \CSLRightInline{Gneiting T, Raftery AE. Strictly proper scoring rules,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{49. }%
 \CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Scoringutils:
@@
 \leavevmode\vadjust pre{\hypertarget{ref-deutschewelleCoronavirusGermanyImpose2020}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{50. }%
 \CSLRightInline{Deutsche Welle. Coronavirus: {Germany} to impose
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Ganyani T, Kremer C, Chen D, Torneri A, Faes C, Wallinga
-J, et al. Estimating the generation interval for coronavirus disease
-(COVID-19) based on symptom onset data, march 2020. Eurosurveillance.
-2020;25. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith
-HR, et al. The incubation period of coronavirus disease 2019 (COVID-19)
-from publicly reported confirmed cases: Estimation and application.
-Annals of Internal Medicine. 2020;172: 577--582. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J,
-Munday J, et al. Covidregionaldata: Subnational data for the covid-19
-outbreak. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957539}{10.5281/zenodo.3957539}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Evaluating the use of the reproduction number as an
-epidemiological tool, using spatio-temporal trends of the {Covid-19}
-outbreak in {England} \textbar{} {medRxiv}. {[}cited 30 May 2021{]}.
-Available:
-\url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Riutort-Mayol G, Bürkner P-C, Andersen MR, Solin A,
-Vehtari A. Practical hilbert space approximate bayesian gaussian
-processes for probabilistic programming. 2020. Available:
-\url{https://arxiv.org/abs/2004.11408}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Scott JA, Gandy A, Mishra S, Unwin J, Flaxman S, Bhatt
-S. Epidemia: Modeling of epidemics using hierarchical bayesian models.
-2020. Available:
-\url{https://imperialcollegelondon.github.io/epidemia/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bhattSemiMechanisticBayesianModeling}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Bhatt S, Ferguson N, Flaxman S, Gandy A, Mishra S, Scott
-JA. Semi-{Mechanistic Bayesian} modeling of {COVID-19} with {Renewal
-Processes}. : 14. }
-
 \end{CSLReferences}

### 2022-08-04 manuscript/manuscript.Rmd
final revisions

--- 2022-05-19 manuscript/manuscript.Rmd
@@
     - \usepackage{lineno}
+    - \usepackage[T1]{fontenc}
     - \linenumbers
-    -  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+    - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} 
+    - \newfloat{text}{thp}{}
+    - \floatname{text}{Text}
+    - \renewcommand{\figurename}{}
+    - \newcommand{\newfigurename}{Hello}
+    - \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+    - \usepackage{nameref,hyperref}
 output: 
-  bookdown::pdf_document2:
-    extra_dependencies: ["float"]
+  rticles::plos_article:
+    extra_dependencies: 
+      caption: null
     keep_tex:  true
@@
 linestretch: 2 
-bibliography:
-  - references.bib
-  - GermanPolishpaper.bib
-csl: vancouver.csl
----
-
-*Nikos I.
-Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy J.
-Quilty, Mark Jit, Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk*
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
-                      out.width = "100%", 
-                      fig.pos = "H", out.extra = "")
-
-library(kableExtra)
-library(magrittr)
-library(knitr)
-```
-
-# Abstract
-
+include-header: 
+  \usepackage[T1]{fontenc}
+author:
+  - name: Nikos I. Bosse
+    email: nikos.bosse@lshtm.ac.uk
+    affiliation: 
+      - London School of Hygiene & Tropical Medicine
+      - CMMID
+    corresponding: nikos.bosse@lshtm.ac.uk
+  - name: Sam Abbott
+    email: sam.abbott@lshtm.ac.uk
+    affiliation: 
+      - London School of Hygiene & Tropical Medicine
+      - CMMID
+  - name: Johannes Bracher
+    email: johannes.bracher@kit.edu
+    affiliation: Karlsruhe Institute of Technology Institute of Economic Theory and Statistics
+  - name: Habakuk Hain
+    email: habakuk.hain@mpinat.mpg.de
+    affiliation: Max Planck Institute for Multidisciplinary Sciences
+  - name: Billy J. Quilty
+    email: Billy.Quilty@lshtm.ac.uk
+    affiliation: 
+      - London School of Hygiene & Tropical Medicine
+      - CMMID
+  - name: Mark Jit
+    email: Mark.Jit@lshtm.ac.uk
+    affiliation: 
+      - London School of Hygiene & Tropical Medicine
+      - CMMID
+  - name: Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group
+    email: cmmid@lshtm.ac.uk
+    affiliation: 
+      - London School of Hygiene & Tropical Medicine
+      - CMMID
+  - name: Edwin van Leeuwen
+    email: Edwin.VanLeeuwen@phe.gov.uk
+    affiliation:
+      - UK Health Security Agency
+      - London School of Hygiene & Tropical Medicine
+  - name: Anne Cori
+    email: a.cori@imperial.ac.uk
+    affiliation: 
+      - Imperial College London
+  - name: Sebastian Funk
+    email: sebastian.funk@lshtm.ac.uk
+    affiliation: 
+      - London School of Hygiene & Tropical Medicine
+      - CMMID
+address:
+  - code: London School of Hygiene & Tropical Medicine
+    address: Department of Infectious Disease Epidemiology, London School of Hygiene & Tropical Medicine, London, United Kingdom
+  - code: CMMID
+    address: Centre for the Mathematical Modelling of Infectious Diseases (members of the CMMID COVID-19 working group are listed in S1 Acknowledgements), London, United Kingdom
+  - code: Karlsruhe Institute of Technology Institute of Economic Theory and Statistics
+    address: Institute of Economic Theory and Statistics, Karlsruhe Institute of Technology, Karlsruhe, Germany
+  - code: Max Planck Institute for Multidisciplinary Sciences
+    address: Max Planck Institute for Multidisciplinary Sciences, Göttingen, Germany
+  - code: UK Health Security Agency
+    address: UK Health Security Agency, London United Kingdom
+  - code: Imperial College London
+    address:  MRC Centre for Outbreak Analysis and Modelling, Department of Infectious Disease Epidemiology, School of Public Health, Imperial College London, London, United Kingdom
+
+abstract: |
   Forecasts based on epidemiological modelling have played an important role in shaping public policy throughout the COVID-19 pandemic.
@@
 
+## Ethics statement
+
+This study has been approved by the London School of Hygiene & Tropical Medicine Research
+Ethics Committee (reference number 22290). Consent from participants was obtained in written form.
+
+## Overview
+
 We created and submitted the following forecasts to the German and Polish Forecast Hub: 1) a direct human forecast (henceforth called “crowd forecast”), elicited from participants through a web application [@crowdforecastr] and 2) two semi-mechanistic model-based forecasts ("renewal model" and "convolution model") informed by basic assumptions about COVID-19 epidemiology.
@@
 These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, @forsal.plRozbieznosciStatystykachKoronawirusa2020), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, @aerzteblattSARSCoV2DiagnostikRKIPasst2020).
-The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \@ref(fig:daily-truth-update) and \@ref(fig:weekly-truth-update)).
+The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figs \nameref{fig:daily-truth-update} and \nameref{fig:weekly-truth-update}).
 
@@
 To make a forecast in the application participants could select a predictive distribution (with the default being log-normal) to represent the probability that the forecasted quantity took certain values.
-Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in Figure \@ref(fig:screenshot) in the SI).
+Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in \nameref{fig:screenshot} in the SI).
 The default shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.
 as $\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )$).
-A comparison of the crowd forecasts against the default baseline shown in the application is displayed in Figure \@ref(fig:compare-forecasters) in the Appendix.
+A comparison of the crowd forecasts against the default baseline shown in the application is displayed in \nameref{fig:compare-forecasters} in the Appendix.
 Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  @ourworldindataCOVID19DataExplorer2020.
@@
 
-individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation and were excluded from the submission as well as the analysis.
-
 Participants were recruited mostly within the Centre of Mathematical Modeling of Infectious Diseases at the London School of Hygiene & Tropical Medicine, but participants were also invited personally or via social media to submit predictions.
@@
 
-The study was approved by the Observational / Interventions Research Ethics Committee at the London School of Hygiene & Tropical Medicine, LSHTM Ethics Reference: 22290.
-
 ## Model-based forecasts
@@
 We used two Bayesian semi-mechanistic models from the `EpiNow2` R package (version 1.3.3) as our model-based forecasts [@epinow2].
-The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths (see details in the SI).
+The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths (see details in \nameref{txt:details-models} in the SI).
 It estimated the effective reproduction number $R_t$ (the average number of people each person infected at time t is expected to infect in turn) and modelled future infections as a weighted sum of past infection multiplied by $R_t$.
@@
 To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available.
-To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see Section \@ref(sensitivity-analysis) in the SI).
+To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see \nameref{fig:agg-performance-all-late} and \nameref{tab:score-table-late-2} and \nameref{tab:score-table-late-4}s in the SI).
 Results remained broadly unchanged.
@@
 how many observed values fall inside all 50% prediction intervals).
-Scoring metrics are explained in more detail in Table \@ref(tab:scoring-metrics) in the SI.
+Scoring metrics are explained in more detail in \nameref{tab:scoring-metrics} in the SI.
 All scores were calculated using the `scoringutils` R package [@scoringutils].
@@
 At all stages of the evaluation our forecasts were compared to the median ensemble of all *other* models submitted to the German and Polish Forecast Hub ("Hub ensemble").
-This "Hub ensemble" was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see details in Section \@ref(contributions-hub), as well as in Table \@ref(tab:table-ensemble-versions) and Figure \@ref(fig:num-ensemble-members) in the SI).
+This "Hub ensemble" was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see \nameref{tab:table-ensemble-versions} and \nameref{fig:num-ensemble-members} in the SI).
 What we call "Hub ensemble" in this article therefore differs from the "official Hub ensemble" (here called "hub-ensemble-realised") which included crowd forecasts as well as renewal model forecasts.
@@
 ```{r}
-caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
+captiontitle <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future."
+caption <- "A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
 WIS is decomposed into its components dispersion, over-prediction and under-prediction.
@@
 Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-v4.png")
-```
-
-```{r}
+
+label <- "fig:agg-performance-all"
+```
+
+```{r agg-performance-all, fig.cap=caption, eval = FALSE}
+# knitr::include_graphics("../analysis/plots/aggregate-performance-all-v4.png")
+```
+
+```{r, results = "asis"}
+cat("\\begin{figure}[H]\n", 
+    "\\caption{\\bf{", captiontitle, "}}\n", 
+    caption, "\n",
+    "\\label{", label, "}\n", 
+    "\\end{figure}", sep = "")
+```
+
+```{r}
+captiontitle <- "Two week ahead forecasts and corresponding scores. "
 caption <- "A, C: Visualisation of 50\\% prediction intervals of two week ahead forecasts against the reported values.
@@
 B, D: Visualisation of corresponding WIS."
-```
-
-```{r forecasts-and-truth, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-2.png")
+label <- "fig:forecasts-and-truth"
+```
+
+```{r forecasts-and-truth, fig.cap=caption, eval = FALSE}
+# knitr::include_graphics("../analysis/plots/figure-forecasts-2.png")
+```
+
+```{r, results = "asis"}
+cat("\\begin{figure}[H]\n", 
+    "\\caption{\\bf{", captiontitle, "}}\n", 
+    caption, "\n",
+    "\\label{", label, "}\n", 
+    "\\end{figure}", sep = "")
 ```
@@
 
-For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure \@ref(fig:performance-locations-rel)A).
-For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \@ref(tab:score-table-2)).
-Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Figure \@ref(fig:distribution-scores)).
-Overall, low variance in forecast performance was closely linked with good mean performance (Figures \@ref(fig:agg-performance-all)H and and \@ref(fig:agg-performance-all)A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores)), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
+For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Fig \ref{fig:agg-performance-all}A) and locations (Fig \nameref{fig:performance-locations-rel}A).
+For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (\nameref{tab:score-table-2} Table).
+Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Fig \ref{fig:distribution-scores}).
+Overall, low variance in forecast performance was closely linked with good mean performance (Figs \ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
+The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Fig \ref{fig:distribution-scores}), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
 WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
@@
 To varying degrees, all forecasts exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened.
-For example, all forecasts failed to predict the change in trend from increase to decrease that happened in November in Germany and severely overshot reported cases (Figure \@ref(fig:forecasts-and-truth)A).
+For example, all forecasts failed to predict the change in trend from increase to decrease that happened in November in Germany and severely overshot reported cases (Fig \ref{fig:forecasts-and-truth}A).
 This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past of observations.
@@
 All forecasting approaches, including the Hub ensemble, were overconfident, i.e.
-they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
+they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figs \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
 Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts.
-This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \@ref(fig:agg-performance-all)E) and only showed a small increase in uncertainty across forecast horizons.
-The crowd forecasts prediction intervals were also noticeably narrower than the default baseline shown to forecasters in the application (see Figure \@ref(fig:compare-forecasters)).
-
-In spite of good performance in terms of the absolute error (Figure \@ref(fig:agg-performance-all)G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Figure \@ref(fig:agg-performance-all)C,D and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
-Despite worse performance in terms of absolute error (Figure \@ref(fig:agg-performance-all)G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
+This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Fig \ref{fig:agg-performance-all}E) and only showed a small increase in uncertainty across forecast horizons.
+The crowd forecasts prediction intervals were also noticeably narrower than the default baseline shown to forecasters in the application (see \nameref{fig:compare-forecasters}).
+
+In spite of good performance in terms of the absolute error (Fig \ref{fig:agg-performance-all}G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Fig \ref{fig:agg-performance-all}C, D as well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
+Despite worse performance in terms of absolute error (Fig \ref{fig:agg-performance-all}G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
 The crowd forecasts, on the other hand, showed a smaller bias than the renewal model, but were overconfident.
@@
 The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons.
-The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \@ref(fig:agg-performance-all)F).
-Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \@ref(fig:agg-performance-all)A and \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
-
-Generally, trends in overall performance were broadly similar across locations (Figures \@ref(fig:performance-locations) and \@ref(fig:performance-locations-rel)).
+The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Fig \ref{fig:agg-performance-all}F).
+Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figs \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
+
+Generally, trends in overall performance were broadly similar across locations (Figs \nameref{fig:performance-locations} and \nameref{fig:performance-locations-rel}).
 Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
-However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \@ref(fig:performance-locations-rel)A, \@ref(fig:performance-locations-rel)G, \@ref(fig:agg-performance-all-Germany), \@ref(fig:agg-performance-all-Poland)).
+However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figs \nameref{fig:performance-locations-rel}A, \nameref{fig:performance-locations-rel}G, \nameref{fig:agg-performance-all-Germany}, \nameref{fig:agg-performance-all-Poland}).
 
@@
 
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B).
+For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figs \ref{fig:agg-performance-all}B and \nameref{fig:performance-locations}B).
 Relative WIS values for the models two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1 (Hub ensemble) and 1.79 (renewal model).
-The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B), and also better than the convolution model three and four weeks ahead.
+The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figs \ref{fig:agg-performance-all}B and \nameref{fig:performance-locations}B), and also better than the convolution model three and four weeks ahead.
 Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate $R_t$ trace from deaths, does not use the available information efficiently.
-The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \@ref(fig:agg-performance-all)B, Table \@ref(tab:score-table-4)).
+The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Fig \ref{fig:agg-performance-all}B, \nameref{tab:score-table-4}).
 
@@
 The Hub ensemble had the greatest coverage, with empirical coverage of the 50% and 90% prediction intervals exceeding 50%, and 90%, respectively, across all forecast horizons.
-Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
+Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figs \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
 As for cases, the crowd forecast tended to have the narrowest prediction intervals and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
@@
 
-For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \@ref(fig:agg-performance-all)F.
+For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict (see Fig \ref{fig:agg-performance-all}F).
 The convolution model had a strong tendency to under-predict, with the magnitude of under-prediction steadily decreasing for longer forecast horizons.
 The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction.
-For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \@ref(fig:agg-performance-all)A, \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2), \@ref(tab:score-table-4)).
-
-```{r}
+For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figs \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
+
+```{r}
+captiontitle <- "Distribution of scores. "
 caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
@@
 Black squares indicate median and black circles mean scores."
-```
-
-```{r distribution-scores, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-2.png")
-```
-
-```{r}
-caption <- "Visualisation of relative aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
-“Hub-ensemble” \textit{excludes} all our models, Hub-ensemble-all \textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
+label <- "fig:distribution-scores"
+```
+
+```{r distribution-scores, fig.cap=caption, eval = FALSE}
+# knitr::include_graphics("../analysis/plots/distribution_scores_wis-2.png")
+```
+
+```{r, results = "asis"}
+cat("\\begin{figure}[H]\n", 
+    "\\caption{\\bf{", captiontitle, "}}\n", 
+    caption, "\n",
+    "\\label{", label, "}\n", 
+    "\\end{figure}", sep = "")
+```
+
+```{r}
+captiontitle <- "Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble."
+caption <- "“Hub-ensemble” \\textit{excludes} all our models, Hub-ensemble-all \\textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
 A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
@@
 Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
+label <- "fig:agg-performance-ensemble-rel"
 ```
@@
 ```{r agg-performance-ensemble-rel, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-v4.png")
-```
-
-## Contribution to the Forecast Hub {#contributions-hub}
+# knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-v4.png")
+```
+
+```{r, results = "asis"}
+cat("\\begin{figure}[H]\n", 
+    "\\caption{\\bf{", captiontitle, "}}\n", 
+    caption, "\n",
+    "\\label{", label, "}\n", 
+    "\\end{figure}", sep = "")
+```
+
+## Contribution to the Forecast Hub
+\label{contributions-hub}
 
@@
 Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
-An overview of all models and ensemble versions is shown in Table \@ref(tab:table-ensemble-versions) in the SI.
+An overview of all models and ensemble versions is shown in \nameref{tab:table-ensemble-versions} in the SI.
 
 For cases, our contributions (compared to the Hub ensemble without our contributions) consistently improved performance across all forecasting horizons (rel.
-WIS 0.9 two weeks ahead, Table \@ref(tab:score-table-ensemble-2)).
+WIS 0.9 two weeks ahead, see \nameref{tab:score-table-ensemble-2} Table).
 Contributions from the crowd forecasts alone also improved performance of the Hub ensemble across all forecast horizons, while contributions from the renewal model had a negative effect for longer horizons (rel.
@@
 The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model have improved performance (Table \@ref(tab:score-table-ensemble-4)).
+Only for predictions four weeks ahead would removing the renewal model have improved performance (\nameref{tab:score-table-ensemble-4}).
 The realised ensemble performed comparably to the crowd forecasts for predictions one to two weeks ahead, and worse for greater forecast horizons.
@@
 For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel.
-WIS of the Hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \@ref(tab:score-table-ensemble-2) and \@ref(tab:score-table-ensemble-4)).
+WIS of the Hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, \nameref{tab:score-table-ensemble-2} and \nameref{tab:score-table-ensemble-4}s).
 Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons).
-This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \@ref(fig:agg-performance-all)) and especially worse for longer horizons.
+This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Fig \ref{fig:agg-performance-all}) and especially worse for longer horizons.
 
@@
 <!-- In general, the median ensemble tended to perform slightly better than the mean ensemble - needs more analysis -->
-General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \@ref(fig:agg-performance-ensemble-rel)B and \@ref(fig:agg-performance-ensemble-mean)B).
+General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figs \ref{fig:agg-performance-ensemble-rel}B and \nameref{fig:agg-performance-ensemble-mean}B).
 This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far.
@@
 This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data).
-The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \@ref(fig:forecasts-and-truth)A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting which have less of an influence on weekly reporting.
+The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Fig \ref{fig:forecasts-and-truth}A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting which have less of an influence on weekly reporting.
 
@@
 
-**Acknowledgements**
-
-NIB received funding from the Health Protection Research Unit (grant code NIHR200908, https://www.nihr.ac.uk/).
-SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/).
-The work of JB was supported by the Helmholtz Foundation (https://www.helmholtz.de/) via the SIMCARD Information and Data Science Pilot Project.
-This research was partly funded by the National Institute for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 & 16/136/46) using UK aid from the UK Government to support global health research.
-The views expressed in this publication are those of the author(s) and not necessarily those of the NIHR or the UK Department of Health and Social Care.
-BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859, https://www.gatesfoundation.org/).
-EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908, https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688, https://ec.europa.eu/programmes/horizon2020/).
-AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/), and the Academy of Medical Sciences (https://acmedsci.ac.uk/).
-SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/), and the NIHR (NIHR200908, https://www.nihr.ac.uk/).
+\section*{Acknowledgments}
 
@@
 
-We would also like to acknowledge (in a randomised order) the members of Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group at the the London School of Hygiene & Tropical Medicine: Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie Diamond, Katherine E.
-Atkins, Rein M G J Houben, Jiayao Lei, Rachel Lowe, David Simons, Sophie R Meakin, Nicholas G.
-Davies, Timothy W Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly, Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas, Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson, Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun, Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche, James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday, Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael Pung, Anna M Foss.
-
 \clearpage
@@
 \beginsupplement
-
-# (APPENDIX) Supplementary information {-}
-
-# Supplementary information
-
-## Scoring metrics used
-
-```{r scoring-metrics}
-wis <- list(
-  Metric = "WIS (Weighted) interval score", 
-  `Explanation` = r"(The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
-It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
-The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction.
-For a single interval, the score is computed as
-  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
-  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e.
-the lower and upper bound of a single prediction interval.
-For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
-  $$WIS = \frac{1}{K + 0.5} \cdot \left( w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y) \right), $$
-  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
-
-Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.)", 
-  `Caveats` = "The wis is based on measures of absolute error. When averaging across multiple targets, it will therefore be dominated by targets with higher absolute values.",
-  `References` = ""
-)
-
-interval_coverage <- list(
-  `Metric` = "Interval coverage", 
-  `Explanation` = r"(Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
-Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
-we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.)",
-  `Caveats` = "",
-  `References` = ""
-)
-
-bias <- list(
-  `Metric` = "Bias", 
-  `Explanation` = r"((Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict.
-Values are between -1 and 1 and 0 ideally.
-For continuous forecasts, bias is given as
-$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
-where $F$ is the CDF of the predictive distribution and $y$ is the observed value.
-
-For quantile forecasts, $F(y)$ is replaced by a quantile rank.
-The appropriate quantile rank is determined by whether the median forecast is below  or above the true value.
-We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.
-
-In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
-It is therefore a more robust measurement.)",
-  `Caveats` = "",
-  `References` = ""
-)
-
-data <- rbind(as.data.frame(wis), 
-              as.data.frame(interval_coverage),
-              as.data.frame(bias))
-
-data[, 1:2] %>%
-  kableExtra::kbl(format = "latex", booktabs = TRUE, 
-                  escape = FALSE,
-                  caption = "Overview of the scoring metrics used.",
-                  longtable = TRUE,
-                  linesep = c('\\addlinespace \\addlinespace')) %>%
-  kableExtra::column_spec(1, width = "2.5cm") %>%
-  kableExtra::column_spec(2, width = "13.0cm") %>%
-  kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))
-
-```
-
-\clearpage
-
-## The crowdforecasting app
-
-```{r}
-caption <- "Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021). "
-```
-
-```{r screenshot, fig.cap=caption}
-knitr::include_graphics("../crowd-forecast/Screenshot-forecasting-app.png")
-```
-
-\clearpage
-
-## Further details on the semi-mechanistic forecasting models
-
-### Renewal equation model
-
-The model was initialised prior to the first observed data point by assuming constant exponential growth for the mean of assumed delays from infection to case report.
-
-\begin{align}
-  I_{t} &= I_0 \exp  \left(r t \right)  \\
-  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
-  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
-\end{align}
-
-Where $I_{obs}$ and $r_{obs}$ are estimated from the first week of observed data.
-For the time window of the observed data infections were then modelled by weighting previous infections by the generation time and scaling by the instantaneous reproduction number.
-These infections were then convolved to cases by date ($O_t$) and cases by date of report ($D_t$) using log-normal delay distributions.
-This model can be defined mathematically as follows,
-
-\begin{align}
-  \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
-  I_t &= R_t \sum_{\tau = 1}^{15} w(\tau | \mu_{w}, \sigma_{w}) I_{t - \tau} \\
-  O_t &= \sum_{\tau = 0}^{15} \xi_{O}(\tau | \mu_{\xi_{O}}, \sigma_{\xi_{O}}) I_{t-\tau} \\
-  D_t &= \alpha \sum_{\tau = 0}^{15} \xi_{D}(\tau | \mu_{\xi_{D}}, \sigma_{\xi_{D}}) O_{t-\tau} \\ 
-  C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
-\end{align}
-
-Where,
-\begin{align}
-     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
-    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
-    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
-\end{align}
-
-This model used the following priors for cases,
-
-\begin{align}
-     R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
-    \mu_w &\sim \mathcal{N}(3.6, 0.7) \\
-    \sigma_w &\sim \mathcal{N}(3.1, 0.8) \\
-    \mu_{\xi_{O}} &\sim \mathcal{N}(1.62, 0.064) \\
-    \sigma_{\xi_{O}} &\sim \mathcal{N}(0.418, 0.069) \\
-    \mu_{\xi_{D}} &\sim \mathcal{N}(0.614, 0.066) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(1.51, 0.048) \\
-    \alpha &\sim \mathcal{N}(0.25, 0.05) \\
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-and updated the reporting process as follows when forecasting deaths,
-
-\begin{align}
-    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
-    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
-\end{align}
-
-$\alpha$, $\mu$, $\sigma$, and $\phi$ were truncated to be greater than 0 and with $\xi$, and $w$ normalised to sum to 1.
-
-The prior for the generation time was sourced from [@generationinterval] but refit using a log-normal incubation period with a mean of 5.2 days (SD 1.1) and SD of 1.52 days (SD 1.1) with this incubation period also being used as a prior [@incubationperiod] for $\xi_{O}$.
-This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
-We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1% or 1769 samples of the available data  [@kraemer2020epidemiological; @covidregionaldata] and combining the posteriors for the mean and standard deviation of the log-normal distribution [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation2020; @EvaluatingUseReproduction; @rstan].
-
-$GP_t$ is an approximate Hilbert space Gaussian process as defined in [@approxGP] using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20% of the number of days used in fitting).
-The length scale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
-The magnitude of the Gaussian process was assumed to be normally distributed centred at 0 with a standard deviation of 0.1.
-
-From the forecast time horizon ($T$) and onwards the last value of the Gaussian process was used (hence $R_t$ was assumed to be fixed) and latent infections were adjusted to account for the proportion of the population that was susceptible to infection as follows,
-
-\begin{equation}
-    I_t = (N - I^c_{t-1}) \left(1 - \exp \left(\frac{-I'_t}{N - I^c_{T}}\right)\right),
-\end{equation}
-
-where $I^c_t = \sum_{s< t} I_s$ are cumulative infections by $t-1$ and $I'_t$ are the unadjusted infections defined above.
-This adjustment is based on that implemented in the `epidemia` R package [@epidemia; @bhattSemiMechanisticBayesianModeling].
-
-#### Convolution model
-
-The convolution model shares the same observation model as the renewal model but rather than assuming that an observation is predicted by itself using the renewal equation instead assumes that it is predicted entirely by another observation after some parametric delay.
-It can be defined mathematically as follows,
-
-\begin{equation} 
-    D_{t} \sim \mathrm{NB}\left(\omega_{(t \mod 7)} \alpha \sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) C_{t-\tau},  \phi \right)
-\end{equation}
-
-with the following priors,
-
-\begin{align}
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \alpha &\sim \mathcal{N}(0.01, 0.02) \\
-    \xi &\sim \mathcal{LN}(\mu, \sigma) \\
-    \mu &\sim \mathcal{N}(2.5, 0.5) \\
-\sigma &\sim \mathcal{N}(0.47, 0.2) \\
-\phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-with $\alpha$, $\mu$, $\sigma$, and $\phi$ truncated to be greater than 0 and with $\xi$ normalised such that $\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1$.
-
-### Model fitting
-
-Both models were implemented using the `EpiNow2` R package (version 1.3.3) [@epinow2].
-Each forecast target was fitted independently for each model using Markov-chain Monte Carlo (MCMC) in stan [@rstan].
-A minimum of 4 chains were used with a warmup of 250 samples for the renewal equation-based model and 1000 samples for the convolution model.
-2000 samples total post warmup were used for the renewal equation model and 4000 samples for the convolution model.
-Different settings were chosen for each model to optimise compute time contingent on convergence.
-Convergence was assessed using the R hat diagnostic [@rstan].
-For the convolution model forecast the case forecast from the renewal equation model was used in place of observed cases beyond the forecast horizon using 1000 posterior samples.
-12 weeks of data was used for both models though only 3 weeks of data were included in the likelihood for the convolution model.
-
-\clearpage
 
@@
 }
-
-```
-
-## Tables with results of the forecast evaluation
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
+```
+
+\section*{Supporting information}
+
+\paragraph*{S1 Table.}
+\label{tab:scoring-metrics}
+\textbf{Overview of the scoring metrics used.}
+
+\paragraph*{S1 Text.}
+\label{txt:details-models}
+\textbf{Further details on the semi-mechanistic forecasting models.}
+
+\paragraph*{S1 Fig.}
+\label{fig:screenshot}
+\textbf{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).}
+
+\paragraph*{S2} \textbf{Table.}
+\label{tab:score-table-2}
+\textbf{Scores for one and two week ahead forecasts.} Scores are cut to three significant digits and rounded).
 Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
@@
 Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-2}
-table <- readRDS("../analysis/plots/table_scores_2_ahead.rds")
-add_caption(table, caption, label = "tab:score-table-2")
-```
-
-```{r}
+50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.
+
+\paragraph*{S3 Table.}
+\label{tab:score-table-4}
+\textbf{Scores for three and four weeks ahead forecasts.} 
+Scores are cut to three significant digits and rounded).
+Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
+Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
+the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
+WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
+Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
+Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
+50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.
+
+```{r}
+captiontitle <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany."
+caption <- "A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
+WIS is decomposed into its components dispersion, over-prediction and under-prediction.
+C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
+D: Empirical coverage of the 90\\% prediction intervals.
+E: Dispersion (same as in panel A, B).
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
+F: Bias, i.e.
+general (relative) tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Absolute error of the median forecast (lower is better).
+H.
+Standard deviation of all WIS values for different horizons"
+label <- "fig:agg-performance-all-Germany"
+```
+
+```{r agg-performance-all-Germany, fig.cap=caption, eval = FALSE}
+# knitr::include_graphics("../analysis/plots/aggregate-performance-all-Germany-v4.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S2} \\textbf{Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland."
+caption <- "A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
+WIS is decomposed into its components dispersion, over-prediction and under-prediction.
+C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
+D: Empirical coverage of the 90\\% prediction intervals.
+E: Dispersion (same as in panel A, B).
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
+F: Bias, i.e.
+general (relative) tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Absolute error of the median forecast (lower is better).
+H.
+Standard deviation of all WIS values for different horizons"
+label <- "fig:agg-performance-all-Poland"
+```
+
+```{r agg-performance-all-Poland, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/aggregate-performance-all-Poland-v4.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S3} \\textbf{Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Visualisation of aggregate performance metrics across locations."
+caption <- "A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
+WIS is decomposed into its components dispersion, over-prediction and under-prediction.
+C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
+D: Empirical coverage of the 90\\% prediction intervals.
+E: Dispersion (same as in panel A, B).
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
+F: Bias, i.e.
+general (relative) tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Absolute error of the median forecast (lower is better).
+H.
+Standard deviation of WIS values."
+label <- "fig:performance-locations"
+```
+
+```{r performance-locations, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-v4.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S4} \\textbf{Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Visualisation of aggregate performance metrics across locations in relative terms."
+caption <- "A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
+C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals.
+E: Dispersion.
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
+F: Bias, i.e.
+general (relative) tendency to over- orunderpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Absolute error of the median forecast.
+H.
+Standard deviation of WIS values."
+label <- "fig:performance-locations-rel"
+```
+
+```{r performance-locations-rel, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S5} \\textbf{Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Visualisation of daily report data."
+caption <- "The black line represents weekly data divided by seven. Data were last accessed through the German and Polish Forecast Hub on August 21 2021."
+label <- "fig:daily-truth"
+```
+
+```{r daily-truth, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/daily_truth.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S6} \\textbf{Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Visualisation of the absolute difference between the daily report data at the time and the data now."
+caption <- "In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
+Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
+label <- "fig:daily-truth-update"
+```
+
+```{r daily-truth-update, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/daily-data-updates.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S7} \\textbf{Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Visualisation of the relative difference between the weekly report data at the time and the data now."
+caption <- "Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
+Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
+label <- "fig:weekly-truth-update"
+```
+
+```{r weekly-truth-update, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/weekly-data-updates.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S8} \\textbf{Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Visualisation of forecasts and scores for one week ahead forecasts."
+caption <- "A, C: Visualisation of 50\\% prediction intervals of one week ahead forecasts against the reported values.
+Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
+B, D: Visualisation of corresponding WIS."
+label <- "fig:forecasts-and-truth-1"
+```
+
+```{r forecasts-and-truth-1, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/figure-forecasts-1.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S9 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- gsub(x = captiontitle, pattern = "one", replacement = "three")
+caption <- gsub(x = caption, pattern = "one", replacement = "three")
+label <- "fig:forecasts-and-truth-3"
+```
+
+```{r forecasts-and-truth-3, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/figure-forecasts-3.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S10 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- gsub(x = captiontitle, pattern = "one", replacement = "four")
+caption <- gsub(x = caption, pattern = "three", replacement = "four")
+label <- "fig:forecasts-and-truth-4"
+```
+
+```{r forecasts-and-truth-4, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/figure-forecasts-4.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S11 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Distribution of weighted interval scores for one week ahead forecasts"
+caption <- "A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets pooled across locations. B: Distribution of WIS separate by country."
+label <- "fig:distribution-scores-1"
+```
+
+```{r distribution-scores-1, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/distribution_scores_wis-1.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S12 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- gsub(x = captiontitle, pattern = "one", replacement = "three")
+caption <- gsub(x = caption, pattern = "one", replacement = "three")
+label <- gsub(x = caption, pattern = "1", replacement = "3")
+```
+
+```{r distribution-scores-3, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/distribution_scores_wis-3.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S13 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- gsub(x = captiontitle, pattern = "three", replacement = "four")
+caption <- gsub(x = caption, pattern = "three", replacement = "four")
+label <- gsub(x = caption, pattern = "3", replacement = "4")
+```
+
+```{r distribution-scores-4, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/distribution_scores_wis-4.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S14 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Distribution of model ranks (in terms of WIS) for one week ahead forecasts"
+caption <- "A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets, pooled across locations.
+B: Distribution of ranks separate by country."
+label <- "fig:distribution-scores-ranks-1"
+```
+
+```{r distribution-scores-ranks-1, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/distribution_scores_wis-1-ranks.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S15 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- gsub(x = captiontitle, pattern = "one", replacement = "two")
+caption <- gsub(x = caption, pattern = "one", replacement = "two")
+label <- gsub(x = caption, pattern = "1", replacement = "2")
+```
+
+```{r distribution-scores-ranks-2, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/distribution_scores_wis-2-ranks.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S16 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- gsub(x = captiontitle, pattern = "two", replacement = "three")
+caption <- gsub(x = caption, pattern = "two", replacement = "three")
+label <- gsub(x = caption, pattern = "2", replacement = "3")
+```
+
+```{r distribution-scores-ranks-3, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/distribution_scores_wis-3-ranks.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S17 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- gsub(x = captiontitle, pattern = "three", replacement = "four")
+caption <- gsub(x = caption, pattern = "three", replacement = "four")
+label <- gsub(x = caption, pattern = "3", replacement = "4")
+```
+
+```{r distribution-scores-ranks-4, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/distribution_scores_wis-4-ranks.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S18 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Difference in WIS between the Crowd forecast and the Hub ensemble for two week ahead forecasts."
+caption <- "Values below zero mean better performance of the Crowd forecasts."
+label <- "fig:distribution-scores-differences"
+```
+
+```{r distribution-scores-differences, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
+# knitr::include_graphics("../analysis/plots/difference-wis-crowd-ensemble.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S19 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Difference in WIS between the Crowd forecast and the Renewal model for two week ahead forecasts."
+caption <- "Values below zero mean better performance of the Crowd forecasts."
+label <- "fig:distribution-scores-differences-renewal"
+```
+
+```{r distribution-scores-differences-renewal, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
+# knitr::include_graphics("../analysis/plots/difference-wis-crowd-renewal.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S20 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble."
+caption <- "“Hub-ensemble” \\textit{excludes} all our models, Hub-ensemble-all \\textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
+Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
+For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
+A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
+C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble.
+E: Dispersion relative to the dispersion of the Hub ensemble.
+Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
+F: Bias, i.e.
+general (relative) tendency to over- orunderpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Absolute error of the median forecast relative to the Hub ensemble.
+H.
+Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
+label <- "fig:agg-performance-ensemble-mean"
+```
+
+```{r agg-performance-ensemble-mean, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-mean-v4.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S21} \\textbf{Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Scores for one and two week ahead forecasts for the different versions of the median ensemble."
+caption <- 
+  "Scores are cut to three significant digits and rounded.
+Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
+Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
+the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
+WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
+Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
+Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
+50\\% and 90\\%-coverage are the percentage of observed values that fell within the 50\\% and 90\\% prediction intervals of a model."
+label <- "tab:score-table-ensemble-2"
+```
+
+```{r score-table-ensemble-2}
+# table <- readRDS("../analysis/plots/table_median-ensemble_scores_2_ahead.rds")
+# add_caption(table, caption)
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S4} \\textbf{Table.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- gsub(x = captiontitle, pattern = "one and two", replacement = "three and four")
 caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-4}
-table <- readRDS("../analysis/plots/table_scores_4_ahead.rds")
-add_caption(table, caption, label = "tab:score-table-4")
-
-```
-
-\clearpage
-
-## Aggregate performance by location
-
-### Performance in Germany
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
+label <- gsub(x = label, pattern = "2", replacement = "4")
+```
+
+```{r score-table-ensemble-4}
+# table <- readRDS("../analysis/plots/table_median-ensemble_scores_4_ahead.rds")
+# add_caption(table, caption)
+
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S5 Table.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Scores for one and two week ahead forecasts for the different versions of the mean ensemble"
+caption <- 
+  "Scores are cut to three significant digits and rounded.
+Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
+Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
+the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
+WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
+Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
+Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
+50\\% and 90\\%-coverage are the percentage of observed values that fell within the 50\\% and 90\\% prediction intervals of a model."
+label <- "tab:score-table-ensemble-mean-2"
+```
+
+```{r score-table-ensemble-mean-2}
+# table <- readRDS("../analysis/plots/table_mean-ensemble_scores_2_ahead.rds")
+# add_caption(table, caption)
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S6 Table.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- gsub(x = captiontitle, pattern = "one and two", replacement = "three and four")
+caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
+label <- gsub(x = label, pattern = "2", replacement = "4")
+```
+
+```{r score-table-ensemble-mean-4}
+# table <- readRDS("../analysis/plots/table_mean-ensemble_scores_4_ahead.rds")
+# add_caption(table, caption)
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S7 Table.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Visualisation of aggregate performance metrics across forecast horizons (period from December 14th 2020 on)"
+caption <- "From December 14th 2020 on, all models were available.
+In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later.
+This sensitivity analysis shows performance of all models restricted to the period from December 14 2020 until March 1st 2021 where all models were available.
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
@@
 Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all-Germany, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-Germany-v4.png")
-```
-
-### Performance in Poland
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all-Poland, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-Poland-v4.png")
-```
-
-### Performance across locations in absolute terms
-```{r}
-caption <- "Visualisation of aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of WIS values."
-```
-
-```{r performance-locations, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-v4.png")
-```
-
-## Performance across locations in relative terms
-
-```{r}
-caption <- "Visualisation of relative aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals.
-E: Dispersion.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast.
-H.
-Standard deviation of WIS values."
-```
-
-```{r performance-locations-rel, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4.png")
-```
-
-\clearpage
-
-## Visualisation of daily reported cases and deaths
-
-```{r}
-caption <- "Visualisation of daily report data. The black line represents weekly data divided by seven. Data were last accessed through the German and Polish Forecast Hub on August 21 2021."
-```
-
-```{r daily-truth, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/daily_truth.png")
-```
-
-```{r}
-caption <- "Visualisation of the absolute difference between the daily report data at the time and the data now.
-In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
-```
-
-```{r daily-truth-update, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/daily-data-updates.png")
-```
-
-```{r}
-caption <- "Visualisation of the relative difference between the weekly report data at the time and the data now.
-Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
-```
-
-```{r weekly-truth-update, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/weekly-data-updates.png")
-```
-
-\clearpage
-
-## Visualisation of scores and forecasts 1, 3, 4 weeks ahead
-
-```{r}
-caption <- "A, C: Visualisation of 50\\% prediction intervals of one week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS."
-```
-
-```{r forecasts-and-truth-1, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-1.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one", replacement = "three")
-```
-
-```{r forecasts-and-truth-3, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-3.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-```
-
-```{r forecasts-and-truth-4, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/figure-forecasts-4.png")
-```
-
-\clearpage
-
-## Distribution of scores
-
-### Absolute scores
-
-```{r}
-caption <- "A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country."
-```
-
-```{r distribution-scores-1, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-1.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one", replacement = "three")
-```
-
-```{r distribution-scores-3, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-3.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-```
-
-```{r distribution-scores-4, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-4.png")
-```
-
-### Ranks achieved by forecasts
-
-```{r}
-caption <- "A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country."
-```
-
-```{r distribution-scores-ranks-1, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-1-ranks.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one", replacement = "two")
-```
-
-```{r distribution-scores-ranks-2, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-2-ranks.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "two", replacement = "three")
-```
-
-```{r distribution-scores-ranks-3, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-3-ranks.png")
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-```
-
-```{r distribution-scores-ranks-4, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/distribution_scores_wis-4-ranks.png")
-```
-
-```{r distribution-scores-differences, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
-knitr::include_graphics("../analysis/plots/difference-wis-crowd-ensemble.png")
-```
-
-```{r distribution-scores-differences-renewal, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
-knitr::include_graphics("../analysis/plots/difference-wis-crowd-renewal.png")
-```
-
-\newpage
-
-## Comparison of ensembles
-
-### Performance visualisation mean ensemble
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble” \textit{excludes} all our models, Hub-ensemble-all \textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
-Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
-```
-
-```{r agg-performance-ensemble-mean, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-mean-v4.png")
-```
-
-### Tables median ensemble
-
-```{r}
+label <- "fig:agg-performance-all-late"
+```
+
+```{r agg-performance-all-late, fig.cap=caption}
+# knitr::include_graphics("../analysis/plots/aggregate-performance-all-late-period-v4.png")
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S22 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- "Scores for one and two week ahead forecasts (sensitivity analysis)"
 caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
+  "Scores are cut to three significant digits and rounded.
+In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later.
+This table shows performance of all models restricted to the period from December 14 2020 until March 1st 2021 where all models were available.
 Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
@@
 Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-ensemble-2}
-table <- readRDS("../analysis/plots/table_median-ensemble_scores_2_ahead.rds")
-add_caption(table, caption)
-```
-
-```{r}
+50\\% and 90\\%-coverage are the percentage of observed values that fell within the 50\\% and 90\\% prediction intervals of a model."
+label <- "tab:score-table-late-2"
+```
+
+```{r score-table-late-2}
+# table <- readRDS("../analysis/plots/table-late-period_2_ahead.rds")
+# add_caption(table, caption)
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S8} \\textbf{Table.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r}
+captiontitle <- gsub(x = captiontitle, pattern = "one and two", replacement = "three and four")
 caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-ensemble-4}
-table <- readRDS("../analysis/plots/table_median-ensemble_scores_4_ahead.rds")
-add_caption(table, caption)
-
-```
-
-### Tables mean ensemble
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-ensemble-mean-2}
-table <- readRDS("../analysis/plots/table_mean-ensemble_scores_2_ahead.rds")
-add_caption(table, caption)
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-```
-
-```{r score-table-ensemble-mean-4}
-table <- readRDS("../analysis/plots/table_mean-ensemble_scores_4_ahead.rds")
-add_caption(table, caption)
-```
-
-\clearpage
-
-## Sensitivity analysis
-
-In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later.
-This sensitivity shows performance of all models restricted to the period from December 14 2020 until March 1st 2021 where all models were available.
-
-```{r}
-caption <- "Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-```
-
-```{r agg-performance-all-late, fig.cap=caption}
-knitr::include_graphics("../analysis/plots/aggregate-performance-all-late-period-v4.png")
-```
-
-```{r}
-caption <- 
-  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
-```
-
-```{r score-table-late-2}
-table <- readRDS("../analysis/plots/table-late-period_2_ahead.rds")
-add_caption(table, caption)
-```
-
-```{r}
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
+label <- gsub(x = label, pattern = "2", replacement = "4")
 ```
@@
 ```{r score-table-late-4}
-table <- readRDS("../analysis/plots/table-late-period_4_ahead.rds")
-add_caption(table, caption)
-
-```
-
-\clearpage
-
-## Overview of models and forecasters
+# table <- readRDS("../analysis/plots/table-late-period_4_ahead.rds")
+# add_caption(table, caption)
+```
+
+```{r, results = "asis"}
+cat("\\paragraph{S9 Table.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
 
 ```{r table-ensemble-versions}
-
-rbind(
-  list(
-    Name = "Hub-ensemble-realised", 
-    `Explanation` = "Official Forecast Hub median ensemble.
-Created by the Forecast Hub officially under the name 'KITCOVIDhub-median\\_ensemble' and used as the default ensemble.
-Included are our crowd forecasts as well as the renewal model (with one missed submission on December 28 2020, but not the convolution model which was deemed to similar to the renewal model."
-  ),
-  list(
-    Name = "Hub-ensemble-realised-mean", 
-    `Explanation` = "Official Forecast Hub mean ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-mean\\_ensemble'."
-  ),
-  list(Name = "", Explanation = ""),
-
-  list(
-    Name = "Hub-ensemble", 
-    `Explanation` = "Version of the official Hub median ensemble which excludes all our contributions."
-  ),
-  list(
-    Name = "Hub-ensemble-mean", 
-    `Explanation` = "Version of the official Hub mean ensemble which excludes all our contributions."
-  ),
-  list(
-    Name = "Hub-ensemble-with-renewal, 
-    Hub-ensemble-with-renewal-mean", 
-    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Renewal model."
-  ),
-  list(
-    Name = "Hub-ensemble-with-crowd, 
-    Hub-ensemble-with-crowd-mean", 
-    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Crowd forecast."
-  ),
-  list(
-    Name = "Hub-ensemble-with-convolution, 
-    Hub-ensemble-with-convolution-mean", 
-    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Convolution model (which originally was never included in any official Hub ensemble)."
-  ),
-    list(
-    Name = "Hub-ensemble-with-all, 
-    Hub-ensemble-with-all-mean", 
-    `Explanation` = "Versions of the official Hub ensembles which includes all our contributions.
-For cases, this is identical to the official Hub ensembles, but for deaths the convolution model was added."
-  ),
-
-  list(Name = "", Explanation = ""),
-  list(
-    Name = "Crowd forecast", 
-    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'"
-  ),  
-  list(
-    Name = "Renewal model", 
-    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'"
-  ),  
-  list(
-    Name = "Convolution model", 
-    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\\_secondary'"
-  )
-) %>%
-  kableExtra::kbl(format = "latex", booktabs = TRUE, 
-                  escape = FALSE,
-                  caption = "Overview of the models and ensembles used.",
-                  longtable = TRUE,
-                  linesep = c('\\addlinespace \\addlinespace')) %>%
-  kableExtra::column_spec(1, width = "4.5cm") %>%
-  kableExtra::column_spec(2, width = "11.0cm") %>%
-  kableExtra::kable_styling(latex_options = c("striped", "repeat_header")) 
+```
+
+```{r, results = "asis"}
+label <- "tab:table-ensemble-versions"
+captiontitle <- "Overview of the models and ensembles used."
+caption <- ""
+
+cat("\\paragraph{S10 Table.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
 ```
@@
 ```{r num-forecasters, fig.cap="Number of participants who submitted a forecast over time."}
-knitr::include_graphics("../analysis/plots/number-forecasters.png")
+# knitr::include_graphics("../analysis/plots/number-forecasters.png")
+```
+
+```{r, results = "asis"}
+captiontitle <- "Number of participants who submitted a forecast over time."
+caption <- ""
+label <- "fig:num-forecasters"
+cat("\\paragraph{S23 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
 ```
@@
 Note that the renewal model was not included in the ensemble on December 28th 2020."}
-knitr::include_graphics("../analysis/plots/ensemble-members.png")
-```
+# knitr::include_graphics("../analysis/plots/ensemble-members.png")
+```
+
+```{r, results = "asis"}
+captiontitle <- "Number of member models in the official Hub ensemble"
+caption <- "This includes our crowd forecasts and the renewal model. Note that the renewal model was not included in the ensemble on December 28th 2020."
+label <- "fig:num-ensemble-members"
+cat("\\paragraph{S24 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+```{r compare-forecasters, fig.cap="Crowd forecasts and baseline shown in the application for a two week horizon.
+Shown are the median, as well as the 50\\% and 90\\% prediction intervals (in order of decreasing opacity).
+For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons)."}
+# knitr::include_graphics("../analysis/plots/comparison-forecast-interals.png")
+```
+
+```{r, results = "asis"}
+captiontitle <- "Crowd forecasts and baseline shown in the application for a two week horizon."
+caption <- "Shown are the median, as well as the 50\\% and 90\\% prediction intervals (in order of decreasing opacity).
+For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons)."
+label <- "fig:compare-forecasters"
+cat("\\paragraph{S25 Fig.}\n", 
+    "\\label{", label, "}\n", 
+    "\\textbf{", captiontitle, "} ", caption, 
+    sep = "")
+```
+
+\paragraph*{S1 Acknoweledgmenents.}
+\textbf{Members of the CMMID COVID-19 working group}
 
@@
 
-## Comparison of crowd forecasts and application baseline
-
-```{r compare-forecasters, fig.cap="Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the 90\\% and 50\\% prediction intervals as well as the median (in order of increasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons)."}
-knitr::include_graphics("../analysis/plots/comparison-forecast-interals.png")
-```
+\section*{References}

### 2022-08-20 manuscript/manuscript.Rmd
small manuscript revisions

@@
 These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, @forsal.plRozbieznosciStatystykachKoronawirusa2020), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, @aerzteblattSARSCoV2DiagnostikRKIPasst2020).
-The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figs \nameref{fig:daily-truth-update} and \nameref{fig:weekly-truth-update}).
+The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see \nameref{fig:daily-truth-update} and \nameref{fig:weekly-truth-update} Figs).
 
@@
 To make a forecast in the application participants could select a predictive distribution (with the default being log-normal) to represent the probability that the forecasted quantity took certain values.
-Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in \nameref{fig:screenshot} in the SI).
+Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in \nameref{fig:screenshot}).
 The default shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.
 as $\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )$).
-A comparison of the crowd forecasts against the default baseline shown in the application is displayed in \nameref{fig:compare-forecasters} in the Appendix.
+A comparison of the crowd forecasts against the default baseline shown in the application is displayed in \nameref{fig:compare-forecasters}.
 Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  @ourworldindataCOVID19DataExplorer2020.
@@
 We used two Bayesian semi-mechanistic models from the `EpiNow2` R package (version 1.3.3) as our model-based forecasts [@epinow2].
-The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths (see details in \nameref{txt:details-models} in the SI).
+The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths (see details in \nameref{txt:details-models}).
 It estimated the effective reproduction number $R_t$ (the average number of people each person infected at time t is expected to infect in turn) and modelled future infections as a weighted sum of past infection multiplied by $R_t$.
@@
 
-The second model (“convolution model”, see details in SI) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses).
+The second model (“convolution model”, see details in \nameref{txt:details-models}) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses).
 The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model.
@@
 To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available.
-To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see \nameref{fig:agg-performance-all-late} and \nameref{tab:score-table-late-2} and \nameref{tab:score-table-late-4}s in the SI).
+To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see \nameref{fig:agg-performance-all-late} and \nameref{tab:score-table-late-2} and \nameref{tab:score-table-late-4}s).
 Results remained broadly unchanged.
@@
 how many observed values fall inside all 50% prediction intervals).
-Scoring metrics are explained in more detail in \nameref{tab:scoring-metrics} in the SI.
+Scoring metrics are explained in more detail in \nameref{tab:scoring-metrics}.
 All scores were calculated using the `scoringutils` R package [@scoringutils].
@@
 At all stages of the evaluation our forecasts were compared to the median ensemble of all *other* models submitted to the German and Polish Forecast Hub ("Hub ensemble").
-This "Hub ensemble" was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see \nameref{tab:table-ensemble-versions} and \nameref{fig:num-ensemble-members} in the SI).
+This "Hub ensemble" was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see \nameref{tab:table-ensemble-versions} and \nameref{fig:num-ensemble-members}).
 What we call "Hub ensemble" in this article therefore differs from the "official Hub ensemble" (here called "hub-ensemble-realised") which included crowd forecasts as well as renewal model forecasts.
@@
 
-For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Fig \ref{fig:agg-performance-all}A) and locations (Fig \nameref{fig:performance-locations-rel}A).
+For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Fig \ref{fig:agg-performance-all}A) and locations (\nameref{fig:performance-locations-rel}A Fig).
 For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (\nameref{tab:score-table-2} Table).
 Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Fig \ref{fig:distribution-scores}).
-Overall, low variance in forecast performance was closely linked with good mean performance (Figs \ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
+Overall, low variance in forecast performance was closely linked with good mean performance (Fig \ref{fig:agg-performance-all}H and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
 The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Fig \ref{fig:distribution-scores}), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
@@
 All forecasting approaches, including the Hub ensemble, were overconfident, i.e.
-they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figs \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
+they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Fig \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
 Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts.
@@
 
-In spite of good performance in terms of the absolute error (Fig \ref{fig:agg-performance-all}G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Fig \ref{fig:agg-performance-all}C, D as well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
+In spite of good performance in terms of the absolute error (Fig \ref{fig:agg-performance-all}G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Fig \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D as well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
 Despite worse performance in terms of absolute error (Fig \ref{fig:agg-performance-all}G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
@@
 The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Fig \ref{fig:agg-performance-all}F).
-Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figs \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
-
-Generally, trends in overall performance were broadly similar across locations (Figs \nameref{fig:performance-locations} and \nameref{fig:performance-locations-rel}).
+Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Fig \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
+
+Generally, trends in overall performance were broadly similar across locations (\nameref{fig:performance-locations} and \nameref{fig:performance-locations-rel} Figs).
 Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
-However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figs \nameref{fig:performance-locations-rel}A, \nameref{fig:performance-locations-rel}G, \nameref{fig:agg-performance-all-Germany}, \nameref{fig:agg-performance-all-Poland}).
+However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (\nameref{fig:performance-locations-rel}A, \nameref{fig:performance-locations-rel}G, \nameref{fig:agg-performance-all-Germany} and \nameref{fig:agg-performance-all-Poland} Figs).
 
@@
 The Hub ensemble had the greatest coverage, with empirical coverage of the 50% and 90% prediction intervals exceeding 50%, and 90%, respectively, across all forecast horizons.
-Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figs \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
+Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Fig \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
 As for cases, the crowd forecast tended to have the narrowest prediction intervals and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
@@
 The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction.
-For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figs \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
+For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Fig \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
 
@@
 Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
-An overview of all models and ensemble versions is shown in \nameref{tab:table-ensemble-versions} in the SI.
+An overview of all models and ensemble versions is shown in \nameref{tab:table-ensemble-versions}.
 
@@
 Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile to further develop and explore.
+
+\clearpage
+
+\section*{References}
+::: {#refs}
+:::
 
@@
 
-\paragraph*{S1 Acknoweledgmenents.}
+\paragraph*{S1 Acknowledgmenents.}
 \textbf{Members of the CMMID COVID-19 working group}
-
-\clearpage
-
-\section*{References}

### 2022-08-20 manuscript/manuscript.tex
small manuscript revisions

@@
 \newcommand{\getAff}[1]{
-  \getIndex{#1}{London School of Hygiene \& Tropical Medicine,Karlsruhe
-Institute of Technology Institute of Economic Theory and Statistics,Max
-Planck Institute for Multidisciplinary Sciences,UK Health Security
-Agency,Imperial College London}
+  \getIndex{#1}{London School of Hygiene \& Tropical
+Medicine,CMMID,Karlsruhe Institute of Technology Institute of Economic
+Theory and Statistics,Max Planck Institute for Multidisciplinary
+Sciences,UK Health Security Agency,Imperial College London}
 }
@@
 Nikos I. Bosse\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\textsuperscript{*},
+Tropical Medicine}, \getAff{CMMID}}\textsuperscript{*},
 Sam Abbott\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
+Medicine}, \getAff{CMMID}},
 Johannes Bracher\textsuperscript{\getAff{Karlsruhe Institute of
@@
 Billy J. Quilty\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
+Tropical Medicine}, \getAff{CMMID}},
 Mark Jit\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
+Medicine}, \getAff{CMMID}},
 Centre for the Mathematical Modelling of Infectious Diseases COVID-19
 Working Group\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
+Tropical Medicine}, \getAff{CMMID}},
 Edwin van Leeuwen\textsuperscript{\getAff{UK Health Security
@@
 Sebastian Funk\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\\
+Tropical Medicine}, \getAff{CMMID}}\\
 \bigskip
-\textbf{\getAff{London School of Hygiene \& Tropical Medicine}}London
-School of Hygiene \& Tropical Medicine, Keppel Street, London WC1E7HT,
-United Kingdom\\
+\textbf{\getAff{London School of Hygiene \& Tropical
+Medicine}}Department of Infectious Disease Epidemiology, London School
+of Hygiene \& Tropical Medicine, London, United Kingdom\\
+\textbf{\getAff{CMMID}}Centre for the Mathematical Modelling of
+Infectious Diseases (members of the CMMID COVID-19 working group are
+listed in S1 Acknowledgements), London, United Kingdom\\
 \textbf{\getAff{Karlsruhe Institute of Technology Institute of Economic
-Theory and Statistics}}Karlsruhe Institute of Technology - Institute of
-Economic Theory and Statistics, Post Box 6980, 76049 Karlsruhe,
-Germany\\
+Theory and Statistics}}Institute of Economic Theory and Statistics,
+Karlsruhe Institute of Technology, Karlsruhe, Germany\\
 \textbf{\getAff{Max Planck Institute for Multidisciplinary Sciences}}Max
-Planck Institute for Multidisciplinary Sciences, Am Faßberg 11, 37077
-Göttingen, Germany\\
+Planck Institute for Multidisciplinary Sciences, Göttingen, Germany\\
 \textbf{\getAff{UK Health Security Agency}}UK Health Security Agency,
-London NW9 5EQ, United Kingdom\\
-\textbf{\getAff{Imperial College London}}Imperial College London,
-Norfolk Place, London W2 1PG, United Kingdom\\
+London United Kingdom\\
+\textbf{\getAff{Imperial College London}}MRC Centre for Outbreak
+Analysis and Modelling, Department of Infectious Disease Epidemiology,
+School of Public Health, Imperial College London, London, United
+Kingdom\\
 \bigskip
-* Corresponding author: nikos.bosse@lshtm.ac.uk\\
+* nikos.bosse@lshtm.ac.uk\\
 \end{flushleft}
@@
 
+\hypertarget{ethics-statement}{%
+\subsection{Ethics statement}\label{ethics-statement}}
+
+This study has been approved by the London School of Hygiene \& Tropical
+Medicine Research Ethics Committee (reference number 22290). Consent
+from participants was obtained in written form.
+
+\hypertarget{overview}{%
+\subsection{Overview}\label{overview}}
+
 We created and submitted the following forecasts to the German and
@@
 a notable exception of a data update for October 12 2020 in Germany)
-only affected daily, not weekly data (see Figures
-\ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).
+only affected daily, not weekly data (see
+\nameref{fig:daily-truth-update} and \nameref{fig:weekly-truth-update}
+Figs).
 
@@
 showing their forecast or providing numerical values (see screenshot in
-Figure \ref{fig:screenshot} in the SI). The default shown was a
-repetition of the last known observation with constant uncertainty
-around it computed as the standard deviation of the last four changes in
-weekly log observed forecasts (i.e.~as
+\nameref{fig:screenshot}). The default shown was a repetition of the
+last known observation with constant uncertainty around it computed as
+the standard deviation of the last four changes in weekly log observed
+forecasts (i.e.~as
 \(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
 A comparison of the crowd forecasts against the default baseline shown
-in the application is displayed in Figure \ref{fig:compare-forecasters}
-in the Appendix. Our interface also allowed participants to view past
-observations based on the hub data, as well as their forecasts, on a
-logarithmic scale and presented additional contextual COVID-19 data
-sourced from {[}39{]}. These data included, for example, notifications
-of both test positive COVID-19 cases and COVID-19 linked deaths and the
-number of COVID-19 tests conducted over time. From November 26 2020 on
-we displayed weekly small reports with a visualisation of past forecasts
-and scores on our website, epiforecasts.io.
+in the application is displayed in \nameref{fig:compare-forecasters}.
+Our interface also allowed participants to view past observations based
+on the hub data, as well as their forecasts, on a logarithmic scale and
+presented additional contextual COVID-19 data sourced from {[}39{]}.
+These data included, for example, notifications of both test positive
+COVID-19 cases and COVID-19 linked deaths and the number of COVID-19
+tests conducted over time. From November 26 2020 on we displayed weekly
+small reports with a visualisation of past forecasts and scores on our
+website, epiforecasts.io.
 
@@
 equation {[}41{]} to predict reported cases and deaths (see details in
-the SI). It estimated the effective reproduction number \(R_t\) (the
-average number of people each person infected at time t is expected to
-infect in turn) and modelled future infections as a weighted sum of past
-infection multiplied by \(R_t\). \(R_t\) was assumed to stay constant
-beyond the forecast date, roughly corresponding to continuing the latest
-exponential trend in infections. On the 9th of November we altered the
-date when \(R_t\) was assumed to be constant from two weeks prior to the
-date of the forecast to the forecast date, which we found to yield a
-more stable \(R_t\) estimate. Reported case and death notifications were
-obtained by convolving predicted infections over data-based delay
-distributions {[}40,42--44{]} to model the time between infection and
-report date. The renewal model was used to predict cases as well as
-deaths with forecasts being generated for each target separately. Death
-forecasts from the renewal model were therefore not informed by past
-cases. One submission of the renewal model on December 28th 2020 was
-delayed and therefore not included in the official Forecast hub
-ensemble.
-
-The second model (``convolution model'', see details in SI) was only
-used to forecast deaths and was added later, starting December 7th 2020
-(with the first forecast from December 7th suffering from a software bug
-and therefore disregarded in all further analyses). The convolution
-model was submitted, but never included in the official Forecast hub
-ensemble due to concerns that it could be too similar to the renewal
-model. The convolution model predicted deaths as a fraction of infected
-people who would die with some delay, by using a convolution of reported
-cases with a distribution that described the delay from case report to
-death and a scaling factor (the case-fatality ratio). Both the renewal
-and the convolution model used daily observations and assumed a negative
-binomial observation model with a multiplicative day-of-the-week effect
-{[}40{]}.
+\nameref{txt:details-models}). It estimated the effective reproduction
+number \(R_t\) (the average number of people each person infected at
+time t is expected to infect in turn) and modelled future infections as
+a weighted sum of past infection multiplied by \(R_t\). \(R_t\) was
+assumed to stay constant beyond the forecast date, roughly corresponding
+to continuing the latest exponential trend in infections. On the 9th of
+November we altered the date when \(R_t\) was assumed to be constant
+from two weeks prior to the date of the forecast to the forecast date,
+which we found to yield a more stable \(R_t\) estimate. Reported case
+and death notifications were obtained by convolving predicted infections
+over data-based delay distributions {[}40,42--44{]} to model the time
+between infection and report date. The renewal model was used to predict
+cases as well as deaths with forecasts being generated for each target
+separately. Death forecasts from the renewal model were therefore not
+informed by past cases. One submission of the renewal model on December
+28th 2020 was delayed and therefore not included in the official
+Forecast hub ensemble.
+
+The second model (``convolution model'', see details in
+\nameref{txt:details-models}) was only used to forecast deaths and was
+added later, starting December 7th 2020 (with the first forecast from
+December 7th suffering from a software bug and therefore disregarded in
+all further analyses). The convolution model was submitted, but never
+included in the official Forecast hub ensemble due to concerns that it
+could be too similar to the renewal model. The convolution model
+predicted deaths as a fraction of infected people who would die with
+some delay, by using a convolution of reported cases with a distribution
+that described the delay from case report to death and a scaling factor
+(the case-fatality ratio). Both the renewal and the convolution model
+used daily observations and assumed a negative binomial observation
+model with a multiplicative day-of-the-week effect {[}40{]}.
 
@@
 (including cases) were scored only over the later period for which all
-forecasts were available (see Section \ref{sensitivity-analysis} in the
-SI). Results remained broadly unchanged.
+forecasts were available (see \nameref{fig:agg-performance-all-late} and
+\nameref{tab:score-table-late-2} and \nameref{tab:score-table-late-4}s).
+Results remained broadly unchanged.
 
@@
 interval (e.g.~how many observed values fall inside all 50\% prediction
-intervals). Scoring metrics are explained in more detail in Table
-\ref{tab:scoring-metrics} in the SI. All scores were calculated using
-the \texttt{scoringutils} R package {[}49{]}.
+intervals). Scoring metrics are explained in more detail in
+\nameref{tab:scoring-metrics}. All scores were calculated using the
+\texttt{scoringutils} R package {[}49{]}.
 
@@
 retrospectively computed and excludes all our models, leaving on average
-five ensemble member models (see details in Section
-\ref{contributions-hub}, as well as in Table
-\ref{tab:table-ensemble-versions} and Figure
-\ref{fig:num-ensemble-members} in the SI). What we call ``Hub ensemble''
+five ensemble member models (see \nameref{tab:table-ensemble-versions}
+and \nameref{fig:num-ensemble-members}). What we call ``Hub ensemble''
 in this article therefore differs from the ``official Hub ensemble''
@@
 (WIS, lower values indicate better performance) than both the renewal
-model and the Hub ensemble across all forecast horizons (Figure
-\ref{fig:agg-performance-all}A) and locations (Figure
-\ref{fig:performance-locations-rel}A). For two week ahead forecasts,
-mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts
-and 1.40 for the renewal model (Table \ref{tab:score-table-2}). Across
-all forecasting approaches, locations and forecast horizons, the
-distribution of WIS values was very right-skewed, and average
-performance was heavily influenced by outliers (Figure
-\ref{fig:distribution-scores}). Overall, low variance in forecast
-performance was closely linked with good mean performance (Figures
-\ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A),
+model and the Hub ensemble across all forecast horizons (Fig
+\ref{fig:agg-performance-all}A) and locations
+(\nameref{fig:performance-locations-rel}A Fig). For two week ahead
+forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for
+crowd forecasts and 1.40 for the renewal model
+(\nameref{tab:score-table-2} Table). Across all forecasting approaches,
+locations and forecast horizons, the distribution of WIS values was very
+right-skewed, and average performance was heavily influenced by outliers
+(Fig \ref{fig:distribution-scores}). Overall, low variance in forecast
+performance was closely linked with good mean performance (Fig
+\ref{fig:agg-performance-all}H and \ref{fig:agg-performance-all}A),
 suggesting that the ability to avoid large errors was an important
@@
 forecasts made at a two week forecast horizon, and only 5\% and 38\%
-four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables
-\ref{tab:score-table-2} and \ref{tab:score-table-4}). Despite worse
-performance in terms of absolute error (Figure
-\ref{fig:agg-performance-all}G), the renewal model achieved better
-calibration (comparable to the Hub ensemble), as uncertainty increased
-rapidly across forecast horizons. The crowd forecasts, on the other
-hand, showed a smaller bias than the renewal model, but were
-overconfident.
+four weeks ahead) (Fig \ref{fig:agg-performance-all}C and
+\ref{fig:agg-performance-all}D as well as \nameref{tab:score-table-2}
+and \nameref{tab:score-table-4}s). Despite worse performance in terms of
+absolute error (Fig \ref{fig:agg-performance-all}G), the renewal model
+achieved better calibration (comparable to the Hub ensemble), as
+uncertainty increased rapidly across forecast horizons. The crowd
+forecasts, on the other hand, showed a smaller bias than the renewal
+model, but were overconfident.
 
@@
 tended to over-predict at longer forecast horizons, whereas the Hub
-ensemble showed no systematic bias (Figure
-\ref{fig:agg-performance-all}F). Regardless of a general relative
-tendency to over-predict, all forecasting approaches incurred larger
-absolute penalties from over- than from under-prediction (see
-decomposition of the WIS into absolute penalties for over-prediction,
-under-prediction and dispersion in Figures
-\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
+ensemble showed no systematic bias (Fig \ref{fig:agg-performance-all}F).
+Regardless of a general relative tendency to over-predict, all
+forecasting approaches incurred larger absolute penalties from over-
+than from under-prediction (see decomposition of the WIS into absolute
+penalties for over-prediction, under-prediction and dispersion in Fig
+\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as
+well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
 
 Generally, trends in overall performance were broadly similar across
-locations (Figures \ref{fig:performance-locations} and
-\ref{fig:performance-locations-rel}). Due to the differing population
-sizes and numbers of notifications in Germany and Poland absolute scores
-were difficult to compare directly. However, relative to the Hub
-ensemble, the crowd forecasts performed noticeably better in Germany
-than in Poland and the renewal model better in Poland than in Germany
-(Figures \ref{fig:performance-locations-rel}A,
-\ref{fig:performance-locations-rel}G,
-\ref{fig:agg-performance-all-Germany},
-\ref{fig:agg-performance-all-Poland}).
+locations (\nameref{fig:performance-locations} and
+\nameref{fig:performance-locations-rel} Figs). Due to the differing
+population sizes and numbers of notifications in Germany and Poland
+absolute scores were difficult to compare directly. However, relative to
+the Hub ensemble, the crowd forecasts performed noticeably better in
+Germany than in Poland and the renewal model better in Poland than in
+Germany (\nameref{fig:performance-locations-rel}A,
+\nameref{fig:performance-locations-rel}G,
+\nameref{fig:agg-performance-all-Germany} and
+\nameref{fig:agg-performance-all-Poland} Figs).
 
@@
 approaches was generally lower than that of the Hub ensemble and mostly
-slightly lower than nominal coverage (Figure
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D). As
-for cases, the crowd forecast tended to have the narrowest prediction
-intervals and uncertainty increased most slowly across forecast
-horizons, and the renewal model forecasts generally were widest. The
-convolution model had relatively narrow prediction intervals for short
-forecast horizons, but had rapidly (and non-linearly) increasing
-uncertainty for longer forecast horizons, driven by increasing
-uncertainty in the underlying case forecasts.
+slightly lower than nominal coverage (Fig \ref{fig:agg-performance-all}C
+and \ref{fig:agg-performance-all}D). As for cases, the crowd forecast
+tended to have the narrowest prediction intervals and uncertainty
+increased most slowly across forecast horizons, and the renewal model
+forecasts generally were widest. The convolution model had relatively
+narrow prediction intervals for short forecast horizons, but had rapidly
+(and non-linearly) increasing uncertainty for longer forecast horizons,
+driven by increasing uncertainty in the underlying case forecasts.
 
 For deaths, the ensemble of crowd forecasts had a consistent tendency to
-over-predict \ref{fig:agg-performance-all}F. The convolution model had a
-strong tendency to under-predict, with the magnitude of under-prediction
-steadily decreasing for longer forecast horizons. The renewal model
-(which over-predicted for cases) and the Hub ensemble slightly tended
-towards under-prediction. For deaths, absolute over- and
+over-predict (see Fig \ref{fig:agg-performance-all}F). The convolution
+model had a strong tendency to under-predict, with the magnitude of
+under-prediction steadily decreasing for longer forecast horizons. The
+renewal model (which over-predicted for cases) and the Hub ensemble
+slightly tended towards under-prediction. For deaths, absolute over- and
 under-prediction penalties were more in line with a general relative
-tendency to over- or under-predict than for cases (Figure
-\ref{fig:agg-performance-all}A, \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2}, \ref{tab:score-table-4}).
+tendency to over- or under-predict than for cases (Fig
+\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as
+well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
 
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} \caption{Distribution of scores.
+\caption{\bf{Distribution of scores. }}
 A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
@@
 \begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.
-“Hub-ensemble”    extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
+\caption{\bf{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.}}
+“Hub-ensemble” \textit{excludes} all our models, Hub-ensemble-all \textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
 A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
@@
 one of them (``hub-ensemble-with-X'') were computed retrospectively. An
-overview of all models and ensemble versions is shown in Table
-\ref{tab:table-ensemble-versions} in the SI.
+overview of all models and ensemble versions is shown in
+\nameref{tab:table-ensemble-versions}.
 
@@
 horizons (rel. WIS of the Hub-ensemble-realised 1.01 two weeks ahead,
-1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and
-\ref{tab:score-table-ensemble-4}). Individual contributions from both
-the renewal model and the crowd forecast were largely negative, while a
-version of the Hub ensemble with only the convolution model included
-would have performed consistently better across all forecast horizons
-(with the positive impact increasing for longer horizons). This is
-especially interesting as the convolution model performed consistently
-worse than the pre-existing Hub ensemble (Figure
+1.05 four weeks ahead, \nameref{tab:score-table-ensemble-2} and
+\nameref{tab:score-table-ensemble-4}s). Individual contributions from
+both the renewal model and the crowd forecast were largely negative,
+while a version of the Hub ensemble with only the convolution model
+included would have performed consistently better across all forecast
+horizons (with the positive impact increasing for longer horizons). This
+is especially interesting as the convolution model performed
+consistently worse than the pre-existing Hub ensemble (Fig
 \ref{fig:agg-performance-all}) and especially worse for longer horizons.
@@
 
-\textbf{Acknowledgements}
-
-NIB received funding from the Health Protection Research Unit (grant
-code NIHR200908, https://www.nihr.ac.uk/). SA's work was funded by the
-Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/). The work
-of JB was supported by the Helmholtz Foundation
-(https://www.helmholtz.de/) via the SIMCARD Information and Data Science
-Pilot Project. This research was partly funded by the National Institute
-for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 \&
-16/136/46) using UK aid from the UK Government to support global health
-research. The views expressed in this publication are those of the
-author(s) and not necessarily those of the NIHR or the UK Department of
-Health and Social Care. BJQ is supported in part by a grant from the
-Bill and Melinda Gates Foundation (OPP1139859,
-https://www.gatesfoundation.org/). EvL acknowledges funding by the
-National Institute for Health Research (NIHR) Health Protection Research
-Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908,
-https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research
-and innovation programme - project EpiPose (101003688,
-https://ec.europa.eu/programmes/horizon2020/). AC acknowledges funding
-by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/),
-and the Academy of Medical Sciences (https://acmedsci.ac.uk/). SF's work
-was supported by the Wellcome Trust (grant: 210758/Z/18/Z,
-https://wellcome.org/), and the NIHR (NIHR200908,
-https://www.nihr.ac.uk/).
-
-We thank all forecasters who participated in this study for their
-contribution.
-
-We would also like to acknowledge (in a randomised order) the members of
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group at the the London School of Hygiene \& Tropical Medicine:
-Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie
-Diamond, Katherine E. Atkins, Rein M G J Houben, Jiayao Lei, Rachel
-Lowe, David Simons, Sophie R Meakin, Nicholas G. Davies, Timothy W
-Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly,
-Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas,
-Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia
-Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson,
-Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang
-Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C
-Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun,
-Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche,
-James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday,
-Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan
-Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R
-Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael
-Pung, Anna M Foss.
-
-\clearpage
-
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
-
-\hypertarget{appendix-supplementary-information}{%
-\section*{(APPENDIX) Supplementary
-information}\label{appendix-supplementary-information}}
-\addcontentsline{toc}{section}{(APPENDIX) Supplementary information}
-
-\hypertarget{supplementary-information}{%
-\section{Supplementary information}\label{supplementary-information}}
-
-\hypertarget{scoring-metrics-used}{%
-\subsection{Scoring metrics used}\label{scoring-metrics-used}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{9.3cm}}
-\caption{\label{tab:scoring-metrics}Overview of the scoring metrics used.}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{Overview of the scoring metrics used. \textit{(continued)}}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-WIS (Weighted) interval score & The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
-It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
-The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction.
-For a single interval, the score is computed as
-  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
-  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e.
-the lower and upper bound of a single prediction interval.
-For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
-  $$WIS = \frac{1}{K + 0.5} \cdot \left( w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y) \right), $$
-  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
-
-\cellcolor{gray!6}{Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.}\\
-\addlinespace \addlinespace
-Interval coverage & Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
-Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
-we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.\\
-\addlinespace \addlinespace
-Bias & (Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict. Values are between -1 and 1 and 0 ideally. For continuous forecasts, bias is given as 
-$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
-where $F$ is the CDF of the predictive distribution and $y$ is the observed value.
-
-For quantile forecasts, $F(y)$ is replaced by a quantile rank.
-The appropriate quantile rank is determined by whether the median forecast is below  or above the true value.
-We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.
-
-\cellcolor{gray!6}{In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
-It is therefore a more robust measurement.}\\*
-\end{longtable}
-
-\clearpage
-
-\hypertarget{the-crowdforecasting-app}{%
-\subsection{The crowdforecasting app}\label{the-crowdforecasting-app}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../crowd-forecast/Screenshot-forecasting-app} \caption{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).
-}\label{fig:screenshot}
-\end{figure}
-
-\clearpage
-
-\hypertarget{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}{%
-\subsection{Text S1. Further details on the semi-mechanistic forecasting
-models}\label{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}}
-
-\hypertarget{renewal-equation-model}{%
-\subsubsection{Renewal equation model}\label{renewal-equation-model}}
-
-The model was initialised prior to the first observed data point by
-assuming constant exponential growth for the mean of assumed delays from
-infection to case report.
-
-\begin{align}
-  I_{t} &= I_0 \exp  \left(r t \right)  \\
-  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
-  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
-\end{align}
-
-Where \(I_{obs}\) and \(r_{obs}\) are estimated from the first week of
-observed data. For the time window of the observed data infections were
-then modelled by weighting previous infections by the generation time
-and scaling by the instantaneous reproduction number. These infections
-were then convolved to cases by date (\(O_t\)) and cases by date of
-report (\(D_t\)) using log-normal delay distributions. This model can be
-defined mathematically as follows,
-
-\begin{align}
-  \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
-  I_t &= R_t \sum_{\tau = 1}^{15} w(\tau | \mu_{w}, \sigma_{w}) I_{t - \tau} \\
-  O_t &= \sum_{\tau = 0}^{15} \xi_{O}(\tau | \mu_{\xi_{O}}, \sigma_{\xi_{O}}) I_{t-\tau} \\
-  D_t &= \alpha \sum_{\tau = 0}^{15} \xi_{D}(\tau | \mu_{\xi_{D}}, \sigma_{\xi_{D}}) O_{t-\tau} \\ 
-  C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
-\end{align}
-
-Where, \begin{align}
-     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
-    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
-    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
-\end{align}
-
-This model used the following priors for cases,
-
-\begin{align}
-     R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
-    \mu_w &\sim \mathcal{N}(3.6, 0.7) \\
-    \sigma_w &\sim \mathcal{N}(3.1, 0.8) \\
-    \mu_{\xi_{O}} &\sim \mathcal{N}(1.62, 0.064) \\
-    \sigma_{\xi_{O}} &\sim \mathcal{N}(0.418, 0.069) \\
-    \mu_{\xi_{D}} &\sim \mathcal{N}(0.614, 0.066) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(1.51, 0.048) \\
-    \alpha &\sim \mathcal{N}(0.25, 0.05) \\
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-and updated the reporting process as follows when forecasting deaths,
-
-\begin{align}
-    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
-    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
-\end{align}
-
-\(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) were truncated to be
-greater than 0 and with \(\xi\), and \(w\) normalised to sum to 1.
-
-The prior for the generation time was sourced from {[}51{]} but refit
-using a log-normal incubation period with a mean of 5.2 days (SD 1.1)
-and SD of 1.52 days (SD 1.1) with this incubation period also being used
-as a prior {[}52{]} for \(\xi_{O}\). This resulted in a
-gamma-distributed generation time with mean 3.6 days (standard deviation
-(SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates. We estimated
-the delay between symptom onset and case report or death required to
-convolve latent infections to observations by fitting an integer
-adjusted log-normal distribution to 10 subsampled bootstraps of a public
-linelist for cases in Germany from April 2020 to June 2020 with each
-bootstrap using 1\% or 1769 samples of the available data {[}45,53{]}
-and combining the posteriors for the mean and standard deviation of the
-log-normal distribution {[}40,42,46,54{]}.
-
-\(GP_t\) is an approximate Hilbert space Gaussian process as defined in
-{[}55{]} using a Matern 3/2 kernel using a boundary factor of 1.5 and 17
-basis functions (20\% of the number of days used in fitting). The length
-scale of the Gaussian process was given a log-normal prior with a mean
-of 21 days, and a standard deviation of 7 days truncated to be greater
-than 3 days and less than 60 days. The magnitude of the Gaussian process
-was assumed to be normally distributed centred at 0 with a standard
-deviation of 0.1.
-
-From the forecast time horizon (\(T\)) and onwards the last value of the
-Gaussian process was used (hence \(R_t\) was assumed to be fixed) and
-latent infections were adjusted to account for the proportion of the
-population that was susceptible to infection as follows,
-
-\begin{equation}
-    I_t = (N - I^c_{t-1}) \left(1 - \exp \left(\frac{-I'_t}{N - I^c_{T}}\right)\right),
-\end{equation}
-
-where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\)
-and \(I'_t\) are the unadjusted infections defined above. This
-adjustment is based on that implemented in the \texttt{epidemia} R
-package {[}56,57{]}.
-
-\hypertarget{convolution-model}{%
-\paragraph{Convolution model}\label{convolution-model}}
-
-The convolution model shares the same observation model as the renewal
-model but rather than assuming that an observation is predicted by
-itself using the renewal equation instead assumes that it is predicted
-entirely by another observation after some parametric delay. It can be
-defined mathematically as follows,
-
-\begin{equation} 
-    D_{t} \sim \mathrm{NB}\left(\omega_{(t \mod 7)} \alpha \sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) C_{t-\tau},  \phi \right)
-\end{equation}
-
-with the following priors,
-
-\begin{align}
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \alpha &\sim \mathcal{N}(0.01, 0.02) \\
-    \xi &\sim \mathcal{LN}(\mu, \sigma) \\
-    \mu &\sim \mathcal{N}(2.5, 0.5) \\
-\sigma &\sim \mathcal{N}(0.47, 0.2) \\
-\phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-with \(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) truncated to be
-greater than 0 and with \(\xi\) normalised such that
-\(\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1\).
-
-\hypertarget{model-fitting}{%
-\subsubsection{Model fitting}\label{model-fitting}}
-
-Both models were implemented using the \texttt{EpiNow2} R package
-(version 1.3.3) {[}40{]}. Each forecast target was fitted independently
-for each model using Markov-chain Monte Carlo (MCMC) in stan {[}46{]}. A
-minimum of 4 chains were used with a warmup of 250 samples for the
-renewal equation-based model and 1000 samples for the convolution model.
-2000 samples total post warmup were used for the renewal equation model
-and 4000 samples for the convolution model. Different settings were
-chosen for each model to optimise compute time contingent on
-convergence. Convergence was assessed using the R hat diagnostic
-{[}46{]}. For the convolution model forecast the case forecast from the
-renewal equation model was used in place of observed cases beyond the
-forecast horizon using 1000 posterior samples. 12 weeks of data was used
-for both models though only 3 weeks of data were included in the
-likelihood for the convolution model.
-
-\clearpage
-
-\hypertarget{tables-with-results-of-the-forecast-evaluation}{%
-\subsection{Tables with results of the forecast
-evaluation}\label{tables-with-results-of-the-forecast-evaluation}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 7010 (0.8) & 7480 (0.64) & 2680 (0.73) & 1700 (1.38) & 2630 (0.68) & -0.01 & 10400 (0.82) & 0.55 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 8740 (1) & 11800 (1.01) & 2190 (0.6) & 2720 (2.21) & 3830 (0.99) & 0.18 & 12000 (0.94) & 0.48 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 16200 (0.89) & 16600 (0.76) & 3660 (0.6) & 5930 (1.56) & 6600 (0.78) & -0.01 & 23300 (0.87) & 0.36 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25600 (1.4) & 33800 (1.54) & 5420 (0.88) & 5920 (1.56) & 14200 (1.69) & 0.17 & 34600 (1.29) & 0.43 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 27000 (0.81) & 26200 (0.64) & 4750 (0.52) & 11000 (1.43) & 11200 (0.67) & 0.02 & 39000 (0.83) & 0.14 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 50600 (1.51) & 70000 (1.72) & 10800 (1.18) & 7710 (1) & 32100 (1.93) & 0.13 & 68700 (1.46) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 39200 (0.7) & 38600 (0.52) & 5970 (0.49) & 15600 (1.26) & 17600 (0.56) & 0.07 & 54800 (0.74) & 0.05 & 0.38\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 91700 (1.64) & 135000 (1.83) & 19500 (1.6) & 8990 (0.72) & 63200 (2.02) & 0.09 & 125000 (1.68) & 0.31 & 0.48\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{aggregate-performance-by-location}{%
-\subsection{Aggregate performance by
-location}\label{aggregate-performance-by-location}}
-
-\hypertarget{performance-in-germany}{%
-\subsubsection{Performance in Germany}\label{performance-in-germany}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Germany-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Germany}
-\end{figure}
-
-\hypertarget{performance-in-poland}{%
-\subsubsection{Performance in Poland}\label{performance-in-poland}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Poland-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Poland}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-absolute-terms}{%
-\subsubsection{Performance across locations in absolute
-terms}\label{performance-across-locations-in-absolute-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-v4} \caption{Visualisation of aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-relative-terms}{%
-\subsection{Performance across locations in relative
-terms}\label{performance-across-locations-in-relative-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4} \caption{Visualisation of relative aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals.
-E: Dispersion.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast.
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations-rel}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-daily-reported-cases-and-deaths}{%
-\subsection{Visualisation of daily reported cases and
-deaths}\label{visualisation-of-daily-reported-cases-and-deaths}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily_truth} \caption{Visualisation of daily report data.
-The black line represents weekly data divided by seven.
-Data were last accessed through the German and Polish Forecast Hub on August 21 2021.}\label{fig:daily-truth}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily-data-updates} \caption{Visualisation of the absolute difference between the daily report data at the time and the data now.
-In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:daily-truth-update}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/weekly-data-updates} \caption{Visualisation of the relative difference between the weekly report data at the time and the data now.
-Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:weekly-truth-update}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}{%
-\subsection{Visualisation of scores and forecasts 1, 3, 4 weeks
-ahead}\label{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} \caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} \caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} \caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-4}
-\end{figure}
-
-\clearpage
-
-\hypertarget{distribution-of-scores}{%
-\subsection{Distribution of scores}\label{distribution-of-scores}}
-
-\hypertarget{absolute-scores}{%
-\subsubsection{Absolute scores}\label{absolute-scores}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1} \caption{A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3} \caption{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4} \caption{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-4}
-\end{figure}
-
-\hypertarget{ranks-achieved-by-forecasts}{%
-\subsubsection{Ranks achieved by
-forecasts}\label{ranks-achieved-by-forecasts}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-2}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-4}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} \caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-renewal} \caption{Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences-renewal}
-\end{figure}
-
-\newpage
-
-\hypertarget{comparison-of-ensembles}{%
-\subsection{Comparison of ensembles}\label{comparison-of-ensembles}}
-
-\hypertarget{performance-visualisation-mean-ensemble}{%
-\subsubsection{Performance visualisation mean
-ensemble}\label{performance-visualisation-mean-ensemble}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble”     extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
-Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-mean}
-\end{figure}
-
-\hypertarget{tables-median-ensemble}{%
-\subsubsection{Tables median ensemble}\label{tables-median-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 6970 (0.79) & 8260 (0.71) & 3060 (0.83) & 943 (0.77) & 2970 (0.77) & 0.04 & 10800 (0.85) & 0.55 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 7820 (0.89) & 9630 (0.82) & 3270 (0.89) & 1210 (0.98) & 3330 (0.86) & -0.02 & 12000 (0.94) & 0.48 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 7960 (0.91) & 10300 (0.88) & 3190 (0.87) & 1020 (0.83) & 3760 (0.97) & 0.04 & 12100 (0.95) & 0.57 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 16400 (0.9) & 19600 (0.89) & 5350 (0.87) & 3290 (0.87) & 7730 (0.92) & 0.02 & 24200 (0.9) & 0.43 & 0.69\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 16900 (0.92) & 19600 (0.89) & 5230 (0.85) & 4310 (1.13) & 7370 (0.88) & 0.00 & 24600 (0.92) & 0.38 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 17500 (0.96) & 21400 (0.98) & 5830 (0.95) & 2880 (0.76) & 8770 (1.04) & 0.00 & 25500 (0.95) & 0.45 & 0.71\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 235 (0.95) & 332 (0.98) & 88.6 (0.96) & 90.4 (0.79) & 55.5 (1.33) & -0.01 & 323 (0.97) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 234 (0.94) & 331 (0.98) & 85.2 (0.92) & 98.1 (0.85) & 50.2 (1.21) & -0.05 & 329 (0.99) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 234 (0.94) & 329 (0.97) & 90.7 (0.98) & 118 (1.03) & 25.3 (0.61) & -0.08 & 333 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 239 (0.96) & 337 (1) & 85.2 (0.92) & 99.6 (0.87) & 54.2 (1.3) & -0.03 & 322 (0.96) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 246 (0.99) & 342 (1.01) & 91.5 (0.99) & 106 (0.92) & 48.6 (1.17) & -0.06 & 342 (1.02) & 0.67 & 0.92\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 296 (1.01) & 398 (1.03) & 125 (0.95) & 91 (0.84) & 80.2 (1.55) & 0.05 & 486 (1.13) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 303 (1.04) & 423 (1.1) & 115 (0.87) & 122 (1.13) & 66.1 (1.27) & 0.00 & 483 (1.13) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 270 (0.92) & 385 (1) & 121 (0.92) & 119 (1.1) & 29.9 (0.58) & -0.04 & 403 (0.94) & 0.58 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 303 (1.04) & 392 (1.02) & 122 (0.92) & 106 (0.98) & 74.6 (1.44) & 0.03 & 499 (1.16) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 296 (1.01) & 397 (1.03) & 128 (0.97) & 97.1 (0.9) & 71.2 (1.37) & -0.01 & 462 (1.08) & 0.67 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 30800 (0.92) & 38600 (0.95) & 7910 (0.87) & 6890 (0.9) & 16000 (0.96) & 0.03 & 44200 (0.94) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 30800 (0.92) & 34100 (0.84) & 7500 (0.82) & 8960 (1.17) & 14300 (0.86) & 0.02 & 44100 (0.94) & 0.24 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 34000 (1.02) & 43100 (1.06) & 8860 (0.97) & 6300 (0.82) & 18900 (1.14) & 0.02 & 48100 (1.03) & 0.29 & 0.60\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 51200 (0.92) & 69900 (0.95) & 10900 (0.89) & 11100 (0.9) & 29300 (0.94) & 0.04 & 69600 (0.94) & 0.19 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 48800 (0.87) & 58600 (0.8) & 9700 (0.8) & 13700 (1.1) & 25400 (0.81) & 0.00 & 65800 (0.88) & 0.19 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 59100 (1.06) & 84100 (1.14) & 12600 (1.03) & 10100 (0.81) & 36400 (1.16) & 0.01 & 78900 (1.06) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 332 (1.04) & 388 (1.18) & 158 (0.92) & 78.7 (0.85) & 95 (1.72) & -0.02 & 547 (1.12) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 321 (1.01) & 385 (1.17) & 153 (0.89) & 100 (1.08) & 68.1 (1.24) & -0.01 & 535 (1.1) & 0.54 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 298 (0.93) & 337 (1.03) & 155 (0.9) & 106 (1.14) & 37.5 (0.68) & -0.04 & 441 (0.9) & 0.67 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 319 (1) & 342 (1.04) & 160 (0.93) & 85.1 (0.92) & 73.6 (1.34) & -0.02 & 547 (1.12) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 332 (1.04) & 363 (1.11) & 168 (0.98) & 86.1 (0.93) & 78.2 (1.42) & -0.02 & 528 (1.08) & 0.58 & 0.96\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 445 (1.05) & 532 (1.2) & 193 (0.91) & 107 (0.85) & 144 (1.68) & -0.03 & 700 (1.04) & 0.54 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 399 (0.94) & 438 (0.99) & 195 (0.92) & 105 (0.83) & 97.9 (1.14) & -0.05 & 692 (1.03) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 384 (0.91) & 387 (0.87) & 196 (0.92) & 122 (0.97) & 65.9 (0.77) & -0.06 & 602 (0.89) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 407 (0.96) & 456 (1.03) & 202 (0.95) & 105 (0.83) & 101 (1.18) & -0.03 & 669 (0.99) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 457 (1.08) & 527 (1.19) & 208 (0.98) & 129 (1.02) & 121 (1.41) & -0.06 & 744 (1.1) & 0.50 & 0.96\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\hypertarget{tables-mean-ensemble}{%
-\subsubsection{Tables mean ensemble}\label{tables-mean-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 8680 (1) & 10300 (1) & 3700 (1) & 1460 (1) & 3520 (1) & -0.02 & 13400 (1) & 0.50 & 0.86\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 7600 (0.88) & 8770 (0.85) & 3360 (0.91) & 1090 (0.75) & 3140 (0.89) & 0.01 & 11900 (0.89) & 0.52 & 0.90\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 8050 (0.93) & 9070 (0.88) & 3520 (0.95) & 1410 (0.97) & 3120 (0.89) & -0.02 & 12600 (0.94) & 0.48 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 8090 (0.93) & 9780 (0.95) & 3490 (0.94) & 1110 (0.76) & 3490 (0.99) & 0.02 & 12700 (0.95) & 0.57 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 19000 (1) & 22100 (1) & 5960 (1) & 3690 (1) & 9340 (1) & 0.02 & 28800 (1) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 17100 (0.9) & 20600 (0.93) & 5550 (0.93) & 2850 (0.77) & 8660 (0.93) & 0.05 & 26000 (0.9) & 0.38 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 17600 (0.93) & 20000 (0.9) & 5540 (0.93) & 3790 (1.03) & 8230 (0.88) & 0.01 & 26800 (0.93) & 0.36 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 18300 (0.96) & 22600 (1.02) & 5910 (0.99) & 2640 (0.72) & 9720 (1.04) & 0.06 & 27700 (0.96) & 0.38 & 0.76\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 229 (1) & 292 (1) & 101 (1) & 90.4 (1) & 36.7 (1) & -0.07 & 315 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 219 (0.96) & 289 (0.99) & 96.8 (0.96) & 79.8 (0.88) & 42.6 (1.16) & -0.04 & 297 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 217 (0.95) & 287 (0.98) & 95.3 (0.94) & 83.1 (0.92) & 38.7 (1.05) & -0.07 & 300 (0.95) & 0.67 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 225 (0.98) & 292 (1) & 98.7 (0.98) & 94.2 (1.04) & 32 (0.87) & -0.09 & 314 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 222 (0.97) & 289 (0.99) & 98 (0.97) & 84.1 (0.93) & 39.6 (1.08) & -0.04 & 295 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 225 (0.98) & 290 (0.99) & 99.7 (0.99) & 84.7 (0.94) & 40.5 (1.1) & -0.05 & 314 (1) & 0.71 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 256 (1) & 306 (1) & 138 (1) & 64.5 (1) & 53.2 (1) & 0.04 & 374 (1) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 270 (1.05) & 338 (1.1) & 136 (0.99) & 65.2 (1.01) & 68.1 (1.28) & 0.06 & 413 (1.1) & 0.75 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 268 (1.05) & 346 (1.13) & 133 (0.96) & 78.7 (1.22) & 57.1 (1.07) & 0.05 & 408 (1.09) & 0.75 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 259 (1.01) & 322 (1.05) & 133 (0.96) & 81.7 (1.27) & 44.4 (0.83) & 0.03 & 380 (1.02) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 264 (1.03) & 315 (1.03) & 133 (0.96) & 70.1 (1.09) & 60 (1.13) & 0.06 & 404 (1.08) & 0.71 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 264 (1.03) & 332 (1.08) & 141 (1.02) & 60.1 (0.93) & 63.1 (1.19) & 0.06 & 390 (1.04) & 0.79 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 35600 (1) & 42100 (1) & 9340 (1) & 7050 (1) & 19200 (1) & 0.03 & 51200 (1) & 0.26 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 32100 (0.9) & 40500 (0.96) & 8830 (0.95) & 4920 (0.7) & 18300 (0.95) & 0.07 & 47200 (0.92) & 0.29 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 32200 (0.9) & 36700 (0.87) & 8430 (0.9) & 7190 (1.02) & 16500 (0.86) & 0.04 & 46900 (0.92) & 0.24 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 35200 (0.99) & 46000 (1.09) & 9630 (1.03) & 4600 (0.65) & 20900 (1.09) & 0.08 & 51000 (1) & 0.38 & 0.67\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 60300 (1) & 79300 (1) & 15700 (1) & 10400 (1) & 34100 (1) & 0.04 & 78600 (1) & 0.29 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 55000 (0.91) & 77100 (0.97) & 14600 (0.93) & 6620 (0.64) & 33800 (0.99) & 0.11 & 75200 (0.96) & 0.33 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 53400 (0.89) & 66600 (0.84) & 13700 (0.87) & 10600 (1.02) & 29200 (0.86) & 0.06 & 70400 (0.9) & 0.26 & 0.60\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 61700 (1.02) & 89800 (1.13) & 16400 (1.04) & 6400 (0.62) & 38900 (1.14) & 0.12 & 82900 (1.05) & 0.31 & 0.64\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 289 (1) & 293 (1) & 178 (1) & 45.9 (1) & 65.7 (1) & 0.01 & 443 (1) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 310 (1.07) & 348 (1.19) & 182 (1.02) & 42 (0.92) & 86.5 (1.32) & 0.08 & 502 (1.13) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 315 (1.09) & 339 (1.16) & 178 (1) & 62.2 (1.36) & 74 (1.13) & 0.07 & 507 (1.14) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 297 (1.03) & 292 (1) & 174 (0.98) & 67.7 (1.47) & 55 (0.84) & 0.01 & 452 (1.02) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 294 (1.02) & 299 (1.02) & 172 (0.97) & 48 (1.05) & 74.2 (1.13) & 0.03 & 476 (1.07) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 310 (1.07) & 349 (1.19) & 189 (1.06) & 39.4 (0.86) & 81.9 (1.25) & 0.05 & 482 (1.09) & 0.62 & 1.00\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 437 (1) & 568 (1) & 232 (1) & 72 (1) & 134 (1) & 0.00 & 702 (1) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 445 (1.02) & 598 (1.05) & 237 (1.02) & 56.4 (0.78) & 152 (1.13) & 0.06 & 707 (1.01) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 421 (0.96) & 520 (0.92) & 239 (1.03) & 49.9 (0.69) & 132 (0.99) & 0.05 & 678 (0.97) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 398 (0.91) & 465 (0.82) & 235 (1.01) & 55.6 (0.77) & 107 (0.8) & 0.00 & 628 (0.89) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 418 (0.96) & 533 (0.94) & 222 (0.96) & 66.8 (0.93) & 129 (0.96) & 0.03 & 662 (0.94) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 467 (1.07) & 636 (1.12) & 248 (1.07) & 61 (0.85) & 158 (1.18) & 0.05 & 755 (1.08) & 0.67 & 1.00\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{sensitivity-analysis}{%
-\subsection{Sensitivity analysis}\label{sensitivity-analysis}}
-
-In the original analysis, cases and deaths were scored on different
-periods, as the convolution model was only added later. This sensitivity
-shows performance of all models restricted to the period from December
-14 2020 until March 1st 2021 where all models were available.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-late}
-\end{figure}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 4980 (0.74) & 5730 (0.64) & 2070 (0.6) & 728 (0.74) & 2190 (0.94) & 0.09 & 7810 (0.82) & 0.54 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 6730 (1) & 8960 (1) & 3430 (1) & 978 (1) & 2330 (1) & -0.09 & 9550 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 9640 (1.43) & 13300 (1.48) & 1970 (0.57) & 4170 (4.26) & 3500 (1.5) & 0.09 & 12700 (1.33) & 0.46 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 10700 (0.99) & 13800 (1.1) & 2880 (0.58) & 2350 (0.85) & 5430 (1.79) & 0.08 & 15400 (1.07) & 0.46 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 10800 (1) & 12500 (1) & 4940 (1) & 2780 (1) & 3030 (1) & -0.13 & 14400 (1) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25000 (2.31) & 34000 (2.72) & 4780 (0.97) & 8710 (3.13) & 11500 (3.8) & 0.05 & 32000 (2.22) & 0.50 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 17200 (1) & 16000 (0.98) & 3800 (0.63) & 5660 (0.85) & 7770 (1.74) & 0.07 & 26800 (1.1) & 0.08 & 0.58\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 17200 (1) & 16300 (1) & 6030 (1) & 6670 (1) & 4470 (1) & -0.16 & 24400 (1) & 0.33 & 0.67\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 37700 (2.19) & 55900 (3.43) & 8840 (1.47) & 10700 (1.6) & 18100 (4.05) & -0.03 & 49800 (2.04) & 0.33 & 0.58\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 26100 (0.95) & 21000 (0.84) & 4810 (0.7) & 11300 (0.83) & 10100 (1.43) & 0.04 & 39400 (1.05) & 0.00 & 0.46\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 27600 (1) & 25000 (1) & 6900 (1) & 13600 (1) & 7060 (1) & -0.19 & 37400 (1) & 0.29 & 0.54\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 48900 (1.77) & 77800 (3.11) & 13800 (2) & 11900 (0.88) & 23200 (3.29) & -0.10 & 65500 (1.75) & 0.38 & 0.58\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{overview-of-models-and-forecasters}{%
-\subsection{Overview of models and
-forecasters}\label{overview-of-models-and-forecasters}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{7.3cm}}
-\caption{\label{tab:table-ensemble-versions}Overview of the models and ensembles used.}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{Overview of the models and ensembles used. \textit{(continued)}}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-\cellcolor{gray!6}{Hub-ensemble-realised} & \cellcolor{gray!6}{Official Forecast Hub median ensemble.
-Created by the Forecast Hub officially under the name 'KITCOVIDhub-median\_ensemble' and used as the default ensemble.
-Included are our crowd forecasts as well as the renewal model (with one missed submission on December 28 2020, but not the convolution model which was deemed to similar to the renewal model.}\\
-\addlinespace \addlinespace
-Hub-ensemble-realised-mean & Official Forecast Hub mean ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-mean\_ensemble'.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{ \vphantom{1}} & \cellcolor{gray!6}{}\\
-\addlinespace \addlinespace
-Hub-ensemble & Version of the official Hub median ensemble which excludes all our contributions.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Hub-ensemble-mean} & \cellcolor{gray!6}{Version of the official Hub mean ensemble which excludes all our contributions.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-renewal, 
-    Hub-ensemble-with-renewal-mean & Versions of the official Hub ensembles which of our contributions includes only the Renewal model.\\
-\addlinespace \addlinespace
-Hub-ensemble-with-crowd, 
-\cellcolor{gray!6}{    Hub-ensemble-with-crowd-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which of our contributions includes only the Crowd forecast.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-convolution, 
-    Hub-ensemble-with-convolution-mean & Versions of the official Hub ensembles which of our contributions includes only the Convolution model (which originally was never included in any official Hub ensemble).\\
-\addlinespace \addlinespace
-Hub-ensemble-with-all, 
-\cellcolor{gray!6}{    Hub-ensemble-with-all-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which includes all our contributions.
-For cases, this is identical to the official Hub ensembles, but for deaths the convolution model was added.}\\
-\addlinespace \addlinespace
- & \\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Crowd forecast} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'}\\
-\addlinespace \addlinespace
-Renewal model & Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Convolution model} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\_secondary'}\\*
-\end{longtable}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/number-forecasters} \caption{Number of participants who submitted a forecast over time.}\label{fig:num-forecasters}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/ensemble-members} \caption{Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
-Note that the renewal model was not included in the ensemble on December 28th 2020.}\label{fig:num-ensemble-members}
-\end{figure}
-
-\clearpage
-
-\hypertarget{comparison-of-crowd-forecasts-and-application-baseline}{%
-\subsection{Comparison of crowd forecasts and application
-baseline}\label{comparison-of-crowd-forecasts-and-application-baseline}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} \caption{Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the median, as well as the 50\% and 90\% prediction intervals (in order of decreasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons).}\label{fig:compare-forecasters}
-\end{figure}
+\section*{References}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Ganyani T, Kremer C, Chen D, Torneri A, Faes C, Wallinga
-J, et al. Estimating the generation interval for coronavirus disease
-(COVID-19) based on symptom onset data, march 2020. Eurosurveillance.
-2020;25. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith
-HR, et al. The incubation period of coronavirus disease 2019 (COVID-19)
-from publicly reported confirmed cases: Estimation and application.
-Annals of Internal Medicine. 2020;172: 577--582. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J,
-Munday J, et al. Covidregionaldata: Subnational data for the covid-19
-outbreak. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957539}{10.5281/zenodo.3957539}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Evaluating the use of the reproduction number as an
-epidemiological tool, using spatio-temporal trends of the {Covid-19}
-outbreak in {England} \textbar{} {medRxiv}. {[}cited 30 May 2021{]}.
-Available:
-\url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Riutort-Mayol G, Bürkner P-C, Andersen MR, Solin A,
-Vehtari A. Practical hilbert space approximate bayesian gaussian
-processes for probabilistic programming. 2020. Available:
-\url{https://arxiv.org/abs/2004.11408}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Scott JA, Gandy A, Mishra S, Unwin J, Flaxman S, Bhatt
-S. Epidemia: Modeling of epidemics using hierarchical bayesian models.
-2020. Available:
-\url{https://imperialcollegelondon.github.io/epidemia/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bhattSemiMechanisticBayesianModeling}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Bhatt S, Ferguson N, Flaxman S, Gandy A, Mishra S, Scott
-JA. Semi-{Mechanistic Bayesian} modeling of {COVID-19} with {Renewal
-Processes}. : 14. }
-
 \end{CSLReferences}
 
+\clearpage
+
+\section*{Acknowledgments}
+
+We thank all forecasters who participated in this study for their
+contribution.
+
+\clearpage
+
+\beginsupplement
+
+\section*{Supporting information}
+
+\paragraph*{S1 Table.}
+\label{tab:scoring-metrics}
+
+\textbf{Overview of the scoring metrics used.}
+
+\paragraph*{S1 Text.}
+\label{txt:details-models}
+
+\textbf{Further details on the semi-mechanistic forecasting models.}
+
+\paragraph*{S1 Fig.}
+\label{fig:screenshot}
+
+\textbf{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).}
+
+\paragraph*{S2}
+
+\textbf{Table.} \label{tab:score-table-2}
+\textbf{Scores for one and two week ahead forecasts.} Scores are cut to
+three significant digits and rounded). Note that scores for cases (which
+include the whole period from October 12th 2020 until March 1st 2021)
+and deaths (which include only forecasts from the 21st of December 2020
+on) are computed on different subsets. Numbers in brackets show the
+metrics relative to the Hub ensemble (i.e.~the median ensemble of all
+other models submitted to the German and Polish Forecast Hub, excluding
+our contributions). WIS is the mean weighted interval score (lower
+values are better), WIS - sd is the standard deviation of all scores
+achieved by a model. Dispersion, over-prediction and under-prediction
+together sum up to the weighted interval score. Bias (between -1 and 1,
+0 is ideal) represents the general average tendency of a model to over-
+or underpredict. 50\% and 90\%-coverage are the percentage of observed
+values that fell within the 50\% and 90\% prediction intervals of a
+model.
+
+\paragraph*{S3 Table.}
+\label{tab:score-table-4}
+
+\textbf{Scores for three and four weeks ahead forecasts.} Scores are cut
+to three significant digits and rounded). Note that scores for cases
+(which include the whole period from October 12th 2020 until March 1st
+2021) and deaths (which include only forecasts from the 21st of December
+2020 on) are computed on different subsets. Numbers in brackets show the
+metrics relative to the Hub ensemble (i.e.~the median ensemble of all
+other models submitted to the German and Polish Forecast Hub, excluding
+our contributions). WIS is the mean weighted interval score (lower
+values are better), WIS - sd is the standard deviation of all scores
+achieved by a model. Dispersion, over-prediction and under-prediction
+together sum up to the weighted interval score. Bias (between -1 and 1,
+0 is ideal) represents the general average tendency of a model to over-
+or underpredict. 50\% and 90\%-coverage are the percentage of observed
+values that fell within the 50\% and 90\% prediction intervals of a
+model.
+
+\paragraph{S2}
+
+\textbf{Fig.} \label{fig:agg-performance-all-Germany}
+\textbf{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.}
+A, B: mean weighted interval score (WIS, lower indicates better
+performance) across horizons. WIS is decomposed into its components
+dispersion, over-prediction and under-prediction. C: Empirical coverage
+of the 50\% prediction intervals (50\% coverage is perfect). D:
+Empirical coverage of the 90\% prediction intervals. E: Dispersion (same
+as in panel A, B). Higher values mean greater dispersion of the forecast
+and imply ceteris paribus a worse score. F: Bias, i.e.~general
+(relative) tendency to over- or underpredict. Values are between -1
+(complete under-prediction) and 1 (complete over-prediction) and 0
+ideally. G: Absolute error of the median forecast (lower is better). H.
+Standard deviation of all WIS values for different horizons
+
+\paragraph{S3}
+
+\textbf{Fig.} \label{fig:agg-performance-all-Poland}
+\textbf{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.}
+A, B: mean weighted interval score (WIS, lower indicates better
+performance) across horizons. WIS is decomposed into its components
+dispersion, over-prediction and under-prediction. C: Empirical coverage
+of the 50\% prediction intervals (50\% coverage is perfect). D:
+Empirical coverage of the 90\% prediction intervals. E: Dispersion (same
+as in panel A, B). Higher values mean greater dispersion of the forecast
+and imply ceteris paribus a worse score. F: Bias, i.e.~general
+(relative) tendency to over- or underpredict. Values are between -1
+(complete under-prediction) and 1 (complete over-prediction) and 0
+ideally. G: Absolute error of the median forecast (lower is better). H.
+Standard deviation of all WIS values for different horizons
+
+\paragraph{S4}
+
+\textbf{Fig.} \label{fig:performance-locations}
+\textbf{Visualisation of aggregate performance metrics across locations.}
+A, B: mean weighted interval score (WIS, lower indicates better
+performance) across horizons. WIS is decomposed into its components
+dispersion, over-prediction and under-prediction. C: Empirical coverage
+of the 50\% prediction intervals (50\% coverage is perfect). D:
+Empirical coverage of the 90\% prediction intervals. E: Dispersion (same
+as in panel A, B). Higher values mean greater dispersion of the forecast
+and imply ceteris paribus a worse score. F: Bias, i.e.~general
+(relative) tendency to over- or underpredict. Values are between -1
+(complete under-prediction) and 1 (complete over-prediction) and 0
+ideally. G: Absolute error of the median forecast (lower is better). H.
+Standard deviation of WIS values.
+
+\paragraph{S5}
+
+\textbf{Fig.} \label{fig:performance-locations-rel}
+\textbf{Visualisation of aggregate performance metrics across locations in relative terms.}
+A, B: mean weighted interval score (WIS) across locations (lower values
+indicate better performance). C, D: Empirical coverage of the 50\% and
+90\% prediction intervals. E: Dispersion. Higher values mean greater
+dispersion of the forecast and imply ceteris paribus a worse score. F:
+Bias, i.e.~general (relative) tendency to over- orunderpredict. Values
+are between -1 (complete under-prediction) and 1 (complete
+over-prediction) and 0 ideally. G: Absolute error of the median
+forecast. H. Standard deviation of WIS values.
+
+\paragraph{S6}
+
+\textbf{Fig.} \label{fig:daily-truth}
+\textbf{Visualisation of daily report data.} The black line represents
+weekly data divided by seven. Data were last accessed through the German
+and Polish Forecast Hub on August 21 2021.
+
+\paragraph{S7}
+
+\textbf{Fig.} \label{fig:daily-truth-update}
+\textbf{Visualisation of the absolute difference between the daily report data at the time and the data now.}
+In Germany, there were zero cases and deaths reported on 2020-10-12, and
+only later 2467 cases and 6 deaths were added. Data were last accessed
+through the German and Polish Forecast Hub on May 10 2022.
+
+\paragraph{S8}
+
+\textbf{Fig.} \label{fig:weekly-truth-update}
+\textbf{Visualisation of the relative difference between the weekly report data at the time and the data now.}
+Apart from the data that was retrospectively added on 2020-10-12, data
+updates did not have a noticeable effect on weekly data (as shown in the
+forecasting application). Data were last accessed through the German and
+Polish Forecast Hub on May 10 2022.
+
+\paragraph{S9 Fig.}
+\label{fig:forecasts-and-truth-1}
+
+\textbf{Visualisation of forecasts and scores for one week ahead forecasts.}
+A, C: Visualisation of 50\% prediction intervals of one week ahead
+forecasts against the reported values. Forecasts that were not scored
+(because there was no complete set of death forecasts available) are
+greyed out. B, D: Visualisation of corresponding WIS.
+
+\paragraph{S10 Fig.}
+\label{fig:forecasts-and-truth-3}
+
+\textbf{Visualisation of forecasts and scores for three week ahead forecasts.}
+A, C: Visualisation of 50\% prediction intervals of three week ahead
+forecasts against the reported values. Forecasts that were not scored
+(because there was no complete set of death forecasts available) are
+greyed out. B, D: Visualisation of corresponding WIS.
+
+\paragraph{S11 Fig.}
+\label{fig:forecasts-and-truth-4}
+
+\textbf{Visualisation of forecasts and scores for three week ahead forecasts.}
+A, C: Visualisation of 50\% prediction intervals of four week ahead
+forecasts against the reported values. Forecasts that were not scored
+(because there was no complete set of death forecasts available) are
+greyed out. B, D: Visualisation of corresponding WIS.
+
+\paragraph{S12 Fig.}
+\label{fig:distribution-scores-1}
+
+\textbf{Distribution of weighted interval scores for one week ahead forecasts}
+A: Distribution of weighted interval scores for one week ahead forecasts
+of the different models and forecast targets pooled across locations. B:
+Distribution of WIS separate by country.
+
+\paragraph{S13 Fig.}
+\label{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets pooled across locations. B: Distribution of WIS separate by country.}
+
+\textbf{Distribution of weighted interval scores for three week ahead forecasts}
+A: Distribution of weighted interval scores for three week ahead
+forecasts of the different models and forecast targets pooled across
+locations. B: Distribution of WIS separate by country.
+
+\paragraph{S14 Fig.}
+\label{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets pooled across locations. B: Distribution of WIS separate by country.}
+
+\textbf{Distribution of weighted interval scores for four week ahead forecasts}
+A: Distribution of weighted interval scores for four week ahead
+forecasts of the different models and forecast targets pooled across
+locations. B: Distribution of WIS separate by country.
+
+\paragraph{S15 Fig.}
+\label{fig:distribution-scores-ranks-1}
+
+\textbf{Distribution of model ranks (in terms of WIS) for one week ahead forecasts}
+A: Distribution of the ranks (determined by the weighted interval score)
+for one week ahead forecasts of the different models and forecast
+targets, pooled across locations. B: Distribution of ranks separate by
+country.
+
+\paragraph{S16 Fig.}
+\label{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets, pooled across locations.
+B: Distribution of ranks separate by country.}
+
+\textbf{Distribution of model ranks (in terms of WIS) for two week ahead forecasts}
+A: Distribution of the ranks (determined by the weighted interval score)
+for two week ahead forecasts of the different models and forecast
+targets, pooled across locations. B: Distribution of ranks separate by
+country.
+
+\paragraph{S17 Fig.}
+\label{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets, pooled across locations.
+B: Distribution of ranks separate by country.}
+
+\textbf{Distribution of model ranks (in terms of WIS) for three week ahead forecasts}
+A: Distribution of the ranks (determined by the weighted interval score)
+for three week ahead forecasts of the different models and forecast
+targets, pooled across locations. B: Distribution of ranks separate by
+country.
+
+\paragraph{S18 Fig.}
+\label{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets, pooled across locations.
+B: Distribution of ranks separate by country.}
+
+\textbf{Distribution of model ranks (in terms of WIS) for four week ahead forecasts}
+A: Distribution of the ranks (determined by the weighted interval score)
+for four week ahead forecasts of the different models and forecast
+targets, pooled across locations. B: Distribution of ranks separate by
+country.
+
+\paragraph{S19 Fig.}
+\label{fig:distribution-scores-differences}
+
+\textbf{Difference in WIS between the Crowd forecast and the Hub ensemble for two week ahead forecasts.}
+Values below zero mean better performance of the Crowd forecasts.
+
+\paragraph{S20 Fig.}
+\label{fig:distribution-scores-differences-renewal}
+
+\textbf{Difference in WIS between the Crowd forecast and the Renewal model for two week ahead forecasts.}
+Values below zero mean better performance of the Crowd forecasts.
+
+\paragraph{S21}
+
+\textbf{Fig.} \label{fig:agg-performance-ensemble-mean}
+\textbf{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.}
+``Hub-ensemble'' \textit{excludes} all our models, Hub-ensemble-all
+\textit{includes} all of our models, ``Hub-ensemble-realised'' is the
+actual hub-ensemble observed in reality, which includes the renewal
+model and the crowd forecasts, but ont the convolution model. Values
+(except for Bias) are computed as differences to the Hub ensemble which
+excludes our contributions. For Coverage, this is an absolute
+difference, for other metrics this is a percentage difference. A, B:
+mean weighted interval score (WIS) across horizons relative to the Hub
+ensemble (lower values indicate better performance). C, D: Empirical
+coverage of the 50\% and 90\% prediction intervals minus empirical
+coverage observed for the Hub ensemble. E: Dispersion relative to the
+dispersion of the Hub ensemble. Higher values mean greater dispersion of
+the forecast and imply ceteris paribus a worse score. F: Bias,
+i.e.~general (relative) tendency to over- orunderpredict. Values are
+between -1 (complete under-prediction) and 1 (complete over-prediction)
+and 0 ideally. G: Absolute error of the median forecast relative to the
+Hub ensemble. H. Standard deviation of all WIS values for different
+horizons relative to the Hub ensemble.
+
+\paragraph{S4}
+
+\textbf{Table.} \label{tab:score-table-ensemble-2}
+\textbf{Scores for one and two week ahead forecasts for the different versions of the median ensemble.}
+Scores are cut to three significant digits and rounded. Note that scores
+for cases (which include the whole period from October 12th 2020 until
+March 1st 2021) and deaths (which include only forecasts from the 21st
+of December 2020 on) are computed on different subsets. Numbers in
+brackets show the metrics relative to the Hub ensemble (i.e.~the median
+ensemble of all other models submitted to the German and Polish Forecast
+Hub, excluding our contributions). WIS is the mean weighted interval
+score (lower values are better), WIS - sd is the standard deviation of
+all scores achieved by a model. Dispersion, over-prediction and
+under-prediction together sum up to the weighted interval score. Bias
+(between -1 and 1, 0 is ideal) represents the general average tendency
+of a model to over- or underpredict. 50\% and 90\%-coverage are the
+percentage of observed values that fell within the 50\% and 90\%
+prediction intervals of a model.
+
+\paragraph{S5 Table.}
+\label{tab:score-table-ensemble-4}
+
+\textbf{Scores for three and four week ahead forecasts for the different versions of the median ensemble.}
+Scores are cut to three significant digits and rounded. Note that scores
+for cases (which include the whole period from October 12th 2020 until
+March 1st 2021) and deaths (which include only forecasts from the 21st
+of December 2020 on) are computed on different subsets. Numbers in
+brackets show the metrics relative to the Hub ensemble (i.e.~the median
+ensemble of all other models submitted to the German and Polish Forecast
+Hub, excluding our contributions). WIS is the mean weighted interval
+score (lower values are better), WIS - sd is the standard deviation of
+all scores achieved by a model. Dispersion, over-prediction and
+under-prediction together sum up to the weighted interval score. Bias
+(between -1 and 1, 0 is ideal) represents the general average tendency
+of a model to over- or underpredict. 50\% and 90\%-coverage are the
+percentage of observed values that fell within the 50\% and 90\%
+prediction intervals of a model.
+
+\paragraph{S6 Table.}
+\label{tab:score-table-ensemble-mean-2}
+
+\textbf{Scores for one and two week ahead forecasts for the different versions of the mean ensemble}
+Scores are cut to three significant digits and rounded. Note that scores
+for cases (which include the whole period from October 12th 2020 until
+March 1st 2021) and deaths (which include only forecasts from the 21st
+of December 2020 on) are computed on different subsets. Numbers in
+brackets show the metrics relative to the Hub mean ensemble (i.e.~the
+mean ensemble of all other models submitted to the German and Polish
+Forecast Hub, excluding our contributions). WIS is the mean weighted
+interval score (lower values are better), WIS - sd is the standard
+deviation of all scores achieved by a model. Dispersion, over-prediction
+and under-prediction together sum up to the weighted interval score.
+Bias (between -1 and 1, 0 is ideal) represents the general average
+tendency of a model to over- or underpredict. 50\% and 90\%-coverage are
+the percentage of observed values that fell within the 50\% and 90\%
+prediction intervals of a model.
+
+\paragraph{S7 Table.}
+\label{tab:score-table-ensemble-mean-4}
+
+\textbf{Scores for three and four week ahead forecasts for the different versions of the mean ensemble}
+Scores are cut to three significant digits and rounded. Note that scores
+for cases (which include the whole period from October 12th 2020 until
+March 1st 2021) and deaths (which include only forecasts from the 21st
+of December 2020 on) are computed on different subsets. Numbers in
+brackets show the metrics relative to the Hub mean ensemble (i.e.~the
+mean ensemble of all other models submitted to the German and Polish
+Forecast Hub, excluding our contributions). WIS is the mean weighted
+interval score (lower values are better), WIS - sd is the standard
+deviation of all scores achieved by a model. Dispersion, over-prediction
+and under-prediction together sum up to the weighted interval score.
+Bias (between -1 and 1, 0 is ideal) represents the general average
+tendency of a model to over- or underpredict. 50\% and 90\%-coverage are
+the percentage of observed values that fell within the 50\% and 90\%
+prediction intervals of a model.
+
+\paragraph{S22 Fig.}
+\label{fig:agg-performance-all-late}
+
+\textbf{Visualisation of aggregate performance metrics across forecast horizons (period from December 14th 2020 on)}
+From December 14th 2020 on, all models were available. In the original
+analysis, cases and deaths were scored on different periods, as the
+convolution model was only added later. This sensitivity analysis shows
+performance of all models restricted to the period from December 14 2020
+until March 1st 2021 where all models were available. A, B: mean
+weighted interval score (WIS, lower indicates better performance) across
+horizons. WIS is decomposed into its components dispersion,
+over-prediction and under-prediction. C: Empirical coverage of the 50\%
+prediction intervals (50\% coverage is perfect). D: Empirical coverage
+of the 90\% prediction intervals. E: Dispersion (same as in panel A, B).
+Higher values mean greater dispersion of the forecast and imply ceteris
+paribus a worse score. F: Bias, i.e.~general (relative) tendency to
+over- or underpredict. Values are between -1 (complete under-prediction)
+and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the
+median forecast (lower is better). H. Standard deviation of all WIS
+values for different horizons
+
+\paragraph{S8}
+
+\textbf{Table.} \label{tab:score-table-late-2}
+\textbf{Scores for one and two week ahead forecasts (sensitivity analysis)}
+Scores are cut to three significant digits and rounded. In the original
+analysis, cases and deaths were scored on different periods, as the
+convolution model was only added later. This table shows performance of
+all models restricted to the period from December 14 2020 until March
+1st 2021 where all models were available. Numbers in brackets show the
+metrics relative to the Hub ensemble (i.e.~the median ensemble of all
+other models submitted to the German and Polish Forecast Hub, excluding
+our contributions). WIS is the mean weighted interval score (lower
+values are better), WIS - sd is the standard deviation of all scores
+achieved by a model. Dispersion, over-prediction and under-prediction
+together sum up to the weighted interval score. Bias (between -1 and 1,
+0 is ideal) represents the general average tendency of a model to over-
+or underpredict. 50\% and 90\%-coverage are the percentage of observed
+values that fell within the 50\% and 90\% prediction intervals of a
+model.
+
+\paragraph{S9 Table.}
+\label{tab:score-table-late-4}
+
+\textbf{Scores for three and four week ahead forecasts (sensitivity analysis)}
+Scores are cut to three significant digits and rounded. In the original
+analysis, cases and deaths were scored on different periods, as the
+convolution model was only added later. This table shows performance of
+all models restricted to the period from December 14 2020 until March
+1st 2021 where all models were available. Numbers in brackets show the
+metrics relative to the Hub ensemble (i.e.~the median ensemble of all
+other models submitted to the German and Polish Forecast Hub, excluding
+our contributions). WIS is the mean weighted interval score (lower
+values are better), WIS - sd is the standard deviation of all scores
+achieved by a model. Dispersion, over-prediction and under-prediction
+together sum up to the weighted interval score. Bias (between -1 and 1,
+0 is ideal) represents the general average tendency of a model to over-
+or underpredict. 50\% and 90\%-coverage are the percentage of observed
+values that fell within the 50\% and 90\% prediction intervals of a
+model.
+
+\paragraph{S10 Table.}
+\label{tab:table-ensemble-versions}
+
+\textbf{Overview of the models and ensembles used.}
+
+\paragraph{S23 Fig.}
+\label{fig:num-forecasters}
+
+\textbf{Number of participants who submitted a forecast over time.}
+
+\paragraph{S24 Fig.}
+\label{fig:num-ensemble-members}
+
+\textbf{Number of member models in the official Hub ensemble} This
+includes our crowd forecasts and the renewal model. Note that the
+renewal model was not included in the ensemble on December 28th 2020.
+
+\paragraph{S25 Fig.}
+\label{fig:compare-forecasters}
+
+\textbf{Crowd forecasts and baseline shown in the application for a two week horizon.}
+Shown are the median, as well as the 50\% and 90\% prediction intervals
+(in order of decreasing opacity). For any given point in time, the
+baseline shown in red is what forecasters saw when they opened the app
+(the baseline shown was constant across all forecast horizons).
+
+\paragraph*{S1 Acknowledgmenents.}
+
+\textbf{Members of the CMMID COVID-19 working group}
+
 \nolinenumbers

### 2022-09-07 manuscript/manuscript.tex
update manuscript for submission

@@
 
+\cite{mcgowanCollaborativeEffortsForecast2019}
+
 Infectious disease modelling has a long tradition and has helped inform
@@
 locations and forecast horizons, the distribution of WIS values was very
-right-skewed, and average performance was heavily influenced by outliers
-(Fig \ref{fig:distribution-scores}). Overall, low variance in forecast
-performance was closely linked with good mean performance (Fig
-\ref{fig:agg-performance-all}H and \ref{fig:agg-performance-all}A),
-suggesting that the ability to avoid large errors was an important
-factor in determining overall performance. The impact of outlier values
-was especially pronounced for the renewal model, which had more outliers
-(Fig \ref{fig:distribution-scores}), as well as the highest standard
-deviation of WIS values (standard deviation of the WIS relative to the
-WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon),
-while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub
-ensemble (= 1) showed more stable performance.
+right-skewed, and average performance was heavily influenced by
+outliers. Overall, low variance in forecast performance was closely
+linked with good mean performance (Fig \ref{fig:agg-performance-all}H
+and \ref{fig:agg-performance-all}A), suggesting that the ability to
+avoid large errors was an important factor in determining overall
+performance. The impact of outlier values was especially pronounced for
+the renewal model, which had more outliers, as well as the highest
+standard deviation of WIS values (standard deviation of the WIS relative
+to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead
+horizon), while the ensemble of crowd forecasts (rel. WIS sd 0.76) and
+the Hub ensemble (= 1) showed more stable performance.
 
@@
 \section*{References}
+\bibliographystyle{plos2015}
+\bibliography{germanpolishpaper.bib, references.bib}
 
@@
 
-\section*{Acknowledgments}
+\section*{Acknowledgements}
 
@@
 
-\paragraph*{S1 Acknowledgmenents.}
+\paragraph*{S1 Acknowledgements.}
 

### 2022-09-14 manuscript/manuscript.Rmd
attempt to update the way references are cited

@@
   - references.bib
-  - GermanPolishpaper.bib
+  - germanpolishpaper.bib
 csl: plos.csl
@@
 
-Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza [e.g.
-@mcgowanCollaborativeEffortsForecast2019; @reichCollaborativeMultiyearMultimodel2019; @shamanForecastingSeasonalOutbreaks2012; @biggerstaffResultsCentersDisease2016], dengue fever [e.g.
+Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza (e.g.
+\cite{mcgowanCollaborativeEffortsForecast2019, reichCollaborativeMultiyearMultimodel2019,  shamanForecastingSeasonalOutbreaks2012, biggerstaffResultsCentersDisease2016}), dengue fever [e.g.
 @johanssonOpenChallengeAdvance2019; @yamanaSuperensembleForecastsDengue2016; @colon-gonzalezProbabilisticSeasonalDengue2021], ebola [e.g.
@@
 For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (\nameref{tab:score-table-2} Table).
-Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Fig \ref{fig:distribution-scores}).
+Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers.
 Overall, low variance in forecast performance was closely linked with good mean performance (Fig \ref{fig:agg-performance-all}H and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Fig \ref{fig:distribution-scores}), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
+The impact of outlier values was especially pronounced for the renewal model, which had more outliers, as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
 WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
@@
 \section*{References}
+\bibliographystyle{plos2015}
+\bibliography{germanpolishpaper.bib, references.bib}
+
 ::: {#refs}
@@
 
-\paragraph*{S1 Acknowledgmenents.}
+\paragraph*{S1 Acknowledgements.}
 \textbf{Members of the CMMID COVID-19 working group}

### 2022-09-14 manuscript/manuscript.tex
attempt to update the way references are cited

@@
 
-\cite{mcgowanCollaborativeEffortsForecast2019}
-
 Infectious disease modelling has a long tradition and has helped inform
 public health decisions both through scenario modelling, as well as
-actual forecasts of (among others) influenza {[}e.g. 1,2--4{]}, dengue
-fever {[}e.g. 5,6,7{]}, ebola {[}e.g. 8,9{]}, chikungunya {[}e.g.
-10,11{]} and now COVID-19 {[}e.g. 12,13--17{]}. Applications of
+actual forecasts of (among others) influenza
+(e.g.~\cite{mcgowanCollaborativeEffortsForecast2019, reichCollaborativeMultiyearMultimodel2019,  shamanForecastingSeasonalOutbreaks2012, biggerstaffResultsCentersDisease2016},
+dengue fever {[}e.g. 1,2,3{]}, ebola {[}e.g. 4,5{]}, chikungunya {[}e.g.
+6,7{]} and now COVID-19 {[}e.g. 8,9--13{]}. Applications of
 epidemiological models differ in the way they make statements about the
@@
 collected, aggregated and compared by Forecast Hubs such as the US
-Forecast Hub {[}13,14{]}, the German and Polish Forecast Hub {[}15,16{]}
-and the European Forecast Hub {[}17{]}. Often, different individual
+Forecast Hub {[}9,10{]}, the German and Polish Forecast Hub {[}11,12{]}
+and the European Forecast Hub {[}13{]}. Often, different individual
 forecasts are combined into a single forecast, e.g.~by taking the mean
@@
 perform better and more consistently than individual forecasts (see e.g.
-{[}6{]}; {[}18{]}).
+{[}2{]}; {[}14{]}).
 
@@
 Previous work has examined such direct human forecasts in various
-contexts, such as geopolitics {[}19,20{]}, meta-science {[}21,22{]},
-sports {[}23{]} and epidemiology {[}11,24,25{]}. Several prediction
-platforms {[}26--28{]} and prediction markets {[}29{]} have been created
+contexts, such as geopolitics {[}15,16{]}, meta-science {[}17,18{]},
+sports {[}19{]} and epidemiology {[}7,20,21{]}. Several prediction
+platforms {[}22--24{]} and prediction markets {[}25{]} have been created
 to collate expert and non-expert predictions. However, with the notable
-exception of {[}11{]}, these forecasts were not designed to be evaluated
+exception of {[}7{]}, these forecasts were not designed to be evaluated
 alongside model-based forecasts and usually follow their own (often
@@
 clear in which situations human forecasts perform well or badly. For
-example, {[}11{]} found that humans could outperform computer models at
+example, {[}7{]} found that humans could outperform computer models at
 predicting the 2014/15 and 2015/16 flu season in the US, a setting where
@@
 intervention, which we submitted in real time to the German and Polish
-Forecast Hub. In contrast to {[}11{]} we elicited not only point
+Forecast Hub. In contrast to {[}7{]} we elicited not only point
 predictions, but full predictive distributions (``probabilistic
-forecasts'', see e.g. {[}30{]}) from participants. This allows us to
+forecasts'', see e.g. {[}26{]}) from participants. This allows us to
 compare not only predictive accuracy, but also how well human
@@
 ``crowd forecast''), elicited from participants through a web
-application {[}31{]} and 2) two semi-mechanistic model-based forecasts
+application {[}27{]} and 2) two semi-mechanistic model-based forecasts
 (``renewal model'' and ``convolution model'') informed by basic
@@
 until March 1st 2021 and submitted to the German and Polish Forecast hub
-{[}15,16{]}. All code and tools necessary to generate the forecasts and
+{[}11,12{]}. All code and tools necessary to generate the forecasts and
 make a forecast submission are available in the
-\texttt{covid.german.forecasts} R package {[}32{]}. This repository also
+\texttt{covid.german.forecasts} R package {[}28{]}. This repository also
 contains a record of all forecasts submitted to the German and Polish
@@
 
-The German and Polish Forecast Hub (now mostly merged into the {[}17{]})
+The German and Polish Forecast Hub (now mostly merged into the {[}13{]})
 elicits predictions for various COVID-19 related forecast targets from
@@
 Until December 14th, 2020, these data were sourced from the European
-Centre for Disease Control {[}33{]}. After ECDC stopped publishing daily
+Centre for Disease Control {[}29{]}. After ECDC stopped publishing daily
 data, observations were sourced from the Robert Koch Institute (RKI) and
 the Polish Ministry of Health for the remainder of the submission period
-{[}34{]}. These data are subject to reporting artefacts, (such as for
+{[}30{]}. These data are subject to reporting artefacts, (such as for
 example delayed case reporting in Poland on the 24th November,
-{[}35{]}), changes in reporting over time, and variation in testing
-regimes (for example in Germany from the 11th of November on, {[}36{]}).
+{[}31{]}), changes in reporting over time, and variation in testing
+regimes (for example in Germany from the 11th of November on, {[}32{]}).
 The ECDC data as well as the data published by the Polish Ministry of
@@
 Monday night. The application was built using the \texttt{shiny} and
-\texttt{golem} R packages {[}37,38{]} and is available in the
-\texttt{crowdforecastr} R package {[}31{]}. To make a forecast in the
+\texttt{golem} R packages {[}33,34{]} and is available in the
+\texttt{crowdforecastr} R package {[}27{]}. To make a forecast in the
 application participants could select a predictive distribution (with
@@
 on the hub data, as well as their forecasts, on a logarithmic scale and
-presented additional contextual COVID-19 data sourced from {[}39{]}.
+presented additional contextual COVID-19 data sourced from {[}35{]}.
 These data included, for example, notifications of both test positive
@@
 We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R
-package (version 1.3.3) as our model-based forecasts {[}40{]}. The first
+package (version 1.3.3) as our model-based forecasts {[}36{]}. The first
 of these models, here called ``renewal model'', used the renewal
-equation {[}41{]} to predict reported cases and deaths (see details in
+equation {[}37{]} to predict reported cases and deaths (see details in
 \nameref{txt:details-models}). It estimated the effective reproduction
@@
 and death notifications were obtained by convolving predicted infections
-over data-based delay distributions {[}40,42--44{]} to model the time
+over data-based delay distributions {[}36,38--40{]} to model the time
 between infection and report date. The renewal model was used to predict
@@
 used daily observations and assumed a negative binomial observation
-model with a multiplicative day-of-the-week effect {[}40{]}.
+model with a multiplicative day-of-the-week effect {[}36{]}.
 
@@
 to test positive case report or death in the model-based forecasts was
-sourced from {[}45{]} with data available up to the 1st of August. All
+sourced from {[}41{]} with data available up to the 1st of August. All
 model fitting was done using Markov-chain Monte Carlo (MCMC) in stan
-{[}46{]} with each location and forecast target being fitted separately.
+{[}42{]} with each location and forecast target being fitted separately.
 
@@
 COVID-19 forecasts, especially for cases, were in the past found to have
-poor predictive performance beyond this horizon {[}15{]}. Forecasts for
+poor predictive performance beyond this horizon {[}11{]}. Forecasts for
 cases were scored using the full period from October 2020 until March
@@
 Forecasts were analysed using the following scoring metrics: The
-weighted interval score (WIS) {[}47{]}, the absolute error, relative
+weighted interval score (WIS) {[}43{]}, the absolute error, relative
 bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule {[}48{]}, meaning that in expectation
+The WIS is a proper scoring rule {[}44{]}, meaning that in expectation
 the score is optimised by reporting a predictive distribution that is
@@
 also look at a relative tendency to make biased forecasts. The bias
-metric {[}9{]} we use captures how much probability mass of the forecast
+metric {[}5{]} we use captures how much probability mass of the forecast
 was above or below the true value (mapped to values between -1 and 1)
@@
 \nameref{tab:scoring-metrics}. All scores were calculated using the
-\texttt{scoringutils} R package {[}49{]}.
+\texttt{scoringutils} R package {[}45{]}.
 
@@
 forecasters, possibly aware of the semi-lockdown announced on November
-2nd 2020 {[}50{]} and the change in the testing regime (with stricter
-test criteria) on November 11th 2020 {[}36{]}, were fastest to adapt to
+2nd 2020 {[}46{]} and the change in the testing regime (with stricter
+test criteria) on November 11th 2020 {[}32{]}, were fastest to adapt to
 the new trend, and the Hub ensemble slowest. In December, cases rose
@@
 However, most of these studies either focused only on the evaluation of
-(expert-tuned) model-based approaches {[}e.g. 12,13,14{]}, or
-exclusively on human forecasts {[}19,20,24,25{]}. In contrast, we
-directly compared human and model-based forecasts. This is similar to
-the approach taken by {[}11{]}, but extends it in several ways. While
-Farrow et al.~only asked for point predictions and constructed a
-predictive distribution from these, we asked participants to provide a
-full predictive distribution, allowing us to compare human forecasts and
-models without any further assumptions, as well as to analyse how humans
-quantified their uncertainty. In addition, we compared crowd forecasts
-to two semi-mechanistic models informed by basic epidemiological
-knowledge of COVID-19, allowing us to assess not only relative
-performance but also to analyse qualitative differences between human
-judgement and model-based insight. In terms of interpretability of the
-results, exact knowledge of our two models, as well as focus on a
-limited set of targets and locations was a major advantage of our study
-compared to larger studies conducted by the Forecast Hubs
-{[}12--15,17{]}.
+(expert-tuned) model-based approaches {[}e.g. 8,9,10{]}, or exclusively
+on human forecasts {[}15,16,20,21{]}. In contrast, we directly compared
+human and model-based forecasts. This is similar to the approach taken
+by {[}7{]}, but extends it in several ways. While Farrow et al.~only
+asked for point predictions and constructed a predictive distribution
+from these, we asked participants to provide a full predictive
+distribution, allowing us to compare human forecasts and models without
+any further assumptions, as well as to analyse how humans quantified
+their uncertainty. In addition, we compared crowd forecasts to two
+semi-mechanistic models informed by basic epidemiological knowledge of
+COVID-19, allowing us to assess not only relative performance but also
+to analyse qualitative differences between human judgement and
+model-based insight. In terms of interpretability of the results, exact
+knowledge of our two models, as well as focus on a limited set of
+targets and locations was a major advantage of our study compared to
+larger studies conducted by the Forecast Hubs {[}8--11,13{]}.
 
@@
 \begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
 \CSLLeftMargin{1. }%
-\CSLRightInline{McGowan CJ, Biggerstaff M, Johansson M, Apfeldorf KM,
-Ben-Nun M, Brooks L, et al. Collaborative efforts to forecast seasonal
-influenza in the {United States}, 2015--2016. Scientific Reports.
-2019;9: 683.
-doi:\href{https://doi.org/10.1038/s41598-018-36361-9}{10.1038/s41598-018-36361-9}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
-\CSLLeftMargin{2. }%
-\CSLRightInline{Reich NG, Brooks LC, Fox SJ, Kandula S, McGowan CJ,
-Moore E, et al. A collaborative multiyear, multimodel assessment of
-seasonal influenza forecasting in the {United States}. PNAS. 2019;116:
-3146--3154.
-doi:\href{https://doi.org/10.1073/pnas.1812594116}{10.1073/pnas.1812594116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
-\CSLLeftMargin{3. }%
-\CSLRightInline{Shaman J, Karspeck A. Forecasting seasonal outbreaks of
-influenza. PNAS. 2012;109: 20425--20430.
-doi:\href{https://doi.org/10.1073/pnas.1208772109}{10.1073/pnas.1208772109}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
-\CSLLeftMargin{4. }%
-\CSLRightInline{Biggerstaff M, Alper D, Dredze M, Fox S, Fung IC-H,
-Hickmann KS, et al. Results from the centers for disease control and
-prevention's predict the 2013--2014 {Influenza Season Challenge}. BMC
-Infectious Diseases. 2016;16: 357.
-doi:\href{https://doi.org/10.1186/s12879-016-1669-x}{10.1186/s12879-016-1669-x}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
-\CSLLeftMargin{5. }%
 \CSLRightInline{Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak
@@
 \leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
-\CSLLeftMargin{6. }%
+\CSLLeftMargin{2. }%
 \CSLRightInline{Yamana TK, Kandula S, Shaman J. Superensemble forecasts
@@
 \leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
-\CSLLeftMargin{7. }%
+\CSLLeftMargin{3. }%
 \CSLRightInline{Colón-González FJ, Bastos LS, Hofmann B, Hopkin A,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
-\CSLLeftMargin{8. }%
+\CSLLeftMargin{4. }%
 \CSLRightInline{Viboud C, Sun K, Gaffey R, Ajelli M, Fumanelli L, Merler
@@
 \leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
-\CSLLeftMargin{9. }%
+\CSLLeftMargin{5. }%
 \CSLRightInline{Funk S, Camacho A, Kucharski AJ, Lowe R, Eggo RM,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
-\CSLLeftMargin{10. }%
+\CSLLeftMargin{6. }%
 \CSLRightInline{Del Valle SY, McMahon BH, Asher J, Hatchett R, Lega JC,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
-\CSLLeftMargin{11. }%
+\CSLLeftMargin{7. }%
 \CSLRightInline{Farrow DC, Brooks LC, Hyun S, Tibshirani RJ, Burke DS,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
-\CSLLeftMargin{12. }%
+\CSLLeftMargin{8. }%
 \CSLRightInline{Funk S, Abbott S, Atkins BD, Baguelin M, Baillie JK,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
-\CSLLeftMargin{13. }%
+\CSLLeftMargin{9. }%
 \CSLRightInline{Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
-\CSLLeftMargin{14. }%
+\CSLLeftMargin{10. }%
 \CSLRightInline{Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
-\CSLLeftMargin{15. }%
+\CSLLeftMargin{11. }%
 \CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
-\CSLLeftMargin{16. }%
+\CSLLeftMargin{12. }%
 \CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
@@
 \leavevmode\vadjust pre{\hypertarget{ref-europeancovid-19forecasthubEuropeanCovid19Forecast2021}{}}%
-\CSLLeftMargin{17. }%
+\CSLLeftMargin{13. }%
 \CSLRightInline{European Covid-19 Forecast Hub. European {Covid-19
@@
 \leavevmode\vadjust pre{\hypertarget{ref-reichAccuracyRealtimeMultimodel2019}{}}%
-\CSLLeftMargin{18. }%
+\CSLLeftMargin{14. }%
 \CSLRightInline{Reich NG, McGowan CJ, Yamana TK, Tushar A, Ray EL,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
-\CSLLeftMargin{19. }%
+\CSLLeftMargin{15. }%
 \CSLRightInline{Tetlock PE, Mellers BA, Rohrbaugh N, Chen E. Forecasting
@@
 \leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
-\CSLLeftMargin{20. }%
+\CSLLeftMargin{16. }%
 \CSLRightInline{Atanasov P, Rescober P, Stone E, Swift SA,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
-\CSLLeftMargin{21. }%
+\CSLLeftMargin{17. }%
 \CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers E-J. Laypeople
@@
 \leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
-\CSLLeftMargin{22. }%
+\CSLLeftMargin{18. }%
 \CSLRightInline{ReplicationMarkets. Replication {Markets} -- {Reliable}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
-\CSLLeftMargin{23. }%
+\CSLLeftMargin{19. }%
 \CSLRightInline{Servan-Schreiber E, Wolfers J, Pennock DM, Galebach B.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
-\CSLLeftMargin{24. }%
+\CSLLeftMargin{20. }%
 \CSLRightInline{McAndrew TC, Reich NG. An expert judgment model to
@@
 \leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
-\CSLLeftMargin{25. }%
+\CSLLeftMargin{21. }%
 \CSLRightInline{Recchia G, Freeman ALJ, Spiegelhalter D. How well did
@@
 \leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
-\CSLLeftMargin{26. }%
+\CSLLeftMargin{22. }%
 \CSLRightInline{Metaculus. A {Preliminary Look} at {Metaculus} and
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
-\CSLLeftMargin{27. }%
+\CSLLeftMargin{23. }%
 \CSLRightInline{Hypermind. Hypermind \textbar{} {Supercollective}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
-\CSLLeftMargin{28. }%
+\CSLLeftMargin{24. }%
 \CSLRightInline{CSET Foretell. {CSET Foretell}. 2021 {[}cited 13 Oct
@@
 \leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
-\CSLLeftMargin{29. }%
+\CSLLeftMargin{25. }%
 \CSLRightInline{PredictIt. {PredictIt}. 2021 {[}cited 13 Oct 2021{]}.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
-\CSLLeftMargin{30. }%
+\CSLLeftMargin{26. }%
 \CSLRightInline{Held L, Meyer S, Bracher J. Probabilistic forecasting in
@@
 \leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
-\CSLLeftMargin{31. }%
+\CSLLeftMargin{27. }%
 \CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
-\CSLLeftMargin{32. }%
+\CSLLeftMargin{28. }%
 \CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ecdcDownloadHistoricalData2020}{}}%
-\CSLLeftMargin{33. }%
+\CSLLeftMargin{29. }%
 \CSLRightInline{ECDC. Download historical data (to 14 {December} 2020)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rkiRKICoronavirusSARSCoV22021}{}}%
-\CSLLeftMargin{34. }%
+\CSLLeftMargin{30. }%
 \CSLRightInline{RKI. {RKI} - {Coronavirus SARS-CoV-2} - {Aktueller
@@
 \leavevmode\vadjust pre{\hypertarget{ref-forsal.plRozbieznosciStatystykachKoronawirusa2020}{}}%
-\CSLLeftMargin{35. }%
+\CSLLeftMargin{31. }%
 \CSLRightInline{Forsal.pl. Rozbieżności w statystykach koronawirusa. 22
@@
 \leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
-\CSLLeftMargin{36. }%
+\CSLLeftMargin{32. }%
 \CSLRightInline{Ärzteblatt DÄG Redaktion Deutsches.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
-\CSLLeftMargin{37. }%
+\CSLLeftMargin{33. }%
 \CSLRightInline{Fay C, Guyader V, Rochette S, Girard C. Golem: A
@@
 \leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
-\CSLLeftMargin{38. }%
+\CSLLeftMargin{34. }%
 \CSLRightInline{Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
-\CSLLeftMargin{39. }%
+\CSLLeftMargin{35. }%
 \CSLRightInline{Our World in Data. {COVID-19 Data Explorer}. {Our World
@@
 \leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
-\CSLLeftMargin{40. }%
+\CSLLeftMargin{36. }%
 \CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
-\CSLLeftMargin{41. }%
+\CSLLeftMargin{37. }%
 \CSLRightInline{Fraser C. Estimating {Individual} and {Household
@@
 \leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation2020}{}}%
-\CSLLeftMargin{42. }%
+\CSLLeftMargin{38. }%
 \CSLRightInline{epiforecasts.io/covid. Covid-19: {Temporal} variation in
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
-\CSLLeftMargin{43. }%
+\CSLLeftMargin{39. }%
 \CSLRightInline{Sherratt K, Abbott S, Meakin SR, Hellewell J, Munday JD,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-abbottEstimatingTimevaryingReproduction2020a}{}}%
-\CSLLeftMargin{44. }%
+\CSLLeftMargin{40. }%
 \CSLRightInline{Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
-\CSLLeftMargin{45. }%
+\CSLLeftMargin{41. }%
 \CSLRightInline{Xu B, Gutierrez B, Hill S, Scarpino S, Loskill A, Wu J,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
-\CSLLeftMargin{46. }%
+\CSLLeftMargin{42. }%
 \CSLRightInline{Stan Development Team. RStan: The r interface to stan.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
-\CSLLeftMargin{47. }%
+\CSLLeftMargin{43. }%
 \CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG. Evaluating
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
-\CSLLeftMargin{48. }%
+\CSLLeftMargin{44. }%
 \CSLRightInline{Gneiting T, Raftery AE. Strictly proper scoring rules,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
-\CSLLeftMargin{49. }%
+\CSLLeftMargin{45. }%
 \CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Scoringutils:
@@
 \leavevmode\vadjust pre{\hypertarget{ref-deutschewelleCoronavirusGermanyImpose2020}{}}%
-\CSLLeftMargin{50. }%
+\CSLLeftMargin{46. }%
 \CSLRightInline{Deutsche Welle. Coronavirus: {Germany} to impose

### 2023-12-11 analysis/analysis.Rmd

@@
 
-    ggsave(here(output_dir, paste0(plotname, "-v4.png")), 
-           height = 9.1, width = 10)
+    ggsave(here(output_dir, paste0(plotname, "-v4.tiff")), 
+           height = 9.1, width = 10, device = "tiff", dpi = 300)
 }
@@
     ggsave(here(output_dir, 
-                paste0(plotname, "-", i, ".png")), width = 10, height = 11)
+                paste0(plotname, "-", i, ".tiff")), width = 10, height = 11, 
+           device = "tiff", dpi = 300)
 
@@
   ggsave(here("analysis", "plots", 
-              paste0("distribution_scores_wis-", i, ".png")), 
-         plot = pl_wis, height = 6, width = 9)
+              paste0("distribution_scores_wis-", i, ".tiff")), 
+         plot = pl_wis, height = 6, width = 9, device = "tiff", dpi = 300)
 }

### 2023-12-11 manuscript/S1 Acknowledgements.Rmd

--- 2022-08-04 manuscript/final submission/manuscript.tex
@@
-% Template for PLoS
-% Version 3.5 March 2018
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended
-% to minimize problems and delays during our production
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% Once your paper is accepted for publication,
-% PLEASE REMOVE ALL TRACKED CHANGES in this file
-% and leave only the final text of your manuscript.
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file.
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig" instead of "Figure".
-% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-%
-% Do not include text that is not math in the math environment.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column.
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
+---
+output: 
+  pdf_document:
+    keep_tex: true
+---
 
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+```{r setup, echo=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+```
 
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
+We would like to acknowledge (in a randomised order) the members of Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group at the the London School of Hygiene & Tropical Medicine:
 
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8x]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% cite package, to clean up citations in the main text. Do not remove.
-% \usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% color can be used to apply background shading to table cells only
-\usepackage[table]{xcolor}
-
-% array package and thick rules for tables
-\usepackage{array}
-
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-
-% create \thickcline for thick horizontal lines of variable length
-\newlength\savedwidth
-\newcommand\thickcline[1]{%
-  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-  \cline{#1}%
-  \noalign{\vskip\arrayrulewidth}%
-  \noalign{\global\arrayrulewidth\savedwidth}%
-}
-
-% \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-\hline
-\noalign{\global\arrayrulewidth\savedwidth}}
-
-% Remove comment for double spacing
-%\usepackage{setspace}
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-\renewcommand{\figurename}{Fig}
-
-% Use the PLoS provided BiBTeX style
-% \bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr,graphicx}
-\usepackage{epstopdf}
-%\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-%\setlength{\headheight}{27.023pt}
-%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\headrulewidth}{0pt}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\today}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-% tightlist command for lists without linebreak
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% Pandoc citation processing
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-% for Pandoc 2.8 to 2.10.1
-\newenvironment{cslreferences}%
-  {}%
-  {\par}
-% For Pandoc 2.11+
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\usepackage{lineno}
-\usepackage[T1]{fontenc}
-\linenumbers
-\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}}
-\newfloat{text}{thp}{}
-\floatname{text}{Text}
-\renewcommand{\figurename}{}
-\newcommand{\newfigurename}{Hello}
-\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-\usepackage{nameref,hyperref}
-\usepackage{caption}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
-
-\usepackage{forarray}
-\usepackage{xstring}
-\newcommand{\getIndex}[2]{
-  \ForEach{,}{\IfEq{#1}{\thislevelitem}{\number\thislevelcount\ExitForEach}{}}{#2}
-}
-
-\setcounter{secnumdepth}{0}
-
-\newcommand{\getAff}[1]{
-  \getIndex{#1}{London School of Hygiene \& Tropical Medicine,Karlsruhe
-Institute of Technology Institute of Economic Theory and Statistics,Max
-Planck Institute for Multidisciplinary Sciences,UK Health Security
-Agency,Imperial College London}
-}
-
-\begin{document}
-\vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{Comparing human and model-based forecasts of COVID-19 in
-Germany and
-Poland} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Nikos I. Bosse\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\textsuperscript{*},
-Sam Abbott\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Johannes Bracher\textsuperscript{\getAff{Karlsruhe Institute of
-Technology Institute of Economic Theory and Statistics}},
-Habakuk Hain\textsuperscript{\getAff{Max Planck Institute for
-Multidisciplinary Sciences}},
-Billy J. Quilty\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Mark Jit\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Edwin van Leeuwen\textsuperscript{\getAff{UK Health Security
-Agency}, \getAff{London School of Hygiene \& Tropical Medicine}},
-Anne Cori\textsuperscript{\getAff{Imperial College London}},
-Sebastian Funk\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\\
-\bigskip
-\textbf{\getAff{London School of Hygiene \& Tropical Medicine}}Centre
-for the Mathematical Modelling of Infectious Diseases, Department of
-Infectious Disease Epidemiology, London School of Hygiene \& Tropical
-Medicine, London, United Kingdom\\
-\textbf{\getAff{Karlsruhe Institute of Technology Institute of Economic
-Theory and Statistics}}Institute of Economic Theory and Statistics,
-Karlsruhe Institute of Technology, Karlsruhe, Germany\\
-\textbf{\getAff{Max Planck Institute for Multidisciplinary Sciences}}Max
-Planck Institute for Multidisciplinary Sciences, Göttingen, Germany\\
-\textbf{\getAff{UK Health Security Agency}}UK Health Security Agency,
-London United Kingdom\\
-\textbf{\getAff{Imperial College London}}MRC Centre for Outbreak
-Analysis and Modelling, Department of Infectious Disease Epidemiology,
-School of Public Health, Imperial College London, London, United
-Kingdom\\
-\bigskip
-* nikos.bosse@lshtm.ac.uk\\
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-Forecasts based on epidemiological modelling have played an important
-role in shaping public policy throughout the COVID-19 pandemic. This
-modelling combines knowledge about infectious disease dynamics with the
-subjective opinion of the researcher who develops and refines the model
-and often also adjusts model outputs. Developing a forecast model is
-difficult, resource- and time-consuming. It is therefore worth asking
-what modelling is able to add beyond the subjective opinion of the
-researcher alone. To investigate this, we analysed different real-time
-forecasts of cases of and deaths from COVID-19 in Germany and Poland
-over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
-We compared crowd forecasts elicited from researchers and volunteers,
-against a) forecasts from two semi-mechanistic models based on common
-epidemiological assumptions and b) the ensemble of all other models
-submitted to the Forecast Hub. We found crowd forecasts, despite being
-overconfident, to outperform all other methods across all forecast
-horizons when forecasting cases (weighted interval score relative to the
-Hub ensemble 2 weeks ahead: 0.89). Forecasts based on computational
-models performed comparably better when predicting deaths (rel. WIS
-1.26), suggesting that epidemiological modelling and human judgement can
-complement each other in important ways.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step.
-% Author Summary not valid for PLOS ONE submissions.
-\section*{Author summary}
-Mathematical models of COVID-19 have played a key role in informing
-governments across the world. While mathematical models are informed by
-our knowledge of infectious disease dynamics, they are ultimately
-developed and iteratively adjusted by the researchers and shaped by
-their subjective opinions. To investigate what modelling is able to add
-beyond the subjective opinion of the researcher alone, we compared human
-forecasts with model-based predictions of COVID-19 cases and deaths
-submitted to the so-called German/Polish Forecast Hub (which collates a
-variety of models from a range of teams). \textbar{} We found that our
-human forecasts consistently outperformed an aggregate of all available
-model-based forecasts when predicting cases, but not when predicting
-deaths. Our findings suggest that human insight may be most valuable
-when forecasting highly uncertain quantities, which depend on many
-factors that are hard to model using equations, while mathematical
-models may be most useful in settings like predicting deaths, where
-leading indicators with a clear connection to the target variable are
-available. This potentially has very relevant policy implications, as
-agencies informing policy-makers could benefit from routinely eliciting
-human forecasts in addition to model-based predictions to inform
-policies.
-
-\linenumbers
-
-% Use "Eq" instead of "Equation" for equation citations.
-\newcommand{\createmylabel}[2]{%
-  \phantomsection
-  #1\def\@currentlabel{\unexpanded{#1}}\label{#2}%
-}
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Infectious disease modelling has a long tradition and has helped inform
-public health decisions both through scenario modelling, as well as
-actual forecasts of (among others) influenza {[}e.g. 1,2--4{]}, dengue
-fever {[}e.g. 5,6,7{]}, ebola {[}e.g. 8,9{]}, chikungunya {[}e.g.
-10,11{]} and now COVID-19 {[}e.g. 12,13--17{]}. Applications of
-epidemiological models differ in the way they make statements about the
-future. Forecasts aim to predict the future as it will occur, while
-scenario modelling and projections aim to represent what the future
-could look like under certain scenario assumptions or if conditions
-stayed the same as they were in the past. Forecasts can be judged by
-comparing them against observed data. Since it is much harder to fairly
-assess the accuracy and usefulness of projections and scenario modelling
-in the same way, this work focuses on forecasts, which represent only a
-subset of all epidemiological modelling.
-
-Since March 2020, forecasts of COVID-19 from multiple teams have been
-collected, aggregated and compared by Forecast Hubs such as the US
-Forecast Hub {[}13,14{]}, the German and Polish Forecast Hub {[}15,16{]}
-and the European Forecast Hub {[}17{]}. Often, different individual
-forecasts are combined into a single forecast, e.g.~by taking the mean
-or median of all forecasts. These ensemble forecasts usually tend to
-perform better and more consistently than individual forecasts (see e.g.
-{[}6{]}; {[}18{]}).
-
-Individual computational models usually rely to varying degrees on
-mechanistic assumptions about infectious disease dynamics (such as
-SIR-type compartmental models that aim to represent how individuals move
-from being susceptible to infected and then recovered or dead). Some are
-more statistical in nature (such as time series models that detect
-statistical patterns without explicitly modelling disease dynamics). How
-exactly such a mathematical or computational model is constructed and
-which assumptions are made depends on subjective opinion and judgement
-of the researcher who develops and refines the model. Models are
-commonly adjusted and improved based on whether the model output looks
-plausible to the researchers involved.
-
-The process of model construction and refinement is laborious and
-time-consuming, and it is therefore worth asking what modelling can add
-beyond the subjective judgment of the researcher alone. In this work, we
-ask this question specifically in the context of predictive performance,
-and set aside other advantages of epidemiological modelling (such as
-reproducibility or the ability to obtain a deeper fundamental
-understanding of how diseases spread). One natural way to do this is to
-compare the predictive performance of forecasts based on computational
-models (``model-based forecasts'') against forecasts made by individual
-humans without explicit use of a computer model (``direct human
-forecasts'') or a combination of multiple such forecasts (``crowd
-forecasts'').
-
-Previous work has examined such direct human forecasts in various
-contexts, such as geopolitics {[}19,20{]}, meta-science {[}21,22{]},
-sports {[}23{]} and epidemiology {[}11,24,25{]}. Several prediction
-platforms {[}26--28{]} and prediction markets {[}29{]} have been created
-to collate expert and non-expert predictions. However, with the notable
-exception of {[}11{]}, these forecasts were not designed to be evaluated
-alongside model-based forecasts and usually follow their own (often
-binary) prediction formats. Direct human forecasts may be able to take
-into account insights and relationships between variables which are hard
-to specify using epidemiological models. However, it is not entirely
-clear in which situations human forecasts perform well or badly. For
-example, {[}11{]} found that humans could outperform computer models at
-predicting the 2014/15 and 2015/16 flu season in the US, a setting where
-the disease was well known and information about previous seasons was
-available. However, humans tended to do slightly worse at predicting the
-2014/15 outbreak of chikungunya in the Americas, a disease previously
-largely unobserved and unknown in these regions at the time.
-
-In this study, we analyse the performance of direct human forecasts
-relative to model-based forecasts and discuss the added benefit of
-epidemiological modelling over human judgement alone. As a case study,
-we use different forecasts, involving varying degrees of human
-intervention, which we submitted in real time to the German and Polish
-Forecast Hub. In contrast to {[}11{]} we elicited not only point
-predictions, but full predictive distributions (``probabilistic
-forecasts'', see e.g. {[}30{]}) from participants. This allows us to
-compare not only predictive accuracy, but also how well human
-forecasters and model-based forecasts were able to quantify forecast
-uncertainty.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{ethics-statement}{%
-\subsection{Ethics statement}\label{ethics-statement}}
-
-This study has been approved by the London School of Hygiene \& Tropical
-Medicine Research Ethics Committee (reference number 22290). Consent
-from participants was obtained in written form.
-
-\hypertarget{overview}{%
-\subsection{Overview}\label{overview}}
-
-We created and submitted the following forecasts to the German and
-Polish Forecast Hub: 1) a direct human forecast (henceforth called
-``crowd forecast''), elicited from participants through a web
-application {[}31{]} and 2) two semi-mechanistic model-based forecasts
-(``renewal model'' and ``convolution model'') informed by basic
-assumptions about COVID-19 epidemiology. While the two semi-mechanistic
-forecasts were necessarily shaped by our implicit assumptions and
-decisions, they were designed such as to minimise the amount of human
-intervention involved. For example, we refrained from adjusting model
-outputs or refining the models based on past performance. Forecasts were
-created in real time over a period of 21 weeks from October 12th 2020
-until March 1st 2021 and submitted to the German and Polish Forecast hub
-{[}15,16{]}. All code and tools necessary to generate the forecasts and
-make a forecast submission are available in the
-\texttt{covid.german.forecasts} R package {[}32{]}. This repository also
-contains a record of all forecasts submitted to the German and Polish
-Forecast Hub. Forecasts were evaluated using a variety of scoring
-metrics and compared among each other and against an ensemble of all
-other models submitted to the German and Polish Forecast Hub.
-
-\hypertarget{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}{%
-\subsection{Forecast targets and interaction with the German and Polish
-Forecast
-Hub}\label{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}}
-
-The German and Polish Forecast Hub (now mostly merged into the {[}17{]})
-elicits predictions for various COVID-19 related forecast targets from
-different research groups every week. Forecasts had to be made every
-Monday (with submissions allowed until Tuesday 3pm) and were permitted
-to use any data that was available by Monday 11.59pm. We submitted
-forecasts for incident and cumulative weekly reported numbers of cases
-of and deaths from COVID-19 on a national level in Germany and Poland
-over a one to four week forecast horizon. Forecasts were submitted on
-Mondays, but weeks were defined as ending on a Saturday (and starting on
-Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26
-days. Submissions were required in a quantile-based format with 23
-quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10,
-0.15, \ldots, 0.95, 0.975, 0.99. Forecasts submitted to the Forecast Hub
-were combined into different ensembles every week, with the median
-ensemble (i.e., the \(\alpha\)-quantile of the ensemble is given by the
-median of all submitted \(\alpha\)-quantiles) being the default ensemble
-shown on all official Forecast hub visualisations
-(https://kitmetricslab.github.io/forecasthub/forecast).
-
-Data on daily reported test positive cases and deaths linked to COVID-19
-were provided by the organisers of the German and Polish Forecast hub.
-Until December 14th, 2020, these data were sourced from the European
-Centre for Disease Control {[}33{]}. After ECDC stopped publishing daily
-data, observations were sourced from the Robert Koch Institute (RKI) and
-the Polish Ministry of Health for the remainder of the submission period
-{[}34{]}. These data are subject to reporting artefacts, (such as for
-example delayed case reporting in Poland on the 24th November,
-{[}35{]}), changes in reporting over time, and variation in testing
-regimes (for example in Germany from the 11th of November on, {[}36{]}).
-The ECDC data as well as the data published by the Polish Ministry of
-Health were also subject to data revisions, although most of them (with
-a notable exception of a data update for October 12 2020 in Germany)
-only affected daily, not weekly data (see Figs
-\nameref{fig:daily-truth-update} and \nameref{fig:weekly-truth-update}).
-
-\hypertarget{crowd-forecasts}{%
-\subsection{Crowd forecasts}\label{crowd-forecasts}}
-
-Our crowd forecasts were created as an ensemble of forecasts made by
-individual participants every week through a web application
-(https://cmmid-lshtm.shinyapps.io/crowd-forecast/). Weekly forecasts had
-to be submitted before Tuesday 12pm every week, but participants were
-asked to only use any information or data that was already available by
-Monday night. The application was built using the \texttt{shiny} and
-\texttt{golem} R packages {[}37,38{]} and is available in the
-\texttt{crowdforecastr} R package {[}31{]}. To make a forecast in the
-application participants could select a predictive distribution (with
-the default being log-normal) to represent the probability that the
-forecasted quantity took certain values. Median and width of the
-uncertainty could be adjusted by either interacting with a figure
-showing their forecast or providing numerical values (see screenshot in
-\nameref{fig:screenshot} in the SI). The default shown was a repetition
-of the last known observation with constant uncertainty around it
-computed as the standard deviation of the last four changes in weekly
-log observed forecasts (i.e.~as
-\(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
-A comparison of the crowd forecasts against the default baseline shown
-in the application is displayed in \nameref{fig:compare-forecasters} in
-the Appendix. Our interface also allowed participants to view past
-observations based on the hub data, as well as their forecasts, on a
-logarithmic scale and presented additional contextual COVID-19 data
-sourced from {[}39{]}. These data included, for example, notifications
-of both test positive COVID-19 cases and COVID-19 linked deaths and the
-number of COVID-19 tests conducted over time. From November 26 2020 on
-we displayed weekly small reports with a visualisation of past forecasts
-and scores on our website, epiforecasts.io.
-
-Forecasts were stored in a Google Sheet and downloaded, cleaned and
-processed every week for submission to the Forecast Hub. If a forecaster
-had submitted multiple predictions for a single target, only the latest
-submission was kept. Information on the chosen distribution as well as
-the parameters for median and width were used to obtain the required set
-of 23 quantiles from that distribution. Forecasts from all forecasters
-were then aggregated using an unweighted quantile-wise mean (i.e., the
-\(\alpha\)-quantile of the ensemble is given by the mean of all
-submitted \(\alpha\)-quantiles). To avoid issues with users trying out
-the app and submitting a random forecast, we required that a forecaster
-needed to make a forecast for at least two targets for a given forecast
-in order to be included in the crowd forecast ensemble. On a few
-occasions we deleted forecasts that were clearly the result of a user or
-software error (such as for example forecasts that were zero
-everywhere).
-
-Participants were recruited mostly within the Centre of Mathematical
-Modeling of Infectious Diseases at the London School of Hygiene \&
-Tropical Medicine, but participants were also invited personally or via
-social media to submit predictions. Depending on whether they had a
-background in either statistics, forecasting or epidemiology,
-participants were asked to self-identify as `experts' or `non-experts'.
-
-\hypertarget{model-based-forecasts}{%
-\subsection{Model-based forecasts}\label{model-based-forecasts}}
-
-We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R
-package (version 1.3.3) as our model-based forecasts {[}40{]}. The first
-of these models, here called ``renewal model'', used the renewal
-equation {[}41{]} to predict reported cases and deaths (see details in
-S1 Text in the SI). It estimated the effective reproduction number
-\(R_t\) (the average number of people each person infected at time t is
-expected to infect in turn) and modelled future infections as a weighted
-sum of past infection multiplied by \(R_t\). \(R_t\) was assumed to stay
-constant beyond the forecast date, roughly corresponding to continuing
-the latest exponential trend in infections. On the 9th of November we
-altered the date when \(R_t\) was assumed to be constant from two weeks
-prior to the date of the forecast to the forecast date, which we found
-to yield a more stable \(R_t\) estimate. Reported case and death
-notifications were obtained by convolving predicted infections over
-data-based delay distributions {[}40,42--44{]} to model the time between
-infection and report date. The renewal model was used to predict cases
-as well as deaths with forecasts being generated for each target
-separately. Death forecasts from the renewal model were therefore not
-informed by past cases. One submission of the renewal model on December
-28th 2020 was delayed and therefore not included in the official
-Forecast hub ensemble.
-
-The second model (``convolution model'', see details in SI) was only
-used to forecast deaths and was added later, starting December 7th 2020
-(with the first forecast from December 7th suffering from a software bug
-and therefore disregarded in all further analyses). The convolution
-model was submitted, but never included in the official Forecast hub
-ensemble due to concerns that it could be too similar to the renewal
-model. The convolution model predicted deaths as a fraction of infected
-people who would die with some delay, by using a convolution of reported
-cases with a distribution that described the delay from case report to
-death and a scaling factor (the case-fatality ratio). Both the renewal
-and the convolution model used daily observations and assumed a negative
-binomial observation model with a multiplicative day-of-the-week effect
-{[}40{]}.
-
-Line list data used to inform the prior for the delay from symptom onset
-to test positive case report or death in the model-based forecasts was
-sourced from {[}45{]} with data available up to the 1st of August. All
-model fitting was done using Markov-chain Monte Carlo (MCMC) in stan
-{[}46{]} with each location and forecast target being fitted separately.
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-For the main analysis we focused mostly on two week ahead forecasts, as
-COVID-19 forecasts, especially for cases, were in the past found to have
-poor predictive performance beyond this horizon {[}15{]}. Forecasts for
-cases were scored using the full period from October 2020 until March
-2021. To ensure comparability between models, all death forecasts were
-scored using only the period from December 14th on, where all models
-including the convolution model were available. To ensure robustness of
-our results we conducted a sensitivity analysis where all forecasts
-(including cases) were scored only over the later period for which all
-forecasts were available (see \nameref{fig:agg-performance-all-late} and
-\nameref{tab:score-table-late-2} and \nameref{tab:score-table-late-4}s
-in the SI). Results remained broadly unchanged.
-
-Forecasts were analysed using the following scoring metrics: The
-weighted interval score (WIS) {[}47{]}, the absolute error, relative
-bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule {[}48{]}, meaning that in expectation
-the score is optimised by reporting a predictive distribution that is
-identical to the true data-generating distribution. Forecasters are
-therefore incentivised to report their true belief about the future. The
-WIS can be understood as a generalisation of the absolute error to
-quantile-based forecasts (also meaning that smaller values are better)
-and can be decomposed into three separate penalties: forecast spread
-(i.e.~uncertainty of forecasts), over-prediction and under-prediction.
-While the over- and under-prediction components of the WIS capture the
-amount of over-prediction and under-prediction in absolute terms, we
-also look at a relative tendency to make biased forecasts. The bias
-metric {[}9{]} we use captures how much probability mass of the forecast
-was above or below the true value (mapped to values between -1 and 1)
-and therefore represents a general tendency to over- or under-predict in
-relative terms. A value of -1 implies that all quantiles of the
-predictive distribution are below the observed value and a value of 1
-that all quantiles are above the observed value. Empirical coverage is
-the percentage of observed values that fall inside a given prediction
-interval (e.g.~how many observed values fall inside all 50\% prediction
-intervals). Scoring metrics are explained in more detail in
-\nameref{tab:scoring-metrics} in the SI. All scores were calculated
-using the \texttt{scoringutils} R package {[}49{]}.
-
-At all stages of the evaluation our forecasts were compared to the
-median ensemble of all \emph{other} models submitted to the German and
-Polish Forecast Hub (``Hub ensemble''). This ``Hub ensemble'' was
-retrospectively computed and excludes all our models, leaving on average
-five ensemble member models (see \nameref{tab:table-ensemble-versions}
-and \nameref{fig:num-ensemble-members} in the SI). What we call ``Hub
-ensemble'' in this article therefore differs from the ``official Hub
-ensemble'' (here called ``hub-ensemble-realised'') which included crowd
-forecasts as well as renewal model forecasts. To enhance
-interpretability of scores we mainly report WIS relative to the Hub
-ensemble in the main text, i.e.~we divided the average scores for a
-given model by the average score achieved by the Hub ensemble on the
-same set of forecasts (with values \textgreater1 implying worse and
-values \textless1 implying better performance than the Hub ensemble). In
-addition to comparing our forecasts against the hub ensemble excluding
-our models, we also assessed the impact of our forecasts on the
-performance of the forecasting hub by recalculating separate versions of
-the Hub ensemble with only some (or all) of our forecasts included.
-Versions that included either all of our models
-(``hub-ensemble-with-all'') or only one of them
-(``hub-ensemble-with-X'') were computed retrospectively.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{crowd-forecast-participation}{%
-\subsection{Crowd forecast
-participation}\label{crowd-forecast-participation}}
-
-A total number of 32 participants submitted forecasts, 17 of those
-self-identified as `expert' in either forecasting or epidemiology. The
-median number of forecasters for any given forecast target was 6, the
-minimum 2 and the maximum 10. The mean number of submissions from an
-individual forecaster was 4.7 but the median number was only one - most
-participants dropped out after their first submission. Only two
-participants submitted a forecast every single week, both of whom are
-authors on this study.
-
-\begin{figure}[H]
-\caption{\bf{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.}}
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons
-\label{fig:agg-performance-all}
-\end{figure}
-
-\begin{figure}[H]
-\caption{\bf{Two week ahead forecasts and corresponding scores. }}
-A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.
-\label{fig:forecasts-and-truth}
-\end{figure}
-
-\hypertarget{case-forecasts}{%
-\subsection{Case Forecasts}\label{case-forecasts}}
-
-For cases, crowd forecasts had a lower mean weighted interval score
-(WIS, lower values indicate better performance) than both the renewal
-model and the Hub ensemble across all forecast horizons (Fig
-\ref{fig:agg-performance-all}A) and locations (Fig
-\nameref{fig:performance-locations-rel}A). For two week ahead forecasts,
-mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts
-and 1.40 for the renewal model (\nameref{tab:score-table-2} Table).
-Across all forecasting approaches, locations and forecast horizons, the
-distribution of WIS values was very right-skewed, and average
-performance was heavily influenced by outliers (Fig
-\ref{fig:distribution-scores}). Overall, low variance in forecast
-performance was closely linked with good mean performance (Figs
-\ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A),
-suggesting that the ability to avoid large errors was an important
-factor in determining overall performance. The impact of outlier values
-was especially pronounced for the renewal model, which had more outliers
-(Fig \ref{fig:distribution-scores}), as well as the highest standard
-deviation of WIS values (standard deviation of the WIS relative to the
-WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon),
-while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub
-ensemble (= 1) showed more stable performance.
-
-To varying degrees, all forecasts exhibited trend-following behaviour
-and were rarely able to predict a change in trend before it had
-happened. For example, all forecasts failed to predict the change in
-trend from increase to decrease that happened in November in Germany and
-severely overshot reported cases (Fig \ref{fig:forecasts-and-truth}A).
-This was most striking for the renewal model, which extrapolated
-unconstrained exponential growth based on the recent past of
-observations. The Hub ensemble and the crowd forecast, which had both
-been under-predicting throughout October, also failed to predict the
-change in trend after cases peaked, but less severely so. Human
-forecasters, possibly aware of the semi-lockdown announced on November
-2nd 2020 {[}50{]} and the change in the testing regime (with stricter
-test criteria) on November 11th 2020 {[}36{]}, were fastest to adapt to
-the new trend, and the Hub ensemble slowest. In December, cases rose
-again in Germany, with all models under-predicting this growth to
-varying extents. As in October, the renewal model captured the phase of
-exponential growth in cases slightly better than other approaches, but
-again overshot when reported case numbers fell over Christmas. The large
-variance in predictions in January in Germany (severe under-prediction
-followed by severe over-prediction) may in part be caused by the fact
-that the renewal model operated on daily data and therefore was
-susceptible to fluctuations in daily reporting around Christmas that
-would not have influenced on weekly reporting. Similar trends in
-performance were evident in Poland, with the crowd forecast quickest at
-adapting to the change in trend in November. In general, there were
-fewer large outlier forecasts in Poland and in particular the renewal
-model performed more in line with other forecasts there.
-
-All forecasting approaches, including the Hub ensemble, were
-overconfident, i.e.~they showed lower than nominal coverage (meaning
-that 50\% (90\%) prediction intervals generally covered less than 50\%
-(90\%) of the actually observed values) (Fig
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
-Coverage for all forecasts deteriorated with increasing forecast
-horizon, indicating that all forecasting approaches struggled to
-quantify uncertainty appropriately for case forecasts. This was
-especially an issue for crowd forecasts, which had markedly shorter
-prediction intervals (i.e., narrower and more confident predictive
-distributions) than other approaches (Fig
-\ref{fig:agg-performance-all}E) and only showed a small increase in
-uncertainty across forecast horizons. The crowd forecasts prediction
-intervals were also noticeably narrower than the default baseline shown
-to forecasters in the application (see
-\nameref{fig:compare-forecasters}).
-
-In spite of good performance in terms of the absolute error (Fig
-\ref{fig:agg-performance-all}G), the narrow forecast intervals led to
-forecasts which were severely overconfident (covering only 36\% and 55\%
-of all observations with the 50\% and 90\% prediction intervals of all
-forecasts made at a two week forecast horizon, and only 5\% and 38\%
-four weeks ahead) (Fig \ref{fig:agg-performance-all}C, D as well as
-\nameref{tab:score-table-2} and \nameref{tab:score-table-4}s). Despite
-worse performance in terms of absolute error (Fig
-\ref{fig:agg-performance-all}G), the renewal model achieved better
-calibration (comparable to the Hub ensemble), as uncertainty increased
-rapidly across forecast horizons. The crowd forecasts, on the other
-hand, showed a smaller bias than the renewal model, but were
-overconfident.
-
-The renewal model exhibited a noticeable tendency towards
-over-predicting reported cases across all horizons. The crowd forecast
-tended to over-predict at longer forecast horizons, whereas the Hub
-ensemble showed no systematic bias (Fig \ref{fig:agg-performance-all}F).
-Regardless of a general relative tendency to over-predict, all
-forecasting approaches incurred larger absolute penalties from over-
-than from under-prediction (see decomposition of the WIS into absolute
-penalties for over-prediction, under-prediction and dispersion in Figs
-\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as
-well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
-
-Generally, trends in overall performance were broadly similar across
-locations (Figs \nameref{fig:performance-locations} and
-\nameref{fig:performance-locations-rel}). Due to the differing
-population sizes and numbers of notifications in Germany and Poland
-absolute scores were difficult to compare directly. However, relative to
-the Hub ensemble, the crowd forecasts performed noticeably better in
-Germany than in Poland and the renewal model better in Poland than in
-Germany (Figs \nameref{fig:performance-locations-rel}A,
-\nameref{fig:performance-locations-rel}G,
-\nameref{fig:agg-performance-all-Germany},
-\nameref{fig:agg-performance-all-Poland}).
-
-\hypertarget{death-forecasts}{%
-\subsection{Death Forecasts}\label{death-forecasts}}
-
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as
-our model-based approaches across all forecast horizons and locations
-(Figs \ref{fig:agg-performance-all}B and
-\nameref{fig:performance-locations}B). Relative WIS values for the
-models two weeks ahead were 1.22 (convolution model), 1.26 (crowd
-forecast), 1 (Hub ensemble) and 1.79 (renewal model). The crowd
-forecasts performed better than the renewal model across all forecast
-horizons and locations (Figs \ref{fig:agg-performance-all}B and
-\nameref{fig:performance-locations}B), and also better than the
-convolution model three and four weeks ahead. Poor performance of the
-renewal model, especially at longer horizons, indicates that an approach
-that does not know about past cases, but instead estimates and projects
-a separate \(R_t\) trace from deaths, does not use the available
-information efficiently. The convolution model was able to outperform
-both the renewal model and the crowd forecasts at shorter forecast
-horizons (where the delay between cases and deaths means that future
-deaths are largely informed by present cases), but saw performance
-deteriorate at three and four weeks ahead (where case predictions from
-the renewal model were increasingly used to inform death predictions)
-(Fig \ref{fig:agg-performance-all}B, \nameref{tab:score-table-4}).
-
-As past cases and hospitalisations can be used as predictors, predicting
-a change in trend may be easier for deaths than for cases. Even though
-all forecasts generally struggled with this, there were some instances
-where changing trends were well captured or even anticipated. In Poland,
-for example, the Hub ensemble was able to capture or even anticipate the
-peak in deaths in December quite well (whereas the renewal model and
-crowd forecast did not). The renewal model, which mostly exhibited
-trend-following behaviour, correctly predicted another increase in
-weekly deaths in mid-January (potentially based on changes in daily
-deaths, as the renewal model did not know about past cases). In Germany
-in early January, all models predicted a decrease in deaths two to three
-weeks before it actually happened. Predictions from the renewal model at
-that time were likely strongly influenced by an unexpected drop in
-reported deaths in December. The other forecasting approaches and in
-particular, the convolution model may have been affected by potentially
-under-reported case numbers around Christmas. When the decrease that all
-models had predicted to happen in early January failed to materialise,
-the renewal model and the crowd forecast noticeably over-corrected and
-over-predicted deaths in the following weeks, while the Hub ensemble,
-and to a slightly lesser degree, the convolution model were able to
-capture the downturn well when it finally happened at the end of
-January.
-
-Death forecasts, generally, showed greater coverage of the 50\% and 90\%
-prediction intervals than case forecasts and no decrease in coverage
-across forecast horizons, indicating that it might be easier to
-appropriately quantify uncertainty for death forecasts. The Hub ensemble
-had the greatest coverage, with empirical coverage of the 50\% and 90\%
-prediction intervals exceeding 50\%, and 90\%, respectively, across all
-forecast horizons. Coverage for the crowd forecasts and our model-based
-approaches was generally lower than that of the Hub ensemble and mostly
-slightly lower than nominal coverage (Figs
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D). As
-for cases, the crowd forecast tended to have the narrowest prediction
-intervals and uncertainty increased most slowly across forecast
-horizons, and the renewal model forecasts generally were widest. The
-convolution model had relatively narrow prediction intervals for short
-forecast horizons, but had rapidly (and non-linearly) increasing
-uncertainty for longer forecast horizons, driven by increasing
-uncertainty in the underlying case forecasts.
-
-For deaths, the ensemble of crowd forecasts had a consistent tendency to
-over-predict (see Fig \ref{fig:agg-performance-all}F). The convolution
-model had a strong tendency to under-predict, with the magnitude of
-under-prediction steadily decreasing for longer forecast horizons. The
-renewal model (which over-predicted for cases) and the Hub ensemble
-slightly tended towards under-prediction. For deaths, absolute over- and
-under-prediction penalties were more in line with a general relative
-tendency to over- or under-predict than for cases (Figs
-\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as
-well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
-
-\begin{figure}[H]
-\caption{\bf{Distribution of scores. }}
-A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
-Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores.
-\label{fig:distribution-scores}
-\end{figure}
-
-\begin{figure}[H]
-\caption{\bf{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.}}
-“Hub-ensemble”  extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.
-\label{fig:agg-performance-ensemble-rel}
-\end{figure}
-
-\hypertarget{contribution-to-the-forecast-hub}{%
-\subsection{Contribution to the Forecast
-Hub}\label{contribution-to-the-forecast-hub}}
-
-\label{contributions-hub}
-
-Of our three models, only the renewal model and the crowd forecast were
-included in the official Forecast Hub median ensemble
-(``hub-ensemble-realised''), while the convolution model was never
-included as it was deemed too similar to the existing renewal model. In
-the official Hub ensemble, there were on average 7.1 models included
-(including our own), with a median of 7, a minimum of 4 (on 28 December
-2020 over the Christmas period) and a maximum of 10. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively. An
-overview of all models and ensemble versions is shown in
-\nameref{tab:table-ensemble-versions} in the SI.
-
-For cases, our contributions (compared to the Hub ensemble without our
-contributions) consistently improved performance across all forecasting
-horizons (rel. WIS 0.9 two weeks ahead, see
-\nameref{tab:score-table-ensemble-2} Table). Contributions from the
-crowd forecasts alone also improved performance of the Hub ensemble
-across all forecast horizons, while contributions from the renewal model
-had a negative effect for longer horizons (rel. WIS 1.02 three weeks
-ahead, 1.06 four weeks ahead). The realised ensemble including both
-models performed better or equal compared to all versions with only one
-model included for up to three weeks ahead, suggesting synergistic
-effects. Only for predictions four weeks ahead would removing the
-renewal model have improved performance
-(\nameref{tab:score-table-ensemble-4}). The realised ensemble performed
-comparably to the crowd forecasts for predictions one to two weeks
-ahead, and worse for greater forecast horizons.
-
-For deaths, contributions from the renewal model and crowd forecast
-together improved performance only for one week ahead predictions and
-showed an increasingly negative impact on performance for longer
-horizons (rel. WIS of the Hub-ensemble-realised 1.01 two weeks ahead,
-1.05 four weeks ahead, \ref{tab:score-table-ensemble-2} and
-\ref{tab:score-table-ensemble-4}s). Individual contributions from both
-the renewal model and the crowd forecast were largely negative, while a
-version of the Hub ensemble with only the convolution model included
-would have performed consistently better across all forecast horizons
-(with the positive impact increasing for longer horizons). This is
-especially interesting as the convolution model performed consistently
-worse than the pre-existing Hub ensemble (Fig
-\ref{fig:agg-performance-all}) and especially worse for longer horizons.
-
-We also considered the impact of our contributions on a version of the
-Hub ensemble constructed by taking the quantile-wise mean, rather than
-the median. General trends were similar, with the notable exception of
-the convolution model, which had a consistently positive impact on the
-median ensemble, but a mixed and mostly slightly negative impact on the
-mean ensemble (Figs \ref{fig:agg-performance-ensemble-rel}B and
-\nameref{fig:agg-performance-ensemble-mean}B). This may happen if a
-model is more correct directionally relative to the pre-existing
-ensemble, but overshoots in absolute terms, thereby moving the ensemble
-too far. For both the mean and the median ensemble, changes in
-performance from adding or removing models were of a similar order of
-magnitude, suggesting that at least in this instance, with a relatively
-small ensemble size, the median ensemble was not necessarily more
-`robust' to changes than the mean ensemble. However, the ensemble
-version with all our forecasts included (``hub-ensemble-with-all'')
-tended to perform relatively better for the median ensemble than the
-mean ensemble, suggesting that adding more models may be more beneficial
-or `safer' for the median than for the mean ensemble as directional
-errors can more easily cancel out than errors in absolute terms.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Epidemiological forecasting modelling combines knowledge about
-infectious disease dynamics with the subjective opinion of the
-researcher who develops and refines the model. In this study, we
-compared forecasts of cases of and deaths from COVID-19 in Germany and
-Poland based purely on human judgement and elicited from a crowd of
-researchers and volunteers against forecasts from two semi-mechanistic
-epidemiological models. In spite of the small number of participants and
-a general tendency to be overconfident, crowd forecasts consistently
-outperformed our epidemiological models as well as the Hub ensemble when
-forecasting cases but not when forecasting deaths. This suggests that
-humans might be relatively good at foreseeing trends that are hard to
-model but may struggle to form an intuition for the exact relationship
-between cases and deaths.
-
-Past studies have evaluated the performance of model-based forecasting
-approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of
-(expert-tuned) model-based approaches {[}e.g. 12,13,14{]}, or
-exclusively on human forecasts {[}19,20,24,25{]}. In contrast, we
-directly compared human and model-based forecasts. This is similar to
-the approach taken by {[}11{]}, but extends it in several ways. While
-Farrow et al.~only asked for point predictions and constructed a
-predictive distribution from these, we asked participants to provide a
-full predictive distribution, allowing us to compare human forecasts and
-models without any further assumptions, as well as to analyse how humans
-quantified their uncertainty. In addition, we compared crowd forecasts
-to two semi-mechanistic models informed by basic epidemiological
-knowledge of COVID-19, allowing us to assess not only relative
-performance but also to analyse qualitative differences between human
-judgement and model-based insight. In terms of interpretability of the
-results, exact knowledge of our two models, as well as focus on a
-limited set of targets and locations was a major advantage of our study
-compared to larger studies conducted by the Forecast Hubs
-{[}12--15,17{]}.
-
-The strong performance of crowd forecasts in our study is in line with
-results from Farrow et al.~who also report strong performance of human
-predictions in past Flu challenges despite difficulties to recruit a
-large number of participants. The advantage of crowd forecasts we
-observed over our semi-mechanistic models is likely in part explained by
-the fact that we compared an ensemble of crowd forecasts with single
-models. However, this probably explains only part of the difference, and
-performance relative to the Hub ensemble strongly suggests that human
-insight is valuable when forecasting highly volatile and potentially
-hard-to-predict quantities such as case numbers. One potential
-explanation is that humans can have access to data that is not available
-to or hard to integrate into model-based forecasts. Relatively good
-performance of our semi-mechanistic models short-term, but not
-longer-term, suggests that model-based forecasts are helpful to
-extrapolate from current conditions, but require some form of human
-intervention or additional assumptions to inform forecasts when
-conditions change over time. This human intervention may be particularly
-important when dealing with artefacts in reporting and data anomalies
-(and especially when using daily, rather than weekly data). The large
-variance in predictions in January in Germany for example (severe
-under-prediction followed by severe over-prediction, see Fig
-\ref{fig:forecasts-and-truth}A), may in part be caused by the fact that
-the renewal model operated on daily data and therefore was susceptible
-to fluctuations in daily reporting which have less of an influence on
-weekly reporting.
-
-Our results suggest that human intervention may be less beneficial when
-forecasting deaths (especially at shorter horizons, when deaths are
-largely dependent on already observed cases), which benefits from the
-ability to model the delays and exact epidemiological relationships
-between different leading and lagged indicators. Relatively good
-performance of the convolution model, especially compared to the poor
-performance of the renewal model on deaths (which used only deaths to
-estimate and predict the effective reproduction number) underlines the
-importance of including leading indicators such as cases as a predictor
-for deaths.
-
-Given the low number of participants in our study, it is difficult to
-generalise conclusions about crowd predictions to other settings. Using
-R shiny as a platform for the web application arguably created some
-limits to user experience and performance, influencing the number of
-participants and potentially creating a self-selection effect.
-Motivating forecasters to contribute regularly proved challenging,
-especially given that the majority of our participants were from the UK
-and may not have been familiar with all relevant details of the
-situation in Germany and Poland. On the other hand, R shiny facilitated
-quick development and allowed us to provide our crowd forecasting
-tooling as an open source R package, meaning that it is available for
-others to use, for example in settings like early-stage outbreaks where
-model-based forecasts are not available. In light of the relatively
-small number of Hub ensemble models, performance of the Hub ensemble is
-also difficult to generalise. More research is needed to replicate these
-findings and investigate how crowd forecasts compare against the types
-of models and model ensembles policy makers use to inform their
-decisions.
-
-Our work suggests that crowd forecasts and model-based forecasts could
-have different strengths and may be able to complement each other. When
-choosing a suitable approach for a given task it is important to take
-into account how the output will be used. In this work we focused on
-forecasts (which aim to predict future data points whilst accounting for
-all factors that might influence them), whereas policy makers might be
-more interested in projections (which show what would happen in the
-absence of any events that could change the trend) or scenario
-modelling. Forecasts may not be a suitable basis for informing policy
-decisions, if forecasters already have factored in the expectation of a
-future intervention. Model-based approaches can be either forecasts or
-projections depending on the assumptions, whereas eliciting projections
-that are not influenced by implicit assumptions about the future from
-humans may be harder.
-
-Further work should explore the effects of humans refining their
-mathematical models or changing model outputs in more detail.
-Model-based forecasts could be used as an input to human judgement, with
-researchers adjusting predictions generated by models. Seeing a
-model-based forecast could help humans calibrate uncertainty better,
-while allowing for manual intervention to adapt spurious trend
-predictions. Tools need to be developed to facilitate this process at a
-larger scale. Human insight could also be used as an input to models.
-Such a `hybrid' forecasting approach could for example ask humans to
-predict the trend of the effective reproduction number \(R_t\) or the
-doubling rate (i.e.~how the epidemic evolves) into the future and use
-this to estimate the exact number of cases, hospitalisations or deaths
-this would imply. In light of severe overconfidence, yet good
-performance in terms of the absolute error, post-processing of human
-forecasts to adjust and widen prediction intervals may be another
-promising approach. Crowd forecasting in general could benefit greatly
-from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of
-the limited resources available and the small number of participants,
-this seems worthwhile to further develop and explore.
-
-\clearpage
-
-\section*{Acknowledgments}
-
-We thank all forecasters who participated in this study for their
-contribution.
-
-We would also like to thank all members of the Centre for the
-Mathematical Modelling of Infectious Diseases COVID-19 Working Group at
-the London School of Hygiene \& Tropical Medicine: Oliver Brady,
-Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie Diamond,
-Katherine E. Atkins, Rein M G J Houben, Jiayao Lei, Rachel Lowe, David
-Simons, Sophie R Meakin, Nicholas G. Davies, Timothy W Russell, Kevin
-van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly, Stéphane Hué,
-Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas, Thibaut
-Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia Showering,
-Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson, Frank G
-Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang Liu, Simon
-R Procter, Emily S Nightingale, William Waites, Rosanna C Barnard, Joel
-Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun, Hamish P Gibbs,
-Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche, James W Rudge, Akira
-Endo, Naomi R Waterlow, Paul Mee, James D Munday, Ciara V McCarthy,
-Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan Auzenbergs,
-Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R
-Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael
-Pung, Anna M Foss.
-
-\clearpage
-
-\beginsupplement
-
-\section*{Supporting information}
-
-\paragraph*{S1 Table.}
-\label{tab:scoring-metrics}
-
-\textbf{Overview of the scoring metrics used.}
-
-\paragraph*{S1 Fig.}
-\label{fig:screenshot}
-
-\textbf{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).}
-
-\paragraph*{S2}
-
-\textbf{Table.} \label{tab:score-table-2}
-\textbf{Scores for one and two week ahead forecasts.} Scores are cut to
-three significant digits and rounded). Note that scores for cases (which
-include the whole period from October 12th 2020 until March 1st 2021)
-and deaths (which include only forecasts from the 21st of December 2020
-on) are computed on different subsets. Numbers in brackets show the
-metrics relative to the Hub ensemble (i.e.~the median ensemble of all
-other models submitted to the German and Polish Forecast Hub, excluding
-our contributions). WIS is the mean weighted interval score (lower
-values are better), WIS - sd is the standard deviation of all scores
-achieved by a model. Dispersion, over-prediction and under-prediction
-together sum up to the weighted interval score. Bias (between -1 and 1,
-0 is ideal) represents the general average tendency of a model to over-
-or underpredict. 50\% and 90\%-coverage are the percentage of observed
-values that fell within the 50\% and 90\% prediction intervals of a
-model.
-
-\paragraph*{S3 Table.}
-\label{tab:score-table-4}
-
-\textbf{Scores for three and four weeks ahead forecasts.} Scores are cut
-to three significant digits and rounded). Note that scores for cases
-(which include the whole period from October 12th 2020 until March 1st
-2021) and deaths (which include only forecasts from the 21st of December
-2020 on) are computed on different subsets. Numbers in brackets show the
-metrics relative to the Hub ensemble (i.e.~the median ensemble of all
-other models submitted to the German and Polish Forecast Hub, excluding
-our contributions). WIS is the mean weighted interval score (lower
-values are better), WIS - sd is the standard deviation of all scores
-achieved by a model. Dispersion, over-prediction and under-prediction
-together sum up to the weighted interval score. Bias (between -1 and 1,
-0 is ideal) represents the general average tendency of a model to over-
-or underpredict. 50\% and 90\%-coverage are the percentage of observed
-values that fell within the 50\% and 90\% prediction intervals of a
-model.
-
-\paragraph{S2}
-
-\textbf{Fig.} \label{fig:agg-performance-all-Germany}
-\textbf{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.}
-A, B: mean weighted interval score (WIS, lower indicates better
-performance) across horizons. WIS is decomposed into its components
-dispersion, over-prediction and under-prediction. C: Empirical coverage
-of the 50\% prediction intervals (50\% coverage is perfect). D:
-Empirical coverage of the 90\% prediction intervals. E: Dispersion (same
-as in panel A, B). Higher values mean greater dispersion of the forecast
-and imply ceteris paribus a worse score. F: Bias, i.e.~general
-(relative) tendency to over- or underpredict. Values are between -1
-(complete under-prediction) and 1 (complete over-prediction) and 0
-ideally. G: Absolute error of the median forecast (lower is better). H.
-Standard deviation of all WIS values for different horizons
-
-\paragraph{S3}
-
-\textbf{Fig.} \label{fig:agg-performance-all-Poland}
-\textbf{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.}
-A, B: mean weighted interval score (WIS, lower indicates better
-performance) across horizons. WIS is decomposed into its components
-dispersion, over-prediction and under-prediction. C: Empirical coverage
-of the 50\% prediction intervals (50\% coverage is perfect). D:
-Empirical coverage of the 90\% prediction intervals. E: Dispersion (same
-as in panel A, B). Higher values mean greater dispersion of the forecast
-and imply ceteris paribus a worse score. F: Bias, i.e.~general
-(relative) tendency to over- or underpredict. Values are between -1
-(complete under-prediction) and 1 (complete over-prediction) and 0
-ideally. G: Absolute error of the median forecast (lower is better). H.
-Standard deviation of all WIS values for different horizons
-
-\paragraph{S4}
-
-\textbf{Fig.} \label{fig:performance-locations}
-\textbf{Visualisation of aggregate performance metrics across locations.}
-A, B: mean weighted interval score (WIS, lower indicates better
-performance) across horizons. WIS is decomposed into its components
-dispersion, over-prediction and under-prediction. C: Empirical coverage
-of the 50\% prediction intervals (50\% coverage is perfect). D:
-Empirical coverage of the 90\% prediction intervals. E: Dispersion (same
-as in panel A, B). Higher values mean greater dispersion of the forecast
-and imply ceteris paribus a worse score. F: Bias, i.e.~general
-(relative) tendency to over- or underpredict. Values are between -1
-(complete under-prediction) and 1 (complete over-prediction) and 0
-ideally. G: Absolute error of the median forecast (lower is better). H.
-Standard deviation of WIS values.
-
-\paragraph{S5}
-
-\textbf{Fig.} \label{fig:performance-locations-rel}
-\textbf{Visualisation of aggregate performance metrics across locations in relative terms.}
-A, B: mean weighted interval score (WIS) across locations (lower values
-indicate better performance). C, D: Empirical coverage of the 50\% and
-90\% prediction intervals. E: Dispersion. Higher values mean greater
-dispersion of the forecast and imply ceteris paribus a worse score. F:
-Bias, i.e.~general (relative) tendency to over- orunderpredict. Values
-are between -1 (complete under-prediction) and 1 (complete
-over-prediction) and 0 ideally. G: Absolute error of the median
-forecast. H. Standard deviation of WIS values.
-
-\paragraph{S6}
-
-\textbf{Fig.} \label{fig:daily-truth}
-\textbf{Visualisation of daily report data.} The black line represents
-weekly data divided by seven. Data were last accessed through the German
-and Polish Forecast Hub on August 21 2021.
-
-\paragraph{S7}
-
-\textbf{Fig.} \label{fig:daily-truth-update}
-\textbf{Visualisation of the absolute difference between the daily report data at the time and the data now.}
-In Germany, there were zero cases and deaths reported on 2020-10-12, and
-only later 2467 cases and 6 deaths were added. Data were last accessed
-through the German and Polish Forecast Hub on May 10 2022.
-
-\paragraph{S8}
-
-\textbf{Fig.} \label{fig:weekly-truth-update}
-\textbf{Visualisation of the relative difference between the weekly report data at the time and the data now.}
-Apart from the data that was retrospectively added on 2020-10-12, data
-updates did not have a noticeable effect on weekly data (as shown in the
-forecasting application). Data were last accessed through the German and
-Polish Forecast Hub on May 10 2022.
-
-\paragraph{S9 Fig.}
-\label{fig:forecasts-and-truth-1}
-
-\textbf{Visualisation of forecasts and scores for one week ahead forecasts.}
-A, C: Visualisation of 50\% prediction intervals of one week ahead
-forecasts against the reported values. Forecasts that were not scored
-(because there was no complete set of death forecasts available) are
-greyed out. B, D: Visualisation of corresponding WIS.
-
-\paragraph{S10 Fig.}
-\label{fig:forecasts-and-truth-3}
-
-\textbf{Visualisation of forecasts and scores for three week ahead forecasts.}
-A, C: Visualisation of 50\% prediction intervals of three week ahead
-forecasts against the reported values. Forecasts that were not scored
-(because there was no complete set of death forecasts available) are
-greyed out. B, D: Visualisation of corresponding WIS.
-
-\paragraph{S11 Fig.}
-\label{fig:forecasts-and-truth-4}
-
-\textbf{Visualisation of forecasts and scores for three week ahead forecasts.}
-A, C: Visualisation of 50\% prediction intervals of four week ahead
-forecasts against the reported values. Forecasts that were not scored
-(because there was no complete set of death forecasts available) are
-greyed out. B, D: Visualisation of corresponding WIS.
-
-\paragraph{S12 Fig.}
-\label{fig:distribution-scores-1}
-
-\textbf{Distribution of weighted interval scores for one week ahead forecasts}
-A: Distribution of weighted interval scores for one week ahead forecasts
-of the different models and forecast targets pooled across locations. B:
-Distribution of WIS separate by country.
-
-\paragraph{S13 Fig.}
-\label{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets pooled across locations. B: Distribution of WIS separate by country.}
-
-\textbf{Distribution of weighted interval scores for three week ahead forecasts}
-A: Distribution of weighted interval scores for three week ahead
-forecasts of the different models and forecast targets pooled across
-locations. B: Distribution of WIS separate by country.
-
-\paragraph{S14 Fig.}
-\label{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets pooled across locations. B: Distribution of WIS separate by country.}
-
-\textbf{Distribution of weighted interval scores for four week ahead forecasts}
-A: Distribution of weighted interval scores for four week ahead
-forecasts of the different models and forecast targets pooled across
-locations. B: Distribution of WIS separate by country.
-
-\paragraph{S15 Fig.}
-\label{fig:distribution-scores-ranks-1}
-
-\textbf{Distribution of model ranks (in terms of WIS) for one week ahead forecasts}
-A: Distribution of the ranks (determined by the weighted interval score)
-for one week ahead forecasts of the different models and forecast
-targets, pooled across locations. B: Distribution of ranks separate by
-country.
-
-\paragraph{S16 Fig.}
-\label{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets, pooled across locations.
-B: Distribution of ranks separate by country.}
-
-\textbf{Distribution of model ranks (in terms of WIS) for two week ahead forecasts}
-A: Distribution of the ranks (determined by the weighted interval score)
-for two week ahead forecasts of the different models and forecast
-targets, pooled across locations. B: Distribution of ranks separate by
-country.
-
-\paragraph{S17 Fig.}
-\label{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets, pooled across locations.
-B: Distribution of ranks separate by country.}
-
-\textbf{Distribution of model ranks (in terms of WIS) for three week ahead forecasts}
-A: Distribution of the ranks (determined by the weighted interval score)
-for three week ahead forecasts of the different models and forecast
-targets, pooled across locations. B: Distribution of ranks separate by
-country.
-
-\paragraph{S18 Fig.}
-\label{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets, pooled across locations.
-B: Distribution of ranks separate by country.}
-
-\textbf{Distribution of model ranks (in terms of WIS) for four week ahead forecasts}
-A: Distribution of the ranks (determined by the weighted interval score)
-for four week ahead forecasts of the different models and forecast
-targets, pooled across locations. B: Distribution of ranks separate by
-country.
-
-\paragraph{S19 Fig.}
-\label{fig:distribution-scores-differences}
-
-\textbf{Difference in WIS between the Crowd forecast and the Hub ensemble for two week ahead forecasts.}
-Values below zero mean better performance of the Crowd forecasts.
-
-\paragraph{S20 Fig.}
-\label{fig:distribution-scores-differences-renewal}
-
-\textbf{Difference in WIS between the Crowd forecast and the Renewal model for two week ahead forecasts.}
-Values below zero mean better performance of the Crowd forecasts.
-
-\paragraph{S21}
-
-\textbf{Fig.} \label{fig:agg-performance-ensemble-mean}
-\textbf{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.}
-``Hub-ensemble'' extit\{excludes\} all our models, Hub-ensemble-all
-extit\{includes\} all of our models, ``Hub-ensemble-realised'' is the
-actual hub-ensemble observed in reality, which includes the renewal
-model and the crowd forecasts, but ont the convolution model. Values
-(except for Bias) are computed as differences to the Hub ensemble which
-excludes our contributions. For Coverage, this is an absolute
-difference, for other metrics this is a percentage difference. A, B:
-mean weighted interval score (WIS) across horizons relative to the Hub
-ensemble (lower values indicate better performance). C, D: Empirical
-coverage of the 50\% and 90\% prediction intervals minus empirical
-coverage observed for the Hub ensemble. E: Dispersion relative to the
-dispersion of the Hub ensemble. Higher values mean greater dispersion of
-the forecast and imply ceteris paribus a worse score. F: Bias,
-i.e.~general (relative) tendency to over- orunderpredict. Values are
-between -1 (complete under-prediction) and 1 (complete over-prediction)
-and 0 ideally. G: Absolute error of the median forecast relative to the
-Hub ensemble. H. Standard deviation of all WIS values for different
-horizons relative to the Hub ensemble.
-
-\paragraph{S4}
-
-\textbf{Table.} \label{tab:score-table-ensemble-2}
-\textbf{Scores for one and two week ahead forecasts for the different versions of the median ensemble.}
-Scores are cut to three significant digits and rounded. Note that scores
-for cases (which include the whole period from October 12th 2020 until
-March 1st 2021) and deaths (which include only forecasts from the 21st
-of December 2020 on) are computed on different subsets. Numbers in
-brackets show the metrics relative to the Hub ensemble (i.e.~the median
-ensemble of all other models submitted to the German and Polish Forecast
-Hub, excluding our contributions). WIS is the mean weighted interval
-score (lower values are better), WIS - sd is the standard deviation of
-all scores achieved by a model. Dispersion, over-prediction and
-under-prediction together sum up to the weighted interval score. Bias
-(between -1 and 1, 0 is ideal) represents the general average tendency
-of a model to over- or underpredict. 50\% and 90\%-coverage are the
-percentage of observed values that fell within the 50\% and 90\%
-prediction intervals of a model.
-
-\paragraph{S5 Table.}
-\label{tab:score-table-ensemble-4}
-
-\textbf{Scores for three and four week ahead forecasts for the different versions of the median ensemble.}
-Scores are cut to three significant digits and rounded. Note that scores
-for cases (which include the whole period from October 12th 2020 until
-March 1st 2021) and deaths (which include only forecasts from the 21st
-of December 2020 on) are computed on different subsets. Numbers in
-brackets show the metrics relative to the Hub ensemble (i.e.~the median
-ensemble of all other models submitted to the German and Polish Forecast
-Hub, excluding our contributions). WIS is the mean weighted interval
-score (lower values are better), WIS - sd is the standard deviation of
-all scores achieved by a model. Dispersion, over-prediction and
-under-prediction together sum up to the weighted interval score. Bias
-(between -1 and 1, 0 is ideal) represents the general average tendency
-of a model to over- or underpredict. 50\% and 90\%-coverage are the
-percentage of observed values that fell within the 50\% and 90\%
-prediction intervals of a model.
-
-\paragraph{S6 Table.}
-\label{tab:score-table-ensemble-mean-2}
-
-\textbf{Scores for one and two week ahead forecasts for the different versions of the mean ensemble}
-Scores are cut to three significant digits and rounded. Note that scores
-for cases (which include the whole period from October 12th 2020 until
-March 1st 2021) and deaths (which include only forecasts from the 21st
-of December 2020 on) are computed on different subsets. Numbers in
-brackets show the metrics relative to the Hub mean ensemble (i.e.~the
-mean ensemble of all other models submitted to the German and Polish
-Forecast Hub, excluding our contributions). WIS is the mean weighted
-interval score (lower values are better), WIS - sd is the standard
-deviation of all scores achieved by a model. Dispersion, over-prediction
-and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average
-tendency of a model to over- or underpredict. 50\% and 90\%-coverage are
-the percentage of observed values that fell within the 50\% and 90\%
-prediction intervals of a model.
-
-\paragraph{S7 Table.}
-\label{tab:score-table-ensemble-mean-4}
-
-\textbf{Scores for three and four week ahead forecasts for the different versions of the mean ensemble}
-Scores are cut to three significant digits and rounded. Note that scores
-for cases (which include the whole period from October 12th 2020 until
-March 1st 2021) and deaths (which include only forecasts from the 21st
-of December 2020 on) are computed on different subsets. Numbers in
-brackets show the metrics relative to the Hub mean ensemble (i.e.~the
-mean ensemble of all other models submitted to the German and Polish
-Forecast Hub, excluding our contributions). WIS is the mean weighted
-interval score (lower values are better), WIS - sd is the standard
-deviation of all scores achieved by a model. Dispersion, over-prediction
-and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average
-tendency of a model to over- or underpredict. 50\% and 90\%-coverage are
-the percentage of observed values that fell within the 50\% and 90\%
-prediction intervals of a model.
-
-\paragraph{S22 Fig.}
-\label{fig:agg-performance-all-late}
-
-\textbf{Visualisation of aggregate performance metrics across forecast horizons (period from December 14th 2020 on)}
-From December 14th 2020 on, all models were available. In the original
-analysis, cases and deaths were scored on different periods, as the
-convolution model was only added later. This sensitivity analysis shows
-performance of all models restricted to the period from December 14 2020
-until March 1st 2021 where all models were available. A, B: mean
-weighted interval score (WIS, lower indicates better performance) across
-horizons. WIS is decomposed into its components dispersion,
-over-prediction and under-prediction. C: Empirical coverage of the 50\%
-prediction intervals (50\% coverage is perfect). D: Empirical coverage
-of the 90\% prediction intervals. E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris
-paribus a worse score. F: Bias, i.e.~general (relative) tendency to
-over- or underpredict. Values are between -1 (complete under-prediction)
-and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the
-median forecast (lower is better). H. Standard deviation of all WIS
-values for different horizons
-
-\paragraph{S8}
-
-\textbf{Table.} \label{tab:score-table-late-2}
-\textbf{Scores for one and two week ahead forecasts (sensitivity analysis)}
-Scores are cut to three significant digits and rounded. In the original
-analysis, cases and deaths were scored on different periods, as the
-convolution model was only added later. This table shows performance of
-all models restricted to the period from December 14 2020 until March
-1st 2021 where all models were available. Numbers in brackets show the
-metrics relative to the Hub ensemble (i.e.~the median ensemble of all
-other models submitted to the German and Polish Forecast Hub, excluding
-our contributions). WIS is the mean weighted interval score (lower
-values are better), WIS - sd is the standard deviation of all scores
-achieved by a model. Dispersion, over-prediction and under-prediction
-together sum up to the weighted interval score. Bias (between -1 and 1,
-0 is ideal) represents the general average tendency of a model to over-
-or underpredict. 50\% and 90\%-coverage are the percentage of observed
-values that fell within the 50\% and 90\% prediction intervals of a
-model.
-
-\paragraph{S9 Table.}
-\label{tab:score-table-late-4}
-
-\textbf{Scores for three and four week ahead forecasts (sensitivity analysis)}
-Scores are cut to three significant digits and rounded. In the original
-analysis, cases and deaths were scored on different periods, as the
-convolution model was only added later. This table shows performance of
-all models restricted to the period from December 14 2020 until March
-1st 2021 where all models were available. Numbers in brackets show the
-metrics relative to the Hub ensemble (i.e.~the median ensemble of all
-other models submitted to the German and Polish Forecast Hub, excluding
-our contributions). WIS is the mean weighted interval score (lower
-values are better), WIS - sd is the standard deviation of all scores
-achieved by a model. Dispersion, over-prediction and under-prediction
-together sum up to the weighted interval score. Bias (between -1 and 1,
-0 is ideal) represents the general average tendency of a model to over-
-or underpredict. 50\% and 90\%-coverage are the percentage of observed
-values that fell within the 50\% and 90\% prediction intervals of a
-model.
-
-\paragraph{S10 Table.}
-\label{tab:table-ensemble-versions}
-
-\textbf{Overview of the models and ensembles used.}
-
-\paragraph{S23 Fig.}
-\label{fig:num-forecasters}
-
-\textbf{Number of participants who submitted a forecast over time.}
-
-\paragraph{S24 Fig.}
-\label{fig:num-ensemble-members}
-
-\textbf{Number of member models in the official Hub ensemble} This
-includes our crowd forecasts and the renewal model. Note that the
-renewal model was not included in the ensemble on December 28th 2020.
-
-\paragraph{S25 Fig.}
-\label{fig:compare-forecasters}
-
-\textbf{Crowd forecasts and baseline shown in the application for a two week horizon.}
-Shown are the median, as well as the 50\% and 90\% prediction intervals
-(in order of decreasing opacity). For any given point in time, the
-baseline shown in red is what forecasters saw when they opened the app
-(the baseline shown was constant across all forecast horizons).
-
-\clearpage
-
-\section*{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
-\CSLLeftMargin{1. }%
-\CSLRightInline{McGowan CJ, Biggerstaff M, Johansson M, Apfeldorf KM,
-Ben-Nun M, Brooks L, et al. Collaborative efforts to forecast seasonal
-influenza in the {United States}, 2015--2016. Scientific Reports.
-2019;9: 683.
-doi:\href{https://doi.org/10.1038/s41598-018-36361-9}{10.1038/s41598-018-36361-9}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
-\CSLLeftMargin{2. }%
-\CSLRightInline{Reich NG, Brooks LC, Fox SJ, Kandula S, McGowan CJ,
-Moore E, et al. A collaborative multiyear, multimodel assessment of
-seasonal influenza forecasting in the {United States}. PNAS. 2019;116:
-3146--3154.
-doi:\href{https://doi.org/10.1073/pnas.1812594116}{10.1073/pnas.1812594116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
-\CSLLeftMargin{3. }%
-\CSLRightInline{Shaman J, Karspeck A. Forecasting seasonal outbreaks of
-influenza. PNAS. 2012;109: 20425--20430.
-doi:\href{https://doi.org/10.1073/pnas.1208772109}{10.1073/pnas.1208772109}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
-\CSLLeftMargin{4. }%
-\CSLRightInline{Biggerstaff M, Alper D, Dredze M, Fox S, Fung IC-H,
-Hickmann KS, et al. Results from the centers for disease control and
-prevention's predict the 2013--2014 {Influenza Season Challenge}. BMC
-Infectious Diseases. 2016;16: 357.
-doi:\href{https://doi.org/10.1186/s12879-016-1669-x}{10.1186/s12879-016-1669-x}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
-\CSLLeftMargin{5. }%
-\CSLRightInline{Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak
-AL, Baugher B, et al. An open challenge to advance probabilistic
-forecasting for dengue epidemics. PNAS. 2019;116: 24268--24274.
-doi:\href{https://doi.org/10.1073/pnas.1909865116}{10.1073/pnas.1909865116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
-\CSLLeftMargin{6. }%
-\CSLRightInline{Yamana TK, Kandula S, Shaman J. Superensemble forecasts
-of dengue outbreaks. Journal of The Royal Society Interface. 2016;13:
-20160410.
-doi:\href{https://doi.org/10.1098/rsif.2016.0410}{10.1098/rsif.2016.0410}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
-\CSLLeftMargin{7. }%
-\CSLRightInline{Colón-González FJ, Bastos LS, Hofmann B, Hopkin A,
-Harpham Q, Crocker T, et al. Probabilistic seasonal dengue forecasting
-in {Vietnam}: {A} modelling study using superensembles. PLOS Medicine.
-2021;18: e1003542.
-doi:\href{https://doi.org/10.1371/journal.pmed.1003542}{10.1371/journal.pmed.1003542}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
-\CSLLeftMargin{8. }%
-\CSLRightInline{Viboud C, Sun K, Gaffey R, Ajelli M, Fumanelli L, Merler
-S, et al. The {RAPIDD} ebola forecasting challenge: {Synthesis} and
-lessons learnt. Epidemics. 2018;22: 13--21.
-doi:\href{https://doi.org/10.1016/j.epidem.2017.08.002}{10.1016/j.epidem.2017.08.002}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
-\CSLLeftMargin{9. }%
-\CSLRightInline{Funk S, Camacho A, Kucharski AJ, Lowe R, Eggo RM,
-Edmunds WJ. Assessing the performance of real-time epidemic forecasts:
-{A} case study of {Ebola} in the {Western Area} region of {Sierra
-Leone}, 2014-15. PLOS Computational Biology. 2019;15: e1006785.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1006785}{10.1371/journal.pcbi.1006785}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
-\CSLLeftMargin{10. }%
-\CSLRightInline{Del Valle SY, McMahon BH, Asher J, Hatchett R, Lega JC,
-Brown HE, et al. Summary results of the 2014-2015 {DARPA Chikungunya}
-challenge. BMC Infectious Diseases. 2018;18: 245.
-doi:\href{https://doi.org/10.1186/s12879-018-3124-7}{10.1186/s12879-018-3124-7}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
-\CSLLeftMargin{11. }%
-\CSLRightInline{Farrow DC, Brooks LC, Hyun S, Tibshirani RJ, Burke DS,
-Rosenfeld R. A human judgment approach to epidemiological forecasting.
-PLOS Computational Biology. 2017;13: e1005248.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1005248}{10.1371/journal.pcbi.1005248}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{Funk S, Abbott S, Atkins BD, Baguelin M, Baillie JK,
-Birrell P, et al. Short-term forecasts to inform the response to the
-{Covid-19} epidemic in the {UK}. medRxiv. 2020; 2020.11.11.20220962.
-doi:\href{https://doi.org/10.1101/2020.11.11.20220962}{10.1101/2020.11.11.20220962}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
-\CSLLeftMargin{13. }%
-\CSLRightInline{Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K,
-et al. {COVID-19 Forecast Hub}: 4 {December} 2020 snapshot. {Zenodo};
-2020.
-doi:\href{https://doi.org/10.5281/zenodo.3963371}{10.5281/zenodo.3963371}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
-\CSLLeftMargin{14. }%
-\CSLRightInline{Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A,
-Rivadeneira AJC, et al. Evaluation of individual and ensemble
-probabilistic forecasts of {COVID-19} mortality in the {US}. medRxiv.
-2021; 2021.02.03.21250974.
-doi:\href{https://doi.org/10.1101/2021.02.03.21250974}{10.1101/2021.02.03.21250974}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
-\CSLLeftMargin{15. }%
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. Short-term forecasting of {COVID-19} in {Germany}
-and {Poland} during the second wave -- a preregistered study. medRxiv.
-2021; 2020.12.24.20248826.
-doi:\href{https://doi.org/10.1101/2020.12.24.20248826}{10.1101/2020.12.24.20248826}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. National and subnational short-term forecasting of
-{COVID-19} in {Germany} and {Poland}, early 2021. 2021;
-2021.11.05.21265810.
-doi:\href{https://doi.org/10.1101/2021.11.05.21265810}{10.1101/2021.11.05.21265810}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-europeancovid-19forecasthubEuropeanCovid19Forecast2021}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{European Covid-19 Forecast Hub. European {Covid-19
-Forecast Hub}. 2021 {[}cited 30 May 2021{]}. Available:
-\url{https://covid19forecasthub.eu/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichAccuracyRealtimeMultimodel2019}{}}%
-\CSLLeftMargin{18. }%
-\CSLRightInline{Reich NG, McGowan CJ, Yamana TK, Tushar A, Ray EL,
-Osthus D, et al. Accuracy of real-time multi-model ensemble forecasts
-for seasonal influenza in the {U}.{S}. PLOS Computational Biology.
-2019;15: e1007486.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1007486}{10.1371/journal.pcbi.1007486}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{Tetlock PE, Mellers BA, Rohrbaugh N, Chen E. Forecasting
-{Tournaments}: {Tools} for {Increasing Transparency} and {Improving} the
-{Quality} of {Debate}. Curr Dir Psychol Sci. 2014;23: 290--295.
-doi:\href{https://doi.org/10.1177/0963721414534257}{10.1177/0963721414534257}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{Atanasov P, Rescober P, Stone E, Swift SA,
-Servan-Schreiber E, Tetlock P, et al. Distilling the {Wisdom} of
-{Crowds}: {Prediction Markets} vs. {Prediction Polls}. Management
-Science. 2016;63: 691--706.
-doi:\href{https://doi.org/10.1287/mnsc.2015.2374}{10.1287/mnsc.2015.2374}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers E-J. Laypeople
-{Can Predict Which Social-Science Studies Will Be Replicated
-Successfully}. Advances in Methods and Practices in Psychological
-Science. 2020;3: 267--285.
-doi:\href{https://doi.org/10.1177/2515245920919667}{10.1177/2515245920919667}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{ReplicationMarkets. Replication {Markets} -- {Reliable}
-research replicates\ldots you can bet on it. 2020 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.replicationmarkets.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{Servan-Schreiber E, Wolfers J, Pennock DM, Galebach B.
-Prediction {Markets}: {Does Money Matter}? Electronic Markets. 2004;14:
-243--251.
-doi:\href{https://doi.org/10.1080/1019678042000245254}{10.1080/1019678042000245254}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{McAndrew TC, Reich NG. An expert judgment model to
-predict early stages of the {COVID-19} outbreak in the {United States}.
-medRxiv. 2020; 2020.09.21.20196725.
-doi:\href{https://doi.org/10.1101/2020.09.21.20196725}{10.1101/2020.09.21.20196725}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{Recchia G, Freeman ALJ, Spiegelhalter D. How well did
-experts and laypeople forecast the size of the {COVID-19} pandemic? PLOS
-ONE. 2021;16: e0250935.
-doi:\href{https://doi.org/10.1371/journal.pone.0250935}{10.1371/journal.pone.0250935}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{Metaculus. A {Preliminary Look} at {Metaculus} and
-{Expert Forecasts}. 22 Jun 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.metaculus.com/news/2020/06/02/LRT/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{Hypermind. Hypermind \textbar{} {Supercollective}
-intelligence for decision makers. {Hypermind}; 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.hypermind.com/en/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{CSET Foretell. {CSET Foretell}. 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.cset-foretell.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
-\CSLLeftMargin{29. }%
-\CSLRightInline{PredictIt. {PredictIt}. 2021 {[}cited 13 Oct 2021{]}.
-Available: \url{https://www.predictit.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
-\CSLLeftMargin{30. }%
-\CSLRightInline{Held L, Meyer S, Bracher J. Probabilistic forecasting in
-infectious disease epidemiology: The 13th {Armitage} lecture. Statistics
-in Medicine. 2017;36: 3443--3460.
-doi:\href{https://doi.org/10.1002/sim.7363}{10.1002/sim.7363}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Crowdforecastr: Eliciting crowd forecasts in r shiny. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618519}{10.5281/zenodo.4618519}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Covid.german.forecasts: Forecasting covid-19 related metrics for the
-german/poland forecast hub. 2020. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-ecdcDownloadHistoricalData2020}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{ECDC. Download historical data (to 14 {December} 2020)
-on the daily number of new reported {COVID-19} cases and deaths
-worldwide. {European Centre for Disease Prevention and Control}; 14 Dec
-2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rkiRKICoronavirusSARSCoV22021}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{RKI. {RKI} - {Coronavirus SARS-CoV-2} - {Aktueller
-Lage-}/{Situationsbericht} des {RKI} zu {COVID-19}. 2021 {[}cited 30 May
-2021{]}. Available:
-\url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-forsal.plRozbieznosciStatystykachKoronawirusa2020}{}}%
-\CSLLeftMargin{35. }%
-\CSLRightInline{Forsal.pl. Rozbieżności w statystykach koronawirusa. 22
-tys. przypadków będą doliczone do ogólnej liczby wyników. 2020 {[}cited
-30 May 2021{]}. Available:
-\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
-\CSLLeftMargin{36. }%
-\CSLRightInline{Ärzteblatt DÄG Redaktion Deutsches.
-SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an. {Deutsches
-Ärzteblatt}; 3 Nov 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
-\CSLLeftMargin{37. }%
-\CSLRightInline{Fay C, Guyader V, Rochette S, Girard C. Golem: A
-framework for robust shiny applications. 2021. Available:
-\url{https://github.com/ThinkR-open/golem}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
-\CSLLeftMargin{38. }%
-\CSLRightInline{Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie
-Y, et al. Shiny: Web application framework for r. 2021. Available:
-\url{https://CRAN.R-project.org/package=shiny}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
-\CSLLeftMargin{39. }%
-\CSLRightInline{Our World in Data. {COVID-19 Data Explorer}. {Our World
-in Data}; 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://ourworldindata.org/coronavirus-data-explorer}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
-\CSLLeftMargin{40. }%
-\CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K,
-Ellis P, et al. EpiNow2: Estimate real-time case counts and time-varying
-epidemiological parameters. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957489}{10.5281/zenodo.3957489}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
-\CSLLeftMargin{41. }%
-\CSLRightInline{Fraser C. Estimating {Individual} and {Household
-Reproduction Numbers} in an {Emerging Epidemic}. PLOS ONE. 2007;2: e758.
-doi:\href{https://doi.org/10.1371/journal.pone.0000758}{10.1371/journal.pone.0000758}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation2020}{}}%
-\CSLLeftMargin{42. }%
-\CSLRightInline{epiforecasts.io/covid. Covid-19: {Temporal} variation in
-transmission during the {COVID-19} outbreak. {Covid-19}; 2020 {[}cited
-30 May 2021{]}. Available: \url{https://epiforecasts.io/covid/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
-\CSLLeftMargin{43. }%
-\CSLRightInline{Sherratt K, Abbott S, Meakin SR, Hellewell J, Munday JD,
-Bosse N, et al. Exploring surveillance data biases when estimating the
-reproduction number: With insights into subpopulation transmission of
-{Covid-19} in {England}. 2021; 2020.10.18.20214585.
-doi:\href{https://doi.org/10.1101/2020.10.18.20214585}{10.1101/2020.10.18.20214585}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abbottEstimatingTimevaryingReproduction2020a}{}}%
-\CSLLeftMargin{44. }%
-\CSLRightInline{Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs
-HP, Bosse NI, et al. Estimating the time-varying reproduction number of
-{SARS-CoV-2} using national and subnational case counts. 2020 {[}cited
-14 Oct 2021{]}.
-doi:\href{https://doi.org/10.12688/wellcomeopenres.16006.1}{10.12688/wellcomeopenres.16006.1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
-\CSLLeftMargin{45. }%
-\CSLRightInline{Xu B, Gutierrez B, Hill S, Scarpino S, Loskill A, Wu J,
-et al. Epidemiological data from the nCoV-2019 outbreak: Early
-descriptions from publicly available data. 2020. Available:
-\url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
-\CSLLeftMargin{46. }%
-\CSLRightInline{Stan Development Team. RStan: The r interface to stan.
-2020. Available: \url{http://mc-stan.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
-\CSLLeftMargin{47. }%
-\CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG. Evaluating
-epidemic forecasts in an interval format. PLoS Comput Biol. 2021;17:
-e1008618.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1008618}{10.1371/journal.pcbi.1008618}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
-\CSLLeftMargin{48. }%
-\CSLRightInline{Gneiting T, Raftery AE. Strictly proper scoring rules,
-prediction, and estimation. Journal of the American Statistical
-Association. 2007;102: 359--378.
-doi:\href{https://doi.org/10.1198/016214506000001437}{10.1198/016214506000001437}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
-\CSLLeftMargin{49. }%
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Scoringutils:
-Utilities for scoring and assessing predictions. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618017}{10.5281/zenodo.4618017}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-deutschewelleCoronavirusGermanyImpose2020}{}}%
-\CSLLeftMargin{50. }%
-\CSLRightInline{Deutsche Welle. Coronavirus: {Germany} to impose
-one-month partial lockdown \textbar{} {DW} \textbar{} 28.10.2020. 2020
-{[}cited 29 Jun 2021{]}. Available:
-\url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}}
-
-\end{CSLReferences}
-
-\nolinenumbers
-
-\end{document}
+Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie Diamond, Katherine E.
+Atkins, Rein M G J Houben, Jiayao Lei, Rachel Lowe, David Simons, Sophie R Meakin, Nicholas G.
+Davies, Timothy W Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly, Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas, Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson, Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun, Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche, James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday, Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael Pung, Anna M Foss.

### 2023-12-11 manuscript/S1 Table.Rmd

--- 2022-06-02 manuscript/manuscript.tex
@@
-% Template for PLoS
-% Version 3.5 March 2018
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended
-% to minimize problems and delays during our production
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% Once your paper is accepted for publication,
-% PLEASE REMOVE ALL TRACKED CHANGES in this file
-% and leave only the final text of your manuscript.
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file.
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig" instead of "Figure".
-% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-%
-% Do not include text that is not math in the math environment.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column.
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
+---
+output: 
+  pdf_document:
+    keep_tex: true
+geometry: margin=2cm
+---
 
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+```{r echo=FALSE}
 
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
+library(kableExtra)
+library(magrittr)
 
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8x]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% cite package, to clean up citations in the main text. Do not remove.
-% \usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% color can be used to apply background shading to table cells only
-\usepackage[table]{xcolor}
-
-% array package and thick rules for tables
-\usepackage{array}
-
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-
-% create \thickcline for thick horizontal lines of variable length
-\newlength\savedwidth
-\newcommand\thickcline[1]{%
-  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-  \cline{#1}%
-  \noalign{\vskip\arrayrulewidth}%
-  \noalign{\global\arrayrulewidth\savedwidth}%
-}
-
-% \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-\hline
-\noalign{\global\arrayrulewidth\savedwidth}}
-
-% Remove comment for double spacing
-%\usepackage{setspace}
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-\renewcommand{\figurename}{Fig}
-
-% Use the PLoS provided BiBTeX style
-% \bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr,graphicx}
-\usepackage{epstopdf}
-%\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-%\setlength{\headheight}{27.023pt}
-%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\headrulewidth}{0pt}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\today}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-% tightlist command for lists without linebreak
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% Pandoc citation processing
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-% for Pandoc 2.8 to 2.10.1
-\newenvironment{cslreferences}%
-  {}%
-  {\par}
-% For Pandoc 2.11+
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\usepackage{lineno}
-\usepackage[T1]{fontenc}
-\linenumbers
-\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-\usepackage{caption}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
-
-\usepackage{forarray}
-\usepackage{xstring}
-\newcommand{\getIndex}[2]{
-  \ForEach{,}{\IfEq{#1}{\thislevelitem}{\number\thislevelcount\ExitForEach}{}}{#2}
-}
-
-\setcounter{secnumdepth}{0}
-
-\newcommand{\getAff}[1]{
-  \getIndex{#1}{London School of Hygiene \& Tropical Medicine,Karlsruhe
-Institute of Technology Institute of Economic Theory and Statistics,Max
-Planck Institute for Multidisciplinary Sciences,UK Health Security
-Agency,Imperial College London}
-}
-
-\begin{document}
-\vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{Comparing human and model-based forecasts of COVID-19 in
-Germany and
-Poland} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Nikos I. Bosse\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\textsuperscript{*},
-Sam Abbott\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Johannes Bracher\textsuperscript{\getAff{Karlsruhe Institute of
-Technology Institute of Economic Theory and Statistics}},
-Habakuk Hain\textsuperscript{\getAff{Max Planck Institute for
-Multidisciplinary Sciences}},
-Billy J. Quilty\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Mark Jit\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Edwin van Leeuwen\textsuperscript{\getAff{UK Health Security
-Agency}, \getAff{London School of Hygiene \& Tropical Medicine}},
-Anne Cori\textsuperscript{\getAff{Imperial College London}},
-Sebastian Funk\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\\
-\bigskip
-\textbf{\getAff{London School of Hygiene \& Tropical Medicine}}London
-School of Hygiene \& Tropical Medicine, Keppel Street, London WC1E7HT,
-United Kingdom\\
-\textbf{\getAff{Karlsruhe Institute of Technology Institute of Economic
-Theory and Statistics}}Karlsruhe Institute of Technology - Institute of
-Economic Theory and Statistics, Post Box 6980, 76049 Karlsruhe,
-Germany\\
-\textbf{\getAff{Max Planck Institute for Multidisciplinary Sciences}}Max
-Planck Institute for Multidisciplinary Sciences, Am Faßberg 11, 37077
-Göttingen, Germany\\
-\textbf{\getAff{UK Health Security Agency}}UK Health Security Agency,
-London NW9 5EQ, United Kingdom\\
-\textbf{\getAff{Imperial College London}}Imperial College London,
-Norfolk Place, London W2 1PG, United Kingdom\\
-\bigskip
-* Corresponding author: nikos.bosse@lshtm.ac.uk\\
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-Forecasts based on epidemiological modelling have played an important
-role in shaping public policy throughout the COVID-19 pandemic. This
-modelling combines knowledge about infectious disease dynamics with the
-subjective opinion of the researcher who develops and refines the model
-and often also adjusts model outputs. Developing a forecast model is
-difficult, resource- and time-consuming. It is therefore worth asking
-what modelling is able to add beyond the subjective opinion of the
-researcher alone. To investigate this, we analysed different real-time
-forecasts of cases of and deaths from COVID-19 in Germany and Poland
-over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
-We compared crowd forecasts elicited from researchers and volunteers,
-against a) forecasts from two semi-mechanistic models based on common
-epidemiological assumptions and b) the ensemble of all other models
-submitted to the Forecast Hub. We found crowd forecasts, despite being
-overconfident, to outperform all other methods across all forecast
-horizons when forecasting cases (weighted interval score relative to the
-Hub ensemble 2 weeks ahead: 0.89). Forecasts based on computational
-models performed comparably better when predicting deaths (rel. WIS
-1.26), suggesting that epidemiological modelling and human judgement can
-complement each other in important ways.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step.
-% Author Summary not valid for PLOS ONE submissions.
-\section*{Author summary}
-Mathematical models of COVID-19 have played a key role in informing
-governments across the world. While mathematical models are informed by
-our knowledge of infectious disease dynamics, they are ultimately
-developed and iteratively adjusted by the researchers and shaped by
-their subjective opinions. To investigate what modelling is able to add
-beyond the subjective opinion of the researcher alone, we compared human
-forecasts with model-based predictions of COVID-19 cases and deaths
-submitted to the so-called German/Polish Forecast Hub (which collates a
-variety of models from a range of teams). \textbar{} We found that our
-human forecasts consistently outperformed an aggregate of all available
-model-based forecasts when predicting cases, but not when predicting
-deaths. Our findings suggest that human insight may be most valuable
-when forecasting highly uncertain quantities, which depend on many
-factors that are hard to model using equations, while mathematical
-models may be most useful in settings like predicting deaths, where
-leading indicators with a clear connection to the target variable are
-available. This potentially has very relevant policy implications, as
-agencies informing policy-makers could benefit from routinely eliciting
-human forecasts in addition to model-based predictions to inform
-policies.
-
-\linenumbers
-
-% Use "Eq" instead of "Equation" for equation citations.
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Infectious disease modelling has a long tradition and has helped inform
-public health decisions both through scenario modelling, as well as
-actual forecasts of (among others) influenza {[}e.g. 1,2--4{]}, dengue
-fever {[}e.g. 5,6,7{]}, ebola {[}e.g. 8,9{]}, chikungunya {[}e.g.
-10,11{]} and now COVID-19 {[}e.g. 12,13--17{]}. Applications of
-epidemiological models differ in the way they make statements about the
-future. Forecasts aim to predict the future as it will occur, while
-scenario modelling and projections aim to represent what the future
-could look like under certain scenario assumptions or if conditions
-stayed the same as they were in the past. Forecasts can be judged by
-comparing them against observed data. Since it is much harder to fairly
-assess the accuracy and usefulness of projections and scenario modelling
-in the same way, this work focuses on forecasts, which represent only a
-subset of all epidemiological modelling.
-
-Since March 2020, forecasts of COVID-19 from multiple teams have been
-collected, aggregated and compared by Forecast Hubs such as the US
-Forecast Hub {[}13,14{]}, the German and Polish Forecast Hub {[}15,16{]}
-and the European Forecast Hub {[}17{]}. Often, different individual
-forecasts are combined into a single forecast, e.g.~by taking the mean
-or median of all forecasts. These ensemble forecasts usually tend to
-perform better and more consistently than individual forecasts (see e.g.
-{[}6{]}; {[}18{]}).
-
-Individual computational models usually rely to varying degrees on
-mechanistic assumptions about infectious disease dynamics (such as
-SIR-type compartmental models that aim to represent how individuals move
-from being susceptible to infected and then recovered or dead). Some are
-more statistical in nature (such as time series models that detect
-statistical patterns without explicitly modelling disease dynamics). How
-exactly such a mathematical or computational model is constructed and
-which assumptions are made depends on subjective opinion and judgement
-of the researcher who develops and refines the model. Models are
-commonly adjusted and improved based on whether the model output looks
-plausible to the researchers involved.
-
-The process of model construction and refinement is laborious and
-time-consuming, and it is therefore worth asking what modelling can add
-beyond the subjective judgment of the researcher alone. In this work, we
-ask this question specifically in the context of predictive performance,
-and set aside other advantages of epidemiological modelling (such as
-reproducibility or the ability to obtain a deeper fundamental
-understanding of how diseases spread). One natural way to do this is to
-compare the predictive performance of forecasts based on computational
-models (``model-based forecasts'') against forecasts made by individual
-humans without explicit use of a computer model (``direct human
-forecasts'') or a combination of multiple such forecasts (``crowd
-forecasts'').
-
-Previous work has examined such direct human forecasts in various
-contexts, such as geopolitics {[}19,20{]}, meta-science {[}21,22{]},
-sports {[}23{]} and epidemiology {[}11,24,25{]}. Several prediction
-platforms {[}26--28{]} and prediction markets {[}29{]} have been created
-to collate expert and non-expert predictions. However, with the notable
-exception of {[}11{]}, these forecasts were not designed to be evaluated
-alongside model-based forecasts and usually follow their own (often
-binary) prediction formats. Direct human forecasts may be able to take
-into account insights and relationships between variables which are hard
-to specify using epidemiological models. However, it is not entirely
-clear in which situations human forecasts perform well or badly. For
-example, {[}11{]} found that humans could outperform computer models at
-predicting the 2014/15 and 2015/16 flu season in the US, a setting where
-the disease was well known and information about previous seasons was
-available. However, humans tended to do slightly worse at predicting the
-2014/15 outbreak of chikungunya in the Americas, a disease previously
-largely unobserved and unknown in these regions at the time.
-
-In this study, we analyse the performance of direct human forecasts
-relative to model-based forecasts and discuss the added benefit of
-epidemiological modelling over human judgement alone. As a case study,
-we use different forecasts, involving varying degrees of human
-intervention, which we submitted in real time to the German and Polish
-Forecast Hub. In contrast to {[}11{]} we elicited not only point
-predictions, but full predictive distributions (``probabilistic
-forecasts'', see e.g. {[}30{]}) from participants. This allows us to
-compare not only predictive accuracy, but also how well human
-forecasters and model-based forecasts were able to quantify forecast
-uncertainty.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-We created and submitted the following forecasts to the German and
-Polish Forecast Hub: 1) a direct human forecast (henceforth called
-``crowd forecast''), elicited from participants through a web
-application {[}31{]} and 2) two semi-mechanistic model-based forecasts
-(``renewal model'' and ``convolution model'') informed by basic
-assumptions about COVID-19 epidemiology. While the two semi-mechanistic
-forecasts were necessarily shaped by our implicit assumptions and
-decisions, they were designed such as to minimise the amount of human
-intervention involved. For example, we refrained from adjusting model
-outputs or refining the models based on past performance. Forecasts were
-created in real time over a period of 21 weeks from October 12th 2020
-until March 1st 2021 and submitted to the German and Polish Forecast hub
-{[}15,16{]}. All code and tools necessary to generate the forecasts and
-make a forecast submission are available in the
-\texttt{covid.german.forecasts} R package {[}32{]}. This repository also
-contains a record of all forecasts submitted to the German and Polish
-Forecast Hub. Forecasts were evaluated using a variety of scoring
-metrics and compared among each other and against an ensemble of all
-other models submitted to the German and Polish Forecast Hub.
-
-\hypertarget{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}{%
-\subsection{Forecast targets and interaction with the German and Polish
-Forecast
-Hub}\label{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}}
-
-The German and Polish Forecast Hub (now mostly merged into the {[}17{]})
-elicits predictions for various COVID-19 related forecast targets from
-different research groups every week. Forecasts had to be made every
-Monday (with submissions allowed until Tuesday 3pm) and were permitted
-to use any data that was available by Monday 11.59pm. We submitted
-forecasts for incident and cumulative weekly reported numbers of cases
-of and deaths from COVID-19 on a national level in Germany and Poland
-over a one to four week forecast horizon. Forecasts were submitted on
-Mondays, but weeks were defined as ending on a Saturday (and starting on
-Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26
-days. Submissions were required in a quantile-based format with 23
-quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10,
-0.15, \ldots, 0.95, 0.975, 0.99. Forecasts submitted to the Forecast Hub
-were combined into different ensembles every week, with the median
-ensemble (i.e., the \(\alpha\)-quantile of the ensemble is given by the
-median of all submitted \(\alpha\)-quantiles) being the default ensemble
-shown on all official Forecast hub visualisations
-(https://kitmetricslab.github.io/forecasthub/forecast).
-
-Data on daily reported test positive cases and deaths linked to COVID-19
-were provided by the organisers of the German and Polish Forecast hub.
-Until December 14th, 2020, these data were sourced from the European
-Centre for Disease Control {[}33{]}. After ECDC stopped publishing daily
-data, observations were sourced from the Robert Koch Institute (RKI) and
-the Polish Ministry of Health for the remainder of the submission period
-{[}34{]}. These data are subject to reporting artefacts, (such as for
-example delayed case reporting in Poland on the 24th November,
-{[}35{]}), changes in reporting over time, and variation in testing
-regimes (for example in Germany from the 11th of November on, {[}36{]}).
-The ECDC data as well as the data published by the Polish Ministry of
-Health were also subject to data revisions, although most of them (with
-a notable exception of a data update for October 12 2020 in Germany)
-only affected daily, not weekly data (see Figures
-\ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).
-
-\hypertarget{crowd-forecasts}{%
-\subsection{Crowd forecasts}\label{crowd-forecasts}}
-
-Our crowd forecasts were created as an ensemble of forecasts made by
-individual participants every week through a web application
-(https://cmmid-lshtm.shinyapps.io/crowd-forecast/). Weekly forecasts had
-to be submitted before Tuesday 12pm every week, but participants were
-asked to only use any information or data that was already available by
-Monday night. The application was built using the \texttt{shiny} and
-\texttt{golem} R packages {[}37,38{]} and is available in the
-\texttt{crowdforecastr} R package {[}31{]}. To make a forecast in the
-application participants could select a predictive distribution (with
-the default being log-normal) to represent the probability that the
-forecasted quantity took certain values. Median and width of the
-uncertainty could be adjusted by either interacting with a figure
-showing their forecast or providing numerical values (see screenshot in
-Figure \ref{fig:screenshot} in the SI). The default shown was a
-repetition of the last known observation with constant uncertainty
-around it computed as the standard deviation of the last four changes in
-weekly log observed forecasts (i.e.~as
-\(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
-A comparison of the crowd forecasts against the default baseline shown
-in the application is displayed in Figure \ref{fig:compare-forecasters}
-in the Appendix. Our interface also allowed participants to view past
-observations based on the hub data, as well as their forecasts, on a
-logarithmic scale and presented additional contextual COVID-19 data
-sourced from {[}39{]}. These data included, for example, notifications
-of both test positive COVID-19 cases and COVID-19 linked deaths and the
-number of COVID-19 tests conducted over time. From November 26 2020 on
-we displayed weekly small reports with a visualisation of past forecasts
-and scores on our website, epiforecasts.io.
-
-Forecasts were stored in a Google Sheet and downloaded, cleaned and
-processed every week for submission to the Forecast Hub. If a forecaster
-had submitted multiple predictions for a single target, only the latest
-submission was kept. Information on the chosen distribution as well as
-the parameters for median and width were used to obtain the required set
-of 23 quantiles from that distribution. Forecasts from all forecasters
-were then aggregated using an unweighted quantile-wise mean (i.e., the
-\(\alpha\)-quantile of the ensemble is given by the mean of all
-submitted \(\alpha\)-quantiles). To avoid issues with users trying out
-the app and submitting a random forecast, we required that a forecaster
-needed to make a forecast for at least two targets for a given forecast
-in order to be included in the crowd forecast ensemble. On a few
-occasions we deleted forecasts that were clearly the result of a user or
-software error (such as for example forecasts that were zero
-everywhere).
-
-individual forecasts were assessed as clearly erroneous by visual
-inspection and subsequently removed before aggregation and were excluded
-from the submission as well as the analysis.
-
-Participants were recruited mostly within the Centre of Mathematical
-Modeling of Infectious Diseases at the London School of Hygiene \&
-Tropical Medicine, but participants were also invited personally or via
-social media to submit predictions. Depending on whether they had a
-background in either statistics, forecasting or epidemiology,
-participants were asked to self-identify as `experts' or `non-experts'.
-
-The study was approved by the Observational / Interventions Research
-Ethics Committee at the London School of Hygiene \& Tropical Medicine,
-LSHTM Ethics Reference: 22290. Formal consent from participants was
-taken in written form through the web application.
-
-\hypertarget{model-based-forecasts}{%
-\subsection{Model-based forecasts}\label{model-based-forecasts}}
-
-We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R
-package (version 1.3.3) as our model-based forecasts {[}40{]}. The first
-of these models, here called ``renewal model'', used the renewal
-equation {[}41{]} to predict reported cases and deaths (see details in
-the SI). It estimated the effective reproduction number \(R_t\) (the
-average number of people each person infected at time t is expected to
-infect in turn) and modelled future infections as a weighted sum of past
-infection multiplied by \(R_t\). \(R_t\) was assumed to stay constant
-beyond the forecast date, roughly corresponding to continuing the latest
-exponential trend in infections. On the 9th of November we altered the
-date when \(R_t\) was assumed to be constant from two weeks prior to the
-date of the forecast to the forecast date, which we found to yield a
-more stable \(R_t\) estimate. Reported case and death notifications were
-obtained by convolving predicted infections over data-based delay
-distributions {[}40,42--44{]} to model the time between infection and
-report date. The renewal model was used to predict cases as well as
-deaths with forecasts being generated for each target separately. Death
-forecasts from the renewal model were therefore not informed by past
-cases. One submission of the renewal model on December 28th 2020 was
-delayed and therefore not included in the official Forecast hub
-ensemble.
-
-The second model (``convolution model'', see details in SI) was only
-used to forecast deaths and was added later, starting December 7th 2020
-(with the first forecast from December 7th suffering from a software bug
-and therefore disregarded in all further analyses). The convolution
-model was submitted, but never included in the official Forecast hub
-ensemble due to concerns that it could be too similar to the renewal
-model. The convolution model predicted deaths as a fraction of infected
-people who would die with some delay, by using a convolution of reported
-cases with a distribution that described the delay from case report to
-death and a scaling factor (the case-fatality ratio). Both the renewal
-and the convolution model used daily observations and assumed a negative
-binomial observation model with a multiplicative day-of-the-week effect
-{[}40{]}.
-
-Line list data used to inform the prior for the delay from symptom onset
-to test positive case report or death in the model-based forecasts was
-sourced from {[}45{]} with data available up to the 1st of August. All
-model fitting was done using Markov-chain Monte Carlo (MCMC) in stan
-{[}46{]} with each location and forecast target being fitted separately.
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-For the main analysis we focused mostly on two week ahead forecasts, as
-COVID-19 forecasts, especially for cases, were in the past found to have
-poor predictive performance beyond this horizon {[}15{]}. Forecasts for
-cases were scored using the full period from October 2020 until March
-2021. To ensure comparability between models, all death forecasts were
-scored using only the period from December 14th on, where all models
-including the convolution model were available. To ensure robustness of
-our results we conducted a sensitivity analysis where all forecasts
-(including cases) were scored only over the later period for which all
-forecasts were available (see Section \ref{sensitivity-analysis} in the
-SI). Results remained broadly unchanged.
-
-Forecasts were analysed using the following scoring metrics: The
-weighted interval score (WIS) {[}47{]}, the absolute error, relative
-bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule {[}48{]}, meaning that in expectation
-the score is optimised by reporting a predictive distribution that is
-identical to the true data-generating distribution. Forecasters are
-therefore incentivised to report their true belief about the future. The
-WIS can be understood as a generalisation of the absolute error to
-quantile-based forecasts (also meaning that smaller values are better)
-and can be decomposed into three separate penalties: forecast spread
-(i.e.~uncertainty of forecasts), over-prediction and under-prediction.
-While the over- and under-prediction components of the WIS capture the
-amount of over-prediction and under-prediction in absolute terms, we
-also look at a relative tendency to make biased forecasts. The bias
-metric {[}9{]} we use captures how much probability mass of the forecast
-was above or below the true value (mapped to values between -1 and 1)
-and therefore represents a general tendency to over- or under-predict in
-relative terms. A value of -1 implies that all quantiles of the
-predictive distribution are below the observed value and a value of 1
-that all quantiles are above the observed value. Empirical coverage is
-the percentage of observed values that fall inside a given prediction
-interval (e.g.~how many observed values fall inside all 50\% prediction
-intervals). Scoring metrics are explained in more detail in Table
-\ref{tab:scoring-metrics} in the SI. All scores were calculated using
-the \texttt{scoringutils} R package {[}49{]}.
-
-At all stages of the evaluation our forecasts were compared to the
-median ensemble of all \emph{other} models submitted to the German and
-Polish Forecast Hub (``Hub ensemble''). This ``Hub ensemble'' was
-retrospectively computed and excludes all our models, leaving on average
-five ensemble member models (see details in Section
-\ref{contributions-hub}, as well as in Table
-\ref{tab:table-ensemble-versions} and Figure
-\ref{fig:num-ensemble-members} in the SI). What we call ``Hub ensemble''
-in this article therefore differs from the ``official Hub ensemble''
-(here called ``hub-ensemble-realised'') which included crowd forecasts
-as well as renewal model forecasts. To enhance interpretability of
-scores we mainly report WIS relative to the Hub ensemble in the main
-text, i.e.~we divided the average scores for a given model by the
-average score achieved by the Hub ensemble on the same set of forecasts
-(with values \textgreater1 implying worse and values \textless1 implying
-better performance than the Hub ensemble). In addition to comparing our
-forecasts against the hub ensemble excluding our models, we also
-assessed the impact of our forecasts on the performance of the
-forecasting hub by recalculating separate versions of the Hub ensemble
-with only some (or all) of our forecasts included. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{crowd-forecast-participation}{%
-\subsection{Crowd forecast
-participation}\label{crowd-forecast-participation}}
-
-A total number of 32 participants submitted forecasts, 17 of those
-self-identified as `expert' in either forecasting or epidemiology. The
-median number of forecasters for any given forecast target was 6, the
-minimum 2 and the maximum 10. The mean number of submissions from an
-individual forecaster was 4.7 but the median number was only one - most
-participants dropped out after their first submission. Only two
-participants submitted a forecast every single week, both of whom are
-authors on this study.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} \caption{Two week ahead forecasts and corresponding scores.
-A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth}
-\end{figure}
-
-\hypertarget{case-forecasts}{%
-\subsection{Case Forecasts}\label{case-forecasts}}
-
-For cases, crowd forecasts had a lower mean weighted interval score
-(WIS, lower values indicate better performance) than both the renewal
-model and the Hub ensemble across all forecast horizons (Figure
-\ref{fig:agg-performance-all}A) and locations (Figure
-\ref{fig:performance-locations-rel}A). For two week ahead forecasts,
-mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts
-and 1.40 for the renewal model (Table \ref{tab:score-table-2}). Across
-all forecasting approaches, locations and forecast horizons, the
-distribution of WIS values was very right-skewed, and average
-performance was heavily influenced by outliers (Figure
-\ref{fig:distribution-scores}). Overall, low variance in forecast
-performance was closely linked with good mean performance (Figures
-\ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A),
-suggesting that the ability to avoid large errors was an important
-factor in determining overall performance. The impact of outlier values
-was especially pronounced for the renewal model, which had more outliers
-(Figure \ref{fig:distribution-scores}), as well as the highest standard
-deviation of WIS values (standard deviation of the WIS relative to the
-WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon),
-while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub
-ensemble (= 1) showed more stable performance.
-
-To varying degrees, all forecasts exhibited trend-following behaviour
-and were rarely able to predict a change in trend before it had
-happened. For example, all forecasts failed to predict the change in
-trend from increase to decrease that happened in November in Germany and
-severely overshot reported cases (Figure
-\ref{fig:forecasts-and-truth}A). This was most striking for the renewal
-model, which extrapolated unconstrained exponential growth based on the
-recent past of observations. The Hub ensemble and the crowd forecast,
-which had both been under-predicting throughout October, also failed to
-predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on
-November 2nd 2020 {[}50{]} and the change in the testing regime (with
-stricter test criteria) on November 11th 2020 {[}36{]}, were fastest to
-adapt to the new trend, and the Hub ensemble slowest. In December, cases
-rose again in Germany, with all models under-predicting this growth to
-varying extents. As in October, the renewal model captured the phase of
-exponential growth in cases slightly better than other approaches, but
-again overshot when reported case numbers fell over Christmas. The large
-variance in predictions in January in Germany (severe under-prediction
-followed by severe over-prediction) may in part be caused by the fact
-that the renewal model operated on daily data and therefore was
-susceptible to fluctuations in daily reporting around Christmas that
-would not have influenced on weekly reporting. Similar trends in
-performance were evident in Poland, with the crowd forecast quickest at
-adapting to the change in trend in November. In general, there were
-fewer large outlier forecasts in Poland and in particular the renewal
-model performed more in line with other forecasts there.
-
-All forecasting approaches, including the Hub ensemble, were
-overconfident, i.e.~they showed lower than nominal coverage (meaning
-that 50\% (90\%) prediction intervals generally covered less than 50\%
-(90\%) of the actually observed values) (Figure
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
-Coverage for all forecasts deteriorated with increasing forecast
-horizon, indicating that all forecasting approaches struggled to
-quantify uncertainty appropriately for case forecasts. This was
-especially an issue for crowd forecasts, which had markedly shorter
-prediction intervals (i.e., narrower and more confident predictive
-distributions) than other approaches (Figure
-\ref{fig:agg-performance-all}E) and only showed a small increase in
-uncertainty across forecast horizons. The crowd forecasts prediction
-intervals were also noticeably narrower than the default baseline shown
-to forecasters in the application (see Figure
-\ref{fig:compare-forecasters}).
-
-In spite of good performance in terms of the absolute error (Figure
-\ref{fig:agg-performance-all}G), the narrow forecast intervals led to
-forecasts which were severely overconfident (covering only 36\% and 55\%
-of all observations with the 50\% and 90\% prediction intervals of all
-forecasts made at a two week forecast horizon, and only 5\% and 38\%
-four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables
-\ref{tab:score-table-2} and \ref{tab:score-table-4}). Despite worse
-performance in terms of absolute error (Figure
-\ref{fig:agg-performance-all}G), the renewal model achieved better
-calibration (comparable to the Hub ensemble), as uncertainty increased
-rapidly across forecast horizons. The crowd forecasts, on the other
-hand, showed a smaller bias than the renewal model, but were
-overconfident.
-
-The renewal model exhibited a noticeable tendency towards
-over-predicting reported cases across all horizons. The crowd forecast
-tended to over-predict at longer forecast horizons, whereas the Hub
-ensemble showed no systematic bias (Figure
-\ref{fig:agg-performance-all}F). Regardless of a general relative
-tendency to over-predict, all forecasting approaches incurred larger
-absolute penalties from over- than from under-prediction (see
-decomposition of the WIS into absolute penalties for over-prediction,
-under-prediction and dispersion in Figures
-\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
-
-Generally, trends in overall performance were broadly similar across
-locations (Figures \ref{fig:performance-locations} and
-\ref{fig:performance-locations-rel}). Due to the differing population
-sizes and numbers of notifications in Germany and Poland absolute scores
-were difficult to compare directly. However, relative to the Hub
-ensemble, the crowd forecasts performed noticeably better in Germany
-than in Poland and the renewal model better in Poland than in Germany
-(Figures \ref{fig:performance-locations-rel}A,
-\ref{fig:performance-locations-rel}G,
-\ref{fig:agg-performance-all-Germany},
-\ref{fig:agg-performance-all-Poland}).
-
-\hypertarget{death-forecasts}{%
-\subsection{Death Forecasts}\label{death-forecasts}}
-
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as
-our model-based approaches across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B). Relative WIS values for the models
-two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1
-(Hub ensemble) and 1.79 (renewal model). The crowd forecasts performed
-better than the renewal model across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B), and also better than the convolution
-model three and four weeks ahead. Poor performance of the renewal model,
-especially at longer horizons, indicates that an approach that does not
-know about past cases, but instead estimates and projects a separate
-\(R_t\) trace from deaths, does not use the available information
-efficiently. The convolution model was able to outperform both the
-renewal model and the crowd forecasts at shorter forecast horizons
-(where the delay between cases and deaths means that future deaths are
-largely informed by present cases), but saw performance deteriorate at
-three and four weeks ahead (where case predictions from the renewal
-model were increasingly used to inform death predictions) (Figure
-\ref{fig:agg-performance-all}B, Table \ref{tab:score-table-4}).
-
-As past cases and hospitalisations can be used as predictors, predicting
-a change in trend may be easier for deaths than for cases. Even though
-all forecasts generally struggled with this, there were some instances
-where changing trends were well captured or even anticipated. In Poland,
-for example, the Hub ensemble was able to capture or even anticipate the
-peak in deaths in December quite well (whereas the renewal model and
-crowd forecast did not). The renewal model, which mostly exhibited
-trend-following behaviour, correctly predicted another increase in
-weekly deaths in mid-January (potentially based on changes in daily
-deaths, as the renewal model did not know about past cases). In Germany
-in early January, all models predicted a decrease in deaths two to three
-weeks before it actually happened. Predictions from the renewal model at
-that time were likely strongly influenced by an unexpected drop in
-reported deaths in December. The other forecasting approaches and in
-particular, the convolution model may have been affected by potentially
-under-reported case numbers around Christmas. When the decrease that all
-models had predicted to happen in early January failed to materialise,
-the renewal model and the crowd forecast noticeably over-corrected and
-over-predicted deaths in the following weeks, while the Hub ensemble,
-and to a slightly lesser degree, the convolution model were able to
-capture the downturn well when it finally happened at the end of
-January.
-
-Death forecasts, generally, showed greater coverage of the 50\% and 90\%
-prediction intervals than case forecasts and no decrease in coverage
-across forecast horizons, indicating that it might be easier to
-appropriately quantify uncertainty for death forecasts. The Hub ensemble
-had the greatest coverage, with empirical coverage of the 50\% and 90\%
-prediction intervals exceeding 50\%, and 90\%, respectively, across all
-forecast horizons. Coverage for the crowd forecasts and our model-based
-approaches was generally lower than that of the Hub ensemble and mostly
-slightly lower than nominal coverage (Figure
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D). As
-for cases, the crowd forecast tended to have the narrowest prediction
-intervals and uncertainty increased most slowly across forecast
-horizons, and the renewal model forecasts generally were widest. The
-convolution model had relatively narrow prediction intervals for short
-forecast horizons, but had rapidly (and non-linearly) increasing
-uncertainty for longer forecast horizons, driven by increasing
-uncertainty in the underlying case forecasts.
-
-For deaths, the ensemble of crowd forecasts had a consistent tendency to
-over-predict \ref{fig:agg-performance-all}F. The convolution model had a
-strong tendency to under-predict, with the magnitude of under-prediction
-steadily decreasing for longer forecast horizons. The renewal model
-(which over-predicted for cases) and the Hub ensemble slightly tended
-towards under-prediction. For deaths, absolute over- and
-under-prediction penalties were more in line with a general relative
-tendency to over- or under-predict than for cases (Figure
-\ref{fig:agg-performance-all}A, \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2}, \ref{tab:score-table-4}).
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} \caption{Distribution of scores.
-A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
-Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores.}\label{fig:distribution-scores}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.
-“Hub-ensemble”    extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-rel}
-\end{figure}
-
-\hypertarget{contributions-hub}{%
-\subsection{Contribution to the Forecast Hub}\label{contributions-hub}}
-
-Of our three models, only the renewal model and the crowd forecast were
-included in the official Forecast Hub median ensemble
-(``hub-ensemble-realised''), while the convolution model was never
-included as it was deemed too similar to the existing renewal model. In
-the official Hub ensemble, there were on average 7.1 models included
-(including our own), with a median of 7, a minimum of 4 (on 28 December
-2020 over the Christmas period) and a maximum of 10. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively. An
-overview of all models and ensemble versions is shown in Table
-\ref{tab:table-ensemble-versions} in the SI.
-
-For cases, our contributions (compared to the Hub ensemble without our
-contributions) consistently improved performance across all forecasting
-horizons (rel. WIS 0.9 two weeks ahead, Table
-\ref{tab:score-table-ensemble-2}). Contributions from the crowd
-forecasts alone also improved performance of the Hub ensemble across all
-forecast horizons, while contributions from the renewal model had a
-negative effect for longer horizons (rel. WIS 1.02 three weeks ahead,
-1.06 four weeks ahead). The realised ensemble including both models
-performed better or equal compared to all versions with only one model
-included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model
-have improved performance (Table \ref{tab:score-table-ensemble-4}). The
-realised ensemble performed comparably to the crowd forecasts for
-predictions one to two weeks ahead, and worse for greater forecast
-horizons.
-
-For deaths, contributions from the renewal model and crowd forecast
-together improved performance only for one week ahead predictions and
-showed an increasingly negative impact on performance for longer
-horizons (rel. WIS of the Hub-ensemble-realised 1.01 two weeks ahead,
-1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and
-\ref{tab:score-table-ensemble-4}). Individual contributions from both
-the renewal model and the crowd forecast were largely negative, while a
-version of the Hub ensemble with only the convolution model included
-would have performed consistently better across all forecast horizons
-(with the positive impact increasing for longer horizons). This is
-especially interesting as the convolution model performed consistently
-worse than the pre-existing Hub ensemble (Figure
-\ref{fig:agg-performance-all}) and especially worse for longer horizons.
-
-We also considered the impact of our contributions on a version of the
-Hub ensemble constructed by taking the quantile-wise mean, rather than
-the median. General trends were similar, with the notable exception of
-the convolution model, which had a consistently positive impact on the
-median ensemble, but a mixed and mostly slightly negative impact on the
-mean ensemble (Figures \ref{fig:agg-performance-ensemble-rel}B and
-\ref{fig:agg-performance-ensemble-mean}B). This may happen if a model is
-more correct directionally relative to the pre-existing ensemble, but
-overshoots in absolute terms, thereby moving the ensemble too far. For
-both the mean and the median ensemble, changes in performance from
-adding or removing models were of a similar order of magnitude,
-suggesting that at least in this instance, with a relatively small
-ensemble size, the median ensemble was not necessarily more `robust' to
-changes than the mean ensemble. However, the ensemble version with all
-our forecasts included (``hub-ensemble-with-all'') tended to perform
-relatively better for the median ensemble than the mean ensemble,
-suggesting that adding more models may be more beneficial or `safer' for
-the median than for the mean ensemble as directional errors can more
-easily cancel out than errors in absolute terms.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Epidemiological forecasting modelling combines knowledge about
-infectious disease dynamics with the subjective opinion of the
-researcher who develops and refines the model. In this study, we
-compared forecasts of cases of and deaths from COVID-19 in Germany and
-Poland based purely on human judgement and elicited from a crowd of
-researchers and volunteers against forecasts from two semi-mechanistic
-epidemiological models. In spite of the small number of participants and
-a general tendency to be overconfident, crowd forecasts consistently
-outperformed our epidemiological models as well as the Hub ensemble when
-forecasting cases but not when forecasting deaths. This suggests that
-humans might be relatively good at foreseeing trends that are hard to
-model but may struggle to form an intuition for the exact relationship
-between cases and deaths.
-
-Past studies have evaluated the performance of model-based forecasting
-approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of
-(expert-tuned) model-based approaches {[}e.g. 12,13,14{]}, or
-exclusively on human forecasts {[}19,20,24,25{]}. In contrast, we
-directly compared human and model-based forecasts. This is similar to
-the approach taken by {[}11{]}, but extends it in several ways. While
-Farrow et al.~only asked for point predictions and constructed a
-predictive distribution from these, we asked participants to provide a
-full predictive distribution, allowing us to compare human forecasts and
-models without any further assumptions, as well as to analyse how humans
-quantified their uncertainty. In addition, we compared crowd forecasts
-to two semi-mechanistic models informed by basic epidemiological
-knowledge of COVID-19, allowing us to assess not only relative
-performance but also to analyse qualitative differences between human
-judgement and model-based insight. In terms of interpretability of the
-results, exact knowledge of our two models, as well as focus on a
-limited set of targets and locations was a major advantage of our study
-compared to larger studies conducted by the Forecast Hubs
-{[}12--15,17{]}.
-
-The strong performance of crowd forecasts in our study is in line with
-results from Farrow et al.~who also report strong performance of human
-predictions in past Flu challenges despite difficulties to recruit a
-large number of participants. The advantage of crowd forecasts we
-observed over our semi-mechanistic models is likely in part explained by
-the fact that we compared an ensemble of crowd forecasts with single
-models. However, this probably explains only part of the difference, and
-performance relative to the Hub ensemble strongly suggests that human
-insight is valuable when forecasting highly volatile and potentially
-hard-to-predict quantities such as case numbers. One potential
-explanation is that humans can have access to data that is not available
-to or hard to integrate into model-based forecasts. Relatively good
-performance of our semi-mechanistic models short-term, but not
-longer-term, suggests that model-based forecasts are helpful to
-extrapolate from current conditions, but require some form of human
-intervention or additional assumptions to inform forecasts when
-conditions change over time. This human intervention may be particularly
-important when dealing with artefacts in reporting and data anomalies
-(and especially when using daily, rather than weekly data). The large
-variance in predictions in January in Germany for example (severe
-under-prediction followed by severe over-prediction, see Figure
-\ref{fig:forecasts-and-truth}A), may in part be caused by the fact that
-the renewal model operated on daily data and therefore was susceptible
-to fluctuations in daily reporting which have less of an influence on
-weekly reporting.
-
-Our results suggest that human intervention may be less beneficial when
-forecasting deaths (especially at shorter horizons, when deaths are
-largely dependent on already observed cases), which benefits from the
-ability to model the delays and exact epidemiological relationships
-between different leading and lagged indicators. Relatively good
-performance of the convolution model, especially compared to the poor
-performance of the renewal model on deaths (which used only deaths to
-estimate and predict the effective reproduction number) underlines the
-importance of including leading indicators such as cases as a predictor
-for deaths.
-
-Given the low number of participants in our study, it is difficult to
-generalise conclusions about crowd predictions to other settings. Using
-R shiny as a platform for the web application arguably created some
-limits to user experience and performance, influencing the number of
-participants and potentially creating a self-selection effect.
-Motivating forecasters to contribute regularly proved challenging,
-especially given that the majority of our participants were from the UK
-and may not have been familiar with all relevant details of the
-situation in Germany and Poland. On the other hand, R shiny facilitated
-quick development and allowed us to provide our crowd forecasting
-tooling as an open source R package, meaning that it is available for
-others to use, for example in settings like early-stage outbreaks where
-model-based forecasts are not available. In light of the relatively
-small number of Hub ensemble models, performance of the Hub ensemble is
-also difficult to generalise. More research is needed to replicate these
-findings and investigate how crowd forecasts compare against the types
-of models and model ensembles policy makers use to inform their
-decisions.
-
-Our work suggests that crowd forecasts and model-based forecasts could
-have different strengths and may be able to complement each other. When
-choosing a suitable approach for a given task it is important to take
-into account how the output will be used. In this work we focused on
-forecasts (which aim to predict future data points whilst accounting for
-all factors that might influence them), whereas policy makers might be
-more interested in projections (which show what would happen in the
-absence of any events that could change the trend) or scenario
-modelling. Forecasts may not be a suitable basis for informing policy
-decisions, if forecasters already have factored in the expectation of a
-future intervention. Model-based approaches can be either forecasts or
-projections depending on the assumptions, whereas eliciting projections
-that are not influenced by implicit assumptions about the future from
-humans may be harder.
-
-Further work should explore the effects of humans refining their
-mathematical models or changing model outputs in more detail.
-Model-based forecasts could be used as an input to human judgement, with
-researchers adjusting predictions generated by models. Seeing a
-model-based forecast could help humans calibrate uncertainty better,
-while allowing for manual intervention to adapt spurious trend
-predictions. Tools need to be developed to facilitate this process at a
-larger scale. Human insight could also be used as an input to models.
-Such a `hybrid' forecasting approach could for example ask humans to
-predict the trend of the effective reproduction number \(R_t\) or the
-doubling rate (i.e.~how the epidemic evolves) into the future and use
-this to estimate the exact number of cases, hospitalisations or deaths
-this would imply. In light of severe overconfidence, yet good
-performance in terms of the absolute error, post-processing of human
-forecasts to adjust and widen prediction intervals may be another
-promising approach. Crowd forecasting in general could benefit greatly
-from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of
-the limited resources available and the small number of participants,
-this seems worthwhile to further develop and explore.
-
-\clearpage
-
-\textbf{Acknowledgements}
-
-NIB received funding from the Health Protection Research Unit (grant
-code NIHR200908, https://www.nihr.ac.uk/). SA's work was funded by the
-Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/). The work
-of JB was supported by the Helmholtz Foundation
-(https://www.helmholtz.de/) via the SIMCARD Information and Data Science
-Pilot Project. This research was partly funded by the National Institute
-for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 \&
-16/136/46) using UK aid from the UK Government to support global health
-research. The views expressed in this publication are those of the
-author(s) and not necessarily those of the NIHR or the UK Department of
-Health and Social Care. BJQ is supported in part by a grant from the
-Bill and Melinda Gates Foundation (OPP1139859,
-https://www.gatesfoundation.org/). EvL acknowledges funding by the
-National Institute for Health Research (NIHR) Health Protection Research
-Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908,
-https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research
-and innovation programme - project EpiPose (101003688,
-https://ec.europa.eu/programmes/horizon2020/). AC acknowledges funding
-by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/),
-and the Academy of Medical Sciences (https://acmedsci.ac.uk/). SF's work
-was supported by the Wellcome Trust (grant: 210758/Z/18/Z,
-https://wellcome.org/), and the NIHR (NIHR200908,
-https://www.nihr.ac.uk/).
-
-We thank all forecasters who participated in this study for their
-contribution.
-
-We would also like to acknowledge (in a randomised order) the members of
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group at the the London School of Hygiene \& Tropical Medicine:
-Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie
-Diamond, Katherine E. Atkins, Rein M G J Houben, Jiayao Lei, Rachel
-Lowe, David Simons, Sophie R Meakin, Nicholas G. Davies, Timothy W
-Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly,
-Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas,
-Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia
-Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson,
-Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang
-Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C
-Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun,
-Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche,
-James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday,
-Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan
-Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R
-Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael
-Pung, Anna M Foss.
-
-\clearpage
-
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
-
-\hypertarget{appendix-supplementary-information}{%
-\section*{(APPENDIX) Supplementary
-information}\label{appendix-supplementary-information}}
-\addcontentsline{toc}{section}{(APPENDIX) Supplementary information}
-
-\hypertarget{supplementary-information}{%
-\section{Supplementary information}\label{supplementary-information}}
-
-\hypertarget{scoring-metrics-used}{%
-\subsection{Scoring metrics used}\label{scoring-metrics-used}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{9.3cm}}
-\caption{\label{tab:scoring-metrics}Overview of the scoring metrics used.}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{Overview of the scoring metrics used. \textit{(continued)}}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-WIS (Weighted) interval score & The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
+wis <- list(
+  Metric = "WIS (Weighted) interval score", 
+  `Explanation` = r"(The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
 It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
@@
 
-\cellcolor{gray!6}{Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.}\\
-\addlinespace \addlinespace
-Interval coverage & Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
+Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.)", 
+  `Caveats` = "The wis is based on measures of absolute error. When averaging across multiple targets, it will therefore be dominated by targets with higher absolute values.",
+  `References` = ""
+)
+
+interval_coverage <- list(
+  `Metric` = "Interval coverage", 
+  `Explanation` = r"(Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
 Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
-we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.\\
-\addlinespace \addlinespace
-Bias & (Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict. Values are between -1 and 1 and 0 ideally. For continuous forecasts, bias is given as 
+we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.)",
+  `Caveats` = "",
+  `References` = ""
+)
+
+bias <- list(
+  `Metric` = "Bias", 
+  `Explanation` = r"((Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict.
+Values are between -1 and 1 and 0 ideally.
+For continuous forecasts, bias is given as
 $$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
@@
 
-\cellcolor{gray!6}{In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
-It is therefore a more robust measurement.}\\*
-\end{longtable}
+In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
+It is therefore a more robust measurement.)",
+  `Caveats` = "",
+  `References` = ""
+)
 
-\clearpage
+data <- rbind(as.data.frame(wis), 
+              as.data.frame(interval_coverage),
+              as.data.frame(bias))
 
-\hypertarget{the-crowdforecasting-app}{%
-\subsection{The crowdforecasting app}\label{the-crowdforecasting-app}}
+data[, 1:2] %>%
+  kableExtra::kbl(format = "latex", booktabs = TRUE, 
+                  escape = FALSE,
+                  longtable = TRUE,
+                  linesep = c('\\addlinespace \\addlinespace')) %>%
+  kableExtra::column_spec(1, width = "2.5cm") %>%
+  kableExtra::column_spec(2, width = "9.3cm") %>%
+  kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))
 
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../crowd-forecast/Screenshot-forecasting-app} \caption{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).
-}\label{fig:screenshot}
-\end{figure}
-
-\clearpage
-
-\hypertarget{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}{%
-\subsection{Text S1. Further details on the semi-mechanistic forecasting
-models}\label{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}}
-
-\hypertarget{renewal-equation-model}{%
-\subsubsection{Renewal equation model}\label{renewal-equation-model}}
-
-The model was initialised prior to the first observed data point by
-assuming constant exponential growth for the mean of assumed delays from
-infection to case report.
-
-\begin{align}
-  I_{t} &= I_0 \exp  \left(r t \right)  \\
-  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
-  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
-\end{align}
-
-Where \(I_{obs}\) and \(r_{obs}\) are estimated from the first week of
-observed data. For the time window of the observed data infections were
-then modelled by weighting previous infections by the generation time
-and scaling by the instantaneous reproduction number. These infections
-were then convolved to cases by date (\(O_t\)) and cases by date of
-report (\(D_t\)) using log-normal delay distributions. This model can be
-defined mathematically as follows,
-
-\begin{align}
-  \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
-  I_t &= R_t \sum_{\tau = 1}^{15} w(\tau | \mu_{w}, \sigma_{w}) I_{t - \tau} \\
-  O_t &= \sum_{\tau = 0}^{15} \xi_{O}(\tau | \mu_{\xi_{O}}, \sigma_{\xi_{O}}) I_{t-\tau} \\
-  D_t &= \alpha \sum_{\tau = 0}^{15} \xi_{D}(\tau | \mu_{\xi_{D}}, \sigma_{\xi_{D}}) O_{t-\tau} \\ 
-  C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
-\end{align}
-
-Where, \begin{align}
-     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
-    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
-    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
-\end{align}
-
-This model used the following priors for cases,
-
-\begin{align}
-     R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
-    \mu_w &\sim \mathcal{N}(3.6, 0.7) \\
-    \sigma_w &\sim \mathcal{N}(3.1, 0.8) \\
-    \mu_{\xi_{O}} &\sim \mathcal{N}(1.62, 0.064) \\
-    \sigma_{\xi_{O}} &\sim \mathcal{N}(0.418, 0.069) \\
-    \mu_{\xi_{D}} &\sim \mathcal{N}(0.614, 0.066) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(1.51, 0.048) \\
-    \alpha &\sim \mathcal{N}(0.25, 0.05) \\
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-and updated the reporting process as follows when forecasting deaths,
-
-\begin{align}
-    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
-    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
-\end{align}
-
-\(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) were truncated to be
-greater than 0 and with \(\xi\), and \(w\) normalised to sum to 1.
-
-The prior for the generation time was sourced from {[}51{]} but refit
-using a log-normal incubation period with a mean of 5.2 days (SD 1.1)
-and SD of 1.52 days (SD 1.1) with this incubation period also being used
-as a prior {[}52{]} for \(\xi_{O}\). This resulted in a
-gamma-distributed generation time with mean 3.6 days (standard deviation
-(SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates. We estimated
-the delay between symptom onset and case report or death required to
-convolve latent infections to observations by fitting an integer
-adjusted log-normal distribution to 10 subsampled bootstraps of a public
-linelist for cases in Germany from April 2020 to June 2020 with each
-bootstrap using 1\% or 1769 samples of the available data {[}45,53{]}
-and combining the posteriors for the mean and standard deviation of the
-log-normal distribution {[}40,42,46,54{]}.
-
-\(GP_t\) is an approximate Hilbert space Gaussian process as defined in
-{[}55{]} using a Matern 3/2 kernel using a boundary factor of 1.5 and 17
-basis functions (20\% of the number of days used in fitting). The length
-scale of the Gaussian process was given a log-normal prior with a mean
-of 21 days, and a standard deviation of 7 days truncated to be greater
-than 3 days and less than 60 days. The magnitude of the Gaussian process
-was assumed to be normally distributed centred at 0 with a standard
-deviation of 0.1.
-
-From the forecast time horizon (\(T\)) and onwards the last value of the
-Gaussian process was used (hence \(R_t\) was assumed to be fixed) and
-latent infections were adjusted to account for the proportion of the
-population that was susceptible to infection as follows,
-
-\begin{equation}
-    I_t = (N - I^c_{t-1}) \left(1 - \exp \left(\frac{-I'_t}{N - I^c_{T}}\right)\right),
-\end{equation}
-
-where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\)
-and \(I'_t\) are the unadjusted infections defined above. This
-adjustment is based on that implemented in the \texttt{epidemia} R
-package {[}56,57{]}.
-
-\hypertarget{convolution-model}{%
-\paragraph{Convolution model}\label{convolution-model}}
-
-The convolution model shares the same observation model as the renewal
-model but rather than assuming that an observation is predicted by
-itself using the renewal equation instead assumes that it is predicted
-entirely by another observation after some parametric delay. It can be
-defined mathematically as follows,
-
-\begin{equation} 
-    D_{t} \sim \mathrm{NB}\left(\omega_{(t \mod 7)} \alpha \sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) C_{t-\tau},  \phi \right)
-\end{equation}
-
-with the following priors,
-
-\begin{align}
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \alpha &\sim \mathcal{N}(0.01, 0.02) \\
-    \xi &\sim \mathcal{LN}(\mu, \sigma) \\
-    \mu &\sim \mathcal{N}(2.5, 0.5) \\
-\sigma &\sim \mathcal{N}(0.47, 0.2) \\
-\phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-with \(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) truncated to be
-greater than 0 and with \(\xi\) normalised such that
-\(\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1\).
-
-\hypertarget{model-fitting}{%
-\subsubsection{Model fitting}\label{model-fitting}}
-
-Both models were implemented using the \texttt{EpiNow2} R package
-(version 1.3.3) {[}40{]}. Each forecast target was fitted independently
-for each model using Markov-chain Monte Carlo (MCMC) in stan {[}46{]}. A
-minimum of 4 chains were used with a warmup of 250 samples for the
-renewal equation-based model and 1000 samples for the convolution model.
-2000 samples total post warmup were used for the renewal equation model
-and 4000 samples for the convolution model. Different settings were
-chosen for each model to optimise compute time contingent on
-convergence. Convergence was assessed using the R hat diagnostic
-{[}46{]}. For the convolution model forecast the case forecast from the
-renewal equation model was used in place of observed cases beyond the
-forecast horizon using 1000 posterior samples. 12 weeks of data was used
-for both models though only 3 weeks of data were included in the
-likelihood for the convolution model.
-
-\clearpage
-
-\hypertarget{tables-with-results-of-the-forecast-evaluation}{%
-\subsection{Tables with results of the forecast
-evaluation}\label{tables-with-results-of-the-forecast-evaluation}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 7010 (0.8) & 7480 (0.64) & 2680 (0.73) & 1700 (1.38) & 2630 (0.68) & -0.01 & 10400 (0.82) & 0.55 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 8740 (1) & 11800 (1.01) & 2190 (0.6) & 2720 (2.21) & 3830 (0.99) & 0.18 & 12000 (0.94) & 0.48 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 16200 (0.89) & 16600 (0.76) & 3660 (0.6) & 5930 (1.56) & 6600 (0.78) & -0.01 & 23300 (0.87) & 0.36 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25600 (1.4) & 33800 (1.54) & 5420 (0.88) & 5920 (1.56) & 14200 (1.69) & 0.17 & 34600 (1.29) & 0.43 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 27000 (0.81) & 26200 (0.64) & 4750 (0.52) & 11000 (1.43) & 11200 (0.67) & 0.02 & 39000 (0.83) & 0.14 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 50600 (1.51) & 70000 (1.72) & 10800 (1.18) & 7710 (1) & 32100 (1.93) & 0.13 & 68700 (1.46) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 39200 (0.7) & 38600 (0.52) & 5970 (0.49) & 15600 (1.26) & 17600 (0.56) & 0.07 & 54800 (0.74) & 0.05 & 0.38\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 91700 (1.64) & 135000 (1.83) & 19500 (1.6) & 8990 (0.72) & 63200 (2.02) & 0.09 & 125000 (1.68) & 0.31 & 0.48\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{aggregate-performance-by-location}{%
-\subsection{Aggregate performance by
-location}\label{aggregate-performance-by-location}}
-
-\hypertarget{performance-in-germany}{%
-\subsubsection{Performance in Germany}\label{performance-in-germany}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Germany-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Germany}
-\end{figure}
-
-\hypertarget{performance-in-poland}{%
-\subsubsection{Performance in Poland}\label{performance-in-poland}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Poland-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Poland}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-absolute-terms}{%
-\subsubsection{Performance across locations in absolute
-terms}\label{performance-across-locations-in-absolute-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-v4} \caption{Visualisation of aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-relative-terms}{%
-\subsection{Performance across locations in relative
-terms}\label{performance-across-locations-in-relative-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4} \caption{Visualisation of relative aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals.
-E: Dispersion.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast.
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations-rel}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-daily-reported-cases-and-deaths}{%
-\subsection{Visualisation of daily reported cases and
-deaths}\label{visualisation-of-daily-reported-cases-and-deaths}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily_truth} \caption{Visualisation of daily report data.
-The black line represents weekly data divided by seven.
-Data were last accessed through the German and Polish Forecast Hub on August 21 2021.}\label{fig:daily-truth}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily-data-updates} \caption{Visualisation of the absolute difference between the daily report data at the time and the data now.
-In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:daily-truth-update}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/weekly-data-updates} \caption{Visualisation of the relative difference between the weekly report data at the time and the data now.
-Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:weekly-truth-update}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}{%
-\subsection{Visualisation of scores and forecasts 1, 3, 4 weeks
-ahead}\label{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} \caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} \caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} \caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-4}
-\end{figure}
-
-\clearpage
-
-\hypertarget{distribution-of-scores}{%
-\subsection{Distribution of scores}\label{distribution-of-scores}}
-
-\hypertarget{absolute-scores}{%
-\subsubsection{Absolute scores}\label{absolute-scores}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1} \caption{A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3} \caption{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4} \caption{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-4}
-\end{figure}
-
-\hypertarget{ranks-achieved-by-forecasts}{%
-\subsubsection{Ranks achieved by
-forecasts}\label{ranks-achieved-by-forecasts}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-2}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-4}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} \caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-renewal} \caption{Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences-renewal}
-\end{figure}
-
-\newpage
-
-\hypertarget{comparison-of-ensembles}{%
-\subsection{Comparison of ensembles}\label{comparison-of-ensembles}}
-
-\hypertarget{performance-visualisation-mean-ensemble}{%
-\subsubsection{Performance visualisation mean
-ensemble}\label{performance-visualisation-mean-ensemble}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble”     extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
-Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-mean}
-\end{figure}
-
-\hypertarget{tables-median-ensemble}{%
-\subsubsection{Tables median ensemble}\label{tables-median-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 6970 (0.79) & 8260 (0.71) & 3060 (0.83) & 943 (0.77) & 2970 (0.77) & 0.04 & 10800 (0.85) & 0.55 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 7820 (0.89) & 9630 (0.82) & 3270 (0.89) & 1210 (0.98) & 3330 (0.86) & -0.02 & 12000 (0.94) & 0.48 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 7960 (0.91) & 10300 (0.88) & 3190 (0.87) & 1020 (0.83) & 3760 (0.97) & 0.04 & 12100 (0.95) & 0.57 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 16400 (0.9) & 19600 (0.89) & 5350 (0.87) & 3290 (0.87) & 7730 (0.92) & 0.02 & 24200 (0.9) & 0.43 & 0.69\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 16900 (0.92) & 19600 (0.89) & 5230 (0.85) & 4310 (1.13) & 7370 (0.88) & 0.00 & 24600 (0.92) & 0.38 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 17500 (0.96) & 21400 (0.98) & 5830 (0.95) & 2880 (0.76) & 8770 (1.04) & 0.00 & 25500 (0.95) & 0.45 & 0.71\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 235 (0.95) & 332 (0.98) & 88.6 (0.96) & 90.4 (0.79) & 55.5 (1.33) & -0.01 & 323 (0.97) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 234 (0.94) & 331 (0.98) & 85.2 (0.92) & 98.1 (0.85) & 50.2 (1.21) & -0.05 & 329 (0.99) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 234 (0.94) & 329 (0.97) & 90.7 (0.98) & 118 (1.03) & 25.3 (0.61) & -0.08 & 333 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 239 (0.96) & 337 (1) & 85.2 (0.92) & 99.6 (0.87) & 54.2 (1.3) & -0.03 & 322 (0.96) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 246 (0.99) & 342 (1.01) & 91.5 (0.99) & 106 (0.92) & 48.6 (1.17) & -0.06 & 342 (1.02) & 0.67 & 0.92\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 296 (1.01) & 398 (1.03) & 125 (0.95) & 91 (0.84) & 80.2 (1.55) & 0.05 & 486 (1.13) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 303 (1.04) & 423 (1.1) & 115 (0.87) & 122 (1.13) & 66.1 (1.27) & 0.00 & 483 (1.13) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 270 (0.92) & 385 (1) & 121 (0.92) & 119 (1.1) & 29.9 (0.58) & -0.04 & 403 (0.94) & 0.58 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 303 (1.04) & 392 (1.02) & 122 (0.92) & 106 (0.98) & 74.6 (1.44) & 0.03 & 499 (1.16) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 296 (1.01) & 397 (1.03) & 128 (0.97) & 97.1 (0.9) & 71.2 (1.37) & -0.01 & 462 (1.08) & 0.67 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 30800 (0.92) & 38600 (0.95) & 7910 (0.87) & 6890 (0.9) & 16000 (0.96) & 0.03 & 44200 (0.94) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 30800 (0.92) & 34100 (0.84) & 7500 (0.82) & 8960 (1.17) & 14300 (0.86) & 0.02 & 44100 (0.94) & 0.24 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 34000 (1.02) & 43100 (1.06) & 8860 (0.97) & 6300 (0.82) & 18900 (1.14) & 0.02 & 48100 (1.03) & 0.29 & 0.60\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 51200 (0.92) & 69900 (0.95) & 10900 (0.89) & 11100 (0.9) & 29300 (0.94) & 0.04 & 69600 (0.94) & 0.19 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 48800 (0.87) & 58600 (0.8) & 9700 (0.8) & 13700 (1.1) & 25400 (0.81) & 0.00 & 65800 (0.88) & 0.19 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 59100 (1.06) & 84100 (1.14) & 12600 (1.03) & 10100 (0.81) & 36400 (1.16) & 0.01 & 78900 (1.06) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 332 (1.04) & 388 (1.18) & 158 (0.92) & 78.7 (0.85) & 95 (1.72) & -0.02 & 547 (1.12) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 321 (1.01) & 385 (1.17) & 153 (0.89) & 100 (1.08) & 68.1 (1.24) & -0.01 & 535 (1.1) & 0.54 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 298 (0.93) & 337 (1.03) & 155 (0.9) & 106 (1.14) & 37.5 (0.68) & -0.04 & 441 (0.9) & 0.67 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 319 (1) & 342 (1.04) & 160 (0.93) & 85.1 (0.92) & 73.6 (1.34) & -0.02 & 547 (1.12) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 332 (1.04) & 363 (1.11) & 168 (0.98) & 86.1 (0.93) & 78.2 (1.42) & -0.02 & 528 (1.08) & 0.58 & 0.96\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 445 (1.05) & 532 (1.2) & 193 (0.91) & 107 (0.85) & 144 (1.68) & -0.03 & 700 (1.04) & 0.54 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 399 (0.94) & 438 (0.99) & 195 (0.92) & 105 (0.83) & 97.9 (1.14) & -0.05 & 692 (1.03) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 384 (0.91) & 387 (0.87) & 196 (0.92) & 122 (0.97) & 65.9 (0.77) & -0.06 & 602 (0.89) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 407 (0.96) & 456 (1.03) & 202 (0.95) & 105 (0.83) & 101 (1.18) & -0.03 & 669 (0.99) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 457 (1.08) & 527 (1.19) & 208 (0.98) & 129 (1.02) & 121 (1.41) & -0.06 & 744 (1.1) & 0.50 & 0.96\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\hypertarget{tables-mean-ensemble}{%
-\subsubsection{Tables mean ensemble}\label{tables-mean-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 8680 (1) & 10300 (1) & 3700 (1) & 1460 (1) & 3520 (1) & -0.02 & 13400 (1) & 0.50 & 0.86\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 7600 (0.88) & 8770 (0.85) & 3360 (0.91) & 1090 (0.75) & 3140 (0.89) & 0.01 & 11900 (0.89) & 0.52 & 0.90\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 8050 (0.93) & 9070 (0.88) & 3520 (0.95) & 1410 (0.97) & 3120 (0.89) & -0.02 & 12600 (0.94) & 0.48 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 8090 (0.93) & 9780 (0.95) & 3490 (0.94) & 1110 (0.76) & 3490 (0.99) & 0.02 & 12700 (0.95) & 0.57 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 19000 (1) & 22100 (1) & 5960 (1) & 3690 (1) & 9340 (1) & 0.02 & 28800 (1) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 17100 (0.9) & 20600 (0.93) & 5550 (0.93) & 2850 (0.77) & 8660 (0.93) & 0.05 & 26000 (0.9) & 0.38 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 17600 (0.93) & 20000 (0.9) & 5540 (0.93) & 3790 (1.03) & 8230 (0.88) & 0.01 & 26800 (0.93) & 0.36 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 18300 (0.96) & 22600 (1.02) & 5910 (0.99) & 2640 (0.72) & 9720 (1.04) & 0.06 & 27700 (0.96) & 0.38 & 0.76\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 229 (1) & 292 (1) & 101 (1) & 90.4 (1) & 36.7 (1) & -0.07 & 315 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 219 (0.96) & 289 (0.99) & 96.8 (0.96) & 79.8 (0.88) & 42.6 (1.16) & -0.04 & 297 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 217 (0.95) & 287 (0.98) & 95.3 (0.94) & 83.1 (0.92) & 38.7 (1.05) & -0.07 & 300 (0.95) & 0.67 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 225 (0.98) & 292 (1) & 98.7 (0.98) & 94.2 (1.04) & 32 (0.87) & -0.09 & 314 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 222 (0.97) & 289 (0.99) & 98 (0.97) & 84.1 (0.93) & 39.6 (1.08) & -0.04 & 295 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 225 (0.98) & 290 (0.99) & 99.7 (0.99) & 84.7 (0.94) & 40.5 (1.1) & -0.05 & 314 (1) & 0.71 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 256 (1) & 306 (1) & 138 (1) & 64.5 (1) & 53.2 (1) & 0.04 & 374 (1) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 270 (1.05) & 338 (1.1) & 136 (0.99) & 65.2 (1.01) & 68.1 (1.28) & 0.06 & 413 (1.1) & 0.75 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 268 (1.05) & 346 (1.13) & 133 (0.96) & 78.7 (1.22) & 57.1 (1.07) & 0.05 & 408 (1.09) & 0.75 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 259 (1.01) & 322 (1.05) & 133 (0.96) & 81.7 (1.27) & 44.4 (0.83) & 0.03 & 380 (1.02) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 264 (1.03) & 315 (1.03) & 133 (0.96) & 70.1 (1.09) & 60 (1.13) & 0.06 & 404 (1.08) & 0.71 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 264 (1.03) & 332 (1.08) & 141 (1.02) & 60.1 (0.93) & 63.1 (1.19) & 0.06 & 390 (1.04) & 0.79 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 35600 (1) & 42100 (1) & 9340 (1) & 7050 (1) & 19200 (1) & 0.03 & 51200 (1) & 0.26 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 32100 (0.9) & 40500 (0.96) & 8830 (0.95) & 4920 (0.7) & 18300 (0.95) & 0.07 & 47200 (0.92) & 0.29 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 32200 (0.9) & 36700 (0.87) & 8430 (0.9) & 7190 (1.02) & 16500 (0.86) & 0.04 & 46900 (0.92) & 0.24 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 35200 (0.99) & 46000 (1.09) & 9630 (1.03) & 4600 (0.65) & 20900 (1.09) & 0.08 & 51000 (1) & 0.38 & 0.67\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 60300 (1) & 79300 (1) & 15700 (1) & 10400 (1) & 34100 (1) & 0.04 & 78600 (1) & 0.29 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 55000 (0.91) & 77100 (0.97) & 14600 (0.93) & 6620 (0.64) & 33800 (0.99) & 0.11 & 75200 (0.96) & 0.33 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 53400 (0.89) & 66600 (0.84) & 13700 (0.87) & 10600 (1.02) & 29200 (0.86) & 0.06 & 70400 (0.9) & 0.26 & 0.60\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 61700 (1.02) & 89800 (1.13) & 16400 (1.04) & 6400 (0.62) & 38900 (1.14) & 0.12 & 82900 (1.05) & 0.31 & 0.64\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 289 (1) & 293 (1) & 178 (1) & 45.9 (1) & 65.7 (1) & 0.01 & 443 (1) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 310 (1.07) & 348 (1.19) & 182 (1.02) & 42 (0.92) & 86.5 (1.32) & 0.08 & 502 (1.13) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 315 (1.09) & 339 (1.16) & 178 (1) & 62.2 (1.36) & 74 (1.13) & 0.07 & 507 (1.14) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 297 (1.03) & 292 (1) & 174 (0.98) & 67.7 (1.47) & 55 (0.84) & 0.01 & 452 (1.02) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 294 (1.02) & 299 (1.02) & 172 (0.97) & 48 (1.05) & 74.2 (1.13) & 0.03 & 476 (1.07) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 310 (1.07) & 349 (1.19) & 189 (1.06) & 39.4 (0.86) & 81.9 (1.25) & 0.05 & 482 (1.09) & 0.62 & 1.00\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 437 (1) & 568 (1) & 232 (1) & 72 (1) & 134 (1) & 0.00 & 702 (1) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 445 (1.02) & 598 (1.05) & 237 (1.02) & 56.4 (0.78) & 152 (1.13) & 0.06 & 707 (1.01) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 421 (0.96) & 520 (0.92) & 239 (1.03) & 49.9 (0.69) & 132 (0.99) & 0.05 & 678 (0.97) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 398 (0.91) & 465 (0.82) & 235 (1.01) & 55.6 (0.77) & 107 (0.8) & 0.00 & 628 (0.89) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 418 (0.96) & 533 (0.94) & 222 (0.96) & 66.8 (0.93) & 129 (0.96) & 0.03 & 662 (0.94) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 467 (1.07) & 636 (1.12) & 248 (1.07) & 61 (0.85) & 158 (1.18) & 0.05 & 755 (1.08) & 0.67 & 1.00\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{sensitivity-analysis}{%
-\subsection{Sensitivity analysis}\label{sensitivity-analysis}}
-
-In the original analysis, cases and deaths were scored on different
-periods, as the convolution model was only added later. This sensitivity
-shows performance of all models restricted to the period from December
-14 2020 until March 1st 2021 where all models were available.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-late}
-\end{figure}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 4980 (0.74) & 5730 (0.64) & 2070 (0.6) & 728 (0.74) & 2190 (0.94) & 0.09 & 7810 (0.82) & 0.54 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 6730 (1) & 8960 (1) & 3430 (1) & 978 (1) & 2330 (1) & -0.09 & 9550 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 9640 (1.43) & 13300 (1.48) & 1970 (0.57) & 4170 (4.26) & 3500 (1.5) & 0.09 & 12700 (1.33) & 0.46 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 10700 (0.99) & 13800 (1.1) & 2880 (0.58) & 2350 (0.85) & 5430 (1.79) & 0.08 & 15400 (1.07) & 0.46 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 10800 (1) & 12500 (1) & 4940 (1) & 2780 (1) & 3030 (1) & -0.13 & 14400 (1) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25000 (2.31) & 34000 (2.72) & 4780 (0.97) & 8710 (3.13) & 11500 (3.8) & 0.05 & 32000 (2.22) & 0.50 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 17200 (1) & 16000 (0.98) & 3800 (0.63) & 5660 (0.85) & 7770 (1.74) & 0.07 & 26800 (1.1) & 0.08 & 0.58\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 17200 (1) & 16300 (1) & 6030 (1) & 6670 (1) & 4470 (1) & -0.16 & 24400 (1) & 0.33 & 0.67\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 37700 (2.19) & 55900 (3.43) & 8840 (1.47) & 10700 (1.6) & 18100 (4.05) & -0.03 & 49800 (2.04) & 0.33 & 0.58\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 26100 (0.95) & 21000 (0.84) & 4810 (0.7) & 11300 (0.83) & 10100 (1.43) & 0.04 & 39400 (1.05) & 0.00 & 0.46\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 27600 (1) & 25000 (1) & 6900 (1) & 13600 (1) & 7060 (1) & -0.19 & 37400 (1) & 0.29 & 0.54\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 48900 (1.77) & 77800 (3.11) & 13800 (2) & 11900 (0.88) & 23200 (3.29) & -0.10 & 65500 (1.75) & 0.38 & 0.58\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{overview-of-models-and-forecasters}{%
-\subsection{Overview of models and
-forecasters}\label{overview-of-models-and-forecasters}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{7.3cm}}
-\caption{\label{tab:table-ensemble-versions}Overview of the models and ensembles used.}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{Overview of the models and ensembles used. \textit{(continued)}}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-\cellcolor{gray!6}{Hub-ensemble-realised} & \cellcolor{gray!6}{Official Forecast Hub median ensemble.
-Created by the Forecast Hub officially under the name 'KITCOVIDhub-median\_ensemble' and used as the default ensemble.
-Included are our crowd forecasts as well as the renewal model (with one missed submission on December 28 2020, but not the convolution model which was deemed to similar to the renewal model.}\\
-\addlinespace \addlinespace
-Hub-ensemble-realised-mean & Official Forecast Hub mean ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-mean\_ensemble'.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{ \vphantom{1}} & \cellcolor{gray!6}{}\\
-\addlinespace \addlinespace
-Hub-ensemble & Version of the official Hub median ensemble which excludes all our contributions.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Hub-ensemble-mean} & \cellcolor{gray!6}{Version of the official Hub mean ensemble which excludes all our contributions.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-renewal, 
-    Hub-ensemble-with-renewal-mean & Versions of the official Hub ensembles which of our contributions includes only the Renewal model.\\
-\addlinespace \addlinespace
-Hub-ensemble-with-crowd, 
-\cellcolor{gray!6}{    Hub-ensemble-with-crowd-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which of our contributions includes only the Crowd forecast.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-convolution, 
-    Hub-ensemble-with-convolution-mean & Versions of the official Hub ensembles which of our contributions includes only the Convolution model (which originally was never included in any official Hub ensemble).\\
-\addlinespace \addlinespace
-Hub-ensemble-with-all, 
-\cellcolor{gray!6}{    Hub-ensemble-with-all-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which includes all our contributions.
-For cases, this is identical to the official Hub ensembles, but for deaths the convolution model was added.}\\
-\addlinespace \addlinespace
- & \\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Crowd forecast} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'}\\
-\addlinespace \addlinespace
-Renewal model & Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Convolution model} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\_secondary'}\\*
-\end{longtable}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/number-forecasters} \caption{Number of participants who submitted a forecast over time.}\label{fig:num-forecasters}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/ensemble-members} \caption{Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
-Note that the renewal model was not included in the ensemble on December 28th 2020.}\label{fig:num-ensemble-members}
-\end{figure}
-
-\clearpage
-
-\hypertarget{comparison-of-crowd-forecasts-and-application-baseline}{%
-\subsection{Comparison of crowd forecasts and application
-baseline}\label{comparison-of-crowd-forecasts-and-application-baseline}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} \caption{Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the median, as well as the 50\% and 90\% prediction intervals (in order of decreasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons).}\label{fig:compare-forecasters}
-\end{figure}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{McGowan CJ, Biggerstaff M, Johansson M, Apfeldorf KM,
-Ben-Nun M, Brooks L, et al. Collaborative efforts to forecast seasonal
-influenza in the {United States}, 2015--2016. Scientific Reports.
-2019;9: 683.
-doi:\href{https://doi.org/10.1038/s41598-018-36361-9}{10.1038/s41598-018-36361-9}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Reich NG, Brooks LC, Fox SJ, Kandula S, McGowan CJ,
-Moore E, et al. A collaborative multiyear, multimodel assessment of
-seasonal influenza forecasting in the {United States}. PNAS. 2019;116:
-3146--3154.
-doi:\href{https://doi.org/10.1073/pnas.1812594116}{10.1073/pnas.1812594116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Shaman J, Karspeck A. Forecasting seasonal outbreaks of
-influenza. PNAS. 2012;109: 20425--20430.
-doi:\href{https://doi.org/10.1073/pnas.1208772109}{10.1073/pnas.1208772109}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Biggerstaff M, Alper D, Dredze M, Fox S, Fung IC-H,
-Hickmann KS, et al. Results from the centers for disease control and
-prevention's predict the 2013--2014 {Influenza Season Challenge}. BMC
-Infectious Diseases. 2016;16: 357.
-doi:\href{https://doi.org/10.1186/s12879-016-1669-x}{10.1186/s12879-016-1669-x}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak
-AL, Baugher B, et al. An open challenge to advance probabilistic
-forecasting for dengue epidemics. PNAS. 2019;116: 24268--24274.
-doi:\href{https://doi.org/10.1073/pnas.1909865116}{10.1073/pnas.1909865116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Yamana TK, Kandula S, Shaman J. Superensemble forecasts
-of dengue outbreaks. Journal of The Royal Society Interface. 2016;13:
-20160410.
-doi:\href{https://doi.org/10.1098/rsif.2016.0410}{10.1098/rsif.2016.0410}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Colón-González FJ, Bastos LS, Hofmann B, Hopkin A,
-Harpham Q, Crocker T, et al. Probabilistic seasonal dengue forecasting
-in {Vietnam}: {A} modelling study using superensembles. PLOS Medicine.
-2021;18: e1003542.
-doi:\href{https://doi.org/10.1371/journal.pmed.1003542}{10.1371/journal.pmed.1003542}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Viboud C, Sun K, Gaffey R, Ajelli M, Fumanelli L, Merler
-S, et al. The {RAPIDD} ebola forecasting challenge: {Synthesis} and
-lessons learnt. Epidemics. 2018;22: 13--21.
-doi:\href{https://doi.org/10.1016/j.epidem.2017.08.002}{10.1016/j.epidem.2017.08.002}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Funk S, Camacho A, Kucharski AJ, Lowe R, Eggo RM,
-Edmunds WJ. Assessing the performance of real-time epidemic forecasts:
-{A} case study of {Ebola} in the {Western Area} region of {Sierra
-Leone}, 2014-15. PLOS Computational Biology. 2019;15: e1006785.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1006785}{10.1371/journal.pcbi.1006785}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Del Valle SY, McMahon BH, Asher J, Hatchett R, Lega JC,
-Brown HE, et al. Summary results of the 2014-2015 {DARPA Chikungunya}
-challenge. BMC Infectious Diseases. 2018;18: 245.
-doi:\href{https://doi.org/10.1186/s12879-018-3124-7}{10.1186/s12879-018-3124-7}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Farrow DC, Brooks LC, Hyun S, Tibshirani RJ, Burke DS,
-Rosenfeld R. A human judgment approach to epidemiological forecasting.
-PLOS Computational Biology. 2017;13: e1005248.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1005248}{10.1371/journal.pcbi.1005248}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Funk S, Abbott S, Atkins BD, Baguelin M, Baillie JK,
-Birrell P, et al. Short-term forecasts to inform the response to the
-{Covid-19} epidemic in the {UK}. medRxiv. 2020; 2020.11.11.20220962.
-doi:\href{https://doi.org/10.1101/2020.11.11.20220962}{10.1101/2020.11.11.20220962}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K,
-et al. {COVID-19 Forecast Hub}: 4 {December} 2020 snapshot. {Zenodo};
-2020.
-doi:\href{https://doi.org/10.5281/zenodo.3963371}{10.5281/zenodo.3963371}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A,
-Rivadeneira AJC, et al. Evaluation of individual and ensemble
-probabilistic forecasts of {COVID-19} mortality in the {US}. medRxiv.
-2021; 2021.02.03.21250974.
-doi:\href{https://doi.org/10.1101/2021.02.03.21250974}{10.1101/2021.02.03.21250974}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. Short-term forecasting of {COVID-19} in {Germany}
-and {Poland} during the second wave -- a preregistered study. medRxiv.
-2021; 2020.12.24.20248826.
-doi:\href{https://doi.org/10.1101/2020.12.24.20248826}{10.1101/2020.12.24.20248826}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. National and subnational short-term forecasting of
-{COVID-19} in {Germany} and {Poland}, early 2021. 2021;
-2021.11.05.21265810.
-doi:\href{https://doi.org/10.1101/2021.11.05.21265810}{10.1101/2021.11.05.21265810}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-europeancovid-19forecasthubEuropeanCovid19Forecast2021}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{European Covid-19 Forecast Hub. European {Covid-19
-Forecast Hub}. 2021 {[}cited 30 May 2021{]}. Available:
-\url{https://covid19forecasthub.eu/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichAccuracyRealtimeMultimodel2019}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Reich NG, McGowan CJ, Yamana TK, Tushar A, Ray EL,
-Osthus D, et al. Accuracy of real-time multi-model ensemble forecasts
-for seasonal influenza in the {U}.{S}. PLOS Computational Biology.
-2019;15: e1007486.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1007486}{10.1371/journal.pcbi.1007486}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Tetlock PE, Mellers BA, Rohrbaugh N, Chen E. Forecasting
-{Tournaments}: {Tools} for {Increasing Transparency} and {Improving} the
-{Quality} of {Debate}. Curr Dir Psychol Sci. 2014;23: 290--295.
-doi:\href{https://doi.org/10.1177/0963721414534257}{10.1177/0963721414534257}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Atanasov P, Rescober P, Stone E, Swift SA,
-Servan-Schreiber E, Tetlock P, et al. Distilling the {Wisdom} of
-{Crowds}: {Prediction Markets} vs. {Prediction Polls}. Management
-Science. 2016;63: 691--706.
-doi:\href{https://doi.org/10.1287/mnsc.2015.2374}{10.1287/mnsc.2015.2374}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers E-J. Laypeople
-{Can Predict Which Social-Science Studies Will Be Replicated
-Successfully}. Advances in Methods and Practices in Psychological
-Science. 2020;3: 267--285.
-doi:\href{https://doi.org/10.1177/2515245920919667}{10.1177/2515245920919667}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{ReplicationMarkets. Replication {Markets} -- {Reliable}
-research replicates\ldots you can bet on it. 2020 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.replicationmarkets.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Servan-Schreiber E, Wolfers J, Pennock DM, Galebach B.
-Prediction {Markets}: {Does Money Matter}? Electronic Markets. 2004;14:
-243--251.
-doi:\href{https://doi.org/10.1080/1019678042000245254}{10.1080/1019678042000245254}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{McAndrew TC, Reich NG. An expert judgment model to
-predict early stages of the {COVID-19} outbreak in the {United States}.
-medRxiv. 2020; 2020.09.21.20196725.
-doi:\href{https://doi.org/10.1101/2020.09.21.20196725}{10.1101/2020.09.21.20196725}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Recchia G, Freeman ALJ, Spiegelhalter D. How well did
-experts and laypeople forecast the size of the {COVID-19} pandemic? PLOS
-ONE. 2021;16: e0250935.
-doi:\href{https://doi.org/10.1371/journal.pone.0250935}{10.1371/journal.pone.0250935}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Metaculus. A {Preliminary Look} at {Metaculus} and
-{Expert Forecasts}. 22 Jun 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.metaculus.com/news/2020/06/02/LRT/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Hypermind. Hypermind \textbar{} {Supercollective}
-intelligence for decision makers. {Hypermind}; 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.hypermind.com/en/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{CSET Foretell. {CSET Foretell}. 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.cset-foretell.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{PredictIt. {PredictIt}. 2021 {[}cited 13 Oct 2021{]}.
-Available: \url{https://www.predictit.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Held L, Meyer S, Bracher J. Probabilistic forecasting in
-infectious disease epidemiology: The 13th {Armitage} lecture. Statistics
-in Medicine. 2017;36: 3443--3460.
-doi:\href{https://doi.org/10.1002/sim.7363}{10.1002/sim.7363}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Crowdforecastr: Eliciting crowd forecasts in r shiny. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618519}{10.5281/zenodo.4618519}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Covid.german.forecasts: Forecasting covid-19 related metrics for the
-german/poland forecast hub. 2020. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-ecdcDownloadHistoricalData2020}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{ECDC. Download historical data (to 14 {December} 2020)
-on the daily number of new reported {COVID-19} cases and deaths
-worldwide. {European Centre for Disease Prevention and Control}; 14 Dec
-2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rkiRKICoronavirusSARSCoV22021}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{RKI. {RKI} - {Coronavirus SARS-CoV-2} - {Aktueller
-Lage-}/{Situationsbericht} des {RKI} zu {COVID-19}. 2021 {[}cited 30 May
-2021{]}. Available:
-\url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-forsal.plRozbieznosciStatystykachKoronawirusa2020}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Forsal.pl. Rozbieżności w statystykach koronawirusa. 22
-tys. przypadków będą doliczone do ogólnej liczby wyników. 2020 {[}cited
-30 May 2021{]}. Available:
-\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Ärzteblatt DÄG Redaktion Deutsches.
-SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an. {Deutsches
-Ärzteblatt}; 3 Nov 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Fay C, Guyader V, Rochette S, Girard C. Golem: A
-framework for robust shiny applications. 2021. Available:
-\url{https://github.com/ThinkR-open/golem}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie
-Y, et al. Shiny: Web application framework for r. 2021. Available:
-\url{https://CRAN.R-project.org/package=shiny}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Our World in Data. {COVID-19 Data Explorer}. {Our World
-in Data}; 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://ourworldindata.org/coronavirus-data-explorer}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K,
-Ellis P, et al. EpiNow2: Estimate real-time case counts and time-varying
-epidemiological parameters. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957489}{10.5281/zenodo.3957489}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Fraser C. Estimating {Individual} and {Household
-Reproduction Numbers} in an {Emerging Epidemic}. PLOS ONE. 2007;2: e758.
-doi:\href{https://doi.org/10.1371/journal.pone.0000758}{10.1371/journal.pone.0000758}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation2020}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{epiforecasts.io/covid. Covid-19: {Temporal} variation in
-transmission during the {COVID-19} outbreak. {Covid-19}; 2020 {[}cited
-30 May 2021{]}. Available: \url{https://epiforecasts.io/covid/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Sherratt K, Abbott S, Meakin SR, Hellewell J, Munday JD,
-Bosse N, et al. Exploring surveillance data biases when estimating the
-reproduction number: With insights into subpopulation transmission of
-{Covid-19} in {England}. 2021; 2020.10.18.20214585.
-doi:\href{https://doi.org/10.1101/2020.10.18.20214585}{10.1101/2020.10.18.20214585}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abbottEstimatingTimevaryingReproduction2020a}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs
-HP, Bosse NI, et al. Estimating the time-varying reproduction number of
-{SARS-CoV-2} using national and subnational case counts. 2020 {[}cited
-14 Oct 2021{]}.
-doi:\href{https://doi.org/10.12688/wellcomeopenres.16006.1}{10.12688/wellcomeopenres.16006.1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Xu B, Gutierrez B, Hill S, Scarpino S, Loskill A, Wu J,
-et al. Epidemiological data from the nCoV-2019 outbreak: Early
-descriptions from publicly available data. 2020. Available:
-\url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Stan Development Team. RStan: The r interface to stan.
-2020. Available: \url{http://mc-stan.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG. Evaluating
-epidemic forecasts in an interval format. PLoS Comput Biol. 2021;17:
-e1008618.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1008618}{10.1371/journal.pcbi.1008618}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Gneiting T, Raftery AE. Strictly proper scoring rules,
-prediction, and estimation. Journal of the American Statistical
-Association. 2007;102: 359--378.
-doi:\href{https://doi.org/10.1198/016214506000001437}{10.1198/016214506000001437}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Scoringutils:
-Utilities for scoring and assessing predictions. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618017}{10.5281/zenodo.4618017}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-deutschewelleCoronavirusGermanyImpose2020}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Deutsche Welle. Coronavirus: {Germany} to impose
-one-month partial lockdown \textbar{} {DW} \textbar{} 28.10.2020. 2020
-{[}cited 29 Jun 2021{]}. Available:
-\url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Ganyani T, Kremer C, Chen D, Torneri A, Faes C, Wallinga
-J, et al. Estimating the generation interval for coronavirus disease
-(COVID-19) based on symptom onset data, march 2020. Eurosurveillance.
-2020;25. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith
-HR, et al. The incubation period of coronavirus disease 2019 (COVID-19)
-from publicly reported confirmed cases: Estimation and application.
-Annals of Internal Medicine. 2020;172: 577--582. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J,
-Munday J, et al. Covidregionaldata: Subnational data for the covid-19
-outbreak. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957539}{10.5281/zenodo.3957539}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Evaluating the use of the reproduction number as an
-epidemiological tool, using spatio-temporal trends of the {Covid-19}
-outbreak in {England} \textbar{} {medRxiv}. {[}cited 30 May 2021{]}.
-Available:
-\url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Riutort-Mayol G, Bürkner P-C, Andersen MR, Solin A,
-Vehtari A. Practical hilbert space approximate bayesian gaussian
-processes for probabilistic programming. 2020. Available:
-\url{https://arxiv.org/abs/2004.11408}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Scott JA, Gandy A, Mishra S, Unwin J, Flaxman S, Bhatt
-S. Epidemia: Modeling of epidemics using hierarchical bayesian models.
-2020. Available:
-\url{https://imperialcollegelondon.github.io/epidemia/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bhattSemiMechanisticBayesianModeling}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Bhatt S, Ferguson N, Flaxman S, Gandy A, Mishra S, Scott
-JA. Semi-{Mechanistic Bayesian} modeling of {COVID-19} with {Renewal
-Processes}. : 14. }
-
-\end{CSLReferences}
-
-\nolinenumbers
-
-\end{document}
+```

### 2023-12-11 manuscript/S1-Acknowledgements.tex

--- 2022-08-04 manuscript/final submission/Supplementary/S1-Table.tex
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage[margin=2cm]{geometry}
+\usepackage[margin=1in]{geometry}
 \usepackage{graphicx}
@@
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
 \ifLuaTeX
@@
 
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{9.3cm}}
-\toprule
-Metric & Explanation\\
-\midrule
-\endfirsthead
-\multicolumn{2}{@{}l}{\textit{(continued)}}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endhead
+We would like to thank (in a randomised order) the members of
+Centre for the Mathematical Modelling of Infectious Diseases COVID-19
+Working Group at the the London School of Hygiene \& Tropical Medicine:
 
-\endfoot
-\bottomrule
-\endlastfoot
-WIS (Weighted) interval score & The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
-It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
-The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction.
-For a single interval, the score is computed as
-  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
-  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e.
-the lower and upper bound of a single prediction interval.
-For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
-  $$WIS = \frac{1}{K + 0.5} \cdot \left( w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y) \right), $$
-  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
-
-\cellcolor{gray!6}{Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.}\\
-\addlinespace \addlinespace
-Interval coverage & Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
-Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
-we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.\\
-\addlinespace \addlinespace
-Bias & (Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict. Values are between -1 and 1 and 0 ideally. For continuous forecasts, bias is given as 
-$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
-where $F$ is the CDF of the predictive distribution and $y$ is the observed value.
-
-For quantile forecasts, $F(y)$ is replaced by a quantile rank.
-The appropriate quantile rank is determined by whether the median forecast is below  or above the true value.
-We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.
-
-\cellcolor{gray!6}{In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
-It is therefore a more robust measurement.}\\*
-\end{longtable}
+Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie
+Diamond, Katherine E. Atkins, Rein M G J Houben, Jiayao Lei, Rachel
+Lowe, David Simons, Sophie R Meakin, Nicholas G. Davies, Timothy W
+Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly,
+Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas,
+Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia
+Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson,
+Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang
+Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C
+Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun,
+Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche,
+James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday,
+Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan
+Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R
+Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael
+Pung, Anna M Foss.
 

### 2023-12-11 manuscript/S2 Table.Rmd

--- 2022-08-04 manuscript/S3 Table.Rmd
@@
 ---
+title: ""
 output: 
@@
 caption <- 
-  "Scores for three and four week ahead forecasts (cut to three significant digits and rounded).
+  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
 Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
@@
 ```{r score-table-2}
-table <- readRDS("../analysis/plots/table_scores_4_ahead.rds")
+table <- readRDS("../analysis/plots/table_scores_2_ahead.rds")
+# add_caption(table, caption, label = "tab:score-table-2")
 table
-# add_caption(table, caption, label = "tab:score-table-2")
 ```

### 2023-12-11 manuscript/final submission/Supplementary/S1-Text.tex

--- 2022-06-02 manuscript/manuscript.tex
@@
-% Template for PLoS
-% Version 3.5 March 2018
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
 %
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended
-% to minimize problems and delays during our production
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% Once your paper is accepted for publication,
-% PLEASE REMOVE ALL TRACKED CHANGES in this file
-% and leave only the final text of your manuscript.
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file.
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig" instead of "Figure".
-% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-%
-% Do not include text that is not math in the math environment.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column.
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
-
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\documentclass[
+]{article}
 \usepackage{amsmath,amssymb}
-
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8x]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% cite package, to clean up citations in the main text. Do not remove.
-% \usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% color can be used to apply background shading to table cells only
-\usepackage[table]{xcolor}
-
-% array package and thick rules for tables
-\usepackage{array}
-
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-
-% create \thickcline for thick horizontal lines of variable length
-\newlength\savedwidth
-\newcommand\thickcline[1]{%
-  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-  \cline{#1}%
-  \noalign{\vskip\arrayrulewidth}%
-  \noalign{\global\arrayrulewidth\savedwidth}%
-}
-
-% \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-\hline
-\noalign{\global\arrayrulewidth\savedwidth}}
-
-% Remove comment for double spacing
-%\usepackage{setspace}
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-\renewcommand{\figurename}{Fig}
-
-% Use the PLoS provided BiBTeX style
-% \bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
 \makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
 \makeatother
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr,graphicx}
-\usepackage{epstopdf}
-%\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-%\setlength{\headheight}{27.023pt}
-%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\headrulewidth}{0pt}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\today}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-% tightlist command for lists without linebreak
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Text S1. Further details on the semi-mechanistic forecasting models},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage[margin=1in]{geometry}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% Pandoc citation processing
+\setcounter{secnumdepth}{5}
 \newlength{\cslhangindent}
@@
 \setlength{\cslentryspacingunit}{\parskip}
-% for Pandoc 2.8 to 2.10.1
-\newenvironment{cslreferences}%
-  {}%
-  {\par}
-% For Pandoc 2.11+
 \newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 
-\usepackage{lineno}
-\usepackage[T1]{fontenc}
-\linenumbers
-\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-\usepackage{caption}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
-
-\usepackage{forarray}
-\usepackage{xstring}
-\newcommand{\getIndex}[2]{
-  \ForEach{,}{\IfEq{#1}{\thislevelitem}{\number\thislevelcount\ExitForEach}{}}{#2}
-}
-
-\setcounter{secnumdepth}{0}
-
-\newcommand{\getAff}[1]{
-  \getIndex{#1}{London School of Hygiene \& Tropical Medicine,Karlsruhe
-Institute of Technology Institute of Economic Theory and Statistics,Max
-Planck Institute for Multidisciplinary Sciences,UK Health Security
-Agency,Imperial College London}
-}
+\title{Text S1. Further details on the semi-mechanistic forecasting models}
+\author{}
+\date{\vspace{-2.5em}}
 
 \begin{document}
-\vspace*{0.2in}
+\maketitle
 
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{Comparing human and model-based forecasts of COVID-19 in
-Germany and
-Poland} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+{
+\setcounter{tocdepth}{2}
+\tableofcontents
 }
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Nikos I. Bosse\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\textsuperscript{*},
-Sam Abbott\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Johannes Bracher\textsuperscript{\getAff{Karlsruhe Institute of
-Technology Institute of Economic Theory and Statistics}},
-Habakuk Hain\textsuperscript{\getAff{Max Planck Institute for
-Multidisciplinary Sciences}},
-Billy J. Quilty\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Mark Jit\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Edwin van Leeuwen\textsuperscript{\getAff{UK Health Security
-Agency}, \getAff{London School of Hygiene \& Tropical Medicine}},
-Anne Cori\textsuperscript{\getAff{Imperial College London}},
-Sebastian Funk\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\\
-\bigskip
-\textbf{\getAff{London School of Hygiene \& Tropical Medicine}}London
-School of Hygiene \& Tropical Medicine, Keppel Street, London WC1E7HT,
-United Kingdom\\
-\textbf{\getAff{Karlsruhe Institute of Technology Institute of Economic
-Theory and Statistics}}Karlsruhe Institute of Technology - Institute of
-Economic Theory and Statistics, Post Box 6980, 76049 Karlsruhe,
-Germany\\
-\textbf{\getAff{Max Planck Institute for Multidisciplinary Sciences}}Max
-Planck Institute for Multidisciplinary Sciences, Am Faßberg 11, 37077
-Göttingen, Germany\\
-\textbf{\getAff{UK Health Security Agency}}UK Health Security Agency,
-London NW9 5EQ, United Kingdom\\
-\textbf{\getAff{Imperial College London}}Imperial College London,
-Norfolk Place, London W2 1PG, United Kingdom\\
-\bigskip
-* Corresponding author: nikos.bosse@lshtm.ac.uk\\
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-Forecasts based on epidemiological modelling have played an important
-role in shaping public policy throughout the COVID-19 pandemic. This
-modelling combines knowledge about infectious disease dynamics with the
-subjective opinion of the researcher who develops and refines the model
-and often also adjusts model outputs. Developing a forecast model is
-difficult, resource- and time-consuming. It is therefore worth asking
-what modelling is able to add beyond the subjective opinion of the
-researcher alone. To investigate this, we analysed different real-time
-forecasts of cases of and deaths from COVID-19 in Germany and Poland
-over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
-We compared crowd forecasts elicited from researchers and volunteers,
-against a) forecasts from two semi-mechanistic models based on common
-epidemiological assumptions and b) the ensemble of all other models
-submitted to the Forecast Hub. We found crowd forecasts, despite being
-overconfident, to outperform all other methods across all forecast
-horizons when forecasting cases (weighted interval score relative to the
-Hub ensemble 2 weeks ahead: 0.89). Forecasts based on computational
-models performed comparably better when predicting deaths (rel. WIS
-1.26), suggesting that epidemiological modelling and human judgement can
-complement each other in important ways.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step.
-% Author Summary not valid for PLOS ONE submissions.
-\section*{Author summary}
-Mathematical models of COVID-19 have played a key role in informing
-governments across the world. While mathematical models are informed by
-our knowledge of infectious disease dynamics, they are ultimately
-developed and iteratively adjusted by the researchers and shaped by
-their subjective opinions. To investigate what modelling is able to add
-beyond the subjective opinion of the researcher alone, we compared human
-forecasts with model-based predictions of COVID-19 cases and deaths
-submitted to the so-called German/Polish Forecast Hub (which collates a
-variety of models from a range of teams). \textbar{} We found that our
-human forecasts consistently outperformed an aggregate of all available
-model-based forecasts when predicting cases, but not when predicting
-deaths. Our findings suggest that human insight may be most valuable
-when forecasting highly uncertain quantities, which depend on many
-factors that are hard to model using equations, while mathematical
-models may be most useful in settings like predicting deaths, where
-leading indicators with a clear connection to the target variable are
-available. This potentially has very relevant policy implications, as
-agencies informing policy-makers could benefit from routinely eliciting
-human forecasts in addition to model-based predictions to inform
-policies.
-
-\linenumbers
-
-% Use "Eq" instead of "Equation" for equation citations.
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Infectious disease modelling has a long tradition and has helped inform
-public health decisions both through scenario modelling, as well as
-actual forecasts of (among others) influenza {[}e.g. 1,2--4{]}, dengue
-fever {[}e.g. 5,6,7{]}, ebola {[}e.g. 8,9{]}, chikungunya {[}e.g.
-10,11{]} and now COVID-19 {[}e.g. 12,13--17{]}. Applications of
-epidemiological models differ in the way they make statements about the
-future. Forecasts aim to predict the future as it will occur, while
-scenario modelling and projections aim to represent what the future
-could look like under certain scenario assumptions or if conditions
-stayed the same as they were in the past. Forecasts can be judged by
-comparing them against observed data. Since it is much harder to fairly
-assess the accuracy and usefulness of projections and scenario modelling
-in the same way, this work focuses on forecasts, which represent only a
-subset of all epidemiological modelling.
-
-Since March 2020, forecasts of COVID-19 from multiple teams have been
-collected, aggregated and compared by Forecast Hubs such as the US
-Forecast Hub {[}13,14{]}, the German and Polish Forecast Hub {[}15,16{]}
-and the European Forecast Hub {[}17{]}. Often, different individual
-forecasts are combined into a single forecast, e.g.~by taking the mean
-or median of all forecasts. These ensemble forecasts usually tend to
-perform better and more consistently than individual forecasts (see e.g.
-{[}6{]}; {[}18{]}).
-
-Individual computational models usually rely to varying degrees on
-mechanistic assumptions about infectious disease dynamics (such as
-SIR-type compartmental models that aim to represent how individuals move
-from being susceptible to infected and then recovered or dead). Some are
-more statistical in nature (such as time series models that detect
-statistical patterns without explicitly modelling disease dynamics). How
-exactly such a mathematical or computational model is constructed and
-which assumptions are made depends on subjective opinion and judgement
-of the researcher who develops and refines the model. Models are
-commonly adjusted and improved based on whether the model output looks
-plausible to the researchers involved.
-
-The process of model construction and refinement is laborious and
-time-consuming, and it is therefore worth asking what modelling can add
-beyond the subjective judgment of the researcher alone. In this work, we
-ask this question specifically in the context of predictive performance,
-and set aside other advantages of epidemiological modelling (such as
-reproducibility or the ability to obtain a deeper fundamental
-understanding of how diseases spread). One natural way to do this is to
-compare the predictive performance of forecasts based on computational
-models (``model-based forecasts'') against forecasts made by individual
-humans without explicit use of a computer model (``direct human
-forecasts'') or a combination of multiple such forecasts (``crowd
-forecasts'').
-
-Previous work has examined such direct human forecasts in various
-contexts, such as geopolitics {[}19,20{]}, meta-science {[}21,22{]},
-sports {[}23{]} and epidemiology {[}11,24,25{]}. Several prediction
-platforms {[}26--28{]} and prediction markets {[}29{]} have been created
-to collate expert and non-expert predictions. However, with the notable
-exception of {[}11{]}, these forecasts were not designed to be evaluated
-alongside model-based forecasts and usually follow their own (often
-binary) prediction formats. Direct human forecasts may be able to take
-into account insights and relationships between variables which are hard
-to specify using epidemiological models. However, it is not entirely
-clear in which situations human forecasts perform well or badly. For
-example, {[}11{]} found that humans could outperform computer models at
-predicting the 2014/15 and 2015/16 flu season in the US, a setting where
-the disease was well known and information about previous seasons was
-available. However, humans tended to do slightly worse at predicting the
-2014/15 outbreak of chikungunya in the Americas, a disease previously
-largely unobserved and unknown in these regions at the time.
-
-In this study, we analyse the performance of direct human forecasts
-relative to model-based forecasts and discuss the added benefit of
-epidemiological modelling over human judgement alone. As a case study,
-we use different forecasts, involving varying degrees of human
-intervention, which we submitted in real time to the German and Polish
-Forecast Hub. In contrast to {[}11{]} we elicited not only point
-predictions, but full predictive distributions (``probabilistic
-forecasts'', see e.g. {[}30{]}) from participants. This allows us to
-compare not only predictive accuracy, but also how well human
-forecasters and model-based forecasts were able to quantify forecast
-uncertainty.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-We created and submitted the following forecasts to the German and
-Polish Forecast Hub: 1) a direct human forecast (henceforth called
-``crowd forecast''), elicited from participants through a web
-application {[}31{]} and 2) two semi-mechanistic model-based forecasts
-(``renewal model'' and ``convolution model'') informed by basic
-assumptions about COVID-19 epidemiology. While the two semi-mechanistic
-forecasts were necessarily shaped by our implicit assumptions and
-decisions, they were designed such as to minimise the amount of human
-intervention involved. For example, we refrained from adjusting model
-outputs or refining the models based on past performance. Forecasts were
-created in real time over a period of 21 weeks from October 12th 2020
-until March 1st 2021 and submitted to the German and Polish Forecast hub
-{[}15,16{]}. All code and tools necessary to generate the forecasts and
-make a forecast submission are available in the
-\texttt{covid.german.forecasts} R package {[}32{]}. This repository also
-contains a record of all forecasts submitted to the German and Polish
-Forecast Hub. Forecasts were evaluated using a variety of scoring
-metrics and compared among each other and against an ensemble of all
-other models submitted to the German and Polish Forecast Hub.
-
-\hypertarget{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}{%
-\subsection{Forecast targets and interaction with the German and Polish
-Forecast
-Hub}\label{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}}
-
-The German and Polish Forecast Hub (now mostly merged into the {[}17{]})
-elicits predictions for various COVID-19 related forecast targets from
-different research groups every week. Forecasts had to be made every
-Monday (with submissions allowed until Tuesday 3pm) and were permitted
-to use any data that was available by Monday 11.59pm. We submitted
-forecasts for incident and cumulative weekly reported numbers of cases
-of and deaths from COVID-19 on a national level in Germany and Poland
-over a one to four week forecast horizon. Forecasts were submitted on
-Mondays, but weeks were defined as ending on a Saturday (and starting on
-Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26
-days. Submissions were required in a quantile-based format with 23
-quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10,
-0.15, \ldots, 0.95, 0.975, 0.99. Forecasts submitted to the Forecast Hub
-were combined into different ensembles every week, with the median
-ensemble (i.e., the \(\alpha\)-quantile of the ensemble is given by the
-median of all submitted \(\alpha\)-quantiles) being the default ensemble
-shown on all official Forecast hub visualisations
-(https://kitmetricslab.github.io/forecasthub/forecast).
-
-Data on daily reported test positive cases and deaths linked to COVID-19
-were provided by the organisers of the German and Polish Forecast hub.
-Until December 14th, 2020, these data were sourced from the European
-Centre for Disease Control {[}33{]}. After ECDC stopped publishing daily
-data, observations were sourced from the Robert Koch Institute (RKI) and
-the Polish Ministry of Health for the remainder of the submission period
-{[}34{]}. These data are subject to reporting artefacts, (such as for
-example delayed case reporting in Poland on the 24th November,
-{[}35{]}), changes in reporting over time, and variation in testing
-regimes (for example in Germany from the 11th of November on, {[}36{]}).
-The ECDC data as well as the data published by the Polish Ministry of
-Health were also subject to data revisions, although most of them (with
-a notable exception of a data update for October 12 2020 in Germany)
-only affected daily, not weekly data (see Figures
-\ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).
-
-\hypertarget{crowd-forecasts}{%
-\subsection{Crowd forecasts}\label{crowd-forecasts}}
-
-Our crowd forecasts were created as an ensemble of forecasts made by
-individual participants every week through a web application
-(https://cmmid-lshtm.shinyapps.io/crowd-forecast/). Weekly forecasts had
-to be submitted before Tuesday 12pm every week, but participants were
-asked to only use any information or data that was already available by
-Monday night. The application was built using the \texttt{shiny} and
-\texttt{golem} R packages {[}37,38{]} and is available in the
-\texttt{crowdforecastr} R package {[}31{]}. To make a forecast in the
-application participants could select a predictive distribution (with
-the default being log-normal) to represent the probability that the
-forecasted quantity took certain values. Median and width of the
-uncertainty could be adjusted by either interacting with a figure
-showing their forecast or providing numerical values (see screenshot in
-Figure \ref{fig:screenshot} in the SI). The default shown was a
-repetition of the last known observation with constant uncertainty
-around it computed as the standard deviation of the last four changes in
-weekly log observed forecasts (i.e.~as
-\(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
-A comparison of the crowd forecasts against the default baseline shown
-in the application is displayed in Figure \ref{fig:compare-forecasters}
-in the Appendix. Our interface also allowed participants to view past
-observations based on the hub data, as well as their forecasts, on a
-logarithmic scale and presented additional contextual COVID-19 data
-sourced from {[}39{]}. These data included, for example, notifications
-of both test positive COVID-19 cases and COVID-19 linked deaths and the
-number of COVID-19 tests conducted over time. From November 26 2020 on
-we displayed weekly small reports with a visualisation of past forecasts
-and scores on our website, epiforecasts.io.
-
-Forecasts were stored in a Google Sheet and downloaded, cleaned and
-processed every week for submission to the Forecast Hub. If a forecaster
-had submitted multiple predictions for a single target, only the latest
-submission was kept. Information on the chosen distribution as well as
-the parameters for median and width were used to obtain the required set
-of 23 quantiles from that distribution. Forecasts from all forecasters
-were then aggregated using an unweighted quantile-wise mean (i.e., the
-\(\alpha\)-quantile of the ensemble is given by the mean of all
-submitted \(\alpha\)-quantiles). To avoid issues with users trying out
-the app and submitting a random forecast, we required that a forecaster
-needed to make a forecast for at least two targets for a given forecast
-in order to be included in the crowd forecast ensemble. On a few
-occasions we deleted forecasts that were clearly the result of a user or
-software error (such as for example forecasts that were zero
-everywhere).
-
-individual forecasts were assessed as clearly erroneous by visual
-inspection and subsequently removed before aggregation and were excluded
-from the submission as well as the analysis.
-
-Participants were recruited mostly within the Centre of Mathematical
-Modeling of Infectious Diseases at the London School of Hygiene \&
-Tropical Medicine, but participants were also invited personally or via
-social media to submit predictions. Depending on whether they had a
-background in either statistics, forecasting or epidemiology,
-participants were asked to self-identify as `experts' or `non-experts'.
-
-The study was approved by the Observational / Interventions Research
-Ethics Committee at the London School of Hygiene \& Tropical Medicine,
-LSHTM Ethics Reference: 22290. Formal consent from participants was
-taken in written form through the web application.
-
-\hypertarget{model-based-forecasts}{%
-\subsection{Model-based forecasts}\label{model-based-forecasts}}
-
-We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R
-package (version 1.3.3) as our model-based forecasts {[}40{]}. The first
-of these models, here called ``renewal model'', used the renewal
-equation {[}41{]} to predict reported cases and deaths (see details in
-the SI). It estimated the effective reproduction number \(R_t\) (the
-average number of people each person infected at time t is expected to
-infect in turn) and modelled future infections as a weighted sum of past
-infection multiplied by \(R_t\). \(R_t\) was assumed to stay constant
-beyond the forecast date, roughly corresponding to continuing the latest
-exponential trend in infections. On the 9th of November we altered the
-date when \(R_t\) was assumed to be constant from two weeks prior to the
-date of the forecast to the forecast date, which we found to yield a
-more stable \(R_t\) estimate. Reported case and death notifications were
-obtained by convolving predicted infections over data-based delay
-distributions {[}40,42--44{]} to model the time between infection and
-report date. The renewal model was used to predict cases as well as
-deaths with forecasts being generated for each target separately. Death
-forecasts from the renewal model were therefore not informed by past
-cases. One submission of the renewal model on December 28th 2020 was
-delayed and therefore not included in the official Forecast hub
-ensemble.
-
-The second model (``convolution model'', see details in SI) was only
-used to forecast deaths and was added later, starting December 7th 2020
-(with the first forecast from December 7th suffering from a software bug
-and therefore disregarded in all further analyses). The convolution
-model was submitted, but never included in the official Forecast hub
-ensemble due to concerns that it could be too similar to the renewal
-model. The convolution model predicted deaths as a fraction of infected
-people who would die with some delay, by using a convolution of reported
-cases with a distribution that described the delay from case report to
-death and a scaling factor (the case-fatality ratio). Both the renewal
-and the convolution model used daily observations and assumed a negative
-binomial observation model with a multiplicative day-of-the-week effect
-{[}40{]}.
-
-Line list data used to inform the prior for the delay from symptom onset
-to test positive case report or death in the model-based forecasts was
-sourced from {[}45{]} with data available up to the 1st of August. All
-model fitting was done using Markov-chain Monte Carlo (MCMC) in stan
-{[}46{]} with each location and forecast target being fitted separately.
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-For the main analysis we focused mostly on two week ahead forecasts, as
-COVID-19 forecasts, especially for cases, were in the past found to have
-poor predictive performance beyond this horizon {[}15{]}. Forecasts for
-cases were scored using the full period from October 2020 until March
-2021. To ensure comparability between models, all death forecasts were
-scored using only the period from December 14th on, where all models
-including the convolution model were available. To ensure robustness of
-our results we conducted a sensitivity analysis where all forecasts
-(including cases) were scored only over the later period for which all
-forecasts were available (see Section \ref{sensitivity-analysis} in the
-SI). Results remained broadly unchanged.
-
-Forecasts were analysed using the following scoring metrics: The
-weighted interval score (WIS) {[}47{]}, the absolute error, relative
-bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule {[}48{]}, meaning that in expectation
-the score is optimised by reporting a predictive distribution that is
-identical to the true data-generating distribution. Forecasters are
-therefore incentivised to report their true belief about the future. The
-WIS can be understood as a generalisation of the absolute error to
-quantile-based forecasts (also meaning that smaller values are better)
-and can be decomposed into three separate penalties: forecast spread
-(i.e.~uncertainty of forecasts), over-prediction and under-prediction.
-While the over- and under-prediction components of the WIS capture the
-amount of over-prediction and under-prediction in absolute terms, we
-also look at a relative tendency to make biased forecasts. The bias
-metric {[}9{]} we use captures how much probability mass of the forecast
-was above or below the true value (mapped to values between -1 and 1)
-and therefore represents a general tendency to over- or under-predict in
-relative terms. A value of -1 implies that all quantiles of the
-predictive distribution are below the observed value and a value of 1
-that all quantiles are above the observed value. Empirical coverage is
-the percentage of observed values that fall inside a given prediction
-interval (e.g.~how many observed values fall inside all 50\% prediction
-intervals). Scoring metrics are explained in more detail in Table
-\ref{tab:scoring-metrics} in the SI. All scores were calculated using
-the \texttt{scoringutils} R package {[}49{]}.
-
-At all stages of the evaluation our forecasts were compared to the
-median ensemble of all \emph{other} models submitted to the German and
-Polish Forecast Hub (``Hub ensemble''). This ``Hub ensemble'' was
-retrospectively computed and excludes all our models, leaving on average
-five ensemble member models (see details in Section
-\ref{contributions-hub}, as well as in Table
-\ref{tab:table-ensemble-versions} and Figure
-\ref{fig:num-ensemble-members} in the SI). What we call ``Hub ensemble''
-in this article therefore differs from the ``official Hub ensemble''
-(here called ``hub-ensemble-realised'') which included crowd forecasts
-as well as renewal model forecasts. To enhance interpretability of
-scores we mainly report WIS relative to the Hub ensemble in the main
-text, i.e.~we divided the average scores for a given model by the
-average score achieved by the Hub ensemble on the same set of forecasts
-(with values \textgreater1 implying worse and values \textless1 implying
-better performance than the Hub ensemble). In addition to comparing our
-forecasts against the hub ensemble excluding our models, we also
-assessed the impact of our forecasts on the performance of the
-forecasting hub by recalculating separate versions of the Hub ensemble
-with only some (or all) of our forecasts included. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{crowd-forecast-participation}{%
-\subsection{Crowd forecast
-participation}\label{crowd-forecast-participation}}
-
-A total number of 32 participants submitted forecasts, 17 of those
-self-identified as `expert' in either forecasting or epidemiology. The
-median number of forecasters for any given forecast target was 6, the
-minimum 2 and the maximum 10. The mean number of submissions from an
-individual forecaster was 4.7 but the median number was only one - most
-participants dropped out after their first submission. Only two
-participants submitted a forecast every single week, both of whom are
-authors on this study.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} \caption{Two week ahead forecasts and corresponding scores.
-A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth}
-\end{figure}
-
-\hypertarget{case-forecasts}{%
-\subsection{Case Forecasts}\label{case-forecasts}}
-
-For cases, crowd forecasts had a lower mean weighted interval score
-(WIS, lower values indicate better performance) than both the renewal
-model and the Hub ensemble across all forecast horizons (Figure
-\ref{fig:agg-performance-all}A) and locations (Figure
-\ref{fig:performance-locations-rel}A). For two week ahead forecasts,
-mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts
-and 1.40 for the renewal model (Table \ref{tab:score-table-2}). Across
-all forecasting approaches, locations and forecast horizons, the
-distribution of WIS values was very right-skewed, and average
-performance was heavily influenced by outliers (Figure
-\ref{fig:distribution-scores}). Overall, low variance in forecast
-performance was closely linked with good mean performance (Figures
-\ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A),
-suggesting that the ability to avoid large errors was an important
-factor in determining overall performance. The impact of outlier values
-was especially pronounced for the renewal model, which had more outliers
-(Figure \ref{fig:distribution-scores}), as well as the highest standard
-deviation of WIS values (standard deviation of the WIS relative to the
-WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon),
-while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub
-ensemble (= 1) showed more stable performance.
-
-To varying degrees, all forecasts exhibited trend-following behaviour
-and were rarely able to predict a change in trend before it had
-happened. For example, all forecasts failed to predict the change in
-trend from increase to decrease that happened in November in Germany and
-severely overshot reported cases (Figure
-\ref{fig:forecasts-and-truth}A). This was most striking for the renewal
-model, which extrapolated unconstrained exponential growth based on the
-recent past of observations. The Hub ensemble and the crowd forecast,
-which had both been under-predicting throughout October, also failed to
-predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on
-November 2nd 2020 {[}50{]} and the change in the testing regime (with
-stricter test criteria) on November 11th 2020 {[}36{]}, were fastest to
-adapt to the new trend, and the Hub ensemble slowest. In December, cases
-rose again in Germany, with all models under-predicting this growth to
-varying extents. As in October, the renewal model captured the phase of
-exponential growth in cases slightly better than other approaches, but
-again overshot when reported case numbers fell over Christmas. The large
-variance in predictions in January in Germany (severe under-prediction
-followed by severe over-prediction) may in part be caused by the fact
-that the renewal model operated on daily data and therefore was
-susceptible to fluctuations in daily reporting around Christmas that
-would not have influenced on weekly reporting. Similar trends in
-performance were evident in Poland, with the crowd forecast quickest at
-adapting to the change in trend in November. In general, there were
-fewer large outlier forecasts in Poland and in particular the renewal
-model performed more in line with other forecasts there.
-
-All forecasting approaches, including the Hub ensemble, were
-overconfident, i.e.~they showed lower than nominal coverage (meaning
-that 50\% (90\%) prediction intervals generally covered less than 50\%
-(90\%) of the actually observed values) (Figure
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
-Coverage for all forecasts deteriorated with increasing forecast
-horizon, indicating that all forecasting approaches struggled to
-quantify uncertainty appropriately for case forecasts. This was
-especially an issue for crowd forecasts, which had markedly shorter
-prediction intervals (i.e., narrower and more confident predictive
-distributions) than other approaches (Figure
-\ref{fig:agg-performance-all}E) and only showed a small increase in
-uncertainty across forecast horizons. The crowd forecasts prediction
-intervals were also noticeably narrower than the default baseline shown
-to forecasters in the application (see Figure
-\ref{fig:compare-forecasters}).
-
-In spite of good performance in terms of the absolute error (Figure
-\ref{fig:agg-performance-all}G), the narrow forecast intervals led to
-forecasts which were severely overconfident (covering only 36\% and 55\%
-of all observations with the 50\% and 90\% prediction intervals of all
-forecasts made at a two week forecast horizon, and only 5\% and 38\%
-four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables
-\ref{tab:score-table-2} and \ref{tab:score-table-4}). Despite worse
-performance in terms of absolute error (Figure
-\ref{fig:agg-performance-all}G), the renewal model achieved better
-calibration (comparable to the Hub ensemble), as uncertainty increased
-rapidly across forecast horizons. The crowd forecasts, on the other
-hand, showed a smaller bias than the renewal model, but were
-overconfident.
-
-The renewal model exhibited a noticeable tendency towards
-over-predicting reported cases across all horizons. The crowd forecast
-tended to over-predict at longer forecast horizons, whereas the Hub
-ensemble showed no systematic bias (Figure
-\ref{fig:agg-performance-all}F). Regardless of a general relative
-tendency to over-predict, all forecasting approaches incurred larger
-absolute penalties from over- than from under-prediction (see
-decomposition of the WIS into absolute penalties for over-prediction,
-under-prediction and dispersion in Figures
-\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
-
-Generally, trends in overall performance were broadly similar across
-locations (Figures \ref{fig:performance-locations} and
-\ref{fig:performance-locations-rel}). Due to the differing population
-sizes and numbers of notifications in Germany and Poland absolute scores
-were difficult to compare directly. However, relative to the Hub
-ensemble, the crowd forecasts performed noticeably better in Germany
-than in Poland and the renewal model better in Poland than in Germany
-(Figures \ref{fig:performance-locations-rel}A,
-\ref{fig:performance-locations-rel}G,
-\ref{fig:agg-performance-all-Germany},
-\ref{fig:agg-performance-all-Poland}).
-
-\hypertarget{death-forecasts}{%
-\subsection{Death Forecasts}\label{death-forecasts}}
-
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as
-our model-based approaches across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B). Relative WIS values for the models
-two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1
-(Hub ensemble) and 1.79 (renewal model). The crowd forecasts performed
-better than the renewal model across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B), and also better than the convolution
-model three and four weeks ahead. Poor performance of the renewal model,
-especially at longer horizons, indicates that an approach that does not
-know about past cases, but instead estimates and projects a separate
-\(R_t\) trace from deaths, does not use the available information
-efficiently. The convolution model was able to outperform both the
-renewal model and the crowd forecasts at shorter forecast horizons
-(where the delay between cases and deaths means that future deaths are
-largely informed by present cases), but saw performance deteriorate at
-three and four weeks ahead (where case predictions from the renewal
-model were increasingly used to inform death predictions) (Figure
-\ref{fig:agg-performance-all}B, Table \ref{tab:score-table-4}).
-
-As past cases and hospitalisations can be used as predictors, predicting
-a change in trend may be easier for deaths than for cases. Even though
-all forecasts generally struggled with this, there were some instances
-where changing trends were well captured or even anticipated. In Poland,
-for example, the Hub ensemble was able to capture or even anticipate the
-peak in deaths in December quite well (whereas the renewal model and
-crowd forecast did not). The renewal model, which mostly exhibited
-trend-following behaviour, correctly predicted another increase in
-weekly deaths in mid-January (potentially based on changes in daily
-deaths, as the renewal model did not know about past cases). In Germany
-in early January, all models predicted a decrease in deaths two to three
-weeks before it actually happened. Predictions from the renewal model at
-that time were likely strongly influenced by an unexpected drop in
-reported deaths in December. The other forecasting approaches and in
-particular, the convolution model may have been affected by potentially
-under-reported case numbers around Christmas. When the decrease that all
-models had predicted to happen in early January failed to materialise,
-the renewal model and the crowd forecast noticeably over-corrected and
-over-predicted deaths in the following weeks, while the Hub ensemble,
-and to a slightly lesser degree, the convolution model were able to
-capture the downturn well when it finally happened at the end of
-January.
-
-Death forecasts, generally, showed greater coverage of the 50\% and 90\%
-prediction intervals than case forecasts and no decrease in coverage
-across forecast horizons, indicating that it might be easier to
-appropriately quantify uncertainty for death forecasts. The Hub ensemble
-had the greatest coverage, with empirical coverage of the 50\% and 90\%
-prediction intervals exceeding 50\%, and 90\%, respectively, across all
-forecast horizons. Coverage for the crowd forecasts and our model-based
-approaches was generally lower than that of the Hub ensemble and mostly
-slightly lower than nominal coverage (Figure
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D). As
-for cases, the crowd forecast tended to have the narrowest prediction
-intervals and uncertainty increased most slowly across forecast
-horizons, and the renewal model forecasts generally were widest. The
-convolution model had relatively narrow prediction intervals for short
-forecast horizons, but had rapidly (and non-linearly) increasing
-uncertainty for longer forecast horizons, driven by increasing
-uncertainty in the underlying case forecasts.
-
-For deaths, the ensemble of crowd forecasts had a consistent tendency to
-over-predict \ref{fig:agg-performance-all}F. The convolution model had a
-strong tendency to under-predict, with the magnitude of under-prediction
-steadily decreasing for longer forecast horizons. The renewal model
-(which over-predicted for cases) and the Hub ensemble slightly tended
-towards under-prediction. For deaths, absolute over- and
-under-prediction penalties were more in line with a general relative
-tendency to over- or under-predict than for cases (Figure
-\ref{fig:agg-performance-all}A, \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2}, \ref{tab:score-table-4}).
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} \caption{Distribution of scores.
-A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
-Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores.}\label{fig:distribution-scores}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.
-“Hub-ensemble”    extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-rel}
-\end{figure}
-
-\hypertarget{contributions-hub}{%
-\subsection{Contribution to the Forecast Hub}\label{contributions-hub}}
-
-Of our three models, only the renewal model and the crowd forecast were
-included in the official Forecast Hub median ensemble
-(``hub-ensemble-realised''), while the convolution model was never
-included as it was deemed too similar to the existing renewal model. In
-the official Hub ensemble, there were on average 7.1 models included
-(including our own), with a median of 7, a minimum of 4 (on 28 December
-2020 over the Christmas period) and a maximum of 10. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively. An
-overview of all models and ensemble versions is shown in Table
-\ref{tab:table-ensemble-versions} in the SI.
-
-For cases, our contributions (compared to the Hub ensemble without our
-contributions) consistently improved performance across all forecasting
-horizons (rel. WIS 0.9 two weeks ahead, Table
-\ref{tab:score-table-ensemble-2}). Contributions from the crowd
-forecasts alone also improved performance of the Hub ensemble across all
-forecast horizons, while contributions from the renewal model had a
-negative effect for longer horizons (rel. WIS 1.02 three weeks ahead,
-1.06 four weeks ahead). The realised ensemble including both models
-performed better or equal compared to all versions with only one model
-included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model
-have improved performance (Table \ref{tab:score-table-ensemble-4}). The
-realised ensemble performed comparably to the crowd forecasts for
-predictions one to two weeks ahead, and worse for greater forecast
-horizons.
-
-For deaths, contributions from the renewal model and crowd forecast
-together improved performance only for one week ahead predictions and
-showed an increasingly negative impact on performance for longer
-horizons (rel. WIS of the Hub-ensemble-realised 1.01 two weeks ahead,
-1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and
-\ref{tab:score-table-ensemble-4}). Individual contributions from both
-the renewal model and the crowd forecast were largely negative, while a
-version of the Hub ensemble with only the convolution model included
-would have performed consistently better across all forecast horizons
-(with the positive impact increasing for longer horizons). This is
-especially interesting as the convolution model performed consistently
-worse than the pre-existing Hub ensemble (Figure
-\ref{fig:agg-performance-all}) and especially worse for longer horizons.
-
-We also considered the impact of our contributions on a version of the
-Hub ensemble constructed by taking the quantile-wise mean, rather than
-the median. General trends were similar, with the notable exception of
-the convolution model, which had a consistently positive impact on the
-median ensemble, but a mixed and mostly slightly negative impact on the
-mean ensemble (Figures \ref{fig:agg-performance-ensemble-rel}B and
-\ref{fig:agg-performance-ensemble-mean}B). This may happen if a model is
-more correct directionally relative to the pre-existing ensemble, but
-overshoots in absolute terms, thereby moving the ensemble too far. For
-both the mean and the median ensemble, changes in performance from
-adding or removing models were of a similar order of magnitude,
-suggesting that at least in this instance, with a relatively small
-ensemble size, the median ensemble was not necessarily more `robust' to
-changes than the mean ensemble. However, the ensemble version with all
-our forecasts included (``hub-ensemble-with-all'') tended to perform
-relatively better for the median ensemble than the mean ensemble,
-suggesting that adding more models may be more beneficial or `safer' for
-the median than for the mean ensemble as directional errors can more
-easily cancel out than errors in absolute terms.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Epidemiological forecasting modelling combines knowledge about
-infectious disease dynamics with the subjective opinion of the
-researcher who develops and refines the model. In this study, we
-compared forecasts of cases of and deaths from COVID-19 in Germany and
-Poland based purely on human judgement and elicited from a crowd of
-researchers and volunteers against forecasts from two semi-mechanistic
-epidemiological models. In spite of the small number of participants and
-a general tendency to be overconfident, crowd forecasts consistently
-outperformed our epidemiological models as well as the Hub ensemble when
-forecasting cases but not when forecasting deaths. This suggests that
-humans might be relatively good at foreseeing trends that are hard to
-model but may struggle to form an intuition for the exact relationship
-between cases and deaths.
-
-Past studies have evaluated the performance of model-based forecasting
-approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of
-(expert-tuned) model-based approaches {[}e.g. 12,13,14{]}, or
-exclusively on human forecasts {[}19,20,24,25{]}. In contrast, we
-directly compared human and model-based forecasts. This is similar to
-the approach taken by {[}11{]}, but extends it in several ways. While
-Farrow et al.~only asked for point predictions and constructed a
-predictive distribution from these, we asked participants to provide a
-full predictive distribution, allowing us to compare human forecasts and
-models without any further assumptions, as well as to analyse how humans
-quantified their uncertainty. In addition, we compared crowd forecasts
-to two semi-mechanistic models informed by basic epidemiological
-knowledge of COVID-19, allowing us to assess not only relative
-performance but also to analyse qualitative differences between human
-judgement and model-based insight. In terms of interpretability of the
-results, exact knowledge of our two models, as well as focus on a
-limited set of targets and locations was a major advantage of our study
-compared to larger studies conducted by the Forecast Hubs
-{[}12--15,17{]}.
-
-The strong performance of crowd forecasts in our study is in line with
-results from Farrow et al.~who also report strong performance of human
-predictions in past Flu challenges despite difficulties to recruit a
-large number of participants. The advantage of crowd forecasts we
-observed over our semi-mechanistic models is likely in part explained by
-the fact that we compared an ensemble of crowd forecasts with single
-models. However, this probably explains only part of the difference, and
-performance relative to the Hub ensemble strongly suggests that human
-insight is valuable when forecasting highly volatile and potentially
-hard-to-predict quantities such as case numbers. One potential
-explanation is that humans can have access to data that is not available
-to or hard to integrate into model-based forecasts. Relatively good
-performance of our semi-mechanistic models short-term, but not
-longer-term, suggests that model-based forecasts are helpful to
-extrapolate from current conditions, but require some form of human
-intervention or additional assumptions to inform forecasts when
-conditions change over time. This human intervention may be particularly
-important when dealing with artefacts in reporting and data anomalies
-(and especially when using daily, rather than weekly data). The large
-variance in predictions in January in Germany for example (severe
-under-prediction followed by severe over-prediction, see Figure
-\ref{fig:forecasts-and-truth}A), may in part be caused by the fact that
-the renewal model operated on daily data and therefore was susceptible
-to fluctuations in daily reporting which have less of an influence on
-weekly reporting.
-
-Our results suggest that human intervention may be less beneficial when
-forecasting deaths (especially at shorter horizons, when deaths are
-largely dependent on already observed cases), which benefits from the
-ability to model the delays and exact epidemiological relationships
-between different leading and lagged indicators. Relatively good
-performance of the convolution model, especially compared to the poor
-performance of the renewal model on deaths (which used only deaths to
-estimate and predict the effective reproduction number) underlines the
-importance of including leading indicators such as cases as a predictor
-for deaths.
-
-Given the low number of participants in our study, it is difficult to
-generalise conclusions about crowd predictions to other settings. Using
-R shiny as a platform for the web application arguably created some
-limits to user experience and performance, influencing the number of
-participants and potentially creating a self-selection effect.
-Motivating forecasters to contribute regularly proved challenging,
-especially given that the majority of our participants were from the UK
-and may not have been familiar with all relevant details of the
-situation in Germany and Poland. On the other hand, R shiny facilitated
-quick development and allowed us to provide our crowd forecasting
-tooling as an open source R package, meaning that it is available for
-others to use, for example in settings like early-stage outbreaks where
-model-based forecasts are not available. In light of the relatively
-small number of Hub ensemble models, performance of the Hub ensemble is
-also difficult to generalise. More research is needed to replicate these
-findings and investigate how crowd forecasts compare against the types
-of models and model ensembles policy makers use to inform their
-decisions.
-
-Our work suggests that crowd forecasts and model-based forecasts could
-have different strengths and may be able to complement each other. When
-choosing a suitable approach for a given task it is important to take
-into account how the output will be used. In this work we focused on
-forecasts (which aim to predict future data points whilst accounting for
-all factors that might influence them), whereas policy makers might be
-more interested in projections (which show what would happen in the
-absence of any events that could change the trend) or scenario
-modelling. Forecasts may not be a suitable basis for informing policy
-decisions, if forecasters already have factored in the expectation of a
-future intervention. Model-based approaches can be either forecasts or
-projections depending on the assumptions, whereas eliciting projections
-that are not influenced by implicit assumptions about the future from
-humans may be harder.
-
-Further work should explore the effects of humans refining their
-mathematical models or changing model outputs in more detail.
-Model-based forecasts could be used as an input to human judgement, with
-researchers adjusting predictions generated by models. Seeing a
-model-based forecast could help humans calibrate uncertainty better,
-while allowing for manual intervention to adapt spurious trend
-predictions. Tools need to be developed to facilitate this process at a
-larger scale. Human insight could also be used as an input to models.
-Such a `hybrid' forecasting approach could for example ask humans to
-predict the trend of the effective reproduction number \(R_t\) or the
-doubling rate (i.e.~how the epidemic evolves) into the future and use
-this to estimate the exact number of cases, hospitalisations or deaths
-this would imply. In light of severe overconfidence, yet good
-performance in terms of the absolute error, post-processing of human
-forecasts to adjust and widen prediction intervals may be another
-promising approach. Crowd forecasting in general could benefit greatly
-from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of
-the limited resources available and the small number of participants,
-this seems worthwhile to further develop and explore.
-
-\clearpage
-
-\textbf{Acknowledgements}
-
-NIB received funding from the Health Protection Research Unit (grant
-code NIHR200908, https://www.nihr.ac.uk/). SA's work was funded by the
-Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/). The work
-of JB was supported by the Helmholtz Foundation
-(https://www.helmholtz.de/) via the SIMCARD Information and Data Science
-Pilot Project. This research was partly funded by the National Institute
-for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 \&
-16/136/46) using UK aid from the UK Government to support global health
-research. The views expressed in this publication are those of the
-author(s) and not necessarily those of the NIHR or the UK Department of
-Health and Social Care. BJQ is supported in part by a grant from the
-Bill and Melinda Gates Foundation (OPP1139859,
-https://www.gatesfoundation.org/). EvL acknowledges funding by the
-National Institute for Health Research (NIHR) Health Protection Research
-Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908,
-https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research
-and innovation programme - project EpiPose (101003688,
-https://ec.europa.eu/programmes/horizon2020/). AC acknowledges funding
-by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/),
-and the Academy of Medical Sciences (https://acmedsci.ac.uk/). SF's work
-was supported by the Wellcome Trust (grant: 210758/Z/18/Z,
-https://wellcome.org/), and the NIHR (NIHR200908,
-https://www.nihr.ac.uk/).
-
-We thank all forecasters who participated in this study for their
-contribution.
-
-We would also like to acknowledge (in a randomised order) the members of
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group at the the London School of Hygiene \& Tropical Medicine:
-Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie
-Diamond, Katherine E. Atkins, Rein M G J Houben, Jiayao Lei, Rachel
-Lowe, David Simons, Sophie R Meakin, Nicholas G. Davies, Timothy W
-Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly,
-Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas,
-Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia
-Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson,
-Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang
-Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C
-Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun,
-Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche,
-James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday,
-Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan
-Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R
-Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael
-Pung, Anna M Foss.
-
-\clearpage
-
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
-
-\hypertarget{appendix-supplementary-information}{%
-\section*{(APPENDIX) Supplementary
-information}\label{appendix-supplementary-information}}
-\addcontentsline{toc}{section}{(APPENDIX) Supplementary information}
-
-\hypertarget{supplementary-information}{%
-\section{Supplementary information}\label{supplementary-information}}
-
-\hypertarget{scoring-metrics-used}{%
-\subsection{Scoring metrics used}\label{scoring-metrics-used}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{9.3cm}}
-\caption{\label{tab:scoring-metrics}Overview of the scoring metrics used.}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{Overview of the scoring metrics used. \textit{(continued)}}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-WIS (Weighted) interval score & The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
-It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
-The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction.
-For a single interval, the score is computed as
-  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
-  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e.
-the lower and upper bound of a single prediction interval.
-For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
-  $$WIS = \frac{1}{K + 0.5} \cdot \left( w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y) \right), $$
-  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
-
-\cellcolor{gray!6}{Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.}\\
-\addlinespace \addlinespace
-Interval coverage & Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
-Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
-we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.\\
-\addlinespace \addlinespace
-Bias & (Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict. Values are between -1 and 1 and 0 ideally. For continuous forecasts, bias is given as 
-$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
-where $F$ is the CDF of the predictive distribution and $y$ is the observed value.
-
-For quantile forecasts, $F(y)$ is replaced by a quantile rank.
-The appropriate quantile rank is determined by whether the median forecast is below  or above the true value.
-We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.
-
-\cellcolor{gray!6}{In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
-It is therefore a more robust measurement.}\\*
-\end{longtable}
-
-\clearpage
-
-\hypertarget{the-crowdforecasting-app}{%
-\subsection{The crowdforecasting app}\label{the-crowdforecasting-app}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../crowd-forecast/Screenshot-forecasting-app} \caption{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).
-}\label{fig:screenshot}
-\end{figure}
-
-\clearpage
-
 \hypertarget{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}{%
-\subsection{Text S1. Further details on the semi-mechanistic forecasting
-models}\label{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}}
+\subsection{Text S1. Further details on the semi-mechanistic forecasting models}\label{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}}
 
@@
 
-The model was initialised prior to the first observed data point by
-assuming constant exponential growth for the mean of assumed delays from
-infection to case report.
+The model was initialised prior to the first observed data point by assuming constant exponential growth for the mean of assumed delays from infection to case report.
 
@@
 
-Where \(I_{obs}\) and \(r_{obs}\) are estimated from the first week of
-observed data. For the time window of the observed data infections were
-then modelled by weighting previous infections by the generation time
-and scaling by the instantaneous reproduction number. These infections
-were then convolved to cases by date (\(O_t\)) and cases by date of
-report (\(D_t\)) using log-normal delay distributions. This model can be
-defined mathematically as follows,
+Where \(I_{obs}\) and \(r_{obs}\) are estimated from the first week of observed data.
+For the time window of the observed data infections were then modelled by weighting previous infections by the generation time and scaling by the instantaneous reproduction number.
+These infections were then convolved to cases by date (\(O_t\)) and cases by date of report (\(D_t\)) using log-normal delay distributions.
+This model can be defined mathematically as follows,
 
@@
 
-Where, \begin{align}
+Where,
+\begin{align}
      w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
@@
 
-\(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) were truncated to be
-greater than 0 and with \(\xi\), and \(w\) normalised to sum to 1.
+\(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) were truncated to be greater than 0 and with \(\xi\), and \(w\) normalised to sum to 1.
 
-The prior for the generation time was sourced from {[}51{]} but refit
-using a log-normal incubation period with a mean of 5.2 days (SD 1.1)
-and SD of 1.52 days (SD 1.1) with this incubation period also being used
-as a prior {[}52{]} for \(\xi_{O}\). This resulted in a
-gamma-distributed generation time with mean 3.6 days (standard deviation
-(SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates. We estimated
-the delay between symptom onset and case report or death required to
-convolve latent infections to observations by fitting an integer
-adjusted log-normal distribution to 10 subsampled bootstraps of a public
-linelist for cases in Germany from April 2020 to June 2020 with each
-bootstrap using 1\% or 1769 samples of the available data {[}45,53{]}
-and combining the posteriors for the mean and standard deviation of the
-log-normal distribution {[}40,42,46,54{]}.
+The prior for the generation time was sourced from (Ganyani et al.
+2020) but refit using a log-normal incubation period with a mean of 5.2 days (SD 1.1) and SD of 1.52 days (SD 1.1) with this incubation period also being used as a prior (Lauer et al.
+2020) for \(\xi_{O}\).
+This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
+We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1\% or 1769 samples of the available data (Xu et al.
+2020; Abbott, Sherratt, et al.
+2020) and combining the posteriors for the mean and standard deviation of the log-normal distribution (Abbott, Hellewell, et al.
+2020; epiforecasts.io/covid 2020; {``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid-19} Outbreak in {England} \textbar{} {medRxiv}''} n.d.; Stan Development Team 2020).
 
-\(GP_t\) is an approximate Hilbert space Gaussian process as defined in
-{[}55{]} using a Matern 3/2 kernel using a boundary factor of 1.5 and 17
-basis functions (20\% of the number of days used in fitting). The length
-scale of the Gaussian process was given a log-normal prior with a mean
-of 21 days, and a standard deviation of 7 days truncated to be greater
-than 3 days and less than 60 days. The magnitude of the Gaussian process
-was assumed to be normally distributed centred at 0 with a standard
-deviation of 0.1.
+\(GP_t\) is an approximate Hilbert space Gaussian process as defined in (Riutort-Mayol et al.
+2020) using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20\% of the number of days used in fitting).
+The length scale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
+The magnitude of the Gaussian process was assumed to be normally distributed centred at 0 with a standard deviation of 0.1.
 
-From the forecast time horizon (\(T\)) and onwards the last value of the
-Gaussian process was used (hence \(R_t\) was assumed to be fixed) and
-latent infections were adjusted to account for the proportion of the
-population that was susceptible to infection as follows,
+From the forecast time horizon (\(T\)) and onwards the last value of the Gaussian process was used (hence \(R_t\) was assumed to be fixed) and latent infections were adjusted to account for the proportion of the population that was susceptible to infection as follows,
 
@@
 
-where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\)
-and \(I'_t\) are the unadjusted infections defined above. This
-adjustment is based on that implemented in the \texttt{epidemia} R
-package {[}56,57{]}.
+where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\) and \(I'_t\) are the unadjusted infections defined above.
+This adjustment is based on that implemented in the \texttt{epidemia} R package (Scott et al.
+2020; Bhatt et al., n.d.).
 
@@
 
-The convolution model shares the same observation model as the renewal
-model but rather than assuming that an observation is predicted by
-itself using the renewal equation instead assumes that it is predicted
-entirely by another observation after some parametric delay. It can be
-defined mathematically as follows,
+The convolution model shares the same observation model as the renewal model but rather than assuming that an observation is predicted by itself using the renewal equation instead assumes that it is predicted entirely by another observation after some parametric delay.
+It can be defined mathematically as follows,
 
@@
 
-with \(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) truncated to be
-greater than 0 and with \(\xi\) normalised such that
-\(\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1\).
+with \(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) truncated to be greater than 0 and with \(\xi\) normalised such that \(\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1\).
 
@@
 
-Both models were implemented using the \texttt{EpiNow2} R package
-(version 1.3.3) {[}40{]}. Each forecast target was fitted independently
-for each model using Markov-chain Monte Carlo (MCMC) in stan {[}46{]}. A
-minimum of 4 chains were used with a warmup of 250 samples for the
-renewal equation-based model and 1000 samples for the convolution model.
-2000 samples total post warmup were used for the renewal equation model
-and 4000 samples for the convolution model. Different settings were
-chosen for each model to optimise compute time contingent on
-convergence. Convergence was assessed using the R hat diagnostic
-{[}46{]}. For the convolution model forecast the case forecast from the
-renewal equation model was used in place of observed cases beyond the
-forecast horizon using 1000 posterior samples. 12 weeks of data was used
-for both models though only 3 weeks of data were included in the
-likelihood for the convolution model.
+Both models were implemented using the \texttt{EpiNow2} R package (version 1.3.3) (Abbott, Hellewell, et al.
+2020).
+Each forecast target was fitted independently for each model using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020).
+A minimum of 4 chains were used with a warmup of 250 samples for the renewal equation-based model and 1000 samples for the convolution model.
+2000 samples total post warmup were used for the renewal equation model and 4000 samples for the convolution model.
+Different settings were chosen for each model to optimise compute time contingent on convergence.
+Convergence was assessed using the R hat diagnostic (Stan Development Team 2020).
+For the convolution model forecast the case forecast from the renewal equation model was used in place of observed cases beyond the forecast horizon using 1000 posterior samples.
+12 weeks of data was used for both models though only 3 weeks of data were included in the likelihood for the convolution model.
 
@@
 
-\hypertarget{tables-with-results-of-the-forecast-evaluation}{%
-\subsection{Tables with results of the forecast
-evaluation}\label{tables-with-results-of-the-forecast-evaluation}}
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
+Abbott, Sam, Joel Hellewell, Joe Hickson, James Munday, Katelyn Gostic, Peter Ellis, Katharine Sherratt, et al.
+2020.
+{``EpiNow2: Estimate Real-Time Case Counts and Time-Varying Epidemiological Parameters.''} \emph{-} - (-): --.
+\url{https://doi.org/10.5281/zenodo.3957489}.
 
-\begin{table}[!h]
-\caption{\label{tab:score-table-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
+\leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
+Abbott, Sam, Katharine Sherratt, Jonnie Bevan, Hamish Gibbs, Joel Hellewell, James Munday, Patrick Barks, Paul Campbell, Flavio Finger, and Sebastian Funk.
+2020.
+{``Covidregionaldata: Subnational Data for the Covid-19 Outbreak.''} \emph{-} - (-): --.
+\url{https://doi.org/10.5281/zenodo.3957539}.
 
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 7010 (0.8) & 7480 (0.64) & 2680 (0.73) & 1700 (1.38) & 2630 (0.68) & -0.01 & 10400 (0.82) & 0.55 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 8740 (1) & 11800 (1.01) & 2190 (0.6) & 2720 (2.21) & 3830 (0.99) & 0.18 & 12000 (0.94) & 0.48 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 16200 (0.89) & 16600 (0.76) & 3660 (0.6) & 5930 (1.56) & 6600 (0.78) & -0.01 & 23300 (0.87) & 0.36 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25600 (1.4) & 33800 (1.54) & 5420 (0.88) & 5920 (1.56) & 14200 (1.69) & 0.17 & 34600 (1.29) & 0.43 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 27000 (0.81) & 26200 (0.64) & 4750 (0.52) & 11000 (1.43) & 11200 (0.67) & 0.02 & 39000 (0.83) & 0.14 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 50600 (1.51) & 70000 (1.72) & 10800 (1.18) & 7710 (1) & 32100 (1.93) & 0.13 & 68700 (1.46) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 39200 (0.7) & 38600 (0.52) & 5970 (0.49) & 15600 (1.26) & 17600 (0.56) & 0.07 & 54800 (0.74) & 0.05 & 0.38\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 91700 (1.64) & 135000 (1.83) & 19500 (1.6) & 8990 (0.72) & 63200 (2.02) & 0.09 & 125000 (1.68) & 0.31 & 0.48\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{aggregate-performance-by-location}{%
-\subsection{Aggregate performance by
-location}\label{aggregate-performance-by-location}}
-
-\hypertarget{performance-in-germany}{%
-\subsubsection{Performance in Germany}\label{performance-in-germany}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Germany-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Germany}
-\end{figure}
-
-\hypertarget{performance-in-poland}{%
-\subsubsection{Performance in Poland}\label{performance-in-poland}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Poland-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Poland}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-absolute-terms}{%
-\subsubsection{Performance across locations in absolute
-terms}\label{performance-across-locations-in-absolute-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-v4} \caption{Visualisation of aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-relative-terms}{%
-\subsection{Performance across locations in relative
-terms}\label{performance-across-locations-in-relative-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4} \caption{Visualisation of relative aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals.
-E: Dispersion.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast.
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations-rel}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-daily-reported-cases-and-deaths}{%
-\subsection{Visualisation of daily reported cases and
-deaths}\label{visualisation-of-daily-reported-cases-and-deaths}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily_truth} \caption{Visualisation of daily report data.
-The black line represents weekly data divided by seven.
-Data were last accessed through the German and Polish Forecast Hub on August 21 2021.}\label{fig:daily-truth}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily-data-updates} \caption{Visualisation of the absolute difference between the daily report data at the time and the data now.
-In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:daily-truth-update}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/weekly-data-updates} \caption{Visualisation of the relative difference between the weekly report data at the time and the data now.
-Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:weekly-truth-update}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}{%
-\subsection{Visualisation of scores and forecasts 1, 3, 4 weeks
-ahead}\label{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} \caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} \caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} \caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-4}
-\end{figure}
-
-\clearpage
-
-\hypertarget{distribution-of-scores}{%
-\subsection{Distribution of scores}\label{distribution-of-scores}}
-
-\hypertarget{absolute-scores}{%
-\subsubsection{Absolute scores}\label{absolute-scores}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1} \caption{A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3} \caption{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4} \caption{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-4}
-\end{figure}
-
-\hypertarget{ranks-achieved-by-forecasts}{%
-\subsubsection{Ranks achieved by
-forecasts}\label{ranks-achieved-by-forecasts}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-2}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-4}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} \caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-renewal} \caption{Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences-renewal}
-\end{figure}
-
-\newpage
-
-\hypertarget{comparison-of-ensembles}{%
-\subsection{Comparison of ensembles}\label{comparison-of-ensembles}}
-
-\hypertarget{performance-visualisation-mean-ensemble}{%
-\subsubsection{Performance visualisation mean
-ensemble}\label{performance-visualisation-mean-ensemble}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble”     extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
-Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-mean}
-\end{figure}
-
-\hypertarget{tables-median-ensemble}{%
-\subsubsection{Tables median ensemble}\label{tables-median-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 6970 (0.79) & 8260 (0.71) & 3060 (0.83) & 943 (0.77) & 2970 (0.77) & 0.04 & 10800 (0.85) & 0.55 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 7820 (0.89) & 9630 (0.82) & 3270 (0.89) & 1210 (0.98) & 3330 (0.86) & -0.02 & 12000 (0.94) & 0.48 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 7960 (0.91) & 10300 (0.88) & 3190 (0.87) & 1020 (0.83) & 3760 (0.97) & 0.04 & 12100 (0.95) & 0.57 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 16400 (0.9) & 19600 (0.89) & 5350 (0.87) & 3290 (0.87) & 7730 (0.92) & 0.02 & 24200 (0.9) & 0.43 & 0.69\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 16900 (0.92) & 19600 (0.89) & 5230 (0.85) & 4310 (1.13) & 7370 (0.88) & 0.00 & 24600 (0.92) & 0.38 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 17500 (0.96) & 21400 (0.98) & 5830 (0.95) & 2880 (0.76) & 8770 (1.04) & 0.00 & 25500 (0.95) & 0.45 & 0.71\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 235 (0.95) & 332 (0.98) & 88.6 (0.96) & 90.4 (0.79) & 55.5 (1.33) & -0.01 & 323 (0.97) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 234 (0.94) & 331 (0.98) & 85.2 (0.92) & 98.1 (0.85) & 50.2 (1.21) & -0.05 & 329 (0.99) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 234 (0.94) & 329 (0.97) & 90.7 (0.98) & 118 (1.03) & 25.3 (0.61) & -0.08 & 333 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 239 (0.96) & 337 (1) & 85.2 (0.92) & 99.6 (0.87) & 54.2 (1.3) & -0.03 & 322 (0.96) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 246 (0.99) & 342 (1.01) & 91.5 (0.99) & 106 (0.92) & 48.6 (1.17) & -0.06 & 342 (1.02) & 0.67 & 0.92\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 296 (1.01) & 398 (1.03) & 125 (0.95) & 91 (0.84) & 80.2 (1.55) & 0.05 & 486 (1.13) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 303 (1.04) & 423 (1.1) & 115 (0.87) & 122 (1.13) & 66.1 (1.27) & 0.00 & 483 (1.13) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 270 (0.92) & 385 (1) & 121 (0.92) & 119 (1.1) & 29.9 (0.58) & -0.04 & 403 (0.94) & 0.58 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 303 (1.04) & 392 (1.02) & 122 (0.92) & 106 (0.98) & 74.6 (1.44) & 0.03 & 499 (1.16) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 296 (1.01) & 397 (1.03) & 128 (0.97) & 97.1 (0.9) & 71.2 (1.37) & -0.01 & 462 (1.08) & 0.67 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 30800 (0.92) & 38600 (0.95) & 7910 (0.87) & 6890 (0.9) & 16000 (0.96) & 0.03 & 44200 (0.94) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 30800 (0.92) & 34100 (0.84) & 7500 (0.82) & 8960 (1.17) & 14300 (0.86) & 0.02 & 44100 (0.94) & 0.24 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 34000 (1.02) & 43100 (1.06) & 8860 (0.97) & 6300 (0.82) & 18900 (1.14) & 0.02 & 48100 (1.03) & 0.29 & 0.60\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 51200 (0.92) & 69900 (0.95) & 10900 (0.89) & 11100 (0.9) & 29300 (0.94) & 0.04 & 69600 (0.94) & 0.19 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 48800 (0.87) & 58600 (0.8) & 9700 (0.8) & 13700 (1.1) & 25400 (0.81) & 0.00 & 65800 (0.88) & 0.19 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 59100 (1.06) & 84100 (1.14) & 12600 (1.03) & 10100 (0.81) & 36400 (1.16) & 0.01 & 78900 (1.06) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 332 (1.04) & 388 (1.18) & 158 (0.92) & 78.7 (0.85) & 95 (1.72) & -0.02 & 547 (1.12) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 321 (1.01) & 385 (1.17) & 153 (0.89) & 100 (1.08) & 68.1 (1.24) & -0.01 & 535 (1.1) & 0.54 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 298 (0.93) & 337 (1.03) & 155 (0.9) & 106 (1.14) & 37.5 (0.68) & -0.04 & 441 (0.9) & 0.67 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 319 (1) & 342 (1.04) & 160 (0.93) & 85.1 (0.92) & 73.6 (1.34) & -0.02 & 547 (1.12) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 332 (1.04) & 363 (1.11) & 168 (0.98) & 86.1 (0.93) & 78.2 (1.42) & -0.02 & 528 (1.08) & 0.58 & 0.96\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 445 (1.05) & 532 (1.2) & 193 (0.91) & 107 (0.85) & 144 (1.68) & -0.03 & 700 (1.04) & 0.54 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 399 (0.94) & 438 (0.99) & 195 (0.92) & 105 (0.83) & 97.9 (1.14) & -0.05 & 692 (1.03) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 384 (0.91) & 387 (0.87) & 196 (0.92) & 122 (0.97) & 65.9 (0.77) & -0.06 & 602 (0.89) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 407 (0.96) & 456 (1.03) & 202 (0.95) & 105 (0.83) & 101 (1.18) & -0.03 & 669 (0.99) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 457 (1.08) & 527 (1.19) & 208 (0.98) & 129 (1.02) & 121 (1.41) & -0.06 & 744 (1.1) & 0.50 & 0.96\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\hypertarget{tables-mean-ensemble}{%
-\subsubsection{Tables mean ensemble}\label{tables-mean-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 8680 (1) & 10300 (1) & 3700 (1) & 1460 (1) & 3520 (1) & -0.02 & 13400 (1) & 0.50 & 0.86\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 7600 (0.88) & 8770 (0.85) & 3360 (0.91) & 1090 (0.75) & 3140 (0.89) & 0.01 & 11900 (0.89) & 0.52 & 0.90\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 8050 (0.93) & 9070 (0.88) & 3520 (0.95) & 1410 (0.97) & 3120 (0.89) & -0.02 & 12600 (0.94) & 0.48 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 8090 (0.93) & 9780 (0.95) & 3490 (0.94) & 1110 (0.76) & 3490 (0.99) & 0.02 & 12700 (0.95) & 0.57 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 19000 (1) & 22100 (1) & 5960 (1) & 3690 (1) & 9340 (1) & 0.02 & 28800 (1) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 17100 (0.9) & 20600 (0.93) & 5550 (0.93) & 2850 (0.77) & 8660 (0.93) & 0.05 & 26000 (0.9) & 0.38 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 17600 (0.93) & 20000 (0.9) & 5540 (0.93) & 3790 (1.03) & 8230 (0.88) & 0.01 & 26800 (0.93) & 0.36 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 18300 (0.96) & 22600 (1.02) & 5910 (0.99) & 2640 (0.72) & 9720 (1.04) & 0.06 & 27700 (0.96) & 0.38 & 0.76\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 229 (1) & 292 (1) & 101 (1) & 90.4 (1) & 36.7 (1) & -0.07 & 315 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 219 (0.96) & 289 (0.99) & 96.8 (0.96) & 79.8 (0.88) & 42.6 (1.16) & -0.04 & 297 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 217 (0.95) & 287 (0.98) & 95.3 (0.94) & 83.1 (0.92) & 38.7 (1.05) & -0.07 & 300 (0.95) & 0.67 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 225 (0.98) & 292 (1) & 98.7 (0.98) & 94.2 (1.04) & 32 (0.87) & -0.09 & 314 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 222 (0.97) & 289 (0.99) & 98 (0.97) & 84.1 (0.93) & 39.6 (1.08) & -0.04 & 295 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 225 (0.98) & 290 (0.99) & 99.7 (0.99) & 84.7 (0.94) & 40.5 (1.1) & -0.05 & 314 (1) & 0.71 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 256 (1) & 306 (1) & 138 (1) & 64.5 (1) & 53.2 (1) & 0.04 & 374 (1) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 270 (1.05) & 338 (1.1) & 136 (0.99) & 65.2 (1.01) & 68.1 (1.28) & 0.06 & 413 (1.1) & 0.75 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 268 (1.05) & 346 (1.13) & 133 (0.96) & 78.7 (1.22) & 57.1 (1.07) & 0.05 & 408 (1.09) & 0.75 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 259 (1.01) & 322 (1.05) & 133 (0.96) & 81.7 (1.27) & 44.4 (0.83) & 0.03 & 380 (1.02) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 264 (1.03) & 315 (1.03) & 133 (0.96) & 70.1 (1.09) & 60 (1.13) & 0.06 & 404 (1.08) & 0.71 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 264 (1.03) & 332 (1.08) & 141 (1.02) & 60.1 (0.93) & 63.1 (1.19) & 0.06 & 390 (1.04) & 0.79 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 35600 (1) & 42100 (1) & 9340 (1) & 7050 (1) & 19200 (1) & 0.03 & 51200 (1) & 0.26 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 32100 (0.9) & 40500 (0.96) & 8830 (0.95) & 4920 (0.7) & 18300 (0.95) & 0.07 & 47200 (0.92) & 0.29 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 32200 (0.9) & 36700 (0.87) & 8430 (0.9) & 7190 (1.02) & 16500 (0.86) & 0.04 & 46900 (0.92) & 0.24 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 35200 (0.99) & 46000 (1.09) & 9630 (1.03) & 4600 (0.65) & 20900 (1.09) & 0.08 & 51000 (1) & 0.38 & 0.67\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 60300 (1) & 79300 (1) & 15700 (1) & 10400 (1) & 34100 (1) & 0.04 & 78600 (1) & 0.29 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 55000 (0.91) & 77100 (0.97) & 14600 (0.93) & 6620 (0.64) & 33800 (0.99) & 0.11 & 75200 (0.96) & 0.33 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 53400 (0.89) & 66600 (0.84) & 13700 (0.87) & 10600 (1.02) & 29200 (0.86) & 0.06 & 70400 (0.9) & 0.26 & 0.60\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 61700 (1.02) & 89800 (1.13) & 16400 (1.04) & 6400 (0.62) & 38900 (1.14) & 0.12 & 82900 (1.05) & 0.31 & 0.64\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 289 (1) & 293 (1) & 178 (1) & 45.9 (1) & 65.7 (1) & 0.01 & 443 (1) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 310 (1.07) & 348 (1.19) & 182 (1.02) & 42 (0.92) & 86.5 (1.32) & 0.08 & 502 (1.13) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 315 (1.09) & 339 (1.16) & 178 (1) & 62.2 (1.36) & 74 (1.13) & 0.07 & 507 (1.14) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 297 (1.03) & 292 (1) & 174 (0.98) & 67.7 (1.47) & 55 (0.84) & 0.01 & 452 (1.02) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 294 (1.02) & 299 (1.02) & 172 (0.97) & 48 (1.05) & 74.2 (1.13) & 0.03 & 476 (1.07) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 310 (1.07) & 349 (1.19) & 189 (1.06) & 39.4 (0.86) & 81.9 (1.25) & 0.05 & 482 (1.09) & 0.62 & 1.00\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 437 (1) & 568 (1) & 232 (1) & 72 (1) & 134 (1) & 0.00 & 702 (1) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 445 (1.02) & 598 (1.05) & 237 (1.02) & 56.4 (0.78) & 152 (1.13) & 0.06 & 707 (1.01) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 421 (0.96) & 520 (0.92) & 239 (1.03) & 49.9 (0.69) & 132 (0.99) & 0.05 & 678 (0.97) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 398 (0.91) & 465 (0.82) & 235 (1.01) & 55.6 (0.77) & 107 (0.8) & 0.00 & 628 (0.89) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 418 (0.96) & 533 (0.94) & 222 (0.96) & 66.8 (0.93) & 129 (0.96) & 0.03 & 662 (0.94) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 467 (1.07) & 636 (1.12) & 248 (1.07) & 61 (0.85) & 158 (1.18) & 0.05 & 755 (1.08) & 0.67 & 1.00\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{sensitivity-analysis}{%
-\subsection{Sensitivity analysis}\label{sensitivity-analysis}}
-
-In the original analysis, cases and deaths were scored on different
-periods, as the convolution model was only added later. This sensitivity
-shows performance of all models restricted to the period from December
-14 2020 until March 1st 2021 where all models were available.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-late}
-\end{figure}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 4980 (0.74) & 5730 (0.64) & 2070 (0.6) & 728 (0.74) & 2190 (0.94) & 0.09 & 7810 (0.82) & 0.54 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 6730 (1) & 8960 (1) & 3430 (1) & 978 (1) & 2330 (1) & -0.09 & 9550 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 9640 (1.43) & 13300 (1.48) & 1970 (0.57) & 4170 (4.26) & 3500 (1.5) & 0.09 & 12700 (1.33) & 0.46 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 10700 (0.99) & 13800 (1.1) & 2880 (0.58) & 2350 (0.85) & 5430 (1.79) & 0.08 & 15400 (1.07) & 0.46 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 10800 (1) & 12500 (1) & 4940 (1) & 2780 (1) & 3030 (1) & -0.13 & 14400 (1) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25000 (2.31) & 34000 (2.72) & 4780 (0.97) & 8710 (3.13) & 11500 (3.8) & 0.05 & 32000 (2.22) & 0.50 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 17200 (1) & 16000 (0.98) & 3800 (0.63) & 5660 (0.85) & 7770 (1.74) & 0.07 & 26800 (1.1) & 0.08 & 0.58\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 17200 (1) & 16300 (1) & 6030 (1) & 6670 (1) & 4470 (1) & -0.16 & 24400 (1) & 0.33 & 0.67\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 37700 (2.19) & 55900 (3.43) & 8840 (1.47) & 10700 (1.6) & 18100 (4.05) & -0.03 & 49800 (2.04) & 0.33 & 0.58\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 26100 (0.95) & 21000 (0.84) & 4810 (0.7) & 11300 (0.83) & 10100 (1.43) & 0.04 & 39400 (1.05) & 0.00 & 0.46\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 27600 (1) & 25000 (1) & 6900 (1) & 13600 (1) & 7060 (1) & -0.19 & 37400 (1) & 0.29 & 0.54\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 48900 (1.77) & 77800 (3.11) & 13800 (2) & 11900 (0.88) & 23200 (3.29) & -0.10 & 65500 (1.75) & 0.38 & 0.58\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{overview-of-models-and-forecasters}{%
-\subsection{Overview of models and
-forecasters}\label{overview-of-models-and-forecasters}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{7.3cm}}
-\caption{\label{tab:table-ensemble-versions}Overview of the models and ensembles used.}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{Overview of the models and ensembles used. \textit{(continued)}}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-\cellcolor{gray!6}{Hub-ensemble-realised} & \cellcolor{gray!6}{Official Forecast Hub median ensemble.
-Created by the Forecast Hub officially under the name 'KITCOVIDhub-median\_ensemble' and used as the default ensemble.
-Included are our crowd forecasts as well as the renewal model (with one missed submission on December 28 2020, but not the convolution model which was deemed to similar to the renewal model.}\\
-\addlinespace \addlinespace
-Hub-ensemble-realised-mean & Official Forecast Hub mean ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-mean\_ensemble'.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{ \vphantom{1}} & \cellcolor{gray!6}{}\\
-\addlinespace \addlinespace
-Hub-ensemble & Version of the official Hub median ensemble which excludes all our contributions.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Hub-ensemble-mean} & \cellcolor{gray!6}{Version of the official Hub mean ensemble which excludes all our contributions.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-renewal, 
-    Hub-ensemble-with-renewal-mean & Versions of the official Hub ensembles which of our contributions includes only the Renewal model.\\
-\addlinespace \addlinespace
-Hub-ensemble-with-crowd, 
-\cellcolor{gray!6}{    Hub-ensemble-with-crowd-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which of our contributions includes only the Crowd forecast.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-convolution, 
-    Hub-ensemble-with-convolution-mean & Versions of the official Hub ensembles which of our contributions includes only the Convolution model (which originally was never included in any official Hub ensemble).\\
-\addlinespace \addlinespace
-Hub-ensemble-with-all, 
-\cellcolor{gray!6}{    Hub-ensemble-with-all-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which includes all our contributions.
-For cases, this is identical to the official Hub ensembles, but for deaths the convolution model was added.}\\
-\addlinespace \addlinespace
- & \\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Crowd forecast} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'}\\
-\addlinespace \addlinespace
-Renewal model & Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Convolution model} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\_secondary'}\\*
-\end{longtable}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/number-forecasters} \caption{Number of participants who submitted a forecast over time.}\label{fig:num-forecasters}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/ensemble-members} \caption{Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
-Note that the renewal model was not included in the ensemble on December 28th 2020.}\label{fig:num-ensemble-members}
-\end{figure}
-
-\clearpage
-
-\hypertarget{comparison-of-crowd-forecasts-and-application-baseline}{%
-\subsection{Comparison of crowd forecasts and application
-baseline}\label{comparison-of-crowd-forecasts-and-application-baseline}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} \caption{Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the median, as well as the 50\% and 90\% prediction intervals (in order of decreasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons).}\label{fig:compare-forecasters}
-\end{figure}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{McGowan CJ, Biggerstaff M, Johansson M, Apfeldorf KM,
-Ben-Nun M, Brooks L, et al. Collaborative efforts to forecast seasonal
-influenza in the {United States}, 2015--2016. Scientific Reports.
-2019;9: 683.
-doi:\href{https://doi.org/10.1038/s41598-018-36361-9}{10.1038/s41598-018-36361-9}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Reich NG, Brooks LC, Fox SJ, Kandula S, McGowan CJ,
-Moore E, et al. A collaborative multiyear, multimodel assessment of
-seasonal influenza forecasting in the {United States}. PNAS. 2019;116:
-3146--3154.
-doi:\href{https://doi.org/10.1073/pnas.1812594116}{10.1073/pnas.1812594116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Shaman J, Karspeck A. Forecasting seasonal outbreaks of
-influenza. PNAS. 2012;109: 20425--20430.
-doi:\href{https://doi.org/10.1073/pnas.1208772109}{10.1073/pnas.1208772109}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Biggerstaff M, Alper D, Dredze M, Fox S, Fung IC-H,
-Hickmann KS, et al. Results from the centers for disease control and
-prevention's predict the 2013--2014 {Influenza Season Challenge}. BMC
-Infectious Diseases. 2016;16: 357.
-doi:\href{https://doi.org/10.1186/s12879-016-1669-x}{10.1186/s12879-016-1669-x}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak
-AL, Baugher B, et al. An open challenge to advance probabilistic
-forecasting for dengue epidemics. PNAS. 2019;116: 24268--24274.
-doi:\href{https://doi.org/10.1073/pnas.1909865116}{10.1073/pnas.1909865116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Yamana TK, Kandula S, Shaman J. Superensemble forecasts
-of dengue outbreaks. Journal of The Royal Society Interface. 2016;13:
-20160410.
-doi:\href{https://doi.org/10.1098/rsif.2016.0410}{10.1098/rsif.2016.0410}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Colón-González FJ, Bastos LS, Hofmann B, Hopkin A,
-Harpham Q, Crocker T, et al. Probabilistic seasonal dengue forecasting
-in {Vietnam}: {A} modelling study using superensembles. PLOS Medicine.
-2021;18: e1003542.
-doi:\href{https://doi.org/10.1371/journal.pmed.1003542}{10.1371/journal.pmed.1003542}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Viboud C, Sun K, Gaffey R, Ajelli M, Fumanelli L, Merler
-S, et al. The {RAPIDD} ebola forecasting challenge: {Synthesis} and
-lessons learnt. Epidemics. 2018;22: 13--21.
-doi:\href{https://doi.org/10.1016/j.epidem.2017.08.002}{10.1016/j.epidem.2017.08.002}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Funk S, Camacho A, Kucharski AJ, Lowe R, Eggo RM,
-Edmunds WJ. Assessing the performance of real-time epidemic forecasts:
-{A} case study of {Ebola} in the {Western Area} region of {Sierra
-Leone}, 2014-15. PLOS Computational Biology. 2019;15: e1006785.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1006785}{10.1371/journal.pcbi.1006785}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Del Valle SY, McMahon BH, Asher J, Hatchett R, Lega JC,
-Brown HE, et al. Summary results of the 2014-2015 {DARPA Chikungunya}
-challenge. BMC Infectious Diseases. 2018;18: 245.
-doi:\href{https://doi.org/10.1186/s12879-018-3124-7}{10.1186/s12879-018-3124-7}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Farrow DC, Brooks LC, Hyun S, Tibshirani RJ, Burke DS,
-Rosenfeld R. A human judgment approach to epidemiological forecasting.
-PLOS Computational Biology. 2017;13: e1005248.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1005248}{10.1371/journal.pcbi.1005248}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Funk S, Abbott S, Atkins BD, Baguelin M, Baillie JK,
-Birrell P, et al. Short-term forecasts to inform the response to the
-{Covid-19} epidemic in the {UK}. medRxiv. 2020; 2020.11.11.20220962.
-doi:\href{https://doi.org/10.1101/2020.11.11.20220962}{10.1101/2020.11.11.20220962}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K,
-et al. {COVID-19 Forecast Hub}: 4 {December} 2020 snapshot. {Zenodo};
-2020.
-doi:\href{https://doi.org/10.5281/zenodo.3963371}{10.5281/zenodo.3963371}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A,
-Rivadeneira AJC, et al. Evaluation of individual and ensemble
-probabilistic forecasts of {COVID-19} mortality in the {US}. medRxiv.
-2021; 2021.02.03.21250974.
-doi:\href{https://doi.org/10.1101/2021.02.03.21250974}{10.1101/2021.02.03.21250974}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. Short-term forecasting of {COVID-19} in {Germany}
-and {Poland} during the second wave -- a preregistered study. medRxiv.
-2021; 2020.12.24.20248826.
-doi:\href{https://doi.org/10.1101/2020.12.24.20248826}{10.1101/2020.12.24.20248826}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. National and subnational short-term forecasting of
-{COVID-19} in {Germany} and {Poland}, early 2021. 2021;
-2021.11.05.21265810.
-doi:\href{https://doi.org/10.1101/2021.11.05.21265810}{10.1101/2021.11.05.21265810}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-europeancovid-19forecasthubEuropeanCovid19Forecast2021}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{European Covid-19 Forecast Hub. European {Covid-19
-Forecast Hub}. 2021 {[}cited 30 May 2021{]}. Available:
-\url{https://covid19forecasthub.eu/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichAccuracyRealtimeMultimodel2019}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Reich NG, McGowan CJ, Yamana TK, Tushar A, Ray EL,
-Osthus D, et al. Accuracy of real-time multi-model ensemble forecasts
-for seasonal influenza in the {U}.{S}. PLOS Computational Biology.
-2019;15: e1007486.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1007486}{10.1371/journal.pcbi.1007486}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Tetlock PE, Mellers BA, Rohrbaugh N, Chen E. Forecasting
-{Tournaments}: {Tools} for {Increasing Transparency} and {Improving} the
-{Quality} of {Debate}. Curr Dir Psychol Sci. 2014;23: 290--295.
-doi:\href{https://doi.org/10.1177/0963721414534257}{10.1177/0963721414534257}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Atanasov P, Rescober P, Stone E, Swift SA,
-Servan-Schreiber E, Tetlock P, et al. Distilling the {Wisdom} of
-{Crowds}: {Prediction Markets} vs. {Prediction Polls}. Management
-Science. 2016;63: 691--706.
-doi:\href{https://doi.org/10.1287/mnsc.2015.2374}{10.1287/mnsc.2015.2374}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers E-J. Laypeople
-{Can Predict Which Social-Science Studies Will Be Replicated
-Successfully}. Advances in Methods and Practices in Psychological
-Science. 2020;3: 267--285.
-doi:\href{https://doi.org/10.1177/2515245920919667}{10.1177/2515245920919667}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{ReplicationMarkets. Replication {Markets} -- {Reliable}
-research replicates\ldots you can bet on it. 2020 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.replicationmarkets.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Servan-Schreiber E, Wolfers J, Pennock DM, Galebach B.
-Prediction {Markets}: {Does Money Matter}? Electronic Markets. 2004;14:
-243--251.
-doi:\href{https://doi.org/10.1080/1019678042000245254}{10.1080/1019678042000245254}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{McAndrew TC, Reich NG. An expert judgment model to
-predict early stages of the {COVID-19} outbreak in the {United States}.
-medRxiv. 2020; 2020.09.21.20196725.
-doi:\href{https://doi.org/10.1101/2020.09.21.20196725}{10.1101/2020.09.21.20196725}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Recchia G, Freeman ALJ, Spiegelhalter D. How well did
-experts and laypeople forecast the size of the {COVID-19} pandemic? PLOS
-ONE. 2021;16: e0250935.
-doi:\href{https://doi.org/10.1371/journal.pone.0250935}{10.1371/journal.pone.0250935}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Metaculus. A {Preliminary Look} at {Metaculus} and
-{Expert Forecasts}. 22 Jun 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.metaculus.com/news/2020/06/02/LRT/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Hypermind. Hypermind \textbar{} {Supercollective}
-intelligence for decision makers. {Hypermind}; 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.hypermind.com/en/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{CSET Foretell. {CSET Foretell}. 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.cset-foretell.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{PredictIt. {PredictIt}. 2021 {[}cited 13 Oct 2021{]}.
-Available: \url{https://www.predictit.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Held L, Meyer S, Bracher J. Probabilistic forecasting in
-infectious disease epidemiology: The 13th {Armitage} lecture. Statistics
-in Medicine. 2017;36: 3443--3460.
-doi:\href{https://doi.org/10.1002/sim.7363}{10.1002/sim.7363}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Crowdforecastr: Eliciting crowd forecasts in r shiny. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618519}{10.5281/zenodo.4618519}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Covid.german.forecasts: Forecasting covid-19 related metrics for the
-german/poland forecast hub. 2020. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-ecdcDownloadHistoricalData2020}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{ECDC. Download historical data (to 14 {December} 2020)
-on the daily number of new reported {COVID-19} cases and deaths
-worldwide. {European Centre for Disease Prevention and Control}; 14 Dec
-2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rkiRKICoronavirusSARSCoV22021}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{RKI. {RKI} - {Coronavirus SARS-CoV-2} - {Aktueller
-Lage-}/{Situationsbericht} des {RKI} zu {COVID-19}. 2021 {[}cited 30 May
-2021{]}. Available:
-\url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-forsal.plRozbieznosciStatystykachKoronawirusa2020}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Forsal.pl. Rozbieżności w statystykach koronawirusa. 22
-tys. przypadków będą doliczone do ogólnej liczby wyników. 2020 {[}cited
-30 May 2021{]}. Available:
-\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Ärzteblatt DÄG Redaktion Deutsches.
-SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an. {Deutsches
-Ärzteblatt}; 3 Nov 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Fay C, Guyader V, Rochette S, Girard C. Golem: A
-framework for robust shiny applications. 2021. Available:
-\url{https://github.com/ThinkR-open/golem}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie
-Y, et al. Shiny: Web application framework for r. 2021. Available:
-\url{https://CRAN.R-project.org/package=shiny}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Our World in Data. {COVID-19 Data Explorer}. {Our World
-in Data}; 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://ourworldindata.org/coronavirus-data-explorer}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K,
-Ellis P, et al. EpiNow2: Estimate real-time case counts and time-varying
-epidemiological parameters. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957489}{10.5281/zenodo.3957489}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Fraser C. Estimating {Individual} and {Household
-Reproduction Numbers} in an {Emerging Epidemic}. PLOS ONE. 2007;2: e758.
-doi:\href{https://doi.org/10.1371/journal.pone.0000758}{10.1371/journal.pone.0000758}}
+\leavevmode\vadjust pre{\hypertarget{ref-bhattSemiMechanisticBayesianModeling}{}}%
+Bhatt, Samir, Neil Ferguson, Seth Flaxman, Axel Gandy, Swapnil Mishra, and James A Scott. n.d. {``Semi-{Mechanistic Bayesian} Modeling of {COVID-19} with {Renewal Processes},''} 14.
 
 \leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation2020}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{epiforecasts.io/covid. Covid-19: {Temporal} variation in
-transmission during the {COVID-19} outbreak. {Covid-19}; 2020 {[}cited
-30 May 2021{]}. Available: \url{https://epiforecasts.io/covid/}}
+epiforecasts.io/covid. 2020. {``Covid-19: {Temporal} Variation in Transmission During the {COVID-19} Outbreak.''} {Covid-19}. 2020. \url{https://epiforecasts.io/covid/}.
 
-\leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Sherratt K, Abbott S, Meakin SR, Hellewell J, Munday JD,
-Bosse N, et al. Exploring surveillance data biases when estimating the
-reproduction number: With insights into subpopulation transmission of
-{Covid-19} in {England}. 2021; 2020.10.18.20214585.
-doi:\href{https://doi.org/10.1101/2020.10.18.20214585}{10.1101/2020.10.18.20214585}}
+\leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
+{``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid-19} Outbreak in {England} \textbar{} {medRxiv}.''} n.d.
+Accessed May 30, 2021.
+\url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}.
 
-\leavevmode\vadjust pre{\hypertarget{ref-abbottEstimatingTimevaryingReproduction2020a}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs
-HP, Bosse NI, et al. Estimating the time-varying reproduction number of
-{SARS-CoV-2} using national and subnational case counts. 2020 {[}cited
-14 Oct 2021{]}.
-doi:\href{https://doi.org/10.12688/wellcomeopenres.16006.1}{10.12688/wellcomeopenres.16006.1}}
+\leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
+Ganyani, Tapiwa, Cecile Kremer, Dongxuan Chen, Andrea Torneri, Christel Faes, Jacco Wallinga, and Niel Hens.
+2020.
+{``Estimating the Generation Interval for Coronavirus Disease (COVID-19) Based on Symptom Onset Data, March 2020.''} \emph{Eurosurveillance} 25 (17).
+
+\leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
+Lauer, Stephen A, Kyra H Grantz, Qifang Bi, Forrest K Jones, Qulu Zheng, Hannah R Meredith, Andrew S Azman, Nicholas G Reich, and Justin Lessler.
+2020.
+{``The Incubation Period of Coronavirus Disease 2019 (COVID-19) from Publicly Reported Confirmed Cases: Estimation and Application.''} \emph{Annals of Internal Medicine} 172 (9): 577--82.
+
+\leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
+Riutort-Mayol, Gabriel, Paul-Christian Bürkner, Michael R.
+Andersen, Arno Solin, and Aki Vehtari.
+2020.
+{``Practical Hilbert Space Approximate Bayesian Gaussian Processes for Probabilistic Programming.''} \url{https://arxiv.org/abs/2004.11408}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
+Scott, James A., Axel Gandy, Swapnil Mishra, Juliette Unwin, Seth Flaxman, and Samir Bhatt.
+2020.
+{``Epidemia: Modeling of Epidemics Using Hierarchical Bayesian Models.''} \url{https://imperialcollegelondon.github.io/epidemia/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
+Stan Development Team. 2020. {``RStan: The r Interface to Stan.''} \url{http://mc-stan.org/}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Xu B, Gutierrez B, Hill S, Scarpino S, Loskill A, Wu J,
-et al. Epidemiological data from the nCoV-2019 outbreak: Early
-descriptions from publicly available data. 2020. Available:
-\url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Stan Development Team. RStan: The r interface to stan.
-2020. Available: \url{http://mc-stan.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG. Evaluating
-epidemic forecasts in an interval format. PLoS Comput Biol. 2021;17:
-e1008618.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1008618}{10.1371/journal.pcbi.1008618}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Gneiting T, Raftery AE. Strictly proper scoring rules,
-prediction, and estimation. Journal of the American Statistical
-Association. 2007;102: 359--378.
-doi:\href{https://doi.org/10.1198/016214506000001437}{10.1198/016214506000001437}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Scoringutils:
-Utilities for scoring and assessing predictions. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618017}{10.5281/zenodo.4618017}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-deutschewelleCoronavirusGermanyImpose2020}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Deutsche Welle. Coronavirus: {Germany} to impose
-one-month partial lockdown \textbar{} {DW} \textbar{} 28.10.2020. 2020
-{[}cited 29 Jun 2021{]}. Available:
-\url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Ganyani T, Kremer C, Chen D, Torneri A, Faes C, Wallinga
-J, et al. Estimating the generation interval for coronavirus disease
-(COVID-19) based on symptom onset data, march 2020. Eurosurveillance.
-2020;25. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith
-HR, et al. The incubation period of coronavirus disease 2019 (COVID-19)
-from publicly reported confirmed cases: Estimation and application.
-Annals of Internal Medicine. 2020;172: 577--582. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J,
-Munday J, et al. Covidregionaldata: Subnational data for the covid-19
-outbreak. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957539}{10.5281/zenodo.3957539}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Evaluating the use of the reproduction number as an
-epidemiological tool, using spatio-temporal trends of the {Covid-19}
-outbreak in {England} \textbar{} {medRxiv}. {[}cited 30 May 2021{]}.
-Available:
-\url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Riutort-Mayol G, Bürkner P-C, Andersen MR, Solin A,
-Vehtari A. Practical hilbert space approximate bayesian gaussian
-processes for probabilistic programming. 2020. Available:
-\url{https://arxiv.org/abs/2004.11408}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Scott JA, Gandy A, Mishra S, Unwin J, Flaxman S, Bhatt
-S. Epidemia: Modeling of epidemics using hierarchical bayesian models.
-2020. Available:
-\url{https://imperialcollegelondon.github.io/epidemia/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bhattSemiMechanisticBayesianModeling}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Bhatt S, Ferguson N, Flaxman S, Gandy A, Mishra S, Scott
-JA. Semi-{Mechanistic Bayesian} modeling of {COVID-19} with {Renewal
-Processes}. : 14. }
+Xu, Bo, Bernardo Gutierrez, Sarah Hill, Samuel Scarpino, Alyssa Loskill, Jessie Wu, Kara Sewalk, et al.
+2020.
+{``Epidemiological Data from the nCoV-2019 Outbreak: Early Descriptions from Publicly Available Data.''} \url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}.
 
@@
 
-\nolinenumbers
-
 \end{document}

### 2023-12-11 manuscript/final submission/Supplementary/S10-Table.tex

--- 2022-06-02 manuscript/manuscript.tex
@@
-% Template for PLoS
-% Version 3.5 March 2018
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
 %
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended
-% to minimize problems and delays during our production
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% Once your paper is accepted for publication,
-% PLEASE REMOVE ALL TRACKED CHANGES in this file
-% and leave only the final text of your manuscript.
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file.
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig" instead of "Figure".
-% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-%
-% Do not include text that is not math in the math environment.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column.
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
-
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\documentclass[
+]{article}
 \usepackage{amsmath,amssymb}
-
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8x]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% cite package, to clean up citations in the main text. Do not remove.
-% \usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% color can be used to apply background shading to table cells only
-\usepackage[table]{xcolor}
-
-% array package and thick rules for tables
-\usepackage{array}
-
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-
-% create \thickcline for thick horizontal lines of variable length
-\newlength\savedwidth
-\newcommand\thickcline[1]{%
-  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-  \cline{#1}%
-  \noalign{\vskip\arrayrulewidth}%
-  \noalign{\global\arrayrulewidth\savedwidth}%
-}
-
-% \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-\hline
-\noalign{\global\arrayrulewidth\savedwidth}}
-
-% Remove comment for double spacing
-%\usepackage{setspace}
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-\renewcommand{\figurename}{Fig}
-
-% Use the PLoS provided BiBTeX style
-% \bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
 \makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
 \makeatother
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr,graphicx}
-\usepackage{epstopdf}
-%\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-%\setlength{\headheight}{27.023pt}
-%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\headrulewidth}{0pt}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\today}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-% tightlist command for lists without linebreak
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage[margin=1in]{geometry}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% Pandoc citation processing
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-% for Pandoc 2.8 to 2.10.1
-\newenvironment{cslreferences}%
-  {}%
-  {\par}
-% For Pandoc 2.11+
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\usepackage{lineno}
-\usepackage[T1]{fontenc}
-\linenumbers
-\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-\usepackage{caption}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 \usepackage{booktabs}
@@
 \usepackage{xcolor}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 
-\usepackage{forarray}
-\usepackage{xstring}
-\newcommand{\getIndex}[2]{
-  \ForEach{,}{\IfEq{#1}{\thislevelitem}{\number\thislevelcount\ExitForEach}{}}{#2}
-}
-
-\setcounter{secnumdepth}{0}
-
-\newcommand{\getAff}[1]{
-  \getIndex{#1}{London School of Hygiene \& Tropical Medicine,Karlsruhe
-Institute of Technology Institute of Economic Theory and Statistics,Max
-Planck Institute for Multidisciplinary Sciences,UK Health Security
-Agency,Imperial College London}
-}
+\author{}
+\date{\vspace{-2.5em}}
 
 \begin{document}
-\vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{Comparing human and model-based forecasts of COVID-19 in
-Germany and
-Poland} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Nikos I. Bosse\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\textsuperscript{*},
-Sam Abbott\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Johannes Bracher\textsuperscript{\getAff{Karlsruhe Institute of
-Technology Institute of Economic Theory and Statistics}},
-Habakuk Hain\textsuperscript{\getAff{Max Planck Institute for
-Multidisciplinary Sciences}},
-Billy J. Quilty\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Mark Jit\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Edwin van Leeuwen\textsuperscript{\getAff{UK Health Security
-Agency}, \getAff{London School of Hygiene \& Tropical Medicine}},
-Anne Cori\textsuperscript{\getAff{Imperial College London}},
-Sebastian Funk\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\\
-\bigskip
-\textbf{\getAff{London School of Hygiene \& Tropical Medicine}}London
-School of Hygiene \& Tropical Medicine, Keppel Street, London WC1E7HT,
-United Kingdom\\
-\textbf{\getAff{Karlsruhe Institute of Technology Institute of Economic
-Theory and Statistics}}Karlsruhe Institute of Technology - Institute of
-Economic Theory and Statistics, Post Box 6980, 76049 Karlsruhe,
-Germany\\
-\textbf{\getAff{Max Planck Institute for Multidisciplinary Sciences}}Max
-Planck Institute for Multidisciplinary Sciences, Am Faßberg 11, 37077
-Göttingen, Germany\\
-\textbf{\getAff{UK Health Security Agency}}UK Health Security Agency,
-London NW9 5EQ, United Kingdom\\
-\textbf{\getAff{Imperial College London}}Imperial College London,
-Norfolk Place, London W2 1PG, United Kingdom\\
-\bigskip
-* Corresponding author: nikos.bosse@lshtm.ac.uk\\
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-Forecasts based on epidemiological modelling have played an important
-role in shaping public policy throughout the COVID-19 pandemic. This
-modelling combines knowledge about infectious disease dynamics with the
-subjective opinion of the researcher who develops and refines the model
-and often also adjusts model outputs. Developing a forecast model is
-difficult, resource- and time-consuming. It is therefore worth asking
-what modelling is able to add beyond the subjective opinion of the
-researcher alone. To investigate this, we analysed different real-time
-forecasts of cases of and deaths from COVID-19 in Germany and Poland
-over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
-We compared crowd forecasts elicited from researchers and volunteers,
-against a) forecasts from two semi-mechanistic models based on common
-epidemiological assumptions and b) the ensemble of all other models
-submitted to the Forecast Hub. We found crowd forecasts, despite being
-overconfident, to outperform all other methods across all forecast
-horizons when forecasting cases (weighted interval score relative to the
-Hub ensemble 2 weeks ahead: 0.89). Forecasts based on computational
-models performed comparably better when predicting deaths (rel. WIS
-1.26), suggesting that epidemiological modelling and human judgement can
-complement each other in important ways.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step.
-% Author Summary not valid for PLOS ONE submissions.
-\section*{Author summary}
-Mathematical models of COVID-19 have played a key role in informing
-governments across the world. While mathematical models are informed by
-our knowledge of infectious disease dynamics, they are ultimately
-developed and iteratively adjusted by the researchers and shaped by
-their subjective opinions. To investigate what modelling is able to add
-beyond the subjective opinion of the researcher alone, we compared human
-forecasts with model-based predictions of COVID-19 cases and deaths
-submitted to the so-called German/Polish Forecast Hub (which collates a
-variety of models from a range of teams). \textbar{} We found that our
-human forecasts consistently outperformed an aggregate of all available
-model-based forecasts when predicting cases, but not when predicting
-deaths. Our findings suggest that human insight may be most valuable
-when forecasting highly uncertain quantities, which depend on many
-factors that are hard to model using equations, while mathematical
-models may be most useful in settings like predicting deaths, where
-leading indicators with a clear connection to the target variable are
-available. This potentially has very relevant policy implications, as
-agencies informing policy-makers could benefit from routinely eliciting
-human forecasts in addition to model-based predictions to inform
-policies.
-
-\linenumbers
-
-% Use "Eq" instead of "Equation" for equation citations.
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Infectious disease modelling has a long tradition and has helped inform
-public health decisions both through scenario modelling, as well as
-actual forecasts of (among others) influenza {[}e.g. 1,2--4{]}, dengue
-fever {[}e.g. 5,6,7{]}, ebola {[}e.g. 8,9{]}, chikungunya {[}e.g.
-10,11{]} and now COVID-19 {[}e.g. 12,13--17{]}. Applications of
-epidemiological models differ in the way they make statements about the
-future. Forecasts aim to predict the future as it will occur, while
-scenario modelling and projections aim to represent what the future
-could look like under certain scenario assumptions or if conditions
-stayed the same as they were in the past. Forecasts can be judged by
-comparing them against observed data. Since it is much harder to fairly
-assess the accuracy and usefulness of projections and scenario modelling
-in the same way, this work focuses on forecasts, which represent only a
-subset of all epidemiological modelling.
-
-Since March 2020, forecasts of COVID-19 from multiple teams have been
-collected, aggregated and compared by Forecast Hubs such as the US
-Forecast Hub {[}13,14{]}, the German and Polish Forecast Hub {[}15,16{]}
-and the European Forecast Hub {[}17{]}. Often, different individual
-forecasts are combined into a single forecast, e.g.~by taking the mean
-or median of all forecasts. These ensemble forecasts usually tend to
-perform better and more consistently than individual forecasts (see e.g.
-{[}6{]}; {[}18{]}).
-
-Individual computational models usually rely to varying degrees on
-mechanistic assumptions about infectious disease dynamics (such as
-SIR-type compartmental models that aim to represent how individuals move
-from being susceptible to infected and then recovered or dead). Some are
-more statistical in nature (such as time series models that detect
-statistical patterns without explicitly modelling disease dynamics). How
-exactly such a mathematical or computational model is constructed and
-which assumptions are made depends on subjective opinion and judgement
-of the researcher who develops and refines the model. Models are
-commonly adjusted and improved based on whether the model output looks
-plausible to the researchers involved.
-
-The process of model construction and refinement is laborious and
-time-consuming, and it is therefore worth asking what modelling can add
-beyond the subjective judgment of the researcher alone. In this work, we
-ask this question specifically in the context of predictive performance,
-and set aside other advantages of epidemiological modelling (such as
-reproducibility or the ability to obtain a deeper fundamental
-understanding of how diseases spread). One natural way to do this is to
-compare the predictive performance of forecasts based on computational
-models (``model-based forecasts'') against forecasts made by individual
-humans without explicit use of a computer model (``direct human
-forecasts'') or a combination of multiple such forecasts (``crowd
-forecasts'').
-
-Previous work has examined such direct human forecasts in various
-contexts, such as geopolitics {[}19,20{]}, meta-science {[}21,22{]},
-sports {[}23{]} and epidemiology {[}11,24,25{]}. Several prediction
-platforms {[}26--28{]} and prediction markets {[}29{]} have been created
-to collate expert and non-expert predictions. However, with the notable
-exception of {[}11{]}, these forecasts were not designed to be evaluated
-alongside model-based forecasts and usually follow their own (often
-binary) prediction formats. Direct human forecasts may be able to take
-into account insights and relationships between variables which are hard
-to specify using epidemiological models. However, it is not entirely
-clear in which situations human forecasts perform well or badly. For
-example, {[}11{]} found that humans could outperform computer models at
-predicting the 2014/15 and 2015/16 flu season in the US, a setting where
-the disease was well known and information about previous seasons was
-available. However, humans tended to do slightly worse at predicting the
-2014/15 outbreak of chikungunya in the Americas, a disease previously
-largely unobserved and unknown in these regions at the time.
-
-In this study, we analyse the performance of direct human forecasts
-relative to model-based forecasts and discuss the added benefit of
-epidemiological modelling over human judgement alone. As a case study,
-we use different forecasts, involving varying degrees of human
-intervention, which we submitted in real time to the German and Polish
-Forecast Hub. In contrast to {[}11{]} we elicited not only point
-predictions, but full predictive distributions (``probabilistic
-forecasts'', see e.g. {[}30{]}) from participants. This allows us to
-compare not only predictive accuracy, but also how well human
-forecasters and model-based forecasts were able to quantify forecast
-uncertainty.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-We created and submitted the following forecasts to the German and
-Polish Forecast Hub: 1) a direct human forecast (henceforth called
-``crowd forecast''), elicited from participants through a web
-application {[}31{]} and 2) two semi-mechanistic model-based forecasts
-(``renewal model'' and ``convolution model'') informed by basic
-assumptions about COVID-19 epidemiology. While the two semi-mechanistic
-forecasts were necessarily shaped by our implicit assumptions and
-decisions, they were designed such as to minimise the amount of human
-intervention involved. For example, we refrained from adjusting model
-outputs or refining the models based on past performance. Forecasts were
-created in real time over a period of 21 weeks from October 12th 2020
-until March 1st 2021 and submitted to the German and Polish Forecast hub
-{[}15,16{]}. All code and tools necessary to generate the forecasts and
-make a forecast submission are available in the
-\texttt{covid.german.forecasts} R package {[}32{]}. This repository also
-contains a record of all forecasts submitted to the German and Polish
-Forecast Hub. Forecasts were evaluated using a variety of scoring
-metrics and compared among each other and against an ensemble of all
-other models submitted to the German and Polish Forecast Hub.
-
-\hypertarget{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}{%
-\subsection{Forecast targets and interaction with the German and Polish
-Forecast
-Hub}\label{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}}
-
-The German and Polish Forecast Hub (now mostly merged into the {[}17{]})
-elicits predictions for various COVID-19 related forecast targets from
-different research groups every week. Forecasts had to be made every
-Monday (with submissions allowed until Tuesday 3pm) and were permitted
-to use any data that was available by Monday 11.59pm. We submitted
-forecasts for incident and cumulative weekly reported numbers of cases
-of and deaths from COVID-19 on a national level in Germany and Poland
-over a one to four week forecast horizon. Forecasts were submitted on
-Mondays, but weeks were defined as ending on a Saturday (and starting on
-Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26
-days. Submissions were required in a quantile-based format with 23
-quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10,
-0.15, \ldots, 0.95, 0.975, 0.99. Forecasts submitted to the Forecast Hub
-were combined into different ensembles every week, with the median
-ensemble (i.e., the \(\alpha\)-quantile of the ensemble is given by the
-median of all submitted \(\alpha\)-quantiles) being the default ensemble
-shown on all official Forecast hub visualisations
-(https://kitmetricslab.github.io/forecasthub/forecast).
-
-Data on daily reported test positive cases and deaths linked to COVID-19
-were provided by the organisers of the German and Polish Forecast hub.
-Until December 14th, 2020, these data were sourced from the European
-Centre for Disease Control {[}33{]}. After ECDC stopped publishing daily
-data, observations were sourced from the Robert Koch Institute (RKI) and
-the Polish Ministry of Health for the remainder of the submission period
-{[}34{]}. These data are subject to reporting artefacts, (such as for
-example delayed case reporting in Poland on the 24th November,
-{[}35{]}), changes in reporting over time, and variation in testing
-regimes (for example in Germany from the 11th of November on, {[}36{]}).
-The ECDC data as well as the data published by the Polish Ministry of
-Health were also subject to data revisions, although most of them (with
-a notable exception of a data update for October 12 2020 in Germany)
-only affected daily, not weekly data (see Figures
-\ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).
-
-\hypertarget{crowd-forecasts}{%
-\subsection{Crowd forecasts}\label{crowd-forecasts}}
-
-Our crowd forecasts were created as an ensemble of forecasts made by
-individual participants every week through a web application
-(https://cmmid-lshtm.shinyapps.io/crowd-forecast/). Weekly forecasts had
-to be submitted before Tuesday 12pm every week, but participants were
-asked to only use any information or data that was already available by
-Monday night. The application was built using the \texttt{shiny} and
-\texttt{golem} R packages {[}37,38{]} and is available in the
-\texttt{crowdforecastr} R package {[}31{]}. To make a forecast in the
-application participants could select a predictive distribution (with
-the default being log-normal) to represent the probability that the
-forecasted quantity took certain values. Median and width of the
-uncertainty could be adjusted by either interacting with a figure
-showing their forecast or providing numerical values (see screenshot in
-Figure \ref{fig:screenshot} in the SI). The default shown was a
-repetition of the last known observation with constant uncertainty
-around it computed as the standard deviation of the last four changes in
-weekly log observed forecasts (i.e.~as
-\(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
-A comparison of the crowd forecasts against the default baseline shown
-in the application is displayed in Figure \ref{fig:compare-forecasters}
-in the Appendix. Our interface also allowed participants to view past
-observations based on the hub data, as well as their forecasts, on a
-logarithmic scale and presented additional contextual COVID-19 data
-sourced from {[}39{]}. These data included, for example, notifications
-of both test positive COVID-19 cases and COVID-19 linked deaths and the
-number of COVID-19 tests conducted over time. From November 26 2020 on
-we displayed weekly small reports with a visualisation of past forecasts
-and scores on our website, epiforecasts.io.
-
-Forecasts were stored in a Google Sheet and downloaded, cleaned and
-processed every week for submission to the Forecast Hub. If a forecaster
-had submitted multiple predictions for a single target, only the latest
-submission was kept. Information on the chosen distribution as well as
-the parameters for median and width were used to obtain the required set
-of 23 quantiles from that distribution. Forecasts from all forecasters
-were then aggregated using an unweighted quantile-wise mean (i.e., the
-\(\alpha\)-quantile of the ensemble is given by the mean of all
-submitted \(\alpha\)-quantiles). To avoid issues with users trying out
-the app and submitting a random forecast, we required that a forecaster
-needed to make a forecast for at least two targets for a given forecast
-in order to be included in the crowd forecast ensemble. On a few
-occasions we deleted forecasts that were clearly the result of a user or
-software error (such as for example forecasts that were zero
-everywhere).
-
-individual forecasts were assessed as clearly erroneous by visual
-inspection and subsequently removed before aggregation and were excluded
-from the submission as well as the analysis.
-
-Participants were recruited mostly within the Centre of Mathematical
-Modeling of Infectious Diseases at the London School of Hygiene \&
-Tropical Medicine, but participants were also invited personally or via
-social media to submit predictions. Depending on whether they had a
-background in either statistics, forecasting or epidemiology,
-participants were asked to self-identify as `experts' or `non-experts'.
-
-The study was approved by the Observational / Interventions Research
-Ethics Committee at the London School of Hygiene \& Tropical Medicine,
-LSHTM Ethics Reference: 22290. Formal consent from participants was
-taken in written form through the web application.
-
-\hypertarget{model-based-forecasts}{%
-\subsection{Model-based forecasts}\label{model-based-forecasts}}
-
-We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R
-package (version 1.3.3) as our model-based forecasts {[}40{]}. The first
-of these models, here called ``renewal model'', used the renewal
-equation {[}41{]} to predict reported cases and deaths (see details in
-the SI). It estimated the effective reproduction number \(R_t\) (the
-average number of people each person infected at time t is expected to
-infect in turn) and modelled future infections as a weighted sum of past
-infection multiplied by \(R_t\). \(R_t\) was assumed to stay constant
-beyond the forecast date, roughly corresponding to continuing the latest
-exponential trend in infections. On the 9th of November we altered the
-date when \(R_t\) was assumed to be constant from two weeks prior to the
-date of the forecast to the forecast date, which we found to yield a
-more stable \(R_t\) estimate. Reported case and death notifications were
-obtained by convolving predicted infections over data-based delay
-distributions {[}40,42--44{]} to model the time between infection and
-report date. The renewal model was used to predict cases as well as
-deaths with forecasts being generated for each target separately. Death
-forecasts from the renewal model were therefore not informed by past
-cases. One submission of the renewal model on December 28th 2020 was
-delayed and therefore not included in the official Forecast hub
-ensemble.
-
-The second model (``convolution model'', see details in SI) was only
-used to forecast deaths and was added later, starting December 7th 2020
-(with the first forecast from December 7th suffering from a software bug
-and therefore disregarded in all further analyses). The convolution
-model was submitted, but never included in the official Forecast hub
-ensemble due to concerns that it could be too similar to the renewal
-model. The convolution model predicted deaths as a fraction of infected
-people who would die with some delay, by using a convolution of reported
-cases with a distribution that described the delay from case report to
-death and a scaling factor (the case-fatality ratio). Both the renewal
-and the convolution model used daily observations and assumed a negative
-binomial observation model with a multiplicative day-of-the-week effect
-{[}40{]}.
-
-Line list data used to inform the prior for the delay from symptom onset
-to test positive case report or death in the model-based forecasts was
-sourced from {[}45{]} with data available up to the 1st of August. All
-model fitting was done using Markov-chain Monte Carlo (MCMC) in stan
-{[}46{]} with each location and forecast target being fitted separately.
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-For the main analysis we focused mostly on two week ahead forecasts, as
-COVID-19 forecasts, especially for cases, were in the past found to have
-poor predictive performance beyond this horizon {[}15{]}. Forecasts for
-cases were scored using the full period from October 2020 until March
-2021. To ensure comparability between models, all death forecasts were
-scored using only the period from December 14th on, where all models
-including the convolution model were available. To ensure robustness of
-our results we conducted a sensitivity analysis where all forecasts
-(including cases) were scored only over the later period for which all
-forecasts were available (see Section \ref{sensitivity-analysis} in the
-SI). Results remained broadly unchanged.
-
-Forecasts were analysed using the following scoring metrics: The
-weighted interval score (WIS) {[}47{]}, the absolute error, relative
-bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule {[}48{]}, meaning that in expectation
-the score is optimised by reporting a predictive distribution that is
-identical to the true data-generating distribution. Forecasters are
-therefore incentivised to report their true belief about the future. The
-WIS can be understood as a generalisation of the absolute error to
-quantile-based forecasts (also meaning that smaller values are better)
-and can be decomposed into three separate penalties: forecast spread
-(i.e.~uncertainty of forecasts), over-prediction and under-prediction.
-While the over- and under-prediction components of the WIS capture the
-amount of over-prediction and under-prediction in absolute terms, we
-also look at a relative tendency to make biased forecasts. The bias
-metric {[}9{]} we use captures how much probability mass of the forecast
-was above or below the true value (mapped to values between -1 and 1)
-and therefore represents a general tendency to over- or under-predict in
-relative terms. A value of -1 implies that all quantiles of the
-predictive distribution are below the observed value and a value of 1
-that all quantiles are above the observed value. Empirical coverage is
-the percentage of observed values that fall inside a given prediction
-interval (e.g.~how many observed values fall inside all 50\% prediction
-intervals). Scoring metrics are explained in more detail in Table
-\ref{tab:scoring-metrics} in the SI. All scores were calculated using
-the \texttt{scoringutils} R package {[}49{]}.
-
-At all stages of the evaluation our forecasts were compared to the
-median ensemble of all \emph{other} models submitted to the German and
-Polish Forecast Hub (``Hub ensemble''). This ``Hub ensemble'' was
-retrospectively computed and excludes all our models, leaving on average
-five ensemble member models (see details in Section
-\ref{contributions-hub}, as well as in Table
-\ref{tab:table-ensemble-versions} and Figure
-\ref{fig:num-ensemble-members} in the SI). What we call ``Hub ensemble''
-in this article therefore differs from the ``official Hub ensemble''
-(here called ``hub-ensemble-realised'') which included crowd forecasts
-as well as renewal model forecasts. To enhance interpretability of
-scores we mainly report WIS relative to the Hub ensemble in the main
-text, i.e.~we divided the average scores for a given model by the
-average score achieved by the Hub ensemble on the same set of forecasts
-(with values \textgreater1 implying worse and values \textless1 implying
-better performance than the Hub ensemble). In addition to comparing our
-forecasts against the hub ensemble excluding our models, we also
-assessed the impact of our forecasts on the performance of the
-forecasting hub by recalculating separate versions of the Hub ensemble
-with only some (or all) of our forecasts included. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{crowd-forecast-participation}{%
-\subsection{Crowd forecast
-participation}\label{crowd-forecast-participation}}
-
-A total number of 32 participants submitted forecasts, 17 of those
-self-identified as `expert' in either forecasting or epidemiology. The
-median number of forecasters for any given forecast target was 6, the
-minimum 2 and the maximum 10. The mean number of submissions from an
-individual forecaster was 4.7 but the median number was only one - most
-participants dropped out after their first submission. Only two
-participants submitted a forecast every single week, both of whom are
-authors on this study.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} \caption{Two week ahead forecasts and corresponding scores.
-A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth}
-\end{figure}
-
-\hypertarget{case-forecasts}{%
-\subsection{Case Forecasts}\label{case-forecasts}}
-
-For cases, crowd forecasts had a lower mean weighted interval score
-(WIS, lower values indicate better performance) than both the renewal
-model and the Hub ensemble across all forecast horizons (Figure
-\ref{fig:agg-performance-all}A) and locations (Figure
-\ref{fig:performance-locations-rel}A). For two week ahead forecasts,
-mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts
-and 1.40 for the renewal model (Table \ref{tab:score-table-2}). Across
-all forecasting approaches, locations and forecast horizons, the
-distribution of WIS values was very right-skewed, and average
-performance was heavily influenced by outliers (Figure
-\ref{fig:distribution-scores}). Overall, low variance in forecast
-performance was closely linked with good mean performance (Figures
-\ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A),
-suggesting that the ability to avoid large errors was an important
-factor in determining overall performance. The impact of outlier values
-was especially pronounced for the renewal model, which had more outliers
-(Figure \ref{fig:distribution-scores}), as well as the highest standard
-deviation of WIS values (standard deviation of the WIS relative to the
-WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon),
-while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub
-ensemble (= 1) showed more stable performance.
-
-To varying degrees, all forecasts exhibited trend-following behaviour
-and were rarely able to predict a change in trend before it had
-happened. For example, all forecasts failed to predict the change in
-trend from increase to decrease that happened in November in Germany and
-severely overshot reported cases (Figure
-\ref{fig:forecasts-and-truth}A). This was most striking for the renewal
-model, which extrapolated unconstrained exponential growth based on the
-recent past of observations. The Hub ensemble and the crowd forecast,
-which had both been under-predicting throughout October, also failed to
-predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on
-November 2nd 2020 {[}50{]} and the change in the testing regime (with
-stricter test criteria) on November 11th 2020 {[}36{]}, were fastest to
-adapt to the new trend, and the Hub ensemble slowest. In December, cases
-rose again in Germany, with all models under-predicting this growth to
-varying extents. As in October, the renewal model captured the phase of
-exponential growth in cases slightly better than other approaches, but
-again overshot when reported case numbers fell over Christmas. The large
-variance in predictions in January in Germany (severe under-prediction
-followed by severe over-prediction) may in part be caused by the fact
-that the renewal model operated on daily data and therefore was
-susceptible to fluctuations in daily reporting around Christmas that
-would not have influenced on weekly reporting. Similar trends in
-performance were evident in Poland, with the crowd forecast quickest at
-adapting to the change in trend in November. In general, there were
-fewer large outlier forecasts in Poland and in particular the renewal
-model performed more in line with other forecasts there.
-
-All forecasting approaches, including the Hub ensemble, were
-overconfident, i.e.~they showed lower than nominal coverage (meaning
-that 50\% (90\%) prediction intervals generally covered less than 50\%
-(90\%) of the actually observed values) (Figure
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
-Coverage for all forecasts deteriorated with increasing forecast
-horizon, indicating that all forecasting approaches struggled to
-quantify uncertainty appropriately for case forecasts. This was
-especially an issue for crowd forecasts, which had markedly shorter
-prediction intervals (i.e., narrower and more confident predictive
-distributions) than other approaches (Figure
-\ref{fig:agg-performance-all}E) and only showed a small increase in
-uncertainty across forecast horizons. The crowd forecasts prediction
-intervals were also noticeably narrower than the default baseline shown
-to forecasters in the application (see Figure
-\ref{fig:compare-forecasters}).
-
-In spite of good performance in terms of the absolute error (Figure
-\ref{fig:agg-performance-all}G), the narrow forecast intervals led to
-forecasts which were severely overconfident (covering only 36\% and 55\%
-of all observations with the 50\% and 90\% prediction intervals of all
-forecasts made at a two week forecast horizon, and only 5\% and 38\%
-four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables
-\ref{tab:score-table-2} and \ref{tab:score-table-4}). Despite worse
-performance in terms of absolute error (Figure
-\ref{fig:agg-performance-all}G), the renewal model achieved better
-calibration (comparable to the Hub ensemble), as uncertainty increased
-rapidly across forecast horizons. The crowd forecasts, on the other
-hand, showed a smaller bias than the renewal model, but were
-overconfident.
-
-The renewal model exhibited a noticeable tendency towards
-over-predicting reported cases across all horizons. The crowd forecast
-tended to over-predict at longer forecast horizons, whereas the Hub
-ensemble showed no systematic bias (Figure
-\ref{fig:agg-performance-all}F). Regardless of a general relative
-tendency to over-predict, all forecasting approaches incurred larger
-absolute penalties from over- than from under-prediction (see
-decomposition of the WIS into absolute penalties for over-prediction,
-under-prediction and dispersion in Figures
-\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
-
-Generally, trends in overall performance were broadly similar across
-locations (Figures \ref{fig:performance-locations} and
-\ref{fig:performance-locations-rel}). Due to the differing population
-sizes and numbers of notifications in Germany and Poland absolute scores
-were difficult to compare directly. However, relative to the Hub
-ensemble, the crowd forecasts performed noticeably better in Germany
-than in Poland and the renewal model better in Poland than in Germany
-(Figures \ref{fig:performance-locations-rel}A,
-\ref{fig:performance-locations-rel}G,
-\ref{fig:agg-performance-all-Germany},
-\ref{fig:agg-performance-all-Poland}).
-
-\hypertarget{death-forecasts}{%
-\subsection{Death Forecasts}\label{death-forecasts}}
-
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as
-our model-based approaches across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B). Relative WIS values for the models
-two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1
-(Hub ensemble) and 1.79 (renewal model). The crowd forecasts performed
-better than the renewal model across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B), and also better than the convolution
-model three and four weeks ahead. Poor performance of the renewal model,
-especially at longer horizons, indicates that an approach that does not
-know about past cases, but instead estimates and projects a separate
-\(R_t\) trace from deaths, does not use the available information
-efficiently. The convolution model was able to outperform both the
-renewal model and the crowd forecasts at shorter forecast horizons
-(where the delay between cases and deaths means that future deaths are
-largely informed by present cases), but saw performance deteriorate at
-three and four weeks ahead (where case predictions from the renewal
-model were increasingly used to inform death predictions) (Figure
-\ref{fig:agg-performance-all}B, Table \ref{tab:score-table-4}).
-
-As past cases and hospitalisations can be used as predictors, predicting
-a change in trend may be easier for deaths than for cases. Even though
-all forecasts generally struggled with this, there were some instances
-where changing trends were well captured or even anticipated. In Poland,
-for example, the Hub ensemble was able to capture or even anticipate the
-peak in deaths in December quite well (whereas the renewal model and
-crowd forecast did not). The renewal model, which mostly exhibited
-trend-following behaviour, correctly predicted another increase in
-weekly deaths in mid-January (potentially based on changes in daily
-deaths, as the renewal model did not know about past cases). In Germany
-in early January, all models predicted a decrease in deaths two to three
-weeks before it actually happened. Predictions from the renewal model at
-that time were likely strongly influenced by an unexpected drop in
-reported deaths in December. The other forecasting approaches and in
-particular, the convolution model may have been affected by potentially
-under-reported case numbers around Christmas. When the decrease that all
-models had predicted to happen in early January failed to materialise,
-the renewal model and the crowd forecast noticeably over-corrected and
-over-predicted deaths in the following weeks, while the Hub ensemble,
-and to a slightly lesser degree, the convolution model were able to
-capture the downturn well when it finally happened at the end of
-January.
-
-Death forecasts, generally, showed greater coverage of the 50\% and 90\%
-prediction intervals than case forecasts and no decrease in coverage
-across forecast horizons, indicating that it might be easier to
-appropriately quantify uncertainty for death forecasts. The Hub ensemble
-had the greatest coverage, with empirical coverage of the 50\% and 90\%
-prediction intervals exceeding 50\%, and 90\%, respectively, across all
-forecast horizons. Coverage for the crowd forecasts and our model-based
-approaches was generally lower than that of the Hub ensemble and mostly
-slightly lower than nominal coverage (Figure
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D). As
-for cases, the crowd forecast tended to have the narrowest prediction
-intervals and uncertainty increased most slowly across forecast
-horizons, and the renewal model forecasts generally were widest. The
-convolution model had relatively narrow prediction intervals for short
-forecast horizons, but had rapidly (and non-linearly) increasing
-uncertainty for longer forecast horizons, driven by increasing
-uncertainty in the underlying case forecasts.
-
-For deaths, the ensemble of crowd forecasts had a consistent tendency to
-over-predict \ref{fig:agg-performance-all}F. The convolution model had a
-strong tendency to under-predict, with the magnitude of under-prediction
-steadily decreasing for longer forecast horizons. The renewal model
-(which over-predicted for cases) and the Hub ensemble slightly tended
-towards under-prediction. For deaths, absolute over- and
-under-prediction penalties were more in line with a general relative
-tendency to over- or under-predict than for cases (Figure
-\ref{fig:agg-performance-all}A, \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2}, \ref{tab:score-table-4}).
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} \caption{Distribution of scores.
-A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
-Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores.}\label{fig:distribution-scores}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.
-“Hub-ensemble”    extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-rel}
-\end{figure}
-
-\hypertarget{contributions-hub}{%
-\subsection{Contribution to the Forecast Hub}\label{contributions-hub}}
-
-Of our three models, only the renewal model and the crowd forecast were
-included in the official Forecast Hub median ensemble
-(``hub-ensemble-realised''), while the convolution model was never
-included as it was deemed too similar to the existing renewal model. In
-the official Hub ensemble, there were on average 7.1 models included
-(including our own), with a median of 7, a minimum of 4 (on 28 December
-2020 over the Christmas period) and a maximum of 10. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively. An
-overview of all models and ensemble versions is shown in Table
-\ref{tab:table-ensemble-versions} in the SI.
-
-For cases, our contributions (compared to the Hub ensemble without our
-contributions) consistently improved performance across all forecasting
-horizons (rel. WIS 0.9 two weeks ahead, Table
-\ref{tab:score-table-ensemble-2}). Contributions from the crowd
-forecasts alone also improved performance of the Hub ensemble across all
-forecast horizons, while contributions from the renewal model had a
-negative effect for longer horizons (rel. WIS 1.02 three weeks ahead,
-1.06 four weeks ahead). The realised ensemble including both models
-performed better or equal compared to all versions with only one model
-included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model
-have improved performance (Table \ref{tab:score-table-ensemble-4}). The
-realised ensemble performed comparably to the crowd forecasts for
-predictions one to two weeks ahead, and worse for greater forecast
-horizons.
-
-For deaths, contributions from the renewal model and crowd forecast
-together improved performance only for one week ahead predictions and
-showed an increasingly negative impact on performance for longer
-horizons (rel. WIS of the Hub-ensemble-realised 1.01 two weeks ahead,
-1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and
-\ref{tab:score-table-ensemble-4}). Individual contributions from both
-the renewal model and the crowd forecast were largely negative, while a
-version of the Hub ensemble with only the convolution model included
-would have performed consistently better across all forecast horizons
-(with the positive impact increasing for longer horizons). This is
-especially interesting as the convolution model performed consistently
-worse than the pre-existing Hub ensemble (Figure
-\ref{fig:agg-performance-all}) and especially worse for longer horizons.
-
-We also considered the impact of our contributions on a version of the
-Hub ensemble constructed by taking the quantile-wise mean, rather than
-the median. General trends were similar, with the notable exception of
-the convolution model, which had a consistently positive impact on the
-median ensemble, but a mixed and mostly slightly negative impact on the
-mean ensemble (Figures \ref{fig:agg-performance-ensemble-rel}B and
-\ref{fig:agg-performance-ensemble-mean}B). This may happen if a model is
-more correct directionally relative to the pre-existing ensemble, but
-overshoots in absolute terms, thereby moving the ensemble too far. For
-both the mean and the median ensemble, changes in performance from
-adding or removing models were of a similar order of magnitude,
-suggesting that at least in this instance, with a relatively small
-ensemble size, the median ensemble was not necessarily more `robust' to
-changes than the mean ensemble. However, the ensemble version with all
-our forecasts included (``hub-ensemble-with-all'') tended to perform
-relatively better for the median ensemble than the mean ensemble,
-suggesting that adding more models may be more beneficial or `safer' for
-the median than for the mean ensemble as directional errors can more
-easily cancel out than errors in absolute terms.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Epidemiological forecasting modelling combines knowledge about
-infectious disease dynamics with the subjective opinion of the
-researcher who develops and refines the model. In this study, we
-compared forecasts of cases of and deaths from COVID-19 in Germany and
-Poland based purely on human judgement and elicited from a crowd of
-researchers and volunteers against forecasts from two semi-mechanistic
-epidemiological models. In spite of the small number of participants and
-a general tendency to be overconfident, crowd forecasts consistently
-outperformed our epidemiological models as well as the Hub ensemble when
-forecasting cases but not when forecasting deaths. This suggests that
-humans might be relatively good at foreseeing trends that are hard to
-model but may struggle to form an intuition for the exact relationship
-between cases and deaths.
-
-Past studies have evaluated the performance of model-based forecasting
-approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of
-(expert-tuned) model-based approaches {[}e.g. 12,13,14{]}, or
-exclusively on human forecasts {[}19,20,24,25{]}. In contrast, we
-directly compared human and model-based forecasts. This is similar to
-the approach taken by {[}11{]}, but extends it in several ways. While
-Farrow et al.~only asked for point predictions and constructed a
-predictive distribution from these, we asked participants to provide a
-full predictive distribution, allowing us to compare human forecasts and
-models without any further assumptions, as well as to analyse how humans
-quantified their uncertainty. In addition, we compared crowd forecasts
-to two semi-mechanistic models informed by basic epidemiological
-knowledge of COVID-19, allowing us to assess not only relative
-performance but also to analyse qualitative differences between human
-judgement and model-based insight. In terms of interpretability of the
-results, exact knowledge of our two models, as well as focus on a
-limited set of targets and locations was a major advantage of our study
-compared to larger studies conducted by the Forecast Hubs
-{[}12--15,17{]}.
-
-The strong performance of crowd forecasts in our study is in line with
-results from Farrow et al.~who also report strong performance of human
-predictions in past Flu challenges despite difficulties to recruit a
-large number of participants. The advantage of crowd forecasts we
-observed over our semi-mechanistic models is likely in part explained by
-the fact that we compared an ensemble of crowd forecasts with single
-models. However, this probably explains only part of the difference, and
-performance relative to the Hub ensemble strongly suggests that human
-insight is valuable when forecasting highly volatile and potentially
-hard-to-predict quantities such as case numbers. One potential
-explanation is that humans can have access to data that is not available
-to or hard to integrate into model-based forecasts. Relatively good
-performance of our semi-mechanistic models short-term, but not
-longer-term, suggests that model-based forecasts are helpful to
-extrapolate from current conditions, but require some form of human
-intervention or additional assumptions to inform forecasts when
-conditions change over time. This human intervention may be particularly
-important when dealing with artefacts in reporting and data anomalies
-(and especially when using daily, rather than weekly data). The large
-variance in predictions in January in Germany for example (severe
-under-prediction followed by severe over-prediction, see Figure
-\ref{fig:forecasts-and-truth}A), may in part be caused by the fact that
-the renewal model operated on daily data and therefore was susceptible
-to fluctuations in daily reporting which have less of an influence on
-weekly reporting.
-
-Our results suggest that human intervention may be less beneficial when
-forecasting deaths (especially at shorter horizons, when deaths are
-largely dependent on already observed cases), which benefits from the
-ability to model the delays and exact epidemiological relationships
-between different leading and lagged indicators. Relatively good
-performance of the convolution model, especially compared to the poor
-performance of the renewal model on deaths (which used only deaths to
-estimate and predict the effective reproduction number) underlines the
-importance of including leading indicators such as cases as a predictor
-for deaths.
-
-Given the low number of participants in our study, it is difficult to
-generalise conclusions about crowd predictions to other settings. Using
-R shiny as a platform for the web application arguably created some
-limits to user experience and performance, influencing the number of
-participants and potentially creating a self-selection effect.
-Motivating forecasters to contribute regularly proved challenging,
-especially given that the majority of our participants were from the UK
-and may not have been familiar with all relevant details of the
-situation in Germany and Poland. On the other hand, R shiny facilitated
-quick development and allowed us to provide our crowd forecasting
-tooling as an open source R package, meaning that it is available for
-others to use, for example in settings like early-stage outbreaks where
-model-based forecasts are not available. In light of the relatively
-small number of Hub ensemble models, performance of the Hub ensemble is
-also difficult to generalise. More research is needed to replicate these
-findings and investigate how crowd forecasts compare against the types
-of models and model ensembles policy makers use to inform their
-decisions.
-
-Our work suggests that crowd forecasts and model-based forecasts could
-have different strengths and may be able to complement each other. When
-choosing a suitable approach for a given task it is important to take
-into account how the output will be used. In this work we focused on
-forecasts (which aim to predict future data points whilst accounting for
-all factors that might influence them), whereas policy makers might be
-more interested in projections (which show what would happen in the
-absence of any events that could change the trend) or scenario
-modelling. Forecasts may not be a suitable basis for informing policy
-decisions, if forecasters already have factored in the expectation of a
-future intervention. Model-based approaches can be either forecasts or
-projections depending on the assumptions, whereas eliciting projections
-that are not influenced by implicit assumptions about the future from
-humans may be harder.
-
-Further work should explore the effects of humans refining their
-mathematical models or changing model outputs in more detail.
-Model-based forecasts could be used as an input to human judgement, with
-researchers adjusting predictions generated by models. Seeing a
-model-based forecast could help humans calibrate uncertainty better,
-while allowing for manual intervention to adapt spurious trend
-predictions. Tools need to be developed to facilitate this process at a
-larger scale. Human insight could also be used as an input to models.
-Such a `hybrid' forecasting approach could for example ask humans to
-predict the trend of the effective reproduction number \(R_t\) or the
-doubling rate (i.e.~how the epidemic evolves) into the future and use
-this to estimate the exact number of cases, hospitalisations or deaths
-this would imply. In light of severe overconfidence, yet good
-performance in terms of the absolute error, post-processing of human
-forecasts to adjust and widen prediction intervals may be another
-promising approach. Crowd forecasting in general could benefit greatly
-from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of
-the limited resources available and the small number of participants,
-this seems worthwhile to further develop and explore.
-
-\clearpage
-
-\textbf{Acknowledgements}
-
-NIB received funding from the Health Protection Research Unit (grant
-code NIHR200908, https://www.nihr.ac.uk/). SA's work was funded by the
-Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/). The work
-of JB was supported by the Helmholtz Foundation
-(https://www.helmholtz.de/) via the SIMCARD Information and Data Science
-Pilot Project. This research was partly funded by the National Institute
-for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 \&
-16/136/46) using UK aid from the UK Government to support global health
-research. The views expressed in this publication are those of the
-author(s) and not necessarily those of the NIHR or the UK Department of
-Health and Social Care. BJQ is supported in part by a grant from the
-Bill and Melinda Gates Foundation (OPP1139859,
-https://www.gatesfoundation.org/). EvL acknowledges funding by the
-National Institute for Health Research (NIHR) Health Protection Research
-Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908,
-https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research
-and innovation programme - project EpiPose (101003688,
-https://ec.europa.eu/programmes/horizon2020/). AC acknowledges funding
-by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/),
-and the Academy of Medical Sciences (https://acmedsci.ac.uk/). SF's work
-was supported by the Wellcome Trust (grant: 210758/Z/18/Z,
-https://wellcome.org/), and the NIHR (NIHR200908,
-https://www.nihr.ac.uk/).
-
-We thank all forecasters who participated in this study for their
-contribution.
-
-We would also like to acknowledge (in a randomised order) the members of
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group at the the London School of Hygiene \& Tropical Medicine:
-Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie
-Diamond, Katherine E. Atkins, Rein M G J Houben, Jiayao Lei, Rachel
-Lowe, David Simons, Sophie R Meakin, Nicholas G. Davies, Timothy W
-Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly,
-Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas,
-Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia
-Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson,
-Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang
-Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C
-Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun,
-Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche,
-James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday,
-Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan
-Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R
-Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael
-Pung, Anna M Foss.
-
-\clearpage
-
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
-
-\hypertarget{appendix-supplementary-information}{%
-\section*{(APPENDIX) Supplementary
-information}\label{appendix-supplementary-information}}
-\addcontentsline{toc}{section}{(APPENDIX) Supplementary information}
-
-\hypertarget{supplementary-information}{%
-\section{Supplementary information}\label{supplementary-information}}
-
-\hypertarget{scoring-metrics-used}{%
-\subsection{Scoring metrics used}\label{scoring-metrics-used}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{9.3cm}}
-\caption{\label{tab:scoring-metrics}Overview of the scoring metrics used.}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{Overview of the scoring metrics used. \textit{(continued)}}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-WIS (Weighted) interval score & The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
-It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
-The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction.
-For a single interval, the score is computed as
-  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
-  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e.
-the lower and upper bound of a single prediction interval.
-For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
-  $$WIS = \frac{1}{K + 0.5} \cdot \left( w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y) \right), $$
-  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
-
-\cellcolor{gray!6}{Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.}\\
-\addlinespace \addlinespace
-Interval coverage & Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
-Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
-we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.\\
-\addlinespace \addlinespace
-Bias & (Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict. Values are between -1 and 1 and 0 ideally. For continuous forecasts, bias is given as 
-$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
-where $F$ is the CDF of the predictive distribution and $y$ is the observed value.
-
-For quantile forecasts, $F(y)$ is replaced by a quantile rank.
-The appropriate quantile rank is determined by whether the median forecast is below  or above the true value.
-We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.
-
-\cellcolor{gray!6}{In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
-It is therefore a more robust measurement.}\\*
-\end{longtable}
-
-\clearpage
-
-\hypertarget{the-crowdforecasting-app}{%
-\subsection{The crowdforecasting app}\label{the-crowdforecasting-app}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../crowd-forecast/Screenshot-forecasting-app} \caption{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).
-}\label{fig:screenshot}
-\end{figure}
-
-\clearpage
-
-\hypertarget{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}{%
-\subsection{Text S1. Further details on the semi-mechanistic forecasting
-models}\label{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}}
-
-\hypertarget{renewal-equation-model}{%
-\subsubsection{Renewal equation model}\label{renewal-equation-model}}
-
-The model was initialised prior to the first observed data point by
-assuming constant exponential growth for the mean of assumed delays from
-infection to case report.
-
-\begin{align}
-  I_{t} &= I_0 \exp  \left(r t \right)  \\
-  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
-  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
-\end{align}
-
-Where \(I_{obs}\) and \(r_{obs}\) are estimated from the first week of
-observed data. For the time window of the observed data infections were
-then modelled by weighting previous infections by the generation time
-and scaling by the instantaneous reproduction number. These infections
-were then convolved to cases by date (\(O_t\)) and cases by date of
-report (\(D_t\)) using log-normal delay distributions. This model can be
-defined mathematically as follows,
-
-\begin{align}
-  \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
-  I_t &= R_t \sum_{\tau = 1}^{15} w(\tau | \mu_{w}, \sigma_{w}) I_{t - \tau} \\
-  O_t &= \sum_{\tau = 0}^{15} \xi_{O}(\tau | \mu_{\xi_{O}}, \sigma_{\xi_{O}}) I_{t-\tau} \\
-  D_t &= \alpha \sum_{\tau = 0}^{15} \xi_{D}(\tau | \mu_{\xi_{D}}, \sigma_{\xi_{D}}) O_{t-\tau} \\ 
-  C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
-\end{align}
-
-Where, \begin{align}
-     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
-    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
-    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
-\end{align}
-
-This model used the following priors for cases,
-
-\begin{align}
-     R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
-    \mu_w &\sim \mathcal{N}(3.6, 0.7) \\
-    \sigma_w &\sim \mathcal{N}(3.1, 0.8) \\
-    \mu_{\xi_{O}} &\sim \mathcal{N}(1.62, 0.064) \\
-    \sigma_{\xi_{O}} &\sim \mathcal{N}(0.418, 0.069) \\
-    \mu_{\xi_{D}} &\sim \mathcal{N}(0.614, 0.066) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(1.51, 0.048) \\
-    \alpha &\sim \mathcal{N}(0.25, 0.05) \\
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-and updated the reporting process as follows when forecasting deaths,
-
-\begin{align}
-    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
-    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
-\end{align}
-
-\(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) were truncated to be
-greater than 0 and with \(\xi\), and \(w\) normalised to sum to 1.
-
-The prior for the generation time was sourced from {[}51{]} but refit
-using a log-normal incubation period with a mean of 5.2 days (SD 1.1)
-and SD of 1.52 days (SD 1.1) with this incubation period also being used
-as a prior {[}52{]} for \(\xi_{O}\). This resulted in a
-gamma-distributed generation time with mean 3.6 days (standard deviation
-(SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates. We estimated
-the delay between symptom onset and case report or death required to
-convolve latent infections to observations by fitting an integer
-adjusted log-normal distribution to 10 subsampled bootstraps of a public
-linelist for cases in Germany from April 2020 to June 2020 with each
-bootstrap using 1\% or 1769 samples of the available data {[}45,53{]}
-and combining the posteriors for the mean and standard deviation of the
-log-normal distribution {[}40,42,46,54{]}.
-
-\(GP_t\) is an approximate Hilbert space Gaussian process as defined in
-{[}55{]} using a Matern 3/2 kernel using a boundary factor of 1.5 and 17
-basis functions (20\% of the number of days used in fitting). The length
-scale of the Gaussian process was given a log-normal prior with a mean
-of 21 days, and a standard deviation of 7 days truncated to be greater
-than 3 days and less than 60 days. The magnitude of the Gaussian process
-was assumed to be normally distributed centred at 0 with a standard
-deviation of 0.1.
-
-From the forecast time horizon (\(T\)) and onwards the last value of the
-Gaussian process was used (hence \(R_t\) was assumed to be fixed) and
-latent infections were adjusted to account for the proportion of the
-population that was susceptible to infection as follows,
-
-\begin{equation}
-    I_t = (N - I^c_{t-1}) \left(1 - \exp \left(\frac{-I'_t}{N - I^c_{T}}\right)\right),
-\end{equation}
-
-where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\)
-and \(I'_t\) are the unadjusted infections defined above. This
-adjustment is based on that implemented in the \texttt{epidemia} R
-package {[}56,57{]}.
-
-\hypertarget{convolution-model}{%
-\paragraph{Convolution model}\label{convolution-model}}
-
-The convolution model shares the same observation model as the renewal
-model but rather than assuming that an observation is predicted by
-itself using the renewal equation instead assumes that it is predicted
-entirely by another observation after some parametric delay. It can be
-defined mathematically as follows,
-
-\begin{equation} 
-    D_{t} \sim \mathrm{NB}\left(\omega_{(t \mod 7)} \alpha \sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) C_{t-\tau},  \phi \right)
-\end{equation}
-
-with the following priors,
-
-\begin{align}
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \alpha &\sim \mathcal{N}(0.01, 0.02) \\
-    \xi &\sim \mathcal{LN}(\mu, \sigma) \\
-    \mu &\sim \mathcal{N}(2.5, 0.5) \\
-\sigma &\sim \mathcal{N}(0.47, 0.2) \\
-\phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-with \(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) truncated to be
-greater than 0 and with \(\xi\) normalised such that
-\(\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1\).
-
-\hypertarget{model-fitting}{%
-\subsubsection{Model fitting}\label{model-fitting}}
-
-Both models were implemented using the \texttt{EpiNow2} R package
-(version 1.3.3) {[}40{]}. Each forecast target was fitted independently
-for each model using Markov-chain Monte Carlo (MCMC) in stan {[}46{]}. A
-minimum of 4 chains were used with a warmup of 250 samples for the
-renewal equation-based model and 1000 samples for the convolution model.
-2000 samples total post warmup were used for the renewal equation model
-and 4000 samples for the convolution model. Different settings were
-chosen for each model to optimise compute time contingent on
-convergence. Convergence was assessed using the R hat diagnostic
-{[}46{]}. For the convolution model forecast the case forecast from the
-renewal equation model was used in place of observed cases beyond the
-forecast horizon using 1000 posterior samples. 12 weeks of data was used
-for both models though only 3 weeks of data were included in the
-likelihood for the convolution model.
-
-\clearpage
-
-\hypertarget{tables-with-results-of-the-forecast-evaluation}{%
-\subsection{Tables with results of the forecast
-evaluation}\label{tables-with-results-of-the-forecast-evaluation}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 7010 (0.8) & 7480 (0.64) & 2680 (0.73) & 1700 (1.38) & 2630 (0.68) & -0.01 & 10400 (0.82) & 0.55 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 8740 (1) & 11800 (1.01) & 2190 (0.6) & 2720 (2.21) & 3830 (0.99) & 0.18 & 12000 (0.94) & 0.48 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 16200 (0.89) & 16600 (0.76) & 3660 (0.6) & 5930 (1.56) & 6600 (0.78) & -0.01 & 23300 (0.87) & 0.36 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25600 (1.4) & 33800 (1.54) & 5420 (0.88) & 5920 (1.56) & 14200 (1.69) & 0.17 & 34600 (1.29) & 0.43 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 27000 (0.81) & 26200 (0.64) & 4750 (0.52) & 11000 (1.43) & 11200 (0.67) & 0.02 & 39000 (0.83) & 0.14 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 50600 (1.51) & 70000 (1.72) & 10800 (1.18) & 7710 (1) & 32100 (1.93) & 0.13 & 68700 (1.46) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 39200 (0.7) & 38600 (0.52) & 5970 (0.49) & 15600 (1.26) & 17600 (0.56) & 0.07 & 54800 (0.74) & 0.05 & 0.38\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 91700 (1.64) & 135000 (1.83) & 19500 (1.6) & 8990 (0.72) & 63200 (2.02) & 0.09 & 125000 (1.68) & 0.31 & 0.48\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{aggregate-performance-by-location}{%
-\subsection{Aggregate performance by
-location}\label{aggregate-performance-by-location}}
-
-\hypertarget{performance-in-germany}{%
-\subsubsection{Performance in Germany}\label{performance-in-germany}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Germany-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Germany}
-\end{figure}
-
-\hypertarget{performance-in-poland}{%
-\subsubsection{Performance in Poland}\label{performance-in-poland}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Poland-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Poland}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-absolute-terms}{%
-\subsubsection{Performance across locations in absolute
-terms}\label{performance-across-locations-in-absolute-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-v4} \caption{Visualisation of aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-relative-terms}{%
-\subsection{Performance across locations in relative
-terms}\label{performance-across-locations-in-relative-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4} \caption{Visualisation of relative aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals.
-E: Dispersion.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast.
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations-rel}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-daily-reported-cases-and-deaths}{%
-\subsection{Visualisation of daily reported cases and
-deaths}\label{visualisation-of-daily-reported-cases-and-deaths}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily_truth} \caption{Visualisation of daily report data.
-The black line represents weekly data divided by seven.
-Data were last accessed through the German and Polish Forecast Hub on August 21 2021.}\label{fig:daily-truth}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily-data-updates} \caption{Visualisation of the absolute difference between the daily report data at the time and the data now.
-In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:daily-truth-update}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/weekly-data-updates} \caption{Visualisation of the relative difference between the weekly report data at the time and the data now.
-Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:weekly-truth-update}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}{%
-\subsection{Visualisation of scores and forecasts 1, 3, 4 weeks
-ahead}\label{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} \caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} \caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} \caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-4}
-\end{figure}
-
-\clearpage
-
-\hypertarget{distribution-of-scores}{%
-\subsection{Distribution of scores}\label{distribution-of-scores}}
-
-\hypertarget{absolute-scores}{%
-\subsubsection{Absolute scores}\label{absolute-scores}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1} \caption{A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3} \caption{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4} \caption{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-4}
-\end{figure}
-
-\hypertarget{ranks-achieved-by-forecasts}{%
-\subsubsection{Ranks achieved by
-forecasts}\label{ranks-achieved-by-forecasts}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-2}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-4}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} \caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-renewal} \caption{Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences-renewal}
-\end{figure}
-
-\newpage
-
-\hypertarget{comparison-of-ensembles}{%
-\subsection{Comparison of ensembles}\label{comparison-of-ensembles}}
-
-\hypertarget{performance-visualisation-mean-ensemble}{%
-\subsubsection{Performance visualisation mean
-ensemble}\label{performance-visualisation-mean-ensemble}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble”     extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
-Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-mean}
-\end{figure}
-
-\hypertarget{tables-median-ensemble}{%
-\subsubsection{Tables median ensemble}\label{tables-median-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 6970 (0.79) & 8260 (0.71) & 3060 (0.83) & 943 (0.77) & 2970 (0.77) & 0.04 & 10800 (0.85) & 0.55 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 7820 (0.89) & 9630 (0.82) & 3270 (0.89) & 1210 (0.98) & 3330 (0.86) & -0.02 & 12000 (0.94) & 0.48 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 7960 (0.91) & 10300 (0.88) & 3190 (0.87) & 1020 (0.83) & 3760 (0.97) & 0.04 & 12100 (0.95) & 0.57 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 16400 (0.9) & 19600 (0.89) & 5350 (0.87) & 3290 (0.87) & 7730 (0.92) & 0.02 & 24200 (0.9) & 0.43 & 0.69\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 16900 (0.92) & 19600 (0.89) & 5230 (0.85) & 4310 (1.13) & 7370 (0.88) & 0.00 & 24600 (0.92) & 0.38 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 17500 (0.96) & 21400 (0.98) & 5830 (0.95) & 2880 (0.76) & 8770 (1.04) & 0.00 & 25500 (0.95) & 0.45 & 0.71\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 235 (0.95) & 332 (0.98) & 88.6 (0.96) & 90.4 (0.79) & 55.5 (1.33) & -0.01 & 323 (0.97) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 234 (0.94) & 331 (0.98) & 85.2 (0.92) & 98.1 (0.85) & 50.2 (1.21) & -0.05 & 329 (0.99) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 234 (0.94) & 329 (0.97) & 90.7 (0.98) & 118 (1.03) & 25.3 (0.61) & -0.08 & 333 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 239 (0.96) & 337 (1) & 85.2 (0.92) & 99.6 (0.87) & 54.2 (1.3) & -0.03 & 322 (0.96) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 246 (0.99) & 342 (1.01) & 91.5 (0.99) & 106 (0.92) & 48.6 (1.17) & -0.06 & 342 (1.02) & 0.67 & 0.92\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 296 (1.01) & 398 (1.03) & 125 (0.95) & 91 (0.84) & 80.2 (1.55) & 0.05 & 486 (1.13) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 303 (1.04) & 423 (1.1) & 115 (0.87) & 122 (1.13) & 66.1 (1.27) & 0.00 & 483 (1.13) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 270 (0.92) & 385 (1) & 121 (0.92) & 119 (1.1) & 29.9 (0.58) & -0.04 & 403 (0.94) & 0.58 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 303 (1.04) & 392 (1.02) & 122 (0.92) & 106 (0.98) & 74.6 (1.44) & 0.03 & 499 (1.16) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 296 (1.01) & 397 (1.03) & 128 (0.97) & 97.1 (0.9) & 71.2 (1.37) & -0.01 & 462 (1.08) & 0.67 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 30800 (0.92) & 38600 (0.95) & 7910 (0.87) & 6890 (0.9) & 16000 (0.96) & 0.03 & 44200 (0.94) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 30800 (0.92) & 34100 (0.84) & 7500 (0.82) & 8960 (1.17) & 14300 (0.86) & 0.02 & 44100 (0.94) & 0.24 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 34000 (1.02) & 43100 (1.06) & 8860 (0.97) & 6300 (0.82) & 18900 (1.14) & 0.02 & 48100 (1.03) & 0.29 & 0.60\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 51200 (0.92) & 69900 (0.95) & 10900 (0.89) & 11100 (0.9) & 29300 (0.94) & 0.04 & 69600 (0.94) & 0.19 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 48800 (0.87) & 58600 (0.8) & 9700 (0.8) & 13700 (1.1) & 25400 (0.81) & 0.00 & 65800 (0.88) & 0.19 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 59100 (1.06) & 84100 (1.14) & 12600 (1.03) & 10100 (0.81) & 36400 (1.16) & 0.01 & 78900 (1.06) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 332 (1.04) & 388 (1.18) & 158 (0.92) & 78.7 (0.85) & 95 (1.72) & -0.02 & 547 (1.12) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 321 (1.01) & 385 (1.17) & 153 (0.89) & 100 (1.08) & 68.1 (1.24) & -0.01 & 535 (1.1) & 0.54 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 298 (0.93) & 337 (1.03) & 155 (0.9) & 106 (1.14) & 37.5 (0.68) & -0.04 & 441 (0.9) & 0.67 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 319 (1) & 342 (1.04) & 160 (0.93) & 85.1 (0.92) & 73.6 (1.34) & -0.02 & 547 (1.12) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 332 (1.04) & 363 (1.11) & 168 (0.98) & 86.1 (0.93) & 78.2 (1.42) & -0.02 & 528 (1.08) & 0.58 & 0.96\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 445 (1.05) & 532 (1.2) & 193 (0.91) & 107 (0.85) & 144 (1.68) & -0.03 & 700 (1.04) & 0.54 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 399 (0.94) & 438 (0.99) & 195 (0.92) & 105 (0.83) & 97.9 (1.14) & -0.05 & 692 (1.03) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 384 (0.91) & 387 (0.87) & 196 (0.92) & 122 (0.97) & 65.9 (0.77) & -0.06 & 602 (0.89) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 407 (0.96) & 456 (1.03) & 202 (0.95) & 105 (0.83) & 101 (1.18) & -0.03 & 669 (0.99) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 457 (1.08) & 527 (1.19) & 208 (0.98) & 129 (1.02) & 121 (1.41) & -0.06 & 744 (1.1) & 0.50 & 0.96\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\hypertarget{tables-mean-ensemble}{%
-\subsubsection{Tables mean ensemble}\label{tables-mean-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 8680 (1) & 10300 (1) & 3700 (1) & 1460 (1) & 3520 (1) & -0.02 & 13400 (1) & 0.50 & 0.86\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 7600 (0.88) & 8770 (0.85) & 3360 (0.91) & 1090 (0.75) & 3140 (0.89) & 0.01 & 11900 (0.89) & 0.52 & 0.90\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 8050 (0.93) & 9070 (0.88) & 3520 (0.95) & 1410 (0.97) & 3120 (0.89) & -0.02 & 12600 (0.94) & 0.48 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 8090 (0.93) & 9780 (0.95) & 3490 (0.94) & 1110 (0.76) & 3490 (0.99) & 0.02 & 12700 (0.95) & 0.57 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 19000 (1) & 22100 (1) & 5960 (1) & 3690 (1) & 9340 (1) & 0.02 & 28800 (1) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 17100 (0.9) & 20600 (0.93) & 5550 (0.93) & 2850 (0.77) & 8660 (0.93) & 0.05 & 26000 (0.9) & 0.38 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 17600 (0.93) & 20000 (0.9) & 5540 (0.93) & 3790 (1.03) & 8230 (0.88) & 0.01 & 26800 (0.93) & 0.36 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 18300 (0.96) & 22600 (1.02) & 5910 (0.99) & 2640 (0.72) & 9720 (1.04) & 0.06 & 27700 (0.96) & 0.38 & 0.76\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 229 (1) & 292 (1) & 101 (1) & 90.4 (1) & 36.7 (1) & -0.07 & 315 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 219 (0.96) & 289 (0.99) & 96.8 (0.96) & 79.8 (0.88) & 42.6 (1.16) & -0.04 & 297 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 217 (0.95) & 287 (0.98) & 95.3 (0.94) & 83.1 (0.92) & 38.7 (1.05) & -0.07 & 300 (0.95) & 0.67 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 225 (0.98) & 292 (1) & 98.7 (0.98) & 94.2 (1.04) & 32 (0.87) & -0.09 & 314 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 222 (0.97) & 289 (0.99) & 98 (0.97) & 84.1 (0.93) & 39.6 (1.08) & -0.04 & 295 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 225 (0.98) & 290 (0.99) & 99.7 (0.99) & 84.7 (0.94) & 40.5 (1.1) & -0.05 & 314 (1) & 0.71 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 256 (1) & 306 (1) & 138 (1) & 64.5 (1) & 53.2 (1) & 0.04 & 374 (1) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 270 (1.05) & 338 (1.1) & 136 (0.99) & 65.2 (1.01) & 68.1 (1.28) & 0.06 & 413 (1.1) & 0.75 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 268 (1.05) & 346 (1.13) & 133 (0.96) & 78.7 (1.22) & 57.1 (1.07) & 0.05 & 408 (1.09) & 0.75 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 259 (1.01) & 322 (1.05) & 133 (0.96) & 81.7 (1.27) & 44.4 (0.83) & 0.03 & 380 (1.02) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 264 (1.03) & 315 (1.03) & 133 (0.96) & 70.1 (1.09) & 60 (1.13) & 0.06 & 404 (1.08) & 0.71 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 264 (1.03) & 332 (1.08) & 141 (1.02) & 60.1 (0.93) & 63.1 (1.19) & 0.06 & 390 (1.04) & 0.79 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 35600 (1) & 42100 (1) & 9340 (1) & 7050 (1) & 19200 (1) & 0.03 & 51200 (1) & 0.26 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 32100 (0.9) & 40500 (0.96) & 8830 (0.95) & 4920 (0.7) & 18300 (0.95) & 0.07 & 47200 (0.92) & 0.29 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 32200 (0.9) & 36700 (0.87) & 8430 (0.9) & 7190 (1.02) & 16500 (0.86) & 0.04 & 46900 (0.92) & 0.24 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 35200 (0.99) & 46000 (1.09) & 9630 (1.03) & 4600 (0.65) & 20900 (1.09) & 0.08 & 51000 (1) & 0.38 & 0.67\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 60300 (1) & 79300 (1) & 15700 (1) & 10400 (1) & 34100 (1) & 0.04 & 78600 (1) & 0.29 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 55000 (0.91) & 77100 (0.97) & 14600 (0.93) & 6620 (0.64) & 33800 (0.99) & 0.11 & 75200 (0.96) & 0.33 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 53400 (0.89) & 66600 (0.84) & 13700 (0.87) & 10600 (1.02) & 29200 (0.86) & 0.06 & 70400 (0.9) & 0.26 & 0.60\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 61700 (1.02) & 89800 (1.13) & 16400 (1.04) & 6400 (0.62) & 38900 (1.14) & 0.12 & 82900 (1.05) & 0.31 & 0.64\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 289 (1) & 293 (1) & 178 (1) & 45.9 (1) & 65.7 (1) & 0.01 & 443 (1) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 310 (1.07) & 348 (1.19) & 182 (1.02) & 42 (0.92) & 86.5 (1.32) & 0.08 & 502 (1.13) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 315 (1.09) & 339 (1.16) & 178 (1) & 62.2 (1.36) & 74 (1.13) & 0.07 & 507 (1.14) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 297 (1.03) & 292 (1) & 174 (0.98) & 67.7 (1.47) & 55 (0.84) & 0.01 & 452 (1.02) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 294 (1.02) & 299 (1.02) & 172 (0.97) & 48 (1.05) & 74.2 (1.13) & 0.03 & 476 (1.07) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 310 (1.07) & 349 (1.19) & 189 (1.06) & 39.4 (0.86) & 81.9 (1.25) & 0.05 & 482 (1.09) & 0.62 & 1.00\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 437 (1) & 568 (1) & 232 (1) & 72 (1) & 134 (1) & 0.00 & 702 (1) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 445 (1.02) & 598 (1.05) & 237 (1.02) & 56.4 (0.78) & 152 (1.13) & 0.06 & 707 (1.01) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 421 (0.96) & 520 (0.92) & 239 (1.03) & 49.9 (0.69) & 132 (0.99) & 0.05 & 678 (0.97) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 398 (0.91) & 465 (0.82) & 235 (1.01) & 55.6 (0.77) & 107 (0.8) & 0.00 & 628 (0.89) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 418 (0.96) & 533 (0.94) & 222 (0.96) & 66.8 (0.93) & 129 (0.96) & 0.03 & 662 (0.94) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 467 (1.07) & 636 (1.12) & 248 (1.07) & 61 (0.85) & 158 (1.18) & 0.05 & 755 (1.08) & 0.67 & 1.00\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{sensitivity-analysis}{%
-\subsection{Sensitivity analysis}\label{sensitivity-analysis}}
-
-In the original analysis, cases and deaths were scored on different
-periods, as the convolution model was only added later. This sensitivity
-shows performance of all models restricted to the period from December
-14 2020 until March 1st 2021 where all models were available.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-late}
-\end{figure}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 4980 (0.74) & 5730 (0.64) & 2070 (0.6) & 728 (0.74) & 2190 (0.94) & 0.09 & 7810 (0.82) & 0.54 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 6730 (1) & 8960 (1) & 3430 (1) & 978 (1) & 2330 (1) & -0.09 & 9550 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 9640 (1.43) & 13300 (1.48) & 1970 (0.57) & 4170 (4.26) & 3500 (1.5) & 0.09 & 12700 (1.33) & 0.46 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 10700 (0.99) & 13800 (1.1) & 2880 (0.58) & 2350 (0.85) & 5430 (1.79) & 0.08 & 15400 (1.07) & 0.46 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 10800 (1) & 12500 (1) & 4940 (1) & 2780 (1) & 3030 (1) & -0.13 & 14400 (1) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25000 (2.31) & 34000 (2.72) & 4780 (0.97) & 8710 (3.13) & 11500 (3.8) & 0.05 & 32000 (2.22) & 0.50 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 17200 (1) & 16000 (0.98) & 3800 (0.63) & 5660 (0.85) & 7770 (1.74) & 0.07 & 26800 (1.1) & 0.08 & 0.58\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 17200 (1) & 16300 (1) & 6030 (1) & 6670 (1) & 4470 (1) & -0.16 & 24400 (1) & 0.33 & 0.67\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 37700 (2.19) & 55900 (3.43) & 8840 (1.47) & 10700 (1.6) & 18100 (4.05) & -0.03 & 49800 (2.04) & 0.33 & 0.58\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 26100 (0.95) & 21000 (0.84) & 4810 (0.7) & 11300 (0.83) & 10100 (1.43) & 0.04 & 39400 (1.05) & 0.00 & 0.46\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 27600 (1) & 25000 (1) & 6900 (1) & 13600 (1) & 7060 (1) & -0.19 & 37400 (1) & 0.29 & 0.54\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 48900 (1.77) & 77800 (3.11) & 13800 (2) & 11900 (0.88) & 23200 (3.29) & -0.10 & 65500 (1.75) & 0.38 & 0.58\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{overview-of-models-and-forecasters}{%
-\subsection{Overview of models and
-forecasters}\label{overview-of-models-and-forecasters}}
 
 \begin{longtable}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{7.3cm}}
-\caption{\label{tab:table-ensemble-versions}Overview of the models and ensembles used.}\\
 \toprule
@@
 \endfirsthead
-\caption[]{Overview of the models and ensembles used. \textit{(continued)}}\\
+\multicolumn{2}{@{}l}{\textit{(continued)}}\\
 \toprule
@@
 
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/number-forecasters} \caption{Number of participants who submitted a forecast over time.}\label{fig:num-forecasters}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/ensemble-members} \caption{Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
-Note that the renewal model was not included in the ensemble on December 28th 2020.}\label{fig:num-ensemble-members}
-\end{figure}
-
-\clearpage
-
-\hypertarget{comparison-of-crowd-forecasts-and-application-baseline}{%
-\subsection{Comparison of crowd forecasts and application
-baseline}\label{comparison-of-crowd-forecasts-and-application-baseline}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} \caption{Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the median, as well as the 50\% and 90\% prediction intervals (in order of decreasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons).}\label{fig:compare-forecasters}
-\end{figure}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{McGowan CJ, Biggerstaff M, Johansson M, Apfeldorf KM,
-Ben-Nun M, Brooks L, et al. Collaborative efforts to forecast seasonal
-influenza in the {United States}, 2015--2016. Scientific Reports.
-2019;9: 683.
-doi:\href{https://doi.org/10.1038/s41598-018-36361-9}{10.1038/s41598-018-36361-9}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Reich NG, Brooks LC, Fox SJ, Kandula S, McGowan CJ,
-Moore E, et al. A collaborative multiyear, multimodel assessment of
-seasonal influenza forecasting in the {United States}. PNAS. 2019;116:
-3146--3154.
-doi:\href{https://doi.org/10.1073/pnas.1812594116}{10.1073/pnas.1812594116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Shaman J, Karspeck A. Forecasting seasonal outbreaks of
-influenza. PNAS. 2012;109: 20425--20430.
-doi:\href{https://doi.org/10.1073/pnas.1208772109}{10.1073/pnas.1208772109}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Biggerstaff M, Alper D, Dredze M, Fox S, Fung IC-H,
-Hickmann KS, et al. Results from the centers for disease control and
-prevention's predict the 2013--2014 {Influenza Season Challenge}. BMC
-Infectious Diseases. 2016;16: 357.
-doi:\href{https://doi.org/10.1186/s12879-016-1669-x}{10.1186/s12879-016-1669-x}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak
-AL, Baugher B, et al. An open challenge to advance probabilistic
-forecasting for dengue epidemics. PNAS. 2019;116: 24268--24274.
-doi:\href{https://doi.org/10.1073/pnas.1909865116}{10.1073/pnas.1909865116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Yamana TK, Kandula S, Shaman J. Superensemble forecasts
-of dengue outbreaks. Journal of The Royal Society Interface. 2016;13:
-20160410.
-doi:\href{https://doi.org/10.1098/rsif.2016.0410}{10.1098/rsif.2016.0410}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Colón-González FJ, Bastos LS, Hofmann B, Hopkin A,
-Harpham Q, Crocker T, et al. Probabilistic seasonal dengue forecasting
-in {Vietnam}: {A} modelling study using superensembles. PLOS Medicine.
-2021;18: e1003542.
-doi:\href{https://doi.org/10.1371/journal.pmed.1003542}{10.1371/journal.pmed.1003542}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Viboud C, Sun K, Gaffey R, Ajelli M, Fumanelli L, Merler
-S, et al. The {RAPIDD} ebola forecasting challenge: {Synthesis} and
-lessons learnt. Epidemics. 2018;22: 13--21.
-doi:\href{https://doi.org/10.1016/j.epidem.2017.08.002}{10.1016/j.epidem.2017.08.002}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Funk S, Camacho A, Kucharski AJ, Lowe R, Eggo RM,
-Edmunds WJ. Assessing the performance of real-time epidemic forecasts:
-{A} case study of {Ebola} in the {Western Area} region of {Sierra
-Leone}, 2014-15. PLOS Computational Biology. 2019;15: e1006785.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1006785}{10.1371/journal.pcbi.1006785}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Del Valle SY, McMahon BH, Asher J, Hatchett R, Lega JC,
-Brown HE, et al. Summary results of the 2014-2015 {DARPA Chikungunya}
-challenge. BMC Infectious Diseases. 2018;18: 245.
-doi:\href{https://doi.org/10.1186/s12879-018-3124-7}{10.1186/s12879-018-3124-7}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Farrow DC, Brooks LC, Hyun S, Tibshirani RJ, Burke DS,
-Rosenfeld R. A human judgment approach to epidemiological forecasting.
-PLOS Computational Biology. 2017;13: e1005248.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1005248}{10.1371/journal.pcbi.1005248}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Funk S, Abbott S, Atkins BD, Baguelin M, Baillie JK,
-Birrell P, et al. Short-term forecasts to inform the response to the
-{Covid-19} epidemic in the {UK}. medRxiv. 2020; 2020.11.11.20220962.
-doi:\href{https://doi.org/10.1101/2020.11.11.20220962}{10.1101/2020.11.11.20220962}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K,
-et al. {COVID-19 Forecast Hub}: 4 {December} 2020 snapshot. {Zenodo};
-2020.
-doi:\href{https://doi.org/10.5281/zenodo.3963371}{10.5281/zenodo.3963371}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A,
-Rivadeneira AJC, et al. Evaluation of individual and ensemble
-probabilistic forecasts of {COVID-19} mortality in the {US}. medRxiv.
-2021; 2021.02.03.21250974.
-doi:\href{https://doi.org/10.1101/2021.02.03.21250974}{10.1101/2021.02.03.21250974}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. Short-term forecasting of {COVID-19} in {Germany}
-and {Poland} during the second wave -- a preregistered study. medRxiv.
-2021; 2020.12.24.20248826.
-doi:\href{https://doi.org/10.1101/2020.12.24.20248826}{10.1101/2020.12.24.20248826}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. National and subnational short-term forecasting of
-{COVID-19} in {Germany} and {Poland}, early 2021. 2021;
-2021.11.05.21265810.
-doi:\href{https://doi.org/10.1101/2021.11.05.21265810}{10.1101/2021.11.05.21265810}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-europeancovid-19forecasthubEuropeanCovid19Forecast2021}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{European Covid-19 Forecast Hub. European {Covid-19
-Forecast Hub}. 2021 {[}cited 30 May 2021{]}. Available:
-\url{https://covid19forecasthub.eu/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichAccuracyRealtimeMultimodel2019}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Reich NG, McGowan CJ, Yamana TK, Tushar A, Ray EL,
-Osthus D, et al. Accuracy of real-time multi-model ensemble forecasts
-for seasonal influenza in the {U}.{S}. PLOS Computational Biology.
-2019;15: e1007486.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1007486}{10.1371/journal.pcbi.1007486}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Tetlock PE, Mellers BA, Rohrbaugh N, Chen E. Forecasting
-{Tournaments}: {Tools} for {Increasing Transparency} and {Improving} the
-{Quality} of {Debate}. Curr Dir Psychol Sci. 2014;23: 290--295.
-doi:\href{https://doi.org/10.1177/0963721414534257}{10.1177/0963721414534257}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Atanasov P, Rescober P, Stone E, Swift SA,
-Servan-Schreiber E, Tetlock P, et al. Distilling the {Wisdom} of
-{Crowds}: {Prediction Markets} vs. {Prediction Polls}. Management
-Science. 2016;63: 691--706.
-doi:\href{https://doi.org/10.1287/mnsc.2015.2374}{10.1287/mnsc.2015.2374}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers E-J. Laypeople
-{Can Predict Which Social-Science Studies Will Be Replicated
-Successfully}. Advances in Methods and Practices in Psychological
-Science. 2020;3: 267--285.
-doi:\href{https://doi.org/10.1177/2515245920919667}{10.1177/2515245920919667}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{ReplicationMarkets. Replication {Markets} -- {Reliable}
-research replicates\ldots you can bet on it. 2020 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.replicationmarkets.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Servan-Schreiber E, Wolfers J, Pennock DM, Galebach B.
-Prediction {Markets}: {Does Money Matter}? Electronic Markets. 2004;14:
-243--251.
-doi:\href{https://doi.org/10.1080/1019678042000245254}{10.1080/1019678042000245254}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{McAndrew TC, Reich NG. An expert judgment model to
-predict early stages of the {COVID-19} outbreak in the {United States}.
-medRxiv. 2020; 2020.09.21.20196725.
-doi:\href{https://doi.org/10.1101/2020.09.21.20196725}{10.1101/2020.09.21.20196725}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Recchia G, Freeman ALJ, Spiegelhalter D. How well did
-experts and laypeople forecast the size of the {COVID-19} pandemic? PLOS
-ONE. 2021;16: e0250935.
-doi:\href{https://doi.org/10.1371/journal.pone.0250935}{10.1371/journal.pone.0250935}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Metaculus. A {Preliminary Look} at {Metaculus} and
-{Expert Forecasts}. 22 Jun 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.metaculus.com/news/2020/06/02/LRT/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Hypermind. Hypermind \textbar{} {Supercollective}
-intelligence for decision makers. {Hypermind}; 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.hypermind.com/en/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{CSET Foretell. {CSET Foretell}. 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.cset-foretell.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{PredictIt. {PredictIt}. 2021 {[}cited 13 Oct 2021{]}.
-Available: \url{https://www.predictit.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Held L, Meyer S, Bracher J. Probabilistic forecasting in
-infectious disease epidemiology: The 13th {Armitage} lecture. Statistics
-in Medicine. 2017;36: 3443--3460.
-doi:\href{https://doi.org/10.1002/sim.7363}{10.1002/sim.7363}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Crowdforecastr: Eliciting crowd forecasts in r shiny. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618519}{10.5281/zenodo.4618519}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Covid.german.forecasts: Forecasting covid-19 related metrics for the
-german/poland forecast hub. 2020. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-ecdcDownloadHistoricalData2020}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{ECDC. Download historical data (to 14 {December} 2020)
-on the daily number of new reported {COVID-19} cases and deaths
-worldwide. {European Centre for Disease Prevention and Control}; 14 Dec
-2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rkiRKICoronavirusSARSCoV22021}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{RKI. {RKI} - {Coronavirus SARS-CoV-2} - {Aktueller
-Lage-}/{Situationsbericht} des {RKI} zu {COVID-19}. 2021 {[}cited 30 May
-2021{]}. Available:
-\url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-forsal.plRozbieznosciStatystykachKoronawirusa2020}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Forsal.pl. Rozbieżności w statystykach koronawirusa. 22
-tys. przypadków będą doliczone do ogólnej liczby wyników. 2020 {[}cited
-30 May 2021{]}. Available:
-\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Ärzteblatt DÄG Redaktion Deutsches.
-SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an. {Deutsches
-Ärzteblatt}; 3 Nov 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Fay C, Guyader V, Rochette S, Girard C. Golem: A
-framework for robust shiny applications. 2021. Available:
-\url{https://github.com/ThinkR-open/golem}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie
-Y, et al. Shiny: Web application framework for r. 2021. Available:
-\url{https://CRAN.R-project.org/package=shiny}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Our World in Data. {COVID-19 Data Explorer}. {Our World
-in Data}; 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://ourworldindata.org/coronavirus-data-explorer}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K,
-Ellis P, et al. EpiNow2: Estimate real-time case counts and time-varying
-epidemiological parameters. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957489}{10.5281/zenodo.3957489}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Fraser C. Estimating {Individual} and {Household
-Reproduction Numbers} in an {Emerging Epidemic}. PLOS ONE. 2007;2: e758.
-doi:\href{https://doi.org/10.1371/journal.pone.0000758}{10.1371/journal.pone.0000758}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation2020}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{epiforecasts.io/covid. Covid-19: {Temporal} variation in
-transmission during the {COVID-19} outbreak. {Covid-19}; 2020 {[}cited
-30 May 2021{]}. Available: \url{https://epiforecasts.io/covid/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Sherratt K, Abbott S, Meakin SR, Hellewell J, Munday JD,
-Bosse N, et al. Exploring surveillance data biases when estimating the
-reproduction number: With insights into subpopulation transmission of
-{Covid-19} in {England}. 2021; 2020.10.18.20214585.
-doi:\href{https://doi.org/10.1101/2020.10.18.20214585}{10.1101/2020.10.18.20214585}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abbottEstimatingTimevaryingReproduction2020a}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs
-HP, Bosse NI, et al. Estimating the time-varying reproduction number of
-{SARS-CoV-2} using national and subnational case counts. 2020 {[}cited
-14 Oct 2021{]}.
-doi:\href{https://doi.org/10.12688/wellcomeopenres.16006.1}{10.12688/wellcomeopenres.16006.1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Xu B, Gutierrez B, Hill S, Scarpino S, Loskill A, Wu J,
-et al. Epidemiological data from the nCoV-2019 outbreak: Early
-descriptions from publicly available data. 2020. Available:
-\url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Stan Development Team. RStan: The r interface to stan.
-2020. Available: \url{http://mc-stan.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG. Evaluating
-epidemic forecasts in an interval format. PLoS Comput Biol. 2021;17:
-e1008618.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1008618}{10.1371/journal.pcbi.1008618}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Gneiting T, Raftery AE. Strictly proper scoring rules,
-prediction, and estimation. Journal of the American Statistical
-Association. 2007;102: 359--378.
-doi:\href{https://doi.org/10.1198/016214506000001437}{10.1198/016214506000001437}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Scoringutils:
-Utilities for scoring and assessing predictions. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618017}{10.5281/zenodo.4618017}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-deutschewelleCoronavirusGermanyImpose2020}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Deutsche Welle. Coronavirus: {Germany} to impose
-one-month partial lockdown \textbar{} {DW} \textbar{} 28.10.2020. 2020
-{[}cited 29 Jun 2021{]}. Available:
-\url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Ganyani T, Kremer C, Chen D, Torneri A, Faes C, Wallinga
-J, et al. Estimating the generation interval for coronavirus disease
-(COVID-19) based on symptom onset data, march 2020. Eurosurveillance.
-2020;25. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith
-HR, et al. The incubation period of coronavirus disease 2019 (COVID-19)
-from publicly reported confirmed cases: Estimation and application.
-Annals of Internal Medicine. 2020;172: 577--582. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J,
-Munday J, et al. Covidregionaldata: Subnational data for the covid-19
-outbreak. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957539}{10.5281/zenodo.3957539}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Evaluating the use of the reproduction number as an
-epidemiological tool, using spatio-temporal trends of the {Covid-19}
-outbreak in {England} \textbar{} {medRxiv}. {[}cited 30 May 2021{]}.
-Available:
-\url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Riutort-Mayol G, Bürkner P-C, Andersen MR, Solin A,
-Vehtari A. Practical hilbert space approximate bayesian gaussian
-processes for probabilistic programming. 2020. Available:
-\url{https://arxiv.org/abs/2004.11408}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Scott JA, Gandy A, Mishra S, Unwin J, Flaxman S, Bhatt
-S. Epidemia: Modeling of epidemics using hierarchical bayesian models.
-2020. Available:
-\url{https://imperialcollegelondon.github.io/epidemia/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bhattSemiMechanisticBayesianModeling}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Bhatt S, Ferguson N, Flaxman S, Gandy A, Mishra S, Scott
-JA. Semi-{Mechanistic Bayesian} modeling of {COVID-19} with {Renewal
-Processes}. : 14. }
-
-\end{CSLReferences}
-
-\nolinenumbers
-
 \end{document}

### 2023-12-11 manuscript/final submission/Supplementary/S6-Table.tex

--- 2022-06-02 manuscript/manuscript.tex
@@
 \usepackage{xcolor}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 
-\usepackage{forarray}
-\usepackage{xstring}
-\newcommand{\getIndex}[2]{
-  \ForEach{,}{\IfEq{#1}{\thislevelitem}{\number\thislevelcount\ExitForEach}{}}{#2}
-}
-
-\setcounter{secnumdepth}{0}
-
-\newcommand{\getAff}[1]{
-  \getIndex{#1}{London School of Hygiene \& Tropical Medicine,Karlsruhe
-Institute of Technology Institute of Economic Theory and Statistics,Max
-Planck Institute for Multidisciplinary Sciences,UK Health Security
-Agency,Imperial College London}
-}
+\author{}
+\date{\vspace{-2.5em}}
 
 \begin{document}
-\vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{Comparing human and model-based forecasts of COVID-19 in
-Germany and
-Poland} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Nikos I. Bosse\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\textsuperscript{*},
-Sam Abbott\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Johannes Bracher\textsuperscript{\getAff{Karlsruhe Institute of
-Technology Institute of Economic Theory and Statistics}},
-Habakuk Hain\textsuperscript{\getAff{Max Planck Institute for
-Multidisciplinary Sciences}},
-Billy J. Quilty\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Mark Jit\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Edwin van Leeuwen\textsuperscript{\getAff{UK Health Security
-Agency}, \getAff{London School of Hygiene \& Tropical Medicine}},
-Anne Cori\textsuperscript{\getAff{Imperial College London}},
-Sebastian Funk\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\\
-\bigskip
-\textbf{\getAff{London School of Hygiene \& Tropical Medicine}}London
-School of Hygiene \& Tropical Medicine, Keppel Street, London WC1E7HT,
-United Kingdom\\
-\textbf{\getAff{Karlsruhe Institute of Technology Institute of Economic
-Theory and Statistics}}Karlsruhe Institute of Technology - Institute of
-Economic Theory and Statistics, Post Box 6980, 76049 Karlsruhe,
-Germany\\
-\textbf{\getAff{Max Planck Institute for Multidisciplinary Sciences}}Max
-Planck Institute for Multidisciplinary Sciences, Am Faßberg 11, 37077
-Göttingen, Germany\\
-\textbf{\getAff{UK Health Security Agency}}UK Health Security Agency,
-London NW9 5EQ, United Kingdom\\
-\textbf{\getAff{Imperial College London}}Imperial College London,
-Norfolk Place, London W2 1PG, United Kingdom\\
-\bigskip
-* Corresponding author: nikos.bosse@lshtm.ac.uk\\
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-Forecasts based on epidemiological modelling have played an important
-role in shaping public policy throughout the COVID-19 pandemic. This
-modelling combines knowledge about infectious disease dynamics with the
-subjective opinion of the researcher who develops and refines the model
-and often also adjusts model outputs. Developing a forecast model is
-difficult, resource- and time-consuming. It is therefore worth asking
-what modelling is able to add beyond the subjective opinion of the
-researcher alone. To investigate this, we analysed different real-time
-forecasts of cases of and deaths from COVID-19 in Germany and Poland
-over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
-We compared crowd forecasts elicited from researchers and volunteers,
-against a) forecasts from two semi-mechanistic models based on common
-epidemiological assumptions and b) the ensemble of all other models
-submitted to the Forecast Hub. We found crowd forecasts, despite being
-overconfident, to outperform all other methods across all forecast
-horizons when forecasting cases (weighted interval score relative to the
-Hub ensemble 2 weeks ahead: 0.89). Forecasts based on computational
-models performed comparably better when predicting deaths (rel. WIS
-1.26), suggesting that epidemiological modelling and human judgement can
-complement each other in important ways.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step.
-% Author Summary not valid for PLOS ONE submissions.
-\section*{Author summary}
-Mathematical models of COVID-19 have played a key role in informing
-governments across the world. While mathematical models are informed by
-our knowledge of infectious disease dynamics, they are ultimately
-developed and iteratively adjusted by the researchers and shaped by
-their subjective opinions. To investigate what modelling is able to add
-beyond the subjective opinion of the researcher alone, we compared human
-forecasts with model-based predictions of COVID-19 cases and deaths
-submitted to the so-called German/Polish Forecast Hub (which collates a
-variety of models from a range of teams). \textbar{} We found that our
-human forecasts consistently outperformed an aggregate of all available
-model-based forecasts when predicting cases, but not when predicting
-deaths. Our findings suggest that human insight may be most valuable
-when forecasting highly uncertain quantities, which depend on many
-factors that are hard to model using equations, while mathematical
-models may be most useful in settings like predicting deaths, where
-leading indicators with a clear connection to the target variable are
-available. This potentially has very relevant policy implications, as
-agencies informing policy-makers could benefit from routinely eliciting
-human forecasts in addition to model-based predictions to inform
-policies.
-
-\linenumbers
-
-% Use "Eq" instead of "Equation" for equation citations.
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Infectious disease modelling has a long tradition and has helped inform
-public health decisions both through scenario modelling, as well as
-actual forecasts of (among others) influenza {[}e.g. 1,2--4{]}, dengue
-fever {[}e.g. 5,6,7{]}, ebola {[}e.g. 8,9{]}, chikungunya {[}e.g.
-10,11{]} and now COVID-19 {[}e.g. 12,13--17{]}. Applications of
-epidemiological models differ in the way they make statements about the
-future. Forecasts aim to predict the future as it will occur, while
-scenario modelling and projections aim to represent what the future
-could look like under certain scenario assumptions or if conditions
-stayed the same as they were in the past. Forecasts can be judged by
-comparing them against observed data. Since it is much harder to fairly
-assess the accuracy and usefulness of projections and scenario modelling
-in the same way, this work focuses on forecasts, which represent only a
-subset of all epidemiological modelling.
-
-Since March 2020, forecasts of COVID-19 from multiple teams have been
-collected, aggregated and compared by Forecast Hubs such as the US
-Forecast Hub {[}13,14{]}, the German and Polish Forecast Hub {[}15,16{]}
-and the European Forecast Hub {[}17{]}. Often, different individual
-forecasts are combined into a single forecast, e.g.~by taking the mean
-or median of all forecasts. These ensemble forecasts usually tend to
-perform better and more consistently than individual forecasts (see e.g.
-{[}6{]}; {[}18{]}).
-
-Individual computational models usually rely to varying degrees on
-mechanistic assumptions about infectious disease dynamics (such as
-SIR-type compartmental models that aim to represent how individuals move
-from being susceptible to infected and then recovered or dead). Some are
-more statistical in nature (such as time series models that detect
-statistical patterns without explicitly modelling disease dynamics). How
-exactly such a mathematical or computational model is constructed and
-which assumptions are made depends on subjective opinion and judgement
-of the researcher who develops and refines the model. Models are
-commonly adjusted and improved based on whether the model output looks
-plausible to the researchers involved.
-
-The process of model construction and refinement is laborious and
-time-consuming, and it is therefore worth asking what modelling can add
-beyond the subjective judgment of the researcher alone. In this work, we
-ask this question specifically in the context of predictive performance,
-and set aside other advantages of epidemiological modelling (such as
-reproducibility or the ability to obtain a deeper fundamental
-understanding of how diseases spread). One natural way to do this is to
-compare the predictive performance of forecasts based on computational
-models (``model-based forecasts'') against forecasts made by individual
-humans without explicit use of a computer model (``direct human
-forecasts'') or a combination of multiple such forecasts (``crowd
-forecasts'').
-
-Previous work has examined such direct human forecasts in various
-contexts, such as geopolitics {[}19,20{]}, meta-science {[}21,22{]},
-sports {[}23{]} and epidemiology {[}11,24,25{]}. Several prediction
-platforms {[}26--28{]} and prediction markets {[}29{]} have been created
-to collate expert and non-expert predictions. However, with the notable
-exception of {[}11{]}, these forecasts were not designed to be evaluated
-alongside model-based forecasts and usually follow their own (often
-binary) prediction formats. Direct human forecasts may be able to take
-into account insights and relationships between variables which are hard
-to specify using epidemiological models. However, it is not entirely
-clear in which situations human forecasts perform well or badly. For
-example, {[}11{]} found that humans could outperform computer models at
-predicting the 2014/15 and 2015/16 flu season in the US, a setting where
-the disease was well known and information about previous seasons was
-available. However, humans tended to do slightly worse at predicting the
-2014/15 outbreak of chikungunya in the Americas, a disease previously
-largely unobserved and unknown in these regions at the time.
-
-In this study, we analyse the performance of direct human forecasts
-relative to model-based forecasts and discuss the added benefit of
-epidemiological modelling over human judgement alone. As a case study,
-we use different forecasts, involving varying degrees of human
-intervention, which we submitted in real time to the German and Polish
-Forecast Hub. In contrast to {[}11{]} we elicited not only point
-predictions, but full predictive distributions (``probabilistic
-forecasts'', see e.g. {[}30{]}) from participants. This allows us to
-compare not only predictive accuracy, but also how well human
-forecasters and model-based forecasts were able to quantify forecast
-uncertainty.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-We created and submitted the following forecasts to the German and
-Polish Forecast Hub: 1) a direct human forecast (henceforth called
-``crowd forecast''), elicited from participants through a web
-application {[}31{]} and 2) two semi-mechanistic model-based forecasts
-(``renewal model'' and ``convolution model'') informed by basic
-assumptions about COVID-19 epidemiology. While the two semi-mechanistic
-forecasts were necessarily shaped by our implicit assumptions and
-decisions, they were designed such as to minimise the amount of human
-intervention involved. For example, we refrained from adjusting model
-outputs or refining the models based on past performance. Forecasts were
-created in real time over a period of 21 weeks from October 12th 2020
-until March 1st 2021 and submitted to the German and Polish Forecast hub
-{[}15,16{]}. All code and tools necessary to generate the forecasts and
-make a forecast submission are available in the
-\texttt{covid.german.forecasts} R package {[}32{]}. This repository also
-contains a record of all forecasts submitted to the German and Polish
-Forecast Hub. Forecasts were evaluated using a variety of scoring
-metrics and compared among each other and against an ensemble of all
-other models submitted to the German and Polish Forecast Hub.
-
-\hypertarget{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}{%
-\subsection{Forecast targets and interaction with the German and Polish
-Forecast
-Hub}\label{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}}
-
-The German and Polish Forecast Hub (now mostly merged into the {[}17{]})
-elicits predictions for various COVID-19 related forecast targets from
-different research groups every week. Forecasts had to be made every
-Monday (with submissions allowed until Tuesday 3pm) and were permitted
-to use any data that was available by Monday 11.59pm. We submitted
-forecasts for incident and cumulative weekly reported numbers of cases
-of and deaths from COVID-19 on a national level in Germany and Poland
-over a one to four week forecast horizon. Forecasts were submitted on
-Mondays, but weeks were defined as ending on a Saturday (and starting on
-Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26
-days. Submissions were required in a quantile-based format with 23
-quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10,
-0.15, \ldots, 0.95, 0.975, 0.99. Forecasts submitted to the Forecast Hub
-were combined into different ensembles every week, with the median
-ensemble (i.e., the \(\alpha\)-quantile of the ensemble is given by the
-median of all submitted \(\alpha\)-quantiles) being the default ensemble
-shown on all official Forecast hub visualisations
-(https://kitmetricslab.github.io/forecasthub/forecast).
-
-Data on daily reported test positive cases and deaths linked to COVID-19
-were provided by the organisers of the German and Polish Forecast hub.
-Until December 14th, 2020, these data were sourced from the European
-Centre for Disease Control {[}33{]}. After ECDC stopped publishing daily
-data, observations were sourced from the Robert Koch Institute (RKI) and
-the Polish Ministry of Health for the remainder of the submission period
-{[}34{]}. These data are subject to reporting artefacts, (such as for
-example delayed case reporting in Poland on the 24th November,
-{[}35{]}), changes in reporting over time, and variation in testing
-regimes (for example in Germany from the 11th of November on, {[}36{]}).
-The ECDC data as well as the data published by the Polish Ministry of
-Health were also subject to data revisions, although most of them (with
-a notable exception of a data update for October 12 2020 in Germany)
-only affected daily, not weekly data (see Figures
-\ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).
-
-\hypertarget{crowd-forecasts}{%
-\subsection{Crowd forecasts}\label{crowd-forecasts}}
-
-Our crowd forecasts were created as an ensemble of forecasts made by
-individual participants every week through a web application
-(https://cmmid-lshtm.shinyapps.io/crowd-forecast/). Weekly forecasts had
-to be submitted before Tuesday 12pm every week, but participants were
-asked to only use any information or data that was already available by
-Monday night. The application was built using the \texttt{shiny} and
-\texttt{golem} R packages {[}37,38{]} and is available in the
-\texttt{crowdforecastr} R package {[}31{]}. To make a forecast in the
-application participants could select a predictive distribution (with
-the default being log-normal) to represent the probability that the
-forecasted quantity took certain values. Median and width of the
-uncertainty could be adjusted by either interacting with a figure
-showing their forecast or providing numerical values (see screenshot in
-Figure \ref{fig:screenshot} in the SI). The default shown was a
-repetition of the last known observation with constant uncertainty
-around it computed as the standard deviation of the last four changes in
-weekly log observed forecasts (i.e.~as
-\(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
-A comparison of the crowd forecasts against the default baseline shown
-in the application is displayed in Figure \ref{fig:compare-forecasters}
-in the Appendix. Our interface also allowed participants to view past
-observations based on the hub data, as well as their forecasts, on a
-logarithmic scale and presented additional contextual COVID-19 data
-sourced from {[}39{]}. These data included, for example, notifications
-of both test positive COVID-19 cases and COVID-19 linked deaths and the
-number of COVID-19 tests conducted over time. From November 26 2020 on
-we displayed weekly small reports with a visualisation of past forecasts
-and scores on our website, epiforecasts.io.
-
-Forecasts were stored in a Google Sheet and downloaded, cleaned and
-processed every week for submission to the Forecast Hub. If a forecaster
-had submitted multiple predictions for a single target, only the latest
-submission was kept. Information on the chosen distribution as well as
-the parameters for median and width were used to obtain the required set
-of 23 quantiles from that distribution. Forecasts from all forecasters
-were then aggregated using an unweighted quantile-wise mean (i.e., the
-\(\alpha\)-quantile of the ensemble is given by the mean of all
-submitted \(\alpha\)-quantiles). To avoid issues with users trying out
-the app and submitting a random forecast, we required that a forecaster
-needed to make a forecast for at least two targets for a given forecast
-in order to be included in the crowd forecast ensemble. On a few
-occasions we deleted forecasts that were clearly the result of a user or
-software error (such as for example forecasts that were zero
-everywhere).
-
-individual forecasts were assessed as clearly erroneous by visual
-inspection and subsequently removed before aggregation and were excluded
-from the submission as well as the analysis.
-
-Participants were recruited mostly within the Centre of Mathematical
-Modeling of Infectious Diseases at the London School of Hygiene \&
-Tropical Medicine, but participants were also invited personally or via
-social media to submit predictions. Depending on whether they had a
-background in either statistics, forecasting or epidemiology,
-participants were asked to self-identify as `experts' or `non-experts'.
-
-The study was approved by the Observational / Interventions Research
-Ethics Committee at the London School of Hygiene \& Tropical Medicine,
-LSHTM Ethics Reference: 22290. Formal consent from participants was
-taken in written form through the web application.
-
-\hypertarget{model-based-forecasts}{%
-\subsection{Model-based forecasts}\label{model-based-forecasts}}
-
-We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R
-package (version 1.3.3) as our model-based forecasts {[}40{]}. The first
-of these models, here called ``renewal model'', used the renewal
-equation {[}41{]} to predict reported cases and deaths (see details in
-the SI). It estimated the effective reproduction number \(R_t\) (the
-average number of people each person infected at time t is expected to
-infect in turn) and modelled future infections as a weighted sum of past
-infection multiplied by \(R_t\). \(R_t\) was assumed to stay constant
-beyond the forecast date, roughly corresponding to continuing the latest
-exponential trend in infections. On the 9th of November we altered the
-date when \(R_t\) was assumed to be constant from two weeks prior to the
-date of the forecast to the forecast date, which we found to yield a
-more stable \(R_t\) estimate. Reported case and death notifications were
-obtained by convolving predicted infections over data-based delay
-distributions {[}40,42--44{]} to model the time between infection and
-report date. The renewal model was used to predict cases as well as
-deaths with forecasts being generated for each target separately. Death
-forecasts from the renewal model were therefore not informed by past
-cases. One submission of the renewal model on December 28th 2020 was
-delayed and therefore not included in the official Forecast hub
-ensemble.
-
-The second model (``convolution model'', see details in SI) was only
-used to forecast deaths and was added later, starting December 7th 2020
-(with the first forecast from December 7th suffering from a software bug
-and therefore disregarded in all further analyses). The convolution
-model was submitted, but never included in the official Forecast hub
-ensemble due to concerns that it could be too similar to the renewal
-model. The convolution model predicted deaths as a fraction of infected
-people who would die with some delay, by using a convolution of reported
-cases with a distribution that described the delay from case report to
-death and a scaling factor (the case-fatality ratio). Both the renewal
-and the convolution model used daily observations and assumed a negative
-binomial observation model with a multiplicative day-of-the-week effect
-{[}40{]}.
-
-Line list data used to inform the prior for the delay from symptom onset
-to test positive case report or death in the model-based forecasts was
-sourced from {[}45{]} with data available up to the 1st of August. All
-model fitting was done using Markov-chain Monte Carlo (MCMC) in stan
-{[}46{]} with each location and forecast target being fitted separately.
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-For the main analysis we focused mostly on two week ahead forecasts, as
-COVID-19 forecasts, especially for cases, were in the past found to have
-poor predictive performance beyond this horizon {[}15{]}. Forecasts for
-cases were scored using the full period from October 2020 until March
-2021. To ensure comparability between models, all death forecasts were
-scored using only the period from December 14th on, where all models
-including the convolution model were available. To ensure robustness of
-our results we conducted a sensitivity analysis where all forecasts
-(including cases) were scored only over the later period for which all
-forecasts were available (see Section \ref{sensitivity-analysis} in the
-SI). Results remained broadly unchanged.
-
-Forecasts were analysed using the following scoring metrics: The
-weighted interval score (WIS) {[}47{]}, the absolute error, relative
-bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule {[}48{]}, meaning that in expectation
-the score is optimised by reporting a predictive distribution that is
-identical to the true data-generating distribution. Forecasters are
-therefore incentivised to report their true belief about the future. The
-WIS can be understood as a generalisation of the absolute error to
-quantile-based forecasts (also meaning that smaller values are better)
-and can be decomposed into three separate penalties: forecast spread
-(i.e.~uncertainty of forecasts), over-prediction and under-prediction.
-While the over- and under-prediction components of the WIS capture the
-amount of over-prediction and under-prediction in absolute terms, we
-also look at a relative tendency to make biased forecasts. The bias
-metric {[}9{]} we use captures how much probability mass of the forecast
-was above or below the true value (mapped to values between -1 and 1)
-and therefore represents a general tendency to over- or under-predict in
-relative terms. A value of -1 implies that all quantiles of the
-predictive distribution are below the observed value and a value of 1
-that all quantiles are above the observed value. Empirical coverage is
-the percentage of observed values that fall inside a given prediction
-interval (e.g.~how many observed values fall inside all 50\% prediction
-intervals). Scoring metrics are explained in more detail in Table
-\ref{tab:scoring-metrics} in the SI. All scores were calculated using
-the \texttt{scoringutils} R package {[}49{]}.
-
-At all stages of the evaluation our forecasts were compared to the
-median ensemble of all \emph{other} models submitted to the German and
-Polish Forecast Hub (``Hub ensemble''). This ``Hub ensemble'' was
-retrospectively computed and excludes all our models, leaving on average
-five ensemble member models (see details in Section
-\ref{contributions-hub}, as well as in Table
-\ref{tab:table-ensemble-versions} and Figure
-\ref{fig:num-ensemble-members} in the SI). What we call ``Hub ensemble''
-in this article therefore differs from the ``official Hub ensemble''
-(here called ``hub-ensemble-realised'') which included crowd forecasts
-as well as renewal model forecasts. To enhance interpretability of
-scores we mainly report WIS relative to the Hub ensemble in the main
-text, i.e.~we divided the average scores for a given model by the
-average score achieved by the Hub ensemble on the same set of forecasts
-(with values \textgreater1 implying worse and values \textless1 implying
-better performance than the Hub ensemble). In addition to comparing our
-forecasts against the hub ensemble excluding our models, we also
-assessed the impact of our forecasts on the performance of the
-forecasting hub by recalculating separate versions of the Hub ensemble
-with only some (or all) of our forecasts included. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{crowd-forecast-participation}{%
-\subsection{Crowd forecast
-participation}\label{crowd-forecast-participation}}
-
-A total number of 32 participants submitted forecasts, 17 of those
-self-identified as `expert' in either forecasting or epidemiology. The
-median number of forecasters for any given forecast target was 6, the
-minimum 2 and the maximum 10. The mean number of submissions from an
-individual forecaster was 4.7 but the median number was only one - most
-participants dropped out after their first submission. Only two
-participants submitted a forecast every single week, both of whom are
-authors on this study.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} \caption{Two week ahead forecasts and corresponding scores.
-A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth}
-\end{figure}
-
-\hypertarget{case-forecasts}{%
-\subsection{Case Forecasts}\label{case-forecasts}}
-
-For cases, crowd forecasts had a lower mean weighted interval score
-(WIS, lower values indicate better performance) than both the renewal
-model and the Hub ensemble across all forecast horizons (Figure
-\ref{fig:agg-performance-all}A) and locations (Figure
-\ref{fig:performance-locations-rel}A). For two week ahead forecasts,
-mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts
-and 1.40 for the renewal model (Table \ref{tab:score-table-2}). Across
-all forecasting approaches, locations and forecast horizons, the
-distribution of WIS values was very right-skewed, and average
-performance was heavily influenced by outliers (Figure
-\ref{fig:distribution-scores}). Overall, low variance in forecast
-performance was closely linked with good mean performance (Figures
-\ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A),
-suggesting that the ability to avoid large errors was an important
-factor in determining overall performance. The impact of outlier values
-was especially pronounced for the renewal model, which had more outliers
-(Figure \ref{fig:distribution-scores}), as well as the highest standard
-deviation of WIS values (standard deviation of the WIS relative to the
-WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon),
-while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub
-ensemble (= 1) showed more stable performance.
-
-To varying degrees, all forecasts exhibited trend-following behaviour
-and were rarely able to predict a change in trend before it had
-happened. For example, all forecasts failed to predict the change in
-trend from increase to decrease that happened in November in Germany and
-severely overshot reported cases (Figure
-\ref{fig:forecasts-and-truth}A). This was most striking for the renewal
-model, which extrapolated unconstrained exponential growth based on the
-recent past of observations. The Hub ensemble and the crowd forecast,
-which had both been under-predicting throughout October, also failed to
-predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on
-November 2nd 2020 {[}50{]} and the change in the testing regime (with
-stricter test criteria) on November 11th 2020 {[}36{]}, were fastest to
-adapt to the new trend, and the Hub ensemble slowest. In December, cases
-rose again in Germany, with all models under-predicting this growth to
-varying extents. As in October, the renewal model captured the phase of
-exponential growth in cases slightly better than other approaches, but
-again overshot when reported case numbers fell over Christmas. The large
-variance in predictions in January in Germany (severe under-prediction
-followed by severe over-prediction) may in part be caused by the fact
-that the renewal model operated on daily data and therefore was
-susceptible to fluctuations in daily reporting around Christmas that
-would not have influenced on weekly reporting. Similar trends in
-performance were evident in Poland, with the crowd forecast quickest at
-adapting to the change in trend in November. In general, there were
-fewer large outlier forecasts in Poland and in particular the renewal
-model performed more in line with other forecasts there.
-
-All forecasting approaches, including the Hub ensemble, were
-overconfident, i.e.~they showed lower than nominal coverage (meaning
-that 50\% (90\%) prediction intervals generally covered less than 50\%
-(90\%) of the actually observed values) (Figure
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
-Coverage for all forecasts deteriorated with increasing forecast
-horizon, indicating that all forecasting approaches struggled to
-quantify uncertainty appropriately for case forecasts. This was
-especially an issue for crowd forecasts, which had markedly shorter
-prediction intervals (i.e., narrower and more confident predictive
-distributions) than other approaches (Figure
-\ref{fig:agg-performance-all}E) and only showed a small increase in
-uncertainty across forecast horizons. The crowd forecasts prediction
-intervals were also noticeably narrower than the default baseline shown
-to forecasters in the application (see Figure
-\ref{fig:compare-forecasters}).
-
-In spite of good performance in terms of the absolute error (Figure
-\ref{fig:agg-performance-all}G), the narrow forecast intervals led to
-forecasts which were severely overconfident (covering only 36\% and 55\%
-of all observations with the 50\% and 90\% prediction intervals of all
-forecasts made at a two week forecast horizon, and only 5\% and 38\%
-four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables
-\ref{tab:score-table-2} and \ref{tab:score-table-4}). Despite worse
-performance in terms of absolute error (Figure
-\ref{fig:agg-performance-all}G), the renewal model achieved better
-calibration (comparable to the Hub ensemble), as uncertainty increased
-rapidly across forecast horizons. The crowd forecasts, on the other
-hand, showed a smaller bias than the renewal model, but were
-overconfident.
-
-The renewal model exhibited a noticeable tendency towards
-over-predicting reported cases across all horizons. The crowd forecast
-tended to over-predict at longer forecast horizons, whereas the Hub
-ensemble showed no systematic bias (Figure
-\ref{fig:agg-performance-all}F). Regardless of a general relative
-tendency to over-predict, all forecasting approaches incurred larger
-absolute penalties from over- than from under-prediction (see
-decomposition of the WIS into absolute penalties for over-prediction,
-under-prediction and dispersion in Figures
-\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
-
-Generally, trends in overall performance were broadly similar across
-locations (Figures \ref{fig:performance-locations} and
-\ref{fig:performance-locations-rel}). Due to the differing population
-sizes and numbers of notifications in Germany and Poland absolute scores
-were difficult to compare directly. However, relative to the Hub
-ensemble, the crowd forecasts performed noticeably better in Germany
-than in Poland and the renewal model better in Poland than in Germany
-(Figures \ref{fig:performance-locations-rel}A,
-\ref{fig:performance-locations-rel}G,
-\ref{fig:agg-performance-all-Germany},
-\ref{fig:agg-performance-all-Poland}).
-
-\hypertarget{death-forecasts}{%
-\subsection{Death Forecasts}\label{death-forecasts}}
-
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as
-our model-based approaches across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B). Relative WIS values for the models
-two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1
-(Hub ensemble) and 1.79 (renewal model). The crowd forecasts performed
-better than the renewal model across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B), and also better than the convolution
-model three and four weeks ahead. Poor performance of the renewal model,
-especially at longer horizons, indicates that an approach that does not
-know about past cases, but instead estimates and projects a separate
-\(R_t\) trace from deaths, does not use the available information
-efficiently. The convolution model was able to outperform both the
-renewal model and the crowd forecasts at shorter forecast horizons
-(where the delay between cases and deaths means that future deaths are
-largely informed by present cases), but saw performance deteriorate at
-three and four weeks ahead (where case predictions from the renewal
-model were increasingly used to inform death predictions) (Figure
-\ref{fig:agg-performance-all}B, Table \ref{tab:score-table-4}).
-
-As past cases and hospitalisations can be used as predictors, predicting
-a change in trend may be easier for deaths than for cases. Even though
-all forecasts generally struggled with this, there were some instances
-where changing trends were well captured or even anticipated. In Poland,
-for example, the Hub ensemble was able to capture or even anticipate the
-peak in deaths in December quite well (whereas the renewal model and
-crowd forecast did not). The renewal model, which mostly exhibited
-trend-following behaviour, correctly predicted another increase in
-weekly deaths in mid-January (potentially based on changes in daily
-deaths, as the renewal model did not know about past cases). In Germany
-in early January, all models predicted a decrease in deaths two to three
-weeks before it actually happened. Predictions from the renewal model at
-that time were likely strongly influenced by an unexpected drop in
-reported deaths in December. The other forecasting approaches and in
-particular, the convolution model may have been affected by potentially
-under-reported case numbers around Christmas. When the decrease that all
-models had predicted to happen in early January failed to materialise,
-the renewal model and the crowd forecast noticeably over-corrected and
-over-predicted deaths in the following weeks, while the Hub ensemble,
-and to a slightly lesser degree, the convolution model were able to
-capture the downturn well when it finally happened at the end of
-January.
-
-Death forecasts, generally, showed greater coverage of the 50\% and 90\%
-prediction intervals than case forecasts and no decrease in coverage
-across forecast horizons, indicating that it might be easier to
-appropriately quantify uncertainty for death forecasts. The Hub ensemble
-had the greatest coverage, with empirical coverage of the 50\% and 90\%
-prediction intervals exceeding 50\%, and 90\%, respectively, across all
-forecast horizons. Coverage for the crowd forecasts and our model-based
-approaches was generally lower than that of the Hub ensemble and mostly
-slightly lower than nominal coverage (Figure
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D). As
-for cases, the crowd forecast tended to have the narrowest prediction
-intervals and uncertainty increased most slowly across forecast
-horizons, and the renewal model forecasts generally were widest. The
-convolution model had relatively narrow prediction intervals for short
-forecast horizons, but had rapidly (and non-linearly) increasing
-uncertainty for longer forecast horizons, driven by increasing
-uncertainty in the underlying case forecasts.
-
-For deaths, the ensemble of crowd forecasts had a consistent tendency to
-over-predict \ref{fig:agg-performance-all}F. The convolution model had a
-strong tendency to under-predict, with the magnitude of under-prediction
-steadily decreasing for longer forecast horizons. The renewal model
-(which over-predicted for cases) and the Hub ensemble slightly tended
-towards under-prediction. For deaths, absolute over- and
-under-prediction penalties were more in line with a general relative
-tendency to over- or under-predict than for cases (Figure
-\ref{fig:agg-performance-all}A, \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2}, \ref{tab:score-table-4}).
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} \caption{Distribution of scores.
-A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
-Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores.}\label{fig:distribution-scores}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.
-“Hub-ensemble”    extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-rel}
-\end{figure}
-
-\hypertarget{contributions-hub}{%
-\subsection{Contribution to the Forecast Hub}\label{contributions-hub}}
-
-Of our three models, only the renewal model and the crowd forecast were
-included in the official Forecast Hub median ensemble
-(``hub-ensemble-realised''), while the convolution model was never
-included as it was deemed too similar to the existing renewal model. In
-the official Hub ensemble, there were on average 7.1 models included
-(including our own), with a median of 7, a minimum of 4 (on 28 December
-2020 over the Christmas period) and a maximum of 10. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively. An
-overview of all models and ensemble versions is shown in Table
-\ref{tab:table-ensemble-versions} in the SI.
-
-For cases, our contributions (compared to the Hub ensemble without our
-contributions) consistently improved performance across all forecasting
-horizons (rel. WIS 0.9 two weeks ahead, Table
-\ref{tab:score-table-ensemble-2}). Contributions from the crowd
-forecasts alone also improved performance of the Hub ensemble across all
-forecast horizons, while contributions from the renewal model had a
-negative effect for longer horizons (rel. WIS 1.02 three weeks ahead,
-1.06 four weeks ahead). The realised ensemble including both models
-performed better or equal compared to all versions with only one model
-included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model
-have improved performance (Table \ref{tab:score-table-ensemble-4}). The
-realised ensemble performed comparably to the crowd forecasts for
-predictions one to two weeks ahead, and worse for greater forecast
-horizons.
-
-For deaths, contributions from the renewal model and crowd forecast
-together improved performance only for one week ahead predictions and
-showed an increasingly negative impact on performance for longer
-horizons (rel. WIS of the Hub-ensemble-realised 1.01 two weeks ahead,
-1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and
-\ref{tab:score-table-ensemble-4}). Individual contributions from both
-the renewal model and the crowd forecast were largely negative, while a
-version of the Hub ensemble with only the convolution model included
-would have performed consistently better across all forecast horizons
-(with the positive impact increasing for longer horizons). This is
-especially interesting as the convolution model performed consistently
-worse than the pre-existing Hub ensemble (Figure
-\ref{fig:agg-performance-all}) and especially worse for longer horizons.
-
-We also considered the impact of our contributions on a version of the
-Hub ensemble constructed by taking the quantile-wise mean, rather than
-the median. General trends were similar, with the notable exception of
-the convolution model, which had a consistently positive impact on the
-median ensemble, but a mixed and mostly slightly negative impact on the
-mean ensemble (Figures \ref{fig:agg-performance-ensemble-rel}B and
-\ref{fig:agg-performance-ensemble-mean}B). This may happen if a model is
-more correct directionally relative to the pre-existing ensemble, but
-overshoots in absolute terms, thereby moving the ensemble too far. For
-both the mean and the median ensemble, changes in performance from
-adding or removing models were of a similar order of magnitude,
-suggesting that at least in this instance, with a relatively small
-ensemble size, the median ensemble was not necessarily more `robust' to
-changes than the mean ensemble. However, the ensemble version with all
-our forecasts included (``hub-ensemble-with-all'') tended to perform
-relatively better for the median ensemble than the mean ensemble,
-suggesting that adding more models may be more beneficial or `safer' for
-the median than for the mean ensemble as directional errors can more
-easily cancel out than errors in absolute terms.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Epidemiological forecasting modelling combines knowledge about
-infectious disease dynamics with the subjective opinion of the
-researcher who develops and refines the model. In this study, we
-compared forecasts of cases of and deaths from COVID-19 in Germany and
-Poland based purely on human judgement and elicited from a crowd of
-researchers and volunteers against forecasts from two semi-mechanistic
-epidemiological models. In spite of the small number of participants and
-a general tendency to be overconfident, crowd forecasts consistently
-outperformed our epidemiological models as well as the Hub ensemble when
-forecasting cases but not when forecasting deaths. This suggests that
-humans might be relatively good at foreseeing trends that are hard to
-model but may struggle to form an intuition for the exact relationship
-between cases and deaths.
-
-Past studies have evaluated the performance of model-based forecasting
-approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of
-(expert-tuned) model-based approaches {[}e.g. 12,13,14{]}, or
-exclusively on human forecasts {[}19,20,24,25{]}. In contrast, we
-directly compared human and model-based forecasts. This is similar to
-the approach taken by {[}11{]}, but extends it in several ways. While
-Farrow et al.~only asked for point predictions and constructed a
-predictive distribution from these, we asked participants to provide a
-full predictive distribution, allowing us to compare human forecasts and
-models without any further assumptions, as well as to analyse how humans
-quantified their uncertainty. In addition, we compared crowd forecasts
-to two semi-mechanistic models informed by basic epidemiological
-knowledge of COVID-19, allowing us to assess not only relative
-performance but also to analyse qualitative differences between human
-judgement and model-based insight. In terms of interpretability of the
-results, exact knowledge of our two models, as well as focus on a
-limited set of targets and locations was a major advantage of our study
-compared to larger studies conducted by the Forecast Hubs
-{[}12--15,17{]}.
-
-The strong performance of crowd forecasts in our study is in line with
-results from Farrow et al.~who also report strong performance of human
-predictions in past Flu challenges despite difficulties to recruit a
-large number of participants. The advantage of crowd forecasts we
-observed over our semi-mechanistic models is likely in part explained by
-the fact that we compared an ensemble of crowd forecasts with single
-models. However, this probably explains only part of the difference, and
-performance relative to the Hub ensemble strongly suggests that human
-insight is valuable when forecasting highly volatile and potentially
-hard-to-predict quantities such as case numbers. One potential
-explanation is that humans can have access to data that is not available
-to or hard to integrate into model-based forecasts. Relatively good
-performance of our semi-mechanistic models short-term, but not
-longer-term, suggests that model-based forecasts are helpful to
-extrapolate from current conditions, but require some form of human
-intervention or additional assumptions to inform forecasts when
-conditions change over time. This human intervention may be particularly
-important when dealing with artefacts in reporting and data anomalies
-(and especially when using daily, rather than weekly data). The large
-variance in predictions in January in Germany for example (severe
-under-prediction followed by severe over-prediction, see Figure
-\ref{fig:forecasts-and-truth}A), may in part be caused by the fact that
-the renewal model operated on daily data and therefore was susceptible
-to fluctuations in daily reporting which have less of an influence on
-weekly reporting.
-
-Our results suggest that human intervention may be less beneficial when
-forecasting deaths (especially at shorter horizons, when deaths are
-largely dependent on already observed cases), which benefits from the
-ability to model the delays and exact epidemiological relationships
-between different leading and lagged indicators. Relatively good
-performance of the convolution model, especially compared to the poor
-performance of the renewal model on deaths (which used only deaths to
-estimate and predict the effective reproduction number) underlines the
-importance of including leading indicators such as cases as a predictor
-for deaths.
-
-Given the low number of participants in our study, it is difficult to
-generalise conclusions about crowd predictions to other settings. Using
-R shiny as a platform for the web application arguably created some
-limits to user experience and performance, influencing the number of
-participants and potentially creating a self-selection effect.
-Motivating forecasters to contribute regularly proved challenging,
-especially given that the majority of our participants were from the UK
-and may not have been familiar with all relevant details of the
-situation in Germany and Poland. On the other hand, R shiny facilitated
-quick development and allowed us to provide our crowd forecasting
-tooling as an open source R package, meaning that it is available for
-others to use, for example in settings like early-stage outbreaks where
-model-based forecasts are not available. In light of the relatively
-small number of Hub ensemble models, performance of the Hub ensemble is
-also difficult to generalise. More research is needed to replicate these
-findings and investigate how crowd forecasts compare against the types
-of models and model ensembles policy makers use to inform their
-decisions.
-
-Our work suggests that crowd forecasts and model-based forecasts could
-have different strengths and may be able to complement each other. When
-choosing a suitable approach for a given task it is important to take
-into account how the output will be used. In this work we focused on
-forecasts (which aim to predict future data points whilst accounting for
-all factors that might influence them), whereas policy makers might be
-more interested in projections (which show what would happen in the
-absence of any events that could change the trend) or scenario
-modelling. Forecasts may not be a suitable basis for informing policy
-decisions, if forecasters already have factored in the expectation of a
-future intervention. Model-based approaches can be either forecasts or
-projections depending on the assumptions, whereas eliciting projections
-that are not influenced by implicit assumptions about the future from
-humans may be harder.
-
-Further work should explore the effects of humans refining their
-mathematical models or changing model outputs in more detail.
-Model-based forecasts could be used as an input to human judgement, with
-researchers adjusting predictions generated by models. Seeing a
-model-based forecast could help humans calibrate uncertainty better,
-while allowing for manual intervention to adapt spurious trend
-predictions. Tools need to be developed to facilitate this process at a
-larger scale. Human insight could also be used as an input to models.
-Such a `hybrid' forecasting approach could for example ask humans to
-predict the trend of the effective reproduction number \(R_t\) or the
-doubling rate (i.e.~how the epidemic evolves) into the future and use
-this to estimate the exact number of cases, hospitalisations or deaths
-this would imply. In light of severe overconfidence, yet good
-performance in terms of the absolute error, post-processing of human
-forecasts to adjust and widen prediction intervals may be another
-promising approach. Crowd forecasting in general could benefit greatly
-from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of
-the limited resources available and the small number of participants,
-this seems worthwhile to further develop and explore.
-
-\clearpage
-
-\textbf{Acknowledgements}
-
-NIB received funding from the Health Protection Research Unit (grant
-code NIHR200908, https://www.nihr.ac.uk/). SA's work was funded by the
-Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/). The work
-of JB was supported by the Helmholtz Foundation
-(https://www.helmholtz.de/) via the SIMCARD Information and Data Science
-Pilot Project. This research was partly funded by the National Institute
-for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 \&
-16/136/46) using UK aid from the UK Government to support global health
-research. The views expressed in this publication are those of the
-author(s) and not necessarily those of the NIHR or the UK Department of
-Health and Social Care. BJQ is supported in part by a grant from the
-Bill and Melinda Gates Foundation (OPP1139859,
-https://www.gatesfoundation.org/). EvL acknowledges funding by the
-National Institute for Health Research (NIHR) Health Protection Research
-Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908,
-https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research
-and innovation programme - project EpiPose (101003688,
-https://ec.europa.eu/programmes/horizon2020/). AC acknowledges funding
-by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/),
-and the Academy of Medical Sciences (https://acmedsci.ac.uk/). SF's work
-was supported by the Wellcome Trust (grant: 210758/Z/18/Z,
-https://wellcome.org/), and the NIHR (NIHR200908,
-https://www.nihr.ac.uk/).
-
-We thank all forecasters who participated in this study for their
-contribution.
-
-We would also like to acknowledge (in a randomised order) the members of
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group at the the London School of Hygiene \& Tropical Medicine:
-Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie
-Diamond, Katherine E. Atkins, Rein M G J Houben, Jiayao Lei, Rachel
-Lowe, David Simons, Sophie R Meakin, Nicholas G. Davies, Timothy W
-Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly,
-Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas,
-Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia
-Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson,
-Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang
-Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C
-Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun,
-Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche,
-James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday,
-Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan
-Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R
-Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael
-Pung, Anna M Foss.
-
-\clearpage
-
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
-
-\hypertarget{appendix-supplementary-information}{%
-\section*{(APPENDIX) Supplementary
-information}\label{appendix-supplementary-information}}
-\addcontentsline{toc}{section}{(APPENDIX) Supplementary information}
-
-\hypertarget{supplementary-information}{%
-\section{Supplementary information}\label{supplementary-information}}
-
-\hypertarget{scoring-metrics-used}{%
-\subsection{Scoring metrics used}\label{scoring-metrics-used}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{9.3cm}}
-\caption{\label{tab:scoring-metrics}Overview of the scoring metrics used.}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{Overview of the scoring metrics used. \textit{(continued)}}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-WIS (Weighted) interval score & The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
-It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
-The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction.
-For a single interval, the score is computed as
-  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
-  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e.
-the lower and upper bound of a single prediction interval.
-For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
-  $$WIS = \frac{1}{K + 0.5} \cdot \left( w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y) \right), $$
-  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
-
-\cellcolor{gray!6}{Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.}\\
-\addlinespace \addlinespace
-Interval coverage & Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
-Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
-we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.\\
-\addlinespace \addlinespace
-Bias & (Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict. Values are between -1 and 1 and 0 ideally. For continuous forecasts, bias is given as 
-$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
-where $F$ is the CDF of the predictive distribution and $y$ is the observed value.
-
-For quantile forecasts, $F(y)$ is replaced by a quantile rank.
-The appropriate quantile rank is determined by whether the median forecast is below  or above the true value.
-We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.
-
-\cellcolor{gray!6}{In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
-It is therefore a more robust measurement.}\\*
-\end{longtable}
-
-\clearpage
-
-\hypertarget{the-crowdforecasting-app}{%
-\subsection{The crowdforecasting app}\label{the-crowdforecasting-app}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../crowd-forecast/Screenshot-forecasting-app} \caption{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).
-}\label{fig:screenshot}
-\end{figure}
-
-\clearpage
-
-\hypertarget{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}{%
-\subsection{Text S1. Further details on the semi-mechanistic forecasting
-models}\label{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}}
-
-\hypertarget{renewal-equation-model}{%
-\subsubsection{Renewal equation model}\label{renewal-equation-model}}
-
-The model was initialised prior to the first observed data point by
-assuming constant exponential growth for the mean of assumed delays from
-infection to case report.
-
-\begin{align}
-  I_{t} &= I_0 \exp  \left(r t \right)  \\
-  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
-  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
-\end{align}
-
-Where \(I_{obs}\) and \(r_{obs}\) are estimated from the first week of
-observed data. For the time window of the observed data infections were
-then modelled by weighting previous infections by the generation time
-and scaling by the instantaneous reproduction number. These infections
-were then convolved to cases by date (\(O_t\)) and cases by date of
-report (\(D_t\)) using log-normal delay distributions. This model can be
-defined mathematically as follows,
-
-\begin{align}
-  \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
-  I_t &= R_t \sum_{\tau = 1}^{15} w(\tau | \mu_{w}, \sigma_{w}) I_{t - \tau} \\
-  O_t &= \sum_{\tau = 0}^{15} \xi_{O}(\tau | \mu_{\xi_{O}}, \sigma_{\xi_{O}}) I_{t-\tau} \\
-  D_t &= \alpha \sum_{\tau = 0}^{15} \xi_{D}(\tau | \mu_{\xi_{D}}, \sigma_{\xi_{D}}) O_{t-\tau} \\ 
-  C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
-\end{align}
-
-Where, \begin{align}
-     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
-    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
-    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
-\end{align}
-
-This model used the following priors for cases,
-
-\begin{align}
-     R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
-    \mu_w &\sim \mathcal{N}(3.6, 0.7) \\
-    \sigma_w &\sim \mathcal{N}(3.1, 0.8) \\
-    \mu_{\xi_{O}} &\sim \mathcal{N}(1.62, 0.064) \\
-    \sigma_{\xi_{O}} &\sim \mathcal{N}(0.418, 0.069) \\
-    \mu_{\xi_{D}} &\sim \mathcal{N}(0.614, 0.066) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(1.51, 0.048) \\
-    \alpha &\sim \mathcal{N}(0.25, 0.05) \\
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-and updated the reporting process as follows when forecasting deaths,
-
-\begin{align}
-    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
-    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
-\end{align}
-
-\(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) were truncated to be
-greater than 0 and with \(\xi\), and \(w\) normalised to sum to 1.
-
-The prior for the generation time was sourced from {[}51{]} but refit
-using a log-normal incubation period with a mean of 5.2 days (SD 1.1)
-and SD of 1.52 days (SD 1.1) with this incubation period also being used
-as a prior {[}52{]} for \(\xi_{O}\). This resulted in a
-gamma-distributed generation time with mean 3.6 days (standard deviation
-(SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates. We estimated
-the delay between symptom onset and case report or death required to
-convolve latent infections to observations by fitting an integer
-adjusted log-normal distribution to 10 subsampled bootstraps of a public
-linelist for cases in Germany from April 2020 to June 2020 with each
-bootstrap using 1\% or 1769 samples of the available data {[}45,53{]}
-and combining the posteriors for the mean and standard deviation of the
-log-normal distribution {[}40,42,46,54{]}.
-
-\(GP_t\) is an approximate Hilbert space Gaussian process as defined in
-{[}55{]} using a Matern 3/2 kernel using a boundary factor of 1.5 and 17
-basis functions (20\% of the number of days used in fitting). The length
-scale of the Gaussian process was given a log-normal prior with a mean
-of 21 days, and a standard deviation of 7 days truncated to be greater
-than 3 days and less than 60 days. The magnitude of the Gaussian process
-was assumed to be normally distributed centred at 0 with a standard
-deviation of 0.1.
-
-From the forecast time horizon (\(T\)) and onwards the last value of the
-Gaussian process was used (hence \(R_t\) was assumed to be fixed) and
-latent infections were adjusted to account for the proportion of the
-population that was susceptible to infection as follows,
-
-\begin{equation}
-    I_t = (N - I^c_{t-1}) \left(1 - \exp \left(\frac{-I'_t}{N - I^c_{T}}\right)\right),
-\end{equation}
-
-where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\)
-and \(I'_t\) are the unadjusted infections defined above. This
-adjustment is based on that implemented in the \texttt{epidemia} R
-package {[}56,57{]}.
-
-\hypertarget{convolution-model}{%
-\paragraph{Convolution model}\label{convolution-model}}
-
-The convolution model shares the same observation model as the renewal
-model but rather than assuming that an observation is predicted by
-itself using the renewal equation instead assumes that it is predicted
-entirely by another observation after some parametric delay. It can be
-defined mathematically as follows,
-
-\begin{equation} 
-    D_{t} \sim \mathrm{NB}\left(\omega_{(t \mod 7)} \alpha \sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) C_{t-\tau},  \phi \right)
-\end{equation}
-
-with the following priors,
-
-\begin{align}
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \alpha &\sim \mathcal{N}(0.01, 0.02) \\
-    \xi &\sim \mathcal{LN}(\mu, \sigma) \\
-    \mu &\sim \mathcal{N}(2.5, 0.5) \\
-\sigma &\sim \mathcal{N}(0.47, 0.2) \\
-\phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-with \(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) truncated to be
-greater than 0 and with \(\xi\) normalised such that
-\(\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1\).
-
-\hypertarget{model-fitting}{%
-\subsubsection{Model fitting}\label{model-fitting}}
-
-Both models were implemented using the \texttt{EpiNow2} R package
-(version 1.3.3) {[}40{]}. Each forecast target was fitted independently
-for each model using Markov-chain Monte Carlo (MCMC) in stan {[}46{]}. A
-minimum of 4 chains were used with a warmup of 250 samples for the
-renewal equation-based model and 1000 samples for the convolution model.
-2000 samples total post warmup were used for the renewal equation model
-and 4000 samples for the convolution model. Different settings were
-chosen for each model to optimise compute time contingent on
-convergence. Convergence was assessed using the R hat diagnostic
-{[}46{]}. For the convolution model forecast the case forecast from the
-renewal equation model was used in place of observed cases beyond the
-forecast horizon using 1000 posterior samples. 12 weeks of data was used
-for both models though only 3 weeks of data were included in the
-likelihood for the convolution model.
-
-\clearpage
-
-\hypertarget{tables-with-results-of-the-forecast-evaluation}{%
-\subsection{Tables with results of the forecast
-evaluation}\label{tables-with-results-of-the-forecast-evaluation}}
 
 \begin{table}[!h]
-\caption{\label{tab:score-table-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 7010 (0.8) & 7480 (0.64) & 2680 (0.73) & 1700 (1.38) & 2630 (0.68) & -0.01 & 10400 (0.82) & 0.55 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 8740 (1) & 11800 (1.01) & 2190 (0.6) & 2720 (2.21) & 3830 (0.99) & 0.18 & 12000 (0.94) & 0.48 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 16200 (0.89) & 16600 (0.76) & 3660 (0.6) & 5930 (1.56) & 6600 (0.78) & -0.01 & 23300 (0.87) & 0.36 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25600 (1.4) & 33800 (1.54) & 5420 (0.88) & 5920 (1.56) & 14200 (1.69) & 0.17 & 34600 (1.29) & 0.43 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 27000 (0.81) & 26200 (0.64) & 4750 (0.52) & 11000 (1.43) & 11200 (0.67) & 0.02 & 39000 (0.83) & 0.14 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 50600 (1.51) & 70000 (1.72) & 10800 (1.18) & 7710 (1) & 32100 (1.93) & 0.13 & 68700 (1.46) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 39200 (0.7) & 38600 (0.52) & 5970 (0.49) & 15600 (1.26) & 17600 (0.56) & 0.07 & 54800 (0.74) & 0.05 & 0.38\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 91700 (1.64) & 135000 (1.83) & 19500 (1.6) & 8990 (0.72) & 63200 (2.02) & 0.09 & 125000 (1.68) & 0.31 & 0.48\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{aggregate-performance-by-location}{%
-\subsection{Aggregate performance by
-location}\label{aggregate-performance-by-location}}
-
-\hypertarget{performance-in-germany}{%
-\subsubsection{Performance in Germany}\label{performance-in-germany}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Germany-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Germany}
-\end{figure}
-
-\hypertarget{performance-in-poland}{%
-\subsubsection{Performance in Poland}\label{performance-in-poland}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Poland-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Poland}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-absolute-terms}{%
-\subsubsection{Performance across locations in absolute
-terms}\label{performance-across-locations-in-absolute-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-v4} \caption{Visualisation of aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-relative-terms}{%
-\subsection{Performance across locations in relative
-terms}\label{performance-across-locations-in-relative-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4} \caption{Visualisation of relative aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals.
-E: Dispersion.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast.
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations-rel}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-daily-reported-cases-and-deaths}{%
-\subsection{Visualisation of daily reported cases and
-deaths}\label{visualisation-of-daily-reported-cases-and-deaths}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily_truth} \caption{Visualisation of daily report data.
-The black line represents weekly data divided by seven.
-Data were last accessed through the German and Polish Forecast Hub on August 21 2021.}\label{fig:daily-truth}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily-data-updates} \caption{Visualisation of the absolute difference between the daily report data at the time and the data now.
-In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:daily-truth-update}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/weekly-data-updates} \caption{Visualisation of the relative difference between the weekly report data at the time and the data now.
-Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:weekly-truth-update}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}{%
-\subsection{Visualisation of scores and forecasts 1, 3, 4 weeks
-ahead}\label{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} \caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} \caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} \caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-4}
-\end{figure}
-
-\clearpage
-
-\hypertarget{distribution-of-scores}{%
-\subsection{Distribution of scores}\label{distribution-of-scores}}
-
-\hypertarget{absolute-scores}{%
-\subsubsection{Absolute scores}\label{absolute-scores}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1} \caption{A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3} \caption{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4} \caption{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-4}
-\end{figure}
-
-\hypertarget{ranks-achieved-by-forecasts}{%
-\subsubsection{Ranks achieved by
-forecasts}\label{ranks-achieved-by-forecasts}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-2}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-4}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} \caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-renewal} \caption{Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences-renewal}
-\end{figure}
-
-\newpage
-
-\hypertarget{comparison-of-ensembles}{%
-\subsection{Comparison of ensembles}\label{comparison-of-ensembles}}
-
-\hypertarget{performance-visualisation-mean-ensemble}{%
-\subsubsection{Performance visualisation mean
-ensemble}\label{performance-visualisation-mean-ensemble}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble”     extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
-Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-mean}
-\end{figure}
-
-\hypertarget{tables-median-ensemble}{%
-\subsubsection{Tables median ensemble}\label{tables-median-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 6970 (0.79) & 8260 (0.71) & 3060 (0.83) & 943 (0.77) & 2970 (0.77) & 0.04 & 10800 (0.85) & 0.55 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 7820 (0.89) & 9630 (0.82) & 3270 (0.89) & 1210 (0.98) & 3330 (0.86) & -0.02 & 12000 (0.94) & 0.48 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 7960 (0.91) & 10300 (0.88) & 3190 (0.87) & 1020 (0.83) & 3760 (0.97) & 0.04 & 12100 (0.95) & 0.57 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 16400 (0.9) & 19600 (0.89) & 5350 (0.87) & 3290 (0.87) & 7730 (0.92) & 0.02 & 24200 (0.9) & 0.43 & 0.69\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 16900 (0.92) & 19600 (0.89) & 5230 (0.85) & 4310 (1.13) & 7370 (0.88) & 0.00 & 24600 (0.92) & 0.38 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 17500 (0.96) & 21400 (0.98) & 5830 (0.95) & 2880 (0.76) & 8770 (1.04) & 0.00 & 25500 (0.95) & 0.45 & 0.71\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 235 (0.95) & 332 (0.98) & 88.6 (0.96) & 90.4 (0.79) & 55.5 (1.33) & -0.01 & 323 (0.97) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 234 (0.94) & 331 (0.98) & 85.2 (0.92) & 98.1 (0.85) & 50.2 (1.21) & -0.05 & 329 (0.99) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 234 (0.94) & 329 (0.97) & 90.7 (0.98) & 118 (1.03) & 25.3 (0.61) & -0.08 & 333 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 239 (0.96) & 337 (1) & 85.2 (0.92) & 99.6 (0.87) & 54.2 (1.3) & -0.03 & 322 (0.96) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 246 (0.99) & 342 (1.01) & 91.5 (0.99) & 106 (0.92) & 48.6 (1.17) & -0.06 & 342 (1.02) & 0.67 & 0.92\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 296 (1.01) & 398 (1.03) & 125 (0.95) & 91 (0.84) & 80.2 (1.55) & 0.05 & 486 (1.13) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 303 (1.04) & 423 (1.1) & 115 (0.87) & 122 (1.13) & 66.1 (1.27) & 0.00 & 483 (1.13) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 270 (0.92) & 385 (1) & 121 (0.92) & 119 (1.1) & 29.9 (0.58) & -0.04 & 403 (0.94) & 0.58 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 303 (1.04) & 392 (1.02) & 122 (0.92) & 106 (0.98) & 74.6 (1.44) & 0.03 & 499 (1.16) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 296 (1.01) & 397 (1.03) & 128 (0.97) & 97.1 (0.9) & 71.2 (1.37) & -0.01 & 462 (1.08) & 0.67 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 30800 (0.92) & 38600 (0.95) & 7910 (0.87) & 6890 (0.9) & 16000 (0.96) & 0.03 & 44200 (0.94) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 30800 (0.92) & 34100 (0.84) & 7500 (0.82) & 8960 (1.17) & 14300 (0.86) & 0.02 & 44100 (0.94) & 0.24 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 34000 (1.02) & 43100 (1.06) & 8860 (0.97) & 6300 (0.82) & 18900 (1.14) & 0.02 & 48100 (1.03) & 0.29 & 0.60\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 51200 (0.92) & 69900 (0.95) & 10900 (0.89) & 11100 (0.9) & 29300 (0.94) & 0.04 & 69600 (0.94) & 0.19 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 48800 (0.87) & 58600 (0.8) & 9700 (0.8) & 13700 (1.1) & 25400 (0.81) & 0.00 & 65800 (0.88) & 0.19 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 59100 (1.06) & 84100 (1.14) & 12600 (1.03) & 10100 (0.81) & 36400 (1.16) & 0.01 & 78900 (1.06) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 332 (1.04) & 388 (1.18) & 158 (0.92) & 78.7 (0.85) & 95 (1.72) & -0.02 & 547 (1.12) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 321 (1.01) & 385 (1.17) & 153 (0.89) & 100 (1.08) & 68.1 (1.24) & -0.01 & 535 (1.1) & 0.54 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 298 (0.93) & 337 (1.03) & 155 (0.9) & 106 (1.14) & 37.5 (0.68) & -0.04 & 441 (0.9) & 0.67 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 319 (1) & 342 (1.04) & 160 (0.93) & 85.1 (0.92) & 73.6 (1.34) & -0.02 & 547 (1.12) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 332 (1.04) & 363 (1.11) & 168 (0.98) & 86.1 (0.93) & 78.2 (1.42) & -0.02 & 528 (1.08) & 0.58 & 0.96\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 445 (1.05) & 532 (1.2) & 193 (0.91) & 107 (0.85) & 144 (1.68) & -0.03 & 700 (1.04) & 0.54 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 399 (0.94) & 438 (0.99) & 195 (0.92) & 105 (0.83) & 97.9 (1.14) & -0.05 & 692 (1.03) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 384 (0.91) & 387 (0.87) & 196 (0.92) & 122 (0.97) & 65.9 (0.77) & -0.06 & 602 (0.89) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 407 (0.96) & 456 (1.03) & 202 (0.95) & 105 (0.83) & 101 (1.18) & -0.03 & 669 (0.99) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 457 (1.08) & 527 (1.19) & 208 (0.98) & 129 (1.02) & 121 (1.41) & -0.06 & 744 (1.1) & 0.50 & 0.96\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\hypertarget{tables-mean-ensemble}{%
-\subsubsection{Tables mean ensemble}\label{tables-mean-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
 \centering
@@
 
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 35600 (1) & 42100 (1) & 9340 (1) & 7050 (1) & 19200 (1) & 0.03 & 51200 (1) & 0.26 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 32100 (0.9) & 40500 (0.96) & 8830 (0.95) & 4920 (0.7) & 18300 (0.95) & 0.07 & 47200 (0.92) & 0.29 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 32200 (0.9) & 36700 (0.87) & 8430 (0.9) & 7190 (1.02) & 16500 (0.86) & 0.04 & 46900 (0.92) & 0.24 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 35200 (0.99) & 46000 (1.09) & 9630 (1.03) & 4600 (0.65) & 20900 (1.09) & 0.08 & 51000 (1) & 0.38 & 0.67\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 60300 (1) & 79300 (1) & 15700 (1) & 10400 (1) & 34100 (1) & 0.04 & 78600 (1) & 0.29 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 55000 (0.91) & 77100 (0.97) & 14600 (0.93) & 6620 (0.64) & 33800 (0.99) & 0.11 & 75200 (0.96) & 0.33 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 53400 (0.89) & 66600 (0.84) & 13700 (0.87) & 10600 (1.02) & 29200 (0.86) & 0.06 & 70400 (0.9) & 0.26 & 0.60\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 61700 (1.02) & 89800 (1.13) & 16400 (1.04) & 6400 (0.62) & 38900 (1.14) & 0.12 & 82900 (1.05) & 0.31 & 0.64\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 289 (1) & 293 (1) & 178 (1) & 45.9 (1) & 65.7 (1) & 0.01 & 443 (1) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 310 (1.07) & 348 (1.19) & 182 (1.02) & 42 (0.92) & 86.5 (1.32) & 0.08 & 502 (1.13) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 315 (1.09) & 339 (1.16) & 178 (1) & 62.2 (1.36) & 74 (1.13) & 0.07 & 507 (1.14) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 297 (1.03) & 292 (1) & 174 (0.98) & 67.7 (1.47) & 55 (0.84) & 0.01 & 452 (1.02) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 294 (1.02) & 299 (1.02) & 172 (0.97) & 48 (1.05) & 74.2 (1.13) & 0.03 & 476 (1.07) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal-mean & 310 (1.07) & 349 (1.19) & 189 (1.06) & 39.4 (0.86) & 81.9 (1.25) & 0.05 & 482 (1.09) & 0.62 & 1.00\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 437 (1) & 568 (1) & 232 (1) & 72 (1) & 134 (1) & 0.00 & 702 (1) & 0.62 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 445 (1.02) & 598 (1.05) & 237 (1.02) & 56.4 (0.78) & 152 (1.13) & 0.06 & 707 (1.01) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 421 (0.96) & 520 (0.92) & 239 (1.03) & 49.9 (0.69) & 132 (0.99) & 0.05 & 678 (0.97) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 398 (0.91) & 465 (0.82) & 235 (1.01) & 55.6 (0.77) & 107 (0.8) & 0.00 & 628 (0.89) & 0.67 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 418 (0.96) & 533 (0.94) & 222 (0.96) & 66.8 (0.93) & 129 (0.96) & 0.03 & 662 (0.94) & 0.58 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal-mean & 467 (1.07) & 636 (1.12) & 248 (1.07) & 61 (0.85) & 158 (1.18) & 0.05 & 755 (1.08) & 0.67 & 1.00\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{sensitivity-analysis}{%
-\subsection{Sensitivity analysis}\label{sensitivity-analysis}}
-
-In the original analysis, cases and deaths were scored on different
-periods, as the convolution model was only added later. This sensitivity
-shows performance of all models restricted to the period from December
-14 2020 until March 1st 2021 where all models were available.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-late}
-\end{figure}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 4980 (0.74) & 5730 (0.64) & 2070 (0.6) & 728 (0.74) & 2190 (0.94) & 0.09 & 7810 (0.82) & 0.54 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 6730 (1) & 8960 (1) & 3430 (1) & 978 (1) & 2330 (1) & -0.09 & 9550 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 9640 (1.43) & 13300 (1.48) & 1970 (0.57) & 4170 (4.26) & 3500 (1.5) & 0.09 & 12700 (1.33) & 0.46 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 10700 (0.99) & 13800 (1.1) & 2880 (0.58) & 2350 (0.85) & 5430 (1.79) & 0.08 & 15400 (1.07) & 0.46 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 10800 (1) & 12500 (1) & 4940 (1) & 2780 (1) & 3030 (1) & -0.13 & 14400 (1) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25000 (2.31) & 34000 (2.72) & 4780 (0.97) & 8710 (3.13) & 11500 (3.8) & 0.05 & 32000 (2.22) & 0.50 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 17200 (1) & 16000 (0.98) & 3800 (0.63) & 5660 (0.85) & 7770 (1.74) & 0.07 & 26800 (1.1) & 0.08 & 0.58\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 17200 (1) & 16300 (1) & 6030 (1) & 6670 (1) & 4470 (1) & -0.16 & 24400 (1) & 0.33 & 0.67\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 37700 (2.19) & 55900 (3.43) & 8840 (1.47) & 10700 (1.6) & 18100 (4.05) & -0.03 & 49800 (2.04) & 0.33 & 0.58\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 26100 (0.95) & 21000 (0.84) & 4810 (0.7) & 11300 (0.83) & 10100 (1.43) & 0.04 & 39400 (1.05) & 0.00 & 0.46\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 27600 (1) & 25000 (1) & 6900 (1) & 13600 (1) & 7060 (1) & -0.19 & 37400 (1) & 0.29 & 0.54\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 48900 (1.77) & 77800 (3.11) & 13800 (2) & 11900 (0.88) & 23200 (3.29) & -0.10 & 65500 (1.75) & 0.38 & 0.58\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{overview-of-models-and-forecasters}{%
-\subsection{Overview of models and
-forecasters}\label{overview-of-models-and-forecasters}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{7.3cm}}
-\caption{\label{tab:table-ensemble-versions}Overview of the models and ensembles used.}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{Overview of the models and ensembles used. \textit{(continued)}}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-\cellcolor{gray!6}{Hub-ensemble-realised} & \cellcolor{gray!6}{Official Forecast Hub median ensemble.
-Created by the Forecast Hub officially under the name 'KITCOVIDhub-median\_ensemble' and used as the default ensemble.
-Included are our crowd forecasts as well as the renewal model (with one missed submission on December 28 2020, but not the convolution model which was deemed to similar to the renewal model.}\\
-\addlinespace \addlinespace
-Hub-ensemble-realised-mean & Official Forecast Hub mean ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-mean\_ensemble'.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{ \vphantom{1}} & \cellcolor{gray!6}{}\\
-\addlinespace \addlinespace
-Hub-ensemble & Version of the official Hub median ensemble which excludes all our contributions.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Hub-ensemble-mean} & \cellcolor{gray!6}{Version of the official Hub mean ensemble which excludes all our contributions.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-renewal, 
-    Hub-ensemble-with-renewal-mean & Versions of the official Hub ensembles which of our contributions includes only the Renewal model.\\
-\addlinespace \addlinespace
-Hub-ensemble-with-crowd, 
-\cellcolor{gray!6}{    Hub-ensemble-with-crowd-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which of our contributions includes only the Crowd forecast.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-convolution, 
-    Hub-ensemble-with-convolution-mean & Versions of the official Hub ensembles which of our contributions includes only the Convolution model (which originally was never included in any official Hub ensemble).\\
-\addlinespace \addlinespace
-Hub-ensemble-with-all, 
-\cellcolor{gray!6}{    Hub-ensemble-with-all-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which includes all our contributions.
-For cases, this is identical to the official Hub ensembles, but for deaths the convolution model was added.}\\
-\addlinespace \addlinespace
- & \\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Crowd forecast} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'}\\
-\addlinespace \addlinespace
-Renewal model & Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Convolution model} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\_secondary'}\\*
-\end{longtable}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/number-forecasters} \caption{Number of participants who submitted a forecast over time.}\label{fig:num-forecasters}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/ensemble-members} \caption{Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
-Note that the renewal model was not included in the ensemble on December 28th 2020.}\label{fig:num-ensemble-members}
-\end{figure}
-
-\clearpage
-
-\hypertarget{comparison-of-crowd-forecasts-and-application-baseline}{%
-\subsection{Comparison of crowd forecasts and application
-baseline}\label{comparison-of-crowd-forecasts-and-application-baseline}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} \caption{Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the median, as well as the 50\% and 90\% prediction intervals (in order of decreasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons).}\label{fig:compare-forecasters}
-\end{figure}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{McGowan CJ, Biggerstaff M, Johansson M, Apfeldorf KM,
-Ben-Nun M, Brooks L, et al. Collaborative efforts to forecast seasonal
-influenza in the {United States}, 2015--2016. Scientific Reports.
-2019;9: 683.
-doi:\href{https://doi.org/10.1038/s41598-018-36361-9}{10.1038/s41598-018-36361-9}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Reich NG, Brooks LC, Fox SJ, Kandula S, McGowan CJ,
-Moore E, et al. A collaborative multiyear, multimodel assessment of
-seasonal influenza forecasting in the {United States}. PNAS. 2019;116:
-3146--3154.
-doi:\href{https://doi.org/10.1073/pnas.1812594116}{10.1073/pnas.1812594116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Shaman J, Karspeck A. Forecasting seasonal outbreaks of
-influenza. PNAS. 2012;109: 20425--20430.
-doi:\href{https://doi.org/10.1073/pnas.1208772109}{10.1073/pnas.1208772109}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Biggerstaff M, Alper D, Dredze M, Fox S, Fung IC-H,
-Hickmann KS, et al. Results from the centers for disease control and
-prevention's predict the 2013--2014 {Influenza Season Challenge}. BMC
-Infectious Diseases. 2016;16: 357.
-doi:\href{https://doi.org/10.1186/s12879-016-1669-x}{10.1186/s12879-016-1669-x}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak
-AL, Baugher B, et al. An open challenge to advance probabilistic
-forecasting for dengue epidemics. PNAS. 2019;116: 24268--24274.
-doi:\href{https://doi.org/10.1073/pnas.1909865116}{10.1073/pnas.1909865116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Yamana TK, Kandula S, Shaman J. Superensemble forecasts
-of dengue outbreaks. Journal of The Royal Society Interface. 2016;13:
-20160410.
-doi:\href{https://doi.org/10.1098/rsif.2016.0410}{10.1098/rsif.2016.0410}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Colón-González FJ, Bastos LS, Hofmann B, Hopkin A,
-Harpham Q, Crocker T, et al. Probabilistic seasonal dengue forecasting
-in {Vietnam}: {A} modelling study using superensembles. PLOS Medicine.
-2021;18: e1003542.
-doi:\href{https://doi.org/10.1371/journal.pmed.1003542}{10.1371/journal.pmed.1003542}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Viboud C, Sun K, Gaffey R, Ajelli M, Fumanelli L, Merler
-S, et al. The {RAPIDD} ebola forecasting challenge: {Synthesis} and
-lessons learnt. Epidemics. 2018;22: 13--21.
-doi:\href{https://doi.org/10.1016/j.epidem.2017.08.002}{10.1016/j.epidem.2017.08.002}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Funk S, Camacho A, Kucharski AJ, Lowe R, Eggo RM,
-Edmunds WJ. Assessing the performance of real-time epidemic forecasts:
-{A} case study of {Ebola} in the {Western Area} region of {Sierra
-Leone}, 2014-15. PLOS Computational Biology. 2019;15: e1006785.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1006785}{10.1371/journal.pcbi.1006785}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Del Valle SY, McMahon BH, Asher J, Hatchett R, Lega JC,
-Brown HE, et al. Summary results of the 2014-2015 {DARPA Chikungunya}
-challenge. BMC Infectious Diseases. 2018;18: 245.
-doi:\href{https://doi.org/10.1186/s12879-018-3124-7}{10.1186/s12879-018-3124-7}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Farrow DC, Brooks LC, Hyun S, Tibshirani RJ, Burke DS,
-Rosenfeld R. A human judgment approach to epidemiological forecasting.
-PLOS Computational Biology. 2017;13: e1005248.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1005248}{10.1371/journal.pcbi.1005248}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Funk S, Abbott S, Atkins BD, Baguelin M, Baillie JK,
-Birrell P, et al. Short-term forecasts to inform the response to the
-{Covid-19} epidemic in the {UK}. medRxiv. 2020; 2020.11.11.20220962.
-doi:\href{https://doi.org/10.1101/2020.11.11.20220962}{10.1101/2020.11.11.20220962}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K,
-et al. {COVID-19 Forecast Hub}: 4 {December} 2020 snapshot. {Zenodo};
-2020.
-doi:\href{https://doi.org/10.5281/zenodo.3963371}{10.5281/zenodo.3963371}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A,
-Rivadeneira AJC, et al. Evaluation of individual and ensemble
-probabilistic forecasts of {COVID-19} mortality in the {US}. medRxiv.
-2021; 2021.02.03.21250974.
-doi:\href{https://doi.org/10.1101/2021.02.03.21250974}{10.1101/2021.02.03.21250974}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. Short-term forecasting of {COVID-19} in {Germany}
-and {Poland} during the second wave -- a preregistered study. medRxiv.
-2021; 2020.12.24.20248826.
-doi:\href{https://doi.org/10.1101/2020.12.24.20248826}{10.1101/2020.12.24.20248826}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. National and subnational short-term forecasting of
-{COVID-19} in {Germany} and {Poland}, early 2021. 2021;
-2021.11.05.21265810.
-doi:\href{https://doi.org/10.1101/2021.11.05.21265810}{10.1101/2021.11.05.21265810}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-europeancovid-19forecasthubEuropeanCovid19Forecast2021}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{European Covid-19 Forecast Hub. European {Covid-19
-Forecast Hub}. 2021 {[}cited 30 May 2021{]}. Available:
-\url{https://covid19forecasthub.eu/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichAccuracyRealtimeMultimodel2019}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Reich NG, McGowan CJ, Yamana TK, Tushar A, Ray EL,
-Osthus D, et al. Accuracy of real-time multi-model ensemble forecasts
-for seasonal influenza in the {U}.{S}. PLOS Computational Biology.
-2019;15: e1007486.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1007486}{10.1371/journal.pcbi.1007486}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Tetlock PE, Mellers BA, Rohrbaugh N, Chen E. Forecasting
-{Tournaments}: {Tools} for {Increasing Transparency} and {Improving} the
-{Quality} of {Debate}. Curr Dir Psychol Sci. 2014;23: 290--295.
-doi:\href{https://doi.org/10.1177/0963721414534257}{10.1177/0963721414534257}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Atanasov P, Rescober P, Stone E, Swift SA,
-Servan-Schreiber E, Tetlock P, et al. Distilling the {Wisdom} of
-{Crowds}: {Prediction Markets} vs. {Prediction Polls}. Management
-Science. 2016;63: 691--706.
-doi:\href{https://doi.org/10.1287/mnsc.2015.2374}{10.1287/mnsc.2015.2374}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers E-J. Laypeople
-{Can Predict Which Social-Science Studies Will Be Replicated
-Successfully}. Advances in Methods and Practices in Psychological
-Science. 2020;3: 267--285.
-doi:\href{https://doi.org/10.1177/2515245920919667}{10.1177/2515245920919667}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{ReplicationMarkets. Replication {Markets} -- {Reliable}
-research replicates\ldots you can bet on it. 2020 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.replicationmarkets.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Servan-Schreiber E, Wolfers J, Pennock DM, Galebach B.
-Prediction {Markets}: {Does Money Matter}? Electronic Markets. 2004;14:
-243--251.
-doi:\href{https://doi.org/10.1080/1019678042000245254}{10.1080/1019678042000245254}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{McAndrew TC, Reich NG. An expert judgment model to
-predict early stages of the {COVID-19} outbreak in the {United States}.
-medRxiv. 2020; 2020.09.21.20196725.
-doi:\href{https://doi.org/10.1101/2020.09.21.20196725}{10.1101/2020.09.21.20196725}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Recchia G, Freeman ALJ, Spiegelhalter D. How well did
-experts and laypeople forecast the size of the {COVID-19} pandemic? PLOS
-ONE. 2021;16: e0250935.
-doi:\href{https://doi.org/10.1371/journal.pone.0250935}{10.1371/journal.pone.0250935}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Metaculus. A {Preliminary Look} at {Metaculus} and
-{Expert Forecasts}. 22 Jun 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.metaculus.com/news/2020/06/02/LRT/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Hypermind. Hypermind \textbar{} {Supercollective}
-intelligence for decision makers. {Hypermind}; 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.hypermind.com/en/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{CSET Foretell. {CSET Foretell}. 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.cset-foretell.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{PredictIt. {PredictIt}. 2021 {[}cited 13 Oct 2021{]}.
-Available: \url{https://www.predictit.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Held L, Meyer S, Bracher J. Probabilistic forecasting in
-infectious disease epidemiology: The 13th {Armitage} lecture. Statistics
-in Medicine. 2017;36: 3443--3460.
-doi:\href{https://doi.org/10.1002/sim.7363}{10.1002/sim.7363}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Crowdforecastr: Eliciting crowd forecasts in r shiny. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618519}{10.5281/zenodo.4618519}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Covid.german.forecasts: Forecasting covid-19 related metrics for the
-german/poland forecast hub. 2020. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-ecdcDownloadHistoricalData2020}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{ECDC. Download historical data (to 14 {December} 2020)
-on the daily number of new reported {COVID-19} cases and deaths
-worldwide. {European Centre for Disease Prevention and Control}; 14 Dec
-2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rkiRKICoronavirusSARSCoV22021}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{RKI. {RKI} - {Coronavirus SARS-CoV-2} - {Aktueller
-Lage-}/{Situationsbericht} des {RKI} zu {COVID-19}. 2021 {[}cited 30 May
-2021{]}. Available:
-\url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-forsal.plRozbieznosciStatystykachKoronawirusa2020}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Forsal.pl. Rozbieżności w statystykach koronawirusa. 22
-tys. przypadków będą doliczone do ogólnej liczby wyników. 2020 {[}cited
-30 May 2021{]}. Available:
-\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Ärzteblatt DÄG Redaktion Deutsches.
-SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an. {Deutsches
-Ärzteblatt}; 3 Nov 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Fay C, Guyader V, Rochette S, Girard C. Golem: A
-framework for robust shiny applications. 2021. Available:
-\url{https://github.com/ThinkR-open/golem}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie
-Y, et al. Shiny: Web application framework for r. 2021. Available:
-\url{https://CRAN.R-project.org/package=shiny}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Our World in Data. {COVID-19 Data Explorer}. {Our World
-in Data}; 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://ourworldindata.org/coronavirus-data-explorer}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K,
-Ellis P, et al. EpiNow2: Estimate real-time case counts and time-varying
-epidemiological parameters. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957489}{10.5281/zenodo.3957489}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Fraser C. Estimating {Individual} and {Household
-Reproduction Numbers} in an {Emerging Epidemic}. PLOS ONE. 2007;2: e758.
-doi:\href{https://doi.org/10.1371/journal.pone.0000758}{10.1371/journal.pone.0000758}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation2020}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{epiforecasts.io/covid. Covid-19: {Temporal} variation in
-transmission during the {COVID-19} outbreak. {Covid-19}; 2020 {[}cited
-30 May 2021{]}. Available: \url{https://epiforecasts.io/covid/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Sherratt K, Abbott S, Meakin SR, Hellewell J, Munday JD,
-Bosse N, et al. Exploring surveillance data biases when estimating the
-reproduction number: With insights into subpopulation transmission of
-{Covid-19} in {England}. 2021; 2020.10.18.20214585.
-doi:\href{https://doi.org/10.1101/2020.10.18.20214585}{10.1101/2020.10.18.20214585}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abbottEstimatingTimevaryingReproduction2020a}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs
-HP, Bosse NI, et al. Estimating the time-varying reproduction number of
-{SARS-CoV-2} using national and subnational case counts. 2020 {[}cited
-14 Oct 2021{]}.
-doi:\href{https://doi.org/10.12688/wellcomeopenres.16006.1}{10.12688/wellcomeopenres.16006.1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Xu B, Gutierrez B, Hill S, Scarpino S, Loskill A, Wu J,
-et al. Epidemiological data from the nCoV-2019 outbreak: Early
-descriptions from publicly available data. 2020. Available:
-\url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Stan Development Team. RStan: The r interface to stan.
-2020. Available: \url{http://mc-stan.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG. Evaluating
-epidemic forecasts in an interval format. PLoS Comput Biol. 2021;17:
-e1008618.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1008618}{10.1371/journal.pcbi.1008618}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Gneiting T, Raftery AE. Strictly proper scoring rules,
-prediction, and estimation. Journal of the American Statistical
-Association. 2007;102: 359--378.
-doi:\href{https://doi.org/10.1198/016214506000001437}{10.1198/016214506000001437}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Scoringutils:
-Utilities for scoring and assessing predictions. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618017}{10.5281/zenodo.4618017}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-deutschewelleCoronavirusGermanyImpose2020}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Deutsche Welle. Coronavirus: {Germany} to impose
-one-month partial lockdown \textbar{} {DW} \textbar{} 28.10.2020. 2020
-{[}cited 29 Jun 2021{]}. Available:
-\url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Ganyani T, Kremer C, Chen D, Torneri A, Faes C, Wallinga
-J, et al. Estimating the generation interval for coronavirus disease
-(COVID-19) based on symptom onset data, march 2020. Eurosurveillance.
-2020;25. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith
-HR, et al. The incubation period of coronavirus disease 2019 (COVID-19)
-from publicly reported confirmed cases: Estimation and application.
-Annals of Internal Medicine. 2020;172: 577--582. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J,
-Munday J, et al. Covidregionaldata: Subnational data for the covid-19
-outbreak. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957539}{10.5281/zenodo.3957539}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Evaluating the use of the reproduction number as an
-epidemiological tool, using spatio-temporal trends of the {Covid-19}
-outbreak in {England} \textbar{} {medRxiv}. {[}cited 30 May 2021{]}.
-Available:
-\url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Riutort-Mayol G, Bürkner P-C, Andersen MR, Solin A,
-Vehtari A. Practical hilbert space approximate bayesian gaussian
-processes for probabilistic programming. 2020. Available:
-\url{https://arxiv.org/abs/2004.11408}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Scott JA, Gandy A, Mishra S, Unwin J, Flaxman S, Bhatt
-S. Epidemia: Modeling of epidemics using hierarchical bayesian models.
-2020. Available:
-\url{https://imperialcollegelondon.github.io/epidemia/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bhattSemiMechanisticBayesianModeling}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Bhatt S, Ferguson N, Flaxman S, Gandy A, Mishra S, Scott
-JA. Semi-{Mechanistic Bayesian} modeling of {COVID-19} with {Renewal
-Processes}. : 14. }
-
-\end{CSLReferences}
-
-\nolinenumbers
-
 \end{document}

### 2023-12-11 manuscript/final submission/Supplementary/S7-Table.tex

--- 2022-06-02 manuscript/manuscript.tex
@@
 \usepackage{xcolor}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 
-\usepackage{forarray}
-\usepackage{xstring}
-\newcommand{\getIndex}[2]{
-  \ForEach{,}{\IfEq{#1}{\thislevelitem}{\number\thislevelcount\ExitForEach}{}}{#2}
-}
-
-\setcounter{secnumdepth}{0}
-
-\newcommand{\getAff}[1]{
-  \getIndex{#1}{London School of Hygiene \& Tropical Medicine,Karlsruhe
-Institute of Technology Institute of Economic Theory and Statistics,Max
-Planck Institute for Multidisciplinary Sciences,UK Health Security
-Agency,Imperial College London}
-}
+\author{}
+\date{\vspace{-2.5em}}
 
 \begin{document}
-\vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{Comparing human and model-based forecasts of COVID-19 in
-Germany and
-Poland} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Nikos I. Bosse\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\textsuperscript{*},
-Sam Abbott\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Johannes Bracher\textsuperscript{\getAff{Karlsruhe Institute of
-Technology Institute of Economic Theory and Statistics}},
-Habakuk Hain\textsuperscript{\getAff{Max Planck Institute for
-Multidisciplinary Sciences}},
-Billy J. Quilty\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Mark Jit\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Edwin van Leeuwen\textsuperscript{\getAff{UK Health Security
-Agency}, \getAff{London School of Hygiene \& Tropical Medicine}},
-Anne Cori\textsuperscript{\getAff{Imperial College London}},
-Sebastian Funk\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\\
-\bigskip
-\textbf{\getAff{London School of Hygiene \& Tropical Medicine}}London
-School of Hygiene \& Tropical Medicine, Keppel Street, London WC1E7HT,
-United Kingdom\\
-\textbf{\getAff{Karlsruhe Institute of Technology Institute of Economic
-Theory and Statistics}}Karlsruhe Institute of Technology - Institute of
-Economic Theory and Statistics, Post Box 6980, 76049 Karlsruhe,
-Germany\\
-\textbf{\getAff{Max Planck Institute for Multidisciplinary Sciences}}Max
-Planck Institute for Multidisciplinary Sciences, Am Faßberg 11, 37077
-Göttingen, Germany\\
-\textbf{\getAff{UK Health Security Agency}}UK Health Security Agency,
-London NW9 5EQ, United Kingdom\\
-\textbf{\getAff{Imperial College London}}Imperial College London,
-Norfolk Place, London W2 1PG, United Kingdom\\
-\bigskip
-* Corresponding author: nikos.bosse@lshtm.ac.uk\\
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-Forecasts based on epidemiological modelling have played an important
-role in shaping public policy throughout the COVID-19 pandemic. This
-modelling combines knowledge about infectious disease dynamics with the
-subjective opinion of the researcher who develops and refines the model
-and often also adjusts model outputs. Developing a forecast model is
-difficult, resource- and time-consuming. It is therefore worth asking
-what modelling is able to add beyond the subjective opinion of the
-researcher alone. To investigate this, we analysed different real-time
-forecasts of cases of and deaths from COVID-19 in Germany and Poland
-over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
-We compared crowd forecasts elicited from researchers and volunteers,
-against a) forecasts from two semi-mechanistic models based on common
-epidemiological assumptions and b) the ensemble of all other models
-submitted to the Forecast Hub. We found crowd forecasts, despite being
-overconfident, to outperform all other methods across all forecast
-horizons when forecasting cases (weighted interval score relative to the
-Hub ensemble 2 weeks ahead: 0.89). Forecasts based on computational
-models performed comparably better when predicting deaths (rel. WIS
-1.26), suggesting that epidemiological modelling and human judgement can
-complement each other in important ways.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step.
-% Author Summary not valid for PLOS ONE submissions.
-\section*{Author summary}
-Mathematical models of COVID-19 have played a key role in informing
-governments across the world. While mathematical models are informed by
-our knowledge of infectious disease dynamics, they are ultimately
-developed and iteratively adjusted by the researchers and shaped by
-their subjective opinions. To investigate what modelling is able to add
-beyond the subjective opinion of the researcher alone, we compared human
-forecasts with model-based predictions of COVID-19 cases and deaths
-submitted to the so-called German/Polish Forecast Hub (which collates a
-variety of models from a range of teams). \textbar{} We found that our
-human forecasts consistently outperformed an aggregate of all available
-model-based forecasts when predicting cases, but not when predicting
-deaths. Our findings suggest that human insight may be most valuable
-when forecasting highly uncertain quantities, which depend on many
-factors that are hard to model using equations, while mathematical
-models may be most useful in settings like predicting deaths, where
-leading indicators with a clear connection to the target variable are
-available. This potentially has very relevant policy implications, as
-agencies informing policy-makers could benefit from routinely eliciting
-human forecasts in addition to model-based predictions to inform
-policies.
-
-\linenumbers
-
-% Use "Eq" instead of "Equation" for equation citations.
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Infectious disease modelling has a long tradition and has helped inform
-public health decisions both through scenario modelling, as well as
-actual forecasts of (among others) influenza {[}e.g. 1,2--4{]}, dengue
-fever {[}e.g. 5,6,7{]}, ebola {[}e.g. 8,9{]}, chikungunya {[}e.g.
-10,11{]} and now COVID-19 {[}e.g. 12,13--17{]}. Applications of
-epidemiological models differ in the way they make statements about the
-future. Forecasts aim to predict the future as it will occur, while
-scenario modelling and projections aim to represent what the future
-could look like under certain scenario assumptions or if conditions
-stayed the same as they were in the past. Forecasts can be judged by
-comparing them against observed data. Since it is much harder to fairly
-assess the accuracy and usefulness of projections and scenario modelling
-in the same way, this work focuses on forecasts, which represent only a
-subset of all epidemiological modelling.
-
-Since March 2020, forecasts of COVID-19 from multiple teams have been
-collected, aggregated and compared by Forecast Hubs such as the US
-Forecast Hub {[}13,14{]}, the German and Polish Forecast Hub {[}15,16{]}
-and the European Forecast Hub {[}17{]}. Often, different individual
-forecasts are combined into a single forecast, e.g.~by taking the mean
-or median of all forecasts. These ensemble forecasts usually tend to
-perform better and more consistently than individual forecasts (see e.g.
-{[}6{]}; {[}18{]}).
-
-Individual computational models usually rely to varying degrees on
-mechanistic assumptions about infectious disease dynamics (such as
-SIR-type compartmental models that aim to represent how individuals move
-from being susceptible to infected and then recovered or dead). Some are
-more statistical in nature (such as time series models that detect
-statistical patterns without explicitly modelling disease dynamics). How
-exactly such a mathematical or computational model is constructed and
-which assumptions are made depends on subjective opinion and judgement
-of the researcher who develops and refines the model. Models are
-commonly adjusted and improved based on whether the model output looks
-plausible to the researchers involved.
-
-The process of model construction and refinement is laborious and
-time-consuming, and it is therefore worth asking what modelling can add
-beyond the subjective judgment of the researcher alone. In this work, we
-ask this question specifically in the context of predictive performance,
-and set aside other advantages of epidemiological modelling (such as
-reproducibility or the ability to obtain a deeper fundamental
-understanding of how diseases spread). One natural way to do this is to
-compare the predictive performance of forecasts based on computational
-models (``model-based forecasts'') against forecasts made by individual
-humans without explicit use of a computer model (``direct human
-forecasts'') or a combination of multiple such forecasts (``crowd
-forecasts'').
-
-Previous work has examined such direct human forecasts in various
-contexts, such as geopolitics {[}19,20{]}, meta-science {[}21,22{]},
-sports {[}23{]} and epidemiology {[}11,24,25{]}. Several prediction
-platforms {[}26--28{]} and prediction markets {[}29{]} have been created
-to collate expert and non-expert predictions. However, with the notable
-exception of {[}11{]}, these forecasts were not designed to be evaluated
-alongside model-based forecasts and usually follow their own (often
-binary) prediction formats. Direct human forecasts may be able to take
-into account insights and relationships between variables which are hard
-to specify using epidemiological models. However, it is not entirely
-clear in which situations human forecasts perform well or badly. For
-example, {[}11{]} found that humans could outperform computer models at
-predicting the 2014/15 and 2015/16 flu season in the US, a setting where
-the disease was well known and information about previous seasons was
-available. However, humans tended to do slightly worse at predicting the
-2014/15 outbreak of chikungunya in the Americas, a disease previously
-largely unobserved and unknown in these regions at the time.
-
-In this study, we analyse the performance of direct human forecasts
-relative to model-based forecasts and discuss the added benefit of
-epidemiological modelling over human judgement alone. As a case study,
-we use different forecasts, involving varying degrees of human
-intervention, which we submitted in real time to the German and Polish
-Forecast Hub. In contrast to {[}11{]} we elicited not only point
-predictions, but full predictive distributions (``probabilistic
-forecasts'', see e.g. {[}30{]}) from participants. This allows us to
-compare not only predictive accuracy, but also how well human
-forecasters and model-based forecasts were able to quantify forecast
-uncertainty.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-We created and submitted the following forecasts to the German and
-Polish Forecast Hub: 1) a direct human forecast (henceforth called
-``crowd forecast''), elicited from participants through a web
-application {[}31{]} and 2) two semi-mechanistic model-based forecasts
-(``renewal model'' and ``convolution model'') informed by basic
-assumptions about COVID-19 epidemiology. While the two semi-mechanistic
-forecasts were necessarily shaped by our implicit assumptions and
-decisions, they were designed such as to minimise the amount of human
-intervention involved. For example, we refrained from adjusting model
-outputs or refining the models based on past performance. Forecasts were
-created in real time over a period of 21 weeks from October 12th 2020
-until March 1st 2021 and submitted to the German and Polish Forecast hub
-{[}15,16{]}. All code and tools necessary to generate the forecasts and
-make a forecast submission are available in the
-\texttt{covid.german.forecasts} R package {[}32{]}. This repository also
-contains a record of all forecasts submitted to the German and Polish
-Forecast Hub. Forecasts were evaluated using a variety of scoring
-metrics and compared among each other and against an ensemble of all
-other models submitted to the German and Polish Forecast Hub.
-
-\hypertarget{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}{%
-\subsection{Forecast targets and interaction with the German and Polish
-Forecast
-Hub}\label{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}}
-
-The German and Polish Forecast Hub (now mostly merged into the {[}17{]})
-elicits predictions for various COVID-19 related forecast targets from
-different research groups every week. Forecasts had to be made every
-Monday (with submissions allowed until Tuesday 3pm) and were permitted
-to use any data that was available by Monday 11.59pm. We submitted
-forecasts for incident and cumulative weekly reported numbers of cases
-of and deaths from COVID-19 on a national level in Germany and Poland
-over a one to four week forecast horizon. Forecasts were submitted on
-Mondays, but weeks were defined as ending on a Saturday (and starting on
-Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26
-days. Submissions were required in a quantile-based format with 23
-quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10,
-0.15, \ldots, 0.95, 0.975, 0.99. Forecasts submitted to the Forecast Hub
-were combined into different ensembles every week, with the median
-ensemble (i.e., the \(\alpha\)-quantile of the ensemble is given by the
-median of all submitted \(\alpha\)-quantiles) being the default ensemble
-shown on all official Forecast hub visualisations
-(https://kitmetricslab.github.io/forecasthub/forecast).
-
-Data on daily reported test positive cases and deaths linked to COVID-19
-were provided by the organisers of the German and Polish Forecast hub.
-Until December 14th, 2020, these data were sourced from the European
-Centre for Disease Control {[}33{]}. After ECDC stopped publishing daily
-data, observations were sourced from the Robert Koch Institute (RKI) and
-the Polish Ministry of Health for the remainder of the submission period
-{[}34{]}. These data are subject to reporting artefacts, (such as for
-example delayed case reporting in Poland on the 24th November,
-{[}35{]}), changes in reporting over time, and variation in testing
-regimes (for example in Germany from the 11th of November on, {[}36{]}).
-The ECDC data as well as the data published by the Polish Ministry of
-Health were also subject to data revisions, although most of them (with
-a notable exception of a data update for October 12 2020 in Germany)
-only affected daily, not weekly data (see Figures
-\ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).
-
-\hypertarget{crowd-forecasts}{%
-\subsection{Crowd forecasts}\label{crowd-forecasts}}
-
-Our crowd forecasts were created as an ensemble of forecasts made by
-individual participants every week through a web application
-(https://cmmid-lshtm.shinyapps.io/crowd-forecast/). Weekly forecasts had
-to be submitted before Tuesday 12pm every week, but participants were
-asked to only use any information or data that was already available by
-Monday night. The application was built using the \texttt{shiny} and
-\texttt{golem} R packages {[}37,38{]} and is available in the
-\texttt{crowdforecastr} R package {[}31{]}. To make a forecast in the
-application participants could select a predictive distribution (with
-the default being log-normal) to represent the probability that the
-forecasted quantity took certain values. Median and width of the
-uncertainty could be adjusted by either interacting with a figure
-showing their forecast or providing numerical values (see screenshot in
-Figure \ref{fig:screenshot} in the SI). The default shown was a
-repetition of the last known observation with constant uncertainty
-around it computed as the standard deviation of the last four changes in
-weekly log observed forecasts (i.e.~as
-\(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
-A comparison of the crowd forecasts against the default baseline shown
-in the application is displayed in Figure \ref{fig:compare-forecasters}
-in the Appendix. Our interface also allowed participants to view past
-observations based on the hub data, as well as their forecasts, on a
-logarithmic scale and presented additional contextual COVID-19 data
-sourced from {[}39{]}. These data included, for example, notifications
-of both test positive COVID-19 cases and COVID-19 linked deaths and the
-number of COVID-19 tests conducted over time. From November 26 2020 on
-we displayed weekly small reports with a visualisation of past forecasts
-and scores on our website, epiforecasts.io.
-
-Forecasts were stored in a Google Sheet and downloaded, cleaned and
-processed every week for submission to the Forecast Hub. If a forecaster
-had submitted multiple predictions for a single target, only the latest
-submission was kept. Information on the chosen distribution as well as
-the parameters for median and width were used to obtain the required set
-of 23 quantiles from that distribution. Forecasts from all forecasters
-were then aggregated using an unweighted quantile-wise mean (i.e., the
-\(\alpha\)-quantile of the ensemble is given by the mean of all
-submitted \(\alpha\)-quantiles). To avoid issues with users trying out
-the app and submitting a random forecast, we required that a forecaster
-needed to make a forecast for at least two targets for a given forecast
-in order to be included in the crowd forecast ensemble. On a few
-occasions we deleted forecasts that were clearly the result of a user or
-software error (such as for example forecasts that were zero
-everywhere).
-
-individual forecasts were assessed as clearly erroneous by visual
-inspection and subsequently removed before aggregation and were excluded
-from the submission as well as the analysis.
-
-Participants were recruited mostly within the Centre of Mathematical
-Modeling of Infectious Diseases at the London School of Hygiene \&
-Tropical Medicine, but participants were also invited personally or via
-social media to submit predictions. Depending on whether they had a
-background in either statistics, forecasting or epidemiology,
-participants were asked to self-identify as `experts' or `non-experts'.
-
-The study was approved by the Observational / Interventions Research
-Ethics Committee at the London School of Hygiene \& Tropical Medicine,
-LSHTM Ethics Reference: 22290. Formal consent from participants was
-taken in written form through the web application.
-
-\hypertarget{model-based-forecasts}{%
-\subsection{Model-based forecasts}\label{model-based-forecasts}}
-
-We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R
-package (version 1.3.3) as our model-based forecasts {[}40{]}. The first
-of these models, here called ``renewal model'', used the renewal
-equation {[}41{]} to predict reported cases and deaths (see details in
-the SI). It estimated the effective reproduction number \(R_t\) (the
-average number of people each person infected at time t is expected to
-infect in turn) and modelled future infections as a weighted sum of past
-infection multiplied by \(R_t\). \(R_t\) was assumed to stay constant
-beyond the forecast date, roughly corresponding to continuing the latest
-exponential trend in infections. On the 9th of November we altered the
-date when \(R_t\) was assumed to be constant from two weeks prior to the
-date of the forecast to the forecast date, which we found to yield a
-more stable \(R_t\) estimate. Reported case and death notifications were
-obtained by convolving predicted infections over data-based delay
-distributions {[}40,42--44{]} to model the time between infection and
-report date. The renewal model was used to predict cases as well as
-deaths with forecasts being generated for each target separately. Death
-forecasts from the renewal model were therefore not informed by past
-cases. One submission of the renewal model on December 28th 2020 was
-delayed and therefore not included in the official Forecast hub
-ensemble.
-
-The second model (``convolution model'', see details in SI) was only
-used to forecast deaths and was added later, starting December 7th 2020
-(with the first forecast from December 7th suffering from a software bug
-and therefore disregarded in all further analyses). The convolution
-model was submitted, but never included in the official Forecast hub
-ensemble due to concerns that it could be too similar to the renewal
-model. The convolution model predicted deaths as a fraction of infected
-people who would die with some delay, by using a convolution of reported
-cases with a distribution that described the delay from case report to
-death and a scaling factor (the case-fatality ratio). Both the renewal
-and the convolution model used daily observations and assumed a negative
-binomial observation model with a multiplicative day-of-the-week effect
-{[}40{]}.
-
-Line list data used to inform the prior for the delay from symptom onset
-to test positive case report or death in the model-based forecasts was
-sourced from {[}45{]} with data available up to the 1st of August. All
-model fitting was done using Markov-chain Monte Carlo (MCMC) in stan
-{[}46{]} with each location and forecast target being fitted separately.
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-For the main analysis we focused mostly on two week ahead forecasts, as
-COVID-19 forecasts, especially for cases, were in the past found to have
-poor predictive performance beyond this horizon {[}15{]}. Forecasts for
-cases were scored using the full period from October 2020 until March
-2021. To ensure comparability between models, all death forecasts were
-scored using only the period from December 14th on, where all models
-including the convolution model were available. To ensure robustness of
-our results we conducted a sensitivity analysis where all forecasts
-(including cases) were scored only over the later period for which all
-forecasts were available (see Section \ref{sensitivity-analysis} in the
-SI). Results remained broadly unchanged.
-
-Forecasts were analysed using the following scoring metrics: The
-weighted interval score (WIS) {[}47{]}, the absolute error, relative
-bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule {[}48{]}, meaning that in expectation
-the score is optimised by reporting a predictive distribution that is
-identical to the true data-generating distribution. Forecasters are
-therefore incentivised to report their true belief about the future. The
-WIS can be understood as a generalisation of the absolute error to
-quantile-based forecasts (also meaning that smaller values are better)
-and can be decomposed into three separate penalties: forecast spread
-(i.e.~uncertainty of forecasts), over-prediction and under-prediction.
-While the over- and under-prediction components of the WIS capture the
-amount of over-prediction and under-prediction in absolute terms, we
-also look at a relative tendency to make biased forecasts. The bias
-metric {[}9{]} we use captures how much probability mass of the forecast
-was above or below the true value (mapped to values between -1 and 1)
-and therefore represents a general tendency to over- or under-predict in
-relative terms. A value of -1 implies that all quantiles of the
-predictive distribution are below the observed value and a value of 1
-that all quantiles are above the observed value. Empirical coverage is
-the percentage of observed values that fall inside a given prediction
-interval (e.g.~how many observed values fall inside all 50\% prediction
-intervals). Scoring metrics are explained in more detail in Table
-\ref{tab:scoring-metrics} in the SI. All scores were calculated using
-the \texttt{scoringutils} R package {[}49{]}.
-
-At all stages of the evaluation our forecasts were compared to the
-median ensemble of all \emph{other} models submitted to the German and
-Polish Forecast Hub (``Hub ensemble''). This ``Hub ensemble'' was
-retrospectively computed and excludes all our models, leaving on average
-five ensemble member models (see details in Section
-\ref{contributions-hub}, as well as in Table
-\ref{tab:table-ensemble-versions} and Figure
-\ref{fig:num-ensemble-members} in the SI). What we call ``Hub ensemble''
-in this article therefore differs from the ``official Hub ensemble''
-(here called ``hub-ensemble-realised'') which included crowd forecasts
-as well as renewal model forecasts. To enhance interpretability of
-scores we mainly report WIS relative to the Hub ensemble in the main
-text, i.e.~we divided the average scores for a given model by the
-average score achieved by the Hub ensemble on the same set of forecasts
-(with values \textgreater1 implying worse and values \textless1 implying
-better performance than the Hub ensemble). In addition to comparing our
-forecasts against the hub ensemble excluding our models, we also
-assessed the impact of our forecasts on the performance of the
-forecasting hub by recalculating separate versions of the Hub ensemble
-with only some (or all) of our forecasts included. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{crowd-forecast-participation}{%
-\subsection{Crowd forecast
-participation}\label{crowd-forecast-participation}}
-
-A total number of 32 participants submitted forecasts, 17 of those
-self-identified as `expert' in either forecasting or epidemiology. The
-median number of forecasters for any given forecast target was 6, the
-minimum 2 and the maximum 10. The mean number of submissions from an
-individual forecaster was 4.7 but the median number was only one - most
-participants dropped out after their first submission. Only two
-participants submitted a forecast every single week, both of whom are
-authors on this study.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} \caption{Two week ahead forecasts and corresponding scores.
-A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth}
-\end{figure}
-
-\hypertarget{case-forecasts}{%
-\subsection{Case Forecasts}\label{case-forecasts}}
-
-For cases, crowd forecasts had a lower mean weighted interval score
-(WIS, lower values indicate better performance) than both the renewal
-model and the Hub ensemble across all forecast horizons (Figure
-\ref{fig:agg-performance-all}A) and locations (Figure
-\ref{fig:performance-locations-rel}A). For two week ahead forecasts,
-mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts
-and 1.40 for the renewal model (Table \ref{tab:score-table-2}). Across
-all forecasting approaches, locations and forecast horizons, the
-distribution of WIS values was very right-skewed, and average
-performance was heavily influenced by outliers (Figure
-\ref{fig:distribution-scores}). Overall, low variance in forecast
-performance was closely linked with good mean performance (Figures
-\ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A),
-suggesting that the ability to avoid large errors was an important
-factor in determining overall performance. The impact of outlier values
-was especially pronounced for the renewal model, which had more outliers
-(Figure \ref{fig:distribution-scores}), as well as the highest standard
-deviation of WIS values (standard deviation of the WIS relative to the
-WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon),
-while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub
-ensemble (= 1) showed more stable performance.
-
-To varying degrees, all forecasts exhibited trend-following behaviour
-and were rarely able to predict a change in trend before it had
-happened. For example, all forecasts failed to predict the change in
-trend from increase to decrease that happened in November in Germany and
-severely overshot reported cases (Figure
-\ref{fig:forecasts-and-truth}A). This was most striking for the renewal
-model, which extrapolated unconstrained exponential growth based on the
-recent past of observations. The Hub ensemble and the crowd forecast,
-which had both been under-predicting throughout October, also failed to
-predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on
-November 2nd 2020 {[}50{]} and the change in the testing regime (with
-stricter test criteria) on November 11th 2020 {[}36{]}, were fastest to
-adapt to the new trend, and the Hub ensemble slowest. In December, cases
-rose again in Germany, with all models under-predicting this growth to
-varying extents. As in October, the renewal model captured the phase of
-exponential growth in cases slightly better than other approaches, but
-again overshot when reported case numbers fell over Christmas. The large
-variance in predictions in January in Germany (severe under-prediction
-followed by severe over-prediction) may in part be caused by the fact
-that the renewal model operated on daily data and therefore was
-susceptible to fluctuations in daily reporting around Christmas that
-would not have influenced on weekly reporting. Similar trends in
-performance were evident in Poland, with the crowd forecast quickest at
-adapting to the change in trend in November. In general, there were
-fewer large outlier forecasts in Poland and in particular the renewal
-model performed more in line with other forecasts there.
-
-All forecasting approaches, including the Hub ensemble, were
-overconfident, i.e.~they showed lower than nominal coverage (meaning
-that 50\% (90\%) prediction intervals generally covered less than 50\%
-(90\%) of the actually observed values) (Figure
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
-Coverage for all forecasts deteriorated with increasing forecast
-horizon, indicating that all forecasting approaches struggled to
-quantify uncertainty appropriately for case forecasts. This was
-especially an issue for crowd forecasts, which had markedly shorter
-prediction intervals (i.e., narrower and more confident predictive
-distributions) than other approaches (Figure
-\ref{fig:agg-performance-all}E) and only showed a small increase in
-uncertainty across forecast horizons. The crowd forecasts prediction
-intervals were also noticeably narrower than the default baseline shown
-to forecasters in the application (see Figure
-\ref{fig:compare-forecasters}).
-
-In spite of good performance in terms of the absolute error (Figure
-\ref{fig:agg-performance-all}G), the narrow forecast intervals led to
-forecasts which were severely overconfident (covering only 36\% and 55\%
-of all observations with the 50\% and 90\% prediction intervals of all
-forecasts made at a two week forecast horizon, and only 5\% and 38\%
-four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables
-\ref{tab:score-table-2} and \ref{tab:score-table-4}). Despite worse
-performance in terms of absolute error (Figure
-\ref{fig:agg-performance-all}G), the renewal model achieved better
-calibration (comparable to the Hub ensemble), as uncertainty increased
-rapidly across forecast horizons. The crowd forecasts, on the other
-hand, showed a smaller bias than the renewal model, but were
-overconfident.
-
-The renewal model exhibited a noticeable tendency towards
-over-predicting reported cases across all horizons. The crowd forecast
-tended to over-predict at longer forecast horizons, whereas the Hub
-ensemble showed no systematic bias (Figure
-\ref{fig:agg-performance-all}F). Regardless of a general relative
-tendency to over-predict, all forecasting approaches incurred larger
-absolute penalties from over- than from under-prediction (see
-decomposition of the WIS into absolute penalties for over-prediction,
-under-prediction and dispersion in Figures
-\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
-
-Generally, trends in overall performance were broadly similar across
-locations (Figures \ref{fig:performance-locations} and
-\ref{fig:performance-locations-rel}). Due to the differing population
-sizes and numbers of notifications in Germany and Poland absolute scores
-were difficult to compare directly. However, relative to the Hub
-ensemble, the crowd forecasts performed noticeably better in Germany
-than in Poland and the renewal model better in Poland than in Germany
-(Figures \ref{fig:performance-locations-rel}A,
-\ref{fig:performance-locations-rel}G,
-\ref{fig:agg-performance-all-Germany},
-\ref{fig:agg-performance-all-Poland}).
-
-\hypertarget{death-forecasts}{%
-\subsection{Death Forecasts}\label{death-forecasts}}
-
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as
-our model-based approaches across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B). Relative WIS values for the models
-two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1
-(Hub ensemble) and 1.79 (renewal model). The crowd forecasts performed
-better than the renewal model across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B), and also better than the convolution
-model three and four weeks ahead. Poor performance of the renewal model,
-especially at longer horizons, indicates that an approach that does not
-know about past cases, but instead estimates and projects a separate
-\(R_t\) trace from deaths, does not use the available information
-efficiently. The convolution model was able to outperform both the
-renewal model and the crowd forecasts at shorter forecast horizons
-(where the delay between cases and deaths means that future deaths are
-largely informed by present cases), but saw performance deteriorate at
-three and four weeks ahead (where case predictions from the renewal
-model were increasingly used to inform death predictions) (Figure
-\ref{fig:agg-performance-all}B, Table \ref{tab:score-table-4}).
-
-As past cases and hospitalisations can be used as predictors, predicting
-a change in trend may be easier for deaths than for cases. Even though
-all forecasts generally struggled with this, there were some instances
-where changing trends were well captured or even anticipated. In Poland,
-for example, the Hub ensemble was able to capture or even anticipate the
-peak in deaths in December quite well (whereas the renewal model and
-crowd forecast did not). The renewal model, which mostly exhibited
-trend-following behaviour, correctly predicted another increase in
-weekly deaths in mid-January (potentially based on changes in daily
-deaths, as the renewal model did not know about past cases). In Germany
-in early January, all models predicted a decrease in deaths two to three
-weeks before it actually happened. Predictions from the renewal model at
-that time were likely strongly influenced by an unexpected drop in
-reported deaths in December. The other forecasting approaches and in
-particular, the convolution model may have been affected by potentially
-under-reported case numbers around Christmas. When the decrease that all
-models had predicted to happen in early January failed to materialise,
-the renewal model and the crowd forecast noticeably over-corrected and
-over-predicted deaths in the following weeks, while the Hub ensemble,
-and to a slightly lesser degree, the convolution model were able to
-capture the downturn well when it finally happened at the end of
-January.
-
-Death forecasts, generally, showed greater coverage of the 50\% and 90\%
-prediction intervals than case forecasts and no decrease in coverage
-across forecast horizons, indicating that it might be easier to
-appropriately quantify uncertainty for death forecasts. The Hub ensemble
-had the greatest coverage, with empirical coverage of the 50\% and 90\%
-prediction intervals exceeding 50\%, and 90\%, respectively, across all
-forecast horizons. Coverage for the crowd forecasts and our model-based
-approaches was generally lower than that of the Hub ensemble and mostly
-slightly lower than nominal coverage (Figure
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D). As
-for cases, the crowd forecast tended to have the narrowest prediction
-intervals and uncertainty increased most slowly across forecast
-horizons, and the renewal model forecasts generally were widest. The
-convolution model had relatively narrow prediction intervals for short
-forecast horizons, but had rapidly (and non-linearly) increasing
-uncertainty for longer forecast horizons, driven by increasing
-uncertainty in the underlying case forecasts.
-
-For deaths, the ensemble of crowd forecasts had a consistent tendency to
-over-predict \ref{fig:agg-performance-all}F. The convolution model had a
-strong tendency to under-predict, with the magnitude of under-prediction
-steadily decreasing for longer forecast horizons. The renewal model
-(which over-predicted for cases) and the Hub ensemble slightly tended
-towards under-prediction. For deaths, absolute over- and
-under-prediction penalties were more in line with a general relative
-tendency to over- or under-predict than for cases (Figure
-\ref{fig:agg-performance-all}A, \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2}, \ref{tab:score-table-4}).
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} \caption{Distribution of scores.
-A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
-Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores.}\label{fig:distribution-scores}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4} \caption{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.
-“Hub-ensemble”    extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-rel}
-\end{figure}
-
-\hypertarget{contributions-hub}{%
-\subsection{Contribution to the Forecast Hub}\label{contributions-hub}}
-
-Of our three models, only the renewal model and the crowd forecast were
-included in the official Forecast Hub median ensemble
-(``hub-ensemble-realised''), while the convolution model was never
-included as it was deemed too similar to the existing renewal model. In
-the official Hub ensemble, there were on average 7.1 models included
-(including our own), with a median of 7, a minimum of 4 (on 28 December
-2020 over the Christmas period) and a maximum of 10. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively. An
-overview of all models and ensemble versions is shown in Table
-\ref{tab:table-ensemble-versions} in the SI.
-
-For cases, our contributions (compared to the Hub ensemble without our
-contributions) consistently improved performance across all forecasting
-horizons (rel. WIS 0.9 two weeks ahead, Table
-\ref{tab:score-table-ensemble-2}). Contributions from the crowd
-forecasts alone also improved performance of the Hub ensemble across all
-forecast horizons, while contributions from the renewal model had a
-negative effect for longer horizons (rel. WIS 1.02 three weeks ahead,
-1.06 four weeks ahead). The realised ensemble including both models
-performed better or equal compared to all versions with only one model
-included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model
-have improved performance (Table \ref{tab:score-table-ensemble-4}). The
-realised ensemble performed comparably to the crowd forecasts for
-predictions one to two weeks ahead, and worse for greater forecast
-horizons.
-
-For deaths, contributions from the renewal model and crowd forecast
-together improved performance only for one week ahead predictions and
-showed an increasingly negative impact on performance for longer
-horizons (rel. WIS of the Hub-ensemble-realised 1.01 two weeks ahead,
-1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and
-\ref{tab:score-table-ensemble-4}). Individual contributions from both
-the renewal model and the crowd forecast were largely negative, while a
-version of the Hub ensemble with only the convolution model included
-would have performed consistently better across all forecast horizons
-(with the positive impact increasing for longer horizons). This is
-especially interesting as the convolution model performed consistently
-worse than the pre-existing Hub ensemble (Figure
-\ref{fig:agg-performance-all}) and especially worse for longer horizons.
-
-We also considered the impact of our contributions on a version of the
-Hub ensemble constructed by taking the quantile-wise mean, rather than
-the median. General trends were similar, with the notable exception of
-the convolution model, which had a consistently positive impact on the
-median ensemble, but a mixed and mostly slightly negative impact on the
-mean ensemble (Figures \ref{fig:agg-performance-ensemble-rel}B and
-\ref{fig:agg-performance-ensemble-mean}B). This may happen if a model is
-more correct directionally relative to the pre-existing ensemble, but
-overshoots in absolute terms, thereby moving the ensemble too far. For
-both the mean and the median ensemble, changes in performance from
-adding or removing models were of a similar order of magnitude,
-suggesting that at least in this instance, with a relatively small
-ensemble size, the median ensemble was not necessarily more `robust' to
-changes than the mean ensemble. However, the ensemble version with all
-our forecasts included (``hub-ensemble-with-all'') tended to perform
-relatively better for the median ensemble than the mean ensemble,
-suggesting that adding more models may be more beneficial or `safer' for
-the median than for the mean ensemble as directional errors can more
-easily cancel out than errors in absolute terms.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Epidemiological forecasting modelling combines knowledge about
-infectious disease dynamics with the subjective opinion of the
-researcher who develops and refines the model. In this study, we
-compared forecasts of cases of and deaths from COVID-19 in Germany and
-Poland based purely on human judgement and elicited from a crowd of
-researchers and volunteers against forecasts from two semi-mechanistic
-epidemiological models. In spite of the small number of participants and
-a general tendency to be overconfident, crowd forecasts consistently
-outperformed our epidemiological models as well as the Hub ensemble when
-forecasting cases but not when forecasting deaths. This suggests that
-humans might be relatively good at foreseeing trends that are hard to
-model but may struggle to form an intuition for the exact relationship
-between cases and deaths.
-
-Past studies have evaluated the performance of model-based forecasting
-approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of
-(expert-tuned) model-based approaches {[}e.g. 12,13,14{]}, or
-exclusively on human forecasts {[}19,20,24,25{]}. In contrast, we
-directly compared human and model-based forecasts. This is similar to
-the approach taken by {[}11{]}, but extends it in several ways. While
-Farrow et al.~only asked for point predictions and constructed a
-predictive distribution from these, we asked participants to provide a
-full predictive distribution, allowing us to compare human forecasts and
-models without any further assumptions, as well as to analyse how humans
-quantified their uncertainty. In addition, we compared crowd forecasts
-to two semi-mechanistic models informed by basic epidemiological
-knowledge of COVID-19, allowing us to assess not only relative
-performance but also to analyse qualitative differences between human
-judgement and model-based insight. In terms of interpretability of the
-results, exact knowledge of our two models, as well as focus on a
-limited set of targets and locations was a major advantage of our study
-compared to larger studies conducted by the Forecast Hubs
-{[}12--15,17{]}.
-
-The strong performance of crowd forecasts in our study is in line with
-results from Farrow et al.~who also report strong performance of human
-predictions in past Flu challenges despite difficulties to recruit a
-large number of participants. The advantage of crowd forecasts we
-observed over our semi-mechanistic models is likely in part explained by
-the fact that we compared an ensemble of crowd forecasts with single
-models. However, this probably explains only part of the difference, and
-performance relative to the Hub ensemble strongly suggests that human
-insight is valuable when forecasting highly volatile and potentially
-hard-to-predict quantities such as case numbers. One potential
-explanation is that humans can have access to data that is not available
-to or hard to integrate into model-based forecasts. Relatively good
-performance of our semi-mechanistic models short-term, but not
-longer-term, suggests that model-based forecasts are helpful to
-extrapolate from current conditions, but require some form of human
-intervention or additional assumptions to inform forecasts when
-conditions change over time. This human intervention may be particularly
-important when dealing with artefacts in reporting and data anomalies
-(and especially when using daily, rather than weekly data). The large
-variance in predictions in January in Germany for example (severe
-under-prediction followed by severe over-prediction, see Figure
-\ref{fig:forecasts-and-truth}A), may in part be caused by the fact that
-the renewal model operated on daily data and therefore was susceptible
-to fluctuations in daily reporting which have less of an influence on
-weekly reporting.
-
-Our results suggest that human intervention may be less beneficial when
-forecasting deaths (especially at shorter horizons, when deaths are
-largely dependent on already observed cases), which benefits from the
-ability to model the delays and exact epidemiological relationships
-between different leading and lagged indicators. Relatively good
-performance of the convolution model, especially compared to the poor
-performance of the renewal model on deaths (which used only deaths to
-estimate and predict the effective reproduction number) underlines the
-importance of including leading indicators such as cases as a predictor
-for deaths.
-
-Given the low number of participants in our study, it is difficult to
-generalise conclusions about crowd predictions to other settings. Using
-R shiny as a platform for the web application arguably created some
-limits to user experience and performance, influencing the number of
-participants and potentially creating a self-selection effect.
-Motivating forecasters to contribute regularly proved challenging,
-especially given that the majority of our participants were from the UK
-and may not have been familiar with all relevant details of the
-situation in Germany and Poland. On the other hand, R shiny facilitated
-quick development and allowed us to provide our crowd forecasting
-tooling as an open source R package, meaning that it is available for
-others to use, for example in settings like early-stage outbreaks where
-model-based forecasts are not available. In light of the relatively
-small number of Hub ensemble models, performance of the Hub ensemble is
-also difficult to generalise. More research is needed to replicate these
-findings and investigate how crowd forecasts compare against the types
-of models and model ensembles policy makers use to inform their
-decisions.
-
-Our work suggests that crowd forecasts and model-based forecasts could
-have different strengths and may be able to complement each other. When
-choosing a suitable approach for a given task it is important to take
-into account how the output will be used. In this work we focused on
-forecasts (which aim to predict future data points whilst accounting for
-all factors that might influence them), whereas policy makers might be
-more interested in projections (which show what would happen in the
-absence of any events that could change the trend) or scenario
-modelling. Forecasts may not be a suitable basis for informing policy
-decisions, if forecasters already have factored in the expectation of a
-future intervention. Model-based approaches can be either forecasts or
-projections depending on the assumptions, whereas eliciting projections
-that are not influenced by implicit assumptions about the future from
-humans may be harder.
-
-Further work should explore the effects of humans refining their
-mathematical models or changing model outputs in more detail.
-Model-based forecasts could be used as an input to human judgement, with
-researchers adjusting predictions generated by models. Seeing a
-model-based forecast could help humans calibrate uncertainty better,
-while allowing for manual intervention to adapt spurious trend
-predictions. Tools need to be developed to facilitate this process at a
-larger scale. Human insight could also be used as an input to models.
-Such a `hybrid' forecasting approach could for example ask humans to
-predict the trend of the effective reproduction number \(R_t\) or the
-doubling rate (i.e.~how the epidemic evolves) into the future and use
-this to estimate the exact number of cases, hospitalisations or deaths
-this would imply. In light of severe overconfidence, yet good
-performance in terms of the absolute error, post-processing of human
-forecasts to adjust and widen prediction intervals may be another
-promising approach. Crowd forecasting in general could benefit greatly
-from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of
-the limited resources available and the small number of participants,
-this seems worthwhile to further develop and explore.
-
-\clearpage
-
-\textbf{Acknowledgements}
-
-NIB received funding from the Health Protection Research Unit (grant
-code NIHR200908, https://www.nihr.ac.uk/). SA's work was funded by the
-Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/). The work
-of JB was supported by the Helmholtz Foundation
-(https://www.helmholtz.de/) via the SIMCARD Information and Data Science
-Pilot Project. This research was partly funded by the National Institute
-for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 \&
-16/136/46) using UK aid from the UK Government to support global health
-research. The views expressed in this publication are those of the
-author(s) and not necessarily those of the NIHR or the UK Department of
-Health and Social Care. BJQ is supported in part by a grant from the
-Bill and Melinda Gates Foundation (OPP1139859,
-https://www.gatesfoundation.org/). EvL acknowledges funding by the
-National Institute for Health Research (NIHR) Health Protection Research
-Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908,
-https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research
-and innovation programme - project EpiPose (101003688,
-https://ec.europa.eu/programmes/horizon2020/). AC acknowledges funding
-by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/),
-and the Academy of Medical Sciences (https://acmedsci.ac.uk/). SF's work
-was supported by the Wellcome Trust (grant: 210758/Z/18/Z,
-https://wellcome.org/), and the NIHR (NIHR200908,
-https://www.nihr.ac.uk/).
-
-We thank all forecasters who participated in this study for their
-contribution.
-
-We would also like to acknowledge (in a randomised order) the members of
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group at the the London School of Hygiene \& Tropical Medicine:
-Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie
-Diamond, Katherine E. Atkins, Rein M G J Houben, Jiayao Lei, Rachel
-Lowe, David Simons, Sophie R Meakin, Nicholas G. Davies, Timothy W
-Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly,
-Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas,
-Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia
-Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson,
-Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang
-Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C
-Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun,
-Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche,
-James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday,
-Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan
-Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R
-Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael
-Pung, Anna M Foss.
-
-\clearpage
-
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
-
-\hypertarget{appendix-supplementary-information}{%
-\section*{(APPENDIX) Supplementary
-information}\label{appendix-supplementary-information}}
-\addcontentsline{toc}{section}{(APPENDIX) Supplementary information}
-
-\hypertarget{supplementary-information}{%
-\section{Supplementary information}\label{supplementary-information}}
-
-\hypertarget{scoring-metrics-used}{%
-\subsection{Scoring metrics used}\label{scoring-metrics-used}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{9.3cm}}
-\caption{\label{tab:scoring-metrics}Overview of the scoring metrics used.}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{Overview of the scoring metrics used. \textit{(continued)}}\\
-\toprule
-Metric & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-WIS (Weighted) interval score & The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
-It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
-The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction.
-For a single interval, the score is computed as
-  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
-  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e.
-the lower and upper bound of a single prediction interval.
-For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
-  $$WIS = \frac{1}{K + 0.5} \cdot \left( w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y) \right), $$
-  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
-
-\cellcolor{gray!6}{Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.}\\
-\addlinespace \addlinespace
-Interval coverage & Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
-Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
-we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.\\
-\addlinespace \addlinespace
-Bias & (Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict. Values are between -1 and 1 and 0 ideally. For continuous forecasts, bias is given as 
-$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
-where $F$ is the CDF of the predictive distribution and $y$ is the observed value.
-
-For quantile forecasts, $F(y)$ is replaced by a quantile rank.
-The appropriate quantile rank is determined by whether the median forecast is below  or above the true value.
-We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.
-
-\cellcolor{gray!6}{In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
-It is therefore a more robust measurement.}\\*
-\end{longtable}
-
-\clearpage
-
-\hypertarget{the-crowdforecasting-app}{%
-\subsection{The crowdforecasting app}\label{the-crowdforecasting-app}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../crowd-forecast/Screenshot-forecasting-app} \caption{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).
-}\label{fig:screenshot}
-\end{figure}
-
-\clearpage
-
-\hypertarget{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}{%
-\subsection{Text S1. Further details on the semi-mechanistic forecasting
-models}\label{text-s1.-further-details-on-the-semi-mechanistic-forecasting-models}}
-
-\hypertarget{renewal-equation-model}{%
-\subsubsection{Renewal equation model}\label{renewal-equation-model}}
-
-The model was initialised prior to the first observed data point by
-assuming constant exponential growth for the mean of assumed delays from
-infection to case report.
-
-\begin{align}
-  I_{t} &= I_0 \exp  \left(r t \right)  \\
-  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
-  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
-\end{align}
-
-Where \(I_{obs}\) and \(r_{obs}\) are estimated from the first week of
-observed data. For the time window of the observed data infections were
-then modelled by weighting previous infections by the generation time
-and scaling by the instantaneous reproduction number. These infections
-were then convolved to cases by date (\(O_t\)) and cases by date of
-report (\(D_t\)) using log-normal delay distributions. This model can be
-defined mathematically as follows,
-
-\begin{align}
-  \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
-  I_t &= R_t \sum_{\tau = 1}^{15} w(\tau | \mu_{w}, \sigma_{w}) I_{t - \tau} \\
-  O_t &= \sum_{\tau = 0}^{15} \xi_{O}(\tau | \mu_{\xi_{O}}, \sigma_{\xi_{O}}) I_{t-\tau} \\
-  D_t &= \alpha \sum_{\tau = 0}^{15} \xi_{D}(\tau | \mu_{\xi_{D}}, \sigma_{\xi_{D}}) O_{t-\tau} \\ 
-  C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
-\end{align}
-
-Where, \begin{align}
-     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
-    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
-    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
-\end{align}
-
-This model used the following priors for cases,
-
-\begin{align}
-     R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
-    \mu_w &\sim \mathcal{N}(3.6, 0.7) \\
-    \sigma_w &\sim \mathcal{N}(3.1, 0.8) \\
-    \mu_{\xi_{O}} &\sim \mathcal{N}(1.62, 0.064) \\
-    \sigma_{\xi_{O}} &\sim \mathcal{N}(0.418, 0.069) \\
-    \mu_{\xi_{D}} &\sim \mathcal{N}(0.614, 0.066) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(1.51, 0.048) \\
-    \alpha &\sim \mathcal{N}(0.25, 0.05) \\
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-and updated the reporting process as follows when forecasting deaths,
-
-\begin{align}
-    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
-    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
-    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
-\end{align}
-
-\(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) were truncated to be
-greater than 0 and with \(\xi\), and \(w\) normalised to sum to 1.
-
-The prior for the generation time was sourced from {[}51{]} but refit
-using a log-normal incubation period with a mean of 5.2 days (SD 1.1)
-and SD of 1.52 days (SD 1.1) with this incubation period also being used
-as a prior {[}52{]} for \(\xi_{O}\). This resulted in a
-gamma-distributed generation time with mean 3.6 days (standard deviation
-(SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates. We estimated
-the delay between symptom onset and case report or death required to
-convolve latent infections to observations by fitting an integer
-adjusted log-normal distribution to 10 subsampled bootstraps of a public
-linelist for cases in Germany from April 2020 to June 2020 with each
-bootstrap using 1\% or 1769 samples of the available data {[}45,53{]}
-and combining the posteriors for the mean and standard deviation of the
-log-normal distribution {[}40,42,46,54{]}.
-
-\(GP_t\) is an approximate Hilbert space Gaussian process as defined in
-{[}55{]} using a Matern 3/2 kernel using a boundary factor of 1.5 and 17
-basis functions (20\% of the number of days used in fitting). The length
-scale of the Gaussian process was given a log-normal prior with a mean
-of 21 days, and a standard deviation of 7 days truncated to be greater
-than 3 days and less than 60 days. The magnitude of the Gaussian process
-was assumed to be normally distributed centred at 0 with a standard
-deviation of 0.1.
-
-From the forecast time horizon (\(T\)) and onwards the last value of the
-Gaussian process was used (hence \(R_t\) was assumed to be fixed) and
-latent infections were adjusted to account for the proportion of the
-population that was susceptible to infection as follows,
-
-\begin{equation}
-    I_t = (N - I^c_{t-1}) \left(1 - \exp \left(\frac{-I'_t}{N - I^c_{T}}\right)\right),
-\end{equation}
-
-where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\)
-and \(I'_t\) are the unadjusted infections defined above. This
-adjustment is based on that implemented in the \texttt{epidemia} R
-package {[}56,57{]}.
-
-\hypertarget{convolution-model}{%
-\paragraph{Convolution model}\label{convolution-model}}
-
-The convolution model shares the same observation model as the renewal
-model but rather than assuming that an observation is predicted by
-itself using the renewal equation instead assumes that it is predicted
-entirely by another observation after some parametric delay. It can be
-defined mathematically as follows,
-
-\begin{equation} 
-    D_{t} \sim \mathrm{NB}\left(\omega_{(t \mod 7)} \alpha \sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) C_{t-\tau},  \phi \right)
-\end{equation}
-
-with the following priors,
-
-\begin{align}
-    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
-    \alpha &\sim \mathcal{N}(0.01, 0.02) \\
-    \xi &\sim \mathcal{LN}(\mu, \sigma) \\
-    \mu &\sim \mathcal{N}(2.5, 0.5) \\
-\sigma &\sim \mathcal{N}(0.47, 0.2) \\
-\phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
-\end{align}
-
-with \(\alpha\), \(\mu\), \(\sigma\), and \(\phi\) truncated to be
-greater than 0 and with \(\xi\) normalised such that
-\(\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1\).
-
-\hypertarget{model-fitting}{%
-\subsubsection{Model fitting}\label{model-fitting}}
-
-Both models were implemented using the \texttt{EpiNow2} R package
-(version 1.3.3) {[}40{]}. Each forecast target was fitted independently
-for each model using Markov-chain Monte Carlo (MCMC) in stan {[}46{]}. A
-minimum of 4 chains were used with a warmup of 250 samples for the
-renewal equation-based model and 1000 samples for the convolution model.
-2000 samples total post warmup were used for the renewal equation model
-and 4000 samples for the convolution model. Different settings were
-chosen for each model to optimise compute time contingent on
-convergence. Convergence was assessed using the R hat diagnostic
-{[}46{]}. For the convolution model forecast the case forecast from the
-renewal equation model was used in place of observed cases beyond the
-forecast horizon using 1000 posterior samples. 12 weeks of data was used
-for both models though only 3 weeks of data were included in the
-likelihood for the convolution model.
-
-\clearpage
-
-\hypertarget{tables-with-results-of-the-forecast-evaluation}{%
-\subsection{Tables with results of the forecast
-evaluation}\label{tables-with-results-of-the-forecast-evaluation}}
 
 \begin{table}[!h]
-\caption{\label{tab:score-table-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 7010 (0.8) & 7480 (0.64) & 2680 (0.73) & 1700 (1.38) & 2630 (0.68) & -0.01 & 10400 (0.82) & 0.55 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 8740 (1) & 11800 (1.01) & 2190 (0.6) & 2720 (2.21) & 3830 (0.99) & 0.18 & 12000 (0.94) & 0.48 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 16200 (0.89) & 16600 (0.76) & 3660 (0.6) & 5930 (1.56) & 6600 (0.78) & -0.01 & 23300 (0.87) & 0.36 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25600 (1.4) & 33800 (1.54) & 5420 (0.88) & 5920 (1.56) & 14200 (1.69) & 0.17 & 34600 (1.29) & 0.43 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded).
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 27000 (0.81) & 26200 (0.64) & 4750 (0.52) & 11000 (1.43) & 11200 (0.67) & 0.02 & 39000 (0.83) & 0.14 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 50600 (1.51) & 70000 (1.72) & 10800 (1.18) & 7710 (1) & 32100 (1.93) & 0.13 & 68700 (1.46) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 39200 (0.7) & 38600 (0.52) & 5970 (0.49) & 15600 (1.26) & 17600 (0.56) & 0.07 & 54800 (0.74) & 0.05 & 0.38\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 91700 (1.64) & 135000 (1.83) & 19500 (1.6) & 8990 (0.72) & 63200 (2.02) & 0.09 & 125000 (1.68) & 0.31 & 0.48\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{aggregate-performance-by-location}{%
-\subsection{Aggregate performance by
-location}\label{aggregate-performance-by-location}}
-
-\hypertarget{performance-in-germany}{%
-\subsubsection{Performance in Germany}\label{performance-in-germany}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Germany-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Germany}
-\end{figure}
-
-\hypertarget{performance-in-poland}{%
-\subsubsection{Performance in Poland}\label{performance-in-poland}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Poland-v4} \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-Poland}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-absolute-terms}{%
-\subsubsection{Performance across locations in absolute
-terms}\label{performance-across-locations-in-absolute-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-v4} \caption{Visualisation of aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations}
-\end{figure}
-
-\hypertarget{performance-across-locations-in-relative-terms}{%
-\subsection{Performance across locations in relative
-terms}\label{performance-across-locations-in-relative-terms}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4} \caption{Visualisation of relative aggregate performance metrics across locations.
-A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals.
-E: Dispersion.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast.
-H.
-Standard deviation of WIS values.}\label{fig:performance-locations-rel}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-daily-reported-cases-and-deaths}{%
-\subsection{Visualisation of daily reported cases and
-deaths}\label{visualisation-of-daily-reported-cases-and-deaths}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily_truth} \caption{Visualisation of daily report data.
-The black line represents weekly data divided by seven.
-Data were last accessed through the German and Polish Forecast Hub on August 21 2021.}\label{fig:daily-truth}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/daily-data-updates} \caption{Visualisation of the absolute difference between the daily report data at the time and the data now.
-In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:daily-truth-update}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/weekly-data-updates} \caption{Visualisation of the relative difference between the weekly report data at the time and the data now.
-Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022.}\label{fig:weekly-truth-update}
-\end{figure}
-
-\clearpage
-
-\hypertarget{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}{%
-\subsection{Visualisation of scores and forecasts 1, 3, 4 weeks
-ahead}\label{visualisation-of-scores-and-forecasts-1-3-4-weeks-ahead}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} \caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} \caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} \caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth-4}
-\end{figure}
-
-\clearpage
-
-\hypertarget{distribution-of-scores}{%
-\subsection{Distribution of scores}\label{distribution-of-scores}}
-
-\hypertarget{absolute-scores}{%
-\subsubsection{Absolute scores}\label{absolute-scores}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1} \caption{A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3} \caption{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4} \caption{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of WIS separate by country.}\label{fig:distribution-scores-4}
-\end{figure}
-
-\hypertarget{ranks-achieved-by-forecasts}{%
-\subsubsection{Ranks achieved by
-forecasts}\label{ranks-achieved-by-forecasts}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-1}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-2}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-3}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4-ranks} \caption{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets.
-B: Distribution of ranks separate by country.}\label{fig:distribution-scores-ranks-4}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} \caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-renewal} \caption{Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences-renewal}
-\end{figure}
-
-\newpage
-
-\hypertarget{comparison-of-ensembles}{%
-\subsection{Comparison of ensembles}\label{comparison-of-ensembles}}
-
-\hypertarget{performance-visualisation-mean-ensemble}{%
-\subsubsection{Performance visualisation mean
-ensemble}\label{performance-visualisation-mean-ensemble}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
-“Hub-ensemble”     extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
-Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-mean}
-\end{figure}
-
-\hypertarget{tables-median-ensemble}{%
-\subsubsection{Tables median ensemble}\label{tables-median-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 8770 (1) & 11700 (1) & 3670 (1) & 1230 (1) & 3870 (1) & -0.04 & 12700 (1) & 0.57 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 6970 (0.79) & 8260 (0.71) & 3060 (0.83) & 943 (0.77) & 2970 (0.77) & 0.04 & 10800 (0.85) & 0.55 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 7820 (0.89) & 9630 (0.82) & 3270 (0.89) & 1210 (0.98) & 3330 (0.86) & -0.02 & 12000 (0.94) & 0.48 & 0.81\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 7960 (0.91) & 10300 (0.88) & 3190 (0.87) & 1020 (0.83) & 3760 (0.97) & 0.04 & 12100 (0.95) & 0.57 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 18300 (1) & 21900 (1) & 6140 (1) & 3800 (1) & 8410 (1) & -0.03 & 26800 (1) & 0.43 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 16400 (0.9) & 19600 (0.89) & 5350 (0.87) & 3290 (0.87) & 7730 (0.92) & 0.02 & 24200 (0.9) & 0.43 & 0.69\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 16900 (0.92) & 19600 (0.89) & 5230 (0.85) & 4310 (1.13) & 7370 (0.88) & 0.00 & 24600 (0.92) & 0.38 & 0.64\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 17500 (0.96) & 21400 (0.98) & 5830 (0.95) & 2880 (0.76) & 8770 (1.04) & 0.00 & 25500 (0.95) & 0.45 & 0.71\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 235 (0.95) & 332 (0.98) & 88.6 (0.96) & 90.4 (0.79) & 55.5 (1.33) & -0.01 & 323 (0.97) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 234 (0.94) & 331 (0.98) & 85.2 (0.92) & 98.1 (0.85) & 50.2 (1.21) & -0.05 & 329 (0.99) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 234 (0.94) & 329 (0.97) & 90.7 (0.98) & 118 (1.03) & 25.3 (0.61) & -0.08 & 333 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 239 (0.96) & 337 (1) & 85.2 (0.92) & 99.6 (0.87) & 54.2 (1.3) & -0.03 & 322 (0.96) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal & 246 (0.99) & 342 (1.01) & 91.5 (0.99) & 106 (0.92) & 48.6 (1.17) & -0.06 & 342 (1.02) & 0.67 & 0.92\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 296 (1.01) & 398 (1.03) & 125 (0.95) & 91 (0.84) & 80.2 (1.55) & 0.05 & 486 (1.13) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 303 (1.04) & 423 (1.1) & 115 (0.87) & 122 (1.13) & 66.1 (1.27) & 0.00 & 483 (1.13) & 0.62 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 270 (0.92) & 385 (1) & 121 (0.92) & 119 (1.1) & 29.9 (0.58) & -0.04 & 403 (0.94) & 0.58 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 303 (1.04) & 392 (1.02) & 122 (0.92) & 106 (0.98) & 74.6 (1.44) & 0.03 & 499 (1.16) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal & 296 (1.01) & 397 (1.03) & 128 (0.97) & 97.1 (0.9) & 71.2 (1.37) & -0.01 & 462 (1.08) & 0.67 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 33400 (1) & 40700 (1) & 9130 (1) & 7690 (1) & 16600 (1) & -0.01 & 46900 (1) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 30800 (0.92) & 38600 (0.95) & 7910 (0.87) & 6890 (0.9) & 16000 (0.96) & 0.03 & 44200 (0.94) & 0.29 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 30800 (0.92) & 34100 (0.84) & 7500 (0.82) & 8960 (1.17) & 14300 (0.86) & 0.02 & 44100 (0.94) & 0.24 & 0.55\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 34000 (1.02) & 43100 (1.06) & 8860 (0.97) & 6300 (0.82) & 18900 (1.14) & 0.02 & 48100 (1.03) & 0.29 & 0.60\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 55900 (1) & 73700 (1) & 12200 (1) & 12400 (1) & 31300 (1) & 0.01 & 74400 (1) & 0.24 & 0.52\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 51200 (0.92) & 69900 (0.95) & 10900 (0.89) & 11100 (0.9) & 29300 (0.94) & 0.04 & 69600 (0.94) & 0.19 & 0.57\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 48800 (0.87) & 58600 (0.8) & 9700 (0.8) & 13700 (1.1) & 25400 (0.81) & 0.00 & 65800 (0.88) & 0.19 & 0.48\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 59100 (1.06) & 84100 (1.14) & 12600 (1.03) & 10100 (0.81) & 36400 (1.16) & 0.01 & 78900 (1.06) & 0.29 & 0.55\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 332 (1.04) & 388 (1.18) & 158 (0.92) & 78.7 (0.85) & 95 (1.72) & -0.02 & 547 (1.12) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 321 (1.01) & 385 (1.17) & 153 (0.89) & 100 (1.08) & 68.1 (1.24) & -0.01 & 535 (1.1) & 0.54 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 298 (0.93) & 337 (1.03) & 155 (0.9) & 106 (1.14) & 37.5 (0.68) & -0.04 & 441 (0.9) & 0.67 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 319 (1) & 342 (1.04) & 160 (0.93) & 85.1 (0.92) & 73.6 (1.34) & -0.02 & 547 (1.12) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 3 wk ahead}} & Hub-ensemble-with-renewal & 332 (1.04) & 363 (1.11) & 168 (0.98) & 86.1 (0.93) & 78.2 (1.42) & -0.02 & 528 (1.08) & 0.58 & 0.96\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised & 445 (1.05) & 532 (1.2) & 193 (0.91) & 107 (0.85) & 144 (1.68) & -0.03 & 700 (1.04) & 0.54 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all & 399 (0.94) & 438 (0.99) & 195 (0.92) & 105 (0.83) & 97.9 (1.14) & -0.05 & 692 (1.03) & 0.46 & 1.00\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution & 384 (0.91) & 387 (0.87) & 196 (0.92) & 122 (0.97) & 65.9 (0.77) & -0.06 & 602 (0.89) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd & 407 (0.96) & 456 (1.03) & 202 (0.95) & 105 (0.83) & 101 (1.18) & -0.03 & 669 (0.99) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 4 wk ahead}} & Hub-ensemble-with-renewal & 457 (1.08) & 527 (1.19) & 208 (0.98) & 129 (1.02) & 121 (1.41) & -0.06 & 744 (1.1) & 0.50 & 0.96\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\hypertarget{tables-mean-ensemble}{%
-\subsubsection{Tables mean ensemble}\label{tables-mean-ensemble}}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 8680 (1) & 10300 (1) & 3700 (1) & 1460 (1) & 3520 (1) & -0.02 & 13400 (1) & 0.50 & 0.86\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 7600 (0.88) & 8770 (0.85) & 3360 (0.91) & 1090 (0.75) & 3140 (0.89) & 0.01 & 11900 (0.89) & 0.52 & 0.90\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 8050 (0.93) & 9070 (0.88) & 3520 (0.95) & 1410 (0.97) & 3120 (0.89) & -0.02 & 12600 (0.94) & 0.48 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 8090 (0.93) & 9780 (0.95) & 3490 (0.94) & 1110 (0.76) & 3490 (0.99) & 0.02 & 12700 (0.95) & 0.57 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 19000 (1) & 22100 (1) & 5960 (1) & 3690 (1) & 9340 (1) & 0.02 & 28800 (1) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 17100 (0.9) & 20600 (0.93) & 5550 (0.93) & 2850 (0.77) & 8660 (0.93) & 0.05 & 26000 (0.9) & 0.38 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 17600 (0.93) & 20000 (0.9) & 5540 (0.93) & 3790 (1.03) & 8230 (0.88) & 0.01 & 26800 (0.93) & 0.36 & 0.76\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 18300 (0.96) & 22600 (1.02) & 5910 (0.99) & 2640 (0.72) & 9720 (1.04) & 0.06 & 27700 (0.96) & 0.38 & 0.76\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Hub-ensemble-mean & 229 (1) & 292 (1) & 101 (1) & 90.4 (1) & 36.7 (1) & -0.07 & 315 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 219 (0.96) & 289 (0.99) & 96.8 (0.96) & 79.8 (0.88) & 42.6 (1.16) & -0.04 & 297 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 217 (0.95) & 287 (0.98) & 95.3 (0.94) & 83.1 (0.92) & 38.7 (1.05) & -0.07 & 300 (0.95) & 0.67 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 225 (0.98) & 292 (1) & 98.7 (0.98) & 94.2 (1.04) & 32 (0.87) & -0.09 & 314 (1) & 0.71 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 222 (0.97) & 289 (0.99) & 98 (0.97) & 84.1 (0.93) & 39.6 (1.08) & -0.04 & 295 (0.94) & 0.71 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 1 wk ahead}} & Hub-ensemble-with-renewal-mean & 225 (0.98) & 290 (0.99) & 99.7 (0.99) & 84.7 (0.94) & 40.5 (1.1) & -0.05 & 314 (1) & 0.71 & 0.88\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Hub-ensemble-mean & 256 (1) & 306 (1) & 138 (1) & 64.5 (1) & 53.2 (1) & 0.04 & 374 (1) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-realised-mean & 270 (1.05) & 338 (1.1) & 136 (0.99) & 65.2 (1.01) & 68.1 (1.28) & 0.06 & 413 (1.1) & 0.75 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-all-mean & 268 (1.05) & 346 (1.13) & 133 (0.96) & 78.7 (1.22) & 57.1 (1.07) & 0.05 & 408 (1.09) & 0.75 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-convolution-mean & 259 (1.01) & 322 (1.05) & 133 (0.96) & 81.7 (1.27) & 44.4 (0.83) & 0.03 & 380 (1.02) & 0.67 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble-with-crowd-mean & 264 (1.03) & 315 (1.03) & 133 (0.96) & 70.1 (1.09) & 60 (1.13) & 0.06 & 404 (1.08) & 0.71 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-6}{*}{\raggedright\arraybackslash 2 wk ahead}} & Hub-ensemble-with-renewal-mean & 264 (1.03) & 332 (1.08) & 141 (1.02) & 60.1 (0.93) & 63.1 (1.19) & 0.06 & 390 (1.04) & 0.79 & 0.92\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-ensemble-mean-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e.
-the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
 \centering
@@
 
-\clearpage
-
-\hypertarget{sensitivity-analysis}{%
-\subsection{Sensitivity analysis}\label{sensitivity-analysis}}
-
-In the original analysis, cases and deaths were scored on different
-periods, as the convolution model was only added later. This sensitivity
-shows performance of all models restricted to the period from December
-14 2020 until March 1st 2021 where all models were available.
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4} \caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all-late}
-\end{figure}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-2}Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 4980 (0.74) & 5730 (0.64) & 2070 (0.6) & 728 (0.74) & 2190 (0.94) & 0.09 & 7810 (0.82) & 0.54 & 0.88\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 6730 (1) & 8960 (1) & 3430 (1) & 978 (1) & 2330 (1) & -0.09 & 9550 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 9640 (1.43) & 13300 (1.48) & 1970 (0.57) & 4170 (4.26) & 3500 (1.5) & 0.09 & 12700 (1.33) & 0.46 & 0.71\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 10700 (0.99) & 13800 (1.1) & 2880 (0.58) & 2350 (0.85) & 5430 (1.79) & 0.08 & 15400 (1.07) & 0.46 & 0.62\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 10800 (1) & 12500 (1) & 4940 (1) & 2780 (1) & 3030 (1) & -0.13 & 14400 (1) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 25000 (2.31) & 34000 (2.72) & 4780 (0.97) & 8710 (3.13) & 11500 (3.8) & 0.05 & 32000 (2.22) & 0.50 & 0.67\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 255 (1.03) & 343 (1.01) & 82 (0.89) & 142 (1.23) & 31.1 (0.75) & -0.18 & 399 (1.19) & 0.42 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 265 (1.07) & 317 (0.94) & 78.2 (0.85) & 82 (0.71) & 105 (2.52) & 0.08 & 402 (1.2) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 248 (1) & 338 (1) & 92.2 (1) & 115 (1) & 41.6 (1) & -0.04 & 334 (1) & 0.62 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 1 wk ahead}} & Renewal & 298 (1.2) & 403 (1.19) & 87 (0.94) & 107 (0.93) & 105 (2.52) & -0.07 & 413 (1.24) & 0.50 & 0.79\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 357 (1.22) & 573 (1.49) & 104 (0.79) & 204 (1.89) & 48.8 (0.94) & -0.10 & 565 (1.32) & 0.33 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 368 (1.26) & 442 (1.15) & 107 (0.81) & 102 (0.94) & 160 (3.08) & 0.14 & 576 (1.34) & 0.38 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 292 (1) & 385 (1) & 132 (1) & 108 (1) & 51.9 (1) & 0.01 & 429 (1) & 0.62 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 2 wk ahead}} & Renewal & 524 (1.79) & 671 (1.74) & 155 (1.17) & 133 (1.23) & 236 (4.55) & -0.02 & 750 (1.75) & 0.50 & 0.71\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{table}[!h]
-\caption{\label{tab:score-table-late-4}Scores for three and four week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.\\\hspace{\textwidth}}
-
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{>{}llccccccccc}
-\toprule
-  & Model & WIS & WIS - sd & dispersion & Underpred. & Overpred. & Bias & Abs. error & 50\%-Cov. & 90\%-Cov.\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Cases}}\\
-\hline
-\cellcolor{white}{} & Crowd forecast & 17200 (1) & 16000 (0.98) & 3800 (0.63) & 5660 (0.85) & 7770 (1.74) & 0.07 & 26800 (1.1) & 0.08 & 0.58\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 17200 (1) & 16300 (1) & 6030 (1) & 6670 (1) & 4470 (1) & -0.16 & 24400 (1) & 0.33 & 0.67\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 37700 (2.19) & 55900 (3.43) & 8840 (1.47) & 10700 (1.6) & 18100 (4.05) & -0.03 & 49800 (2.04) & 0.33 & 0.58\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Crowd forecast & 26100 (0.95) & 21000 (0.84) & 4810 (0.7) & 11300 (0.83) & 10100 (1.43) & 0.04 & 39400 (1.05) & 0.00 & 0.46\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 27600 (1) & 25000 (1) & 6900 (1) & 13600 (1) & 7060 (1) & -0.19 & 37400 (1) & 0.29 & 0.54\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-3}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 48900 (1.77) & 77800 (3.11) & 13800 (2) & 11900 (0.88) & 23200 (3.29) & -0.10 & 65500 (1.75) & 0.38 & 0.58\\
-\cmidrule{1-11}
-\addlinespace[0.3em]
-\multicolumn{11}{l}{\textbf{Deaths}}\\
-\hline
-\cellcolor{white}{} & Convolution & 541 (1.7) & 802 (2.45) & 157 (0.91) & 279 (3.01) & 105 (1.91) & -0.04 & 747 (1.53) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 414 (1.3) & 526 (1.6) & 137 (0.8) & 82 (0.88) & 194 (3.52) & 0.12 & 648 (1.33) & 0.42 & 0.83\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 319 (1) & 328 (1) & 172 (1) & 92.7 (1) & 55.1 (1) & -0.03 & 488 (1) & 0.54 & 0.96\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 3 wk ahead}} & Renewal & 724 (2.27) & 916 (2.79) & 249 (1.45) & 158 (1.7) & 317 (5.75) & -0.01 & 1040 (2.13) & 0.46 & 0.83\\
-\cmidrule{1-11}
-\cellcolor{white}{} & Convolution & 763 (1.8) & 932 (2.1) & 268 (1.26) & 331 (2.63) & 164 (1.91) & 0.01 & 985 (1.46) & 0.54 & 0.75\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Crowd forecast & 498 (1.17) & 633 (1.43) & 168 (0.79) & 83.6 (0.66) & 246 (2.87) & 0.14 & 756 (1.12) & 0.38 & 0.79\\
-\cmidrule{2-11}
-\cellcolor{white}{} & Hub-ensemble & 424 (1) & 443 (1) & 212 (1) & 126 (1) & 85.7 (1) & -0.06 & 675 (1) & 0.58 & 0.92\\
-\cmidrule{2-11}
-\cellcolor{white}{\multirow{-4}{*}{\raggedright\arraybackslash 4 wk ahead}} & Renewal & 959 (2.26) & 1210 (2.73) & 337 (1.59) & 200 (1.59) & 421 (4.91) & -0.05 & 1350 (2) & 0.50 & 0.79\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\hypertarget{overview-of-models-and-forecasters}{%
-\subsection{Overview of models and
-forecasters}\label{overview-of-models-and-forecasters}}
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{7.3cm}}
-\caption{\label{tab:table-ensemble-versions}Overview of the models and ensembles used.}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endfirsthead
-\caption[]{Overview of the models and ensembles used. \textit{(continued)}}\\
-\toprule
-Name & Explanation\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-\cellcolor{gray!6}{Hub-ensemble-realised} & \cellcolor{gray!6}{Official Forecast Hub median ensemble.
-Created by the Forecast Hub officially under the name 'KITCOVIDhub-median\_ensemble' and used as the default ensemble.
-Included are our crowd forecasts as well as the renewal model (with one missed submission on December 28 2020, but not the convolution model which was deemed to similar to the renewal model.}\\
-\addlinespace \addlinespace
-Hub-ensemble-realised-mean & Official Forecast Hub mean ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-mean\_ensemble'.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{ \vphantom{1}} & \cellcolor{gray!6}{}\\
-\addlinespace \addlinespace
-Hub-ensemble & Version of the official Hub median ensemble which excludes all our contributions.\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Hub-ensemble-mean} & \cellcolor{gray!6}{Version of the official Hub mean ensemble which excludes all our contributions.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-renewal, 
-    Hub-ensemble-with-renewal-mean & Versions of the official Hub ensembles which of our contributions includes only the Renewal model.\\
-\addlinespace \addlinespace
-Hub-ensemble-with-crowd, 
-\cellcolor{gray!6}{    Hub-ensemble-with-crowd-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which of our contributions includes only the Crowd forecast.}\\
-\addlinespace \addlinespace
-Hub-ensemble-with-convolution, 
-    Hub-ensemble-with-convolution-mean & Versions of the official Hub ensembles which of our contributions includes only the Convolution model (which originally was never included in any official Hub ensemble).\\
-\addlinespace \addlinespace
-Hub-ensemble-with-all, 
-\cellcolor{gray!6}{    Hub-ensemble-with-all-mean} & \cellcolor{gray!6}{Versions of the official Hub ensembles which includes all our contributions.
-For cases, this is identical to the official Hub ensembles, but for deaths the convolution model was added.}\\
-\addlinespace \addlinespace
- & \\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Crowd forecast} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'}\\
-\addlinespace \addlinespace
-Renewal model & Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'\\
-\addlinespace \addlinespace
-\cellcolor{gray!6}{Convolution model} & \cellcolor{gray!6}{Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\_secondary'}\\*
-\end{longtable}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/number-forecasters} \caption{Number of participants who submitted a forecast over time.}\label{fig:num-forecasters}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/ensemble-members} \caption{Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
-Note that the renewal model was not included in the ensemble on December 28th 2020.}\label{fig:num-ensemble-members}
-\end{figure}
-
-\clearpage
-
-\hypertarget{comparison-of-crowd-forecasts-and-application-baseline}{%
-\subsection{Comparison of crowd forecasts and application
-baseline}\label{comparison-of-crowd-forecasts-and-application-baseline}}
-
-\begin{figure}[H]
-\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} \caption{Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the median, as well as the 50\% and 90\% prediction intervals (in order of decreasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons).}\label{fig:compare-forecasters}
-\end{figure}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{McGowan CJ, Biggerstaff M, Johansson M, Apfeldorf KM,
-Ben-Nun M, Brooks L, et al. Collaborative efforts to forecast seasonal
-influenza in the {United States}, 2015--2016. Scientific Reports.
-2019;9: 683.
-doi:\href{https://doi.org/10.1038/s41598-018-36361-9}{10.1038/s41598-018-36361-9}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Reich NG, Brooks LC, Fox SJ, Kandula S, McGowan CJ,
-Moore E, et al. A collaborative multiyear, multimodel assessment of
-seasonal influenza forecasting in the {United States}. PNAS. 2019;116:
-3146--3154.
-doi:\href{https://doi.org/10.1073/pnas.1812594116}{10.1073/pnas.1812594116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Shaman J, Karspeck A. Forecasting seasonal outbreaks of
-influenza. PNAS. 2012;109: 20425--20430.
-doi:\href{https://doi.org/10.1073/pnas.1208772109}{10.1073/pnas.1208772109}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Biggerstaff M, Alper D, Dredze M, Fox S, Fung IC-H,
-Hickmann KS, et al. Results from the centers for disease control and
-prevention's predict the 2013--2014 {Influenza Season Challenge}. BMC
-Infectious Diseases. 2016;16: 357.
-doi:\href{https://doi.org/10.1186/s12879-016-1669-x}{10.1186/s12879-016-1669-x}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak
-AL, Baugher B, et al. An open challenge to advance probabilistic
-forecasting for dengue epidemics. PNAS. 2019;116: 24268--24274.
-doi:\href{https://doi.org/10.1073/pnas.1909865116}{10.1073/pnas.1909865116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Yamana TK, Kandula S, Shaman J. Superensemble forecasts
-of dengue outbreaks. Journal of The Royal Society Interface. 2016;13:
-20160410.
-doi:\href{https://doi.org/10.1098/rsif.2016.0410}{10.1098/rsif.2016.0410}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Colón-González FJ, Bastos LS, Hofmann B, Hopkin A,
-Harpham Q, Crocker T, et al. Probabilistic seasonal dengue forecasting
-in {Vietnam}: {A} modelling study using superensembles. PLOS Medicine.
-2021;18: e1003542.
-doi:\href{https://doi.org/10.1371/journal.pmed.1003542}{10.1371/journal.pmed.1003542}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Viboud C, Sun K, Gaffey R, Ajelli M, Fumanelli L, Merler
-S, et al. The {RAPIDD} ebola forecasting challenge: {Synthesis} and
-lessons learnt. Epidemics. 2018;22: 13--21.
-doi:\href{https://doi.org/10.1016/j.epidem.2017.08.002}{10.1016/j.epidem.2017.08.002}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Funk S, Camacho A, Kucharski AJ, Lowe R, Eggo RM,
-Edmunds WJ. Assessing the performance of real-time epidemic forecasts:
-{A} case study of {Ebola} in the {Western Area} region of {Sierra
-Leone}, 2014-15. PLOS Computational Biology. 2019;15: e1006785.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1006785}{10.1371/journal.pcbi.1006785}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Del Valle SY, McMahon BH, Asher J, Hatchett R, Lega JC,
-Brown HE, et al. Summary results of the 2014-2015 {DARPA Chikungunya}
-challenge. BMC Infectious Diseases. 2018;18: 245.
-doi:\href{https://doi.org/10.1186/s12879-018-3124-7}{10.1186/s12879-018-3124-7}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Farrow DC, Brooks LC, Hyun S, Tibshirani RJ, Burke DS,
-Rosenfeld R. A human judgment approach to epidemiological forecasting.
-PLOS Computational Biology. 2017;13: e1005248.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1005248}{10.1371/journal.pcbi.1005248}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Funk S, Abbott S, Atkins BD, Baguelin M, Baillie JK,
-Birrell P, et al. Short-term forecasts to inform the response to the
-{Covid-19} epidemic in the {UK}. medRxiv. 2020; 2020.11.11.20220962.
-doi:\href{https://doi.org/10.1101/2020.11.11.20220962}{10.1101/2020.11.11.20220962}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K,
-et al. {COVID-19 Forecast Hub}: 4 {December} 2020 snapshot. {Zenodo};
-2020.
-doi:\href{https://doi.org/10.5281/zenodo.3963371}{10.5281/zenodo.3963371}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A,
-Rivadeneira AJC, et al. Evaluation of individual and ensemble
-probabilistic forecasts of {COVID-19} mortality in the {US}. medRxiv.
-2021; 2021.02.03.21250974.
-doi:\href{https://doi.org/10.1101/2021.02.03.21250974}{10.1101/2021.02.03.21250974}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. Short-term forecasting of {COVID-19} in {Germany}
-and {Poland} during the second wave -- a preregistered study. medRxiv.
-2021; 2020.12.24.20248826.
-doi:\href{https://doi.org/10.1101/2020.12.24.20248826}{10.1101/2020.12.24.20248826}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. National and subnational short-term forecasting of
-{COVID-19} in {Germany} and {Poland}, early 2021. 2021;
-2021.11.05.21265810.
-doi:\href{https://doi.org/10.1101/2021.11.05.21265810}{10.1101/2021.11.05.21265810}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-europeancovid-19forecasthubEuropeanCovid19Forecast2021}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{European Covid-19 Forecast Hub. European {Covid-19
-Forecast Hub}. 2021 {[}cited 30 May 2021{]}. Available:
-\url{https://covid19forecasthub.eu/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichAccuracyRealtimeMultimodel2019}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Reich NG, McGowan CJ, Yamana TK, Tushar A, Ray EL,
-Osthus D, et al. Accuracy of real-time multi-model ensemble forecasts
-for seasonal influenza in the {U}.{S}. PLOS Computational Biology.
-2019;15: e1007486.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1007486}{10.1371/journal.pcbi.1007486}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Tetlock PE, Mellers BA, Rohrbaugh N, Chen E. Forecasting
-{Tournaments}: {Tools} for {Increasing Transparency} and {Improving} the
-{Quality} of {Debate}. Curr Dir Psychol Sci. 2014;23: 290--295.
-doi:\href{https://doi.org/10.1177/0963721414534257}{10.1177/0963721414534257}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Atanasov P, Rescober P, Stone E, Swift SA,
-Servan-Schreiber E, Tetlock P, et al. Distilling the {Wisdom} of
-{Crowds}: {Prediction Markets} vs. {Prediction Polls}. Management
-Science. 2016;63: 691--706.
-doi:\href{https://doi.org/10.1287/mnsc.2015.2374}{10.1287/mnsc.2015.2374}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers E-J. Laypeople
-{Can Predict Which Social-Science Studies Will Be Replicated
-Successfully}. Advances in Methods and Practices in Psychological
-Science. 2020;3: 267--285.
-doi:\href{https://doi.org/10.1177/2515245920919667}{10.1177/2515245920919667}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{ReplicationMarkets. Replication {Markets} -- {Reliable}
-research replicates\ldots you can bet on it. 2020 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.replicationmarkets.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Servan-Schreiber E, Wolfers J, Pennock DM, Galebach B.
-Prediction {Markets}: {Does Money Matter}? Electronic Markets. 2004;14:
-243--251.
-doi:\href{https://doi.org/10.1080/1019678042000245254}{10.1080/1019678042000245254}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{McAndrew TC, Reich NG. An expert judgment model to
-predict early stages of the {COVID-19} outbreak in the {United States}.
-medRxiv. 2020; 2020.09.21.20196725.
-doi:\href{https://doi.org/10.1101/2020.09.21.20196725}{10.1101/2020.09.21.20196725}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Recchia G, Freeman ALJ, Spiegelhalter D. How well did
-experts and laypeople forecast the size of the {COVID-19} pandemic? PLOS
-ONE. 2021;16: e0250935.
-doi:\href{https://doi.org/10.1371/journal.pone.0250935}{10.1371/journal.pone.0250935}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Metaculus. A {Preliminary Look} at {Metaculus} and
-{Expert Forecasts}. 22 Jun 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.metaculus.com/news/2020/06/02/LRT/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Hypermind. Hypermind \textbar{} {Supercollective}
-intelligence for decision makers. {Hypermind}; 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.hypermind.com/en/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{CSET Foretell. {CSET Foretell}. 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.cset-foretell.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{PredictIt. {PredictIt}. 2021 {[}cited 13 Oct 2021{]}.
-Available: \url{https://www.predictit.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Held L, Meyer S, Bracher J. Probabilistic forecasting in
-infectious disease epidemiology: The 13th {Armitage} lecture. Statistics
-in Medicine. 2017;36: 3443--3460.
-doi:\href{https://doi.org/10.1002/sim.7363}{10.1002/sim.7363}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Crowdforecastr: Eliciting crowd forecasts in r shiny. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618519}{10.5281/zenodo.4618519}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Covid.german.forecasts: Forecasting covid-19 related metrics for the
-german/poland forecast hub. 2020. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-ecdcDownloadHistoricalData2020}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{ECDC. Download historical data (to 14 {December} 2020)
-on the daily number of new reported {COVID-19} cases and deaths
-worldwide. {European Centre for Disease Prevention and Control}; 14 Dec
-2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rkiRKICoronavirusSARSCoV22021}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{RKI. {RKI} - {Coronavirus SARS-CoV-2} - {Aktueller
-Lage-}/{Situationsbericht} des {RKI} zu {COVID-19}. 2021 {[}cited 30 May
-2021{]}. Available:
-\url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-forsal.plRozbieznosciStatystykachKoronawirusa2020}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Forsal.pl. Rozbieżności w statystykach koronawirusa. 22
-tys. przypadków będą doliczone do ogólnej liczby wyników. 2020 {[}cited
-30 May 2021{]}. Available:
-\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Ärzteblatt DÄG Redaktion Deutsches.
-SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an. {Deutsches
-Ärzteblatt}; 3 Nov 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Fay C, Guyader V, Rochette S, Girard C. Golem: A
-framework for robust shiny applications. 2021. Available:
-\url{https://github.com/ThinkR-open/golem}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie
-Y, et al. Shiny: Web application framework for r. 2021. Available:
-\url{https://CRAN.R-project.org/package=shiny}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Our World in Data. {COVID-19 Data Explorer}. {Our World
-in Data}; 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://ourworldindata.org/coronavirus-data-explorer}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K,
-Ellis P, et al. EpiNow2: Estimate real-time case counts and time-varying
-epidemiological parameters. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957489}{10.5281/zenodo.3957489}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Fraser C. Estimating {Individual} and {Household
-Reproduction Numbers} in an {Emerging Epidemic}. PLOS ONE. 2007;2: e758.
-doi:\href{https://doi.org/10.1371/journal.pone.0000758}{10.1371/journal.pone.0000758}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation2020}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{epiforecasts.io/covid. Covid-19: {Temporal} variation in
-transmission during the {COVID-19} outbreak. {Covid-19}; 2020 {[}cited
-30 May 2021{]}. Available: \url{https://epiforecasts.io/covid/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Sherratt K, Abbott S, Meakin SR, Hellewell J, Munday JD,
-Bosse N, et al. Exploring surveillance data biases when estimating the
-reproduction number: With insights into subpopulation transmission of
-{Covid-19} in {England}. 2021; 2020.10.18.20214585.
-doi:\href{https://doi.org/10.1101/2020.10.18.20214585}{10.1101/2020.10.18.20214585}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abbottEstimatingTimevaryingReproduction2020a}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs
-HP, Bosse NI, et al. Estimating the time-varying reproduction number of
-{SARS-CoV-2} using national and subnational case counts. 2020 {[}cited
-14 Oct 2021{]}.
-doi:\href{https://doi.org/10.12688/wellcomeopenres.16006.1}{10.12688/wellcomeopenres.16006.1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Xu B, Gutierrez B, Hill S, Scarpino S, Loskill A, Wu J,
-et al. Epidemiological data from the nCoV-2019 outbreak: Early
-descriptions from publicly available data. 2020. Available:
-\url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Stan Development Team. RStan: The r interface to stan.
-2020. Available: \url{http://mc-stan.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG. Evaluating
-epidemic forecasts in an interval format. PLoS Comput Biol. 2021;17:
-e1008618.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1008618}{10.1371/journal.pcbi.1008618}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Gneiting T, Raftery AE. Strictly proper scoring rules,
-prediction, and estimation. Journal of the American Statistical
-Association. 2007;102: 359--378.
-doi:\href{https://doi.org/10.1198/016214506000001437}{10.1198/016214506000001437}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Scoringutils:
-Utilities for scoring and assessing predictions. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618017}{10.5281/zenodo.4618017}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-deutschewelleCoronavirusGermanyImpose2020}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Deutsche Welle. Coronavirus: {Germany} to impose
-one-month partial lockdown \textbar{} {DW} \textbar{} 28.10.2020. 2020
-{[}cited 29 Jun 2021{]}. Available:
-\url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Ganyani T, Kremer C, Chen D, Torneri A, Faes C, Wallinga
-J, et al. Estimating the generation interval for coronavirus disease
-(COVID-19) based on symptom onset data, march 2020. Eurosurveillance.
-2020;25. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith
-HR, et al. The incubation period of coronavirus disease 2019 (COVID-19)
-from publicly reported confirmed cases: Estimation and application.
-Annals of Internal Medicine. 2020;172: 577--582. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J,
-Munday J, et al. Covidregionaldata: Subnational data for the covid-19
-outbreak. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957539}{10.5281/zenodo.3957539}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Evaluating the use of the reproduction number as an
-epidemiological tool, using spatio-temporal trends of the {Covid-19}
-outbreak in {England} \textbar{} {medRxiv}. {[}cited 30 May 2021{]}.
-Available:
-\url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Riutort-Mayol G, Bürkner P-C, Andersen MR, Solin A,
-Vehtari A. Practical hilbert space approximate bayesian gaussian
-processes for probabilistic programming. 2020. Available:
-\url{https://arxiv.org/abs/2004.11408}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Scott JA, Gandy A, Mishra S, Unwin J, Flaxman S, Bhatt
-S. Epidemia: Modeling of epidemics using hierarchical bayesian models.
-2020. Available:
-\url{https://imperialcollegelondon.github.io/epidemia/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bhattSemiMechanisticBayesianModeling}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Bhatt S, Ferguson N, Flaxman S, Gandy A, Mishra S, Scott
-JA. Semi-{Mechanistic Bayesian} modeling of {COVID-19} with {Renewal
-Processes}. : 14. }
-
-\end{CSLReferences}
-
-\nolinenumbers
-
 \end{document}

### 2023-12-11 manuscript/manuscript.Rmd

@@
 
-Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza (e.g.
-\cite{mcgowanCollaborativeEffortsForecast2019, reichCollaborativeMultiyearMultimodel2019,  shamanForecastingSeasonalOutbreaks2012, biggerstaffResultsCentersDisease2016}), dengue fever [e.g.
+\cite{mcgowanCollaborativeEffortsForecast2019}
+
+Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza [e.g.
+@mcgowanCollaborativeEffortsForecast2019; @reichCollaborativeMultiyearMultimodel2019; @shamanForecastingSeasonalOutbreaks2012; @biggerstaffResultsCentersDisease2016], dengue fever [e.g.
 @johanssonOpenChallengeAdvance2019; @yamanaSuperensembleForecastsDengue2016; @colon-gonzalezProbabilisticSeasonalDengue2021], ebola [e.g.

### 2023-12-11 manuscript/original submission/manuscript.Rmd

--- 2022-08-20 manuscript/manuscript.Rmd
@@
     - \usepackage{lineno}
-    - \usepackage[T1]{fontenc}
     - \linenumbers
-    - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} 
-    - \newfloat{text}{thp}{}
-    - \floatname{text}{Text} 
-    - \renewcommand{\figurename}{}
-    - \newcommand{\newfigurename}{Hello}
-    - \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-    - \usepackage{nameref,hyperref}
+    -  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 output: 
-  rticles::plos_article:
-    extra_dependencies: 
-      caption: null
+  bookdown::pdf_document2:
+    extra_dependencies: ["float"]
     keep_tex:  true
@@
 linestretch: 2 
-include-header: 
-  \usepackage[T1]{fontenc}
-author:
-  - name: Nikos I. Bosse
-    email: nikos.bosse@lshtm.ac.uk
-    affiliation: 
-      - London School of Hygiene & Tropical Medicine
-      - CMMID
-    corresponding: nikos.bosse@lshtm.ac.uk
-  - name: Sam Abbott
-    email: sam.abbott@lshtm.ac.uk
-    affiliation: 
-      - London School of Hygiene & Tropical Medicine
-      - CMMID
-  - name: Johannes Bracher
-    email: johannes.bracher@kit.edu
-    affiliation: Karlsruhe Institute of Technology Institute of Economic Theory and Statistics
-  - name: Habakuk Hain
-    email: habakuk.hain@mpinat.mpg.de
-    affiliation: Max Planck Institute for Multidisciplinary Sciences
-  - name: Billy J. Quilty
-    email: Billy.Quilty@lshtm.ac.uk
-    affiliation: 
-      - London School of Hygiene & Tropical Medicine
-      - CMMID
-  - name: Mark Jit
-    email: Mark.Jit@lshtm.ac.uk
-    affiliation: 
-      - London School of Hygiene & Tropical Medicine
-      - CMMID
-  - name: Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group
-    email: cmmid@lshtm.ac.uk
-    affiliation: 
-      - London School of Hygiene & Tropical Medicine
-      - CMMID
-  - name: Edwin van Leeuwen
-    email: Edwin.VanLeeuwen@phe.gov.uk
-    affiliation:
-      - UK Health Security Agency
-      - London School of Hygiene & Tropical Medicine
-  - name: Anne Cori
-    email: a.cori@imperial.ac.uk
-    affiliation: 
-      - Imperial College London
-  - name: Sebastian Funk
-    email: sebastian.funk@lshtm.ac.uk
-    affiliation: 
-      - London School of Hygiene & Tropical Medicine
-      - CMMID
-address:
-  - code: London School of Hygiene & Tropical Medicine
-    address: Department of Infectious Disease Epidemiology, London School of Hygiene & Tropical Medicine, London, United Kingdom
-  - code: CMMID
-    address: Centre for the Mathematical Modelling of Infectious Diseases (members of the CMMID COVID-19 working group are listed in S1 Acknowledgements), London, United Kingdom
-  - code: Karlsruhe Institute of Technology Institute of Economic Theory and Statistics
-    address: Institute of Economic Theory and Statistics, Karlsruhe Institute of Technology, Karlsruhe, Germany
-  - code: Max Planck Institute for Multidisciplinary Sciences
-    address: Max Planck Institute for Multidisciplinary Sciences, Göttingen, Germany
-  - code: UK Health Security Agency
-    address: UK Health Security Agency, London United Kingdom
-  - code: Imperial College London
-    address:  MRC Centre for Outbreak Analysis and Modelling, Department of Infectious Disease Epidemiology, School of Public Health, Imperial College London, London, United Kingdom
-
-abstract: |
+bibliography:
+  - references.bib
+  - GermanPolishpaper.bib
+csl: vancouver.csl
+---
+
+*Nikos I.
+Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy J.
+Quilty, Mark Jit, Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk*
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
+                      out.width = "100%", 
+                      fig.pos = "H", out.extra = "")
+
+library(kableExtra)
+library(magrittr)
+library(knitr)
+```
+
+# Abstract
+
 Forecasts based on epidemiological modelling have played an important role in shaping public policy throughout the COVID-19 pandemic.
@@
 
-author_summary: |
+# Author summary
+
 Mathematical models of COVID-19 have played a key role in informing governments across the world.
@@
 To investigate what modelling is able to add beyond the subjective opinion of the researcher alone, we compared human forecasts with model-based predictions of COVID-19 cases and deaths submitted to the so-called German/Polish Forecast Hub (which collates a variety of models from a range of teams).
-|
 We found that our human forecasts consistently outperformed an aggregate of all available model-based forecasts when predicting cases, but not when predicting deaths.
@@
 This potentially has very relevant policy implications, as agencies informing policy-makers could benefit from routinely eliciting human forecasts in addition to model-based predictions to inform policies.
-
-bibliography:
-  - references.bib
-  - GermanPolishpaper.bib
-csl: plos.csl
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
-                      out.width = "100%", 
-                      fig.pos = "H", out.extra = "")
-
-library(kableExtra)
-library(magrittr)
-library(knitr)
-```
 
@@
 
-## Ethics statement
-
-This study has been approved by the London School of Hygiene & Tropical Medicine Research
-Ethics Committee (reference number 22290). Consent from participants was obtained in written form.
-
-## Overview
-
 We created and submitted the following forecasts to the German and Polish Forecast Hub: 1) a direct human forecast (henceforth called “crowd forecast”), elicited from participants through a web application [@crowdforecastr] and 2) two semi-mechanistic model-based forecasts ("renewal model" and "convolution model") informed by basic assumptions about COVID-19 epidemiology.
@@
 These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, @forsal.plRozbieznosciStatystykachKoronawirusa2020), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, @aerzteblattSARSCoV2DiagnostikRKIPasst2020).
-The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see \nameref{fig:daily-truth-update} and \nameref{fig:weekly-truth-update} Figs).
 
@@
 To make a forecast in the application participants could select a predictive distribution (with the default being log-normal) to represent the probability that the forecasted quantity took certain values.
-Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in \nameref{fig:screenshot}).
+Median and width of the uncertainty could be adjusted by either interacting with a figure showing their forecast or providing numerical values (see screenshot in Figure \@ref(fig:screenshot) in the SI).
 The default shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in weekly log observed forecasts (i.e.
 as $\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )$).
-A comparison of the crowd forecasts against the default baseline shown in the application is displayed in \nameref{fig:compare-forecasters}.
 Our interface also allowed participants to view past observations based on the hub data, as well as their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  @ourworldindataCOVID19DataExplorer2020.
 These data included, for example, notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.
-From November 26 2020 on we displayed weekly small reports with a visualisation of past forecasts and scores on our website, epiforecasts.io.
 
@@
 Forecasts from all forecasters were then aggregated using an unweighted quantile-wise mean (i.e., the $\alpha$-quantile of the ensemble is given by the mean of all submitted $\alpha$-quantiles).
-To avoid issues with users trying out the app and submitting a random forecast, we required that a forecaster needed to make a forecast for at least two targets for a given forecast in order to be included in the crowd forecast ensemble.
-On a few occasions we deleted forecasts that were clearly the result of a user or software error (such as for example forecasts that were zero everywhere).
+On a few occasions, individual forecasts were assessed as clearly erroneous by visual inspection and subsequently removed before aggregation and were excluded from the submission as well as the analysis.
 
@@
 
+The study was approved by the Observational / Interventions Research Ethics Committee at the London School of Hygiene & Tropical Medicine, LSHTM Ethics Reference: 22290.
+
 ## Model-based forecasts
@@
 We used two Bayesian semi-mechanistic models from the `EpiNow2` R package (version 1.3.3) as our model-based forecasts [@epinow2].
-The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths (see details in \nameref{txt:details-models}).
+The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths (see details in the SI).
 It estimated the effective reproduction number $R_t$ (the average number of people each person infected at time t is expected to infect in turn) and modelled future infections as a weighted sum of past infection multiplied by $R_t$.
@@
 
-The second model (“convolution model”, see details in \nameref{txt:details-models}) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses).
+The second model (“convolution model”, see details in SI) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses).
 The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model.
@@
 To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available.
-To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see \nameref{fig:agg-performance-all-late} and \nameref{tab:score-table-late-2} and \nameref{tab:score-table-late-4}s).
+To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) were scored only over the later period for which all forecasts were available (see Section \@ref(sensitivity-analysis) in the SI).
 Results remained broadly unchanged.
@@
 how many observed values fall inside all 50% prediction intervals).
-Scoring metrics are explained in more detail in \nameref{tab:scoring-metrics}.
+Scoring metrics are explained in more detail in Table \@ref(tab:scoring-metrics) in the SI.
 All scores were calculated using the `scoringutils` R package [@scoringutils].
@@
 At all stages of the evaluation our forecasts were compared to the median ensemble of all *other* models submitted to the German and Polish Forecast Hub ("Hub ensemble").
-This "Hub ensemble" was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see \nameref{tab:table-ensemble-versions} and \nameref{fig:num-ensemble-members}).
-What we call "Hub ensemble" in this article therefore differs from the "official Hub ensemble" (here called "hub-ensemble-realised") which included crowd forecasts as well as renewal model forecasts.
+This "Hub ensemble" was retrospectively computed and excludes all our models.
+It therefore differs from the official Hub ensemble (here called "hub-ensemble-realised") which included crowd forecasts as well as renewal model forecasts.
 To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e.
@@
 ```{r}
-captiontitle <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future."
-caption <- "A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
+caption <- "Visualisation of aggregate performance metrics across for forecasts one to four weeks into the future (marked as 1 - 4 on the x axis).
+A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
 WIS is decomposed into its components dispersion, over-prediction and under-prediction.
@@
 Standard deviation of all WIS values for different horizons"
-
-label <- "fig:agg-performance-all"
-```
-
-```{r agg-performance-all, fig.cap=caption, eval = FALSE}
-# knitr::include_graphics("../analysis/plots/aggregate-performance-all-v4.png")
-```
-
-```{r, results = "asis"}
-cat("\\begin{figure}[H]\n", 
-    "\\caption{\\bf{", captiontitle, "}}\n", 
-    caption, "\n",
-    "\\label{", label, "}\n", 
-    "\\end{figure}", sep = "")
-```
-
-```{r}
-captiontitle <- "Two week ahead forecasts and corresponding scores. "
+```
+
+```{r agg-performance-all, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/aggregate-performance-all-v4.png")
+```
+
+```{r}
 caption <- "A, C: Visualisation of 50\\% prediction intervals of two week ahead forecasts against the reported values.
@@
 B, D: Visualisation of corresponding WIS."
-label <- "fig:forecasts-and-truth"
-```
-
-```{r forecasts-and-truth, fig.cap=caption, eval = FALSE}
-# knitr::include_graphics("../analysis/plots/figure-forecasts-2.png")
-```
-
-```{r, results = "asis"}
-cat("\\begin{figure}[H]\n", 
-    "\\caption{\\bf{", captiontitle, "}}\n", 
-    caption, "\n",
-    "\\label{", label, "}\n", 
-    "\\end{figure}", sep = "")
+```
+
+```{r forecasts-and-truth, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/figure-forecasts-2.png")
 ```
@@
 
-For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Fig \ref{fig:agg-performance-all}A) and locations (\nameref{fig:performance-locations-rel}A Fig).
-For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (\nameref{tab:score-table-2} Table).
-Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Fig \ref{fig:distribution-scores}).
-Overall, low variance in forecast performance was closely linked with good mean performance (Fig \ref{fig:agg-performance-all}H and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
-The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Fig \ref{fig:distribution-scores}), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
+For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure \@ref(fig:performance-locations-rel)A).
+For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \@ref(tab:score-table-2)).
+Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Figure \@ref(fig:distribution-scores)).
+Overall, low variance in forecast performance was closely linked with good mean performance (Figures \@ref(fig:agg-performance-all)H and and \@ref(fig:agg-performance-all)A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
+The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel.
 WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.
@@
 To varying degrees, all forecasts exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened.
-For example, all forecasts failed to predict the change in trend from increase to decrease that happened in November in Germany and severely overshot reported cases (Fig \ref{fig:forecasts-and-truth}A).
+For example, all forecasts failed to predict the change in trend from increase to decrease that happened in November in Germany and severely overshot reported cases (Figure \@ref(fig:forecasts-and-truth)A).
 This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past of observations.
@@
 All forecasting approaches, including the Hub ensemble, were overconfident, i.e.
-they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Fig \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
+they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
 Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts.
-This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Fig \ref{fig:agg-performance-all}E) and only showed a small increase in uncertainty across forecast horizons.
-The crowd forecasts prediction intervals were also noticeably narrower than the default baseline shown to forecasters in the application (see \nameref{fig:compare-forecasters}).
-
-In spite of good performance in terms of the absolute error (Fig \ref{fig:agg-performance-all}G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Fig \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D as well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
-Despite worse performance in terms of absolute error (Fig \ref{fig:agg-performance-all}G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
-The crowd forecasts, on the other hand, showed a smaller bias than the renewal model, but were overconfident.
+This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \@ref(fig:agg-performance-all)E) and only showed a small increase in uncertainty across forecast horizons.
+In spite of good performance in terms of the absolute error (Figure \@ref(fig:agg-performance-all)G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Figure \@ref(fig:agg-performance-all)C,D and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
+Despite worse performance in terms of absolute error (Figure \@ref(fig:agg-performance-all)G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.
 
 The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons.
-The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Fig \ref{fig:agg-performance-all}F).
-Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Fig \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
-
-Generally, trends in overall performance were broadly similar across locations (\nameref{fig:performance-locations} and \nameref{fig:performance-locations-rel} Figs).
+The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \@ref(fig:agg-performance-all)F).
+Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \@ref(fig:agg-performance-all)A and \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)).
+
+Generally, trends in overall performance were broadly similar across locations (Figures \@ref(fig:performance-locations) and \@ref(fig:performance-locations-rel)).
 Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly.
-However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (\nameref{fig:performance-locations-rel}A, \nameref{fig:performance-locations-rel}G, \nameref{fig:agg-performance-all-Germany} and \nameref{fig:agg-performance-all-Poland} Figs).
+However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figure \@ref(fig:performance-locations-rel)A and \@ref(fig:performance-locations-rel)G).
 
@@
 
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figs \ref{fig:agg-performance-all}B and \nameref{fig:performance-locations}B).
+For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B).
 Relative WIS values for the models two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1 (Hub ensemble) and 1.79 (renewal model).
-The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figs \ref{fig:agg-performance-all}B and \nameref{fig:performance-locations}B), and also better than the convolution model three and four weeks ahead.
+The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B), and also better than the convolution model three and four weeks ahead.
 Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate $R_t$ trace from deaths, does not use the available information efficiently.
-The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Fig \ref{fig:agg-performance-all}B, \nameref{tab:score-table-4}).
+The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \@ref(fig:agg-performance-all)B, Table \@ref(tab:score-table-4)).
 
@@
 The Hub ensemble had the greatest coverage, with empirical coverage of the 50% and 90% prediction intervals exceeding 50%, and 90%, respectively, across all forecast horizons.
-Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Fig \ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
+Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D).
 As for cases, the crowd forecast tended to have the narrowest prediction intervals and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest.
@@
 
-For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict (see Fig \ref{fig:agg-performance-all}F).
-The convolution model had a strong tendency to under-predict, with the magnitude of under-prediction steadily decreasing for longer forecast horizons.
+For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \@ref(fig:agg-performance-all)F.
+The convolution model had a strong tendency to under-predict, which steadily decreased for longer forecast horizons.
 The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction.
-For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Fig \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
-
-```{r}
-captiontitle <- "Distribution of scores. "
+For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \@ref(fig:agg-performance-all)A, \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2), \@ref(tab:score-table-4)).
+
+```{r}
 caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
 Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores."
-label <- "fig:distribution-scores"
-```
-
-```{r distribution-scores, fig.cap=caption, eval = FALSE}
-# knitr::include_graphics("../analysis/plots/distribution_scores_wis-2.png")
-```
-
-```{r, results = "asis"}
-cat("\\begin{figure}[H]\n", 
-    "\\caption{\\bf{", captiontitle, "}}\n", 
-    caption, "\n",
-    "\\label{", label, "}\n", 
-    "\\end{figure}", sep = "")
-```
-
-```{r}
-captiontitle <- "Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble."
-caption <- "“Hub-ensemble” \\textit{excludes} all our models, Hub-ensemble-all \\textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
+B: Distribution of WIS separate by country."
+```
+
+```{r distribution-scores, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/distribution_scores_wis-2.png")
+```
+
+```{r}
+caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble.
+“Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included.
+Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions.
+For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
+A: mean weighted interval score (WIS) across horizons.
+B: median WIS.
+C: Absolute error of the median forecast.
+D: Standard deviation of the WIS.
+E: Dispersion (higher values mean greater spread of the forecast).
 F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
+general tendency to over- or underpredict.
 Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
-label <- "fig:agg-performance-ensemble-rel"
-```
-
-```{r agg-performance-ensemble-rel, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-v4.png")
-```
-
-```{r, results = "asis"}
-cat("\\begin{figure}[H]\n", 
-    "\\caption{\\bf{", captiontitle, "}}\n", 
-    caption, "\n",
-    "\\label{", label, "}\n", 
-    "\\end{figure}", sep = "")
+G: Empirical coverage of the 50\\% prediction intervals.
+F: Empirical coverage of the 90\\% prediction intervals"
+```
+
+```{r agg-performance-ensemble, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-v4.png")
 ```
@@
 ## Contribution to the Forecast Hub
-\label{contributions-hub}
 
@@
 Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.
-An overview of all models and ensemble versions is shown in \nameref{tab:table-ensemble-versions}.
+An overview of all models and ensemble versions is shown in Table \@ref(tab:table-ensemble-versions) in the SI.
 
 For cases, our contributions (compared to the Hub ensemble without our contributions) consistently improved performance across all forecasting horizons (rel.
-WIS 0.9 two weeks ahead, see \nameref{tab:score-table-ensemble-2} Table).
+WIS 0.9 two weeks ahead, Table \@ref(tab:score-table-ensemble-2)).
 Contributions from the crowd forecasts alone also improved performance of the Hub ensemble across all forecast horizons, while contributions from the renewal model had a negative effect for longer horizons (rel.
@@
 The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model have improved performance (\nameref{tab:score-table-ensemble-4}).
+Only for predictions four weeks ahead would removing the renewal model have improved performance (Table \@ref(tab:score-table-ensemble-4)).
 The realised ensemble performed comparably to the crowd forecasts for predictions one to two weeks ahead, and worse for greater forecast horizons.
@@
 For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel.
-WIS of the Hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, \nameref{tab:score-table-ensemble-2} and \nameref{tab:score-table-ensemble-4}s).
+WIS of the hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \@ref(tab:score-table-ensemble-2) and \@ref(tab:score-table-ensemble-4)).
 Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons).
-This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Fig \ref{fig:agg-performance-all}) and especially worse for longer horizons.
+This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \@ref(fig:agg-performance-all)) and especially worse for longer horizons.
 
@@
 <!-- In general, the median ensemble tended to perform slightly better than the mean ensemble - needs more analysis -->
-General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figs \ref{fig:agg-performance-ensemble-rel}B and \nameref{fig:agg-performance-ensemble-mean}B).
+General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \@ref(fig:agg-performance-ensemble)B and \@ref(fig:agg-performance-ensemble-mean)B).
 This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far.
@@
 This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data).
-The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Fig \ref{fig:forecasts-and-truth}A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting which have less of an influence on weekly reporting.
+The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \@ref(fig:forecasts-and-truth)A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.
 
@@
 On the other hand, R shiny facilitated quick development and allowed us to provide our crowd forecasting tooling as an open source R package, meaning that it is available for others to use, for example in settings like early-stage outbreaks where model-based forecasts are not available.
-In light of the relatively small number of Hub ensemble models, performance of the Hub ensemble is also difficult to generalise.
-More research is needed to replicate these findings and investigate how crowd forecasts compare against the types of models and model ensembles policy makers use to inform their decisions.
-
-Our work suggests that crowd forecasts and model-based forecasts could have different strengths and may be able to complement each other.
+
+Our work suggests that crowd forecasts and model-based forecasts have different strengths and may be able to complement each other.
 When choosing a suitable approach for a given task it is important to take into account how the output will be used.
@@
 
-\section*{References}
-::: {#refs}
-:::
-
-\clearpage
-
-\section*{Acknowledgments}
+**Acknowledgements**
+
+NIB received funding from the Health Protection Research Unit (grant code NIHR200908, https://www.nihr.ac.uk/).
+SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/).
+The work of JB was supported by the Helmholtz Foundation (https://www.helmholtz.de/) via the SIMCARD Information and Data Science Pilot Project.
+This research was partly funded by the National Institute for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 & 16/136/46) using UK aid from the UK Government to support global health research.
+The views expressed in this publication are those of the author(s) and not necessarily those of the NIHR or the UK Department of Health and Social Care.
+BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859, https://www.gatesfoundation.org/).
+EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908, https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688, https://ec.europa.eu/programmes/horizon2020/).
+AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/), and the Academy of Medical Sciences (https://acmedsci.ac.uk/).
+SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/), and the NIHR (NIHR200908, https://www.nihr.ac.uk/).
 
@@
 
+We would also like to acknowledge (in a randomised order) the members of Centre for the Mathematical Modelling of Infectious Diseases COVID-19 Working Group at the the London School of Hygiene & Tropical Medicine: Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie Diamond, Katherine E.
+Atkins, Rein M G J Houben, Jiayao Lei, Rachel Lowe, David Simons, Sophie R Meakin, Nicholas G.
+Davies, Timothy W Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly, Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas, Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson, Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun, Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche, James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday, Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael Pung, Anna M Foss.
+
 \clearpage
@@
 \beginsupplement
+
+# (APPENDIX) Supplementary information {-}
+
+# Supplementary information
+
+## Scoring metrics used
+
+```{r scoring-metrics}
+wis <- list(
+  Metric = "WIS (Weighted) interval score", 
+  `Explanation` = r"(The weighted interval score (smaller values are better) is a proper scoring rule for quantile forecasts.
+It converges to the continuos ranked probability score (which itself is a generalisation of the absolute error to probabilistic forecasts) for an increasing number of intervals.
+The score can be decomposed into a dispersion (uncertainty) component and penalties for over- and underprediction.
+For a single interval, the score is computed as
+  $$IS_\alpha(F,y) = (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u), $$ 
+  where $1()$ is the indicator function, $y$ is the true value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution $F$, i.e.
+the lower and upper bound of a single prediction interval.
+For a set of $K$ prediction intervals and the median $m$, the score is computed as a weighted sum,
+  $$WIS = \frac{1}{K + 0.5} \cdot \left( w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y) \right), $$
+  where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.
+
+Its proximity to the absolute error means that when averaging across multiple targets (e.g. different weeks), it will be dominated by targets with higher absolute values.)", 
+  `Caveats` = "The wis is based on measures of absolute error. When averaging across multiple targets, it will therefore be dominated by targets with higher absolute values.",
+  `References` = ""
+)
+
+interval_coverage <- list(
+  `Metric` = "Interval coverage", 
+  `Explanation` = r"(Interval coverage is a measure of marginal calibration and indicates the proportion of observed values that fall in a given prediction interval range.
+Nominal coverage represents the percentage of observed values that should ideally be covered (e.g.
+we would like a 50 percent prediction interval to cover on average 50 percent of the observations), while empirical coverage is the actual percentage of observations covered by a certain prediction interval.)",
+  `Caveats` = "",
+  `References` = ""
+)
+
+bias <- list(
+  `Metric` = "Bias", 
+  `Explanation` = r"((Relative) bias is a measure of the general tendency of a forecaster to over- or underpredict.
+Values are between -1 and 1 and 0 ideally.
+For continuous forecasts, bias is given as
+$$B(F, y) = 1 - 2 \cdot (F (y)), $$ 
+where $F$ is the CDF of the predictive distribution and $y$ is the observed value.
+
+For quantile forecasts, $F(y)$ is replaced by a quantile rank.
+The appropriate quantile rank is determined by whether the median forecast is below  or above the true value.
+We then take the innermost quantile rank for which the quantile is still larger (under-prediction) or smaller (over-prediction) than the observed value.
+
+In contrast to the over- and underprediction penalties of the interval score it is bound between 0 and 1 and represents a general tendency of forecasts to be biased rather than the absolute amount of over- and underprediction.
+It is therefore a more robust measurement.)",
+  `Caveats` = "",
+  `References` = ""
+)
+
+data <- rbind(as.data.frame(wis), 
+              as.data.frame(interval_coverage),
+              as.data.frame(bias))
+
+data[, 1:2] %>%
+  kableExtra::kbl(format = "latex", booktabs = TRUE, 
+                  escape = FALSE,
+                  caption = "Overview of the scoring metrics used.",
+                  longtable = TRUE,
+                  linesep = c('\\addlinespace \\addlinespace')) %>%
+  kableExtra::column_spec(1, width = "2.5cm") %>%
+  kableExtra::column_spec(2, width = "13.0cm") %>%
+  kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))
+
+```
+
+\clearpage
+
+## The crowdforecasting app
+
+```{r}
+caption <- "Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021). "
+```
+
+```{r screenshot, fig.cap=caption}
+knitr::include_graphics("../crowd-forecast/Screenshot-forecasting-app.png")
+```
+
+\clearpage
+
+## Further details on the semi-mechanistic forecasting models
+
+### Renewal equation model
+
+The model was initialised prior to the first observed data point by assuming constant exponential growth for the mean of assumed delays from infection to case report.
+
+\begin{align}
+  I_{t} &= I_0 \exp  \left(r t \right)  \\
+  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
+  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
+\end{align}
+
+Where $I_{obs}$ and $r_{obs}$ are estimated from the first week of observed data.
+For the time window of the observed data infections were then modelled by weighting previous infections by the generation time and scaling by the instantaneous reproduction number.
+These infections were then convolved to cases by date ($O_t$) and cases by date of report ($D_t$) using log-normal delay distributions.
+This model can be defined mathematically as follows,
+
+\begin{align}
+  \log R_{t} &= \log R_{t-1} + \mathrm{GP}_t \\
+  I_t &= R_t \sum_{\tau = 1}^{15} w(\tau | \mu_{w}, \sigma_{w}) I_{t - \tau} \\
+  O_t &= \sum_{\tau = 0}^{15} \xi_{O}(\tau | \mu_{\xi_{O}}, \sigma_{\xi_{O}}) I_{t-\tau} \\
+  D_t &= \alpha \sum_{\tau = 0}^{15} \xi_{D}(\tau | \mu_{\xi_{D}}, \sigma_{\xi_{D}}) O_{t-\tau} \\ 
+  C_t &\sim \mathrm{NB}\left(\omega_{(t \mod 7)}D_t, \phi\right)
+\end{align}
+
+Where,
+\begin{align}
+     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
+    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
+    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
+\end{align}
+
+This model used the following priors for cases,
+
+\begin{align}
+     R_0 &\sim \mathcal{LN}(0.079, 0.18) \\
+    \mu_w &\sim \mathcal{N}(3.6, 0.7) \\
+    \sigma_w &\sim \mathcal{N}(3.1, 0.8) \\
+    \mu_{\xi_{O}} &\sim \mathcal{N}(1.62, 0.064) \\
+    \sigma_{\xi_{O}} &\sim \mathcal{N}(0.418, 0.069) \\
+    \mu_{\xi_{D}} &\sim \mathcal{N}(0.614, 0.066) \\
+    \sigma_{\xi_{D}} &\sim \mathcal{N}(1.51, 0.048) \\
+    \alpha &\sim \mathcal{N}(0.25, 0.05) \\
+    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
+    \phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
+\end{align}
+
+and updated the reporting process as follows when forecasting deaths,
+
+\begin{align}
+    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
+    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
+    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
+\end{align}
+
+$\alpha$, $\mu$, $\sigma$, and $\phi$ were truncated to be greater than 0 and with $\xi$, and $w$ normalised to sum to 1.
+
+The prior for the generation time was sourced from [@generationinterval] but refit using a log-normal incubation period with a mean of 5.2 days (SD 1.1) and SD of 1.52 days (SD 1.1) with this incubation period also being used as a prior [@incubationperiod] for $\xi_{O}$.
+This resulted in a gamma-distributed generation time with mean 3.6 days (standard deviation (SD) 0.7), and SD of 3.1 days (SD 0.8) for all estimates.
+We estimated the delay between symptom onset and case report or death required to convolve latent infections to observations by fitting an integer adjusted log-normal distribution to 10 subsampled bootstraps of a public linelist for cases in Germany from April 2020 to June 2020 with each bootstrap using 1% or 1769 samples of the available data  [@kraemer2020epidemiological; @covidregionaldata] and combining the posteriors for the mean and standard deviation of the log-normal distribution [@epinow2; @epiforecasts.io/covidCovid19TemporalVariation2020; @EvaluatingUseReproduction; @rstan].
+
+$GP_t$ is an approximate Hilbert space Gaussian process as defined in [@approxGP] using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20% of the number of days used in fitting).
+The length scale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days.
+The magnitude of the Gaussian process was assumed to be normally distributed centred at 0 with a standard deviation of 0.1.
+
+From the forecast time horizon ($T$) and onwards the last value of the Gaussian process was used (hence $R_t$ was assumed to be fixed) and latent infections were adjusted to account for the proportion of the population that was susceptible to infection as follows,
+
+\begin{equation}
+    I_t = (N - I^c_{t-1}) \left(1 - \exp \left(\frac{-I'_t}{N - I^c_{T}}\right)\right),
+\end{equation}
+
+where $I^c_t = \sum_{s< t} I_s$ are cumulative infections by $t-1$ and $I'_t$ are the unadjusted infections defined above.
+This adjustment is based on that implemented in the `epidemia` R package [@epidemia; @bhattSemiMechanisticBayesianModeling].
+
+#### Convolution model
+
+The convolution model shares the same observation model as the renewal model but rather than assuming that an observation is predicted by itself using the renewal equation instead assumes that it is predicted entirely by another observation after some parametric delay.
+It can be defined mathematically as follows,
+
+\begin{equation} 
+    D_{t} \sim \mathrm{NB}\left(\omega_{(t \mod 7)} \alpha \sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) C_{t-\tau},  \phi \right)
+\end{equation}
+
+with the following priors,
+
+\begin{align}
+    \frac{\omega}{7} &\sim \mathrm{Dirichlet}(1, 1, 1, 1, 1, 1, 1) \\
+    \alpha &\sim \mathcal{N}(0.01, 0.02) \\
+    \xi &\sim \mathcal{LN}(\mu, \sigma) \\
+    \mu &\sim \mathcal{N}(2.5, 0.5) \\
+\sigma &\sim \mathcal{N}(0.47, 0.2) \\
+\phi &\sim \frac{1}{\sqrt{\mathcal{N}(0, 1)}}
+\end{align}
+
+with $\alpha$, $\mu$, $\sigma$, and $\phi$ truncated to be greater than 0 and with $\xi$ normalised such that $\sum_{\tau = 0}^{30} \xi(\tau | \mu, \sigma) = 1$.
+
+### Model fitting
+
+Both models were implemented using the `EpiNow2` R package (version 1.3.3) [@epinow2].
+Each forecast target was fitted independently for each model using Markov-chain Monte Carlo (MCMC) in stan [@rstan].
+A minimum of 4 chains were used with a warmup of 250 samples for the renewal equation-based model and 1000 samples for the convolution model.
+2000 samples total post warmup were used for the renewal equation model and 4000 samples for the convolution model.
+Different settings were chosen for each model to optimise compute time contingent on convergence.
+Convergence was assessed using the R hat diagnostic [@rstan].
+For the convolution model forecast the case forecast from the renewal equation model was used in place of observed cases beyond the forecast horizon using 1000 posterior samples.
+12 weeks of data was used for both models though only 3 weeks of data were included in the likelihood for the convolution model.
+
+\clearpage
 
@@
 }
-```
-
-\section*{Supporting information}
-
-\paragraph*{S1 Table.}
-\label{tab:scoring-metrics}
-\textbf{Overview of the scoring metrics used.}
-
-\paragraph*{S1 Text.}
-\label{txt:details-models}
-\textbf{Further details on the semi-mechanistic forecasting models.}
-
-\paragraph*{S1 Fig.}
-\label{fig:screenshot}
-\textbf{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021).}
-
-\paragraph*{S2} \textbf{Table.}
-\label{tab:score-table-2}
-\textbf{Scores for one and two week ahead forecasts.} Scores are cut to three significant digits and rounded).
+
+```
+
+## Tables with results of the forecast evaluation
+
+```{r}
+caption <- 
+  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded).
 Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
@@
 Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.
-
-\paragraph*{S3 Table.}
-\label{tab:score-table-4}
-\textbf{Scores for three and four weeks ahead forecasts.} 
-Scores are cut to three significant digits and rounded).
+50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
+```
+
+```{r score-table-2}
+table <- readRDS("../analysis/plots/table_scores_2_ahead.rds")
+add_caption(table, caption, label = "tab:score-table-2")
+```
+
+```{r}
+caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
+```
+
+```{r score-table-4}
+table <- readRDS("../analysis/plots/table_scores_4_ahead.rds")
+add_caption(table, caption, label = "tab:score-table-4")
+
+```
+
+\clearpage
+
+## Aggregate performance by location
+
+### Performance across locations in absolute terms
+```{r}
+caption <- "Visualisation of aggregate performance metrics across locations.
+A: mean weighted interval score (WIS) across horizons.
+B: median WIS.
+C: Absolute error of the median forecast.
+D: Standard deviation of the WIS.
+E: Dispersion (higher values mean further spread out forecast).
+F: Bias, i.e.
+general tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Empirical coverage of the 50\\% prediction intervals.
+F: Empirical coverage of the 90\\% prediction intervals."
+```
+
+```{r performance-locations, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-v4.png")
+```
+
+## Performance across locations in relative terms
+
+```{r}
+caption <- " Visualisation of aggregate performance metrics across locations relative to the Hub ensemble (excluding our contributions).
+A: mean weighted interval score (WIS) across horizons.
+B: median WIS.
+C: Absolute error of the median forecast.
+D: Standard deviation of the WIS.
+E: Dispersion (higher values mean further spread out forecast).
+F: Bias, i.e.
+general tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Empirical coverage of the 50\\% prediction intervals.
+F: Empirical coverage of the 90\\% prediction intervals."
+```
+
+```{r performance-locations-rel, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4.png")
+```
+
+\clearpage
+
+## Visualisation of daily reported cases and deaths
+
+```{r}
+caption <- "Visualisation of daily report data. The black line represents weekly data divided by seven. Data were last accessed through the German and Polish Forecast Hub on August 21 2021."
+```
+
+```{r daily-truth, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/daily_truth.png")
+```
+
+\clearpage
+
+## Visualisation of scores and forecasts 1, 3, 4 weeks ahead
+
+```{r}
+caption <- "A, C: Visualisation of 50\\% prediction intervals of one week ahead forecasts against the reported values.
+Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
+B, D: Visualisation of corresponding WIS."
+```
+
+```{r forecasts-and-truth-1, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/figure-forecasts-1.png")
+```
+
+```{r}
+caption <- gsub(x = caption, pattern = "one", replacement = "three")
+```
+
+```{r forecasts-and-truth-3, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/figure-forecasts-3.png")
+```
+
+```{r}
+caption <- gsub(x = caption, pattern = "three", replacement = "four")
+```
+
+```{r forecasts-and-truth-4, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/figure-forecasts-4.png")
+```
+
+\clearpage
+
+## Distribution of scores
+
+### Absolute scores
+
+```{r}
+caption <- "A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country."
+```
+
+```{r distribution-scores-1, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/distribution_scores_wis-1.png")
+```
+
+```{r}
+caption <- gsub(x = caption, pattern = "one", replacement = "three")
+```
+
+```{r distribution-scores-3, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/distribution_scores_wis-3.png")
+```
+
+```{r}
+caption <- gsub(x = caption, pattern = "three", replacement = "four")
+```
+
+```{r distribution-scores-4, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/distribution_scores_wis-4.png")
+```
+
+### Ranks achieved by forecasts
+
+```{r}
+caption <- "A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
+B: Distribution of ranks separate by country."
+```
+
+```{r distribution-scores-ranks-1, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/distribution_scores_wis-1-ranks.png")
+```
+
+```{r}
+caption <- gsub(x = caption, pattern = "one", replacement = "two")
+```
+
+```{r distribution-scores-ranks-2, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/distribution_scores_wis-2-ranks.png")
+```
+
+```{r}
+caption <- gsub(x = caption, pattern = "two", replacement = "three")
+```
+
+```{r distribution-scores-ranks-3, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/distribution_scores_wis-3-ranks.png")
+```
+
+```{r}
+caption <- gsub(x = caption, pattern = "three", replacement = "four")
+```
+
+```{r distribution-scores-ranks-4, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/distribution_scores_wis-4-ranks.png")
+```
+
+\clearpage
+
+## Comparison of ensembles
+
+### Performance visualisation mean ensemble
+
+```{r}
+caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
+“Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included.
+Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions.
+For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
+A: mean weighted interval score (WIS) across horizons.
+B: median WIS.
+C: Absolute error of the median forecast.
+D: Standard deviation of the WIS.
+E: Dispersion (higher values mean greater spread of the forecast).
+F: Bias, i.e.
+general tendency to over- or underpredict.
+Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
+G: Empirical coverage of the 50\\% prediction intervals.
+F: Empirical coverage of the 90\\% prediction intervals"
+```
+
+```{r agg-performance-ensemble-mean, fig.cap=caption}
+knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-mean-v4.png")
+```
+
+### Tables median ensemble
+
+```{r}
+caption <- 
+  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble.
 Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
@@
 Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\% and 90\%-coverage are the percentage of observed values that fell within the 50\% and 90\% prediction intervals of a model.
-
-```{r}
-captiontitle <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany."
-caption <- "A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-label <- "fig:agg-performance-all-Germany"
-```
-
-```{r agg-performance-all-Germany, fig.cap=caption, eval = FALSE}
-# knitr::include_graphics("../analysis/plots/aggregate-performance-all-Germany-v4.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S2} \\textbf{Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland."
-caption <- "A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons"
-label <- "fig:agg-performance-all-Poland"
-```
-
-```{r agg-performance-all-Poland, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/aggregate-performance-all-Poland-v4.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S3} \\textbf{Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Visualisation of aggregate performance metrics across locations."
-caption <- "A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect).
-D: Empirical coverage of the 90\\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of WIS values."
-label <- "fig:performance-locations"
-```
-
-```{r performance-locations, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-v4.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S4} \\textbf{Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Visualisation of aggregate performance metrics across locations in relative terms."
-caption <- "A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals.
-E: Dispersion.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast.
-H.
-Standard deviation of WIS values."
-label <- "fig:performance-locations-rel"
-```
-
-```{r performance-locations-rel, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S5} \\textbf{Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Visualisation of daily report data."
-caption <- "The black line represents weekly data divided by seven. Data were last accessed through the German and Polish Forecast Hub on August 21 2021."
-label <- "fig:daily-truth"
-```
-
-```{r daily-truth, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/daily_truth.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S6} \\textbf{Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Visualisation of the absolute difference between the daily report data at the time and the data now."
-caption <- "In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added.
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
-label <- "fig:daily-truth-update"
-```
-
-```{r daily-truth-update, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/daily-data-updates.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S7} \\textbf{Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Visualisation of the relative difference between the weekly report data at the time and the data now."
-caption <- "Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application).
-Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
-label <- "fig:weekly-truth-update"
-```
-
-```{r weekly-truth-update, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/weekly-data-updates.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S8} \\textbf{Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Visualisation of forecasts and scores for one week ahead forecasts."
-caption <- "A, C: Visualisation of 50\\% prediction intervals of one week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS."
-label <- "fig:forecasts-and-truth-1"
-```
-
-```{r forecasts-and-truth-1, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/figure-forecasts-1.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S9 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- gsub(x = captiontitle, pattern = "one", replacement = "three")
-caption <- gsub(x = caption, pattern = "one", replacement = "three")
-label <- "fig:forecasts-and-truth-3"
-```
-
-```{r forecasts-and-truth-3, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/figure-forecasts-3.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S10 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- gsub(x = captiontitle, pattern = "one", replacement = "four")
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-label <- "fig:forecasts-and-truth-4"
-```
-
-```{r forecasts-and-truth-4, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/figure-forecasts-4.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S11 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Distribution of weighted interval scores for one week ahead forecasts"
-caption <- "A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets pooled across locations. B: Distribution of WIS separate by country."
-label <- "fig:distribution-scores-1"
-```
-
-```{r distribution-scores-1, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/distribution_scores_wis-1.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S12 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- gsub(x = captiontitle, pattern = "one", replacement = "three")
-caption <- gsub(x = caption, pattern = "one", replacement = "three")
-label <- gsub(x = caption, pattern = "1", replacement = "3")
-```
-
-```{r distribution-scores-3, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/distribution_scores_wis-3.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S13 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- gsub(x = captiontitle, pattern = "three", replacement = "four")
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-label <- gsub(x = caption, pattern = "3", replacement = "4")
-```
-
-```{r distribution-scores-4, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/distribution_scores_wis-4.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S14 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Distribution of model ranks (in terms of WIS) for one week ahead forecasts"
-caption <- "A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets, pooled across locations.
-B: Distribution of ranks separate by country."
-label <- "fig:distribution-scores-ranks-1"
-```
-
-```{r distribution-scores-ranks-1, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/distribution_scores_wis-1-ranks.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S15 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- gsub(x = captiontitle, pattern = "one", replacement = "two")
-caption <- gsub(x = caption, pattern = "one", replacement = "two")
-label <- gsub(x = caption, pattern = "1", replacement = "2")
-```
-
-```{r distribution-scores-ranks-2, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/distribution_scores_wis-2-ranks.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S16 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- gsub(x = captiontitle, pattern = "two", replacement = "three")
-caption <- gsub(x = caption, pattern = "two", replacement = "three")
-label <- gsub(x = caption, pattern = "2", replacement = "3")
-```
-
-```{r distribution-scores-ranks-3, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/distribution_scores_wis-3-ranks.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S17 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- gsub(x = captiontitle, pattern = "three", replacement = "four")
-caption <- gsub(x = caption, pattern = "three", replacement = "four")
-label <- gsub(x = caption, pattern = "3", replacement = "4")
-```
-
-```{r distribution-scores-ranks-4, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/distribution_scores_wis-4-ranks.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S18 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Difference in WIS between the Crowd forecast and the Hub ensemble for two week ahead forecasts."
-caption <- "Values below zero mean better performance of the Crowd forecasts."
-label <- "fig:distribution-scores-differences"
-```
-
-```{r distribution-scores-differences, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
-# knitr::include_graphics("../analysis/plots/difference-wis-crowd-ensemble.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S19 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Difference in WIS between the Crowd forecast and the Renewal model for two week ahead forecasts."
-caption <- "Values below zero mean better performance of the Crowd forecasts."
-label <- "fig:distribution-scores-differences-renewal"
-```
-
-```{r distribution-scores-differences-renewal, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon."}
-# knitr::include_graphics("../analysis/plots/difference-wis-crowd-renewal.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S20 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble."
-caption <- "“Hub-ensemble” \\textit{excludes} all our models, Hub-ensemble-all \\textit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model.
-Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions.
-For Coverage, this is an absolute difference, for other metrics this is a percentage difference.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
-label <- "fig:agg-performance-ensemble-mean"
-```
-
-```{r agg-performance-ensemble-mean, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-mean-v4.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S21} \\textbf{Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Scores for one and two week ahead forecasts for the different versions of the median ensemble."
+50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
+```
+
+```{r score-table-ensemble-2}
+table <- readRDS("../analysis/plots/table_median-ensemble_scores_2_ahead.rds")
+add_caption(table, caption)
+```
+
+```{r}
+caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
+```
+
+```{r score-table-ensemble-4}
+table <- readRDS("../analysis/plots/table_median-ensemble_scores_4_ahead.rds")
+add_caption(table, caption)
+
+```
+
+### Tables mean ensemble
+
+```{r}
 caption <- 
-  "Scores are cut to three significant digits and rounded.
-Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
-Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
-the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions).
-WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model.
-Dispersion, over-prediction and under-prediction together sum up to the weighted interval score.
-Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\% and 90\\%-coverage are the percentage of observed values that fell within the 50\\% and 90\\% prediction intervals of a model."
-label <- "tab:score-table-ensemble-2"
-```
-
-```{r score-table-ensemble-2}
-# table <- readRDS("../analysis/plots/table_median-ensemble_scores_2_ahead.rds")
-# add_caption(table, caption)
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S4} \\textbf{Table.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- gsub(x = captiontitle, pattern = "one and two", replacement = "three and four")
-caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-label <- gsub(x = label, pattern = "2", replacement = "4")
-```
-
-```{r score-table-ensemble-4}
-# table <- readRDS("../analysis/plots/table_median-ensemble_scores_4_ahead.rds")
-# add_caption(table, caption)
-
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S5 Table.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Scores for one and two week ahead forecasts for the different versions of the mean ensemble"
-caption <- 
-  "Scores are cut to three significant digits and rounded.
+  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble.
 Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets.
@@
 Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\% and 90\\%-coverage are the percentage of observed values that fell within the 50\\% and 90\\% prediction intervals of a model."
-label <- "tab:score-table-ensemble-mean-2"
+50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
 ```
@@
 ```{r score-table-ensemble-mean-2}
-# table <- readRDS("../analysis/plots/table_mean-ensemble_scores_2_ahead.rds")
-# add_caption(table, caption)
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S6 Table.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- gsub(x = captiontitle, pattern = "one and two", replacement = "three and four")
+table <- readRDS("../analysis/plots/table_mean-ensemble_scores_2_ahead.rds")
+add_caption(table, caption)
+```
+
+```{r}
 caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-label <- gsub(x = label, pattern = "2", replacement = "4")
 ```
@@
 ```{r score-table-ensemble-mean-4}
-# table <- readRDS("../analysis/plots/table_mean-ensemble_scores_4_ahead.rds")
-# add_caption(table, caption)
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S7 Table.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Visualisation of aggregate performance metrics across forecast horizons (period from December 14th 2020 on)"
-caption <- "From December 14th 2020 on, all models were available.
+table <- readRDS("../analysis/plots/table_mean-ensemble_scores_4_ahead.rds")
+add_caption(table, caption)
+```
+
+\clearpage
+
+## Sensitivity analysis
+
 In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later.
-This sensitivity analysis shows performance of all models restricted to the period from December 14 2020 until March 1st 2021 where all models were available.
+This sensitivity shows performance of all models restricted to the period from October 14 2020 until March 1st 2021 where all models were available.
+
+```{r}
+caption <- "Visualisation of aggregate performance metrics across forecast horizons only for the period from October 14th 2020 on where all models were available.
 A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
@@
 Standard deviation of all WIS values for different horizons"
-label <- "fig:agg-performance-all-late"
 ```
@@
 ```{r agg-performance-all-late, fig.cap=caption}
-# knitr::include_graphics("../analysis/plots/aggregate-performance-all-late-period-v4.png")
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S22 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- "Scores for one and two week ahead forecasts (sensitivity analysis)"
+knitr::include_graphics("../analysis/plots/aggregate-performance-all-late-period-v4.png")
+```
+
+```{r}
 caption <- 
-  "Scores are cut to three significant digits and rounded.
-In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later.
-This table shows performance of all models restricted to the period from December 14 2020 until March 1st 2021 where all models were available.
+  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021.
 Numbers in brackets show the metrics relative to the Hub ensemble (i.e.
@@
 Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict.
-50\\% and 90\\%-coverage are the percentage of observed values that fell within the 50\\% and 90\\% prediction intervals of a model."
-label <- "tab:score-table-late-2"
+50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
 ```
@@
 ```{r score-table-late-2}
-# table <- readRDS("../analysis/plots/table-late-period_2_ahead.rds")
-# add_caption(table, caption)
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S8} \\textbf{Table.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r}
-captiontitle <- gsub(x = captiontitle, pattern = "one and two", replacement = "three and four")
+table <- readRDS("../analysis/plots/table-late-period_2_ahead.rds")
+add_caption(table, caption)
+```
+
+```{r}
 caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
-label <- gsub(x = label, pattern = "2", replacement = "4")
 ```
@@
 ```{r score-table-late-4}
-# table <- readRDS("../analysis/plots/table-late-period_4_ahead.rds")
-# add_caption(table, caption)
-```
-
-```{r, results = "asis"}
-cat("\\paragraph{S9 Table.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
+table <- readRDS("../analysis/plots/table-late-period_4_ahead.rds")
+add_caption(table, caption)
+
+```
+
+\clearpage
+
+## Overview of models and forecasters
 
 ```{r table-ensemble-versions}
-```
-
-```{r, results = "asis"}
-label <- "tab:table-ensemble-versions"
-captiontitle <- "Overview of the models and ensembles used."
-caption <- ""
-
-cat("\\paragraph{S10 Table.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
+
+rbind(
+  list(
+    Name = "Hub-ensemble-realised", 
+    `Explanation` = "Official Forecast Hub median ensemble.
+Created by the Forecast Hub officially under the name 'KITCOVIDhub-median\\_ensemble' and used as the default ensemble.
+Included are our crowd forecasts as well as the renewal model (with one missed submission on December 28 2020, but not the convolution model which was deemed to similar to the renewal model."
+  ),
+  list(
+    Name = "Hub-ensemble-realised-mean", 
+    `Explanation` = "Official Forecast Hub mean ensemble. Created by the Forecast Hub officially under the name 'KITCOVIDhub-mean\\_ensemble'."
+  ),
+  list(Name = "", Explanation = ""),
+
+  list(
+    Name = "Hub-ensemble", 
+    `Explanation` = "Version of the official Hub median ensemble which excludes all our contributions."
+  ),
+  list(
+    Name = "Hub-ensemble-mean", 
+    `Explanation` = "Version of the official Hub mean ensemble which excludes all our contributions."
+  ),
+  list(
+    Name = "Hub-ensemble-with-renewal, 
+    Hub-ensemble-with-renewal-mean", 
+    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Renewal model."
+  ),
+  list(
+    Name = "Hub-ensemble-with-crowd, 
+    Hub-ensemble-with-crowd-mean", 
+    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Crowd forecast."
+  ),
+  list(
+    Name = "Hub-ensemble-with-convolution, 
+    Hub-ensemble-with-convolution-mean", 
+    `Explanation` = "Versions of the official Hub ensembles which of our contributions includes only the Convolution model (which originally was never included in any official Hub ensemble)."
+  ),
+    list(
+    Name = "Hub-ensemble-with-all, 
+    Hub-ensemble-with-all-mean", 
+    `Explanation` = "Versions of the official Hub ensembles which includes all our contributions.
+For cases, this is identical to the official Hub ensembles, but for deaths the convolution model was added."
+  ),
+
+  list(Name = "", Explanation = ""),
+  list(
+    Name = "Crowd forecast", 
+    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'"
+  ),  
+  list(
+    Name = "Renewal model", 
+    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'"
+  ),  
+  list(
+    Name = "Convolution model", 
+    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\\_secondary'"
+  )
+) %>%
+  kableExtra::kbl(format = "latex", booktabs = TRUE, 
+                  escape = FALSE,
+                  caption = "Overview of the models and ensembles used.",
+                  longtable = TRUE,
+                  linesep = c('\\addlinespace \\addlinespace')) %>%
+  kableExtra::column_spec(1, width = "4.5cm") %>%
+  kableExtra::column_spec(2, width = "11.0cm") %>%
+  kableExtra::kable_styling(latex_options = c("striped", "repeat_header")) 
 ```
@@
 ```{r num-forecasters, fig.cap="Number of participants who submitted a forecast over time."}
-# knitr::include_graphics("../analysis/plots/number-forecasters.png")
-```
-
-```{r, results = "asis"}
-captiontitle <- "Number of participants who submitted a forecast over time."
-caption <- ""
-label <- "fig:num-forecasters"
-cat("\\paragraph{S23 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
+knitr::include_graphics("../analysis/plots/number-forecasters.png")
 ```
@@
 Note that the renewal model was not included in the ensemble on December 28th 2020."}
-# knitr::include_graphics("../analysis/plots/ensemble-members.png")
-```
-
-```{r, results = "asis"}
-captiontitle <- "Number of member models in the official Hub ensemble"
-caption <- "This includes our crowd forecasts and the renewal model. Note that the renewal model was not included in the ensemble on December 28th 2020."
-label <- "fig:num-ensemble-members"
-cat("\\paragraph{S24 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-```{r compare-forecasters, fig.cap="Crowd forecasts and baseline shown in the application for a two week horizon.
-Shown are the median, as well as the 50\\% and 90\\% prediction intervals (in order of decreasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons)."}
-# knitr::include_graphics("../analysis/plots/comparison-forecast-interals.png")
-```
-
-```{r, results = "asis"}
-captiontitle <- "Crowd forecasts and baseline shown in the application for a two week horizon."
-caption <- "Shown are the median, as well as the 50\\% and 90\\% prediction intervals (in order of decreasing opacity).
-For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons)."
-label <- "fig:compare-forecasters"
-cat("\\paragraph{S25 Fig.}\n", 
-    "\\label{", label, "}\n", 
-    "\\textbf{", captiontitle, "} ", caption, 
-    sep = "")
-```
-
-\paragraph*{S1 Acknowledgmenents.}
-\textbf{Members of the CMMID COVID-19 working group}
+knitr::include_graphics("../analysis/plots/ensemble-members.png")
+```
+
+\clearpage

### 2024-01-13 manuscript/journal submission/LaTeX supplementary only/manuscript-only-supplementary.tex
committing various changes

--- 2022-08-04 manuscript/final submission/manuscript-no-plots.tex
@@
 
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{Comparing human and model-based forecasts of COVID-19 in
-Germany and
-Poland} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Nikos I. Bosse\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\textsuperscript{*},
-Sam Abbott\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Johannes Bracher\textsuperscript{\getAff{Karlsruhe Institute of
-Technology Institute of Economic Theory and Statistics}},
-Habakuk Hain\textsuperscript{\getAff{Max Planck Institute for
-Multidisciplinary Sciences}},
-Billy J. Quilty\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Mark Jit\textsuperscript{\getAff{London School of Hygiene \& Tropical
-Medicine}},
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}},
-Edwin van Leeuwen\textsuperscript{\getAff{UK Health Security
-Agency}, \getAff{London School of Hygiene \& Tropical Medicine}},
-Anne Cori\textsuperscript{\getAff{Imperial College London}},
-Sebastian Funk\textsuperscript{\getAff{London School of Hygiene \&
-Tropical Medicine}}\\
-\bigskip
-\textbf{\getAff{London School of Hygiene \& Tropical Medicine}}London
-School of Hygiene \& Tropical Medicine, Keppel Street, London WC1E7HT,
-United Kingdom\\
-\textbf{\getAff{Karlsruhe Institute of Technology Institute of Economic
-Theory and Statistics}}Karlsruhe Institute of Technology - Institute of
-Economic Theory and Statistics, Post Box 6980, 76049 Karlsruhe,
-Germany\\
-\textbf{\getAff{Max Planck Institute for Multidisciplinary Sciences}}Max
-Planck Institute for Multidisciplinary Sciences, Am Faßberg 11, 37077
-Göttingen, Germany\\
-\textbf{\getAff{UK Health Security Agency}}UK Health Security Agency,
-London NW9 5EQ, United Kingdom\\
-\textbf{\getAff{Imperial College London}}Imperial College London,
-Norfolk Place, London W2 1PG, United Kingdom\\
-\bigskip
-* Corresponding author: nikos.bosse@lshtm.ac.uk\\
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-Forecasts based on epidemiological modelling have played an important
-role in shaping public policy throughout the COVID-19 pandemic. This
-modelling combines knowledge about infectious disease dynamics with the
-subjective opinion of the researcher who develops and refines the model
-and often also adjusts model outputs. Developing a forecast model is
-difficult, resource- and time-consuming. It is therefore worth asking
-what modelling is able to add beyond the subjective opinion of the
-researcher alone. To investigate this, we analysed different real-time
-forecasts of cases of and deaths from COVID-19 in Germany and Poland
-over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
-We compared crowd forecasts elicited from researchers and volunteers,
-against a) forecasts from two semi-mechanistic models based on common
-epidemiological assumptions and b) the ensemble of all other models
-submitted to the Forecast Hub. We found crowd forecasts, despite being
-overconfident, to outperform all other methods across all forecast
-horizons when forecasting cases (weighted interval score relative to the
-Hub ensemble 2 weeks ahead: 0.89). Forecasts based on computational
-models performed comparably better when predicting deaths (rel. WIS
-1.26), suggesting that epidemiological modelling and human judgement can
-complement each other in important ways.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step.
-% Author Summary not valid for PLOS ONE submissions.
-\section*{Author summary}
-Mathematical models of COVID-19 have played a key role in informing
-governments across the world. While mathematical models are informed by
-our knowledge of infectious disease dynamics, they are ultimately
-developed and iteratively adjusted by the researchers and shaped by
-their subjective opinions. To investigate what modelling is able to add
-beyond the subjective opinion of the researcher alone, we compared human
-forecasts with model-based predictions of COVID-19 cases and deaths
-submitted to the so-called German/Polish Forecast Hub (which collates a
-variety of models from a range of teams). \textbar{} We found that our
-human forecasts consistently outperformed an aggregate of all available
-model-based forecasts when predicting cases, but not when predicting
-deaths. Our findings suggest that human insight may be most valuable
-when forecasting highly uncertain quantities, which depend on many
-factors that are hard to model using equations, while mathematical
-models may be most useful in settings like predicting deaths, where
-leading indicators with a clear connection to the target variable are
-available. This potentially has very relevant policy implications, as
-agencies informing policy-makers could benefit from routinely eliciting
-human forecasts in addition to model-based predictions to inform
-policies.
-
-\linenumbers
-
-% Use "Eq" instead of "Equation" for equation citations.
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Infectious disease modelling has a long tradition and has helped inform
-public health decisions both through scenario modelling, as well as
-actual forecasts of (among others) influenza {[}e.g. 1,2--4{]}, dengue
-fever {[}e.g. 5,6,7{]}, ebola {[}e.g. 8,9{]}, chikungunya {[}e.g.
-10,11{]} and now COVID-19 {[}e.g. 12,13--17{]}. Applications of
-epidemiological models differ in the way they make statements about the
-future. Forecasts aim to predict the future as it will occur, while
-scenario modelling and projections aim to represent what the future
-could look like under certain scenario assumptions or if conditions
-stayed the same as they were in the past. Forecasts can be judged by
-comparing them against observed data. Since it is much harder to fairly
-assess the accuracy and usefulness of projections and scenario modelling
-in the same way, this work focuses on forecasts, which represent only a
-subset of all epidemiological modelling.
-
-Since March 2020, forecasts of COVID-19 from multiple teams have been
-collected, aggregated and compared by Forecast Hubs such as the US
-Forecast Hub {[}13,14{]}, the German and Polish Forecast Hub {[}15,16{]}
-and the European Forecast Hub {[}17{]}. Often, different individual
-forecasts are combined into a single forecast, e.g.~by taking the mean
-or median of all forecasts. These ensemble forecasts usually tend to
-perform better and more consistently than individual forecasts (see e.g.
-{[}6{]}; {[}18{]}).
-
-Individual computational models usually rely to varying degrees on
-mechanistic assumptions about infectious disease dynamics (such as
-SIR-type compartmental models that aim to represent how individuals move
-from being susceptible to infected and then recovered or dead). Some are
-more statistical in nature (such as time series models that detect
-statistical patterns without explicitly modelling disease dynamics). How
-exactly such a mathematical or computational model is constructed and
-which assumptions are made depends on subjective opinion and judgement
-of the researcher who develops and refines the model. Models are
-commonly adjusted and improved based on whether the model output looks
-plausible to the researchers involved.
-
-The process of model construction and refinement is laborious and
-time-consuming, and it is therefore worth asking what modelling can add
-beyond the subjective judgment of the researcher alone. In this work, we
-ask this question specifically in the context of predictive performance,
-and set aside other advantages of epidemiological modelling (such as
-reproducibility or the ability to obtain a deeper fundamental
-understanding of how diseases spread). One natural way to do this is to
-compare the predictive performance of forecasts based on computational
-models (``model-based forecasts'') against forecasts made by individual
-humans without explicit use of a computer model (``direct human
-forecasts'') or a combination of multiple such forecasts (``crowd
-forecasts'').
-
-Previous work has examined such direct human forecasts in various
-contexts, such as geopolitics {[}19,20{]}, meta-science {[}21,22{]},
-sports {[}23{]} and epidemiology {[}11,24,25{]}. Several prediction
-platforms {[}26--28{]} and prediction markets {[}29{]} have been created
-to collate expert and non-expert predictions. However, with the notable
-exception of {[}11{]}, these forecasts were not designed to be evaluated
-alongside model-based forecasts and usually follow their own (often
-binary) prediction formats. Direct human forecasts may be able to take
-into account insights and relationships between variables which are hard
-to specify using epidemiological models. However, it is not entirely
-clear in which situations human forecasts perform well or badly. For
-example, {[}11{]} found that humans could outperform computer models at
-predicting the 2014/15 and 2015/16 flu season in the US, a setting where
-the disease was well known and information about previous seasons was
-available. However, humans tended to do slightly worse at predicting the
-2014/15 outbreak of chikungunya in the Americas, a disease previously
-largely unobserved and unknown in these regions at the time.
-
-In this study, we analyse the performance of direct human forecasts
-relative to model-based forecasts and discuss the added benefit of
-epidemiological modelling over human judgement alone. As a case study,
-we use different forecasts, involving varying degrees of human
-intervention, which we submitted in real time to the German and Polish
-Forecast Hub. In contrast to {[}11{]} we elicited not only point
-predictions, but full predictive distributions (``probabilistic
-forecasts'', see e.g. {[}30{]}) from participants. This allows us to
-compare not only predictive accuracy, but also how well human
-forecasters and model-based forecasts were able to quantify forecast
-uncertainty.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-We created and submitted the following forecasts to the German and
-Polish Forecast Hub: 1) a direct human forecast (henceforth called
-``crowd forecast''), elicited from participants through a web
-application {[}31{]} and 2) two semi-mechanistic model-based forecasts
-(``renewal model'' and ``convolution model'') informed by basic
-assumptions about COVID-19 epidemiology. While the two semi-mechanistic
-forecasts were necessarily shaped by our implicit assumptions and
-decisions, they were designed such as to minimise the amount of human
-intervention involved. For example, we refrained from adjusting model
-outputs or refining the models based on past performance. Forecasts were
-created in real time over a period of 21 weeks from October 12th 2020
-until March 1st 2021 and submitted to the German and Polish Forecast hub
-{[}15,16{]}. All code and tools necessary to generate the forecasts and
-make a forecast submission are available in the
-\texttt{covid.german.forecasts} R package {[}32{]}. This repository also
-contains a record of all forecasts submitted to the German and Polish
-Forecast Hub. Forecasts were evaluated using a variety of scoring
-metrics and compared among each other and against an ensemble of all
-other models submitted to the German and Polish Forecast Hub.
-
-\hypertarget{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}{%
-\subsection{Forecast targets and interaction with the German and Polish
-Forecast
-Hub}\label{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}}
-
-The German and Polish Forecast Hub (now mostly merged into the {[}17{]})
-elicits predictions for various COVID-19 related forecast targets from
-different research groups every week. Forecasts had to be made every
-Monday (with submissions allowed until Tuesday 3pm) and were permitted
-to use any data that was available by Monday 11.59pm. We submitted
-forecasts for incident and cumulative weekly reported numbers of cases
-of and deaths from COVID-19 on a national level in Germany and Poland
-over a one to four week forecast horizon. Forecasts were submitted on
-Mondays, but weeks were defined as ending on a Saturday (and starting on
-Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26
-days. Submissions were required in a quantile-based format with 23
-quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10,
-0.15, \ldots, 0.95, 0.975, 0.99. Forecasts submitted to the Forecast Hub
-were combined into different ensembles every week, with the median
-ensemble (i.e., the \(\alpha\)-quantile of the ensemble is given by the
-median of all submitted \(\alpha\)-quantiles) being the default ensemble
-shown on all official Forecast hub visualisations
-(https://kitmetricslab.github.io/forecasthub/forecast).
-
-Data on daily reported test positive cases and deaths linked to COVID-19
-were provided by the organisers of the German and Polish Forecast hub.
-Until December 14th, 2020, these data were sourced from the European
-Centre for Disease Control {[}33{]}. After ECDC stopped publishing daily
-data, observations were sourced from the Robert Koch Institute (RKI) and
-the Polish Ministry of Health for the remainder of the submission period
-{[}34{]}. These data are subject to reporting artefacts, (such as for
-example delayed case reporting in Poland on the 24th November,
-{[}35{]}), changes in reporting over time, and variation in testing
-regimes (for example in Germany from the 11th of November on, {[}36{]}).
-The ECDC data as well as the data published by the Polish Ministry of
-Health were also subject to data revisions, although most of them (with
-a notable exception of a data update for October 12 2020 in Germany)
-only affected daily, not weekly data (see Figures
-\ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).
-
-\hypertarget{crowd-forecasts}{%
-\subsection{Crowd forecasts}\label{crowd-forecasts}}
-
-Our crowd forecasts were created as an ensemble of forecasts made by
-individual participants every week through a web application
-(https://cmmid-lshtm.shinyapps.io/crowd-forecast/). Weekly forecasts had
-to be submitted before Tuesday 12pm every week, but participants were
-asked to only use any information or data that was already available by
-Monday night. The application was built using the \texttt{shiny} and
-\texttt{golem} R packages {[}37,38{]} and is available in the
-\texttt{crowdforecastr} R package {[}31{]}. To make a forecast in the
-application participants could select a predictive distribution (with
-the default being log-normal) to represent the probability that the
-forecasted quantity took certain values. Median and width of the
-uncertainty could be adjusted by either interacting with a figure
-showing their forecast or providing numerical values (see screenshot in
-Figure \ref{fig:screenshot} in the SI). The default shown was a
-repetition of the last known observation with constant uncertainty
-around it computed as the standard deviation of the last four changes in
-weekly log observed forecasts (i.e.~as
-\(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
-A comparison of the crowd forecasts against the default baseline shown
-in the application is displayed in Figure \ref{fig:compare-forecasters}
-in the Appendix. Our interface also allowed participants to view past
-observations based on the hub data, as well as their forecasts, on a
-logarithmic scale and presented additional contextual COVID-19 data
-sourced from {[}39{]}. These data included, for example, notifications
-of both test positive COVID-19 cases and COVID-19 linked deaths and the
-number of COVID-19 tests conducted over time. From November 26 2020 on
-we displayed weekly small reports with a visualisation of past forecasts
-and scores on our website, epiforecasts.io.
-
-Forecasts were stored in a Google Sheet and downloaded, cleaned and
-processed every week for submission to the Forecast Hub. If a forecaster
-had submitted multiple predictions for a single target, only the latest
-submission was kept. Information on the chosen distribution as well as
-the parameters for median and width were used to obtain the required set
-of 23 quantiles from that distribution. Forecasts from all forecasters
-were then aggregated using an unweighted quantile-wise mean (i.e., the
-\(\alpha\)-quantile of the ensemble is given by the mean of all
-submitted \(\alpha\)-quantiles). To avoid issues with users trying out
-the app and submitting a random forecast, we required that a forecaster
-needed to make a forecast for at least two targets for a given forecast
-in order to be included in the crowd forecast ensemble. On a few
-occasions we deleted forecasts that were clearly the result of a user or
-software error (such as for example forecasts that were zero
-everywhere).
-
-individual forecasts were assessed as clearly erroneous by visual
-inspection and subsequently removed before aggregation and were excluded
-from the submission as well as the analysis.
-
-Participants were recruited mostly within the Centre of Mathematical
-Modeling of Infectious Diseases at the London School of Hygiene \&
-Tropical Medicine, but participants were also invited personally or via
-social media to submit predictions. Depending on whether they had a
-background in either statistics, forecasting or epidemiology,
-participants were asked to self-identify as `experts' or `non-experts'.
-
-The study was approved by the Observational / Interventions Research
-Ethics Committee at the London School of Hygiene \& Tropical Medicine,
-LSHTM Ethics Reference: 22290. Formal consent from participants was
-taken in written form through the web application.
-
-\hypertarget{model-based-forecasts}{%
-\subsection{Model-based forecasts}\label{model-based-forecasts}}
-
-We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R
-package (version 1.3.3) as our model-based forecasts {[}40{]}. The first
-of these models, here called ``renewal model'', used the renewal
-equation {[}41{]} to predict reported cases and deaths (see details in
-the SI). It estimated the effective reproduction number \(R_t\) (the
-average number of people each person infected at time t is expected to
-infect in turn) and modelled future infections as a weighted sum of past
-infection multiplied by \(R_t\). \(R_t\) was assumed to stay constant
-beyond the forecast date, roughly corresponding to continuing the latest
-exponential trend in infections. On the 9th of November we altered the
-date when \(R_t\) was assumed to be constant from two weeks prior to the
-date of the forecast to the forecast date, which we found to yield a
-more stable \(R_t\) estimate. Reported case and death notifications were
-obtained by convolving predicted infections over data-based delay
-distributions {[}40,42--44{]} to model the time between infection and
-report date. The renewal model was used to predict cases as well as
-deaths with forecasts being generated for each target separately. Death
-forecasts from the renewal model were therefore not informed by past
-cases. One submission of the renewal model on December 28th 2020 was
-delayed and therefore not included in the official Forecast hub
-ensemble.
-
-The second model (``convolution model'', see details in SI) was only
-used to forecast deaths and was added later, starting December 7th 2020
-(with the first forecast from December 7th suffering from a software bug
-and therefore disregarded in all further analyses). The convolution
-model was submitted, but never included in the official Forecast hub
-ensemble due to concerns that it could be too similar to the renewal
-model. The convolution model predicted deaths as a fraction of infected
-people who would die with some delay, by using a convolution of reported
-cases with a distribution that described the delay from case report to
-death and a scaling factor (the case-fatality ratio). Both the renewal
-and the convolution model used daily observations and assumed a negative
-binomial observation model with a multiplicative day-of-the-week effect
-{[}40{]}.
-
-Line list data used to inform the prior for the delay from symptom onset
-to test positive case report or death in the model-based forecasts was
-sourced from {[}45{]} with data available up to the 1st of August. All
-model fitting was done using Markov-chain Monte Carlo (MCMC) in stan
-{[}46{]} with each location and forecast target being fitted separately.
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-For the main analysis we focused mostly on two week ahead forecasts, as
-COVID-19 forecasts, especially for cases, were in the past found to have
-poor predictive performance beyond this horizon {[}15{]}. Forecasts for
-cases were scored using the full period from October 2020 until March
-2021. To ensure comparability between models, all death forecasts were
-scored using only the period from December 14th on, where all models
-including the convolution model were available. To ensure robustness of
-our results we conducted a sensitivity analysis where all forecasts
-(including cases) were scored only over the later period for which all
-forecasts were available (see Section \ref{sensitivity-analysis} in the
-SI). Results remained broadly unchanged.
-
-Forecasts were analysed using the following scoring metrics: The
-weighted interval score (WIS) {[}47{]}, the absolute error, relative
-bias, and empirical coverage of the 50\% and 90\% prediction intervals.
-The WIS is a proper scoring rule {[}48{]}, meaning that in expectation
-the score is optimised by reporting a predictive distribution that is
-identical to the true data-generating distribution. Forecasters are
-therefore incentivised to report their true belief about the future. The
-WIS can be understood as a generalisation of the absolute error to
-quantile-based forecasts (also meaning that smaller values are better)
-and can be decomposed into three separate penalties: forecast spread
-(i.e.~uncertainty of forecasts), over-prediction and under-prediction.
-While the over- and under-prediction components of the WIS capture the
-amount of over-prediction and under-prediction in absolute terms, we
-also look at a relative tendency to make biased forecasts. The bias
-metric {[}9{]} we use captures how much probability mass of the forecast
-was above or below the true value (mapped to values between -1 and 1)
-and therefore represents a general tendency to over- or under-predict in
-relative terms. A value of -1 implies that all quantiles of the
-predictive distribution are below the observed value and a value of 1
-that all quantiles are above the observed value. Empirical coverage is
-the percentage of observed values that fall inside a given prediction
-interval (e.g.~how many observed values fall inside all 50\% prediction
-intervals). Scoring metrics are explained in more detail in Table
-\ref{tab:scoring-metrics} in the SI. All scores were calculated using
-the \texttt{scoringutils} R package {[}49{]}.
-
-At all stages of the evaluation our forecasts were compared to the
-median ensemble of all \emph{other} models submitted to the German and
-Polish Forecast Hub (``Hub ensemble''). This ``Hub ensemble'' was
-retrospectively computed and excludes all our models, leaving on average
-five ensemble member models (see details in Section
-\ref{contributions-hub}, as well as in Table
-\ref{tab:table-ensemble-versions} and Figure
-\ref{fig:num-ensemble-members} in the SI). What we call ``Hub ensemble''
-in this article therefore differs from the ``official Hub ensemble''
-(here called ``hub-ensemble-realised'') which included crowd forecasts
-as well as renewal model forecasts. To enhance interpretability of
-scores we mainly report WIS relative to the Hub ensemble in the main
-text, i.e.~we divided the average scores for a given model by the
-average score achieved by the Hub ensemble on the same set of forecasts
-(with values \textgreater1 implying worse and values \textless1 implying
-better performance than the Hub ensemble). In addition to comparing our
-forecasts against the hub ensemble excluding our models, we also
-assessed the impact of our forecasts on the performance of the
-forecasting hub by recalculating separate versions of the Hub ensemble
-with only some (or all) of our forecasts included. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{crowd-forecast-participation}{%
-\subsection{Crowd forecast
-participation}\label{crowd-forecast-participation}}
-
-A total number of 32 participants submitted forecasts, 17 of those
-self-identified as `expert' in either forecasting or epidemiology. The
-median number of forecasters for any given forecast target was 6, the
-minimum 2 and the maximum 10. The mean number of submissions from an
-individual forecaster was 4.7 but the median number was only one - most
-participants dropped out after their first submission. Only two
-participants submitted a forecast every single week, both of whom are
-authors on this study.
-
-\begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} 
-\caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future.
-A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons.
-WIS is decomposed into its components dispersion, over-prediction and under-prediction.
-C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect).
-D: Empirical coverage of the 90\% prediction intervals.
-E: Dispersion (same as in panel A, B).
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- or underpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast (lower is better).
-H.
-Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all}
-\end{figure}
-
-\begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} 
-\caption{Two week ahead forecasts and corresponding scores.
-A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values.
-Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out.
-B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth}
-\end{figure}
-
-\hypertarget{case-forecasts}{%
-\subsection{Case Forecasts}\label{case-forecasts}}
-
-For cases, crowd forecasts had a lower mean weighted interval score
-(WIS, lower values indicate better performance) than both the renewal
-model and the Hub ensemble across all forecast horizons (Figure
-\ref{fig:agg-performance-all}A) and locations (Figure
-\ref{fig:performance-locations-rel}A). For two week ahead forecasts,
-mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts
-and 1.40 for the renewal model (Table \ref{tab:score-table-2}). Across
-all forecasting approaches, locations and forecast horizons, the
-distribution of WIS values was very right-skewed, and average
-performance was heavily influenced by outliers (Figure
-\ref{fig:distribution-scores}). Overall, low variance in forecast
-performance was closely linked with good mean performance (Figures
-\ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A),
-suggesting that the ability to avoid large errors was an important
-factor in determining overall performance. The impact of outlier values
-was especially pronounced for the renewal model, which had more outliers
-(Figure \ref{fig:distribution-scores}), as well as the highest standard
-deviation of WIS values (standard deviation of the WIS relative to the
-WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon),
-while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub
-ensemble (= 1) showed more stable performance.
-
-To varying degrees, all forecasts exhibited trend-following behaviour
-and were rarely able to predict a change in trend before it had
-happened. For example, all forecasts failed to predict the change in
-trend from increase to decrease that happened in November in Germany and
-severely overshot reported cases (Figure
-\ref{fig:forecasts-and-truth}A). This was most striking for the renewal
-model, which extrapolated unconstrained exponential growth based on the
-recent past of observations. The Hub ensemble and the crowd forecast,
-which had both been under-predicting throughout October, also failed to
-predict the change in trend after cases peaked, but less severely so.
-Human forecasters, possibly aware of the semi-lockdown announced on
-November 2nd 2020 {[}50{]} and the change in the testing regime (with
-stricter test criteria) on November 11th 2020 {[}36{]}, were fastest to
-adapt to the new trend, and the Hub ensemble slowest. In December, cases
-rose again in Germany, with all models under-predicting this growth to
-varying extents. As in October, the renewal model captured the phase of
-exponential growth in cases slightly better than other approaches, but
-again overshot when reported case numbers fell over Christmas. The large
-variance in predictions in January in Germany (severe under-prediction
-followed by severe over-prediction) may in part be caused by the fact
-that the renewal model operated on daily data and therefore was
-susceptible to fluctuations in daily reporting around Christmas that
-would not have influenced on weekly reporting. Similar trends in
-performance were evident in Poland, with the crowd forecast quickest at
-adapting to the change in trend in November. In general, there were
-fewer large outlier forecasts in Poland and in particular the renewal
-model performed more in line with other forecasts there.
-
-All forecasting approaches, including the Hub ensemble, were
-overconfident, i.e.~they showed lower than nominal coverage (meaning
-that 50\% (90\%) prediction intervals generally covered less than 50\%
-(90\%) of the actually observed values) (Figure
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D).
-Coverage for all forecasts deteriorated with increasing forecast
-horizon, indicating that all forecasting approaches struggled to
-quantify uncertainty appropriately for case forecasts. This was
-especially an issue for crowd forecasts, which had markedly shorter
-prediction intervals (i.e., narrower and more confident predictive
-distributions) than other approaches (Figure
-\ref{fig:agg-performance-all}E) and only showed a small increase in
-uncertainty across forecast horizons. The crowd forecasts prediction
-intervals were also noticeably narrower than the default baseline shown
-to forecasters in the application (see Figure
-\ref{fig:compare-forecasters}).
-
-In spite of good performance in terms of the absolute error (Figure
-\ref{fig:agg-performance-all}G), the narrow forecast intervals led to
-forecasts which were severely overconfident (covering only 36\% and 55\%
-of all observations with the 50\% and 90\% prediction intervals of all
-forecasts made at a two week forecast horizon, and only 5\% and 38\%
-four weeks ahead) (Figure \ref{fig:agg-performance-all}C,D and Tables
-\ref{tab:score-table-2} and \ref{tab:score-table-4}). Despite worse
-performance in terms of absolute error (Figure
-\ref{fig:agg-performance-all}G), the renewal model achieved better
-calibration (comparable to the Hub ensemble), as uncertainty increased
-rapidly across forecast horizons. The crowd forecasts, on the other
-hand, showed a smaller bias than the renewal model, but were
-overconfident.
-
-The renewal model exhibited a noticeable tendency towards
-over-predicting reported cases across all horizons. The crowd forecast
-tended to over-predict at longer forecast horizons, whereas the Hub
-ensemble showed no systematic bias (Figure
-\ref{fig:agg-performance-all}F). Regardless of a general relative
-tendency to over-predict, all forecasting approaches incurred larger
-absolute penalties from over- than from under-prediction (see
-decomposition of the WIS into absolute penalties for over-prediction,
-under-prediction and dispersion in Figures
-\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).
-
-Generally, trends in overall performance were broadly similar across
-locations (Figures \ref{fig:performance-locations} and
-\ref{fig:performance-locations-rel}). Due to the differing population
-sizes and numbers of notifications in Germany and Poland absolute scores
-were difficult to compare directly. However, relative to the Hub
-ensemble, the crowd forecasts performed noticeably better in Germany
-than in Poland and the renewal model better in Poland than in Germany
-(Figures \ref{fig:performance-locations-rel}A,
-\ref{fig:performance-locations-rel}G,
-\ref{fig:agg-performance-all-Germany},
-\ref{fig:agg-performance-all-Poland}).
-
-\hypertarget{death-forecasts}{%
-\subsection{Death Forecasts}\label{death-forecasts}}
-
-For deaths, the Hub ensemble outperformed the crowd forecasts as well as
-our model-based approaches across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B). Relative WIS values for the models
-two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1
-(Hub ensemble) and 1.79 (renewal model). The crowd forecasts performed
-better than the renewal model across all forecast horizons and locations
-(Figure \ref{fig:agg-performance-all}B, Figure
-\ref{fig:performance-locations}B), and also better than the convolution
-model three and four weeks ahead. Poor performance of the renewal model,
-especially at longer horizons, indicates that an approach that does not
-know about past cases, but instead estimates and projects a separate
-\(R_t\) trace from deaths, does not use the available information
-efficiently. The convolution model was able to outperform both the
-renewal model and the crowd forecasts at shorter forecast horizons
-(where the delay between cases and deaths means that future deaths are
-largely informed by present cases), but saw performance deteriorate at
-three and four weeks ahead (where case predictions from the renewal
-model were increasingly used to inform death predictions) (Figure
-\ref{fig:agg-performance-all}B, Table \ref{tab:score-table-4}).
-
-As past cases and hospitalisations can be used as predictors, predicting
-a change in trend may be easier for deaths than for cases. Even though
-all forecasts generally struggled with this, there were some instances
-where changing trends were well captured or even anticipated. In Poland,
-for example, the Hub ensemble was able to capture or even anticipate the
-peak in deaths in December quite well (whereas the renewal model and
-crowd forecast did not). The renewal model, which mostly exhibited
-trend-following behaviour, correctly predicted another increase in
-weekly deaths in mid-January (potentially based on changes in daily
-deaths, as the renewal model did not know about past cases). In Germany
-in early January, all models predicted a decrease in deaths two to three
-weeks before it actually happened. Predictions from the renewal model at
-that time were likely strongly influenced by an unexpected drop in
-reported deaths in December. The other forecasting approaches and in
-particular, the convolution model may have been affected by potentially
-under-reported case numbers around Christmas. When the decrease that all
-models had predicted to happen in early January failed to materialise,
-the renewal model and the crowd forecast noticeably over-corrected and
-over-predicted deaths in the following weeks, while the Hub ensemble,
-and to a slightly lesser degree, the convolution model were able to
-capture the downturn well when it finally happened at the end of
-January.
-
-Death forecasts, generally, showed greater coverage of the 50\% and 90\%
-prediction intervals than case forecasts and no decrease in coverage
-across forecast horizons, indicating that it might be easier to
-appropriately quantify uncertainty for death forecasts. The Hub ensemble
-had the greatest coverage, with empirical coverage of the 50\% and 90\%
-prediction intervals exceeding 50\%, and 90\%, respectively, across all
-forecast horizons. Coverage for the crowd forecasts and our model-based
-approaches was generally lower than that of the Hub ensemble and mostly
-slightly lower than nominal coverage (Figure
-\ref{fig:agg-performance-all}C and \ref{fig:agg-performance-all}D). As
-for cases, the crowd forecast tended to have the narrowest prediction
-intervals and uncertainty increased most slowly across forecast
-horizons, and the renewal model forecasts generally were widest. The
-convolution model had relatively narrow prediction intervals for short
-forecast horizons, but had rapidly (and non-linearly) increasing
-uncertainty for longer forecast horizons, driven by increasing
-uncertainty in the underlying case forecasts.
-
-For deaths, the ensemble of crowd forecasts had a consistent tendency to
-over-predict \ref{fig:agg-performance-all}F. The convolution model had a
-strong tendency to under-predict, with the magnitude of under-prediction
-steadily decreasing for longer forecast horizons. The renewal model
-(which over-predicted for cases) and the Hub ensemble slightly tended
-towards under-prediction. For deaths, absolute over- and
-under-prediction penalties were more in line with a general relative
-tendency to over- or under-predict than for cases (Figure
-\ref{fig:agg-performance-all}A, \ref{fig:agg-performance-all}B and
-Tables \ref{tab:score-table-2}, \ref{tab:score-table-4}).
-
-\begin{figure}[H]
-% \includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2} 
-\caption{Distribution of scores.
-A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
-Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores.}\label{fig:distribution-scores}
-\end{figure}
-
-\begin{figure}[H]
-% \includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-v4}
-\caption{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.
-“Hub-ensemble”    extit{excludes} all our models, Hub-ensemble-all    extit{includes} all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model.
-A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance).
-C, D: Empirical coverage of the 50\% and 90\% prediction intervals minus empirical coverage observed for the Hub ensemble.
-E: Dispersion relative to the dispersion of the Hub ensemble.
-Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score.
-F: Bias, i.e.
-general (relative) tendency to over- orunderpredict.
-Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally.
-G: Absolute error of the median forecast relative to the Hub ensemble.
-H.
-Standard deviation of all WIS values for different horizons relative to the Hub ensemble.}\label{fig:agg-performance-ensemble-rel}
-\end{figure}
-
-\hypertarget{contributions-hub}{%
-\subsection{Contribution to the Forecast Hub}\label{contributions-hub}}
-
-Of our three models, only the renewal model and the crowd forecast were
-included in the official Forecast Hub median ensemble
-(``hub-ensemble-realised''), while the convolution model was never
-included as it was deemed too similar to the existing renewal model. In
-the official Hub ensemble, there were on average 7.1 models included
-(including our own), with a median of 7, a minimum of 4 (on 28 December
-2020 over the Christmas period) and a maximum of 10. Versions that
-included either all of our models (``hub-ensemble-with-all'') or only
-one of them (``hub-ensemble-with-X'') were computed retrospectively. An
-overview of all models and ensemble versions is shown in Table
-\ref{tab:table-ensemble-versions} in the SI.
-
-For cases, our contributions (compared to the Hub ensemble without our
-contributions) consistently improved performance across all forecasting
-horizons (rel. WIS 0.9 two weeks ahead, Table
-\ref{tab:score-table-ensemble-2}). Contributions from the crowd
-forecasts alone also improved performance of the Hub ensemble across all
-forecast horizons, while contributions from the renewal model had a
-negative effect for longer horizons (rel. WIS 1.02 three weeks ahead,
-1.06 four weeks ahead). The realised ensemble including both models
-performed better or equal compared to all versions with only one model
-included for up to three weeks ahead, suggesting synergistic effects.
-Only for predictions four weeks ahead would removing the renewal model
-have improved performance (Table \ref{tab:score-table-ensemble-4}). The
-realised ensemble performed comparably to the crowd forecasts for
-predictions one to two weeks ahead, and worse for greater forecast
-horizons.
-
-For deaths, contributions from the renewal model and crowd forecast
-together improved performance only for one week ahead predictions and
-showed an increasingly negative impact on performance for longer
-horizons (rel. WIS of the Hub-ensemble-realised 1.01 two weeks ahead,
-1.05 four weeks ahead, Tables \ref{tab:score-table-ensemble-2} and
-\ref{tab:score-table-ensemble-4}). Individual contributions from both
-the renewal model and the crowd forecast were largely negative, while a
-version of the Hub ensemble with only the convolution model included
-would have performed consistently better across all forecast horizons
-(with the positive impact increasing for longer horizons). This is
-especially interesting as the convolution model performed consistently
-worse than the pre-existing Hub ensemble (Figure
-\ref{fig:agg-performance-all}) and especially worse for longer horizons.
-
-We also considered the impact of our contributions on a version of the
-Hub ensemble constructed by taking the quantile-wise mean, rather than
-the median. General trends were similar, with the notable exception of
-the convolution model, which had a consistently positive impact on the
-median ensemble, but a mixed and mostly slightly negative impact on the
-mean ensemble (Figures \ref{fig:agg-performance-ensemble-rel}B and
-\ref{fig:agg-performance-ensemble-mean}B). This may happen if a model is
-more correct directionally relative to the pre-existing ensemble, but
-overshoots in absolute terms, thereby moving the ensemble too far. For
-both the mean and the median ensemble, changes in performance from
-adding or removing models were of a similar order of magnitude,
-suggesting that at least in this instance, with a relatively small
-ensemble size, the median ensemble was not necessarily more `robust' to
-changes than the mean ensemble. However, the ensemble version with all
-our forecasts included (``hub-ensemble-with-all'') tended to perform
-relatively better for the median ensemble than the mean ensemble,
-suggesting that adding more models may be more beneficial or `safer' for
-the median than for the mean ensemble as directional errors can more
-easily cancel out than errors in absolute terms.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Epidemiological forecasting modelling combines knowledge about
-infectious disease dynamics with the subjective opinion of the
-researcher who develops and refines the model. In this study, we
-compared forecasts of cases of and deaths from COVID-19 in Germany and
-Poland based purely on human judgement and elicited from a crowd of
-researchers and volunteers against forecasts from two semi-mechanistic
-epidemiological models. In spite of the small number of participants and
-a general tendency to be overconfident, crowd forecasts consistently
-outperformed our epidemiological models as well as the Hub ensemble when
-forecasting cases but not when forecasting deaths. This suggests that
-humans might be relatively good at foreseeing trends that are hard to
-model but may struggle to form an intuition for the exact relationship
-between cases and deaths.
-
-Past studies have evaluated the performance of model-based forecasting
-approaches as well as human experts and non-experts in various contexts.
-However, most of these studies either focused only on the evaluation of
-(expert-tuned) model-based approaches {[}e.g. 12,13,14{]}, or
-exclusively on human forecasts {[}19,20,24,25{]}. In contrast, we
-directly compared human and model-based forecasts. This is similar to
-the approach taken by {[}11{]}, but extends it in several ways. While
-Farrow et al.~only asked for point predictions and constructed a
-predictive distribution from these, we asked participants to provide a
-full predictive distribution, allowing us to compare human forecasts and
-models without any further assumptions, as well as to analyse how humans
-quantified their uncertainty. In addition, we compared crowd forecasts
-to two semi-mechanistic models informed by basic epidemiological
-knowledge of COVID-19, allowing us to assess not only relative
-performance but also to analyse qualitative differences between human
-judgement and model-based insight. In terms of interpretability of the
-results, exact knowledge of our two models, as well as focus on a
-limited set of targets and locations was a major advantage of our study
-compared to larger studies conducted by the Forecast Hubs
-{[}12--15,17{]}.
-
-The strong performance of crowd forecasts in our study is in line with
-results from Farrow et al.~who also report strong performance of human
-predictions in past Flu challenges despite difficulties to recruit a
-large number of participants. The advantage of crowd forecasts we
-observed over our semi-mechanistic models is likely in part explained by
-the fact that we compared an ensemble of crowd forecasts with single
-models. However, this probably explains only part of the difference, and
-performance relative to the Hub ensemble strongly suggests that human
-insight is valuable when forecasting highly volatile and potentially
-hard-to-predict quantities such as case numbers. One potential
-explanation is that humans can have access to data that is not available
-to or hard to integrate into model-based forecasts. Relatively good
-performance of our semi-mechanistic models short-term, but not
-longer-term, suggests that model-based forecasts are helpful to
-extrapolate from current conditions, but require some form of human
-intervention or additional assumptions to inform forecasts when
-conditions change over time. This human intervention may be particularly
-important when dealing with artefacts in reporting and data anomalies
-(and especially when using daily, rather than weekly data). The large
-variance in predictions in January in Germany for example (severe
-under-prediction followed by severe over-prediction, see Figure
-\ref{fig:forecasts-and-truth}A), may in part be caused by the fact that
-the renewal model operated on daily data and therefore was susceptible
-to fluctuations in daily reporting which have less of an influence on
-weekly reporting.
-
-Our results suggest that human intervention may be less beneficial when
-forecasting deaths (especially at shorter horizons, when deaths are
-largely dependent on already observed cases), which benefits from the
-ability to model the delays and exact epidemiological relationships
-between different leading and lagged indicators. Relatively good
-performance of the convolution model, especially compared to the poor
-performance of the renewal model on deaths (which used only deaths to
-estimate and predict the effective reproduction number) underlines the
-importance of including leading indicators such as cases as a predictor
-for deaths.
-
-Given the low number of participants in our study, it is difficult to
-generalise conclusions about crowd predictions to other settings. Using
-R shiny as a platform for the web application arguably created some
-limits to user experience and performance, influencing the number of
-participants and potentially creating a self-selection effect.
-Motivating forecasters to contribute regularly proved challenging,
-especially given that the majority of our participants were from the UK
-and may not have been familiar with all relevant details of the
-situation in Germany and Poland. On the other hand, R shiny facilitated
-quick development and allowed us to provide our crowd forecasting
-tooling as an open source R package, meaning that it is available for
-others to use, for example in settings like early-stage outbreaks where
-model-based forecasts are not available. In light of the relatively
-small number of Hub ensemble models, performance of the Hub ensemble is
-also difficult to generalise. More research is needed to replicate these
-findings and investigate how crowd forecasts compare against the types
-of models and model ensembles policy makers use to inform their
-decisions.
-
-Our work suggests that crowd forecasts and model-based forecasts could
-have different strengths and may be able to complement each other. When
-choosing a suitable approach for a given task it is important to take
-into account how the output will be used. In this work we focused on
-forecasts (which aim to predict future data points whilst accounting for
-all factors that might influence them), whereas policy makers might be
-more interested in projections (which show what would happen in the
-absence of any events that could change the trend) or scenario
-modelling. Forecasts may not be a suitable basis for informing policy
-decisions, if forecasters already have factored in the expectation of a
-future intervention. Model-based approaches can be either forecasts or
-projections depending on the assumptions, whereas eliciting projections
-that are not influenced by implicit assumptions about the future from
-humans may be harder.
-
-Further work should explore the effects of humans refining their
-mathematical models or changing model outputs in more detail.
-Model-based forecasts could be used as an input to human judgement, with
-researchers adjusting predictions generated by models. Seeing a
-model-based forecast could help humans calibrate uncertainty better,
-while allowing for manual intervention to adapt spurious trend
-predictions. Tools need to be developed to facilitate this process at a
-larger scale. Human insight could also be used as an input to models.
-Such a `hybrid' forecasting approach could for example ask humans to
-predict the trend of the effective reproduction number \(R_t\) or the
-doubling rate (i.e.~how the epidemic evolves) into the future and use
-this to estimate the exact number of cases, hospitalisations or deaths
-this would imply. In light of severe overconfidence, yet good
-performance in terms of the absolute error, post-processing of human
-forecasts to adjust and widen prediction intervals may be another
-promising approach. Crowd forecasting in general could benefit greatly
-from the availability of tools suitable to appeal to a greater audience.
-Given the good performance we and previous authors observed in spite of
-the limited resources available and the small number of participants,
-this seems worthwhile to further develop and explore.
-
-\clearpage
-
-\textbf{Acknowledgements}
-
-NIB received funding from the Health Protection Research Unit (grant
-code NIHR200908, https://www.nihr.ac.uk/). SA's work was funded by the
-Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/). The work
-of JB was supported by the Helmholtz Foundation
-(https://www.helmholtz.de/) via the SIMCARD Information and Data Science
-Pilot Project. This research was partly funded by the National Institute
-for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 \&
-16/136/46) using UK aid from the UK Government to support global health
-research. The views expressed in this publication are those of the
-author(s) and not necessarily those of the NIHR or the UK Department of
-Health and Social Care. BJQ is supported in part by a grant from the
-Bill and Melinda Gates Foundation (OPP1139859,
-https://www.gatesfoundation.org/). EvL acknowledges funding by the
-National Institute for Health Research (NIHR) Health Protection Research
-Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908,
-https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research
-and innovation programme - project EpiPose (101003688,
-https://ec.europa.eu/programmes/horizon2020/). AC acknowledges funding
-by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/),
-and the Academy of Medical Sciences (https://acmedsci.ac.uk/). SF's work
-was supported by the Wellcome Trust (grant: 210758/Z/18/Z,
-https://wellcome.org/), and the NIHR (NIHR200908,
-https://www.nihr.ac.uk/).
-
-We thank all forecasters who participated in this study for their
-contribution.
-
-We would also like to acknowledge (in a randomised order) the members of
-Centre for the Mathematical Modelling of Infectious Diseases COVID-19
-Working Group at the the London School of Hygiene \& Tropical Medicine:
-Oliver Brady, Katharine Sherratt, Kaja Abbas, Kerry LM Wong, Charlie
-Diamond, Katherine E. Atkins, Rein M G J Houben, Jiayao Lei, Rachel
-Lowe, David Simons, Sophie R Meakin, Nicholas G. Davies, Timothy W
-Russell, Kevin van Zandvoort, Quentin J Leclerc, Kathleen O'Reilly,
-Stéphane Hué, Alicia Rosello, Emilie Finch, C Julian Villabona-Arenas,
-Thibaut Jombart, W John Edmunds, Yalda Jafari, Jack Williams, Alicia
-Showering, Damien C Tully, Jon C Emery, Carl A B Pearson, David Hodgson,
-Frank G Sandmann, Petra Klepac, Adam J Kucharski, Graham Medley, Yang
-Liu, Simon R Procter, Emily S Nightingale, William Waites, Rosanna C
-Barnard, Joel Hellewell, Yung-Wai Desmond Chan, Fiona Yueqian Sun,
-Hamish P Gibbs, Rosalind M Eggo, Lloyd A C Chapman, Stefan Flasche,
-James W Rudge, Akira Endo, Naomi R Waterlow, Paul Mee, James D Munday,
-Ciara V McCarthy, Mihaly Koltai, Amy Gimma, Christopher I Jarvis, Megan
-Auzenbergs, Matthew Quaife, Fabienne Krauer, Samuel Clifford, Georgia R
-Gore-Langton, Arminder K Deol, Kiesha Prem, Gwenan M Knight, Rachael
-Pung, Anna M Foss.
-
-\clearpage
-
 \setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../crowd-forecast/Screenshot-forecasting-app} 
+\includegraphics[width=1\linewidth,]{../../../crowd-forecast/Screenshot-forecasting-app} 
 \caption{Screenshot of the crowdforecasting app used to elicit predictions (made in June 2021). }\label{fig:screenshot}
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Germany-v4}
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/aggregate-performance-all-Germany-v4}
 \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-Poland-v4}
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/aggregate-performance-all-Poland-v4}
 \caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-v4}
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/aggregate-performance-2-weeks-locations-all-v4}
 \caption{Visualisation of aggregate performance metrics across locations.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4}
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/aggregate-performance-2-weeks-locations-all-rel-v4}
 \caption{Visualisation of relative aggregate performance metrics across locations.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/daily_truth} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/daily_truth} 
 \caption{Visualisation of daily report data.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/daily-data-updates}
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/daily-data-updates}
 \caption{Visualisation of the absolute difference between the daily report data at the time and the data now.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/weekly-data-updates}
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/weekly-data-updates}
 \caption{Visualisation of the relative difference between the weekly report data at the time and the data now.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-1} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/figure-forecasts-1.png} 
 \caption{A, C: Visualisation of 50\% prediction intervals of one week ahead forecasts against the reported values.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-3} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/figure-forecasts-3} 
 \caption{A, C: Visualisation of 50\% prediction intervals of three week ahead forecasts against the reported values.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-4} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/figure-forecasts-4} 
 \caption{A, C: Visualisation of 50\% prediction intervals of four week ahead forecasts against the reported values.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/distribution_scores_wis-1} 
 \caption{A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/distribution_scores_wis-3} 
 \caption{A: Distribution of weighted interval scores for three week ahead forecasts of the different models and forecast targets.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/distribution_scores_wis-4} 
 \caption{A: Distribution of weighted interval scores for four week ahead forecasts of the different models and forecast targets.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-1-ranks} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/distribution_scores_wis-1-ranks} 
 \caption{A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-2-ranks} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/distribution_scores_wis-2-ranks} 
 \caption{A: Distribution of the ranks (determined by the weighted interval score) for two week ahead forecasts of the different models and forecast targets.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-3-ranks} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/distribution_scores_wis-3-ranks} 
 \caption{A: Distribution of the ranks (determined by the weighted interval score) for three week ahead forecasts of the different models and forecast targets.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/distribution_scores_wis-4-ranks} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/distribution_scores_wis-4-ranks} 
 \caption{A: Distribution of the ranks (determined by the weighted interval score) for four week ahead forecasts of the different models and forecast targets.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-ensemble} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/difference-wis-crowd-ensemble} 
 \caption{Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences}
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/difference-wis-crowd-renewal} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/difference-wis-crowd-renewal} 
 \caption{Density plot with the difference in WIS between the Crowd forecast and the Renewal model (values below zero mean better performance of the Crowd forecasts) for a 2 week ahead forecast horizon.}\label{fig:distribution-scores-differences-renewal}
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-rel-ensemble-mean-v4}
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/aggregate-performance-rel-ensemble-mean-v4}
 \caption{Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-late-period-v4}
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/aggregate-performance-all-late-period-v4}
 \caption{Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/number-forecasters} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/number-forecasters} 
 \caption{Number of participants who submitted a forecast over time.}\label{fig:num-forecasters}
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/ensemble-members} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/ensemble-members} 
 \caption{Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble.
@@
 \begin{figure}[H]
-%\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} 
+\includegraphics[width=1\linewidth,]{../../../analysis/plots/comparison-forecast-interals}
 \caption{Crowd forecasts and baseline shown in the application for a two week horizon.
@@
 
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{McGowan CJ, Biggerstaff M, Johansson M, Apfeldorf KM,
-Ben-Nun M, Brooks L, et al. Collaborative efforts to forecast seasonal
-influenza in the {United States}, 2015--2016. Scientific Reports.
-2019;9: 683.
-doi:\href{https://doi.org/10.1038/s41598-018-36361-9}{10.1038/s41598-018-36361-9}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichCollaborativeMultiyearMultimodel2019}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Reich NG, Brooks LC, Fox SJ, Kandula S, McGowan CJ,
-Moore E, et al. A collaborative multiyear, multimodel assessment of
-seasonal influenza forecasting in the {United States}. PNAS. 2019;116:
-3146--3154.
-doi:\href{https://doi.org/10.1073/pnas.1812594116}{10.1073/pnas.1812594116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Shaman J, Karspeck A. Forecasting seasonal outbreaks of
-influenza. PNAS. 2012;109: 20425--20430.
-doi:\href{https://doi.org/10.1073/pnas.1208772109}{10.1073/pnas.1208772109}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-biggerstaffResultsCentersDisease2016}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Biggerstaff M, Alper D, Dredze M, Fox S, Fung IC-H,
-Hickmann KS, et al. Results from the centers for disease control and
-prevention's predict the 2013--2014 {Influenza Season Challenge}. BMC
-Infectious Diseases. 2016;16: 357.
-doi:\href{https://doi.org/10.1186/s12879-016-1669-x}{10.1186/s12879-016-1669-x}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak
-AL, Baugher B, et al. An open challenge to advance probabilistic
-forecasting for dengue epidemics. PNAS. 2019;116: 24268--24274.
-doi:\href{https://doi.org/10.1073/pnas.1909865116}{10.1073/pnas.1909865116}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Yamana TK, Kandula S, Shaman J. Superensemble forecasts
-of dengue outbreaks. Journal of The Royal Society Interface. 2016;13:
-20160410.
-doi:\href{https://doi.org/10.1098/rsif.2016.0410}{10.1098/rsif.2016.0410}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Colón-González FJ, Bastos LS, Hofmann B, Hopkin A,
-Harpham Q, Crocker T, et al. Probabilistic seasonal dengue forecasting
-in {Vietnam}: {A} modelling study using superensembles. PLOS Medicine.
-2021;18: e1003542.
-doi:\href{https://doi.org/10.1371/journal.pmed.1003542}{10.1371/journal.pmed.1003542}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Viboud C, Sun K, Gaffey R, Ajelli M, Fumanelli L, Merler
-S, et al. The {RAPIDD} ebola forecasting challenge: {Synthesis} and
-lessons learnt. Epidemics. 2018;22: 13--21.
-doi:\href{https://doi.org/10.1016/j.epidem.2017.08.002}{10.1016/j.epidem.2017.08.002}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Funk S, Camacho A, Kucharski AJ, Lowe R, Eggo RM,
-Edmunds WJ. Assessing the performance of real-time epidemic forecasts:
-{A} case study of {Ebola} in the {Western Area} region of {Sierra
-Leone}, 2014-15. PLOS Computational Biology. 2019;15: e1006785.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1006785}{10.1371/journal.pcbi.1006785}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Del Valle SY, McMahon BH, Asher J, Hatchett R, Lega JC,
-Brown HE, et al. Summary results of the 2014-2015 {DARPA Chikungunya}
-challenge. BMC Infectious Diseases. 2018;18: 245.
-doi:\href{https://doi.org/10.1186/s12879-018-3124-7}{10.1186/s12879-018-3124-7}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Farrow DC, Brooks LC, Hyun S, Tibshirani RJ, Burke DS,
-Rosenfeld R. A human judgment approach to epidemiological forecasting.
-PLOS Computational Biology. 2017;13: e1005248.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1005248}{10.1371/journal.pcbi.1005248}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Funk S, Abbott S, Atkins BD, Baguelin M, Baillie JK,
-Birrell P, et al. Short-term forecasts to inform the response to the
-{Covid-19} epidemic in the {UK}. medRxiv. 2020; 2020.11.11.20220962.
-doi:\href{https://doi.org/10.1101/2020.11.11.20220962}{10.1101/2020.11.11.20220962}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerCOVID19ForecastHub2020}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K,
-et al. {COVID-19 Forecast Hub}: 4 {December} 2020 snapshot. {Zenodo};
-2020.
-doi:\href{https://doi.org/10.5281/zenodo.3963371}{10.5281/zenodo.3963371}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A,
-Rivadeneira AJC, et al. Evaluation of individual and ensemble
-probabilistic forecasts of {COVID-19} mortality in the {US}. medRxiv.
-2021; 2021.02.03.21250974.
-doi:\href{https://doi.org/10.1101/2021.02.03.21250974}{10.1101/2021.02.03.21250974}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. Short-term forecasting of {COVID-19} in {Germany}
-and {Poland} during the second wave -- a preregistered study. medRxiv.
-2021; 2020.12.24.20248826.
-doi:\href{https://doi.org/10.1101/2020.12.24.20248826}{10.1101/2020.12.24.20248826}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherNationalSubnationalShortterm2021}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Bracher J, Wolffram D, Deuschel J, Görgen K, Ketterer
-JL, Ullrich A, et al. National and subnational short-term forecasting of
-{COVID-19} in {Germany} and {Poland}, early 2021. 2021;
-2021.11.05.21265810.
-doi:\href{https://doi.org/10.1101/2021.11.05.21265810}{10.1101/2021.11.05.21265810}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-europeancovid-19forecasthubEuropeanCovid19Forecast2021}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{European Covid-19 Forecast Hub. European {Covid-19
-Forecast Hub}. 2021 {[}cited 30 May 2021{]}. Available:
-\url{https://covid19forecasthub.eu/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reichAccuracyRealtimeMultimodel2019}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Reich NG, McGowan CJ, Yamana TK, Tushar A, Ray EL,
-Osthus D, et al. Accuracy of real-time multi-model ensemble forecasts
-for seasonal influenza in the {U}.{S}. PLOS Computational Biology.
-2019;15: e1007486.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1007486}{10.1371/journal.pcbi.1007486}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Tetlock PE, Mellers BA, Rohrbaugh N, Chen E. Forecasting
-{Tournaments}: {Tools} for {Increasing Transparency} and {Improving} the
-{Quality} of {Debate}. Curr Dir Psychol Sci. 2014;23: 290--295.
-doi:\href{https://doi.org/10.1177/0963721414534257}{10.1177/0963721414534257}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Atanasov P, Rescober P, Stone E, Swift SA,
-Servan-Schreiber E, Tetlock P, et al. Distilling the {Wisdom} of
-{Crowds}: {Prediction Markets} vs. {Prediction Polls}. Management
-Science. 2016;63: 691--706.
-doi:\href{https://doi.org/10.1287/mnsc.2015.2374}{10.1287/mnsc.2015.2374}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers E-J. Laypeople
-{Can Predict Which Social-Science Studies Will Be Replicated
-Successfully}. Advances in Methods and Practices in Psychological
-Science. 2020;3: 267--285.
-doi:\href{https://doi.org/10.1177/2515245920919667}{10.1177/2515245920919667}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-replicationmarketsReplicationMarketsReliable2020}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{ReplicationMarkets. Replication {Markets} -- {Reliable}
-research replicates\ldots you can bet on it. 2020 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.replicationmarkets.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Servan-Schreiber E, Wolfers J, Pennock DM, Galebach B.
-Prediction {Markets}: {Does Money Matter}? Electronic Markets. 2004;14:
-243--251.
-doi:\href{https://doi.org/10.1080/1019678042000245254}{10.1080/1019678042000245254}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{McAndrew TC, Reich NG. An expert judgment model to
-predict early stages of the {COVID-19} outbreak in the {United States}.
-medRxiv. 2020; 2020.09.21.20196725.
-doi:\href{https://doi.org/10.1101/2020.09.21.20196725}{10.1101/2020.09.21.20196725}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Recchia G, Freeman ALJ, Spiegelhalter D. How well did
-experts and laypeople forecast the size of the {COVID-19} pandemic? PLOS
-ONE. 2021;16: e0250935.
-doi:\href{https://doi.org/10.1371/journal.pone.0250935}{10.1371/journal.pone.0250935}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Metaculus. A {Preliminary Look} at {Metaculus} and
-{Expert Forecasts}. 22 Jun 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.metaculus.com/news/2020/06/02/LRT/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hypermindHypermindSupercollectiveIntelligence2021}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Hypermind. Hypermind \textbar{} {Supercollective}
-intelligence for decision makers. {Hypermind}; 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.hypermind.com/en/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-csetforetellCSETForetell2021}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{CSET Foretell. {CSET Foretell}. 2021 {[}cited 13 Oct
-2021{]}. Available: \url{https://www.cset-foretell.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-predictitPredictIt2021}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{PredictIt. {PredictIt}. 2021 {[}cited 13 Oct 2021{]}.
-Available: \url{https://www.predictit.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Held L, Meyer S, Bracher J. Probabilistic forecasting in
-infectious disease epidemiology: The 13th {Armitage} lecture. Statistics
-in Medicine. 2017;36: 3443--3460.
-doi:\href{https://doi.org/10.1002/sim.7363}{10.1002/sim.7363}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Crowdforecastr: Eliciting crowd forecasts in r shiny. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618519}{10.5281/zenodo.4618519}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S.
-Covid.german.forecasts: Forecasting covid-19 related metrics for the
-german/poland forecast hub. 2020. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-ecdcDownloadHistoricalData2020}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{ECDC. Download historical data (to 14 {December} 2020)
-on the daily number of new reported {COVID-19} cases and deaths
-worldwide. {European Centre for Disease Prevention and Control}; 14 Dec
-2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rkiRKICoronavirusSARSCoV22021}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{RKI. {RKI} - {Coronavirus SARS-CoV-2} - {Aktueller
-Lage-}/{Situationsbericht} des {RKI} zu {COVID-19}. 2021 {[}cited 30 May
-2021{]}. Available:
-\url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-forsal.plRozbieznosciStatystykachKoronawirusa2020}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Forsal.pl. Rozbieżności w statystykach koronawirusa. 22
-tys. przypadków będą doliczone do ogólnej liczby wyników. 2020 {[}cited
-30 May 2021{]}. Available:
-\url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Ärzteblatt DÄG Redaktion Deutsches.
-SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an. {Deutsches
-Ärzteblatt}; 3 Nov 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Fay C, Guyader V, Rochette S, Girard C. Golem: A
-framework for robust shiny applications. 2021. Available:
-\url{https://github.com/ThinkR-open/golem}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie
-Y, et al. Shiny: Web application framework for r. 2021. Available:
-\url{https://CRAN.R-project.org/package=shiny}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ourworldindataCOVID19DataExplorer2020}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Our World in Data. {COVID-19 Data Explorer}. {Our World
-in Data}; 2020 {[}cited 30 May 2021{]}. Available:
-\url{https://ourworldindata.org/coronavirus-data-explorer}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epinow2}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{Abbott S, Hellewell J, Hickson J, Munday J, Gostic K,
-Ellis P, et al. EpiNow2: Estimate real-time case counts and time-varying
-epidemiological parameters. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957489}{10.5281/zenodo.3957489}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fraserEstimatingIndividualHousehold2007}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Fraser C. Estimating {Individual} and {Household
-Reproduction Numbers} in an {Emerging Epidemic}. PLOS ONE. 2007;2: e758.
-doi:\href{https://doi.org/10.1371/journal.pone.0000758}{10.1371/journal.pone.0000758}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epiforecasts.ioux2fcovidCovid19TemporalVariation2020}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{epiforecasts.io/covid. Covid-19: {Temporal} variation in
-transmission during the {COVID-19} outbreak. {Covid-19}; 2020 {[}cited
-30 May 2021{]}. Available: \url{https://epiforecasts.io/covid/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sherrattExploringSurveillanceData2021}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Sherratt K, Abbott S, Meakin SR, Hellewell J, Munday JD,
-Bosse N, et al. Exploring surveillance data biases when estimating the
-reproduction number: With insights into subpopulation transmission of
-{Covid-19} in {England}. 2021; 2020.10.18.20214585.
-doi:\href{https://doi.org/10.1101/2020.10.18.20214585}{10.1101/2020.10.18.20214585}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abbottEstimatingTimevaryingReproduction2020a}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs
-HP, Bosse NI, et al. Estimating the time-varying reproduction number of
-{SARS-CoV-2} using national and subnational case counts. 2020 {[}cited
-14 Oct 2021{]}.
-doi:\href{https://doi.org/10.12688/wellcomeopenres.16006.1}{10.12688/wellcomeopenres.16006.1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kraemer2020epidemiological}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Xu B, Gutierrez B, Hill S, Scarpino S, Loskill A, Wu J,
-et al. Epidemiological data from the nCoV-2019 outbreak: Early
-descriptions from publicly available data. 2020. Available:
-\url{http://virological.org/t/epidemiological-data-from-the-ncov-2019-outbreak-early-descriptions-from-publicly-available-data/337}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rstan}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Stan Development Team. RStan: The r interface to stan.
-2020. Available: \url{http://mc-stan.org/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Bracher J, Ray EL, Gneiting T, Reich NG. Evaluating
-epidemic forecasts in an interval format. PLoS Comput Biol. 2021;17:
-e1008618.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1008618}{10.1371/journal.pcbi.1008618}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Gneiting T, Raftery AE. Strictly proper scoring rules,
-prediction, and estimation. Journal of the American Statistical
-Association. 2007;102: 359--378.
-doi:\href{https://doi.org/10.1198/016214506000001437}{10.1198/016214506000001437}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-scoringutils}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{Bosse NI, Abbott S, EpiForecasts, Funk S. Scoringutils:
-Utilities for scoring and assessing predictions. 2020.
-doi:\href{https://doi.org/10.5281/zenodo.4618017}{10.5281/zenodo.4618017}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-deutschewelleCoronavirusGermanyImpose2020}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Deutsche Welle. Coronavirus: {Germany} to impose
-one-month partial lockdown \textbar{} {DW} \textbar{} 28.10.2020. 2020
-{[}cited 29 Jun 2021{]}. Available:
-\url{https://www.dw.com/en/coronavirus-germany-to-impose-one-month-partial-lockdown/a-55421241}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-generationinterval}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Ganyani T, Kremer C, Chen D, Torneri A, Faes C, Wallinga
-J, et al. Estimating the generation interval for coronavirus disease
-(COVID-19) based on symptom onset data, march 2020. Eurosurveillance.
-2020;25. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-incubationperiod}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith
-HR, et al. The incubation period of coronavirus disease 2019 (COVID-19)
-from publicly reported confirmed cases: Estimation and application.
-Annals of Internal Medicine. 2020;172: 577--582. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-covidregionaldata}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Abbott S, Sherratt K, Bevan J, Gibbs H, Hellewell J,
-Munday J, et al. Covidregionaldata: Subnational data for the covid-19
-outbreak. -. 2020;-: --.
-doi:\href{https://doi.org/10.5281/zenodo.3957539}{10.5281/zenodo.3957539}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-EvaluatingUseReproduction}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Evaluating the use of the reproduction number as an
-epidemiological tool, using spatio-temporal trends of the {Covid-19}
-outbreak in {England} \textbar{} {medRxiv}. {[}cited 30 May 2021{]}.
-Available:
-\url{https://www.medrxiv.org/content/10.1101/2020.10.18.20214585v1}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-approxGP}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Riutort-Mayol G, Bürkner P-C, Andersen MR, Solin A,
-Vehtari A. Practical hilbert space approximate bayesian gaussian
-processes for probabilistic programming. 2020. Available:
-\url{https://arxiv.org/abs/2004.11408}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epidemia}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Scott JA, Gandy A, Mishra S, Unwin J, Flaxman S, Bhatt
-S. Epidemia: Modeling of epidemics using hierarchical bayesian models.
-2020. Available:
-\url{https://imperialcollegelondon.github.io/epidemia/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bhattSemiMechanisticBayesianModeling}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Bhatt S, Ferguson N, Flaxman S, Gandy A, Mishra S, Scott
-JA. Semi-{Mechanistic Bayesian} modeling of {COVID-19} with {Renewal
-Processes}. : 14. }
-
-\end{CSLReferences}
-
-\nolinenumbers
-
 \end{document}

### 2024-01-13 manuscript/manuscript.Rmd
committing various changes

@@
 ```{r}
+captiontitle <- "Distribution of scores. "
+caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
+Points denote single forecasts scores, while the shaded area shows an estimated probability density.
+B: Distribution of WIS separate by country.
+Black squares indicate median and black circles mean scores."
+label <- "fig:distribution-scores"
+```
+
+```{r distribution-scores, fig.cap=caption, eval = FALSE}
+# knitr::include_graphics("../analysis/plots/distribution_scores_wis-2.png")
+```
+
+```{r, results = "asis"}
+cat("\\begin{figure}[H]\n", 
+    "\\caption{\\bf{", captiontitle, "}}\n", 
+    caption, "\n",
+    "\\label{", label, "}\n", 
+    "\\end{figure}", sep = "")
+```
+
+```{r}
 captiontitle <- "Two week ahead forecasts and corresponding scores. "
@@
 For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (\nameref{tab:score-table-2} Table).
-Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers.
+Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (see Fig \ref{fig:distribution-scores}).
 Overall, low variance in forecast performance was closely linked with good mean performance (Fig \ref{fig:agg-performance-all}H and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance.
@@
 For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Fig \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B, as well as \nameref{tab:score-table-2} and \nameref{tab:score-table-4}s).
-
-```{r}
-captiontitle <- "Distribution of scores. "
-caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
-Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores."
-label <- "fig:distribution-scores"
-```
-
-```{r distribution-scores, fig.cap=caption, eval = FALSE}
-# knitr::include_graphics("../analysis/plots/distribution_scores_wis-2.png")
-```
-
-```{r, results = "asis"}
-cat("\\begin{figure}[H]\n", 
-    "\\caption{\\bf{", captiontitle, "}}\n", 
-    caption, "\n",
-    "\\label{", label, "}\n", 
-    "\\end{figure}", sep = "")
-```
 

### 2024-01-13 manuscript/manuscript.tex
committing various changes

--- 2022-09-07 manuscript/manuscript.tex
@@
 \begin{figure}[H]
+\caption{\bf{Distribution of scores. }}
+A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
+Points denote single forecasts scores, while the shaded area shows an estimated probability density.
+B: Distribution of WIS separate by country.
+Black squares indicate median and black circles mean scores.
+\label{fig:distribution-scores}
+\end{figure}
+
+\begin{figure}[H]
 \caption{\bf{Two week ahead forecasts and corresponding scores. }}
@@
 locations and forecast horizons, the distribution of WIS values was very
-right-skewed, and average performance was heavily influenced by
-outliers. Overall, low variance in forecast performance was closely
-linked with good mean performance (Fig \ref{fig:agg-performance-all}H
-and \ref{fig:agg-performance-all}A), suggesting that the ability to
-avoid large errors was an important factor in determining overall
-performance. The impact of outlier values was especially pronounced for
-the renewal model, which had more outliers, as well as the highest
-standard deviation of WIS values (standard deviation of the WIS relative
-to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead
-horizon), while the ensemble of crowd forecasts (rel. WIS sd 0.76) and
-the Hub ensemble (= 1) showed more stable performance.
+right-skewed, and average performance was heavily influenced by outliers
+(see Fig \ref{fig:distribution-scores}). Overall, low variance in
+forecast performance was closely linked with good mean performance (Fig
+\ref{fig:agg-performance-all}H and \ref{fig:agg-performance-all}A),
+suggesting that the ability to avoid large errors was an important
+factor in determining overall performance. The impact of outlier values
+was especially pronounced for the renewal model, which had more
+outliers, as well as the highest standard deviation of WIS values
+(standard deviation of the WIS relative to the WIS sd of the Hub
+ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of
+crowd forecasts (rel. WIS sd 0.76) and the Hub ensemble (= 1) showed
+more stable performance.
 
@@
 \begin{figure}[H]
-\caption{\bf{Distribution of scores. }}
-A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets.
-Points denote single forecasts scores, while the shaded area shows an estimated probability density.
-B: Distribution of WIS separate by country.
-Black squares indicate median and black circles mean scores.
-\label{fig:distribution-scores}
-\end{figure}
-
-\begin{figure}[H]
 \caption{\bf{Relative aggregate performance metrics across forecast horizons for different versions of the Hub median ensemble.}}
